### 2012-01-23 rules/rules11.tex
Draft rules and call documents

\documentclass[12pt]{article}
\usepackage{times}
\usepackage{fullpage}
\usepackage{url}
\usepackage{epsf}

\newcommand{\akey}[1]{\textbf{#1}}

\begin{document}

\date{}

\title{Satisfiability Modulo Theories Competition (SMT-COMP) 2011: Rules and 
Procedures
}

% [morgan] do our own layout of authors; the four-author layout spacing
% was screwed up...
\def\doauthor#1{{%
  \hsize.5\hsize \advance\hsize by-1cm %
  \def\\{\hss\egroup\hbox to\hsize\bgroup\strut\hss}%
  \vbox{\hbox to\hsize\bgroup\strut\hss#1\hss\egroup}}}%

\def\header#1{\medskip\noindent\textbf{#1}}

\author{
Roberto Bruttomesso\\
Computer Science\\
USI, Lugano (Switzerland)
\and
Morgan Deters \\
Computer Science \\
New York University \\
\and
Alberto Griggio\\
ES Division\\
FBK, Trento (Italy)
}

\maketitle

\def\eg{\textit{e.g.}}
\def\ie{\textit{i.e.}}

\section{Introduction}
\label{sec:intro}

The annual Satisfiability Modulo Theories Competition~(SMT-COMP) is
held to spur advances in SMT solver implementations on benchmark
formulas of practical interest.  Public competitions are a well-known
means of stimulating advancement in software tools.  For example, in
automated reasoning, the CASC and SAT competitions for first-order and
propositional reasoning tools, respectively, have spurred significant
innovation in their fields~\cite{PSS02,leberre+03}.  More information
on the history and motivation for SMT-COMP can be found at the
SMT-COMP web site, \url{www.smtcomp.org}, and in reports on previous
competitions~(\cite{SMTCOMP-2008,BDOS08,SMTCOMP-FMSD,SMTCOMP-JAR}).
SMT-COMP 2011 is affiliated with the 23nd International
Conference on Computer Aided Verification~(CAV).

The rest of this document, updated from the last year's
version\footnote{Earlier versions of this document include contributions from
Clark Barrett, Albert Oliveras, and Aaron Stump.},
describes the rules and competition procedures for SMT-COMP~2011.
The principal change from last year's version is:

\begin{itemize}
\item the introduction of an ``application track,'' based on incremental
      model-checking queries, to promote the integration of SMT solvers
      within actual verification frameworks;
%\item updates to the benchmark selection algorithm, to reduce
%      overwhelming a competition division with a single ``family'' of
%      benchmarks.
% rb 25/3: see later
%\item updates to the difficulty calculation;
%\item a track for parallel solvers, to run before the regular competition.
%\item 5 random ``check'' benchmarks will be generated using Robert
%  Brummayer's SMT fuzzing tool, after all the solvers are uploaded.
%  These will be included in the competition, to help promote attention
%  to the problem of solver correctness (cf.~\cite{brummayer+09}).
\end{itemize}

\section{Entrants}
\label{sec:entrants}

\header{Solver format.} %
An entrant to SMT-COMP is an SMT solver
submitted using the SMT-Exec service.  SMT-Exec enables members of the
SMT research community to run solvers on jobs consisting of benchmarks
from the SMT-LIB benchmark library.  Jobs are run on a 12-node computer
cluster purchased with funds from a National Science Foundation
Computing Research Infrastructure grant.  SMT-Exec is provided free of
charge, but it does require a minimal registration, which verifies an
email address and prevents misuse of the service.  Registered users
may then upload their own solvers to run, or may run public solvers
already uploaded to SMT-Exec.  SMT-Exec provides a variety of tabular
and graphical displays of results of solver executions, for
comparison. For the main (sequential-solver)
% rb 23/3: I guess also application track runs on 
% the same clusters as sequential
and application tracks 
of SMT-COMP 2011, SMT-Exec will be configured so that jobs are run on a 64-bit,
uniprocessor Linux kernel.  For the parallel-solver track, SMT-Exec
will be configured so that jobs are run on a 64-bit, multiprocessor
Linux kernel.\footnote{This year, the competition may take
  advantage of off-site computing resources not normally part of
  SMT-Exec; please stay tuned to the SMT-COMP mailing list for final
  details regarding the effective SMT-COMP 2011 competition cluster.}

For participation in SMT-COMP, a solver must be
uploaded as a ``competition'' solver via the usual SMT-Exec upload
mechanism, or, alternatively, a previously-uploaded solver may be
marked as a ``competition'' solver.  In either case, \emph{uploads
must be marked for competition before the deadline;} uploading a solver
to SMT-Exec is not sufficient for competition entry if it's not marked
as being a competition entrant.  The md5 checksums of competition
submissions will be public immediately after the deadline for competition
entry has passed to ensure transparency, and the submissions themselves
will be made public after the competition.  Source code need not be
provided.  However, in order to encourage sharing of source code, extra
recognition will be given to solvers providing source code distributions
including recognition for the top such solver in each division.  See
SMT-Exec~(\url{www.smtexec.org}) for instructions on uploading solvers, as well
as machine specifications.

\header{System description.} %
As part of their submission via SMT-Exec,
SMT-COMP entrants must also include a short (1--2 pages) description of
the system.  This should include a list of all authors of the system
and their present institutional affiliations.  The programming
language(s) and basic SMT solving approach employed should be
described (\eg, lazy integration of a Nelson-Oppen combination with
SAT, translation to SAT, etc.).  System descriptions are encouraged to
include a URL for a web site for the submitted tool, but this is
optional.  System descriptions must also include a 32-bit unsigned
integer.  These numbers, collected from all submissions, are used
to seed the pseudo-random benchmark selection algorithm, as well
as the benchmark scrambler.

The SMT-Exec upload system will ask for the system description and
the random seed when a solver is marked for competition, so
their inclusion in the uploaded archive itself is optional.

\header{Other systems.} %
As in previous years, due to limitations on
computational resources, the organizers reserve the right not to
accept multiple versions of the same solver (defined as sharing 50\%
or more of its source code).  The organizers reserve the right to
submit their own systems, or other systems of interest, to the
competition.

\header{Wrapper tools.} %
A \emph{wrapper tool} is defined as any tool
which calls an SMT solver not written by the author of the wrapper
tool.  The other solver is called the \emph{wrapped tool}.  There are
several rules governing wrapper tools.  For the purposes of these rules,
multiple versions of a wrapped tool are considered different tools.
The goal of these rules is to require wrapper tools to outperform the
tools they wrap (since otherwise, there is no apparent quantitative
way to argue that the wrapper tool improves upon the wrapped tool).

\begin{itemize}
\item The name of the wrapper tool must end with ``+name'', where name
is the name of the wrapped tool (\eg\ ``Flash+CVC3'' for a tool
wrapping CVC3).

\item If the wrapped tool is from last year's SMT-COMP or earlier, then for
each division entered by the wrapper tool, if the wrapper tool does not place ahead, according to the scoring
rules below, of last year's winner in that division, it will be disqualified
from that division (but not necessarily from the whole competition).

\item If the wrapped tool was released after last year's SMT-COMP,
then the wrapper tool can be entered only if

\begin{itemize}
\item Permission has been given by the author of the wrapped tool

\item The wrapped tool is submitted and entered in every division
      in which the wrapper tool is entered.
\end{itemize}

For each division entered by the wrapper tool, if the wrapper tool
does not place ahead of the wrapped tool in that division, it will be
disqualified from that division.
\end{itemize}

\header{Attendance.} %
As with previous SMT-COMPs, submitters of an SMT-COMP entrant need not 
be physically present at the competition to
participate or win.

\subsection*{Deadlines} %

\paragraph{Main competition track.} %
SMT-COMP entries must be submitted via SMT-Exec by 7pm, Eastern U.S.
time, July~9th, 2011.  At that time the SMT-Exec service will be
closed to the public to prepare for the competition, with the
exception that resubmissions of existing entries will be accepted
until 7pm, Eastern U.S. time, July~11th, 2011.  We strongly encourage
participants to use this two day grace period \emph{only} for the
purpose of fixing any bugs that may be discovered and not for adding
new features as there will be no opportunity to do extensive testing
using SMT-Exec after the original deadline on July~9th.

The versions that are present on SMT-Exec at the conclusion of the
grace period will be the ones used for the competition, and versions
submitted after this time will not be used.  The organizers reserve
the right to start the competition itself at any time after the open
of the New York Stock Exchange on the morning of July~12th.  See
Section~\ref{sec:timeline} below for a full timeline.

\paragraph{Application track.} %
The same deadlines and procedure for submitting to the main track will be used
also for the application track. Submissions to both the application track and
the main competition are independent: participants must submit explicitly to
both events to participate in both, and they may submit different (or
differently configured) solvers to each.  Benchmarks will be scrambled also
for this division, using the same scrambler and seed as the main track.
Entrants should still include a system description, as for the regular
competition.

\paragraph{Parallel solver track.} %
Solvers employing concurrency are invited to participate in a
demonstration that will be run before the regular competition.
Parallel solvers must be submitted by the same July~9th deadline,
with the same two-day grace period for resubmission as in the regular
competition.  Submissions to both the parallel solver track
and the main competition are independent: participants must submit
explicitly to both events to participate in both, and they may submit
different (or differently configured) solvers to each.  Benchmarks may
or may not be scrambled for this division.  Entrants should still
include a system description, as for the regular competition.

\medskip
\noindent
Note that the SMT-COMP organizers are considering ways to include
other (``historical'' or otherwise relevant) solvers in all the competition tracks for
demonstration and comparison.  The organizers reserve the right to
include or exclude such solvers, and to make simple modifications
to historical sequential solvers to (na\"ively) take advantage of
multiple processors 
or to connect them with a parser for the SMT-LIB version 2.0 format
(\eg\ by implementing a wrapper tool).

\section{Execution of Solvers}
\label{sec:exec}

\subsection{Main track and parallel track}
\label{sec:exec:main}

\header{Dates of competition.}
%
We anticipate that the bulk of the main track of the competition will take place during
the course of CAV 2011, from July~14th to~20th.  Results will be
announced in a special session of CAV, on the last day of the
conference, as well as on the SMT-COMP web site.  Intermediate results
will be regularly posted to the SMT-COMP website as the competition
runs.
%
If there are enough competitors to run the parallel track, we intend
to run it before or after the main competition (depending on the
estimated duration of the track).

\header{Input and Output.}
%
Participating solvers must read a single benchmark script (defined
below, not part of the 2.0 standard), presented on its standard input
channel. The script is in the concrete syntax of the SMT-LIB format,
version 2.0.  A benchmark script is essentially just the translation
of a benchmark from the version 1.2 specification.  In more detail, a
\textbf{benchmark script} is just a script where:

\begin{enumerate}
\item The (single) $\akey{set-logic}$ command setting the benchmark's
logic is the first command.
% rb 25/3: added
% \item A (single) \akey{set-option :print-success false} command, sent just
%       after $\akey{set-logic}$. This is to
%       avoid the output ``\texttt{success}'' to interfere with the
%       answer of the solver to the benchmark. 
\item The $\akey{exit}$ command is the last command.
\item There is exactly one $\akey{check-sat}$ command,
following possibly several $\akey{assert}$ commands.
\item There is at most one $\akey{set-info}$ command for \texttt{status}.
\item The formulas in the script belong to the benchmark's logic, with
any free symbols declared in the script.
\item Extra symbols are declared exactly once before any
  use, using $\akey{declare-sort}$
  %, $\akey{define-sort}$,
  %$\akey{declare-fun}$, or $\akey{define-fun}$.  
  or $\akey{declare-fun}$.
  They must be part of the allowed signature expansion for the logic.
  Moreover, all sorts declared with a $\akey{declare-sort}$ command must have zero arity.
\item No other commands besides the ones just mentioned may be used.
\end{enumerate}

% \noindent Note that the final version of the 2.0 format will be frozen
% in early March.  
\noindent The SMT-LIB format specification is publicly
available from the ``Documents'' section of the SMT-LIB
website~\cite{SMT-LIB}.  Solvers will be given formulas just from the
Problem Divisions indicated during their submission to SMT-Exec.
Example benchmark scripts for several Problem Divisions are reported in the Appendix.
Note that they are provided for illustrative purposes only: 
please refer to the SMT-LIB format specification 
and the above definition of benchmark script for the official specification 
of the input format for SMT-COMP.

\medskip
Each SMT-COMP entrant is then expected to attempt to report on its
standard output channel whether the formula is satisfiable
(``\texttt{sat}'', in lowercase, without the quotation marks) or unsatisfiable
(``\texttt{unsat}'').  An entrant may also report ``\texttt{unknown}''
to indicate that it cannot determine satisfiability of the formula.
For more detailed information on the output format, see the
description on the SMT-Exec ``Upload a Solver'' page.

\header{Timeouts.} %
Each SMT-COMP solver will be executed on an
unloaded competition machine for each given formula, up to a fixed
time limit.  The time limit is yet to be determined, but it is
anticipated to be around 20 minutes.  Solvers that take more than this
time limit will be killed.  Solvers are allowed to spawn other
processes.  These will be killed at approximately the same time as the
first started process, using the TreeLimitedRun script, developed for
the CASC competition and available on the SMT-COMP web page.  A
timeout scores the same as if the output is ``\texttt{unknown}''.

\header{Aborts and unparsable output.} %
Solvers which exit before the time
limit without reporting a result (\ie\ due to exhausting memory, crashing,
or producing output other than \texttt{sat}, \texttt{unsat}, or
\texttt{unknown})
will be considered to have aborted. 
An abort scores the same as if the output is ``\texttt{unknown}''. 
% rb 25/3: added
Also, as a further measure to prevent misjudgments of solvers,
the first burst of  ``\texttt{success}'' outputs will be 
ignored\footnote{
Note that SMT-LIBv2 requires to produce a ``\texttt{success}'' answer
after each \akey{set-logic}, \akey{declare-sort}, \akey{declare-fun} and
\akey{assert} command (among others), unless the option
\akey{:print-success} is set to false: ignoring the first burst of
\texttt{success} outputs therefore allows for submitting fully-compliant
solvers without the need of a wrapper script, while still allowing entrants
of SMT-COMP 2010 to run without changes.}.

\header{Persistent state.} %
Solvers are allowed to create and write to
files and directories during the course of an execution, but they are
not allowed to read such files back during later executions.  Any
files written should be put in the directory in which the tool is
started, or in a subdirectory.

\subsection{Application track}
\label{sec:exec:application}

The application track aims at evaluating SMT solvers when interacting
with an external verification framework, \eg, a model
checker. This interaction, ideally, happens by means of an online
communication between the model checker and the solver: the model
checker repeatedly sends queries to the SMT solver, which in turn
answers either sat or unsat.  In this interaction an SMT-solver is
required to accept queries incrementally via its standard input channel.

In order to facilitate the evaluation of the solvers in this track, we
propose to set up a ``simulation'' of the aforementioned interaction. In
particular each benchmark in the application track represents a realistic
communication trace, containing multiple \akey{check-sat} commands (possibly
with corresponding \akey{push 1}/\akey{pop 1} commands), which
is parsed by a {\em trace executor}. The trace executor serves the following purposes:
\begin{itemize}
\item it simulates the online interaction by sending single queries to the SMT solver
      (through stdin);
\item it prevents ``look-ahead'' behaviours of SMT solvers;
\item it records time and answers for each call, possibly aborting the execution
      in case of a wrong answer;
\item it guarantees a fair execution for all solvers by abstracting from any possible
      crash, misbehaviour, etc. that may happen on the model checker side.
\end{itemize}

\header{Input and Output.}
Participating solvers will be connected to a trace executor 
which will incrementally send commands to the standard input channel of the solver
and read responses from the standard output channel of the solver.
The commands will be taken from an \textbf{incremental benchmark script},
which is an SMT-LIB 2.0 script which satisfies points 1., 2., 4.--7. of the definition of benchmark script given in \S\ref{sec:exec:main}, plus the following:

\begin{enumerate}
\item[3'.] There are one or more \akey{check-sat} commands, 
  each preceded by one or more \akey{assert} commands 
  and zero or more \akey{push 1} commands, 
  and followed by zero or more \akey{pop 1} commands.
\end{enumerate}

\noindent
Furthermore, the trace executor will send a single 
\akey{set-option :print-success true} command to the solver before 
sending commands from the incremental benchmark script.

\medskip
Solvers must respond immediately to the commands sent by the trace executor, 
with the answers defined in the SMT-LIB 2.0 format specification: that is,
with a \texttt{success} answer for 
\akey{set-option}, 
\akey{declare-sort}, 
\akey{declare-fun}, 
\akey{assert}, 
\akey{push 1}, 
and \akey{pop 1} 
commands,
and with a \texttt{sat}, \texttt{unsat}, or \texttt{unknown} 
for \akey{check-sat} commands.

\header{Timeouts.}
A time limit is set for the whole execution of each application
benchmark (consisting of multiple queries).

\header{Scoring.}
The score for each benchmark is a pair $\langle n,m\rangle$, with
$n\in[0,N]$ an integral number of points scored for the benchmark,
where $N$ is the number of \akey{check-sat} commands
in the benchmark.  $m\in[0,T]$ is the (real-valued) time is seconds, where $T$ is
the timeout.  The score for the benchmark is initialized with
$\langle0,0\rangle$ and then computed as follows.
\begin{itemize}
\item A correctly-reported \texttt{sat} or \texttt{unsat} answer after
  $s$~seconds (counting from the beginning of this particular
  \akey{check-sat}) contributes $\langle1,s\rangle$ to the running
  score.
\item An answer of \texttt{unknown}, an unexpected answer, a crash, or a memory-out during
  execution of the query, or a benchmark timeout, aborts the execution
  of the benchmark and assigns the current value of the running score
  to the benchmark.  (Recall that there is one timeout for the entire
  benchmark; there are no individual timeouts for queries.)
\item The first incorrect answer to a \akey{check-sat} command has the effect of terminating the
  trace executor, and the returned score for the overall benchmark
  will be $\langle0,0\rangle$, effectively canceling the running score.
\end{itemize}

For example, if a benchmark has 5~\akey{check-sat} commands, and a
timeout of 100~seconds, and a solver solves the first four in
10~seconds each, then times out on the fifth, then the solver's score
is $\langle4,40\rangle$.  If another solver solves each of the first
four in 10~seconds each, and the fifth in another 40~seconds, its
score is $\langle5,80\rangle$.  If a third solver solves the first
four queries in 2~seconds each, but incorrectly answers the fifth, its
score is $\langle0,0\rangle$.

As queries are only presented in order, this scoring system may mean
that relatively ``easier'' queries are hidden behind more difficult
ones located at the middle of the query sequence.

Scores are compared lexicographically---a solver with a higher
$n$-value wins, with the cumulative time only used to break ties.
Benchmarks' scores are summed componentwise to form a solver's total
score for the competition.

\section{Benchmarks and Problem Divisions}
\label{sec:theories}

We expect the problem divisions for SMT-COMP 2011 to include the following
SMT-LIB \emph{logics}.  These logics are specified in SMT-LIB format on the
SMT-LIB web page.  Note that the ``QF\_'' prefix means the division's
formulas are quantifier-free.  However, the organizers reserve the right to add
(remove) divisions if (not) enough benchmarks and solvers exist for a
particular division.

\begin{itemize}
\item QF\_UF: uninterpreted functions.
\item QF\_RDL: real difference logic.
\item QF\_IDL: integer difference logic.
\item QF\_UFIDL: uninterpreted functions and integer difference logic.
\item QF\_UFLIA: uninterpreted functions and linear integer arithmetic.
\item QF\_UFLRA: uninterpreted functions and linear real arithmetic.
\item QF\_UFNRA: uninterpreted functions and nonlinear real arithmetic.
\item QF\_LRA: linear real arithmetic.
\item QF\_LIA: linear integer arithmetic.
\item QF\_NIA: nonlinear integer arithmetic.
\item QF\_AX: arrays with extensionality.
\item QF\_AUFLIA: arrays, uninterpreted functions and linear integer 
                  arithmetic.
\item QF\_BV: fixed-width bitvectors.
\item QF\_AUFBV: arrays, fixed-width bitvectors and uninterpreted
functions.
\item LRA: (quantified) linear real arithmetic.
\item AUFLIA$+p$: (quantified) arrays, uninterpreted functions and 
linear integer arithmetic, patterns included.
\item AUFLIA$-p$: (quantified) arrays, uninterpreted functions and 
linear integer arithmetic, patterns not included.
\item AUFLIRA: (quantified) arrays, uninterpreted functions and 
mixed linear integer and real arithmetic.
\item UFNIA$+p$: (quantified) uninterpreted functions and 
nonlinear integer arithmetic, patterns included.
\item AUFNIRA: (quantified) arrays, uninterpreted functions and 
mixed nonlinear integer and real arithmetic.
\end{itemize}

\subsection{Main and parallel tracks}

\header{Benchmark sources.} %
Benchmark formulas for these divisions
will be drawn from the SMT-LIB library.  Any benchmarks added to
SMT-LIB by the May 15th release (see the timeline in
Section~\ref{sec:timeline}) will be considered eligible.  SMT-COMP
attempts to give preference to benchmarks that are ``real-world,'' in
the sense of coming from or having some intended application outside
SMT.

\header{Benchmark availability.} % A first release of the competition
Benchmarks will be made available within May 15th, 2011.
% A second and almost final release will be available on June 1st. 
No additional
benchmarks will be added after this date, but benchmarks can be
modified or removed to fix possible bugs or other issues, or to adjust their difficulty score (see below). 
The final release that will be used for the competition will be posted on June
30th. The set of selected benchmarks will be published when the
competition begins.

\header{Benchmark demographics.} %
In SMT-LIB, benchmarks are organized according to \emph{families}.  A benchmark
family contains problems that are similar in some significant way.  Typically
they come from the same source or application, or are all output by the same
tool.  \emph{Each top-level subdirectory within a division represents a distinct
family.}  This represents a significant change from
competition years before 2010, where
\emph{terminal} subdirectories delineated families.
%
Each benchmark in SMT-LIB also has a \emph{category}.  There are four possible
categories:
%
\begin{itemize}
\item \emph{check.} These benchmarks are hand-crafted to test whether
  solvers support specific features of each division.  In particular,
  there are checks for integer completeness (\ie\ benchmarks that are
  satisfiable under the reals but not under the integers) and big
  number support (\ie\ benchmarks that are likely to fail if integers
  cannot be represented beyond some maximum value, such as
  $2^{31}-1$).

  \noindent%\textbf{New for 2010:} 
  Using the same random seed as
  for benchmark selection and scrambling, 5 ``check'' benchmarks will
  be randomly generated using Robert Brummayer's SMT fuzzing
  tool~\cite{brummayer+09}.  The (exact version of this) tool will be
  publicly available from the SMT-COMP~2011 web site before the
  competition.  Since these benchmarks are generated after the random
  seed is fixed, they cannot be known in advance to any competitors,
  including the organizers.  The rationale for including these
  benchmarks is to try to take a step towards stronger certification
  that solvers are correct.  In future years, we envision SMT-COMP
  requiring that solvers pass some kind of pre-qualifying round based
  on SMT fuzzing.  The inclusion of these fuzzing benchmarks that are
  not known in advance is intended to encourage (without requring)
  solver implementors to test their solvers using fuzzing or similar
  bug-discovery techniques.
\item \emph{industrial.} These benchmarks come from some real application
      and are produced by tools such as bounded model checkers, static analyzers, extended
      static checkers, etc.
\item \emph{random.} These benchmarks are randomly generated.
\item \emph{crafted.} This category is for all other benchmarks.  Usually,
  benchmarks in this category are designed to be particularly difficult or to
  test a specific feature of the logic.
\end{itemize}

\header{Benchmark selection.} %
Before the selection process, each benchmark will be assigned a
\emph{difficulty:} a number between 0.0 and 5.0 inclusive.  The
difficulty for a particular benchmark will be assigned by running SMT
solvers from the 2010 competition that finished in good
standing and using the formula:

\[\mathrm{difficulty} = {5\cdot\ln\!\left(1+A^2\right) \over \ln\!\left(1+30^2\right)}\]

\noindent
where $A$ is the average time for the solvers to correctly solve the
instance (in minutes).  This computation of difficulties
replaces a simpler formulation in earlier SMT-COMPs that didn't take
into account the time solvers take.  This calculation of difficulty
recognizes that problems requiring more time by many solvers are
more difficult problems.  The logarithm is used to
mark a larger change in difficulty (given a corresponding increase in
solver average time) at smaller time scales than at higher ones (if $A=1$,
difficulty is 0.5; at $A=1.7$, difficulty is 1.0; but a difficulty of 2.0
requires that $A=4$); the square is used to flatten out this curve sightly
at the low end.  Figure~\ref{difficultyplot} shows this curve.

\begin{figure}
  \centerline{\epsffile{difficultyplot.eps}}
  \caption{The shape of the difficulty assignment curve.}
  \label{difficultyplot}
\end{figure}

When 5 or more solvers are used for the
calculation, two times are dropped from the calculation of the average
(one at the maximum and one at the minimum).  Solvers giving an
incorrect answer are not counted in the average; solvers crashing,
timing out, or giving an unknown result are considered as taking 30
minutes (which, with the above formula, pulls the difficulty
toward~5.0).  If there are available solvers, but no average is
defined under these rules, the difficulty shall be 5.0.  For new
divisions, where there are no available solvers to compute the
difficulty, the difficulty will be computed using whatever means are
available to the organizers for that purpose.

The following scheme will be used to choose competition benchmarks
within each division.  Unknown-status benchmarks from SMT-LIB are
considered ineligible for competition and are not used.
%
Additionally, certain benchmarks deemed inappropriate for competition
may be cut by the organizers, and in some cases, representative subsets
of benchmarks from a certain source may be included for the selection
instead of all benchmarks from that source.
%
The selection
is implemented by our benchmark selection tool, source for which will
be available at \url{www.smtcomp.org}.

\begin{enumerate}

\item \textbf{Check benchmarks included.} %
  All benchmarks in category \emph{check} are included.

\item \textbf{Retire very easy benchmarks.} %
  The most difficult~300 non-check non-unknown benchmarks in each
  division are always included, together with all benchmarks on which
  at least one 2010 solver required more than 5~seconds.  \emph{This
    is intended to have the effect of retiring ``very easy''
    benchmarks that were solved by every 2010 solver in less
    than 5~seconds, \emph{unless} doing so reduces the pool of
    benchmarks for the division to less than~300.}

\item \textbf{Retire inappropriate benchmarks.} %
  The competition organizers will remove from the eligibility pool
  certain SMT-LIB benchmarks that are inappropriate or uninteresting
  for competition, or cut the size of certain benchmark families to
  avoid their over-representation.

\item\label{step:pool} \textbf{Division selection pools created.} %
  For non-\emph{check} benchmarks, selection pools are created.
  For benchmark families with $\leq200$ eligible,
  non-\emph{check} benchmarks, all are added to this pool;
  otherwise, 200 such benchmarks are added to the pool with the
  following distribution:
%
  \begin{itemize}
  \item 20 with solution \textbf{sat} and difficulty on $\left[0,1\right]$
  \item 20 with solution \textbf{sat} and difficulty on $\left(1,2\right]$
  \item 20 with solution \textbf{sat} and difficulty on $\left(2,3\right]$
  \item 20 with solution \textbf{sat} and difficulty on $\left(3,4\right]$
  \item 20 with solution \textbf{sat} and difficulty on $\left(4,5\right]$
  \item 20 with solution \textbf{unsat} and difficulty on $\left[0,1\right]$
  \item 20 with solution \textbf{unsat} and difficulty on $\left(1,2\right]$
  \item 20 with solution \textbf{unsat} and difficulty on $\left(2,3\right]$
  \item 20 with solution \textbf{unsat} and difficulty on $\left(3,4\right]$
  \item 20 with solution \textbf{unsat} and difficulty on $\left(4,5\right]$
  \end{itemize}
%
  If 20 are not available in one of these subdivisions, all that are
  available are added, and remaining slots are reallocated to the
  others.  This process is iterated so that it is guaranteed that 200
  benchmarks from the benchmark family are in the selection pool, in
  equal numbers from each subdivision, so far as possible.
  (In cases where \eg\ there are only two available slots and
  they can be allocated to one of three subdivisions, they are allocated
  randomly but are guaranteed to be allocated to \emph{distinct}
  subdivisions.)

\item\textbf{Category slot allocation.} %
  Next, 200 slots are allocated for the division as follows:\footnote{The
  number ``200'' is a guideline, and is expected to be used.  However, the
  SMT-COMP organizers reserve the right to reduce this to an appropriate
  value to ensure a timely end to the competition, and may do so on a
  per-division basis.  The category allotments, etc., will remain the same
  proportion of the total.}
%
  \begin{itemize}
  \item 170 from category \emph{industrial}
  \item 20 from category \emph{crafted}
  \item 10 from category \emph{random}
  \end{itemize}
%
  If there are fewer than 20 (respectively, 10) \emph{crafted} or
  \emph{random} benchmarks in the division pool, more
  \emph{industrial} slots are allocated to make 200 total for the
  division.  If there are too few \emph{industrial} benchmarks in the
  division pool, more \emph{crafted} slots are allocated to make 200
  total for the division.  (In no division are there not enough of
  both industrial and crafted benchmarks.)

\item\textbf{Category subdivision slot allocation.} %
  For each category, given that it has $n$ slots allocated to it,
  the slot allocation is further subdivided as follows:
%
  \begin{itemize}
  \item $\left\lfloor n\over10\right\rfloor$ slots for solution \textbf{sat} with difficulty on $\left[0,1\right]$
  \item $\left\lfloor n\over10\right\rfloor$ slots for solution \textbf{sat} with difficulty on $\left(1,2\right]$
  \item $\left\lfloor n\over10\right\rfloor$ slots for solution \textbf{sat} with difficulty on $\left(2,3\right]$
  \item $\left\lfloor n\over10\right\rfloor$ slots for solution \textbf{sat} with difficulty on $\left(3,4\right]$
  \item $\left\lfloor n\over10\right\rfloor$ slots for solution \textbf{sat} with difficulty on $\left(4,5\right]$
  \item $\left\lfloor n\over10\right\rfloor$ slots for solution \textbf{unsat} with difficulty on $\left[0,1\right]$
  \item $\left\lfloor n\over10\right\rfloor$ slots for solution \textbf{unsat} with difficulty on $\left(1,2\right]$
  \item $\left\lfloor n\over10\right\rfloor$ slots for solution \textbf{unsat} with difficulty on $\left(2,3\right]$
  \item $\left\lfloor n\over10\right\rfloor$ slots for solution \textbf{unsat} with difficulty on $\left(3,4\right]$
  \item $\left\lfloor n\over10\right\rfloor$ slots for solution \textbf{unsat} with difficulty on $\left(4,5\right]$
  \end{itemize}
%
  Remaining slots are allocated randomly to distinct subdivisions.
  If there aren't enough benchmarks in the pool meeting one or more of
  the above subdivision requirements for the category, the subdivision
  allocation is reduced to the number available in the pool that meet
  the requirements.  To make up the full category allotment, remaining
  slots are allocated equally to subdivisions with enough benchmarks
  in the pool meeting their requirements.  This process ensures that
  all slots can be filled with benchmarks from the pool.

\item\textbf{Benchmark selection.} %
  Benchmarks from the pool are assigned randomly to slots.
\end{enumerate}
%
In the end, up to 200 non-\emph{check} benchmarks per division are
included in the competition, together with all the \emph{check}
benchmarks.  Some divisions may have fewer than 200 non-\emph{check}
benchmarks, in which case all of them are included using this selection
scheme.

The main purpose of the algorithm above is to have a balanced and complete set
of benchmarks.  The one built-in bias is towards industrial rather than crafted
or random benchmarks.  This reflects a desire by the organizers and agreed upon
by the SMT community to emphasize problems that come from real applications.

Pseudo-random numbers will be generated using the standard C library
function \texttt{random()}, seeded (using \texttt{srandom()}) with the
sum, modulo $2^{30}$, of the numbers provided in the system
descriptions (see Section~\ref{sec:entrants} above) by all SMT-COMP
entrants other than the organizers.  Additionally, the integer part of
the opening value of the New York Stock Exchange Composite Index on
July~12th
will be added to the other seeding values.  This helps provide transparency,
by guaranteeing that the organizers cannot manipulate the seed in
favor of their submitted solvers.  Benchmarks will also be slightly
scrambled before the competition, using a simple benchmark scrambler %the same scrambler as last year,
seeded with the same seed as the benchmark selector.  Both the
scrambler and benchmark selector will be publicly available before the
competition.  Naturally, solvers must not rely on previously
determined identifying syntactic characteristics of competition
benchmarks in testing satisfiability (violation of this is considered
cheating).

\subsection{Application track}

\header{Benchmark sources.} %
Benchmarks for the application track will be collected by the SMT-COMP organizers.
Any benchmark available to the organizers by May 15th (see the timeline in
Section~\ref{sec:timeline}) will be considered eligible.

\header{Benchmark availability.} 
A first release of the application track
benchmarks will be made available within March 31st, 2011.
More benchmarks can be collected, until May 15th.
No additional
benchmarks will be added after this date, but benchmarks can be
modified or removed to fix possible bugs or other issues. 
The final release that will be used for the competition will be posted on 
% rb 23/3: changed from June 30th to agree with sec 6.
June 15th.

\header{Benchmark demographics and selection.} 
All the available benchmarks will be used for the competition. 
For this first year of the application track, no difficulty will be assigned to the benchmarks.
Benchmarks will be slightly scrambled before the competition, using the same scrambler and 
random seed as the main track. 
% rb 25/3: added
For this year, the selection algorithm for the application track will be chosen after the
deadline of May 15th, when the exact demographic of the benchmarks (collected with a usual
``call for benchmarks'') will be available.

\section{Judging and Scoring}
\label{sec:judging}

\begin{figure}
\begin{center}
\begin{tabular}{|l|c|c|}
\hline \textbf{Reported} & \textbf{Correct?} &
\textbf{Point/penalty}\\ \hline \texttt{unsat} & yes & +1 \\ \hline
\texttt{unsat} & no & -8 \\ \hline \texttt{sat} & yes & +1 \\ \hline
\texttt{sat} & no & -8 \\ \hline \texttt{unknown} & n.a. & 0 \\ \hline
\emph{timeout} & n.a. & 0 \\ \hline
\emph{abort} & n.a. & 0 \\ \hline
\end{tabular}
\end{center}
\caption{\label{fig:points}Points and Penalties for the main and parallel tracks.}
\end{figure}

Winners in each Problem Division for which there are at least three
entrants from distinct research groups competing will be taken to be
those with the highest score. In addition to recognizing the overall
winner in each division, the top solver that provides its source code will also be
recognized in each division.  
For Problem Divisions with fewer than three
entrants, the results will be reported but no winner officially
declared.

For the main and parallel tracks, the score will be computed according to the system of points and
penalties in Figure~\ref{fig:points}. 
As indicated, correct answers
are awarded a positive number of points, while incorrect answers are
penalized by assigning a negative number of points.  Timeouts, aborts,
and reports of \texttt{unknown} are awarded zero points.
%
In the event of a tie
in total number of points, the solver with the lowest average CPU time
on formulas for which it gave a correct answer will be
considered the winner.

For the application track, the score will be computed according to the procedure described in \S\ref{sec:exec:application}.

\penalty0

\section{Timeline}
\label{sec:timeline}

\nobreak
\vbox{% no page break here, please!
\begin{description}
\item[March 31] First version of the benchmark library for the application track posted for comment.
  First version of the benchmark scrambler, benchmark selector and trace exector made available.
\item[April 30] Final version of the benchmark scrambler, benchmark selector and trace exector made available.
\item[May 15] No new benchmarks can be added after this date, but
  problems with existing benchmarks may be fixed.
\item[June 15] Benchmark libraries are frozen.
\item[July 9 (7pm ET)] Solvers due via SMT-Exec (for
  all tracks), including system
  descriptions and magic numbers for benchmark scrambling.
\item[July 11 (7pm ET)] Final versions due, fixing any last-minute
 bugs (this marks the end of the two-day grace period for
 submissions).
\item[July 12] Opening value of NYSE Composite Index used to complete random seed.
\item[July 14--20] Anticipated dates for SMT-COMP 2011.
\end{description}}

\section{Mailing List}
\label{sec:ps}

Interested parties should subscribe to the SMT-COMP mailing list, a
link to which is found at \url{www.smtcomp.org}.  Important
late-breaking news and any necessary clarifications and edits to these
rules will be announced there, and it is the primary way that such
announcements will be communicated.

\bibliographystyle{plain}
\bibliography{biblio}

\appendix
\section{Sample benchmark scripts for the main track}

\header{QF\_UF}

{\footnotesize
\begin{verbatim}
(set-logic QF_UF)
(set-info :status sat)
(declare-sort U 0)
(declare-fun f (U) U)
(declare-fun g (U) U)
(declare-fun A () Bool)
(declare-fun x () U)
(declare-fun y () U)
(assert
(let ((fx (f x))
      (cls1 (or A (= x y))))
  (and cls1 (distinct fx (g y)))))
(check-sat)
(exit)
\end{verbatim}}

\header{QF\_LRA}

{\footnotesize
\begin{verbatim}
(set-logic QF_LRA)
(declare-fun x () Real)
(declare-fun y () Real)
(declare-fun A () Bool)
(assert
  (let ((i1 (ite A (<= (+ (* 2.0 x) (* (/ 1 3) y)) (- 4))
                   (= (* y 1.5) (- 2 x)))))
    (and
      i1
      (or (> x y) (= A (< (* 3 x) (+ (- 1) (* (/ 1 5) (+ x y)))))))))
(check-sat)
(exit)
\end{verbatim}}

\header{QF\_LIA}

{\footnotesize
\begin{verbatim}
(set-logic QF_LIA)
(declare-fun x () Int)
(declare-fun y () Int)
(declare-fun A () Bool)
(assert
  (let ((i1 (ite A (<= (+ (* 2 x) (* (- 1) y)) (- 4))
                   (= (* y 5) (- 2 x)))))
    (and
      i1
      (or (> x y) (= A (< (* 3 x) (+ (- 1) (* 1 (+ x y)))))))))
(check-sat)
(exit)
\end{verbatim}}

\header{QF\_BV}

{\footnotesize
\begin{verbatim}
(set-logic QF_BV)
(declare-fun x () (_ BitVec 32))
(declare-fun y () (_ BitVec 16))
(declare-fun z () (_ BitVec 20))
(assert
  (let ((c1 (= x ((_ sign_extend 12) z))))
   (let ((c2 (= y ((_ extract 18 3) x))))
    (let ((c3 
            (bvslt (concat z (_ bv5 12)) 
              (bvand (bvor (bvxor (bvnot x) ((_ zero_extend 28) #b1111)) 
                                    (concat #xAF02 y))
                    (concat (bvmul ((_ extract 31 16) x) y) 
                            (bvashr (_ bv42 16) #x0001))))))
   (and c1 (xor c2 c3))))))
(check-sat)
(exit)
\end{verbatim}}

\header{QF\_AUFLIA}

{\footnotesize
\begin{verbatim}
(set-logic QF_AUFLIA)
(declare-fun A () (Array Int Int))
(declare-fun x () Int)
(declare-fun y () Int)
(declare-fun P () Bool)
(declare-sort U 0)
(declare-fun f (U) (Array Int Int))
(declare-fun c () U)
(assert
  (let ((fc (f c)))
    (and
      (=> (= A (store fc x 5)) (> (+ (select fc y) (* 4 x)) 0))
      (= P (< (select A (+ 3 y)) (* (- 2) x))))))
(check-sat)
(exit)
\end{verbatim}}

\header{QF\_ABV}

\footnotesize
\begin{verbatim}
(set-logic QF_ABV)
(declare-fun x () (_ BitVec 32))
(declare-fun y () (_ BitVec 16))
(declare-fun z () (_ BitVec 20))
(declare-fun A () (Array (_ BitVec 16) (_ BitVec 32)))
(assert
  (let ((c1 (= ((_ sign_extend 12) z) (select A y)))
        (A2 (store A ((_ extract 15 0) x) x)))
   (let ((c2 (= A A2)))
    (let ((c3 
            (bvslt (concat z (_ bv5 12)) 
              (bvand (bvor (bvxor (bvnot x) 
                                  (select A2 ((_ zero_extend 12) #b1111)))
                                    (concat #xAF02 y))
                    (concat ((_ extract 15 0) 
                                (bvmul x (select (store A y x) #x35FB))) 
                            (bvashr (_ bv42 16) #x0001))))))
   (and c1 (xor c2 c3))))))
(check-sat)
(exit)
\end{verbatim}

\section{Sample benchmark scripts for the application track}

\footnotesize
\begin{verbatim}
(set-option :print-success true)
(set-logic QF_LRA)
(declare-fun c0 () Bool)
(declare-fun E0 () Bool)
(declare-fun f0 () Bool)
(declare-fun f1 () Bool)
(push 1)
(assert 
  (let ((.def_10 (not f0)))
   (let ((.def_9 (not c0)))
    (let ((.def_11 (or .def_9 .def_10)))
     (let ((.def_7 (not f1)))
      (let ((.def_8 (or c0 .def_7)))
       (let ((.def_12 (and .def_8 .def_11)))
 .def_12
)))))))
(check-sat)
(pop 1)
(declare-fun f2 () Bool)
(declare-fun f3 () Bool)
(declare-fun f4 () Bool)
(declare-fun c1 () Bool)
(declare-fun E1 () Bool)
(assert 
 (let ((.def_23 (not f2)))
  (let ((.def_20 (= c0 c1)))
   (let ((.def_22 (or E0 .def_20)))
    (let ((.def_24 (or .def_22 .def_23)))
     (let ((.def_18 (not f4)))
      (let ((.def_19 (or c1 .def_18)))
       (let ((.def_25 (and .def_19 .def_24)))
 .def_25
))))))))
(push 1)
(check-sat)
(assert (and f1 (not f1)))
(check-sat)
(pop 1)
(exit)
\end{verbatim}

\end{document}

### 2012-01-23 rules/rules12.tex
Draft rules and call documents

--- 2012-01-23 rules/rules11.tex
@@
 
-\date{}
-
-\title{Satisfiability Modulo Theories Competition (SMT-COMP) 2011: Rules and 
+\date{\small This version revised \the\year-\the\month-\the\day}
+
+\title{DRAFT DRAFT Satisfiability Modulo Theories Competition (SMT-COMP) 2012: Rules and 
 Procedures
@@
 \and
-Morgan Deters \\
-Computer Science \\
-New York University \\
+David R. Cok \\
+GrammaTech, Inc. \\
+Ithaca, NY USA \\
 \and
@@
 competitions~(\cite{SMTCOMP-2008,BDOS08,SMTCOMP-FMSD,SMTCOMP-JAR}).
-SMT-COMP 2011 is affiliated with the 23nd International
-Conference on Computer Aided Verification~(CAV).
+SMT-COMP 2012 is affiliated with the SMT workshop (\url {http://smt2012.loria.fr/}) at the 6th International
+Joint Conference on Automated Reasoning~(IJCAR) (\url{http://ijcar.cs.manchester.ac.uk/}).
 
@@
 version\footnote{Earlier versions of this document include contributions from
-Clark Barrett, Albert Oliveras, and Aaron Stump.},
-describes the rules and competition procedures for SMT-COMP~2011.
-The principal change from last year's version is:
-
-\begin{itemize}
-\item the introduction of an ``application track,'' based on incremental
-      model-checking queries, to promote the integration of SMT solvers
-      within actual verification frameworks;
-%\item updates to the benchmark selection algorithm, to reduce
-%      overwhelming a competition division with a single ``family'' of
-%      benchmarks.
-% rb 25/3: see later
-%\item updates to the difficulty calculation;
-%\item a track for parallel solvers, to run before the regular competition.
-%\item 5 random ``check'' benchmarks will be generated using Robert
-%  Brummayer's SMT fuzzing tool, after all the solvers are uploaded.
-%  These will be included in the competition, to help promote attention
-%  to the problem of solver correctness (cf.~\cite{brummayer+09}).
-\end{itemize}
+Clark Barrett, Albert Oliveras, Aaron Stump, and Morgan Deters.},
+describes the rules and competition procedures for SMT-COMP~2012.
+The principal changes from last year's version are the following:
+
+\begin{itemize}
+
+\item We are concentrating on just a few of the benchmark divisions this year.
+  Some divisions, such as QF\_UF, are subsumed into more expressive
+  logics; others have received only light interest in past competitions. Our goal is to
+  focus the competition on divisions of particular interest to
+  applications. To encourage new entrants, we will also accept
+  solvers against any benchmark class in an exhibition category:
+  results will be displayed and publicly reported.
+
+\item We are retaining and accenting last year's ``application track" and
+  encourage submission of benchmarks and competition against these
+  benchmarks.
+
+\item The penalty for producing an incorrect result is increased. Competitors
+  producing all correct results are ranked above those producing
+  incorrect results (a ``soft" disqualification for unsound tools).
+
+\item We are adding an ``unsat core" division of QF\_BV.
+
+\item We will have an exhibition division of solvers that produce proofs.
+
+\item The competition will be run with a new StarExec service, replacing
+  the previous SMT-Exec service. At this writing, the new service is
+  still being completed and tested; it will be announced later. (The
+  previous service will be maintained in reserve.)
+
+\end{itemize}
+
+Additionally, non-competitive divisions and tracks will not be exhibited as
+part of the competition: at least two competitors must be entered
+into a division for it to run as part of the competition.
+If necessary, and based on final submissions, the organizers may elect to
+combine competition divisions to make them competitive (such decisions will
+be made with input from the community).
+
+As in SMT-COMP 2011, the 2012 version will incorporate a small number of
+random ``fuzzer-generated" instances (see below) to help promote
+attention to solver correctness.
+
+It is important for competitors to track discussions on the SMT-COMP mailing
+list, as clarifications and any updates to these rules will be posted there.
 
@@
 An entrant to SMT-COMP is an SMT solver
-submitted using the SMT-Exec service.  SMT-Exec enables members of the
+submitted using the StarExec\footnote{StarExec is still under development as of 21 January 2012;
+updates on its progress and use will be posted on www.smtcomp.org and through
+the SMT-COMP mailing list. Statements in these rules may need correction once the UI for the service is completed.} service.  
+StarExec enables members of the
 SMT research community to run solvers on jobs consisting of benchmarks
-from the SMT-LIB benchmark library.  Jobs are run on a 12-node computer
+from the SMT-LIB benchmark library.  Jobs are run on a computer
 cluster purchased with funds from a National Science Foundation
-Computing Research Infrastructure grant.  SMT-Exec is provided free of
+Computing Research Infrastructure grant.  StarExec is provided free of
 charge, but it does require a minimal registration, which verifies an
@@
 may then upload their own solvers to run, or may run public solvers
-already uploaded to SMT-Exec.  SMT-Exec provides a variety of tabular
+already uploaded to StarExec.  StarExec provides a variety of tabular
 and graphical displays of results of solver executions, for
@@
 and application tracks 
-of SMT-COMP 2011, SMT-Exec will be configured so that jobs are run on a 64-bit,
-uniprocessor Linux kernel.  For the parallel-solver track, SMT-Exec
+of SMT-COMP 2012, StarExec will be configured so that jobs are run on a 64-bit,
+uniprocessor Linux kernel.  For the parallel-solver track, StarExec
 will be configured so that jobs are run on a 64-bit, multiprocessor
-Linux kernel.\footnote{This year, the competition may take
-  advantage of off-site computing resources not normally part of
-  SMT-Exec; please stay tuned to the SMT-COMP mailing list for final
-  details regarding the effective SMT-COMP 2011 competition cluster.}
+Linux kernel.
 
 For participation in SMT-COMP, a solver must be
-uploaded as a ``competition'' solver via the usual SMT-Exec upload
+uploaded as a ``competition'' solver via the StarExec upload
 mechanism, or, alternatively, a previously-uploaded solver may be
@@
 must be marked for competition before the deadline;} uploading a solver
-to SMT-Exec is not sufficient for competition entry if it's not marked
+to StarExec is not sufficient for competition entry if it's not marked
 as being a competition entrant.  The md5 checksums of competition
@@
 recognition will be given to solvers providing source code distributions
-including recognition for the top such solver in each division.  See
-SMT-Exec~(\url{www.smtexec.org}) for instructions on uploading solvers, as well
-as machine specifications.
+including recognition for the top such solver in each division.  Instructions
+for uploading solvers and machine specifications will be posted as soon
+as they are available.
 
 \header{System description.} %
-As part of their submission via SMT-Exec,
+As part of their submission via StarExec,
 SMT-COMP entrants must also include a short (1--2 pages) description of
@@
 
-The SMT-Exec upload system will ask for the system description and
+The StarExec upload system will ask for the system description and
 the random seed when a solver is marked for competition, so
@@
 tool.  The other solver is called the \emph{wrapped tool}.  There are
-several rules governing wrapper tools.  For the purposes of these rules,
+several rules governing wrapper tools that wrap tools that have been or could be submitted as independent entrants.\footnote{A wrapper
+for a wrapped tool that does not accept SMT-LIBv2 format is considered to simply be an SMT version of the underlying tool.}
+For the purposes of these rules,
 multiple versions of a wrapped tool are considered different tools.
@@
 \paragraph{Main competition track.} %
-SMT-COMP entries must be submitted via SMT-Exec by 7pm, Eastern U.S.
-time, July~9th, 2011.  At that time the SMT-Exec service will be
+SMT-COMP entries must be submitted via StarExec by 7pm, Eastern U.S.
+time, June~15, 2012.  At that time the StarExec service will be
 closed to the public to prepare for the competition, with the
 exception that resubmissions of existing entries will be accepted
-until 7pm, Eastern U.S. time, July~11th, 2011.  We strongly encourage
-participants to use this two day grace period \emph{only} for the
+until 7pm, Eastern U.S. time, June~18, 2012.  We strongly encourage
+participants to use this weekend grace period \emph{only} for the
 purpose of fixing any bugs that may be discovered and not for adding
 new features as there will be no opportunity to do extensive testing
-using SMT-Exec after the original deadline on July~9th.
-
-The versions that are present on SMT-Exec at the conclusion of the
+using StarExec after the original deadline on June~15.
+
+The versions that are present on StarExec at the conclusion of the
 grace period will be the ones used for the competition, and versions
@@
 the right to start the competition itself at any time after the open
-of the New York Stock Exchange on the morning of July~12th.  See
+of the New York Stock Exchange on the morning of June~22.  See
 Section~\ref{sec:timeline} below for a full timeline.
@@
 demonstration that will be run before the regular competition.
-Parallel solvers must be submitted by the same July~9th deadline,
-with the same two-day grace period for resubmission as in the regular
+Parallel solvers must be submitted by the same June~15th deadline,
+with the same grace period for resubmission as in the regular
 competition.  Submissions to both the parallel solver track
@@
 \noindent
-Note that the SMT-COMP organizers are considering ways to include
+Note that the SMT-COMP organizers may include
 other (``historical'' or otherwise relevant) solvers in all the competition tracks for
@@
 
-\subsection{Main track and parallel track}
-\label{sec:exec:main}
+Solvers will be publicly evaluated in the following tracks, listed here and 
+described in detail below.
+In exhibition tracks, solvers are evaluated and results posted, but no awards are announced.
+The other tracks are competition tracks; if there are sufficient entrants, a winner will be announced.
+\begin{itemize}
+\item a main track: sequential execution evaluated separately on benchmarks from each of several different logics
+\item a parallel track: parallel execution evaluated on the same benchmarks and the same divisions as the main track
+\item application track: evaluation on command scripts [TODO: FOR WHICH LOGICS]
+\item exhibition track: solvers (particularly new entrants) may be submitted against any benchmark division; the solver will be evaluated and the results posted, though not included in competition
+\item unsat-core track: a competition among solvers capable of computing unsat cores
+\item proof-generation exhibition: an exhibition track for solvers capable of generating proofs
+\end{itemize}
+
+\subsection{Logistics}
 
@@
 We anticipate that the bulk of the main track of the competition will take place during
-the course of CAV 2011, from July~14th to~20th.  Results will be
-announced in a special session of CAV, on the last day of the
-conference, as well as on the SMT-COMP web site.  Intermediate results
+the course of IJCAR 2012, from June~26 to the 29th.  Results will be
+announced in a special session of IJCAR, on the last day of the
+conference, as well as at the SMT workshop and on the SMT-COMP web site.  Intermediate results
 will be regularly posted to the SMT-COMP website as the competition
 runs.
-%
+
 If there are enough competitors to run the parallel track, we intend
@@
 estimated duration of the track).
+
+The organizers will prioritize the running of the competition tracks, and may shift the
+time period or order of the competition or exhibition tracks in order to complete SMT-COMP
+in the course of the IJCAR conference.
 
@@
 \item There is at most one $\akey{set-info}$ command for \texttt{status}.
+%%%%%%%%%%%%%%%%%%% TODO: Need to define the set-info command.
 \item The formulas in the script belong to the benchmark's logic, with
@@
   Moreover, all sorts declared with a $\akey{declare-sort}$ command must have zero arity.
+\item In the unsat-core competition, the $\akey{set-logic}$ command is preceded by a 
+$\akey{set-option :produce-unsat-cores true}$ command and the 
+$\akey{check-sat}$ command is followed by a $\akey{get-unsat-core}$ command.
+Also, some or all of the $\akey{assert}$ commands will assert named formula
+(for example, \akey{assert (! P :named F1)}). The $\akey{get-unsat-core}$
+command must return a parenthesized list of formula names, as specified by the 
+SMTLIBv2 standard.
+\item In the proof generation competition, the $\akey{set-logic}$ command is preceded by a 
+$\akey{set-option :produce-proofs true}$ command and the 
+$\akey{check-sat}$ command is followed by a $\akey{get-proof}$ command.
+The $\akey{get-proof}$ command must return a proof in a solver-dependent format as an
+S-expression.
 \item No other commands besides the ones just mentioned may be used.
+
 \end{enumerate}
 
-% \noindent Note that the final version of the 2.0 format will be frozen
-% in early March.  
 \noindent The SMT-LIB format specification is publicly
@@
 
-\medskip
+\subsection{Main track and parallel track}
+\label{sec:exec:main}
+
+The main track competition will consist of selected benchmarks in each of the
+logic divisions given below.
+Each benchmark script will be presented to the standard input of the solver.
 Each SMT-COMP entrant is then expected to attempt to report on its
@@
 For more detailed information on the output format, see the
-description on the SMT-Exec ``Upload a Solver'' page.
+description on the StarExec ``Upload a Solver'' page.  %%%%%%% TODO: CHeck this and all referecnes to StarExec
 
@@
 time limit.  The time limit is yet to be determined, but it is
-anticipated to be around 20 minutes.  Solvers that take more than this
+anticipated to be 20 minutes, as it was in 2011.  Solvers that take more than this
 time limit will be killed.  Solvers are allowed to spawn other
@@
 timeout scores the same as if the output is ``\texttt{unknown}''.
+%%%%%%%%%%% TODO: Clarify time limit
 
@@
 Also, as a further measure to prevent misjudgments of solvers,
-the first burst of  ``\texttt{success}'' outputs will be 
+any  ``\texttt{success}'' outputs will be 
 ignored\footnote{
@@
 \akey{assert} command (among others), unless the option
-\akey{:print-success} is set to false: ignoring the first burst of
+\akey{:print-success} is set to false; ignoring the
 \texttt{success} outputs therefore allows for submitting fully-compliant
 solvers without the need of a wrapper script, while still allowing entrants
-of SMT-COMP 2010 to run without changes.}.
+of previous competitions to run without changes.}.
 
@@
 
-The application track aims at evaluating SMT solvers when interacting
+The application track evaluates SMT solvers when interacting
 with an external verification framework, \eg, a model
@@
 checker repeatedly sends queries to the SMT solver, which in turn
-answers either sat or unsat.  In this interaction an SMT-solver is
+answers either \texttt{sat} or \texttt{unsat}.  In this interaction an SMT-solver is
 required to accept queries incrementally via its standard input channel.
@@
 In order to facilitate the evaluation of the solvers in this track, we
-propose to set up a ``simulation'' of the aforementioned interaction. In
+will set up a ``simulation'' of the aforementioned interaction, as was done in 2011. In
 particular each benchmark in the application track represents a realistic
@@
 Solvers must respond immediately to the commands sent by the trace executor, 
-with the answers defined in the SMT-LIB 2.0 format specification: that is,
+with the answers defined in the SMT-LIB 2.0 format specification, that is,
 with a \texttt{success} answer for 
@@
 A time limit is set for the whole execution of each application
-benchmark (consisting of multiple queries).
-
-\header{Scoring.}
-The score for each benchmark is a pair $\langle n,m\rangle$, with
-$n\in[0,N]$ an integral number of points scored for the benchmark,
-where $N$ is the number of \akey{check-sat} commands
-in the benchmark.  $m\in[0,T]$ is the (real-valued) time is seconds, where $T$ is
-the timeout.  The score for the benchmark is initialized with
-$\langle0,0\rangle$ and then computed as follows.
-\begin{itemize}
-\item A correctly-reported \texttt{sat} or \texttt{unsat} answer after
-  $s$~seconds (counting from the beginning of this particular
-  \akey{check-sat}) contributes $\langle1,s\rangle$ to the running
-  score.
-\item An answer of \texttt{unknown}, an unexpected answer, a crash, or a memory-out during
-  execution of the query, or a benchmark timeout, aborts the execution
-  of the benchmark and assigns the current value of the running score
-  to the benchmark.  (Recall that there is one timeout for the entire
-  benchmark; there are no individual timeouts for queries.)
-\item The first incorrect answer to a \akey{check-sat} command has the effect of terminating the
-  trace executor, and the returned score for the overall benchmark
-  will be $\langle0,0\rangle$, effectively canceling the running score.
-\end{itemize}
-
-For example, if a benchmark has 5~\akey{check-sat} commands, and a
-timeout of 100~seconds, and a solver solves the first four in
-10~seconds each, then times out on the fifth, then the solver's score
-is $\langle4,40\rangle$.  If another solver solves each of the first
-four in 10~seconds each, and the fifth in another 40~seconds, its
-score is $\langle5,80\rangle$.  If a third solver solves the first
-four queries in 2~seconds each, but incorrectly answers the fifth, its
-score is $\langle0,0\rangle$.
-
-As queries are only presented in order, this scoring system may mean
-that relatively ``easier'' queries are hidden behind more difficult
-ones located at the middle of the query sequence.
-
-Scores are compared lexicographically---a solver with a higher
-$n$-value wins, with the cumulative time only used to break ties.
-Benchmarks' scores are summed componentwise to form a solver's total
-score for the competition.
+benchmark (consisting of multiple queries).  We anticipate the
+timeout to be around 30~minutes (as it was in 2011).
+
+\subsection{Exhibition track}
+
+To encourage new entrants in any logic, we will have an exhibition track.
+Any solver submitted for ``competition'' in a non-competitive track will
+be executed on benchmarks for the logic divisions chosen for that solver.
+The results will be made public and the solver acknowledged. Any logic divisions
+for which there are benchmarks may be specified.
+
+\subsection{Unsat-core and proof-generation tracks}
+
+Applications such as software verification and model checking are enhanced by having
+proofs and unsatisfiable cores available from SMT solvers. Accordingly we are 
+encouraging solvers to add such capabilities by recognizing them in SMTCOMP 2012.
+
+The unsat-core track will evaluate solvers' capability to generate unsatisfiable cores for
+problems that are known to be unsatisfiable. Solvers will be measured by the smallness of
+the unsat core they return. The SMT-LIBv2 language accommodates this functionality by 
+providing two features: the ability to name top-level (asserted) formula and the ability to
+request an unsat-core after a check-sat command returns \texttt{unsat}. The unsat-core that
+is returned consists of a list of names of formula. In the competition we will check that the
+returned unsat-core is well-defined and is still unsatisfiable.
+
+Similarly, the competition will feature an exhibition track of proof-generating solvers. This is
+simply an exhibition track because there is as yet no SMT-LIB standard way to express proofs. We hope
+that encouraging the capability in solvers will also encourage a common proof format. The exhibition
+will count the number of benchmarks for which a solver successfully generates a proof; the proofs 
+themselves may be spot checked by hand or in a semi-automated fashion, depending on the format.
+
+TODO: What benchmark logics will be used.
 
@@
 
-We expect the problem divisions for SMT-COMP 2011 to include the following
+We expect the problem divisions for SMT-COMP 2012 to include the following
 SMT-LIB \emph{logics}.  These logics are specified in SMT-LIB format on the
@@
 
-\begin{itemize}
-\item QF\_UF: uninterpreted functions.
-\item QF\_RDL: real difference logic.
-\item QF\_IDL: integer difference logic.
-\item QF\_UFIDL: uninterpreted functions and integer difference logic.
-\item QF\_UFLIA: uninterpreted functions and linear integer arithmetic.
-\item QF\_UFLRA: uninterpreted functions and linear real arithmetic.
-\item QF\_UFNRA: uninterpreted functions and nonlinear real arithmetic.
-\item QF\_LRA: linear real arithmetic.
-\item QF\_LIA: linear integer arithmetic.
-\item QF\_NIA: nonlinear integer arithmetic.
-\item QF\_AX: arrays with extensionality.
-\item QF\_AUFLIA: arrays, uninterpreted functions and linear integer 
-                  arithmetic.
-\item QF\_BV: fixed-width bitvectors.
+Note that this year we are reducing the number of competitive benchmark divisions.
+Our reasons are to concentrate the competition and to focus development and attention
+on benchmarks that are more challenging and relevant to applications.
+
+\begin{itemize}
+
+\item QF\_BV: fixed-width bitvectors. This logic is important to ``bit-blasting'' model checking of software.
 \item QF\_AUFBV: arrays, fixed-width bitvectors and uninterpreted
-functions.
-\item LRA: (quantified) linear real arithmetic.
+functions. This logic is also key to software model-checking, but adds arrays (which can be used for memory models) and uninterpreted functions.
+
+\item QF\_UFLIA: uninterpreted functions and linear integer arithmetic (benchmarks may also be taken from  QF\_LIA). This division evaluates reasoning about integers.
+\item QF\_UFLRA: uninterpreted functions and linear real arithmetic (benchmarks may also be taken from  QF\_LRA). This division evaluates reasoning about real numbers.
+
 \item AUFLIA$+p$: (quantified) arrays, uninterpreted functions and 
-linear integer arithmetic, patterns included.
+linear integer arithmetic, patterns included. This and the subsequent divisions evaluate solvers' abilities to handle quantified formula.
 \item AUFLIA$-p$: (quantified) arrays, uninterpreted functions and 
 linear integer arithmetic, patterns not included.
-\item AUFLIRA: (quantified) arrays, uninterpreted functions and 
-mixed linear integer and real arithmetic.
-\item UFNIA$+p$: (quantified) uninterpreted functions and 
-nonlinear integer arithmetic, patterns included.
 \item AUFNIRA: (quantified) arrays, uninterpreted functions and 
-mixed nonlinear integer and real arithmetic.
+mixed nonlinear integer and real arithmetic
+
 \end{itemize}
@@
 will be drawn from the SMT-LIB library.  Any benchmarks added to
-SMT-LIB by the May 15th release (see the timeline in
+SMT-LIB by the April 15th release (see the timeline in
 Section~\ref{sec:timeline}) will be considered eligible.  SMT-COMP
@@
 \header{Benchmark availability.} % A first release of the competition
-Benchmarks will be made available within May 15th, 2011.
+Benchmarks will be made available by April 15, 2012.
 % A second and almost final release will be available on June 1st. 
 No additional
-benchmarks will be added after this date, but benchmarks can be
+benchmarks will be added after this date, but benchmarks may be
 modified or removed to fix possible bugs or other issues, or to adjust their difficulty score (see below). 
 The final release that will be used for the competition will be posted on June
-30th. The set of selected benchmarks will be published when the
+1. The set of selected benchmarks will be published when the
 competition begins.
@@
 tool.  \emph{Each top-level subdirectory within a division represents a distinct
-family.}  This represents a significant change from
-competition years before 2010, where
-\emph{terminal} subdirectories delineated families.
+family.}  
 %
+
 Each benchmark in SMT-LIB also has a \emph{category}.  There are four possible
@@
   tool~\cite{brummayer+09}.  The (exact version of this) tool will be
-  publicly available from the SMT-COMP~2011 web site before the
+  publicly available from the SMT-COMP~2012 web site before the
   competition.  Since these benchmarks are generated after the random
@@
   on SMT fuzzing.  The inclusion of these fuzzing benchmarks that are
-  not known in advance is intended to encourage (without requring)
+  not known in advance is intended to encourage (without requiring)
   solver implementors to test their solvers using fuzzing or similar
@@
 Before the selection process, each benchmark will be assigned a
-\emph{difficulty:} a number between 0.0 and 5.0 inclusive.  The
+\emph{difficulty:} a number between 0.0 and 5.0 inclusive, calculated as in 2011.  The
 difficulty for a particular benchmark will be assigned by running SMT
-solvers from the 2010 competition that finished in good
+solvers from previous competitions that finished in good
 standing and using the formula:
@@
 requires that $A=4$); the square is used to flatten out this curve sightly
-at the low end.  Figure~\ref{difficultyplot} shows this curve.
-
-\begin{figure}
-  \centerline{\epsffile{difficultyplot.eps}}
-  \caption{The shape of the difficulty assignment curve.}
-  \label{difficultyplot}
-\end{figure}
+at the low end.  
+%%Figure~\ref{difficultyplot} shows this curve.
+%%
+%%\begin{figure}
+%%  \centerline{\epsffile{difficultyplot.eps}}
+%%  \caption{The shape of the difficulty assignment curve.}
+%%  \label{difficultyplot}
+%%\end{figure}
 
@@
 %
-Additionally, certain benchmarks deemed inappropriate for competition
-may be cut by the organizers, and in some cases, representative subsets
-of benchmarks from a certain source may be included for the selection
-instead of all benchmarks from that source.
-%
 The selection
@@
 be available at \url{www.smtcomp.org}.
+%%% TODO: Make sure this tool is available.
 
@@
   division are always included, together with all benchmarks on which
-  at least one 2010 solver required more than 5~seconds.  \emph{This
+  at least one 2011 solver required more than 5~seconds.  \emph{This
     is intended to have the effect of retiring ``very easy''
-    benchmarks that were solved by every 2010 solver in less
+    benchmarks that were solved by every 2011 solver in less
     than 5~seconds, \emph{unless} doing so reduces the pool of
@@
 the opening value of the New York Stock Exchange Composite Index on
-July~12th
+June~25
 will be added to the other seeding values.  This helps provide transparency,
 by guaranteeing that the organizers cannot manipulate the seed in
-favor of their submitted solvers.  Benchmarks will also be slightly
-scrambled before the competition, using a simple benchmark scrambler %the same scrambler as last year,
+favor of or against any particular submitted solver.  Benchmarks will also be slightly
+scrambled before the competition, using a simple benchmark scrambler
 seeded with the same seed as the benchmark selector.  Both the
@@
 Benchmarks for the application track will be collected by the SMT-COMP organizers.
-Any benchmark available to the organizers by May 15th (see the timeline in
+Any benchmark available to the organizers by April 15th (see the timeline in
 Section~\ref{sec:timeline}) will be considered eligible.
@@
 A first release of the application track
-benchmarks will be made available within March 31st, 2011.
-More benchmarks can be collected, until May 15th.
+benchmarks will be made available March 15, 2012.
+More benchmarks can be collected, until April 15.
 No additional
@@
 The final release that will be used for the competition will be posted on 
-% rb 23/3: changed from June 30th to agree with sec 6.
-June 15th.
+June 1.
 
@@
 All the available benchmarks will be used for the competition. 
-For this first year of the application track, no difficulty will be assigned to the benchmarks.
+As was the case in 2011, no difficulty will be assigned to the benchmarks for the application track.
 Benchmarks will be slightly scrambled before the competition, using the same scrambler and 
@@
 For this year, the selection algorithm for the application track will be chosen after the
-deadline of May 15th, when the exact demographic of the benchmarks (collected with a usual
+ April 15th deadline, when the exact demographic of the benchmarks (collected with a usual
 ``call for benchmarks'') will be available.
+
+TODO: Divisions for unsat core and proof tracks
 
@@
 
-\begin{figure}
-\begin{center}
-\begin{tabular}{|l|c|c|}
-\hline \textbf{Reported} & \textbf{Correct?} &
-\textbf{Point/penalty}\\ \hline \texttt{unsat} & yes & +1 \\ \hline
-\texttt{unsat} & no & -8 \\ \hline \texttt{sat} & yes & +1 \\ \hline
-\texttt{sat} & no & -8 \\ \hline \texttt{unknown} & n.a. & 0 \\ \hline
-\emph{timeout} & n.a. & 0 \\ \hline
-\emph{abort} & n.a. & 0 \\ \hline
-\end{tabular}
-\end{center}
-\caption{\label{fig:points}Points and Penalties for the main and parallel tracks.}
-\end{figure}
-
+\header{Main and application tracks}
+The score for each benchmark is a triple $\langle e,n,m\rangle$, with
+$e$ a non-negative number of erroneous results,
+$n\in[0,N]$ an integral number of points scored for the benchmark,
+where $N$ is the number of \akey{check-sat} commands
+in the benchmark, and $m\in[0,T]$ is the (real-valued) time is seconds, where $T$ is
+the timeout.  Recall that main track benchmarks will have just one \akey{check-sat} command;
+application track benchmarks may have multiple \akey{check-sat} commands.
+The score for the benchmark is initialized with
+$\langle0,0,0\rangle$ and then computed as follows.
+\begin{itemize}
+\item A correctly-reported \texttt{sat} or \texttt{unsat} answer after
+  $s$~seconds (counting from the beginning of this particular
+  \akey{check-sat}) contributes $\langle0,1,s\rangle$ to the running
+  score.
+\item An answer of \texttt{unknown}, an unexpected answer, a crash, or a memory-out during
+  execution of the query, or a benchmark timeout, aborts the execution
+  of the benchmark and assigns the current value of the running score
+  to the benchmark.  (Recall that there is one timeout for the entire
+  benchmark; there are no individual timeouts for queries.)
+\item An incorrect answer to a \akey{check-sat} command has the effect of terminating the
+  evaluation of that individual benchmark, and the returned score for the benchmark
+  will be $\langle1,0,0\rangle$.
+\end{itemize}
+
+For example, if a benchmark has 5~\akey{check-sat} commands, and a
+timeout of 100~seconds, and a solver solves the first four in
+10~seconds each, then times out on the fifth, then the solver's score
+is $\langle0,4,40\rangle$.  If another solver solves each of the first
+four in 10~seconds each, and the fifth in another 40~seconds, its
+score is $\langle0,5,80\rangle$.  If a third solver solves the first
+four queries in 2~seconds each, but incorrectly answers the fifth, its
+score is $\langle1,0,0\rangle$.
+
+As queries are only presented in order, this scoring system may mean
+that relatively ``easier'' queries are hidden behind more difficult
+ones located at the middle of the query sequence.
+
+Benchmarks' scores are summed componentwise to form a solver's total
+score for the competition.
+Total scores are compared lexicographically---a score $\langle e,n,m\rangle$ is better than 
+$\langle e',n',m'\rangle$ iff $e < e'$ or ($e = e'$ and $n > n'$) or ($e = e'$ and $n = n'$ and $m < m'$).
+That is, fewer errors takes precedence over more correct solutions, which takes precedence over less time taken.
+
+\header{Unsat-core track}
+
+The unsat-core track will be scored as follows. The score for each benchmark is a triple $\langle e,n,m\rangle$, with
+$e$ a non-negative number of erroneous results,
+$n$ the number of formula in the unsat core for the benchmark,
+and $m\in[0,T]$ is the (real-valued) time is seconds, where $T$ is
+the timeout. 
+The score for the benchmark is initialized with
+$\langle0,0,0\rangle$ and then computed as follows.
+\begin{itemize}
+\item A correctly-reported unsat-core answer after
+  $s$~seconds (counting from the beginning of this particular
+  \akey{check-sat}) contributes $\langle0,n,s\rangle$ to the running
+  score, where $n$ is the number of formula in the unsat core.
+\item An answer of \texttt{unknown}, an unexpected answer, a crash, or a memory-out during
+  execution of the query, or a benchmark timeout, aborts the execution
+  of the benchmark and assigns a score of $\langle0,N,T\rangle$ for the benchmark, where
+  $N$ is the number of named asserted formula in the benchmark and $T$ is the timeout value.
+
+\item The score for an incorrect answer to a \akey{check-sat} or \akey{get-unsat-core} command 
+  will be $\langle1,N,T\rangle$, where
+  $N$ is the number of named asserted formula in the benchmark and $T$ is the timeout value.
+\end{itemize}
+
+Scores are summed and ordered as for the main track, except that lower $n$ values are preferred, rather than higher values.
+
+\header{Number of competitors}
 Winners in each Problem Division for which there are at least three
 entrants from distinct research groups competing will be taken to be
-those with the highest score. In addition to recognizing the overall
+those with the highest score and no erroneous results. In addition to recognizing the overall
 winner in each division, the top solver that provides its source code will also be
@@
 
-For the main and parallel tracks, the score will be computed according to the system of points and
-penalties in Figure~\ref{fig:points}. 
-As indicated, correct answers
-are awarded a positive number of points, while incorrect answers are
-penalized by assigning a negative number of points.  Timeouts, aborts,
-and reports of \texttt{unknown} are awarded zero points.
-%
-In the event of a tie
-in total number of points, the solver with the lowest average CPU time
-on formulas for which it gave a correct answer will be
-considered the winner.
-
-For the application track, the score will be computed according to the procedure described in \S\ref{sec:exec:application}.
-
-\penalty0
-
 \section{Timeline}
@@
 \begin{description}
-\item[March 31] First version of the benchmark library for the application track posted for comment.
+\item[March 15] First version of the benchmark library for the application track posted for comment.
   First version of the benchmark scrambler, benchmark selector and trace exector made available.
-\item[April 30] Final version of the benchmark scrambler, benchmark selector and trace exector made available.
-\item[May 15] No new benchmarks can be added after this date, but
+\item[April 15] Final version of the benchmark scrambler, benchmark selector and trace exector made available.
+\item[April 15] No new benchmarks can be added after this date, but
   problems with existing benchmarks may be fixed.
-\item[June 15] Benchmark libraries are frozen.
-\item[July 9 (7pm ET)] Solvers due via SMT-Exec (for
+\item[June 1] Benchmark libraries are frozen.
+\item[June 15 (7pm EDT)] Solvers due via StarExec (for
   all tracks), including system
   descriptions and magic numbers for benchmark scrambling.
-\item[July 11 (7pm ET)] Final versions due, fixing any last-minute
- bugs (this marks the end of the two-day grace period for
+\item[June 18 (7pm EDT)] Final versions due, fixing any last-minute
+ bugs (this marks the end of the grace period for
  submissions).
-\item[July 12] Opening value of NYSE Composite Index used to complete random seed.
-\item[July 14--20] Anticipated dates for SMT-COMP 2011.
+\item[June 22] Opening value of NYSE Composite Index used to complete random seed.
+\item[June 25--29] Anticipated dates for SMT-COMP 2012.
 \end{description}}
@@
 
+\section{Disclaimer}
+\begin{itemize}
+\item David Cok is the chief organizer of SMT-COMP 2012. He is 
+responsible for all policy and procedure decisions, such as these
+rules. He is not associated 
+with any group creating or submitting solvers. He has used solvers
+in industrial settings and is keenly interested to know which are the best.
+
+\item Alberto Griggio and Roberto Bruttomesso are co-organizers. They 
+were also co-organizers in 2011. They are responsible for bringing 
+recommendations from the previous year's experience. They will also 
+be validating the competition setup, checking benchmarks, and
+operating the competition. They are associated with solver groups
+that will be submitting the solvers 
+MathSat and OpenSMT, respectively.
+\end{itemize}
 \bibliographystyle{plain}

### 2012-01-27 rules/rules12.tex
Updates to web pages for announcements

@@
 
-\title{DRAFT DRAFT Satisfiability Modulo Theories Competition (SMT-COMP) 2012: Rules and 
-Procedures
+\title{Satisfiability Modulo Theories Competition (SMT-COMP) 2012: Rules and 
+Procedures \\
+\small{Draft for comment \\
+(comments due to organizers by 31 January 2012)}
 }
@@
 Roberto Bruttomesso\\
-Computer Science\\
-USI, Lugano (Switzerland)
+Dept. of Computer Science\\
+University of Milan, Milan (Italy)
 \and
@@
 GrammaTech, Inc. \\
-Ithaca, NY USA \\
+Ithaca, NY (USA) \\
 \and
@@
 \def\ie{\textit{i.e.}}
+
+\noindent This is a preliminary version of the 2012 SMT-COMP rules, issued for comment
+by potential participants. Comments should be emailed to the smtcomp mailing
+list or, if necessary, directly to the organizers. To receive full consideration,
+comments must be received by 31 January 2012.
 
@@
 
+Accordingly, researchers are highly encouraged to submit both new benchmarks
+and new or improved solvers to raise the level of competition and advance
+the state-of-the-art in automated SMT problem solving.
+
+Note that SMTCOMP 2012 has several tracks: a main track, a parallel track, an
+application track, an unsat-core track, and a proof-generation track.
+Within a track there are one or more divisions, where each division
+uses benchmarks from a specific SMT-LIB logic (or group of logics).
+
 The rest of this document, updated from the last year's
@@
 The principal changes from last year's version are the following:
-
-\begin{itemize}
-
-\item We are concentrating on just a few of the benchmark divisions this year.
+\begin{itemize}
+
+\item In the main and parallel competition, we are concentrating on just a few of the benchmark divisions this year.
   Some divisions, such as QF\_UF, are subsumed into more expressive
@@
   focus the competition on divisions of particular interest to
-  applications. To encourage new entrants, we will also accept
-  solvers against any benchmark class in an exhibition category:
+  applications. Solvers requesting to be run against other benchmark divisions are
+  welcome and will be run in exhibition mode:
   results will be displayed and publicly reported.
@@
 \item We are retaining and accenting last year's ``application track" and
-  encourage submission of benchmarks and competition against these
+  encourage submission of benchmarks for this track and competition against these
   benchmarks.
@@
 
-\item We are adding an ``unsat core" division of QF\_BV.
-
-\item We will have an exhibition division of solvers that produce proofs.
+\item We are adding an ``unsat core" track.
+
+\item We will have an exhibition track of solvers that produce proofs.
 
@@
 
-Additionally, non-competitive divisions and tracks will not be exhibited as
+Additionally, non-competitive divisions will not be exhibited as
 part of the competition: at least two competitors must be entered
@@
 must be marked for competition before the deadline;} uploading a solver
-to StarExec is not sufficient for competition entry if it's not marked
+to StarExec is not sufficient for competition entry if it is not marked
 as being a competition entrant.  The md5 checksums of competition
@@
 the right to start the competition itself at any time after the open
-of the New York Stock Exchange on the morning of June~22.  See
+of the New York Stock Exchange on the morning of June~20.  See
 Section~\ref{sec:timeline} below for a full timeline.
@@
 described in detail below.
-In exhibition tracks, solvers are evaluated and results posted, but no awards are announced.
-The other tracks are competition tracks; if there are sufficient entrants, a winner will be announced.
-\begin{itemize}
-\item a main track: sequential execution evaluated separately on benchmarks from each of several different logics
-\item a parallel track: parallel execution evaluated on the same benchmarks and the same divisions as the main track
-\item application track: evaluation on command scripts [TODO: FOR WHICH LOGICS]
-\item exhibition track: solvers (particularly new entrants) may be submitted against any benchmark division; the solver will be evaluated and the results posted, though not included in competition
+In exhibition divisions of these tracks, solvers are evaluated and results posted, but no awards are announced.
+The other divisions are competition divisions; if there are sufficient entrants, a winner will be announced.
+\begin{itemize}
+\item a main track: sequential execution evaluated separately on benchmarks from each of several different logics (some competitive and some exhibition divisions)
+\item a parallel track: parallel execution evaluated on the same benchmarks and the same divisions as the main track (some competitive and some exhibition divisions)
+\item application track: evaluation on command scripts (all divisions with sufficient benchmarks and entrants are competitive)
 \item unsat-core track: a competition among solvers capable of computing unsat cores
@@
 to run it before or after the main competition (depending on the
-estimated duration of the track).
+estimated duration of the track). We may choose to use an NYSE seed from a different date
+to accommodate an early start.
 
@@
 \item The (single) $\akey{set-logic}$ command setting the benchmark's
-logic is the first command.
+logic is the first command after any $\akey{set-option}$ commands described below.
 % rb 25/3: added
@@
 \item The $\akey{exit}$ command is the last command.
-\item There is exactly one $\akey{check-sat}$ command,
+\item For tracks other than the application track, there is exactly one $\akey{check-sat}$ command,
 following possibly several $\akey{assert}$ commands.
+\item For the application track, there are one or more \akey{check-sat} commands, 
+  each preceded by one or more \akey{assert} commands 
+  and zero or more \akey{push 1} commands, 
+  and followed by zero or more \akey{pop 1} commands.
+\item Scripts for the application track will have an initial $\akey{set-option :print-success true}$ command.
 \item There is at most one $\akey{set-info}$ command for \texttt{status}.
@@
   Moreover, all sorts declared with a $\akey{declare-sort}$ command must have zero arity.
-\item In the unsat-core competition, the $\akey{set-logic}$ command is preceded by a 
+\item In the unsat-core competition, the $\akey{set-logic}$ command is preceded by a \\
 $\akey{set-option :produce-unsat-cores true}$ command and the 
@@
 SMTLIBv2 standard.
-\item In the proof generation competition, the $\akey{set-logic}$ command is preceded by a 
+\item In the proof generation competition, the $\akey{set-logic}$ command is preceded by a \\
 $\akey{set-option :produce-proofs true}$ command and the 
 $\akey{check-sat}$ command is followed by a $\akey{get-proof}$ command.
-The $\akey{get-proof}$ command must return a proof in a solver-dependent format as an
-S-expression.
+The $\akey{get-proof}$ command must return a proof in a solver-dependent format made known to the organizers.
 \item No other commands besides the ones just mentioned may be used.
@@
 
+Solvers that register in non-competition logic divisions (cf. section \ref{sec:theories})
+will be run in an exhibition mode: results will be generated and publicly
+posted, but no awards will be announced.
+
 \header{Timeouts.} %
@@
 time limit.  The time limit is yet to be determined, but it is
-anticipated to be 20 minutes, as it was in 2011.  Solvers that take more than this
+anticipated to be 20 minutes, as it was in 2011.\footnote{The time limit may be adjusted once we understand the resources and capabilities of the StarExec service.} 
+Solvers that take more than this
 time limit will be killed.  Solvers are allowed to spawn other
@@
 any  ``\texttt{success}'' outputs will be 
-ignored\footnote{
+ignored.\footnote{
 Note that SMT-LIBv2 requires to produce a ``\texttt{success}'' answer
@@
 solvers without the need of a wrapper script, while still allowing entrants
-of previous competitions to run without changes.}.
+of previous competitions to run without changes.}
 
@@
 The commands will be taken from an \textbf{incremental benchmark script},
-which is an SMT-LIB 2.0 script which satisfies points 1., 2., 4.--7. of the definition of benchmark script given in \S\ref{sec:exec:main}, plus the following:
-
-\begin{enumerate}
-\item[3'.] There are one or more \akey{check-sat} commands, 
-  each preceded by one or more \akey{assert} commands 
-  and zero or more \akey{push 1} commands, 
-  and followed by zero or more \akey{pop 1} commands.
-\end{enumerate}
-
-\noindent
-Furthermore, the trace executor will send a single 
+which is an SMT-LIB 2.0 script which satisfies the rules for an application script given above.
+Note also that the trace executor will send a single 
 \akey{set-option :print-success true} command to the solver before 
@@
 \akey{set-option}, 
+\akey{set-logic}, 
 \akey{declare-sort}, 
@@
 commands,
-and with a \texttt{sat}, \texttt{unsat}, or \texttt{unknown} 
-for \akey{check-sat} commands.
+ with a \texttt{sat}, \texttt{unsat}, or \texttt{unknown} 
+for \akey{check-sat} commands, and with the defined responses for \akey{get-unsat-core} and \akey{get-proof} commands.
 
@@
 benchmark (consisting of multiple queries).  We anticipate the
-timeout to be around 30~minutes (as it was in 2011).
-
-\subsection{Exhibition track}
-
-To encourage new entrants in any logic, we will have an exhibition track.
-Any solver submitted for ``competition'' in a non-competitive track will
-be executed on benchmarks for the logic divisions chosen for that solver.
-The results will be made public and the solver acknowledged. Any logic divisions
-for which there are benchmarks may be specified.
+timeout to be around 30~minutes (as it was in 2011).\footnote{The timeout may be adjusted once we have experience with the abilities and resources of the StarExec service.}
 
@@
 that encouraging the capability in solvers will also encourage a common proof format. The exhibition
-will count the number of benchmarks for which a solver successfully generates a proof; the proofs 
-themselves may be spot checked by hand or in a semi-automated fashion, depending on the format.
-
-TODO: What benchmark logics will be used.
+will count the number of benchmarks for which a solver successfully generates a proof.
+Solvers submitted against this track must be accompanied by a description of the format of the 
+generated proofs. The organizers are considering how and whether to check the proofs (with automated tools);
+comment from teams submitting proof-generating solvers is welcome. %%TODO
+
+The organizers are still reviewing which logic divisions will be supported for the unsat-core and proof generating tracks; 
+those divisions will be announced later.
+Input from teams considering submitting unsat-core or proof generating solvers is welcome.
+%% TODO
 
@@
 
-We expect the problem divisions for SMT-COMP 2012 to include the following
+The competition divisions for SMT-COMP 2012 are planned to be the following
 SMT-LIB \emph{logics}.  These logics are specified in SMT-LIB format on the
-SMT-LIB web page.  Note that the ``QF\_'' prefix means the division's
-formulas are quantifier-free.  However, the organizers reserve the right to add
+SMT-LIB web page.  However, the organizers reserve the right to add
 (remove) divisions if (not) enough benchmarks and solvers exist for a
@@
 \item QF\_UFLRA: uninterpreted functions and linear real arithmetic (benchmarks may also be taken from  QF\_LRA). This division evaluates reasoning about real numbers.
+
+\item QF\_IDL: quantifier-free formulas to be
+  tested for satisfiability modulo a background theory of integer
+  arithmetic.  The syntax of atomic formulas is restricted to
+  difference logic, i.e. x - y op c, where op is either equality or
+  inequality and c is an integer constant. This division is included because it was highly popular in 2011.
 
@@
 When 5 or more solvers are used for the
-calculation, two times are dropped from the calculation of the average
-(one at the maximum and one at the minimum).  Solvers giving an
+calculation, the maximum and the minimum times are dropped from the calculation of the average.  Solvers giving an
 incorrect answer are not counted in the average; solvers crashing,
@@
 
+Once the StarExec service is evaluated, and if the organizers decide that
+the service has sufficient resources, the target number of benchmarks for 
+a division may be increased above 200, with all subpopulations being enlarged
+proportionately, insofar as there are sufficient benchmarks. The target number
+of benchmarks will not be raised if that requires reducing the timeout limits
+below the values used in 2011.
+
 The main purpose of the algorithm above is to have a balanced and complete set
@@
 the opening value of the New York Stock Exchange Composite Index on
-June~25
+a publicized day
 will be added to the other seeding values.  This helps provide transparency,
@@
 random seed as the main track. 
-% rb 25/3: added
-For this year, the selection algorithm for the application track will be chosen after the
+The selection algorithm for the application track will be chosen after the
  April 15th deadline, when the exact demographic of the benchmarks (collected with a usual
@@
 
-TODO: Divisions for unsat core and proof tracks
+\subsection{Benchmarks for the unsat-core and proof-generation tracks}
+
+These benchmarks will be selected from the pool of available and newly submitted benchmarks,
+adjusted to add formula naming for the unsat-core track. The organizers are still discussing
+which logic divisions to use.
+%%TODO: Divisions for unsat core and proof tracks
 
@@
 where $N$ is the number of \akey{check-sat} commands
-in the benchmark, and $m\in[0,T]$ is the (real-valued) time is seconds, where $T$ is
+in the benchmark, and $m\in[0,T]$ is the (real-valued) time in seconds, where $T$ is
 the timeout.  Recall that main track benchmarks will have just one \akey{check-sat} command;
@@
 \header{Number of competitors}
-Winners in each Problem Division for which there are at least three
+Winners in each competition Problem Division for which there are at least three
 entrants from distinct research groups competing will be taken to be
@@
  submissions).
-\item[June 22] Opening value of NYSE Composite Index used to complete random seed.
+\item[June 20] Opening value of NYSE Composite Index used to complete random seed.
 \item[June 25--29] Anticipated dates for SMT-COMP 2012.
@@
 be validating the competition setup, checking benchmarks, and
-operating the competition. They are associated with solver groups
-that will be submitting the solvers 
-MathSat and OpenSMT, respectively.
+operating the competition. They have been associated with solver groups
+that have submitted solvers to the competition, and may again in 2012 (in 2011, 
+MathSat and OpenSMT, respectively).
 \end{itemize}

### 2012-05-13 rules/rules12.tex
Updating rules to reflect our use of SMT-Exec instead of StarExec

@@
 \title{Satisfiability Modulo Theories Competition (SMT-COMP) 2012: Rules and 
-Procedures \\
-\small{Draft for comment \\
-(comments due to organizers by 31 January 2012)}
-}
+Procedures}
 
@@
 
-\noindent This is a preliminary version of the 2012 SMT-COMP rules, issued for comment
-by potential participants. Comments should be emailed to the smtcomp mailing
-list or, if necessary, directly to the organizers. To receive full consideration,
-comments must be received by 31 January 2012.
+\noindent Comments on this document should be emailed to the smtcomp mailing
+list or, if necessary, directly to the organizers.
 
@@
 \item In the main and parallel competition, we are concentrating on just a few of the benchmark divisions this year.
-  Some divisions, such as QF\_UF, are subsumed into more expressive
-  logics; others have received only light interest in past competitions. Our goal is to
+  Some divisions, such as QF\_LIA, are subsumed into more expressive
+  logics (QF\_UFLIA for QF\_LIA); others have received only light interest in past competitions. Our goal is to
   focus the competition on divisions of particular interest to
@@
 
-\item The competition will be run with a new StarExec service, replacing
-  the previous SMT-Exec service. At this writing, the new service is
-  still being completed and tested; it will be announced later. (The
-  previous service will be maintained in reserve.)
+\item The competition will be run with the SMT-Exec service used last year.
+  The organizers had expected to use a new StarExec service, replacing
+  the previous SMT-Exec service. However, at this writing the new service
+  is not yet available.
 
@@
 An entrant to SMT-COMP is an SMT solver
-submitted using the StarExec\footnote{StarExec is still under development as of 21 January 2012;
-updates on its progress and use will be posted on www.smtcomp.org and through
-the SMT-COMP mailing list. Statements in these rules may need correction once the UI for the service is completed.} service.  
-StarExec enables members of the
+submitted using the SMT-Exec\footnote{The organizers may switch to StarExec, 
+though Star-Exec is still under development as of 12 May 2012.} service.  
+The execution service enables members of the
 SMT research community to run solvers on jobs consisting of benchmarks
-from the SMT-LIB benchmark library.  Jobs are run on a computer
-cluster purchased with funds from a National Science Foundation
-Computing Research Infrastructure grant.  StarExec is provided free of
+from the SMT-LIB benchmark library.  Jobs are run on a shared computer
+cluster.  The execution service is provided free of
 charge, but it does require a minimal registration, which verifies an
@@
 may then upload their own solvers to run, or may run public solvers
-already uploaded to StarExec.  StarExec provides a variety of tabular
+already uploaded to the service.  The service provides a variety of tabular
 and graphical displays of results of solver executions, for
@@
 and application tracks 
-of SMT-COMP 2012, StarExec will be configured so that jobs are run on a 64-bit,
+of SMT-COMP 2012, the service will be configured so that jobs are run on a 64-bit,
 uniprocessor Linux kernel.  For the parallel-solver track, StarExec
@@
 For participation in SMT-COMP, a solver must be
-uploaded as a ``competition'' solver via the StarExec upload
+uploaded as a ``competition'' solver via the service's upload
 mechanism, or, alternatively, a previously-uploaded solver may be
 marked as a ``competition'' solver.  In either case, \emph{uploads
-must be marked for competition before the deadline;} uploading a solver
-to StarExec is not sufficient for competition entry if it is not marked
+must be marked for competition before the deadline}; uploading a solver
+to the service is not sufficient for competition entry if it is not marked
 as being a competition entrant.  The md5 checksums of competition
@@
 \header{System description.} %
-As part of their submission via StarExec,
+As part of their submission,
 SMT-COMP entrants must also include a short (1--2 pages) description of
@@
 
-The StarExec upload system will ask for the system description and
+The upload system will ask for the system description and
 the random seed when a solver is marked for competition, so
@@
 \paragraph{Main competition track.} %
-SMT-COMP entries must be submitted via StarExec by 7pm, Eastern U.S.
-time, June~15, 2012.  At that time the StarExec service will be
+SMT-COMP entries must be submitted via SMTExec by 7pm, Eastern U.S.
+time, June~15, 2012.  At that time the service will be
 closed to the public to prepare for the competition, with the
@@
 
-The versions that are present on StarExec at the conclusion of the
+The versions that are present on the execution service at the conclusion of the
 grace period will be the ones used for the competition, and versions
@@
 Solvers employing concurrency are invited to participate in a
-demonstration that will be run before the regular competition.
+demonstration that will be run in conjunction with the regular competition.
 Parallel solvers must be submitted by the same June~15th deadline,
@@
 \item unsat-core track: a competition among solvers capable of computing unsat cores
-\item proof-generation exhibition: an exhibition track for solvers capable of generating proofs
+\item proof-generation exhibition: an exhibition track for solvers capable of generating proofs (this track is tentative, given that the organizers must work with the SMT-Exec service)
 \end{itemize}
@@
 Similarly, the competition will feature an exhibition track of proof-generating solvers. This is
-simply an exhibition track because there is as yet no SMT-LIB standard way to express proofs. We hope
+simply an exhibition track because there is as yet no SMT-LIB standard way to express proofs and no
+means of checking the proofs. We hope
 that encouraging the capability in solvers will also encourage a common proof format. The exhibition
@@
 Solvers submitted against this track must be accompanied by a description of the format of the 
-generated proofs. The organizers are considering how and whether to check the proofs (with automated tools);
-comment from teams submitting proof-generating solvers is welcome. %%TODO
+generated proofs.
 
@@
 those divisions will be announced later.
-Input from teams considering submitting unsat-core or proof generating solvers is welcome.
+Input from teams considering submitting unsat-core or proof generating solvers is welcome. In addition, because
+the competition has had to revert to the SMT-Exec, the organizers may simply make the proof genreation demonstration 
+informational or omit it.
 %% TODO
@@
   equal numbers from each subdivision, so far as possible.
-  (In cases where \eg\ there are only two available slots and
+  (In cases where, \eg, there are only two available slots and
   they can be allocated to one of three subdivisions, they are allocated
@@
 \item[June 1] Benchmark libraries are frozen.
-\item[June 15 (7pm EDT)] Solvers due via StarExec (for
+\item[June 15 (7pm EDT)] Solvers due via SMTExec (for
   all tracks), including system

### 2014-01-24 rules/rules14.tex
Initial version (from 2012) of the 2014 rules

--- 2012-05-13 rules/rules12.tex
@@
 
+In addition, the organizers reserve the right to include in the benchmark population benchmarks
+from subsumed logics. For example, QF\_UFLIA may include some samples from QF\_LIA, and QF\_UFLRA may include some from QF\_LRA.
+We will not use benchmarks from QF\_UF in other divisions.
+
 \begin{itemize}
@@
 
-\item QF\_UFLIA: uninterpreted functions and linear integer arithmetic (benchmarks may also be taken from  QF\_LIA). This division evaluates reasoning about integers.
-\item QF\_UFLRA: uninterpreted functions and linear real arithmetic (benchmarks may also be taken from  QF\_LRA). This division evaluates reasoning about real numbers.
+\item QF\_UFLIA: uninterpreted functions and linear integer arithmetic. This division evaluates reasoning about integers.
+\item QF\_UFLRA: uninterpreted functions and linear real arithmetic. This division evaluates reasoning about real numbers.
 
@@
 $e$ a non-negative number of erroneous results,
-$n$ the number of formula in the unsat core for the benchmark,
+$n$ the reduction in number of formula in the unsat core for the benchmark,
 and $m\in[0,T]$ is the (real-valued) time is seconds, where $T$ is
@@
   \akey{check-sat}) contributes $\langle0,n,s\rangle$ to the running
-  score, where $n$ is the number of formula in the unsat core.
+  score, where $n$ is the reduction in number of formula in the unsat core (number of named formula in the benchmark minus
+  the number reported as the unsat core).
 \item An answer of \texttt{unknown}, an unexpected answer, a crash, or a memory-out during
   execution of the query, or a benchmark timeout, aborts the execution
-  of the benchmark and assigns a score of $\langle0,N,T\rangle$ for the benchmark, where
-  $N$ is the number of named asserted formula in the benchmark and $T$ is the timeout value.
-
-\item The score for an incorrect answer to a \akey{check-sat} or \akey{get-unsat-core} command 
-  will be $\langle1,N,T\rangle$, where
-  $N$ is the number of named asserted formula in the benchmark and $T$ is the timeout value.
-\end{itemize}
-
-Scores are summed and ordered as for the main track, except that lower $n$ values are preferred, rather than higher values.
+  of the benchmark and assigns a score of $\langle0,0,T\rangle$ for the benchmark, where
+  $T$ is the timeout value.
+
+\item The score for an incorrect answer to a \akey{check-sat} command 
+  will be $\langle1,0,T\rangle$, where
+  $T$ is the timeout value.
+\end{itemize}
+
+Scores are summed and ordered as for the main track.
 

### 2014-05-06 rules/rules14.tex
Updates for 2014.

@@
 
-\title{Satisfiability Modulo Theories Competition (SMT-COMP) 2012: Rules and 
+\title{Satisfiability Modulo Theories Competition (SMT-COMP) 2014: Rules and 
 Procedures}
@@
 \author{
-Roberto Bruttomesso\\
-Dept. of Computer Science\\
-University of Milan, Milan (Italy)
-\and
 David R. Cok \\
@@
 Ithaca, NY (USA) \\
+cok@frontiernet.net \\
 \and
-Alberto Griggio\\
-ES Division\\
-FBK, Trento (Italy)
+David Deharbe \\
+Federal University of Rio Grande do Norte \\
+Brazil \\
+David.Deharbe@loria.fr \\
+\and
+Tjark Weber \\
+Uppsala University, \\
+Sweden, \\
+tjark.weber@it.uu.se \\ 
 }
@@
 list or, if necessary, directly to the organizers.
+
+\section{Important dates and information}
+\begin{itemize}
+\item May 15 - deadline for new benchmarks
+\item May 25 - deadline for solver entrants
+\item June 1 - deadline for final versions of solvers (but no new entrants after May 25).
+\item June 17 - SMT workshop; completion of competition.
+\item SMT COMP mailing list: smt-comp@cs.nyu.edu
+\item signup site for mailing list: \url{cs.nyu.edu/mailman/listinfo/smt-comp}
+\item competition web site: \url{www.smtcomp.org}  or \url{smtcomp.sourceforge.net/2014}
+\end{itemize}
 
@@
 SMT-COMP web site, \url{www.smtcomp.org}, and in reports on previous
-competitions~(\cite{SMTCOMP-2008,BDOS08,SMTCOMP-FMSD,SMTCOMP-JAR}).
-SMT-COMP 2012 is affiliated with the SMT workshop (\url {http://smt2012.loria.fr/}) at the 6th International
-Joint Conference on Automated Reasoning~(IJCAR) (\url{http://ijcar.cs.manchester.ac.uk/}).
+competitions~(\cite{SMTCOMP-2008,BDOS08,SMTCOMP-FMSD,SMTCOMP-JAR,TBD-2012,TBD-2013}).
+SMT-COMP 2014 is affiliated with the SMT workshop (\url {http://smt2014.it.uu.se/}) at the co-located meetings of CAV, IJCAR, and SAT at FLoC 2014 (\url{http://vsl2014.at/}); the competition is part of the
+Olympic Games (\url{http://vsl2014.at/olympics/}).
 
@@
 
-Note that SMTCOMP 2012 has several tracks: a main track, a parallel track, an
-application track, an unsat-core track, and a proof-generation track.
+SMTCOMP 2014 will have two tracks: the conventional main track and a repeat of 2012's application track.
 Within a track there are one or more divisions, where each division
@@
 
-The rest of this document, updated from the last year's
+The rest of this document, revised from the previous year's
 version\footnote{Earlier versions of this document include contributions from
-Clark Barrett, Albert Oliveras, Aaron Stump, and Morgan Deters.},
-describes the rules and competition procedures for SMT-COMP~2012.
-The principal changes from last year's version are the following:
+Clark Barrett, Albert Oliveras, Aaron Stump, Morgan Deters, David Cok, Alberto Griggio, and Roberto Bruttomesso.},
+describes the rules and competition procedures for SMT-COMP~2014.
+The principal changes from last competition are the following:
 \begin{itemize}
-
-\item In the main and parallel competition, we are concentrating on just a few of the benchmark divisions this year.
-  Some divisions, such as QF\_LIA, are subsumed into more expressive
-  logics (QF\_UFLIA for QF\_LIA); others have received only light interest in past competitions. Our goal is to
-  focus the competition on divisions of particular interest to
-  applications. Solvers requesting to be run against other benchmark divisions are
-  welcome and will be run in exhibition mode:
-  results will be displayed and publicly reported.
+\item The competition will be run with StarExec. Accordingly we are simplifying the competition somewhat, since some of the infrastructure needs to be recreated.
+\item We will hold just a main and application track.
+[ The demonstration parallel solvers, unsat core, and proof generation tracks will be deferred until benchmarks and result analysis tools are reorganized.]
+\item In the main track, we will measure comparative performance within all divisions to which sufficient solvers are submitted.
 
@@
 
-\item The penalty for producing an incorrect result is increased. Competitors
-  producing all correct results are ranked above those producing
-  incorrect results (a ``soft" disqualification for unsound tools).
-
-\item We are adding an ``unsat core" track.
-
-\item We will have an exhibition track of solvers that produce proofs.
-
-\item The competition will be run with the SMT-Exec service used last year.
-  The organizers had expected to use a new StarExec service, replacing
-  the previous SMT-Exec service. However, at this writing the new service
-  is not yet available.
+\item In addition to the traditional SMTCOMP winners, we will recognize winners in other categories, as described below. 
+Also, importantly, the Olympic Games has an award ceremony (with actual medals). A selection of the SMTCOMP winners (as described below) will be awarded Olympic Games medals.
 
@@
 
-Additionally, non-competitive divisions will not be exhibited as
-part of the competition: at least two competitors must be entered
-into a division for it to run as part of the competition.
+All results of the competition will be made public. However, 
+winners will be declared only for divisions in which at least two solvers are submitted.
+Although the organizers may add other solvers for comparison purposes, only solvers that
+are explicitly submitted by their authors' are eligible to be designated as winners.
 If necessary, and based on final submissions, the organizers may elect to
@@
 
-As in SMT-COMP 2011, the 2012 version will incorporate a small number of
-random ``fuzzer-generated" instances (see below) to help promote
-attention to solver correctness.
-
 It is important for competitors to track discussions on the SMT-COMP mailing
@@
 An entrant to SMT-COMP is an SMT solver
-submitted using the SMT-Exec\footnote{The organizers may switch to StarExec, 
-though Star-Exec is still under development as of 12 May 2012.} service.  
+submitted by its authors using the Star-Exec (\url{http://www.starexec.org}) service.  
 The execution service enables members of the
@@
 cluster.  The execution service is provided free of
-charge, but it does require a minimal registration, which verifies an
-email address and prevents misuse of the service.  Registered users
+charge, but it does require registration to create a login account.  Registered users
 may then upload their own solvers to run, or may run public solvers
-already uploaded to the service.  The service provides a variety of tabular
-and graphical displays of results of solver executions, for
-comparison. For the main (sequential-solver)
-% rb 23/3: I guess also application track runs on 
-% the same clusters as sequential
-and application tracks 
-of SMT-COMP 2012, the service will be configured so that jobs are run on a 64-bit,
-uniprocessor Linux kernel.  For the parallel-solver track, StarExec
-will be configured so that jobs are run on a 64-bit, multiprocessor
-Linux kernel.
+already uploaded to the service.
 
 For participation in SMT-COMP, a solver must be
-uploaded as a ``competition'' solver via the service's upload
-mechanism, or, alternatively, a previously-uploaded solver may be
-marked as a ``competition'' solver.  In either case, \emph{uploads
-must be marked for competition before the deadline}; uploading a solver
-to the service is not sufficient for competition entry if it is not marked
-as being a competition entrant.  The md5 checksums of competition
-submissions will be public immediately after the deadline for competition
-entry has passed to ensure transparency, and the submissions themselves
-will be made public after the competition.  Source code need not be
-provided.  However, in order to encourage sharing of source code, extra
-recognition will be given to solvers providing source code distributions
-including recognition for the top such solver in each division.  Instructions
-for uploading solvers and machine specifications will be posted as soon
-as they are available.
+uploaded to Star-Exec, made publicly available, and the organizers informed of its presence {|em and thte logic divisions in which it is participating}.
+
+A submission must also include a 32-bit unsigned
+integer.  These numbers, collected from all submissions, are used
+to seed the pseudo-random benchmark selection algorithm, as well
+as the benchmark scrambler.
 
 \header{System description.} %
-As part of their submission,
-SMT-COMP entrants must also include a short (1--2 pages) description of
+As part of a submission,
+SMT-COMP entrants are encouraged to provide a short (1--2 pages) description of
 the system.  This should include a list of all authors of the system
@@
 include a URL for a web site for the submitted tool, but this is
-optional.  System descriptions must also include a 32-bit unsigned
-integer.  These numbers, collected from all submissions, are used
-to seed the pseudo-random benchmark selection algorithm, as well
-as the benchmark scrambler.
-
-The upload system will ask for the system description and
-the random seed when a solver is marked for competition, so
-their inclusion in the uploaded archive itself is optional.
+optional.
 
@@
 or more of its source code).  The organizers reserve the right to
-submit their own systems, or other systems of interest, to the
+include other systems of interest (such as entrants in previous competitions), to the
 competition.
@@
 A \emph{wrapper tool} is defined as any tool
-which calls an SMT solver not written by the author of the wrapper
-tool.  The other solver is called the \emph{wrapped tool}.  There are
-several rules governing wrapper tools that wrap tools that have been or could be submitted as independent entrants.\footnote{A wrapper
-for a wrapped tool that does not accept SMT-LIBv2 format is considered to simply be an SMT version of the underlying tool.}
-For the purposes of these rules,
-multiple versions of a wrapped tool are considered different tools.
-The goal of these rules is to require wrapper tools to outperform the
-tools they wrap (since otherwise, there is no apparent quantitative
-way to argue that the wrapper tool improves upon the wrapped tool).
-
-\begin{itemize}
-\item The name of the wrapper tool must end with ``+name'', where name
-is the name of the wrapped tool (\eg\ ``Flash+CVC3'' for a tool
-wrapping CVC3).
-
-\item If the wrapped tool is from last year's SMT-COMP or earlier, then for
-each division entered by the wrapper tool, if the wrapper tool does not place ahead, according to the scoring
-rules below, of last year's winner in that division, it will be disqualified
-from that division (but not necessarily from the whole competition).
-
-\item If the wrapped tool was released after last year's SMT-COMP,
-then the wrapper tool can be entered only if
-
-\begin{itemize}
-\item Permission has been given by the author of the wrapped tool
-
-\item The wrapped tool is submitted and entered in every division
-      in which the wrapper tool is entered.
-\end{itemize}
-
-For each division entered by the wrapper tool, if the wrapper tool
-does not place ahead of the wrapped tool in that division, it will be
-disqualified from that division.
-\end{itemize}
+which calls one or more SMT solvers not written by the author of the wrapper
+tool.  The other solvers are is called the \emph{wrapped} tools.  
+A wrapper tool must explicitly acknowledge any tools that it wraps.
+Its system description should make clear the technical innovations  by which the
+wrapper tool expects to improve on the wrapped tools.
 
@@
 \paragraph{Main competition track.} %
-SMT-COMP entries must be submitted via SMTExec by 7pm, Eastern U.S.
-time, June~15, 2012.  At that time the service will be
+SMT-COMP entries must be submitted via StarExec and email to the organizers by 7pm, Eastern U.S.
+time, May~25, 2014.  At that time new entrants will be
 closed to the public to prepare for the competition, with the
 exception that resubmissions of existing entries will be accepted
-until 7pm, Eastern U.S. time, June~18, 2012.  We strongly encourage
-participants to use this weekend grace period \emph{only} for the
+until 7pm, Eastern U.S. time, June~1, 2014.  We strongly encourage
+participants to use this grace period \emph{only} for the
 purpose of fixing any bugs that may be discovered and not for adding
 new features as there will be no opportunity to do extensive testing
-using StarExec after the original deadline on June~15.
+using StarExec after the original deadline on May~25.
 
@@
 the right to start the competition itself at any time after the open
-of the New York Stock Exchange on the morning of June~20.  See
+of the New York Stock Exchange on the morning of June~2.  See
 Section~\ref{sec:timeline} below for a full timeline.
+
+\paragraph{Parallel track}
+StarExec reports both cpu time and wall clock time.
+The main competition will be measured by cpu time taken across all processes and threads that are spawned by the starting process.
+For single-process executions the wall-clock time is typically slightly larger than the cpu time.
+Multi-threaded solvers will see reduced wall-clock times.
+While we will not run an explicit parallel track in 2014.
+We will recognize the solvers with the best wall-clock time in each division.
 
@@
 
-\paragraph{Parallel solver track.} %
-Solvers employing concurrency are invited to participate in a
-demonstration that will be run in conjunction with the regular competition.
-Parallel solvers must be submitted by the same June~15th deadline,
-with the same grace period for resubmission as in the regular
-competition.  Submissions to both the parallel solver track
-and the main competition are independent: participants must submit
-explicitly to both events to participate in both, and they may submit
-different (or differently configured) solvers to each.  Benchmarks may
-or may not be scrambled for this division.  Entrants should still
-include a system description, as for the regular competition.
-
-\medskip
-\noindent
-Note that the SMT-COMP organizers may include
-other (``historical'' or otherwise relevant) solvers in all the competition tracks for
-demonstration and comparison.  The organizers reserve the right to
-include or exclude such solvers, and to make simple modifications
-to historical sequential solvers to (na\"ively) take advantage of
-multiple processors 
-or to connect them with a parser for the SMT-LIB version 2.0 format
-(\eg\ by implementing a wrapper tool).
+The infrastructure for the application track is in the process of being recreated for StarExec.
+If it is not ready in time, the organizers may choose to drop this track or only run it as a demonstration track.
 
@@
 
-Solvers will be publicly evaluated in the following tracks, listed here and 
-described in detail below.
+Solvers will be publicly evaluated in the following tracks.
 In exhibition divisions of these tracks, solvers are evaluated and results posted, but no awards are announced.
@@
 \begin{itemize}
-\item a main track: sequential execution evaluated separately on benchmarks from each of several different logics (some competitive and some exhibition divisions)
-\item a parallel track: parallel execution evaluated on the same benchmarks and the same divisions as the main track (some competitive and some exhibition divisions)
+\item a main track: sequential execution evaluated separately on benchmarks from each of the logics for which there are benchmarks in StarExec.
 \item application track: evaluation on command scripts (all divisions with sufficient benchmarks and entrants are competitive)
-\item unsat-core track: a competition among solvers capable of computing unsat cores
-\item proof-generation exhibition: an exhibition track for solvers capable of generating proofs (this track is tentative, given that the organizers must work with the SMT-Exec service)
 \end{itemize}
@@
 We anticipate that the bulk of the main track of the competition will take place during
-the course of IJCAR 2012, from June~26 to the 29th.  Results will be
-announced in a special session of IJCAR, on the last day of the
-conference, as well as at the SMT workshop and on the SMT-COMP web site.  Intermediate results
+the weeks leading up to SMT 2014, from about June~2 to the July~17.  Results will be
+announced at SMT 2014 and in an awards ceremony scheduled by the Olympic Games coordinator.
+  Intermediate results
 will be regularly posted to the SMT-COMP website as the competition
@@
 
-If there are enough competitors to run the parallel track, we intend
-to run it before or after the main competition (depending on the
-estimated duration of the track). We may choose to use an NYSE seed from a different date
-to accommodate an early start.
-
 The organizers will prioritize the running of the competition tracks, and may shift the
 time period or order of the competition or exhibition tracks in order to complete SMT-COMP
-in the course of the IJCAR conference.
+prior to the SMT workshop and awards ceremony.
 
@@
 channel. The script is in the concrete syntax of the SMT-LIB format,
-version 2.0.  A benchmark script is essentially just the translation
-of a benchmark from the version 1.2 specification.  In more detail, a
-\textbf{benchmark script} is just a script where:
+version 2.0.   A
+\textbf{benchmark script} is just a text file containing a sequence of SMTLIBv2 commands in which:
 
@@
   Moreover, all sorts declared with a $\akey{declare-sort}$ command must have zero arity.
-\item In the unsat-core competition, the $\akey{set-logic}$ command is preceded by a \\
-$\akey{set-option :produce-unsat-cores true}$ command and the 
-$\akey{check-sat}$ command is followed by a $\akey{get-unsat-core}$ command.
-Also, some or all of the $\akey{assert}$ commands will assert named formula
-(for example, \akey{assert (! P :named F1)}). The $\akey{get-unsat-core}$
-command must return a parenthesized list of formula names, as specified by the 
-SMTLIBv2 standard.
-\item In the proof generation competition, the $\akey{set-logic}$ command is preceded by a \\
-$\akey{set-option :produce-proofs true}$ command and the 
-$\akey{check-sat}$ command is followed by a $\akey{get-proof}$ command.
-The $\akey{get-proof}$ command must return a proof in a solver-dependent format made known to the organizers.
+
 \item No other commands besides the ones just mentioned may be used.
@@
 
-\subsection{Main track and parallel track}
+\subsection{Main track}
 \label{sec:exec:main}
@@
 The main track competition will consist of selected benchmarks in each of the
-logic divisions given below.
+logic divisions.
 Each benchmark script will be presented to the standard input of the solver.
@@
 to indicate that it cannot determine satisfiability of the formula.
-For more detailed information on the output format, see the
-description on the StarExec ``Upload a Solver'' page.  %%%%%%% TODO: CHeck this and all referecnes to StarExec
+
+The main track competition uses a StarExec postprocessor (SMT2 results conserv) to accumulate the results.
 
@@
 time limit.  The time limit is yet to be determined, but it is
-anticipated to be 20 minutes, as it was in 2011.\footnote{The time limit may be adjusted once we understand the resources and capabilities of the StarExec service.} 
+anticipated to be 1500 seconds (25 minutes) of wall clock time and 6000 seconds of CPU time.\footnote{The time limit may be adjusted once we understand the resources and capabilities of the StarExec service and the number of competition solvers.}
+% TBD- TODO - how to constrain solvers to single processes?
 Solvers that take more than this
@@
 processes.  These will be killed at approximately the same time as the
-first started process, using the TreeLimitedRun script, developed for
-the CASC competition and available on the SMT-COMP web page.  A
+first started process.  A
 timeout scores the same as if the output is ``\texttt{unknown}''.
-%%%%%%%%%%% TODO: Clarify time limit
 
@@
 An abort scores the same as if the output is ``\texttt{unknown}''. 
-% rb 25/3: added
 Also, as a further measure to prevent misjudgments of solvers,
@@
 ignored.\footnote{
-Note that SMT-LIBv2 requires to produce a ``\texttt{success}'' answer
+Note that SMT-LIBv2 requires that a solver produce a ``\texttt{success}'' answer
 after each \akey{set-logic}, \akey{declare-sort}, \akey{declare-fun} and
@@
 In order to facilitate the evaluation of the solvers in this track, we
-will set up a ``simulation'' of the aforementioned interaction, as was done in 2011. In
+will set up a ``simulation'' of the aforementioned interaction, as was done in 2012. In
 particular each benchmark in the application track represents a realistic
@@
 benchmark (consisting of multiple queries).  We anticipate the
-timeout to be around 30~minutes (as it was in 2011).\footnote{The timeout may be adjusted once we have experience with the abilities and resources of the StarExec service.}
-
-\subsection{Unsat-core and proof-generation tracks}
-
-Applications such as software verification and model checking are enhanced by having
-proofs and unsatisfiable cores available from SMT solvers. Accordingly we are 
-encouraging solvers to add such capabilities by recognizing them in SMTCOMP 2012.
-
-The unsat-core track will evaluate solvers' capability to generate unsatisfiable cores for
-problems that are known to be unsatisfiable. Solvers will be measured by the smallness of
-the unsat core they return. The SMT-LIBv2 language accommodates this functionality by 
-providing two features: the ability to name top-level (asserted) formula and the ability to
-request an unsat-core after a check-sat command returns \texttt{unsat}. The unsat-core that
-is returned consists of a list of names of formula. In the competition we will check that the
-returned unsat-core is well-defined and is still unsatisfiable.
-
-Similarly, the competition will feature an exhibition track of proof-generating solvers. This is
-simply an exhibition track because there is as yet no SMT-LIB standard way to express proofs and no
-means of checking the proofs. We hope
-that encouraging the capability in solvers will also encourage a common proof format. The exhibition
-will count the number of benchmarks for which a solver successfully generates a proof.
-Solvers submitted against this track must be accompanied by a description of the format of the 
-generated proofs.
-
-The organizers are still reviewing which logic divisions will be supported for the unsat-core and proof generating tracks; 
-those divisions will be announced later.
-Input from teams considering submitting unsat-core or proof generating solvers is welcome. In addition, because
-the competition has had to revert to the SMT-Exec, the organizers may simply make the proof genreation demonstration 
-informational or omit it.
-%% TODO
+timeout to be around 25~minutes (as it has been in the past).\footnote{The timeout may be adjusted once we have experience with the abilities and resources of the StarExec service.}
 
@@
 
-The competition divisions for SMT-COMP 2012 are planned to be the following
-SMT-LIB \emph{logics}.  These logics are specified in SMT-LIB format on the
-SMT-LIB web page.  However, the organizers reserve the right to add
-(remove) divisions if (not) enough benchmarks and solvers exist for a
-particular division.
-
-Note that this year we are reducing the number of competitive benchmark divisions.
-Our reasons are to concentrate the competition and to focus development and attention
-on benchmarks that are more challenging and relevant to applications.
-
-In addition, the organizers reserve the right to include in the benchmark population benchmarks
+In 2012 the competition ran only some logics as competitive divisions.
+In 2014 we will revert to previous practice and run all logics as competitive divisions, if there are multiple solvers submitted.
+
+The organizers reserve the right to include in the benchmark population for a given logic benchmarks
 from subsumed logics. For example, QF\_UFLIA may include some samples from QF\_LIA, and QF\_UFLRA may include some from QF\_LRA.
@@
 
-\begin{itemize}
-
-\item QF\_BV: fixed-width bitvectors. This logic is important to ``bit-blasting'' model checking of software.
-\item QF\_AUFBV: arrays, fixed-width bitvectors and uninterpreted
-functions. This logic is also key to software model-checking, but adds arrays (which can be used for memory models) and uninterpreted functions.
-
-\item QF\_UFLIA: uninterpreted functions and linear integer arithmetic. This division evaluates reasoning about integers.
-\item QF\_UFLRA: uninterpreted functions and linear real arithmetic. This division evaluates reasoning about real numbers.
-
-\item QF\_IDL: quantifier-free formulas to be
-  tested for satisfiability modulo a background theory of integer
-  arithmetic.  The syntax of atomic formulas is restricted to
-  difference logic, i.e. x - y op c, where op is either equality or
-  inequality and c is an integer constant. This division is included because it was highly popular in 2011.
-
-\item AUFLIA$+p$: (quantified) arrays, uninterpreted functions and 
-linear integer arithmetic, patterns included. This and the subsequent divisions evaluate solvers' abilities to handle quantified formula.
-\item AUFLIA$-p$: (quantified) arrays, uninterpreted functions and 
-linear integer arithmetic, patterns not included.
-\item AUFNIRA: (quantified) arrays, uninterpreted functions and 
-mixed nonlinear integer and real arithmetic
-
-\end{itemize}
-
 \subsection{Main and parallel tracks}
@@
 Benchmark formulas for these divisions
-will be drawn from the SMT-LIB library.  Any benchmarks added to
-SMT-LIB by the April 15th release (see the timeline in
-Section~\ref{sec:timeline}) will be considered eligible.  SMT-COMP
+will be drawn from the SMT-LIB library. The deadline for new benchmarks is
+May 15. The organizers will be checking and curating these until June 1;
+the organizers reserve the option to exclude new benchmarks if any prove problematic for some reason.
+SMT-COMP
 attempts to give preference to benchmarks that are ``real-world,'' in
@@
 
-\header{Benchmark availability.} % A first release of the competition
-Benchmarks will be made available by April 15, 2012.
-% A second and almost final release will be available on June 1st. 
+\header{Benchmark availability.} % 
+A first release of the competition
+benchmarks will be made available by May 15, 2014.
+A second and almost final release will be available on June 1st. 
 No additional
@@
 
-  \noindent%\textbf{New for 2010:} 
-  Using the same random seed as
-  for benchmark selection and scrambling, 5 ``check'' benchmarks will
-  be randomly generated using Robert Brummayer's SMT fuzzing
-  tool~\cite{brummayer+09}.  The (exact version of this) tool will be
-  publicly available from the SMT-COMP~2012 web site before the
-  competition.  Since these benchmarks are generated after the random
-  seed is fixed, they cannot be known in advance to any competitors,
-  including the organizers.  The rationale for including these
-  benchmarks is to try to take a step towards stronger certification
-  that solvers are correct.  In future years, we envision SMT-COMP
-  requiring that solvers pass some kind of pre-qualifying round based
-  on SMT fuzzing.  The inclusion of these fuzzing benchmarks that are
-  not known in advance is intended to encourage (without requiring)
-  solver implementors to test their solvers using fuzzing or similar
-  bug-discovery techniques.
+%  \noindent%\textbf{New for 2010:} 
+%  Using the same random seed as
+%  for benchmark selection and scrambling, 5 ``check'' benchmarks will
+%  be randomly generated using Robert Brummayer's SMT fuzzing
+%  tool~\cite{brummayer+09}.  The (exact version of this) tool will be
+%  publicly available from the SMT-COMP~2012 web site before the
+%  competition.  Since these benchmarks are generated after the random
+%  seed is fixed, they cannot be known in advance to any competitors,
+%  including the organizers.  The rationale for including these
+%  benchmarks is to try to take a step towards stronger certification
+%  that solvers are correct.  In future years, we envision SMT-COMP
+%  requiring that solvers pass some kind of pre-qualifying round based
+%  on SMT fuzzing.  The inclusion of these fuzzing benchmarks that are
+%  not known in advance is intended to encourage (without requiring)
+%  solver implementors to test their solvers using fuzzing or similar
+%  bug-discovery techniques.
+
 \item \emph{industrial.} These benchmarks come from some real application
@@
 \header{Benchmark selection.} %
-Before the selection process, each benchmark will be assigned a
-\emph{difficulty:} a number between 0.0 and 5.0 inclusive, calculated as in 2011.  The
-difficulty for a particular benchmark will be assigned by running SMT
-solvers from previous competitions that finished in good
-standing and using the formula:
-
-\[\mathrm{difficulty} = {5\cdot\ln\!\left(1+A^2\right) \over \ln\!\left(1+30^2\right)}\]
-
-\noindent
-where $A$ is the average time for the solvers to correctly solve the
-instance (in minutes).  This computation of difficulties
-replaces a simpler formulation in earlier SMT-COMPs that didn't take
-into account the time solvers take.  This calculation of difficulty
-recognizes that problems requiring more time by many solvers are
-more difficult problems.  The logarithm is used to
-mark a larger change in difficulty (given a corresponding increase in
-solver average time) at smaller time scales than at higher ones (if $A=1$,
-difficulty is 0.5; at $A=1.7$, difficulty is 1.0; but a difficulty of 2.0
-requires that $A=4$); the square is used to flatten out this curve sightly
-at the low end.  
-%%Figure~\ref{difficultyplot} shows this curve.
-%%
-%%\begin{figure}
-%%  \centerline{\epsffile{difficultyplot.eps}}
-%%  \caption{The shape of the difficulty assignment curve.}
-%%  \label{difficultyplot}
-%%\end{figure}
-
-When 5 or more solvers are used for the
-calculation, the maximum and the minimum times are dropped from the calculation of the average.  Solvers giving an
-incorrect answer are not counted in the average; solvers crashing,
-timing out, or giving an unknown result are considered as taking 30
-minutes (which, with the above formula, pulls the difficulty
-toward~5.0).  If there are available solvers, but no average is
-defined under these rules, the difficulty shall be 5.0.  For new
-divisions, where there are no available solvers to compute the
-difficulty, the difficulty will be computed using whatever means are
-available to the organizers for that purpose.
-
-The following scheme will be used to choose competition benchmarks
-within each division.  Unknown-status benchmarks from SMT-LIB are
-considered ineligible for competition and are not used.
-%
-The selection
-is implemented by our benchmark selection tool, source for which will
-be available at \url{www.smtcomp.org}.
-%%% TODO: Make sure this tool is available.
-
+
+The benchmarks are assigned a difficulty. For 2014, the difficulty measure is the
+cpu time taken by the best performing solver in the 2013 SMTEVAL. These times will be posted 
+as soon after May 15 as possible.
+
+The selection of benchmarks for the competition will be biased towards more difficult benchmarks
+as follows. First, the benchmark pool is culled as follows:
 \begin{enumerate}
 
-\item \textbf{Check benchmarks included.} %
-  All benchmarks in category \emph{check} are included.
-
 \item \textbf{Retire very easy benchmarks.} %
-  The most difficult~300 non-check non-unknown benchmarks in each
-  division are always included, together with all benchmarks on which
-  at least one 2011 solver required more than 5~seconds.  \emph{This
-    is intended to have the effect of retiring ``very easy''
-    benchmarks that were solved by every 2011 solver in less
-    than 5~seconds, \emph{unless} doing so reduces the pool of
-    benchmarks for the division to less than~300.}
+  Eliminate benchmarks for which all of the current solvers in SMTEVAL-2103
+  solved the benchmark in under 5 seconds,
+  \emph{unless} doing so reduces the pool of
+    benchmarks for the division to less than~300.
 
@@
 
-\item\label{step:pool} \textbf{Division selection pools created.} %
-  For non-\emph{check} benchmarks, selection pools are created.
-  For benchmark families with $\leq200$ eligible,
-  non-\emph{check} benchmarks, all are added to this pool;
-  otherwise, 200 such benchmarks are added to the pool with the
-  following distribution:
-%
+\end{enumerate}
+
+Then, for each division, the benchmarks are divided into quintiles according to the difficulty measure.
+Then a random selection of N competition benchmarks is made as follows:
 \begin{itemize}
-  \item 20 with solution \textbf{sat} and difficulty on $\left[0,1\right]$
-  \item 20 with solution \textbf{sat} and difficulty on $\left(1,2\right]$
-  \item 20 with solution \textbf{sat} and difficulty on $\left(2,3\right]$
-  \item 20 with solution \textbf{sat} and difficulty on $\left(3,4\right]$
-  \item 20 with solution \textbf{sat} and difficulty on $\left(4,5\right]$
-  \item 20 with solution \textbf{unsat} and difficulty on $\left[0,1\right]$
-  \item 20 with solution \textbf{unsat} and difficulty on $\left(1,2\right]$
-  \item 20 with solution \textbf{unsat} and difficulty on $\left(2,3\right]$
-  \item 20 with solution \textbf{unsat} and difficulty on $\left(3,4\right]$
-  \item 20 with solution \textbf{unsat} and difficulty on $\left(4,5\right]$
+\item N*40\% are taken from the top quintile, if sufficient benchmarks are available
+\item additional benchmarks are taken from the second quintile, to produce N*55\% benchmarks, if sufficient benchmarks are available
+\item additional benchmarks are taken from the third quintile, to produce N*70\% benchmarks, if sufficient benchmarks are available
+\item additional benchmarks are taken from the fourth quintile, to produce N*85\% benchmarks, if sufficient benchmarks are available
+\item any remaining needed benchmarks are taken from the bottom quintile.
 \end{itemize}
-%
-  If 20 are not available in one of these subdivisions, all that are
-  available are added, and remaining slots are reallocated to the
-  others.  This process is iterated so that it is guaranteed that 200
-  benchmarks from the benchmark family are in the selection pool, in
-  equal numbers from each subdivision, so far as possible.
-  (In cases where, \eg, there are only two available slots and
-  they can be allocated to one of three subdivisions, they are allocated
-  randomly but are guaranteed to be allocated to \emph{distinct}
-  subdivisions.)
-
-\item\textbf{Category slot allocation.} %
-  Next, 200 slots are allocated for the division as follows:\footnote{The
-  number ``200'' is a guideline, and is expected to be used.  However, the
-  SMT-COMP organizers reserve the right to reduce this to an appropriate
-  value to ensure a timely end to the competition, and may do so on a
-  per-division basis.  The category allotments, etc., will remain the same
-  proportion of the total.}
-%
-  \begin{itemize}
-  \item 170 from category \emph{industrial}
-  \item 20 from category \emph{crafted}
-  \item 10 from category \emph{random}
-  \end{itemize}
-%
-  If there are fewer than 20 (respectively, 10) \emph{crafted} or
-  \emph{random} benchmarks in the division pool, more
-  \emph{industrial} slots are allocated to make 200 total for the
-  division.  If there are too few \emph{industrial} benchmarks in the
-  division pool, more \emph{crafted} slots are allocated to make 200
-  total for the division.  (In no division are there not enough of
-  both industrial and crafted benchmarks.)
-
-\item\textbf{Category subdivision slot allocation.} %
-  For each category, given that it has $n$ slots allocated to it,
-  the slot allocation is further subdivided as follows:
-%
-  \begin{itemize}
-  \item $\left\lfloor n\over10\right\rfloor$ slots for solution \textbf{sat} with difficulty on $\left[0,1\right]$
-  \item $\left\lfloor n\over10\right\rfloor$ slots for solution \textbf{sat} with difficulty on $\left(1,2\right]$
-  \item $\left\lfloor n\over10\right\rfloor$ slots for solution \textbf{sat} with difficulty on $\left(2,3\right]$
-  \item $\left\lfloor n\over10\right\rfloor$ slots for solution \textbf{sat} with difficulty on $\left(3,4\right]$
-  \item $\left\lfloor n\over10\right\rfloor$ slots for solution \textbf{sat} with difficulty on $\left(4,5\right]$
-  \item $\left\lfloor n\over10\right\rfloor$ slots for solution \textbf{unsat} with difficulty on $\left[0,1\right]$
-  \item $\left\lfloor n\over10\right\rfloor$ slots for solution \textbf{unsat} with difficulty on $\left(1,2\right]$
-  \item $\left\lfloor n\over10\right\rfloor$ slots for solution \textbf{unsat} with difficulty on $\left(2,3\right]$
-  \item $\left\lfloor n\over10\right\rfloor$ slots for solution \textbf{unsat} with difficulty on $\left(3,4\right]$
-  \item $\left\lfloor n\over10\right\rfloor$ slots for solution \textbf{unsat} with difficulty on $\left(4,5\right]$
-  \end{itemize}
-%
-  Remaining slots are allocated randomly to distinct subdivisions.
-  If there aren't enough benchmarks in the pool meeting one or more of
-  the above subdivision requirements for the category, the subdivision
-  allocation is reduced to the number available in the pool that meet
-  the requirements.  To make up the full category allotment, remaining
-  slots are allocated equally to subdivisions with enough benchmarks
-  in the pool meeting their requirements.  This process ensures that
-  all slots can be filled with benchmarks from the pool.
-
-\item\textbf{Benchmark selection.} %
-  Benchmarks from the pool are assigned randomly to slots.
-\end{enumerate}
-%
-In the end, up to 200 non-\emph{check} benchmarks per division are
-included in the competition, together with all the \emph{check}
-benchmarks.  Some divisions may have fewer than 200 non-\emph{check}
-benchmarks, in which case all of them are included using this selection
-scheme.
-
-Once the StarExec service is evaluated, and if the organizers decide that
-the service has sufficient resources, the target number of benchmarks for 
-a division may be increased above 200, with all subpopulations being enlarged
-proportionately, insofar as there are sufficient benchmarks. The target number
-of benchmarks will not be raised if that requires reducing the timeout limits
-below the values used in 2011.
+Within each quintile selection, if sufficient benchmarks are available, 85\% will be chosen from the industrial benchmarks,
+
+Since the organizers at this point are unsure how long a set of benchmarks may take (which will depend also on the number of solvers submitted), the competition will be run in {\em heats}.
+Some number $N$ of benchmarks will be selected and the competition run.
+If there is time, an additional $N_1$ benchmarks will be run, etc., until the end of the competition is reached.
+
+%Before the selection process, each benchmark will be assigned a
+%\emph{difficulty:} a number between 0.0 and 5.0 inclusive, calculated as in previous years.  The
+%difficulty for a particular benchmark will be assigned by running SMT
+%solvers from previous competitions that finished in good
+%standing and using the formula:
+%
+%\[\mathrm{difficulty} = {5\cdot\ln\!\left(1+A^2\right) \over \ln\!\left(1+30^2\right)}\]
+%
+%\noindent
+%where $A$ is the average time for the solvers to correctly solve the
+%instance (in minutes).  This computation of difficulties
+%replaces a simpler formulation in earlier SMT-COMPs that didn't take
+%into account the time solvers take.  This calculation of difficulty
+%recognizes that problems requiring more time by many solvers are
+%more difficult problems.  The logarithm is used to
+%mark a larger change in difficulty (given a corresponding increase in
+%solver average time) at smaller time scales than at higher ones (if $A=1$,
+%difficulty is 0.5; at $A=1.7$, difficulty is 1.0; but a difficulty of 2.0
+%requires that $A=4$); the square is used to flatten out this curve sightly
+%at the low end.  
+%%%Figure~\ref{difficultyplot} shows this curve.
+%%%
+%%%\begin{figure}
+%%%  \centerline{\epsffile{difficultyplot.eps}}
+%%%  \caption{The shape of the difficulty assignment curve.}
+%%%  \label{difficultyplot}
+%%%\end{figure}
+%
+%When 5 or more solvers are used for the
+%calculation, the maximum and the minimum times are dropped from the calculation of the average.  Solvers giving an
+%incorrect answer are not counted in the average; solvers crashing,
+%timing out, or giving an unknown result are considered as taking 30
+%minutes (which, with the above formula, pulls the difficulty
+%toward~5.0).  If there are available solvers, but no average is
+%defined under these rules, the difficulty shall be 5.0.  For new
+%divisions, where there are no available solvers to compute the
+%difficulty, the difficulty will be computed using whatever means are
+%available to the organizers for that purpose.
+%
+%The following scheme will be used to choose competition benchmarks
+%within each division.  Unknown-status benchmarks from SMT-LIB are
+%considered ineligible for competition and are not used.
+%
+%The selection
+%is implemented by our benchmark selection tool, source for which will
+%be available at \url{www.smtcomp.org}.
+%%%% TODO: Make sure this tool is available.
+%
+%\begin{enumerate}
+%
+%\item \textbf{Check benchmarks included.} %
+%  All benchmarks in category \emph{check} are included.
+%
+%\item \textbf{Retire very easy benchmarks.} %
+%  The most difficult~300 non-check non-unknown benchmarks in each
+%  division are always included, together with all benchmarks on which
+%  at least one 2011 solver required more than 5~seconds.  \emph{This
+%    is intended to have the effect of retiring ``very easy''
+%    benchmarks that were solved by every 2011 solver in less
+%    than 5~seconds, \emph{unless} doing so reduces the pool of
+%    benchmarks for the division to less than~300.}
+%
+%\item \textbf{Retire inappropriate benchmarks.} %
+%  The competition organizers will remove from the eligibility pool
+%  certain SMT-LIB benchmarks that are inappropriate or uninteresting
+%  for competition, or cut the size of certain benchmark families to
+%  avoid their over-representation.
+%
+%\item\label{step:pool} \textbf{Division selection pools created.} %
+%  For non-\emph{check} benchmarks, selection pools are created.
+%  For benchmark families with $\leq200$ eligible,
+%  non-\emph{check} benchmarks, all are added to this pool;
+%  otherwise, 200 such benchmarks are added to the pool with the
+%  following distribution:
+%%
+%  \begin{itemize}
+%  \item 20 with solution \textbf{sat} and difficulty on $\left[0,1\right]$
+%  \item 20 with solution \textbf{sat} and difficulty on $\left(1,2\right]$
+%  \item 20 with solution \textbf{sat} and difficulty on $\left(2,3\right]$
+%  \item 20 with solution \textbf{sat} and difficulty on $\left(3,4\right]$
+%  \item 20 with solution \textbf{sat} and difficulty on $\left(4,5\right]$
+%  \item 20 with solution \textbf{unsat} and difficulty on $\left[0,1\right]$
+%  \item 20 with solution \textbf{unsat} and difficulty on $\left(1,2\right]$
+%  \item 20 with solution \textbf{unsat} and difficulty on $\left(2,3\right]$
+%  \item 20 with solution \textbf{unsat} and difficulty on $\left(3,4\right]$
+%  \item 20 with solution \textbf{unsat} and difficulty on $\left(4,5\right]$
+%  \end{itemize}
+%%
+%  If 20 are not available in one of these subdivisions, all that are
+%  available are added, and remaining slots are reallocated to the
+%  others.  This process is iterated so that it is guaranteed that 200
+%  benchmarks from the benchmark family are in the selection pool, in
+%  equal numbers from each subdivision, so far as possible.
+%  (In cases where, \eg, there are only two available slots and
+%  they can be allocated to one of three subdivisions, they are allocated
+%  randomly but are guaranteed to be allocated to \emph{distinct}
+%  subdivisions.)
+%
+%\item\textbf{Category slot allocation.} %
+%  Next, 200 slots are allocated for the division as follows:\footnote{The
+%  number ``200'' is a guideline, and is expected to be used.  However, the
+%  SMT-COMP organizers reserve the right to reduce this to an appropriate
+%  value to ensure a timely end to the competition, and may do so on a
+%  per-division basis.  The category allotments, etc., will remain the same
+%  proportion of the total.}
+%%
+%  \begin{itemize}
+%  \item 170 from category \emph{industrial}
+%  \item 20 from category \emph{crafted}
+%  \item 10 from category \emph{random}
+%  \end{itemize}
+%%
+%  If there are fewer than 20 (respectively, 10) \emph{crafted} or
+%  \emph{random} benchmarks in the division pool, more
+%  \emph{industrial} slots are allocated to make 200 total for the
+%  division.  If there are too few \emph{industrial} benchmarks in the
+%  division pool, more \emph{crafted} slots are allocated to make 200
+%  total for the division.  (In no division are there not enough of
+%  both industrial and crafted benchmarks.)
+%
+%\item\textbf{Category subdivision slot allocation.} %
+%  For each category, given that it has $n$ slots allocated to it,
+%  the slot allocation is further subdivided as follows:
+%%
+%  \begin{itemize}
+%  \item $\left\lfloor n\over10\right\rfloor$ slots for solution \textbf{sat} with difficulty on $\left[0,1\right]$
+%  \item $\left\lfloor n\over10\right\rfloor$ slots for solution \textbf{sat} with difficulty on $\left(1,2\right]$
+%  \item $\left\lfloor n\over10\right\rfloor$ slots for solution \textbf{sat} with difficulty on $\left(2,3\right]$
+%  \item $\left\lfloor n\over10\right\rfloor$ slots for solution \textbf{sat} with difficulty on $\left(3,4\right]$
+%  \item $\left\lfloor n\over10\right\rfloor$ slots for solution \textbf{sat} with difficulty on $\left(4,5\right]$
+%  \item $\left\lfloor n\over10\right\rfloor$ slots for solution \textbf{unsat} with difficulty on $\left[0,1\right]$
+%  \item $\left\lfloor n\over10\right\rfloor$ slots for solution \textbf{unsat} with difficulty on $\left(1,2\right]$
+%  \item $\left\lfloor n\over10\right\rfloor$ slots for solution \textbf{unsat} with difficulty on $\left(2,3\right]$
+%  \item $\left\lfloor n\over10\right\rfloor$ slots for solution \textbf{unsat} with difficulty on $\left(3,4\right]$
+%  \item $\left\lfloor n\over10\right\rfloor$ slots for solution \textbf{unsat} with difficulty on $\left(4,5\right]$
+%  \end{itemize}
+%%
+%  Remaining slots are allocated randomly to distinct subdivisions.
+%  If there aren't enough benchmarks in the pool meeting one or more of
+%  the above subdivision requirements for the category, the subdivision
+%  allocation is reduced to the number available in the pool that meet
+%  the requirements.  To make up the full category allotment, remaining
+%  slots are allocated equally to subdivisions with enough benchmarks
+%  in the pool meeting their requirements.  This process ensures that
+%  all slots can be filled with benchmarks from the pool.
+%
+%\item\textbf{Benchmark selection.} %
+%  Benchmarks from the pool are assigned randomly to slots.
+%\end{enumerate}
+%%
+%In the end, up to 200 non-\emph{check} benchmarks per division are
+%included in the competition, together with all the \emph{check}
+%benchmarks.  Some divisions may have fewer than 200 non-\emph{check}
+%benchmarks, in which case all of them are included using this selection
+%scheme.
+%
+%Once the StarExec service is evaluated, and if the organizers decide that
+%the service has sufficient resources, the target number of benchmarks for 
+%a division may be increased above 200, with all subpopulations being enlarged
+%proportionately, insofar as there are sufficient benchmarks. The target number
+%of benchmarks will not be raised if that requires reducing the timeout limits
+%below the values used in 2011.
 
 The main purpose of the algorithm above is to have a balanced and complete set
-of benchmarks.  The one built-in bias is towards industrial rather than crafted
-or random benchmarks.  This reflects a desire by the organizers and agreed upon
+of benchmarks.  The  built-in bias is towards industrial rather than crafted
+or random benchmarks and towards more difficult benchmarks.
+  This reflects a desire by the organizers and agreed upon
 by the SMT community to emphasize problems that come from real applications.
@@
 Benchmarks for the application track will be collected by the SMT-COMP organizers.
-Any benchmark available to the organizers by April 15th (see the timeline in
-Section~\ref{sec:timeline}) will be considered eligible.
+Any benchmark available to the organizers by June 1st will be considered eligible.
 
@@
 A first release of the application track
-benchmarks will be made available March 15, 2012.
-More benchmarks can be collected, until April 15.
+benchmarks will be made available May 15, 2014.
+More benchmarks can be collected, until June 1.
 No additional
@@
 \header{Benchmark demographics and selection.} 
-All the available benchmarks will be used for the competition. 
-As was the case in 2011, no difficulty will be assigned to the benchmarks for the application track.
+A random selection of all the available benchmarks will be used for the competition. 
+As was the case in 2012, no difficulty will be assigned to the benchmarks for the application track.
 Benchmarks will be slightly scrambled before the competition, using the same scrambler and 
 random seed as the main track. 
-The selection algorithm for the application track will be chosen after the
- April 15th deadline, when the exact demographic of the benchmarks (collected with a usual
-``call for benchmarks'') will be available.
-
-\subsection{Benchmarks for the unsat-core and proof-generation tracks}
-
-These benchmarks will be selected from the pool of available and newly submitted benchmarks,
-adjusted to add formula naming for the unsat-core track. The organizers are still discussing
-which logic divisions to use.
-%%TODO: Divisions for unsat core and proof tracks
+If the organizers determine that there is adequate time to complete the competition, all of the benchmarks will be used.
+Otherwise a unbiased random subset will be used to ensure timely completion of the competition.
 
@@
 
-\header{Main and application tracks}
+\subsection{Main and application tracks}
+\header{Scoring}
 The score for each benchmark is a triple $\langle e,n,m\rangle$, with
@@
 where $N$ is the number of \akey{check-sat} commands
-in the benchmark, and $m\in[0,T]$ is the (real-valued) time in seconds, where $T$ is
+in the benchmark, and $m\in[0,T]$ is the (real-valued) (TBD - which kind of time) time in seconds, where $T$ is
 the timeout.  Recall that main track benchmarks will have just one \akey{check-sat} command;
@@
 
-\header{Unsat-core track}
-
-The unsat-core track will be scored as follows. The score for each benchmark is a triple $\langle e,n,m\rangle$, with
-$e$ a non-negative number of erroneous results,
-$n$ the reduction in number of formula in the unsat core for the benchmark,
-and $m\in[0,T]$ is the (real-valued) time is seconds, where $T$ is
-the timeout. 
-The score for the benchmark is initialized with
-$\langle0,0,0\rangle$ and then computed as follows.
-\begin{itemize}
-\item A correctly-reported unsat-core answer after
-  $s$~seconds (counting from the beginning of this particular
-  \akey{check-sat}) contributes $\langle0,n,s\rangle$ to the running
-  score, where $n$ is the reduction in number of formula in the unsat core (number of named formula in the benchmark minus
-  the number reported as the unsat core).
-\item An answer of \texttt{unknown}, an unexpected answer, a crash, or a memory-out during
-  execution of the query, or a benchmark timeout, aborts the execution
-  of the benchmark and assigns a score of $\langle0,0,T\rangle$ for the benchmark, where
-  $T$ is the timeout value.
-
-\item The score for an incorrect answer to a \akey{check-sat} command 
-  will be $\langle1,0,T\rangle$, where
-  $T$ is the timeout value.
-\end{itemize}
-
-Scores are summed and ordered as for the main track.
-
 \header{Number of competitors}
@@
 
+\subsection{Other recognitions}
+The organizers will also recognize the following contribution:
+\begin{itemize}
+\item {\em Best new entrant}. The best performing entrant from a new solver implementation team. as measured by the average of 
+(solver time)/(winning solver time) over the competition benchmarks.
+\item Others TBD
+\end{itemize}
+
+\subsection{Olympic Games medals}
+
+TBD
+
 \section{Timeline}
@@
 \begin{description}
-\item[March 15] First version of the benchmark library for the application track posted for comment.
-  First version of the benchmark scrambler, benchmark selector and trace exector made available.
-\item[April 15] Final version of the benchmark scrambler, benchmark selector and trace exector made available.
-\item[April 15] No new benchmarks can be added after this date, but
-  problems with existing benchmarks may be fixed.
-\item[June 1] Benchmark libraries are frozen.
-\item[June 15 (7pm EDT)] Solvers due via SMTExec (for
-  all tracks), including system
+\item[May 15] Deadline for benchmark contributions.
+  First version of the benchmark scrambler, benchmark selector and trace executor made available.
+\item[May 25] First versions of solver competitors are due to the organizers.
+\item[June 1] Final version of the benchmark scrambler, benchmark selector and trace executor made available.
+\item[June 1] Benchmark libraries are frozen; final versions of solver competitors due.
+\item[June 1 (7pm EDT)] Final versions of solvers due via StarExec (for
+  all tracks), including divisions being entered, system
   descriptions and magic numbers for benchmark scrambling.
-\item[June 18 (7pm EDT)] Final versions due, fixing any last-minute
- bugs (this marks the end of the grace period for
- submissions).
-\item[June 20] Opening value of NYSE Composite Index used to complete random seed.
-\item[June 25--29] Anticipated dates for SMT-COMP 2012.
+\item[June 2] Opening value of NYSE Composite Index used to complete random seed.
+\item[July 17] SMT 2014; end of competition.
 \end{description}}
@@
 
-Interested parties should subscribe to the SMT-COMP mailing list, a
-link to which is found at \url{www.smtcomp.org}.  Important
+Interested parties should subscribe to the SMT-COMP mailing list:
+.  Important
 late-breaking news and any necessary clarifications and edits to these
@@
 \begin{itemize}
-\item David Cok is the chief organizer of SMT-COMP 2012. He is 
+\item David Cok is the chief organizer of SMT-COMP 2014. He is 
 responsible for all policy and procedure decisions, such as these
@@
 
-\item Alberto Griggio and Roberto Bruttomesso are co-organizers. They 
-were also co-organizers in 2011. They are responsible for bringing 
-recommendations from the previous year's experience. They will also 
+\item David Deharbe and Tjark Weber are co-organizers. 
+They will  
 be validating the competition setup, checking benchmarks, and
-operating the competition. They have been associated with solver groups
-that have submitted solvers to the competition, and may again in 2012 (in 2011, 
-MathSat and OpenSMT, respectively).
+operating the competition. Deharbe is associated with the solver group producing the veriT solver.
 \end{itemize}

### 2014-05-07 rules/rules14.tex
Next draft of the 2014 rules.

@@
 
-\title{Satisfiability Modulo Theories Competition (SMT-COMP) 2014: Rules and 
+\title{DRAFT\\Satisfiability Modulo Theories Competition (SMT-COMP) 2014: Rules and 
 Procedures}
@@
 Tjark Weber \\
-Uppsala University, \\
-Sweden, \\
+Uppsala University \\
+Sweden \\
 tjark.weber@it.uu.se \\ 
@@
 \noindent Comments on this document should be emailed to the smtcomp mailing
-list or, if necessary, directly to the organizers.
+list or, if necessary, directly to the organizers (cf. email addresses in the following section and in the authors' affiliation information).
 
@@
 \item June 1 - deadline for final versions of solvers (but no new entrants after May 25).
-\item June 17 - SMT workshop; completion of competition.
-\item SMT COMP mailing list: smt-comp@cs.nyu.edu
+\item July 17 - SMT workshop; completion of competition.
+\item SMT-COMP mailing list: smt-comp@cs.nyu.edu
 \item signup site for mailing list: \url{cs.nyu.edu/mailman/listinfo/smt-comp}
@@
 SMT-COMP web site, \url{www.smtcomp.org}, and in reports on previous
-competitions~(\cite{SMTCOMP-2008,BDOS08,SMTCOMP-FMSD,SMTCOMP-JAR,TBD-2012,TBD-2013}).
+competitions~(\cite{SMTCOMP-2008,BDOS08,SMTCOMP-FMSD,SMTCOMP-JAR,SMTCOMP2012,SMTEVAL2013}).
 SMT-COMP 2014 is affiliated with the SMT workshop (\url {http://smt2014.it.uu.se/}) at the co-located meetings of CAV, IJCAR, and SAT at FLoC 2014 (\url{http://vsl2014.at/}); the competition is part of the
-Olympic Games (\url{http://vsl2014.at/olympics/}).
+FLoC Olympic Games (\url{http://vsl2014.at/olympics/}).
 
@@
 
-SMTCOMP 2014 will have two tracks: the conventional main track and a repeat of 2012's application track.
-Within a track there are one or more divisions, where each division
+SMT-COMP 2014 will have two tracks: the conventional main track and a repeat of 2012's application track.
+Within a track there are multiple divisions, where each division
 uses benchmarks from a specific SMT-LIB logic (or group of logics).
 
-The rest of this document, revised from the previous year's
-version\footnote{Earlier versions of this document include contributions from
-Clark Barrett, Albert Oliveras, Aaron Stump, Morgan Deters, David Cok, Alberto Griggio, and Roberto Bruttomesso.},
+The rest of this document, revised from the previous 
+version,\footnote{Earlier versions of this document include contributions from
+Clark Barrett, Albert Oliveras, Aaron Stump, Morgan Deters, David Cok, Alberto Griggio, and Roberto Bruttomesso.}
 describes the rules and competition procedures for SMT-COMP~2014.
-The principal changes from last competition are the following:
+The principal changes from the previous competition rules are the following:
 \begin{itemize}
-\item The competition will be run with StarExec. Accordingly we are simplifying the competition somewhat, since some of the infrastructure needs to be recreated.
-\item We will hold just a main and application track.
-[ The demonstration parallel solvers, unsat core, and proof generation tracks will be deferred until benchmarks and result analysis tools are reorganized.]
-\item In the main track, we will measure comparative performance within all divisions to which sufficient solvers are submitted.
+\item The competition will be run with StarExec (\url{www.starexec.org}). Accordingly we are simplifying the competition somewhat, since some of the infrastructure needs to be recreated.
+\item We will hold just a main and application track. [ The demonstration unsat core, and proof generation tracks will be deferred until benchmarks and result analysis tools are reorganized.]
+\item In the main track, we will measure comparative performance within all divisions to which at least two solvers are submitted.
+We will use the data to determine both sequential and parallel winners.
 
@@
 
-\item In addition to the traditional SMTCOMP winners, we will recognize winners in other categories, as described below. 
-Also, importantly, the Olympic Games has an award ceremony (with actual medals). A selection of the SMTCOMP winners (as described below) will be awarded Olympic Games medals.
+\item We will recognize winners as measured by number of benchmarks solved; we will also recognize best open source contributions and best new entrants, as described below. 
+Also, importantly, the FLoC Olympic Games is sponsoring award ceremonies (with actual medals). A selection of the SMT-COMP winners (as described below) will be awarded FLoC Olympic Games medals.
 
@@
 Although the organizers may add other solvers for comparison purposes, only solvers that
-are explicitly submitted by their authors' are eligible to be designated as winners.
-If necessary, and based on final submissions, the organizers may elect to
-combine competition divisions to make them competitive (such decisions will
-be made with input from the community).
+are explicitly submitted by their authors are eligible to be designated as winners.
 
@@
 For participation in SMT-COMP, a solver must be
-uploaded to Star-Exec, made publicly available, and the organizers informed of its presence {|em and thte logic divisions in which it is participating}.
-
+uploaded to Star-Exec, made publicly available, and the organizers informed of its presence {\em and the logic divisions in which it is participating}.
 A submission must also include a 32-bit unsigned
@@
 SMT-COMP entrants are encouraged to provide a short (1--2 pages) description of
-the system.  This should include a list of all authors of the system
-and their present institutional affiliations.  The programming
+the system.  This should include a list of all authors of the system,
+ their present institutional affiliations, and any appropriate acknowledgements.  The programming
 language(s) and basic SMT solving approach employed should be
@@
 SAT, translation to SAT, etc.).  System descriptions are encouraged to
-include a URL for a web site for the submitted tool, but this is
-optional.
+include a URL for a web site for the submitted tool.
 
 \header{Other systems.} %
-As in previous years, due to limitations on
-computational resources, the organizers reserve the right not to
-accept multiple versions of the same solver (defined as sharing 50\%
-or more of its source code).  The organizers reserve the right to
-include other systems of interest (such as entrants in previous competitions), to the
+The organizers' intent is to promote as wide a comparison among solver options as possible.
+However, if the number of solver submissions is too large for the
+computational resources available to the competition, the organizers reserve the right not to
+accept multiple versions of solvers from the same solver team.  The organizers also reserve the right to
+include other systems of interest (such as entrants in previous competitions) in the
 competition.
@@
 which calls one or more SMT solvers not written by the author of the wrapper
-tool.  The other solvers are is called the \emph{wrapped} tools.  
+tool.  The other solvers are called the \emph{wrapped} tools.  
 A wrapper tool must explicitly acknowledge any tools that it wraps.
@@
 
+%%%%%% Make main and parallel competitions together.
+
 \paragraph{Main competition track.} %
-SMT-COMP entries must be submitted via StarExec and email to the organizers by 7pm, Eastern U.S.
-time, May~25, 2014.  At that time new entrants will be
+SMT-COMP entries must be submitted via StarExec and email to the organizers by the end of May~25, 2014 (anywhere on earth).  At that time new entrants will be
 closed to the public to prepare for the competition, with the
 exception that resubmissions of existing entries will be accepted
-until 7pm, Eastern U.S. time, June~1, 2014.  We strongly encourage
+until the end of June~1, 2014 (anywhere on earth).  We strongly encourage
 participants to use this grace period \emph{only} for the
@@
 Section~\ref{sec:timeline} below for a full timeline.
-
-\paragraph{Parallel track}
-StarExec reports both cpu time and wall clock time.
-The main competition will be measured by cpu time taken across all processes and threads that are spawned by the starting process.
-For single-process executions the wall-clock time is typically slightly larger than the cpu time.
-Multi-threaded solvers will see reduced wall-clock times.
-While we will not run an explicit parallel track in 2014.
-We will recognize the solvers with the best wall-clock time in each division.
 
@@
 
-Solvers will be publicly evaluated in the following tracks.
-In exhibition divisions of these tracks, solvers are evaluated and results posted, but no awards are announced.
-The other divisions are competition divisions; if there are sufficient entrants, a winner will be announced.
-\begin{itemize}
-\item a main track: sequential execution evaluated separately on benchmarks from each of the logics for which there are benchmarks in StarExec.
-\item application track: evaluation on command scripts (all divisions with sufficient benchmarks and entrants are competitive)
-\end{itemize}
+Solvers will be publicly evaluated in the main and application tracks, each in several logic divisions. 
+All divisions with at least two solver entrants are competition divisions, i.e., a winner will be announced.
+The other divisions are exhibition divisions, i.e., solvers are evaluated and results posted, but no awards are announced.
 
@@
 We anticipate that the bulk of the main track of the competition will take place during
-the weeks leading up to SMT 2014, from about June~2 to the July~17.  Results will be
-announced at SMT 2014 and in an awards ceremony scheduled by the Olympic Games coordinator.
+the weeks leading up to SMT 2014, from about June~2 to July~17.  Results will be
+announced at SMT 2014 and in an awards ceremony scheduled by the FLoC Olympic Games coordinator.
   Intermediate results
@@
 %
-Participating solvers must read a single benchmark script (defined
-below, not part of the 2.0 standard), presented on its standard input
+Participating solvers must read a single benchmark script presented on its standard input
 channel. The script is in the concrete syntax of the SMT-LIB format,
-version 2.0.   A
+version 2.0, though with a restricted set of commands.   A
 \textbf{benchmark script} is just a text file containing a sequence of SMTLIBv2 commands in which:
@@
 website~\cite{SMT-LIB}.  Solvers will be given formulas just from the
-Problem Divisions indicated during their submission to SMT-Exec.
-Example benchmark scripts for several Problem Divisions are reported in the Appendix.
-Note that they are provided for illustrative purposes only: 
-please refer to the SMT-LIB format specification 
-and the above definition of benchmark script for the official specification 
-of the input format for SMT-COMP.
+Problem Divisions indicated during their submission to SMT-COMP.
 
@@
 
-The main track competition uses a StarExec postprocessor (SMT2 results conserv) to accumulate the results.
-
-Solvers that register in non-competition logic divisions (cf. section \ref{sec:theories})
-will be run in an exhibition mode: results will be generated and publicly
-posted, but no awards will be announced.
+The main track competition uses a StarExec postprocessor (named ``SMT2 results conserv") to accumulate the results.
 
@@
 Each SMT-COMP solver will be executed on an
-unloaded competition machine for each given formula, up to a fixed
+unloaded competition machine for each given benchmark, up to a fixed
 time limit.  The time limit is yet to be determined, but it is
-anticipated to be 1500 seconds (25 minutes) of wall clock time and 6000 seconds of CPU time.\footnote{The time limit may be adjusted once we understand the resources and capabilities of the StarExec service and the number of competition solvers.}
+anticipated to be 1500 seconds (25 minutes) of CPU time and the same limit on wall clock time.\footnote{The time limit may be adjusted once we understand the resources and capabilities of the StarExec service and the number of competition solvers.}
 % TBD- TODO - how to constrain solvers to single processes?
@@
 \medskip
-Solvers must respond immediately to the commands sent by the trace executor, 
+Solvers must respond to each command sent by the trace executor, 
 with the answers defined in the SMT-LIB 2.0 format specification, that is,
@@
  with a \texttt{sat}, \texttt{unsat}, or \texttt{unknown} 
-for \akey{check-sat} commands, and with the defined responses for \akey{get-unsat-core} and \akey{get-proof} commands.
+for \akey{check-sat} commands. There should be no \akey{get-unsat-core} or \akey{get-proof} commands in these benchmarks.
 
@@
 benchmark (consisting of multiple queries).  We anticipate the
-timeout to be around 25~minutes (as it has been in the past).\footnote{The timeout may be adjusted once we have experience with the abilities and resources of the StarExec service.}
+timeout to be around 25~minutes (as it has been in the past).\footnote{The time limit may be adjusted once we understand the resources and capabilities of the StarExec service and the number of competition solvers.}
 
@@
 In 2012 the competition ran only some logics as competitive divisions.
-In 2014 we will revert to previous practice and run all logics as competitive divisions, if there are multiple solvers submitted.
+In 2014 we will revert to previous practice and run each logic as a competitive division, if there are two or more solvers submitted.
 
-The organizers reserve the right to include in the benchmark population for a given logic benchmarks
-from subsumed logics. For example, QF\_UFLIA may include some samples from QF\_LIA, and QF\_UFLRA may include some from QF\_LRA.
-We will not use benchmarks from QF\_UF in other divisions.
-
-\subsection{Main and parallel tracks}
+\subsection{Main track}
 
 \header{Benchmark sources.} %
-Benchmark formulas for these divisions
+Benchmark formulas for each division of the main track
 will be drawn from the SMT-LIB library. The deadline for new benchmarks is
@@
 \header{Benchmark availability.} % 
-A first release of the competition
-benchmarks will be made available by May 15, 2014.
-A second and almost final release will be available on June 1st. 
-No additional
-benchmarks will be added after this date, but benchmarks may be
-modified or removed to fix possible bugs or other issues, or to adjust their difficulty score (see below). 
-The final release that will be used for the competition will be posted on June
-1. The set of selected benchmarks will be published when the
+The deadline for new benchmarks is May 15, 2014.
+The benchmarks will be made available as soon as possible after that, as they are checked and curated.
+The goal for completing the set of benchmarks is June 1.
+The set of selected benchmarks will be published when the
 competition begins.
@@
   cannot be represented beyond some maximum value, such as
-  $2^{31}-1$).
+  $(2^{31}-1)$).
 
@@
 The benchmarks are assigned a difficulty. For 2014, the difficulty measure is the
-cpu time taken by the best performing solver in the 2013 SMTEVAL. These times will be posted 
+CPU time taken by the best performing solver in the 2013 SMT-EVAL. These times will be posted 
 as soon after May 15 as possible.
@@
 \item \textbf{Retire very easy benchmarks.} %
-  Eliminate benchmarks for which all of the current solvers in SMTEVAL-2103
+  Eliminate benchmarks for which all of the current solvers in SMT-EVAL-2013
   solved the benchmark in under 5 seconds,
@@
 \item N*40\% are taken from the top quintile, if sufficient benchmarks are available
-\item additional benchmarks are taken from the second quintile, to produce N*55\% benchmarks, if sufficient benchmarks are available
-\item additional benchmarks are taken from the third quintile, to produce N*70\% benchmarks, if sufficient benchmarks are available
-\item additional benchmarks are taken from the fourth quintile, to produce N*85\% benchmarks, if sufficient benchmarks are available
+\item additional benchmarks are taken from the second quintile, to produce N*60\% benchmarks, if sufficient benchmarks are available
+\item additional benchmarks are taken from the third quintile, to produce N*75\% benchmarks, if sufficient benchmarks are available
+\item additional benchmarks are taken from the fourth quintile, to produce N*90\% benchmarks, if sufficient benchmarks are available
 \item any remaining needed benchmarks are taken from the bottom quintile.
 \end{itemize}
-Within each quintile selection, if sufficient benchmarks are available, 85\% will be chosen from the industrial benchmarks,
+Within each quintile selection,
+\begin{itemize}
+\item if the industrial benchmarks comprise less than 85\% of the benchmarks in that quintile, 85\% will be chosen from the industrial benchmarks (if a sufficient number are available), and the others from the population of random and crafted benchmarks;
+\item if the industrial benchmarks comprise at least 85\% of the benchmarks in that quintile, the benchmarks are chosen at random from the population of industrial, random and crafted benchmarks in that quintile.
+\end{itemize}
 
 Since the organizers at this point are unsure how long a set of benchmarks may take (which will depend also on the number of solvers submitted), the competition will be run in {\em heats}.
-Some number $N$ of benchmarks will be selected and the competition run.
-If there is time, an additional $N_1$ benchmarks will be run, etc., until the end of the competition is reached.
-
-%Before the selection process, each benchmark will be assigned a
-%\emph{difficulty:} a number between 0.0 and 5.0 inclusive, calculated as in previous years.  The
-%difficulty for a particular benchmark will be assigned by running SMT
-%solvers from previous competitions that finished in good
-%standing and using the formula:
-%
-%\[\mathrm{difficulty} = {5\cdot\ln\!\left(1+A^2\right) \over \ln\!\left(1+30^2\right)}\]
-%
-%\noindent
-%where $A$ is the average time for the solvers to correctly solve the
-%instance (in minutes).  This computation of difficulties
-%replaces a simpler formulation in earlier SMT-COMPs that didn't take
-%into account the time solvers take.  This calculation of difficulty
-%recognizes that problems requiring more time by many solvers are
-%more difficult problems.  The logarithm is used to
-%mark a larger change in difficulty (given a corresponding increase in
-%solver average time) at smaller time scales than at higher ones (if $A=1$,
-%difficulty is 0.5; at $A=1.7$, difficulty is 1.0; but a difficulty of 2.0
-%requires that $A=4$); the square is used to flatten out this curve sightly
-%at the low end.  
-%%%Figure~\ref{difficultyplot} shows this curve.
-%%%
-%%%\begin{figure}
-%%%  \centerline{\epsffile{difficultyplot.eps}}
-%%%  \caption{The shape of the difficulty assignment curve.}
-%%%  \label{difficultyplot}
-%%%\end{figure}
-%
-%When 5 or more solvers are used for the
-%calculation, the maximum and the minimum times are dropped from the calculation of the average.  Solvers giving an
-%incorrect answer are not counted in the average; solvers crashing,
-%timing out, or giving an unknown result are considered as taking 30
-%minutes (which, with the above formula, pulls the difficulty
-%toward~5.0).  If there are available solvers, but no average is
-%defined under these rules, the difficulty shall be 5.0.  For new
-%divisions, where there are no available solvers to compute the
-%difficulty, the difficulty will be computed using whatever means are
-%available to the organizers for that purpose.
-%
-%The following scheme will be used to choose competition benchmarks
-%within each division.  Unknown-status benchmarks from SMT-LIB are
-%considered ineligible for competition and are not used.
-%
-%The selection
-%is implemented by our benchmark selection tool, source for which will
-%be available at \url{www.smtcomp.org}.
-%%%% TODO: Make sure this tool is available.
-%
-%\begin{enumerate}
-%
-%\item \textbf{Check benchmarks included.} %
-%  All benchmarks in category \emph{check} are included.
-%
-%\item \textbf{Retire very easy benchmarks.} %
-%  The most difficult~300 non-check non-unknown benchmarks in each
-%  division are always included, together with all benchmarks on which
-%  at least one 2011 solver required more than 5~seconds.  \emph{This
-%    is intended to have the effect of retiring ``very easy''
-%    benchmarks that were solved by every 2011 solver in less
-%    than 5~seconds, \emph{unless} doing so reduces the pool of
-%    benchmarks for the division to less than~300.}
-%
-%\item \textbf{Retire inappropriate benchmarks.} %
-%  The competition organizers will remove from the eligibility pool
-%  certain SMT-LIB benchmarks that are inappropriate or uninteresting
-%  for competition, or cut the size of certain benchmark families to
-%  avoid their over-representation.
-%
-%\item\label{step:pool} \textbf{Division selection pools created.} %
-%  For non-\emph{check} benchmarks, selection pools are created.
-%  For benchmark families with $\leq200$ eligible,
-%  non-\emph{check} benchmarks, all are added to this pool;
-%  otherwise, 200 such benchmarks are added to the pool with the
-%  following distribution:
-%%
-%  \begin{itemize}
-%  \item 20 with solution \textbf{sat} and difficulty on $\left[0,1\right]$
-%  \item 20 with solution \textbf{sat} and difficulty on $\left(1,2\right]$
-%  \item 20 with solution \textbf{sat} and difficulty on $\left(2,3\right]$
-%  \item 20 with solution \textbf{sat} and difficulty on $\left(3,4\right]$
-%  \item 20 with solution \textbf{sat} and difficulty on $\left(4,5\right]$
-%  \item 20 with solution \textbf{unsat} and difficulty on $\left[0,1\right]$
-%  \item 20 with solution \textbf{unsat} and difficulty on $\left(1,2\right]$
-%  \item 20 with solution \textbf{unsat} and difficulty on $\left(2,3\right]$
-%  \item 20 with solution \textbf{unsat} and difficulty on $\left(3,4\right]$
-%  \item 20 with solution \textbf{unsat} and difficulty on $\left(4,5\right]$
-%  \end{itemize}
-%%
-%  If 20 are not available in one of these subdivisions, all that are
-%  available are added, and remaining slots are reallocated to the
-%  others.  This process is iterated so that it is guaranteed that 200
-%  benchmarks from the benchmark family are in the selection pool, in
-%  equal numbers from each subdivision, so far as possible.
-%  (In cases where, \eg, there are only two available slots and
-%  they can be allocated to one of three subdivisions, they are allocated
-%  randomly but are guaranteed to be allocated to \emph{distinct}
-%  subdivisions.)
-%
-%\item\textbf{Category slot allocation.} %
-%  Next, 200 slots are allocated for the division as follows:\footnote{The
-%  number ``200'' is a guideline, and is expected to be used.  However, the
-%  SMT-COMP organizers reserve the right to reduce this to an appropriate
-%  value to ensure a timely end to the competition, and may do so on a
-%  per-division basis.  The category allotments, etc., will remain the same
-%  proportion of the total.}
-%%
-%  \begin{itemize}
-%  \item 170 from category \emph{industrial}
-%  \item 20 from category \emph{crafted}
-%  \item 10 from category \emph{random}
-%  \end{itemize}
-%%
-%  If there are fewer than 20 (respectively, 10) \emph{crafted} or
-%  \emph{random} benchmarks in the division pool, more
-%  \emph{industrial} slots are allocated to make 200 total for the
-%  division.  If there are too few \emph{industrial} benchmarks in the
-%  division pool, more \emph{crafted} slots are allocated to make 200
-%  total for the division.  (In no division are there not enough of
-%  both industrial and crafted benchmarks.)
-%
-%\item\textbf{Category subdivision slot allocation.} %
-%  For each category, given that it has $n$ slots allocated to it,
-%  the slot allocation is further subdivided as follows:
-%%
-%  \begin{itemize}
-%  \item $\left\lfloor n\over10\right\rfloor$ slots for solution \textbf{sat} with difficulty on $\left[0,1\right]$
-%  \item $\left\lfloor n\over10\right\rfloor$ slots for solution \textbf{sat} with difficulty on $\left(1,2\right]$
-%  \item $\left\lfloor n\over10\right\rfloor$ slots for solution \textbf{sat} with difficulty on $\left(2,3\right]$
-%  \item $\left\lfloor n\over10\right\rfloor$ slots for solution \textbf{sat} with difficulty on $\left(3,4\right]$
-%  \item $\left\lfloor n\over10\right\rfloor$ slots for solution \textbf{sat} with difficulty on $\left(4,5\right]$
-%  \item $\left\lfloor n\over10\right\rfloor$ slots for solution \textbf{unsat} with difficulty on $\left[0,1\right]$
-%  \item $\left\lfloor n\over10\right\rfloor$ slots for solution \textbf{unsat} with difficulty on $\left(1,2\right]$
-%  \item $\left\lfloor n\over10\right\rfloor$ slots for solution \textbf{unsat} with difficulty on $\left(2,3\right]$
-%  \item $\left\lfloor n\over10\right\rfloor$ slots for solution \textbf{unsat} with difficulty on $\left(3,4\right]$
-%  \item $\left\lfloor n\over10\right\rfloor$ slots for solution \textbf{unsat} with difficulty on $\left(4,5\right]$
-%  \end{itemize}
-%%
-%  Remaining slots are allocated randomly to distinct subdivisions.
-%  If there aren't enough benchmarks in the pool meeting one or more of
-%  the above subdivision requirements for the category, the subdivision
-%  allocation is reduced to the number available in the pool that meet
-%  the requirements.  To make up the full category allotment, remaining
-%  slots are allocated equally to subdivisions with enough benchmarks
-%  in the pool meeting their requirements.  This process ensures that
-%  all slots can be filled with benchmarks from the pool.
-%
-%\item\textbf{Benchmark selection.} %
-%  Benchmarks from the pool are assigned randomly to slots.
-%\end{enumerate}
-%%
-%In the end, up to 200 non-\emph{check} benchmarks per division are
-%included in the competition, together with all the \emph{check}
-%benchmarks.  Some divisions may have fewer than 200 non-\emph{check}
-%benchmarks, in which case all of them are included using this selection
-%scheme.
-%
-%Once the StarExec service is evaluated, and if the organizers decide that
-%the service has sufficient resources, the target number of benchmarks for 
-%a division may be increased above 200, with all subpopulations being enlarged
-%proportionately, insofar as there are sufficient benchmarks. The target number
-%of benchmarks will not be raised if that requires reducing the timeout limits
-%below the values used in 2011.
+For each division, some number $N$ of benchmarks will be selected as described and randomly divided into a number of heats.
+The heats will be run in order.
+If the competition ends before all heats have completed, the remaining heats will be ignored.
+All benchmarks will be chosen at the beginning (that is, without reference to the results of any given heat).
 
@@
 the opening value of the New York Stock Exchange Composite Index on
-a publicized day
+the first day the exchange is open on or after June 2
 will be added to the other seeding values.  This helps provide transparency,
@@
 Benchmarks for the application track will be collected by the SMT-COMP organizers.
-Any benchmark available to the organizers by June 1st will be considered eligible.
+Any benchmark available to the organizers by May 15 will be considered eligible.
 
@@
 benchmarks will be made available May 15, 2014.
-More benchmarks can be collected, until June 1.
 No additional
@@
 modified or removed to fix possible bugs or other issues. 
-The final release that will be used for the competition will be posted on 
-June 1.
+The final selection that will be used for the competition will be posted when the competition begins.
 
@@
 If the organizers determine that there is adequate time to complete the competition, all of the benchmarks will be used.
-Otherwise a unbiased random subset will be used to ensure timely completion of the competition.
+Otherwise an unbiased random subset will be used to ensure timely completion of the competition.
 
@@
 
-\subsection{Main and application tracks}
-\header{Scoring}
+\subsection{Scoring}
+
 The score for each benchmark is a triple $\langle e,n,m\rangle$, with
-$e$ a non-negative number of erroneous results,
+$e$ a non-negative number of erroneous results (usually 0, possibly 1 for main track benchmarks, and possibly more than one for application benchmarks),
 $n\in[0,N]$ an integral number of points scored for the benchmark,
 where $N$ is the number of \akey{check-sat} commands
-in the benchmark, and $m\in[0,T]$ is the (real-valued) (TBD - which kind of time) time in seconds, where $T$ is
+in the benchmark, and $m\in[0,T]$ is the (real-valued) CPU time in seconds, where $T$ is
 the timeout.  Recall that main track benchmarks will have just one \akey{check-sat} command;
 application track benchmarks may have multiple \akey{check-sat} commands.
-The score for the benchmark is initialized with
-$\langle0,0,0\rangle$ and then computed as follows.
+
+\header{Main track - sequential mode.}
+For the main track, the score on a given benchmark is the single $\langle e,n,m\rangle$ triple, with $m$ being the CPU time it takes to process the benchmark, that is, until the solver process terminates, and
 \begin{itemize}
-\item A correctly-reported \texttt{sat} or \texttt{unsat} answer after
-  $s$~seconds (counting from the beginning of this particular
-  \akey{check-sat}) contributes $\langle0,1,s\rangle$ to the running
-  score.
-\item An answer of \texttt{unknown}, an unexpected answer, a crash, or a memory-out during
-  execution of the query, or a benchmark timeout, aborts the execution
-  of the benchmark and assigns the current value of the running score
-  to the benchmark.  (Recall that there is one timeout for the entire
-  benchmark; there are no individual timeouts for queries.)
-\item An incorrect answer to a \akey{check-sat} command has the effect of terminating the
-  evaluation of that individual benchmark, and the returned score for the benchmark
-  will be $\langle1,0,0\rangle$.
+\item $e=0, n=1$ if the result of the check-sat command is correct,
+\item $e=0, n=0$ if the result is {\tt unknown}, and
+\item $e=1, n=0$ if the result is incorrect.
 \end{itemize}
 
-For example, if a benchmark has 5~\akey{check-sat} commands, and a
-timeout of 100~seconds, and a solver solves the first four in
-10~seconds each, then times out on the fifth, then the solver's score
-is $\langle0,4,40\rangle$.  If another solver solves each of the first
-four in 10~seconds each, and the fifth in another 40~seconds, its
-score is $\langle0,5,80\rangle$.  If a third solver solves the first
-four queries in 2~seconds each, but incorrectly answers the fifth, its
-score is $\langle1,0,0\rangle$.
+\header{Main track - parallel mode.}
+The Star-Exec infrastructure reports both wall-clock time and CPU time for a given benchmark-solver job-pair.
+Each Star-Exec node has multiple (currently 4) cores; a multi-threaded solver can in principle make use of these cores to reduce its wall-clock time.
+Since the competition has not to date emphasized parallel solvers, we will use total CPU time (across all cores and subprocesses) as the measure of performance in the sequential mode of the main track; the imposed time out will also be on the CPU time.
+
+However, we can also measure the performance using wall-clock time, the key performance criterion for a parallel solver.
+We will use the same competition data to determine a parallel-solver winner as follows.
+The competition will be run with a timeout T for both CPU time and wall-clock time.
+Since the computation nodes have C=4 cores, we can simulate a competition that had a time out of T CPU seconds and T/C wall-clock seconds by simply declaring that any solver taking more than T/C wall-clock time has timed out for the parallel competition.
+We then recompute the scoring as above but using wall-clock time and a timeout value of T/C.
+
+\header{Application track.}
+An application benchmark may have multiple check-sat commands and may partially solve the benchmark before timing out.
+The benchmark is run by the benchmark executor, measuring the total time (summed over all individual commands) taken by
+the solver to respond to commands.
+It is expected that nearly all of this time will be in response to a check-sat command, but assert, push or pop commands might also entail a reasonable amount of processing.
+\begin{itemize}
+\item If the solver completes the benchmark without timing out, the solver receives a score of $\langle e,n,m\rangle$,
+where $e$ is the number of erroneous responses to commands, $n$ is the number of correct responses to check-sat commands, and $m$ is the CPU time taken.
+\item If the solver times out while processing the benchmark, the solver receives a score of $\langle e,n,m\rangle$,
+where $e$ is the number of erroneous responses to commands, $n$ is the number of correct responses to check-sat commands before timing out, and $m$ is equal to the timeout value.
+\end{itemize}
 
@@
 that relatively ``easier'' queries are hidden behind more difficult
-ones located at the middle of the query sequence.
+ones located at the middle of the query sequence. We will not perform a parallel performance analysis of the application track.
 
-Benchmarks' scores are summed componentwise to form a solver's total
-score for the competition.
+\header{Competition scoring.}
+Benchmarks' scores are summed component-wise to form a solver's total
+score for that division of the competition.
 Total scores are compared lexicographically---a score $\langle e,n,m\rangle$ is better than 
@@
 
-\header{Number of competitors}
-Winners in each competition Problem Division for which there are at least three
-entrants from distinct research groups competing will be taken to be
-those with the highest score and no erroneous results. In addition to recognizing the overall
-winner in each division, the top solver that provides its source code will also be
+\subsection{Other recognitions}
+The organizers will also recognize the following contributions:
+\begin{itemize}
+\item {\em Open source}. In addition to recognizing the overall
+winner in each division, the top solver that provides its source code as open source will also be
 recognized in each division.  
-For Problem Divisions with fewer than three
-entrants, the results will be reported but no winner officially
-declared.
-
-\subsection{Other recognitions}
-The organizers will also recognize the following contribution:
-\begin{itemize}
-\item {\em Best new entrant}. The best performing entrant from a new solver implementation team. as measured by the average of 
+\item {\em Best new entrant}. The best performing entrant from a new solver implementation team, as measured by the average of 
 (solver time)/(winning solver time) over the competition benchmarks.
-\item Others TBD
+\item The organizers reserve the right to recognize other outstanding contributions that become apparent in the competition results.
 \end{itemize}
 
-\subsection{Olympic Games medals}
+\subsection{FLoC Olympic Games medals}
 
-TBD
+The FLoC Olympics games medals will be awarded based on competition-wide critera. The organizers are still determining what those criteria should be. Comments are welcome.
+
+%% TBD: DD suggestion: We could have a system similar to that of the Diamond's league.
+For each problem division with at least three entrants, attribute 4, 2 and 1 points to the first three solvers.
+The medals will be awarded based on the total number of points.
 
@@
 \item[June 1] Benchmark libraries are frozen; final versions of solver competitors due.
-\item[June 1 (7pm EDT)] Final versions of solvers due via StarExec (for
+\item[June 1] Final versions of solvers due via StarExec (for
   all tracks), including divisions being entered, system
@@
 
-Interested parties should subscribe to the SMT-COMP mailing list:
-.  Important
+Interested parties should subscribe to the SMT-COMP mailing list (at \url{cs.nyu.edu/mailman/listinfo/smt-comp}).
+Important
 late-breaking news and any necessary clarifications and edits to these
@@
 \begin{itemize}
-\item David Cok is the chief organizer of SMT-COMP 2014. He is 
-responsible for all policy and procedure decisions, such as these
-rules. He is not associated 
+\item David Cok, David Deharbe and Tjark Weber are the organizers of SMT-COMP 2014. 
+David Cok is the lead and is 
+responsible for policy and procedure decisions, such as these
+rules, with input from the co-organizers. He is not associated 
 with any group creating or submitting solvers. He has used solvers
@@
 
-\item David Deharbe and Tjark Weber are co-organizers. 
-They will  
-be validating the competition setup, checking benchmarks, and
-operating the competition. Deharbe is associated with the solver group producing the veriT solver.
+\item David Deharbe is associated with the solver group producing the veriT solver.
 \end{itemize}
@@
 
-\appendix
-\section{Sample benchmark scripts for the main track}
-
-\header{QF\_UF}
-
-{\footnotesize
-\begin{verbatim}
-(set-logic QF_UF)
-(set-info :status sat)
-(declare-sort U 0)
-(declare-fun f (U) U)
-(declare-fun g (U) U)
-(declare-fun A () Bool)
-(declare-fun x () U)
-(declare-fun y () U)
-(assert
-(let ((fx (f x))
-      (cls1 (or A (= x y))))
-  (and cls1 (distinct fx (g y)))))
-(check-sat)
-(exit)
-\end{verbatim}}
-
-\header{QF\_LRA}
-
-{\footnotesize
-\begin{verbatim}
-(set-logic QF_LRA)
-(declare-fun x () Real)
-(declare-fun y () Real)
-(declare-fun A () Bool)
-(assert
-  (let ((i1 (ite A (<= (+ (* 2.0 x) (* (/ 1 3) y)) (- 4))
-                   (= (* y 1.5) (- 2 x)))))
-    (and
-      i1
-      (or (> x y) (= A (< (* 3 x) (+ (- 1) (* (/ 1 5) (+ x y)))))))))
-(check-sat)
-(exit)
-\end{verbatim}}
-
-\header{QF\_LIA}
-
-{\footnotesize
-\begin{verbatim}
-(set-logic QF_LIA)
-(declare-fun x () Int)
-(declare-fun y () Int)
-(declare-fun A () Bool)
-(assert
-  (let ((i1 (ite A (<= (+ (* 2 x) (* (- 1) y)) (- 4))
-                   (= (* y 5) (- 2 x)))))
-    (and
-      i1
-      (or (> x y) (= A (< (* 3 x) (+ (- 1) (* 1 (+ x y)))))))))
-(check-sat)
-(exit)
-\end{verbatim}}
-
-\header{QF\_BV}
-
-{\footnotesize
-\begin{verbatim}
-(set-logic QF_BV)
-(declare-fun x () (_ BitVec 32))
-(declare-fun y () (_ BitVec 16))
-(declare-fun z () (_ BitVec 20))
-(assert
-  (let ((c1 (= x ((_ sign_extend 12) z))))
-   (let ((c2 (= y ((_ extract 18 3) x))))
-    (let ((c3 
-            (bvslt (concat z (_ bv5 12)) 
-              (bvand (bvor (bvxor (bvnot x) ((_ zero_extend 28) #b1111)) 
-                                    (concat #xAF02 y))
-                    (concat (bvmul ((_ extract 31 16) x) y) 
-                            (bvashr (_ bv42 16) #x0001))))))
-   (and c1 (xor c2 c3))))))
-(check-sat)
-(exit)
-\end{verbatim}}
-
-\header{QF\_AUFLIA}
-
-{\footnotesize
-\begin{verbatim}
-(set-logic QF_AUFLIA)
-(declare-fun A () (Array Int Int))
-(declare-fun x () Int)
-(declare-fun y () Int)
-(declare-fun P () Bool)
-(declare-sort U 0)
-(declare-fun f (U) (Array Int Int))
-(declare-fun c () U)
-(assert
-  (let ((fc (f c)))
-    (and
-      (=> (= A (store fc x 5)) (> (+ (select fc y) (* 4 x)) 0))
-      (= P (< (select A (+ 3 y)) (* (- 2) x))))))
-(check-sat)
-(exit)
-\end{verbatim}}
-
-\header{QF\_ABV}
-
-\footnotesize
-\begin{verbatim}
-(set-logic QF_ABV)
-(declare-fun x () (_ BitVec 32))
-(declare-fun y () (_ BitVec 16))
-(declare-fun z () (_ BitVec 20))
-(declare-fun A () (Array (_ BitVec 16) (_ BitVec 32)))
-(assert
-  (let ((c1 (= ((_ sign_extend 12) z) (select A y)))
-        (A2 (store A ((_ extract 15 0) x) x)))
-   (let ((c2 (= A A2)))
-    (let ((c3 
-            (bvslt (concat z (_ bv5 12)) 
-              (bvand (bvor (bvxor (bvnot x) 
-                                  (select A2 ((_ zero_extend 12) #b1111)))
-                                    (concat #xAF02 y))
-                    (concat ((_ extract 15 0) 
-                                (bvmul x (select (store A y x) #x35FB))) 
-                            (bvashr (_ bv42 16) #x0001))))))
-   (and c1 (xor c2 c3))))))
-(check-sat)
-(exit)
-\end{verbatim}
-
-\section{Sample benchmark scripts for the application track}
-
-\footnotesize
-\begin{verbatim}
-(set-option :print-success true)
-(set-logic QF_LRA)
-(declare-fun c0 () Bool)
-(declare-fun E0 () Bool)
-(declare-fun f0 () Bool)
-(declare-fun f1 () Bool)
-(push 1)
-(assert 
-  (let ((.def_10 (not f0)))
-   (let ((.def_9 (not c0)))
-    (let ((.def_11 (or .def_9 .def_10)))
-     (let ((.def_7 (not f1)))
-      (let ((.def_8 (or c0 .def_7)))
-       (let ((.def_12 (and .def_8 .def_11)))
- .def_12
-)))))))
-(check-sat)
-(pop 1)
-(declare-fun f2 () Bool)
-(declare-fun f3 () Bool)
-(declare-fun f4 () Bool)
-(declare-fun c1 () Bool)
-(declare-fun E1 () Bool)
-(assert 
- (let ((.def_23 (not f2)))
-  (let ((.def_20 (= c0 c1)))
-   (let ((.def_22 (or E0 .def_20)))
-    (let ((.def_24 (or .def_22 .def_23)))
-     (let ((.def_18 (not f4)))
-      (let ((.def_19 (or c1 .def_18)))
-       (let ((.def_25 (and .def_19 .def_24)))
- .def_25
-))))))))
-(push 1)
-(check-sat)
-(assert (and f1 (not f1)))
-(check-sat)
-(pop 1)
-(exit)
-\end{verbatim}
-
 \end{document}

### 2014-05-08 rules/rules14.tex
Fixing language about solver input.

@@
 
+Information about how to configure and upload a solver is contained in the StarExec user guide on its wiki:
+\url{https://wiki.uiowa.edu/display/stardev/User+Guide}.
+
 \header{System description.} %
@@
 %
-Participating solvers must read a single benchmark script presented on its standard input
-channel. The script is in the concrete syntax of the SMT-LIB format,
+Participating solvers must read a single benchmark script presented as its first argument.
+Note that previous competitions presented benchmarks to a solver on its standard input
+channel, and that the application track will send command inputs to the solver's standard input.
+Accordingly, solvers are advised to support both input mechanisms.
+
+ The script is in the concrete syntax of the SMT-LIB format,
 version 2.0, though with a restricted set of commands.   A
@@
 logic divisions.
-Each benchmark script will be presented to the standard input of the solver.
+Each benchmark script will be presented to the solver as its first command-line argument.
 Each SMT-COMP entrant is then expected to attempt to report on its
@@
 answers either \texttt{sat} or \texttt{unsat}.  In this interaction an SMT-solver is
-required to accept queries incrementally via its standard input channel.
+required to accept queries incrementally via its {\em standard input channel}.
 

### 2014-05-19 rules/rules14.tex
slight edits
Rule revisions

@@
 \item The competition will be run with StarExec (\url{www.starexec.org}). Accordingly we are simplifying the competition somewhat, since some of the infrastructure needs to be recreated.
-\item We will hold just a main and application track. [ The demonstration unsat core, and proof generation tracks will be deferred until benchmarks and result analysis tools are reorganized.]
+\item We will hold just a main and application track.
+[ The demonstration unsat core, and proof generation tracks will be deferred until benchmarks and result analysis tools are reorganized.] We encourage submission of solvers and benchmarks for both tracks.
 \item In the main track, we will measure comparative performance within all divisions to which at least two solvers are submitted.
 We will use the data to determine both sequential and parallel winners.
-
-\item We are retaining and accenting last year's ``application track" and
-  encourage submission of benchmarks for this track and competition against these
-  benchmarks.
 
@@
 include a URL for a web site for the submitted tool.
+System descriptions may be submitted after the solver deadline, but to be useful should be sent to the organizers before the competition ends (July 16).
 
@@
 \paragraph{Main competition track.} %
-SMT-COMP entries must be submitted via StarExec and email to the organizers by the end of May~25, 2014 (anywhere on earth).  At that time new entrants will be
+SMT-COMP entries must be submitted via StarExec and email to the organizers by the end of June~1, 2014 (anywhere on earth).  At that time new entrants will be
 closed to the public to prepare for the competition, with the
 exception that resubmissions of existing entries will be accepted
-until the end of June~1, 2014 (anywhere on earth).  We strongly encourage
+until the end of June~15, 2014 (anywhere on earth).  We strongly encourage
 participants to use this grace period \emph{only} for the
@@
 new features as there will be no opportunity to do extensive testing
-using StarExec after the original deadline on May~25.
+using StarExec after the initial deadline.
 
@@
 the right to start the competition itself at any time after the open
-of the New York Stock Exchange on the morning of June~2.  See
+of the New York Stock Exchange on the day after the final solver deadline.  See
 Section~\ref{sec:timeline} below for a full timeline.
@@
 We anticipate that the bulk of the main track of the competition will take place during
-the weeks leading up to SMT 2014, from about June~2 to July~17.  Results will be
+the weeks leading up to SMT 2014, from about June~16 to July~17.  Results will be
 announced at SMT 2014 and in an awards ceremony scheduled by the FLoC Olympic Games coordinator.
@@
 channel, and that the application track will send command inputs to the solver's standard input.
-Accordingly, solvers are advised to support both input mechanisms.
+Accordingly, solvers are advised to support both input mechanisms. The organizers have easily adapted solvers that use only the standard input to Star-Exec with a simple wrapper script.
 
@@
 logic is the first command after any $\akey{set-option}$ commands described below.
-% rb 25/3: added
-% \item A (single) \akey{set-option :print-success false} command, sent just
-%       after $\akey{set-logic}$. This is to
-%       avoid the output ``\texttt{success}'' to interfere with the
-%       answer of the solver to the benchmark. 
+\item In the main track, there may be a (single) \akey{set-option :print-success ...} command. Note that {\tt success} outputs are ignored by the post-processor used by the competition.
+\item Scripts for the application track will have an initial $\akey{set-option :print-success true}$ command.
+\item The script next optionally contains (any number of) $\akey{set-info}$ commands, which may be ignored by the solver.
 \item The $\akey{exit}$ command is the last command.
@@
   and followed by zero or more \akey{pop 1} commands.
-\item Scripts for the application track will have an initial $\akey{set-option :print-success true}$ command.
-\item There is at most one $\akey{set-info}$ command for \texttt{status}.
+
 %%%%%%%%%%%%%%%%%%% TODO: Need to define the set-info command.
@@
 \item No other commands besides the ones just mentioned may be used.
+\item Named formulas are not used in benchmark scripts.
 
@@
 anticipated to be 1500 seconds (25 minutes) of CPU time and the same limit on wall clock time.\footnote{The time limit may be adjusted once we understand the resources and capabilities of the StarExec service and the number of competition solvers.}
-% TBD- TODO - how to constrain solvers to single processes?
 Solvers that take more than this
@@
 started, or in a subdirectory.
+
+The solver is executed with a temporary directory as the current working directory.
+Any generated files should be produced there, not, for example, in the system tmp area.
+The temporary directory and its contents are deleted after the job is complete.
 
@@
  with a \texttt{sat}, \texttt{unsat}, or \texttt{unknown} 
-for \akey{check-sat} commands. There should be no \akey{get-unsat-core} or \akey{get-proof} commands in these benchmarks.
+for \akey{check-sat} commands. There should be no \akey{get-unsat-core}, \akey{get-proof}, \akey{get-model}, \akey{get-assignments}, or \akey{get-values}commands in these benchmarks.
 
@@
 The goal for completing the set of benchmarks is June 1.
-The set of selected benchmarks will be published when the
+The set of benchmarks selected for the competition will be published when the
 competition begins.
@@
 The benchmarks are assigned a difficulty. For 2014, the difficulty measure is the
-CPU time taken by the best performing solver in the 2013 SMT-EVAL. These times will be posted 
+CPU time taken by the best performing solver in the 2013 SMT-EVAL. 
+ For new benchmarks, we will determine an approximate difficulty
+using trial runs.
+The difficulty values will be posted 
 as soon after May 15 as possible.
+The difficulty values are best estimates by the organizers and may not always completely correlate with actual difficulty.
 
@@
 Then, for each division, the benchmarks are divided into quintiles according to the difficulty measure.
-Then a random selection of N competition benchmarks is made as follows:
+Next a random selection of N competition benchmarks is made as follows:
 \begin{itemize}
-\item N*40\% are taken from the top quintile, if sufficient benchmarks are available
-\item additional benchmarks are taken from the second quintile, to produce N*60\% benchmarks, if sufficient benchmarks are available
-\item additional benchmarks are taken from the third quintile, to produce N*75\% benchmarks, if sufficient benchmarks are available
-\item additional benchmarks are taken from the fourth quintile, to produce N*90\% benchmarks, if sufficient benchmarks are available
-\item any remaining needed benchmarks are taken from the bottom quintile.
+\item N*40\% are randomly selected from the top quintile, if sufficient benchmarks are available
+\item additional benchmarks are randomly selected from the second quintile, to produce N*60\% benchmarks, if sufficient benchmarks are available
+\item additional benchmarks are randomly selected from the third quintile, to produce N*75\% benchmarks, if sufficient benchmarks are available
+\item additional benchmarks are randomly selected from the fourth quintile, to produce N*90\% benchmarks, if sufficient benchmarks are available
+\item any remaining needed benchmarks are randomly selected from the bottom quintile.
 \end{itemize}
@@
 Since the organizers at this point are unsure how long a set of benchmarks may take (which will depend also on the number of solvers submitted), the competition will be run in {\em heats}.
-For each division, some number $N$ of benchmarks will be selected as described and randomly divided into a number of heats.
+For each division, some number $N$ of benchmarks will be selected as described and randomly divided into a number of (possibly unequal-sized) heats.
 The heats will be run in order.
@@
 the opening value of the New York Stock Exchange Composite Index on
-the first day the exchange is open on or after June 2
+the first day the exchange is open on or after the date specified in the timeline
 will be added to the other seeding values.  This helps provide transparency,
@@
 A first release of the application track
-benchmarks will be made available May 15, 2014.
+benchmarks will be made available as soon after the benchmark deadline as the organizers can arrange.
 No additional
@@
 \header{Competition scoring.}
+\label{scoring}
 Benchmarks' scores are summed component-wise to form a solver's total
@@
 recognized in each division.  
-\item {\em Best new entrant}. The best performing entrant from a new solver implementation team, as measured by the average of 
-(solver time)/(winning solver time) over the competition benchmarks.
+\item {\em Best new entrant}. The best performing entrant from a new solver implementation team, as measured by the Olympic Games metric defined below.
+\item {\em Breadth of logics}. Tools that cover the most theories and logics.
+\item {\em Benchmarks}. Contributors of new benchmarks.
 \item The organizers reserve the right to recognize other outstanding contributions that become apparent in the competition results.
@@
 
-The FLoC Olympics games medals will be awarded based on competition-wide critera. The organizers are still determining what those criteria should be. Comments are welcome.
+The FLoC Olympics games medals will be awarded based on competition-wide critera.
 
-%% TBD: DD suggestion: We could have a system similar to that of the Diamond's league.
-For each problem division with at least three entrants, attribute 4, 2 and 1 points to the first three solvers.
-The medals will be awarded based on the total number of points.
+We define a competition-wide metric M as follows.
+Each solver competing in a division receives a number of points for its performance in that division: $(n/N)^2$, where $n$ is the number of benchmarks solved correctly and $N$ is the number of benchmarks used in that division.
+A solver's score for the whole competition is the sum of these values over all the
+divisions in which the solver participates.
+
+The Olympic Games medals will be awarded as follows.
+\begin{itemize}
+\item The gold medal we will be awarded to the solver with the best competition-wide value of M.
+\item The silver medal will be awarded to the solver that wins the (sequential) QF\_BV division according to the usual $\langle e',n',m'\rangle$ metric of subsection \ref{scoring}.
+\item The bronze medal will be awarded to the solver with the second-best  competition-wide value of M.
+\end{itemize}
+
+{\em Rationale.} The metric M purposely emphasizes breadth of solver participation - a solver participating in many logics need not be the best in any one of them.
+The use of the square in the metric limits that somewhat - a solver still needs to do reasonably well compared to winners to be able to catch up by breadth of participation.
+The non-linear metric also gives added weight to completing close to all benchmarks in a division.
+The metric is also quite simple and the metric for a solver is independent of the performance of other solvers.
 
@@
 \item[May 15] Deadline for benchmark contributions.
-  First version of the benchmark scrambler, benchmark selector and trace executor made available.
-\item[May 25] First versions of solver competitors are due to the organizers.
-\item[June 1] Final version of the benchmark scrambler, benchmark selector and trace executor made available.
-\item[June 1] Benchmark libraries are frozen; final versions of solver competitors due.
-\item[June 1] Final versions of solvers due via StarExec (for
+\item[June 1] First versions of solver competitors are due to the organizers, including divisions being entered.
+  Versions of the benchmark scrambler, benchmark selector and trace executor made available.
+\item[June 8] Final version of the benchmark scrambler, benchmark selector and trace executor made available.
+\item[June 8] Benchmark libraries are frozen.
+\item[June 15] Final versions of solvers due via StarExec (for
   all tracks), including divisions being entered, system
   descriptions and magic numbers for benchmark scrambling.
-\item[June 2] Opening value of NYSE Composite Index used to complete random seed.
+\item[June 16] Opening value of NYSE Composite Index used to complete random seed.
 \item[July 17] SMT 2014; end of competition.
@@
 with any group creating or submitting solvers. He has used solvers
-in industrial settings and is keenly interested to know which are the best.
+in industrial settings and is keenly interested to know which are the best for various applications.
 

### 2014-05-29 rules/rules14.tex
Updates to rules

@@
 \item May 15 - deadline for new benchmarks
-\item May 25 - deadline for solver entrants
-\item June 1 - deadline for final versions of solvers (but no new entrants after May 25).
+\item June 1 - deadline for solver entrants
+\item June 15 - deadline for final versions of solvers (but no new entrants after May 25).
 \item July 17 - SMT workshop; completion of competition.
@@
 \item We will hold just a main and application track.
-[ The demonstration unsat core, and proof generation tracks will be deferred until benchmarks and result analysis tools are reorganized.] We encourage submission of solvers and benchmarks for both tracks.
+[The demonstration unsat core, and proof generation tracks will be deferred until benchmarks and result analysis tools are reorganized.] We encourage submission of solvers and benchmarks for both tracks.
 \item In the main track, we will measure comparative performance within all divisions to which at least two solvers are submitted.
@@
 
-It is important for competitors to track discussions on the SMT-COMP mailing
-list, as clarifications and any updates to these rules will be posted there.
-
 \section{Entrants}
@@
 An entrant to SMT-COMP is an SMT solver
-submitted by its authors using the Star-Exec (\url{http://www.starexec.org}) service.  
+submitted by its authors using the StarExec (\url{http://www.starexec.org}) service.  
 The execution service enables members of the
@@
 For participation in SMT-COMP, a solver must be
-uploaded to Star-Exec, made publicly available, and the organizers informed of its presence {\em and the logic divisions in which it is participating}.
+uploaded to StarExec, made publicly available, and the organizers informed of its presence {\em and the logic divisions in which it is participating}.
+For clarity, the solver should have just one configuration, or at least, that the default configuration is the one to be used for competition.
 A submission must also include a 32-bit unsigned
@@
 
+Competition solvers should be submitted with just one StarExec configuration so that it is
+clear what configuration should be used for the competition. Separately named StarExec solvers can wrap the same underlying tool with a different configuration, if needed, for the application track.
+
 The versions that are present on the execution service at the conclusion of the
@@
 %
-Participating solvers must read a single benchmark script presented as its first argument.
+A participating solver must read a single benchmark script presented as its first argument.
 Note that previous competitions presented benchmarks to a solver on its standard input
 channel, and that the application track will send command inputs to the solver's standard input.
-Accordingly, solvers are advised to support both input mechanisms. The organizers have easily adapted solvers that use only the standard input to Star-Exec with a simple wrapper script.
+Accordingly, solvers are advised to support both input mechanisms. The organizers have easily adapted solvers that use only the standard input to StarExec with a simple wrapper script.
 
@@
 logic is the first command after any $\akey{set-option}$ commands described below.
-\item In the main track, there may be a (single) \akey{set-option :print-success ...} command. Note that {\tt success} outputs are ignored by the post-processor used by the competition.
-\item Scripts for the application track will have an initial $\akey{set-option :print-success true}$ command.
+\item In the main track, there may be a (single) \akey{set-option :print-success ...} command. Note that {\tt success} outputs are ignored by the post-processor used by the competition; in 
+the application track, the :print-success option may not be disabled.
+\item The application track executor will send an initial $\akey{set-option :print-success true}$ command to the solver. 
 \item The script next optionally contains (any number of) $\akey{set-info}$ commands, which may be ignored by the solver.
+Benchmarks are expected to have the following \akey{set-info} commands: \akey{(set-info :smt-lib-version 2.0)}, \akey{(set-info :category ...)}, \akey{(set-info :source ...)} (indicating the authorship or tool that produced the benchmark), and \akey{(set-info :status ...)}.
 \item The $\akey{exit}$ command is the last command.
@@
 \item For the application track, there are one or more \akey{check-sat} commands, 
-  each preceded by one or more \akey{assert} commands 
-  and zero or more \akey{push 1} commands, 
-  and followed by zero or more \akey{pop 1} commands.
+  each preceded by one or more \akey{assert} commands; 
+  there may also be zero or more \akey{push 1} commands, 
+  and zero or more \akey{pop 1} commands, consistent with the uses of those commands in
+  the SMT-LIB standard. Each \akey{check-sat} command may be preceded by a \akey{set-info :status} command that indicates the expected result of the 
+  \akey{check-sat} command.
 
-%%%%%%%%%%%%%%%%%%% TODO: Need to define the set-info command.
 \item The formulas in the script belong to the benchmark's logic, with
 any free symbols declared in the script.
-\item Extra symbols are declared exactly once before any
-  use, using $\akey{declare-sort}$
-  %, $\akey{define-sort}$,
-  %$\akey{declare-fun}$, or $\akey{define-fun}$.  
-  or $\akey{declare-fun}$.
-  They must be part of the allowed signature expansion for the logic.
-  Moreover, all sorts declared with a $\akey{declare-sort}$ command must have zero arity.
+\item All sorts declared with a $\akey{declare-sort}$ command must have zero arity.
 
+\item Application track scripts may have $\akey{define-sort}$ and $\akey{define-sort}$ commands. 
 \item No other commands besides the ones just mentioned may be used.
@@
 processes.  These will be killed at approximately the same time as the
-first started process.  A
-timeout scores the same as if the output is ``\texttt{unknown}''.
+first started process.
+
+The StarExec service also limits the memory consumption of the solver processes.
+We expect the limit per solver-benchmark job-pair to be quite high, on the order of 100GB.
+The values of both the timeout limit and the memory limit are available to a solver process through environment variables defined and set by the StarExec service (see the StarExec user guide for more information).
 
@@
 will be considered to have aborted. 
-An abort scores the same as if the output is ``\texttt{unknown}''. 
 Also, as a further measure to prevent misjudgments of solvers,
@@
       (through stdin);
-\item it prevents ``look-ahead'' behaviours of SMT solvers;
+\item it prevents ``look-ahead'' behaviors of SMT solvers;
 \item it records time and answers for each call, possibly aborting the execution
@@
 \item it guarantees a fair execution for all solvers by abstracting from any possible
-      crash, misbehaviour, etc. that may happen on the model checker side.
+      crash, misbehavior, etc. that may happen on the model checker side.
 \end{itemize}
+Note that the executor terminates processing the script upon receiving an incorrect response.
 
@@
 The commands will be taken from an \textbf{incremental benchmark script},
-which is an SMT-LIB 2.0 script which satisfies the rules for an application script given above.
+which is an SMT-LIBv2 script which satisfies the rules for an application script given above.
 Note also that the trace executor will send a single 
@@
 \akey{declare-fun}, 
+\akey{define-sort}, 
+\akey{define-fun}, 
 \akey{assert}, 
@@
  with a \texttt{sat}, \texttt{unsat}, or \texttt{unknown} 
-for \akey{check-sat} commands. There should be no \akey{get-unsat-core}, \akey{get-proof}, \akey{get-model}, \akey{get-assignments}, or \akey{get-values}commands in these benchmarks.
+for \akey{check-sat} commands. There will be no \akey{get-unsat-core}, \akey{get-proof}, \akey{get-model}, \akey{get-assignments}, or \akey{get-values} commands in these benchmarks.
 
@@
 \item $e=0, n=1$ if the result of the check-sat command is correct,
-\item $e=0, n=0$ if the result is {\tt unknown}, and
 \item $e=1, n=0$ if the result is incorrect.
+\item $e=0, n=0$ if the result is {\tt unknown} or the solver times-out or otherwise aborts without a response, and
 \end{itemize}
@@
 \header{Main track - parallel mode.}
-The Star-Exec infrastructure reports both wall-clock time and CPU time for a given benchmark-solver job-pair.
-Each Star-Exec node has multiple (currently 4) cores; a multi-threaded solver can in principle make use of these cores to reduce its wall-clock time.
+The StarExec infrastructure reports both wall-clock time and CPU time for a given benchmark-solver job-pair.
+Each StarExec node has multiple (currently 4) cores; a multi-threaded solver can in principle make use of these cores to reduce its wall-clock time.
 Since the competition has not to date emphasized parallel solvers, we will use total CPU time (across all cores and subprocesses) as the measure of performance in the sequential mode of the main track; the imposed time out will also be on the CPU time.
@@
 We then recompute the scoring as above but using wall-clock time and a timeout value of T/C.
+
+Parallel track scores are not directly comparable to the sequential track scores. However, we will use them to determine a parallel-track winner in each division.
 
@@
 
+\subsection{Judging}
+
+It may happen that faulty benchmarks are discovered in the course of the competition. The judges reserve the right, with careful deliberation, to remove a benchmark from the competition
+results if it is determined that the benchmark is faulty (e.g., syntactically invalid in a way that affects some solvers but not others).
+Organizers on solver teams will be recused from such decisions.
+Solver teams may appeal to the organizers if they suspect that a benchmark is faulty or otherwise not within the rules.
+
 \subsection{Other recognitions}
@@
 We define a competition-wide metric M as follows.
-Each solver competing in a division receives a number of points for its performance in that division: $(n/N)^2$, where $n$ is the number of benchmarks solved correctly and $N$ is the number of benchmarks used in that division.
-A solver's score for the whole competition is the sum of these values over all the
+Each solver competing in a division receives a number of points for its performance in that division: $\langle e,(n/N)^2 \rangle$, where $e$ is the number of wrong answers to benchmarks, $n$ is the number of benchmarks solved correctly, and $N$ is the number of benchmarks used in that division.
+A solver's score for the whole competition is the sum of these tuples over all the
 divisions in which the solver participates.
+The best value of M is the one with the least total value of $e$, secondly, the largest total value for the second component of the tuple, and thirdly, the least value of $m$.
 
@@
 \item The gold medal we will be awarded to the solver with the best competition-wide value of M.
-\item The silver medal will be awarded to the solver that wins the (sequential) QF\_BV division according to the usual $\langle e',n',m'\rangle$ metric of subsection \ref{scoring}.
-\item The bronze medal will be awarded to the solver with the second-best  competition-wide value of M.
+\item The silver medal will be awarded to the solver with the second-best competition-wide value of M.
+\item The bronze medal will be awarded to the solver that wins the (sequential) QF\_BV division according to the usual $\langle e,n,m\rangle$ metric of subsection \ref{scoring}. 
+\item The winner of the gold medal is excluded from consideration for the silver medal; the winners of the gold and silver medals are excluded from consideration for the bronze medal.
 \end{itemize}
@@
 The metric is also quite simple and the metric for a solver is independent of the performance of other solvers.
+Time is omitted from the metric both to simplify the metric and because it is only of third importance in the regular competition metric and is difficult to compare across divisions.
 

### 2015-02-11 rules/rules10.tex
svn propdel svn:executable

--- 2012-01-23 rules/rules11.tex
@@
 
-\title{Satisfiability Modulo Theories Competition (SMT-COMP) 2011: Rules and 
-Procedures
-}
+\title{Satisfiability Modulo Theories Competition (SMT-COMP) 2010: Rules and 
+Procedures}
 
@@
 \author{
-Roberto Bruttomesso\\
+Clark Barrett\\
 Computer Science\\
-USI, Lugano (Switzerland)
+New York University\\
+\\
+Albert Oliveras \\
+LSI Department \\
+Technical University of Catalonia \\
 \and
@@
 New York University \\
-\and
-Alberto Griggio\\
-ES Division\\
-FBK, Trento (Italy)
-}
+\\
+Aaron Stump \\
+Department of Computer Science \\
+University of Iowa}
 
@@
 competitions~(\cite{SMTCOMP-2008,BDOS08,SMTCOMP-FMSD,SMTCOMP-JAR}).
-SMT-COMP 2011 is affiliated with the 23nd International
-Conference on Computer Aided Verification~(CAV).
+SMT-COMP 2010 is jointly affiliated with the 22nd International
+Conference on Computer Aided Verification~(CAV), and with the 13th
+International Conference on Theory and Applications of Satisfiability
+Testing, both held in Edinburgh, Scotland.
 
-The rest of this document, updated from the last year's
-version\footnote{Earlier versions of this document include contributions from
-Clark Barrett, Albert Oliveras, and Aaron Stump.},
-describes the rules and competition procedures for SMT-COMP~2011.
-The principal change from last year's version is:
+The rest of this document, updated from the last year's version,
+describes the rules and competition procedures for SMT-COMP 2009.
+The primary changes from last year's version are:
 
 \begin{itemize}
-\item the introduction of an ``application track,'' based on incremental
-      model-checking queries, to promote the integration of SMT solvers
-      within actual verification frameworks;
-%\item updates to the benchmark selection algorithm, to reduce
-%      overwhelming a competition division with a single ``family'' of
-%      benchmarks.
-% rb 25/3: see later
-%\item updates to the difficulty calculation;
-%\item a track for parallel solvers, to run before the regular competition.
-%\item 5 random ``check'' benchmarks will be generated using Robert
-%  Brummayer's SMT fuzzing tool, after all the solvers are uploaded.
-%  These will be included in the competition, to help promote attention
-%  to the problem of solver correctness (cf.~\cite{brummayer+09}).
+\item adoption of the SMT-LIB 2.0 standard;
+\item updates to the benchmark selection algorithm, including a change
+  in the notion of what constitutes a ``family'' of benchmarks;
+\item updates to the difficulty calculation;
+\item a track for concurrent solvers, to run before the
+  regular competition.
+\item 5 random ``check'' benchmarks will be generated using Robert
+  Brummayer's SMT fuzzing tool, after all the solvers are uploaded.
+  These will be included in the competition, to help promote attention
+  to the problem of solver correctness (cf.~\cite{brummayer+09}).
 \end{itemize}
@@
 and graphical displays of results of solver executions, for
-comparison. For the main (sequential-solver)
-% rb 23/3: I guess also application track runs on 
-% the same clusters as sequential
-and application tracks 
-of SMT-COMP 2011, SMT-Exec will be configured so that jobs are run on a 64-bit,
-uniprocessor Linux kernel.  For the parallel-solver track, SMT-Exec
+comparison. For the main (sequential-solver) track of SMT-COMP 2010,
+SMT-Exec will be configured so that jobs are run on a 64-bit,
+uniprocessor Linux kernel.  For the concurrent-solver track, SMT-Exec
 will be configured so that jobs are run on a 64-bit, multiprocessor
@@
   SMT-Exec; please stay tuned to the SMT-COMP mailing list for final
-  details regarding the effective SMT-COMP 2011 competition cluster.}
+  details regarding the effective SMT-COMP 2010 competition cluster.}
 
@@
 \header{Attendance.} %
-As with previous SMT-COMPs, submitters of an SMT-COMP entrant need not 
-be physically present at the competition to
+As with previous SMT-COMPs, submitters of an
+SMT-COMP entrant need not be physically present at the competition to
 participate or win.
 
-\subsection*{Deadlines} %
+\subsection*{Deadlines} % To guarantee inclusion in the competition,
 
@@
 SMT-COMP entries must be submitted via SMT-Exec by 7pm, Eastern U.S.
-time, July~9th, 2011.  At that time the SMT-Exec service will be
+time, July~8th, 2010.  At that time the SMT-Exec service will be
 closed to the public to prepare for the competition, with the
 exception that resubmissions of existing entries will be accepted
-until 7pm, Eastern U.S. time, July~11th, 2011.  We strongly encourage
+until 7pm, Eastern U.S. time, July~10th, 2010.  We strongly encourage
 participants to use this two day grace period \emph{only} for the
@@
 new features as there will be no opportunity to do extensive testing
-using SMT-Exec after the original deadline on July~9th.
+using SMT-Exec after the original deadline on July~8th.
 
@@
 
-\paragraph{Application track.} %
-The same deadlines and procedure for submitting to the main track will be used
-also for the application track. Submissions to both the application track and
-the main competition are independent: participants must submit explicitly to
-both events to participate in both, and they may submit different (or
-differently configured) solvers to each.  Benchmarks will be scrambled also
-for this division, using the same scrambler and seed as the main track.
-Entrants should still include a system description, as for the regular
-competition.
-
-\paragraph{Parallel solver track.} %
+\paragraph{Concurrent solver demonstration.} %
 Solvers employing concurrency are invited to participate in a
 demonstration that will be run before the regular competition.
-Parallel solvers must be submitted by the same July~9th deadline,
+Concurrent solvers must be submitted by the same July~8th deadline,
 with the same two-day grace period for resubmission as in the regular
-competition.  Submissions to both the parallel solver track
+competition.  Submissions to both the concurrent solver track
 and the main competition are independent: participants must submit
@@
 Note that the SMT-COMP organizers are considering ways to include
-other (``historical'' or otherwise relevant) solvers in all the competition tracks for
+``historical'' solvers in both the main and concurrent track for
 demonstration and comparison.  The organizers reserve the right to
@@
 to historical sequential solvers to (na\"ively) take advantage of
-multiple processors 
-or to connect them with a parser for the SMT-LIB version 2.0 format
-(\eg\ by implementing a wrapper tool).
+multiple processors.
 
@@
 
-\subsection{Main track and parallel track}
-\label{sec:exec:main}
+\header{Dates of competition.} % We anticipate that the bulk of the
+competition will take place during the course of CAV 2010, SAT 2010,
+and SMT 2010, from July~14th to~19th.  Results will be announced in a
+special session of CAV, on the last day of the conference, as well as
+on the SMT-COMP web site.  Intermediate results will be regularly
+posted to the SMT-COMP website as the competition runs.
 
-\header{Dates of competition.}
-%
-We anticipate that the bulk of the main track of the competition will take place during
-the course of CAV 2011, from July~14th to~20th.  Results will be
-announced in a special session of CAV, on the last day of the
-conference, as well as on the SMT-COMP web site.  Intermediate results
-will be regularly posted to the SMT-COMP website as the competition
-runs.
-%
-If there are enough competitors to run the parallel track, we intend
-to run it before or after the main competition (depending on the
-estimated duration of the track).
-
-\header{Input and Output.}
-%
+\header{Input and Output.} % Each SMT-COMP entrant, when executed,
 Participating solvers must read a single benchmark script (defined
@@
 
-\begin{enumerate}
+\begin{itemize}
 \item The (single) $\akey{set-logic}$ command setting the benchmark's
 logic is the first command.
-% rb 25/3: added
-% \item A (single) \akey{set-option :print-success false} command, sent just
-%       after $\akey{set-logic}$. This is to
-%       avoid the output ``\texttt{success}'' to interfere with the
-%       answer of the solver to the benchmark. 
 \item The $\akey{exit}$ command is the last command.
@@
 any free symbols declared in the script.
-\item Extra symbols are declared exactly once before any
-  use, using $\akey{declare-sort}$
-  %, $\akey{define-sort}$,
-  %$\akey{declare-fun}$, or $\akey{define-fun}$.  
-  or $\akey{declare-fun}$.
-  They must be part of the allowed signature expansion for the logic.
-  Moreover, all sorts declared with a $\akey{declare-sort}$ command must have zero arity.
+\item Extra symbols are declared or defined exactly once before any
+  use, using $\akey{declare-sort}$, $\akey{define-sort}$,
+  $\akey{declare-fun}$, or $\akey{define-fun}$.  They must be part of
+  the allowed signature expansion for the logic.
 \item No other commands besides the ones just mentioned may be used.
-\end{enumerate}
+\end{itemize}
 
-% \noindent Note that the final version of the 2.0 format will be frozen
-% in early March.  
-\noindent The SMT-LIB format specification is publicly
+\noindent Note that the final version of the 2.0 format will be frozen
+in early March.  The SMT-LIB format specification is publicly
 available from the ``Documents'' section of the SMT-LIB
 website~\cite{SMT-LIB}.  Solvers will be given formulas just from the
-Problem Divisions indicated during their submission to SMT-Exec.
-Example benchmark scripts for several Problem Divisions are reported in the Appendix.
-Note that they are provided for illustrative purposes only: 
-please refer to the SMT-LIB format specification 
-and the above definition of benchmark script for the official specification 
-of the input format for SMT-COMP.
+Problem Divisions indicated in their system descriptions.
 
-\medskip
 Each SMT-COMP entrant is then expected to attempt to report on its
 standard output channel whether the formula is satisfiable
-(``\texttt{sat}'', in lowercase, without the quotation marks) or unsatisfiable
+(``\texttt{sat}'', without the quotation marks) or unsatisfiable
 (``\texttt{unsat}'').  An entrant may also report ``\texttt{unknown}''
@@
 \texttt{unknown})
-will be considered to have aborted. 
-An abort scores the same as if the output is ``\texttt{unknown}''. 
-% rb 25/3: added
-Also, as a further measure to prevent misjudgments of solvers,
-the first burst of  ``\texttt{success}'' outputs will be 
-ignored\footnote{
-Note that SMT-LIBv2 requires to produce a ``\texttt{success}'' answer
-after each \akey{set-logic}, \akey{declare-sort}, \akey{declare-fun} and
-\akey{assert} command (among others), unless the option
-\akey{:print-success} is set to false: ignoring the first burst of
-\texttt{success} outputs therefore allows for submitting fully-compliant
-solvers without the need of a wrapper script, while still allowing entrants
-of SMT-COMP 2010 to run without changes.}.
+will be considered to have aborted.  An abort scores the same as if
+the output is ``\texttt{unknown}''.
 
@@
 
-\subsection{Application track}
-\label{sec:exec:application}
-
-The application track aims at evaluating SMT solvers when interacting
-with an external verification framework, \eg, a model
-checker. This interaction, ideally, happens by means of an online
-communication between the model checker and the solver: the model
-checker repeatedly sends queries to the SMT solver, which in turn
-answers either sat or unsat.  In this interaction an SMT-solver is
-required to accept queries incrementally via its standard input channel.
-
-In order to facilitate the evaluation of the solvers in this track, we
-propose to set up a ``simulation'' of the aforementioned interaction. In
-particular each benchmark in the application track represents a realistic
-communication trace, containing multiple \akey{check-sat} commands (possibly
-with corresponding \akey{push 1}/\akey{pop 1} commands), which
-is parsed by a {\em trace executor}. The trace executor serves the following purposes:
-\begin{itemize}
-\item it simulates the online interaction by sending single queries to the SMT solver
-      (through stdin);
-\item it prevents ``look-ahead'' behaviours of SMT solvers;
-\item it records time and answers for each call, possibly aborting the execution
-      in case of a wrong answer;
-\item it guarantees a fair execution for all solvers by abstracting from any possible
-      crash, misbehaviour, etc. that may happen on the model checker side.
-\end{itemize}
-
-\header{Input and Output.}
-Participating solvers will be connected to a trace executor 
-which will incrementally send commands to the standard input channel of the solver
-and read responses from the standard output channel of the solver.
-The commands will be taken from an \textbf{incremental benchmark script},
-which is an SMT-LIB 2.0 script which satisfies points 1., 2., 4.--7. of the definition of benchmark script given in \S\ref{sec:exec:main}, plus the following:
-
-\begin{enumerate}
-\item[3'.] There are one or more \akey{check-sat} commands, 
-  each preceded by one or more \akey{assert} commands 
-  and zero or more \akey{push 1} commands, 
-  and followed by zero or more \akey{pop 1} commands.
-\end{enumerate}
-
-\noindent
-Furthermore, the trace executor will send a single 
-\akey{set-option :print-success true} command to the solver before 
-sending commands from the incremental benchmark script.
-
-\medskip
-Solvers must respond immediately to the commands sent by the trace executor, 
-with the answers defined in the SMT-LIB 2.0 format specification: that is,
-with a \texttt{success} answer for 
-\akey{set-option}, 
-\akey{declare-sort}, 
-\akey{declare-fun}, 
-\akey{assert}, 
-\akey{push 1}, 
-and \akey{pop 1} 
-commands,
-and with a \texttt{sat}, \texttt{unsat}, or \texttt{unknown} 
-for \akey{check-sat} commands.
-
-\header{Timeouts.}
-A time limit is set for the whole execution of each application
-benchmark (consisting of multiple queries).
-
-\header{Scoring.}
-The score for each benchmark is a pair $\langle n,m\rangle$, with
-$n\in[0,N]$ an integral number of points scored for the benchmark,
-where $N$ is the number of \akey{check-sat} commands
-in the benchmark.  $m\in[0,T]$ is the (real-valued) time is seconds, where $T$ is
-the timeout.  The score for the benchmark is initialized with
-$\langle0,0\rangle$ and then computed as follows.
-\begin{itemize}
-\item A correctly-reported \texttt{sat} or \texttt{unsat} answer after
-  $s$~seconds (counting from the beginning of this particular
-  \akey{check-sat}) contributes $\langle1,s\rangle$ to the running
-  score.
-\item An answer of \texttt{unknown}, an unexpected answer, a crash, or a memory-out during
-  execution of the query, or a benchmark timeout, aborts the execution
-  of the benchmark and assigns the current value of the running score
-  to the benchmark.  (Recall that there is one timeout for the entire
-  benchmark; there are no individual timeouts for queries.)
-\item The first incorrect answer to a \akey{check-sat} command has the effect of terminating the
-  trace executor, and the returned score for the overall benchmark
-  will be $\langle0,0\rangle$, effectively canceling the running score.
-\end{itemize}
-
-For example, if a benchmark has 5~\akey{check-sat} commands, and a
-timeout of 100~seconds, and a solver solves the first four in
-10~seconds each, then times out on the fifth, then the solver's score
-is $\langle4,40\rangle$.  If another solver solves each of the first
-four in 10~seconds each, and the fifth in another 40~seconds, its
-score is $\langle5,80\rangle$.  If a third solver solves the first
-four queries in 2~seconds each, but incorrectly answers the fifth, its
-score is $\langle0,0\rangle$.
-
-As queries are only presented in order, this scoring system may mean
-that relatively ``easier'' queries are hidden behind more difficult
-ones located at the middle of the query sequence.
-
-Scores are compared lexicographically---a solver with a higher
-$n$-value wins, with the cumulative time only used to break ties.
-Benchmarks' scores are summed componentwise to form a solver's total
-score for the competition.
-
 \section{Benchmarks and Problem Divisions}
@@
 
-We expect the problem divisions for SMT-COMP 2011 to include the following
+We expect the problem divisions for SMT-COMP 2009 to include the following
 SMT-LIB \emph{logics}.  These logics are specified in SMT-LIB format on the
@@
 
-\subsection{Main and parallel tracks}
-
 \header{Benchmark sources.} %
@@
 will be drawn from the SMT-LIB library.  Any benchmarks added to
-SMT-LIB by the May 15th release (see the timeline in
+SMT-LIB by the July 1 release (see the timeline in
 Section~\ref{sec:timeline}) will be considered eligible.  SMT-COMP
@@
 \header{Benchmark availability.} % A first release of the competition
-Benchmarks will be made available within May 15th, 2011.
-% A second and almost final release will be available on June 1st. 
-No additional
+Benchmarks will be made available on May 1st, 2010. A second and
+almost final release will be available on June 1st. No additional
 benchmarks will be added after this date, but benchmarks can be
-modified or removed to fix possible bugs or other issues, or to adjust their difficulty score (see below). 
-The final release that will be used for the competition will be posted on June
+modified or removed to fix possible bugs or other issues. The final
+release that will be used for the competition will be posted on June
 30th. The set of selected benchmarks will be published when the
@@
 tool.  \emph{Each top-level subdirectory within a division represents a distinct
-family.}  This represents a significant change from
-competition years before 2010, where
-\emph{terminal} subdirectories delineated families.
+family.}  This represents a significant change from previous
+competition years, where \emph{terminal} subdirectories delineated families.
 %
@@
 
-  \noindent%\textbf{New for 2010:} 
-  Using the same random seed as
+  \noindent\textbf{New for 2010:} using the same random seed as
   for benchmark selection and scrambling, 5 ``check'' benchmarks will
@@
   tool~\cite{brummayer+09}.  The (exact version of this) tool will be
-  publicly available from the SMT-COMP~2011 web site before the
+  publicly available from the SMT 2010 web site before the
   competition.  Since these benchmarks are generated after the random
@@
   bug-discovery techniques.
-\item \emph{industrial.} These benchmarks come from some real application
-      and are produced by tools such as bounded model checkers, static analyzers, extended
-      static checkers, etc.
+\item \emph{industrial.} These benchmarks come from some real application and are produced by tools such as bounded model checkers, static analyzers, extended static checkers, etc.
 \item \emph{random.} These benchmarks are randomly generated.
@@
 difficulty for a particular benchmark will be assigned by running SMT
-solvers from the 2010 competition that finished in good
-standing and using the formula:
+solvers from the 2009 competition that finished in good
+standing\footnote{Note that the corrected version of MathSat that was
+  submitted after the 2009 deadline, which ran \textit{hors concours}
+  in the 2009 competition, will be used instead of its ``official''
+  counterpart.} and using the formula:
 
@@
   division are always included, together with all benchmarks on which
-  at least one 2010 solver required more than 5~seconds.  \emph{This
+  at least one 2009 solver required more than 5~seconds.  \emph{This
     is intended to have the effect of retiring ``very easy''
-    benchmarks that were solved by every 2010 solver in less
+    benchmarks that were solved by every 2009 solver in less
     than 5~seconds, \emph{unless} doing so reduces the pool of
     benchmarks for the division to less than~300.}
-
-\item \textbf{Retire inappropriate benchmarks.} %
-  The competition organizers will remove from the eligibility pool
-  certain SMT-LIB benchmarks that are inappropriate or uninteresting
-  for competition, or cut the size of certain benchmark families to
-  avoid their over-representation.
 
@@
   Next, 200 slots are allocated for the division as follows:\footnote{The
-  number ``200'' is a guideline, and is expected to be used.  However, the
+  number "200" is a guideline, and is expected to be used.  However, the
   SMT-COMP organizers reserve the right to reduce this to an appropriate
@@
 entrants other than the organizers.  Additionally, the integer part of
-the opening value of the New York Stock Exchange Composite Index on
-July~12th
+the opening value of the New York Stock Exchange Composite Index on August 4th
 will be added to the other seeding values.  This helps provide transparency,
@@
 favor of their submitted solvers.  Benchmarks will also be slightly
-scrambled before the competition, using a simple benchmark scrambler %the same scrambler as last year,
+scrambled before the competition, using the same scrambler as last year,
 seeded with the same seed as the benchmark selector.  Both the
@@
 cheating).
-
-\subsection{Application track}
-
-\header{Benchmark sources.} %
-Benchmarks for the application track will be collected by the SMT-COMP organizers.
-Any benchmark available to the organizers by May 15th (see the timeline in
-Section~\ref{sec:timeline}) will be considered eligible.
-
-\header{Benchmark availability.} 
-A first release of the application track
-benchmarks will be made available within March 31st, 2011.
-More benchmarks can be collected, until May 15th.
-No additional
-benchmarks will be added after this date, but benchmarks can be
-modified or removed to fix possible bugs or other issues. 
-The final release that will be used for the competition will be posted on 
-% rb 23/3: changed from June 30th to agree with sec 6.
-June 15th.
-
-\header{Benchmark demographics and selection.} 
-All the available benchmarks will be used for the competition. 
-For this first year of the application track, no difficulty will be assigned to the benchmarks.
-Benchmarks will be slightly scrambled before the competition, using the same scrambler and 
-random seed as the main track. 
-% rb 25/3: added
-For this year, the selection algorithm for the application track will be chosen after the
-deadline of May 15th, when the exact demographic of the benchmarks (collected with a usual
-``call for benchmarks'') will be available.
 
@@
 \end{center}
-\caption{\label{fig:points}Points and Penalties for the main and parallel tracks.}
+\caption{\label{fig:points}Points and Penalties}
 \end{figure}
@@
 entrants from distinct research groups competing will be taken to be
-those with the highest score. In addition to recognizing the overall
-winner in each division, the top solver that provides its source code will also be
-recognized in each division.  
-For Problem Divisions with fewer than three
-entrants, the results will be reported but no winner officially
-declared.
-
-For the main and parallel tracks, the score will be computed according to the system of points and
-penalties in Figure~\ref{fig:points}. 
-As indicated, correct answers
+those with the highest score, according to the system of points and
+penalties in Figure~\ref{fig:points}.  In addition to recognizing the overall
+winner in each division, the top solver providing its source code will also be
+recognized in each division.  As indicated, correct answers
 are awarded a positive number of points, while incorrect answers are
@@
 on formulas for which it gave a correct answer will be
-considered the winner.
-
-For the application track, the score will be computed according to the procedure described in \S\ref{sec:exec:application}.
+considered the winner.  For Problem Divisions with fewer than three
+entrants, the results will be reported but no winner officially
+declared.
 
@@
 \begin{description}
-\item[March 31] First version of the benchmark library for the application track posted for comment.
-  First version of the benchmark scrambler, benchmark selector and trace exector made available.
-\item[April 30] Final version of the benchmark scrambler, benchmark selector and trace exector made available.
-\item[May 15] No new benchmarks can be added after this date, but
+\item[May 1] First version of the benchmark library posted
+for comment. 
+\item[June 1] No new benchmarks can be added after this date, but
   problems with existing benchmarks may be fixed.
-\item[June 15] Benchmark libraries are frozen.
-\item[July 9 (7pm ET)] Solvers due via SMT-Exec (for
-  all tracks), including system
+\item[June 15] Benchmark library is frozen.
+\item[July 8] (7pm ET) Solvers due via SMT-Exec (for
+  both sequential and concurrent tracks), including system
   descriptions and magic numbers for benchmark scrambling.
-\item[July 11 (7pm ET)] Final versions due, fixing any last-minute
+\item[July 10 (7pm ET)] Final versions due, fixing any last-minute
  bugs (this marks the end of the two-day grace period for
@@
 \item[July 12] Opening value of NYSE Composite Index used to complete random seed.
-\item[July 14--20] Anticipated dates for SMT-COMP 2011.
+\item[July 14--16] Anticipated dates for the concurrent track of
+  SMT-COMP 2010.
+\item[July 16--19] Anticipated dates for the main sequential track of
+  SMT-COMP 2010.
 \end{description}}

### 2015-02-11 rules/rules15.tex
2014 rules copied as basis for 2015.

--- 2014-05-29 rules/rules14.tex
@@
 
-\title{DRAFT\\Satisfiability Modulo Theories Competition (SMT-COMP) 2014: Rules and 
+\title{Satisfiability Modulo Theories Competition (SMT-COMP) 2014: Rules and 
 Procedures}
@@
 Any generated files should be produced there, not, for example, in the system tmp area.
+The StarExec system sets a limit on the amount of disk storage permitted - typically 20GB (cf. the User Guide).
 The temporary directory and its contents are deleted after the job is complete.
@@
 Note that the executor terminates processing the script upon receiving an incorrect response.
+
+The disk space and memory limits on the application track are the same as for the main track.
 
@@
   avoid their over-representation.
+
+\item \textbf{Eliminate benchmarks whose status is unknown.} %
+  The selection process ignores any benchmark whose expected output is neither sat nor unsat.
+There is a significant number of `unknown' benchmarks in the library; these are certainly interesting and are a challenge to solve, but they are not used in the competition.
 
@@
 A solver's score for the whole competition is the sum of these tuples over all the
-divisions in which the solver participates.
-The best value of M is the one with the least total value of $e$, secondly, the largest total value for the second component of the tuple, and thirdly, the least value of $m$.
+divisions in which the solver participates. The best value of M is the one with the least total value of $e$, and secondly, the largest total value for the second component of the tuple.
 
@@
 \item The bronze medal will be awarded to the solver that wins the (sequential) QF\_BV division according to the usual $\langle e,n,m\rangle$ metric of subsection \ref{scoring}. 
-\item The winner of the gold medal is excluded from consideration for the silver medal; the winners of the gold and silver medals are excluded from consideration for the bronze medal.
+\item The team winning the gold medal is excluded from consideration for the silver medal; the teams winning the gold and silver medals are excluded from consideration for the bronze medal.
 \end{itemize}
@@
 Time is omitted from the metric both to simplify the metric and because it is only of third importance in the regular competition metric and is difficult to compare across divisions.
+
+The gold and silver medals emphasize breadth of logic support; the organizers chose to award the bronze medal to excellence in a single logic.
+Rather than try to compare performance across logics, we selected on logic, QF\_BV, for this award.
+This logic is a commonly supported logic and many solvers concentrate on BV problems alone.
 
@@
 
-\section{Disclaimer}
+\section{Acknlwedgements and Disclaimer}
 \begin{itemize}
@@
 
+\item Many others have contributed benchmarks, effort, and feedback.
+In particular, Clark Barrett and Morgan Deters processed the many benchmark submissions and completed the work of transitioning benchmarks from SMTExec to StarExec.
+Aaron Stump field many questions and diagnosed and managed the fixing of bugs in Star Exec.
+
+\item The StarExec cluster is supported by NSF grants \#1058748 and \#1058925.
+
 \item David Deharbe is associated with the solver group producing the veriT solver.

### 2015-02-16 rules/rules11.tex
I believe this was the final (official) version of the 2011 rules.

@@
 
-\date{}
+\date{\small This version revised \the\year-\the\month-\the\day}
 
@@
 \end{itemize}
+
+Additionally, non-competitive divisions and tracks will not be exhibited as
+part of the competition: at least two competitors must be entered
+into a division for it to run as part of the competition.
+If necessary, and based on final submissions, the organizers may elect to
+combine competition divisions to make them competitive (such decisions will
+be made with input from the community).
+
+As in SMT-COMP 2010, the 2011 version will incorporate a small number of
+random "fuzzer-generated" instances (see below) to help promote
+attention to solver correctness.
+
+It is important for competitors to track discussions on the SMT-COMP mailing
+list, as clarifications and any updates to these rules will be posted there.
 
@@
 A time limit is set for the whole execution of each application
-benchmark (consisting of multiple queries).
+benchmark (consisting of multiple queries).  We anticipate the
+timeout to be around 30~minutes.
 
@@
 \item QF\_LIA: linear integer arithmetic.
+\item QF\_NRA: nonlinear real arithmetic.
 \item QF\_NIA: nonlinear integer arithmetic.
@@
 considered ineligible for competition and are not used.
-%
-Additionally, certain benchmarks deemed inappropriate for competition
-may be cut by the organizers, and in some cases, representative subsets
-of benchmarks from a certain source may be included for the selection
-instead of all benchmarks from that source.
 %

### 2015-02-16 2013/report-JAR/SMTEVAL-2013-R.tex
Moved (non-public) source files out of smtcomp-web.

%%\documentclass[12pt,oneside]{article}

\documentclass[smallcondensed]{svjour3}
%\providecommand{\event}{Journal TBD}
%\providecommand{\publicationstatus}{ } %% TBD - fill in any footer
%%\documentclass[12pt,oneside]{llncs}

%% Language %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{hyperref}   %% sets hyperlinks within a pdf
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{parskip}
\usepackage{enumitem}
\usepackage{wrapfig}
\usepackage{subcaption}
\usepackage{caption}
\usepackage{array}
\usepackage{color}
\usepackage{colortab}
\usepackage{xcolor}
\usepackage{tabularx}
\usepackage{pdfpages}

%%\usepackage{subcaption}

%%\usepackage{lmodern} %Type1-font for non-english texts and characters

%% Packages for Graphics & Figures %%%%%%%%%%%%%%%%%%%%%%%%%%
%\usepackage{graphicx} %%For loading graphic files
%\usepackage{subfig} %%Subfigures inside a figure
%\usepackage{tikz} %%Generate vector graphics from within LaTeX

%\usepackage{mathptmx} %% Times fonts, for math as well

%%\makeindex

%% The adjustment amounts depend on the font
%% -.5 for 12pt, -.875 for 10pt
%% FIXME: should these be set instead of adjusted?
%% Use these with lncls?
%\addtolength{\oddsidemargin}{-.5in}
%\addtolength{\evensidemargin}{-.5in}
%\addtolength{\textwidth}{1.0in}
%\addtolength{\topmargin}{-.5in}
%\addtolength{\textheight}{1.0in}

%\def\titlerunning{SMTEVAL-2013}
%\def\authorrunning{Cok, Stump, Weber}

\newcommand{\tb}{\textbullet}
\newcommand{\tjark}[1]{\marginpar{\footnotesize{#1}}}
\newcommand{\tjarkx}[1]{\makebox[0pt][c]{\raisebox{0pt}[0pt][0pt]{\Large\textcolor{red}{${}^*$}}}\marginpar{\footnotesize{#1}}}

\newcommand{\cellbr}[2][c]{\begin{tabular}[#1]{@{}c@{}}#2\end{tabular}}

\journalname{Journal of Automated Reasoning}

\begin{document}
\title{The 2013 Evaluation of SMT-COMP and SMT-LIB}

%\author{
%David R. Cok \\ GrammaTech, Inc., USA \\ \email{dcok@grammatech.com} \\ 
%Aaron Stump \\ University of Iowa, IA, USA \\ \email{aaron-stump@uiowa.edu} \\ 
%Tjark Weber \\ Uppsala University, Sweden \\ \email{tjark.weber@it.uu.se} }

%% eptcs format
\author{
David R. Cok 
\and  
Aaron Stump
\and  
Tjark Weber
}

\institute{
David R. Cok  \at GrammaTech, Inc., USA \email{dcok@grammatech.com}
\and
Aaron Stump \at University of Iowa, IA, USA \email{aaron-stump@uiowa.edu}
\and
Tjark Weber \at Uppsala University, Sweden \email{tjark.weber@it.uu.se}
}
%% lncls format
%\author{David R. Cok \inst{1} \and \\ 
%Aaron Stump \inst{2} \and \\ 
%Tjark Weber \inst{3}  \\
%}
%
%\institute{GrammaTech, Inc., USA \email{dcok@grammatech.com} \and
%University of Iowa, IA, USA \email{aaron-stump@uiowa.edu} \and
%Uppsala University, Sweden, \email{tjark.weber@it.uu.se}
%}

\date{}
\maketitle
%\pagestyle{headings}
%\pagenumbering{arabic}
%\centerline{\today}

%\abstract{
\begin{abstract}
After 8 years of SMT Competitions, the SMT Steering Committee decided,
for 2013, to sponsor an evaluation of the status of SMT benchmarks and
solvers, rather than another competition.  This report summarizes the
results of the evaluation, conducted by the authors.  The key
observations are that (1)~the competition results are quite sensitive
to randomness and (2)~the most significant need for the future is
assessment and improvement of benchmarks in the light of SMT
applications.  The evaluation also measured competitiveness of
solvers, general coverage of solvers, logics, and benchmarks, and
degree of repeatability of measurements and competitions.
\end{abstract}

\section{Introduction}

\subsection{The Competition history and goals}
From 2005 through 2012 (and in 2014), the SMT community
sponsored an annual competition among SMT solvers
(cf.\ Fig.~\ref{Fig:history}).  The purpose of the competition is to
encourage advances in SMT solver implementations acting on benchmark
formulas of theoretical or practical interest.  Public competitions
are a well-known means of stimulating advancement in software tools.
For example, in automated reasoning, the SAT and CASC competitions for
propositional and first-order reasoning tools, respectively, have
spurred significant innovation in their fields~\cite{leberre+03,PSS02}.  Indeed, the SMT competition increased in
size each year: more benchmarks were added, new solver teams
participated, solver performance improved, and more logic divisions were defined.

The particular goals of SMT-COMP include the following~\cite{smtcompweb}:
\begin{itemize}[noitemsep]
\item enable research on SMT solvers by benchmarking and comparing performance;
\item promote a standard format for SMT problems (SMT-LIB v2~\cite{BarST-SMT-10});
\item collect additional benchmarks;
\item identify and develop new theories and logics for SMT, encouraging their inclusion in SMT solvers;
\item introduce SMT users and implementors to each other;
\item provide a forum for SMT implementors to promote their SMT solvers and for SMT users to assess the comparative performance of solvers; and
\item encourage the development of industrial-strength solvers for wide-spread use.
\end{itemize}

\begin{figure}
\centering
\includegraphics[width=\textwidth]{SMTCOMP-History}
\caption{SMT-COMP history}
\label{Fig:history}
\end{figure}

\subsection{Concerns prompting an evaluation}

In 2013, the SMT Steering Committee decided to take a collective breath and sponsor an evaluation of the current state of the art, without the pressure of a competition. In particular, the implementation teams found that preparing for a competition required considerable engineering work that detracted from other goals. On the one hand, the engineering work is necessary for users to use the tools as off-the-shelf applications. But holding the competition every year was causing some otherwise highly involved teams to withdraw. Thus there was a collective desire to pause the competition cycle for a year.

Second, there was a desire to evaluate the state of the SMT community and the competition. The competition had become focused on details of performance on a particular set of benchmarks for particular logics and there was a feeling that its overall results had become somewhat predictable. An evaluation of progress of the SMT community was desired, with a consideration of other metrics and goals, not just winning narrowly focused competitions.

And third, for many years the competition had relied on the SMT-Exec computational infrastructure~\cite{springerlink:10.1007/s10817-012-9246-5}.  A new infrastructure, StarExec~\cite{StuST-IJCAR-14,webStarExec} had been funded by the NSF and developed at the University of Iowa, but had not yet been tried out in earnest.  In fact, a goal in~2012 had been to use StarExec for SMT-COMP~2012; however, StarExec was not sufficiently operational and the competition had to revert to SMT-Exec.  It was anticipated that an evaluation in 2013, with less deadline pressure, would enable using StarExec on a shake-down cruise prior to a competition in 2014 at the Federated Logic Conference~(FLoC) Olympic Games~\cite{webOlympicGames}.

\subsection{Evaluation topics}

The SMT Steering Committee appointed a team of evaluators (the authors
of this report) to examine areas of interest. The evaluators, who are
not affiliated with any solver team, independently studied the
following topics:
\begin{itemize}[noitemsep]
\item continuity and turnover in SMT solver participation in past competitions (\ref{Solvers})
\item the performance of all historical and current solvers on the full set of benchmarks, measuring
\begin{itemize}[noitemsep]
\item the improvement in performance over time (\ref{Progress})
\item repeatability of performance measurements (\ref{Accuracy})
\item repeatability of competition results (\ref{CompetitionRepeatability})
\item competitiveness of solvers (\ref{Competitiveness})
\item parallel vs. sequential performance (\ref{parallel})
\end{itemize}
\item the usefulness of various logics
\begin{itemize}[noitemsep]
\item characteristics of existing logics (\ref{Lattice})
\item which logics are implemented by solvers (\ref{Coverage})
\item which logics are particularly relevant to application areas (\ref{Applications})
\end{itemize}
\item the state of existing benchmarks
\begin{itemize}[noitemsep]
\item the range of computational difficulty of the benchmarks (\ref{Benchmarks})
\item the degree to which benchmarks discriminate among solvers (\ref{Benchmarks})
\item which logics have support in benchmarks (\ref{Benchmarks})
\end{itemize}
\end{itemize}

\section{Evaluation tools}

\subsection{SMT-LIB benchmarks}

One goal of the SMT project since its inception has been collecting benchmarks by which to evaluate SMT solvers and to represent challenge problems in the field. The growth in the number of benchmarks available is shown in the graphics of Fig.~\ref{Fig:history}. All\footnote{One benchmark, added late, was not included in all of the data accumulation; hence some tables report 95\,491 benchmarks and some 95\,492.} of the benchmarks present in StarExec at the time of evaluation (95\,492 benchmarks) were used for the evaluation, including those with unknown status. Of course, in previous years only a subset of these were available, since new benchmarks were added from year to year. Also in 2012, some benchmarks were used in the competition that were not yet added into the SMT-LIB benchmark set and were not yet in StarExec at the time of the evaluation. The 2012 benchmark set also included some incremental benchmarks that were not used in this evaluation. Furthermore, the competition each year used a random selection of benchmarks (guided by a difficulty distribution). The fact that the set of benchmarks used in competitions was different each year muddied any year-to-year comparison of results. By using all available benchmarks in the evaluation, we ensure that the current assessment is not susceptible to random choices in benchmark selection (cf.~Section~\ref{CompetitionRepeatability}). The various kinds of benchmarks and their distribution across logics are discussed below in Section~\ref{Evaluations}.

\subsection{Solvers}
\label{sec:solvers}

The SMT competitions required that participating solvers be publicly available Linux applications, and that they be available for any future experimenter to use on new experiments. Thus all historical solvers are still available. However, in 2010, the competition adopted the then new benchmark format, SMT-LIB~v2~\cite{BarST-SMT-10}. Thus solvers prior to 2010 do not run on the current benchmark set. The participating solvers are shown in Fig.~\ref{Fig:solvers}.

\begin{figure}
\centering
\begin{tabular}{|l|l|*{8}{c@{\hskip 10pt}}c|}
\hline
\input{solvers2}
\end{tabular}

\caption{Solvers used in each year of SMT-COMP and SMT-EVAL. Solvers prior to 2010 (marked by~X) do not support SMT-LIB~v2 and were not used for SMT-EVAL. Boxes marked with a~\textbullet{} symbol identify solvers that are new for the evaluation; all solvers since 2010 (marked with~+ or~\textbullet{} symbols) were used for the evaluation.}
\label{Fig:solvers}
\end{figure}

SMT-EVAL used all historical solvers since~2010 (32~total), added 9 versions of previous solvers that were updated in~2013, and included 4 additional experimental solvers,\footnote{These were four variations of a portfolio-style solver submitted by Abziz~\cite{aziz:msc,aziz2012machine}.} for a total of~45 solvers.  All solver implementation teams that we could reach were apprised of the upcoming evaluation and given the opportunity to submit new versions of their solvers. Some teams simply submitted the current version of their solver or advised us to download the current public version from the team's website. Thus the solvers are not necessarily tuned to particular application domains or for competition. Any comparisons for particular applications or kinds of benchmark problems should perform an independent analysis.

\subsection{Interpreting solver output}

Given the large number of solver-benchmark combinations, it was not
feasible to manually inspect the output of each job pair.  Thus, we
needed to determine mechanically whether a solver reported a benchmark
as satisfiable, unsatisfiable or unknown (or did not return a result
within the time limit).

On StarExec, this is done by providing a \emph{post-processor}, i.e.,
an executable that operates on the output of each job pair.
Unfortunately, two features of StarExec made it difficult to interpret
solver output in a way that is fully SMT-LIB~v2 compliant.  First,
StarExec collects the entire output of a job pair in a single file
before passing it to the post-processor.  Thus, it is not possible to
reliably determine which output a solver has generated specifically in
response to a benchmark's {\tt check-sat} command.  Second, StarExec
conflates standard output and standard error.  We hope that this
behavior will be changed in the future, but for SMT-EVAL this made it
impossible to distinguish between regular solver responses and error
messages.

To determine the result of each job pair, we used a post-processor
that searched for the words {\tt sat}, {\tt unsat} and {\tt unknown}
in the output file, and reported the corresponding result if it found
exactly one of them; otherwise, it reported no result.  This
conservative approach may have caused a small number of (otherwise
valid) solver responses to be discarded.  It was adopted to minimize the
number of incorrect results reported by the post-processor.

\subsection{Benchmark scrambling}

SMT-COMPs in previous years used benchmark scrambling~\cite{springerlink:10.1007/s10817-012-9246-5}.  We
did not scramble benchmarks for SMT-EVAL, mainly because support for
this feature was not yet available in StarExec.  In principle, this
means that solvers could have cheated by matching benchmark contents
or filenames against a database of known SMT-LIB benchmarks, or even
by simply extracting the {\tt :status} information present in most
benchmarks.  Ruling out cheating with certainty would require careful
inspection of solver sources, which are not available for all solvers.
However, based on the evaluation data, and taking into account the
lack of strong incentives for cheating in SMT-EVAL, we have no reason
to believe that such shortcuts to success occurred.

An additional use of benchmark scrambling is that the change in syntax
and identifiers can, for some solvers, change the search paths or the
preprocessing that is performed. Thus scrambling serves to exercise
different code paths and adds an additional dimension of testing and
performance measurement to competitions and evaluations. It would be
interesting to investigate these effects of scrambling in detail; we
did not do this as part of SMT-EVAL.

%Several solvers reported syntax errors on some benchmarks.  We
%validated all benchmarks with two independently developed SMT-LIB~v2
%parsers~\cite{TODO,TODO} to ensure that they are syntactically
%conforming.

\subsection{StarExec}

SMT-EVAL successfully used the new StarExec computational framework~\cite{StuST-IJCAR-14,webStarExec}. Running SMT-EVAL on StarExec did indeed expose a number of bugs and user interface issues; these were corrected in the course of the SMT-EVAL runs. Thus SMT-EVAL served a valuable purpose in preparing StarExec for larger scale use.

SMT-EVAL's largest computational job was running all 45 of the evaluated solvers on all of the relevant non-incremental benchmarks in the SMT library. 
The benchmarks belong to different {\em logics} and solvers are characterized by which logics they support. 
So for each logic, the evaluation executed the cross product of all benchmarks for that logic and all solvers (in all years) that support problems in that logic, for a total of 1\,663\,478 solver-benchmark combinations (called {\em job-pairs} in StarExec). 
This job took several months of wall-clock time to run. 
We ran it in quarters, using the result of the first quarter to adjust our procedures and debug some of StarExec, before running the rest of the solver-benchmark job pairs. 
Because of a bug (now corrected), the results of about 600 job-pairs were not present in the accumulated results. 
These were identified and rerun as an additional ``mop-up'' job. 
Each solver-benchmark pair was run in an independent environment, on a computation node by itself, with time and memory limits, as described in Section~\ref{parallel}.

\section{Evaluation results}
\label{Evaluations}

The evaluation team's observations on the questions it considered are presented in the following subsections; our overall conclusions are listed in Section~\ref{Conclusions}.  The raw data used as the basis for our observations, collected from StarExec, are all archived on the SMT-COMP website, at \url{http://sourceforge.net/p/smtcomp/code/HEAD/tree/trunk/smtcomp-web/2013/data} as 7z-compressed files.  (The largest is~25\,MB.)  The data can also be viewed directly on StarExec, at \url{https://www.starexec.org/starexec/secure/explore/spaces.jsp?id=4566}, using its guest login.

\subsection{Solver participation}
\label{Solvers}

The historically participating solvers are shown in Fig.~\ref{Fig:solvers}. There are a number of observations to be made about solver participation.

\begin{figure}
\centering
\begin{tabular}{|l|ccccccccc|}
\hline
year                & 2005 & 2006 & 2007 & 2008 & 2009 & 2010 & 2011 & 2012 & 2013 \\ \hline
\# of participants  & 11   & 11   & 9    & 13   & 12   & 10   & 11   & 11   & 9   \\ \hline
\# dropping out     &      &  4   & 6    &  2   &  3   &  7   &  2   &  4   & \\ \hline
\# new participants & (11) &  4   & 4    &  6   &  2   &  5   &  3   &  4   &      \\ \hline
\end{tabular}
\caption{Turnover in solver team participation. There are no entries for changes in 2013 because in that year there was no competition with entrants.}
\label{Fig:participation}
\end{figure}
\begin{itemize}
\item As shown in Fig. \ref{Fig:participation}, the number of solvers participating each year has been fairly constant, ranging
from 9-13, with a median value of 11 participants. The data for 2013 is an anomaly in two respects. The count of 9 only includes those solvers that were explicitly submitted new for 2013. Second, Abziz contributed a portfolio solver that makes an automatic choice, based on machine learning, of which among other existing solvers to apply to a benchmark using observed features of the benchmark. Abziz submitted two instances of his portfolio that used solvers from 2011; those instances of his portfolio solver are not counted in 
Fig. \ref{Fig:participation} since they were not available in 2011, though they are included in Fig.~\ref{Fig:solvers}. In addition, three variations were contributed in 2012; we count just one participation unit in 
Fig. \ref{Fig:participation} for 2012, though all three (and the two 2011 entries) were used in the evaluations described in this paper.

\item Though any team dropping out of future years' competitions is to be regretted, such turnover is to be expected: research projects and Ph.D.\ students move on to other topics. The year of the most drop-outs is~2010, when the benchmark format changed; not all teams could invest the effort to change their front-ends and to accommodate the new semantic features of SMT-LIB~v2. 
\item Accompanying the drop-outs is a roughly equal number of new participants each year; roughly 1/3 of the participants each year are new. One of the goals of an organized competition is to foster new participation, providing a venue in which it is easy to participate and self-evaluate against the state-of-the-art. Our observation is that this goal is being accomplished, despite the significant effort required to implement a reasonably competitive solver. 
\item Despite the turnover, some teams have participated regularly throughout the history of the competition: CVC3/4 and MathSat have participated since the beginning; several others have participated in most of the years since they began being involved.
\end{itemize}

\subsection{Logics}
\label{Lattice}

\begin{figure}
\centering
\includegraphics[width=\textwidth]{LogicLatticeN}
\caption{Graph of SMT logics defined in SMT-LIB. The links represent a natural inclusion by characteristics, but {\it not} a sub-logic relationship. QF\_ABV is defined, but is often subsumed in QF\_AUFBV, and is not usually listed separately in other tables in this report. Q is not a logic by itself but is a characteristic indicating that quantified expressions are permitted in the logic; similarly N indicates non-linear arithmetic is allowed.}
\label{Fig:lattice}
\end{figure}

SMT-LIB defines a number of theories and logics. The logics are a combination of theories with additional functions or logic symbols or restrictions on the vocabulary of the theories. For example, the QF\_IDL logic uses the underlying Ints theory, but restricts terms to equalities and inequalities between constants and simple differences of variables.
The combination of the Ints theory and the Reals theory adds functions that convert between integers and reals (among other things).

Leaving aside difference logics as special cases of integer and real logics, there are essentially these mostly orthogonal characteristics underlying the theories and logics:
\begin{itemize}[noitemsep,nolistsep] %% these modifiers are not supported in all document classes
\item IA: integers 
\item RA: reals
\item N: non-linear arithmetic
\item A or AX: arrays
\item UF: uninterpreted functions
\item QF\_: quantifier freeness
\item BV: bit-vectors
\end{itemize}
This list of characteristics partially corresponds to the set of SMT-LIB theories. The exceptions are quantification and non-linearity, both of which designate lifting restrictions on the kinds of terms allowed in the resulting logic. (Since they do not correspond exactly to underlying SMT theories, the term {\em characteristics} is used in this discussion.)

It is possible to define a logic with any powerset of these characteristics in an almost purely combinatorial sense. 
Barring non-linearity without arithmetic and the useless empty set, there are 111 combinations of characteristics (instead of the full 128). SMT-LIB has definitions and benchmarks for 20 of these logics (excluding QF\_IDL, QF\_RDL, and QF\_UFIDL) at the time of the evaluation, expanded to 34 in 2014. Fig.~\ref{Fig:lattice} shows what might be expected to be natural containment relationships among the logics defined at the time of this evaluation.

However, what might be expected to be natural containment relationships are not actually sub-logic relationships. That more accurate relationship is shown in a diagram on the SMT-LIB website: \url{http://smtlib.cs.uiowa.edu/logics.shtml} (due to Cesare Tinelli). The principal cause of this lack of sub-logic relationship is that many of the logics supporting arrays support only specific sorts of arrays. For example, the basic QF\_AX logic allows arbitrary new sort symbols, including arrays over those free sorts. However, QF\_ABV (arrays and bit-vectors) does not allow new sort symbols and only allows arrays over bit-vector sorts.

The naming convention for logics is almost but not quite simply a combination of the letters indicated in the list above,
corresponding to the characteristics of the logic, with the letters listed in order by convention:
\begin{center}
[QF\_][A\textbar AX][UF][BV][N\textbar L][IA\textbar RA\textbar IRA].
\end{center}

\noindent The non-uniformities are these:
\begin{itemize}[noitemsep,nolistsep]
\item quantification is indicated by {\em removing} a QF\_ prefix;
\item the absence of non-linearity~(N), i.e., linearity, is indicated by an~L, instead of by no designator;
\item integer and real arithmetic are indicated by two letters (IA and~RA) and their combination by~IRA;
\item the~A used in the arithmetic designators could be ambiguous with the designator for arrays, except for position;
\item a logic with just arrays is named QF\_AX, whereas in other combinations including arrays, just an~A instead of~AX is used.
\end{itemize}
For example, UFNIA includes quantification (no QF\_ prefix), uninterpreted functions~(UF), non-linearity~(N), and integer arithmetic~(IA), leaving out arrays, bit-vectors, and reals.

These names have roots in the history of development of SMT-LIB. Nevertheless as the set of logics grows---23 here and 34 by the 2014 competition---the situation will increasingly confuse new users of SMT-LIB trying to understand the structure of logics; in addition new theories and accompanying logics are anticipated.
It would be useful to standardize the naming convention along the lines of current use, perhaps with slight adjustments (e.g., renaming QF\_AX to QF\_A and removing the excess~A from~IA and~RA), in order to define precisely the logic implied by any combination of designators. A policy regarding names would provide a process for defining names for new theories and logics. This would
also make it easier to accurately characterize new benchmarks and to summarize the logics supported by a given solver. This need has been raised to the SMT-LIB coordinators and some work has been started to address it.

%The absence of many combinations appears to be simply a matter of ad hoc lack of research or non-existence of benchmarks. For example,
%all five meaningful combinations of {\tt UF}, {\tt N} and {\tt RA} are present, but only four of the combinations of {\tt UF}, {\tt N} and {\tt IA}. Obviously there is no point to filling out all combinations, just for completeness. However,
%benchmarks could come in any form, and it would be useful to be able to categorize them precisely. The collection of benchmarks should be driven by technical interest and application need. With the exception of some of the needed conversions (e.g., between bitvectors and numbers), there seems little technical impediment to combining characteristics once the corresponding underlying theories and decision procedures are implemented. That leaves application need as a driver; this is discussed further in section \ref{Applications}. It is also conceivable that some logics should be deemphasized, either because solvers have progressed to such an extent that the logic no longer poses interesting technical questions or because applications have little need for the logic.

\subsection{Coverage of logics by solvers}
\label{Coverage}

\begin{figure}
\centering
\input{LogicSupportBySolvers}
\caption{Support for each logic as stated by solver implementors. The dots instead of Xs identify the 2013 versions of solvers. The numbers in the bottom row are the number of 2013 solvers for each logic.}
\label{Fig:solversupport}
\end{figure}

Each solver supports some subset of the SMT logics and the corresponding theories and characteristics described in the previous section. The set of logics supported by solvers (as stated by the solver teams) is shown in Fig.~\ref{Fig:solversupport}. CVC and Z3 support all or nearly all logics, with CVC4 just missing full support for non-linear arithmetic (it does have partial support, with full support in the 2014 competition); veriT and MathSat support a significant number of logics.

The numbers in the bottom row of the figure state the number of current (2013) solvers that support a given logic. The characteristics most lacking are quantifiers and nonlinearity. Those with the most support are bitvectors, uninterpreted functions and arithmetic.

Note that the support indicated is that stated by the solver supplier at the time the solver was submitted to a competition. 
In some cases, a solver supports one logic but is not listed as supporting a subset of that logic. The general reason is that the subset, with restricted characteristics, allows for specific optimizations that are not implemented. The more general solver could act on problems of the
more restricted benchmarks but is not deemed competitive and thus was not formally entered into the competition for the restricted logic.

\subsection{Progress in solver performance}
\label{Progress}

We can obtain a measure of the overall year-by-year improvement in solver performance by applying each year's solvers to all the benchmarks (within each logic), observing the best performance on each benchmark. That is, the data shows a {\em virtual best performer}, obtained by an all-knowing oracle choosing, for each benchmark, the solver that performs best on that benchmark.

Fig.~\ref{Fig:CumulativeTimes} shows the fraction of benchmarks completed (y-axis) within a given time (in seconds, on the x-axis); thus points toward the upper left are better (more completed in less time). The results for all logics are shown together. 
The four curves are the data for the four years from 2010 to 2013. The lowest (marked with fine dots) curve is that for 2010. 
There is clearly significant progress made from 2010 to later years: the number of benchmarks completed within a given time is noticeably higher; we did not attempt to identify the source of this historical improvement. The curves for 2011 and 2012 (heavy dashes and short dashes, respectively) are clearly above 2010, but are not substantially different from each other. The solvers for 2013 (heavy solid line) are uniformly above those for previous years, but not by a large amount.

By this data, the improvements in raw SMT solver performance on the current set of benchmark problems have slowed down, though they may have improved by other measures.

\begin{figure}
\centering
\includegraphics[width=.95\textwidth]{CumulativeTimes}
\caption{The fraction of benchmarks (y-axis) whose winning time is less than the given number of seconds (x-axis), by year.}
\label{Fig:CumulativeTimes}
\end{figure}

An alternate measure of solver progress is to count, for a given logic, what fraction of the benchmarks have a better time in a given year than in the previous year, by the best solver for each year. That data is shown in Fig.~\ref{Fig:bettertime}. Though most data points indicate that most benchmarks improved year to year, the progress is not uniform. The progress from 2010 to 2013 shows nearly all logics having improvement rates above 80\%, but there are definitely some laggards. There is not necessarily a monotonic improvement because the set of solvers is different from year to year; some well-performing solvers may choose not to participate every year.

\begin{figure}
\centering
%\begin{tabular}{|l|r|rrrr|}
%\hline
%\input{bettertime}
%\hline
%\end{tabular}
\includegraphics[width=\textwidth]{bettertime.pdf}
\caption{The fraction of benchmarks whose best time improved between the given years.}
\label{Fig:bettertime}
\end{figure}

\subsection{Repeatability of competitions}
\label{CompetitionRepeatability}

The SMT competition aims to be a repeatable measurement of relative performance of solvers. To that end the details of the competition, such as the rules and selection of benchmarks, are made public. In addition the solvers themselves are required to be made public after the competition.

However, there are aspects of the competition that are not deterministic. We measured two of those in this evaluation:
\begin{itemize}[noitemsep,nolistsep]
\item {\em The repeatability of the time a given solver takes on a given benchmark} (Section~\ref{Accuracy}). This variation is a combination of two factors: any variation in execution and timing by the StarExec system itself, and any non-determinism in the execution of the solver.
\item {\em Variation caused by selection of benchmarks} (Section~\ref{BenchmarkSelection}). \end{itemize}

 There is the additional risk that the set of benchmarks in SMT-LIB is not representative of any particular application area. 
We do not evaluate that risk here, but expect that this is quite likely the case.
As noted in our conclusions, we consider assessment of benchmarks as the most 
important aspect of future work. It would consist of a survey of the uses of SMT solvers, determination of the corresponding characteristics needed of solvers, an assessment of the degree to which current benchmarks are representative of the identified uses, and collection of additional benchmarks.

\subsubsection{Accuracy of performance measurements}
\label{Accuracy}

To measure the repeatability of a given solver on a given benchmark, we produced a random selection of benchmark-solver pairs (job-pairs), selecting only among job-pairs that did not timeout and had a running time of at least 0.1~seconds. The random selection produced 10\,165 job-pairs (out of the total 1\,663\,478 job-pairs). These job-pairs were run 8 times on 8 different days. Each such run took only a few hours. This resulted in 8 repetitions of each of the selected job-pairs. The data set is archived with the other evaluation data on the SMT-EVAL website. StarExec was lightly loaded on these days, so we did not measure any effect owing to interference with other uses of StarExec.

The 8 measured values for a job-pair were sorted and the first, median, and third quartile measured; these are as the average of sorted values 2 and 3, 4 and 5, and 6 and 7, respectively, and designated as Q1, Q2, and Q3. We noted the following points:
\begin{itemize}[noitemsep,nolistsep]
\item Of the measured job-pairs, about 78\% had an interquartile range (difference between Q3 and Q1) less than 10\% of the median value. That is, repeated measurements will fall within about 10\% of each other roughly 50\% of the time.\footnote{We did not measure skew: the degree to which Q3 and Q1 are unequally distant from the median.}
\item 3.5\% of job-pairs showed an interquartile range more than 50\% of the median value. 
\item Nine cases of the 10165 had a Q3 value more than double the median. These clearly showed multi-modal behavior among the eight data points for each benchmark-solver pair. Such behavior is likely the result of non-deterministic choices within the solver's search algorithms. 
\item We did not expand our study to determine whether the variation in performance was correlated to the choice of solver or to certain benchmarks. Also, we did not measure any effects owing to benchmark scrambling, which we now know can change solver behavior significantly.
\end{itemize}

An approximate conclusion from the above is that variation in timing itself plays a relatively small role in any variation in the competition. We expect the variation averages out over\ many benchmarks and is not correlated with particular solvers. It might have a larger effect on benchmarks with short running times (but we did not quantify this). The number of benchmarks per division used in previous competitions was on the order of 200, but did vary from division to division; the standard deviation of a mean calculated from a sample of 200 observations of an approximately normal distribution would be only about 0.05 of the interquartile range.

Any variation due to non-determinism within a solver we consider part of that solver's design. Thus it is possible that in some competition a non-deterministic solver might do quite well, while in a repeat of the same competition that solver, making other internal random choices, might do poorly.

\subsubsection{Accuracy of competitions}
\label{BenchmarkSelection}
The data we collected allows us to simulate various competition organizations. One such competition design would be, for each logic, to run all solvers for the given year on all benchmarks. The result of such an exercise is shown in Figs. \ref{Fig:virtual-competition-all} and \ref{Fig:virtual-competition-all2} for the set of 9 solvers for the year 2013. By summing all the CPU times for each benchmark-solver combination, we obtain that such a competition would use about 443 days of wall-clock time (using one computational node); for this computation we consider all timeout and memory exhaustion results to have taken the full timeout value (1500 seconds) of time. It is possible that in some cases a solver may exhaust memory prior to the timeout.

In previous competitions, the winner was determined as the solver that correctly solved the most benchmarks within the timeout limit (solvers producing incorrect results are disqualified). Ties among solvers solving the same number of benchmarks are resolved in favor of the solver taking the least amount of time to produce its solutions. In the tables showing the results, for each logic, the results are reported in the order of a virtual winner.

\begin{figure}
\centering
\begin{tabular}{|p{.01in}rrl|}
\hline
\input{virtual-competition-all-alt1.tex}
\end{tabular}
\caption{(Part 1) Results of a virtual competition using the 2013 solvers on all benchmarks.}
\label{Fig:virtual-competition-all}
\end{figure}

\begin{figure}
\centering
\begin{tabular}{|p{.01in}rrl|}
\hline
\input{virtual-competition-all-alt2.tex}
\end{tabular}
\caption{(Part 2) Results of a virtual competition using the 2013 solvers on all benchmarks.}
\label{Fig:virtual-competition-all2}
\end{figure}

%\begin{figure}
%\centering
%\begin{tabular}{|p{.1in}rrl|}
%\hline
%\input{virtual-competition-all3.tex}
%\end{tabular}
%\caption{(Part 3) Results of a virtual competition using the 2013 solvers on all benchmarks.}
%\label{Fig:virtual-competition-all3}
%\end{figure}

However, past competitions have not used all benchmarks, but rather a random subset of a selection of the benchmarks. It is worth asking how susceptible the competition results are to the particular subset of benchmarks used for the competition. Typically, the choice was not completely random; rather, the distribution was (a) constrained to have roughly equal representation of various categories of difficulty and (b) curated to avoid over-representation of benchmark families that contained many similar benchmarks. For our evaluation here, we determined the results of a virtual competition by simply randomly selecting different equal-sized subsets (ignoring difficulty measures), determining the competition results for each, and observing whether the competition results vary significantly depending on the subset.  Fig.~\ref{Fig:virtual-competition-some} shows the result of an experiment in which a virtual competition was executed on 1000 random subsets; we tallied the fraction of times that the winner was different than the winner in the full virtual competition (Figs.~\ref{Fig:virtual-competition-all}--\ref{Fig:virtual-competition-all2}) and the fraction of times that the complete order of the finishers was different. (We limited our consideration to those logics with at least 100 benchmarks and with more than one solver.)

Note that we did not curate the benchmarks to address the issue of over-represent-ation of some benchmark families (the authors of this report are not knowledgeable about which families are at issue); we simply used all of the benchmarks.  Thus the study should not be seen as a competition that ranks solvers, but as one that investigates various competition organizations.

The results are quite instructive. In many logics, the competition winners change in only a small fraction of trials.
However, in several logics, the fraction of trials in which the winner changes is quite significant, in some cases over~60\%. Inspection of the data reveals two contributing causes.
\begin{itemize}
\item First, some logics have a relatively large number of benchmarks that are unsolved by some solver within the timeout limit.  The fraction of benchmarks that are not solved is shown in the final column of Fig.~\ref{Fig:virtual-competition-some} (this is the average fraction over all the solvers for that logic). Random selection of benchmarks can readily change the subset of unsolved benchmarks included in the virtual competition or change the balance of benchmarks solved by one solver vs. another. Since ``winning'' the virtual competition is determined primarily by the number of benchmarks solved, rather than the time, any change in the relative number of solved benchmarks may change the order of winners.

For example, the logic QF\_AUFBV has 14335 benchmarks. Of those, 520 are unsolved by Boolector and 543 are unsolved by SONOLAR (the winner and runner up of the virtual competition). Of these only 346 are unsolved by both, leaving 174 unsolved only by Boolector and 197 unsolved only by SONOLAR. Choosing 1433 benchmarks at random, over 1000 trials, yields more benchmarks unsolvable by Boolector about 31\% of the time, more unsolved by SONOLAR about 62\% of the time, and the same about 7\% of the time. Thus, the random selection of the competition benchmark set would allow SONOLAR to best Boolector about 1/3 of the time, despite Boolector being better on the overall benchmark population for this logic.

\item Second, even when unsolved benchmarks are not a contributing factor, some pairs of solvers have total times that are close. Variations in time caused by slightly different choices of benchmarks might cause changes in winning order. The experiment described next explores this phenomenon further.

\end{itemize}

A second virtual competition can be run using only benchmarks that all competitors solved within the timeout period. This would not make a useful real competition because the result could be easily gamed: a solver could win by thoroughly optimizing performance on a few benchmarks and purposely not solving the remainder. However, in this evaluation, no solver has had the chance to do that; performing this evaluation allows comparing running times alone, without the additional factor of unsolved benchmarks.

Figs.~\ref{Fig:virtual-competition-solved} and~\ref{Fig:virtual-competition-solved2} show the result of such a competition, for the nine 2013 solvers; it uses all benchmarks that all the solvers registered for a given logic solve. In addition we performed the same experiment of 1000 virtual competitions each using 10\% of these benchmarks.  Fig.~\ref{Fig:virtual-competition-solved-some} shows the variation in winning order across these trials. The variation is even more than that shown in Fig.~\ref{Fig:virtual-competition-some}. To obtain some insight into this variation, we tabulate, in columns~2 and~3 of Figs.~\ref{Fig:virtual-competition-solved} and~\ref{Fig:virtual-competition-solved2}, the mean and standard deviation\footnote{This is the population standard devation. To obtain the sample standard deviation scale these values by $\sqrt{0.999}$.} of the total solution time for each of the solvers in each logic. The standard deviations are substantial compared to the differences in mean times between competing solvers; even though the distributions of solving times are not necessarily Gaussian, the data indicate a substantial probability that the order would change based solely on the random choice of benchmark subset.

\begin{figure}
\centering
\begin{tabular}{|lrr|rr|r|}
\hline
\input{virtual-competition-some.tex}
\end{tabular}
\caption{Results of virtual competitions using the 2013 solvers on random subsets of 10\% of the benchmarks.}
\label{Fig:virtual-competition-some}
\end{figure}

\begin{figure}
\centering
\begin{tabular}{|p{.01in}rrrl|}
\hline
\input{virtual-competition-solved-alt1.tex}
\end{tabular}
\caption{(Part 1) A virtual competition run only on benchmarks that all solvers solve.}
\label{Fig:virtual-competition-solved}
\end{figure}

\begin{figure}
\centering
\begin{tabular}{|p{.01in}rrrl|}
\hline
\input{virtual-competition-solved-alt2.tex}
\end{tabular}
\caption{(Part 2) A virtual competition run only on benchmarks that all solvers solve.}
\label{Fig:virtual-competition-solved2}
\end{figure}

%\begin{figure}
%\centering
%\begin{tabular}{|p{.01in}rrrl|}
%\hline
%\input{virtual-competition-solved3.tex}
%\end{tabular}
%\caption{(Part 3) A virtual competition run only on benchmarks that all solvers solve.}
%\label{Fig:virtual-competition-solved3}
%\end{figure}

\begin{figure}
\centering
\begin{tabular}{|lrr|rr|}
\hline
\input{virtual-competition-solved-some.tex}
\end{tabular}
\caption{Stability of competition results when run only on benchmarks solved by all solvers.}
\label{Fig:virtual-competition-solved-some}
\end{figure}

\subsection{Competitiveness of solvers}
\label{Competitiveness}

To assess competitiveness of the competitions and the set of solvers, we measured four quantities:
\begin{itemize}
\item {\em The ratio of the first to second place times on each benchmark in each logic.} The closer this quantity is to 1.0, the closer the race and the more the runner-up is challenging the leader. The ratio is averaged over all the benchmarks for each logic and year. The results are shown in Fig. \ref{Fig:runnerup1}: for each logic and year that had more than one competitor, the mean, and 1st, median, and 3rd quartiles of the distribution of runner-up ratios are shown.

A few logics, LRA and UFLRA, are very uncompetitive: the median case has the winner more than 10 times better than the runner-up. In a few others, such as QF\_IDL, QF\_NIA, QF\_NRA the winner is often less than half the time of the runner-up. But in most cases, the ratio is in the 50\%--100\% range. That is, the races are not neck-and-neck but the winners have only a modest lead over the next finisher. Note that the particular solver that is the winner varies from benchmark to benchmark.

\item {\em The degree to which the leader for a given benchmark changes from year to year.} Since all solvers are new each year, we placed solvers into families by the research group that produced them (e.g., the CVC family includes the CVC3 and CVC4 series of solvers). We counted it a {\em turnover} if the family of the winning solver changed from the previous year; we measured the fraction of benchmarks for a given logic and year that saw a turnover. The results are shown in 
Fig.~\ref{Fig:turnover}. There are many cases in which there is complete turnover from one year to the next; often this is because the previous solver family no longer participated or a new solver joined the competition and dominated the results. However, overall most
divisions see a more than 50\% turnover from year to year. We see this as indicative of reasonably robust competition.

\item {\em The distribution of winning solvers across the benchmarks within a logic.} A highly competitive environment would have each competing solver win a roughly equal fraction of the benchmarks; a non-competitive environment would have a single solver winning nearly all of the benchmarks. Our measure of competitiveness is a scaled entropy measure: if $f_i$ is the fraction of benchmarks won by solver $i$, and there are $N$ competing solvers, then the competitiveness measure is $ 2^{( - \sum_i f_i \log_2 f_i )} / N$. This quantity is $p/N$ if the wins are equally distributed among $p$ of the $N$ solvers ($f_i = 1/p$ for $p$ of the solvers and 0 for the other $N-p$). The results are shown in Figs. \ref{Fig:entropyA} and \ref{Fig:entropyB}; this data only includes benchmarks that were solved by a winner. The first entropy column gives the value of $ 2^{( - \sum_i f_i \log_2 f_i )}$, whose value is roughly the number of solvers over which the wins are distributed. The second entropy column is  $ 2^{( - \sum_i f_i \log_2 f_i )} / N$, which scales the first value between 
$1/N$ and 1.

There is a trivial case of one solver, with all wins distributed equally over the N=1 solvers and an unscaled `competitiveness' measure of 1.0; in all the combinations of logic and year, there are 18 such cases. Of the other year-logic combinations, note that in all but 11 (of the 70), despite any dominance by one solver, all competitors won at least one benchmark. The `competitiveness' metric itself shows that in most cases there are approximately 2 solvers sharing the bulk of the wins, increasing to about 3 in a few cases that have many participants. The case of the most participants---11 solvers for QF\_BV in 2012---had a distribution among about 3.5 winning solvers. Thus, although nearly all solvers contribute something, performance is dominated by a few, but not by only one, in nearly all competitive logics.

\item {\em SOTAC}. As a final measurement in this subcategory, we measured the {\em state of the art contribution} (SOTAC), as proposed  in~\cite{webCASC}. This measures the uniqueness of the contribution of each solver. It does not consider the time taken to solve a benchmark, but just whether a solver solves a benchmark (within the timeout period). The contribution of a benchmark to a solver's SOTAC is 0 if the solver does not solve the benchmark; the contribution is 1/(the number of solvers that solve that benchmark) if it does solve it. Thus the maximum contribution is obtained when a solver is the only one to solve a benchmark. Fig. \ref{Fig:sotac} shows the computation for each of the solvers for the year 2013. The first column shows the sum of the SOTAC over all benchmarks in which a solver participated;
the second column is the average over all the benchmarks that that solver attempted (including ones that timed out), but not benchmarks in logics in which the solver did not participate; the third column\footnote{The third column corresponds to Sutcliffe's definition of SOTAC.} is the average over all benchmarks for which the solver was successful (did not time out).

The CVC4 and Z3 solvers have a high total SOTAC because they contribute to a broad range of logics; MathSAT and veriT also contribute broadly. The averages in the last two columns are not significantly different from each other. MiniSMT has a high average SOTAC because it does well at just a few logics. VeriT suffers slightly on an overall average, but has a relatively higher SOTAC averaged over those benchmarks that it does solve.

\end{itemize}

%\begin{figure}
%\centering
%\begin{tabular}{|ll|r|rrrr|}
%\hline
%\input{firstoversecond1.tex}
%\end{tabular}
%\caption{(Part 1) Runner-up: Ratio of winning time to runner-up time.}
%\label{Fig:runnerup1}
%\end{figure}
%
%\begin{figure}
%\centering
%\begin{tabular}{|ll|r|rrrr|}
%\hline
%\input{firstoversecond2.tex}
%\end{tabular}
%\caption{(Part 2) Runner-up: Ratio of winning time to runner-up time.}
%\label{Fig:runnerup2}
%\end{figure}

\begin{figure}
\centering
\includegraphics[angle=270,origin=c,width=\columnwidth,height=.83\textheight]{runnerup.pdf}
\caption{Runner-up: Ratio of winning time to runner-up time, showing median, first and third quartiles.}
\label{Fig:runnerup1}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=\columnwidth]{turnover.pdf}
%\begin{tabular}{|l|rrr|p{.3in}|l|rrr|}
%\hline
%\input{turnover12.tex}
%\hline
%\end{tabular}
\caption{Turnover: Fraction of benchmarks for the given year and logic for which the winning solver is from a different solver family than in the prior year.}
\label{Fig:turnover}
\end{figure}

\begin{figure}
\centering
\centering
\begin{tabular}{|ll|ccrrr|}
\hline
\input{windistA.tex}
\end{tabular}
\caption{(Part 1) Winner distribution: The degree to which winning is distributed among solvers vs. dominated by one solver.}
\label{Fig:entropyA}
\end{figure}

\begin{figure}
\centering
\begin{tabular}{|ll|ccrrr|}
\hline
\input{windistB.tex}
\end{tabular}
\caption{(Part 2) Winner distribution: The degree to which winning is distributed among solvers vs. dominated by one solver.}
\label{Fig:entropyB}
\end{figure}

\begin{figure}
\centering
\begin{tabular}{|l|rrr|}
\hline
\input{sotac-sorted.tex}
\hline
\end{tabular}
\caption{State of the art contribution from each of the 2013 solvers, sorted by total SOTAC.}
\label{Fig:sotac}
\end{figure}

\subsection{Sequential vs. parallel computation}
\label{parallel}

The StarExec cluster contains computation nodes with 4 cores each; solvers configured for multi-threaded computation can take advantage of the parallel processing possibilities and reduce their overall wall-clock time in solving a benchmark. Previous competitions have had demonstration divisions featuring parallel computation.
For this evaluation we set a wall-clock timeout of 25 minutes and a CPU-time timeout of 100 minutes. Thus the evaluation measured the performance of solvers for parallel computation, if they were so configured. A competition focused on sequential processing would set the wall-clock and CPU-time timeouts at the same value.
We did not rerun the evaluation data to assess sequential processing performance. The data showing both wall-clock and CPU time was not available when we did our 
primary evaluation, and some of the early CPU-time data appears inconsistent with the wall-clock times. Thus we left questions about parallel vs. sequential performance for further study: 
\begin{itemize}
\item what fraction of solvers use parallel computation?
\item what is the speedup generally achieved by these solvers and the kinds of problems represented by the benchmark set?
\item what is the observed overhead, that is, for purely sequential performance by how much does the wall-clock time exceed the CPU-time?
\item are competition results significantly different when judged by CPU time vs. wall-clock time?
\end{itemize}
We expect that the 2014 competition will generate a data set better able to answer these questions.

With respect to this study, note that we used solvers as they were historically configured. They may have been configured solely for sequential performance, and the authors do not know in every case what the configurations of the older solvers are. Modern configurations of the same solvers might make use of multiple cores. The configuration of StarExec used for the evaluation (4 cores, 25 minute timeout) might be less than ideal for some historical solvers, but it is typical of what a user might use at the present time. Thus, to repeat a point made before in Section~\ref{sec:solvers}, the results of the virtual competitions should not be used to compare specific solvers. Rather, they offer a comparison of different modes of organizing and running the competition.

\subsection{Benchmarks}
\label{Benchmarks}

The number of benchmarks has successfully grown since SMT-LIB was established; at the time of this evaluation, there were more than 100\,000 in all of the logics combined, including both incremental and non-incremental collections. However, the logics differ significantly in the number of available benchmarks and in their overall difficulty.

SMT-LIB distinguishes four loosely-defined kinds of benchmarks:
\begin{itemize}[noitemsep,nolistsep]
\item {\em check} benchmarks are simple tasks that are designed to ensure that a solver has the basic functionality required for a division;
\item {\em industrial} benchmarks are generated from some application; ideally these are substantial examples showing real-world variation, but they may be from toy applications running on a toy examples;
\item {\em crafted} benchmarks are hand-crafted to exercise a particular functionality or technical challenge;
\item {\em random} benchmarks are randomly generated from some distribution.
\end{itemize}
Fig.~\ref{Fig:category} shows the number of benchmarks for each logic and the distribution over the categories just listed. The numbers vary considerably. Some logics, such as UFLRA, have just a very few benchmarks, while others have tens of thousands. Note that in nearly all logics, the bulk of the benchmarks are 
considered industrial.

The same table also shows the distribution of benchmarks among those known to be satisfiable, unsatisfiable, and with an unknown status. Here there is 
considerable variation. Some logics have nearly no satisfiable benchmarks. Some have a large proportion (at least as of 2013) of benchmarks of unknown status.
This is particularly the case for the popular and important QF\_BV logic.
Part of the effort of benchmark curation for the 2014 competition is to more carefully assign benchmarks to logics and to determine status that is currently unknown.

\begin{figure}
\centering
\begin{tabular}{|l|r|r@{\hskip 8pt}r@{\hskip 8pt}r@{\hskip 8pt}r|r@{\hskip 8pt}r@{\hskip 8pt}r|}
\hline
\input{category.tex}
\end{tabular}
\caption{The numbers of benchmarks by logic, category, and result.}
\label{Fig:category}
\end{figure}

Some benchmarks are {\em incremental}; that is, they contain more than one {\tt check-sat} command in a command script. This is relevant to interactive applications, but is not the main focus of the competition. In 2012, there were demonstration divisions on generating unsat cores and proof generation. These did not require special benchmarks, but do require different evaluation. The evaluation reported here did not consider the incremental benchmarks.

Fig.~\ref{Fig:completion} shows the fraction of benchmarks (for each logic and year) that are solved within the 25 minute timeout period. For each combination of solver and year we report the fraction of benchmarks that are completed by all solvers and the fraction that are completed by at least one solver. In 2013, in about half of the logics, all benchmarks are completed by at least one solver within the timeout period (though not necessarily the same solver); in all but one logic (QF\_RDL), at least 95\% of the benchmarks are completed by at least one solver. The values for the fraction of benchmarks completed by all solvers are not as high, since some of the solvers may be initial experimental versions and not tuned for competition. Even so, in more than half of the logics, at least 85\% of benchmarks were completed by all solvers.

Fig.~\ref{Fig:quintiles} is another view of benchmark difficulty. Here, for each logic, the distributions of winning times among the 2013 solvers are shown. In particular, selected
percentiles of each distribution are tabulated (the value for the {\em n}th percentile is the number of seconds for which that fraction of the benchmarks is completed by the winning solver for that benchmark). In all but three logics more than 80\% of the benchmarks for that logic take less than just a few seconds, if not less than a second. Only four of the logics have more than 5\% of their benchmarks that take more than the timeout period.

These results indicate that there is substantial room for more difficult benchmarks in almost all of the logics. On the other hand, if the benchmarks are indeed typical of application problems, the results indicate that today's solvers are very capable.

An additional question that would be interesting to address in a benchmark evaluation
 is the degree to which benchmarks discriminate among solvers. A small set of `discriminating' benchmarks would be more useful than a large set of undifferentiated ones. One could, for example, measure a quantity akin to the SOTAC measure of Section~\ref{Competitiveness}: benchmarks that are easy for all solvers would be discounted, ones that are hard for all would be challenges, and ones that show a wide range of performance might be discriminating benchmarks.

For example, consider a competition with just two solvers. There are then four categories of benchmarks corresponding to the subsets of solvers that solve the
benchmarks. The key point is whether benchmarks that are grouped together would nearly always be grouped together in other competitions with other sets of solvers or other competition rules. To fully elucidate this question will require analysis of the characteristics of the benchmarks combined with 
experimental assessment of their similarity in a wide variety of competition designs. We determined that the principal data collection of SMT-EVAL was not adequate to answer this question and that it deserved a full analysis in 
conjunction with a broad evaluation of benchmarks.

\begin{figure}
\centering
\begin{tabular}{|l|r|rrrr|rrrr|}
\hline
\input{completion}
\end{tabular}
\caption{The fraction of benchmarks completed by the solvers for the given year and logic.}
\label{Fig:completion}
\end{figure}

\begin{figure}
\centering
\begin{tabular}{|l|r|rrrr|}
\hline
\input{quintiles}
\hline
\end{tabular}
\caption{The distribution of winning benchmark times by logic (for 2013 solvers).}
\label{Fig:quintiles}
\end{figure}

\subsection{Application needs}
\label{Applications}

As part of its evaluation, the SMT-EVAL team solicited input on applications that use SMT-LIB. The response was not broad enough to be representative. In addition, the authors 
have encountered, by happenstance, enough users of SMT-LIB who are not active in the user community to indicate that there is likely a wide variety of uses that are not well-organized or well-represented in benchmarks on specific logics. A few application domains are fairly well-known, including software verification and synthesis, scheduling, planning and routing optimization, and invariant inference. Software verification applications in particular will benefit from broader support for combinations of theories and better heuristics for quantification.

In general, a better understanding of the variety of application needs is needed to target future development of SMT solvers and the SMT benchmark library.

%{\em Scheduling problems} typically use difference logics, either integer or real. A recent example is the Mihal's paper \cite{Mihal2013} at the SMT 2013 workshop.
%
%
%{\em Software verification} research uses SMT solvers to discharge verification conditions. In a purely model checking formalism, without user supplied axioms and specifications, a {\tt QF\_BV} or {\tt QF\_UFBV} logic would be sufficient (the latter is not defined, but would seem straightforward). However, in the formalism used by tools such as OpenJML \cite{Cok-2014-OpenJML,Cok-2011-OpenJML}, Dafny \cite{Leino:Dafny:LPAR16,Dafny2014} or Frama-C \cite{webframac}, both code and user-supplied specifications are translated to a logical form, expressed in SMT-LIB. In this case, the logic requires a broad range of underlying theories, including quantification. For this purpose solvers need to support all of the characteristics listed in subsection \ref{Lattice} and add support (theories and decision procedures) for strings, partially-ordered sets (to represent programming language types), and innovative theories and decision procedures to reason about uses of dynamic memory. Similarly SMT solvers are used underneath Ada tools 
%
%{\em Function synthesis}. A newer application of SMT constraint solving is to find functions or predicates satisfying given properties. Heizmann and Leike \cite{webLasso}
%use QF\_LRA and QF\_NRA logics to synthesize appropriate ranking functions for loops. 
%Similar work by the same authors uses interpolants to create or refine specifications; thus they use the interpolant-generation capability of some SMT solvers and the QF\_UFLIRA or AUFNIRA logics.

\section{Conclusions and recommendations}
\label{Conclusions}

\subsection{Observations from the evaluation data}

The analyses described point to three principal conclusions and a number of observations.
\begin{itemize}
\item First, unsurprisingly, there is still a need for more and better benchmarks, despite the successful growth and current large quantity ($>$ 100\,000) of benchmarks in SMT-LIB. Some logics have few benchmarks. In most logics, only a small fraction of benchmarks are significantly challenging (measured by time required to solve them).
Effort toward determining status of benchmarks whose status is currently unknown would also be worthwhile.
\item Related to the above, a better sense of the application areas of SMT is needed. Such an analysis will drive solver research in application-oriented directions, provide focus on application-oriented logics, and guide application-relevant benchmark acquisition.
\item Finally, we discovered that using a random subset of benchmarks as the basis for the annual competition, together with inherent non-determinism in running solvers, significantly lessens the ability of a competition to determine `best' solvers at a given point in time. Simply rerunning a competition is quite likely to result in a different ordering of results. The best mitigation is to run as large a benchmark set as possible in a competition (and to work toward application-relevant benchmark sets).
\end{itemize}

Other observations are these:
\begin{itemize}
\item {\em Participation}. The number of participants is relatively stable (9 to~13) with an average turnover of 35\% (low of 16\%, high of 50\%) each year. There is also a core of continuing participants (about 1/3 of the total).
\item {\em Progress in solver performance}. Solver performance increased significantly from 2010 to 2013. 
Most of that improvement occurred from 2010 to 2011; we did not determine a reason for that improvement. There is improvement across nearly all logics, though some logics are lagging.  
\item {\em Repeatability}. The repeatability of benchmarks is reduced by solver nondeterminism. Most importantly, however, competition repeatability is compromised by significant differences in performance of solvers on particular benchmarks, such that different random subsets of benchmarks will produce different assessments of solvers. The relevance of competitions is also threatened by the relevance of the total benchmark set.
\item {\em Competitiveness of solvers}. Within a logic nearly all solvers contribute something (e.g., a solution that no other solver produces). However, generally the winning times across benchmarks within a logic are obtained by 2-3 solvers that dominate that division. Comparing first-place times to second-place times shows that (a) in many logics the runner-up is quite close to the winner, but (b) in some logics, presumably with state-of-the-art tuning and advanced algorithms, the winner far outstrips the other competitors. It is also relevant that most benchmarks change winner from one year to the next. Overall, we judge that there is a moderate degree of competitiveness among solvers - a few tend to dominate in any logic, but other solvers do also make their contribution.
\item {\em Difficulty of benchmarks}. A relatively low fraction of benchmarks require more than the timeout period to solve. Most benchmarks are solved by all solvers within the timeout period.

\end{itemize}

\subsection{Recommendations for competitions and for SMT-LIB}

The experience of past competitions and this evaluation point to a number of ideas for future competitions. Most past policies have worked well and should be continued: openness, transparency, reproducibility, public submission of solvers. Other aspects could use improvement. Some of these have already begun for 2014.
\begin{itemize}
\item To reduce potential variation caused by choice of benchmarks in a competition, a competition should include as many benchmarks as possible.
\item Invigorate the collection of benchmarks and promote a round of curating the existing benchmarks. This might include discontinuing or combining some logics.
\item Encourage the participation of new entrants through tool support and recognition. Some ideas are recognizing the best new entrant and promoting reference infrastructure for elements like parsing input files or standard reporting mechanisms.
\item Encourage broad participation by measuring performance in all logics, even when some logics are deemed more relevant than others.
\item Encourage broadening measures of performance beyond solution of single satisfiability problems, by including, for example, determining unsat cores, measuring performance on incremental benchmarks, computing interpolants, producing proofs, producing satisfying assignments, or encouraging solvers that use multi-processing implementations.
\item Investigate the naming convention and inclusion relationships for logics, with the goal of simplifying the relationships and with an eye toward adding additional theories and a significant expansion of the number of logics. This may not mean changing existing names, but would at least set a policy for how new theories and logics are to be named. At minimum this would clarify the process of naming new theories and logics.
\item There is a relative paucity of difficult benchmarks (those that are not solved within the timeout period). Perhaps this is because of progress in solver performance and in hardware speed. In either case, additional difficult benchmarks are needed.
\item The scoring criterion should be revisited. The current scoring emphasizes number solved over time to solve. First, time performance is important to applications, perhaps even more than solving the last 10\% of hard problems, so some balance between number solved and time to solve might be appropriate. Second, some solvers issue `unknown' indicating a possible satisfying solution is available, but it is not known to be sound (perhaps because of the presence of quantifiers). Such a solution may be available well before a timeout; however, such a result currently counts the same as a timeout.
\end{itemize}

\subsection{Future work}
The most important aspect of future work is to increase and improve benchmark quality, as described above. Thus we would encourage
\begin{itemize}
\item a broad survey of SMT application domains and their needs in solver support, both logics and functionality beyond determining satisfiability. 
A corresponding review of the benchmarks in SMT-LIB would determine the degree
to which benchmarks are representative of the application domains and would 
provide guidelines for collecting new benchmarks.
\end{itemize}
There are also a number of questions that we posed but did not have the time or data to answer. 
\begin{itemize}
\item Are there interesting differences in performance between satisfiable and unsatisfiable benchmarks?
\item Do solvers support all of SMT-LIB~v2? Should the community encourage expansion to new capabilities (e.g., unsat cores, incremental, interpolants, model generation, proof generation)? Should the community define a core language that is used for the competition, with other aspects being optional?
\item Which logics should be retired or deemphasized, based on solver progress or application need?
\item Competitions primarily measure ability to solve benchmarks, with the time to do so a secondary criterion. However, in some applications it is important to discharge easy problems quickly. We did not assess this characteristic of the available solvers, but it would be worth doing so.
\item It would also be worth extending our study with an evaluation of incremental benchmarks and means of measuring performance in an interactive environment.
\item Measuring the contribution of individual benchmarks.
\end{itemize}

As this report is being finalized, the 2014 SMT Competition is underway. Some of the proposals and hopes expressed in this report have been realized: 2014 is seeing a record number of participants, including new solver entries; there is a record number of benchmarks being used; and with only minor, recoverable problems, the StarExec infrastructure is performing a massive amount of computation over a week or so of competition time.

%\section*{Acknowledgments} 
\begin{acknowledgements}

The cost of executing the SMT competition is underwritten by the SMT
Workshop.  The evaluation used the StarExec cluster at the University
of Iowa.  This computation cluster replaces the SMT-Exec cluster used
for all previous competitions.  The cluster is supported by the
U.S.\ National Science Foundation under grants \#1058748 and \#1058925.  Cok's
contribution is supported by GrammaTech, Inc.\ and in part by the
National Science Foundation under grant ACI-1314674.  Any opinions,
findings, and conclusions or recommendations expressed in this
material are those of the authors and do not necessarily reflect the
views of the National Science Foundation.
\end{acknowledgements}

\bibliographystyle{plain}
\bibliography{SMTEVAL-2013,cok,sv}

\end{document}

### 2015-02-16 2013/report/SMTEVAL-2013.tex
Moved (non-public) source files out of smtcomp-web.

--- 2015-02-16 2013/report-JAR/SMTEVAL-2013-R.tex
@@
 
-\documentclass[smallcondensed]{svjour3}
-%\providecommand{\event}{Journal TBD}
-%\providecommand{\publicationstatus}{ } %% TBD - fill in any footer
+\documentclass{eptcs}
+\providecommand{\event}{Journal TBD}
+\providecommand{\publicationstatus}{ } %% TBD - fill in any footer
 %%\documentclass[12pt,oneside]{llncs}
@@
 \usepackage{tabularx}
-\usepackage{pdfpages}
 
@@
 
-%\def\titlerunning{SMTEVAL-2013}
-%\def\authorrunning{Cok, Stump, Weber}
+\def\titlerunning{SMTEVAL-2013}
+\def\authorrunning{Cok, Stump, Weber}
 
@@
 
-\newcommand{\cellbr}[2][c]{\begin{tabular}[#1]{@{}c@{}}#2\end{tabular}}
-
-\journalname{Journal of Automated Reasoning}
+\renewcommand{\textfraction}{0.05}
+\renewcommand{\topfraction}{0.8}
+\renewcommand{\bottomfraction}{0.8}
+\renewcommand{\floatpagefraction}{0.75}
 
 \begin{document}
-\title{The 2013 Evaluation of SMT-COMP and SMT-LIB}
+
+\title{The 2013 SMT Evaluation}
 
@@
 \author{
-David R. Cok 
+David R. Cok \institute{GrammaTech, Inc., USA \email{dcok@grammatech.com}}
 \and
-Aaron Stump
+Aaron Stump \institute{University of Iowa, IA, USA \email{aaron-stump@uiowa.edu}}
 \and
-Tjark Weber
+Tjark Weber \institute{Uppsala University, Sweden \email{tjark.weber@it.uu.se}}
 }
 
-\institute{
-David R. Cok  \at GrammaTech, Inc., USA \email{dcok@grammatech.com}
-\and
-Aaron Stump \at University of Iowa, IA, USA \email{aaron-stump@uiowa.edu}
-\and
-Tjark Weber \at Uppsala University, Sweden \email{tjark.weber@it.uu.se}
-}
 %% lncls format
@@
 
-\date{}
 \maketitle
-%\pagestyle{headings}
-%\pagenumbering{arabic}
-%\centerline{\today}
+\pagestyle{headings}
+\pagenumbering{arabic}
+\centerline{\today}
 
@@
 \subsection{The Competition history and goals}
-From 2005 through 2012 (and in 2014), the SMT community
+From 2005 through 2012 (and coming again in 2014), the SMT community
 sponsored an annual competition among SMT solvers
@@
 propositional and first-order reasoning tools, respectively, have
-spurred significant innovation in their fields~\cite{leberre+03,PSS02}.  Indeed, the SMT competition increased in
+spurred significant innovation in their fields
+\cite{leberre+03,PSS02}.  Indeed, the SMT competition increased in
 size each year: more benchmarks were added, new solver teams
@@
 \centering
-\includegraphics[width=\textwidth]{SMTCOMP-History}
+\includegraphics[width=.95\textwidth, viewport=0 85 720 370, clip=true]{SMTCOMP-History}
 \caption{SMT-COMP history}
@@
 
-And third, for many years the competition had relied on the SMT-Exec computational infrastructure~\cite{springerlink:10.1007/s10817-012-9246-5}.
-A new infrastructure, StarExec~\cite{StuST-IJCAR-14,webStarExec} had been funded by the NSF and developed at the University of Iowa, but had not yet been tried out in earnest.
-In fact, a goal in~2012 had been to use StarExec for SMT-COMP~2012; however, StarExec was not sufficiently operational and the competition had to revert to SMT-Exec.
-It was anticipated that an evaluation in 2013, with less deadline pressure, would enable using StarExec on a shake-down cruise prior to a competition in 2014 at the Federated Logic Conference~(FLoC) Olympic Games~\cite{webOlympicGames}.
+And third, for many years the competition had relied on the SMT-Exec computational infrastructure\cite{springerlink:10.1007/s10817-012-9246-5}.
+A new infrastructure, Star-Exec \cite{StuST-IJCAR-14,webStarExec} had been funded by the NSF and developed at the University of Iowa, but had not yet been tried out in earnest.
+In fact, a goal in~2012 had been to use Star-Exec for SMT-COMP~2012; however, Star-Exec was not sufficiently operational and the competition had to revert to SMT-Exec.
+It was anticipated that an evaluation in 2013, with less deadline pressure, would enable using Star-Exec on a shake-down cruise prior to a competition in 2014 at the Federated Logic Conference~(FLoC) Olympic Games \cite{webOlympicGames}.
 
@@
 The SMT Steering Committee appointed a team of evaluators (the authors
-of this report) to examine areas of interest. The evaluators, who are
-not affiliated with any solver team, independently studied the
-following topics:
+of this report) to examine areas of interest. The evaluators studied
+the following topics:
 \begin{itemize}[noitemsep]
@@
 \end{itemize}
+
 \end{itemize}
@@
 The growth in the number of benchmarks available is shown in the graphics of Fig.~\ref{Fig:history}.
-All\footnote{One benchmark, added late, was not included in all of the data accumulation; hence some tables report 95\,491 benchmarks and some 95\,492.} of the benchmarks present in StarExec at the time of evaluation (95\,492 benchmarks) were used for the evaluation, including those with unknown status.
+All\footnote{One benchmark, added late, was not included in all of the data accumulation; hence some tables report 95\,491 benchmarks and some 95\,492.} of the benchmarks present in Star-Exec at the time of evaluation (95\,492 benchmarks) were used for the evaluation, including those with unknown status.
 Of course, in previous years only a subset of these were available, since new benchmarks were added from year to year.
@@
 Furthermore, the competition each year used a random selection of benchmarks (guided by a difficulty distribution).
-The fact that the set of benchmarks used in competitions was different each year muddied any year-to-year comparison of results.
-By using all available benchmarks in the evaluation, we ensure that the current assessment is not susceptible to random choices in benchmark selection (cf.~Section~\ref{CompetitionRepeatability}).
+The fact that the set of benchmarks used in competition was different each year muddied any year-to-year comparison of results.
+By using all available benchmarks in the evaluation, we intend that any comparative assessments across years or solvers be more accurate.
 The various kinds of benchmarks and their distribution across logics are discussed below in Section~\ref{Evaluations}.
@@
 \subsection{Solvers}
-\label{sec:solvers}
 
@@
 \centering
-\begin{tabular}{|l|l|*{8}{c@{\hskip 10pt}}c|}
+\begin{tabular}{|l|l|c@{\hspace{-.1em}}ccccccccc|}
 \hline
@@
 \caption{Solvers used in each year of SMT-COMP and SMT-EVAL.
-Solvers prior to 2010 (marked by~X) do not support SMT-LIB~v2 and were not used for SMT-EVAL.
-Boxes marked with a~\textbullet{} symbol identify solvers that are new for the evaluation; all solvers since 2010 (marked with~+ or~\textbullet{} symbols) were used for the evaluation.}
+Solvers prior to 2010 (marked by X) do not support SMT-LIB~v2 and were not used for SMT-EVAL.
+Entries marked with a~\textbullet{} symbol identify solvers that are new for the evaluation.
+All solvers since 2010 (marked with~+ or~\textbullet{} symbols) were used for the evaluation.}
 \label{Fig:solvers}
@@
 Any comparisons for particular applications or kinds of benchmark problems should perform an independent analysis.
-
-\subsection{Interpreting solver output}
-
-Given the large number of solver-benchmark combinations, it was not
-feasible to manually inspect the output of each job pair.  Thus, we
-needed to determine mechanically whether a solver reported a benchmark
-as satisfiable, unsatisfiable or unknown (or did not return a result
-within the time limit).
-
-On StarExec, this is done by providing a \emph{post-processor}, i.e.,
-an executable that operates on the output of each job pair.
-Unfortunately, two features of StarExec made it difficult to interpret
-solver output in a way that is fully SMT-LIB~v2 compliant.  First,
-StarExec collects the entire output of a job pair in a single file
-before passing it to the post-processor.  Thus, it is not possible to
-reliably determine which output a solver has generated specifically in
-response to a benchmark's {\tt check-sat} command.  Second, StarExec
-conflates standard output and standard error.  We hope that this
-behavior will be changed in the future, but for SMT-EVAL this made it
-impossible to distinguish between regular solver responses and error
-messages.
-
-To determine the result of each job pair, we used a post-processor
-that searched for the words {\tt sat}, {\tt unsat} and {\tt unknown}
-in the output file, and reported the corresponding result if it found
-exactly one of them; otherwise, it reported no result.  This
-conservative approach may have caused a small number of (otherwise
-valid) solver responses to be discarded.  It was adopted to minimize the
-number of incorrect results reported by the post-processor.
 
@@
 
-An additional use of benchmark scrambling is that the change in syntax
-and identifiers can, for some solvers, change the search paths or the
-preprocessing that is performed. Thus scrambling serves to exercise
-different code paths and adds an additional dimension of testing and
-performance measurement to competitions and evaluations. It would be
-interesting to investigate these effects of scrambling in detail; we
-did not do this as part of SMT-EVAL.
+An additional use of benchmark scrambling is that the change in syntax and identifiers can, for some solvers,
+change the search paths or the preprocessing that is performed. Thus scrambling serves to exercise
+different code paths and adds an additional dimension of testing and performance measurement to
+competitions and evaluations.
 
@@
 %conforming.
-
-\subsection{StarExec}
-
-SMT-EVAL successfully used the new StarExec computational framework~\cite{StuST-IJCAR-14,webStarExec}.
-Running SMT-EVAL on StarExec did indeed expose a number of bugs and user interface issues; these were corrected in the course of the SMT-EVAL runs.
-Thus SMT-EVAL served a valuable purpose in preparing StarExec for larger scale use.
-
-SMT-EVAL's largest computational job was running all 45 of the evaluated solvers on all of the relevant non-incremental benchmarks in the SMT library. 
+\subsection{Star-Exec}
+
+SMT-EVAL successfully used the new Star-Exec computational framework \cite{webStarExec,StuST-IJCAR-14}.
+Running SMT-EVAL on Star-Exec did indeed expose a number of bugs and user interface issues; these were corrected in the course of the SMT-EVAL runs.
+Thus SMT-EVAL served a valuable purpose in preparing Star-Exec for larger scale use.
+
+SMT-EVAL's largest computational job was running all 45 of the evaluated solvers on all of the non-incremental benchmarks in the SMT library.
 The benchmarks belong to different {\em logics} and solvers are characterized by which logics they support.
-So for each logic, the evaluation executed the cross product of all benchmarks for that logic and all solvers (in all years) that support problems in that logic, for a total of 1\,663\,478 solver-benchmark combinations (called {\em job-pairs} in StarExec).
-This job took several months of wall-clock time to run. 
-We ran it in quarters, using the result of the first quarter to adjust our procedures and debug some of StarExec, before running the rest of the solver-benchmark job pairs. 
+For each logic, the evaluation executed the cross product of all benchmarks for that logic and all solvers (in all years) that support problems in that logic, for a total of 1\,663\,478 solver-benchmark combinations (called {\em job-pairs} in Star-Exec).
+This job took several months of wall time to run.
+We ran it in quarters, using the result of the first quarter to adjust our procedures and debug some of Star-Exec, before running the rest of the solver-benchmark job-pairs.
 Because of a bug (now corrected), the results of about 600 job-pairs were not present in the accumulated results.
 These were identified and rerun as an additional ``mop-up'' job.
-Each solver-benchmark pair was run in an independent environment, on a computation node by itself, with time and memory limits, as described in Section~\ref{parallel}.
+Each job-pair was run in an independent environment, on a computation node by itself.
+Each node has four cores.
+The job-pair was limited to 25 minutes of wall-clock time, 100 minutes of cpu time, and 1GB of memory.
+
+\subsection{Interpreting solver output}
+
+Given the large number of solver-benchmark combinations, it was not
+feasible to manually inspect the output of each job-pair. Thus, we
+needed to determine mechanically whether a solver reported a benchmark
+as satisfiable, unsatisfiable or unknown (or did not return a result
+within the time limit).
+
+On StarExec, this is done by providing a \emph{post-processor}, i.e.,
+an executable that operates on the output of each job-pair.
+Unfortunately, two features of StarExec made it difficult to interpret
+solver output in a way that is fully SMT-LIB~v2 compliant.  First,
+StarExec collects the entire output of a job-pair in a single file
+before passing it to the post-processor.  Thus, it is not possible to
+reliably determine which output a solver has generated specifically in
+response to a benchmark's {\tt check-sat} command.  Second, StarExec
+conflates standard output and standard error, making it impossible to
+distinguish between regular solver responses and error messages.
+
+To determine the result of each job-pair, we used a post-processor
+that searched for the words {\tt sat}, {\tt unsat} and {\tt unknown}
+in the output file, and reported the corresponding result if it found
+exactly one of them; otherwise, it reported no result.  This
+conservative approach may have caused a small number of (otherwise
+valid) solver responses to be discarded.  It was adopted to minimize the
+number of incorrect results reported by the post-processor.
 
@@
 The evaluation team's observations on the questions it considered are presented in the following subsections; our overall conclusions are listed in Section~\ref{Conclusions}.
-The raw data used as the basis for our observations, collected from StarExec, are all archived on the SMT-COMP website, at \url{http://sourceforge.net/p/smtcomp/code/HEAD/tree/trunk/smtcomp-web/2013/data} as 7z-compressed files.
-(The largest is~25\,MB.)  The data can also be viewed directly on StarExec, at \url{https://www.starexec.org/starexec/secure/explore/spaces.jsp?id=4566}, using its guest login.
+The raw data used as the basis for our observations, collected from Star-Exec, are all archived on the SMT-COMP website, at \url{http://sourceforge.net/p/smtcomp/code/HEAD/tree/trunk/smtcomp-web/2013/data} as 7z-compressed files.
+(The largest is~25\,MB.)
 
@@
 \centering
-\begin{tabular}{|l|ccccccccc|}
-\hline
-year                & 2005 & 2006 & 2007 & 2008 & 2009 & 2010 & 2011 & 2012 & 2013 \\ \hline
-\# of participants  & 11   & 11   & 9    & 13   & 12   & 10   & 11   & 11   & 9   \\ \hline
-\# dropping out     &      &  4   & 6    &  2   &  3   &  7   &  2   &  4   & \\ \hline
+\begin{tabular}{|l|cccccccc|c|}
+\hline
+Year                & 2005 & 2006 & 2007 & 2008 & 2009 & 2010 & 2011 & 2012 & 2013 \\ \hline
+\# of participants  & 11   & 11   & 9    & 13   & 12   & 10   & 11   & 11   & 9 \\
+\# dropping out     &      &  4   & 6    &  2   &  3   &  7   &  2   &  4   & \\
 \# new participants & (11) &  4   & 4    &  6   &  2   &  5   &  3   &  4   & \\ \hline
@@
 \end{figure}
+
 \begin{itemize}
@@
 The data for 2013 is an anomaly in two respects.
-The count of 9 only includes those solvers that were explicitly submitted new for 2013.
+The count of 9 only includes those solvers that were explicitly submitted new for 2013; some teams were glad to be included but did not upgrade their 2012 solvers.
 Second, Abziz contributed a portfolio solver that makes an automatic choice, based on machine learning, of which among other existing solvers to apply to a benchmark using observed features of the benchmark.
@@
 
-\subsection{Logics}
+\subsection{Lattice of logics}
 \label{Lattice}
@@
 \centering
-\includegraphics[width=\textwidth]{LogicLatticeN}
-\caption{Graph of SMT logics defined in SMT-LIB.
+\includegraphics[width=\textwidth,viewport=0 50 720 520, clip=true]{LogicLattice}
+\caption{Lattice of SMT logics defined in SMT-LIB.
 The links represent a natural inclusion by characteristics, but {\it not} a sub-logic relationship.
-QF\_ABV is defined, but is often subsumed in QF\_AUFBV, and is not usually listed separately in other tables in this report.
-Q is not a logic by itself but is a characteristic indicating that quantified expressions are permitted in the logic; similarly N indicates non-linear arithmetic is allowed.}
+{\tt QF\_ABV} is defined, but is often subsumed in {\tt QF\_AUFBV}, and is not usually listed separately in other tables in this report.
+{\tt Q} is not a logic by itself but is a characteristic indicating that quantified expressions are permitted in the logic.}
 \label{Fig:lattice}
@@
 The logics are a combination of theories with additional functions or logic symbols or restrictions on the vocabulary of the theories.
-For example, the QF\_IDL logic uses the underlying Ints theory, but restricts terms to equalities and inequalities between constants and simple differences of variables.
-The combination of the Ints theory and the Reals theory adds functions that convert between integers and reals (among other things).
+For example, the {\tt QF\_IDL} logic uses the underlying {\tt Ints} theory, but restricts terms to equalities and inequalities between constants and simple differences of variables.
+The combination of the {\tt Ints} theory and the {\tt Reals} theory adds functions that convert between integers and reals (among other things).
+Note that the {\tt QF\_ABV} logic is defined, but is often subsumed in {\tt QF\_AUFBV} and has no benchmarks of its own;\footnote{By the time of the 2014 competition, the benchmarks were reorganized and recategorized, and more benchmarks were added.
+So now this logic is populated as well.} it is not usually listed separately in other tables in this report.
 
@@
 \item UF: uninterpreted functions
-\item QF\_: quantifier freeness
+\item QF\_: quantifier-free
 \item BV: bit-vectors
@@
 
-It is possible to define a logic with any powerset of these characteristics in an almost purely combinatorial sense. 
+It is possible to define a logic for any set of these characteristics in an almost purely combinatorial sense.
 Barring non-linearity without arithmetic and the useless empty set, there are 111 combinations of characteristics (instead of the full 128).
-SMT-LIB has definitions and benchmarks for 20 of these logics (excluding QF\_IDL, QF\_RDL, and QF\_UFIDL) at the time of the evaluation, expanded to 34 in 2014.
+SMT-LIB has definitions and benchmarks for 23 of these logics.
 Fig.~\ref{Fig:lattice} shows what might be expected to be natural containment relationships among the logics defined at the time of this evaluation.
 
-However, what might be expected to be natural containment relationships are not actually sub-logic relationships.
+However, these containment relationships are not actually sub-logic relationships.
 That more accurate relationship is shown in a diagram on the SMT-LIB website: \url{http://smtlib.cs.uiowa.edu/logics.shtml} (due to Cesare Tinelli).
@@
 The naming convention for logics is almost but not quite simply a combination of the letters indicated in the list above,
-corresponding to the characteristics of the logic, with the letters listed in order by convention:
-\begin{center}
-[QF\_][A\textbar AX][UF][BV][N\textbar L][IA\textbar RA\textbar IRA].
-\end{center}
-
-\noindent The non-uniformities are these:
+corresponding to the characteristics of the logic, with the letters listed in order by convention: {\tt [QF\_][A|AX][UF][BV][N|L][IA|RA|IRA]}. The non-uniformities are these:
 \begin{itemize}[noitemsep,nolistsep]
-\item quantification is indicated by {\em removing} a QF\_ prefix;
-\item the absence of non-linearity~(N), i.e., linearity, is indicated by an~L, instead of by no designator;
-\item integer and real arithmetic are indicated by two letters (IA and~RA) and their combination by~IRA;
-\item the~A used in the arithmetic designators could be ambiguous with the designator for arrays, except for position;
-\item a logic with just arrays is named QF\_AX, whereas in other combinations including arrays, just an~A instead of~AX is used.
-\end{itemize}
-For example, UFNIA includes quantification (no QF\_ prefix), uninterpreted functions~(UF), non-linearity~(N), and integer arithmetic~(IA), leaving out arrays, bit-vectors, and reals.
+\item quantification is indicated by {\em removing} a {\tt QF\_} prefix;
+\item the absence of non-linearity ({\tt N}), i.e., linearity, is indicated by an {\tt L}, instead of by no designator;
+\item integer and real arithmetic are indicated by two letters ({\tt IA} and {\tt RA}) and their combination by {\tt IRA}; \item the {\tt A} used in the arithmetic designators could be ambiguous with the designator for arrays, except for position;
+\item a logic with just arrays is named {\tt QF\_AX}, whereas in other combinations including arrays, just an {\tt A} instead of {\tt AX} is used.
+\end{itemize}
+For example, {\tt UFNIA} includes quantification (no {\tt QF\_} prefix), uninterpreted functions (UF), non-linearity (N), and integer arithmetic (IA), leaving out arrays, bit-vectors, and reals.
 
@@
 Nevertheless as the set of logics grows---23 here and 34 by the 2014 competition---the situation will increasingly confuse new users of SMT-LIB trying to understand the structure of logics; in addition new theories and accompanying logics are anticipated.
-It would be useful to standardize the naming convention along the lines of current use, perhaps with slight adjustments (e.g., renaming QF\_AX to QF\_A and removing the excess~A from~IA and~RA), in order to define precisely the logic implied by any combination of designators.
+It would be useful to standardize the naming convention along the lines of current use, perhaps with slight adjustments (e.g., renaming {\tt QF\_AX} to {\tt QF\_A} and removing the excess {\tt A} from {\tt IA} and {\tt RA}), in order to define precisely the logic implied by any combination of designators.
 A policy regarding names would provide a process for defining names for new theories and logics.
@@
 \centering
+\resizebox{\columnwidth}{!}{
+%%\includegraphics[width=\textwidth]{LogicSupportBySolvers}
 \input{LogicSupportBySolvers}
+}
+
 \caption{Support for each logic as stated by solver implementors.
 The dots instead of Xs identify the 2013 versions of solvers.
-The numbers in the bottom row are the number of 2013 solvers for each logic.}
+The numbers in the bottom row are the number of 2013 solvers for each logic.
+In some cases, indicated by numbers in parentheses in the left-hand column, there are multiple versions of the same tool in different years with the same support for logics.}
 \label{Fig:solversupport}
@@
 
-Note that the support indicated is that stated by the solver supplier at the time the solver was submitted to a competition. 
+Note that the support indicated is that stated by the solver supplier.
 In some cases, a solver supports one logic but is not listed as supporting a subset of that logic.
@@
 The results for all logics are shown together.
-The four curves are the data for the four years from 2010 to 2013. The lowest (marked with fine dots) curve is that for 2010. 
-There is clearly significant progress made from 2010 to later years: the number of benchmarks completed within a given time is noticeably higher; we did not attempt to identify the source of this historical improvement.
+The four curves are the data for the four years from 2010 to 2013.
+The lowest (marked with fine dots) curve is that for 2010.
+There is clearly significant progress made from 2010 to later years: the number of benchmarks completed within a given time is noticeably higher.
 The curves for 2011 and 2012 (heavy dashes and short dashes, respectively) are clearly above 2010, but are not substantially different from each other.
@@
 \centering
-\includegraphics[width=.95\textwidth]{CumulativeTimes}
+\includegraphics[width=.8\textwidth]{CumulativeTimes3}
 \caption{The fraction of benchmarks (y-axis) whose winning time is less than the given number of seconds (x-axis), by year.}
@@
 \centering
-%\begin{tabular}{|l|r|rrrr|}
-%\hline
-%\input{bettertime}
-%\hline
-%\end{tabular}
-\includegraphics[width=\textwidth]{bettertime.pdf}
+\begin{tabular}{|l|r|rrrr|}
+\hline
+\input{bettertime}
+\hline
+\end{tabular}
 \caption{The fraction of benchmarks whose best time improved between the given years.}
@@
 \begin{itemize}[noitemsep,nolistsep]
-\item {\em The repeatability of the time a given solver takes on a given benchmark} (Section~\ref{Accuracy}).
-This variation is a combination of two factors: any variation in execution and timing by the StarExec system itself, and any non-determinism in the execution of the solver.
-\item {\em Variation caused by selection of benchmarks} (Section~\ref{BenchmarkSelection}). \end{itemize}
+\item {\em The repeatability of the time a given solver takes on a given benchmark} (Section \ref{Accuracy}).
+This variation is a combination of two factors: any variation in execution and timing by the Star-Exec system itself, and any non-determinism in the execution of the solver.
+\item {\em Variation caused by selection of benchmarks} (Section \ref{BenchmarkSelection}). \end{itemize}
 
  There is the additional risk that the set of benchmarks in SMT-LIB is not representative of any particular application area.
-We do not evaluate that risk here, but expect that this is quite likely the case.
-As noted in our conclusions, we consider assessment of benchmarks as the most 
-important aspect of future work.
-It would consist of a survey of the uses of SMT solvers, determination of the corresponding characteristics needed of solvers, an assessment of the degree to which current benchmarks are representative of the identified uses, and collection of additional benchmarks.
+We do not evaluate that risk here, but expect it to be quite likely to be the case.
 
@@
 These job-pairs were run 8 times on 8 different days.
-Each such run took only a few hours.
+One such run took only a few hours.
 This resulted in 8 repetitions of each of the selected job-pairs.
 The data set is archived with the other evaluation data on the SMT-EVAL website.
-StarExec was lightly loaded on these days, so we did not measure any effect owing to interference with other uses of StarExec.
-
-The 8 measured values for a job-pair were sorted and the first, median, and third quartile measured; these are as the average of sorted values 2 and 3, 4 and 5, and 6 and 7, respectively, and designated as Q1, Q2, and Q3.
+Star-Exec was lightly loaded on these days, so we did not measure any effect owing to interference with other uses of Star-Exec.
+
+The 8 measured values for a job-pair were sorted and the first, median, and third quartile measured (as the average of sorted values 2 and 3, 4 and 5, and 6 and 7, respectively).
 We noted the following points:
 \begin{itemize}[noitemsep,nolistsep]
-\item Of the measured job-pairs, about 78\% had an interquartile range (difference between Q3 and Q1) less than 10\% of the median value.
+\item Of the measured job-pairs, about 78\% had a Q3-Q1 spread less than 10\% of the median value.
 That is, repeated measurements will fall within about 10\% of each other roughly 50\% of the time.\footnote{We did not measure skew: the degree to which Q3 and Q1 are unequally distant from the median.}
-\item 3.5\% of job-pairs showed an interquartile range more than 50\% of the median value. 
+\item 3.5\% of job-pairs showed a Q3-Q1 spread more than 50\% of the median value.
 \item Nine cases of the 10165 had a Q3 value more than double the median.
@@
 It might have a larger effect on benchmarks with short running times (but we did not quantify this).
-The number of benchmarks per division used in previous competitions was on the order of 200, but did vary from division to division; the standard deviation of a mean calculated from a sample of 200 observations of an approximately normal distribution would be only about 0.05 of the interquartile range.
 
@@
 One such competition design would be, for each logic, to run all solvers for the given year on all benchmarks.
-The result of such an exercise is shown in Figs.
-\ref{Fig:virtual-competition-all} and \ref{Fig:virtual-competition-all2} for the set of 9 solvers for the year 2013.
-By summing all the CPU times for each benchmark-solver combination, we obtain that such a competition would use about 443 days of wall-clock time (using one computational node); for this computation we consider all timeout and memory exhaustion results to have taken the full timeout value (1500 seconds) of time.
+The result of such an exercise is shown in Figs.~\ref{Fig:virtual-competition-all}, \ref{Fig:virtual-competition-all2} and~\ref{Fig:virtual-competition-all3} for the set of 9 solvers for the year 2013.
+By summing all the reported wall-clock times for each benchmark-solver combination, we obtain that such a competition would use about 443 days of wall-clock time (using one computational node); for this computation we consider all timeout and memory exhaustion results to have taken the full timeout value (1500 sec) of time.
 It is possible that in some cases a solver may exhaust memory prior to the timeout.
@@
 \hline
-\input{virtual-competition-all-alt1.tex}
+\input{virtual-competition-all.tex}
 \end{tabular}
@@
 \hline
-\input{virtual-competition-all-alt2.tex}
+\input{virtual-competition-all2.tex}
 \end{tabular}
@@
 
-%\begin{figure}
-%\centering
-%\begin{tabular}{|p{.1in}rrl|}
-%\hline
-%\input{virtual-competition-all3.tex}
-%\end{tabular}
-%\caption{(Part 3) Results of a virtual competition using the 2013 solvers on all benchmarks.}
-%\label{Fig:virtual-competition-all3}
-%\end{figure}
-
-However, past competitions have not used all benchmarks, but rather a random subset of a selection of the benchmarks.
+\begin{figure}
+\centering
+\begin{tabular}{|p{.1in}rrl|}
+\hline
+\input{virtual-competition-all3.tex}
+\end{tabular}
+\caption{(Part 3) Results of a virtual competition using the 2013 solvers on all benchmarks.}
+\label{Fig:virtual-competition-all3}
+\end{figure}
+
+However, past competitions have not used all benchmarks, but rather a random subset of the benchmarks.
 It is worth asking how susceptible the competition results are to the particular subset of benchmarks used for the competition.
-Typically, the choice was not completely random; rather, the distribution was (a) constrained to have roughly equal representation of various categories of difficulty and (b) curated to avoid over-representation of benchmark families that contained many similar benchmarks.
+Typically, the choice is not completely random; rather, the distribution is constrained to have roughly equal representation of various categories of difficulty.
 For our evaluation here, we determined the results of a virtual competition by simply randomly selecting different equal-sized subsets (ignoring difficulty measures), determining the competition results for each, and observing whether the competition results vary significantly depending on the subset.
-Fig.~\ref{Fig:virtual-competition-some} shows the result of an experiment in which a virtual competition was executed on 1000 random subsets; we tallied the fraction of times that the winner was different than the winner in the full virtual competition (Figs.~\ref{Fig:virtual-competition-all}--\ref{Fig:virtual-competition-all2}) and the fraction of times that the complete order of the finishers was different.
+Fig.~\ref{Fig:virtual-competition-some} shows the result of an experiment in which 1000 virtual competitions were executed each using a different random subset; we tallied the fraction of times that the winner was different than the winner in the full virtual competition (Figs.~\ref{Fig:virtual-competition-all}--\ref{Fig:virtual-competition-all3}) and the fraction of times that the complete order of the finishers was different.
 (We limited our consideration to those logics with at least 100 benchmarks and with more than one solver.)
-
-Note that we did not curate the benchmarks to address the issue of over-represent-ation of some benchmark families (the authors of this report are not knowledgeable about which families are at issue); we simply used all of the benchmarks.
-Thus the study should not be seen as a competition that ranks solvers, but as one that investigates various competition organizations.
 
@@
 
-For example, the logic QF\_AUFBV has 14335 benchmarks.
+For example, the logic QF\_AUFBV has 14\,335 benchmarks.
 Of those, 520 are unsolved by Boolector and 543 are unsolved by SONOLAR (the winner and runner up of the virtual competition).
@@
 Choosing 1433 benchmarks at random, over 1000 trials, yields more benchmarks unsolvable by Boolector about 31\% of the time, more unsolved by SONOLAR about 62\% of the time, and the same about 7\% of the time.
-Thus, the random selection of the competition benchmark set would allow SONOLAR to best Boolector about 1/3 of the time, despite Boolector being better on the overall benchmark population for this logic.
+Thus, the random selection of (in this case, 10\% of) the competition benchmark set would allow SONOLAR to best Boolector about 1/3 of the time, despite Boolector being better on the overall benchmark population for this logic.
 
@@
 
-Figs.~\ref{Fig:virtual-competition-solved} and~\ref{Fig:virtual-competition-solved2} show the result of such a competition, for the nine 2013 solvers; it uses all benchmarks that all the solvers registered for a given logic solve.
+Figs.~\ref{Fig:virtual-competition-solved}, \ref{Fig:virtual-competition-solved2}, and \ref{Fig:virtual-competition-solved3} show the result of such a competition, for the nine 2013 solvers; it uses all benchmarks that all the solvers registered for a given logic solve.
 In addition we performed the same experiment of 1000 virtual competitions each using 10\% of these benchmarks.
@@
 The variation is even more than that shown in Fig.~\ref{Fig:virtual-competition-some}.
-To obtain some insight into this variation, we tabulate, in columns~2 and~3 of Figs.~\ref{Fig:virtual-competition-solved} and~\ref{Fig:virtual-competition-solved2}, the mean and standard deviation\footnote{This is the population standard devation.
+To obtain some insight into this variation, we tabulate, in columns~2 and~3 of Fig.~\ref{Fig:virtual-competition-solved}ff, the mean and standard deviation\footnote{This is the population standard devation.
 To obtain the sample standard deviation scale these values by $\sqrt{0.999}$.} of the total solution time for each of the solvers in each logic.
@@
 \hline
-\input{virtual-competition-solved-alt1.tex}
+\input{virtual-competition-solved.tex}
 \end{tabular}
@@
 \hline
-\input{virtual-competition-solved-alt2.tex}
+\input{virtual-competition-solved2.tex}
 \end{tabular}
@@
 
-%\begin{figure}
-%\centering
-%\begin{tabular}{|p{.01in}rrrl|}
-%\hline
-%\input{virtual-competition-solved3.tex}
-%\end{tabular}
-%\caption{(Part 3) A virtual competition run only on benchmarks that all solvers solve.}
-%\label{Fig:virtual-competition-solved3}
-%\end{figure}
+\begin{figure}
+\centering
+\begin{tabular}{|p{.01in}rrrl|}
+\hline
+\input{virtual-competition-solved3.tex}
+\end{tabular}
+\caption{(Part 3) A virtual competition run only on benchmarks that all solvers solve.}
+\label{Fig:virtual-competition-solved3}
+\end{figure}
 
@@
 \begin{itemize}
-\item {\em The ratio of the first to second place times on each benchmark in each logic.} The closer this quantity is to 1.0, the closer the race and the more the runner-up is challenging the leader.
+\item {\em The ratio of the first to second place times on each benchmark in each logic.} The closer this quantity is to~1.0, the closer the race and the more the runner-up is challenging the leader.
 The ratio is averaged over all the benchmarks for each logic and year.
-The results are shown in Fig.
-\ref{Fig:runnerup1}: for each logic and year that had more than one competitor, the mean, and 1st, median, and 3rd quartiles of the distribution of runner-up ratios are shown.
-
-A few logics, LRA and UFLRA, are very uncompetitive: the median case has the winner more than 10 times better than the runner-up.
+The results are shown in Figs.~\ref{Fig:runnerup1} and~\ref{Fig:runnerup2}: for each logic and year that had more than one competitor, the mean, and 1st, median, and 3rd quartiles of the distribution of runner-up ratios are shown.
+
+A few logics, LRA and UFLRA, are very uncompetitive---the median case has the winner more than 10 times better than the runner-up.
 In a few others, such as QF\_IDL, QF\_NIA, QF\_NRA the winner is often less than half the time of the runner-up.
@@
 This quantity is $p/N$ if the wins are equally distributed among $p$ of the $N$ solvers ($f_i = 1/p$ for $p$ of the solvers and 0 for the other $N-p$).
-The results are shown in Figs.
-\ref{Fig:entropyA} and \ref{Fig:entropyB}; this data only includes benchmarks that were solved by a winner.
+The results are shown in Figs.~\ref{Fig:entropyA} and~\ref{Fig:entropyB}; this data only includes benchmarks that were solved by a winner.
 The first entropy column gives the value of $ 2^{( - \sum_i f_i \log_2 f_i )}$, whose value is roughly the number of solvers over which the wins are distributed.
@@
 Of the other year-logic combinations, note that in all but 11 (of the 70), despite any dominance by one solver, all competitors won at least one benchmark.
-The `competitiveness' metric itself shows that in most cases there are approximately 2 solvers sharing the bulk of the wins, increasing to about 3 in a few cases that have many participants.
-The case of the most participants---11 solvers for QF\_BV in 2012---had a distribution among about 3.5 winning solvers.
+The 'competitiveness' metric itself shows that in most cases there are approximately 2 solvers sharing the bulk of the wins, increasing to about 3 in a few cases that have many participants.
+The case of the most participants -- 11 solvers for QF\_BV in 2012 -- had a distribution among about 3.5 winning solvers.
 Thus, although nearly all solvers contribute something, performance is dominated by a few, but not by only one, in nearly all competitive logics.
@@
 \item {\em SOTAC}.
-As a final measurement in this subcategory, we measured the {\em state of the art contribution} (SOTAC), as proposed  in~\cite{webCASC}.
+As a final measurement in this subcategory, we measured the {\em state of the art contribution} (SOTAC), as proposed  in \cite{webCASC}.
 This measures the uniqueness of the contribution of each solver.
@@
 
-%\begin{figure}
-%\centering
-%\begin{tabular}{|ll|r|rrrr|}
-%\hline
-%\input{firstoversecond1.tex}
-%\end{tabular}
-%\caption{(Part 1) Runner-up: Ratio of winning time to runner-up time.}
-%\label{Fig:runnerup1}
-%\end{figure}
-%
-%\begin{figure}
-%\centering
-%\begin{tabular}{|ll|r|rrrr|}
-%\hline
-%\input{firstoversecond2.tex}
-%\end{tabular}
-%\caption{(Part 2) Runner-up: Ratio of winning time to runner-up time.}
-%\label{Fig:runnerup2}
-%\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics[angle=270,origin=c,width=\columnwidth,height=.83\textheight]{runnerup.pdf}
-\caption{Runner-up: Ratio of winning time to runner-up time, showing median, first and third quartiles.}
+\begin{figure}
+\centering
+\begin{tabular}{|ll|r|rrrr|}
+\hline
+\input{firstoversecond1.tex}
+\end{tabular}
+\caption{(Part 1) Runner-up: Ratio of winning time to runner-up time.}
 \label{Fig:runnerup1}
@@
 \centering
-\includegraphics[width=\columnwidth]{turnover.pdf}
-%\begin{tabular}{|l|rrr|p{.3in}|l|rrr|}
-%\hline
-%\input{turnover12.tex}
-%\hline
-%\end{tabular}
-\caption{Turnover: Fraction of benchmarks for the given year and logic for which the winning solver is from a different solver family than in the prior year.}
+\begin{tabular}{|ll|r|rrrr|}
+\hline
+\input{firstoversecond2.tex}
+\end{tabular}
+\caption{(Part 2) Runner-up: Ratio of winning time to runner-up time.}
+\label{Fig:runnerup2}
+\end{figure}
+
+\begin{figure}
+\centering
+\begin{tabular}{|l|rrr|p{.3in}|l|rrr|}\cline{1-4}\cline{6-9}
+\input{turnover12.tex}
+\end{tabular}
+\caption{Turnover: Fraction of benchmarks for the given year and logic for which the winning solver is from a different solver family than the prior year.}
 \label{Fig:turnover}
@@
 \centering
-\centering
-\begin{tabular}{|ll|ccrrr|}
+\begin{tabular}{|ll|rrrrr|}
 \hline
@@
 \centering
-\begin{tabular}{|ll|ccrrr|}
+\begin{tabular}{|ll|rrrrr|}
 \hline
@@
 \hline
-\input{sotac-sorted.tex}
-\hline
-\end{tabular}
-\caption{State of the art contribution from each of the 2013 solvers, sorted by total SOTAC.}
+\input{sotac.tex}
+\hline
+\end{tabular}
+\caption{State of the art contribution from each of the 2013 solvers.}
 \label{Fig:sotac}
@@
 
-\subsection{Sequential vs. parallel computation}
+\subsection{Sequential vs. Parallel computation}
 \label{parallel}
@@
 Previous competitions have had demonstration divisions featuring parallel computation.
-For this evaluation we set a wall-clock timeout of 25 minutes and a CPU-time timeout of 100 minutes.
+For this evaluation we set a wall-clock timeout of 25 minutes and a cpu-time timeout of 100 minutes.
 Thus the evaluation measured the performance of solvers for parallel computation, if they were so configured.
-A competition focused on sequential processing would set the wall-clock and CPU-time timeouts at the same value.
-We did not rerun the evaluation data to assess sequential processing performance. The data showing both wall-clock and CPU time was not available when we did our 
-primary evaluation, and some of the early CPU-time data appears inconsistent with the wall-clock times. Thus we left questions about parallel vs. sequential performance for further study: 
+A competition focused on sequential processing would set the wall-clock and cpu-time timeouts at the same value.
+We did not rerun the evaluation data to assess sequential processing performance. The data showing both wall-clock and cpu time was not available when we did our
+primary evaluation, and some of the early cpu-time data appears inconsistent with the wall-clock times. Thus we left questions about parallel vs. sequential performance for further study:
 \begin{itemize}
 \item what fraction of solvers use parallel computation?
-\item what is the speedup generally achieved by these solvers and the kinds of problems represented by the benchmark set?
-\item what is the observed overhead, that is, for purely sequential performance by how much does the wall-clock time exceed the CPU-time?
-\item are competition results significantly different when judged by CPU time vs. wall-clock time?
+\item what is the speedup generally achieved by these solvers on the kinds of problems represented by the benchmark set?
+\item what is the observed overhead, that is, for purely sequential performance by how much does the wall-clock time exceed the cpu-time?
+\item are competition results significantly different when judged by cpu time vs. wall-clock time?
 \end{itemize}
 We expect that the 2014 competition will generate a data set better able to answer these questions.
-
-With respect to this study, note that we used solvers as they were historically configured.
-They may have been configured solely for sequential performance, and the authors do not know in every case what the configurations of the older solvers are.
-Modern configurations of the same solvers might make use of multiple cores.
-The configuration of StarExec used for the evaluation (4 cores, 25 minute timeout) might be less than ideal for some historical solvers, but it is typical of what a user might use at the present time.
-Thus, to repeat a point made before in Section~\ref{sec:solvers}, the results of the virtual competitions should not be used to compare specific solvers.
-Rather, they offer a comparison of different modes of organizing and running the competition.
 
@@
 \item {\em check} benchmarks are simple tasks that are designed to ensure that a solver has the basic functionality required for a division;
-\item {\em industrial} benchmarks are generated from some application; ideally these are substantial examples showing real-world variation, but they may be from toy applications running on a toy examples;
-\item {\em crafted} benchmarks are hand-crafted to exercise a particular functionality or technical challenge;
+\item {\em industrial} benchmarks are generated from some application; ideally these are substantial examples showing real-world variation, but they may be from toy applications running on toy examples;
+\item {\em crafted} benchmarks are hand-crafted to exercise a particular bit of functionality or technical challenge
 \item {\em random} benchmarks are randomly generated from some distribution.
@@
 The same table also shows the distribution of benchmarks among those known to be satisfiable, unsatisfiable, and with an unknown status. Here there is
-considerable variation. Some logics have nearly no satisfiable benchmarks. Some have a large proportion (at least as of 2013) of benchmarks of unknown status.
+considerable variation. Some logics have nearly no sat benchmarks. Some have a large proportion (at least as of 2013) of benchmarks of unknown status.
 This is particularly the case for the popular and important QF\_BV logic.
@@
 \centering
-\begin{tabular}{|l|r|r@{\hskip 8pt}r@{\hskip 8pt}r@{\hskip 8pt}r|r@{\hskip 8pt}r@{\hskip 8pt}r|}
+\begin{tabular}{|l|r|rrrr|rrr|}
 \hline
@@
 This is relevant to interactive applications, but is not the main focus of the competition.
-In 2012, there were demonstration divisions on generating unsat cores and proof generation.
+The evaluation reported here did not consider the incremental benchmarks.
+
+In addition, in 2012, there were demonstration divisions on generating unsat cores and proof generation.
 These did not require special benchmarks, but do require different evaluation.
-The evaluation reported here did not consider the incremental benchmarks.
+We did not evaluate these variations either.
 
@@
 
-An additional question that would be interesting to address in a benchmark evaluation
- is the degree to which benchmarks discriminate among solvers.
+An additional question that we did not address in detail is the degree to which benchmarks discriminate among solvers.
 A small set of `discriminating' benchmarks would be more useful than a large set of undifferentiated ones.
-One could, for example, measure a quantity akin to the SOTAC measure of Section~\ref{Competitiveness}: benchmarks that are easy for all solvers would be discounted, ones that are hard for all would be challenges, and ones that show a wide range of performance might be discriminating benchmarks.
-
-For example, consider a competition with just two solvers. There are then four categories of benchmarks corresponding to the subsets of solvers that solve the
-benchmarks.
-The key point is whether benchmarks that are grouped together would nearly always be grouped together in other competitions with other sets of solvers or other competition rules.
-To fully elucidate this question will require analysis of the characteristics of the benchmarks combined with
-experimental assessment of their similarity in a wide variety of competition designs.
-We determined that the principal data collection of SMT-EVAL was not adequate to answer this question and that it deserved a full analysis in
-conjunction with a broad evaluation of benchmarks.
+One could, for example, measure a quantity akin to the SOTAC measure of section \ref{Competitiveness}: benchmarks that are easy for all solvers would be discounted, ones that are hard for all would be challenges, and ones that show a wide range of performance might be discriminating benchmarks.
 
@@
 \end{tabular}
-\caption{The distribution of winning benchmark times by logic (for 2013 solvers).}
+\caption{The distribution of winning benchmark times, in seconds, by logic (for 2013 solvers).}
 \label{Fig:quintiles}
@@
 
-As part of its evaluation, the SMT-EVAL team solicited input on applications that use SMT-LIB. The response was not broad enough to be representative. In addition, the authors 
+As part of its evaluation, the SMT-EVAL team solicited input on applications that use SMT-LIB. The response was not broad enough to be representative. However, the authors
 have encountered, by happenstance, enough users of SMT-LIB who are not active in the user community to indicate that there is likely a wide variety of uses that are not well-organized or well-represented in benchmarks on specific logics.
@@
 \begin{itemize}
-\item First, unsurprisingly, there is still a need for more and better benchmarks, despite the successful growth and current large quantity ($>$ 100\,000) of benchmarks in SMT-LIB.
+\item First, unsurprisingly, there is still a need for more and better benchmarks, despite the successful growth and current large quantity ($>$\,100\,000) of benchmarks in SMT-LIB.
 Some logics have few benchmarks.
@@
 \item {\em Participation}.
-The number of participants is relatively stable (9 to~13) with an average turnover of 35\% (low of 16\%, high of 50\%) each year.
+The number of participants is relatively stable (9-13) with an average turnover of 35\% (low of 16\%, high of 50\%) each year.
 There is also a core of continuing participants (about 1/3 of the total).
-\item {\em Progress in solver performance}. Solver performance increased significantly from 2010 to 2013. 
-Most of that improvement occurred from 2010 to 2011; we did not determine a reason for that improvement. There is improvement across nearly all logics, though some logics are lagging.  
+\item {\em Progress in solver performance}.
+Solver performance increased significantly from 2010 to 2013, but most of that improvement occurred from 2010 to 2011.
+There is improvement across nearly all logics, but some logics are lagging.
 \item {\em Repeatability}.
@@
 It is also relevant that most benchmarks change winner from one year to the next.
-Overall, we judge that there is a moderate degree of competitiveness among solvers - a few tend to dominate in any logic, but other solvers do also make their contribution.
-\item {\em Difficulty of benchmarks}. A relatively low fraction of benchmarks require more than the timeout period to solve. Most benchmarks are solved by all solvers within the timeout period.
+Overall, we judge that there is a moderate degree of competitiveness among solvers---a few tend to dominate in any logic, but other solvers do also make their contribution.
+\item {\em Difficulty of Benchmarks}. A relatively low fraction of benchmarks require more than the timeout period to solve. Most benchmarks are solved by all solvers within the timeout period.
 
@@
 \begin{itemize}
-\item To reduce potential variation caused by choice of benchmarks in a competition, a competition should include as many benchmarks as possible.
+\item Include as many benchmarks as possible in a competition, to reduce potential variation caused by choice of benchmarks in a competition.
 \item Invigorate the collection of benchmarks and promote a round of curating the existing benchmarks. This might include discontinuing or combining some logics.
@@
 \item Encourage broad participation by measuring performance in all logics, even when some logics are deemed more relevant than others.
-\item Encourage broadening measures of performance beyond solution of single satisfiability problems, by including, for example, determining unsat cores, measuring performance on incremental benchmarks, computing interpolants, producing proofs, producing satisfying assignments, or encouraging solvers that use multi-processing implementations.
+\item Encourage broadening measures of performance beyond solution of single sat/unsat problems, by including, for example, determining unsat cores, measuring performance on incremental benchmarks, computing interpolants, producing proofs, producing satisfying assignments, or encouraging solvers that use multi-processing implementations.
 \item Investigate the naming convention and inclusion relationships for logics, with the goal of simplifying the relationships and with an eye toward adding additional theories and a significant expansion of the number of logics.
@@
 \item a broad survey of SMT application domains and their needs in solver support, both logics and functionality beyond determining satisfiability.
-A corresponding review of the benchmarks in SMT-LIB would determine the degree
-to which benchmarks are representative of the application domains and would 
-provide guidelines for collecting new benchmarks.
+This would also drive collection of relevant benchmarks.
 \end{itemize}
@@
 \item Are there interesting differences in performance between satisfiable and unsatisfiable benchmarks?
-\item Do solvers support all of SMT-LIB~v2?
-Should the community encourage expansion to new capabilities (e.g., unsat cores, incremental, interpolants, model generation, proof generation)?
-Should the community define a core language that is used for the competition, with other aspects being optional?
+\item Do solvers support all of SMT-LIB~v2? Should the community define a core language that is used for the competition, with other aspects being optional?
+\item Should the community encourage expansion to new capabilities (e.g., unsat cores, incremental, interpolants, model generation, proof generation)? 
 \item Which logics should be retired or deemphasized, based on solver progress or application need?
@@
 
-%\section*{Acknowledgments} 
-\begin{acknowledgements}
-
-The cost of executing the SMT competition is underwritten by the SMT
-Workshop.  The evaluation used the StarExec cluster at the University
+\section*{Acknowledgments}
+
+The cost of executing SMT competitions is underwritten by the SMT
+Workshop.  This evaluation used the Star-Exec cluster at the University
 of Iowa.  This computation cluster replaces the SMT-Exec cluster used
@@
 views of the National Science Foundation.
-\end{acknowledgements}
 

### 2015-02-16 2014/report/SMTCOMP.tex
Moved (non-public) source files out of smtcomp-web.

%% Based on a TeXnicCenter-Template by Tino Weinkauf.

%%\documentclass[12pt,oneside]{report}
\documentclass[twoside,11pt]{article}

%% Language %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\usepackage[USenglish]{babel} %francais, polish, spanish, ...
\usepackage[T1]{fontenc}
%\usepackage{textcomp}
%\usepackage[ansinew]{inputenc}
%\usepackage{makeidx}	  %% needed to create an index
\usepackage{jsat}
\usepackage{hyperref}   %% sets hyperlinks within a pdf
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{parskip}
\usepackage{subcaption}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage{rotating}
\usepackage{pbox}
\usepackage{listings}
\lstdefinelanguage{smtlib2}
  {alsoletter={-, =},
   morekeywords={set-logic,declare-fun,assert,check-sat,set-info},
   sensitive=false,
   morecomment=[l]{;}}
\lstset{language=smtlib2,
basicstyle=\small\sffamily,
numbers=none,
keywordstyle=\small\bfseries\sffamily,
keywordstyle={[2]\small\bfseries\sffamily\underbar}
}
\usepackage{pifont}
%%\usepackage{lmodern} %Type1-font for non-english texts and characters

%% Packages for Graphics & Figures %%%%%%%%%%%%%%%%%%%%%%%%%%
%\usepackage{graphicx} %%For loading graphic files
%\usepackage{subfig} %%Subfigures inside a figure
%\usepackage{tikz} %%Generate vector graphics from within LaTeX

%\usepackage{mathptmx} %% Times fonts, for math as well

\newcommand{\comment}[2]{\begin{quote}\sc #1\marginpar{\textcolor{red}{$\ast^{\mbox{#2}}$}}\end{quote}}

\newcommand{\tjark}[1]{\comment{#1}{TW}}
\newcommand{\davidd}[1]{\comment{#1}{DD}}
\newcommand{\davidc}[1]{\comment{#1}{DC}}

\newcommand{\rot}[1]{\begin{turn}{90}#1\end{turn}}

\jsatheading{number}{year}{startpage-endpage}
\ShortHeadings{The 2014 SMT Competition}{D.\ Cok et al.}
\firstpageno{1}

\begin{document}

\title{The 2014 SMT Competition}

\author{\name{David R. Cok (chair of organizing committee)}
\email{dcok@grammatech.com} \\
\addr GrammaTech, Inc. \\
\AND
\name{David D\'{e}harbe (co-organizer)}
\email{david@dimap.ufrn.br} \\
\addr Federal University of Rio Grande do Norte, Brazil \\
\AND
\name{Tjark Weber (co-organizer)}
\email{tjark.weber@it.uu.se} \\
\addr Uppsala University, Sweden}

\maketitle

\begin{abstract}
The 2014 SMT Competition was held in conjunction with the SMT workshop, affiliated with the CAV, IJCAR, and SAT conferences at FLoC 2014, at the Vienna Summer of Logic in July 2014. Eighteen solvers participated from thirteen different research groups, across 34 different logic divisions. The competition was also part of the FLoC Olympic Games event, which gave combined visibility to 14 different competitions related to automated logic problem solving.
The 2014 edition of the SMT Competition was executed for the first time on the StarExec logic solving service. Several records were broken: number of participating solvers, number of new entrants, number of logic divisions, number of benchmarks, and amount of computation. The detailed performance of each solver on each benchmark from this first year using StarExec will be a solid baseline to measure improvements in the state-of-the-art of solver performance in future years.
\end{abstract}

\keywords{SMT solver, SMT-COMP, SMT-LIB, Satisfiability Modulo Theories, competitions}

%\published{December 2014}{revision date}{publication date}

%\davidc{Material to include, from the call: Full articles by competition organizers reporting on SAT-related competitions
  %within FLoC Olympic Games 2014. The articles should describe the competition,
  %its criteria, why it is interesting to the SAT research community, execution
  %environment used, analysis of the results (including how they compare to
  %previous instantiations, if appropriate), and give a summary of the main
  %technical contributions to the field, as well as discussions on lessons
  %learned and suggestions for improvements for future competitions. }

\section{Introduction}
\label{sec:intro}

The SAT-solving decision problem can be generalized by replacing
Boolean variables with atomic predicates built with symbols from a
background theory, or a combination of background theories. The
resulting decision problem is called \emph{Satisfiability Modulo
  Theories\/} (SMT). The background theories of interest arise from
	application domains, such as formal verification or scheduling problems, and include arrays,
bit-vectors, equality with uninterpreted functions, linear and
non-linear arithmetics over integers and real numbers. Also, a theory
may explicitly allow or disallow quantification. Tools addressing the
SMT problem are called \emph{SMT solvers\/}. An SMT solver is often
built by combining a SAT solver with (semi-)decision procedures for
specific theories.

The 2014 SMT Competition (SMT-COMP) continued the series of annual competitions in SMT solver capability and performance that began in 2005. This is the 9th competition in the series, skipping only 2013; in that year an evaluation~\cite{it:2014-017} was performed, rather than a competition.

The competition is held to spur advances in
SMT solver implementations acting on benchmark formulas of practical interest. Public competitions are
a well-known means of stimulating advancement in software tools. For example, in automated
reasoning, the SAT and CASC competitions for propositional and first-order reasoning tools, respectively,
have spurred significant innovation in their fields~\cite{leberre+03,PSS02}.

The competition is sponsored by the SMT workshop, which was held in conjunction with the
CAV, IJCAR, and SAT conferences at FLoC 2014~\cite{FLoC2014}, at the Vienna Summer of Logic~\cite{VSL} in July 2014.
Information about the winners
and results of the competition is summarized in this report and is available online at \url{www.smtcomp.org}; information
about previous years' competitions is also available at that website and in published summary reports~\cite{springerlink:10.1007/s10817-012-9246-5,DBLP:conf/cade/CokGBD12,it:2014-017}.

In the succeeding sections we describe the context of the competition (\S\ref{sec:context}), its goals and organization (\S\ref{sec:goals}), timeline (\S\ref{sec:timeline}), procedure (\S\ref{sec:procedure}), participants (\S\ref{sec:participants}), benchmarks (\S\ref{sec:benchmarks}), computational infrastructure (\S\ref{sec:starexec}), results (\S\ref{sec:results}), the place of SMT-COMP in the FLoC Olympic Games (\S\ref{sec:floc}), and post-competition activities (\S\ref{sec:post}). Section \ref{sec:conclusions} presents observations on this competition and recommendations for the future.

\section{Context of the Competition}
\label{sec:context}

The SMT Competition is a competition among SMT solvers on a set of benchmark logic problems expressed in the SMT-LIB~\cite{BarST-RR-10} language. Each benchmark problem is a combination of definitions and logical assertions expressed with respect to an underlying logical theory and, perhaps, some constraints on the kinds of expressions in that theory. Each problem has a set of constant or function symbols; a solution to the problem is an assignment of each constant and function evaluation to values in a way that satisfies all the problem's assertions. That is, the task is to find a \emph{satisfying assignment} for the benchmark problem.

As stated, the goal of SMT-COMP is similar to the goal of the SAT competition. The SMT benchmarks extend SAT by incorporating defined theories, such as the theory of arrays, or of undefined functions, or of arithmetic, or of bit-vectors. In addition, there may be constraints on the set of expressions allowed, such as only linear arithmetic, or only integer difference arithmetic. The theories also define \emph{sorts}, which make the theories a kind of typed first-order logic. Examples of sorts used in current theories are Boolean, Int, Real, bit-vectors of various lengths, and arrays with arbitrary sorts as index and value. Each combination of underlying theories and language constraints is a \emph{logic}.

The benchmark problems are expressed in the concrete syntax defined in the SMT-LIB~(v2) standard \cite{BarST-RR-10}. This standard has been used since 2010; a previous version was used prior to that. One of the goals of the SMT Competition is to encourage use and tool implementations of the SMT-LIB standard. The following example illustrates part of this concrete syntax:

\begin{minipage}{\textwidth}
\begin{quote}
\lstset{frameround=fttt}
\begin{lstlisting}[frame=trBL]
(set-logic UFLIA)
(declare-fun max (Int Int) Int)
(assert (forall ((x Int) (y Int))
   (let ((m (max x y)))
      (and (>= m x) (>= m y) (or (= m x) (= m y))))))
(assert (not (forall ((x Int) (y Int))
   (let ((m (max x y)))
      (= (max (max x y) x) (max x y))))))
(check-sat)
\end{lstlisting}
\end{quote}
\end{minipage}

Commands to the SMT solver are typeset in bold here.  The command
\lstinline{set-logic} sets the background theory: \lstinline{UFLIA} is
the combination of equality with uninterpreted
functions~(\lstinline{UF}) and linear integer
arithmetic~(\lstinline{LIA}). Next, the command
\lstinline{declare-fun} introduces a function symbol, named
\lstinline{max}, which has two arguments of sort \lstinline{Int} and
returns an \lstinline{Int} value. Next, two formulas are asserted. The
first essentially restricts the interpretation of the function named
\lstinline{max} to the standard interpretation. The second expresses
(the negation of) a property of this operator. The command
\lstinline{check-sat} instructs the SMT solver to check if the assertions
are satisfiable. Here the expected result is \lstinline{unsat},
indicating that the desired property is valid.

The language includes commands that allow a fine-grained interaction
with the solver, whereby client tools may incrementally push and pop
symbol declarations and assertions while running several
satisfiability checks, and inspecting models or get unsatisfiability
proofs. Benchmarks problems that have more than one
\lstinline{check-sat} command are called \emph{application} or \emph{incremental
  benchmarks}. Not all SMT solvers support all these interaction
facilities, and the main track of the competition does not use such
application benchmarks.

As of June 2014, the SMT-LIB repository contained over 130,000
non-incremental benchmarks divided into 34 background theories, and
close to 10,000 incremental benchmarks distributed across 8 background
theories. The size of a benchmark file may vary from a few hundred
bytes to several gigabytes. Fig.~\ref{fig:smtlib-bysize} shows the
distribution of the benchmarks by file size.

\begin{figure}
\begin{center}
\begin{tabular}{cc}
\includegraphics[angle=270,width=.47\textwidth]{smtlib2-file-count-by-size.pdf}
&
\includegraphics[angle=270,width=.47\textwidth]{smtlib2-app-file-count-by-size.pdf}
\\
\\
Non-incremental benchmarks & Application benchmarks
\end{tabular}
\end{center}
\caption{Distribution of SMT-LIB benchmarks by file size.
\label{fig:smtlib-bysize}}
\end{figure}

SMT solvers are automated tools that seek to find a satisfying assignment for a given SMT-LIB problem, or to assure that the problem is \emph{unsatisfiable}.
Tools may not be able to solve a given problem, because, for example the tool exhausts available memory or time; a tool is permitted to answer \emph{unknown}. However, giving an incorrect answer (\emph{sat} instead of \emph{unsat}, or vice versa) is considered \emph{unsound} and a serious fault in the tool.

SMT differs from the CASC competition~\cite{PSS02} in directly addressing sorted logics. SMT also focuses on fragments of first-order logic that are \emph{decidable}. For example, a subset of the benchmarks are problems in an integer-difference logic, for which there are specific decision procedures. The competition among tools is to create very efficient implementations of a breadth of decision procedures. Accordingly, SMT solvers have historically not handled logics with quantified expressions, though several solvers now do so.

\section{The Competition Goals and Organization}
\label{sec:goals}

In planning the 2014 competition, the organizers' overall goal was to encourage breadth
in the capability of SMT solvers. SMT-COMP 2014 benefited from the evaluation that was performed in 2013 and the experience of previous competitions. As a result we established the following emphases:
\begin{itemize}
\item In 2012 we narrowed the competition to a smaller number of more significant logics. In response to feedback, in 2014 we reverted to the practice of evaluating solvers in all available divisions.
\item We ran the competition with all available benchmarks. To be eligible, a benchmark must be well-formed and have a known answer. We were able to use all benchmarks because we had nearly exclusive use of the StarExec cluster during the time we were executing SMT-COMP. This point is discussed further in \S\ref{sec:procedure}.
\item In 2012 some experimental tracks were held: parallel performance, unsat cores, and proof generation. The participation in those tracks was light. Since in 2014 we also had to migrate to using StarExec, we held only a main track and an application (incremental) track in the 2014 competition. The organizers still maintain the value of measuring the performance of solvers on new features such as model generation, unsat core determination, and proof generation, and recommend that they be reinstated in some future edition of the competition.
\item A significant change in 2014 was to increase the time-out limit for a solver processing a given benchmark from 25 minutes (in 2012) to 40 minutes.
\item A significant result of the 2013 Evaluation was that the result of a competition was highly sensitive to the selection of benchmarks: different random selections of benchmarks resulted in different winning orders in a large fraction of samples. Hence, an aim for 2014 was to use as large a benchmark set as possible in the competition to minimize this effect.

\end{itemize}

An important difference between the 2014 competition and previous competitions was that this year's competition was executed on the StarExec cluster, described below in \S\ref{sec:starexec}. All the supporting tools and related procedures needed to be ported to this new framework. With watchful eyes by the organizers and the StarExec team, and with some debugging, the StarExec framework worked well and enabled a larger scale of competition than in previous years.

\section{Competition Timeline}
\label{sec:timeline}

The preparation and execution of SMT-COMP 2014 took place over about 7 months, relying on the experience of previous competitions, the 2013 SMT Evaluation, and development activity on StarExec:
\begin{itemize}[noitemsep]
\item July 2013 -- Cok appointed as chair of the organizing committee.
\item December 2013 -- D\'{e}harbe and Weber appointed as co-organizers.
\item 21 January 2014 -- call for applications and benchmarks.
\item 15 May 2014 -- deadline for new benchmarks; benchmarks were being corrected and curated throughout May and June, until the final solver deadline.
\item 19 May 2014 -- revised rules posted.
\item 1 June 2014 -- deadline for initial solver registration; final rules posted.
\item 15 June 2014 -- deadline for final solver registration.
\item 16 June 2014 -- computation begins.
\item 22 June 2014 -- main track computation ends; official results posted on 27~June.
\item 22 June 2014 -- deadline for application track solvers.
\item 28 June 2014 -- application track computation.
\item 17 July 2014 -- SMT Workshop at which results were announced.
\item 21 July 2014 -- FLoC Olympic Games Awards Ceremony.
\end{itemize}

\section{Competition Procedure}
\label{sec:procedure}

The full description of the 2014 SMT Competition's rules is found in the rules document (\url{http://smtcomp.sourceforge.net/2014/rules14.pdf}). The document describes the procedures for determining benchmark difficulties, selecting benchmarks for competition, and judging the results. The preparation and execution of the competition required the following matters to be decided and executed.

\paragraph{Decide the competition parameters.} We set a timeout of 40~minutes for both wall clock and CPU time; the memory limit was 100\,GB. A single solver-benchmark combination (job-pair) was run on a node at a given time. The benchmarks were scrambled; all benchmarks were run. StarExec made about 150 nodes available for the duration of the competition. The timeout setting was a notable difference in 2014; in 2013, this was set at 25~minutes. The effect of this is discussed in \S\ref{sec:timeouts}. Though the memory limit was fairly generous, a small number~(202) of jobs were killed during the competition because of excessive memory use.

\paragraph{Settle any adjustments on the rules and competition timeline, with time for comment.}
The competition rules are largely the same from year to year, but each year there are adjustments and improvements. Matters to be decided are the timeline for the competition, communication vehicles (including instantiating the website for the new competition), the various tracks and divisions, any adjustments to the benchmark selection procedure, the scoring rules, and policies on similar submissions and portfolio solvers. A novel aspect in 2014 was the need for policies regarding the FLoC Olympic Games~\cite{FLoCGames}, described in \S\ref{sec:floc}. During the competition, the organizers had to rule on two issues.
\begin{itemize}[noitemsep,nolistsep]
\item First, whether solvers could be withdrawn from divisions after the competition began; our ruling was no, because that could raise a solver's overall performance score and could change which divisions were deemed competitive. This decision did affect the results of the FLoC medal competition.
\item Second, whether a job-pair that responded with a result before the timeout limit, but did not exit until after the timeout limit, is to be considered a timeout or a correct or wrong answer; the ruling was that it is not a timeout. Only one benchmark was affected by this decision and the decision did not affect any winning order, just a slight change in one solver's score.
\end{itemize}
The organizers also received and adjudicated an appeal after the competition completed (cf.~\S\ref{sec:floc}).

During the testing prior to the competition beginning, different solvers exhibited different behavior on some benchmarks. Investigation revealed that these differences were the result of different treatments of partial operations, divide by zero, in particular. The question is what should be the definition of divide by zero in SMT-LIB's logic of total functions. This question had been discussed at length over previous years, with proposals to clarify the SMT-LIB standard.
There was certainly not time to resolve this matter prior to the competition, not to mention correcting solvers to the agreed behavior.\footnote{The discussion this time around can be found in the archives of the \url{smtcomp-discussion@lists.sourceforge.net} mailing list, in the few days near 2014-06-16.}
Thus, for the competition, we decided to omit all benchmarks (6060 of them, 1348 of which were otherwise eligible) that were affected by divide-by-zero behavior. This question, however, remains open.

\paragraph{Invite and validate solver submissions.} The 2014 competition saw the first use of the StarExec computational cluster (cf. \S\ref{sec:starexec}) for executing the competition. Each solver had to be wrapped in appropriate scripts to be able to run in the StarExec environment. Though this was largely the responsibility of the solver submitter, teams submitting solvers for the first time required guidance and assistance from the organizers and the StarExec development team. This was a significant hurdle; not all solver teams were able to complete it in time. The most significant problem was the need to create a fully statically linked version of the solver that ran on the particular version of Linux used by StarExec. The organizers stipulated a first solver submission deadline and a final solver submission deadline, separated by two weeks, to enable (and encourage) trials and debugging of solver submissions.

Solver submissions comprise the solver itself, a short system description outlining what is new or novel about the solver, and an integer seed. All the submitted seeds and an additional seed derived from a value unknowable until after the solver submission deadline were summed and used as the starting seed for any pseudo-random selection and scrambling processes (see below) in the competition.

\paragraph{Invite and validate benchmark submissions.} New benchmarks are always welcome but an impending competition is a particular opportunity to encourage new submissions. Benchmarks are the responsibility of SMT-LIB coordinators, not the competition organizers. Nevertheless, the organizers worked with the coordinators to ensure that new benchmarks were included in SMT-LIB in time for the competition. Initial submissions are often incomplete; to be useful they must be syntactically correct, include a designation of the logic in which they fit, contain relevant metadata about the source and category of the benchmark, and have a known, validated answer. Benchmarks with unknown answers may also be interesting and worth keeping, but cannot be used in the competition.

\paragraph{Create an appropriate selection of benchmarks.} Not all benchmarks in the SMT-LIB database are necessarily used in the competition. The details of this selection, as executed for the 2014 competition, are described in \S\ref{sec:benchmarks}. Part of the work in preparing the competition to run on the StarExec cluster was to port the benchmark selector to StarExec.

\paragraph{Prepare the benchmark scrambler.} All the benchmarks are public and known to the solver developers beforehand. Indeed, part of the point of the benchmark database is to serve as a testbed for solver development, outside of competitions. However, that raises the possibility that a solver will recognize a benchmark problem by its syntactic structure and look up an answer from a learned database, without doing any logic solving. This is explicitly considered cheating. As a slight impediment against such behavior, the benchmarks are individually scrambled before being presented to a solver, using the random seed described above. For 2014, the benchmark scrambler had to be ported to StarExec.

The scrambling does not change the semantic meaning of the benchmark. It does rename identifiers, alter the order of assertions and the position of the arguments in the application of associative-commutative operators.

The scrambling had another effect, previously unappreciated. Although most of the solvers are deterministic for a given input, scrambling can change the order of search. For example, iterating over the contents of a hashed set may occur in a different order if identifiers have different names. Consequently, the success of the solver on a given benchmark, the time it takes to find an answer, and even whether a latent bug in the solver is triggered may all depend on just how the benchmark is scrambled. Thus the scrambling adds a measure of uncertainty to the competition and prevents full testing on the benchmark set before the competition. Indeed, one solver encountered a bug during the competition that was directly related to the specific, randomly-chosen scrambling used during the competition.

\paragraph{Prepare the real-time results display.} The participants are interested in the progress of the competition as it proceeds. The organizers also need to know if the competition is proceeding correctly and at a reasonable pace. As the competition takes several days, an automatic real-time display of results is helpful and encourages interest.  StarExec does not have such a facility, since different competitions have different needs. Instead the organizers used StarExec's command-line API to regularly (every 10 minutes or so) download the status of all of the executing jobs, extract the results for each solver-benchmark pair, create HTML web pages displaying the current status, and upload them to the competition website. The current (now final) status of each division and a summary page can be seen at \url{http://smtcomp.sourceforge.net/2014/results-toc.shtml}.

\paragraph{Execute the competition.} Executing the competition required preparing a StarExec job for each
division. A job executes the cross-product of a set of solvers and a set of benchmarks. Because each division has different sets of solvers and benchmarks, each division was a separate job (or split into several jobs). This also allowed a restart of portions of the competition if a particular division was incorrectly configured or if a StarExec job stalled for some reason (both of which happened).

In addition, with the new cluster, the new benchmarks, and a longer timeout period, the organizers were unsure how long the competition would take. Our conservative estimate was that a month of computing was needed; in fact it only took about a week, because we had three times more StarExec nodes available than anticipated and jobs took on average less time than estimated. However, to hedge against the competition taking longer than anticipated, we divided larger divisions into \emph{heats}, with each heat comprising about 1000 benchmarks, and with the option (stated in the rules) to terminate the competition before all heats were executed to ensure a timely end prior to FLoC. This required handling a much larger number of StarExec jobs. In the end it was entirely unnecessary for timely completion, but, as mentioned, dividing the jobs into manageable pieces was useful for restarting portions of the computation when StarExec stalled.\footnote{Stalling---that is, no longer making forward progress on a job---was less a concern after some bug fixes during the competition, but was still observed during some post-competition computations.}

In past competitions, the competition was timed to have its last portion overlap with the conference with which it was affiliated. In 2014, because the computation took less time than anticipated, the competition finished well before the conference.

\paragraph{Report the results.} The results of the competition were reported at the SMT Workshop and in this paper.

\section{Participants}
\label{sec:participants}

The competition registration includes information about each competing solver. In addition, some solver groups provided summaries of their solvers and their recent technical advances.
 Note that although one person is listed as the ``submitter,'' there is generally a team of contributors behind each tool. Some teams submitted more than one tool. The 2014 participants were the following:
\begin{itemize}
\item 4Simp -- submitted by Trevor Hansen (U. Melbourne)
\item AbzizPortfolio -- two versions -- submitted by Mohammed Adbul Aziz (U. Cairo). This solver is unusual in that it is a portfolio solver: based on automated learning over benchmark characteristics, it chooses among other solvers to apply to the problem at hand.
\item AProVe~\cite{AProVE2014} -- submitted by Carsten Fuhs (University College London)
\item Boolector~\cite{Boolector2015} -- three versions: Boolector (default),  Boolector-d (dual propagation), Boolector-j (justification) -- submitted by Armin Biere, Aina Niemetz, Mathias Preiner (Johnnes Kepler University)
\item CVC3 v. 2.4.3~\cite{BT07} -- submitted by Morgan Deters (New York University)
\item CVC4 v. 1.4~\cite{BCD+11} -- submitted by the ACSys Group (New York University)
\item Kleaver -- 2 versions -- submitted by Hristina Palikareva, Cristian Cadar (Imperial College)
\item OpenSMT2 -- submitted by Antti Hyv\"arinen (U.~Lugano)
\item raSAT~\cite{DBLP:conf/smt/KhanhVO14} -- submitted by Xuan-Tung Vu (Japan Advanced Insitute of Science and Technology)
\item SMTInterpol~\cite{DBLP:conf/spin/ChristHN12,DBLP:conf/spin/2012} -- submitted by Jochen Hoenicke, J\"urgen Christ (U.~Freiburg)
\item SONOLAR~\cite{Peleska:2011:ATC:1986308.1986333} -- submitted by Florian Lapschies (U.~Bremen)
\item STP-CryptoMiniSat4~\cite{DBLP:conf/cav/GaneshD07,DBLP:conf/cav/2007} -- submitted by Mate Soos (Security Research Lab.), based on previous work by Trevor Hansen (U.~Melbourne) and Vijay Ganesh (Massachusetts Institute of Technology)
\item veriT~\cite{veriT} -- submitted by David D\'{e}harbe (UFRN - Universidade Federal do Rio Grande do Norte), Pascal Fontaine (U.~Lorraine, INRIA - Institut national de recherche en informatique et en automatique)
\item Yices2~\cite{Dutertre:cav2014} -- submitted by Bruno Dutertre (SRI)
\end{itemize}

There were a few solvers that the organizers hoped would be submitted but were not: Tiffany de Wintermonte was submitted in the past by Trevor Hansen, but could not be prepared in time for this competition; similarly SMT-RAT was withdrawn because of last minute bugs; MathSat has been a frequent competitor in the past, but changes in priorities of the development team caused it not to compete in 2014; MiniSMT also was not able to be submitted; similarly, the Z3 team, from Microsoft Research, though Z3 is a strong tool, has chosen not to take the time to prepare competition versions.

Other than those omissions, every competitive solver known to the organizers was represented. Indeed, the participation by solver teams was a record high in 2014. In addition, four teams submitting five solvers had not participated in previous competitions.

As in past competitions, the organizers included some publicly available historical solvers. These solvers are run in the competition for comparison, but are designated as demonstration only and are not eligible for any awards or designations of having won the competition. In result tables, these solvers are listed with their names in square brackets (e.g., [MathSat]). The organizers included current versions of MathSat and Z3. Also, during the competition, a bug-fix release of CVC4 (named CVC4-with-bugfix) was submitted and included as a demonstration only version (cf. \S\ref{sec:floc}).

\begin{table}[t]
\caption{History of solver participation (numbers in parenthesis indicate
the number of versions submitted for the tool). Complete records of early competitions were not available to the 2014 organizers.}
\label{Table:participants}
\renewcommand{\mark}[0]{\ding{51}}
\centering
\setlength{\tabcolsep}{1pt}
\begin{tabular}{|l|l|c|c|c|c|c|c|c|c|c|}
\hline
Solver & Affiliation & 2005 & 2006 & 2007 & 2008 & 2009 & 2010 & 2011 & 2012 & 2014 \\
\hline

4Simp                  & U. Melbourne 	&   &   &   &   &   &   &   &   & \mark  \\
STP-CryptoMiniSat4     & Security Res. Lab.  &   &   &   &   &   &   &   &   & \mark\\
Kleaver	               & Imperial       &   &   &   &   &   &   &   &   & (2) \\
raSAT  	               & JAIST          &   &   &   &   &   &   &   &   & \mark \\
Tiffany de Wintermonte & U. Melbourne 	&   &   &   &   &   &   &   & \mark &  \\
AbzizPortfolio         & U. Cairo       &   &   &   &   &   &   &   & \mark & (2)\\
Boolector              & JKU            &   &   &   & \mark & \mark &   & \mark & \mark & (3)\\
CVC/CVCLite/CVC3       & NYU, U. Iowa   & \mark & \mark & \mark & \mark & \mark & \mark & \mark & \mark & \mark \\
CVC4	                 & NYU, U. Iowa   &   &   &   &   &   & \mark & \mark & \mark & \mark \\

MathSat-HeavyBV        & U. Trento      &   &   &   &   &   &   &   & \mark &   \\
MathSAT 3,4,5          & U. Trento, FBK & \mark & \mark & \mark & \mark & \mark & \mark & \mark & \mark &   \\
SMTInterpol            & U. Freiburg    &   &   &   &   &   &   & \mark & \mark & \mark \\
SONOLAR                & U. Bremen      &   &   &   &   &   & \mark & \mark & \mark & \mark \\
STP, STP2              & MIT            &   & \mark &   &   & \mark &   & \mark & \mark &   \\
AProVE NIA             & RWTH Aachen    &   &   &   &   &   & \mark & \mark &   & \mark \\
OpenSMT, OpenSMT2      & U. Lugano      &   &   &   & \mark & \mark & \mark & \mark &   & \mark \\
veriT                  & Loria, UFRN           &   &   &   &   & \mark & \mark & \mark &   & \mark \\
Z3                & Microsoft Res.  &   &   & \mark & \mark &   &   & \mark &   &   \\
MiniSMT                & U. Innsbruck   &   &   &   &   &   & \mark &   &   &   \\
simplifyingSTP         & U. Melbourne   &   &   &   &   &   & \mark &   &   &   \\
test\_pmathsat         & FBK-IRST       &   &   &   &   &   & \mark &   &   &   \\
barcelogic             & UPC            & \mark & \mark & \mark & \mark & \mark &   &   &   &   \\
beaver                 & UC Berkeley   &   &   &   & \mark & \mark &   &   &   &   \\
clsat                  & Washington U.  &   &   &   & \mark & \mark &   &   &   &   \\
Sateen                 & U. Col-Boulder & \mark & \mark & \mark & \mark & \mark &   &   &   &   \\
sword                  & U. Bremen      &   &   &   & \mark & \mark &   &   &   &   \\
Yices, Yices2          & SRI            & \mark & \mark & \mark & \mark & \mark &   &   &   & \mark \\
Spear                  &   &   &   & \mark & \mark &   &   &   &  &   \\
Alt-Ergo               & U. Paris Sud  &   &   &   & \mark &   &   &   &  &   \\
ArgoLib                &   &   &   & \mark &   &   &   &   &  &   \\
Fx7                    &   &   &   & \mark &   &   &   &   &  &   \\
Ario                   &   & \mark & \mark &   &   &   &   &   &  &   \\
ExtSat                 &   &   & \mark &   &   &   &   &   &  &   \\
HTP                    &   & \mark & \mark &   &   &   &   &   &  &   \\
Jat                    &   &   & \mark &   &   &   &   &   &  &   \\
NuSMV                  & FBK &   & \mark &   &   &   &   &   &  &   \\
Sammy                  &   & \mark &   &   &   &   &   &   &  &   \\
SBT                    &   & \mark &   &   &   &   &   &   &  &   \\
Simplics               & SRI & \mark &   &   &   &   &   &   &  &   \\
SVC	               & Stanford U.  & \mark &   &   &   &   &   &   &  &   \\
\hline
\end{tabular}
\end{table}

\begin{table}
\caption{Changes in participation}
\label{Table:changes}
\centering
\resizebox{\textwidth}{!}{\begin{tabular}{|l|c|c|c|c|c|c|c|c|c|}
\hline
 & 2005 & 2006 & 2007 & 2008 & 2009 & 2010 & 2011 & 2012 & 2014\\
\hline
Participants                 & 12 & 12 & 9 & 13 & 12 & 10 & 11 & 11 & 18 \\
New in given year            & 12 &  4 & 4 &  6 &  2 &  6 &  1 &  4 & 5 \\
Continuing to the next year  &  8 &  6 & 7 & 10 &  4 &  7 &  7 &  6 &  \\
Not ever participating again &  4 &  5 & 2 &  2 &  6 &  3 &  4 &  4 &  \\
\hline
\end{tabular}}
\end{table}

\paragraph{History.} Table~\ref{Table:participants} shows the
 historical participation of each solver. Note that sometimes versions and names change, or there are multiple related versions from the same team.
Table~\ref{Table:changes} summarizes that data in numbers of continuing participants. Except for the record turnout in
 2014, there has been a steady 9-13 participants each year; each year there are an average of 4 new
 participants, about the same number of drop-outs, and an average of 7 continuing participants.

The introduction in 2010 of SMT-LIB~v2 as the standard language for benchmarks was a significant event. The new language required solvers to revise their front-ends and to add new capabilities.
As a result, some solvers did not continue participating, at least not immediately. However, the use of SMT-LIB~v2 also increased the expressiveness of benchmarks. SMT-LIB~v2 introduced a set of (optional) commands to enable richer interactions with solvers. Thus benchmarks representing the needs of industrial applications were able to be added;
the application track of the competition was added to demonstrate the interactive capability and the corresponding abilities of solvers.

\section{Competition Divisions and Benchmarks}
\label{sec:benchmarks}

The SMT-LIB benchmarks each belong to a specific logic. Each logic is one competition division. For each division, we ran the solvers that entered that division on the benchmarks for that division as one event in the overall competition.

SMT-LIB currently defines 34 logics, shown in Table \ref{Table:benchmarks}. The rightmost column shows the number of benchmarks for that logic in the SMT-LIB collection. Two considerations may make a benchmark ineligible for a competition. First, the benchmark may not have a known result. For newly submitted benchmarks
we made an attempt to determine the correct result of the benchmark; the SMT-LIB coordinators require that two
different solvers solve the benchmark and report the same result. However, for benchmarks already in the collection we did not have time to determine their results. We did do this analysis after the competition was over (see~\S\ref{sec:post}).

The second consideration is that the benchmark must be \emph{non-trivial}; a benchmark is deemed trivial if all solvers managed to solve it in less than five seconds during SMT-EVAL 2013.

The numbers of unknown, trivial, and remaining eligible benchmarks are shown in Table \ref{Table:benchmarks}. Note that these numbers vary widely from division to division.

A sizeable number, on the order of 30,000, of benchmarks were added during the lead up to the competition. Some of these were submitted in previous years but never assessed and uploaded. Many others were supplied by solver developers (including some competitors). All of them went through an iterative curation process to be sure that they were syntactically valid, appropriate metadata was included, and a correct result was established. (Not all of these submissions were through the competition organizers.)

The SMT-LIB coordinators performed a curation step on the entire benchmark library prior to the competition, determining the actual logic to which a benchmark belonged, rather than the super-logic to which it had previously been assigned. This resulted in an expansion of logics with benchmarks from 23 to 34, and also created a number of divisions with only a very few benchmarks. Two divisions were not held because they had no eligible benchmarks.

\begin{table}
\caption{Numbers of main-track benchmarks. The second column shows the number of competitive solvers and, in square brackets, the number of demonstration-only solvers. Entries marked * exclude some benchmarks containing partial functions.}
\label{Table:benchmarks}
\centering
\begin{tabular}{|l|r|r|r|r|r|}
\hline
       & \multicolumn{1}{|c|}{\# of} & \multicolumn{4}{|c|}{\# of benchmarks} \\
 Logic & solvers & eligible & unknown  & trivial & total  \\
\hline
ALIA & 3+[1] & 29 & 0 & 13 & 42 \\
AUFLIA & 3+[1] & 4 & 0 & 0 & 4\\
AUFLIRA & 3+[1] & 10791 & 168 & 9055 & 20014 \\
AUFNIRA & 2+[2] & 564 & 468 & 463 & 1495 \\
BV & 2+[1] & 0 & 191 & 0 & 191 \\
LIA & 3+[1] & 46 & 0 & 0 & 46 \\
LRA & 3+[1] & 171 & 450 & 0 & 621\\
NIA & 2+[1] & 9 & 0 & 0 & 9\\
NRA & 2+[1] & 3747 & 66 & 0 & 3813 \\
QF\_ABV & 7+[2] & 6457* & 4191 & 4423 & 15091 \\
QF\_ALIA & 3+[2] & 97 & 0 & 29 & 126 \\
QF\_AUFBV & 2+[2] & 37 & 0 & 0 & 37 \\
QF\_AUFLIA & 4+[2] & 610 & 0 & 399 & 1009\\
QF\_AX & 3+[2] & 335 & 0 & 216 & 551 \\
QF\_BV & 8+[3] & 2488* & 28138 & 546 & 32500 \\
QF\_IDL & 3+[1] & 1315 & 537 & 337 & 2189 \\
QF\_LIA & 4+[3] & 4381 & 1279 & 481 & 6141 \\
QF\_LRA & 4+[2] & 1343 & 208 & 131 & 1682\\
QF\_NIA & 3+[1] & 8327 & 927 & 105 & 9359 \\
QF\_NRA & 3+[1] & 10121 & 1392 & 27 & 11540 \\
QF\_RDL & 3+[1] & 132 & 85 & 38 & 255 \\
QF\_UF & 5+[2] & 4124 & 4 & 2522 & 6650 \\
QF\_UFBV & 2+[2] & 31 & 0 & 0 & 31 \\
QF\_UFIDL & 3+[1] & 311 & 0 & 130 & 441\\
QF\_UFLIA & 4+[2] & 484 & 0 & 114 & 598 \\
QF\_UFLRA & 4+[2] & 1176 & 87 & 367 & 1630 \\
QF\_UFNIA & 2+[1] & 7 & 0 &0 & 7 \\
QF\_UFNRA & 2+[1] & 32 & 11 & 0 & 43\\
UF & 3+[1] & 2830 & 2911 & 7 & 5748 \\
UFBV & 2+[1] & 0 & 191 & 0 & 191 \\
UFIDL & 2+[1] & 49 & 12 & 19 & 80 \\
UFLIA & 3+[1] & 5766 & 5499 & 873 & 12138 \\
UFLRA & 3+[1] & 25 & 0 & 0 & 25\\
UFNIA & 2+[1] & 1587 & 1052 & 712 & 3351 \\
\hline
Total & 18+[3] & 67426 & 47867 & 21007 & 137648 \\
\hline
\end{tabular}
\end{table}

Solvers could participate in any or all divisions at their team's discretion. Most solvers are designed for just one selected logic, but others are intended to be as broadly applicable as their developers have had time to implement. Table~\ref{Table:logics} shows the participation of solvers in various divisions.

\begin{sidewaystable}
\caption{Solver participation in logic divisions}
\label{Table:logics}
\centering
\renewcommand{\mark}[0]{\ding{51}}
%%\small
\setlength\tabcolsep{3pt}
%%\begin{tabular}{|l|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|}
\begin{tabular}{|l|ccccc|cccc|cccccc|cccccc|ccccccc|cccccc|}
\hline
Solver & 	\rot{ALIA} & 	\rot{AUFLIA} & 	\rot{AUFLIRA} & 	\rot{AUFNIRA} & 	\rot{BV} & 	\rot{LIA} & 	\rot{LRA} & 	\rot{NIA} & 	\rot{NRA} & 	\rot{QF\_ABV} & 	\rot{QF\_ALIA} & 	\rot{QF\_AUFBV} & 	\rot{QF\_AUFLIA} & 	\rot{QF\_AX} & 	\rot{QF\_BV} & 	\rot{QF\_IDL} & 	\rot{QF\_LIA} & 	\rot{QF\_LRA} & 	\rot{QF\_NIA} & 	\rot{QF\_NRA} & 	\rot{QF\_RDL} & 	\rot{QF\_UF} & 	\rot{QF\_UFBV} & 	\rot{QF\_UFIDL} & 	\rot{QF\_UFLIA} & 	\rot{QF\_UFLRA} & 	\rot{QF\_UFNIA} & 	\rot{QF\_UFNRA} & 	\rot{UF} & 	\rot{UFBV} & 	\rot{UFIDL} & 	\rot{UFLIA} & 	\rot{UFLRA} & 	\rot{UFNIA} \\
\hline
4Simp & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	\mark & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 \\
Abziz & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	\mark & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 \\
Abziz2 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	\mark & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 \\
AProVE & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	\mark & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 \\
Boolector & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	\mark & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 \\
Boolector-d & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	\mark & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 \\
Boolector-j & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	\mark & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 \\
CVC3 & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	\mark & 	\mark & 	 & 	 & 	 & 	 & 	 & 	 & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark \\
CVC4 & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark \\
Kleaver-STP & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	\mark & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 \\
Kleaver-portfolio & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	\mark & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 \\
OpenSMT2 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	\mark & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 \\
raSAT & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	\mark & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 \\
SMTInterpol & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	\mark & 	&	\mark & 	\mark & 	 & 	 & 	\mark & 	\mark & 	 & 	 & 	 & 	\mark & 	 & 	 & 	\mark & 	\mark & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 \\
SONOLAR & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	\mark & 	 & 	 & 	 & 	 & 	\mark & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 \\
STP-Crypto... & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	\mark & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 \\
veriT & 	\mark & 	\mark & 	\mark & 	 & 	 & 	\mark & 	\mark & 	 & 	 & 	 & 	 & 	 & 	\mark & 	& &		\mark & 	\mark & 	\mark & 	 & 	 & 	\mark & 	\mark & 	&	\mark & 	\mark & 	\mark & 	 & 	 & 	\mark & 	 & 	 & 	\mark & 	\mark &   \\
Yices2 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	 & 	 & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 \\
\hline
{[}MathSAT5] & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	 & 	\mark & 	\mark & 	 & 	 & 	 & 	\mark & 	\mark & 	 & 	\mark & 	\mark & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 \\
{[}Z3] & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark \\
{[}CVC4-with-bugfix] &  &  &  & \mark &  &  &  &  &  &  &  &  &  &  & \mark &  & \mark &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  \\
\hline
\end{tabular}
\end{sidewaystable}

\paragraph{Selection of benchmarks.} In addition to whether a benchmark has a known result or is trivial, there are two other factors that affect the selection of benchmarks for a competition: the benchmark's difficulty and the desire for a distribution of problems.

Each benchmark is assigned a difficulty rating; in 2014, we used the time taken to solve the benchmark by the best performing solver in the 2013 SMT Evaluation. These values were publicly available prior to the competition. The difficulty ratings are used to divide the benchmarks into 5 quintiles. The rules describe a procedure for selecting $N$ out of the eligible benchmarks for a division, with the intent of selecting roughly equal numbers, if they are available, from each of the quintiles.

Benchmarks are also labeled by category: simple checks, randomly generated problems from some template (e.g., N-queens problems for various values of N), problems crafted to test a certain capability, and problems obtained from industrial applications. The selection rules favor industrial benchmarks.

%\davidc{Also want categories of benchmarks and numbers of sat or unsat}

In addition, some kinds of problems may be over-represented in the benchmarks. This may be the case particularly because benchmarks may be submitted by solver developers; a team might add a large number of benchmarks that would then over-represent problems that a particular solver is known to handle well. The rules allow the organizers to limit the selections from sub-populations.

In the end, there was sufficient time to use all eligible benchmarks and no further selection was performed. The 2014 organizers did not have the data to make a principled decision on over-representation of particular problem types and so did not select on this basis either. The absence of such selection may have affected the competition results and future organizing teams should reconsider this aspect even if there are sufficient computational resources to execute all benchmarks. The data from SMT-COMP 2014 could be used to inform this decision.

\paragraph{The SMT-LIB language.} A competition based on benchmark problems needs a standard language in which to express those problems.
For SMT-COMP, that language is the SMT-LIB language (cf.~\url{http://www.smtlib.org}) \cite{BarST-SMT-10,Cok-SMTLIBTutorial-2011}.
In 2010, a significantly reworked version of the language was agreed upon.
This version~2 increased the flexibility and expressiveness of the language while also simplifying the syntax.
It also includes a command language that improves the language's usefulness for interactive applications.
In particular, the standard specifies a typed (sorted), first-order logical language for terms and formulas, a language for specifying background logical theories and logics, and a command language. Some other tools that process SMT-LIB~v2 are listed in the SMT-LIB web pages (cf. \url{http://www.smtlib.org/utilities.shtml}). Further revisions were discussed at the SMT Workshop 2014.

However, it is important to note that some tools used in the competition support only a subset of SMT-LIB. This subset is only informally stated, but the benchmark set only uses this subset. This informality did not cause problems in the competition, but it would be preferable to define this subset explicitly.

\section{StarExec}
\label{sec:starexec}

The competition used the NSF-funded StarExec~\cite{DBLP:conf/cade/StumpST14} computational cluster at U.~Iowa for executing solvers on benchmarks. Past instances of SMT-COMP used a previous SMT-Exec infrastructure. StarExec was used for several other competitions in 2014 as well.

StarExec consists of 192 2.4\,GHz computational nodes, running Red Hat Linux~6.3. Each node has 2 CPUs with 4 cores each and having either 129\,GB (32 nodes) or 258\,GB of memory (160 nodes). In competition, processes were limited to 100\,GB memory. To avoid interference among job-pairs, only one job-pair was executed at a time on each node.

As this was the first year SMT-COMP used StarExec, a variety of tools and procedures needed to be ported to the new infrastructure.
These included the benchmarks, the post-processor for scoring results,
a tool to select benchmarks randomly according to the stated policies
tools for creating StarExec jobs based on selections of benchmarks and solvers,
the driver application for running the application track,
and tools for creating real-time summaries of results in progress.
These are now available to be reused in future years.

The execution of SMT-COMP on StarExec went well, though not flawlessly. As this was a first major use of StarExec for a competition there were some bugs to work through.
The organizers had some bugs of their own: the scripts to create sets of benchmarks and jobs did not account for spaces in filenames; some initial report generation was incorrect; the postprocessor for translating textual output from solvers into official results needed fine-tuning. These problems were all fixed before or early in the competition. The main issue with StarExec itself was that sometimes jobs would hang or the StarExec infrastructure would fail to make
progress or report results correctly. Bugs in scheduling were
fixed during the competition but are not entirely resolved. Accordingly, jobs need regular monitoring that they are making progress.

Overall, however, StarExec performed its function well: evaluations of 339,714 job-pairs were completed for the competition over a period of about 9 days, not even counting the restarts necessary because of bugs or misconfigurations.

\section{Results}
\label{sec:results}

\subsection{Main track results}
\label{sec:timeouts}

Table \ref{Table:maintrack} shows a summary of the main track results. The detailed data for each division is on the competition website: \url{http://smtcomp.sourceforge.net/2014/results-toc.shtml}.

Unfortunately, we cannot make a useful comparison with previous years for a number of reasons. First, until the evaluation in 2013, the competition was run on a different computation infrastructure, so solution times are not comparable. The SMT evaluation in 2013 and the competition in 2014 were both run on StarExec but with different timeouts and different configurations of nodes. Finally the early data from StarExec only captured wall-clock time, not CPU time. The organizers are confident that the 2014 data will be a solid baseline for evaluating progress in solver performance in future years.

\begin{table}
\caption{Main track results}
\vspace{-\smallskipamount}
\label{Table:maintrack}
\centering
\newcommand{\win}[1]{\textbf{#1}}
\resizebox{!}{299pt}{\begin{tabular}{|l|r|r|l|}
\hline
Logic &	Solvers &	Benchmarks & Order (winner in bold) \\
\hline
ALIA & 		4 & 	29  & 	[Z3]; \win{CVC4}; veriT; CVC3. \\
AUFLIA & 	4 & 	4   & 	\win{CVC4}; [Z3]; CVC3; veriT. \\
AUFLIRA & 	4 & 	10791 & 	[Z3]; \win{CVC4}; CVC3; veriT. \\
AUFNIRA & 	4 & 	564 & 	[CVC4-with-bugfix]; [Z3]; \win{CVC3}; CVC4. \\
LIA & 		4 & 	46 & 	[Z3]; \win{CVC4}; CVC3; veriT. \\
LRA & 		4 & 	171 & 	\win{CVC4}; [Z3]; CVC3; veriT. \\
NIA & 		3 & 	9 &  	[Z3]; \win{CVC4}; CVC3. \\
NRA & 		3 & 	3747 & 	[Z3]; \win{CVC4}; CVC3. \\
QF\_ABV & 	9 & 	6457 & \win{Boolector-j}; Boolector-d; [MathSAT]; \\
& & & SONOLAR; CVC4; [Z3]; Yices2; \\
& & & Kleaver-STP; Kleaver-portfolio. \\
QF\_ALIA & 	5 & 	97 & \win{Yices2}; SMTInterpol; [Z3]; [MathSAT]; CVC4. \\
QF\_AUFBV & 	4 & 	37 & \win{CVC4}; Yices2; [Z3]; [MathSAT]. \\
QF\_AUFLIA & 	6 & 	610 & \win{Yices2}; [MathSAT]; [Z3] \\
& & & SMTInterpol; CVC4; veriT. \\
QF\_AX & 	5 & 	335 & \win{Yices2}; [MathSAT]; [Z3]; CVC4; \\
& & & SMTInterpol. \\
QF\_BV & 	11 & 	2488 & \win{Boolector}; STP-CryptoMiniSat4; \\
& & & [CVC4-with-bugfix]; [MathSAT]; [Z3]; \\
& & & CVC4; 4Simp; SONOLAR; Yices2; \\
& & & abziz\_min\_features; abziz\_all\_features. \\
QF\_IDL & 	4 & 	1315 & 	[Z3]; \win{Yices2}; CVC4; veriT. \\
QF\_LIA & 	7 & 	4381 & 	[CVC4-with-bugfix]; [MathSAT]; \\
& & & \win{SMTInterpol}; Yices2; [Z3]; veriT; CVC4. \\
QF\_LRA & 	6 & 	1343  & \win{CVC4}; Yices2; [MathSAT]; SMTInterpol; \\
& & & veriT; [Z3]. \\
QF\_NIA & 	4 & 	8327 & 	[Z3]; \win{AProVE}; CVC3; CVC4. \\
QF\_NRA & 	4 & 	10121 & [Z3]; \win{CVC3}; CVC4; raSAT. \\
QF\_RDL & 	4 & 	132 & 	\win{Yices2}; [Z3]; veriT; CVC4. \\
QF\_UF & 	7 & 	4124 & 	\win{Yices2}; veriT; CVC4; OpenSMT2; [Z3]; \\
& & & [MathSAT]; SMTInterpol. \\
QF\_UFBV & 	4 & 	31 & 	\win{Yices2}; [Z3]; [MathSAT]; CVC4. \\
QF\_UFIDL & 	4 & 	311 & 	[Z3]; \win{Yices2}; CVC4; veriT. \\
QF\_UFLIA & 	6 & 	484 & 	[Z3]; \win{Yices2}; CVC4; SMTInterpol; \\
& & & [MathSAT]; veriT. \\
QF\_UFLRA & 	6 & 	1176 & 	[Z3]; \win{Yices2}; [MathSAT]; CVC4; \\
& & & SMTInterpol; veriT. \\
QF\_UFNIA & 	3 & 	7 & 	\win{CVC4}; [Z3]; CVC3. \\
QF\_UFNRA & 	3 & 	32 & 	[Z3]; \win{CVC3}; CVC4. \\
UF & 		4 & 	2830 & 	\win{CVC4}; [Z3]; CVC3; veriT. \\
UFIDL & 	3 & 	49 & 	[Z3]; \win{CVC4}; CVC3. \\
UFLIA & 	4 & 	5766 & 	\win{CVC4}; [Z3]; veriT; CVC3. \\
UFLRA & 	4 & 	25 & 	[Z3]; \win{veriT}; CVC3; CVC4. \\
UFNIA & 	3 & 	1587 & 	[Z3]; \win{CVC4}; CVC3. \\
\hline
\end{tabular}}
\end{table}

\paragraph{Effect of timeout.}
In the main track competition, the organizers set a timeout of 40~minutes, much longer than in previous competitions (e.g., 25 minutes in 2012).  A common practical question users have is how much benefit is gained by longer timeouts. The data from the competition allows us to analyze this question somewhat.

A first question is how many additional problems are solved if the timeout is lengthened. An approximation
of an answer is shown in Fig.~\ref{Fig:timeouts}. This figure shows the number of benchmarks solved,  combined over all the solvers in the competition, with a solution time less than given timeout values, for the QF\_BV benchmark set.
Most of the benchmarks are solved quickly: 39\% in less than a second, more than half in under 3.5 seconds,
62\% by 10 seconds, and then a slow increase to 88\% by 2400 seconds. There is continual improvement for long timeouts, but the return on time invested certainly decreases.

There are two caveats to this observation. First, the results depend heavily on the character of the benchmarks set. Some logics have only easy benchmarks, some have purposefully crafted difficult benchmarks, others are a mix. The benchmarks are not a representative sampling of problems that might be encountered in practice.  Second, the results described are obtained by observing the wall-clock solution time when the timeout value is set at 2400 seconds. Solvers, if told what the timeout value is, have the option to adjust their search strategies based on the timeout; the solvers might then exhibit better behavior for shorter timeout.\footnote{Though solvers could use the timeout value, current versions of those queried\textemdash Yices2, Z3, Boolector\textemdash do not do so. However, CVC4 and CVC3 do build in the stated timeout into the script used for competition (though it is not used by the core solver) and so might show differences from the behavior stated here.}

Table~\ref{Fig:winners} shows a different view of the same data. Here we note the number of problems solved by each solver within a given wall-clock solution time, subject to the same caveats. The point to observe is that the winning solver changes depending on the timeout chosen. For these benchmarks and this set of solvers Yices2 performs best for timeouts under a second, CVC4 does best in the middle range from 1 to 200 seconds, and Boolector does best above 400 seconds. Other logics, but not all, show changes in winning order as well. This phenomenon could be a result of differences in engineering of the individual solvers or it could be a result of characteristics of the benchmark set.

\begin{figure}
\begin{center}
\includegraphics[width=.95\textwidth]{QF_BV-timeout-logscale.pdf}
\end{center}
\caption{Solver success for QF\_BV benchmarks over time.}
\label{Fig:timeouts}
\end{figure}

\begin{table}
\caption{Solver success per individual solver for 2488 QF\_BV benchmarks, for different timeouts (in seconds).}
\label{Fig:winners}
\centering
\input{QF_BV-winners.tex}
\end{table}

\subsection{Application (incremental) track results}
\label{sec:application-results}

Most solvers are only concerned with raw performance on single benchmarks. However, an important application area for SMT solvers requires what the SMT-LIB standard calls `incremental' operation.
In this mode, a user or some application interacts with the solver repeatedly, issuing various commands to define a problem, check for satisfiability, inspect resulting counterexample models, adjust the problem by retracting some assertions and adding other assertions, and so on. An example use case is a tool that allows a user to author formal specifications in conjunction with software. The tool would
check using a back-end SMT solver whether the specifications are consistent with the code. If not, it might
supply a counterexample that could be inspected in conjunction with the source code. As the user edits the source or the specifications, the problem presented to the SMT solver is modified.

The application track of the competition presents to the solver a series of SMT-LIB commands through a driver program; the solver replies to the driver with a
response to each command. The driver presents commands only one at a time to emulate a realistic environment and so that the solver cannot ``work ahead.'' The driver also measures the accumulated time taken for each response. Note that the time measured includes the response time to every command, not just to the satisfiability-checking commands; while \lstinline{check-sat} commands might be the most time-consuming, \lstinline{assert} commands, and others, might also instigate significant processing. The benchmark text contains \lstinline{(set-info :status ...)} commands that
indicate the expected result for subsequent \lstinline{check-sat} commands; status information is used only by the driver program and not passed on to the solver. Such \lstinline{set-info} command might indicate a status of \lstinline{unknown}; in that case, the driver
considers the benchmark to end after the \emph{previous} \lstinline{check-sat} command for competition purposes.

The application track was first introduced in 2011; a report on that year's application track and the overall design was presented by Griggio and Bruttomesso at the 2012 COMPARE Workshop~\cite{ag+rb+12}. A significantly adapted driver was implemented by the organizers for 2014 on the StarExec framework.

In 2014, the SMT-LIB contains 9,926 benchmarks that  specifically  exercise the incremental solving capability of solvers. Table \ref{Fig:apptrack-benchmarks} lists the numbers of benchmarks in various logics; UFLRA, QF\_UFLRA, and QF\_UFLIA are the only logics with significant numbers of benchmarks. All the benchmarks were used in the competition.

Four solvers participated in this competition track: CVC3, CVC4, SMTInterpol, and Yices2; Z3 was added as a demonstration-only historical comparison. The track was run for 8 divisions; the results are shown in Table \ref{Fig:apptrack-results}. Within each division, solvers are listed in winning order: Yices2 won six of the eight divisions, all of the ones in which it participated. The winner is the solver that solved the most \lstinline{check-sat} commands correctly within the timeout period. No solver produced an erroneous result. The time out (40 minutes) is applied to the entire benchmark, not to individual commands. Since the previous execution of the application track was in 2012 and not on StarExec, we did not attempt a comparison with previous results.

\begin{table}
\caption{Numbers of application benchmarks and distribution of \lstinline{check-sat} commands for different logics.}
\label{Fig:apptrack-benchmarks}
\centering
\begin{tabular}{|l|r|rrrr|}
\multicolumn{6}{c}{\textbf{All benchmarks}} \\
\hline
&  & \multicolumn{4}{c|}{{\small\bfseries\sffamily check--sat} commands} \\
 Logic & Benchmarks & total & min & max & avg. \\
\hline
AUFNIRA & 165  & 3452 & 2 & 615 & 20.9 \\
QF\_AUFLIA & 72 & 4699864 & 5 & 1109912 & 65275.9 \\
QF\_BV & 18 & 2727 & 101 & 202 & 151.5 \\
QF\_LIA & 65 & 19690826 & 101 & 2630828 & 302935.8 \\
QF\_LRA & 10 & 1515 & 101 & 202 & 151.5 \\
QF\_UFLIA & 905 & 790630 & 1 & 474174 & 873.6 \\
QF\_UFLRA & 3333 & 22103 & 2 & 3384 & 6.6 \\
UFLRA & 5358 & 3514613 & 2 & 40758 & 656.0 \\
\hline
\multicolumn{6}{c}{}\\
\multicolumn{6}{c}{\textbf{Eligible benchmarks}} \\
\hline
&  & \multicolumn{4}{c|}{{\small\bfseries\sffamily check--sat} commands} \\
 Logic & Benchmarks & total & min & max & avg. \\
\hline
AUFNIRA & 165  & 0 & 0 & 0 & 0 \\
QF\_AUFLIA & 72 & 4699864 & 5 & 1109912 & 65275.9 \\
QF\_BV & 18 & 2141 & 52 & 202 & 118.9 \\
QF\_LIA & 65 & 19689957 & 30 & 2630828 & 302922.4 \\
QF\_LRA & 10 & 795 & 45 & 107 & 79.5 \\
QF\_UFLIA & 905 & 766079 & 1 & 474174 & 846.5 \\
QF\_UFLRA & 3333 & 22066 & 0 & 3384 & 6.6 \\
UFLRA & 5358 & 223820 & 2 & 201 & 41.8 \\
\hline
\end{tabular}
\end{table}

\begin{table}
\caption{Results of the incremental track, across eight divisions. In each division, solvers are listed in winning order.}
\label{Fig:apptrack-results}
\vspace{-\medskipamount}
\centering
\resizebox{!}{294pt}{\input{apptrack-results.tex}}
\end{table}

\section{FLoC Olympic Games}
\label{sec:floc}

The main track and the application track described in previous sections are staples of recent SMT Competitions. The 2014 edition was unique in also being associated with the FLoC Olympic Games~\cite{FLoCGames}.
This association was positive in providing a platform, along with the other competitions, to present the
rationale, methodology and results of the SMT Competition to a wider audience than just the SMT community.

One additional aspect that resulted from the Olympic Games was the awarding of three medals to the three ``winners'' of the competition. Since SMT-COMP is organized into many separate divisions, with winners determined in each division independently, the organizers had to determine how to award three global prizes.
The metrics for doing so were the subject of significant discussion both before and after the competition.
The metrics were decided by the organizers before the competition began (and before the deadline for solver registration) and were maintained unchanged after the competition.

The organizers chose to award the bronze medal for the best performance in a single division. We chose  the QF\_BV division for this medal because it is significant to applications and because it traditionally received the most solver submissions. Indeed in 2014, there were 8 participants. Determining the winner was straightforward: we used the same metric as is used for each division\textemdash the most problems solved without errors, with ties broken by speed of solution. The Boolector~\cite{boolector} solver won this division and the bronze medal. The results for all participating solvers are shown in Table \ref{Table:bronze}.

The organizers chose to award the silver and gold medals for best performance across the most divisions. Thus we needed a metric that combined the results across divisions. We considered two metrics. For a given solver, let
\begin{itemize}[noitemsep,nolistsep]
\item $e_i$ be the number of benchmarks in division $i$ for which an incorrect result was produced
\item $c_i$ be the number of benchmarks in division $i$ solved correctly
\item $t_i$ be the total time to solve the benchmarks in division $i$ that were solved correctly
\item $N_i$ be the total number of benchmarks in division $i$, used in the competition.
\end{itemize}
The normal metric for a division is that the winning solver is the one with the
smallest value of $e_i$, the largest value of $c_i$
and then the smallest value of $t_i$, for each division taken separately;
that is, the metric is a lexicographic ordering by smallest value of $\langle e_i, -c_i, t_i \rangle$.
The two global metrics we considered are
\begin{itemize}[noitemsep,nolistsep]
\item Metric A: The winning solver is the one with the smallest value of $\sum_i e_i \log N_i$, then the largest value of $\sum_i (c_i/N_i) \log N_i$, then the smallest value of $\sum_i t_i \log N_i$, where for a given solver the sums are over all competitive divisions in which that solver participated.
\item Metric B: The winning solver is the one with the largest value of $\sum_i (e_i == 0\,?\,(c_i/N_i) : - e_i ) \log N_i$, then the smallest value of $\sum_i t_i \log N_i$, where for a given solver the sums are over all competitive divisions in which that solver participated.
\end{itemize}
Note that incorrect results are very rare, but do occur; for almost all solvers and divisions the value of $e_i$ is 0 and the competition hinges on the values of $c_i$. The speed of the solver is important in two ways. First, if the solver is slow, it will time out before a solution is found and thus the value of $c_i$ will be lower. Second, if there is a tie in the number of errors and correctly solved problems, the total time taken on the correctly solved problems is used as the tie-breaker; this is a rare occurrence but does happen if, for example, all the benchmark problems in a division are solvable within the time limit.

Only \emph{competitive divisions} were included in the scoring. For determining medals, a division is competitive if there are at least two officially registered, participating solvers \emph{from different teams}. This prevents a team from gaming the scoring by submitting multiple solvers to divisions in which no one else is participating. This criterion excluded a number of divisions from medal scoring: AUFNIRA, BV, NIA, NRA, QF\_UFNIA, QF\_UFNRA, UFBV, UFIDL, UFNIA.

The log scaling of the scores for each division is a somewhat arbitrary means to adjust the scores for the wide variety of numbers of benchmarks. It seemed a reasonable compromise between linearly combining numbers of benchmarks, which would have overweighted large divisions (in the organizers' view), and simply summing the fraction of benchmarks solved correctly, which would have overweighted small divisions.

These two metrics differ in how errors are treated. If a solver has no errors, it is always better off to participate in as many divisions as possible. However, an error in a division penalizes a solver so that it would be better not to have participated in the division; hence the organizers ruled that once the competition had started, a solver could not be withdrawn from a division in which it was registered.

The penalty for an error is globally significant in Metric A: a single error in one division out of many would put the solver behind any other solver with no errors, even if that other solver participated in just one division. The penalty for an error is more local for Metric~B: the error results in a large negative score for that division, which might be compensated by good performance in other divisions. Both metrics satisfy the criterion of putting heavy weight on correctness of solvers.
The organizers published the choice of Metric A as the metric for the Olympic Games gold and silver medals in the rules prior to the beginning of the competition, with no objection during the comment period.

Though all solvers were scored for the medal metrics, five solvers participated in more than two divisions and were the most competitive during the course of the competition. The final results are shown in Table \ref{Table:medals}. The choice of metric did have a significant effect on the result. CVC4 and Yices2 participated in the most divisions, solved the most problems, and did so the most efficiently. However, Yices2 had a crash on one problem in QF\_ABV, but had emitted an erroneous answer prior to the crash (a simple crash without an answer is scored the same as an `unknown' response, marked neither wrong nor correct). CVC4 had bugs that affected AUFNIRA, which was not a competitive division, and QF\_LIA,
which was competitive. Consequently, by the competition metric, these two otherwise leading solvers placed much further back in the pack.

When the results were published, the resulting winning teams, veriT and SMTInterpol, put an appeal to the organizers to use Metric B instead, arguing that (i)~CVC4 and Yices2 were clearly the more capable solvers and (ii)~there were known bugs in the winning solvers as well, which, simply by good fortune, were not triggered by the competition benchmarks. However, after public comment acknowledging the good will of the winners, the appeal was not accepted by the organizers. The medal ceremony did highlight the differing contributions of all four teams as well as those of the bronze medal winner. Note that the discovered bugs were promptly fixed. In fact, CVC4 submitted an additional demonstration-only version, named CVC4-with-bugfix in the result tables, which the organizers ran in conjunction with the rest of the competition.

\begin{table}
\caption{Gold and silver medal competition, in winning order by Metric A. By Metric B the order is the same except that CVC4 and Yices2 are in first and second place.}
\label{Table:medals}
\centering
\begin{tabular}{|l|r|rr|r|}
\hline
Solver  & Competitive & Metric A & & Metric B \\
 & Divisions & Weighted errors & Weighted solved & \\
\hline
veriT & 17 &	0.000 	& 	25.325 & 25.325 \\
SMTInterpol & 8 &	0.000 	& 	22.831 & 22.831 \\
CVC3 & 10	& 	0.000 	& 	9.618 & 9.618 \\
SONOLAR 	& 2	&  	0.000 	& 	5.978 & 	5.978\\
AProVE 		& 1 & 	0.000 	& 	3.776	& 	3.776\\
Boolector-j & 1	&  	0.000 	& 	3.758	& 	3.758\\
Boolector-d & 1		&  	0.000 	& 	3.755 & 	3.755\\
OpenSMT2 	& 1	&  	0.000 &	3.582 &	3.582\\
Boolector & 1		&  	0.000 &	3.058  &	3.058 \\
STP-CryptoMiniSat4 	& 1	&  	0.000 &	2.859 &	2.859\\
4Simp 	& 1	& 	0.000 	& 	2.468  	& 	2.468 \\
raSAT 	& 1	& 	0.000 	& 	0.000 	& 	0.000 \\
Yices2 	& 15	&  	3.810 	& 	38.624 & 31.059 \\
CVC4 		& 25 &  	7.283 	& 	54.152 & 43.509 \\
abziz\_min\_features 	& 1	& 	30.563 	& 	2.548 & -30.563 \\
abziz\_all\_features 	& 1	&  	30.563 	& 	2.403 & -30.563 \\
Kleaver-STP 	& 1	&  	213.362 	& 	3.103 & -213.362 \\
Kleaver-portfolio & 1		&  	346.713 	& 	3.073  & -346.713 \\
\hline
\end{tabular}
\end{table}

\begin{table}
\caption{Bronze medal competition (QF\_BV division, 2488 benchmarks), in winning order.}
\label{Table:bronze}
\centering
\begin{tabular}{|l|rrr|}
\hline
 Solver & Errors & Solved & Time (sec)\\
\hline
Boolector &	0  &		2361  &		138077.59 \\
STP-CryptoMiniSat4 & 0  &		2283  &		190660.82 	\\
{[}CVC4-with-bugfix] &	0  &		2237 	 &		139205.24 \\
{[}MathSAT]  &	0  &		2199 	 &		262349.39 \\
{[}Z3]  & 	0  &		2180 	 &		214087.66 	\\
CVC4  &	0  &		2166 	 &		87954.62 	\\
4Simp &	0 &	2121 	 &		187966.86 \\
SONOLAR &	0  &		2026  &	 	174134.49 \\
Yices2 &	0  &		1770  &	 	159991.55 \\
abziz\_min\_features &	9  &		2155 	 &	 	134385.22 \\
abziz\_all\_features &	9  &		2093 	 &	 	122540.04 \\
\hline
\end{tabular}
\end{table}

\section{Post-Competition Activity}
\label{sec:post}

After the competition, David Cok (competition chair) and Clark Barrett and Morgan Deters (SMT-LIB coordinators) collaborated, with the assistance of Aaron Stump (StarExec lead), in attempting to discover the status of the SMT-LIB benchmarks that were marked as unknown. For this computation, the timeout was set to 10 hours. This activity required several weeks of computation. A result confirmed by at least two solvers was obtained for 75\% of the unknown benchmarks, with another 4\% having a tentative result from just one solver.
The results are shown in Table~\ref{Fig:post}.

The unknown incremental benchmarks have yet to be resolved.

\begin{table}
\caption{Benchmarks resolved in post-competition computation}
\label{Fig:post}
\centering
\begin{tabular}{|l|c|r|rr|rr|r|}
\hline
Logic & Solvers & Benchmarks & \multicolumn{2}{c|}{\pbox{1.1in}{Resolved by\\2+ solvers as}} & \multicolumn{2}{c|}{\pbox{1.1in}{Resolved by \\ 1 solver as}} & \pbox{.6in}{Still\\unknown} \\
 & & & sat & unsat & sat & unsat & \\
\hline
QF\_BV & 4 & 28138 & 8838 & 19166 & 20 & 10 & 100 \\
AUFNIRA & 2 & 468 & 0 & 23 & 0 & 23 & 422 \\
AUFLIRA & 2 & 168 & 0 & 3 & 0 & 3 & 162 \\
BV & 2 & 191 & 29 & 56 & 42 & 37 & 27 \\
LRA & 2 & 450 & 20 & 148 & 241 & 23 & 18 \\
NRA & 2 & 66 & 0 & 41 & 0 & 16 & 9 \\
QF\_ABV & 4 & 4190 & 3629 & 373 & 0 & 1 & 187 \\
QF\_UF & 3 & 4 & 0 & 3 & 0 & 1 & 0 \\
UFBV & 2 & 191 & 17 & 49 & 51 & 44 & 30 \\
UFIDL & 2 & 12 & 0 & 0 & 0 & 0 & 12 \\
QF\_RDL & 2 & 85 & 50 & 0 & 2 & 1 & 32 \\
QF\_UFLRA & 3 & 87 & 82 & 2 & 2 & 0 & 1 \\
QF\_UFNRA & 2 & 11 & 0 & 2 & 7 & 0 & 2 \\
UF & 2 & 2911 & 0 & 2 & 51 & 50 & 2808 \\
QF\_IDL & 3 & 537 & 324 & 118 & 20 & 14 & 61 \\
QF\_LRA & 2 & 208 & 127 & 25 & 44 & 8 & 4 \\
QF\_LIA & 3 & 1279 & 743 & 230 & 234 & 4 & 68 \\
QF\_NIA & 3 & 927 & 2 & 0 & 39 & 246 & 640 \\
QF\_NRA & 2 & 1392 & 0 & 36 & 283 & 168 & 905 \\
UFLIA & 2 & 5499 & 0 & 1765 & 4 & 113 & 3617 \\
UFNIA & 2 & 1052 & 0 & 20 & 2 & 90 & 940 \\
\hline
Total & & 47866 & 13861 & 22062 & 1042 & 852 & 10045 \\
\hline
\end{tabular}
\end{table}

\section{Concluding Observations and Recommendations}
\label{sec:conclusions}

SMT-COMP 2014 successfully executed the comparison among solvers that is the main goal
of the competition. The new computational infrastructure, StarExec, worked very well for the purpose. The competition saw a renewed interest in participation\textemdash there were record numbers of teams participating, solvers entered, teams and solvers that had never before participated, benchmarks used, and amount of computation performed. Although the 2014 results are not usefully comparable to previous years, the detailed performance of each solver on each benchmark from this first year using StarExec will be a solid baseline to measure improvements in the state-of-the-art of solver performance in future years.

This year's competition also saw the inauguration of a new, sibling competition. The organizers helped start and execute SL-COMP~\cite{SLCOMP}, a competition among solvers for separation logic.

The SMT steering committee is proposing that SMT-COMP 2015 will be held in association with the SMT Workshop, which itself will be affiliated with CAV 2015 in San Franciso, CA, USA from July 18-24, 2015.
The SMT Workshop is being organized by
Vijay Ganesh and
Dejan Jovanovi\'c; the organizers of the competition are Tjark Weber, David D\'eharbe, and Sylvain Conchon.

Based on the experience of 2014, the 2014 organizers have the following recommendations or topics for consideration for future competitions.
\begin{itemize}
\item The 2014 competition used all available benchmarks; though the computation resources enable using all benchmarks, future competitions should consider how to make a principled selection to avoid over-representing benchmarks of particular types or origin.
\item The competition has used numbers of solved benchmarks as the primary success criterion. Time to solve benchmarks should be considered more strongly. In particular, a separate track that emphasizes fast solution of fairly simple problems might be informative.
\item Related to the previous point, currently if a solver times-out or issues a response of `unknown', the time taken to do so is not counted in the accumulated time. Only the time taken to compute correct responses is counted towards the evaluation metric.
A user's experience, however, is that the time taken for a solver to say ``I don't know'' is just as important as time to produce a useful answer. Thus we recommend that such
computation time be included in the evaluation metric. Omitting this time has had no effect so far because time was little used in the overall metric.
\item A key improvement needed is better benchmark sets. Though the accumulation of benchmark problems since the inception of the competition is impressive, attention now needs to be paid to the quality and distribution of benchmarks. Some divisions are represented by only a few benchmarks; others have large numbers of similar benchmarks.
Benchmarks representative of application scenarios are particularly important.
\item Subsequent to SMT-COMP 2014, David Cok, Aaron Stump, Morgan Deters, and Clark Barrett collaborated in resolving the status of many previously unknown benchmarks. Those new expected results are not yet included in the SMT-LIB benchmarks on StarExec. They should be incorporated into SMT-LIB on StarExec prior to the next competition.
\item If a global metric is needed again in the future (per \S\ref{sec:floc}), a review and re-discussion of the appropriate metric should be instigated.
\item Solvers with breadth of application across many logics and solvers that address problems in new logics such as string and floating point computations are important to users. Future competitions should add tracks or otherwise find means to reward solvers that implement such capabilities.
\item Various competition tracks used in the past should be rejuvenated: parallel processing, computation of unsat cores, production of proofs, computation of symbolic models, and computation of concrete counterexamples.
\item One missing tool is a standard SMT-LIB syntax checker. jSMTLIB~\cite{cok2011jsmtlib} has been proposed for this purpose, but is not yet integrated into StarExec. The tool also needs to be updated to include the proposed new SMT-LIB features.
\item The difficulty in preparing a new solver for submission to StarExec for participation in SMT-COMP should be reduced.
\item Resolve the definition of divide-by-zero behavior in SMT-LIB.
\item An item for study is the effect of benchmark scrambling on the outcome of solver comparisons.
\item Clearly define the subset of SMT-LIB~v2 that solvers must support for a competition and that benchmarks must use.
\end{itemize}

\section*{Acknowledgments}

\begin{itemize}
\item The organizers were supported by their respective institutions (GrammaTech, Federal University of Rio Grande do Norte, Brazil and Uppsala University, Sweden respectively).

\item In addition Cok received partial support from the U.S.\ National Science Foundation
under grant ACI-1314674.

\item Clark Barrett and Morgan Deters assisted with some aspects of benchmark preparation,
in their roles as SMT-LIB coordinators.

\item Aaron Stump and the StarExec support team were essential in keeping the competition cluster running;
in this first large-scale, public use of the cluster, numerous small details needed correction and were corrected promptly.
%
The StarExec cluster is supported by
U.S.\ National Science Foundation under grants \#1058748 and \#1058925.
%
\item The cost of executing the SMT Competition is underwritten by the SMT Workshop.
\end{itemize}

Any opinions,
findings, and conclusions or recommendations expressed in this
material are those of the authors and do not necessarily reflect the
views of the National Science Foundation.

\bibliographystyle{plainbv}
\bibliography{SMTCOMP}

\end{document}

\thebibliography

### 2015-02-17 rules/rules15.tex
First draft of 2015 rules added.

--- 2014-05-19 rules/rules14.tex
@@
 \documentclass[12pt]{article}
+
+\usepackage{color}
 \usepackage{times}
 \usepackage{fullpage}
-\usepackage{url}
-\usepackage{epsf}
+\usepackage{hyperref}
+
+\usepackage{draftwatermark}
 
 \newcommand{\akey}[1]{\textbf{#1}}
+
+\newcommand{\remark}[1]{{\small\textcolor{red}{[#1]}}}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-\title{DRAFT\\Satisfiability Modulo Theories Competition (SMT-COMP) 2014: Rules and 
-Procedures}
+\title{10th International Satisfiability Modulo Theories Competition
+  (SMT-COMP 2015): Rules and Procedures}
 
@@
 
-\author{
-David R. Cok \\
-GrammaTech, Inc. \\
-Ithaca, NY (USA) \\
-cok@frontiernet.net \\
+\author{%
+Sylvain Conchon \\
+Paris-Sud University \\
+France \\
+{\small\href{mailto:Sylvain.Conchon@lri.fr}{\tt Sylvain.Conchon@lri.fr}} \\
 \and
-David Deharbe \\
+David D{\'e}harbe \\
 Federal University of Rio Grande do Norte \\
 Brazil \\
-David.Deharbe@loria.fr \\
+{\small\href{mailto:David.Deharbe@loria.fr}{\tt David.Deharbe@loria.fr}} \\
 \and
@@
 Sweden \\
-tjark.weber@it.uu.se \\ 
+{\small\href{mailto:tjark.weber@it.uu.se}{\tt tjark.weber@it.uu.se}} \\
+\\
 }
@@
 
-\def\eg{\textit{e.g.}}
-\def\ie{\textit{i.e.}}
+\noindent Comments on this document should be emailed to the SMT-COMP
+mailing list (see below) or, if necessary, directly to the organizers.
 
-\noindent Comments on this document should be emailed to the smtcomp mailing
-list or, if necessary, directly to the organizers (cf. email addresses in the following section and in the authors' affiliation information).
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-\section{Important dates and information}
+\section{Communication}
+\label{sec:communication}
+
+Interested parties should subscribe to the SMT-COMP mailing list.
+Important late-breaking news and any necessary clarifications and
+edits to these rules will be announced there, and it is the primary
+way that such announcements will be communicated.
+
 \begin{itemize}
-\item May 15 - deadline for new benchmarks
-\item May 25 - deadline for solver entrants
-\item June 1 - deadline for final versions of solvers (but no new entrants after May 25).
-\item July 17 - SMT workshop; completion of competition.
-\item SMT-COMP mailing list: smt-comp@cs.nyu.edu
-\item signup site for mailing list: \url{cs.nyu.edu/mailman/listinfo/smt-comp}
-\item competition web site: \url{www.smtcomp.org}  or \url{smtcomp.sourceforge.net/2014}
+\item SMT-COMP mailing list: \href{mailto:smt-comp@cs.nyu.edu}{\tt
+  smt-comp@cs.nyu.edu}
+\item Sign-up site for the mailing list:
+  \url{cs.nyu.edu/mailman/listinfo/smt-comp}
 \end{itemize}
+
+\noindent Additional material will be made available at the
+competition web site, \url{www.smtcomp.org} or
+\url{smtcomp.sourceforge.net/2015}.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\newpage
+
+\section{Important Dates}
+\label{sec:important}
+
+\begin{description}
+\item[May~1] Deadline for new benchmark contributions.
+\item[June~1] Deadline for first versions of solvers (for all tracks),
+  including information about which tracks and divisions are being
+  entered, and magic numbers for benchmark scrambling.
+\item[June~7] Final versions of competition tools (e.g., benchmark
+  scrambler) are made available.  Benchmark libraries are frozen.
+\item[June~14] Deadline for final versions of solvers, including
+  system descriptions.
+\item[June~15] Opening value of NYSE Composite Index used to complete
+  random seed for benchmark scrambling.
+\item[July~18/19] SMT Workshop; end of competition, presentation of
+  results.
+\end{description}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 propositional reasoning tools, respectively, have spurred significant
-innovation in their fields~\cite{PSS02,leberre+03}.  More information
+innovation in their fields~\cite{leberre+03,PSS02}.  More information
 on the history and motivation for SMT-COMP can be found at the
-SMT-COMP web site, \url{www.smtcomp.org}, and in reports on previous
-competitions~(\cite{SMTCOMP-2008,BDOS08,SMTCOMP-FMSD,SMTCOMP-JAR,SMTCOMP2012,SMTEVAL2013}).
-SMT-COMP 2014 is affiliated with the SMT workshop (\url {http://smt2014.it.uu.se/}) at the co-located meetings of CAV, IJCAR, and SAT at FLoC 2014 (\url{http://vsl2014.at/}); the competition is part of the
-FLoC Olympic Games (\url{http://vsl2014.at/olympics/}).
+competition web site, \url{www.smtcomp.org}, and in reports on
+previous
+competitions~(\cite{SMTCOMP2012,SMTEVAL2013,SMTCOMP-JAR,SMTCOMP-FMSD,SMTCOMP-2008,BDOS08}).
 
-Accordingly, researchers are highly encouraged to submit both new benchmarks
-and new or improved solvers to raise the level of competition and advance
-the state-of-the-art in automated SMT problem solving.
+SMT-COMP~2015 is affiliated with the SMT Workshop~2015
+(\url{http://smt2015.csl.sri.com/}), which is associated with CAV~2015
+(\url{http://i-cav.org/2015/}).  The SMT Workshop and the main CAV
+conference will include a block of time to present the competitors and
+results of the competition.
 
-SMT-COMP 2014 will have two tracks: the conventional main track and a repeat of 2012's application track.
-Within a track there are multiple divisions, where each division
-uses benchmarks from a specific SMT-LIB logic (or group of logics).
+Accordingly, researchers are highly encouraged to submit both new
+benchmarks and new or improved solvers to raise the level of
+competition and advance the state-of-the-art in automated SMT problem
+solving.
+
+SMT-COMP 2015 will have two tracks: the conventional main track and an
+application (i.e., incremental) track.  Within each track there are
+multiple divisions, where each division uses benchmarks from a
+specific SMT-LIB logic (or group of logics). \remark{Additional
+  tracks, e.g., for unsat-core extraction or proof generation, are
+  currently being considered.}  We will recognize winners as measured
+by number of benchmarks solved; we will also recognize solvers based
+on additional criteria.
 
 The rest of this document, revised from the previous
-version,\footnote{Earlier versions of this document include contributions from
-Clark Barrett, Albert Oliveras, Aaron Stump, Morgan Deters, David Cok, Alberto Griggio, and Roberto Bruttomesso.}
-describes the rules and competition procedures for SMT-COMP~2014.
-The principal changes from the previous competition rules are the following:
+version,\footnote{Earlier versions of this document include
+  contributions from Clark Barrett, Roberto Bruttomesso, David Cok,
+  David D{\'e}harbe, Morgan Deters, Alberto Griggio, Albert Oliveras,
+  Aaron Stump, and Tjark Weber.}  describes the rules and competition
+procedures for SMT-COMP~2015.  The principal changes from the previous
+competition rules are the following:
 \begin{itemize}
-\item The competition will be run with StarExec (\url{www.starexec.org}). Accordingly we are simplifying the competition somewhat, since some of the infrastructure needs to be recreated.
-\item We will hold just a main and application track.
-[ The demonstration unsat core, and proof generation tracks will be deferred until benchmarks and result analysis tools are reorganized.] We encourage submission of solvers and benchmarks for both tracks.
-\item In the main track, we will measure comparative performance within all divisions to which at least two solvers are submitted.
-We will use the data to determine both sequential and parallel winners.
-
-\item We will recognize winners as measured by number of benchmarks solved; we will also recognize best open source contributions and best new entrants, as described below. 
-Also, importantly, the FLoC Olympic Games is sponsoring award ceremonies (with actual medals). A selection of the SMT-COMP winners (as described below) will be awarded FLoC Olympic Games medals.
-
+\item All solvers will be run with $n=4$ cores available, and the CPU
+  timeout will be $n$~times the wall-clock timeout.  We will recognize
+  both best sequential and best parallel performance in all divisions.
+\item In addition to recognizing the best solver in each division, we
+  will recognize the three solvers that perform best according to
+  competition-wide criteria, emphasizing breadth of supported logics.
+  These criteria will be a refinement of the criteria used for the
+  FLoC Olympic Games medals in~2014.
+\item \remark{Pending availability of suitable benchmarks and solvers,
+  we may include a new division for floating-point arithmetic.  This
+  should be considered experimental in 2015, and will not be included
+  in the competition-wide ranking.}
+\item \remark{Benchmark selection and relative weight of benchmark
+  families are under review.}
 \end{itemize}
 
-All results of the competition will be made public. However, 
-winners will be declared only for divisions in which at least two solvers are submitted.
-Although the organizers may add other solvers for comparison purposes, only solvers that
-are explicitly submitted by their authors are eligible to be designated as winners.
-
-It is important for competitors to track discussions on the SMT-COMP mailing
-list, as clarifications and any updates to these rules will be posted there.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-\header{Solver format.} %
-An entrant to SMT-COMP is an SMT solver
-submitted by its authors using the Star-Exec (\url{http://www.starexec.org}) service.  
-The execution service enables members of the
-SMT research community to run solvers on jobs consisting of benchmarks
-from the SMT-LIB benchmark library.  Jobs are run on a shared computer
-cluster.  The execution service is provided free of
-charge, but it does require registration to create a login account.  Registered users
-may then upload their own solvers to run, or may run public solvers
-already uploaded to the service.
+\header{Solver submission.}
+%
+An entrant to SMT-COMP is an SMT solver submitted by its authors using
+the StarExec (\url{http://www.starexec.org}) service.  The execution
+service enables members of the SMT research community to run solvers
+on jobs consisting of benchmarks from the SMT-LIB benchmark library.
+Jobs are run on a shared computer cluster.  The execution service is
+provided free of charge, but it does require registration to create a
+login account.  Registered users may then upload their own solvers to
+run, or may run public solvers already uploaded to the service.
 
-For participation in SMT-COMP, a solver must be
-uploaded to Star-Exec, made publicly available, and the organizers informed of its presence {\em and the logic divisions in which it is participating}.
-A submission must also include a 32-bit unsigned
-integer.  These numbers, collected from all submissions, are used
-to seed the pseudo-random benchmark selection algorithm, as well
-as the benchmark scrambler.
+For participation in SMT-COMP, a solver must be uploaded to StarExec,
+made publicly available, and the organizers informed of its presence
+{\em and the tracks and divisions in which it is
+  participating}. StarExec supports solver configurations; for
+clarity, each submitted solver must have one configuration only.  A
+submission must also include a 32-bit unsigned integer.  These
+numbers, collected from all submissions, are used to seed the
+pseudo-random benchmark selection algorithm, as well as the benchmark
+scrambler.
 
-Information about how to configure and upload a solver is contained in the StarExec user guide on its wiki:
+Information about how to configure and upload a solver is contained in
+the StarExec user guide,
 \url{https://wiki.uiowa.edu/display/stardev/User+Guide}.
 
-\header{System description.} %
-As part of a submission,
-SMT-COMP entrants are encouraged to provide a short (1--2 pages) description of
-the system.  This should include a list of all authors of the system,
- their present institutional affiliations, and any appropriate acknowledgements.  The programming
+\header{System description.}
+%
+As part of a submission, SMT-COMP entrants are encouraged to provide a
+short (1--2 pages) description of the system.  This should include a
+list of all authors of the system, their present institutional
+affiliations, and any appropriate acknowledgements.  The programming
 language(s) and basic SMT solving approach employed should be
-described (\eg, lazy integration of a Nelson-Oppen combination with
+described (e.g., lazy integration of a Nelson-Oppen combination with
 SAT, translation to SAT, etc.).  System descriptions are encouraged to
-include a URL for a web site for the submitted tool.
-System descriptions may be submitted after the solver deadline, but to be useful should be sent to the organizers before the competition ends (July 16).
+include a URL for a web site for the submitted tool.  System
+descriptions may be submitted after the solver deadline, but to be
+useful should be sent to the organizers before the competition ends.
 
-\header{Other systems.} %
-The organizers' intent is to promote as wide a comparison among solver options as possible.
-However, if the number of solver submissions is too large for the
-computational resources available to the competition, the organizers reserve the right not to
-accept multiple versions of solvers from the same solver team.  The organizers also reserve the right to
-include other systems of interest (such as entrants in previous competitions) in the
+\header{Other systems.}
+%
+The organizers' intent is to promote as wide a comparison among
+solvers and solver options as possible.  However, if the number of
+solver submissions is too large for the computational resources
+available to the competition, the organizers reserve the right not to
+accept multiple versions of solvers from the same solver team.  The
+organizers also reserve the right to include other systems of interest
+(such as entrants in previous competitions) in the competition.
+
+\header{Wrapper tools.}
+%
+A \emph{wrapper tool} is defined as any tool which calls one or more
+SMT solvers not written by the author of the wrapper tool.  The other
+solvers are called the \emph{wrapped} tools.  A wrapper tool must
+explicitly acknowledge any tools that it wraps.  Its system
+description should make clear the technical innovations by which the
+wrapper tool expects to improve on the wrapped tools.
+
+\header{Attendance.}
+%
+Submitters of an SMT-COMP entrant need not be physically present at
+the competition to participate or win.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection*{Deadlines}
+
+SMT-COMP entrants must be submitted via StarExec (solvers) \emph{and}
+email to the organizers (accompanying information) until the end of
+{\bf June~1, 2015} anywhere on earth.  After this date no new entrants
+will be accepted.  However, updates to existing entrants on StarExec
+will be accepted until the end of {\bf June~14, 2015} anywhere on
+earth.
+
+We strongly encourage participants to use this grace period
+\emph{only} for the purpose of fixing any bugs that may be discovered,
+and not for adding new features, as there may be no opportunity to do
+extensive testing using StarExec after the initial deadline.
+
+The solver versions that are present on StarExec at the conclusion of
+the grace period will be the ones used for the competition, and
+versions submitted after this time will not be used.  The organizers
+reserve the right to start the competition itself at any time after
+the open of the New York Stock Exchange on the day after the final
+solver deadline.
+
+These deadlines and procedures apply equally to all tracks of the
 competition.
 
-\header{Wrapper tools.} %
-A \emph{wrapper tool} is defined as any tool
-which calls one or more SMT solvers not written by the author of the wrapper
-tool.  The other solvers are called the \emph{wrapped} tools.  
-A wrapper tool must explicitly acknowledge any tools that it wraps.
-Its system description should make clear the technical innovations by which the
-wrapper tool expects to improve on the wrapped tools.
-
-\header{Attendance.} %
-As with previous SMT-COMPs, submitters of an SMT-COMP entrant need not 
-be physically present at the competition to
-participate or win.
-
-\subsection*{Deadlines} %
-
-%%%%%% Make main and parallel competitions together.
-
-\paragraph{Main competition track.} %
-SMT-COMP entries must be submitted via StarExec and email to the organizers by the end of June~1, 2014 (anywhere on earth).  At that time new entrants will be
-closed to the public to prepare for the competition, with the
-exception that resubmissions of existing entries will be accepted
-until the end of June~15, 2014 (anywhere on earth).  We strongly encourage
-participants to use this grace period \emph{only} for the
-purpose of fixing any bugs that may be discovered and not for adding
-new features as there will be no opportunity to do extensive testing
-using StarExec after the initial deadline.
-
-The versions that are present on the execution service at the conclusion of the
-grace period will be the ones used for the competition, and versions
-submitted after this time will not be used.  The organizers reserve
-the right to start the competition itself at any time after the open
-of the New York Stock Exchange on the day after the final solver deadline.  See
-Section~\ref{sec:timeline} below for a full timeline.
-
-\paragraph{Application track.} %
-The same deadlines and procedure for submitting to the main track will be used
-also for the application track. Submissions to both the application track and
-the main competition are independent: participants must submit explicitly to
-both events to participate in both, and they may submit different (or
-differently configured) solvers to each.  Benchmarks will be scrambled also
-for this division, using the same scrambler and seed as the main track.
-Entrants should still include a system description, as for the regular
-competition.
-
-The infrastructure for the application track is in the process of being recreated for StarExec.
-If it is not ready in time, the organizers may choose to drop this track or only run it as a demonstration track.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-Solvers will be publicly evaluated in the main and application tracks, each in several logic divisions. 
-All divisions with at least two solver entrants are competition divisions, i.e., a winner will be announced.
-The other divisions are exhibition divisions, i.e., solvers are evaluated and results posted, but no awards are announced.
+Solvers will be publicly evaluated in all tracks and divisions into
+which they have been entered.  All results of the competition will be
+made public.
 
@@
 %
-We anticipate that the bulk of the main track of the competition will take place during
-the weeks leading up to SMT 2014, from about June~16 to July~17.  Results will be
-announced at SMT 2014 and in an awards ceremony scheduled by the FLoC Olympic Games coordinator.
-  Intermediate results
+The bulk of the computation will take place during the weeks leading
+up to SMT~2015, from about June~15 to July~17.  Intermediate results
 will be regularly posted to the SMT-COMP website as the competition
@@
 
-The organizers will prioritize the running of the competition tracks, and may shift the
-time period or order of the competition or exhibition tracks in order to complete SMT-COMP
-prior to the SMT workshop and awards ceremony.
+The organizers reserve the right to prioritize certain competition
+tracks or divisions to ensure their timely completion, and in
+exceptional circumstances to complete divisions after the SMT
+Workshop.
 
-\header{Input and Output.}
+\header{Input and output.}
 %
-Participating solvers must read a single benchmark script presented as its first argument.
-Note that previous competitions presented benchmarks to a solver on its standard input
-channel, and that the application track will send command inputs to the solver's standard input.
-Accordingly, solvers are advised to support both input mechanisms. The organizers have easily adapted solvers that use only the standard input to Star-Exec with a simple wrapper script.
+In the main track, a participating solver must read a single benchmark
+script, whose name is presented as the solver's first argument.  In
+the application track, a trace executor will send commands from a
+benchmark script to the solver's standard input channel.
 
- The script is in the concrete syntax of the SMT-LIB format,
-version 2.0, though with a restricted set of commands.   A
-\textbf{benchmark script} is just a text file containing a sequence of SMTLIBv2 commands in which:
-
+The benchmark script is in the concrete syntax of the SMT-LIB format,
+version~2.0, though with a restricted set of commands.  A benchmark
+script is a text file containing a sequence of SMT-LIB~v2 commands in
+which:
+%
 \begin{enumerate}
 \item The (single) $\akey{set-logic}$ command setting the benchmark's
-logic is the first command after any $\akey{set-option}$ commands described below.
-\item In the main track, there may be a (single) \akey{set-option :print-success ...} command. Note that {\tt success} outputs are ignored by the post-processor used by the competition.
-\item Scripts for the application track will have an initial $\akey{set-option :print-success true}$ command.
-\item The script next optionally contains (any number of) $\akey{set-info}$ commands, which may be ignored by the solver.
+  logic is the first command after any $\akey{set-option}$ commands
+  described below.
+\item In the main track, there may be a (single) \akey{set-option
+  :print-success ...} command. Note that {\tt success} outputs are
+  ignored by the post-processor used by the competition; in the
+  application track, the :print-success option may not be disabled.
+\item The application track executor will send an initial
+  $\akey{set-option :print-success true}$ command to the solver.
+\item The script next optionally contains (any number of)
+  $\akey{set-info}$ commands, which may be ignored by the
+  solver. Benchmarks are expected to have the following
+  \akey{set-info} commands: \akey{(set-info :smt-lib-version 2.0)},
+  \akey{(set-info :category ...)}, \akey{(set-info :source ...)}
+  (indicating the authorship or tool that produced the benchmark), and
+  \akey{(set-info :status ...)}.
 \item The $\akey{exit}$ command is the last command.
-\item For tracks other than the application track, there is exactly one $\akey{check-sat}$ command,
-following possibly several $\akey{assert}$ commands.
-\item For the application track, there are one or more \akey{check-sat} commands, 
-  each preceded by one or more \akey{assert} commands 
-  and zero or more \akey{push 1} commands, 
-  and followed by zero or more \akey{pop 1} commands.
-
-%%%%%%%%%%%%%%%%%%% TODO: Need to define the set-info command.
+\item For tracks other than the application track, there is exactly
+  one $\akey{check-sat}$ command, following possibly several
+  $\akey{assert}$ commands.
+\item For the application track, there are one or more
+  \akey{check-sat} commands, each preceded by one or more
+  \akey{assert} commands; there may also be zero or more \akey{push 1}
+  commands, and zero or more \akey{pop 1} commands, consistent with
+  the uses of those commands in the SMT-LIB standard. Each
+  \akey{check-sat} command may be preceded by a \akey{set-info
+    :status} command that indicates the expected result of the
+  \akey{check-sat} command.
 \item The formulas in the script belong to the benchmark's logic, with
   any free symbols declared in the script.
-\item Extra symbols are declared exactly once before any
-  use, using $\akey{declare-sort}$
-  %, $\akey{define-sort}$,
-  %$\akey{declare-fun}$, or $\akey{define-fun}$.  
-  or $\akey{declare-fun}$.
-  They must be part of the allowed signature expansion for the logic.
-  Moreover, all sorts declared with a $\akey{declare-sort}$ command must have zero arity.
-
+\item All sorts declared with a $\akey{declare-sort}$ command must
+  have zero arity.
+\item Application track scripts may have $\akey{define-sort}$
+  commands.
 \item No other commands besides the ones just mentioned may be used.
 \item Named formulas are not used in benchmark scripts.
+\end{enumerate}
+%
+The SMT-LIB format specification is publicly available from the
+``Documents'' section of the SMT-LIB website~\cite{SMT-LIB}.  Solvers
+will be given formulas only from the divisions into which they have
+been entered.
 
-\end{enumerate}
+\header{Timeouts.}
+%
+Each SMT-COMP solver will be executed on a dedicated processor with
+4~cores of a competition machine for each given benchmark, up to a
+fixed time limit.  Detailed machine specifications are available on
+the competition web site.  The time limit is yet to be determined, but
+it is anticipated to be 40~minutes of wall-clock time (and 160~minutes
+of CPU time).\footnote{The time limit may be adjusted once we know the
+  number of competition entrants and eligible benchmarks.}  Solvers
+that take more than this time limit will be killed.  Solvers are
+allowed to spawn other processes; these will be killed at
+approximately the same time as the first started process.
 
-\noindent The SMT-LIB format specification is publicly
-available from the ``Documents'' section of the SMT-LIB
-website~\cite{SMT-LIB}.  Solvers will be given formulas just from the
-Problem Divisions indicated during their submission to SMT-COMP.
+The StarExec service also limits the memory consumption of the solver
+processes.  We expect the limit per solver-benchmark job-pair to be on
+the order of 60\,GB.  The values of both the timeout limit and the
+memory limit are available to a solver process through environment
+variables defined and set by the StarExec service (see the StarExec
+user guide for more information).
 
@@
 
-The main track competition will consist of selected benchmarks in each of the
-logic divisions.
-Each benchmark script will be presented to the solver as its first command-line argument.
-Each SMT-COMP entrant is then expected to attempt to report on its
-standard output channel whether the formula is satisfiable
-(``\texttt{sat}'', in lowercase, without the quotation marks) or unsatisfiable
-(``\texttt{unsat}'').  An entrant may also report ``\texttt{unknown}''
-to indicate that it cannot determine satisfiability of the formula.
+The main track competition will consist of selected benchmarks in each
+of the logic divisions.  Each benchmark script will be presented to
+the solver as its first command-line argument.  Each SMT-COMP entrant
+is then expected to attempt to report on its standard output channel
+whether the formula is satisfiable (\texttt{sat}, in lowercase) or
+unsatisfiable (\texttt{unsat}).  An entrant may also report
+\texttt{unknown} to indicate that it cannot determine satisfiability
+of the formula.
 
-The main track competition uses a StarExec postprocessor (named ``SMT2 results conserv") to accumulate the results.
+The main track competition uses a StarExec postprocessor (named ``SMT2
+results conserv") to accumulate the results.
 
-\header{Timeouts.} %
-Each SMT-COMP solver will be executed on an
-unloaded competition machine for each given benchmark, up to a fixed
-time limit.  The time limit is yet to be determined, but it is
-anticipated to be 1500 seconds (25 minutes) of CPU time and the same limit on wall clock time.\footnote{The time limit may be adjusted once we understand the resources and capabilities of the StarExec service and the number of competition solvers.}
-Solvers that take more than this
-time limit will be killed.  Solvers are allowed to spawn other
-processes.  These will be killed at approximately the same time as the
-first started process.  A
-timeout scores the same as if the output is ``\texttt{unknown}''.
+\header{Aborts and unparsable output.}
+%
+Solvers which exit before the time limit without reporting a result
+(i.e., due to exhausting memory or crashing) and do not produce output
+that includes \texttt{sat}, \texttt{unsat} or \texttt{unknown} will be
+considered to have aborted.  Also, as a further measure to prevent
+misjudgments of solvers, any \texttt{success} outputs will be
+ignored.\footnote{ Note that SMT-LIB~v2 requires that a solver produce
+  a \texttt{success} answer after each \akey{set-logic},
+  \akey{declare-sort}, \akey{declare-fun} and \akey{assert} command
+  (among others), unless the option \akey{:print-success} is set to
+  false.  Ignoring the \texttt{success} outputs therefore allows for
+  submitting fully-compliant solvers without the need of a wrapper
+  script, while still allowing entrants of previous competitions to
+  run without changes.}
 
-\header{Aborts and unparsable output.} %
-Solvers which exit before the time
-limit without reporting a result (\ie\ due to exhausting memory, crashing,
-or producing output other than \texttt{sat}, \texttt{unsat}, or
-\texttt{unknown})
-will be considered to have aborted. 
-An abort scores the same as if the output is ``\texttt{unknown}''. 
-Also, as a further measure to prevent misjudgments of solvers,
-any  ``\texttt{success}'' outputs will be 
-ignored.\footnote{
-Note that SMT-LIBv2 requires that a solver produce a ``\texttt{success}'' answer
-after each \akey{set-logic}, \akey{declare-sort}, \akey{declare-fun} and
-\akey{assert} command (among others), unless the option
-\akey{:print-success} is set to false; ignoring the
-\texttt{success} outputs therefore allows for submitting fully-compliant
-solvers without the need of a wrapper script, while still allowing entrants
-of previous competitions to run without changes.}
+\header{Persistent state.}
+%
+Solvers are allowed to create and write to files and directories
+during the course of an execution, but they are not allowed to read
+such files back during later executions.  Any files written should be
+put in the directory in which the tool is started, or in a
+subdirectory.
 
-\header{Persistent state.} %
-Solvers are allowed to create and write to
-files and directories during the course of an execution, but they are
-not allowed to read such files back during later executions.  Any
-files written should be put in the directory in which the tool is
-started, or in a subdirectory.
-
-The solver is executed with a temporary directory as the current working directory.
-Any generated files should be produced there, not, for example, in the system tmp area.
-The temporary directory and its contents are deleted after the job is complete.
+The solver is executed with a temporary directory as the current
+working directory.  Any generated files should be produced there (and
+not, say, in the system's {\tt /tmp} directory).  The StarExec system
+sets a limit on the amount of disk storage permitted---typically
+20\,GB (see the User Guide).  The temporary directory and its contents
+are deleted after the job is complete.
 
@@
 
-The application track evaluates SMT solvers when interacting
-with an external verification framework, \eg, a model
-checker. This interaction, ideally, happens by means of an online
-communication between the model checker and the solver: the model
-checker repeatedly sends queries to the SMT solver, which in turn
-answers either \texttt{sat} or \texttt{unsat}.  In this interaction an SMT-solver is
-required to accept queries incrementally via its {\em standard input channel}.
+The application track evaluates SMT solvers when interacting with an
+external verification framework, e.g., a model checker. This
+interaction, ideally, happens by means of an online communication
+between the model checker and the solver: the model checker repeatedly
+sends queries to the SMT solver, which in turn answers either
+\texttt{sat} or \texttt{unsat}.  In this interaction an SMT-solver is
+required to accept queries incrementally via its {\em standard input
+  channel}.
 
 In order to facilitate the evaluation of the solvers in this track, we
-will set up a ``simulation'' of the aforementioned interaction, as was done in 2012. In
-particular each benchmark in the application track represents a realistic
-communication trace, containing multiple \akey{check-sat} commands (possibly
-with corresponding \akey{push 1}/\akey{pop 1} commands), which
-is parsed by a {\em trace executor}. The trace executor serves the following purposes:
+will set up a ``simulation'' of the aforementioned interaction. In
+particular each benchmark in the application track represents a
+realistic communication trace, containing multiple \akey{check-sat}
+commands (possibly with corresponding \akey{push 1}/\akey{pop 1}
+commands), which is parsed by a {\em trace executor}. The trace
+executor serves the following purposes:
 \begin{itemize}
-\item it simulates the online interaction by sending single queries to the SMT solver
-      (through stdin);
-\item it prevents ``look-ahead'' behaviours of SMT solvers;
-\item it records time and answers for each call, possibly aborting the execution
-      in case of a wrong answer;
-\item it guarantees a fair execution for all solvers by abstracting from any possible
-      crash, misbehaviour, etc. that may happen on the model checker side.
+\item it simulates the online interaction by sending single queries to
+  the SMT solver (through stdin);
+\item it prevents ``look-ahead'' behaviors of SMT solvers;
+\item it records time and answers for each call, possibly aborting the
+  execution in case of a wrong answer;
+\item it guarantees a fair execution for all solvers by abstracting
+  from any possible crash, misbehavior, etc. that may happen on the
+  model checker side.
 \end{itemize}
+Note that the executor terminates processing the script upon receiving
+an incorrect response.
+
+The disk space and memory limits on the application track are the same
+as for the main track.
 
 \header{Input and Output.}
-Participating solvers will be connected to a trace executor 
-which will incrementally send commands to the standard input channel of the solver
-and read responses from the standard output channel of the solver.
-The commands will be taken from an \textbf{incremental benchmark script},
-which is an SMT-LIB 2.0 script which satisfies the rules for an application script given above.
-Note also that the trace executor will send a single 
-\akey{set-option :print-success true} command to the solver before 
-sending commands from the incremental benchmark script.
+%
+Participating solvers will be connected to a trace executor which will
+incrementally send commands to the standard input channel of the
+solver and read responses from the standard output channel of the
+solver.  The commands will be taken from an \textbf{incremental
+  benchmark script}, which is an SMT-LIBv2 script which satisfies the
+rules for an application script given above.  Note also that the trace
+executor will send a single \akey{set-option :print-success true}
+command to the solver before sending commands from the incremental
+benchmark script.
 
-\medskip
-Solvers must respond to each command sent by the trace executor, 
-with the answers defined in the SMT-LIB 2.0 format specification, that is,
-with a \texttt{success} answer for 
-\akey{set-option}, 
-\akey{set-logic}, 
-\akey{declare-sort}, 
-\akey{declare-fun}, 
-\akey{assert}, 
-\akey{push 1}, 
-and \akey{pop 1} 
-commands,
- with a \texttt{sat}, \texttt{unsat}, or \texttt{unknown} 
-for \akey{check-sat} commands. There should be no \akey{get-unsat-core}, \akey{get-proof}, \akey{get-model}, \akey{get-assignments}, or \akey{get-values}commands in these benchmarks.
+Solvers must respond to each command sent by the trace executor, with
+the answers defined in the SMT-LIB 2.0 format specification, that is,
+with a \texttt{success} answer for \akey{set-option},
+\akey{set-logic}, \akey{declare-sort}, \akey{declare-fun},
+\akey{define-sort}, \akey{define-fun}, \akey{assert}, \akey{push 1},
+and \akey{pop 1} commands, and with a \texttt{sat}, \texttt{unsat}, or
+\texttt{unknown} for \akey{check-sat} commands. There will be no
+\akey{get-unsat-core}, \akey{get-proof}, \akey{get-model},
+\akey{get-assignments}, or \akey{get-values} commands in these
+benchmarks.
 
-\header{Timeouts.}
-A time limit is set for the whole execution of each application
-benchmark (consisting of multiple queries).  We anticipate the
-timeout to be around 25~minutes (as it has been in the past).\footnote{The time limit may be adjusted once we understand the resources and capabilities of the StarExec service and the number of competition solvers.}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-In 2012 the competition ran only some logics as competitive divisions.
-In 2014 we will revert to previous practice and run each logic as a competitive division, if there are two or more solvers submitted.
-
 \subsection{Main track}
 
-\header{Benchmark sources.} %
-Benchmark formulas for each division of the main track
-will be drawn from the SMT-LIB library. The deadline for new benchmarks is
-May 15. The organizers will be checking and curating these until June 1;
-the organizers reserve the option to exclude new benchmarks if any prove problematic for some reason.
-SMT-COMP
+\header{Benchmark sources.}
+%
+Benchmark formulas for each division of the main track will be drawn
+from the SMT-LIB library. The deadline for new benchmarks is {\bf May
+  1, 2015}. The organizers will be checking and curating these until
+{\bf June 7, 2015}; the organizers reserve the option to exclude new
+benchmarks if any prove problematic for some reason.  SMT-COMP
 attempts to give preference to benchmarks that are ``real-world,'' in
@@
 
-\header{Benchmark availability.} % 
-The deadline for new benchmarks is May 15, 2014.
-The benchmarks will be made available as soon as possible after that, as they are checked and curated.
-The goal for completing the set of benchmarks is June 1.
-The set of benchmarks selected for the competition will be published when the
-competition begins.
+\header{Benchmark availability.}
+%
+New benchmarks will be made available as soon as possible after the
+benchmark submission deadline, as they are checked and curated.  The
+set of benchmarks selected for the competition will be published when
+the competition begins.
 
@@
   solvers support specific features of each division.  In particular,
-  there are checks for integer completeness (\ie\ benchmarks that are
+  there are checks for integer completeness (i.e., benchmarks that are
   satisfiable under the reals but not under the integers) and big
-  number support (\ie\ benchmarks that are likely to fail if integers
+  number support (i.e., benchmarks that are likely to fail if integers
   cannot be represented beyond some maximum value, such as
@@
 
-%  \noindent%\textbf{New for 2010:} 
-%  Using the same random seed as
-%  for benchmark selection and scrambling, 5 ``check'' benchmarks will
-%  be randomly generated using Robert Brummayer's SMT fuzzing
-%  tool~\cite{brummayer+09}.  The (exact version of this) tool will be
-%  publicly available from the SMT-COMP~2012 web site before the
-%  competition.  Since these benchmarks are generated after the random
-%  seed is fixed, they cannot be known in advance to any competitors,
-%  including the organizers.  The rationale for including these
-%  benchmarks is to try to take a step towards stronger certification
-%  that solvers are correct.  In future years, we envision SMT-COMP
-%  requiring that solvers pass some kind of pre-qualifying round based
-%  on SMT fuzzing.  The inclusion of these fuzzing benchmarks that are
-%  not known in advance is intended to encourage (without requiring)
-%  solver implementors to test their solvers using fuzzing or similar
-%  bug-discovery techniques.
+\item \emph{industrial.} These benchmarks come from some real
+  application and are produced by tools such as bounded model
+  checkers, static analyzers, extended static checkers, etc.
 
-\item \emph{industrial.} These benchmarks come from some real application
-      and are produced by tools such as bounded model checkers, static analyzers, extended
-      static checkers, etc.
 \item \emph{random.} These benchmarks are randomly generated.
-\item \emph{crafted.} This category is for all other benchmarks.  Usually,
-  benchmarks in this category are designed to be particularly difficult or to
-  test a specific feature of the logic.
+
+\item \emph{crafted.} This category is for all other benchmarks.
+  Usually, benchmarks in this category are designed to be particularly
+  difficult or to test a specific feature of the logic.
 \end{itemize}
 
-\header{Benchmark selection.} %
-
-The benchmarks are assigned a difficulty. For 2014, the difficulty measure is the
-CPU time taken by the best performing solver in the 2013 SMT-EVAL. 
- For new benchmarks, we will determine an approximate difficulty
-using trial runs.
-The difficulty values will be posted 
-as soon after May 15 as possible.
-The difficulty values are best estimates by the organizers and may not always completely correlate with actual difficulty.
+\header{Benchmark selection.} \remark{This section is under review.}
+%
+Each benchmark is assigned a difficulty. For 2015, the difficulty
+measure is the CPU time taken by the best performing solver in the
+2014 SMT-COMP.  For new benchmarks, we will determine an approximate
+difficulty using trial runs.  The difficulty values will be posted as
+soon after May~1 as possible.  The difficulty values are best
+estimates by the organizers and may not always reflect actual
+difficulty.
 
@@
 
-\item \textbf{Retire very easy benchmarks.} %
-  Eliminate benchmarks for which all of the current solvers in SMT-EVAL-2013
-  solved the benchmark in under 5 seconds,
-  \emph{unless} doing so reduces the pool of
-    benchmarks for the division to less than~300.
+\item \textbf{Retire very easy benchmarks.}
+%
+Eliminate benchmarks for which all \remark{or perhaps some} of the
+current solvers in SMT-COMP 2014 solved the benchmark in under
+5~seconds, \emph{unless} doing so reduces the pool of benchmarks for
+the division to less than~300.
 
-\item \textbf{Retire inappropriate benchmarks.} %
+\item \textbf{Retire inappropriate benchmarks.}
+%
 The competition organizers will remove from the eligibility pool
-  certain SMT-LIB benchmarks that are inappropriate or uninteresting
-  for competition, or cut the size of certain benchmark families to
-  avoid their over-representation.
+certain SMT-LIB benchmarks that are inappropriate or uninteresting for
+competition, or cut the size of certain benchmark families to avoid
+their over-representation.
+
+\item \textbf{Eliminate benchmarks whose status is unknown.}
+%
+The selection process ignores any benchmark whose expected output is
+neither {\tt sat} nor {\tt unsat}.  There is a significant number of
+benchmarks with {\tt unknown} status in the library; these are
+certainly interesting and are a challenge to solve, but they are not
+used in the competition.
 
@@
 
-Since the organizers at this point are unsure how long a set of benchmarks may take (which will depend also on the number of solvers submitted), the competition will be run in {\em heats}.
-For each division, some number $N$ of benchmarks will be selected as described and randomly divided into a number of (possibly unequal-sized) heats.
-The heats will be run in order.
-If the competition ends before all heats have completed, the remaining heats will be ignored.
-All benchmarks will be chosen at the beginning (that is, without reference to the results of any given heat).
+Since the organizers at this point are unsure how long a set of
+benchmarks may take (which will depend also on the number of solvers
+submitted), the competition will be run in {\em heats}. For each
+division, some number $N$ of benchmarks will be selected as described
+and randomly divided into a number of (possibly unequal-sized)
+heats. The heats will be run in order. If the competition ends before
+all heats have completed, the remaining heats will be ignored. All
+benchmarks will be chosen at the beginning (that is, without reference
+to the results of any given heat).
 
-The main purpose of the algorithm above is to have a balanced and complete set
-of benchmarks.  The  built-in bias is towards industrial rather than crafted
-or random benchmarks and towards more difficult benchmarks.
-  This reflects a desire by the organizers and agreed upon
-by the SMT community to emphasize problems that come from real applications.
+The main purpose of the algorithm above is to have a balanced and
+complete set of benchmarks.  The built-in bias is towards industrial
+rather than crafted or random benchmarks and towards more difficult
+benchmarks.  This reflects a desire by the organizers and agreed upon
+by the SMT community to emphasize problems that come from real
+applications.
 
@@
 the opening value of the New York Stock Exchange Composite Index on
-the first day the exchange is open on or after the date specified in the timeline
-will be added to the other seeding values.  This helps provide transparency,
-by guaranteeing that the organizers cannot manipulate the seed in
-favor of or against any particular submitted solver.  Benchmarks will also be slightly
-scrambled before the competition, using a simple benchmark scrambler
-seeded with the same seed as the benchmark selector.  Both the
-scrambler and benchmark selector will be publicly available before the
-competition.  Naturally, solvers must not rely on previously
-determined identifying syntactic characteristics of competition
-benchmarks in testing satisfiability (violation of this is considered
-cheating).
+the first day the exchange is open on or after the date specified in
+the timeline will be added to the other seeding values.  This helps
+provide transparency, by guaranteeing that the organizers cannot
+manipulate the seed in favor of or against any particular submitted
+solver.  Benchmarks will also be slightly scrambled before the
+competition, using a simple benchmark scrambler seeded with the same
+seed as the benchmark selector.  Both the scrambler and benchmark
+selector will be publicly available before the competition.
+Naturally, solvers must not rely on previously determined identifying
+syntactic characteristics of competition benchmarks in testing
+satisfiability (violation of this is considered cheating).
 
@@
 
-\header{Benchmark sources.} %
-Benchmarks for the application track will be collected by the SMT-COMP organizers.
-Any benchmark available to the organizers by May 15 will be considered eligible.
+\header{Benchmark sources.}
+%
+Benchmarks for the application track will be collected by the SMT-COMP
+organizers.  Any benchmark available to the organizers by {\bf May~1,
+  2015} will be considered eligible.
 
@@
 
-\section{Judging and Scoring}
-\label{sec:judging}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-\subsection{Scoring}
+\section{Scoring}
+\label{sec:scoring}
 
-The score for each benchmark is a triple $\langle e,n,m\rangle$, with
-$e$ a non-negative number of erroneous results (usually 0, possibly 1 for main track benchmarks, and possibly more than one for application benchmarks),
-$n\in[0,N]$ an integral number of points scored for the benchmark,
-where $N$ is the number of \akey{check-sat} commands
-in the benchmark, and $m\in[0,T]$ is the (real-valued) CPU time in seconds, where $T$ is
-the timeout.  Recall that main track benchmarks will have just one \akey{check-sat} command;
-application track benchmarks may have multiple \akey{check-sat} commands.
+Scores will be computed for all solvers and divisions.  However,
+winners will be declared only for \emph{competitive} divisions.  A
+division is competitive if at least two substantially different
+solvers (i.e., solvers from two different teams) were submitted.
+Although the organizers may enter other solvers for comparison
+purposes, only solvers that are explicitly submitted by their authors
+determine whether a division is competitive, and are eligible to be
+designated as winners.
 
-\header{Main track - sequential mode.}
-For the main track, the score on a given benchmark is the single $\langle e,n,m\rangle$ triple, with $m$ being the CPU time it takes to process the benchmark, that is, until the solver process terminates, and
-\begin{itemize}
-\item $e=0, n=1$ if the result of the check-sat command is correct,
-\item $e=0, n=0$ if the result is {\tt unknown}, and
-\item $e=1, n=0$ if the result is incorrect.
-\end{itemize}
+\subsection{Benchmark scoring}
 
-\header{Main track - parallel mode.}
-The Star-Exec infrastructure reports both wall-clock time and CPU time for a given benchmark-solver job-pair.
-Each Star-Exec node has multiple (currently 4) cores; a multi-threaded solver can in principle make use of these cores to reduce its wall-clock time.
-Since the competition has not to date emphasized parallel solvers, we will use total CPU time (across all cores and subprocesses) as the measure of performance in the sequential mode of the main track; the imposed time out will also be on the CPU time.
+A solver's score for each benchmark is a quadruple $\langle e, n, w,
+c\rangle$, with $e \in \{0, 1\}$ the number of erroneous results
+(usually~$e = 0$), $n \in [0,N]$ an integral number of points scored
+for the benchmark, where $N$ is the number of \akey{check-sat}
+commands in the benchmark, $c \in [0,4T]$ is the (real-valued) CPU
+time in seconds, and $w \in [0,T]$ is the (real-valued) wall-clock
+time in seconds, where $T$ is the timeout.  Recall that main track
+benchmarks will have just one \akey{check-sat} command; application
+track benchmarks may have multiple \akey{check-sat} commands.
 
-However, we can also measure the performance using wall-clock time, the key performance criterion for a parallel solver.
-We will use the same competition data to determine a parallel-solver winner as follows.
-The competition will be run with a timeout T for both CPU time and wall-clock time.
-Since the computation nodes have C=4 cores, we can simulate a competition that had a time out of T CPU seconds and T/C wall-clock seconds by simply declaring that any solver taking more than T/C wall-clock time has timed out for the parallel competition.
-We then recompute the scoring as above but using wall-clock time and a timeout value of T/C.
+\header{Main track.}
+%
+\remark{Clarify how $\langle e, n, c, w\rangle$ depend on solver
+  behavior.}
 
 \header{Application track.}
-An application benchmark may have multiple check-sat commands and may partially solve the benchmark before timing out.
-The benchmark is run by the benchmark executor, measuring the total time (summed over all individual commands) taken by
-the solver to respond to commands.
-It is expected that nearly all of this time will be in response to a check-sat command, but assert, push or pop commands might also entail a reasonable amount of processing.
-\begin{itemize}
-\item If the solver completes the benchmark without timing out, the solver receives a score of $\langle e,n,m\rangle$,
-where $e$ is the number of erroneous responses to commands, $n$ is the number of correct responses to check-sat commands, and $m$ is the CPU time taken.
-\item If the solver times out while processing the benchmark, the solver receives a score of $\langle e,n,m\rangle$,
-where $e$ is the number of erroneous responses to commands, $n$ is the number of correct responses to check-sat commands before timing out, and $m$ is equal to the timeout value.
-\end{itemize}
+%
+An application benchmark may have multiple check-sat commands and may
+partially solve the benchmark before timing out.  The benchmark is run
+by the benchmark executor, measuring the total time (summed over all
+individual commands) taken by the solver to respond to commands. It is
+expected that nearly all of this time will be in response to
+\akey{check-sat} commands, but \akey{assert}, \akey{push} or
+\akey{pop} commands might also entail a reasonable amount of
+processing.
+%% \begin{itemize}
+%% \item If the solver completes the benchmark without timing out, the
+%%   solver receives a score of $\langle e,n,m\rangle$, where $e$ is the
+%%   number of erroneous responses to commands, $n$ is the number of
+%%   correct responses to check-sat commands, and $m$ is the CPU time
+%%   taken.
+%% \item If the solver times out while processing the benchmark, the
+%%   solver receives a score of $\langle e,n,m\rangle$, where $e$ is the
+%%   number of erroneous responses to commands, $n$ is the number of
+%%   correct responses to check-sat commands before timing out, and $m$
+%%   is equal to the timeout value.
+%% \end{itemize}
 
-As queries are only presented in order, this scoring system may mean
-that relatively ``easier'' queries are hidden behind more difficult
-ones located at the middle of the query sequence. We will not perform a parallel performance analysis of the application track.
+\subsection{Division scoring}
 
-\header{Competition scoring.}
-\label{scoring}
-Benchmarks' scores are summed component-wise to form a solver's total
-score for that division of the competition.
-Total scores are compared lexicographically---a score $\langle e,n,m\rangle$ is better than 
-$\langle e',n',m'\rangle$ iff $e < e'$ or ($e = e'$ and $n > n'$) or ($e = e'$ and $n = n'$ and $m < m'$).
-That is, fewer errors takes precedence over more correct solutions, which takes precedence over less time taken.
+To compute a solver's score for a division, the solver's individual
+benchmark scores for all benchmarks in the division are summed
+component-wise.  Total scores are compared lexicographically: a score
+$\langle e, n, w, c\rangle$ is better than $\langle e', n', w',
+c'\rangle$ iff $e < e'$ or ($e = e'$ and $n > n'$) or ($e = e'$ and $n
+= n'$ and $w < w'$) or ($e = e'$ and $n = n'$ and $w = w'$ and $c <
+c'$).  That is, fewer errors takes precedence over more correct
+solutions, which takes precedence over less wall-clock time taken,
+which takes precedence over less CPU time taken.
+
+\subsection{Competition-wide scoring (main track)}
+
+We define a competition-wide metric for the main track as follows.
+Let $B_i$ be the total number of benchmarks in division~$i$ that were
+used in the competition, and let $\langle e_i, n_i, w_i, c_i\rangle$
+be a solver's score for this division.  The solver's competition-wide
+score is $\sum_i (e_i == 0 ? (n_i/N_i)^2 : -e_i) \log N_i$, where the
+sum is over all \emph{competitive} divisions into which the solver was
+entered.  \remark{Rationale.}
+
+%% {\em Rationale.} The metric M purposely emphasizes breadth of solver
+%% participation---a solver participating in many logics need not be the
+%% best in any one of them.  The use of the square in the metric limits
+%% that somewhat---a solver still needs to do reasonably well compared to
+%% winners to be able to catch up by breadth of participation.  The
+%% non-linear metric also gives added weight to completing close to all
+%% benchmarks in a division.  The metric is also quite simple and the
+%% metric for a solver is independent of the performance of other
+%% solvers.  Time is omitted from the metric both to simplify the metric
+%% and because it is only of third importance in the regular competition
+%% metric and is difficult to compare across divisions.
+
+\subsection{Sequential performance}
+
+SMT-COMP has traditionally emphasized sequential performance (i.e.,
+CPU time) over parallel performance (i.e., wall-clock time).
+Accordingly, we will recognize the best \emph{sequential} solver, both
+in each division and according to the competition-wide metric (for the
+main track).  A solver is eligible for this recognition if, for each
+benchmark in the division, the solver's CPU time does not exceed its
+wall-clock time.
 
 \subsection{Other recognitions}
+
 The organizers will also recognize the following contributions:
+%
 \begin{itemize}
-\item {\em Open source}. In addition to recognizing the overall
-winner in each division, the top solver that provides its source code as open source will also be
-recognized in each division.  
-\item {\em Best new entrant}. The best performing entrant from a new solver implementation team, as measured by the Olympic Games metric defined below.
-\item {\em Breadth of logics}. Tools that cover the most theories and logics.
+\item {\em Open source}. In addition to recognizing the overall winner
+  in each division, the top solver that provides its source code as
+  open source will also be recognized in each division.
+\item {\em Best new entrant}. The best performing entrant from a new
+  solver implementation team, as measured by the Olympic Games metric
+  defined below.
+\item {\em Breadth of logics}. Tools that cover the most theories and
+  logics.
 \item {\em Benchmarks}. Contributors of new benchmarks.
-\item The organizers reserve the right to recognize other outstanding contributions that become apparent in the competition results.
 \end{itemize}
+%
+The organizers reserve the right to recognize other outstanding
+contributions that become apparent in the competition results.
 
-\subsection{FLoC Olympic Games medals}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-The FLoC Olympics games medals will be awarded based on competition-wide critera.
+\section{Judging}
 
-We define a competition-wide metric M as follows.
-Each solver competing in a division receives a number of points for its performance in that division: $(n/N)^2$, where $n$ is the number of benchmarks solved correctly and $N$ is the number of benchmarks used in that division.
-A solver's score for the whole competition is the sum of these values over all the
-divisions in which the solver participates.
+The organizers reserve the right, with careful deliberation, to remove
+a benchmark from the competition results if it is determined that the
+benchmark is faulty (e.g., syntactically invalid in a way that affects
+some solvers but not others); and to clarify ambiguities in these
+rules that are discovered in the course of the competition.  Authors
+of solver entrants may appeal to the organizers to request such
+decisions.  Organizers that are affiliated with solver entrants will
+be recused from these decisions.  The organizers' decisions are final.
 
-The Olympic Games medals will be awarded as follows.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Acknowledgments and Disclaimer}
+
+SMT-COMP 2015 is organized under the direction of the SMT Steering
+Committee. The organizing team is
+%
 \begin{itemize}
-\item The gold medal we will be awarded to the solver with the best competition-wide value of M.
-\item The silver medal will be awarded to the solver that wins the (sequential) QF\_BV division according to the usual $\langle e',n',m'\rangle$ metric of subsection \ref{scoring}.
-\item The bronze medal will be awarded to the solver with the second-best  competition-wide value of M.
+\setlength{\itemsep}{0pt}
+\item \href{https://www.lri.fr/~conchon/}{Sylvain Conchon}~--
+  Paris-Sud University, France (co-organizer)
+\item \href{https://www.sites.google.com/site/deharbe/}{David
+  D{\'e}harbe}~-- Federal University of Rio Grande do Norte, Brazil
+  (co-organizer)
+\item \href{http://user.it.uu.se/~tjawe125/}{Tjark Weber}~-- Uppsala
+  University, Sweden (chair)
 \end{itemize}
+%
+Tjark Weber is responsible for policy and procedure decisions, such as
+these rules, with input from the co-organizers. He is not associated
+with any group creating or submitting solvers.
 
-{\em Rationale.} The metric M purposely emphasizes breadth of solver participation - a solver participating in many logics need not be the best in any one of them.
-The use of the square in the metric limits that somewhat - a solver still needs to do reasonably well compared to winners to be able to catch up by breadth of participation.
-The non-linear metric also gives added weight to completing close to all benchmarks in a division.
-The metric is also quite simple and the metric for a solver is independent of the performance of other solvers.
+Many others have contributed benchmarks, effort, and feedback.
+\remark{Specific individuals will be named later.}
+% In particular, Clark Barrett processed the many benchmark
+% submissions.
+The competition uses the \href{https://www.starexec.org/}{StarExec}
+service, which is hosted at the
+\href{http://www.cs.uiowa.edu/}{University of Iowa}.  Aaron Stump is
+providing essential StarExec support.
 
-\section{Timeline}
-\label{sec:timeline}
+David D{\'e}harbe is associated with the solver group producing the
+veriT solver.
 
-\nobreak
-\vbox{% no page break here, please!
-\begin{description}
-\item[May 15] Deadline for benchmark contributions.
-\item[June 1] First versions of solver competitors are due to the organizers, including divisions being entered.
-  Versions of the benchmark scrambler, benchmark selector and trace executor made available.
-\item[June 8] Final version of the benchmark scrambler, benchmark selector and trace executor made available.
-\item[June 8] Benchmark libraries are frozen.
-\item[June 15] Final versions of solvers due via StarExec (for
-  all tracks), including divisions being entered, system
-  descriptions and magic numbers for benchmark scrambling.
-\item[June 16] Opening value of NYSE Composite Index used to complete random seed.
-\item[July 17] SMT 2014; end of competition.
-\end{description}}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-\section{Mailing List}
-\label{sec:ps}
-
-Interested parties should subscribe to the SMT-COMP mailing list (at \url{cs.nyu.edu/mailman/listinfo/smt-comp}).
-Important
-late-breaking news and any necessary clarifications and edits to these
-rules will be announced there, and it is the primary way that such
-announcements will be communicated.
-
-\section{Disclaimer}
-\begin{itemize}
-\item David Cok, David Deharbe and Tjark Weber are the organizers of SMT-COMP 2014. 
-David Cok is the lead and is 
-responsible for policy and procedure decisions, such as these
-rules, with input from the co-organizers. He is not associated 
-with any group creating or submitting solvers. He has used solvers
-in industrial settings and is keenly interested to know which are the best for various applications.
-
-\item David Deharbe is associated with the solver group producing the veriT solver.
-\end{itemize}
 \bibliographystyle{plain}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \end{document}

### 2015-05-10 rules/rules15.tex
Revised version of 2015 rules.

@@
 
-\usepackage{draftwatermark}
+%\usepackage{draftwatermark}
 
@@
 
-\newcommand{\remark}[1]{{\small\textcolor{red}{[#1]}}}
+\let\OLDthebibliography\thebibliography
+\renewcommand\thebibliography[1]{
+  \OLDthebibliography{#1}
+  \setlength{\parskip}{2pt}
+  \setlength{\itemsep}{1.5pt plus 0.3ex}
+}
 
@@
 \section{Communication}
-\label{sec:communication}
 
@@
 \section{Introduction}
-\label{sec:intro}
 
@@
 previous
-competitions~(\cite{SMTCOMP2012,SMTEVAL2013,SMTCOMP-JAR,SMTCOMP-FMSD,SMTCOMP-2008,BDOS08}).
+competitions~(\cite{SMTCOMP-JAR,SMTCOMP-FMSD,BDOS08,SMTCOMP-2008,SMTCOMP-2014,SMTCOMP-2012,SMTEVAL-2013}).
 
@@
 multiple divisions, where each division uses benchmarks from a
-specific SMT-LIB logic (or group of logics). \remark{Additional
-  tracks, e.g., for unsat-core extraction or proof generation, are
-  currently being considered.}  We will recognize winners as measured
-by number of benchmarks solved; we will also recognize solvers based
-on additional criteria.
+specific SMT-LIB logic (or group of logics).  We will recognize
+winners as measured by number of benchmarks solved; we will also
+recognize solvers based on additional criteria.
 
@@
 \begin{itemize}
-\item All solvers will be run with $n=4$ cores available, and the CPU
-  timeout will be $n$~times the wall-clock timeout.  We will recognize
-  both best sequential and best parallel performance in all divisions.
+\item All solvers will be run with $n=4$ cores available.  We will
+  recognize both best sequential and best parallel performance in all
+  main track divisions, using different CPU time limits.
 \item In addition to recognizing the best solver in each division, we
-  will recognize the three solvers that perform best according to
+  will recognize solvers that perform best according to
   competition-wide criteria, emphasizing breadth of supported logics.
@@
   FLoC Olympic Games medals in~2014.
-\item \remark{Pending availability of suitable benchmarks and solvers,
-  we may include a new division for floating-point arithmetic.  This
-  should be considered experimental in 2015, and will not be included
-  in the competition-wide ranking.}
-\item \remark{Benchmark selection and relative weight of benchmark
-  families are under review.}
+\item We plan to include new divisions for floating-point arithmetic.
+  These should be considered experimental in~2015, and will not be
+  included in the competition-wide ranking.
+\item We plan to run solvers on all eligible benchmarks.  Previous
+  competitions used a proper subset of eligible benchmarks, causing
+  competition results to be affected by a random selection process.
 \end{itemize}
@@
 clarity, each submitted solver must have one configuration only.  A
-submission must also include a 32-bit unsigned integer.  These
+submission must also include a 32-bit unsigned integer.  These integer
 numbers, collected from all submissions, are used to seed the
-pseudo-random benchmark selection algorithm, as well as the benchmark
-scrambler.
+benchmark scrambler.
 
@@
 useful should be sent to the organizers before the competition ends.
+We intend to make system descriptions publicly available.
 
-\header{Other systems.}
+\header{Multiple versions.}
 %
@@
 available to the competition, the organizers reserve the right not to
-accept multiple versions of solvers from the same solver team.  The
-organizers also reserve the right to include other systems of interest
-(such as entrants in previous competitions) in the competition.
+accept multiple versions of solvers from the same solver team.
+
+\header{Other solvers.}
+%
+The organizers reserve the right to include other solvers of interest
+(such as entrants in previous SMT competitions) in the competition,
+e.g., for comparison purposes.
 
@@
 %
-A \emph{wrapper tool} is defined as any tool which calls one or more
+A \emph{wrapper tool} is defined as any solver which calls one or more
 SMT solvers not written by the author of the wrapper tool.  The other
-solvers are called the \emph{wrapped} tools.  A wrapper tool must
-explicitly acknowledge any tools that it wraps.  Its system
+solvers are called the \emph{wrapped} solvers.  A wrapper tool must
+explicitly acknowledge any solvers that it wraps.  Its system
 description should make clear the technical innovations by which the
-wrapper tool expects to improve on the wrapped tools.
+wrapper tool expects to improve on the wrapped solvers.
 
@@
 Submitters of an SMT-COMP entrant need not be physically present at
-the competition to participate or win.
+the competition or the SMT Workshop to participate or win.
 
@@
 The solver versions that are present on StarExec at the conclusion of
-the grace period will be the ones used for the competition, and
-versions submitted after this time will not be used.  The organizers
-reserve the right to start the competition itself at any time after
-the open of the New York Stock Exchange on the day after the final
-solver deadline.
+the grace period will be the ones used for the competition.  Versions
+submitted after this time will not be used.  The organizers reserve
+the right to start the competition itself at any time after the open
+of the New York Stock Exchange on the day after the final solver
+deadline.
 
@@
 \section{Execution of Solvers}
-\label{sec:exec}
 
@@
 \subsection{Logistics}
+\label{sec:logistics}
 
@@
 \begin{enumerate}
-\item The (single) $\akey{set-logic}$ command setting the benchmark's
-  logic is the first command after any $\akey{set-option}$ commands
-  described below.
 \item In the main track, there may be a (single) \akey{set-option
   :print-success ...} command.  Note that {\tt success} outputs are
-  ignored by the post-processor used by the competition; in the
-  application track, the :print-success option may not be disabled.
-\item The application track executor will send an initial
+  ignored by the post-processor used by the
+  competition.\footnote{SMT-LIB~2.0 requires that a solver produce a
+    \texttt{success} answer after each \akey{set-logic},
+    \akey{declare-sort}, \akey{declare-fun} and \akey{assert} command
+    (among others), unless the option \akey{:print-success} is set to
+    false.  Ignoring the \texttt{success} outputs allows for
+    submitting fully SMT-LIB~2.0 compliant solvers without the need
+    for a wrapper script, while still allowing entrants of previous
+    competitions to run without changes.}
+\item In the application track, the \akey{:print-success} option may
+  not be disabled; the application track executor will send an initial
   $\akey{set-option :print-success true}$ command to the solver.
+\item The (single) $\akey{set-logic}$ command setting the benchmark's
+  logic is the first command after any $\akey{set-option}$ commands.
 \item The script next optionally contains (any number of)
   $\akey{set-info}$ commands, which may be ignored by the
-  solver. Benchmarks are expected to have the following
+  solver. Benchmarks will likely have some of the following
   \akey{set-info} commands: \akey{(set-info :smt-lib-version 2.0)},
-  \akey{(set-info :category ...)}, \akey{(set-info :source ...)}
-  (indicating the authorship or tool that produced the benchmark), and
+  \akey{(set-info :category ...)}, \akey{(set-info :source ...)}, and
   \akey{(set-info :status ...)}.
+\item In the main track, there is exactly one $\akey{check-sat}$
+  command, following possibly several $\akey{assert}$ commands.
+\item In the application track, there are one or more \akey{check-sat}
+  commands, each preceded by one or more \akey{assert} commands; there
+  may also be zero or more \akey{push 1} commands, and zero or more
+  \akey{pop 1} commands, consistent with the uses of those commands in
+  the SMT-LIB standard. Each \akey{check-sat} command may be preceded
+  by a \akey{set-info :status} command that indicates the expected
+  result of the \akey{check-sat} command.
 \item The $\akey{exit}$ command is the last command.
-\item For tracks other than the application track, there is exactly
-  one $\akey{check-sat}$ command, following possibly several
-  $\akey{assert}$ commands.
-\item For the application track, there are one or more
-  \akey{check-sat} commands, each preceded by one or more
-  \akey{assert} commands; there may also be zero or more \akey{push 1}
-  commands, and zero or more \akey{pop 1} commands, consistent with
-  the uses of those commands in the SMT-LIB standard. Each
-  \akey{check-sat} command may be preceded by a \akey{set-info
-    :status} command that indicates the expected result of the
-  \akey{check-sat} command.
 \item The formulas in the script belong to the benchmark's logic, with
@@
 %
-The SMT-LIB format specification is publicly available from the
-``Documents'' section of the SMT-LIB website~\cite{SMT-LIB}.  Solvers
-will be given formulas only from the divisions into which they have
-been entered.
+The SMT-LIB format specification is available from the ``Documents''
+section of the SMT-LIB website~\cite{SMT-LIB}.  Solvers will be given
+formulas only from the divisions into which they have been entered.
 
-\header{Timeouts.}
+\header{Time and memory limits.}
 %
-Each SMT-COMP solver will be executed on a dedicated processor with
-4~cores of a competition machine for each given benchmark, up to a
-fixed time limit.  Detailed machine specifications are available on
-the competition web site.  The time limit is yet to be determined, but
-it is anticipated to be 40~minutes of wall-clock time (and 160~minutes
-of CPU time).\footnote{The time limit may be adjusted once we know the
-  number of competition entrants and eligible benchmarks.}  Solvers
-that take more than this time limit will be killed.  Solvers are
-allowed to spawn other processes; these will be killed at
-approximately the same time as the first started process.
+Each SMT-COMP solver will be executed on a dedicated processor of a
+competition machine, for each given benchmark, up to a fixed
+wall-clock time limit~$T$.  Each processor has 4 cores.  Detailed
+machine specifications are available on the competition web site.
+
+The time limit~$T$ is yet to be determined, but it is anticipated to
+be 40~minutes of wall-clock time per solver/benchmark
+pair.\footnote{The time limit may be adjusted once we know the number
+  of competition entrants and eligible benchmarks.}  Solvers that take
+more than this time limit will be killed.  Solvers are allowed to
+spawn other processes; these will be killed at approximately the same
+time as the first started process.
 
 The StarExec service also limits the memory consumption of the solver
-processes.  We expect the limit per solver-benchmark job-pair to be on
-the order of 60\,GB.  The values of both the timeout limit and the
+processes.  We expect the memory limit per solver/benchmark pair to be
+on the order of 60\,GB.  The values of both the time limit and the
 memory limit are available to a solver process through environment
-variables defined and set by the StarExec service (see the StarExec
-user guide for more information).
+variables.  See the StarExec user guide for more information.
 
@@
 %
-Solvers which exit before the time limit without reporting a result
-(i.e., due to exhausting memory or crashing) and do not produce output
-that includes \texttt{sat}, \texttt{unsat} or \texttt{unknown} will be
-considered to have aborted.  Also, as a further measure to prevent
-misjudgments of solvers, any \texttt{success} outputs will be
-ignored.\footnote{ Note that SMT-LIB~v2 requires that a solver produce
-  a \texttt{success} answer after each \akey{set-logic},
-  \akey{declare-sort}, \akey{declare-fun} and \akey{assert} command
-  (among others), unless the option \akey{:print-success} is set to
-  false.  Ignoring the \texttt{success} outputs therefore allows for
-  submitting fully-compliant solvers without the need of a wrapper
-  script, while still allowing entrants of previous competitions to
-  run without changes.}
+Any \texttt{success} outputs will be ignored.  Solvers that exit
+before the time limit without reporting a result (e.g., due to
+exhausting memory or crashing) and do not produce output that includes
+\texttt{sat}, \texttt{unsat} or \texttt{unknown} will be considered to
+have aborted.
 
@@
 %
-Solvers are allowed to create and write to files and directories
-during the course of an execution, but they are not allowed to read
-such files back during later executions.  Any files written should be
-put in the directory in which the tool is started, or in a
-subdirectory.
-
-The solver is executed with a temporary directory as the current
-working directory.  Any generated files should be produced there (and
-not, say, in the system's {\tt /tmp} directory).  The StarExec system
-sets a limit on the amount of disk storage permitted---typically
-20\,GB (see the User Guide).  The temporary directory and its contents
-are deleted after the job is complete.
+Solvers may create and write to files and directories during the
+course of an execution, but they must not read such files back during
+later executions.  Each solver is executed with a temporary directory
+as its current working directory.  Any generated files should be
+produced there (and not, say, in the system's {\tt /tmp} directory).
+The StarExec system sets a limit on the amount of disk storage
+permitted---typically 20\,GB.  See the StarExec user guide for more
+information.  The temporary directory is deleted after the job is
+complete.  Solvers must not attempt to communicate with other
+machines, e.g., over the network.
 
 \subsection{Application track}
-\label{sec:exec:application}
 
@@
 commands (possibly with corresponding \akey{push 1}/\akey{pop 1}
-commands), which is parsed by a {\em trace executor}. The trace
+commands), which is parsed by a \emph{trace executor}. The trace
 executor serves the following purposes:
@@
 \item it prevents ``look-ahead'' behaviors of SMT solvers;
-\item it records time and answers for each call, possibly aborting the
-  execution in case of a wrong answer;
+\item it records time and answers for each call;
 \item it guarantees a fair execution for all solvers by abstracting
@@
 \end{itemize}
-Note that the executor terminates processing the script upon receiving
-an incorrect response.
+%
+The trace executor terminates processing the benchmark script upon
+receiving an incorrect response from the solver.
 
-The disk space and memory limits on the application track are the same
-as for the main track.
+The disk space and memory limits for the application track are the
+same as for the main track (see Section~\ref{sec:exec:main}).
 
-\header{Input and Output.}
+\header{Input and output.}
 %
-Participating solvers will be connected to a trace executor which will
-incrementally send commands to the standard input channel of the
+Participating solvers will be connected to a trace executor, which
+will incrementally send commands to the standard input channel of the
 solver and read responses from the standard output channel of the
-solver.  The commands will be taken from an \textbf{incremental
-  benchmark script}, which is an SMT-LIBv2 script which satisfies the
-rules for an application script given above.  Note also that the trace
-executor will send a single \akey{set-option :print-success true}
-command to the solver before sending commands from the incremental
-benchmark script.
+solver.  The commands will be taken from an SMT-LIB~2.0 benchmark
+script that satisfies the rules for an application script given in
+Section~\ref{sec:logistics}.
 
-Solvers must respond to each command sent by the trace executor, with
-the answers defined in the SMT-LIB 2.0 format specification, that is,
+Solvers must respond to each command sent by the trace executor with
+the answers defined in the SMT-LIB~2.0 format specification, that is,
 with a \texttt{success} answer for \akey{set-option},
@@
 \akey{define-sort}, \akey{define-fun}, \akey{assert}, \akey{push 1},
-and \akey{pop 1} commands, and with a \texttt{sat}, \texttt{unsat}, or
-\texttt{unknown} for \akey{check-sat} commands. There will be no
-\akey{get-unsat-core}, \akey{get-proof}, \akey{get-model},
-\akey{get-assignments}, or \akey{get-values} commands in these
-benchmarks.
+and \akey{pop 1} commands, and with an answer of \texttt{sat},
+\texttt{unsat}, or \texttt{unknown} for \akey{check-sat} commands.
+There will be no \akey{get-unsat-core}, \akey{get-proof},
+\akey{get-model}, \akey{get-assignments}, or \akey{get-values}
+commands in application track benchmarks.
 
@@
 \section{Benchmarks and Problem Divisions}
-\label{sec:theories}
-
-\subsection{Main track}
 
@@
 %
-Benchmark formulas for each division of the main track will be drawn
-from the SMT-LIB library. The deadline for new benchmarks is {\bf May
-  1, 2015}. The organizers will be checking and curating these until
-{\bf June 7, 2015}; the organizers reserve the option to exclude new
-benchmarks if any prove problematic for some reason.  SMT-COMP
-attempts to give preference to benchmarks that are ``real-world,'' in
-the sense of coming from or having some intended application outside
-SMT.
+Benchmarks for each division will be drawn from the SMT-LIB benchmark
+repository.  The main track will use a subset of all
+\emph{non-incremental} benchmarks; the application track will use a
+subset of all \emph{incremental} benchmarks.
 
-\header{Benchmark availability.}
+\header{New benchmarks.}
 %
-New benchmarks will be made available as soon as possible after the
-benchmark submission deadline, as they are checked and curated.  The
-set of benchmarks selected for the competition will be published when
-the competition begins.
+The deadline for submission of new benchmarks is {\bf May~1, 2015}.
+The organizers will be checking and curating these until {\bf June~7,
+  2015}.  The organizers reserve the right to exclude new benchmarks
+if any prove problematic for some reason.  SMT-COMP attempts to give
+preference to benchmarks that are ``real-world,'' in the sense of
+coming from or having some intended application outside SMT.
 
-\header{Benchmark demographics.} %
-In SMT-LIB, benchmarks are organized according to \emph{families}.  A benchmark
-family contains problems that are similar in some significant way.  Typically
-they come from the same source or application, or are all output by the same
-tool.  \emph{Each top-level subdirectory within a division represents a distinct
-family.}
+New benchmarks will be made publicly available as soon as possible
+after the benchmark submission deadline, as they are checked and
+curated.  The set of benchmarks selected for the competition will be
+published when the competition begins.
+
+\header{Benchmark demographics.}
 %
+In SMT-LIB, benchmarks are organized according to \emph{families}.  A
+benchmark family contains problems that are similar in some
+significant way.  Typically they come from the same source or
+application, or are all output by the same tool.  Each top-level
+subdirectory within a division represents a distinct family.
 
-Each benchmark in SMT-LIB also has a \emph{category}.  There are four possible
-categories:
-%
+Each benchmark in SMT-LIB also has a \emph{category}.  There are four
+possible categories:
 \begin{itemize}
 \item \emph{check.} These benchmarks are hand-crafted to test whether
-  solvers support specific features of each division.  In particular,
-  there are checks for integer completeness (i.e., benchmarks that are
-  satisfiable under the reals but not under the integers) and big
-  number support (i.e., benchmarks that are likely to fail if integers
-  cannot be represented beyond some maximum value, such as
-  $(2^{31}-1)$).
-
+  solvers support specific features of each division.
 \item \emph{industrial.} These benchmarks come from some real
@@
   checkers, static analyzers, extended static checkers, etc.
-
 \item \emph{random.} These benchmarks are randomly generated.
-
 \item \emph{crafted.} This category is for all other benchmarks.
@@
 
-\header{Benchmark selection.} \remark{This section is under review.}
+\header{Benchmark selection.}
 %
-Each benchmark is assigned a difficulty. For 2015, the difficulty
-measure is the CPU time taken by the best performing solver in the
-2014 SMT-COMP.  For new benchmarks, we will determine an approximate
-difficulty using trial runs.  The difficulty values will be posted as
-soon after May~1 as possible.  The difficulty values are best
-estimates by the organizers and may not always reflect actual
-difficulty.
+The benchmark pool is culled as follows:
+\begin{enumerate}
+\item \emph{Retire inappropriate benchmarks.} The competition
+  organizers may remove from the eligibility pool certain benchmarks
+  that are inappropriate or uninteresting for competition, or cut the
+  size of certain benchmark families to avoid their
+  over-representation.
+\item \emph{Eliminate benchmarks whose status is unknown.} Any
+  benchmark whose expected output is neither {\tt sat} nor {\tt unsat}
+  is removed.  There is a significant number of benchmarks with {\tt
+    unknown} status in the library; these are certainly interesting
+  and are a challenge to solve, but they are not used in the
+  competition.\footnote{Incremental benchmarks may contain multiple
+    \akey{check-sat} commands, each with its own status.  Incremental
+    benchmarks that contain (some) \akey{check-sat} commands with {\tt
+      unknown} status may still contain a prefix of commands where the
+    status is known for all \akey{check-sat} commands in the prefix.
+    This prefix is eligible for the application track.}
+\end{enumerate}
+%
+All remaining benchmarks are used for the competition.  There will be
+no further selection of benchmarks, e.g., based on benchmark
+difficulty or benchmark category.
 
-The selection of benchmarks for the competition will be biased towards more difficult benchmarks
-as follows. First, the benchmark pool is culled as follows:
-\begin{enumerate}
-
-\item \textbf{Retire very easy benchmarks.}
+\header{Heats.}
 %
-Eliminate benchmarks for which all \remark{or perhaps some} of the
-current solvers in SMT-COMP 2014 solved the benchmark in under
-5~seconds, \emph{unless} doing so reduces the pool of benchmarks for
-the division to less than~300.
-
-\item \textbf{Retire inappropriate benchmarks.}
-%
-The competition organizers will remove from the eligibility pool
-certain SMT-LIB benchmarks that are inappropriate or uninteresting for
-competition, or cut the size of certain benchmark families to avoid
-their over-representation.
-
-\item \textbf{Eliminate benchmarks whose status is unknown.}
-%
-The selection process ignores any benchmark whose expected output is
-neither {\tt sat} nor {\tt unsat}.  There is a significant number of
-benchmarks with {\tt unknown} status in the library; these are
-certainly interesting and are a challenge to solve, but they are not
-used in the competition.
-
-\end{enumerate}
-
-Then, for each division, the benchmarks are divided into quintiles according to the difficulty measure.
-Next a random selection of N competition benchmarks is made as follows:
-\begin{itemize}
-\item N*40\% are randomly selected from the top quintile, if sufficient benchmarks are available
-\item additional benchmarks are randomly selected from the second quintile, to produce N*60\% benchmarks, if sufficient benchmarks are available
-\item additional benchmarks are randomly selected from the third quintile, to produce N*75\% benchmarks, if sufficient benchmarks are available
-\item additional benchmarks are randomly selected from the fourth quintile, to produce N*90\% benchmarks, if sufficient benchmarks are available
-\item any remaining needed benchmarks are randomly selected from the bottom quintile.
-\end{itemize}
-Within each quintile selection,
-\begin{itemize}
-\item if the industrial benchmarks comprise less than 85\% of the benchmarks in that quintile, 85\% will be chosen from the industrial benchmarks (if a sufficient number are available), and the others from the population of random and crafted benchmarks;
-\item if the industrial benchmarks comprise at least 85\% of the benchmarks in that quintile, the benchmarks are chosen at random from the population of industrial, random and crafted benchmarks in that quintile.
-\end{itemize}
-
 Since the organizers at this point are unsure how long a set of
 benchmarks may take (which will depend also on the number of solvers
-submitted), the competition will be run in {\em heats}. For each
-division, some number $N$ of benchmarks will be selected as described
-and randomly divided into a number of (possibly unequal-sized)
-heats. The heats will be run in order. If the competition ends before
-all heats have completed, the remaining heats will be ignored. All
-benchmarks will be chosen at the beginning (that is, without reference
-to the results of any given heat).
+submitted), the competition may be run in \emph{heats}.  For each
+track and division, the selected benchmarks may be randomly divided
+into a number of (possibly unequal-sized) heats.  Heats will be run in
+order.  If the organizers determine that there is adequate time, all
+heats will be used for the competition.  Otherwise, incomplete heats
+will be ignored.
 
-The main purpose of the algorithm above is to have a balanced and
-complete set of benchmarks.  The built-in bias is towards industrial
-rather than crafted or random benchmarks and towards more difficult
-benchmarks.  This reflects a desire by the organizers and agreed upon
-by the SMT community to emphasize problems that come from real
-applications.
+\header{Benchmark scrambling.}
+%
+Benchmarks will be slightly scrambled before the competition, using a
+simple benchmark scrambler.  The benchmark scrambler will be made
+publicly available before the competition.
 
-Pseudo-random numbers will be generated using the standard C library
-function \texttt{random()}, seeded (using \texttt{srandom()}) with the
-sum, modulo $2^{30}$, of the numbers provided in the system
-descriptions (see Section~\ref{sec:entrants} above) by all SMT-COMP
-entrants other than the organizers.  Additionally, the integer part of
-the opening value of the New York Stock Exchange Composite Index on
-the first day the exchange is open on or after the date specified in
-the timeline will be added to the other seeding values.  This helps
-provide transparency, by guaranteeing that the organizers cannot
-manipulate the seed in favor of or against any particular submitted
-solver.  Benchmarks will also be slightly scrambled before the
-competition, using a simple benchmark scrambler seeded with the same
-seed as the benchmark selector.  Both the scrambler and benchmark
-selector will be publicly available before the competition.
 Naturally, solvers must not rely on previously determined identifying
 syntactic characteristics of competition benchmarks in testing
-satisfiability (violation of this is considered cheating).
+satisfiability.  Violation of this rule is considered cheating.
 
-\subsection{Application track}
-
-\header{Benchmark sources.}
+\header{Pseudo-random numbers.}
 %
-Benchmarks for the application track will be collected by the SMT-COMP
-organizers.  Any benchmark available to the organizers by {\bf May~1,
-  2015} will be considered eligible.
-
-\header{Benchmark availability.}
-A first release of the application track
-benchmarks will be made available as soon after the benchmark deadline as the organizers can arrange.
-No additional
-benchmarks will be added after this date, but benchmarks can be
-modified or removed to fix possible bugs or other issues.
-The final selection that will be used for the competition will be posted when the competition begins.
-
-\header{Benchmark demographics and selection.}
-A random selection of all the available benchmarks will be used for the competition.
-As was the case in 2012, no difficulty will be assigned to the benchmarks for the application track.
-Benchmarks will be slightly scrambled before the competition, using the same scrambler and
-random seed as the main track.
-If the organizers determine that there is adequate time to complete the competition, all of the benchmarks will be used.
-Otherwise an unbiased random subset will be used to ensure timely completion of the competition.
+Pseudo-random numbers used, e.g., for the creation of heats or the
+scrambling of benchmarks, will be generated using the standard C
+library function \texttt{random()}, seeded (using \texttt{srandom()})
+with the sum, modulo $2^{30}$, of the integer numbers provided in the
+system descriptions (see Section~\ref{sec:entrants}) by all SMT-COMP
+entrants other than the organizers'.  Additionally, the integer part
+of the opening value of the New York Stock Exchange Composite Index on
+the first day the exchange is open on or after the date specified in
+the timeline (Section~\ref{sec:important}) will be added to the other
+seeding values.  This helps provide transparency, by guaranteeing that
+the organizers cannot manipulate the seed in favor of or against any
+particular submitted solver.
 
@@
 \section{Scoring}
-\label{sec:scoring}
 
@@
 winners will be declared only for \emph{competitive} divisions.  A
-division is competitive if at least two substantially different
-solvers (i.e., solvers from two different teams) were submitted.
-Although the organizers may enter other solvers for comparison
-purposes, only solvers that are explicitly submitted by their authors
-determine whether a division is competitive, and are eligible to be
-designated as winners.
+division in a track is competitive if at least two substantially
+different solvers (i.e., solvers from two different teams) were
+submitted.  Although the organizers may enter other solvers for
+comparison purposes, only solvers that are explicitly submitted by
+their authors determine whether a division is competitive, and are
+eligible to be designated as winners.
+
+Divisions for floating-point arithmetic are experimental in 2015, and
+will not be considered competitive.
 
 \subsection{Benchmark scoring}
+\label{sec:benchmark-scoring}
 
-A solver's score for each benchmark is a quadruple $\langle e, n, w,
-c\rangle$, with $e \in \{0, 1\}$ the number of erroneous results
-(usually~$e = 0$), $n \in [0,N]$ an integral number of points scored
-for the benchmark, where $N$ is the number of \akey{check-sat}
-commands in the benchmark, $c \in [0,4T]$ is the (real-valued) CPU
-time in seconds, and $w \in [0,T]$ is the (real-valued) wall-clock
-time in seconds, where $T$ is the timeout.  Recall that main track
-benchmarks will have just one \akey{check-sat} command; application
-track benchmarks may have multiple \akey{check-sat} commands.
+A solver's \emph{raw score} for each benchmark is a quadruple $\langle
+e, n, w, c\rangle$, with $e \in \{0, 1\}$ the number of erroneous
+results (usually~$e = 0$), $0 \leq n \leq N$ the number of correct
+results,\footnote{Here, $N$ is the number of \akey{check-sat} commands
+  in the benchmark.  Recall that main track benchmarks have just one
+  \akey{check-sat} command; application track benchmarks may have
+  multiple \akey{check-sat} commands.} $w \in [0,T]$ the (real-valued)
+wall-clock time in seconds, and $c \in [0, 4T]$ the (real-valued) CPU
+time in seconds, measured across all cores and sub-processes, until
+the solver process terminates.
 
-\header{Main track.}
+\header{Main track.} More specifically, for the main track, we have
 %
-\remark{Clarify how $\langle e, n, c, w\rangle$ depend on solver
-  behavior.}
+\begin{itemize}
+\item $e=0$, $n=0$ if the solver times out, or the solver aborts
+  without a response, or the result of the \akey{check-sat} command is
+  {\tt unknown},
+\item $e=0$, $n=1$ if the solver does not time out, and the result of
+  the \akey{check-sat} command is correct,
+\item $e=1$, $n=0$ if the solver does not time out, and the result of
+  the \akey{check-sat} command is incorrect.
+\end{itemize}
+%
+Note that for a (correct or incorrect) result to be taken into
+consideration, the solver process must terminate (normally or
+abnormally) within the time limit.
 
@@
 %
-An application benchmark may have multiple check-sat commands and may
-partially solve the benchmark before timing out.  The benchmark is run
-by the benchmark executor, measuring the total time (summed over all
-individual commands) taken by the solver to respond to commands. It is
-expected that nearly all of this time will be in response to
-\akey{check-sat} commands, but \akey{assert}, \akey{push} or
-\akey{pop} commands might also entail a reasonable amount of
-processing.
-%% \begin{itemize}
-%% \item If the solver completes the benchmark without timing out, the
-%%   solver receives a score of $\langle e,n,m\rangle$, where $e$ is the
-%%   number of erroneous responses to commands, $n$ is the number of
-%%   correct responses to check-sat commands, and $m$ is the CPU time
-%%   taken.
-%% \item If the solver times out while processing the benchmark, the
-%%   solver receives a score of $\langle e,n,m\rangle$, where $e$ is the
-%%   number of erroneous responses to commands, $n$ is the number of
-%%   correct responses to check-sat commands before timing out, and $m$
-%%   is equal to the timeout value.
-%% \end{itemize}
+An application benchmark may contain multiple \akey{check-sat}
+commands.  Solvers may partially solve the benchmark before timing
+out.  The benchmark is run by the trace executor, measuring the total
+time (summed over all individual commands) taken by the solver to
+respond to commands.\footnote{Times measured by StarExec may include
+  time spent in the trace executor.  We expect that this time will
+  likely be insignificant compared to time spent in the solver, and
+  nearly constant across solvers.}  Most time will likely be spent in
+response to \akey{check-sat} commands, but \akey{assert}, \akey{push}
+or \akey{pop} commands might also entail a reasonable amount of
+processing.  For the application track, we have
+\begin{itemize}
+\item $e=1$, $n=0$ if the solver returns an incorrect result for any
+  \akey{check-sat} command within the time limit,
+\item otherwise, $e=0$, and $n$ is the number of correct results for
+  \akey{check-sat} commands returned by the solver before the time
+  limit is reached.
+\end{itemize}
+
+\subsection{Sequential performance}
+\label{sec:sequential}
+
+SMT-COMP has traditionally emphasized sequential performance (i.e.,
+CPU time) over parallel performance (i.e., wall-clock time).  StarExec
+is measuring both, and we intend to recognize both best sequential and
+best parallel solvers in all competitive main track divisions.
+
+The raw score, as defined in Section~\ref{sec:benchmark-scoring},
+favors parallel solvers, which may utilize all available processor
+cores.  To evaluate sequential performance, we derive a
+\emph{sequential score} by imposing a (virtual) CPU time limit equal
+to the wall-clock time limit~$T$.  A solver result is taken into
+consideration for the sequential score only if the solver process
+terminates within this CPU time limit.  More specifically, for a given
+raw score $\langle e, n, w, c\rangle$, the corresponding sequential
+score is defined as~$\langle e_S, n_S, c_S\rangle$, where
+\begin{itemize}
+\item $e_S = 0$ and $n_S = 0$ if $c > T$, $e_S = e$ and $n_S = n$
+  otherwise,
+\item $c_S = \min\ \{c, T\}$.\footnote{\emph{Rationale:} Under this
+  score, a solver should not benefit from using multiple processor
+  cores.  Conceptually, the sequential score should be (nearly)
+  unchanged if the solver was run on a single-core processor, up to a
+  time limit of~$T$.}
+\end{itemize}
 
 \subsection{Division scoring}
+\label{sec:division-scoring}
 
@@
 benchmark scores for all benchmarks in the division are summed
-component-wise.  Total scores are compared lexicographically: a score
-$\langle e, n, w, c\rangle$ is better than $\langle e', n', w',
-c'\rangle$ iff $e < e'$ or ($e = e'$ and $n > n'$) or ($e = e'$ and $n
-= n'$ and $w < w'$) or ($e = e'$ and $n = n'$ and $w = w'$ and $c <
-c'$).  That is, fewer errors takes precedence over more correct
-solutions, which takes precedence over less wall-clock time taken,
-which takes precedence over less CPU time taken.
+component-wise.  For main track divisions, we will separately compute
+the sum of all raw scores (Section~\ref{sec:benchmark-scoring}) to
+assess parallel performance, and the sum of all sequential scores
+(Section~\ref{sec:sequential}) to assess sequential performance.  For
+application track divisions, division scores will be based on raw
+scores.\footnote{Since application track benchmarks may be partially
+  solved, defining a useful sequential score for the application track
+  would require information not provided by the raw score, e.g.,
+  detailed timing information for each result.}
 
-\subsection{Competition-wide scoring (main track)}
+Division scores are compared lexicographically:
+\begin{itemize}
+\item A sum of raw scores $\langle e, n, w, c\rangle$ is better than
+  $\langle e', n', w', c'\rangle$ iff $e < e'$ or ($e = e'$ and $n >
+  n'$) or ($e = e'$ and $n = n'$ and $w < w'$) or ($e = e'$ and $n =
+  n'$ and $w = w'$ and $c < c'$).  That is, fewer errors takes
+  precedence over more correct solutions, which takes precedence over
+  less wall-clock time taken, which takes precedence over less CPU
+  time taken.
+\item A sum of sequential scores $\langle e_S, n_S, c_S\rangle$ is
+  better than $\langle e_S', n_S', c_S'\rangle$ iff $e_S < e_S'$ or
+  ($e_S = e_S'$ and $n_S > n_S'$) or ($e_S = e_S'$ and $n_S = n_S'$
+  and $c_S < c_S'$).  That is, fewer errors takes precedence over more
+  correct solutions, which takes precedence over less CPU time taken.
+\end{itemize}
+%
+We will not make any comparisons between raw scores and sequential
+scores, as these are intended to measure fundamentally different
+performance characteristics.
 
-We define a competition-wide metric for the main track as follows.
-Let $B_i$ be the total number of benchmarks in division~$i$ that were
-used in the competition, and let $\langle e_i, n_i, w_i, c_i\rangle$
-be a solver's score for this division.  The solver's competition-wide
-score is $\sum_i (e_i == 0 ? (n_i/N_i)^2 : -e_i) \log N_i$, where the
-sum is over all \emph{competitive} divisions into which the solver was
-entered.  \remark{Rationale.}
+\subsection{Competition-wide scoring}
 
-%% {\em Rationale.} The metric M purposely emphasizes breadth of solver
-%% participation---a solver participating in many logics need not be the
-%% best in any one of them.  The use of the square in the metric limits
-%% that somewhat---a solver still needs to do reasonably well compared to
-%% winners to be able to catch up by breadth of participation.  The
-%% non-linear metric also gives added weight to completing close to all
-%% benchmarks in a division.  The metric is also quite simple and the
-%% metric for a solver is independent of the performance of other
-%% solvers.  Time is omitted from the metric both to simplify the metric
-%% and because it is only of third importance in the regular competition
-%% metric and is difficult to compare across divisions.
-
-\subsection{Sequential performance}
-
-SMT-COMP has traditionally emphasized sequential performance (i.e.,
-CPU time) over parallel performance (i.e., wall-clock time).
-Accordingly, we will recognize the best \emph{sequential} solver, both
-in each division and according to the competition-wide metric (for the
-main track).  A solver is eligible for this recognition if, for each
-benchmark in the division, the solver's CPU time does not exceed its
-wall-clock time.
+We define a competition-wide metric for the main track, separately for
+parallel and sequential performance, as follows.  Let $N_i$ be the
+total number of benchmarks in division~$i$ that were used in the
+competition, and let $\langle e_i, n_i, w_i, c_i\rangle$ be a solver's
+raw score for this division (Section~\ref{sec:division-scoring}).  The
+solver's competition-wide raw score is $\sum_i (e_i == 0 \,?\,
+(n_i/N_i)^2 : -e_i) \log N_i$, where the sum is over all competitive
+divisions into which the solver was
+entered.\footnote{\emph{Rationale:} This metric purposely emphasizes
+  breadth of solver participation---a solver participating in many
+  logics need not be the best in any one of them.  The use of the
+  square in the metric limits that somewhat---a solver still needs to
+  do reasonably well compared to winners to be able to catch up by
+  breadth of participation.  The non-linear metric also gives added
+  weight to completing close to all benchmarks in a division.  The log
+  scaling is a (somewhat arbitrary) means to adjust the scores for the
+  wide variety of numbers of benchmarks in different divisions.  It
+  seems a reasonable compromise between linearly combining numbers of
+  benchmarks, which would overweigh large divisions, and simply
+  summing the fraction of benchmarks solved, which would overweigh
+  small divisions.  The metric is also quite simple, and the metric
+  for a solver is independent of the performance of other solvers.
+  Time is omitted from the metric because it is only of third
+  importance in the regular competition metric, and is difficult to
+  compare across divisions.}  The solver's competition-wide sequential
+score is computed from its sequential division scores
+(Section~\ref{sec:division-scoring}) according to the same formula.
+We will recognize the best three solvers according to these metrics.
 
@@
 \begin{itemize}
-\item {\em Open source}. In addition to recognizing the overall winner
-  in each division, the top solver that provides its source code as
-  open source will also be recognized in each division.
+\item \emph{Open source.}  The top solver that provides its source
+  code as open source will be recognized in each competitive division.
+\item \emph{Best industrial performance.}  There is agreement in the
+  SMT community to emphasize problems that come from real
+  applications.  The solver that performs best on industrial
+  benchmarks, as measured by the division scoring restricted to this
+  benchmark category, will be recognized in each competitive division.
 \item {\em Best new entrant}. The best performing entrant from a new
-  solver implementation team, as measured by the Olympic Games metric
-  defined below.
-\item {\em Breadth of logics}. Tools that cover the most theories and
-  logics.
+  solver implementation team, as measured by the competition-wide
+  metric.
+\item {\em Breadth of logics}. Solvers that cover the most theories
+  and logics.
 \item {\em Benchmarks}. Contributors of new benchmarks.
@@
 
-Many others have contributed benchmarks, effort, and feedback.
-\remark{Specific individuals will be named later.}
-% In particular, Clark Barrett processed the many benchmark
-% submissions.
-The competition uses the \href{https://www.starexec.org/}{StarExec}
-service, which is hosted at the
-\href{http://www.cs.uiowa.edu/}{University of Iowa}.  Aaron Stump is
-providing essential StarExec support.
+Many others have contributed benchmarks, effort, and feedback.  Clark
+Barrett processed the newly submitted benchmarks.  The competition
+uses the \href{https://www.starexec.org/}{StarExec} service, which is
+hosted at the \href{http://www.cs.uiowa.edu/}{University of Iowa}.
+Aaron Stump is providing essential StarExec support.
 

### 2015-05-21 rules/rules15.tex
Pointed out new computation of accumulated run-time, which now takes unsolved benchmarks into account.
Main track post-processor renamed. Benchmarks that use bit-vector division excluded.

@@
   main track divisions, using different CPU time limits.
+\item The division scoring will take time spent on unsolved benchmarks
+  into account.  Previous competitions only considered time spent on
+  solved benchmarks.  However, the number of solved benchmarks still
+  takes precedence over run-time.
 \item In addition to recognizing the best solver in each division, we
@@
 
-The main track competition uses a StarExec postprocessor (named ``SMT2
-results conserv") to accumulate the results.
+The main track competition uses a StarExec post-processor (named
+``SMT-COMP 2015 Main Track Postprocessor") to accumulate the results.
 
@@
   organizers may remove from the eligibility pool certain benchmarks
-  that are inappropriate or uninteresting for competition, or cut the
-  size of certain benchmark families to avoid their
-  over-representation.
+  that are inappropriate\footnote{In 2015, this (again) includes all
+    benchmarks that use bit-vector division or remainder, because of
+    an unresolved discussion about the semantics of division by zero.}
+  or uninteresting for competition, or cut the size of certain
+  benchmark families to avoid their over-representation.
 \item \emph{Eliminate benchmarks whose status is unknown.} Any

### 2015-05-31 rules/rules15.tex
Postprocessor: name fixed.
David's email address updated.

@@
 Brazil \\
-{\small\href{mailto:David.Deharbe@loria.fr}{\tt David.Deharbe@loria.fr}} \\
+{\small\href{mailto:david@dimap.ufrn.br}{\tt david@dimap.ufrn.br}} \\
 \and
@@
 The main track competition uses a StarExec post-processor (named
-``SMT-COMP 2015 Main Track Postprocessor") to accumulate the results.
+``SMTCOMP2015") to accumulate the results.
 

### 2015-06-07 rules/rules15.tex
(exit) command optional.

@@
 \item In the application track, there are one or more \akey{check-sat}
-  commands, each preceded by one or more \akey{assert} commands; there
-  may also be zero or more \akey{push 1} commands, and zero or more
-  \akey{pop 1} commands, consistent with the uses of those commands in
-  the SMT-LIB standard. Each \akey{check-sat} command may be preceded
-  by a \akey{set-info :status} command that indicates the expected
-  result of the \akey{check-sat} command.
-\item The $\akey{exit}$ command is the last command.
+  commands, each preceded by one or more \akey{assert} commands.
+  There may also be zero or more \akey{push 1} commands, and zero or
+  more \akey{pop 1} commands, consistent with the uses of those
+  commands in the SMT-LIB standard. Each \akey{check-sat} command may
+  be preceded by a \akey{set-info :status} command that indicates the
+  expected result of the \akey{check-sat} command.
+\item Optionally, the script may contain an $\akey{exit}$ command as
+  its last command.
 \item The formulas in the script belong to the benchmark's logic, with

### 2015-06-16 rules/rules15.tex
(exit) is mandatory for the application track.
Post-processor renamed.

@@
   expected result of the \akey{check-sat} command.
-\item Optionally, the script may contain an $\akey{exit}$ command as
-  its last command.
+\item The script may optionally contain an $\akey{exit}$ command as
+  its last command.  In the application track, this command must not
+  be omitted.
 \item The formulas in the script belong to the benchmark's logic, with
@@
 The main track competition uses a StarExec post-processor (named
-``SMTCOMP2015") to accumulate the results.
+``SMT-COMP 2015") to accumulate the results.
 

### 2015-06-20 rules/rules15.tex
Grammar.

@@
   benchmark whose expected output is neither {\tt sat} nor {\tt unsat}
-  is removed.  There is a significant number of benchmarks with {\tt
+  is removed.  There are a significant number of benchmarks with {\tt
     unknown} status in the library; these are certainly interesting

### 2015-07-28 2014/report/SMTCOMP.tex
DRC's initial edits

@@
 
-The SAT-solving decision problem can be generalized by replacing
+The SAT decision problem can be generalized by replacing
 Boolean variables with atomic predicates built with symbols from a
@@
 resulting decision problem is called \emph{Satisfiability Modulo
-  Theories\/} (SMT). The background theories of interest arise from
+  Theories\/} ~\cite{DBLP:conf/jelia/Tinelli02}. The background theories of interest arise from
 	application domains, such as formal verification or scheduling problems, and include arrays,
@@
 The 2014 SMT Competition (SMT-COMP) continued the series of annual competitions in SMT solver capability and performance that began in 2005.
-This is the 9th competition in the series, skipping only 2013; in that year an evaluation~\cite{it:2014-017} was performed, rather than a competition.
+This is the 9th competition in the series, skipping only 2013; in that year an evaluation~\cite{it:2014-017} was performed, rather than a competition.\footnote{The evaluation did not measure solvers against each other, as in a competition.
+Rather it assessed concerns such as how the design of the competition (e.g.
+random choice of benchmarks) affects the outcome, the variety and distribution of benchmarks, and the extent to which the competition is dominated by single solvers or by a few solvers or is broadly competitive.}
 
@@
 reasoning, the SAT and CASC competitions for propositional and first-order reasoning tools, respectively,
-have spurred significant innovation in their fields~\cite{leberre+03,PSS02}.
+have spurred significant innovation in their fields~\cite{satwebsite,jarvisalo2012international,leberre+03,PSS02}.
 
@@
 
-In the succeeding sections we describe the context of the competition (\S\ref{sec:context}), its goals and organization (\S\ref{sec:goals}), timeline (\S\ref{sec:timeline}), procedure (\S\ref{sec:procedure}), participants (\S\ref{sec:participants}), benchmarks (\S\ref{sec:benchmarks}), computational infrastructure (\S\ref{sec:starexec}), results (\S\ref{sec:results}), the place of SMT-COMP in the FLoC Olympic Games (\S\ref{sec:floc}), and post-competition activities (\S\ref{sec:post}).
+In the succeeding sections we describe the context of the competition (\S\ref{sec:context}), its goals and organization (\S\ref{sec:goals}), procedure (\S\ref{sec:procedure}), participants (\S\ref{sec:participants}), benchmarks (\S\ref{sec:benchmarks}), computational infrastructure (\S\ref{sec:starexec}), results (\S\ref{sec:results}), the place of SMT-COMP in the FLoC Olympic Games (\S\ref{sec:floc}), and post-competition activities (\S\ref{sec:post}).
 Section \ref{sec:conclusions} presents observations on this competition and recommendations for the future.
 
-\section{Context of the Competition}
+\davidc{Check that the outline is still correct}
+
+\section{Context of the Competition: SMT-LIB language and benchmarks}
 \label{sec:context}
 
-The SMT Competition is a competition among SMT solvers on a set of benchmark logic problems expressed in the SMT-LIB~\cite{BarST-RR-10} language.
+The SMT Competition is a competition among SMT solvers on a set of benchmark logic problems.
 Each benchmark problem is a combination of definitions and logical assertions expressed with respect to an underlying logical theory and, perhaps, some constraints on the kinds of expressions in that theory.
-Each problem has a set of constant or function symbols; a solution to the problem is an assignment of each constant and function evaluation to values in a way that satisfies all the problem's assertions.
-That is, the task is to find a \emph{satisfying assignment} for the benchmark problem.
+For example,  the logic of linear arithmetic includes the multiplication operation, but only allows multiplication by constants.
+Each problem is a set of closed formulas over a set of constant or function symbols, possibly including quantification; a solution to the problem is an assignment of each constant and function evaluation to values in a way that satisfies all the problem's assertions.
+That is, the task is to find a \emph{satisfying assignment} for the benchmark problem or to demonstrate that there is no such assignment.
+Since the presence of quantified expressions introduces incompleteness, solvers may also produce a potential solution that may be marked as possibly incomplete.
 
@@
 Each combination of underlying theories and language constraints is a \emph{logic}.
-
-The benchmark problems are expressed in the concrete syntax defined in the SMT-LIB~(v2) standard \cite{BarST-RR-10}.
-This standard has been used since 2010; a previous version was used prior to that.
+The names of the logics as used in SMT-LIB are cryptic combinations of initials. For example, AUFLIA is the logic with a
+combination of Arrays (A), Uninterpreted Functions (UF), and linear integer arithmetic (LIA). Table \ref{logicAbbreviations} can be used to interpret these names.
+\begin{table}
+\begin{tabular}{|l|l|}
+\hline
+QF\_ & Quantifier-Free \\
+A & Arrays \\
+UF & Unidentified Functions \\
+BV & Bit-Vector \\
+L & Linear (arithmetic) \\
+N & Non-Linear (arithmetic) \\
+IA/RA/IRA & Integer/Real/Both arithmetic \\
+DL & Difference Logic \\
+\hline
+\end{tabular}
+\caption{Abbreviations used in logic names}
+\label{logicAbbreviations}
+\end{table}
+
+A competition based on benchmark problems needs a standard language in which to express those problems.
+For SMT-COMP, that language is the SMT-LIB language (cf.~\url{http://www.smtlib.org}) \cite{BarST-RR-10,BarST-SMT-10,Cok-SMTLIBTutorial-2011}.
+In 2010, a significantly reworked version of the language was agreed upon.
+This version~2 increased the flexibility and expressiveness of the language while also simplifying the syntax.
+It also includes a command language that improves the language's usefulness for interactive applications.
+In particular, the standard specifies a typed (sorted), first-order logical language for terms and formulas, a language for specifying background logical theories and logics, and a command language.
+Some other tools that process SMT-LIB~v2 are listed in the SMT-LIB web pages (cf.
+\url{http://www.smtlib.org/utilities.shtml}).
+Further revisions were discussed at the SMT Workshop 2014.
 One of the goals of the SMT Competition is to encourage use and tool implementations of the SMT-LIB standard.
-The following example illustrates part of this concrete syntax:
+
+However, it is important to note that some tools used in the competition support only a subset of SMT-LIB, leaving out some commands that are essentially syntactic sugar, 
+to simplify the burden on competing solvers.
+This subset is only informally stated, but the benchmark set only uses this subset.
+This informality did not cause problems in the competition, but it would be preferable to define this subset explicitly.
+The competition subset has been
+stable since 2010.  Requiring just a subset for competition works against the goal of 
+producing SMT-LIB-compliant solvers for users. Fortunately, most mature solvers
+have implemented nearly all of SMT-LIB. Features such as incrementality, 
+proof production, and determining unsat cores are evaluated in specialized tracks, 
+separate from the main competition. The presence of such tracks in the competition has varied from year to year.
+
+The following example illustrates part of the language's concrete syntax:
 
@@
 \lstinline{max} to the standard interpretation. The second expresses
-(the negation of) a property of this operator. The command
+the negation of a property of this operator. The command
 \lstinline{check-sat} instructs the SMT solver to check if the assertions
 are satisfiable. Here the expected result is \lstinline{unsat},
-indicating that the desired property is valid.
+indicating that the combination of the two assertions is unsatisfiable and
+so, equivalently, the desired property is valid, given the first assertion.
 
@@
 with the solver, whereby client tools may incrementally push and pop
-symbol declarations and assertions while running several
-satisfiability checks, and inspecting models or get unsatisfiability
+symbol declarations and assertions while running various
+satisfiability checks, inspecting models, or obtaining unsatisfiability
 proofs. Benchmarks problems that have more than one
 \lstinline{check-sat} command are called \emph{application} or \emph{incremental
-  benchmarks}. Not all SMT solvers support all these interaction
+  benchmarks}. Not all SMT solvers support all of these interaction
 facilities, and the main track of the competition does not use such
@@
 \begin{tabular}{cc}
-\includegraphics[angle=270,width=.47\textwidth]{smtlib2-file-count-by-size.pdf}
+\includegraphics[width=.47\textwidth]{smtlib2-file-count-by-size.png}
 &
-\includegraphics[angle=270,width=.47\textwidth]{smtlib2-app-file-count-by-size.pdf}
+\includegraphics[width=.47\textwidth]{smtlib2-app-file-count-by-size.png}
 \\
@@
 
-SMT solvers are automated tools that seek to find a satisfying assignment for a given SMT-LIB problem, or to assure that the problem is \emph{unsatisfiable}.
+SMT \textit{solvers} are automated tools that seek a satisfying assignment for a given SMT-LIB problem, or assure that the problem is \emph{unsatisfiable}.
 Tools may not be able to solve a given problem, because, for example the tool exhausts available memory or time; a tool is permitted to answer \emph{unknown}.
@@
 The competition among tools is to create very efficient implementations of a breadth of decision procedures.
-Accordingly, SMT solvers have historically not handled logics with quantified expressions, though several solvers now do so.
+Accordingly, SMT solvers have historically not handled logics with quantified expressions, though several solvers now do so, responding to strong encouragement from industrial users to include quantification in SMT solvers.
+This can, in general, make the satisfiability problem undecidable and the solvers necessarily rely on heuristics.
+Solvers may respond that the answer to a problem is unknown; that is, although there may be a candidate satisfying value assignment, the solver cannot assure that some combination of instantiations of quantified formulas might not invalidate the assignment.
+Nevertheless, the inclusion of logics with quantification has been welcome by users.
+With SMT solvers moving to include quantification and CASC solvers moving to include types and arithmetic, we see a basis for fruitful future collaboration between these communities.
 
@@
 Since in 2014 we also had to migrate to using StarExec, we held only a main track and an application (incremental) track in the 2014 competition.
-The organizers still maintain the value of measuring the performance of solvers on new features such as model generation, unsat core determination, and proof generation, and recommend that they be reinstated in some future edition of the competition.
+The organizers still appreciate the value of measuring the performance of solvers on new features such as model generation, unsat core determination, and proof generation, and recommend that they be reinstated in some future edition of the competition.
 \item A significant change in 2014 was to increase the time-out limit for a solver processing a given benchmark from 25 minutes (in 2012) to 40 minutes.
@@
 
-\section{Competition Timeline}
-\label{sec:timeline}
-
-The preparation and execution of SMT-COMP 2014 took place over about 7 months, relying on the experience of previous competitions, the 2013 SMT Evaluation, and development activity on StarExec:
-\begin{itemize}[noitemsep]
-\item July 2013 -- Cok appointed as chair of the organizing committee.
-\item December 2013 -- D\'{e}harbe and Weber appointed as co-organizers.
-\item 21 January 2014 -- call for applications and benchmarks.
-\item 15 May 2014 -- deadline for new benchmarks; benchmarks were being corrected and curated throughout May and June, until the final solver deadline.
-\item 19 May 2014 -- revised rules posted.
-\item 1 June 2014 -- deadline for initial solver registration; final rules posted.
-\item 15 June 2014 -- deadline for final solver registration.
-\item 16 June 2014 -- computation begins.
-\item 22 June 2014 -- main track computation ends; official results posted on 27~June.
-\item 22 June 2014 -- deadline for application track solvers.
-\item 28 June 2014 -- application track computation.
-\item 17 July 2014 -- SMT Workshop at which results were announced.
-\item 21 July 2014 -- FLoC Olympic Games Awards Ceremony.
-\end{itemize}
+\paragraph{Competition Timeline}
+
+The preparation and execution of SMT-COMP 2014 took place over about 7 months,
+relying on the experience of previous competitions, the 2013 SMT Evaluation, and
+development activity on StarExec. The timeline is provided in
+table~\ref{tab:timeline} for transparency and as a guideline for forthcoming
+editions of the competition.
+
+\begin{table}
+\caption{\label{tab:timeline}Competition timeline}
+\scalebox{1}{
+\begin{tabular}{r |@{\hspace{-2.3pt}$\bullet$ \hspace{5pt}} p{.8\textwidth}}
+Jul. 2013 & Cok appointed as chair of the organizing committee\\
+Dec. 2013 & D\'{e}harbe and Weber appointed as co-organizers\\
+21 Jan. 2014 & call for applications and benchmarks\\
+15 May 2014 & deadline for new benchmarks; benchmarks were being corrected and curated throughout May and June, until the final solver deadline\\
+19 May 2014 & revised competition rules posted\\
+1 Jun. 2014 & deadline for initial solver registration; final competition rules posted\\
+15 Jun. 2014 & deadline for final solver registration\\
+16 Jun. 2014 & computation begins\\
+22 Jun. 2014 & main track computation ends; official results posted on 27~June\\
+22 Jun. 2014 & deadline for application track solvers\\
+28 Jun. 2014 & application track computation\\
+17 Jul. 2014 & SMT Workshop at which results were announced\\
+21 Jul. 2014 & FLoC Olympic Games Awards Ceremony
+\end{tabular}
+}
+\end{table}
 
@@
 A single solver-benchmark combination (job-pair) was run on a node at a given time.
-The benchmarks were scrambled; all benchmarks were run.
+The benchmarks were scrambled; all benchmarks were run, rather than just a subset.
 StarExec made about 150 nodes available for the duration of the competition.
@@
 The effect of this is discussed in \S\ref{sec:timeouts}.
-Though the memory limit was fairly generous, a small number~(202) of jobs were killed during the competition because of excessive memory use.
+Though the memory limit was fairly generous, there were still a small number~(202) of jobs that were killed during the competition because of excessive memory use.
 
@@
 
-During the testing prior to the competition beginning, different solvers exhibited different behavior on some benchmarks.
+During the testing period prior to the competition beginning, different solvers exhibited different behavior on some benchmarks.
 Investigation revealed that these differences were the result of different treatments of partial operations, divide by zero, in particular.
@@
 
-\paragraph{Invite and validate benchmark submissions.} New benchmarks are always welcome but an impending competition is a particular opportunity to encourage new submissions.
+\paragraph{Invite and validate benchmark submissions.} New benchmarks are always welcome and an impending competition is a particular opportunity to encourage new submissions.
 Benchmarks are the responsibility of SMT-LIB coordinators, not the competition organizers.
@@
 Indeed, one solver encountered a bug during the competition that was directly related to the specific, randomly-chosen scrambling used during the competition.
+The effect of the possible variations in performance caused by scrambling is expected to be balanced by the large of number of benchmarks employed in the competition to compare the solvers, as also observed in the SAT community~\cite{leberre+03}.
+Nevertheless, this point is worthy of future further investigation.
 
@@
 A job executes the cross-product of a set of solvers and a set of benchmarks.
-Because each division has different sets of solvers and benchmarks, each division was a separate job (or split into several jobs).
-This also allowed a restart of portions of the competition if a particular division was incorrectly configured or if a StarExec job stalled for some reason (both of which happened).
+Because each division has different sets of solvers and benchmarks, each division was represented by one or more jobs.
+Splitting a division into multiple jobs allowed a restart of portions of the competition if a particular division was incorrectly configured or if a StarExec job stalled for some reason (both of which happened).
 
@@
 Cairo).
-This solver is unusual in that it is a portfolio solver: based on automated learning over benchmark characteristics, it chooses among other solvers to apply to the problem at hand.
+This solver is atypical in that it is a portfolio solver: based on automated learning over benchmark characteristics, it chooses among other solvers to apply to the problem at hand.
 \item AProVe~\cite{AProVE2014} -- submitted by Carsten Fuhs (University College London)
@@
 \setlength{\tabcolsep}{1pt}
-\begin{tabular}{|l|l|c|c|c|c|c|c|c|c|c|}
+\begin{tabular}{|l@{\,\,}l|c|c|c|c|c|c|c|c|c|}
 \hline
@@
 \hline
-
 4Simp                  & U. Melbourne 	&   &   &   &   &   &   &   &   & \mark  \\
-STP-CryptoMiniSat4     & Security Res. Lab.  &   &   &   &   &   &   &   &   & \mark\\
-Kleaver	               & Imperial       &   &   &   &   &   &   &   &   & (2) \\
-raSAT  	               & JAIST          &   &   &   &   &   &   &   &   & \mark \\
-Tiffany de Wintermonte & U. Melbourne 	&   &   &   &   &   &   &   & \mark &  \\
 AbzizPortfolio         & U. Cairo       &   &   &   &   &   &   &   & \mark & (2)\\
+Alt-Ergo               & U. Paris Sud  &   &   &   & \mark &   &   &   &  &   \\
+AProVE NIA             & RWTH Aachen    &   &   &   &   &   & \mark & \mark &   & \mark \\
+ArgoLib                &   &   &   & \mark &   &   &   &   &  &   \\
+Ario                   &   & \mark & \mark &   &   &   &   &   &  &   \\
+barcelogic             & UPC            & \mark & \mark & \mark & \mark & \mark &   &   &   &   \\
+beaver                 & UC Berkeley   &   &   &   & \mark & \mark &   &   &   &   \\
 Boolector              & JKU            &   &   &   & \mark & \mark &   & \mark & \mark & (3)\\
+clsat                  & Washington U.  &   &   &   & \mark & \mark &   &   &   &   \\
 CVC/CVCLite/CVC3       & NYU, U. Iowa   & \mark & \mark & \mark & \mark & \mark & \mark & \mark & \mark & \mark \\
 CVC4	                 & NYU, U. Iowa   &   &   &   &   &   & \mark & \mark & \mark & \mark \\
-
+ExtSat                 &   &   & \mark &   &   &   &   &   &  &   \\
+Fx7                    &   &   &   & \mark &   &   &   &   &  &   \\
+HTP                    &   & \mark & \mark &   &   &   &   &   &  &   \\
+Jat                    &   &   & \mark &   &   &   &   &   &  &   \\
+Kleaver	               & Imperial       &   &   &   &   &   &   &   &   & (2) \\
+MathSAT 3,4,5          & U. Trento, FBK & \mark & \mark & \mark & \mark & \mark & \mark & \mark & \mark &   \\
 MathSat-HeavyBV        & U. Trento      &   &   &   &   &   &   &   & \mark &   \\
-MathSAT 3,4,5          & U. Trento, FBK & \mark & \mark & \mark & \mark & \mark & \mark & \mark & \mark &   \\
+MiniSMT                & U. Innsbruck   &   &   &   &   &   & \mark &   &   &   \\
+NuSMV                  & FBK &   & \mark &   &   &   &   &   &  &   \\
+OpenSMT, OpenSMT2      & U. Lugano      &   &   &   & \mark & \mark & \mark & \mark &   & \mark \\
+raSAT  	               & JAIST          &   &   &   &   &   &   &   &   & \mark \\
+Sammy                  &   & \mark &   &   &   &   &   &   &  &   \\
+Sateen                 & U. Col-Boulder & \mark & \mark & \mark & \mark & \mark &   &   &   &   \\
+SBT                    &   & \mark &   &   &   &   &   &   &  &   \\
+Simplics               & SRI & \mark &   &   &   &   &   &   &  &   \\
+simplifyingSTP         & U. Melbourne   &   &   &   &   &   & \mark &   &   &   \\
 SMTInterpol            & U. Freiburg    &   &   &   &   &   &   & \mark & \mark & \mark \\
 SONOLAR                & U. Bremen      &   &   &   &   &   & \mark & \mark & \mark & \mark \\
+Spear                  &   &   &   & \mark & \mark &   &   &   &  &   \\
 STP, STP2              & MIT            &   & \mark &   &   & \mark &   & \mark & \mark &   \\
-AProVE NIA             & RWTH Aachen    &   &   &   &   &   & \mark & \mark &   & \mark \\
-OpenSMT, OpenSMT2      & U. Lugano      &   &   &   & \mark & \mark & \mark & \mark &   & \mark \\
+STP-CryptoMiniSat4     & Security Res. Lab.  &   &   &   &   &   &   &   &   & \mark\\
+SVC	               & Stanford U.  & \mark &   &   &   &   &   &   &  &   \\
+sword                  & U. Bremen      &   &   &   & \mark & \mark &   &   &   &   \\
+test\_pmathsat         & FBK-IRST       &   &   &   &   &   & \mark &   &   &   \\
+Tiffany de Wintermonte & U. Melbourne 	&   &   &   &   &   &   &   & \mark &  \\
 veriT                  & Loria, UFRN           &   &   &   &   & \mark & \mark & \mark &   & \mark \\
+Yices, Yices2          & SRI            & \mark & \mark & \mark & \mark & \mark &   &   &   & \mark \\
 Z3                & Microsoft Res.  &   &   & \mark & \mark &   &   & \mark &   &   \\
-MiniSMT                & U. Innsbruck   &   &   &   &   &   & \mark &   &   &   \\
-simplifyingSTP         & U. Melbourne   &   &   &   &   &   & \mark &   &   &   \\
-test\_pmathsat         & FBK-IRST       &   &   &   &   &   & \mark &   &   &   \\
-barcelogic             & UPC            & \mark & \mark & \mark & \mark & \mark &   &   &   &   \\
-beaver                 & UC Berkeley   &   &   &   & \mark & \mark &   &   &   &   \\
-clsat                  & Washington U.  &   &   &   & \mark & \mark &   &   &   &   \\
-Sateen                 & U. Col-Boulder & \mark & \mark & \mark & \mark & \mark &   &   &   &   \\
-sword                  & U. Bremen      &   &   &   & \mark & \mark &   &   &   &   \\
-Yices, Yices2          & SRI            & \mark & \mark & \mark & \mark & \mark &   &   &   & \mark \\
-Spear                  &   &   &   & \mark & \mark &   &   &   &  &   \\
-Alt-Ergo               & U. Paris Sud  &   &   &   & \mark &   &   &   &  &   \\
-ArgoLib                &   &   &   & \mark &   &   &   &   &  &   \\
-Fx7                    &   &   &   & \mark &   &   &   &   &  &   \\
-Ario                   &   & \mark & \mark &   &   &   &   &   &  &   \\
-ExtSat                 &   &   & \mark &   &   &   &   &   &  &   \\
-HTP                    &   & \mark & \mark &   &   &   &   &   &  &   \\
-Jat                    &   &   & \mark &   &   &   &   &   &  &   \\
-NuSMV                  & FBK &   & \mark &   &   &   &   &   &  &   \\
-Sammy                  &   & \mark &   &   &   &   &   &   &  &   \\
-SBT                    &   & \mark &   &   &   &   &   &   &  &   \\
-Simplics               & SRI & \mark &   &   &   &   &   &   &  &   \\
-SVC	               & Stanford U.  & \mark &   &   &   &   &   &   &  &   \\
+\hline
+Total & & 11 & 11 & 9 & 13 & 12 & 10 & 11 & 11 & 18 \\
 \hline
@@
 \hline
-Participants                 & 12 & 12 & 9 & 13 & 12 & 10 & 11 & 11 & 18 \\
+Participants                 & 12 & 12 & 9 & 13 & 12 & 10 & 11 & 10 & 18 \\
 New in given year            & 12 &  4 & 4 &  6 &  2 &  6 &  1 &  4 & 5 \\
-Continuing to the next year  &  8 &  6 & 7 & 10 &  4 &  7 &  7 &  6 &  \\
+Continuing to the next year  &  8 &  6 & 7 & 10 &  4 &  7 &  7 &  6 & 10 \\
 Not ever participating again &  4 &  5 & 2 &  2 &  6 &  3 &  4 &  4 &  \\
@@
 \paragraph{History.} Table~\ref{Table:participants} shows the
- historical participation of each solver. Note that sometimes versions and names change, or there are multiple related versions from the same team.
+ historical participation of each solver.
+Note that sometimes versions and names change, or there are multiple related versions from the same team; generally speaking, though not always, a solver is improved from year to year.
 Table~\ref{Table:changes} summarizes that data in numbers of continuing participants. Except for the record turnout in
@@
 different solvers solve the benchmark and report the same result.
-However, for benchmarks already in the collection we did not have time to determine their results.
+However, for benchmarks with unknown results already in the collection we did not have time to determine their results.
 We did do this analysis after the competition was over (see~\S\ref{sec:post}).
@@
 
-A sizeable number, on the order of 30,000, of benchmarks were added during the lead up to the competition.
+A sizeable number of benchmarks, on the order of 30,000, were added during the lead up to the competition.
 Some of these were submitted in previous years but never assessed and uploaded.
@@
 
-\paragraph{Selection of benchmarks.} In addition to whether a benchmark has a known result or is trivial, there are two other factors that affect the selection of benchmarks for a competition: the benchmark's difficulty and the desire for a distribution of problems.
-
-Each benchmark is assigned a difficulty rating; in 2014, we used the time taken to solve the benchmark by the best performing solver in the 2013 SMT Evaluation.
+\paragraph{Selection of benchmarks.} Due to the mismatch between the amount of available compute time and the number of jobs to run, benchmark selection has been an historical issue for SMT-COMP.
+In addition to whether a benchmark has a known result or is trivial, the SMT-COMP organizers chose two other factors that affect the selection of benchmarks for SMT-COMP: the benchmark's difficulty and the desire for a distribution of problems.
+In 2014, the amount of available CPU time was enough to process all benchmarks on all solvers within the timeout defined in the rules.
+However this could not be anticipated, and the issues described hereafter may happen again, e.g., in case the number or difficulty of benchmarks, number of solvers, or the timeout increase significantly, or the organizers wish to compress the time-frame in which the competition is executed.
+
+Each benchmark is assigned a \emph{difficulty rating}; in 2014, we used the time taken to solve the benchmark by the best performing solver in the 2013 SMT Evaluation.
 These values were publicly available prior to the competition.
 The difficulty ratings are used to divide the benchmarks into 5 quintiles.
-The rules describe a procedure for selecting $N$ out of the eligible benchmarks for a division, with the intent of selecting roughly equal numbers, if they are available, from each of the quintiles.
-
-Benchmarks are also labeled by category: simple checks, randomly generated problems from some template (e.g., N-queens problems for various values of N), problems crafted to test a certain capability, and problems obtained from industrial applications.
+The rules describe a procedure for randomly selecting $N$ out of the eligible benchmarks for a division, with the intent of selecting roughly equal numbers, if they are available, from each of the quintiles.
+The seed for the random number generator used for selection is obtained by summing a number supplied by each solver team and the integer portion of the New York stock exchange index at its opening on the day the competition begins.
+\davidc{Check the rules}
+
+Benchmarks are also labeled by \emph{category}: simple checks, randomly generated problems from some template (e.g., N-queens problems for various values of N), problems crafted to test a certain capability, and problems obtained from industrial applications.
 The selection rules favor industrial benchmarks.
 
-%\davidc{Also want categories of benchmarks and numbers of sat or unsat}
+Another selection criterion, though not used historically, is to balance the numbers of \textit{sat} and \textit{unsat} benchmarks.
 
@@
 
-In the end, there was sufficient time to use all eligible benchmarks and no further selection was performed.
+In the end, in 2014, there was sufficient time to use all eligible benchmarks and no further selection was performed.
 The 2014 organizers did not have the data to make a principled decision on over-representation of particular problem types and so did not select on this basis either.
@@
 
-\paragraph{The SMT-LIB language.} A competition based on benchmark problems needs a standard language in which to express those problems.
-For SMT-COMP, that language is the SMT-LIB language (cf.~\url{http://www.smtlib.org}) \cite{BarST-SMT-10,Cok-SMTLIBTutorial-2011}.
-In 2010, a significantly reworked version of the language was agreed upon.
-This version~2 increased the flexibility and expressiveness of the language while also simplifying the syntax.
-It also includes a command language that improves the language's usefulness for interactive applications.
-In particular, the standard specifies a typed (sorted), first-order logical language for terms and formulas, a language for specifying background logical theories and logics, and a command language.
-Some other tools that process SMT-LIB~v2 are listed in the SMT-LIB web pages (cf.
-\url{http://www.smtlib.org/utilities.shtml}).
-Further revisions were discussed at the SMT Workshop 2014.
-
-However, it is important to note that some tools used in the competition support only a subset of SMT-LIB.
-This subset is only informally stated, but the benchmark set only uses this subset.
-This informality did not cause problems in the competition, but it would be preferable to define this subset explicitly.
-
 \section{StarExec}
@@
 StarExec consists of 192 2.4\,GHz computational nodes, running Red Hat Linux~6.3.
-Each node has 2 CPUs with 4 cores each and having either 129\,GB (32 nodes) or 258\,GB of memory (160 nodes).
+Each node has a dual-processor, quad-core CPU (model Intel Xeon CPU E5-2609 at 2.4GHz), 10240 KB cache, and either 129022\,MB (32 nodes) or 258294\,MB of memory (160 nodes).
 In competition, processes were limited to 100\,GB memory.
@@
 
+For comparison, the previous computational cluster (SMT-Exec) had just 11 nodes:
+\begin{itemize}
+\item Nine are 2.4\,GHz AMD Opteron 250s, configured for single core, 64-bit processing, 1 MB cache, 4 GB main memory
+\item Two are 2.53\,GHz Intel Xeon E5540s, configured for single core, 64-bit processing, 8 MB cache, 12 GB main memory
+\end{itemize}
+All eleven execution nodes have the same software configuration:
+\begin{itemize}
+\item Linux, kernel version 2.6.18-128.2.1.el5
+\item Red Hat Enterprise Linux Client release 5.2 (Tikanga)
+\item glibc-2.5-24.el5_2.2
+\item runtime libraries from gcc-4.1.2-42.el5
+\end{itemize}
+The raw CPU speed is not significantly different, but memory size, number of cores, and number of nodes is greatly increased.
+
 As this was the first year SMT-COMP used StarExec, a variety of tools and procedures needed to be ported to the new infrastructure.
 These included the benchmarks, the post-processor for scoring results,
-a tool to select benchmarks randomly according to the stated policies
+a tool to select benchmarks randomly according to the stated policies,
 tools for creating StarExec jobs based on selections of benchmarks and solvers,
@@
 The main issue with StarExec itself was that sometimes jobs would hang or the StarExec infrastructure would fail to make
-progress or report results correctly. Bugs in scheduling were
-fixed during the competition but are not entirely resolved. Accordingly, jobs need regular monitoring that they are making progress.
-
-Overall, however, StarExec performed its function well: evaluations of 339,714 job-pairs were completed for the competition over a period of about 9 days, not even counting the restarts necessary because of bugs or misconfigurations.
+progress or would report results incorrectly. Bugs in scheduling were
+fixed during the competition but are not entirely resolved. Accordingly, jobs need regular monitoring to insure they are making progress.
+
+Overall, however, StarExec performed its function well and the support team was responsive in fixing any difficulties: evaluations of 339,714 job-pairs were completed for the competition over a period of about 9 days, including the restarts necessary because of bugs or misconfigurations.
 
@@
 \paragraph{Effect of timeout.}
-In the main track competition, the organizers set a timeout of 40~minutes, much longer than in previous competitions (e.g., 25 minutes in 2012).
+For the main track of the competition, the organizers set a timeout of 40~minutes, much longer than in previous competitions (e.g., 25 minutes in 2012).
+The timeout values cannot be directly compared because the hardware changed as well.
+The larger timeout simply reflected the organizers' goal to allow solvers as much time as possible to complete each benchmark problem.
 A common practical question users have is how much benefit is gained by longer timeouts.
@@
 of an answer is shown in Fig.~\ref{Fig:timeouts}.
-This figure shows the number of benchmarks solved,  combined over all the solvers in the competition, with a solution time less than given timeout values, for the QF\_BV benchmark set.
+This figure shows the number of benchmarks solved, combined over all the solvers participating in the competition, with a solution time less than given timeout values, for the QF\_BV benchmark set.
 Most of the benchmarks are solved quickly: 39\% in less than a second, more than half in under 3.5 seconds,
@@
 Table~\ref{Fig:winners} shows a different view of the same data.
-Here we note the number of problems solved by each solver within a given wall-clock solution time, subject to the same caveats.
+Here we present the number of problems solved by each solver within a given wall-clock solution time, subject to the same caveats.
 The point to observe is that the winning solver changes depending on the timeout chosen.
@@
 This phenomenon could be a result of differences in engineering of the individual solvers or it could be a result of characteristics of the benchmark set.
+
+The data in Table~\ref{Fig:winners}also shows that most solvers have a similar trend in success as the timeout is increased.
+For example, most solvers solve about 50\% (ranging from 40\% to 62\%) of the benchmarks that solver solves by 2400 seconds by 1.0 second and
+about 75\% (ranging from 65\% to 79\%) of those solved by 2400 seconds by 10 seconds.
+However, some solvers, such as Boolector, are outliers: Boolector is slow off the mark - solving only 33\% and 61\% of the benchmarks it eventually solves
+by 1 second and 10 seconds, respectively, even though by 2400 seconds it solves more benchmarks than any other tool, in this division.
 
@@
 \begin{itemize}[noitemsep,nolistsep]
-\item $e_i$ be the number of benchmarks in division $i$ for which an incorrect result was produced
-\item $c_i$ be the number of benchmarks in division $i$ solved correctly
-\item $t_i$ be the total time to solve the benchmarks in division $i$ that were solved correctly
+\item $e_i$ be the number of benchmarks in division $i$ for which an incorrect result was produced (that excludes timeouts, runtime errors and \lstinline{unknown} answers);
+\item $c_i$ be the number of benchmarks in division $i$ solved correctly;
+\item $t_i$ be the total time to solve the benchmarks in division $i$ that were solved correctly;
 \item $N_i$ be the total number of benchmarks in division $i$, used in the competition.
@@
 \begin{itemize}[noitemsep,nolistsep]
-\item Metric A: The winning solver is the one with the smallest value of $\sum_i e_i \log N_i$, then the largest value of $\sum_i (c_i/N_i) \log N_i$, then the smallest value of $\sum_i t_i \log N_i$, where for a given solver the sums are over all competitive divisions in which that solver participated.
-\item Metric B: The winning solver is the one with the largest value of $\sum_i (e_i == 0\,?\,(c_i/N_i) : - e_i ) \log N_i$, then the smallest value of $\sum_i t_i \log N_i$, where for a given solver the sums are over all competitive divisions in which that solver participated.
+\item Metric A: The winning solver is the one with the smallest value of $\sum_i e_i \log N_i$, then the largest value of $\sum_i (c_i/N_i)^2 \log N_i$, then the smallest value of $\sum_i t_i \log N_i$, where for a given solver the sums are over all competitive divisions in which that solver participated.
+\item Metric B: The winning solver is the one with the largest value of $\sum_i (e_i == 0\,?\,(c_i/N_i)^2 : - e_i ) \log N_i$, then the smallest value of $\sum_i t_i \log N_i$, where for a given solver the sums are over all competitive divisions in which that solver participated.
 \end{itemize}
-Note that incorrect results are very rare, but do occur; for almost all solvers and divisions the value of $e_i$ is 0 and the competition hinges on the values of $c_i$.
+
+An important issue is how solver errors should be taken into account into the metrics.
+A solver error indicates an unsoundness in the tool, which is highly undesirable; however, highly penalizing errors may discourage new entrants whose tools are not yet mature.
+Different competitions vary on this aspect.
+For the SAT competition, an error disqualifies a tool in the category it occurs\footnote{See \url{http://satcompetition.org/2014/rules.shtml}.}.
+In contrast, in the SV-competition~\cite{svcomp-2015}, successful runs account positively towards the final score, while errors count negatively (with an increased weight).
+
+Note that incorrect results are very rare in SMT-COMP, but do occur; for almost all solvers and divisions the value of $e_i$ is 0 and the competition hinges on the values of $c_i$.
 The speed of the solver is important in two ways.
 First, if the solver is slow, it will time out before a solution is found and thus the value of $c_i$ will be lower.
-Second, if there is a tie in the number of errors and correctly solved problems, the total time taken on the correctly solved problems is used as the tie-breaker; this is a rare occurrence but does happen if, for example, all the benchmark problems in a division are solvable within the time limit.
-
-Only \emph{competitive divisions} were included in the scoring.
+Second, if there is a tie in the number of errors and correctly solved problems, the total time taken on the correctly solved problems is used as the tie-breaker (even if the solvers solve different subsets of benchmarks); this is a rare occurrence but does happen if, for example, all the benchmark problems in a division are solvable within the time limit---the only situation in the competition in which tie-breaking has been needed.
+Other competitions (e.g., SAT and SV-COMP) also award points for successful solutions and use the time to solve problems only as a tie-breaker, if at all.
+
+Only \emph{competitive divisions} were included in the scoring (although all divisions were run and results reported).
 For determining medals, a division is competitive if there are at least two officially registered, participating solvers \emph{from different teams}.
@@
 The log scaling of the scores for each division is a somewhat arbitrary means to adjust the scores for the wide variety of numbers of benchmarks.
-It seemed a reasonable compromise between linearly combining numbers of benchmarks, which would have overweighted large divisions (in the organizers' view), and simply summing the fraction of benchmarks solved correctly, which would have overweighted small divisions.
-
-These two metrics differ in how errors are treated.
+If each division is treated equally, with a score, say, of 1.0 for the division for solving all the benchmarks in the division correctly, then the benchmarks for small divisions would count significantly more toward a composite score than those of divisions with many benchmarks.
+On the other hand, counting each benchmark equally appeared to underweight the effect of a solver's effort to participate in multiple divisions.
+The log scaling seemed a reasonable compromise between linearly combining numbers of benchmarks these two extremes.
+Similarly, the square of the fraction successfully solved is an
+approximate mechanism to give more weight to solving the harder problems than the easier.
+
+Metrics A and B above differ in how errors are treated.
 If a solver has no errors, it is always better off to participate in as many divisions as possible.
@@
 \hline
-Logic & Solvers & Benchmarks & \multicolumn{2}{c|}{\pbox{1.1in}{Resolved by\\2+ solvers as}} & \multicolumn{2}{c|}{\pbox{1.1in}{Resolved by \\ 1 solver as}} & \pbox{.6in}{Still\\unknown} \\
+Logic & Solvers & {\pbox{1.1in}{Unknown\\Benchmarks}} & \multicolumn{2}{c|}{\pbox{1.1in}{Resolved by\\2+ solvers as}} & \multicolumn{2}{c|}{\pbox{1.1in}{Resolved by \\ 1 solver as}} & \pbox{.6in}{Still\\unknown} \\
  & & & sat & unsat & sat & unsat & \\
 \hline
-QF\_BV & 4 & 28138 & 8838 & 19166 & 20 & 10 & 100 \\
+AUFLIRA & 2 & 168 & 0 & 3 & 0 & 3 & 162 \\
 AUFNIRA & 2 & 468 & 0 & 23 & 0 & 23 & 422 \\
-AUFLIRA & 2 & 168 & 0 & 3 & 0 & 3 & 162 \\
 BV & 2 & 191 & 29 & 56 & 42 & 37 & 27 \\
@@
 QF\_ABV & 4 & 4190 & 3629 & 373 & 0 & 1 & 187 \\
+QF\_BV & 4 & 28138 & 8838 & 19166 & 20 & 10 & 100 \\
+QF\_IDL & 3 & 537 & 324 & 118 & 20 & 14 & 61 \\
+QF\_LIA & 3 & 1279 & 743 & 230 & 234 & 4 & 68 \\
+QF\_LRA & 2 & 208 & 127 & 25 & 44 & 8 & 4 \\
+QF\_NIA & 3 & 927 & 2 & 0 & 39 & 246 & 640 \\
+QF\_NRA & 2 & 1392 & 0 & 36 & 283 & 168 & 905 \\
+QF\_RDL & 2 & 85 & 50 & 0 & 2 & 1 & 32 \\
 QF\_UF & 3 & 4 & 0 & 3 & 0 & 1 & 0 \\
-UFBV & 2 & 191 & 17 & 49 & 51 & 44 & 30 \\
-UFIDL & 2 & 12 & 0 & 0 & 0 & 0 & 12 \\
-QF\_RDL & 2 & 85 & 50 & 0 & 2 & 1 & 32 \\
 QF\_UFLRA & 3 & 87 & 82 & 2 & 2 & 0 & 1 \\
@@
 UF & 2 & 2911 & 0 & 2 & 51 & 50 & 2808 \\
-QF\_IDL & 3 & 537 & 324 & 118 & 20 & 14 & 61 \\
-QF\_LRA & 2 & 208 & 127 & 25 & 44 & 8 & 4 \\
-QF\_LIA & 3 & 1279 & 743 & 230 & 234 & 4 & 68 \\
-QF\_NIA & 3 & 927 & 2 & 0 & 39 & 246 & 640 \\
-QF\_NRA & 2 & 1392 & 0 & 36 & 283 & 168 & 905 \\
+UFBV & 2 & 191 & 17 & 49 & 51 & 44 & 30 \\
+UFIDL & 2 & 12 & 0 & 0 & 0 & 0 & 12 \\
 UFLIA & 2 & 5499 & 0 & 1765 & 4 & 113 & 3617 \\
@@
 The competition saw a renewed interest in participation\textemdash there were record numbers of teams participating, solvers entered, teams and solvers that had never before participated, benchmarks used, and amount of computation performed.
-Although the 2014 results are not usefully comparable to previous years, the detailed performance of each solver on each benchmark from this first year using StarExec will be a solid baseline to measure improvements in the state-of-the-art of solver performance in future years.
+Although the 2014 results are not readily comparable to previous years (because of changes in benchmarks and equipement), the detailed performance of each solver on each benchmark from this first year using StarExec will be a solid baseline to measure improvements in the state-of-the-art of solver performance in future years.
+As a partial comparison, solvers that performed well in previous years are included in the this year's competition.
+However, rerunning the competition on the old hardware or on the old benchmarks was out of the scope of the organizers' task.
 
@@
 computation time be included in the evaluation metric. Omitting this time has had no effect so far because time was little used in the overall metric.
+\item The comparison to a previous years' results will now be easier because common hardware will be used and benchmark selection is simplified.
+Future organizers might also include a larger selection of the specific solver versions that were entered in previous competitions.
 \item A key improvement needed is better benchmark sets.

### 2015-07-28 2014/report/SMTCOMP.tex
typo
timeout discussion for application track

@@
 \item Red Hat Enterprise Linux Client release 5.2 (Tikanga)
-\item glibc-2.5-24.el5_2.2
+\item glibc-2.5-24.el5\_2.2
 \item runtime libraries from gcc-4.1.2-42.el5
@@
 
+We can also consider the effect of the choice of timeout on the application track.
+This effect is more complicated than for the main track since an application track benchmark can have partial results.
+For example, if a benchmark contains 100 check-sat commands, a solver may report correct answers on 0 to 100 of them prior to timing out.
+Furthermore the seven divisions that have results show very different characteristics.
+In four of the divisions (QF\_AUFLIA, QF\_UFLIA, QF\_UFLRA, UFLRA) over 90\% of the solver-benchmarks jobs were completed before the timeout; for QF\_UFLRA it was over 99\%.
+The other three divisions had much harder benchmarks.
+For example, for QF\_BF, only 1\% of solver-benchmark pairs were completely solved by 1 second and only 42\% by the timeout.
+These three divisions also have many fewer benchmarks---a few hundred, rather than several thousand.
+Changing the timeouts further might affect the results of these divisions significantly, but not those of the four divisions with many more benchmarks.
+
 \section{FLoC Olympic Games}

### 2015-07-30 2014/report/SMTCOMP.tex
Edits.
Significant reorganization of the sections

@@
 
-\davidc{Check that the outline is still correct}
-
-\section{Context of the Competition: SMT-LIB language and benchmarks}
+\davidc{Correct the outline}
+
+\section{The Competition Goals and Organization}
+\label{sec:goals}
+
+In planning the 2014 competition, the organizers' overall goal was to encourage breadth
+in the capability of SMT solvers. SMT-COMP 2014 benefited from the evaluation that was performed in 2013 and the experience of previous competitions. As a result we established the following emphases:
+\begin{itemize}
+\item In 2012 the competition was narrowed to a smaller number of more significant logics.
+In response to feedback, in 2014 we reverted to the practice of evaluating solvers in all available divisions.
+\item We ran the competition with all available, eligible benchmarks.
+To be eligible, a benchmark must be well-formed and have a known answer.
+We were able to use all benchmarks because we had nearly exclusive use of the StarExec computational cluster during the time we were executing SMT-COMP.
+This point is discussed further in \S\ref{sec:procedure}.
+\
+davidc{Correct reference? maybe to the benchmark section?}
+\item In 2012 some experimental tracks were held: parallel performance, unsat cores, and proof generation.
+The participation in those tracks was light.
+Since in 2014 we also had to migrate to using the new StarExec cluster to execute the competition, we held only a main track and an application (incremental) track in the 2014 competition.
+The organizers still appreciate the value of measuring the performance of solvers on new features such as model generation, unsat core determination, and proof generation, and recommend that they be reinstated in some future edition of the competition.
+\item A significant change in 2014 was to increase the time-out limit for a solver processing a given benchmark from 25 minutes (in 2012) to 40 minutes.
+(cf.
+section \ref{TBD}) \davidc{Add section reference}
+\item A significant result of the 2013 Evaluation was that the result of a competition was highly sensitive to the selection of benchmarks: different random selections of benchmarks resulted in different winning orders in a large fraction of samples.
+Hence, an aim for 2014 was to use as large a benchmark set as possible in the competition to minimize this effect.
+
+\end{itemize}
+
+An important difference between the 2014 competition and previous competitions was that this year's competition was executed on the StarExec cluster, described below in \S\ref{sec:starexec}.
+All the supporting tools and related procedures needed to be ported to this new framework.
+With watchful eyes by the organizers and the StarExec team, and with some debugging, the StarExec framework worked well and enabled a larger scale of competition than in previous years.
+
+\section{SMT-LIB logic, language and solvers}
 \label{sec:context}
@@
 As stated, the goal of SMT-COMP is similar to the goal of the SAT competition.
-The SMT benchmarks extend SAT by incorporating defined theories, such as the theory of arrays, or of undefined functions, or of arithmetic, or of bit-vectors.
+The SMT logic extends SAT by incorporating defined theories, such as the theory of arrays, or of undefined functions, or of arithmetic, or of bit-vectors.
 In addition, there may be constraints on the set of expressions allowed, such as only linear arithmetic, or only integer difference arithmetic.
@@
 
-The language includes commands that allow a fine-grained interaction
-with the solver, whereby client tools may incrementally push and pop
-symbol declarations and assertions while running various
-satisfiability checks, inspecting models, or obtaining unsatisfiability
-proofs. Benchmarks problems that have more than one
-\lstinline{check-sat} command are called \emph{application} or \emph{incremental
-  benchmarks}. Not all SMT solvers support all of these interaction
-facilities, and the main track of the competition does not use such
-application benchmarks.
+SMT \textit{solvers} are automated tools that seek a satisfying assignment for a given SMT-LIB problem, or assure that the problem is \emph{unsatisfiable}.
+Tools may not be able to solve a given problem, because, for example the tool exhausts available memory or time; a tool is permitted to answer \emph{unknown}.
+However, giving an incorrect answer (\emph{sat} instead of \emph{unsat}, or vice versa) is considered \emph{unsound} and a serious fault in the tool.
+
+\section{Competition Divisions and Benchmarks}
+\label{sec:benchmarks}
+
+The SMT-LIB benchmarks each belong to a specific logic.
+Each logic is one competition division.
+For each division, we ran the solvers that entered that division on the benchmarks for that division as one event in the overall competition.
+
+SMT-LIB currently defines 34 logics, shown in Table \ref{Table:benchmarks}.
+The rightmost column shows the number of benchmarks for that logic in the SMT-LIB collection.
+Two considerations may make a benchmark ineligible for a competition.
+First, the benchmark may not have a known result.
+For newly submitted benchmarks
+we made an attempt to determine the correct result of the benchmark; the SMT-LIB coordinators require that two
+different solvers solve the benchmark and report the same result.
+However, for benchmarks with unknown results already in the collection we did not have time to determine their results.
+We did do this analysis after the competition was over (see~\S\ref{sec:post}).
+
+The second consideration is that the benchmark must be \emph{non-trivial}; a benchmark is deemed trivial if all solvers managed to solve it in less than five seconds during SMT-EVAL 2013.
+
+The numbers of unknown, trivial, and remaining eligible benchmarks are shown in Table \ref{Table:benchmarks}. Note that these numbers vary widely from division to division.
 
 As of June 2014, the SMT-LIB repository contained over 130,000
-non-incremental benchmarks divided into 34 background theories, and
+main-track benchmarks divided into 34 background theories, and
 close to 10,000 incremental benchmarks distributed across 8 background
@@
 
-SMT \textit{solvers} are automated tools that seek a satisfying assignment for a given SMT-LIB problem, or assure that the problem is \emph{unsatisfiable}.
-Tools may not be able to solve a given problem, because, for example the tool exhausts available memory or time; a tool is permitted to answer \emph{unknown}.
-However, giving an incorrect answer (\emph{sat} instead of \emph{unsat}, or vice versa) is considered \emph{unsound} and a serious fault in the tool.
-
-SMT differs from the CASC competition~\cite{PSS02} in directly addressing sorted logics.
-SMT also focuses on fragments of first-order logic that are \emph{decidable}.
-For example, a subset of the benchmarks are problems in an integer-difference logic, for which there are specific decision procedures.
-The competition among tools is to create very efficient implementations of a breadth of decision procedures.
-Accordingly, SMT solvers have historically not handled logics with quantified expressions, though several solvers now do so, responding to strong encouragement from industrial users to include quantification in SMT solvers.
-This can, in general, make the satisfiability problem undecidable and the solvers necessarily rely on heuristics.
-Solvers may respond that the answer to a problem is unknown; that is, although there may be a candidate satisfying value assignment, the solver cannot assure that some combination of instantiations of quantified formulas might not invalidate the assignment.
-Nevertheless, the inclusion of logics with quantification has been welcome by users.
-With SMT solvers moving to include quantification and CASC solvers moving to include types and arithmetic, we see a basis for fruitful future collaboration between these communities.
-
-\section{The Competition Goals and Organization}
-\label{sec:goals}
-
-In planning the 2014 competition, the organizers' overall goal was to encourage breadth
-in the capability of SMT solvers. SMT-COMP 2014 benefited from the evaluation that was performed in 2013 and the experience of previous competitions. As a result we established the following emphases:
-\begin{itemize}
-\item In 2012 we narrowed the competition to a smaller number of more significant logics. In response to feedback, in 2014 we reverted to the practice of evaluating solvers in all available divisions.
-\item We ran the competition with all available benchmarks.
-To be eligible, a benchmark must be well-formed and have a known answer.
-We were able to use all benchmarks because we had nearly exclusive use of the StarExec cluster during the time we were executing SMT-COMP.
-This point is discussed further in \S\ref{sec:procedure}.
-\item In 2012 some experimental tracks were held: parallel performance, unsat cores, and proof generation.
-The participation in those tracks was light.
-Since in 2014 we also had to migrate to using StarExec, we held only a main track and an application (incremental) track in the 2014 competition.
-The organizers still appreciate the value of measuring the performance of solvers on new features such as model generation, unsat core determination, and proof generation, and recommend that they be reinstated in some future edition of the competition.
-\item A significant change in 2014 was to increase the time-out limit for a solver processing a given benchmark from 25 minutes (in 2012) to 40 minutes.
-\item A significant result of the 2013 Evaluation was that the result of a competition was highly sensitive to the selection of benchmarks: different random selections of benchmarks resulted in different winning orders in a large fraction of samples.
-Hence, an aim for 2014 was to use as large a benchmark set as possible in the competition to minimize this effect.
-
-\end{itemize}
-
-An important difference between the 2014 competition and previous competitions was that this year's competition was executed on the StarExec cluster, described below in \S\ref{sec:starexec}.
-All the supporting tools and related procedures needed to be ported to this new framework.
-With watchful eyes by the organizers and the StarExec team, and with some debugging, the StarExec framework worked well and enabled a larger scale of competition than in previous years.
-
-\paragraph{Competition Timeline}
-
-The preparation and execution of SMT-COMP 2014 took place over about 7 months,
-relying on the experience of previous competitions, the 2013 SMT Evaluation, and
-development activity on StarExec. The timeline is provided in
-table~\ref{tab:timeline} for transparency and as a guideline for forthcoming
-editions of the competition.
+A sizeable number of benchmarks, on the order of 30,000, were added during the lead up to the competition.
+Some of these were submitted in previous years but never assessed and uploaded.
+Many others were supplied by solver developers (including some competitors).
+All of them went through an iterative curation process to be sure that they were syntactically valid, appropriate metadata was included, and a correct result was established.
+(Not all of these submissions were through the competition organizers.)
+
+The SMT-LIB coordinators performed a curation step on the entire benchmark library prior to the competition, determining the actual logic to which a benchmark belonged, rather than the super-logic to which it had previously been assigned.
+This resulted in an expansion of logics with benchmarks from 23 to 34, and also created a number of divisions with only a very few benchmarks.
+Two divisions were not held because they had no eligible benchmarks.
 
 \begin{table}
-\caption{\label{tab:timeline}Competition timeline}
-\scalebox{1}{
-\begin{tabular}{r |@{\hspace{-2.3pt}$\bullet$ \hspace{5pt}} p{.8\textwidth}}
-Jul. 2013 & Cok appointed as chair of the organizing committee\\
-Dec. 2013 & D\'{e}harbe and Weber appointed as co-organizers\\
-21 Jan. 2014 & call for applications and benchmarks\\
-15 May 2014 & deadline for new benchmarks; benchmarks were being corrected and curated throughout May and June, until the final solver deadline\\
-19 May 2014 & revised competition rules posted\\
-1 Jun. 2014 & deadline for initial solver registration; final competition rules posted\\
-15 Jun. 2014 & deadline for final solver registration\\
-16 Jun. 2014 & computation begins\\
-22 Jun. 2014 & main track computation ends; official results posted on 27~June\\
-22 Jun. 2014 & deadline for application track solvers\\
-28 Jun. 2014 & application track computation\\
-17 Jul. 2014 & SMT Workshop at which results were announced\\
-21 Jul. 2014 & FLoC Olympic Games Awards Ceremony
+\caption{Numbers of main-track benchmarks.
+The second column shows the number of competitive solvers and, in square brackets, the number of demonstration-only solvers.
+Entries marked * exclude some benchmarks containing partial functions.}
+\label{Table:benchmarks}
+\centering
+\begin{tabular}{|l|r|r|r|r|r|}
+\hline
+       & \multicolumn{1}{|c|}{\# of} & \multicolumn{4}{|c|}{\# of benchmarks} \\
+ Logic & solvers & eligible & unknown  & trivial & total  \\
+\hline
+ALIA & 3+[1] & 29 & 0 & 13 & 42 \\
+AUFLIA & 3+[1] & 4 & 0 & 0 & 4\\
+AUFLIRA & 3+[1] & 10791 & 168 & 9055 & 20014 \\
+AUFNIRA & 2+[2] & 564 & 468 & 463 & 1495 \\
+BV & 2+[1] & 0 & 191 & 0 & 191 \\
+LIA & 3+[1] & 46 & 0 & 0 & 46 \\
+LRA & 3+[1] & 171 & 450 & 0 & 621\\
+NIA & 2+[1] & 9 & 0 & 0 & 9\\
+NRA & 2+[1] & 3747 & 66 & 0 & 3813 \\
+QF\_ABV & 7+[2] & 6457* & 4191 & 4423 & 15091 \\
+QF\_ALIA & 3+[2] & 97 & 0 & 29 & 126 \\
+QF\_AUFBV & 2+[2] & 37 & 0 & 0 & 37 \\
+QF\_AUFLIA & 4+[2] & 610 & 0 & 399 & 1009\\
+QF\_AX & 3+[2] & 335 & 0 & 216 & 551 \\
+QF\_BV & 8+[3] & 2488* & 28138 & 546 & 32500 \\
+QF\_IDL & 3+[1] & 1315 & 537 & 337 & 2189 \\
+QF\_LIA & 4+[3] & 4381 & 1279 & 481 & 6141 \\
+QF\_LRA & 4+[2] & 1343 & 208 & 131 & 1682\\
+QF\_NIA & 3+[1] & 8327 & 927 & 105 & 9359 \\
+QF\_NRA & 3+[1] & 10121 & 1392 & 27 & 11540 \\
+QF\_RDL & 3+[1] & 132 & 85 & 38 & 255 \\
+QF\_UF & 5+[2] & 4124 & 4 & 2522 & 6650 \\
+QF\_UFBV & 2+[2] & 31 & 0 & 0 & 31 \\
+QF\_UFIDL & 3+[1] & 311 & 0 & 130 & 441\\
+QF\_UFLIA & 4+[2] & 484 & 0 & 114 & 598 \\
+QF\_UFLRA & 4+[2] & 1176 & 87 & 367 & 1630 \\
+QF\_UFNIA & 2+[1] & 7 & 0 &0 & 7 \\
+QF\_UFNRA & 2+[1] & 32 & 11 & 0 & 43\\
+UF & 3+[1] & 2830 & 2911 & 7 & 5748 \\
+UFBV & 2+[1] & 0 & 191 & 0 & 191 \\
+UFIDL & 2+[1] & 49 & 12 & 19 & 80 \\
+UFLIA & 3+[1] & 5766 & 5499 & 873 & 12138 \\
+UFLRA & 3+[1] & 25 & 0 & 0 & 25\\
+UFNIA & 2+[1] & 1587 & 1052 & 712 & 3351 \\
+\hline
+Total & 18+[3] & 67426 & 47867 & 21007 & 137648 \\
+\hline
 \end{tabular}
-}
 \end{table}
 
-\section{Competition Procedure}
-\label{sec:procedure}
-
-The full description of the 2014 SMT Competition's rules is found in the rules document (\url{http://smtcomp.sourceforge.net/2014/rules14.pdf}).
-The document describes the procedures for determining benchmark difficulties, selecting benchmarks for competition, and judging the results.
-The preparation and execution of the competition required the following matters to be decided and executed.
-
-\paragraph{Decide the competition parameters.} We set a timeout of 40~minutes for both wall clock and CPU time; the memory limit was 100\,GB.
-A single solver-benchmark combination (job-pair) was run on a node at a given time.
-The benchmarks were scrambled; all benchmarks were run, rather than just a subset.
-StarExec made about 150 nodes available for the duration of the competition.
-The timeout setting was a notable difference in 2014; in 2013, this was set at 25~minutes.
-The effect of this is discussed in \S\ref{sec:timeouts}.
-Though the memory limit was fairly generous, there were still a small number~(202) of jobs that were killed during the competition because of excessive memory use.
-
-\paragraph{Settle any adjustments on the rules and competition timeline, with time for comment.}
-The competition rules are largely the same from year to year, but each year there are adjustments and improvements.
-Matters to be decided are the timeline for the competition, communication vehicles (including instantiating the website for the new competition), the various tracks and divisions, any adjustments to the benchmark selection procedure, the scoring rules, and policies on similar submissions and portfolio solvers.
-A novel aspect in 2014 was the need for policies regarding the FLoC Olympic Games~\cite{FLoCGames}, described in \S\ref{sec:floc}.
-During the competition, the organizers had to rule on two issues.
-\begin{itemize}[noitemsep,nolistsep]
-\item First, whether solvers could be withdrawn from divisions after the competition began; our ruling was no, because that could raise a solver's overall performance score and could change which divisions were deemed competitive.
-This decision did affect the results of the FLoC medal competition.
-\item Second, whether a job-pair that responded with a result before the timeout limit, but did not exit until after the timeout limit, is to be considered a timeout or a correct or wrong answer; the ruling was that it is not a timeout.
-Only one benchmark was affected by this decision and the decision did not affect any winning order, just a slight change in one solver's score.
-\end{itemize}
-The organizers also received and adjudicated an appeal after the competition completed (cf.~\S\ref{sec:floc}).
-
-During the testing period prior to the competition beginning, different solvers exhibited different behavior on some benchmarks.
-Investigation revealed that these differences were the result of different treatments of partial operations, divide by zero, in particular.
-The question is what should be the definition of divide by zero in SMT-LIB's logic of total functions.
-This question had been discussed at length over previous years, with proposals to clarify the SMT-LIB standard.
-There was certainly not time to resolve this matter prior to the competition, not to mention correcting solvers to the agreed behavior.\footnote{The discussion this time around can be found in the archives of the \url{smtcomp-discussion@lists.sourceforge.net} mailing list, in the few days near 2014-06-16.}
-Thus, for the competition, we decided to omit all benchmarks (6060 of them, 1348 of which were otherwise eligible) that were affected by divide-by-zero behavior. This question, however, remains open.
-
-\paragraph{Invite and validate solver submissions.} The 2014 competition saw the first use of the StarExec computational cluster (cf.
-\S\ref{sec:starexec}) for executing the competition.
-Each solver had to be wrapped in appropriate scripts to be able to run in the StarExec environment.
-Though this was largely the responsibility of the solver submitter, teams submitting solvers for the first time required guidance and assistance from the organizers and the StarExec development team.
-This was a significant hurdle; not all solver teams were able to complete it in time.
-The most significant problem was the need to create a fully statically linked version of the solver that ran on the particular version of Linux used by StarExec.
-The organizers stipulated a first solver submission deadline and a final solver submission deadline, separated by two weeks, to enable (and encourage) trials and debugging of solver submissions.
-
-Solver submissions comprise the solver itself, a short system description outlining what is new or novel about the solver, and an integer seed.
-All the submitted seeds and an additional seed derived from a value unknowable until after the solver submission deadline were summed and used as the starting seed for any pseudo-random selection and scrambling processes (see below) in the competition.
-
-\paragraph{Invite and validate benchmark submissions.} New benchmarks are always welcome and an impending competition is a particular opportunity to encourage new submissions.
-Benchmarks are the responsibility of SMT-LIB coordinators, not the competition organizers.
-Nevertheless, the organizers worked with the coordinators to ensure that new benchmarks were included in SMT-LIB in time for the competition.
-Initial submissions are often incomplete; to be useful they must be syntactically correct, include a designation of the logic in which they fit, contain relevant metadata about the source and category of the benchmark, and have a known, validated answer.
-Benchmarks with unknown answers may also be interesting and worth keeping, but cannot be used in the competition.
-
-\paragraph{Create an appropriate selection of benchmarks.} Not all benchmarks in the SMT-LIB database are necessarily used in the competition.
-The details of this selection, as executed for the 2014 competition, are described in \S\ref{sec:benchmarks}.
-Part of the work in preparing the competition to run on the StarExec cluster was to port the benchmark selector to StarExec.
-
-\paragraph{Prepare the benchmark scrambler.} All the benchmarks are public and known to the solver developers beforehand.
-Indeed, part of the point of the benchmark database is to serve as a testbed for solver development, outside of competitions.
-However, that raises the possibility that a solver will recognize a benchmark problem by its syntactic structure and look up an answer from a learned database, without doing any logic solving.
-This is explicitly considered cheating.
-As a slight impediment against such behavior, the benchmarks are individually scrambled before being presented to a solver, using the random seed described above.
-For 2014, the benchmark scrambler had to be ported to StarExec.
-
-The scrambling does not change the semantic meaning of the benchmark.
-It does rename identifiers, alter the order of assertions and the position of the arguments in the application of associative-commutative operators.
-
-The scrambling had another effect, previously unappreciated.
-Although most of the solvers are deterministic for a given input, scrambling can change the order of search.
-For example, iterating over the contents of a hashed set may occur in a different order if identifiers have different names.
-Consequently, the success of the solver on a given benchmark, the time it takes to find an answer, and even whether a latent bug in the solver is triggered may all depend on just how the benchmark is scrambled.
-Thus the scrambling adds a measure of uncertainty to the competition and prevents full testing on the benchmark set before the competition.
-Indeed, one solver encountered a bug during the competition that was directly related to the specific, randomly-chosen scrambling used during the competition.
-The effect of the possible variations in performance caused by scrambling is expected to be balanced by the large of number of benchmarks employed in the competition to compare the solvers, as also observed in the SAT community~\cite{leberre+03}.
-Nevertheless, this point is worthy of future further investigation.
-
-\paragraph{Prepare the real-time results display.} The participants are interested in the progress of the competition as it proceeds.
-The organizers also need to know if the competition is proceeding correctly and at a reasonable pace.
-As the competition takes several days, an automatic real-time display of results is helpful and encourages interest.
-StarExec does not have such a facility, since different competitions have different needs.
-Instead the organizers used StarExec's command-line API to regularly (every 10 minutes or so) download the status of all of the executing jobs, extract the results for each solver-benchmark pair, create HTML web pages displaying the current status, and upload them to the competition website.
-The current (now final) status of each division and a summary page can be seen at \url{http://smtcomp.sourceforge.net/2014/results-toc.shtml}.
-
-\paragraph{Execute the competition.} Executing the competition required preparing a StarExec job for each
-division.
-A job executes the cross-product of a set of solvers and a set of benchmarks.
-Because each division has different sets of solvers and benchmarks, each division was represented by one or more jobs.
-Splitting a division into multiple jobs allowed a restart of portions of the competition if a particular division was incorrectly configured or if a StarExec job stalled for some reason (both of which happened).
-
-In addition, with the new cluster, the new benchmarks, and a longer timeout period, the organizers were unsure how long the competition would take.
-Our conservative estimate was that a month of computing was needed; in fact it only took about a week, because we had three times more StarExec nodes available than anticipated and jobs took on average less time than estimated.
-However, to hedge against the competition taking longer than anticipated, we divided larger divisions into \emph{heats}, with each heat comprising about 1000 benchmarks, and with the option (stated in the rules) to terminate the competition before all heats were executed to ensure a timely end prior to FLoC.
-This required handling a much larger number of StarExec jobs.
-In the end it was entirely unnecessary for timely completion, but, as mentioned, dividing the jobs into manageable pieces was useful for restarting portions of the computation when StarExec stalled.\footnote{Stalling---that is, no longer making forward progress on a job---was less a concern after some bug fixes during the competition, but was still observed during some post-competition computations.}
-
-In past competitions, the competition was timed to have its last portion overlap with the conference with which it was affiliated.
-In 2014, because the computation took less time than anticipated, the competition finished well before the conference.
-
-\paragraph{Report the results.} The results of the competition were reported at the SMT Workshop and in this paper.
+Solvers could participate in any or all divisions at their team's discretion.
+Most solvers are designed for just one selected logic, but others are intended to be as broadly applicable as their developers have had time to implement.
+Table~\ref{Table:logics} shows the participation of solvers in various divisions.
+
+\begin{sidewaystable}
+\caption{Solver participation in logic divisions}
+\label{Table:logics}
+\centering
+\renewcommand{\mark}[0]{\ding{51}}
+%%\small
+\setlength\tabcolsep{3pt}
+%%\begin{tabular}{|l|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|}
+\begin{tabular}{|l|ccccc|cccc|cccccc|cccccc|ccccccc|cccccc|}
+\hline
+Solver & 	\rot{ALIA} & 	\rot{AUFLIA} & 	\rot{AUFLIRA} & 	\rot{AUFNIRA} & 	\rot{BV} & 	\rot{LIA} & 	\rot{LRA} & 	\rot{NIA} & 	\rot{NRA} & 	\rot{QF\_ABV} & 	\rot{QF\_ALIA} & 	\rot{QF\_AUFBV} & 	\rot{QF\_AUFLIA} & 	\rot{QF\_AX} & 	\rot{QF\_BV} & 	\rot{QF\_IDL} & 	\rot{QF\_LIA} & 	\rot{QF\_LRA} & 	\rot{QF\_NIA} & 	\rot{QF\_NRA} & 	\rot{QF\_RDL} & 	\rot{QF\_UF} & 	\rot{QF\_UFBV} & 	\rot{QF\_UFIDL} & 	\rot{QF\_UFLIA} & 	\rot{QF\_UFLRA} & 	\rot{QF\_UFNIA} & 	\rot{QF\_UFNRA} & 	\rot{UF} & 	\rot{UFBV} & 	\rot{UFIDL} & 	\rot{UFLIA} & 	\rot{UFLRA} & 	\rot{UFNIA} \\
+\hline
+4Simp & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	\mark & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 \\
+Abziz & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	\mark & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 \\
+Abziz2 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	\mark & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 \\
+AProVE & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	\mark & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 \\
+Boolector & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	\mark & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 \\
+Boolector-d & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	\mark & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 \\
+Boolector-j & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	\mark & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 \\
+CVC3 & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	\mark & 	\mark & 	 & 	 & 	 & 	 & 	 & 	 & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark \\
+CVC4 & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark \\
+Kleaver-STP & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	\mark & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 \\
+Kleaver-portfolio & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	\mark & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 \\
+OpenSMT2 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	\mark & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 \\
+raSAT & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	\mark & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 \\
+SMTInterpol & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	\mark & 	&	\mark & 	\mark & 	 & 	 & 	\mark & 	\mark & 	 & 	 & 	 & 	\mark & 	 & 	 & 	\mark & 	\mark & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 \\
+SONOLAR & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	\mark & 	 & 	 & 	 & 	 & 	\mark & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 \\
+STP-Crypto... & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	\mark & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 \\
+veriT & 	\mark & 	\mark & 	\mark & 	 & 	 & 	\mark & 	\mark & 	 & 	 & 	 & 	 & 	 & 	\mark & 	& &		\mark & 	\mark & 	\mark & 	 & 	 & 	\mark & 	\mark & 	&	\mark & 	\mark & 	\mark & 	 & 	 & 	\mark & 	 & 	 & 	\mark & 	\mark &   \\
+Yices2 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	 & 	 & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 \\
+\hline
+{[}MathSAT5] & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	 & 	\mark & 	\mark & 	 & 	 & 	 & 	\mark & 	\mark & 	 & 	\mark & 	\mark & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 \\
+{[}Z3] & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark \\
+{[}CVC4-with-bugfix] &  &  &  & \mark &  &  &  &  &  &  &  &  &  &  & \mark &  & \mark &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  \\
+\hline
+\end{tabular}
+\end{sidewaystable}
+
+\paragraph{Application benchmarks.} The language includes commands that allow a fine-grained interaction
+with the solver, whereby client tools may incrementally push and pop
+symbol declarations and assertions while running various
+satisfiability checks, inspecting models, or obtaining unsatisfiability
+proofs. Benchmarks problems that have more than one
+\lstinline{check-sat} command are called \emph{application} or \emph{incremental
+  benchmarks}. Not all SMT solvers support all of these interaction
+facilities, and the main track of the competition does not use such
+application benchmarks.
+
+\paragraph{Selection of benchmarks.} Due to the mismatch between the amount of available compute time and the number of jobs to run, benchmark selection has been an historical issue for SMT-COMP.
+In addition to whether a benchmark has a known result or is trivial, the SMT-COMP organizers chose two other factors that affect the selection of benchmarks for SMT-COMP: the benchmark's difficulty and the desire for a distribution of problems.
+In 2014, the amount of available CPU time was enough to process all benchmarks on all solvers within the timeout defined in the rules.
+However this could not be anticipated, and the issues described hereafter may happen again, e.g., in case the number or difficulty of benchmarks, number of solvers, or the timeout increase significantly, or the organizers wish to compress the time-frame in which the competition is executed.
+
+Each benchmark is assigned a \emph{difficulty rating}; in 2014, we used the time taken to solve the benchmark by the best performing solver in the 2013 SMT Evaluation.
+These values were publicly available prior to the competition.
+The difficulty ratings are used to divide the benchmarks into 5 quintiles.
+The rules describe a procedure for randomly selecting $N$ out of the eligible benchmarks for a division, with the intent of selecting roughly equal numbers, if they are available, from each of the quintiles.
+The seed for the random number generator used for selection is obtained by summing a number supplied by each solver team and the integer portion of the New York stock exchange index at its opening on the day the competition begins.
+\davidc{Check the rules}
+
+Benchmarks are also labeled by \emph{category}: simple checks, randomly generated problems from some template (e.g., N-queens problems for various values of N), problems crafted to test a certain capability, and problems obtained from industrial applications.
+The selection rules favor industrial benchmarks.
+
+Another selection criterion, though not used historically, is to balance the numbers of \textit{sat} and \textit{unsat} benchmarks.
+
+In addition, some kinds of problems may be over-represented in the benchmarks.
+This may be the case particularly because benchmarks may be submitted by solver developers; a team might add a large number of benchmarks that would then over-represent problems that a particular solver is known to handle well.
+The rules allow the organizers to limit the selections from sub-populations.
+
+In the end, in 2014, there was sufficient time to use all eligible benchmarks and no further selection was performed.
+The 2014 organizers did not have the data to make a principled decision on over-representation of particular problem types and so did not select on this basis either.
+The absence of such selection may have affected the competition results and future organizing teams should reconsider this aspect even if there are sufficient computational resources to execute all benchmarks.
+The data from SMT-COMP 2014 could be used to inform this decision.
 
@@
 
-\section{Competition Divisions and Benchmarks}
-\label{sec:benchmarks}
-
-The SMT-LIB benchmarks each belong to a specific logic.
-Each logic is one competition division.
-For each division, we ran the solvers that entered that division on the benchmarks for that division as one event in the overall competition.
-
-SMT-LIB currently defines 34 logics, shown in Table \ref{Table:benchmarks}.
-The rightmost column shows the number of benchmarks for that logic in the SMT-LIB collection.
-Two considerations may make a benchmark ineligible for a competition.
-First, the benchmark may not have a known result.
-For newly submitted benchmarks
-we made an attempt to determine the correct result of the benchmark; the SMT-LIB coordinators require that two
-different solvers solve the benchmark and report the same result.
-However, for benchmarks with unknown results already in the collection we did not have time to determine their results.
-We did do this analysis after the competition was over (see~\S\ref{sec:post}).
-
-The second consideration is that the benchmark must be \emph{non-trivial}; a benchmark is deemed trivial if all solvers managed to solve it in less than five seconds during SMT-EVAL 2013.
-
-The numbers of unknown, trivial, and remaining eligible benchmarks are shown in Table \ref{Table:benchmarks}. Note that these numbers vary widely from division to division.
-
-A sizeable number of benchmarks, on the order of 30,000, were added during the lead up to the competition.
-Some of these were submitted in previous years but never assessed and uploaded.
-Many others were supplied by solver developers (including some competitors).
-All of them went through an iterative curation process to be sure that they were syntactically valid, appropriate metadata was included, and a correct result was established.
-(Not all of these submissions were through the competition organizers.)
-
-The SMT-LIB coordinators performed a curation step on the entire benchmark library prior to the competition, determining the actual logic to which a benchmark belonged, rather than the super-logic to which it had previously been assigned.
-This resulted in an expansion of logics with benchmarks from 23 to 34, and also created a number of divisions with only a very few benchmarks.
-Two divisions were not held because they had no eligible benchmarks.
+\paragraph{Competition Timeline}
+
+The preparation and execution of SMT-COMP 2014 took place over about 7 months,
+relying on the experience of previous competitions, the 2013 SMT Evaluation, and
+development activity on StarExec. The timeline is provided in
+table~\ref{tab:timeline} for transparency and as a guideline for forthcoming
+editions of the competition.
 
 \begin{table}
-\caption{Numbers of main-track benchmarks.
-The second column shows the number of competitive solvers and, in square brackets, the number of demonstration-only solvers.
-Entries marked * exclude some benchmarks containing partial functions.}
-\label{Table:benchmarks}
-\centering
-\begin{tabular}{|l|r|r|r|r|r|}
-\hline
-       & \multicolumn{1}{|c|}{\# of} & \multicolumn{4}{|c|}{\# of benchmarks} \\
- Logic & solvers & eligible & unknown  & trivial & total  \\
-\hline
-ALIA & 3+[1] & 29 & 0 & 13 & 42 \\
-AUFLIA & 3+[1] & 4 & 0 & 0 & 4\\
-AUFLIRA & 3+[1] & 10791 & 168 & 9055 & 20014 \\
-AUFNIRA & 2+[2] & 564 & 468 & 463 & 1495 \\
-BV & 2+[1] & 0 & 191 & 0 & 191 \\
-LIA & 3+[1] & 46 & 0 & 0 & 46 \\
-LRA & 3+[1] & 171 & 450 & 0 & 621\\
-NIA & 2+[1] & 9 & 0 & 0 & 9\\
-NRA & 2+[1] & 3747 & 66 & 0 & 3813 \\
-QF\_ABV & 7+[2] & 6457* & 4191 & 4423 & 15091 \\
-QF\_ALIA & 3+[2] & 97 & 0 & 29 & 126 \\
-QF\_AUFBV & 2+[2] & 37 & 0 & 0 & 37 \\
-QF\_AUFLIA & 4+[2] & 610 & 0 & 399 & 1009\\
-QF\_AX & 3+[2] & 335 & 0 & 216 & 551 \\
-QF\_BV & 8+[3] & 2488* & 28138 & 546 & 32500 \\
-QF\_IDL & 3+[1] & 1315 & 537 & 337 & 2189 \\
-QF\_LIA & 4+[3] & 4381 & 1279 & 481 & 6141 \\
-QF\_LRA & 4+[2] & 1343 & 208 & 131 & 1682\\
-QF\_NIA & 3+[1] & 8327 & 927 & 105 & 9359 \\
-QF\_NRA & 3+[1] & 10121 & 1392 & 27 & 11540 \\
-QF\_RDL & 3+[1] & 132 & 85 & 38 & 255 \\
-QF\_UF & 5+[2] & 4124 & 4 & 2522 & 6650 \\
-QF\_UFBV & 2+[2] & 31 & 0 & 0 & 31 \\
-QF\_UFIDL & 3+[1] & 311 & 0 & 130 & 441\\
-QF\_UFLIA & 4+[2] & 484 & 0 & 114 & 598 \\
-QF\_UFLRA & 4+[2] & 1176 & 87 & 367 & 1630 \\
-QF\_UFNIA & 2+[1] & 7 & 0 &0 & 7 \\
-QF\_UFNRA & 2+[1] & 32 & 11 & 0 & 43\\
-UF & 3+[1] & 2830 & 2911 & 7 & 5748 \\
-UFBV & 2+[1] & 0 & 191 & 0 & 191 \\
-UFIDL & 2+[1] & 49 & 12 & 19 & 80 \\
-UFLIA & 3+[1] & 5766 & 5499 & 873 & 12138 \\
-UFLRA & 3+[1] & 25 & 0 & 0 & 25\\
-UFNIA & 2+[1] & 1587 & 1052 & 712 & 3351 \\
-\hline
-Total & 18+[3] & 67426 & 47867 & 21007 & 137648 \\
-\hline
+\caption{\label{tab:timeline}Competition timeline}
+\scalebox{1}{
+\begin{tabular}{r |@{\hspace{-2.3pt}$\bullet$ \hspace{5pt}} p{.8\textwidth}}
+Jul. 2013 & Cok appointed as chair of the organizing committee\\
+Dec. 2013 & D\'{e}harbe and Weber appointed as co-organizers\\
+21 Jan. 2014 & call for applications and benchmarks\\
+15 May 2014 & deadline for new benchmarks; benchmarks were being corrected and curated throughout May and June, until the final solver deadline\\
+19 May 2014 & revised competition rules posted\\
+1 Jun. 2014 & deadline for initial solver registration; final competition rules posted\\
+15 Jun. 2014 & deadline for final solver registration\\
+16 Jun. 2014 & computation begins\\
+22 Jun. 2014 & main track computation ends; official results posted on 27~June\\
+22 Jun. 2014 & deadline for application track solvers\\
+28 Jun. 2014 & application track computation\\
+17 Jul. 2014 & SMT Workshop at which results were announced\\
+21 Jul. 2014 & FLoC Olympic Games Awards Ceremony
 \end{tabular}
+}
 \end{table}
 
-Solvers could participate in any or all divisions at their team's discretion.
-Most solvers are designed for just one selected logic, but others are intended to be as broadly applicable as their developers have had time to implement.
-Table~\ref{Table:logics} shows the participation of solvers in various divisions.
-
-\begin{sidewaystable}
-\caption{Solver participation in logic divisions}
-\label{Table:logics}
-\centering
-\renewcommand{\mark}[0]{\ding{51}}
-%%\small
-\setlength\tabcolsep{3pt}
-%%\begin{tabular}{|l|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|}
-\begin{tabular}{|l|ccccc|cccc|cccccc|cccccc|ccccccc|cccccc|}
-\hline
-Solver & 	\rot{ALIA} & 	\rot{AUFLIA} & 	\rot{AUFLIRA} & 	\rot{AUFNIRA} & 	\rot{BV} & 	\rot{LIA} & 	\rot{LRA} & 	\rot{NIA} & 	\rot{NRA} & 	\rot{QF\_ABV} & 	\rot{QF\_ALIA} & 	\rot{QF\_AUFBV} & 	\rot{QF\_AUFLIA} & 	\rot{QF\_AX} & 	\rot{QF\_BV} & 	\rot{QF\_IDL} & 	\rot{QF\_LIA} & 	\rot{QF\_LRA} & 	\rot{QF\_NIA} & 	\rot{QF\_NRA} & 	\rot{QF\_RDL} & 	\rot{QF\_UF} & 	\rot{QF\_UFBV} & 	\rot{QF\_UFIDL} & 	\rot{QF\_UFLIA} & 	\rot{QF\_UFLRA} & 	\rot{QF\_UFNIA} & 	\rot{QF\_UFNRA} & 	\rot{UF} & 	\rot{UFBV} & 	\rot{UFIDL} & 	\rot{UFLIA} & 	\rot{UFLRA} & 	\rot{UFNIA} \\
-\hline
-4Simp & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	\mark & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 \\
-Abziz & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	\mark & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 \\
-Abziz2 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	\mark & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 \\
-AProVE & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	\mark & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 \\
-Boolector & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	\mark & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 \\
-Boolector-d & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	\mark & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 \\
-Boolector-j & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	\mark & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 \\
-CVC3 & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	\mark & 	\mark & 	 & 	 & 	 & 	 & 	 & 	 & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark \\
-CVC4 & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark \\
-Kleaver-STP & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	\mark & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 \\
-Kleaver-portfolio & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	\mark & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 \\
-OpenSMT2 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	\mark & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 \\
-raSAT & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	\mark & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 \\
-SMTInterpol & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	\mark & 	&	\mark & 	\mark & 	 & 	 & 	\mark & 	\mark & 	 & 	 & 	 & 	\mark & 	 & 	 & 	\mark & 	\mark & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 \\
-SONOLAR & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	\mark & 	 & 	 & 	 & 	 & 	\mark & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 \\
-STP-Crypto... & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	\mark & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 \\
-veriT & 	\mark & 	\mark & 	\mark & 	 & 	 & 	\mark & 	\mark & 	 & 	 & 	 & 	 & 	 & 	\mark & 	& &		\mark & 	\mark & 	\mark & 	 & 	 & 	\mark & 	\mark & 	&	\mark & 	\mark & 	\mark & 	 & 	 & 	\mark & 	 & 	 & 	\mark & 	\mark &   \\
-Yices2 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	 & 	 & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 \\
-\hline
-{[}MathSAT5] & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	 & 	\mark & 	\mark & 	 & 	 & 	 & 	\mark & 	\mark & 	 & 	\mark & 	\mark & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 \\
-{[}Z3] & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark \\
-{[}CVC4-with-bugfix] &  &  &  & \mark &  &  &  &  &  &  &  &  &  &  & \mark &  & \mark &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  \\
-\hline
-\end{tabular}
-\end{sidewaystable}
-
-\paragraph{Selection of benchmarks.} Due to the mismatch between the amount of available compute time and the number of jobs to run, benchmark selection has been an historical issue for SMT-COMP.
-In addition to whether a benchmark has a known result or is trivial, the SMT-COMP organizers chose two other factors that affect the selection of benchmarks for SMT-COMP: the benchmark's difficulty and the desire for a distribution of problems.
-In 2014, the amount of available CPU time was enough to process all benchmarks on all solvers within the timeout defined in the rules.
-However this could not be anticipated, and the issues described hereafter may happen again, e.g., in case the number or difficulty of benchmarks, number of solvers, or the timeout increase significantly, or the organizers wish to compress the time-frame in which the competition is executed.
-
-Each benchmark is assigned a \emph{difficulty rating}; in 2014, we used the time taken to solve the benchmark by the best performing solver in the 2013 SMT Evaluation.
-These values were publicly available prior to the competition.
-The difficulty ratings are used to divide the benchmarks into 5 quintiles.
-The rules describe a procedure for randomly selecting $N$ out of the eligible benchmarks for a division, with the intent of selecting roughly equal numbers, if they are available, from each of the quintiles.
-The seed for the random number generator used for selection is obtained by summing a number supplied by each solver team and the integer portion of the New York stock exchange index at its opening on the day the competition begins.
-\davidc{Check the rules}
-
-Benchmarks are also labeled by \emph{category}: simple checks, randomly generated problems from some template (e.g., N-queens problems for various values of N), problems crafted to test a certain capability, and problems obtained from industrial applications.
-The selection rules favor industrial benchmarks.
-
-Another selection criterion, though not used historically, is to balance the numbers of \textit{sat} and \textit{unsat} benchmarks.
-
-In addition, some kinds of problems may be over-represented in the benchmarks.
-This may be the case particularly because benchmarks may be submitted by solver developers; a team might add a large number of benchmarks that would then over-represent problems that a particular solver is known to handle well.
-The rules allow the organizers to limit the selections from sub-populations.
-
-In the end, in 2014, there was sufficient time to use all eligible benchmarks and no further selection was performed.
-The 2014 organizers did not have the data to make a principled decision on over-representation of particular problem types and so did not select on this basis either.
-The absence of such selection may have affected the competition results and future organizing teams should reconsider this aspect even if there are sufficient computational resources to execute all benchmarks.
-The data from SMT-COMP 2014 could be used to inform this decision.
+\section{Competition Procedure}
+\label{sec:procedure}
+
+The full description of the 2014 SMT Competition's rules is found in the rules document (\url{http://smtcomp.sourceforge.net/2014/rules14.pdf}).
+The document describes the procedures for determining benchmark difficulties, selecting benchmarks for competition, and judging the results.
+The preparation and execution of the competition required the following matters to be decided and executed.
+
+\paragraph{Decide the competition parameters.} We set a timeout of 40~minutes for both wall clock and CPU time; the memory limit was 100\,GB.
+A single solver-benchmark combination (job-pair) was run on a node at a given time.
+The benchmarks were scrambled; all benchmarks were run, rather than just a subset.
+StarExec made about 150 nodes available for the duration of the competition.
+The timeout setting was a notable difference in 2014; in 2013, this was set at 25~minutes.
+The effect of this is discussed in \S\ref{sec:timeouts}.
+Though the memory limit was fairly generous, there were still a small number~(202) of jobs that were killed during the competition because of excessive memory use.
+
+\paragraph{Settle any adjustments on the rules and competition timeline, with time for comment.}
+The competition rules are largely the same from year to year, but each year there are adjustments and improvements.
+Matters to be decided are the timeline for the competition, communication vehicles (including instantiating the website for the new competition), the various tracks and divisions, any adjustments to the benchmark selection procedure, the scoring rules, and policies on similar submissions and portfolio solvers.
+A novel aspect in 2014 was the need for policies regarding the FLoC Olympic Games~\cite{FLoCGames}, described in \S\ref{sec:floc}.
+During the competition, the organizers had to rule on two issues.
+\begin{itemize}[noitemsep,nolistsep]
+\item First, whether solvers could be withdrawn from divisions after the competition began; our ruling was no, because that could raise a solver's overall performance score and could change which divisions were deemed competitive.
+This decision did affect the results of the FLoC medal competition.
+\item Second, whether a job-pair that responded with a result before the timeout limit, but did not exit until after the timeout limit, is to be considered a timeout or a correct or wrong answer; the ruling was that it is not a timeout.
+Only one benchmark was affected by this decision and the decision did not affect any winning order, just a slight change in one solver's score.
+\end{itemize}
+The organizers also received and adjudicated an appeal after the competition completed (cf.~\S\ref{sec:floc}).
+
+During the testing period prior to the competition beginning, different solvers exhibited different behavior on some benchmarks.
+Investigation revealed that these differences were the result of different treatments of partial operations, divide by zero, in particular.
+The question is what should be the definition of divide by zero in SMT-LIB's logic of total functions.
+This question had been discussed at length over previous years, with proposals to clarify the SMT-LIB standard.
+There was certainly not time to resolve this matter prior to the competition, not to mention correcting solvers to the agreed behavior.\footnote{The discussion this time around can be found in the archives of the \url{smtcomp-discussion@lists.sourceforge.net} mailing list, in the few days near 2014-06-16.}
+Thus, for the competition, we decided to omit all benchmarks (6060 of them, 1348 of which were otherwise eligible) that were affected by divide-by-zero behavior. This question, however, remains open.
+
+\paragraph{Invite and validate solver submissions.} The 2014 competition saw the first use of the StarExec computational cluster (cf.
+\S\ref{sec:starexec}) for executing the competition.
+Each solver had to be wrapped in appropriate scripts to be able to run in the StarExec environment.
+Though this was largely the responsibility of the solver submitter, teams submitting solvers for the first time required guidance and assistance from the organizers and the StarExec development team.
+This was a significant hurdle; not all solver teams were able to complete it in time.
+The most significant problem was the need to create a fully statically linked version of the solver that ran on the particular version of Linux used by StarExec.
+The organizers stipulated a first solver submission deadline and a final solver submission deadline, separated by two weeks, to enable (and encourage) trials and debugging of solver submissions.
+
+Solver submissions comprise the solver itself, a short system description outlining what is new or novel about the solver, and an integer seed.
+All the submitted seeds and an additional seed derived from a value unknowable until after the solver submission deadline were summed and used as the starting seed for any pseudo-random selection and scrambling processes (see below) in the competition.
+
+\paragraph{Invite and validate benchmark submissions.} New benchmarks are always welcome and an impending competition is a particular opportunity to encourage new submissions.
+Benchmarks are the responsibility of SMT-LIB coordinators, not the competition organizers.
+Nevertheless, the organizers worked with the coordinators to ensure that new benchmarks were included in SMT-LIB in time for the competition.
+Initial submissions are often incomplete; to be useful they must be syntactically correct, include a designation of the logic in which they fit, contain relevant metadata about the source and category of the benchmark, and have a known, validated answer.
+Benchmarks with unknown answers may also be interesting and worth keeping, but cannot be used in the competition.
+
+\paragraph{Create an appropriate selection of benchmarks.} Not all benchmarks in the SMT-LIB database are necessarily used in the competition.
+The details of this selection, as executed for the 2014 competition, are described in \S\ref{sec:benchmarks}.
+Part of the work in preparing the competition to run on the StarExec cluster was to port the benchmark selector to StarExec.
+
+\paragraph{Prepare the benchmark scrambler.} All the benchmarks are public and known to the solver developers beforehand.
+Indeed, part of the point of the benchmark database is to serve as a testbed for solver development, outside of competitions.
+However, that raises the possibility that a solver will recognize a benchmark problem by its syntactic structure and look up an answer from a learned database, without doing any logic solving.
+This is explicitly considered cheating.
+As a slight impediment against such behavior, the benchmarks are individually scrambled before being presented to a solver, using the random seed described above.
+For 2014, the benchmark scrambler had to be ported to StarExec.
+
+The scrambling does not change the semantic meaning of the benchmark.
+It does rename identifiers, alter the order of assertions and the position of the arguments in the application of associative-commutative operators.
+
+The scrambling had another effect, previously unappreciated.
+Although most of the solvers are deterministic for a given input, scrambling can change the order of search.
+For example, iterating over the contents of a hashed set may occur in a different order if identifiers have different names.
+Consequently, the success of the solver on a given benchmark, the time it takes to find an answer, and even whether a latent bug in the solver is triggered may all depend on just how the benchmark is scrambled.
+Thus the scrambling adds a measure of uncertainty to the competition and prevents full testing on the benchmark set before the competition.
+Indeed, one solver encountered a bug during the competition that was directly related to the specific, randomly-chosen scrambling used during the competition.
+The effect of the possible variations in performance caused by scrambling is expected to be balanced by the large of number of benchmarks employed in the competition to compare the solvers, as also observed in the SAT community~\cite{leberre+03}.
+Nevertheless, this point is worthy of future further investigation.
+
+\paragraph{Prepare the real-time results display.} The participants are interested in the progress of the competition as it proceeds.
+The organizers also need to know if the competition is proceeding correctly and at a reasonable pace.
+As the competition takes several days, an automatic real-time display of results is helpful and encourages interest.
+StarExec does not have such a facility, since different competitions have different needs.
+Instead the organizers used StarExec's command-line API to regularly (every 10 minutes or so) download the status of all of the executing jobs, extract the results for each solver-benchmark pair, create HTML web pages displaying the current status, and upload them to the competition website.
+The current (now final) status of each division and a summary page can be seen at \url{http://smtcomp.sourceforge.net/2014/results-toc.shtml}.
+
+\paragraph{Execute the competition.} Executing the competition required preparing a StarExec job for each
+division.
+A job executes the cross-product of a set of solvers and a set of benchmarks.
+Because each division has different sets of solvers and benchmarks, each division was represented by one or more jobs.
+Splitting a division into multiple jobs allowed a restart of portions of the competition if a particular division was incorrectly configured or if a StarExec job stalled for some reason (both of which happened).
+
+In addition, with the new cluster, the new benchmarks, and a longer timeout period, the organizers were unsure how long the competition would take.
+Our conservative estimate was that a month of computing was needed; in fact it only took about a week, because we had three times more StarExec nodes available than anticipated and jobs took on average less time than estimated.
+However, to hedge against the competition taking longer than anticipated, we divided larger divisions into \emph{heats}, with each heat comprising about 1000 benchmarks, and with the option (stated in the rules) to terminate the competition before all heats were executed to ensure a timely end prior to FLoC.
+This required handling a much larger number of StarExec jobs.
+In the end it was entirely unnecessary for timely completion, but, as mentioned, dividing the jobs into manageable pieces was useful for restarting portions of the computation when StarExec stalled.\footnote{Stalling---that is, no longer making forward progress on a job---was less a concern after some bug fixes during the competition, but was still observed during some post-competition computations.}
+
+In past competitions, the competition was timed to have its last portion overlap with the conference with which it was affiliated.
+In 2014, because the computation took less time than anticipated, the competition finished well before the conference.
+
+\paragraph{Report the results.} The results of the competition were reported at the SMT Workshop and in this paper.
 
@@
 To avoid interference among job-pairs, only one job-pair was executed at a time on each node.
+The software configuration contains
+\begin{itemize}[noitemsep,nolistsep]
+\item Linux kernel 2.6.32-573.1.1.el6.x86\_64
+\item GNU C Library stable release version 2.12
+\item gcc (GCC) 4.4.7 20120313 (Red Hat 4.4.7-11)
+\end{itemize}
 
 For comparison, the previous computational cluster (SMT-Exec) had just 11 nodes:
-\begin{itemize}
+\begin{itemize}[noitemsep,nolistsep]
 \item Nine are 2.4\,GHz AMD Opteron 250s, configured for single core, 64-bit processing, 1 MB cache, 4 GB main memory
@@
 All eleven execution nodes have the same software configuration:
-\begin{itemize}
+\begin{itemize}[noitemsep,nolistsep]
 \item Linux, kernel version 2.6.18-128.2.1.el5
@@
 Overall, however, StarExec performed its function well and the support team was responsive in fixing any difficulties: evaluations of 339,714 job-pairs were completed for the competition over a period of about 9 days, including the restarts necessary because of bugs or misconfigurations.
+
+\section{Other Competitions}
+\label{sec:OtherCompetitions}
+
+Competitions among tools for a specific purpose are now common. Indeed SMT-COMP participated among dozen or so tools in the
+FLoC Olympic Games in 2014~\cite{TBD}. The competitions differ, of course, in their target problem set, but also differ in
+their overall goals, scoring policies, and organization.
+
+SMT differs from the CASC competition~\cite{PSS02} in directly addressing sorted logics.
+SMT also focuses on fragments of first-order logic that are \emph{decidable}.
+For example, a subset of the benchmarks are problems in an integer-difference logic, for which there are specific decision procedures.
+The competition among tools is to create very efficient implementations of a breadth of decision procedures.
+Accordingly, SMT solvers have historically not handled logics with quantified expressions, though several solvers now do so, responding to strong encouragement from industrial users to include quantification in SMT solvers.
+This can, in general, make the satisfiability problem undecidable and the solvers necessarily rely on heuristics.
+Solvers may respond that the answer to a problem is unknown; that is, although there may be a candidate satisfying value assignment, the solver cannot assure that some combination of instantiations of quantified formulas might not invalidate the assignment.
+Nevertheless, the inclusion of logics with quantification has been welcome by users.
+With SMT solvers moving to include quantification and CASC solvers moving to include types and arithmetic, we see a basis for fruitful future collaboration between these communities.
+
+The organizers of SMT-COMP helped organize and execute the first edition of SL-COMP~\cite{SLCOMP} as a sibling competition.
+SL-COMP is a competition among solvers for separation logic.
+The formal logical underpinnings of SL-COMP are still being
+defined and the relationship between the logic used in SL-COMP and the SMZT-LIB logic is under discussion. However, SL-COMP
+did express its benchmark problems in the same syntax as SMT-COMP, used the same StarExec hardware, and used similar 
+organization and scoring rules.
+
+\davidc{Update the reference for SLCOMP}
+
+Besides the subject material, the most interesting difference among competitions is in scoring. (The scoring procedure for
+SMT-COMP is described in detail in section \ref{sec:floc}.)
+Competitions are currently mostly focused on raw solver capability---that is, the numbers and difficulty of problems that can be solved.
+Thus competition winners are primarily determined by the total number of problems solved correctly,
+with the time taken to produce the solutions used only as a tie-breaker. This is the case for SMT-COMP, SAT, and SV-COMP,
+for example.
+
+A more significant issue is how solver errors are taken into account in the metrics.
+A solver error indicates an unsoundness in the tool, which is highly undesirable; however, highly penalizing errors may discourage new entrants whose tools are not yet mature.
+Different competitions vary on this aspect.
+SMT-COMP has historically emphasized soundness; a
+single error in a division caused the solver to be scored lower than any other solver with no errors, even if the other solvers solved very few problems.
+For the SAT competition, an error outright disqualifies a tool in the category it occurs\footnote{See \url{http://satcompetition.org/2014/rules.shtml}.}.
+In contrast, in the SV-competition~\cite{svcomp-2015}, successful runs account positively towards the final score, while errors count negatively (with an increased weight).
+
+\davidc{Research a wider set of competitions}
 
@@
 
-An important issue is how solver errors should be taken into account into the metrics.
-A solver error indicates an unsoundness in the tool, which is highly undesirable; however, highly penalizing errors may discourage new entrants whose tools are not yet mature.
-Different competitions vary on this aspect.
-For the SAT competition, an error disqualifies a tool in the category it occurs\footnote{See \url{http://satcompetition.org/2014/rules.shtml}.}.
-In contrast, in the SV-competition~\cite{svcomp-2015}, successful runs account positively towards the final score, while errors count negatively (with an increased weight).
-
 Note that incorrect results are very rare in SMT-COMP, but do occur; for almost all solvers and divisions the value of $e_i$ is 0 and the competition hinges on the values of $c_i$.
@@
 Second, if there is a tie in the number of errors and correctly solved problems, the total time taken on the correctly solved problems is used as the tie-breaker (even if the solvers solve different subsets of benchmarks); this is a rare occurrence but does happen if, for example, all the benchmark problems in a division are solvable within the time limit---the only situation in the competition in which tie-breaking has been needed.
-Other competitions (e.g., SAT and SV-COMP) also award points for successful solutions and use the time to solve problems only as a tie-breaker, if at all.
 
@@
 However, rerunning the competition on the old hardware or on the old benchmarks was out of the scope of the organizers' task.
-
-This year's competition also saw the inauguration of a new, sibling competition. The organizers helped start and execute SL-COMP~\cite{SLCOMP}, a competition among solvers for separation logic.
 

### 2015-07-30 2014/report/SMTCOMP.tex
revised David C.'s overhaul, removed some redundant pieces, replaced tables

@@
 \documentclass[twoside,11pt]{article}
+
+\sloppy
 
@@
 \usepackage{jsat}
+\usepackage{here}
 \usepackage{hyperref}   %% sets hyperlinks within a pdf
@@
 We were able to use all benchmarks because we had nearly exclusive use of the StarExec computational cluster during the time we were executing SMT-COMP.
-This point is discussed further in \S\ref{sec:procedure}.
-\
-davidc{Correct reference? maybe to the benchmark section?}
+This point is discussed further in \S\ref{sec:benchmark-selection}
 \item In 2012 some experimental tracks were held: parallel performance, unsat cores, and proof generation.
@@
 The organizers still appreciate the value of measuring the performance of solvers on new features such as model generation, unsat core determination, and proof generation, and recommend that they be reinstated in some future edition of the competition.
-\item A significant change in 2014 was to increase the time-out limit for a solver processing a given benchmark from 25 minutes (in 2012) to 40 minutes.
-(cf.
-section \ref{TBD}) \davidc{Add section reference}
+\item A significant change in 2014 was to increase the timeout limit for a solver processing a given benchmark from 25 minutes (in 2012) to 40 minutes (see \S\ref{sec:procedure} for details on the competition parameters and \S\ref{sec:timeouts} for a discussion on their effects).
 \item A significant result of the 2013 Evaluation was that the result of a competition was highly sensitive to the selection of benchmarks: different random selections of benchmarks resulted in different winning orders in a large fraction of samples.
@@
 As stated, the goal of SMT-COMP is similar to the goal of the SAT competition.
-The SMT logic extends SAT by incorporating defined theories, such as the theory of arrays, or of undefined functions, or of arithmetic, or of bit-vectors.
+The SMT logic extends SAT by incorporating defined theories, such as the theory of arrays, or of uninterpreted functions, or of arithmetic, or of bit-vectors.
 In addition, there may be constraints on the set of expressions allowed, such as only linear arithmetic, or only integer difference arithmetic.
@@
 \begin{table}
+\begin{center}
 \begin{tabular}{|l|l|}
@@
 N & Non-Linear (arithmetic) \\
-IA/RA/IRA & Integer/Real/Both arithmetic \\
+IA/RA/IRA & Integer/Real/Mixed arithmetic \\
 DL & Difference Logic \\
@@
 \end{tabular}
+\end{center}
 \caption{Abbreviations used in logic names}
@@
 
-However, it is important to note that some tools used in the competition support only a subset of SMT-LIB, leaving out some commands that are essentially syntactic sugar, 
-to simplify the burden on competing solvers.
-This subset is only informally stated, but the benchmark set only uses this subset.
+However, it is important to note that some tools used in the competition support only a subset of the SMT-LIB command language, leaving out some commands that are essentially syntactic sugar, and are defined as optional in the standard to simplify the burden on competing solvers.
+This subset is only informally stated and has been stable since 2010.
+Moreover, the benchmarks only use this subset.
 This informality did not cause problems in the competition, but it would be preferable to define this subset explicitly.
-The competition subset has been
-stable since 2010.  Requiring just a subset for competition works against the goal of 
-producing SMT-LIB-compliant solvers for users. Fortunately, most mature solvers
-have implemented nearly all of SMT-LIB. Features such as incrementality, 
-proof production, and determining unsat cores are evaluated in specialized tracks, 
-separate from the main competition. The presence of such tracks in the competition has varied from year to year.
+%% [DD] Strictly speaking, these commands are optional and a SMT-LIB
+%% compliant solver needs not implement them. Which is why I commented
+%% out the following sentence 
+%%
+%% Requiring just a subset for competition works against the goal of
+%% producing SMT-LIB-compliant solvers for users.  Fortunately, most
+%% mature solvers have implemented nearly all commands of SMT-LIB.
+Optional features such as incrementality, proof production, and determining unsat cores are evaluated in specialized tracks, separate from the main competition.
+The presence of such tracks in the competition has varied from year to year.
 
@@
 the negation of a property of this operator. The command
-\lstinline{check-sat} instructs the SMT solver to check if the assertions
-are satisfiable. Here the expected result is \lstinline{unsat},
-indicating that the combination of the two assertions is unsatisfiable and
-so, equivalently, the desired property is valid, given the first assertion.
+\lstinline{check-sat} instructs the SMT solver to check if the
+conjunction of the assertions is satisfiable. Here the expected result
+is \lstinline{unsat}, indicating that the combination of the two
+assertions is unsatisfiable and so, equivalently, the desired property
+is valid, given the first assertion.
 
@@
 
-\paragraph{Application benchmarks.} The language includes commands that allow a fine-grained interaction
+\subsection{Application benchmarks.}
+
+The language includes commands that allow a fine-grained interaction
 with the solver, whereby client tools may incrementally push and pop
@@
 
-\paragraph{Selection of benchmarks.} Due to the mismatch between the amount of available compute time and the number of jobs to run, benchmark selection has been an historical issue for SMT-COMP.
+\subsection{Selection of benchmarks. \label{sec:benchmark-selection}}
+
+Due to the mismatch between the amount of available compute time and the number of jobs to run, benchmark selection has been an historical issue for SMT-COMP.
 In addition to whether a benchmark has a known result or is trivial, the SMT-COMP organizers chose two other factors that affect the selection of benchmarks for SMT-COMP: the benchmark's difficulty and the desire for a distribution of problems.
@@
 
-As in past competitions, the organizers included some publicly available historical solvers.
-These solvers are run in the competition for comparison, but are designated as demonstration only and are not eligible for any awards or designations of having won the competition.
-In result tables, these solvers are listed with their names in square brackets (e.g., [MathSat]).
-The organizers included current versions of MathSat and Z3.
-Also, during the competition, a bug-fix release of CVC4 (named CVC4-with-bugfix) was submitted and included as a demonstration only version (cf.
-\S\ref{sec:floc}).
-
-\begin{table}[t]
+\begin{table}[H]
 \caption{History of solver participation (numbers in parenthesis indicate
@@
 
+As in past competitions, the organizers included some publicly available historical solvers.
+These solvers are run in the competition for comparison, but are designated as demonstration only and are not eligible for any awards or designations of having won the competition.
+In result tables, these solvers are listed with their names in square brackets (e.g., [MathSat]).
+The organizers included current versions of MathSat and Z3.
+Also, during the competition, a bug-fix release of CVC4 (named CVC4-with-bugfix) was submitted and included as a demonstration only version (cf.
+\S\ref{sec:floc}).
+
 \begin{table}
@@
 As a result, some solvers did not continue participating, at least not immediately.
-However, the use of SMT-LIB~v2 also increased the expressiveness of benchmarks.
-SMT-LIB~v2 introduced a set of (optional) commands to enable richer interactions with solvers.
-Thus benchmarks representing the needs of industrial applications were able to be added;
+The added expressivity of the command language permitted to add benchmarks representing the needs of industrial applications, and
 the application track of the competition was added to demonstrate the interactive capability and the corresponding abilities of solvers.
@@
 development activity on StarExec. The timeline is provided in
-table~\ref{tab:timeline} for transparency and as a guideline for forthcoming
+Table~\ref{tab:timeline} for transparency and as a guideline for forthcoming
 editions of the competition.
@@
 StarExec made about 150 nodes available for the duration of the competition.
-The timeout setting was a notable difference in 2014; in 2013, this was set at 25~minutes.
-The effect of this is discussed in \S\ref{sec:timeouts}.
+%% [DD] Removed the following sentence to reduce redundancy 
+%% The timeout setting was a notable difference in 2014; in 2013, this
+%% was set at 25~minutes.
+The effect of the new timeout is discussed in \S\ref{sec:timeouts}.
 Though the memory limit was fairly generous, there were still a small number~(202) of jobs that were killed during the competition because of excessive memory use.
@@
 
-Solver submissions comprise the solver itself, a short system description outlining what is new or novel about the solver, and an integer seed.
-All the submitted seeds and an additional seed derived from a value unknowable until after the solver submission deadline were summed and used as the starting seed for any pseudo-random selection and scrambling processes (see below) in the competition.
+Solver submissions comprise the solver itself, a short system description outlining what is new or novel about the solver, and an integer seed used as input to the scrambler (as described in~\S\ref{sec:benchmark-selection}).
+%% [DD] removed following sentence to reduce redundancy
+%%
+%% All the submitted seeds and an additional seed derived from a value
+%% unknowable until after the solver submission deadline were summed
+%% and used as the starting seed for any pseudo-random selection and
+%% scrambling processes (see below) in the competition.
 
@@
 \end{itemize}
-All eleven execution nodes have the same software configuration:
+All eleven execution nodes were running Red Hat Enterprise Linux Client release 5.2 (Tikanga) , with the following software configuration:
 \begin{itemize}[noitemsep,nolistsep]
 \item Linux, kernel version 2.6.18-128.2.1.el5
-\item Red Hat Enterprise Linux Client release 5.2 (Tikanga)
 \item glibc-2.5-24.el5\_2.2
@@
 
-As this was the first year SMT-COMP used StarExec, a variety of tools and procedures needed to be ported to the new infrastructure.
-These included the benchmarks, the post-processor for scoring results,
-a tool to select benchmarks randomly according to the stated policies,
-tools for creating StarExec jobs based on selections of benchmarks and solvers,
-the driver application for running the application track,
-and tools for creating real-time summaries of results in progress.
-These are now available to be reused in future years.
-
+As this was the first year SMT-COMP used StarExec, a variety of tools and procedures needed to be ported to the new infrastructure, as described in \S\ref{sec:procedure}.
+%% [DD]
+%% Removed the following that is redundant
+%%
+%% These included the benchmarks, the post-processor for scoring
+%% results, a tool to select benchmarks randomly according to the
+%% stated policies, tools for creating StarExec jobs based on
+%% selections of benchmarks and solvers, the driver application for
+%% running the application track, and tools for creating real-time
+%% summaries of results in progress.  These are now available to be
+%% reused in future years.
 The execution of SMT-COMP on StarExec went well, though not flawlessly. As this was a first major use of StarExec for a competition there were some bugs to work through.
@@
 
-The organizers of SMT-COMP helped organize and execute the first edition of SL-COMP~\cite{SLCOMP} as a sibling competition.
+The organizers of SMT-COMP helped organize and execute the first edition of SL-COMP~\cite{SLCOMP,sighireanu2014report} as a sibling competition.
 SL-COMP is a competition among solvers for separation logic.
 The formal logical underpinnings of SL-COMP are still being
-defined and the relationship between the logic used in SL-COMP and the SMZT-LIB logic is under discussion. However, SL-COMP
+defined and the relationship between the logic used in SL-COMP and the SMT-LIB logic is under discussion. However, SL-COMP
 did express its benchmark problems in the same syntax as SMT-COMP, used the same StarExec hardware, and used similar 
@@
 \davidc{Update the reference for SLCOMP}
+\davidd{Added a journla submission on SLCOMP 2014}
 
@@
 
-\begin{table}
+\begin{table}[H]
 \caption{Main track results}
@@
 
-The data in Table~\ref{Fig:winners}also shows that most solvers have a similar trend in success as the timeout is increased.
+The data in Table~\ref{Fig:winners} also shows that most solvers have a similar trend in success as the timeout is increased.
 For example, most solvers solve about 50\% (ranging from 40\% to 62\%) of the benchmarks that solver solves by 2400 seconds by 1.0 second and
@@
 In four of the divisions (QF\_AUFLIA, QF\_UFLIA, QF\_UFLRA, UFLRA) over 90\% of the solver-benchmarks jobs were completed before the timeout; for QF\_UFLRA it was over 99\%.
-The other three divisions had much harder benchmarks.
-For example, for QF\_BF, only 1\% of solver-benchmark pairs were completely solved by 1 second and only 42\% by the timeout.
+The other three divisions (QF\_BV, QF\_LIA, QF\_LRA) had much harder benchmarks.
+For example, for QF\_BV, only 1\% of solver-benchmark pairs were completely solved by 1 second and only 42\% by the timeout.
 These three divisions also have many fewer benchmarks---a few hundred, rather than several thousand.

### 2015-08-01 2014/report/SMTCOMP.tex
More edits per review comments

@@
 In planning the 2014 competition, the organizers' overall goal was to encourage breadth
-in the capability of SMT solvers. SMT-COMP 2014 benefited from the evaluation that was performed in 2013 and the experience of previous competitions. As a result we established the following emphases:
+in the capability of SMT solvers.
+SMT-COMP 2014 benefited from the evaluation that was performed in 2013 and the experience of previous competitions.
+As a result we established the following emphases.
+Note that, as described in later sections, the competition is
+divided into a number of divisions, each focuses on a given logic and each with its own set of benchmark problems and solvers.
 \begin{itemize}
@@
 In response to feedback, in 2014 we reverted to the practice of evaluating solvers in all available divisions.
-\item We ran the competition with all available, eligible benchmarks.
-To be eligible, a benchmark must be well-formed and have a known answer.
-We were able to use all benchmarks because we had nearly exclusive use of the StarExec computational cluster during the time we were executing SMT-COMP.
+\item A significant result of the 2013 Evaluation was that the result of a competition was highly sensitive to the selection of benchmarks: different random selections of benchmarks resulted in different winning orders in a large fraction of samples.
+Hence, an aim for 2014 was to use as large a benchmark set as possible in the competition to minimize this effect.
+We were able to run the competition with all eligible benchmarks.
 This point is discussed further in \S\ref{sec:benchmark-selection}
@@
 \item A significant change in 2014 was to increase the timeout limit for a solver processing a given benchmark from 25 minutes (in 2012) to 40 minutes (see \S\ref{sec:procedure} for details on the competition parameters and \S\ref{sec:timeouts} for a discussion on their effects).
-\item A significant result of the 2013 Evaluation was that the result of a competition was highly sensitive to the selection of benchmarks: different random selections of benchmarks resulted in different winning orders in a large fraction of samples.
-Hence, an aim for 2014 was to use as large a benchmark set as possible in the competition to minimize this effect.
 
@@
 Each problem is a set of closed formulas over a set of constant or function symbols, possibly including quantification; a solution to the problem is an assignment of each constant and function evaluation to values in a way that satisfies all the problem's assertions.
-That is, the task is to find a \emph{satisfying assignment} for the benchmark problem or to demonstrate that there is no such assignment.
+That is, the task is to find a \emph{satisfying assignment} for the benchmark problem or to determine that there is no such assignment.
 Since the presence of quantified expressions introduces incompleteness, solvers may also produce a potential solution that may be marked as possibly incomplete.
@@
 
-However, it is important to note that some tools used in the competition support only a subset of the SMT-LIB command language, leaving out some commands that are essentially syntactic sugar, and are defined as optional in the standard to simplify the burden on competing solvers.
+%However, it is important to note that some tools used in the competition support only a subset of the SMT-LIB command language, leaving out some commands that are essentially syntactic sugar, and are defined as optional in the standard to simplify the burden on competing solvers.
 This subset is only informally stated and has been stable since 2010.
@@
 
-SMT-LIB currently defines 34 logics, shown in Table \ref{Table:benchmarks}.
-The rightmost column shows the number of benchmarks for that logic in the SMT-LIB collection.
-Two considerations may make a benchmark ineligible for a competition.
-First, the benchmark may not have a known result.
-For newly submitted benchmarks
-we made an attempt to determine the correct result of the benchmark; the SMT-LIB coordinators require that two
-different solvers solve the benchmark and report the same result.
-However, for benchmarks with unknown results already in the collection we did not have time to determine their results.
-We did do this analysis after the competition was over (see~\S\ref{sec:post}).
-
-The second consideration is that the benchmark must be \emph{non-trivial}; a benchmark is deemed trivial if all solvers managed to solve it in less than five seconds during SMT-EVAL 2013.
-
-The numbers of unknown, trivial, and remaining eligible benchmarks are shown in Table \ref{Table:benchmarks}. Note that these numbers vary widely from division to division.
-
 As of June 2014, the SMT-LIB repository contained over 130,000
@@
 Two divisions were not held because they had no eligible benchmarks.
+
+The 34 logics are shown in Table \ref{Table:benchmarks}.
+The rightmost column shows the number of benchmarks for that logic in the SMT-LIB collection.
+Two considerations may make a benchmark ineligible for a competition.
+First, the benchmark may not have a known result.
+For newly submitted benchmarks
+we made an attempt to determine the correct result of the benchmark; the SMT-LIB coordinators require that two
+different solvers solve the benchmark and report the same result.
+However, for benchmarks with unknown results already in the collection we did not have time to determine their results.
+We did do this analysis after the competition was over (see~\S\ref{sec:post}).
+
+The second consideration is that the benchmark must be \emph{non-trivial}; a benchmark is deemed trivial if all solvers managed to solve it in less than five seconds during SMT-EVAL 2013.
+
+The numbers of unknown, trivial, and remaining eligible benchmarks are shown in Table \ref{Table:benchmarks}. Note that these numbers vary widely from division to division.
 
@@
 The rules describe a procedure for randomly selecting $N$ out of the eligible benchmarks for a division, with the intent of selecting roughly equal numbers, if they are available, from each of the quintiles.
-The seed for the random number generator used for selection is obtained by summing a number supplied by each solver team and the integer portion of the New York stock exchange index at its opening on the day the competition begins.
-\davidc{Check the rules}
+The seed for the random number generator used for selection is obtained by summing a number supplied by each solver team and the integer portion of the New York Stock Exchange Composite Index at its opening on the day the competition begins.
 
@@
 
-The competition registration includes information about each competing solver. In addition, some solver groups provided summaries of their solvers and their recent technical advances.
+The competition registration requires participants to submit information about each competing solver.
+In addition, some solver groups provided summaries of their solvers and their recent technical advances.
  Note that although one person is listed as the ``submitter,'' there is generally a team of contributors behind each tool.
@@
 
+\section{Competition Procedure}
+\label{sec:procedure}
+
+The full description of the 2014 SMT Competition's rules is found in the rules document (\url{http://smtcomp.sourceforge.net/2014/rules14.pdf}).
+The document describes the procedures for determining benchmark difficulties, selecting benchmarks for competition, and judging the results.
+The preparation and execution of the competition required the following matters to be decided and executed.
+
+\paragraph{Decide the competition parameters.} We set a timeout of 40~minutes for both wall clock and CPU time; the memory limit was 100\,GB.
+A single solver-benchmark combination (job-pair) was run on a node at a given time.
+The benchmarks were scrambled; all benchmarks were run, rather than just a subset.
+StarExec made about 150 nodes available for the duration of the competition.
+%% [DD] Removed the following sentence to reduce redundancy 
+%% The timeout setting was a notable difference in 2014; in 2013, this
+%% was set at 25~minutes.
+The effect of the new timeout is discussed in \S\ref{sec:timeouts}.
+Though the memory limit was fairly generous, there were still a small number~(202) of jobs that were killed during the competition because of excessive memory use.
+
+\paragraph{Settle any adjustments on the rules and competition timeline, with time for comment.}
+The competition rules are largely the same from year to year, but each year there are adjustments and improvements.
+Matters to be decided are the timeline for the competition, communication vehicles (including instantiating the website for the new competition), the various tracks and divisions, any adjustments to the benchmark selection procedure, the scoring rules, and policies on similar submissions and portfolio solvers.
+A novel aspect in 2014 was the need for policies regarding the FLoC Olympic Games~\cite{FLoCGames}, described in \S\ref{sec:floc}.
+During the competition, the organizers had to rule on two issues.
+\begin{itemize}[noitemsep,nolistsep]
+\item First, whether solvers could be withdrawn from divisions after the competition began; our ruling was no, because that could raise a solver's overall performance score and could change which divisions were deemed competitive.
+This decision did affect the results of the FLoC medal competition.
+\item Second, whether a job-pair that responded with a result before the timeout limit, but did not exit until after the timeout limit, is to be considered a timeout or a correct or wrong answer; the ruling was that it is not a timeout.
+Only one benchmark was affected by this decision and the decision did not affect any winning order, just a slight change in one solver's score.
+\end{itemize}
+The organizers also received and adjudicated an appeal after the competition completed (cf.~\S\ref{sec:floc}).
+
+\paragraph{Undefined Behavior.} During the testing period prior to the competition beginning, different solvers exhibited different behavior on some benchmarks.
+Investigation revealed that these differences were the result of different treatments of partial operations, divide by zero, in particular.
+The question is what should be the definition of divide by zero in SMT-LIB's logic of total functions.
+This question had been discussed at length over previous years, with proposals to clarify the SMT-LIB standard.
+There was certainly not time to resolve this matter prior to the competition, not to mention correcting solvers to the agreed behavior.\footnote{The discussion this time around can be found in the archives of the \url{smtcomp-discussion@lists.sourceforge.net} mailing list, in the few days near 2014-06-16.}
+Thus, for the competition, we decided to omit all benchmarks (6060 of them, 1348 of which were otherwise eligible) that were affected by divide-by-zero behavior. This question, however, remains open.
+
+\paragraph{Invite and validate solver submissions.} The 2014 competition saw the first use of the StarExec computational cluster (cf.
+\S\ref{sec:starexec}) for executing the competition.
+Each solver had to be wrapped in appropriate scripts to be able to run in the StarExec environment.
+Though this was largely the responsibility of the solver submitter, teams submitting solvers for the first time required guidance and assistance from the organizers and the StarExec development team.
+This was a significant hurdle; not all solver teams were able to complete it in time.
+The most significant problem was the need to create a fully statically linked version of the solver that ran on the particular version of Linux used by StarExec.
+The organizers stipulated a first solver submission deadline and a final solver submission deadline, separated by two weeks, to enable (and encourage) trials and debugging of solver submissions.
+
+Solver submissions comprise the solver itself, a short system description outlining what is new or novel about the solver, and an integer seed used as input to the scrambler (as described in~\S\ref{sec:benchmark-selection}).
+%% [DD] removed following sentence to reduce redundancy
+%%
+%% All the submitted seeds and an additional seed derived from a value
+%% unknowable until after the solver submission deadline were summed
+%% and used as the starting seed for any pseudo-random selection and
+%% scrambling processes (see below) in the competition.
+
+\paragraph{Invite and validate benchmark submissions.} New benchmarks are always welcome and an impending competition is a particular opportunity to encourage new submissions.
+Benchmarks are the responsibility of SMT-LIB coordinators, not the competition organizers.
+Nevertheless, the organizers worked with the coordinators to ensure that new benchmarks were included in SMT-LIB in time for the competition.
+Initial submissions are often incomplete; to be useful they must be syntactically correct, include a designation of the logic in which they fit, contain relevant metadata about the source and category of the benchmark, and have a known, validated answer.
+Benchmarks with unknown answers may also be interesting and worth keeping, but cannot be used in the competition.
+
+\paragraph{Create an appropriate selection of benchmarks.} Not all benchmarks in the SMT-LIB database are necessarily used in the competition.
+The details of this selection, as executed for the 2014 competition, are described in \S\ref{sec:benchmarks}.
+Part of the work in preparing the competition to run on the StarExec cluster was to port the benchmark selector to StarExec.
+
+\paragraph{Prepare the benchmark scrambler.} All the benchmarks are public and known to the solver developers beforehand.
+Indeed, part of the point of the benchmark database is to serve as a testbed for solver development, outside of competitions.
+However, that raises the possibility that a solver will recognize a benchmark problem by its syntactic structure and look up an answer from a learned database, without doing any logic solving.
+This is explicitly considered cheating.
+As a slight impediment against such behavior, the benchmarks are individually scrambled before being presented to a solver, using the random seed described above.
+For 2014, the benchmark scrambler had to be ported to StarExec.
+
+The scrambling does not change the semantic meaning of the benchmark.
+It does rename identifiers, alter the order of assertions and the position of the arguments in the application of associative-commutative operators.
+
+The scrambling had another effect, previously unappreciated.
+Although most of the solvers are deterministic for a given input, scrambling can change the order of search.
+For example, iterating over the contents of a hashed set may occur in a different order if identifiers have different names.
+Consequently, the success of the solver on a given benchmark, the time it takes to find an answer, and even whether a latent bug in the solver is triggered may all depend on just how the benchmark is scrambled.
+Thus the scrambling adds a measure of uncertainty to the competition and prevents full testing on the benchmark set before the competition.
+Indeed, one solver encountered a bug during the competition that was directly related to the specific, randomly-chosen scrambling used during the competition.
+The effect of the possible variations in performance caused by scrambling is expected to be balanced by the large of number of benchmarks employed in the competition to compare the solvers, as also observed in the SAT community~\cite{leberre+03}.
+Nevertheless, this point is worthy of future further investigation.
+
+\paragraph{Prepare the real-time results display.} The participants are interested in the progress of the competition as it proceeds.
+The organizers also need to know if the competition is proceeding correctly and at a reasonable pace.
+As the competition takes several days, an automatic real-time display of results is helpful and encourages interest.
+StarExec does not have such a facility, since different competitions have different needs.
+Instead the organizers used StarExec's command-line API to regularly (every 10 minutes or so) download the status of all of the executing jobs, extract the results for each solver-benchmark pair, create HTML web pages displaying the current status, and upload them to the competition website.
+The current (now final) status of each division and a summary page can be seen at \url{http://smtcomp.sourceforge.net/2014/results-toc.shtml}.
+
+\paragraph{Execute the competition.} Executing the competition required preparing a StarExec job for each
+division.
+A job executes the cross-product of a set of solvers and a set of benchmarks.
+Because each division has different sets of solvers and benchmarks, each division was represented by one or more jobs.
+Splitting a division into multiple jobs allowed a restart of portions of the competition if a particular division was incorrectly configured or if a StarExec job stalled for some reason (both of which happened).
+
+In addition, with the new cluster, the new benchmarks, and a longer timeout period, the organizers were unsure how long the competition would take.
+Our conservative estimate was that a month of computing was needed; in fact it only took about a week, because we had three times more StarExec nodes available than anticipated and jobs took on average less time than estimated.
+However, to hedge against the competition taking longer than anticipated, we divided larger divisions into \emph{heats}, with each heat comprising about 1000 benchmarks, and with the option (stated in the rules) to terminate the competition before all heats were executed to ensure a timely end prior to FLoC.
+This required handling a much larger number of StarExec jobs.
+In the end it was entirely unnecessary for timely completion, but, as mentioned, dividing the jobs into manageable pieces was useful for restarting portions of the computation when StarExec stalled.\footnote{Stalling---that is, no longer making forward progress on a job---was less a concern after some bug fixes during the competition, but was still observed during some post-competition computations.}
+
+In past competitions, the competition was timed to have its last portion overlap with the conference with which it was affiliated.
+In 2014, because the computation took less time than anticipated, the competition finished well before the conference.
+
+\paragraph{Report the results.} The results of the competition were reported at the SMT Workshop and in this paper.
+
 \paragraph{Competition Timeline}
@@
 
-\section{Competition Procedure}
-\label{sec:procedure}
-
-The full description of the 2014 SMT Competition's rules is found in the rules document (\url{http://smtcomp.sourceforge.net/2014/rules14.pdf}).
-The document describes the procedures for determining benchmark difficulties, selecting benchmarks for competition, and judging the results.
-The preparation and execution of the competition required the following matters to be decided and executed.
-
-\paragraph{Decide the competition parameters.} We set a timeout of 40~minutes for both wall clock and CPU time; the memory limit was 100\,GB.
-A single solver-benchmark combination (job-pair) was run on a node at a given time.
-The benchmarks were scrambled; all benchmarks were run, rather than just a subset.
-StarExec made about 150 nodes available for the duration of the competition.
-%% [DD] Removed the following sentence to reduce redundancy 
-%% The timeout setting was a notable difference in 2014; in 2013, this
-%% was set at 25~minutes.
-The effect of the new timeout is discussed in \S\ref{sec:timeouts}.
-Though the memory limit was fairly generous, there were still a small number~(202) of jobs that were killed during the competition because of excessive memory use.
-
-\paragraph{Settle any adjustments on the rules and competition timeline, with time for comment.}
-The competition rules are largely the same from year to year, but each year there are adjustments and improvements.
-Matters to be decided are the timeline for the competition, communication vehicles (including instantiating the website for the new competition), the various tracks and divisions, any adjustments to the benchmark selection procedure, the scoring rules, and policies on similar submissions and portfolio solvers.
-A novel aspect in 2014 was the need for policies regarding the FLoC Olympic Games~\cite{FLoCGames}, described in \S\ref{sec:floc}.
-During the competition, the organizers had to rule on two issues.
-\begin{itemize}[noitemsep,nolistsep]
-\item First, whether solvers could be withdrawn from divisions after the competition began; our ruling was no, because that could raise a solver's overall performance score and could change which divisions were deemed competitive.
-This decision did affect the results of the FLoC medal competition.
-\item Second, whether a job-pair that responded with a result before the timeout limit, but did not exit until after the timeout limit, is to be considered a timeout or a correct or wrong answer; the ruling was that it is not a timeout.
-Only one benchmark was affected by this decision and the decision did not affect any winning order, just a slight change in one solver's score.
-\end{itemize}
-The organizers also received and adjudicated an appeal after the competition completed (cf.~\S\ref{sec:floc}).
-
-During the testing period prior to the competition beginning, different solvers exhibited different behavior on some benchmarks.
-Investigation revealed that these differences were the result of different treatments of partial operations, divide by zero, in particular.
-The question is what should be the definition of divide by zero in SMT-LIB's logic of total functions.
-This question had been discussed at length over previous years, with proposals to clarify the SMT-LIB standard.
-There was certainly not time to resolve this matter prior to the competition, not to mention correcting solvers to the agreed behavior.\footnote{The discussion this time around can be found in the archives of the \url{smtcomp-discussion@lists.sourceforge.net} mailing list, in the few days near 2014-06-16.}
-Thus, for the competition, we decided to omit all benchmarks (6060 of them, 1348 of which were otherwise eligible) that were affected by divide-by-zero behavior. This question, however, remains open.
-
-\paragraph{Invite and validate solver submissions.} The 2014 competition saw the first use of the StarExec computational cluster (cf.
-\S\ref{sec:starexec}) for executing the competition.
-Each solver had to be wrapped in appropriate scripts to be able to run in the StarExec environment.
-Though this was largely the responsibility of the solver submitter, teams submitting solvers for the first time required guidance and assistance from the organizers and the StarExec development team.
-This was a significant hurdle; not all solver teams were able to complete it in time.
-The most significant problem was the need to create a fully statically linked version of the solver that ran on the particular version of Linux used by StarExec.
-The organizers stipulated a first solver submission deadline and a final solver submission deadline, separated by two weeks, to enable (and encourage) trials and debugging of solver submissions.
-
-Solver submissions comprise the solver itself, a short system description outlining what is new or novel about the solver, and an integer seed used as input to the scrambler (as described in~\S\ref{sec:benchmark-selection}).
-%% [DD] removed following sentence to reduce redundancy
-%%
-%% All the submitted seeds and an additional seed derived from a value
-%% unknowable until after the solver submission deadline were summed
-%% and used as the starting seed for any pseudo-random selection and
-%% scrambling processes (see below) in the competition.
-
-\paragraph{Invite and validate benchmark submissions.} New benchmarks are always welcome and an impending competition is a particular opportunity to encourage new submissions.
-Benchmarks are the responsibility of SMT-LIB coordinators, not the competition organizers.
-Nevertheless, the organizers worked with the coordinators to ensure that new benchmarks were included in SMT-LIB in time for the competition.
-Initial submissions are often incomplete; to be useful they must be syntactically correct, include a designation of the logic in which they fit, contain relevant metadata about the source and category of the benchmark, and have a known, validated answer.
-Benchmarks with unknown answers may also be interesting and worth keeping, but cannot be used in the competition.
-
-\paragraph{Create an appropriate selection of benchmarks.} Not all benchmarks in the SMT-LIB database are necessarily used in the competition.
-The details of this selection, as executed for the 2014 competition, are described in \S\ref{sec:benchmarks}.
-Part of the work in preparing the competition to run on the StarExec cluster was to port the benchmark selector to StarExec.
-
-\paragraph{Prepare the benchmark scrambler.} All the benchmarks are public and known to the solver developers beforehand.
-Indeed, part of the point of the benchmark database is to serve as a testbed for solver development, outside of competitions.
-However, that raises the possibility that a solver will recognize a benchmark problem by its syntactic structure and look up an answer from a learned database, without doing any logic solving.
-This is explicitly considered cheating.
-As a slight impediment against such behavior, the benchmarks are individually scrambled before being presented to a solver, using the random seed described above.
-For 2014, the benchmark scrambler had to be ported to StarExec.
-
-The scrambling does not change the semantic meaning of the benchmark.
-It does rename identifiers, alter the order of assertions and the position of the arguments in the application of associative-commutative operators.
-
-The scrambling had another effect, previously unappreciated.
-Although most of the solvers are deterministic for a given input, scrambling can change the order of search.
-For example, iterating over the contents of a hashed set may occur in a different order if identifiers have different names.
-Consequently, the success of the solver on a given benchmark, the time it takes to find an answer, and even whether a latent bug in the solver is triggered may all depend on just how the benchmark is scrambled.
-Thus the scrambling adds a measure of uncertainty to the competition and prevents full testing on the benchmark set before the competition.
-Indeed, one solver encountered a bug during the competition that was directly related to the specific, randomly-chosen scrambling used during the competition.
-The effect of the possible variations in performance caused by scrambling is expected to be balanced by the large of number of benchmarks employed in the competition to compare the solvers, as also observed in the SAT community~\cite{leberre+03}.
-Nevertheless, this point is worthy of future further investigation.
-
-\paragraph{Prepare the real-time results display.} The participants are interested in the progress of the competition as it proceeds.
-The organizers also need to know if the competition is proceeding correctly and at a reasonable pace.
-As the competition takes several days, an automatic real-time display of results is helpful and encourages interest.
-StarExec does not have such a facility, since different competitions have different needs.
-Instead the organizers used StarExec's command-line API to regularly (every 10 minutes or so) download the status of all of the executing jobs, extract the results for each solver-benchmark pair, create HTML web pages displaying the current status, and upload them to the competition website.
-The current (now final) status of each division and a summary page can be seen at \url{http://smtcomp.sourceforge.net/2014/results-toc.shtml}.
-
-\paragraph{Execute the competition.} Executing the competition required preparing a StarExec job for each
-division.
-A job executes the cross-product of a set of solvers and a set of benchmarks.
-Because each division has different sets of solvers and benchmarks, each division was represented by one or more jobs.
-Splitting a division into multiple jobs allowed a restart of portions of the competition if a particular division was incorrectly configured or if a StarExec job stalled for some reason (both of which happened).
-
-In addition, with the new cluster, the new benchmarks, and a longer timeout period, the organizers were unsure how long the competition would take.
-Our conservative estimate was that a month of computing was needed; in fact it only took about a week, because we had three times more StarExec nodes available than anticipated and jobs took on average less time than estimated.
-However, to hedge against the competition taking longer than anticipated, we divided larger divisions into \emph{heats}, with each heat comprising about 1000 benchmarks, and with the option (stated in the rules) to terminate the competition before all heats were executed to ensure a timely end prior to FLoC.
-This required handling a much larger number of StarExec jobs.
-In the end it was entirely unnecessary for timely completion, but, as mentioned, dividing the jobs into manageable pieces was useful for restarting portions of the computation when StarExec stalled.\footnote{Stalling---that is, no longer making forward progress on a job---was less a concern after some bug fixes during the competition, but was still observed during some post-competition computations.}
-
-In past competitions, the competition was timed to have its last portion overlap with the conference with which it was affiliated.
-In 2014, because the computation took less time than anticipated, the competition finished well before the conference.
-
-\paragraph{Report the results.} The results of the competition were reported at the SMT Workshop and in this paper.
-
 \section{StarExec}
@@
 
-SMT differs from the CASC competition~\cite{PSS02} in directly addressing sorted logics.
+\paragraph{CASC} SMT differs from the CASC competition~\cite{PSS02} in directly addressing sorted logics.
 SMT also focuses on fragments of first-order logic that are \emph{decidable}.
@@
 The competition among tools is to create very efficient implementations of a breadth of decision procedures.
-Accordingly, SMT solvers have historically not handled logics with quantified expressions, though several solvers now do so, responding to strong encouragement from industrial users to include quantification in SMT solvers.
-This can, in general, make the satisfiability problem undecidable and the solvers necessarily rely on heuristics.
+Accordingly, SMT solvers have historically not handled logics with quantified expressions, though several solvers now do so, responding to strong encouragement from industrial users to include quantification in SMT solvers; there are benchmarks and competition divisions corresponding to logics with quantification.
+Including quantified expressions can, in general, make the satisfiability problem undecidable and the solvers necessarily rely on heuristics.
 Solvers may respond that the answer to a problem is unknown; that is, although there may be a candidate satisfying value assignment, the solver cannot assure that some combination of instantiations of quantified formulas might not invalidate the assignment.
 Nevertheless, the inclusion of logics with quantification has been welcome by users.
-With SMT solvers moving to include quantification and CASC solvers moving to include types and arithmetic, we see a basis for fruitful future collaboration between these communities.
+With SMT solvers moving to include quantification and CASC solvers moving to include types and arithmetic, we see a basis for fruitful future collaboration and perhaps merging between these communities.
 
@@
 \davidd{Added a journla submission on SLCOMP 2014}
-
-Besides the subject material, the most interesting difference among competitions is in scoring. (The scoring procedure for
+\davidc{Add other solvers, SV-COMP?}
+
+\paragraph{SL-COMP} Besides the subject material, the most interesting difference among competitions is in scoring. (The scoring procedure for
 SMT-COMP is described in detail in section \ref{sec:floc}.)
@@
 
-A more significant issue is how solver errors are taken into account in the metrics.
+\paragraph{Scoring differences.} A more significant issue is how solver errors are taken into account in the metrics.
 A solver error indicates an unsoundness in the tool, which is highly undesirable; however, highly penalizing errors may discourage new entrants whose tools are not yet mature.
@@
 The organizers are confident that the 2014 data will be a solid baseline for evaluating progress in solver performance in future years.
+
+\davidc{Revise the paragraph above per review comments}
+
+\davidc{More assessment needed}
 

### 2015-08-03 2014/report/SMTCOMP.tex
Whitespace.
Non-existing reference replaced.

@@
 resulting decision problem is called \emph{Satisfiability Modulo
-  Theories\/} ~\cite{DBLP:conf/jelia/Tinelli02}. The background theories of interest arise from
+  Theories}~\cite{DBLP:conf/jelia/Tinelli02}. The background theories of interest arise from
 	application domains, such as formal verification or scheduling problems, and include arrays,
@@
 Competitions among tools for a specific purpose are now common. Indeed SMT-COMP participated among dozen or so tools in the
-FLoC Olympic Games in 2014~\cite{TBD}. The competitions differ, of course, in their target problem set, but also differ in
+FLoC Olympic Games in 2014~\cite{FLoC2014}. The competitions differ, of course, in their target problem set, but also differ in
 their overall goals, scoring policies, and organization.

### 2015-08-03 2014/report/SMTCOMP.tex
tools -> competitions

@@
 
-Competitions among tools for a specific purpose are now common. Indeed SMT-COMP participated among dozen or so tools in the
-FLoC Olympic Games in 2014~\cite{FLoC2014}. The competitions differ, of course, in their target problem set, but also differ in
-their overall goals, scoring policies, and organization.
+Competitions among tools for a specific purpose are now common.
+Indeed SMT-COMP participated among a dozen or so competitions in the FLoC Olympic Games in 2014~\cite{FLoC2014}.
+The competitions differ, of course, in their target problem set, but also in their overall goals, scoring policies, and organization.
 

### 2015-08-03 2014/report/SMTCOMP.tex
e.g. -> e.g.,

@@
 This is the 9th competition in the series, skipping only 2013; in that year an evaluation~\cite{it:2014-017} was performed, rather than a competition.\footnote{The evaluation did not measure solvers against each other, as in a competition.
-Rather it assessed concerns such as how the design of the competition (e.g.
-random choice of benchmarks) affects the outcome, the variety and distribution of benchmarks, and the extent to which the competition is dominated by single solvers or by a few solvers or is broadly competitive.}
+Rather it assessed concerns such as how the design of the competition (e.g., random choice of benchmarks) affects the outcome, the variety and distribution of benchmarks, and the extent to which the competition is dominated by single solvers or by a few solvers or is broadly competitive.}
 

### 2015-08-03 2014/report/SMTCOMP.tex
Minor.

@@
 Information about the winners
-and results of the competition is summarized in this report and is available online at \url{www.smtcomp.org}; information
+and results of the competition is summarized in this report and is available online at \url{www.smtcomp.org}.  Information
 about previous years' competitions is also available at that website and in published summary reports~\cite{springerlink:10.1007/s10817-012-9246-5,DBLP:conf/cade/CokGBD12,it:2014-017}.
@@
 
-In planning the 2014 competition, the organizers' overall goal was to encourage breadth
-in the capability of SMT solvers.
+In planning the 2014 competition, the organizers' overall goal was to encourage breadth in the capability of SMT solvers.
 SMT-COMP 2014 benefited from the evaluation that was performed in 2013 and the experience of previous competitions.
 As a result we established the following emphases.
-Note that, as described in later sections, the competition is
-divided into a number of divisions, each focuses on a given logic and each with its own set of benchmark problems and solvers.
+Note that, as described in later sections, the competition is divided into a number of divisions, each focuses on a given logic, and each has its own set of benchmark problems and solvers.
 \begin{itemize}
@@
 In response to feedback, in 2014 we reverted to the practice of evaluating solvers in all available divisions.
-\item A significant result of the 2013 Evaluation was that the result of a competition was highly sensitive to the selection of benchmarks: different random selections of benchmarks resulted in different winning orders in a large fraction of samples.
+\item A significant result of the 2013 Evaluation was that the results of previous competitions were highly sensitive to the selection of benchmarks: different random selections of benchmarks resulted in different winning orders in a large fraction of samples.
 Hence, an aim for 2014 was to use as large a benchmark set as possible in the competition to minimize this effect.
 We were able to run the competition with all eligible benchmarks.
-This point is discussed further in \S\ref{sec:benchmark-selection}
+This point is discussed further in~\S\ref{sec:benchmark-selection}.
 \item In 2012 some experimental tracks were held: parallel performance, unsat cores, and proof generation.
@@
 Since in 2014 we also had to migrate to using the new StarExec cluster to execute the competition, we held only a main track and an application (incremental) track in the 2014 competition.
-The organizers still appreciate the value of measuring the performance of solvers on new features such as model generation, unsat core determination, and proof generation, and recommend that they be reinstated in some future edition of the competition.
+The organizers still appreciate the value of measuring the performance of solvers on new features such as model generation, unsat core determination, and proof generation, and recommend that these tracks be reinstated in some future edition of the competition.
 \item A significant change in 2014 was to increase the timeout limit for a solver processing a given benchmark from 25 minutes (in 2012) to 40 minutes (see \S\ref{sec:procedure} for details on the competition parameters and \S\ref{sec:timeouts} for a discussion on their effects).
@@
 
-\section{SMT-LIB logic, language and solvers}
+\section{SMT-LIB Logic, Language and Solvers}
 \label{sec:context}
@@
 On the other hand, counting each benchmark equally appeared to underweight the effect of a solver's effort to participate in multiple divisions.
-The log scaling seemed a reasonable compromise between linearly combining numbers of benchmarks these two extremes.
-Similarly, the square of the fraction successfully solved is an
-approximate mechanism to give more weight to solving the harder problems than the easier.
+The log scaling seemed a reasonable compromise between these two extremes.
+Similarly, the square of the fraction successfully solved is an approximate mechanism to give more weight to solving the harder problems.
 

### 2015-08-03 2014/report/SMTCOMP.tex
Undefined behavior explained.

@@
 
-\paragraph{Undefined Behavior.} During the testing period prior to the competition beginning, different solvers exhibited different behavior on some benchmarks.
-Investigation revealed that these differences were the result of different treatments of partial operations, divide by zero, in particular.
-The question is what should be the definition of divide by zero in SMT-LIB's logic of total functions.
+\paragraph{Undefined behavior.} \label{par:undefined} During the testing period prior to the competition beginning, different solvers exhibited different behavior on some benchmarks.
+Investigation revealed that these differences were the result of different treatments of partial operations; in particular, divide by zero.
+The semantics of SMT-LIB is based on a logic of total functions, meaning that division by zero cannot raise an exception (or the like), but must have \emph{some} value.
+The SMT-LIB standard leaves this value unspecified (i.e., it could be anything).
+In contrast, some solvers assume a specific, fixed value.
 This question had been discussed at length over previous years, with proposals to clarify the SMT-LIB standard.
-There was certainly not time to resolve this matter prior to the competition, not to mention correcting solvers to the agreed behavior.\footnote{The discussion this time around can be found in the archives of the \url{smtcomp-discussion@lists.sourceforge.net} mailing list, in the few days near 2014-06-16.}
-Thus, for the competition, we decided to omit all benchmarks (6060 of them, 1348 of which were otherwise eligible) that were affected by divide-by-zero behavior. This question, however, remains open.
+There was certainly not time to resolve this matter prior to the competition, not to mention correcting solvers to the agreed behavior.\footnote{The discussion this time around can be found in the archives of the \url{smtcomp-discussion@lists.sourceforge.net} mailing list, in the few days near 2014-06-16.}  Thus, for the competition, we decided to omit all benchmarks (6060 of them, 1348 of which were otherwise eligible) that were potentially affected by divide-by-zero behavior.
+This question, however, remains open.
 
@@
 
-Solver submissions comprise the solver itself, a short system description outlining what is new or novel about the solver, and an integer seed used as input to the scrambler (as described in~\S\ref{sec:benchmark-selection}).
+Solver submissions comprise the solver itself, a short system
+description outlining what is new or novel about the solver, and an
+integer seed used as input to the scrambler (as described
+in~\S\ref{sec:benchmark-selection}).
 %% [DD] removed following sentence to reduce redundancy
@@
 
-\paragraph{Competition Timeline}
+\paragraph{Competition timeline.}
 
@@
 
-The competition used the NSF-funded StarExec~\cite{DBLP:conf/cade/StumpST14} computational cluster at U.~Iowa for executing solvers on benchmarks.
+The competition used the NSF-funded StarExec~\cite{DBLP:conf/cade/StumpST14} computational cluster at the University of Iowa for executing solvers on benchmarks.
 Past instances of SMT-COMP used a previous SMT-Exec infrastructure.
@@
 
-StarExec consists of 192 2.4\,GHz computational nodes, running Red Hat Linux~6.3.
-Each node has a dual-processor, quad-core CPU (model Intel Xeon CPU E5-2609 at 2.4GHz), 10240 KB cache, and either 129022\,MB (32 nodes) or 258294\,MB of memory (160 nodes).
+StarExec currently consists of 192 2.4\,GHz computational nodes, running Red Hat Linux~6.3.
+Each node has a dual-processor, quad-core CPU (model Intel Xeon CPU E5-2609), 10240~KB cache, and either 129022\,MB (32 nodes) or 258294\,MB of memory (160 nodes).
 In competition, processes were limited to 100\,GB memory.
@@
 \item The difficulty in preparing a new solver for submission to StarExec for participation in SMT-COMP should be reduced.
-\item Resolve the definition of divide-by-zero behavior in SMT-LIB.
+\item Resolve the definition of divide-by-zero behavior in SMT-LIB (cf.~\S\ref{par:undefined}).
 \item An item for study is the effect of benchmark scrambling on the outcome of solver comparisons.

### 2015-08-03 2014/report/SMTCOMP.tex
Minor.
DL -> IDL/RDL.

@@
 IA/RA/IRA & Integer/Real/Mixed arithmetic \\
-DL & Difference Logic \\
+IDL/RDL & Integer/Real Difference Logic \\
 \hline
@@
 
-\section{FLoC Olympic Games}
+\section{FLoC Olympic Games Scoring}
 \label{sec:floc}
@@
 Determining the winner was straightforward: we used the same metric as is used for each division\textemdash the most problems solved without errors, with ties broken by speed of solution.
-The Boolector~\cite{boolector} solver won this division and the bronze medal.
+The Boolector~\cite{boolector} solver won this division and therefore the bronze medal.
 The results for all participating solvers are shown in Table \ref{Table:bronze}.

### 2015-08-03 2014/report/SMTCOMP.tex
Minor.

@@
 StarExec currently consists of 192 2.4\,GHz computational nodes, running Red Hat Linux~6.3.
-Each node has a dual-processor, quad-core CPU (model Intel Xeon CPU E5-2609), 10240~KB cache, and either 129022\,MB (32 nodes) or 258294\,MB of memory (160 nodes).
+Each node has two quad-core CPUs (model Intel Xeon E5-2609, 2.4\,GHz, 10\,MB cache), and either 129022\,MB (32 nodes) or 258294\,MB of memory (160 nodes).
 In competition, processes were limited to 100\,GB memory.
@@
 \begin{itemize}[noitemsep,nolistsep]
-\item Nine are 2.4\,GHz AMD Opteron 250s, configured for single core, 64-bit processing, 1 MB cache, 4 GB main memory
-\item Two are 2.53\,GHz Intel Xeon E5540s, configured for single core, 64-bit processing, 8 MB cache, 12 GB main memory
+\item Nine were 2.4\,GHz AMD Opteron 250s, configured for single core, 64-bit processing, 1 MB cache, 4 GB main memory
+\item Two were 2.53\,GHz Intel Xeon E5540s, configured for single core, 64-bit processing, 8 MB cache, 12 GB main memory
 \end{itemize}
-All eleven execution nodes were running Red Hat Enterprise Linux Client release 5.2 (Tikanga) , with the following software configuration:
+All SMT-Exec nodes had been running Red Hat Enterprise Linux Client release 5.2 (Tikanga), with the following software configuration:
 \begin{itemize}[noitemsep,nolistsep]
-\item Linux, kernel version 2.6.18-128.2.1.el5
+\item Linux kernel 2.6.18-128.2.1.el5
 \item glibc-2.5-24.el5\_2.2

### 2015-08-03 2014/report/SMTCOMP.tex
Minor. Local variables (for Emacs) added.

@@
 The competition saw a renewed interest in participation\textemdash there were record numbers of teams participating, solvers entered, teams and solvers that had never before participated, benchmarks used, and amount of computation performed.
-Although the 2014 results are not readily comparable to previous years (because of changes in benchmarks and equipement), the detailed performance of each solver on each benchmark from this first year using StarExec will be a solid baseline to measure improvements in the state-of-the-art of solver performance in future years.
+Although the 2014 results are not readily comparable to previous years (because of changes in benchmarks and equipment), the detailed performance of each solver on each benchmark from this first year using StarExec will be a solid baseline to measure improvements in the state-of-the-art of solver performance in future years.
 As a partial comparison, solvers that performed well in previous years are included in the this year's competition.
@@
 \thebibliography
+
+%% Local Variables:
+%% mode: LaTeX
+%% ispell-local-dictionary: "american"
+%% mode: flyspell
+%% LocalWords: Tjark Uppsala
+%% End:

### 2015-08-03 2014/report/SMTCOMP.tex
Minor.

@@
 
-SMT-COMP 2014 successfully executed the comparison among solvers that is the main goal
-of the competition.
+SMT-COMP 2014 successfully executed the comparison among solvers that is the main goal of the competition.
 The new computational infrastructure, StarExec, worked very well for the purpose.
@@
 Although the 2014 results are not readily comparable to previous years (because of changes in benchmarks and equipment), the detailed performance of each solver on each benchmark from this first year using StarExec will be a solid baseline to measure improvements in the state-of-the-art of solver performance in future years.
-As a partial comparison, solvers that performed well in previous years are included in the this year's competition.
+As a partial comparison, solvers that performed well in previous years were included in this year's competition.
 However, rerunning the competition on the old hardware or on the old benchmarks was out of the scope of the organizers' task.
@@
 The SMT steering committee is proposing that SMT-COMP 2015 will be held in association with the SMT Workshop, which itself will be affiliated with CAV 2015 in San Franciso, CA, USA from July 18-24, 2015.
-The SMT Workshop is being organized by
-Vijay Ganesh and
-Dejan Jovanovi\'c; the organizers of the competition are Tjark Weber, David D\'eharbe, and Sylvain Conchon.
+The SMT Workshop is being organized by Vijay Ganesh and Dejan Jovanovi\'c; the organizers of the competition are Tjark Weber, David D\'eharbe, and Sylvain Conchon.
 
@@
 \item The organizers were supported by their respective institutions (GrammaTech, Federal University of Rio Grande do Norte, Brazil and Uppsala University, Sweden respectively).
-
-\item In addition Cok received partial support from the U.S.\ National Science Foundation
-under grant ACI-1314674.
-
-\item Clark Barrett and Morgan Deters assisted with some aspects of benchmark preparation,
-in their roles as SMT-LIB coordinators.
-
-\item Aaron Stump and the StarExec support team were essential in keeping the competition cluster running;
-in this first large-scale, public use of the cluster, numerous small details needed correction and were corrected promptly.
-%
-The StarExec cluster is supported by
-U.S.\ National Science Foundation under grants \#1058748 and \#1058925.
-%
+In addition, Cok received partial support from the U.S.\ National Science Foundation under grant ACI-1314674.
+
+\item Clark Barrett and Morgan Deters assisted with some aspects of benchmark preparation, in their roles as SMT-LIB coordinators.
+
+\item Aaron Stump and the StarExec support team were essential in keeping the competition cluster running; in this first large-scale, public use of the cluster, numerous small details needed correction and were corrected promptly.
+The StarExec cluster is supported by the U.S.\ National Science Foundation under grants \#1058748 and \#1058925.
+
 \item The cost of executing the SMT Competition is underwritten by the SMT Workshop.
@@
 
-Any opinions,
-findings, and conclusions or recommendations expressed in this
-material are those of the authors and do not necessarily reflect the
-views of the National Science Foundation.
+Any opinions, findings, and conclusions or recommendations expressed in this material are those of the authors, and do not necessarily reflect the views of the National Science Foundation.
 
@@
 \end{document}
-
-\thebibliography
 

### 2015-08-04 2014/report/SMTCOMP.tex
Additional comment on main track results.

@@
 
-\davidc{Update the reference for SLCOMP}
-\davidd{Added a journla submission on SLCOMP 2014}
 \davidc{Add other solvers, SV-COMP?}
@@
 
-Unfortunately, we cannot make a useful comparison with previous years for a number of reasons.
-First, until the evaluation in 2013, the competition was run on a different computation infrastructure, so solution times are not comparable.
-The SMT evaluation in 2013 and the competition in 2014 were both run on StarExec but with different timeouts and different configurations of nodes.
-Finally the early data from StarExec only captured wall-clock time, not CPU time.
+The results of the competition per se were not surprising.
+The solvers that performed best in previous years continued to do so.
+Boolector wins those divisions that focus on bit-vector problems; CVC4 has the most breadth of application and wins most of the other divisions, with Yices2 also having a strong showing.
+Solvers that were optimized with particular decision procedures for particular logics can capture individual wins: AProVE for QF\_NIA; veriT for UFLRA.
+If Z3 had competed, with the current version entered by the organizers, it would have won many divisions, but not all; CVC4 is
+definitely competitive with it.
+Table \ref{Table:maintrack} does not show the computation time used by the solvers; however, that data is available in the detailed results and shows that of the leading contenders for broad application across logics, Z3 is the most efficient and is the solver to beat in future competitions.
+
+In the medal ceremony for the competition at the SMT workshop, the organizers took care not to focus only on the winning solvers.
+The competition was also successful in attracting new interest and many new entrants, even when the new entrants did not score highly or had errors in their submissions.
+In that sense the decision of the SMT steering committee to pause
+the competition for a year, to 'reboot' it and give contestants some breathing room, was also successful.
+
+The organizers chose not to try to make a detailed comparison with previous years' results. Such a comparison had just been
+completed in the 2013 Evaluation exercise. Furthermore, with the change in computation hardware, an accurate comparison
+would have required running all of the 2012 solvers along with the 2014 solvers and making a comparison on just the
+benchmarks used in the 2012 competition. While this is certainly possible, the organizers were not confident enough of the
+ability of the new StarExec to complete even the 2014 competition to contemplate doubling the computational load.
+In addition, such an exercise was out of the scope of their mandate and would have required considerable extra effort.
+However, knowing now that StarExec is fully capable of executing all of the competition benchmarks, such a
+comparative exercise would be definitely possible in the future.
 The organizers are confident that the 2014 data will be a solid baseline for evaluating progress in solver performance in future years.
-
-\davidc{Revise the paragraph above per review comments}
-
-\davidc{More assessment needed}
 

### 2015-08-04 2014/report/SMTCOMP.tex
added info in rules for SL-COMP, QBF

@@
 single error in a division caused the solver to be scored lower than any other solver with no errors, even if the other solvers solved very few problems.
-For the SAT competition, an error outright disqualifies a tool in the category it occurs\footnote{See \url{http://satcompetition.org/2014/rules.shtml}.}.
+In its inaugural edition, the Separation Logic Competition (SL-COMP) adopted the same rules as SMT-COMP.
+For the SAT competition, however, an error outright disqualifies a tool in the category it occurs\footnote{See \url{http://satcompetition.org/2014/rules.shtml}.}.
+In the QBF Gallery, a competitive evaluation of solvers for Quantified Boolean Logic, the score is the number of solved instances.
 In contrast, in the SV-competition~\cite{svcomp-2015}, successful runs account positively towards the final score, while errors count negatively (with an increased weight).

### 2015-08-04 2014/report/SMTCOMP.tex
Additional analyses

@@
 definitely competitive with it.
-Table \ref{Table:maintrack} does not show the computation time used by the solvers; however, that data is available in the detailed results and shows that of the leading contenders for broad application across logics, Z3 is the most efficient and is the solver to beat in future competitions.
 
@@
 
-\begin{table}[H]
+\begin{table}
 \caption{Main track results}
@@
 
+\paragraph{Fastest solvers.} The competition does not weight time to solve a problem significantly.
+However, this is an important characteristic to any user.
+Hence we analyzed the competition results for each division to answer this question:
+for each solver, what fraction of the benchmarks for the division does that solver solve the fastest? 
+The data answering this question is shown in Table \ref{tab:speed}.
+For each division and each benchmark, we determined the solver that solved that benchmark the fastest, and for each solver counted the number of benchmarks for which it was the fastest.
+The table lists the three solvers with the most such benchmarks, with the fraction of benchmarks that it won.
+The winning solvers are a mix of Z3, CVC, Yices2, and a few for veriT.
+In some division, the winning solver does dominate teh competition.
+Yices2, for example tends to win in those divisions in which it participates, with Z3 winning most of the others.
+Note that this analysis does not take into account the margin by which the times are better.
+The times used here are cpu-times; usinjg wall-clock times changes the fractions and sometimes the order, but not the overall observation.
+
+\begin{table}
+\begin{tabular}{|l|lll|}
+\hline
+Logic & Fraction solved fastest & \\
+\hline
+ALIA & 51\% [Z3] & 48\% veriT  & \\
+AUFLIA & 66\% [Z3] & 33\% CVC3  & \\
+AUFLIRA & 60\% [Z3] & 37\% veriT & 1\% CVC3 \\
+AUFNIRA & 72\% [Z3] & 23\% CVC3 & 2\% CVC4 \\
+LIA & 43\% CVC4 & 30\% [Z3] & 17\% CVC3 \\
+LRA & 42\% CVC4 & 38\% veriT & 18\% [Z3] \\
+NIA & 66\% [Z3] & 33\% CVC4  & \\
+NRA & 96\% CVC4 & 3\% [Z3]  & \\
+QF\_ABV & 78\% Yices2 & 9\% SONOLAR & 7\% Kleaver-STP \\
+QF\_ALIA & 95\% Yices2 & 4\% [Z3] & \\
+QF\_AUFBV & 81\% Yices2 & 10\% [MathSAT] & 5\% [Z3] \\
+QF\_AUFLIA & 60\% Yices2 & 38\% [Z3] & 1\% CVC4 \\
+QF\_AX & 92\% Yices2 & 6\% [Z3] & 0\% CVC4 \\
+QF\_BV & 33\% Yices2 & 25\% [Z3] & 13\% 4Simp \\
+QF\_IDL & 87\% Yices2 & 11\% [Z3] & 0\% veriT \\
+QF\_LIA & 76\% Yices2 & 11\% [Z3] & 7\% CVC4 \\
+QF\_LRA & 86\% Yices2 & 3\% veriT & 3\% CVC4 \\
+QF\_NIA & 90\% [Z3] & 7\% AProVE & 1\% CVC3 \\
+QF\_NRA & 88\% [Z3] & 6\% CVC4 & 4\% CVC3 \\
+QF\_RDL & 71\% Yices2 & 25\% [Z3] & 3\% veriT \\
+QF\_UF & 96\% Yices2 & 1\% veriT & 1\% [Z3] \\
+QF\_UFBV & 96\% Yices2 & 3\% [MathSAT]  & \\
+QF\_UFIDL & 59\% [Z3] & 36\% Yices2 & 3\% veriT \\
+QF\_UFLIA & 97\% Yices2 & 2\% [Z3] & 0\% CVC4 \\
+QF\_UFLRA & 91\% Yices2 & 4\% [Z3] & 2\% veriT \\
+QF\_UFNIA & 100\% CVC4 & \\
+QF\_UFNRA & 59\% CVC3 & 37\% [Z3] & 3\% CVC4 \\
+UF & 37\% veriT & 32\% CVC4 & 24\% [Z3] \\
+UFIDL & 57\% CVC4 & 42\% [Z3]  & \\
+UFLIA & 56\% [Z3] & 35\% veriT & 7\% CVC4 \\
+UFLRA & 95\% veriT & 4\% [Z3]  & \\
+UFNIA & 80\% [Z3] & 10\% CVC3 & 9\% CVC4 \\
+
+\hline
+\end{tabular}
+\caption{Fraction of benchmarks solved fastest (cpu-time) by each solver (top 3)}
+\label{tab:speed}
+\end{table}
+
+\paragraph{Solver contribution.} A second comparison that can be made is to determine what a solver adds in addition to 
+what other solvers contribute.
+We measure this `solver contribution' as follows.
+For each benchmark in a division, we award each solver that solves the benchmarks $1/n$ points, where $n$ is the number of solvers that solved the benchmark (within the timeout).
+These points are then summed over all the benchmarks in the division and scaled by the number of benchmarks.
+The sum is a measure of the
+unique contribution provided by a solver; a value of 1.0 would indicate that that solver was the only solver to solve all of the benchmarks in the division.
+The results are shown in Table \ref{tab:cont}.
+The results show again that no one solver dominates in all categories, but that there are several contributing solvers among which users can choose.
+
+\begin{table}
+\begin{tabular}{|l|lll|}
+\hline
+Logic & Unique contribution & & \\
+\hline
+ALIA & 0.4253 [Z3] & 0.4080 CVC4 & 0.1667 veriT \\
+AUFLIA & 0.3889 CVC4 & 0.2778 [Z3] & 0.2222 CVC3 \\
+AUFLIRA & 0.2615 [Z3] & 0.2521 CVC4 & 0.2503 CVC3 \\
+AUFNIRA & 0.2509 [Z3] & 0.2506 CVC4 & 0.2497 CVC3 \\
+LIA & 0.3949 [Z3] & 0.3514 CVC4 & 0.2319 CVC3 \\
+LRA & 0.3070 CVC4 & 0.3070 [Z3] & 0.2895 CVC3 \\
+NIA & 0.8333 [Z3] & 0.1667 CVC4 & 0.0000 Yices2 \\
+NRA & 0.5071 [Z3] & 0.4929 CVC4 & 0.0000 Yices2 \\
+QF\_ABV & 0.1147 Yices2 & 0.1146 Boolector-just... & 0.1144 Boolector-dual... \\
+QF\_ALIA & 0.2235 Yices2 & 0.2235 SMTInterpol & 0.2235 [Z3] \\
+QF\_AUFBV & 0.2635 [MathSAT] & 0.2635 CVC4 & 0.2500 Yices2 \\
+QF\_AUFLIA & 0.1996 Yices2 & 0.1996 [MathSAT] & 0.1996 CVC4 \\
+QF\_AX & 0.2000 Yices2 & 0.2000 [MathSAT] & 0.2000 CVC4 \\
+QF\_BV & 0.1051 Boolector & 0.0976 STP-Crypto... & 0.0934 abziz\_min\_features \\
+QF\_IDL & 0.2893 [Z3] & 0.2731 Yices2 & 0.2395 CVC4 \\
+QF\_LIA & 0.1620 [CVC4-with-bugfix] & 0.1610 [Z3] & 0.1610 SMTInterpol \\
+QF\_LRA & 0.1772 CVC4 & 0.1689 Yices2 & 0.1678 SMTInterpol \\
+QF\_NIA & 0.4990 [Z3] & 0.4912 AProVE & 0.0084 CVC3 \\
+QF\_NRA & 0.7714 [Z3] & 0.1347 CVC3 & 0.0898 CVC4 \\
+QF\_RDL & 0.2734 Yices2 & 0.2431 veriT & 0.2431 [Z3] \\
+QF\_UF & 0.1451 Yices2 & 0.1449 veriT & 0.1446 CVC4 \\
+QF\_UFBV & 0.4140 Yices2 & 0.3172 [Z3] & 0.1720 [MathSAT] \\
+QF\_UFIDL & 0.2708 Yices2 & 0.2708 [Z3] & 0.2309 CVC4 \\
+QF\_UFLIA & 0.1698 Yices2 & 0.1698 [MathSAT] & 0.1698 CVC4 \\
+QF\_UFLRA & 0.1715 [Z3] & 0.1681 Yices2 & 0.1681 [MathSAT] \\
+QF\_UFNIA & 0.5000 CVC4 & 0.5000 [Z3] & 0.0000 Yices2 \\
+QF\_UFNRA & 0.5802 [Z3] & 0.2099 CVC4 & 0.2099 CVC3 \\
+UF & 0.4921 CVC4 & 0.1988 [Z3] & 0.1759 CVC3 \\
+UFIDL & 0.5204 [Z3] & 0.4796 CVC4 & 0.0000 Yices2 \\
+UFLIA & 0.4069 CVC4 & 0.3502 [Z3] & 0.2425 veriT \\
+UFLRA & 0.2857 [Z3] & 0.2381 CVC4 & 0.2381 veriT \\
+UFNIA & 0.4156 [Z3] & 0.3860 CVC4 & 0.1984 CVC3 \\
+\hline
+\end{tabular}
+\caption{Contribution from each solver (top 3)}
+\label{tab:cont}
+\end{table}
+
 \paragraph{Effect of timeout.}

### 2015-08-04 2014/report/SMTCOMP.tex
Fixed outline

@@
 
-In the succeeding sections we describe the context of the competition (\S\ref{sec:context}), its goals and organization (\S\ref{sec:goals}), procedure (\S\ref{sec:procedure}), participants (\S\ref{sec:participants}), benchmarks (\S\ref{sec:benchmarks}), computational infrastructure (\S\ref{sec:starexec}), results (\S\ref{sec:results}), the place of SMT-COMP in the FLoC Olympic Games (\S\ref{sec:floc}), and post-competition activities (\S\ref{sec:post}).
+In the succeeding sections we describe 
+the competition goals (\S\ref{sec:goals}), 
+the SMT-LIB language that is the basis for the competition (\S\ref{sec:context}), 
+the competition benchmarks (\S\ref{sec:benchmarks}), 
+participants (\S\ref{sec:participants}), 
+procedure (\S\ref{sec:procedure}),
+computational infrastructure (\S\ref{sec:starexec}), 
+comparisons with other competitions (\S\ref{sec:OtherCompetitions}), 
+the results (\S\ref{sec:results}), 
+the place of SMT-COMP in the FLoC Olympic Games (\S\ref{sec:floc}), 
+and post-competition activities (\S\ref{sec:post}). 
 Section \ref{sec:conclusions} presents observations on this competition and recommendations for the future.
-
-\davidc{Correct the outline}
 

### 2015-08-04 2014/report/SMTCOMP.tex
Last Todo's but one

@@
 Since in 2014 we also had to migrate to using the new StarExec cluster to execute the competition, we held only a main track and an application (incremental) track in the 2014 competition.
-The organizers still appreciate the value of measuring the performance of solvers on new features such as model generation, unsat core determination, and proof generation, and recommend that these tracks be reinstated in some future edition of the competition.
-\item A significant change in 2014 was to increase the timeout limit for a solver processing a given benchmark from 25 minutes (in 2012) to 40 minutes (see \S\ref{sec:procedure} for details on the competition parameters and \S\ref{sec:timeouts} for a discussion on their effects).
-
+The organizers still appreciate the value of measuring the performance of solvers on new features such as parallel processing, model generation, unsat core determination, and proof generation, and recommend that these tracks be reinstated in some future edition of the competition.
+\item An additional goal was to be able to evaluate the effect of the timeout setting on the competition.
+Thus a change in 2014 was to increase the timeout limit for a solver processing a given benchmark from 25 minutes (in 2012) to 40 minutes (see \S\ref{sec:procedure} for details on the competition parameters and \S\ref{sec:timeouts} for a discussion on their effects).
 \end{itemize}
@@
 Second, the results described are obtained by observing the wall-clock solution time when the timeout value is set at 2400 seconds.
-Solvers, if told what the timeout value is, have the option to adjust their search strategies based on the timeout; the solvers might then exhibit better behavior for shorter timeout.\footnote{Though solvers could use the timeout value, current versions of those queried\textemdash Yices2, Z3, Boolector\textemdash do not do so.
+Solvers, if told what the timeout value is, have the option to adjust their search strategies based on the timeout; the solvers might then exhibit better behavior for shorter timeout.\footnote{Though solvers could use the timeout value to alter their processing algorithms, current versions of those queried\textemdash Yices2, Z3, Boolector\textemdash do not do so.
 However, CVC4 and CVC3 do build in the stated timeout into the script used for competition (though it is not used by the core solver) and so might show differences from the behavior stated here.}
@@
 \begin{center}
-\includegraphics[width=.95\textwidth]{QF_BV-timeout-logscale.pdf}
+\includegraphics[width=.95\textwidth]{QF_BV-timeout-logscale2.png}
 \end{center}
@@
 
-Based on the experience of 2014, the 2014 organizers have the following recommendations or topics for consideration for future competitions.
+\paragraph{Observations}
+
+Solver implementors continue to focus primarily on raw numbers of problems solved. We think that future competitions can 
+help broaden the focus to encompass breadth of problems addressed, fast solutions on simple problems, and other features provided by the SMT-LIB command language.
+
+An unexpected observation is that there is indeed a difference in outcome of even a straightforward competition depending on the value of timeout chosen.
+As a result, there might indeed be an interest and valuable result from trying a competition track focused on fast solving of relatively simple problems.
+
+A satisfying observation is that there is indeed reasonable competition among several highly-performing solvers, as measured by the unique contributions each makes and the distribution of fastest times.
+
+\paragraph{Recommendations.} Based on the experience of 2014, the 2014 organizers have the following recommendations or topics for consideration for future competitions.
 \begin{itemize}
@@
 \item The difficulty in preparing a new solver for submission to StarExec for participation in SMT-COMP should be reduced.
-\item Resolve the definition of divide-by-zero behavior in SMT-LIB (cf.~\S\ref{par:undefined}).
+\item A general means to resolve questions surrounding partial definitions is needed in SMT-LIB, e.g., for divide-by-zero  (cf.~\S\ref{par:undefined}).
 \item An item for study is the effect of benchmark scrambling on the outcome of solver comparisons.

### 2015-08-05 2014/report/SMTCOMP.tex
My final edits.

@@
 \item STP-CryptoMiniSat4~\cite{DBLP:conf/cav/GaneshD07,DBLP:conf/cav/2007} -- submitted by Mate Soos (Security Research Lab.), based on previous work by Trevor Hansen (U.~Melbourne) and Vijay Ganesh (Massachusetts Institute of Technology)
-\item veriT~\cite{veriT} -- submitted by David D\'{e}harbe (UFRN - Universidade Federal do Rio Grande do Norte), Pascal Fontaine (U.~Lorraine, INRIA - Institut national de recherche en informatique et en automatique)
+\item veriT~\cite{veriT} -- submitted by David D\'{e}harbe (UFRN - Universidade Federal do Rio Grande do Norte) and Pascal Fontaine (U.~Lorraine, INRIA - Institut national de recherche en informatique et en automatique)
 \item Yices2~\cite{Dutertre:cav2014} -- submitted by Bruno Dutertre (SRI)
@@
 %% reused in future years.
-The execution of SMT-COMP on StarExec went well, though not flawlessly. As this was a first major use of StarExec for a competition there were some bugs to work through.
+The execution of SMT-COMP on StarExec went well, though not flawlessly: there were some bugs to work through.
 The organizers had some bugs of their own: the scripts to create sets of benchmarks and jobs did not account for spaces in filenames; some initial report generation was incorrect; the postprocessor for translating textual output from solvers into official results needed fine-tuning.
@@
 
-\davidc{Add other solvers, SV-COMP?}
-
 \paragraph{SL-COMP} Besides the subject material, the most interesting difference among competitions is in scoring. (The scoring procedure for
@@
 In contrast, in the SV-competition~\cite{svcomp-2015}, successful runs account positively towards the final score, while errors count negatively (with an increased weight).
-
-\davidc{Research a wider set of competitions}
+A few other sibling competitions with scoring variations are the Answer-Set Programming competition (ASP-COMP: wrong answers receive a 0 score), the Confluence Competition (CoCo: implausible answers disqualify from winning), and Syntax-Guided Synthesis (SyGuS-COMP: no points for wrong answers, extra points for succinct answers).
 
@@
 The winning solvers are a mix of Z3, CVC, Yices2, and a few for veriT.
-In some division, the winning solver does dominate teh competition.
+In some divisions, the winning solver does dominate the competition.
 Yices2, for example tends to win in those divisions in which it participates, with Z3 winning most of the others.
 Note that this analysis does not take into account the margin by which the times are better.
-The times used here are cpu-times; usinjg wall-clock times changes the fractions and sometimes the order, but not the overall observation.
+The times used here are cpu-times; using wall-clock times changes the fractions and sometimes the order, but not the overall observation.
 
@@
 We measure this `solver contribution' as follows.
-For each benchmark in a division, we award each solver that solves the benchmarks $1/n$ points, where $n$ is the number of solvers that solved the benchmark (within the timeout).
+For each benchmark in a division, we award each solver that solves the benchmark $1/n$ points, where $n$ is the number of solvers that solved the benchmark (within the timeout).
 These points are then summed over all the benchmarks in the division and scaled by the number of benchmarks.
@@
 
+\begin{figure}[H]
+\begin{center}
+\includegraphics[width=.95\textwidth]{QF_BV-timeout-logscale2.png}
+\end{center}
+\caption{Solver success for QF\_BV benchmarks over time.}
+\label{Fig:timeouts}
+\end{figure}
+
 There are two caveats to this observation.
@@
 The data in Table~\ref{Fig:winners} also shows that most solvers have a similar trend in success as the timeout is increased.
-For example, most solvers solve about 50\% (ranging from 40\% to 62\%) of the benchmarks that solver solves by 2400 seconds by 1.0 second and
-about 75\% (ranging from 65\% to 79\%) of those solved by 2400 seconds by 10 seconds.
+For example, most solvers solve about 50\% (ranging from 40\% to 62\%) of the benchmarks that solver solves within the timeout by 1.0 second and
+about 75\% (ranging from 65\% to 79\%) of those solved within the timeout by 10 seconds.
 However, some solvers, such as Boolector, are outliers: Boolector is slow off the mark - solving only 33\% and 61\% of the benchmarks it eventually solves
 by 1 second and 10 seconds, respectively, even though by 2400 seconds it solves more benchmarks than any other tool, in this division.
-
-\begin{figure}
-\begin{center}
-\includegraphics[width=.95\textwidth]{QF_BV-timeout-logscale2.png}
-\end{center}
-\caption{Solver success for QF\_BV benchmarks over time.}
-\label{Fig:timeouts}
-\end{figure}
 
@@
 
-\begin{table}
+\begin{table}[H]
 \caption{Numbers of application benchmarks and distribution of \lstinline{check-sat} commands for different logics.}
@@
 As a partial comparison, solvers that performed well in previous years were included in this year's competition.
-However, rerunning the competition on the old hardware or on the old benchmarks was out of the scope of the organizers' task.
-
-The SMT steering committee is proposing that SMT-COMP 2015 will be held in association with the SMT Workshop, which itself will be affiliated with CAV 2015 in San Franciso, CA, USA from July 18-24, 2015.
+
+The SMT steering committee proposed that SMT-COMP 2015 be held in association with the SMT Workshop, which itself will be affiliated with CAV 2015 in San Franciso, CA, USA from July 18-24, 2015.
 The SMT Workshop is being organized by Vijay Ganesh and Dejan Jovanovi\'c; the organizers of the competition are Tjark Weber, David D\'eharbe, and Sylvain Conchon.
@@
 
-A satisfying observation is that there is indeed reasonable competition among several highly-performing solvers, as measured by the unique contributions each makes and the distribution of fastest times.
+A satisfying observation is that there is reasonable competition among several highly-performing solvers, as measured by the unique contributions each makes and the distribution of fastest times.
 

### 2015-08-06 2014/report/SMTCOMP.tex
updated application track results

@@
 considers the benchmark to end after the \emph{previous} \lstinline{check-sat} command for competition purposes.
+The driver originally used to collect the answers had a bug that was
+detected and reported by Kshitij Bansal~\cite{bansal2015email}, which
+also provided a corrected version of the driver. The results discussed
+in this section were obtained with this new driver.
 
@@
 Table \ref{Fig:apptrack-benchmarks} lists the numbers of benchmarks in various logics; UFLRA, QF\_UFLRA, and QF\_UFLIA are the only logics with significant numbers of benchmarks.
+For now, AUFNIRA does not contain any valid \lstinline{check-sat} command.
 All the benchmarks were used in the competition.
@@
 Four solvers participated in this competition track: CVC3, CVC4, SMTInterpol, and Yices2; Z3 was added as a demonstration-only historical comparison.
-The track was run for 8 divisions; the results are shown in Table \ref{Fig:apptrack-results}.
-Within each division, solvers are listed in winning order: Yices2 won six of the eight divisions, all of the ones in which it participated.
 The winner is the solver that solved the most \lstinline{check-sat} commands correctly within the timeout period.
@@
 The time out (40 minutes) is applied to the entire benchmark, not to individual commands.
+The track was run for 8 divisions; the results are shown in Table \ref{Fig:apptrack-results}.
+Within each division, solvers are listed in winning order: Yices2 won four of the eight divisions, out of six in which it participated.
+CVC3, CVC4 and SMTInterpol won one division each.
 Since the previous execution of the application track was in 2012 and not on StarExec, we did not attempt a comparison with previous results.

### 2015-08-06 2014/report/SMTCOMP.tex
Slight correction and embellishment of DD's revision

@@
 The driver originally used to collect the answers had a bug that was
-detected and reported by Kshitij Bansal~\cite{bansal2015email}, which
+detected and reported by Kshitij Bansal~\cite{bansal2015email}, who
 also provided a corrected version of the driver. The results discussed
-in this section were obtained with this new driver.
+in this section were obtained with this new driver and differ from those reported
+earlier, such as at the 2014 SMT workshop.
 

### 2015-08-07 2014/report/SMTCOMP.tex
SMT workshop -> SMT Workshop (for uniformity).

@@
 \begin{abstract}
-The 2014 SMT Competition was held in conjunction with the SMT workshop, affiliated with the CAV, IJCAR, and SAT conferences at FLoC 2014, at the Vienna Summer of Logic in July 2014.
+The 2014 SMT Competition was held in conjunction with the SMT Workshop, affiliated with the CAV, IJCAR, and SAT conferences at FLoC 2014, at the Vienna Summer of Logic in July 2014.
 Eighteen solvers participated from thirteen different research groups, across 34 different logic divisions.
@@
 
-The competition is sponsored by the SMT workshop, which was held in conjunction with the
+The competition is sponsored by the SMT Workshop, which was held in conjunction with the
 CAV, IJCAR, and SAT conferences at FLoC 2014~\cite{FLoC2014}, at the Vienna Summer of Logic~\cite{VSL} in July 2014.
@@
 
-In the medal ceremony for the competition at the SMT workshop, the organizers took care not to focus only on the winning solvers.
+In the medal ceremony for the competition at the SMT Workshop, the organizers took care not to focus only on the winning solvers.
 The competition was also successful in attracting new interest and many new entrants, even when the new entrants did not score highly or had errors in their submissions.
@@
 in this section were obtained with this new driver and differ from those reported
-earlier, such as at the 2014 SMT workshop.
+earlier, such as at the 2014 SMT Workshop.
 

### 2015-08-07 2014/report/SMTCOMP.tex
No period (.) at the end of subsection titles (for uniformity).
Layout tweaks to avoid overfull LaTeX boxes.
Table 8 (fraction solved fastest) centered, frames fixed.

@@
 %%\small
-\setlength\tabcolsep{3pt}
+\setlength\tabcolsep{2.9pt}
 %%\begin{tabular}{|l|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|}
@@
 
-\subsection{Application benchmarks.}
+\subsection{Application benchmarks}
 
@@
 
-\subsection{Selection of benchmarks. \label{sec:benchmark-selection}}
+\subsection{Selection of benchmarks}
+\label{sec:benchmark-selection}
 
@@
 \setlength{\tabcolsep}{1pt}
-\begin{tabular}{|l@{\,\,}l|c|c|c|c|c|c|c|c|c|}
+\scalebox{1}[.984]{\begin{tabular}{|l@{\,\,}l|c|c|c|c|c|c|c|c|c|}
 \hline
@@
 \hline
-\end{tabular}
+\end{tabular}}
 \end{table}
@@
 \caption{\label{tab:timeline}Competition timeline}
-\scalebox{1}{
-\begin{tabular}{r |@{\hspace{-2.3pt}$\bullet$ \hspace{5pt}} p{.8\textwidth}}
+\begin{tabular}{r |@{\hspace{-2.3pt}$\bullet$ \hspace{5pt}} p{.75\textwidth}}
 Jul. 2013 & Cok appointed as chair of the organizing committee\\
@@
 \end{tabular}
-}
 \end{table}
@@
 \begin{table}
-\begin{tabular}{|l|lll|}
-\hline
-Logic & Fraction solved fastest & \\
-\hline
+\centering\begin{tabular}{|l|lll|}
+\hline
+Logic & Fraction solved fastest & & \\ \hline
 ALIA & 51\% [Z3] & 48\% veriT  & \\
@@
 QF\_UFLRA & 91\% Yices2 & 4\% [Z3] & 2\% veriT \\
-QF\_UFNIA & 100\% CVC4 & \\
+QF\_UFNIA & 100\% CVC4 & & \\
 QF\_UFNRA & 59\% CVC3 & 37\% [Z3] & 3\% CVC4 \\

### 2015-08-07 2014/report/SMTCOMP.tex
Layout tweaks to avoid overfull LaTeX boxes.

@@
 \begin{table}
-\begin{tabular}{|l|lll|}
+\centering\begin{tabular}{|l|lll|}
 \hline
@@
 QF\_AX & 0.2000 Yices2 & 0.2000 [MathSAT] & 0.2000 CVC4 \\
-QF\_BV & 0.1051 Boolector & 0.0976 STP-Crypto... & 0.0934 abziz\_min\_features \\
+QF\_BV & 0.1051 Boolector & 0.0976 STP-Crypto... & 0.0934 abziz\_min\_f... \\
 QF\_IDL & 0.2893 [Z3] & 0.2731 Yices2 & 0.2395 CVC4 \\
-QF\_LIA & 0.1620 [CVC4-with-bugfix] & 0.1610 [Z3] & 0.1610 SMTInterpol \\
+QF\_LIA & 0.1620 [CVC4-...fix] & 0.1610 [Z3] & 0.1610 SMTInterpol \\
 QF\_LRA & 0.1772 CVC4 & 0.1689 Yices2 & 0.1678 SMTInterpol \\

### 2016-01-11 2014/report/SMTCOMP.tex
ASP-COMP scoring clarified.

@@
 \paragraph{SL-COMP} Besides the subject material, the most interesting difference among competitions is in scoring. (The scoring procedure for
-SMT-COMP is described in detail in section \ref{sec:floc}.)
+SMT-COMP is described in detail in Section~\ref{sec:floc}.)
 Competitions are currently mostly focused on raw solver capability---that is, the numbers and difficulty of problems that can be solved.
@@
 In its inaugural edition, the Separation Logic Competition (SL-COMP) adopted the same rules as SMT-COMP.
-For the SAT competition, however, an error outright disqualifies a tool in the category it occurs\footnote{See \url{http://satcompetition.org/2014/rules.shtml}.}.
-In the QBF Gallery, a competitive evaluation of solvers for Quantified Boolean Logic, the score is the number of solved instances.
+For the SAT competition, however, an error outright disqualifies a tool in the category it occurs.\footnote{See \url{http://satcompetition.org/2014/rules.shtml}.} In the QBF Gallery, a competitive evaluation of solvers for Quantified Boolean Logic, the score is the number of solved instances.
 In contrast, in the SV-competition~\cite{svcomp-2015}, successful runs account positively towards the final score, while errors count negatively (with an increased weight).
-A few other sibling competitions with scoring variations are the Answer-Set Programming competition (ASP-COMP: wrong answers receive a 0 score), the Confluence Competition (CoCo: implausible answers disqualify from winning), and Syntax-Guided Synthesis (SyGuS-COMP: no points for wrong answers, extra points for succinct answers).
+A few other sibling competitions with scoring variations are the Answer-Set Programming competition (ASP-COMP: wrong answers for some problem instance cause an overall score of zero for the problem), the Confluence Competition (CoCo: implausible answers disqualify from winning), and Syntax-Guided Synthesis (SyGuS-COMP: no points for wrong answers, extra points for succinct answers).
 

### 2016-01-11 2014/report/SMTCOMP.tex
Further second-round comments addressed.

@@
 the competition benchmarks (\S\ref{sec:benchmarks}), 
-participants (\S\ref{sec:participants}), 
+participants~(\S\ref{sec:participants}), 
 procedure (\S\ref{sec:procedure}),
 computational infrastructure (\S\ref{sec:starexec}), 
-comparisons with other competitions (\S\ref{sec:OtherCompetitions}), 
+comparisons with other competitions~(\S\ref{sec:OtherCompetitions}), 
 the results (\S\ref{sec:results}), 
@@
 For example,  the logic of linear arithmetic includes the multiplication operation, but only allows multiplication by constants.
-Each problem is a set of closed formulas over a set of constant or function symbols, possibly including quantification; a solution to the problem is an assignment of each constant and function evaluation to values in a way that satisfies all the problem's assertions.
+Each problem is a set of closed formulas (possibly including quantification over variables) over a set of constant or function symbols; a solution to the problem is an assignment of each constant and function evaluation to values in a way that satisfies all the problem's assertions.
 That is, the task is to find a \emph{satisfying assignment} for the benchmark problem or to determine that there is no such assignment.
-Since the presence of quantified expressions introduces incompleteness, solvers may also produce a potential solution that may be marked as possibly incomplete.
+Since the presence of quantified expressions introduces incompleteness, solvers may also produce a potential solution that may be marked as possibly spurious.
 
@@
 In addition, there may be constraints on the set of expressions allowed, such as only linear arithmetic, or only integer difference arithmetic.
-The theories also define \emph{sorts}, which make the theories a kind of typed first-order logic.
+The theories also define \emph{sorts}, which make the theories a typed first-order logic.
 Examples of sorts used in current theories are Boolean, Int, Real, bit-vectors of various lengths, and arrays with arbitrary sorts as index and value.
 Each combination of underlying theories and language constraints is a \emph{logic}.
-The names of the logics as used in SMT-LIB are cryptic combinations of initials. For example, AUFLIA is the logic with a
+The names of the logics as used in SMT-LIB are combinations of initials. For example, AUFLIA is the logic with a
 combination of Arrays (A), Uninterpreted Functions (UF), and linear integer arithmetic (LIA). Table \ref{logicAbbreviations} can be used to interpret these names.
@@
 A & Arrays \\
-UF & Unidentified Functions \\
+UF & Uninterpreted Functions \\
 BV & Bit-Vector \\
@@
    (let ((m (max x y)))
-      (= (max (max x y) x) (max x y))))))
+      (= (max m x) m)))))
 (check-sat)
@@
 \\
-Non-incremental benchmarks & Application benchmarks
+Non-incremental benchmarks & Incremental benchmarks
 \end{tabular}
@@
 
-The numbers of unknown, trivial, and remaining eligible benchmarks are shown in Table \ref{Table:benchmarks}. Note that these numbers vary widely from division to division.
+The numbers of unknown, trivial, and remaining eligible benchmarks are shown in Table~\ref{Table:benchmarks}.
+Note that these numbers vary widely from division to division.
+As we discuss in Section~\ref{sec:benchmark-selection} below, all eligible benchmarks were actually used in the competition; these numbers are shown in bold.
 
@@
        & \multicolumn{1}{|c|}{\# of} & \multicolumn{4}{|c|}{\# of benchmarks} \\
- Logic & solvers & eligible & unknown  & trivial & total  \\
-\hline
-ALIA & 3+[1] & 29 & 0 & 13 & 42 \\
-AUFLIA & 3+[1] & 4 & 0 & 0 & 4\\
-AUFLIRA & 3+[1] & 10791 & 168 & 9055 & 20014 \\
-AUFNIRA & 2+[2] & 564 & 468 & 463 & 1495 \\
-BV & 2+[1] & 0 & 191 & 0 & 191 \\
-LIA & 3+[1] & 46 & 0 & 0 & 46 \\
-LRA & 3+[1] & 171 & 450 & 0 & 621\\
-NIA & 2+[1] & 9 & 0 & 0 & 9\\
-NRA & 2+[1] & 3747 & 66 & 0 & 3813 \\
-QF\_ABV & 7+[2] & 6457* & 4191 & 4423 & 15091 \\
-QF\_ALIA & 3+[2] & 97 & 0 & 29 & 126 \\
-QF\_AUFBV & 2+[2] & 37 & 0 & 0 & 37 \\
-QF\_AUFLIA & 4+[2] & 610 & 0 & 399 & 1009\\
-QF\_AX & 3+[2] & 335 & 0 & 216 & 551 \\
-QF\_BV & 8+[3] & 2488* & 28138 & 546 & 32500 \\
-QF\_IDL & 3+[1] & 1315 & 537 & 337 & 2189 \\
-QF\_LIA & 4+[3] & 4381 & 1279 & 481 & 6141 \\
-QF\_LRA & 4+[2] & 1343 & 208 & 131 & 1682\\
-QF\_NIA & 3+[1] & 8327 & 927 & 105 & 9359 \\
-QF\_NRA & 3+[1] & 10121 & 1392 & 27 & 11540 \\
-QF\_RDL & 3+[1] & 132 & 85 & 38 & 255 \\
-QF\_UF & 5+[2] & 4124 & 4 & 2522 & 6650 \\
-QF\_UFBV & 2+[2] & 31 & 0 & 0 & 31 \\
-QF\_UFIDL & 3+[1] & 311 & 0 & 130 & 441\\
-QF\_UFLIA & 4+[2] & 484 & 0 & 114 & 598 \\
-QF\_UFLRA & 4+[2] & 1176 & 87 & 367 & 1630 \\
-QF\_UFNIA & 2+[1] & 7 & 0 &0 & 7 \\
-QF\_UFNRA & 2+[1] & 32 & 11 & 0 & 43\\
-UF & 3+[1] & 2830 & 2911 & 7 & 5748 \\
-UFBV & 2+[1] & 0 & 191 & 0 & 191 \\
-UFIDL & 2+[1] & 49 & 12 & 19 & 80 \\
-UFLIA & 3+[1] & 5766 & 5499 & 873 & 12138 \\
-UFLRA & 3+[1] & 25 & 0 & 0 & 25\\
-UFNIA & 2+[1] & 1587 & 1052 & 712 & 3351 \\
-\hline
-Total & 18+[3] & 67426 & 47867 & 21007 & 137648 \\
+ Logic & solvers & {\bf eligible} & unknown  & trivial & total  \\
+\hline
+ALIA & 3+[1] & {\bf 29} & 0 & 13 & 42 \\
+AUFLIA & 3+[1] & {\bf 4} & 0 & 0 & 4\\
+AUFLIRA & 3+[1] & {\bf 10791} & 168 & 9055 & 20014 \\
+AUFNIRA & 2+[2] & {\bf 564} & 468 & 463 & 1495 \\
+BV & 2+[1] & {\bf 0} & 191 & 0 & 191 \\
+LIA & 3+[1] & {\bf 46} & 0 & 0 & 46 \\
+LRA & 3+[1] & {\bf 171} & 450 & 0 & 621\\
+NIA & 2+[1] & {\bf 9} & 0 & 0 & 9\\
+NRA & 2+[1] & {\bf 3747} & 66 & 0 & 3813 \\
+QF\_ABV & 7+[2] & {\bf 6457}* & 4191 & 4423 & 15091 \\
+QF\_ALIA & 3+[2] & {\bf 97} & 0 & 29 & 126 \\
+QF\_AUFBV & 2+[2] & {\bf 37} & 0 & 0 & 37 \\
+QF\_AUFLIA & 4+[2] & {\bf 610} & 0 & 399 & 1009\\
+QF\_AX & 3+[2] & {\bf 335} & 0 & 216 & 551 \\
+QF\_BV & 8+[3] & {\bf 2488}* & 28138 & 546 & 32500 \\
+QF\_IDL & 3+[1] & {\bf 1315} & 537 & 337 & 2189 \\
+QF\_LIA & 4+[3] & {\bf 4381} & 1279 & 481 & 6141 \\
+QF\_LRA & 4+[2] & {\bf 1343} & 208 & 131 & 1682\\
+QF\_NIA & 3+[1] & {\bf 8327} & 927 & 105 & 9359 \\
+QF\_NRA & 3+[1] & {\bf 10121} & 1392 & 27 & 11540 \\
+QF\_RDL & 3+[1] & {\bf 132} & 85 & 38 & 255 \\
+QF\_UF & 5+[2] & {\bf 4124} & 4 & 2522 & 6650 \\
+QF\_UFBV & 2+[2] & {\bf 31} & 0 & 0 & 31 \\
+QF\_UFIDL & 3+[1] & {\bf 311} & 0 & 130 & 441\\
+QF\_UFLIA & 4+[2] & {\bf 484} & 0 & 114 & 598 \\
+QF\_UFLRA & 4+[2] & {\bf 1176} & 87 & 367 & 1630 \\
+QF\_UFNIA & 2+[1] & {\bf 7} & 0 &0 & 7 \\
+QF\_UFNRA & 2+[1] & {\bf 32} & 11 & 0 & 43\\
+UF & 3+[1] & {\bf 2830} & 2911 & 7 & 5748 \\
+UFBV & 2+[1] & {\bf 0} & 191 & 0 & 191 \\
+UFIDL & 2+[1] & {\bf 49} & 12 & 19 & 80 \\
+UFLIA & 3+[1] & {\bf 5766} & 5499 & 873 & 12138 \\
+UFLRA & 3+[1] & {\bf 25} & 0 & 0 & 25\\
+UFNIA & 2+[1] & {\bf 1587} & 1052 & 712 & 3351 \\
+\hline
+Total & 18+[3] & {\bf 67426} & 47867 & 21007 & 137648 \\
 \hline
@@
 satisfiability checks, inspecting models, or obtaining unsatisfiability
-proofs. Benchmarks problems that have more than one
+proofs. Benchmark problems that have more than one
 \lstinline{check-sat} command are called \emph{application} or \emph{incremental
@@
 
-Benchmarks are also labeled by \emph{category}: simple checks, randomly generated problems from some template (e.g., N-queens problems for various values of N), problems crafted to test a certain capability, and problems obtained from industrial applications.
-The selection rules favor industrial benchmarks.
+Benchmarks are also labeled by \emph{category} (not shown in the tables): simple checks, randomly generated problems from some template (e.g., N-queens problems for various values of N), problems crafted to test a certain capability, and problems obtained from industrial applications.
+The selection rules in previous years favored industrial benchmarks.
 
@@
 Indeed, one solver encountered a bug during the competition that was directly related to the specific, randomly-chosen scrambling used during the competition.
-The effect of the possible variations in performance caused by scrambling is expected to be balanced by the large of number of benchmarks employed in the competition to compare the solvers, as also observed in the SAT community~\cite{leberre+03}.
+The effect of the possible variations in performance caused by scrambling is expected to be balanced by the large number of benchmarks employed in the competition to compare the solvers, as also observed in the SAT community~\cite{leberre+03}.
 Nevertheless, this point is worthy of future further investigation.
@@
 \begin{table}
+\caption{Fraction of benchmarks solved fastest (cpu-time) by each solver (top 3)}
+\label{tab:speed}
 \centering\begin{tabular}{|l|lll|}
@@
 \end{tabular}
-\caption{Fraction of benchmarks solved fastest (cpu-time) by each solver (top 3)}
-\label{tab:speed}
 \end{table}
@@
 \begin{table}
+\caption{Contribution from each solver (top 3)}
+\label{tab:cont}
 \centering\begin{tabular}{|l|lll|}
@@
 \end{tabular}
-\caption{Contribution from each solver (top 3)}
-\label{tab:cont}
 \end{table}
@@
 
-\begin{figure}[H]
+\begin{figure}
 \begin{center}
@@
 The data in Table~\ref{Fig:winners} also shows that most solvers have a similar trend in success as the timeout is increased.
-For example, most solvers solve about 50\% (ranging from 40\% to 62\%) of the benchmarks that solver solves within the timeout by 1.0 second and
+For example, most solvers solve about 50\% (ranging from 40\% to~62\%) of the benchmarks that solver solves within the timeout by 1.0 second and
 about 75\% (ranging from 65\% to 79\%) of those solved within the timeout by 10 seconds.
-However, some solvers, such as Boolector, are outliers: Boolector is slow off the mark - solving only 33\% and 61\% of the benchmarks it eventually solves
+However, some solvers, such as Boolector, are outliers: Boolector is slow off the mark---solving only~33\% and 61\% of the benchmarks it eventually solves
 by 1 second and 10 seconds, respectively, even though by 2400 seconds it solves more benchmarks than any other tool, in this division.
@@
 This activity required several weeks of computation.
-A result confirmed by at least two solvers was obtained for 75\% of the unknown benchmarks, with another 4\% having a tentative result from just one solver.
+A result confirmed by at least two solvers was obtained for~75\% of the unknown benchmarks, with another 4\% having a tentative result from just one solver.
 The results are shown in Table~\ref{Fig:post}.

### 2016-01-14 2014/report/SMTCOMP.tex
Copy-edited version received from Marijn Heule.

@@
 
-\sloppy
+%\sloppy
+
+\newif\ifsystemdescription
+\systemdescriptionfalse            % should only be true for system descriptions
+
+\newif\ifblackandwhite              
+\blackandwhitefalse                  % should only be true for the hard copy by IOS Press
+
+\usepackage{jsat_pdf}
+
+\input epsf 
+\special{papersize=8.5in,11in}
 
@@
 %\usepackage[USenglish]{babel} %francais, polish, spanish, ...
-\usepackage[T1]{fontenc}
+%\usepackage[T1]{fontenc}
 %\usepackage{textcomp}
@@
 %\usepackage{makeidx}	  %% needed to create an index
-\usepackage{jsat}
+%\usepackage{jsat}
 \usepackage{here}
-\usepackage{hyperref}   %% sets hyperlinks within a pdf
+%\usepackage{hyperref}   %% sets hyperlinks within a pdf
 \usepackage{graphicx}
-\usepackage{epstopdf}
-\usepackage{parskip}
-\usepackage{subcaption}
+%\usepackage{epstopdf}
+%\usepackage{parskip}
+%\usepackage{subcaption}
 \usepackage{enumitem}
-\usepackage{xcolor}
+%\usepackage{xcolor}
 \usepackage{rotating}
@@
 
-\jsatheading{number}{year}{startpage-endpage}
+\jsatheading{9}{2016}{207-242}
 \ShortHeadings{The 2014 SMT Competition}{D.\ Cok et al.}
-\firstpageno{1}
+\firstpageno{207}
 
@@
 \addr GrammaTech, Inc. \\
+Ithaca, New York\\
+United States
 \AND
@@
 \email{david@dimap.ufrn.br} \\
-\addr Federal University of Rio Grande do Norte, Brazil \\
+\addr Federal University of Rio Grande do Norte\\
+Natal\\
+Brazil 
 \AND
@@
 \email{tjark.weber@it.uu.se} \\
-\addr Uppsala University, Sweden}
+\addr Uppsala University\\
+Uppsala\\
+ Sweden}
 
@@
 
-%\published{December 2014}{revision date}{publication date}
+\published{December 2014}{October 2015}{January 2016}
 
@@
 Information about the winners
-and results of the competition is summarized in this report and is available online at \url{www.smtcomp.org}.  Information
+and results of the competition is summarized in this report and is available online at \url{http://www.smtcomp.org}.  Information
 about previous years' competitions is also available at that website and in published summary reports~\cite{springerlink:10.1007/s10817-012-9246-5,DBLP:conf/cade/CokGBD12,it:2014-017}.
@@
 \begin{table}
-\begin{center}
+\caption{Abbreviations used in logic names}
+\label{logicAbbreviations}
+\centering
 \begin{tabular}{|l|l|}
@@
 \end{tabular}
-\end{center}
-\caption{Abbreviations used in logic names}
-\label{logicAbbreviations}
 \end{table}
@@
 \begin{figure}
-\begin{center}
+\centering
 \begin{tabular}{cc}
@@
 \end{tabular}
-\end{center}
 \caption{Distribution of SMT-LIB benchmarks by file size.
@@
 
-A sizeable number of benchmarks, on the order of 30,000, were added during the lead up to the competition.
+A sizable number of benchmarks, on the order of 30,000, were added during the lead up to the competition.
 Some of these were submitted in previous years but never assessed and uploaded.
@@
 \begin{itemize}
-\item 4Simp -- submitted by Trevor Hansen (U. Melbourne)
+\item 4Simp -- submitted by Trevor Hansen (U. Melbourne)\\[-15pt]
 \item AbzizPortfolio -- two versions -- submitted by Mohammed Adbul Aziz (U.
 Cairo).
-This solver is atypical in that it is a portfolio solver: based on automated learning over benchmark characteristics, it chooses among other solvers to apply to the problem at hand.
-\item AProVe~\cite{AProVE2014} -- submitted by Carsten Fuhs (University College London)
-\item Boolector~\cite{Boolector2015} -- three versions: Boolector (default),  Boolector-d (dual propagation), Boolector-j (justification) -- submitted by Armin Biere, Aina Niemetz, Mathias Preiner (Johnnes Kepler University)
-\item CVC3 v. 2.4.3~\cite{BT07} -- submitted by Morgan Deters (New York University)
-\item CVC4 v. 1.4~\cite{BCD+11} -- submitted by the ACSys Group (New York University)
-\item Kleaver -- 2 versions -- submitted by Hristina Palikareva, Cristian Cadar (Imperial College)
-\item OpenSMT2 -- submitted by Antti Hyv\"arinen (U.~Lugano)
-\item raSAT~\cite{DBLP:conf/smt/KhanhVO14} -- submitted by Xuan-Tung Vu (Japan Advanced Insitute of Science and Technology)
-\item SMTInterpol~\cite{DBLP:conf/spin/ChristHN12,DBLP:conf/spin/2012} -- submitted by Jochen Hoenicke, J\"urgen Christ (U.~Freiburg)
-\item SONOLAR~\cite{Peleska:2011:ATC:1986308.1986333} -- submitted by Florian Lapschies (U.~Bremen)
-\item STP-CryptoMiniSat4~\cite{DBLP:conf/cav/GaneshD07,DBLP:conf/cav/2007} -- submitted by Mate Soos (Security Research Lab.), based on previous work by Trevor Hansen (U.~Melbourne) and Vijay Ganesh (Massachusetts Institute of Technology)
-\item veriT~\cite{veriT} -- submitted by David D\'{e}harbe (UFRN - Universidade Federal do Rio Grande do Norte) and Pascal Fontaine (U.~Lorraine, INRIA - Institut national de recherche en informatique et en automatique)
+This solver is atypical in that it is a portfolio solver: based on automated learning over benchmark characteristics, it chooses among other solvers to apply to the problem at hand.\\[-15pt]
+\item AProVe~\cite{AProVE2014} -- submitted by Carsten Fuhs (University College London)\\[-15pt]
+\item Boolector~\cite{Boolector2015} -- three versions: Boolector (default),  Boolector-d (dual propagation), Boolector-j (justification) -- submitted by Armin Biere, Aina Niemetz, Mathias Preiner (Johnnes Kepler University)\\[-15pt]
+\item CVC3 v. 2.4.3~\cite{BT07} -- submitted by Morgan Deters (New York University)\\[-15pt]
+\item CVC4 v. 1.4~\cite{BCD+11} -- submitted by the ACSys Group (New York University)\\[-15pt]
+\item Kleaver -- 2 versions -- submitted by Hristina Palikareva, Cristian Cadar (Imperial College)\\[-15pt]
+\item OpenSMT2 -- submitted by Antti Hyv\"arinen (U.~Lugano)\\[-15pt]
+\item raSAT~\cite{DBLP:conf/smt/KhanhVO14} -- submitted by Xuan-Tung Vu (Japan Advanced Insitute of Science and Technology)\\[-15pt]
+\item SMTInterpol~\cite{DBLP:conf/spin/ChristHN12,DBLP:conf/spin/2012} -- submitted by Jochen Hoenicke, J\"urgen Christ (U.~Freiburg)\\[-15pt]
+\item SONOLAR~\cite{Peleska:2011:ATC:1986308.1986333} -- submitted by Florian Lapschies (U.~Bremen)\\[-15pt]
+\item STP-CryptoMiniSat4~\cite{DBLP:conf/cav/GaneshD07,DBLP:conf/cav/2007} -- submitted by Mate Soos (Security Research Lab.), based on previous work by Trevor Hansen (U.~Melbourne) and Vijay Ganesh (Massachusetts Institute of Technology)\\[-15pt]
+\item veriT~\cite{veriT} -- submitted by David D\'{e}harbe (UFRN - Universidade Federal do Rio Grande do Norte) and Pascal Fontaine (U.~Lorraine, INRIA - Institut national de recherche en informatique et en automatique)\\[-15pt]
 \item Yices2~\cite{Dutertre:cav2014} -- submitted by Bruno Dutertre (SRI)
@@
 In addition, four teams submitting five solvers had not participated in previous competitions.
+
+\begin{table}[b!]
+\caption{Changes in participation}
+\label{Table:changes}
+\centering
+\resizebox{\textwidth}{!}{\begin{tabular}{|l|c|c|c|c|c|c|c|c|c|}
+\hline
+ & 2005 & 2006 & 2007 & 2008 & 2009 & 2010 & 2011 & 2012 & 2014\\
+\hline
+Participants                 & 12 & 12 & 9 & 13 & 12 & 10 & 11 & 10 & 18 \\
+New in given year            & 12 &  4 & 4 &  6 &  2 &  6 &  1 &  4 & 5 \\
+Continuing to the next year  &  8 &  6 & 7 & 10 &  4 &  7 &  7 &  6 & 10 \\
+Not ever participating again &  4 &  5 & 2 &  2 &  6 &  3 &  4 &  4 &  \\
+\hline
+\end{tabular}}
+\end{table}
+
+As in past competitions, the organizers included some publicly available historical solvers.
+These solvers are run in the competition for comparison, but are designated as demonstration only and are not eligible for any awards or designations of having won the competition.
+In result tables, these solvers are listed with their names in square brackets (e.g., [MathSat]).
+The organizers included current versions of MathSat and Z3.
+Also, during the competition, a bug-fix release of CVC4 (named CVC4-with-bugfix) was submitted and included as a demonstration only version (cf.
+\S\ref{sec:floc}).
 
@@
 
-As in past competitions, the organizers included some publicly available historical solvers.
-These solvers are run in the competition for comparison, but are designated as demonstration only and are not eligible for any awards or designations of having won the competition.
-In result tables, these solvers are listed with their names in square brackets (e.g., [MathSat]).
-The organizers included current versions of MathSat and Z3.
-Also, during the competition, a bug-fix release of CVC4 (named CVC4-with-bugfix) was submitted and included as a demonstration only version (cf.
-\S\ref{sec:floc}).
-
-\begin{table}
-\caption{Changes in participation}
-\label{Table:changes}
-\centering
-\resizebox{\textwidth}{!}{\begin{tabular}{|l|c|c|c|c|c|c|c|c|c|}
-\hline
- & 2005 & 2006 & 2007 & 2008 & 2009 & 2010 & 2011 & 2012 & 2014\\
-\hline
-Participants                 & 12 & 12 & 9 & 13 & 12 & 10 & 11 & 10 & 18 \\
-New in given year            & 12 &  4 & 4 &  6 &  2 &  6 &  1 &  4 & 5 \\
-Continuing to the next year  &  8 &  6 & 7 & 10 &  4 &  7 &  7 &  6 & 10 \\
-Not ever participating again &  4 &  5 & 2 &  2 &  6 &  3 &  4 &  4 &  \\
-\hline
-\end{tabular}}
-\end{table}
-
 \paragraph{History.} Table~\ref{Table:participants} shows the
@@
 Table~\ref{Table:changes} summarizes that data in numbers of continuing participants. Except for the record turnout in
- 2014, there has been a steady 9-13 participants each year; each year there are an average of 4 new
+ 2014, there has been a steady 9-13 participants each year: an average of 4 new
  participants, about the same number of drop-outs, and an average of 7 continuing participants.
@@
 As a result, some solvers did not continue participating, at least not immediately.
-The added expressivity of the command language permitted to add benchmarks representing the needs of industrial applications, and
-the application track of the competition was added to demonstrate the interactive capability and the corresponding abilities of solvers.
+The added expressivity of the command language permitted benchmarks representing the needs of industrial applications.
+The application track of the competition was added to demonstrate the interactive capability and the corresponding abilities of solvers.
 
@@
 Instead the organizers used StarExec's command-line API to regularly (every 10 minutes or so) download the status of all of the executing jobs, extract the results for each solver-benchmark pair, create HTML web pages displaying the current status, and upload them to the competition website.
-The current (now final) status of each division and a summary page can be seen at \url{http://smtcomp.sourceforge.net/2014/results-toc.shtml}.
+The current (now final) status of each division and a summary page can be seen online at \url{http://smtcomp.sourceforge.net/2014/results-toc.shtml}.
 
@@
 
-\begin{table}[H]
+\begin{table}[ht]
 \caption{Numbers of application benchmarks and distribution of \lstinline{check-sat} commands for different logics.}

### 2016-01-14 2014/report/SMTCOMP.tex
Paragraph headings fixed.

@@
 
-The organizers of SMT-COMP helped organize and execute the first edition of SL-COMP~\cite{SLCOMP,sighireanu2014report} as a sibling competition.
+\paragraph{SL-COMP} The organizers of SMT-COMP helped organize and execute the first edition of SL-COMP~\cite{SLCOMP,sighireanu2014report} as a sibling competition.
 SL-COMP is a competition among solvers for separation logic.
-The formal logical underpinnings of SL-COMP are still being
-defined and the relationship between the logic used in SL-COMP and the SMT-LIB logic is under discussion. However, SL-COMP
-did express its benchmark problems in the same syntax as SMT-COMP, used the same StarExec hardware, and used similar 
-organization and scoring rules.
-
-\paragraph{SL-COMP} Besides the subject material, the most interesting difference among competitions is in scoring. (The scoring procedure for
-SMT-COMP is described in detail in Section~\ref{sec:floc}.)
-Competitions are currently mostly focused on raw solver capability---that is, the numbers and difficulty of problems that can be solved.
-Thus competition winners are primarily determined by the total number of problems solved correctly,
-with the time taken to produce the solutions used only as a tie-breaker. This is the case for SMT-COMP, SAT, and SV-COMP,
-for example.
-
-\paragraph{Scoring differences.} A more significant issue is how solver errors are taken into account in the metrics.
+The formal logical underpinnings of SL-COMP are still being defined and the relationship between the logic used in SL-COMP and the SMT-LIB logic is under discussion.
+However, SL-COMP did express its benchmark problems in the same syntax as SMT-COMP, used the same StarExec hardware, and used similar organization and scoring rules.
+
+\paragraph{Scoring differences.} Besides the subject material, the most interesting difference among competitions is in scoring.
+(The scoring procedure for SMT-COMP is described in detail in Section~\ref{sec:floc}.) Competitions are currently mostly focused on raw solver capability---that is, the numbers and difficulty of problems that can be solved.
+Thus competition winners are primarily determined by the total number of problems solved correctly, with the time taken to produce the solutions used only as a tie-breaker.
+This is the case for SMT-COMP, SAT, and SV-COMP, for example.
+
+A more significant issue is how solver errors are taken into account in the metrics.
 A solver error indicates an unsoundness in the tool, which is highly undesirable; however, highly penalizing errors may discourage new entrants whose tools are not yet mature.

### 2016-04-20 rules/rules16.tex
Draft of 2016 rules added.

--- 2015-06-16 rules/rules15.tex
@@
 
-%\usepackage{draftwatermark}
+\usepackage{draftwatermark}
 
@@
 
-\title{10th International Satisfiability Modulo Theories Competition
-  (SMT-COMP 2015): Rules and Procedures}
+\title{11th International Satisfiability Modulo Theories Competition
+  (SMT-COMP 2016): Rules and Procedures}
 
@@
 France \\
-{\small\href{mailto:Sylvain.Conchon@lri.fr}{\tt Sylvain.Conchon@lri.fr}} \\
+{\small\href{mailto:Sylvain.Conchon@lri.fr}{\texttt{Sylvain.Conchon@lri.fr}}} \\
 \and
 David D{\'e}harbe \\
-Federal University of Rio Grande do Norte \\
-Brazil \\
-{\small\href{mailto:david@dimap.ufrn.br}{\tt david@dimap.ufrn.br}} \\
+Clearsy, France \& Federal University\\ of Rio Grande do Norte, Brazil \\
+{\small\href{mailto:david.deharbe@clearsy.com}{\texttt{david.deharbe@clearsy.com}}} \\
 \and
@@
 Sweden \\
-{\small\href{mailto:tjark.weber@it.uu.se}{\tt tjark.weber@it.uu.se}} \\
+{\small\href{mailto:tjark.weber@it.uu.se}{\texttt{tjark.weber@it.uu.se}}} \\
 \\
@@
 \begin{itemize}
-\item SMT-COMP mailing list: \href{mailto:smt-comp@cs.nyu.edu}{\tt
-  smt-comp@cs.nyu.edu}
+\item SMT-COMP mailing list:
+  \href{mailto:smt-comp@cs.nyu.edu}{\texttt{smt-comp@cs.nyu.edu}}
 \item Sign-up site for the mailing list:
@@
 competition web site, \url{www.smtcomp.org} or
-\url{smtcomp.sourceforge.net/2015}.
+\url{smtcomp.sourceforge.net/2016}.
 
@@
 \item[May~1] Deadline for new benchmark contributions.
-\item[June~1] Deadline for first versions of solvers (for all tracks),
+\item[May~15] Deadline for first versions of solvers (for all tracks),
   including information about which tracks and divisions are being
   entered, and magic numbers for benchmark scrambling.
-\item[June~7] Final versions of competition tools (e.g., benchmark
+\item[May~22] Final versions of competition tools (e.g., benchmark
   scrambler) are made available.  Benchmark libraries are frozen.
-\item[June~14] Deadline for final versions of solvers, including
+\item[May~29] Deadline for final versions of solvers, including
   system descriptions.
-\item[June~15] Opening value of NYSE Composite Index used to complete
+\item[May~30] Opening value of NYSE Composite Index used to complete
   random seed for benchmark scrambling.
-\item[July~18/19] SMT Workshop; end of competition, presentation of
+\item[July~1/2] SMT Workshop; end of competition, presentation of
   results.
@@
 previous
-competitions~(\cite{SMTCOMP-JAR,SMTCOMP-FMSD,BDOS08,SMTCOMP-2008,SMTCOMP-2014,SMTCOMP-2012,SMTEVAL-2013}).
+competitions~(\cite{SMTCOMP-JAR,SMTCOMP-FMSD,BDOS08,SMTCOMP-2008,CDW14,SMTCOMP-2012,CSW15}).
 
-SMT-COMP~2015 is affiliated with the SMT Workshop~2015
-(\url{http://smt2015.csl.sri.com/}), which is associated with CAV~2015
-(\url{http://i-cav.org/2015/}).  The SMT Workshop and the main CAV
-conference will include a block of time to present the competitors and
-results of the competition.
+SMT-COMP~2016 is affiliated with the SMT Workshop~2016
+(\url{http://smt-workshop.cs.uiowa.edu/2016/}), which is associated
+with IJCAR~2016 (\url{http://ijcar-2016.info/}).  The SMT Workshop
+will include a block of time to present the results of the
+competition.
 
@@
 
-SMT-COMP 2015 will have two tracks: the conventional main track and an
+SMT-COMP 2016 will have two tracks: the conventional main track and an
 application (i.e., incremental) track.  Within each track there are
@@
   contributions from Clark Barrett, Roberto Bruttomesso, David Cok,
-  David D{\'e}harbe, Morgan Deters, Alberto Griggio, Albert Oliveras,
-  Aaron Stump, and Tjark Weber.} describes the rules and competition
-procedures for SMT-COMP~2015.  The principal changes from the previous
-competition rules are the following:
+  Sylvain Conchon, David D{\'e}harbe, Morgan Deters, Alberto Griggio,
+  Albert Oliveras, Aaron Stump, and Tjark Weber.} describes the rules
+and competition procedures for SMT-COMP~2016.  The principal changes
+from the previous competition rules are the following:
 \begin{itemize}
-\item All solvers will be run with $n=4$ cores available.  We will
-  recognize both best sequential and best parallel performance in all
-  main track divisions, using different CPU time limits.
-\item The division scoring will take time spent on unsolved benchmarks
-  into account.  Previous competitions only considered time spent on
-  solved benchmarks.  However, the number of solved benchmarks still
-  takes precedence over run-time.
-\item In addition to recognizing the best solver in each division, we
-  will recognize solvers that perform best according to
-  competition-wide criteria, emphasizing breadth of supported logics.
-  These criteria will be a refinement of the criteria used for the
-  FLoC Olympic Games medals in~2014.
-\item We plan to include new divisions for floating-point arithmetic.
-  These should be considered experimental in~2015, and will not be
-  included in the competition-wide ranking.
-\item We plan to run solvers on all eligible benchmarks.  Previous
-  competitions used a proper subset of eligible benchmarks, causing
-  competition results to be affected by a random selection process.
+\item Benchmarks will use (a subset of) version~2.5 of the SMT-LIB
+  language.  \emph{Rationale:} This is the latest version of the
+  SMT-LIB language.  It was released on 2015-06-28, and is largely
+  backwards-compatible to version~2.0, which was used in the 2015 SMT
+  Competition.
+\item Solver output may affect the score even when the solver does not
+  terminate within the time limit.  (In 2015, main track solver output
+  was ignored if the solver subsequently timed out.)  Solvers should
+  take care not to accidentally produce output that contains
+  \texttt{sat} or \texttt{unsat} even when they are killed.
+  \emph{Rationale:} Users are likely to trust solver responses even
+  when the solver continues to run for some time.
+\item Divisions for floating-point arithmetic are no longer
+  experimental, and will be considered competitive if the necessary
+  requirements (see Section~\ref{sec:scoring}) are met.
+  \emph{Rationale:} Floating-point divisions were experimental in
+  2015.  By now, their definition is sufficiently stable, and they are
+  supported by several solvers.
+\item Division scores will be based on a weighted sum of scores for
+  benchmark families.  \emph{Rationale:} For some years now, the SMT
+  Competition has had sufficient computational resources to evaluate
+  all solver entrants on all eligible benchmarks.  As a side-effect,
+  the weighting of benchmark families that was achieved in early
+  SMT-COMPs through a careful selection of benchmarks (based on
+  benchmark difficulty and category) was lost.  We believe that a
+  careful weighting (see Section~\ref{sec:division-scoring}), which
+  de-emphasizes large benchmark families, will lead to more meaningful
+  competition results.
+\item Best industrial performance will no longer be recognized
+  separately.  \emph{Rationale:} While there is agreement in the SMT
+  community to emphasize problems that come from real applications,
+  industrial performance largely coincided with overall performance in
+  previous SMT-COMPs (except in some divisions that had a very small
+  number of industrial benchmarks).  Therefore, industrial performance
+  has very limited significance, and we consider the overhead to
+  determine and report it separately not justified.
 \end{itemize}
@@
 made publicly available, and the organizers informed of its presence
-{\em and the tracks and divisions in which it is
-  participating}. StarExec supports solver configurations; for
-clarity, each submitted solver must have one configuration only.  A
-submission must also include a 32-bit unsigned integer.  These integer
-numbers, collected from all submissions, are used to seed the
-benchmark scrambler.
+\emph{and the tracks and divisions in which it is participating}.
+StarExec supports solver configurations; for clarity, \emph{each
+  submitted solver must have one configuration only}.  A submission
+must also include a 32-bit unsigned integer.  These integer numbers,
+collected from all submissions, are used to seed the benchmark
+scrambler.
 
@@
 email to the organizers (accompanying information) until the end of
-{\bf June~1, 2015} anywhere on earth.  After this date no new entrants
+{\bf May~15, 2016} anywhere on earth.  After this date no new entrants
 will be accepted.  However, updates to existing entrants on StarExec
-will be accepted until the end of {\bf June~14, 2015} anywhere on
+will be accepted until the end of {\bf May~29, 2016} anywhere on
 earth.
@@
 The bulk of the computation will take place during the weeks leading
-up to SMT~2015, from about June~15 to July~17.  Intermediate results
+up to SMT~2016, from about May~30 to June~30.  Intermediate results
 will be regularly posted to the SMT-COMP website as the competition
@@
 In the main track, a participating solver must read a single benchmark
-script, whose name is presented as the solver's first argument.  In
-the application track, a trace executor will send commands from a
-benchmark script to the solver's standard input channel.
+script, whose filename is presented as the solver's first command-line
+argument.  In the application track, a trace executor will send
+commands from a benchmark script to the solver's standard input
+channel.
 
 The benchmark script is in the concrete syntax of the SMT-LIB format,
-version~2.0, though with a restricted set of commands.  A benchmark
-script is a text file containing a sequence of SMT-LIB~v2 commands in
-which:
+version~2.5, though with a restricted set of commands.  A benchmark
+script is a text file containing a sequence of SMT-LIB commands that
+satisfies the following requirements:
 %
@@
 \item In the main track, there may be a (single) \akey{set-option
-  :print-success ...} command.  Note that {\tt success} outputs are
+  :print-success ...} command.  Note that \texttt{success} outputs are
   ignored by the post-processor used by the
-  competition.\footnote{SMT-LIB~2.0 requires that a solver produce a
+  competition.\footnote{SMT-LIB~2.5 requires solvers to produce a
     \texttt{success} answer after each \akey{set-logic},
@@
     false.  Ignoring the \texttt{success} outputs allows for
-    submitting fully SMT-LIB~2.0 compliant solvers without the need
+    submitting fully SMT-LIB~2.5 compliant solvers without the need
     for a wrapper script, while still allowing entrants of previous
     competitions to run without changes.}
-\item In the application track, the \akey{:print-success} option may
-  not be disabled; the application track executor will send an initial
+\item In the application track, the \akey{:print-success} option must
+  not be disabled.  The trace executor will send an initial
   $\akey{set-option :print-success true}$ command to the solver.
@@
   logic is the first command after any $\akey{set-option}$ commands.
-\item The script next optionally contains (any number of)
-  $\akey{set-info}$ commands, which may be ignored by the
-  solver. Benchmarks will likely have some of the following
-  \akey{set-info} commands: \akey{(set-info :smt-lib-version 2.0)},
-  \akey{(set-info :category ...)}, \akey{(set-info :source ...)}, and
-  \akey{(set-info :status ...)}.
+\item The script may contain any number of $\akey{set-info}$ commands.
+  These may be ignored by solvers.
+\item The script may contain any number of $\akey{declare-sort}$
+  commands.  All sorts declared with a $\akey{declare-sort}$ command
+  must have zero arity.
+\item Application track scripts may contain $\akey{define-sort}$
+  commands.  \textcolor{red}{TODO: Some main track benchmarks also
+    appear to contain \akey{define-sort} and \akey{define-fun}
+    commands.}
+\item The script may contain any number of $\akey{declare-fun}$
+  commands.  All formulas in the script belong to the benchmark's
+  logic, with any free symbols declared in the script.
 \item In the main track, there is exactly one $\akey{check-sat}$
@@
   There may also be zero or more \akey{push 1} commands, and zero or
-  more \akey{pop 1} commands, consistent with the uses of those
-  commands in the SMT-LIB standard. Each \akey{check-sat} command may
-  be preceded by a \akey{set-info :status} command that indicates the
-  expected result of the \akey{check-sat} command.
+  more \akey{pop 1} commands, consistent with the use of those
+  commands in the SMT-LIB standard.
 \item The script may optionally contain an $\akey{exit}$ command as
@@
   be omitted.
-\item The formulas in the script belong to the benchmark's logic, with
-  any free symbols declared in the script.
-\item All sorts declared with a $\akey{declare-sort}$ command must
-  have zero arity.
-\item Application track scripts may have $\akey{define-sort}$
-  commands.
 \item No other commands besides the ones just mentioned may be used.
@@
 %
-The SMT-LIB format specification is available from the ``Documents''
+The SMT-LIB format specification is available from the ``Standard''
 section of the SMT-LIB website~\cite{SMT-LIB}.  Solvers will be given
@@
 of the logic divisions.  Each benchmark script will be presented to
-the solver as its first command-line argument.  Each SMT-COMP entrant
-is then expected to attempt to report on its standard output channel
-whether the formula is satisfiable (\texttt{sat}, in lowercase) or
-unsatisfiable (\texttt{unsat}).  An entrant may also report
+the solver as its first command-line argument.  The solver is then
+expected to attempt to report on its standard output channel whether
+the formula is satisfiable (\texttt{sat}, in lowercase) or
+unsatisfiable (\texttt{unsat}).  A solver may also report
 \texttt{unknown} to indicate that it cannot determine satisfiability
@@
 The main track competition uses a StarExec post-processor (named
-``SMT-COMP 2015") to accumulate the results.
+``SMT-COMP 2016") to accumulate the results.
 
@@
 before the time limit without reporting a result (e.g., due to
-exhausting memory or crashing) and do not produce output that includes
-\texttt{sat}, \texttt{unsat} or \texttt{unknown} will be considered to
-have aborted.
+exhausting memory or crashing) \emph{and} do not produce output that
+includes \texttt{sat}, \texttt{unsat} or \texttt{unknown} will be
+considered to have aborted.
 
@@
 as its current working directory.  Any generated files should be
-produced there (and not, say, in the system's {\tt /tmp} directory).
-The StarExec system sets a limit on the amount of disk storage
-permitted---typically 20\,GB.  See the StarExec user guide for more
-information.  The temporary directory is deleted after the job is
+produced there (and not, say, in the system's \texttt{/tmp}
+directory).  The StarExec system sets a limit on the amount of disk
+storage permitted---typically 20\,GB.  See the StarExec user guide for
+more information.  The temporary directory is deleted after the job is
 complete.  Solvers must not attempt to communicate with other
@@
 interaction, ideally, happens by means of an online communication
-between the model checker and the solver: the model checker repeatedly
-sends queries to the SMT solver, which in turn answers either
-\texttt{sat} or \texttt{unsat}.  In this interaction an SMT-solver is
-required to accept queries incrementally via its {\em standard input
-  channel}.
+between the framework and the solver: the framework repeatedly sends
+queries to the SMT solver, which in turn answers either \texttt{sat}
+or \texttt{unsat}.  In this interaction an SMT solver is required to
+accept queries incrementally via its \emph{standard input channel}.
 
-In order to facilitate the evaluation of the solvers in this track, we
-will set up a ``simulation'' of the aforementioned interaction. In
-particular each benchmark in the application track represents a
-realistic communication trace, containing multiple \akey{check-sat}
-commands (possibly with corresponding \akey{push 1}/\akey{pop 1}
-commands), which is parsed by a \emph{trace executor}. The trace
-executor serves the following purposes:
+In order to facilitate the evaluation of solvers in this track, we
+will set up a ``simulation'' of the aforementioned interaction.  Each
+benchmark in the application track represents a realistic
+communication trace, containing multiple \akey{check-sat} commands
+(possibly with corresponding \akey{push 1} and \akey{pop 1} commands),
+which is parsed by a \emph{trace executor}. The trace executor serves
+the following purposes:
 \begin{itemize}
@@
 \item it prevents ``look-ahead'' behaviors of SMT solvers;
-\item it records time and answers for each call;
+\item it records time and answers for each command;
 \item it guarantees a fair execution for all solvers by abstracting
-  from any possible crash, misbehavior, etc. that may happen on the
-  model checker side.
+  from any possible crash, misbehavior, etc.\ that might happen in the
+  verification framework.
 \end{itemize}
@@
 solver and read responses from the standard output channel of the
-solver.  The commands will be taken from an SMT-LIB~2.0 benchmark
-script that satisfies the rules for an application script given in
+solver.  The commands will be taken from an SMT-LIB benchmark script
+that satisfies the requirements for application track scripts given in
 Section~\ref{sec:logistics}.
@@
 Solvers must respond to each command sent by the trace executor with
-the answers defined in the SMT-LIB~2.0 format specification, that is,
-with a \texttt{success} answer for \akey{set-option},
-\akey{set-logic}, \akey{declare-sort}, \akey{declare-fun},
-\akey{define-sort}, \akey{define-fun}, \akey{assert}, \akey{push 1},
-and \akey{pop 1} commands, and with an answer of \texttt{sat},
-\texttt{unsat}, or \texttt{unknown} for \akey{check-sat} commands.
-There will be no \akey{get-unsat-core}, \akey{get-proof},
-\akey{get-model}, \akey{get-assignments}, or \akey{get-values}
-commands in application track benchmarks.
+the answers defined in the SMT-LIB format specification, that is, with
+an answer of \texttt{sat}, \texttt{unsat}, or \texttt{unknown} for
+\akey{check-sat} commands, and with a \texttt{success} answer for
+other commands.
 
@@
 Benchmarks for each division will be drawn from the SMT-LIB benchmark
-repository.  The main track will use a subset of all
+library.  The main track will use a subset of all
 \emph{non-incremental} benchmarks; the application track will use a
@@
 %
-The deadline for submission of new benchmarks is {\bf May~1, 2015}.
-The organizers will be checking and curating these until {\bf June~7,
-  2015}.  The organizers reserve the right to exclude new benchmarks
+The deadline for submission of new benchmarks is {\bf May~1, 2016}.
+The organizers will be checking and curating these until {\bf May~22,
+  2016}.  The organizers reserve the right to exclude new benchmarks
 if any prove problematic for some reason.  SMT-COMP attempts to give
@@
   organizers may remove from the eligibility pool certain benchmarks
-  that are inappropriate\footnote{In 2015, this (again) includes all
-    benchmarks that use bit-vector division or remainder, because of
-    an unresolved discussion about the semantics of division by zero.}
-  or uninteresting for competition, or cut the size of certain
-  benchmark families to avoid their over-representation.
+  that are inappropriate\footnote{In 2016, this (again) includes all
+    benchmarks that use partial or underspecified functions, e.g.,
+    \texttt{bvudiv}, \texttt{fp.min}.}  or uninteresting for
+  competition, or cut the size of certain benchmark families to avoid
+  their over-representation.
 \item \emph{Eliminate benchmarks whose status is unknown.} Any
-  benchmark whose expected output is neither {\tt sat} nor {\tt unsat}
-  is removed.  There is a significant number of benchmarks with {\tt
-    unknown} status in the library; these are certainly interesting
-  and are a challenge to solve, but they are not used in the
-  competition.\footnote{Incremental benchmarks may contain multiple
-    \akey{check-sat} commands, each with its own status.  Incremental
-    benchmarks that contain (some) \akey{check-sat} commands with {\tt
-      unknown} status may still contain a prefix of commands where the
-    status is known for all \akey{check-sat} commands in the prefix.
-    This prefix is eligible for the application track.}
+  benchmark whose expected output is neither \texttt{sat} nor
+  \texttt{unsat} is removed.  There are a significant number of
+  benchmarks with \texttt{unknown} status in the library; these are
+  certainly interesting and are a challenge to solve, but they are not
+  used in the competition.\footnote{Incremental benchmarks may contain
+    multiple \akey{check-sat} commands, each with its own status.
+    Incremental benchmarks that contain (some) \akey{check-sat}
+    commands with \texttt{unknown} status may still contain a prefix
+    of commands where the status is known for all \akey{check-sat}
+    commands in the prefix.  This prefix is eligible for the
+    application track.}
 \end{enumerate}
@@
 \section{Scoring}
+\label{sec:scoring}
 
@@
 eligible to be designated as winners.
-
-Divisions for floating-point arithmetic are experimental in 2015, and
-will not be considered competitive.
 
@@
 \begin{itemize}
-\item $e=0$, $n=0$ if the solver times out, or the solver aborts
-  without a response, or the result of the \akey{check-sat} command is
-  {\tt unknown},
-\item $e=0$, $n=1$ if the solver does not time out, and the result of
-  the \akey{check-sat} command is correct,
-\item $e=1$, $n=0$ if the solver does not time out, and the result of
-  the \akey{check-sat} command is incorrect.
+\item $e=0$, $n=0$ if the solver aborts without a response, or the
+  result of the \akey{check-sat} command is \texttt{unknown},
+\item $e=0$, $n=1$ if the result of the \akey{check-sat} command is
+  correct,
+\item $e=1$, $n=0$ if the result of the \akey{check-sat} command is
+  incorrect.
 \end{itemize}
 %
-Note that for a (correct or incorrect) result to be taken into
-consideration, the solver process must terminate (normally or
-abnormally) within the time limit.
+Note that a (correct or incorrect) response is taken into
+consideration even when the the solver process terminates abnormally,
+or does not terminate within the time limit.  Solvers should take care
+not to accidentally produce output that contains \texttt{sat} or
+\texttt{unsat}.
 
@@
 CPU time) over parallel performance (i.e., wall-clock time).  StarExec
-is measuring both, and we intend to recognize both best sequential and
+measures both, and we intend to recognize both best sequential and
 best parallel solvers in all competitive main track divisions.
@@
 To compute a solver's score for a division, the solver's individual
-benchmark scores for all benchmarks in the division are summed
-component-wise.  For main track divisions, we will separately compute
-the sum of all raw scores (Section~\ref{sec:benchmark-scoring}) to
-assess parallel performance, and the sum of all sequential scores
+benchmark scores for all benchmarks in the division are first
+multiplied by a scalar weight that depends on the benchmark's family,
+and then summed component-wise.
+
+For a given competition benchmark~$b$, let~$F_b \geq 1$ be the total
+number of benchmarks in $b$'s benchmark family that were used in the
+competition.  We define the weight for benchmark~$b$ as $\alpha_b = (1
++ \log F_b) / F_b$.\footnote{See Section~\ref{sec:competition-wide}
+  for a motivating discussion of log scaling.}  We define the
+\emph{normalized weight} for benchmark~$b$ as $\alpha'_b = \alpha_b /
+(\sum_{b'} \alpha_{b'})$, where the sum is over all benchmarks in the
+division.
+
+For main track divisions, we will separately compute the weighted sum
+of all raw scores (Section~\ref{sec:benchmark-scoring}) $$\sum_b
+\alpha'_b \cdot \langle e_b, n_b, w_b, c_b\rangle$$ where the sum is
+over all benchmarks in the division to assess parallel performance,
+and the weighted sum of all sequential scores
 (Section~\ref{sec:sequential}) to assess sequential performance.  For
 application track divisions, division scores will be based on raw
-scores.\footnote{Since application track benchmarks may be partially
-  solved, defining a useful sequential score for the application track
-  would require information not provided by the raw score, e.g.,
-  detailed timing information for each result.}
+scores only.\footnote{Since application track benchmarks may be
+  partially solved, defining a useful sequential score for the
+  application track would require information not provided by the raw
+  score, e.g., detailed timing information for each result.}
 
@@
 \begin{itemize}
-\item A sum of raw scores $\langle e, n, w, c\rangle$ is better than
-  $\langle e', n', w', c'\rangle$ iff $e < e'$ or ($e = e'$ and $n >
-  n'$) or ($e = e'$ and $n = n'$ and $w < w'$) or ($e = e'$ and $n =
-  n'$ and $w = w'$ and $c < c'$).  That is, fewer errors takes
+\item A weighted sum of raw scores $\langle e, n, w, c\rangle$ is
+  better than $\langle e', n', w', c'\rangle$ iff $e < e'$ or ($e =
+  e'$ and $n > n'$) or ($e = e'$ and $n = n'$ and $w < w'$) or ($e =
+  e'$ and $n = n'$ and $w = w'$ and $c < c'$).  That is, fewer errors
+  takes precedence over more correct solutions, which takes precedence
+  over less wall-clock time taken, which takes precedence over less
+  CPU time taken.
+\item A weighted sum of sequential scores $\langle e_S, n_S,
+  c_S\rangle$ is better than $\langle e_S', n_S', c_S'\rangle$ iff
+  $e_S < e_S'$ or ($e_S = e_S'$ and $n_S > n_S'$) or ($e_S = e_S'$ and
+  $n_S = n_S'$ and $c_S < c_S'$).  That is, fewer errors takes
   precedence over more correct solutions, which takes precedence over
-  less wall-clock time taken, which takes precedence over less CPU
-  time taken.
-\item A sum of sequential scores $\langle e_S, n_S, c_S\rangle$ is
-  better than $\langle e_S', n_S', c_S'\rangle$ iff $e_S < e_S'$ or
-  ($e_S = e_S'$ and $n_S > n_S'$) or ($e_S = e_S'$ and $n_S = n_S'$
-  and $c_S < c_S'$).  That is, fewer errors takes precedence over more
-  correct solutions, which takes precedence over less CPU time taken.
+  less CPU time taken.
 \end{itemize}
@@
 \subsection{Competition-wide scoring}
+\label{sec:competition-wide}
 
@@
   code as open source will be recognized in each competitive division.
-\item \emph{Best industrial performance.}  There is agreement in the
-  SMT community to emphasize problems that come from real
-  applications.  The solver that performs best on industrial
-  benchmarks, as measured by the division scoring restricted to this
-  benchmark category, will be recognized in each competitive division.
-\item {\em Best new entrant}. The best performing entrant from a new
+\item \emph{Best new entrant}. The best performing entrant from a new
   solver implementation team, as measured by the competition-wide
   metric.
-\item {\em Breadth of logics}. Solvers that cover the most theories
+\item \emph{Breadth of logics}. Solvers that cover the most theories
   and logics.
-\item {\em Benchmarks}. Contributors of new benchmarks.
+\item \emph{Benchmarks}. Contributors of new benchmarks.
 \end{itemize}
@@
 
-SMT-COMP 2015 is organized under the direction of the SMT Steering
+SMT-COMP 2016 is organized under the direction of the SMT Steering
 Committee. The organizing team is
@@
 \item \href{https://www.sites.google.com/site/deharbe/}{David
-  D{\'e}harbe}~-- Federal University of Rio Grande do Norte, Brazil
-  (co-organizer)
+  D{\'e}harbe}~-- Clearsy, France, and Federal University of Rio
+  Grande do Norte, Brazil (co-organizer)
 \item \href{http://user.it.uu.se/~tjawe125/}{Tjark Weber}~-- Uppsala
@@
 Many others have contributed benchmarks, effort, and feedback.  Clark
-Barrett processed the newly submitted benchmarks.  The competition
-uses the \href{https://www.starexec.org/}{StarExec} service, which is
+Barrett
+% processed the newly submitted benchmarks.
+is maintaining the SMT-LIB benchmark library.  The competition uses
+the \href{https://www.starexec.org/}{StarExec} service, which is
 hosted at the \href{http://www.cs.uiowa.edu/}{University of Iowa}.
@@
 \end{document}
+
+%% Local Variables:
+%% mode: latex
+%% mode: flyspell
+%% ispell-local-dictionary: "american"
+%% LocalWords: Conchon logics satisfiability SMT Sylvain Tjark
+%% End:

### 2016-04-21 rules/rules16.tex
Matthias Heizmann added as co-organizer. Minor edits.

@@
 {\small\href{mailto:david.deharbe@clearsy.com}{\texttt{david.deharbe@clearsy.com}}} \\
+\and
+Matthias Heizmann \\
+University of Freiburg \\
+Germany \\
+{\small\href{mailto:heizmann@informatik.uni-freiburg.de}{\texttt{heizmann@informatik.uni-freiburg.de}}} \\
+{\small\textsc{(Unsat Core Track)}} \\
 \and
@@
   SMT-LIB language.  It was released on 2015-06-28, and is largely
-  backwards-compatible to version~2.0, which was used in the 2015 SMT
-  Competition.
+  backwards-compatible to version~2.0, which was used for SMT-COMP
+  2015.
 \item Solver output may affect the score even when the solver does not
@@
 \item Division scores will be based on a weighted sum of scores for
-  benchmark families.  \emph{Rationale:} For some years now, the SMT
-  Competition has had sufficient computational resources to evaluate
-  all solver entrants on all eligible benchmarks.  As a side-effect,
-  the weighting of benchmark families that was achieved in early
-  SMT-COMPs through a careful selection of benchmarks (based on
-  benchmark difficulty and category) was lost.  We believe that a
-  careful weighting (see Section~\ref{sec:division-scoring}), which
-  de-emphasizes large benchmark families, will lead to more meaningful
+  benchmark families.  \emph{Rationale:} For some years now, SMT-COMPs
+  have had sufficient computational resources to evaluate all solver
+  entrants on all eligible benchmarks.  As a side-effect, the
+  weighting of benchmark families that was achieved in early SMT-COMPs
+  through a careful selection of benchmarks (based on benchmark
+  difficulty and category) was lost.  Since there are vast differences
+  in size between benchmark families, we believe that a weighting that
+  de-emphasizes large benchmark families (see
+  Section~\ref{sec:division-scoring}) will lead to more meaningful
   competition results.
@@
   industrial performance largely coincided with overall performance in
-  previous SMT-COMPs (except in some divisions that had a very small
-  number of industrial benchmarks).  Therefore, industrial performance
-  has very limited significance, and we consider the overhead to
-  determine and report it separately not justified.
+  SMT-COMP 2015.  We consider the effort to determine and report it
+  separately no longer justified.
 \end{itemize}
@@
   must have zero arity.
-\item Application track scripts may contain $\akey{define-sort}$
-  commands.  \textcolor{red}{TODO: Some main track benchmarks also
-    appear to contain \akey{define-sort} and \akey{define-fun}
-    commands.}
+\item The script may contain any number of $\akey{define-sort}$
+  commands.  All sorts defined with a $\akey{define-sort}$ command
+  must have zero arity.
 \item The script may contain any number of $\akey{declare-fun}$
-  commands.  All formulas in the script belong to the benchmark's
-  logic, with any free symbols declared in the script.
+  commands.
+\item The script may contain any number of $\akey{define-fun}$
+  commands.
+\item The script may contain any number of $\akey{assert}$ commands.
+  All formulas in the script belong to the benchmark's logic, with any
+  free symbols declared in the script.
+\item Named formulas are not used in benchmark scripts.
 \item In the main track, there is exactly one $\akey{check-sat}$
-  command, following possibly several $\akey{assert}$ commands.
+  command.
 \item In the application track, there are one or more \akey{check-sat}
-  commands, each preceded by one or more \akey{assert} commands.
-  There may also be zero or more \akey{push 1} commands, and zero or
-  more \akey{pop 1} commands, consistent with the use of those
-  commands in the SMT-LIB standard.
+  commands.  There may also be zero or more \akey{push 1} commands,
+  and zero or more \akey{pop 1} commands, consistent with the use of
+  those commands in the SMT-LIB standard.
 \item The script may optionally contain an $\akey{exit}$ command as
@@
 \item No other commands besides the ones just mentioned may be used.
-\item Named formulas are not used in benchmark scripts.
 \end{enumerate}
@@
 competition.  We define the weight for benchmark~$b$ as $\alpha_b = (1
-+ \log F_b) / F_b$.\footnote{See Section~\ref{sec:competition-wide}
++ \log_e F_b) / F_b$.\footnote{See Section~\ref{sec:competition-wide}
   for a motivating discussion of log scaling.}  We define the
@@
 solver's competition-wide raw score is $\sum_i (e_i == 0 \,?\,
-(n_i/N_i)^2 : -e_i) \log N_i$, where the sum is over all competitive
+(n_i/N_i)^2 : -e_i) \log_e N_i$, where the sum is over all competitive
 divisions into which the solver was
@@
   Grande do Norte, Brazil (co-organizer)
+\item
+  \href{https://swt.informatik.uni-freiburg.de/staff/heizmann}{Matthias
+    Heizmann}~-- University of Freiburg, Germany (co-organizer, unsat
+  core track)
 \item \href{http://user.it.uu.se/~tjawe125/}{Tjark Weber}~-- Uppsala
@@
 Many others have contributed benchmarks, effort, and feedback.  Clark
-Barrett
-% processed the newly submitted benchmarks.
-is maintaining the SMT-LIB benchmark library.  The competition uses
-the \href{https://www.starexec.org/}{StarExec} service, which is
+Barrett is maintaining the SMT-LIB benchmark library.  The competition
+uses the \href{https://www.starexec.org/}{StarExec} service, which is
 hosted at the \href{http://www.cs.uiowa.edu/}{University of Iowa}.
@@
 David D{\'e}harbe is associated with the solver group producing the
-veriT solver.
+veriT solver.  Matthias Heizmann is associated with the solver group
+producing the SMTInterpol solver.
 
@@
 %% ispell-local-dictionary: "american"
-%% LocalWords: Conchon logics satisfiability SMT Sylvain Tjark
+%% LocalWords: arity Conchon logics satisfiability SMT Sylvain Tjark
 %% End:

### 2016-04-22 rules/rules16.tex
Unsat core track.

@@
 
-SMT-COMP 2016 will have two tracks: the conventional main track and an
-application (i.e., incremental) track.  Within each track there are
-multiple divisions, where each division uses benchmarks from a
-specific SMT-LIB logic (or group of logics).  We will recognize
-winners as measured by number of benchmarks solved; we will also
-recognize solvers based on additional criteria.
+SMT-COMP 2016 will have three tracks: the conventional main track, an
+application (i.e., incremental) track, and an unsat-core track.  The
+unsat-core track will be experimental in 2016.
+
+Within each track there are multiple divisions, where each division
+uses benchmarks from a specific SMT-LIB logic (or group of logics).
+We will recognize winners as measured by number of benchmarks solved;
+we will also recognize solvers based on additional criteria.
 
@@
   competition results.
+\item The unsat-core track that was introduced in SMT-COMP 2012, but
+  discontinued in 2013-2015 (partly because of the competition's move
+  to StarExec), is back.  It will be experimental in 2016; its results
+  will be reported, but no official winners will be announced.
+  \emph{Rationale:} Unsat cores are important in many applications of
+  SMT solving.  The track was discontinued primarily for
+  infrastructure and resource reasons.  We are pleased that we can
+  finally offer it again, but we ask for your understanding in case of
+  mishaps while we port the required tools.
 \item Best industrial performance will no longer be recognized
@@
 %
-In the main track, a participating solver must read a single benchmark
-script, whose filename is presented as the solver's first command-line
-argument.  In the application track, a trace executor will send
-commands from a benchmark script to the solver's standard input
-channel.
+In the main and unsat-core track, a participating solver must read a
+single benchmark script, whose filename is presented as the solver's
+first command-line argument.  In the application track, a trace
+executor will send commands from a benchmark script to the solver's
+standard input channel.
 
@@
 \begin{enumerate}
-\item In the main track, there may be a (single) \akey{set-option
-  :print-success ...} command.  Note that \texttt{success} outputs are
-  ignored by the post-processor used by the
-  competition.\footnote{SMT-LIB~2.5 requires solvers to produce a
-    \texttt{success} answer after each \akey{set-logic},
-    \akey{declare-sort}, \akey{declare-fun} and \akey{assert} command
-    (among others), unless the option \akey{:print-success} is set to
-    false.  Ignoring the \texttt{success} outputs allows for
-    submitting fully SMT-LIB~2.5 compliant solvers without the need
-    for a wrapper script, while still allowing entrants of previous
-    competitions to run without changes.}
-\item In the application track, the \akey{:print-success} option must
-  not be disabled.  The trace executor will send an initial
-  $\akey{set-option :print-success true}$ command to the solver.
-\item The (single) $\akey{set-logic}$ command setting the benchmark's
-  logic is the first command after any $\akey{set-option}$ commands.
-\item The script may contain any number of $\akey{set-info}$ commands.
-  These may be ignored by solvers.
-\item The script may contain any number of $\akey{declare-sort}$
-  commands.  All sorts declared with a $\akey{declare-sort}$ command
-  must have zero arity.
-\item The script may contain any number of $\akey{define-sort}$
-  commands.  All sorts defined with a $\akey{define-sort}$ command
-  must have zero arity.
-\item The script may contain any number of $\akey{declare-fun}$
-  commands.
-\item The script may contain any number of $\akey{define-fun}$
-  commands.
-\item The script may contain any number of $\akey{assert}$ commands.
+\item
+  \begin{enumerate}
+  \item In the main and unsat-core track, there may be a single
+    \akey{set-option :print-success ...} command.  Note that
+    \texttt{success} outputs are ignored by the post-processor used by
+    the competition.\footnote{SMT-LIB~2.5 requires solvers to produce
+      a \texttt{success} answer after each \akey{set-logic},
+      \akey{declare-sort}, \akey{declare-fun} and \akey{assert}
+      command (among others), unless the option \akey{:print-success}
+      is set to false.  Ignoring the \texttt{success} outputs allows
+      for submitting fully SMT-LIB~2.5 compliant solvers without the
+      need for a wrapper script, while still allowing entrants of
+      previous competitions to run without changes.}
+  \item In the application track, the \akey{:print-success} option
+    must not be disabled.  The trace executor will send an initial
+    \akey{set-option :print-success true} command to the solver.
+  \end{enumerate}
+\item In the unsat-core track, there is a single \akey{set-option
+  :produce-unsat-cores true} command.
+\item The (single) \akey{set-logic} command setting the benchmark's
+  logic is the first command after any \akey{set-option} commands.
+\item The script may contain any number of \akey{set-info} commands.
+\item The script may contain any number of \akey{declare-sort} and
+  \akey{define-sort} commands.  All sorts declared or defined with
+  these commands must have zero arity.
+\item The script may contain any number of \akey{declare-fun} and
+  \akey{define-fun} commands.
+\item The script may contain any number of \akey{assert} commands.
   All formulas in the script belong to the benchmark's logic, with any
   free symbols declared in the script.
-\item Named formulas are not used in benchmark scripts.
-\item In the main track, there is exactly one $\akey{check-sat}$
-  command.
-\item In the application track, there are one or more \akey{check-sat}
-  commands.  There may also be zero or more \akey{push 1} commands,
-  and zero or more \akey{pop 1} commands, consistent with the use of
-  those commands in the SMT-LIB standard.
-\item The script may optionally contain an $\akey{exit}$ command as
-  its last command.  In the application track, this command must not
-  be omitted.
+\item
+  \begin{enumerate}
+    \item In the main and application track, named formulas are not
+      used.
+    \item In the unsat core track, top-level assertions may be named.
+  \end{enumerate}
+\item
+  \begin{enumerate}
+  \item In the main and unsat-core track, there is exactly one
+    \akey{check-sat} command.
+  \item In the application track, there are one or more
+    \akey{check-sat} commands.  There may also be zero or more
+    \akey{push 1} commands, and zero or more \akey{pop 1} commands,
+    consistent with the use of those commands in the SMT-LIB standard.
+  \end{enumerate}
+\item In the unsat-core track, the \akey{check-sat} command (which is
+  always issued in an unsatisfiable context) is followed by a single
+  \akey{get-unsat-core} command.
+\item The script may optionally contain an \akey{exit} command as its
+  last command.  In the application track, this command must not be
+  omitted.
 \item No other commands besides the ones just mentioned may be used.
@@
 
+\subsection{Unsat-core track}
+\label{sec:exec:unsat-core}
+
+The unsat-core track will evaluate the capability of solvers to
+generate unsatisfiable cores (for problems that are known to be
+unsatisfiable).  Solvers will be measured by the smallness of the
+unsatisfiable core they return.
+
+The SMT-LIB language accommodates this functionality by providing two
+features: the ability to name top-level (asserted) formulas, and the
+ability to request an unsatisfiable core after a \akey{check-sat}
+command returns \texttt{unsat}.  The unsatisfiable core that is
+returned must consist of a list of names of formulas, in the format
+prescribed by the SMT-LIB standard.
+
+The result of a solver is considered erroneous if the response to the
+\akey{check-sat} command is \texttt{sat}, or if the returned
+unsatisfiable core is not well-formed (e.g., contains names of
+formulas that have not been asserted before), or if the returned
+unsatisfiable core is not, in fact, unsatisfiable.  The organizers
+intend to check unsatisfiability by running an SMT solver on a
+benchmark that asserts only those formulas in the reported core.  The
+details of the checking procedure, which will be the same for all
+solvers and benchmarks in the unsat-core track, are still to be
+determined.
+
+Solvers must respond to each command in the benchmark script with the
+answers defined in the SMT-LIB format specification.  In particular,
+solvers that respond \texttt{unknown} to the \akey{check-sat} command
+must respond with an error to the following \akey{get-unsat-core}
+command.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \emph{non-incremental} benchmarks; the application track will use a
-subset of all \emph{incremental} benchmarks.
+subset of all \emph{incremental} benchmarks.  The unsat-core track
+will use unsatisfiable main track benchmarks, modified to use named
+top-level assertions.
 
@@
 Note that a (correct or incorrect) response is taken into
-consideration even when the the solver process terminates abnormally,
-or does not terminate within the time limit.  Solvers should take care
+consideration even when the solver process terminates abnormally, or
+does not terminate within the time limit.  Solvers should take care
 not to accidentally produce output that contains \texttt{sat} or
@@
   limit is reached.
+\end{itemize}
+
+\header{Unsat-core track.}
+%
+For the unsat-core track, we instead have $0 \leq n \leq A$, where~$A$
+is the number of named top-level assertions in the benchmark, and
+\begin{itemize}
+\item $e=0$, $n=0$ if the solver aborts without a response, or the
+  result of the \akey{check-sat} command is \texttt{unknown},
+\item $e=1$, $n=0$ if the result is erroneous according to
+  Section~\ref{sec:exec:unsat-core},
+\item otherwise, $e=0$, and $n$ is the reduction in the number of
+  formulas, i.e., $n = A$ minus the number of formula names in the
+  reported unsatisfiable core.
 \end{itemize}
@@
 number of benchmarks in $b$'s benchmark family that were used in the
-competition.  We define the weight for benchmark~$b$ as $\alpha_b = (1
-+ \log_e F_b) / F_b$.\footnote{See Section~\ref{sec:competition-wide}
-  for a motivating discussion of log scaling.}  We define the
-\emph{normalized weight} for benchmark~$b$ as $\alpha'_b = \alpha_b /
-(\sum_{b'} \alpha_{b'})$, where the sum is over all benchmarks in the
-division.
+competition track to which the division belongs.  We define the weight
+for benchmark~$b$ as $\alpha_b = (1 + \log_e F_b) / F_b$.\footnote{See
+  Section~\ref{sec:competition-wide} for a motivating discussion of
+  log scaling.}  We define the \emph{normalized weight} for
+benchmark~$b$ as $\alpha'_b = \alpha_b / (\sum_{b'} \alpha_{b'})$,
+where the sum is over all benchmarks in the division.
 
-For main track divisions, we will separately compute the weighted sum
-of all raw scores (Section~\ref{sec:benchmark-scoring}) $$\sum_b
-\alpha'_b \cdot \langle e_b, n_b, w_b, c_b\rangle$$ where the sum is
-over all benchmarks in the division to assess parallel performance,
-and the weighted sum of all sequential scores
-(Section~\ref{sec:sequential}) to assess sequential performance.  For
-application track divisions, division scores will be based on raw
-scores only.\footnote{Since application track benchmarks may be
-  partially solved, defining a useful sequential score for the
-  application track would require information not provided by the raw
-  score, e.g., detailed timing information for each result.}
+For main track and unsat-core track divisions, we will separately
+compute the weighted sum of all raw scores
+(Section~\ref{sec:benchmark-scoring}) $$\sum_b \alpha'_b \cdot \langle
+e_b, n_b, w_b, c_b\rangle$$ where the sum is over all benchmarks in
+the division to assess parallel performance, and the weighted sum of
+all sequential scores (Section~\ref{sec:sequential}) to assess
+sequential performance.  For application track divisions, division
+scores will be based on raw scores only.\footnote{Since application
+  track benchmarks may be partially solved, defining a useful
+  sequential score for the application track would require information
+  not provided by the raw score, e.g., detailed timing information for
+  each result.}
 

### 2017-04-19 rules/rules17.tex
Add draft of 2017 rules

--- 2016-04-22 rules/rules16.tex
@@
 benchmark~$b$ as $\alpha'_b = \alpha_b / (\sum_{b'} \alpha_{b'})$,
-where the sum is over all benchmarks in the division.
+where the sum is over all benchmarks in the division.  Let~$N$ be the
+total number of benchmarks in the division.
 
@@
 (Section~\ref{sec:benchmark-scoring}) $$\sum_b \alpha'_b \cdot \langle
-e_b, n_b, w_b, c_b\rangle$$ where the sum is over all benchmarks in
-the division to assess parallel performance, and the weighted sum of
-all sequential scores (Section~\ref{sec:sequential}) to assess
-sequential performance.  For application track divisions, division
-scores will be based on raw scores only.\footnote{Since application
-  track benchmarks may be partially solved, defining a useful
-  sequential score for the application track would require information
-  not provided by the raw score, e.g., detailed timing information for
-  each result.}
+e_b \cdot N, n_b \cdot N, w_b, c_b\rangle$$ where the sum is over all
+benchmarks in the division to assess parallel performance, and the
+weighted sum of all sequential scores (Section~\ref{sec:sequential})
+to assess sequential performance.  For application track divisions,
+division scores will be based on raw scores only.\footnote{Since
+  application track benchmarks may be partially solved, defining a
+  useful sequential score for the application track would require
+  information not provided by the raw score, e.g., detailed timing
+  information for each result.}
 

### 2017-04-20 rules/rules17.tex
Various updates for 2017

@@
 
-%\usepackage{draftwatermark}
+\usepackage{draftwatermark}
+
+\hyphenation{data-types}
 
@@
 
-\title{11th International Satisfiability Modulo Theories Competition
-  (SMT-COMP 2016): Rules and Procedures}
+\title{12th International Satisfiability Modulo Theories Competition
+  (SMT-COMP 2017): Rules and Procedures}
 
@@
 \author{%
-Sylvain Conchon \\
-Paris-Sud University \\
-France \\
-{\small\href{mailto:Sylvain.Conchon@lri.fr}{\texttt{Sylvain.Conchon@lri.fr}}} \\
-\and
-David D{\'e}harbe \\
-Clearsy, France \& Federal University\\ of Rio Grande do Norte, Brazil \\
-{\small\href{mailto:david.deharbe@clearsy.com}{\texttt{david.deharbe@clearsy.com}}} \\
-\and
 Matthias Heizmann \\
@@
 {\small\href{mailto:heizmann@informatik.uni-freiburg.de}{\texttt{heizmann@informatik.uni-freiburg.de}}} \\
-{\small\textsc{(Unsat Core Track)}} \\
+\and
+Giles Reger \\
+University of Manchester \\
+UK \\
+{\small\href{mailto:giles.reger@manchester.ac.uk}{\texttt{giles.reger@manchester.ac.uk}}} \\
 \and
@@
 competition web site, \url{www.smtcomp.org} or
-\url{smtcomp.sourceforge.net/2016}.
+\url{smtcomp.sourceforge.net/2017}.
 
@@
 \item[May~1] Deadline for new benchmark contributions.
-\item[May~15] Deadline for first versions of solvers (for all tracks),
+\item[June~1] Final versions of competition tools (e.g., benchmark
+  scrambler) are made available.  Benchmark libraries are frozen.
+\item[June~4] Deadline for first versions of solvers (for all tracks),
   including information about which tracks and divisions are being
   entered, and magic numbers for benchmark scrambling.
-\item[May~22] Final versions of competition tools (e.g., benchmark
-  scrambler) are made available.  Benchmark libraries are frozen.
-\item[May~29] Deadline for final versions of solvers, including
+\item[June~18] Deadline for final versions of solvers, including
   system descriptions.
-\item[May~30] Opening value of NYSE Composite Index used to complete
+\item[June~19] Opening value of NYSE Composite Index used to complete
   random seed for benchmark scrambling.
-\item[July~1/2] SMT Workshop; end of competition, presentation of
+\item[July~22/23] SMT Workshop; end of competition, presentation of
   results.
@@
 
-SMT-COMP~2016 is affiliated with the SMT Workshop~2016
-(\url{http://smt-workshop.cs.uiowa.edu/2016/}), which is associated
-with IJCAR~2016 (\url{http://ijcar-2016.info/}).  The SMT Workshop
-will include a block of time to present the results of the
+SMT-COMP~2017 is part of the SMT Workshop~2017
+(\url{http://smt-workshop.cs.uiowa.edu/2017/}), which is affiliated
+with CAV~2017 (\url{http://cavconference.org/2017/}).  The SMT
+Workshop will include a block of time to present the results of the
 competition.
@@
 
-SMT-COMP 2016 will have three tracks: the conventional main track, an
-application (i.e., incremental) track, and an unsat-core track.  The
-unsat-core track will be experimental in 2016.
+SMT-COMP 2017 will have three tracks: the conventional main track, an
+application (i.e., incremental) track, and an unsat-core track.
 
@@
   Sylvain Conchon, David D{\'e}harbe, Morgan Deters, Alberto Griggio,
-  Albert Oliveras, Aaron Stump, and Tjark Weber.} describes the rules
-and competition procedures for SMT-COMP~2016.  The principal changes
-from the previous competition rules are the following:
+  Matthias Heizmann, Albert Oliveras, Aaron Stump, and Tjark Weber.}
+describes the rules and competition procedures for SMT-COMP~2017.  The
+principal changes from the previous competition rules are the
+following:
 \begin{itemize}
-\item Benchmarks will use (a subset of) version~2.5 of the SMT-LIB
-  language.  \emph{Rationale:} This is the latest version of the
-  SMT-LIB language.  It was released on 2015-06-28, and is largely
-  backwards-compatible to version~2.0, which was used for SMT-COMP
-  2015.
-\item Solver output may affect the score even when the solver does not
-  terminate within the time limit.  (In 2015, main track solver output
-  was ignored if the solver subsequently timed out.)  Solvers should
-  take care not to accidentally produce output that contains
-  \texttt{sat} or \texttt{unsat} even when they are killed.
-  \emph{Rationale:} Users are likely to trust solver responses even
-  when the solver continues to run for some time.
-\item Divisions for floating-point arithmetic are no longer
-  experimental, and will be considered competitive if the necessary
-  requirements (see Section~\ref{sec:scoring}) are met.
-  \emph{Rationale:} Floating-point divisions were experimental in
-  2015.  By now, their definition is sufficiently stable, and they are
-  supported by several solvers.
-\item Division scores will be based on a weighted sum of scores for
-  benchmark families.  \emph{Rationale:} For some years now, SMT-COMPs
-  have had sufficient computational resources to evaluate all solver
-  entrants on all eligible benchmarks.  As a side-effect, the
-  weighting of benchmark families that was achieved in early SMT-COMPs
-  through a careful selection of benchmarks (based on benchmark
-  difficulty and category) was lost.  Since there are vast differences
-  in size between benchmark families, we believe that a weighting that
-  de-emphasizes large benchmark families (see
-  Section~\ref{sec:division-scoring}) will lead to more meaningful
-  competition results.
-\item The unsat-core track that was introduced in SMT-COMP 2012, but
-  discontinued in 2013-2015 (partly because of the competition's move
-  to StarExec), is back.  It will be experimental in 2016; its results
-  will be reported, but no official winners will be announced.
-  \emph{Rationale:} Unsat cores are important in many applications of
-  SMT solving.  The track was discontinued primarily for
-  infrastructure and resource reasons.  We are pleased that we can
-  finally offer it again, but we ask for your understanding in case of
-  mishaps while we port the required tools.
-\item Best industrial performance will no longer be recognized
-  separately.  \emph{Rationale:} While there is agreement in the SMT
-  community to emphasize problems that come from real applications,
-  industrial performance largely coincided with overall performance in
-  SMT-COMP 2015.  We consider the effort to determine and report it
-  separately no longer justified.
+\item Submission of accompanying information for solvers is via a web
+  form (rather than by email to the organizers).  \emph{Rationale:}
+  Email submissions were often incomplete, leading to ambiguity and
+  further inquiries.  The form provides a more structured way of
+  submitting information.
+\item Benchmarks with unknown status will be eligible for the
+  competition's main track.  In 2016, solver performance on benchmarks
+  with unknown status was evaluated but reported separately; in 2017,
+  it will directly affect the competition results.  \emph{Rationale:}
+  Using only benchmarks with known status (i.e., benchmarks that have
+  been solved before) to determine the competition results unjustly
+  favors imitation of existing solvers over true innovation.
+\item Benchmarks will likely use (a subset of) version~2.5 of the
+  SMT-LIB language.  \emph{Rationale:} This is the latest version of
+  the SMT-LIB language.  Its use had been announced for SMT-COMP 2016
+  already, but was delayed because the SMT-LIB benchmark collection
+  had not been updated.  Solvers should ideally support both
+  versions~2.0 and~2.5; the latter is largely backwards-compatible.
+\item Benchmarks that use partial bit-vector functions, such as
+  \texttt{bvudiv}, may become eligible for the competition again,
+  provided the semantics of these functions (according to SMT-LIB) is
+  changed to agree with existing solver implementations, and the
+  status of affected SMT-LIB benchmarks is updated accordingly.
+  \emph{Rationale:} The semantics of these functions has been
+  discussed for a long time, and it appears that a conclusion has
+  finally been reached.
+\item The penalty for erroneous results in the competition-wide
+  scoring is changed from the number of errors to a fixed constant
+  (multiplied by the weight of the respective division).
+  \emph{Rationale:} The weight already takes the number of benchmarks
+  in a division into account; multiplying it by the number of errors
+  overemphasizes large divisions.
+\item The unsat-core track, which was re-introduced in 2016, is no
+  longer experimental.  Its divisions will be considered competitive
+  if the necessary requirements (see Section~\ref{sec:scoring}) are
+  met.  \emph{Rationale:} Rules and tool support for the unsat-core
+  track proved sufficiently stable in 2016.
+\item The competition may feature experimental divisions for
+  benchmarks that use algebraic datatypes, provided suitable
+  benchmarks are available.  \emph{Rationale:} Algebraic datatypes are
+  specified in the draft SMT-LIB~2.6 standard, which is expected to
+  become official in the near future, and are already supported by
+  some solvers.
 \end{itemize}
@@
 run, or may run public solvers already uploaded to the service.
-
-For participation in SMT-COMP, a solver must be uploaded to StarExec,
-made publicly available, and the organizers informed of its presence
-\emph{and the tracks and divisions in which it is participating}.
-StarExec supports solver configurations; for clarity, \emph{each
-  submitted solver must have one configuration only}.  A submission
-must also include a 32-bit unsigned integer.  These integer numbers,
-collected from all submissions, are used to seed the benchmark
-scrambler.
-
 Information about how to configure and upload a solver is contained in
@@
 \url{https://wiki.uiowa.edu/display/stardev/User+Guide}.
+
+For participation in SMT-COMP, a solver must be uploaded to StarExec
+and made publicly available.  StarExec supports solver configurations;
+for clarity, \emph{each submitted solver must have one configuration
+  only}.  Moreover, the organizers must be informed of the solver's
+presence \emph{and the tracks and divisions in which it is
+  participating} via the web form at
+\begin{center}
+  \url{https://goo.gl/forms/HL6rbOywqW4sFo1D2}
+\end{center}
+A submission must also include a 32-bit unsigned integer.  These
+integer numbers, collected from all submissions, are used to seed the
+benchmark scrambler.
 
@@
 SMT-COMP entrants must be submitted via StarExec (solvers) \emph{and}
-email to the organizers (accompanying information) until the end of
-{\bf May~15, 2016} anywhere on earth.  After this date no new entrants
+the above web form (accompanying information) until the end of {\bf
+  June~4, 2017} anywhere on earth.  After this date no new entrants
 will be accepted.  However, updates to existing entrants on StarExec
-will be accepted until the end of {\bf May~29, 2016} anywhere on
+will be accepted until the end of {\bf June~18, 2017} anywhere on
 earth.
@@
 The bulk of the computation will take place during the weeks leading
-up to SMT~2016, from about May~30 to June~30.  Intermediate results
-will be regularly posted to the SMT-COMP website as the competition
-runs.
+up to SMT 2017.  Intermediate results will be regularly posted to the
+SMT-COMP website as the competition runs.
 
@@
 The time limit~$T$ is yet to be determined, but it is anticipated to
-be 40~minutes of wall-clock time per solver/benchmark
+be at most 40~minutes of wall-clock time per solver/benchmark
 pair.\footnote{The time limit may be adjusted once we know the number
-  of competition entrants and eligible benchmarks.}  Solvers that take
-more than this time limit will be killed.  Solvers are allowed to
-spawn other processes; these will be killed at approximately the same
-time as the first started process.
+  of competition entrants and eligible benchmarks.  Because of the
+  inclusion of benchmarks with unknown status, the time limit may be
+  lower than in previous years.}  Solvers that take more than this
+time limit will be killed.  Solvers are allowed to spawn other
+processes; these will be killed at approximately the same time as the
+first started process.
 
@@
 The main track competition uses a StarExec post-processor (named
-``SMT-COMP 2016") to accumulate the results.
+``SMT-COMP 2017") to accumulate the results.
 
@@
 %
-The deadline for submission of new benchmarks is {\bf May~1, 2016}.
-The organizers will be checking and curating these until {\bf May~22,
-  2016}.  The organizers reserve the right to exclude new benchmarks
-if any prove problematic for some reason.  SMT-COMP attempts to give
-preference to benchmarks that are ``real-world,'' in the sense of
-coming from or having some intended application outside SMT.
-
-New benchmarks will be made publicly available as soon as possible
-after the benchmark submission deadline, as they are checked and
-curated.  The set of benchmarks selected for the competition will be
-published when the competition begins.
+The deadline for submission of new benchmarks is {\bf May~1, 2017}.
+The organizers, in collaboration with the SMT-LIB maintainers, will be
+checking and curating these until {\bf June~1, 2017}.  The SMT-LIB
+maintainers intend to make a new release of the benchmark library
+publicly available on or close to this date.
 
@@
 
-Each benchmark in SMT-LIB also has a \emph{category}.  There are four
-possible categories:
-\begin{itemize}
-\item \emph{check.} These benchmarks are hand-crafted to test whether
-  solvers support specific features of each division.
-\item \emph{industrial.} These benchmarks come from some real
-  application and are produced by tools such as bounded model
-  checkers, static analyzers, extended static checkers, etc.
-\item \emph{random.} These benchmarks are randomly generated.
-\item \emph{crafted.} This category is for all other benchmarks.
-  Usually, benchmarks in this category are designed to be particularly
-  difficult or to test a specific feature of the logic.
-\end{itemize}
-
 \header{Benchmark selection.}
 %
-The benchmark pool is culled as follows:
+The competition will use a large subset of SMT-LIB benchmarks.  The
+benchmark pool is culled as follows:
 \begin{enumerate}
-\item \emph{Retire inappropriate benchmarks.} The competition
-  organizers may remove from the eligibility pool certain benchmarks
-  that are inappropriate\footnote{In 2016, this (again) includes all
+\item \emph{Remove inappropriate benchmarks.} The competition
+  organizers may remove benchmarks that are deemed
+  inappropriate\footnote{In 2017, this may (again) include all
     benchmarks that use partial or underspecified functions, e.g.,
-    \texttt{bvudiv}, \texttt{fp.min}.}  or uninteresting for
+    \texttt{bvudiv}, \texttt{fp.min}, unless their semantics can be
+    resolved in time for the competition.}  or uninteresting for
   competition, or cut the size of certain benchmark families to avoid
-  their over-representation.
-\item \emph{Eliminate benchmarks whose status is unknown.} Any
-  benchmark whose expected output is neither \texttt{sat} nor
-  \texttt{unsat} is removed.  There are a significant number of
-  benchmarks with \texttt{unknown} status in the library; these are
-  certainly interesting and are a challenge to solve, but they are not
-  used in the competition.\footnote{Incremental benchmarks may contain
-    multiple \akey{check-sat} commands, each with its own status.
-    Incremental benchmarks that contain (some) \akey{check-sat}
-    commands with \texttt{unknown} status may still contain a prefix
-    of commands where the status is known for all \akey{check-sat}
-    commands in the prefix.  This prefix is eligible for the
-    application track.}
+  their over-representation.  SMT-COMP attempts to give preference to
+  benchmarks that are ``real-world,'' in the sense of coming from or
+  having some intended application outside SMT.
+\item \emph{Remove incremental benchmarks whose first \akey{check-sat}
+  command has unknown status.}  Incremental benchmarks may contain
+  multiple \akey{check-sat} commands, each with its own status.  If an
+  incremental benchmark contains a \akey{check-sat} command whose
+  status is unknown, only the prefix of the benchmark up to the
+  preceding \akey{check-sat} command is eligible for the application
+  track of the competition; if the benchmark's first \akey{check-sat}
+  command has unknown status, the entire benchmark is
+  ineligible.\footnote{It might be desirable to also include
+    \akey{check-sat} commands with unknown status in the application
+    track (for the same reasons they are now included in the main
+    track), but this would require substantial changes to the trace
+    executor and scoring tools.}
 \end{enumerate}
@@
 
+The set of benchmarks selected for the competition will be published
+when the competition begins.
+
 \header{Heats.}
 %
-Since the organizers at this point are unsure how long a set of
+Since the organizers at this point are unsure how long the set of
 benchmarks may take (which will depend also on the number of solvers
@@
 
+\subsection{Competitive divisions}
+
 Scores will be computed for all solvers and divisions.  However,
@@
 \item $e=0$, $n=1$ if the result of the \akey{check-sat} command is
-  correct,
+  \texttt{sat} or \texttt{unsat}, and the result either agrees with
+  the benchmark status or the benchmark status is unknown,\footnote{If
+    the benchmark status is unknown, we thus treat the solver's answer
+    as correct.  Disagreements between different solvers on benchmarks
+    with unknown status are governed in
+    Section~\ref{sec:division-scoring}.}
 \item $e=1$, $n=0$ if the result of the \akey{check-sat} command is
@@
 
-\subsection{Sequential performance}
+\subsection{Sequential performance (main track)}
 \label{sec:sequential}
@@
 
+\header{Main track: removal of disagreements.}
+%
+Before division scores are computed for the main track, benchmarks
+with unknown status are removed from the competition results if two
+(or more) sound solvers disagree on their result.  More specifically,
+a solver (including a solver that was entered into the competition by
+the organizers for comparison purposes) is \emph{sound} for a division
+if its raw score (Section~\ref{sec:benchmark-scoring}) is of the form
+$\langle 0, n, w, c\rangle$ for each benchmark in the division, i.e.,
+if it did not produce any erroneous results.  Two solvers
+\emph{disagree} on a benchmark if one of them reported \texttt{sat}
+and the other reported \texttt{unsat}.  Only the remaining benchmarks
+are used in the following computation of division scores.
+
+\medskip
+
 To compute a solver's score for a division, the solver's individual
@@
 number of benchmarks in $b$'s benchmark family that were used in the
-competition track to which the division belongs.  We define the weight
-for benchmark~$b$ as $\alpha_b = (1 + \log_e F_b) / F_b$.\footnote{See
+competition track to which the division belongs (and not removed
+because of disagreements).  We define the weight for benchmark~$b$ as
+$\alpha_b = (1 + \log_e F_b) / F_b$.\footnote{See
   Section~\ref{sec:competition-wide} for a motivating discussion of
@@
 
-\subsection{Competition-wide scoring}
+\subsection{Competition-wide scoring (main track)}
 \label{sec:competition-wide}
@@
 total number of benchmarks in division~$i$ that were used in the
-competition, and let $\langle e_i, n_i, w_i, c_i\rangle$ be a solver's
-raw score for this division (Section~\ref{sec:division-scoring}).  The
-solver's competition-wide raw score is $\sum_i (e_i == 0 \,?\,
-(n_i/N_i)^2 : -e_i) \log_e N_i$, where the sum is over all competitive
-divisions into which the solver was
-entered.\footnote{\emph{Rationale:} This metric purposely emphasizes
-  breadth of solver participation---a solver participating in many
-  logics need not be the best in any one of them.  The use of the
-  square in the metric limits that somewhat---a solver still needs to
-  do reasonably well compared to winners to be able to catch up by
+competition (and not removed because of disagreements), and let
+$\langle e_i, n_i, w_i, c_i\rangle$ be a solver's raw score for this
+division (Section~\ref{sec:division-scoring}).  The solver's
+competition-wide raw score is
+%
+$$\sum_i (e_i == 0 \,?\, (n_i/N_i)^2 : -4) \log_e N_i$$
+%
+where the sum is over all competitive divisions into which the solver
+was entered.\footnote{\emph{Rationale:} This metric purposely
+  emphasizes breadth of solver participation---a solver participating
+  in many logics need not be the best in any one of them.  The use of
+  the square in the metric limits this somewhat---a solver still needs
+  to do reasonably well compared to winners to be able to catch up by
   breadth of participation.  The non-linear metric also gives added
-  weight to completing close to all benchmarks in a division.  The log
-  scaling is a (somewhat arbitrary) means to adjust the scores for the
-  wide variety of numbers of benchmarks in different divisions.  It
-  seems a reasonable compromise between linearly combining numbers of
-  benchmarks, which would overweigh large divisions, and simply
-  summing the fraction of benchmarks solved, which would overweigh
-  small divisions.  The metric is also quite simple, and the metric
-  for a solver is independent of the performance of other solvers.
-  Time is omitted from the metric because it is only of third
-  importance in the regular competition metric, and is difficult to
-  compare across divisions.}  The solver's competition-wide sequential
-score is computed from its sequential division scores
+  weight to completing close to all benchmarks in a division.
+
+  The constant penalty for errors reflects the fact that any error (in
+  a particular division) renders a solver untrustworthy for that
+  division.  The value~$-4$ balances the community's interest in
+  correct (thoroughly tested) solvers against the risk of stifling
+  innovation: entering a perfect (but possibly buggy) solver into a
+  division has a positive expected value if the probability of a
+  soundness bug is below $\frac{1}{1+4} = 20$\,\%.
+
+  The log scaling is a (somewhat arbitrary) means to adjust the scores
+  for the wide variety of numbers of benchmarks in different
+  divisions.  It seems a reasonable compromise between linearly
+  combining numbers of benchmarks, which would overweigh large
+  divisions, and simply summing the fraction of benchmarks solved,
+  which would overweigh small divisions.
+
+  The metric is also quite simple, and the metric for a solver is
+  independent of the performance of other solvers.  Time is omitted
+  from the metric because it is only of third importance in the
+  regular competition metric, and is difficult to compare across
+  divisions.}  The solver's competition-wide sequential score is
+computed from its sequential division scores
 (Section~\ref{sec:division-scoring}) according to the same formula.
@@
 \begin{itemize}
-\item \emph{Open source.}  The top solver that provides its source
-  code as open source will be recognized in each competitive division.
 \item \emph{Best new entrant}. The best performing entrant from a new
@@
   metric.
-\item \emph{Breadth of logics}. Solvers that cover the most theories
-  and logics.
 \item \emph{Benchmarks}. Contributors of new benchmarks.
@@
 
-\section{Acknowledgments and Disclaimer}
+\section{Acknowledgments}
 
-SMT-COMP 2016 is organized under the direction of the SMT Steering
+SMT-COMP 2017 is organized under the direction of the SMT Steering
 Committee. The organizing team is
@@
 \setlength{\itemsep}{0pt}
-\item \href{https://www.lri.fr/~conchon/}{Sylvain Conchon}~--
-  Paris-Sud University, France (co-organizer)
-\item \href{https://www.sites.google.com/site/deharbe/}{David
-  D{\'e}harbe}~-- Clearsy, France, and Federal University of Rio
-  Grande do Norte, Brazil (co-organizer)
+\item \href{http://www.cs.man.ac.uk/~regerg/}{Giles Reger}~--
+  University of Manchester, UK (co-organizer)
 \item
   \href{https://swt.informatik.uni-freiburg.de/staff/heizmann}{Matthias
-    Heizmann}~-- University of Freiburg, Germany (co-organizer, unsat
-  core track)
+    Heizmann}~-- University of Freiburg, Germany (co-organizer)
 \item \href{http://user.it.uu.se/~tjawe125/}{Tjark Weber}~-- Uppsala
@@
 
-David D{\'e}harbe is associated with the solver group producing the
-veriT solver.  Matthias Heizmann is associated with the solver group
-producing the SMTInterpol solver.
+\header{Disclosure.}
+%
+Matthias Heizmann is associated with the group producing the
+SMTInterpol solver.  Giles Reger is associated with the group
+producing the Vampire system.
 
@@
 %% ispell-local-dictionary: "american"
-%% LocalWords: arity Conchon logics satisfiability SMT Sylvain Tjark
+%% LocalWords: arity Heizmann logics Reger satisfiability SMT StarExec Tjark
 %% End:

### 2017-04-21 rules/rules17.tex
Minor.

@@
   a particular division) renders a solver untrustworthy for that
-  division.  The value~$-4$ balances the community's interest in
+  division.  The value~$4$ balances the community's strong interest in
   correct (thoroughly tested) solvers against the risk of stifling
-  innovation: entering a perfect (but possibly buggy) solver into a
-  division has a positive expected value if the probability of a
-  soundness bug is below $\frac{1}{1+4} = 20$\,\%.
+  innovation: entering a (possibly buggy) solver that can solve all
+  benchmarks into a division has a positive expected value if the
+  probability of a soundness bug is below $\frac{1}{1+4} = 20$\,\%.
 

### 2017-04-21 rules/rules17.tex
Minor.

@@
   submitting information.
+\item Benchmarks may use (a subset of) version~2.5 of the SMT-LIB
+  language.  \emph{Rationale:} This is the latest version of the
+  SMT-LIB language.  Its use had been announced for SMT-COMP 2016
+  already, but was delayed because the SMT-LIB benchmark collection
+  had not been updated.  Solvers should ideally support both
+  versions~2.0 and~2.5; the latter is largely backwards-compatible.
+\item Benchmarks that use partial bit-vector functions, such as
+  \texttt{bvudiv}, or underspecified floating-point functions, such as
+  \texttt{fp.min}, may become eligible for the competition again,
+  provided (i)~the semantics of these functions agrees with existing
+  solver implementations, and (ii)~the status of affected benchmarks
+  in SMT-LIB is not incorrect.  \emph{Rationale:} The semantics of
+  these functions had been under discussion, and it appears that a
+  conclusion has finally been reached.
 \item Benchmarks with unknown status will be eligible for the
@@
   favors imitation of existing solvers over true innovation.
-\item Benchmarks will likely use (a subset of) version~2.5 of the
-  SMT-LIB language.  \emph{Rationale:} This is the latest version of
-  the SMT-LIB language.  Its use had been announced for SMT-COMP 2016
-  already, but was delayed because the SMT-LIB benchmark collection
-  had not been updated.  Solvers should ideally support both
-  versions~2.0 and~2.5; the latter is largely backwards-compatible.
-\item Benchmarks that use partial bit-vector functions, such as
-  \texttt{bvudiv}, may become eligible for the competition again,
-  provided the semantics of these functions (according to SMT-LIB) is
-  changed to agree with existing solver implementations, and the
-  status of affected SMT-LIB benchmarks is updated accordingly.
-  \emph{Rationale:} The semantics of these functions has been
-  discussed for a long time, and it appears that a conclusion has
-  finally been reached.
-\item The penalty for erroneous results in the competition-wide
-  scoring is changed from the number of errors to a fixed constant
-  (multiplied by the weight of the respective division).
+\item In the competition-wide scoring, the (per-division) penalty for
+  erroneous results is changed from the number of errors to a fixed
+  constant (multiplied by the weight of the respective division).
   \emph{Rationale:} The weight already takes the number of benchmarks
-  in a division into account; multiplying it by the number of errors
+  in the division into account; multiplying it by the number of errors
   overemphasizes large divisions.
@@
   organizers may remove benchmarks that are deemed
-  inappropriate\footnote{In 2017, this may (again) include all
+  inappropriate\footnote{In previous years, this included all
     benchmarks that use partial or underspecified functions, e.g.,
-    \texttt{bvudiv}, \texttt{fp.min}, unless their semantics can be
-    resolved in time for the competition.}  or uninteresting for
+    \texttt{bvudiv}, \texttt{fp.min}.  Whether these benchmarks are
+    included in 2017 is yet to be decided.} or uninteresting for
   competition, or cut the size of certain benchmark families to avoid

### 2017-04-26 rules/rules17.tex
Clarify soundness

@@
 with unknown status are removed from the competition results if two
-(or more) sound solvers disagree on their result.  More specifically,
-a solver (including a solver that was entered into the competition by
-the organizers for comparison purposes) is \emph{sound} for a division
-if its raw score (Section~\ref{sec:benchmark-scoring}) is of the form
-$\langle 0, n, w, c\rangle$ for each benchmark in the division, i.e.,
-if it did not produce any erroneous results.  Two solvers
-\emph{disagree} on a benchmark if one of them reported \texttt{sat}
-and the other reported \texttt{unsat}.  Only the remaining benchmarks
-are used in the following computation of division scores.
+(or more) solvers that are sound on benchmarks with known status
+disagree on their result.  More specifically, a solver (including a
+solver that was entered into the competition by the organizers for
+comparison purposes) is \emph{sound on benchmarks with known status}
+for a division if its raw score (Section~\ref{sec:benchmark-scoring})
+is of the form $\langle 0, n, w, c\rangle$ for each benchmark in the
+division, i.e., if it did not produce any erroneous results.  Two
+solvers \emph{disagree} on a benchmark if one of them reported
+\texttt{sat} and the other reported \texttt{unsat}.  Only the
+remaining benchmarks are used in the following computation of division
+scores.
 

### 2017-04-26 rules/rules17.tex
More detailed explanation of checking for the unsat-core track

@@
 formulas that have not been asserted before), or if the returned
-unsatisfiable core is not, in fact, unsatisfiable.  The organizers
-intend to check unsatisfiability by running an SMT solver on a
-benchmark that asserts only those formulas in the reported core.  The
-details of the checking procedure, which will be the same for all
-solvers and benchmarks in the unsat-core track, are still to be
-determined.
+unsatisfiable core is not, in fact, unsatisfiable.
+
+In order to perform this unsatisfiability check, the organizers will
+use a selection of SMT solvers that have been sound (i.e., not
+produced any erroneous result) in the corresponding division of the
+main track.  The unsatisfiability of a produced unsatisfiable core is
+refuted if the number of checking solvers whose result is \textt{sat}
+exceeds the number of checking solvers whose result is \textt{unsat},
+or if the unsat-core producing solver is used as a checking solver and
+its result is \textt{sat}.  The time limit for checking unsatisfiable
+cores is yet to be determined, but is anticipated to be around 5
+minutes of wall-clock time per solver.
 

### 2017-04-26 rules/rules17.tex
Fix LaTeX error

@@
 main track.  The unsatisfiability of a produced unsatisfiable core is
-refuted if the number of checking solvers whose result is \textt{sat}
-exceeds the number of checking solvers whose result is \textt{unsat},
+refuted if the number of checking solvers whose result is \texttt{sat}
+exceeds the number of checking solvers whose result is \texttt{unsat},
 or if the unsat-core producing solver is used as a checking solver and
-its result is \textt{sat}.  The time limit for checking unsatisfiable
+its result is \texttt{sat}.  The time limit for checking unsatisfiable
 cores is yet to be determined, but is anticipated to be around 5

### 2017-06-12 rules/rules17.tex
Update to reflect 2017-06-05 SMT-LIB release and remove draft watermark

@@
   submitting information.
-\item Benchmarks may use (a subset of) version~2.5 of the SMT-LIB
+\item Benchmarks will use (a subset of) version~2.6 of the SMT-LIB
   language.  \emph{Rationale:} This is the latest version of the
-  SMT-LIB language.  Its use had been announced for SMT-COMP 2016
-  already, but was delayed because the SMT-LIB benchmark collection
-  had not been updated.  Solvers should ideally support both
-  versions~2.0 and~2.5; the latter is largely backwards-compatible.
+  SMT-LIB language.  It is largely backwards-compatible with earlier
+  versions (in particular~2.0 and~2.5).
 \item Benchmarks that use partial bit-vector functions, such as
   \texttt{bvudiv}, or underspecified floating-point functions, such as
-  \texttt{fp.min}, may become eligible for the competition again,
-  provided (i)~the semantics of these functions agrees with existing
-  solver implementations, and (ii)~the status of affected benchmarks
-  in SMT-LIB is not incorrect.  \emph{Rationale:} The semantics of
-  these functions had been under discussion, and it appears that a
-  conclusion has finally been reached.
+  \texttt{fp.min}, will be eligible for the competition again.
+  \emph{Rationale:} A conclusion on the semantics of these functions
+  has finally been reached, and the status of affected SMT-LIB
+  benchmarks has been updated accordingly.
 \item Benchmarks with unknown status will be eligible for the
@@
   track proved sufficiently stable in 2016.
-\item The competition may feature experimental divisions for
-  benchmarks that use algebraic datatypes, provided suitable
-  benchmarks are available.  \emph{Rationale:} Algebraic datatypes are
-  specified in the draft SMT-LIB~2.6 standard, which is expected to
-  become official in the near future, and are already supported by
-  some solvers.
+\item The competition will feature experimental divisions for
+  benchmarks that use algebraic datatypes.  \emph{Rationale:}
+  Algebraic datatypes are specified in the draft SMT-LIB~2.6 standard,
+  which is expected to become official in the near future, and are
+  already supported by some solvers.  Benchmarks that use datatypes
+  have recently been added to SMT-LIB.
 \end{itemize}
@@
 The benchmark script is in the concrete syntax of the SMT-LIB format,
-version~2.5, though with a restricted set of commands.  A benchmark
+version~2.6, though with a restricted set of commands.  A benchmark
 script is a text file containing a sequence of SMT-LIB commands that
@@
     \texttt{success} outputs are ignored by the post-processor used by
-    the competition.\footnote{SMT-LIB~2.5 requires solvers to produce
+    the competition.\footnote{SMT-LIB~2.6 requires solvers to produce
       a \texttt{success} answer after each \akey{set-logic},
@@
       is set to false.  Ignoring the \texttt{success} outputs allows
-      for submitting fully SMT-LIB~2.5 compliant solvers without the
+      for submitting fully SMT-LIB~2.6 compliant solvers without the
       need for a wrapper script, while still allowing entrants of
@@
 \item \emph{Remove inappropriate benchmarks.} The competition
-  organizers may remove benchmarks that are deemed
-  inappropriate\footnote{In previous years, this included all
-    benchmarks that use partial or underspecified functions, e.g.,
-    \texttt{bvudiv}, \texttt{fp.min}.  Whether these benchmarks are
-    included in 2017 is yet to be decided.} or uninteresting for
-  competition, or cut the size of certain benchmark families to avoid
-  their over-representation.  SMT-COMP attempts to give preference to
-  benchmarks that are ``real-world,'' in the sense of coming from or
-  having some intended application outside SMT.
+  organizers may remove benchmarks that are deemed inappropriate or
+  uninteresting for competition, or cut the size of certain benchmark
+  families to avoid their over-representation.  SMT-COMP attempts to
+  give preference to benchmarks that are ``real-world,'' in the sense
+  of coming from or having some intended application outside SMT.
 \item \emph{Remove incremental benchmarks whose first \akey{check-sat}
@@
 Many others have contributed benchmarks, effort, and feedback.  Clark
-Barrett is maintaining the SMT-LIB benchmark library.  The competition
-uses the \href{https://www.starexec.org/}{StarExec} service, which is
-hosted at the \href{http://www.cs.uiowa.edu/}{University of Iowa}.
-Aaron Stump is providing essential StarExec support.
+Barrett and Pascal Fontaine are maintaining the SMT-LIB benchmark
+library.  The competition uses the
+\href{https://www.starexec.org/}{StarExec} service, which is hosted at
+the \href{http://www.cs.uiowa.edu/}{University of Iowa}.  Aaron Stump
+is providing essential StarExec support.
 

### 2017-06-19 rules/rules17.tex
Allow declare-datatype(s) commands if the logic features algebraic datatypes
Extend deadline to 2017-06-19

@@
   entered, and magic numbers for benchmark scrambling.
-\item[June~18] Deadline for final versions of solvers, including
+\item[June~19] Deadline for final versions of solvers, including
   system descriptions.
-\item[June~19] Opening value of NYSE Composite Index used to complete
+\item[June~20] Opening value of NYSE Composite Index used to complete
   random seed for benchmark scrambling.
@@
   \akey{define-fun} commands.
+\item If the benchmark's logic features algebraic datatypes, the
+  script may contain any number of \akey{declare-datatype(s)}
+  commands.
 \item The script may contain any number of \akey{assert} commands.

### 2018-04-05 rules/rules18.tex
Add draft of 2018 rules
Unsat-core Track rules

--- 2017-06-19 rules/rules17.tex
@@
 will be accepted.  However, updates to existing entrants on StarExec
-will be accepted until the end of {\bf June~18, 2017} anywhere on
+will be accepted until the end of {\bf June~19, 2017} anywhere on
 earth.
@@
 In order to perform this unsatisfiability check, the organizers will
-use a selection of SMT solvers that have been sound (i.e., not
-produced any erroneous result) in the corresponding division of the
-main track.  The unsatisfiability of a produced unsatisfiable core is
+use a selection of SMT solvers that participate in the main track
+of this competition. For each division, the organizers will
+use only solvers that have been sound (i.e., not
+produced any erroneous result) in test runs of the
+main track for this division.
+The unsatisfiability of a produced unsatisfiable core is
 refuted if the number of checking solvers whose result is \texttt{sat}
-exceeds the number of checking solvers whose result is \texttt{unsat},
-or if the unsat-core producing solver is used as a checking solver and
-its result is \texttt{sat}.  The time limit for checking unsatisfiable
+exceeds the number of checking solvers whose result is \texttt{unsat}.
+The time limit for checking unsatisfiable
 cores is yet to be determined, but is anticipated to be around 5

### 2018-04-07 rules/rules18.tex
Added Aina.

@@
 {\small\href{mailto:heizmann@informatik.uni-freiburg.de}{\texttt{heizmann@informatik.uni-freiburg.de}}} \\
+\and
+Aina Niemetz \\
+Stanford University\\
+USA\\
+{\small\href{mailto:niemetz@cs.stanford.edu}{\texttt{niemetz@cs.stanford.edu}}}\\
 \and
@@
     Heizmann}~-- University of Freiburg, Germany (co-organizer)
+\item
+  \href{http://cs.stanford.edu/people/niemetz}{Aina
+    Niemetz}~-- Stanford University, USA (co-organizer)
 \item \href{http://user.it.uu.se/~tjawe125/}{Tjark Weber}~-- Uppsala
@@
 %
+Aina Niemetz is part of the developing teams of the SMT solvers Boolector
+and CVC4.
 Matthias Heizmann is associated with the group producing the

### 2018-04-10 rules/rules18.tex
Updated dates.

@@
 
+\newcommand{\rem}[1]{\textcolor{red}{[#1]}}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-\title{12th International Satisfiability Modulo Theories Competition
-  (SMT-COMP 2017): Rules and Procedures}
+\title{13th International Satisfiability Modulo Theories Competition
+  (SMT-COMP 2018): Rules and Procedures}
 
@@
 competition web site, \url{www.smtcomp.org} or
-\url{smtcomp.sourceforge.net/2017}.
+\url{smtcomp.sourceforge.net/2018}.
 
@@
 
-SMT-COMP~2017 is part of the SMT Workshop~2017
-(\url{http://smt-workshop.cs.uiowa.edu/2017/}), which is affiliated
-with CAV~2017 (\url{http://cavconference.org/2017/}).  The SMT
-Workshop will include a block of time to present the results of the
+SMT-COMP~2018 is part of the SMT Workshop~2018
+(\url{http://smt-workshop.cs.uiowa.edu/2018/}),
+which is affiliated with IJCAR~2018 (\url{http://ijcar2018.org/}),
+part of FLoC 2018 (\url{http://www.floc2018.org/}).
+The SMT Workshop will include a block of time to present the results of the
 competition.
@@
 
-SMT-COMP 2017 will have three tracks: the conventional main track, an
+SMT-COMP 2018 will have three tracks: the conventional main track, an
 application (i.e., incremental) track, and an unsat-core track.
@@
   Matthias Heizmann, Albert Oliveras, Aaron Stump, and Tjark Weber.}
-describes the rules and competition procedures for SMT-COMP~2017.  The
+describes the rules and competition procedures for SMT-COMP~2018.  The
 principal changes from the previous competition rules are the
@@
 \begin{center}
+  \rem{TODO, this is still the old link}
   \url{https://goo.gl/forms/HL6rbOywqW4sFo1D2}
@@
 the above web form (accompanying information) until the end of {\bf
-  June~4, 2017} anywhere on earth.  After this date no new entrants
-will be accepted.  However, updates to existing entrants on StarExec
-will be accepted until the end of {\bf June~19, 2017} anywhere on
-earth.
+  May~27, 2018} anywhere on earth.
+After this date no new entrants will be accepted.
+However, updates to existing entrants on StarExec
+will be accepted until the end of {\bf June~10, 2018} anywhere on earth.
 
@@
 The bulk of the computation will take place during the weeks leading
-up to SMT 2017.  Intermediate results will be regularly posted to the
+up to SMT 2018.  Intermediate results will be regularly posted to the
 SMT-COMP website as the competition runs.
@@
 The main track competition uses a StarExec post-processor (named
-``SMT-COMP 2017") to accumulate the results.
+``SMT-COMP 2018") to accumulate the results.
 
@@
 %
-The deadline for submission of new benchmarks is {\bf May~1, 2017}.
+The deadline for submission of new benchmarks is {\bf April~8, 2018}.
 The organizers, in collaboration with the SMT-LIB maintainers, will be
-checking and curating these until {\bf June~1, 2017}.  The SMT-LIB
+checking and curating these until {\bf May~1, 2018}.  The SMT-LIB
 maintainers intend to make a new release of the benchmark library
@@
 
-SMT-COMP 2017 is organized under the direction of the SMT Steering
+SMT-COMP 2018 is organized under the direction of the SMT Steering
 Committee. The organizing team is
@@
 \setlength{\itemsep}{0pt}
-\item \href{http://www.cs.man.ac.uk/~regerg/}{Giles Reger}~--
-  University of Manchester, UK (co-organizer)
 \item
@@
     Niemetz}~-- Stanford University, USA (co-organizer)
+\item \href{http://www.cs.man.ac.uk/~regerg/}{Giles Reger}~--
+  University of Manchester, UK (co-organizer)
 \item \href{http://user.it.uu.se/~tjawe125/}{Tjark Weber}~-- Uppsala

### 2018-04-10 rules/rules18.tex
Updated important dates.

@@
 \begin{description}
-\item[May~1] Deadline for new benchmark contributions.
-\item[June~1] Final versions of competition tools (e.g., benchmark
+\item[April~8] Deadline for new benchmark contributions.
+\item[May~1] Final versions of competition tools (e.g., benchmark
   scrambler) are made available.  Benchmark libraries are frozen.
-\item[June~4] Deadline for first versions of solvers (for all tracks),
+\item[May~27] Deadline for first versions of solvers (for all tracks),
   including information about which tracks and divisions are being
   entered, and magic numbers for benchmark scrambling.
-\item[June~19] Deadline for final versions of solvers, including
+\item[June~10] Deadline for final versions of solvers, including
   system descriptions.
-\item[June~20] Opening value of NYSE Composite Index used to complete
+\item[\rem{June~20 TODO update}] Opening value of NYSE Composite Index used to complete
   random seed for benchmark scrambling.
-\item[July~22/23] SMT Workshop; end of competition, presentation of
+\item[July~12/13] SMT Workshop; end of competition, presentation of
   results.

### 2018-04-10 rules/rules18.tex
Updated date for SMT-LIB

@@
 \item[April~8] Deadline for new benchmark contributions.
-\item[May~1] Final versions of competition tools (e.g., benchmark
+\item[May~15] Final versions of competition tools (e.g., benchmark
   scrambler) are made available.  Benchmark libraries are frozen.
@@
 The organizers, in collaboration with the SMT-LIB maintainers, will be
-checking and curating these until {\bf May~1, 2018}.  The SMT-LIB
+checking and curating these until {\bf May~15, 2018}.  The SMT-LIB
 maintainers intend to make a new release of the benchmark library

### 2018-04-11 rules/rules18.tex
Remarks

@@
 we will also recognize solvers based on additional criteria.
+\rem{Aina: Is this up to date? We do use weighting to determine a score that
+determines the winner, right? So, it is actually not the number of solved
+benchmarks that determines the winner.}
 
@@
 following:
+\rem{Aina: All of this bullets are not new in 2018 anymore, maybe move them
+elsewhere? This information should not be lost.}
 \begin{itemize}
@@
 \end{itemize}
+\rem{Aina: Are we going to introduce an experimental strings divisions?}
 
@@
 
+\rem{Aina: Why are there no restrictions as to who can submit which solver?
+Shouldn't we maybe introduce the requirement that only authors can submit
+solvers? Else someone could, e.g., submit CVC4 or Z3 as their solver.}
+
 \header{System description.}
@@
 As part of a submission, SMT-COMP entrants are encouraged to provide a
-short (1--2 pages) description of the system.  This should include a
+short (1--2 pages) description of the system.
+\rem{Aina: I would actually make the submission of the system description a
+requirement, if possible. I would also require that if entrants are based
+on an already existing solver, this must be mentioned in the system description
+and appropriate acknowledgement is due, same as with wrapper tools.}
+This should include a
 list of all authors of the system, their present institutional
@@
 wrapper tool expects to improve on the wrapped solvers.
+\rem{Aina: Again, I'd like to make the submission of system descriptions
+mandatory. SAT competition does that as well, btw.}
 
@@
   \item In the main and unsat-core track, there may be a single
-    \akey{set-option :print-success ...} command.  Note that
+    \akey{(set-option :print-success ...)} command.  Note that
     \texttt{success} outputs are ignored by the post-processor used by
@@
     must not be disabled.  The trace executor will send an initial
-    \akey{set-option :print-success true} command to the solver.
+      \akey{(set-option :print-success true)} command to the solver.
   \end{enumerate}
-\item In the unsat-core track, there is a single \akey{set-option
-  :produce-unsat-cores true} command.
+\item In the unsat-core track, there is a single \akey{(set-option
+  :produce-unsat-cores true)} command.
 \item The (single) \akey{set-logic} command setting the benchmark's
@@
 scores.
+\rem{Aina: I strongly suggest that we make disagreements visible.
+I would add a table to the bottom of the division results page, where
+we list the benchmarks we removed due to disagreements and which results
+which solvers reported. Silently dropping benchmarks on which solvers
+disagree is potentially unfair and dangerous, since people who want to use
+a solver, tend to only
+look at the SMT-COMP results and pick a solver based on this results.
+They will certainly not go through the competition results on StarExec,
+in particular since this is quite tedious.
+For users it is interesting (and might be actually crucial) to know
+if a solver disagreed with other solvers.
+The same is true for solver developers, since they certainly want to know
+if their solver disagreed with other solvers on a certain benchmark.
+They usually run preliminary tests with existing solvers beforehand,
+but not all solvers are available in the newest version.
+Not to mention new solvers.}
 
@@
 
+\rem{Aina: Do we already know how many medals FLOC is going to sponsor?
+Clark offered to pay for printing proper and beautiful certificates for each
+division if we don't have funds for that.
+As for medals, it might be a little late to get sponsors (and the funds
+from SMT-LIB went to the travel fund).}
+
+\rem{Aina: Depending on the number of medals we get from FLOC we should
+decide on how to categorize for prizes. Some ideas:
+\begin{itemize}
+  \item Competition-wide, main track, best solver
+  \item Quantified divisions, best solver
+  \item Either QF\_BV best solver, or QF\_BV + QF\_ABV + QF\_AUFBV + QF\_UFBV
+  \item Comptetition-wide, application track, best solver
+  \item Comptetition-wide, unsat-core track, best solver
+  \item Best newcomer
+\end{itemize}
+Floating-point is currently only officially supported by Z3,
+inofficially also by CVC4, if we expect more than 2 entrants, then FP logics
+would also be a candidate.
+}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %
-Aina Niemetz is part of the developing teams of the SMT solvers Boolector
-and CVC4.
+Aina Niemetz is part of the developing teams of the SMT solvers
+Boolector~\cite{boolector}
+and CVC4~\cite{cvc4}.
 Matthias Heizmann is associated with the group producing the
-SMTInterpol solver.  Giles Reger is associated with the group
-producing the Vampire system.
+SMTInterpol~\cite{smtinterpol} solver.
+Giles Reger is associated with the group
+producing the Vampire system\rem{TODO for Giles: cite Vampire}~\cite{vampire}.
 

### 2018-04-13 rules/rules18.tex
Minor

@@
   system descriptions.
-\item[\rem{June~20 TODO update}] Opening value of NYSE Composite Index used to complete
+\item[June~11] Opening value of NYSE Composite Index used to complete
   random seed for benchmark scrambling.
@@
 uses benchmarks from a specific SMT-LIB logic (or group of logics).
-We will recognize winners as measured by number of benchmarks solved;
-we will also recognize solvers based on additional criteria.
-\rem{Aina: Is this up to date? We do use weighting to determine a score that
-determines the winner, right? So, it is actually not the number of solved
-benchmarks that determines the winner.}
+We will recognize winners as measured by number of benchmarks solved
+(taking into account the weighting detailed in
+Section~\ref{sec:scoring}); we will also recognize solvers based on
+additional criteria.
 
@@
   Sylvain Conchon, David D{\'e}harbe, Morgan Deters, Alberto Griggio,
-  Matthias Heizmann, Albert Oliveras, Aaron Stump, and Tjark Weber.}
-describes the rules and competition procedures for SMT-COMP~2018.  The
-principal changes from the previous competition rules are the
-following:
-\rem{Aina: All of this bullets are not new in 2018 anymore, maybe move them
-elsewhere? This information should not be lost.}
+  Matthias Heizmann, Albert Oliveras, Giles Reger, Aaron Stump, and
+  Tjark Weber.}  describes the rules and competition procedures for
+SMT-COMP~2018.  The principal changes from the previous competition
+rules are the following: \rem{Aina: All of this bullets are not new in
+  2018 anymore, maybe move them elsewhere? This information should not
+  be lost.}
 \begin{itemize}
@@
 \begin{center}
-  \rem{TODO, this is still the old link}
-  \url{https://goo.gl/forms/HL6rbOywqW4sFo1D2}
+  \rem{TODO, this is still the old link: https://goo.gl/forms/HL6rbOywqW4sFo1D2}
+  {\tt TBA}
 \end{center}
@@
 
-\rem{Aina: Why are there no restrictions as to who can submit which solver?
-Shouldn't we maybe introduce the requirement that only authors can submit
-solvers? Else someone could, e.g., submit CVC4 or Z3 as their solver.}
-
 \header{System description.}
 %
-As part of a submission, SMT-COMP entrants are encouraged to provide a
-short (1--2 pages) description of the system.
-\rem{Aina: I would actually make the submission of the system description a
-requirement, if possible. I would also require that if entrants are based
-on an already existing solver, this must be mentioned in the system description
-and appropriate acknowledgement is due, same as with wrapper tools.}
-This should include a
-list of all authors of the system, their present institutional
-affiliations, and any appropriate acknowledgements.  The programming
-language(s) and basic SMT solving approach employed should be
-described (e.g., lazy integration of a Nelson-Oppen combination with
-SAT, translation to SAT, etc.).  System descriptions are encouraged to
+As part of a submission, SMT-COMP entrants are strongly encouraged to
+provide a short (1--2 pages) description of the system.  This should
+include a list of all authors of the system, their present
+institutional affiliations, and any appropriate acknowledgements.  The
+programming language(s) and basic SMT solving approach employed should
+be described (e.g., lazy integration of a Nelson-Oppen combination
+with SAT, translation to SAT, etc.).  System descriptions should also
 include a URL for a web site for the submitted tool.  System
@@
 %
-A \emph{wrapper tool} is defined as any solver which calls one or more
-SMT solvers not written by the author of the wrapper tool.  The other
-solvers are called the \emph{wrapped} solvers.  A wrapper tool must
-explicitly acknowledge any solvers that it wraps.  Its system
-description should make clear the technical innovations by which the
-wrapper tool expects to improve on the wrapped solvers.
-\rem{Aina: Again, I'd like to make the submission of system descriptions
-mandatory. SAT competition does that as well, btw.}
+A \emph{wrapper tool} is defined as any solver which calls (or is in
+some other way based on) one or more SMT solvers not written by the
+author of the wrapper tool.  The other solvers are called the
+\emph{wrapped} solvers.  A wrapper tool must explicitly acknowledge
+any solvers that it wraps.  Its system description should make clear
+the technical innovations by which the wrapper tool expects to improve
+on the wrapped solvers.
 
@@
 The time limit~$T$ is yet to be determined, but it is anticipated to
-be at most 40~minutes of wall-clock time per solver/benchmark
+be at most 20~minutes of wall-clock time per solver/benchmark
 pair.\footnote{The time limit may be adjusted once we know the number
-  of competition entrants and eligible benchmarks.  Because of the
-  inclusion of benchmarks with unknown status, the time limit may be
-  lower than in previous years.}  Solvers that take more than this
-time limit will be killed.  Solvers are allowed to spawn other
-processes; these will be killed at approximately the same time as the
-first started process.
+  of competition entrants and eligible benchmarks.}  Solvers that take
+more than this time limit will be killed.  Solvers are allowed to
+spawn other processes; these will be killed at approximately the same
+time as the first started process.
 
@@
 In order to perform this unsatisfiability check, the organizers will
-use a selection of SMT solvers that participate in the main track
-of this competition. For each division, the organizers will
-use only solvers that have been sound (i.e., not
-produced any erroneous result) in test runs of the
-main track for this division.
-The unsatisfiability of a produced unsatisfiable core is
-refuted if the number of checking solvers whose result is \texttt{sat}
-exceeds the number of checking solvers whose result is \texttt{unsat}.
-The time limit for checking unsatisfiable
-cores is yet to be determined, but is anticipated to be around 5
-minutes of wall-clock time per solver.
+use a selection of SMT solvers that participate in the main track of
+this competition.  For each division, the organizers will use only
+solvers that have been sound (i.e., not produced any erroneous result)
+in the main track for this division.  The unsatisfiability of a
+produced unsatisfiable core is refuted if the number of checking
+solvers whose result is \texttt{sat} exceeds the number of checking
+solvers whose result is \texttt{unsat}.  The time limit for checking
+unsatisfiable cores is yet to be determined, but is anticipated to be
+around 5 minutes of wall-clock time per solver.
 
@@
 remaining benchmarks are used in the following computation of division
-scores.
-\rem{Aina: I strongly suggest that we make disagreements visible.
-I would add a table to the bottom of the division results page, where
-we list the benchmarks we removed due to disagreements and which results
-which solvers reported. Silently dropping benchmarks on which solvers
-disagree is potentially unfair and dangerous, since people who want to use
-a solver, tend to only
-look at the SMT-COMP results and pick a solver based on this results.
-They will certainly not go through the competition results on StarExec,
-in particular since this is quite tedious.
-For users it is interesting (and might be actually crucial) to know
-if a solver disagreed with other solvers.
-The same is true for solver developers, since they certainly want to know
-if their solver disagreed with other solvers on a certain benchmark.
-They usually run preliminary tests with existing solvers beforehand,
-but not all solvers are available in the newest version.
-Not to mention new solvers.}
+scores (but the organizers may report disagreements for informational
+purposes).
+\rem{Aina: I strongly suggest that we make disagreements visible.  I
+  would add a table to the bottom of the division results page, where
+  we list the benchmarks we removed due to disagreements and which
+  results which solvers reported. Silently dropping benchmarks on
+  which solvers disagree is potentially unfair and dangerous, since
+  people who want to use a solver, tend to only look at the SMT-COMP
+  results and pick a solver based on this results.  They will
+  certainly not go through the competition results on StarExec, in
+  particular since this is quite tedious.  For users it is interesting
+  (and might be actually crucial) to know if a solver disagreed with
+  other solvers.  The same is true for solver developers, since they
+  certainly want to know if their solver disagreed with other solvers
+  on a certain benchmark.  They usually run preliminary tests with
+  existing solvers beforehand, but not all solvers are available in
+  the newest version.  Not to mention new solvers.}
 
@@
   \item Either QF\_BV best solver, or QF\_BV + QF\_ABV + QF\_AUFBV + QF\_UFBV
-  \item Comptetition-wide, application track, best solver
-  \item Comptetition-wide, unsat-core track, best solver
+  \item Competition-wide, application track, best solver
+  \item Competition-wide, unsat-core track, best solver
   \item Best newcomer

### 2018-04-17 rules/rules18.tex
add vampire reference
Update principal changes; first public version for 2018 (still draft)

@@
 SMT-COMP~2018.  The principal changes from the previous competition
-rules are the following: \rem{Aina: All of this bullets are not new in
-  2018 anymore, maybe move them elsewhere? This information should not
-  be lost.}
+rules are the following:
 \begin{itemize}
-\item Submission of accompanying information for solvers is via a web
-  form (rather than by email to the organizers).  \emph{Rationale:}
-  Email submissions were often incomplete, leading to ambiguity and
-  further inquiries.  The form provides a more structured way of
-  submitting information.
-\item Benchmarks will use (a subset of) version~2.6 of the SMT-LIB
-  language.  \emph{Rationale:} This is the latest version of the
-  SMT-LIB language.  It is largely backwards-compatible with earlier
-  versions (in particular~2.0 and~2.5).
-\item Benchmarks that use partial bit-vector functions, such as
-  \texttt{bvudiv}, or underspecified floating-point functions, such as
-  \texttt{fp.min}, will be eligible for the competition again.
-  \emph{Rationale:} A conclusion on the semantics of these functions
-  has finally been reached, and the status of affected SMT-LIB
-  benchmarks has been updated accordingly.
-\item Benchmarks with unknown status will be eligible for the
-  competition's main track.  In 2016, solver performance on benchmarks
-  with unknown status was evaluated but reported separately; in 2017,
-  it will directly affect the competition results.  \emph{Rationale:}
-  Using only benchmarks with known status (i.e., benchmarks that have
-  been solved before) to determine the competition results unjustly
-  favors imitation of existing solvers over true innovation.
-\item In the competition-wide scoring, the (per-division) penalty for
-  erroneous results is changed from the number of errors to a fixed
-  constant (multiplied by the weight of the respective division).
-  \emph{Rationale:} The weight already takes the number of benchmarks
-  in the division into account; multiplying it by the number of errors
-  overemphasizes large divisions.
-\item The unsat-core track, which was re-introduced in 2016, is no
-  longer experimental.  Its divisions will be considered competitive
-  if the necessary requirements (see Section~\ref{sec:scoring}) are
-  met.  \emph{Rationale:} Rules and tool support for the unsat-core
-  track proved sufficiently stable in 2016.
-\item The competition will feature experimental divisions for
-  benchmarks that use algebraic datatypes.  \emph{Rationale:}
-  Algebraic datatypes are specified in the draft SMT-LIB~2.6 standard,
-  which is expected to become official in the near future, and are
-  already supported by some solvers.  Benchmarks that use datatypes
-  have recently been added to SMT-LIB.
+\item The organizers plan to recognize additional special
+  contributions.  These might include:
+  \begin{itemize}
+  \item Best application track solver (awarded based on a
+    competition-wide scoring for the application track)
+  \item Best unsat-core track solver (awarded based on a
+    competition-wide scoring for the unsat-core track)
+  \item Best complementary solver (awarded to the solver that performs
+    best when all benchmarks solved by the winning solver are removed)
+  \item Most unique solver (awarded to the solver that performs best
+    on benchmarks solved by only one solver)
+  \item The Prophet (awarded to the solver that performs best on
+    benchmarks with unknown status)
+  \item The 10 Second Wonder (awarded to the solver that would have
+    won if the time limit was 10 seconds)
   \end{itemize}
-\rem{Aina: Are we going to introduce an experimental strings divisions?}
+  The details are still being discussed and subject to change.
+\item In the unsat-core track, the unsatisfiability check for the
+  returned core will be based on a simple majority vote.  The case
+  that a solver finds its own core satisfiable will no longer be
+  treated specially.  \emph{Rationale:} This allows to simplify the
+  post-processing of unsat-core track results considerably.
+
+\item In 2017, the competition featured experimental divisions for
+  benchmarks that use algebraic datatypes.  Provided the competition
+  tools can be enhanced in time to support datatypes, these divisions
+  may become regular (non-experimental) in 2018. \emph{Rationale:}
+  Algebraic datatypes are specified in the latest official release
+  (Version~2.6) of the SMT-LIB standard.
+
+\item The competition may feature experimental divisions for
+  benchmarks that use strings, and for benchmarks that use
+  transcendental functions.  \emph{Rationale:} Corresponding theories
+  and benchmarks are expected to be added to SMT-LIB in the near
+  future.
+\end{itemize}
 
@@
 \begin{center}
-  \rem{TODO, this is still the old link: https://goo.gl/forms/HL6rbOywqW4sFo1D2}
-  {\tt TBA}
+  \rem{{\tt TBA}}
 \end{center}
@@
 purposes).
-\rem{Aina: I strongly suggest that we make disagreements visible.  I
-  would add a table to the bottom of the division results page, where
-  we list the benchmarks we removed due to disagreements and which
-  results which solvers reported. Silently dropping benchmarks on
-  which solvers disagree is potentially unfair and dangerous, since
-  people who want to use a solver, tend to only look at the SMT-COMP
-  results and pick a solver based on this results.  They will
-  certainly not go through the competition results on StarExec, in
-  particular since this is quite tedious.  For users it is interesting
-  (and might be actually crucial) to know if a solver disagreed with
-  other solvers.  The same is true for solver developers, since they
-  certainly want to know if their solver disagreed with other solvers
-  on a certain benchmark.  They usually run preliminary tests with
-  existing solvers beforehand, but not all solvers are available in
-  the newest version.  Not to mention new solvers.}
 
@@
 
-\rem{Aina: Do we already know how many medals FLOC is going to sponsor?
-Clark offered to pay for printing proper and beautiful certificates for each
-division if we don't have funds for that.
-As for medals, it might be a little late to get sponsors (and the funds
-from SMT-LIB went to the travel fund).}
-
-\rem{Aina: Depending on the number of medals we get from FLOC we should
-decide on how to categorize for prizes. Some ideas:
-\begin{itemize}
-  \item Competition-wide, main track, best solver
-  \item Quantified divisions, best solver
-  \item Either QF\_BV best solver, or QF\_BV + QF\_ABV + QF\_AUFBV + QF\_UFBV
-  \item Competition-wide, application track, best solver
-  \item Competition-wide, unsat-core track, best solver
-  \item Best newcomer
-\end{itemize}
-Floating-point is currently only officially supported by Z3,
-inofficially also by CVC4, if we expect more than 2 entrants, then FP logics
-would also be a candidate.
-}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 Giles Reger is associated with the group
-producing the Vampire system\rem{TODO for Giles: cite Vampire}~\cite{vampire}.
+producing the Vampire system~\cite{vampire}.
 

### 2018-04-19 rules/rules18.tex
More detailed discussion of time limit

@@
   The details are still being discussed and subject to change.
+
+\item The time limit per solver/benchmark pair is anticipated to be at
+  most 20 minutes in the main track, and at most 40 minutes in the
+  other tracks.  \emph{Rationale:} Already in 2017, the time limit for
+  the main track was reduced to 20 minutes (down from 40 minutes in
+  earlier years) to cope with the inclusion of a large number of
+  benchmarks with unknown status.
+
 \item In the unsat-core track, the unsatisfiability check for the
@@
 %
-A \emph{wrapper tool} is defined as any solver which calls (or is in
+A \emph{wrapper tool} is defined as any solver that calls (or is in
 some other way based on) one or more SMT solvers not written by the
@@
 
-The time limit~$T$ is yet to be determined, but it is anticipated to
-be at most 20~minutes of wall-clock time per solver/benchmark
-pair.\footnote{The time limit may be adjusted once we know the number
-  of competition entrants and eligible benchmarks.}  Solvers that take
-more than this time limit will be killed.  Solvers are allowed to
-spawn other processes; these will be killed at approximately the same
-time as the first started process.
+The time limit~$T$ is yet to be determined.  It is anticipated to be
+at most 20~minutes of wall-clock time per solver/benchmark pair in the
+main track, and at most 40~minutes in the other tracks.\footnote{The
+  time limit may be adjusted once we know the number of competition
+  entrants and eligible benchmarks.}  Solvers that take more than this
+time limit will be killed.  Solvers are allowed to spawn other
+processes; these will be killed at approximately the same time as the
+first started process.
 

### 2018-07-12 tools/results-processing/up.sh
update compute_app_html and compute_ucore_html scripts

@@ -46,7 +46,7 @@ wall=1200
 #echo "Main track"
 #./competition $dt $wall
 #echo "App track"
-#./compute_app_html $dt $wall
+./compute_app_html $dt $wall
 #echo "Ucore track"
 ./compute_ucore_html $dt $wall
 #echo "Exp track"

### 2018-07-14 rules/rules18.tex
Minor clarification: named terms are not used
Add link to solver submission form
Update rules (after the fact, for future reference)

@@
 }
-
-\newcommand{\rem}[1]{\textcolor{red}{[#1]}}
 
@@
 \begin{itemize}
-\item The organizers plan to recognize additional special
-  contributions.  These might include:
-  \begin{itemize}
-  \item Best application track solver (awarded based on a
-    competition-wide scoring for the application track)
-  \item Best unsat-core track solver (awarded based on a
-    competition-wide scoring for the unsat-core track)
-  \item Best complementary solver (awarded to the solver that performs
-    best when all benchmarks solved by the winning solver are removed)
-  \item Most unique solver (awarded to the solver that performs best
-    on benchmarks solved by only one solver)
-  \item The Prophet (awarded to the solver that performs best on
-    benchmarks with unknown status)
-  \item The 10 Second Wonder (awarded to the solver that would have
-    won if the time limit was 10 seconds)
-  \end{itemize}
-  The details are still being discussed and subject to change.
-
 \item The time limit per solver/benchmark pair is anticipated to be at
@@
 \item In 2017, the competition featured experimental divisions for
-  benchmarks that use algebraic datatypes.  Provided the competition
-  tools can be enhanced in time to support datatypes, these divisions
-  may become regular (non-experimental) in 2018. \emph{Rationale:}
-  Algebraic datatypes are specified in the latest official release
-  (Version~2.6) of the SMT-LIB standard.
+  benchmarks that use algebraic datatypes.  These divisions will be
+  regular (non-experimental) in 2018. \emph{Rationale:} Algebraic
+  datatypes are specified in the latest official release (Version~2.6)
+  of the SMT-LIB standard.
 
-\item The competition may feature experimental divisions for
-  benchmarks that use strings, and for benchmarks that use
-  transcendental functions.  \emph{Rationale:} Corresponding theories
-  and benchmarks are expected to be added to SMT-LIB in the near
-  future.
+\item The competition will feature an experimental divisions for
+  benchmarks that use strings.  \emph{Rationale:} Corresponding
+  theories and benchmarks are expected to be added to SMT-LIB in the
+  near future.
 \end{itemize}
@@
 \begin{center}
-  \rem{{\tt TBA}}
+  \url{https://goo.gl/forms/3pAMFHsfDJqGqucR2}
 \end{center}
@@
   \begin{enumerate}
-    \item In the main and application track, named formulas are not
-      used.
+    \item In the main and application track, named terms (i.e., terms
+      with the \akey{:named} attribute) are not used.
     \item In the unsat core track, top-level assertions may be named.
@@
 
+As part of the FLoC Olympic Games, Kurt G{\"o}del medals will be
+awarded to:
+%
+\begin{itemize}
+\item The best three solvers according to the competition-wide scoring
+  (main track);
+\item the solver that wins the most competitive divisions in the
+  application track;
+\item the solver that wins the most competitive divisions in the
+  unsat-core track;
+\item the solver that wins the QF\_BV division (separately for
+  parallel and sequential performance) in the main track.
+\end{itemize}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2018-09-17 2018/report/SMT-COMP.tex
Add JSAT style

--- 2016-01-11 2014/report/SMTCOMP.tex
@@
-%% Based on a TeXnicCenter-Template by Tino Weinkauf.
-
-%%\documentclass[12pt,oneside]{report}
 \documentclass[twoside,11pt]{article}
 
-\sloppy
+\usepackage{jsat}
+\usepackage{amsmath, amsthm, amssymb}
+%\usepackage[pdf]{pstricks}
+%\usepackage{pst-tree}
 
-%% Language %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\usepackage[USenglish]{babel} %francais, polish, spanish, ...
-\usepackage[T1]{fontenc}
-%\usepackage{textcomp}
-%\usepackage[ansinew]{inputenc}
-%\usepackage{makeidx}	  %% needed to create an index
-\usepackage{jsat}
-\usepackage{here}
-\usepackage{hyperref}   %% sets hyperlinks within a pdf
-\usepackage{graphicx}
-\usepackage{epstopdf}
-\usepackage{parskip}
-\usepackage{subcaption}
-\usepackage{enumitem}
-\usepackage{xcolor}
-\usepackage{rotating}
-\usepackage{pbox}
-\usepackage{listings}
-\lstdefinelanguage{smtlib2}
-  {alsoletter={-, =},
-   morekeywords={set-logic,declare-fun,assert,check-sat,set-info},
-   sensitive=false,
-   morecomment=[l]{;}}
-\lstset{language=smtlib2,
-basicstyle=\small\sffamily,
-numbers=none,
-keywordstyle=\small\bfseries\sffamily,
-keywordstyle={[2]\small\bfseries\sffamily\underbar}
-}
-\usepackage{pifont}
-%%\usepackage{lmodern} %Type1-font for non-english texts and characters
+%\input epsf
+\special{papersize=8.5in,11in}
 
-%% Packages for Graphics & Figures %%%%%%%%%%%%%%%%%%%%%%%%%%
-%\usepackage{graphicx} %%For loading graphic files
-%\usepackage{subfig} %%Subfigures inside a figure
-%\usepackage{tikz} %%Generate vector graphics from within LaTeX
-
-%\usepackage{mathptmx} %% Times fonts, for math as well
-
-\newcommand{\comment}[2]{\begin{quote}\sc #1\marginpar{\textcolor{red}{$\ast^{\mbox{#2}}$}}\end{quote}}
-
-\newcommand{\tjark}[1]{\comment{#1}{TW}}
-\newcommand{\davidd}[1]{\comment{#1}{DD}}
-\newcommand{\davidc}[1]{\comment{#1}{DC}}
-
-\newcommand{\rot}[1]{\begin{turn}{90}#1\end{turn}}
-
-\jsatheading{number}{year}{startpage-endpage}
-\ShortHeadings{The 2014 SMT Competition}{D.\ Cok et al.}
-\firstpageno{1}
+\jsatheading{1}{2004}{25-30}
+\ShortHeadings{The SMT Competition 2015--2018}
+{TODO et al.}
+\firstpageno{25}
 
@@
 
-\title{The 2014 SMT Competition}
+\title{The SMT Competition 2015--2018}
 
-\author{\name{David R. Cok (chair of organizing committee)}
-\email{dcok@grammatech.com} \\
-\addr GrammaTech, Inc. \\
+\author{\name{Sylvain Conchon (co-organizer, 2015--2016)}
+\email{Sylvain.Conchon@lri.fr} \\
+\addr Affiliation \\
+City \\
+Country
 \AND
-\name{David D\'{e}harbe (co-organizer)}
+\name{David D\'{e}harbe (co-organizer, 2015--2016)}
 \email{david@dimap.ufrn.br} \\
-\addr Federal University of Rio Grande do Norte, Brazil \\
+\addr Federal University of Rio Grande do Norte \\
+Natal \\
+Brazil
 \AND
-\name{Tjark Weber (co-organizer)}
+\name{Matthias Heizmann (co-organizer, 2016--2018)}
+\email{heizmann@informatik.uni-freiburg.de} \\
+\addr Affiliation \\
+City \\
+Country
+\AND
+\name{Aina Niemetz (co-organizer, 2018)}
+\email{niemetz@cs.stanford.edu} \\
+\addr Affiliation \\
+City \\
+Country
+\AND
+\name{Giles Reger (co-organizer, 2017--2018)}
+\email{giles.reger@manchester.ac.uk} \\
+\addr Affiliation \\
+City \\
+Country
+\AND
+\name{Tjark Weber (competition chair, 2015--2018)}
 \email{tjark.weber@it.uu.se} \\
-\addr Uppsala University, Sweden}
+\addr Uppsala University \\
+Uppsala \\
+Sweden}
 
@@
 \begin{abstract}
-The 2014 SMT Competition was held in conjunction with the SMT Workshop, affiliated with the CAV, IJCAR, and SAT conferences at FLoC 2014, at the Vienna Summer of Logic in July 2014.
-Eighteen solvers participated from thirteen different research groups, across 34 different logic divisions.
-The competition was also part of the FLoC Olympic Games event, which gave combined visibility to 14 different competitions related to automated logic problem solving.
-The 2014 edition of the SMT Competition was executed for the first time on the StarExec logic solving service.
-Several records were broken: number of participating solvers, number of new entrants, number of logic divisions, number of benchmarks, and amount of computation.
-The detailed performance of each solver on each benchmark from this first year using StarExec will be a solid baseline to measure improvements in the state-of-the-art of solver performance in future years.
+TODO
 \end{abstract}
@@
 
-%\published{December 2014}{revision date}{publication date}
-
-%\davidc{Material to include, from the call: Full articles by competition organizers reporting on SAT-related competitions
-  %within FLoC Olympic Games 2014. The articles should describe the competition,
-  %its criteria, why it is interesting to the SAT research community, execution
-  %environment used, analysis of the results (including how they compare to
-  %previous instantiations, if appropriate), and give a summary of the main
-  %technical contributions to the field, as well as discussions on lessons
-  %learned and suggestions for improvements for future competitions. }
+\published{September 2004}{October 2004}{November 2004}
 
@@
 
-The SAT decision problem can be generalized by replacing
-Boolean variables with atomic predicates built with symbols from a
-background theory, or a combination of background theories. The
-resulting decision problem is called \emph{Satisfiability Modulo
-  Theories}~\cite{DBLP:conf/jelia/Tinelli02}. The background theories of interest arise from
-	application domains, such as formal verification or scheduling problems, and include arrays,
-bit-vectors, equality with uninterpreted functions, linear and
-non-linear arithmetics over integers and real numbers. Also, a theory
-may explicitly allow or disallow quantification. Tools addressing the
-SMT problem are called \emph{SMT solvers\/}. An SMT solver is often
-built by combining a SAT solver with (semi-)decision procedures for
-specific theories.
-
-The 2014 SMT Competition (SMT-COMP) continued the series of annual competitions in SMT solver capability and performance that began in 2005.
-This is the 9th competition in the series, skipping only 2013; in that year an evaluation~\cite{it:2014-017} was performed, rather than a competition.\footnote{The evaluation did not measure solvers against each other, as in a competition.
-Rather it assessed concerns such as how the design of the competition (e.g., random choice of benchmarks) affects the outcome, the variety and distribution of benchmarks, and the extent to which the competition is dominated by single solvers or by a few solvers or is broadly competitive.}
-
-The competition is held to spur advances in
-SMT solver implementations acting on benchmark formulas of practical interest. Public competitions are
-a well-known means of stimulating advancement in software tools. For example, in automated
-reasoning, the SAT and CASC competitions for propositional and first-order reasoning tools, respectively,
-have spurred significant innovation in their fields~\cite{satwebsite,jarvisalo2012international,leberre+03,PSS02}.
-
-The competition is sponsored by the SMT Workshop, which was held in conjunction with the
-CAV, IJCAR, and SAT conferences at FLoC 2014~\cite{FLoC2014}, at the Vienna Summer of Logic~\cite{VSL} in July 2014.
-Information about the winners
-and results of the competition is summarized in this report and is available online at \url{www.smtcomp.org}.  Information
-about previous years' competitions is also available at that website and in published summary reports~\cite{springerlink:10.1007/s10817-012-9246-5,DBLP:conf/cade/CokGBD12,it:2014-017}.
-
-In the succeeding sections we describe 
-the competition goals (\S\ref{sec:goals}), 
-the SMT-LIB language that is the basis for the competition (\S\ref{sec:context}), 
-the competition benchmarks (\S\ref{sec:benchmarks}), 
-participants~(\S\ref{sec:participants}), 
-procedure (\S\ref{sec:procedure}),
-computational infrastructure (\S\ref{sec:starexec}), 
-comparisons with other competitions~(\S\ref{sec:OtherCompetitions}), 
-the results (\S\ref{sec:results}), 
-the place of SMT-COMP in the FLoC Olympic Games (\S\ref{sec:floc}), 
-and post-competition activities (\S\ref{sec:post}). 
-Section \ref{sec:conclusions} presents observations on this competition and recommendations for the future.
-
 \section{The Competition Goals and Organization}
 \label{sec:goals}
-
-In planning the 2014 competition, the organizers' overall goal was to encourage breadth in the capability of SMT solvers.
-SMT-COMP 2014 benefited from the evaluation that was performed in 2013 and the experience of previous competitions.
-As a result we established the following emphases.
-Note that, as described in later sections, the competition is divided into a number of divisions, each focuses on a given logic, and each has its own set of benchmark problems and solvers.
-\begin{itemize}
-\item In 2012 the competition was narrowed to a smaller number of more significant logics.
-In response to feedback, in 2014 we reverted to the practice of evaluating solvers in all available divisions.
-\item A significant result of the 2013 Evaluation was that the results of previous competitions were highly sensitive to the selection of benchmarks: different random selections of benchmarks resulted in different winning orders in a large fraction of samples.
-Hence, an aim for 2014 was to use as large a benchmark set as possible in the competition to minimize this effect.
-We were able to run the competition with all eligible benchmarks.
-This point is discussed further in~\S\ref{sec:benchmark-selection}.
-\item In 2012 some experimental tracks were held: parallel performance, unsat cores, and proof generation.
-The participation in those tracks was light.
-Since in 2014 we also had to migrate to using the new StarExec cluster to execute the competition, we held only a main track and an application (incremental) track in the 2014 competition.
-The organizers still appreciate the value of measuring the performance of solvers on new features such as parallel processing, model generation, unsat core determination, and proof generation, and recommend that these tracks be reinstated in some future edition of the competition.
-\item An additional goal was to be able to evaluate the effect of the timeout setting on the competition.
-Thus a change in 2014 was to increase the timeout limit for a solver processing a given benchmark from 25 minutes (in 2012) to 40 minutes (see \S\ref{sec:procedure} for details on the competition parameters and \S\ref{sec:timeouts} for a discussion on their effects).
-\end{itemize}
-
-An important difference between the 2014 competition and previous competitions was that this year's competition was executed on the StarExec cluster, described below in \S\ref{sec:starexec}.
-All the supporting tools and related procedures needed to be ported to this new framework.
-With watchful eyes by the organizers and the StarExec team, and with some debugging, the StarExec framework worked well and enabled a larger scale of competition than in previous years.
 
@@
 
-The SMT Competition is a competition among SMT solvers on a set of benchmark logic problems.
-Each benchmark problem is a combination of definitions and logical assertions expressed with respect to an underlying logical theory and, perhaps, some constraints on the kinds of expressions in that theory.
-For example,  the logic of linear arithmetic includes the multiplication operation, but only allows multiplication by constants.
-Each problem is a set of closed formulas (possibly including quantification over variables) over a set of constant or function symbols; a solution to the problem is an assignment of each constant and function evaluation to values in a way that satisfies all the problem's assertions.
-That is, the task is to find a \emph{satisfying assignment} for the benchmark problem or to determine that there is no such assignment.
-Since the presence of quantified expressions introduces incompleteness, solvers may also produce a potential solution that may be marked as possibly spurious.
-
-As stated, the goal of SMT-COMP is similar to the goal of the SAT competition.
-The SMT logic extends SAT by incorporating defined theories, such as the theory of arrays, or of uninterpreted functions, or of arithmetic, or of bit-vectors.
-In addition, there may be constraints on the set of expressions allowed, such as only linear arithmetic, or only integer difference arithmetic.
-The theories also define \emph{sorts}, which make the theories a typed first-order logic.
-Examples of sorts used in current theories are Boolean, Int, Real, bit-vectors of various lengths, and arrays with arbitrary sorts as index and value.
-Each combination of underlying theories and language constraints is a \emph{logic}.
-The names of the logics as used in SMT-LIB are combinations of initials. For example, AUFLIA is the logic with a
-combination of Arrays (A), Uninterpreted Functions (UF), and linear integer arithmetic (LIA). Table \ref{logicAbbreviations} can be used to interpret these names.
-\begin{table}
-\begin{center}
-\begin{tabular}{|l|l|}
-\hline
-QF\_ & Quantifier-Free \\
-A & Arrays \\
-UF & Uninterpreted Functions \\
-BV & Bit-Vector \\
-L & Linear (arithmetic) \\
-N & Non-Linear (arithmetic) \\
-IA/RA/IRA & Integer/Real/Mixed arithmetic \\
-IDL/RDL & Integer/Real Difference Logic \\
-\hline
-\end{tabular}
-\end{center}
-\caption{Abbreviations used in logic names}
-\label{logicAbbreviations}
-\end{table}
-
-A competition based on benchmark problems needs a standard language in which to express those problems.
-For SMT-COMP, that language is the SMT-LIB language (cf.~\url{http://www.smtlib.org}) \cite{BarST-RR-10,BarST-SMT-10,Cok-SMTLIBTutorial-2011}.
-In 2010, a significantly reworked version of the language was agreed upon.
-This version~2 increased the flexibility and expressiveness of the language while also simplifying the syntax.
-It also includes a command language that improves the language's usefulness for interactive applications.
-In particular, the standard specifies a typed (sorted), first-order logical language for terms and formulas, a language for specifying background logical theories and logics, and a command language.
-Some other tools that process SMT-LIB~v2 are listed in the SMT-LIB web pages (cf.
-\url{http://www.smtlib.org/utilities.shtml}).
-Further revisions were discussed at the SMT Workshop 2014.
-One of the goals of the SMT Competition is to encourage use and tool implementations of the SMT-LIB standard.
-
-%However, it is important to note that some tools used in the competition support only a subset of the SMT-LIB command language, leaving out some commands that are essentially syntactic sugar, and are defined as optional in the standard to simplify the burden on competing solvers.
-This subset is only informally stated and has been stable since 2010.
-Moreover, the benchmarks only use this subset.
-This informality did not cause problems in the competition, but it would be preferable to define this subset explicitly.
-%% [DD] Strictly speaking, these commands are optional and a SMT-LIB
-%% compliant solver needs not implement them. Which is why I commented
-%% out the following sentence 
-%%
-%% Requiring just a subset for competition works against the goal of
-%% producing SMT-LIB-compliant solvers for users.  Fortunately, most
-%% mature solvers have implemented nearly all commands of SMT-LIB.
-Optional features such as incrementality, proof production, and determining unsat cores are evaluated in specialized tracks, separate from the main competition.
-The presence of such tracks in the competition has varied from year to year.
-
-The following example illustrates part of the language's concrete syntax:
-
-\begin{minipage}{\textwidth}
-\begin{quote}
-\lstset{frameround=fttt}
-\begin{lstlisting}[frame=trBL]
-(set-logic UFLIA)
-(declare-fun max (Int Int) Int)
-(assert (forall ((x Int) (y Int))
-   (let ((m (max x y)))
-      (and (>= m x) (>= m y) (or (= m x) (= m y))))))
-(assert (not (forall ((x Int) (y Int))
-   (let ((m (max x y)))
-      (= (max m x) m)))))
-(check-sat)
-\end{lstlisting}
-\end{quote}
-\end{minipage}
-
-Commands to the SMT solver are typeset in bold here.  The command
-\lstinline{set-logic} sets the background theory: \lstinline{UFLIA} is
-the combination of equality with uninterpreted
-functions~(\lstinline{UF}) and linear integer
-arithmetic~(\lstinline{LIA}). Next, the command
-\lstinline{declare-fun} introduces a function symbol, named
-\lstinline{max}, which has two arguments of sort \lstinline{Int} and
-returns an \lstinline{Int} value. Next, two formulas are asserted. The
-first essentially restricts the interpretation of the function named
-\lstinline{max} to the standard interpretation. The second expresses
-the negation of a property of this operator. The command
-\lstinline{check-sat} instructs the SMT solver to check if the
-conjunction of the assertions is satisfiable. Here the expected result
-is \lstinline{unsat}, indicating that the combination of the two
-assertions is unsatisfiable and so, equivalently, the desired property
-is valid, given the first assertion.
-
-SMT \textit{solvers} are automated tools that seek a satisfying assignment for a given SMT-LIB problem, or assure that the problem is \emph{unsatisfiable}.
-Tools may not be able to solve a given problem, because, for example the tool exhausts available memory or time; a tool is permitted to answer \emph{unknown}.
-However, giving an incorrect answer (\emph{sat} instead of \emph{unsat}, or vice versa) is considered \emph{unsound} and a serious fault in the tool.
-
 \section{Competition Divisions and Benchmarks}
 \label{sec:benchmarks}
-
-The SMT-LIB benchmarks each belong to a specific logic.
-Each logic is one competition division.
-For each division, we ran the solvers that entered that division on the benchmarks for that division as one event in the overall competition.
-
-As of June 2014, the SMT-LIB repository contained over 130,000
-main-track benchmarks divided into 34 background theories, and
-close to 10,000 incremental benchmarks distributed across 8 background
-theories. The size of a benchmark file may vary from a few hundred
-bytes to several gigabytes. Fig.~\ref{fig:smtlib-bysize} shows the
-distribution of the benchmarks by file size.
-
-\begin{figure}
-\begin{center}
-\begin{tabular}{cc}
-\includegraphics[width=.47\textwidth]{smtlib2-file-count-by-size.png}
-&
-\includegraphics[width=.47\textwidth]{smtlib2-app-file-count-by-size.png}
-\\
-\\
-Non-incremental benchmarks & Incremental benchmarks
-\end{tabular}
-\end{center}
-\caption{Distribution of SMT-LIB benchmarks by file size.
-\label{fig:smtlib-bysize}}
-\end{figure}
-
-A sizeable number of benchmarks, on the order of 30,000, were added during the lead up to the competition.
-Some of these were submitted in previous years but never assessed and uploaded.
-Many others were supplied by solver developers (including some competitors).
-All of them went through an iterative curation process to be sure that they were syntactically valid, appropriate metadata was included, and a correct result was established.
-(Not all of these submissions were through the competition organizers.)
-
-The SMT-LIB coordinators performed a curation step on the entire benchmark library prior to the competition, determining the actual logic to which a benchmark belonged, rather than the super-logic to which it had previously been assigned.
-This resulted in an expansion of logics with benchmarks from 23 to 34, and also created a number of divisions with only a very few benchmarks.
-Two divisions were not held because they had no eligible benchmarks.
-
-The 34 logics are shown in Table \ref{Table:benchmarks}.
-The rightmost column shows the number of benchmarks for that logic in the SMT-LIB collection.
-Two considerations may make a benchmark ineligible for a competition.
-First, the benchmark may not have a known result.
-For newly submitted benchmarks
-we made an attempt to determine the correct result of the benchmark; the SMT-LIB coordinators require that two
-different solvers solve the benchmark and report the same result.
-However, for benchmarks with unknown results already in the collection we did not have time to determine their results.
-We did do this analysis after the competition was over (see~\S\ref{sec:post}).
-
-The second consideration is that the benchmark must be \emph{non-trivial}; a benchmark is deemed trivial if all solvers managed to solve it in less than five seconds during SMT-EVAL 2013.
-
-The numbers of unknown, trivial, and remaining eligible benchmarks are shown in Table~\ref{Table:benchmarks}.
-Note that these numbers vary widely from division to division.
-As we discuss in Section~\ref{sec:benchmark-selection} below, all eligible benchmarks were actually used in the competition; these numbers are shown in bold.
-
-\begin{table}
-\caption{Numbers of main-track benchmarks.
-The second column shows the number of competitive solvers and, in square brackets, the number of demonstration-only solvers.
-Entries marked * exclude some benchmarks containing partial functions.}
-\label{Table:benchmarks}
-\centering
-\begin{tabular}{|l|r|r|r|r|r|}
-\hline
-       & \multicolumn{1}{|c|}{\# of} & \multicolumn{4}{|c|}{\# of benchmarks} \\
- Logic & solvers & {\bf eligible} & unknown  & trivial & total  \\
-\hline
-ALIA & 3+[1] & {\bf 29} & 0 & 13 & 42 \\
-AUFLIA & 3+[1] & {\bf 4} & 0 & 0 & 4\\
-AUFLIRA & 3+[1] & {\bf 10791} & 168 & 9055 & 20014 \\
-AUFNIRA & 2+[2] & {\bf 564} & 468 & 463 & 1495 \\
-BV & 2+[1] & {\bf 0} & 191 & 0 & 191 \\
-LIA & 3+[1] & {\bf 46} & 0 & 0 & 46 \\
-LRA & 3+[1] & {\bf 171} & 450 & 0 & 621\\
-NIA & 2+[1] & {\bf 9} & 0 & 0 & 9\\
-NRA & 2+[1] & {\bf 3747} & 66 & 0 & 3813 \\
-QF\_ABV & 7+[2] & {\bf 6457}* & 4191 & 4423 & 15091 \\
-QF\_ALIA & 3+[2] & {\bf 97} & 0 & 29 & 126 \\
-QF\_AUFBV & 2+[2] & {\bf 37} & 0 & 0 & 37 \\
-QF\_AUFLIA & 4+[2] & {\bf 610} & 0 & 399 & 1009\\
-QF\_AX & 3+[2] & {\bf 335} & 0 & 216 & 551 \\
-QF\_BV & 8+[3] & {\bf 2488}* & 28138 & 546 & 32500 \\
-QF\_IDL & 3+[1] & {\bf 1315} & 537 & 337 & 2189 \\
-QF\_LIA & 4+[3] & {\bf 4381} & 1279 & 481 & 6141 \\
-QF\_LRA & 4+[2] & {\bf 1343} & 208 & 131 & 1682\\
-QF\_NIA & 3+[1] & {\bf 8327} & 927 & 105 & 9359 \\
-QF\_NRA & 3+[1] & {\bf 10121} & 1392 & 27 & 11540 \\
-QF\_RDL & 3+[1] & {\bf 132} & 85 & 38 & 255 \\
-QF\_UF & 5+[2] & {\bf 4124} & 4 & 2522 & 6650 \\
-QF\_UFBV & 2+[2] & {\bf 31} & 0 & 0 & 31 \\
-QF\_UFIDL & 3+[1] & {\bf 311} & 0 & 130 & 441\\
-QF\_UFLIA & 4+[2] & {\bf 484} & 0 & 114 & 598 \\
-QF\_UFLRA & 4+[2] & {\bf 1176} & 87 & 367 & 1630 \\
-QF\_UFNIA & 2+[1] & {\bf 7} & 0 &0 & 7 \\
-QF\_UFNRA & 2+[1] & {\bf 32} & 11 & 0 & 43\\
-UF & 3+[1] & {\bf 2830} & 2911 & 7 & 5748 \\
-UFBV & 2+[1] & {\bf 0} & 191 & 0 & 191 \\
-UFIDL & 2+[1] & {\bf 49} & 12 & 19 & 80 \\
-UFLIA & 3+[1] & {\bf 5766} & 5499 & 873 & 12138 \\
-UFLRA & 3+[1] & {\bf 25} & 0 & 0 & 25\\
-UFNIA & 2+[1] & {\bf 1587} & 1052 & 712 & 3351 \\
-\hline
-Total & 18+[3] & {\bf 67426} & 47867 & 21007 & 137648 \\
-\hline
-\end{tabular}
-\end{table}
-
-Solvers could participate in any or all divisions at their team's discretion.
-Most solvers are designed for just one selected logic, but others are intended to be as broadly applicable as their developers have had time to implement.
-Table~\ref{Table:logics} shows the participation of solvers in various divisions.
-
-\begin{sidewaystable}
-\caption{Solver participation in logic divisions}
-\label{Table:logics}
-\centering
-\renewcommand{\mark}[0]{\ding{51}}
-%%\small
-\setlength\tabcolsep{2.9pt}
-%%\begin{tabular}{|l|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|}
-\begin{tabular}{|l|ccccc|cccc|cccccc|cccccc|ccccccc|cccccc|}
-\hline
-Solver & 	\rot{ALIA} & 	\rot{AUFLIA} & 	\rot{AUFLIRA} & 	\rot{AUFNIRA} & 	\rot{BV} & 	\rot{LIA} & 	\rot{LRA} & 	\rot{NIA} & 	\rot{NRA} & 	\rot{QF\_ABV} & 	\rot{QF\_ALIA} & 	\rot{QF\_AUFBV} & 	\rot{QF\_AUFLIA} & 	\rot{QF\_AX} & 	\rot{QF\_BV} & 	\rot{QF\_IDL} & 	\rot{QF\_LIA} & 	\rot{QF\_LRA} & 	\rot{QF\_NIA} & 	\rot{QF\_NRA} & 	\rot{QF\_RDL} & 	\rot{QF\_UF} & 	\rot{QF\_UFBV} & 	\rot{QF\_UFIDL} & 	\rot{QF\_UFLIA} & 	\rot{QF\_UFLRA} & 	\rot{QF\_UFNIA} & 	\rot{QF\_UFNRA} & 	\rot{UF} & 	\rot{UFBV} & 	\rot{UFIDL} & 	\rot{UFLIA} & 	\rot{UFLRA} & 	\rot{UFNIA} \\
-\hline
-4Simp & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	\mark & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 \\
-Abziz & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	\mark & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 \\
-Abziz2 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	\mark & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 \\
-AProVE & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	\mark & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 \\
-Boolector & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	\mark & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 \\
-Boolector-d & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	\mark & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 \\
-Boolector-j & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	\mark & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 \\
-CVC3 & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	\mark & 	\mark & 	 & 	 & 	 & 	 & 	 & 	 & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark \\
-CVC4 & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark \\
-Kleaver-STP & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	\mark & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 \\
-Kleaver-portfolio & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	\mark & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 \\
-OpenSMT2 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	\mark & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 \\
-raSAT & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	\mark & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 \\
-SMTInterpol & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	\mark & 	&	\mark & 	\mark & 	 & 	 & 	\mark & 	\mark & 	 & 	 & 	 & 	\mark & 	 & 	 & 	\mark & 	\mark & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 \\
-SONOLAR & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	\mark & 	 & 	 & 	 & 	 & 	\mark & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 \\
-STP-Crypto... & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	\mark & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 \\
-veriT & 	\mark & 	\mark & 	\mark & 	 & 	 & 	\mark & 	\mark & 	 & 	 & 	 & 	 & 	 & 	\mark & 	& &		\mark & 	\mark & 	\mark & 	 & 	 & 	\mark & 	\mark & 	&	\mark & 	\mark & 	\mark & 	 & 	 & 	\mark & 	 & 	 & 	\mark & 	\mark &   \\
-Yices2 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	 & 	 & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 \\
-\hline
-{[}MathSAT5] & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	 & 	\mark & 	\mark & 	 & 	 & 	 & 	\mark & 	\mark & 	 & 	\mark & 	\mark & 	 & 	 & 	 & 	 & 	 & 	 & 	 & 	 \\
-{[}Z3] & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark & 	\mark \\
-{[}CVC4-with-bugfix] &  &  &  & \mark &  &  &  &  &  &  &  &  &  &  & \mark &  & \mark &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  \\
-\hline
-\end{tabular}
-\end{sidewaystable}
-
-\subsection{Application benchmarks}
-
-The language includes commands that allow a fine-grained interaction
-with the solver, whereby client tools may incrementally push and pop
-symbol declarations and assertions while running various
-satisfiability checks, inspecting models, or obtaining unsatisfiability
-proofs. Benchmark problems that have more than one
-\lstinline{check-sat} command are called \emph{application} or \emph{incremental
-  benchmarks}. Not all SMT solvers support all of these interaction
-facilities, and the main track of the competition does not use such
-application benchmarks.
-
-\subsection{Selection of benchmarks}
-\label{sec:benchmark-selection}
-
-Due to the mismatch between the amount of available compute time and the number of jobs to run, benchmark selection has been an historical issue for SMT-COMP.
-In addition to whether a benchmark has a known result or is trivial, the SMT-COMP organizers chose two other factors that affect the selection of benchmarks for SMT-COMP: the benchmark's difficulty and the desire for a distribution of problems.
-In 2014, the amount of available CPU time was enough to process all benchmarks on all solvers within the timeout defined in the rules.
-However this could not be anticipated, and the issues described hereafter may happen again, e.g., in case the number or difficulty of benchmarks, number of solvers, or the timeout increase significantly, or the organizers wish to compress the time-frame in which the competition is executed.
-
-Each benchmark is assigned a \emph{difficulty rating}; in 2014, we used the time taken to solve the benchmark by the best performing solver in the 2013 SMT Evaluation.
-These values were publicly available prior to the competition.
-The difficulty ratings are used to divide the benchmarks into 5 quintiles.
-The rules describe a procedure for randomly selecting $N$ out of the eligible benchmarks for a division, with the intent of selecting roughly equal numbers, if they are available, from each of the quintiles.
-The seed for the random number generator used for selection is obtained by summing a number supplied by each solver team and the integer portion of the New York Stock Exchange Composite Index at its opening on the day the competition begins.
-
-Benchmarks are also labeled by \emph{category} (not shown in the tables): simple checks, randomly generated problems from some template (e.g., N-queens problems for various values of N), problems crafted to test a certain capability, and problems obtained from industrial applications.
-The selection rules in previous years favored industrial benchmarks.
-
-Another selection criterion, though not used historically, is to balance the numbers of \textit{sat} and \textit{unsat} benchmarks.
-
-In addition, some kinds of problems may be over-represented in the benchmarks.
-This may be the case particularly because benchmarks may be submitted by solver developers; a team might add a large number of benchmarks that would then over-represent problems that a particular solver is known to handle well.
-The rules allow the organizers to limit the selections from sub-populations.
-
-In the end, in 2014, there was sufficient time to use all eligible benchmarks and no further selection was performed.
-The 2014 organizers did not have the data to make a principled decision on over-representation of particular problem types and so did not select on this basis either.
-The absence of such selection may have affected the competition results and future organizing teams should reconsider this aspect even if there are sufficient computational resources to execute all benchmarks.
-The data from SMT-COMP 2014 could be used to inform this decision.
 
@@
 
-The competition registration requires participants to submit information about each competing solver.
-In addition, some solver groups provided summaries of their solvers and their recent technical advances.
- Note that although one person is listed as the ``submitter,'' there is generally a team of contributors behind each tool.
-Some teams submitted more than one tool.
-The 2014 participants were the following:
-\begin{itemize}
-\item 4Simp -- submitted by Trevor Hansen (U. Melbourne)
-\item AbzizPortfolio -- two versions -- submitted by Mohammed Adbul Aziz (U.
-Cairo).
-This solver is atypical in that it is a portfolio solver: based on automated learning over benchmark characteristics, it chooses among other solvers to apply to the problem at hand.
-\item AProVe~\cite{AProVE2014} -- submitted by Carsten Fuhs (University College London)
-\item Boolector~\cite{Boolector2015} -- three versions: Boolector (default),  Boolector-d (dual propagation), Boolector-j (justification) -- submitted by Armin Biere, Aina Niemetz, Mathias Preiner (Johnnes Kepler University)
-\item CVC3 v. 2.4.3~\cite{BT07} -- submitted by Morgan Deters (New York University)
-\item CVC4 v. 1.4~\cite{BCD+11} -- submitted by the ACSys Group (New York University)
-\item Kleaver -- 2 versions -- submitted by Hristina Palikareva, Cristian Cadar (Imperial College)
-\item OpenSMT2 -- submitted by Antti Hyv\"arinen (U.~Lugano)
-\item raSAT~\cite{DBLP:conf/smt/KhanhVO14} -- submitted by Xuan-Tung Vu (Japan Advanced Insitute of Science and Technology)
-\item SMTInterpol~\cite{DBLP:conf/spin/ChristHN12,DBLP:conf/spin/2012} -- submitted by Jochen Hoenicke, J\"urgen Christ (U.~Freiburg)
-\item SONOLAR~\cite{Peleska:2011:ATC:1986308.1986333} -- submitted by Florian Lapschies (U.~Bremen)
-\item STP-CryptoMiniSat4~\cite{DBLP:conf/cav/GaneshD07,DBLP:conf/cav/2007} -- submitted by Mate Soos (Security Research Lab.), based on previous work by Trevor Hansen (U.~Melbourne) and Vijay Ganesh (Massachusetts Institute of Technology)
-\item veriT~\cite{veriT} -- submitted by David D\'{e}harbe (UFRN - Universidade Federal do Rio Grande do Norte) and Pascal Fontaine (U.~Lorraine, INRIA - Institut national de recherche en informatique et en automatique)
-\item Yices2~\cite{Dutertre:cav2014} -- submitted by Bruno Dutertre (SRI)
-\end{itemize}
-
-There were a few solvers that the organizers hoped would be submitted but were not: Tiffany de Wintermonte was submitted in the past by Trevor Hansen, but could not be prepared in time for this competition; similarly SMT-RAT was withdrawn because of last minute bugs; MathSat has been a frequent competitor in the past, but changes in priorities of the development team caused it not to compete in 2014; MiniSMT also was not able to be submitted; similarly, the Z3 team, from Microsoft Research, though Z3 is a strong tool, has chosen not to take the time to prepare competition versions.
-
-Other than those omissions, every competitive solver known to the organizers was represented.
-Indeed, the participation by solver teams was a record high in 2014.
-In addition, four teams submitting five solvers had not participated in previous competitions.
-
-\begin{table}[H]
-\caption{History of solver participation (numbers in parenthesis indicate
-  the number of versions submitted for the tool). Complete records of early competitions were not available to the 2014 organizers.}
-\label{Table:participants}
-\renewcommand{\mark}[0]{\ding{51}}
-\centering
-\setlength{\tabcolsep}{1pt}
-\scalebox{1}[.984]{\begin{tabular}{|l@{\,\,}l|c|c|c|c|c|c|c|c|c|}
-\hline
-Solver & Affiliation & 2005 & 2006 & 2007 & 2008 & 2009 & 2010 & 2011 & 2012 & 2014 \\
-\hline
-4Simp                  & U. Melbourne 	&   &   &   &   &   &   &   &   & \mark  \\
-AbzizPortfolio         & U. Cairo       &   &   &   &   &   &   &   & \mark & (2)\\
-Alt-Ergo               & U. Paris Sud  &   &   &   & \mark &   &   &   &  &   \\
-AProVE NIA             & RWTH Aachen    &   &   &   &   &   & \mark & \mark &   & \mark \\
-ArgoLib                &   &   &   & \mark &   &   &   &   &  &   \\
-Ario                   &   & \mark & \mark &   &   &   &   &   &  &   \\
-barcelogic             & UPC            & \mark & \mark & \mark & \mark & \mark &   &   &   &   \\
-beaver                 & UC Berkeley   &   &   &   & \mark & \mark &   &   &   &   \\
-Boolector              & JKU            &   &   &   & \mark & \mark &   & \mark & \mark & (3)\\
-clsat                  & Washington U.  &   &   &   & \mark & \mark &   &   &   &   \\
-CVC/CVCLite/CVC3       & NYU, U. Iowa   & \mark & \mark & \mark & \mark & \mark & \mark & \mark & \mark & \mark \\
-CVC4	                 & NYU, U. Iowa   &   &   &   &   &   & \mark & \mark & \mark & \mark \\
-ExtSat                 &   &   & \mark &   &   &   &   &   &  &   \\
-Fx7                    &   &   &   & \mark &   &   &   &   &  &   \\
-HTP                    &   & \mark & \mark &   &   &   &   &   &  &   \\
-Jat                    &   &   & \mark &   &   &   &   &   &  &   \\
-Kleaver	               & Imperial       &   &   &   &   &   &   &   &   & (2) \\
-MathSAT 3,4,5          & U. Trento, FBK & \mark & \mark & \mark & \mark & \mark & \mark & \mark & \mark &   \\
-MathSat-HeavyBV        & U. Trento      &   &   &   &   &   &   &   & \mark &   \\
-MiniSMT                & U. Innsbruck   &   &   &   &   &   & \mark &   &   &   \\
-NuSMV                  & FBK &   & \mark &   &   &   &   &   &  &   \\
-OpenSMT, OpenSMT2      & U. Lugano      &   &   &   & \mark & \mark & \mark & \mark &   & \mark \\
-raSAT  	               & JAIST          &   &   &   &   &   &   &   &   & \mark \\
-Sammy                  &   & \mark &   &   &   &   &   &   &  &   \\
-Sateen                 & U. Col-Boulder & \mark & \mark & \mark & \mark & \mark &   &   &   &   \\
-SBT                    &   & \mark &   &   &   &   &   &   &  &   \\
-Simplics               & SRI & \mark &   &   &   &   &   &   &  &   \\
-simplifyingSTP         & U. Melbourne   &   &   &   &   &   & \mark &   &   &   \\
-SMTInterpol            & U. Freiburg    &   &   &   &   &   &   & \mark & \mark & \mark \\
-SONOLAR                & U. Bremen      &   &   &   &   &   & \mark & \mark & \mark & \mark \\
-Spear                  &   &   &   & \mark & \mark &   &   &   &  &   \\
-STP, STP2              & MIT            &   & \mark &   &   & \mark &   & \mark & \mark &   \\
-STP-CryptoMiniSat4     & Security Res. Lab.  &   &   &   &   &   &   &   &   & \mark\\
-SVC	               & Stanford U.  & \mark &   &   &   &   &   &   &  &   \\
-sword                  & U. Bremen      &   &   &   & \mark & \mark &   &   &   &   \\
-test\_pmathsat         & FBK-IRST       &   &   &   &   &   & \mark &   &   &   \\
-Tiffany de Wintermonte & U. Melbourne 	&   &   &   &   &   &   &   & \mark &  \\
-veriT                  & Loria, UFRN           &   &   &   &   & \mark & \mark & \mark &   & \mark \\
-Yices, Yices2          & SRI            & \mark & \mark & \mark & \mark & \mark &   &   &   & \mark \\
-Z3                & Microsoft Res.  &   &   & \mark & \mark &   &   & \mark &   &   \\
-\hline
-Total & & 11 & 11 & 9 & 13 & 12 & 10 & 11 & 11 & 18 \\
-\hline
-\end{tabular}}
-\end{table}
-
-As in past competitions, the organizers included some publicly available historical solvers.
-These solvers are run in the competition for comparison, but are designated as demonstration only and are not eligible for any awards or designations of having won the competition.
-In result tables, these solvers are listed with their names in square brackets (e.g., [MathSat]).
-The organizers included current versions of MathSat and Z3.
-Also, during the competition, a bug-fix release of CVC4 (named CVC4-with-bugfix) was submitted and included as a demonstration only version (cf.
-\S\ref{sec:floc}).
-
-\begin{table}
-\caption{Changes in participation}
-\label{Table:changes}
-\centering
-\resizebox{\textwidth}{!}{\begin{tabular}{|l|c|c|c|c|c|c|c|c|c|}
-\hline
- & 2005 & 2006 & 2007 & 2008 & 2009 & 2010 & 2011 & 2012 & 2014\\
-\hline
-Participants                 & 12 & 12 & 9 & 13 & 12 & 10 & 11 & 10 & 18 \\
-New in given year            & 12 &  4 & 4 &  6 &  2 &  6 &  1 &  4 & 5 \\
-Continuing to the next year  &  8 &  6 & 7 & 10 &  4 &  7 &  7 &  6 & 10 \\
-Not ever participating again &  4 &  5 & 2 &  2 &  6 &  3 &  4 &  4 &  \\
-\hline
-\end{tabular}}
-\end{table}
-
-\paragraph{History.} Table~\ref{Table:participants} shows the
- historical participation of each solver.
-Note that sometimes versions and names change, or there are multiple related versions from the same team; generally speaking, though not always, a solver is improved from year to year.
-Table~\ref{Table:changes} summarizes that data in numbers of continuing participants. Except for the record turnout in
- 2014, there has been a steady 9-13 participants each year; each year there are an average of 4 new
- participants, about the same number of drop-outs, and an average of 7 continuing participants.
-
-The introduction in 2010 of SMT-LIB~v2 as the standard language for benchmarks was a significant event. The new language required solvers to revise their front-ends and to add new capabilities.
-As a result, some solvers did not continue participating, at least not immediately.
-The added expressivity of the command language permitted to add benchmarks representing the needs of industrial applications, and
-the application track of the competition was added to demonstrate the interactive capability and the corresponding abilities of solvers.
-
 \section{Competition Procedure}
 \label{sec:procedure}
-
-The full description of the 2014 SMT Competition's rules is found in the rules document (\url{http://smtcomp.sourceforge.net/2014/rules14.pdf}).
-The document describes the procedures for determining benchmark difficulties, selecting benchmarks for competition, and judging the results.
-The preparation and execution of the competition required the following matters to be decided and executed.
-
-\paragraph{Decide the competition parameters.} We set a timeout of 40~minutes for both wall clock and CPU time; the memory limit was 100\,GB.
-A single solver-benchmark combination (job-pair) was run on a node at a given time.
-The benchmarks were scrambled; all benchmarks were run, rather than just a subset.
-StarExec made about 150 nodes available for the duration of the competition.
-%% [DD] Removed the following sentence to reduce redundancy 
-%% The timeout setting was a notable difference in 2014; in 2013, this
-%% was set at 25~minutes.
-The effect of the new timeout is discussed in \S\ref{sec:timeouts}.
-Though the memory limit was fairly generous, there were still a small number~(202) of jobs that were killed during the competition because of excessive memory use.
-
-\paragraph{Settle any adjustments on the rules and competition timeline, with time for comment.}
-The competition rules are largely the same from year to year, but each year there are adjustments and improvements.
-Matters to be decided are the timeline for the competition, communication vehicles (including instantiating the website for the new competition), the various tracks and divisions, any adjustments to the benchmark selection procedure, the scoring rules, and policies on similar submissions and portfolio solvers.
-A novel aspect in 2014 was the need for policies regarding the FLoC Olympic Games~\cite{FLoCGames}, described in \S\ref{sec:floc}.
-During the competition, the organizers had to rule on two issues.
-\begin{itemize}[noitemsep,nolistsep]
-\item First, whether solvers could be withdrawn from divisions after the competition began; our ruling was no, because that could raise a solver's overall performance score and could change which divisions were deemed competitive.
-This decision did affect the results of the FLoC medal competition.
-\item Second, whether a job-pair that responded with a result before the timeout limit, but did not exit until after the timeout limit, is to be considered a timeout or a correct or wrong answer; the ruling was that it is not a timeout.
-Only one benchmark was affected by this decision and the decision did not affect any winning order, just a slight change in one solver's score.
-\end{itemize}
-The organizers also received and adjudicated an appeal after the competition completed (cf.~\S\ref{sec:floc}).
-
-\paragraph{Undefined behavior.} \label{par:undefined} During the testing period prior to the competition beginning, different solvers exhibited different behavior on some benchmarks.
-Investigation revealed that these differences were the result of different treatments of partial operations; in particular, divide by zero.
-The semantics of SMT-LIB is based on a logic of total functions, meaning that division by zero cannot raise an exception (or the like), but must have \emph{some} value.
-The SMT-LIB standard leaves this value unspecified (i.e., it could be anything).
-In contrast, some solvers assume a specific, fixed value.
-This question had been discussed at length over previous years, with proposals to clarify the SMT-LIB standard.
-There was certainly not time to resolve this matter prior to the competition, not to mention correcting solvers to the agreed behavior.\footnote{The discussion this time around can be found in the archives of the \url{smtcomp-discussion@lists.sourceforge.net} mailing list, in the few days near 2014-06-16.}  Thus, for the competition, we decided to omit all benchmarks (6060 of them, 1348 of which were otherwise eligible) that were potentially affected by divide-by-zero behavior.
-This question, however, remains open.
-
-\paragraph{Invite and validate solver submissions.} The 2014 competition saw the first use of the StarExec computational cluster (cf.
-\S\ref{sec:starexec}) for executing the competition.
-Each solver had to be wrapped in appropriate scripts to be able to run in the StarExec environment.
-Though this was largely the responsibility of the solver submitter, teams submitting solvers for the first time required guidance and assistance from the organizers and the StarExec development team.
-This was a significant hurdle; not all solver teams were able to complete it in time.
-The most significant problem was the need to create a fully statically linked version of the solver that ran on the particular version of Linux used by StarExec.
-The organizers stipulated a first solver submission deadline and a final solver submission deadline, separated by two weeks, to enable (and encourage) trials and debugging of solver submissions.
-
-Solver submissions comprise the solver itself, a short system
-description outlining what is new or novel about the solver, and an
-integer seed used as input to the scrambler (as described
-in~\S\ref{sec:benchmark-selection}).
-%% [DD] removed following sentence to reduce redundancy
-%%
-%% All the submitted seeds and an additional seed derived from a value
-%% unknowable until after the solver submission deadline were summed
-%% and used as the starting seed for any pseudo-random selection and
-%% scrambling processes (see below) in the competition.
-
-\paragraph{Invite and validate benchmark submissions.} New benchmarks are always welcome and an impending competition is a particular opportunity to encourage new submissions.
-Benchmarks are the responsibility of SMT-LIB coordinators, not the competition organizers.
-Nevertheless, the organizers worked with the coordinators to ensure that new benchmarks were included in SMT-LIB in time for the competition.
-Initial submissions are often incomplete; to be useful they must be syntactically correct, include a designation of the logic in which they fit, contain relevant metadata about the source and category of the benchmark, and have a known, validated answer.
-Benchmarks with unknown answers may also be interesting and worth keeping, but cannot be used in the competition.
-
-\paragraph{Create an appropriate selection of benchmarks.} Not all benchmarks in the SMT-LIB database are necessarily used in the competition.
-The details of this selection, as executed for the 2014 competition, are described in \S\ref{sec:benchmarks}.
-Part of the work in preparing the competition to run on the StarExec cluster was to port the benchmark selector to StarExec.
-
-\paragraph{Prepare the benchmark scrambler.} All the benchmarks are public and known to the solver developers beforehand.
-Indeed, part of the point of the benchmark database is to serve as a testbed for solver development, outside of competitions.
-However, that raises the possibility that a solver will recognize a benchmark problem by its syntactic structure and look up an answer from a learned database, without doing any logic solving.
-This is explicitly considered cheating.
-As a slight impediment against such behavior, the benchmarks are individually scrambled before being presented to a solver, using the random seed described above.
-For 2014, the benchmark scrambler had to be ported to StarExec.
-
-The scrambling does not change the semantic meaning of the benchmark.
-It does rename identifiers, alter the order of assertions and the position of the arguments in the application of associative-commutative operators.
-
-The scrambling had another effect, previously unappreciated.
-Although most of the solvers are deterministic for a given input, scrambling can change the order of search.
-For example, iterating over the contents of a hashed set may occur in a different order if identifiers have different names.
-Consequently, the success of the solver on a given benchmark, the time it takes to find an answer, and even whether a latent bug in the solver is triggered may all depend on just how the benchmark is scrambled.
-Thus the scrambling adds a measure of uncertainty to the competition and prevents full testing on the benchmark set before the competition.
-Indeed, one solver encountered a bug during the competition that was directly related to the specific, randomly-chosen scrambling used during the competition.
-The effect of the possible variations in performance caused by scrambling is expected to be balanced by the large number of benchmarks employed in the competition to compare the solvers, as also observed in the SAT community~\cite{leberre+03}.
-Nevertheless, this point is worthy of future further investigation.
-
-\paragraph{Prepare the real-time results display.} The participants are interested in the progress of the competition as it proceeds.
-The organizers also need to know if the competition is proceeding correctly and at a reasonable pace.
-As the competition takes several days, an automatic real-time display of results is helpful and encourages interest.
-StarExec does not have such a facility, since different competitions have different needs.
-Instead the organizers used StarExec's command-line API to regularly (every 10 minutes or so) download the status of all of the executing jobs, extract the results for each solver-benchmark pair, create HTML web pages displaying the current status, and upload them to the competition website.
-The current (now final) status of each division and a summary page can be seen at \url{http://smtcomp.sourceforge.net/2014/results-toc.shtml}.
-
-\paragraph{Execute the competition.} Executing the competition required preparing a StarExec job for each
-division.
-A job executes the cross-product of a set of solvers and a set of benchmarks.
-Because each division has different sets of solvers and benchmarks, each division was represented by one or more jobs.
-Splitting a division into multiple jobs allowed a restart of portions of the competition if a particular division was incorrectly configured or if a StarExec job stalled for some reason (both of which happened).
-
-In addition, with the new cluster, the new benchmarks, and a longer timeout period, the organizers were unsure how long the competition would take.
-Our conservative estimate was that a month of computing was needed; in fact it only took about a week, because we had three times more StarExec nodes available than anticipated and jobs took on average less time than estimated.
-However, to hedge against the competition taking longer than anticipated, we divided larger divisions into \emph{heats}, with each heat comprising about 1000 benchmarks, and with the option (stated in the rules) to terminate the competition before all heats were executed to ensure a timely end prior to FLoC.
-This required handling a much larger number of StarExec jobs.
-In the end it was entirely unnecessary for timely completion, but, as mentioned, dividing the jobs into manageable pieces was useful for restarting portions of the computation when StarExec stalled.\footnote{Stalling---that is, no longer making forward progress on a job---was less a concern after some bug fixes during the competition, but was still observed during some post-competition computations.}
-
-In past competitions, the competition was timed to have its last portion overlap with the conference with which it was affiliated.
-In 2014, because the computation took less time than anticipated, the competition finished well before the conference.
-
-\paragraph{Report the results.} The results of the competition were reported at the SMT Workshop and in this paper.
-
-\paragraph{Competition timeline.}
-
-The preparation and execution of SMT-COMP 2014 took place over about 7 months,
-relying on the experience of previous competitions, the 2013 SMT Evaluation, and
-development activity on StarExec. The timeline is provided in
-Table~\ref{tab:timeline} for transparency and as a guideline for forthcoming
-editions of the competition.
-
-\begin{table}
-\caption{\label{tab:timeline}Competition timeline}
-\begin{tabular}{r |@{\hspace{-2.3pt}$\bullet$ \hspace{5pt}} p{.75\textwidth}}
-Jul. 2013 & Cok appointed as chair of the organizing committee\\
-Dec. 2013 & D\'{e}harbe and Weber appointed as co-organizers\\
-21 Jan. 2014 & call for applications and benchmarks\\
-15 May 2014 & deadline for new benchmarks; benchmarks were being corrected and curated throughout May and June, until the final solver deadline\\
-19 May 2014 & revised competition rules posted\\
-1 Jun. 2014 & deadline for initial solver registration; final competition rules posted\\
-15 Jun. 2014 & deadline for final solver registration\\
-16 Jun. 2014 & computation begins\\
-22 Jun. 2014 & main track computation ends; official results posted on 27~June\\
-22 Jun. 2014 & deadline for application track solvers\\
-28 Jun. 2014 & application track computation\\
-17 Jul. 2014 & SMT Workshop at which results were announced\\
-21 Jul. 2014 & FLoC Olympic Games Awards Ceremony
-\end{tabular}
-\end{table}
 
@@
 
-The competition used the NSF-funded StarExec~\cite{DBLP:conf/cade/StumpST14} computational cluster at the University of Iowa for executing solvers on benchmarks.
-Past instances of SMT-COMP used a previous SMT-Exec infrastructure.
-StarExec was used for several other competitions in 2014 as well.
-
-StarExec currently consists of 192 2.4\,GHz computational nodes, running Red Hat Linux~6.3.
-Each node has two quad-core CPUs (model Intel Xeon E5-2609, 2.4\,GHz, 10\,MB cache), and either 129022\,MB (32 nodes) or 258294\,MB of memory (160 nodes).
-In competition, processes were limited to 100\,GB memory.
-To avoid interference among job-pairs, only one job-pair was executed at a time on each node.
-The software configuration contains
-\begin{itemize}[noitemsep,nolistsep]
-\item Linux kernel 2.6.32-573.1.1.el6.x86\_64
-\item GNU C Library stable release version 2.12
-\item gcc (GCC) 4.4.7 20120313 (Red Hat 4.4.7-11)
-\end{itemize}
-
-For comparison, the previous computational cluster (SMT-Exec) had just 11 nodes:
-\begin{itemize}[noitemsep,nolistsep]
-\item Nine were 2.4\,GHz AMD Opteron 250s, configured for single core, 64-bit processing, 1 MB cache, 4 GB main memory
-\item Two were 2.53\,GHz Intel Xeon E5540s, configured for single core, 64-bit processing, 8 MB cache, 12 GB main memory
-\end{itemize}
-All SMT-Exec nodes had been running Red Hat Enterprise Linux Client release 5.2 (Tikanga), with the following software configuration:
-\begin{itemize}[noitemsep,nolistsep]
-\item Linux kernel 2.6.18-128.2.1.el5
-\item glibc-2.5-24.el5\_2.2
-\item runtime libraries from gcc-4.1.2-42.el5
-\end{itemize}
-The raw CPU speed is not significantly different, but memory size, number of cores, and number of nodes is greatly increased.
-
-As this was the first year SMT-COMP used StarExec, a variety of tools and procedures needed to be ported to the new infrastructure, as described in \S\ref{sec:procedure}.
-%% [DD]
-%% Removed the following that is redundant
-%%
-%% These included the benchmarks, the post-processor for scoring
-%% results, a tool to select benchmarks randomly according to the
-%% stated policies, tools for creating StarExec jobs based on
-%% selections of benchmarks and solvers, the driver application for
-%% running the application track, and tools for creating real-time
-%% summaries of results in progress.  These are now available to be
-%% reused in future years.
-The execution of SMT-COMP on StarExec went well, though not flawlessly: there were some bugs to work through.
-The organizers had some bugs of their own: the scripts to create sets of benchmarks and jobs did not account for spaces in filenames; some initial report generation was incorrect; the postprocessor for translating textual output from solvers into official results needed fine-tuning.
-These problems were all fixed before or early in the competition.
-The main issue with StarExec itself was that sometimes jobs would hang or the StarExec infrastructure would fail to make
-progress or would report results incorrectly. Bugs in scheduling were
-fixed during the competition but are not entirely resolved. Accordingly, jobs need regular monitoring to insure they are making progress.
-
-Overall, however, StarExec performed its function well and the support team was responsive in fixing any difficulties: evaluations of 339,714 job-pairs were completed for the competition over a period of about 9 days, including the restarts necessary because of bugs or misconfigurations.
-
 \section{Other Competitions}
 \label{sec:OtherCompetitions}
-
-Competitions among tools for a specific purpose are now common.
-Indeed SMT-COMP participated among a dozen or so competitions in the FLoC Olympic Games in 2014~\cite{FLoC2014}.
-The competitions differ, of course, in their target problem set, but also in their overall goals, scoring policies, and organization.
-
-\paragraph{CASC} SMT differs from the CASC competition~\cite{PSS02} in directly addressing sorted logics.
-SMT also focuses on fragments of first-order logic that are \emph{decidable}.
-For example, a subset of the benchmarks are problems in an integer-difference logic, for which there are specific decision procedures.
-The competition among tools is to create very efficient implementations of a breadth of decision procedures.
-Accordingly, SMT solvers have historically not handled logics with quantified expressions, though several solvers now do so, responding to strong encouragement from industrial users to include quantification in SMT solvers; there are benchmarks and competition divisions corresponding to logics with quantification.
-Including quantified expressions can, in general, make the satisfiability problem undecidable and the solvers necessarily rely on heuristics.
-Solvers may respond that the answer to a problem is unknown; that is, although there may be a candidate satisfying value assignment, the solver cannot assure that some combination of instantiations of quantified formulas might not invalidate the assignment.
-Nevertheless, the inclusion of logics with quantification has been welcome by users.
-With SMT solvers moving to include quantification and CASC solvers moving to include types and arithmetic, we see a basis for fruitful future collaboration and perhaps merging between these communities.
-
-The organizers of SMT-COMP helped organize and execute the first edition of SL-COMP~\cite{SLCOMP,sighireanu2014report} as a sibling competition.
-SL-COMP is a competition among solvers for separation logic.
-The formal logical underpinnings of SL-COMP are still being
-defined and the relationship between the logic used in SL-COMP and the SMT-LIB logic is under discussion. However, SL-COMP
-did express its benchmark problems in the same syntax as SMT-COMP, used the same StarExec hardware, and used similar 
-organization and scoring rules.
-
-\paragraph{SL-COMP} Besides the subject material, the most interesting difference among competitions is in scoring. (The scoring procedure for
-SMT-COMP is described in detail in Section~\ref{sec:floc}.)
-Competitions are currently mostly focused on raw solver capability---that is, the numbers and difficulty of problems that can be solved.
-Thus competition winners are primarily determined by the total number of problems solved correctly,
-with the time taken to produce the solutions used only as a tie-breaker. This is the case for SMT-COMP, SAT, and SV-COMP,
-for example.
-
-\paragraph{Scoring differences.} A more significant issue is how solver errors are taken into account in the metrics.
-A solver error indicates an unsoundness in the tool, which is highly undesirable; however, highly penalizing errors may discourage new entrants whose tools are not yet mature.
-Different competitions vary on this aspect.
-SMT-COMP has historically emphasized soundness; a
-single error in a division caused the solver to be scored lower than any other solver with no errors, even if the other solvers solved very few problems.
-In its inaugural edition, the Separation Logic Competition (SL-COMP) adopted the same rules as SMT-COMP.
-For the SAT competition, however, an error outright disqualifies a tool in the category it occurs.\footnote{See \url{http://satcompetition.org/2014/rules.shtml}.} In the QBF Gallery, a competitive evaluation of solvers for Quantified Boolean Logic, the score is the number of solved instances.
-In contrast, in the SV-competition~\cite{svcomp-2015}, successful runs account positively towards the final score, while errors count negatively (with an increased weight).
-A few other sibling competitions with scoring variations are the Answer-Set Programming competition (ASP-COMP: wrong answers for some problem instance cause an overall score of zero for the problem), the Confluence Competition (CoCo: implausible answers disqualify from winning), and Syntax-Guided Synthesis (SyGuS-COMP: no points for wrong answers, extra points for succinct answers).
 
@@
 
-\subsection{Main track results}
-\label{sec:timeouts}
-
-Table \ref{Table:maintrack} shows a summary of the main track results. The detailed data for each division is on the competition website: \url{http://smtcomp.sourceforge.net/2014/results-toc.shtml}.
-
-The results of the competition per se were not surprising.
-The solvers that performed best in previous years continued to do so.
-Boolector wins those divisions that focus on bit-vector problems; CVC4 has the most breadth of application and wins most of the other divisions, with Yices2 also having a strong showing.
-Solvers that were optimized with particular decision procedures for particular logics can capture individual wins: AProVE for QF\_NIA; veriT for UFLRA.
-If Z3 had competed, with the current version entered by the organizers, it would have won many divisions, but not all; CVC4 is
-definitely competitive with it.
-
-In the medal ceremony for the competition at the SMT Workshop, the organizers took care not to focus only on the winning solvers.
-The competition was also successful in attracting new interest and many new entrants, even when the new entrants did not score highly or had errors in their submissions.
-In that sense the decision of the SMT steering committee to pause
-the competition for a year, to 'reboot' it and give contestants some breathing room, was also successful.
-
-The organizers chose not to try to make a detailed comparison with previous years' results. Such a comparison had just been
-completed in the 2013 Evaluation exercise. Furthermore, with the change in computation hardware, an accurate comparison
-would have required running all of the 2012 solvers along with the 2014 solvers and making a comparison on just the
-benchmarks used in the 2012 competition. While this is certainly possible, the organizers were not confident enough of the
-ability of the new StarExec to complete even the 2014 competition to contemplate doubling the computational load.
-In addition, such an exercise was out of the scope of their mandate and would have required considerable extra effort.
-However, knowing now that StarExec is fully capable of executing all of the competition benchmarks, such a
-comparative exercise would be definitely possible in the future.
-The organizers are confident that the 2014 data will be a solid baseline for evaluating progress in solver performance in future years.
-
-\begin{table}
-\caption{Main track results}
-\vspace{-\smallskipamount}
-\label{Table:maintrack}
-\centering
-\newcommand{\win}[1]{\textbf{#1}}
-\resizebox{!}{299pt}{\begin{tabular}{|l|r|r|l|}
-\hline
-Logic &	Solvers &	Benchmarks & Order (winner in bold) \\
-\hline
-ALIA & 		4 & 	29  & 	[Z3]; \win{CVC4}; veriT; CVC3. \\
-AUFLIA & 	4 & 	4   & 	\win{CVC4}; [Z3]; CVC3; veriT. \\
-AUFLIRA & 	4 & 	10791 & 	[Z3]; \win{CVC4}; CVC3; veriT. \\
-AUFNIRA & 	4 & 	564 & 	[CVC4-with-bugfix]; [Z3]; \win{CVC3}; CVC4. \\
-LIA & 		4 & 	46 & 	[Z3]; \win{CVC4}; CVC3; veriT. \\
-LRA & 		4 & 	171 & 	\win{CVC4}; [Z3]; CVC3; veriT. \\
-NIA & 		3 & 	9 &  	[Z3]; \win{CVC4}; CVC3. \\
-NRA & 		3 & 	3747 & 	[Z3]; \win{CVC4}; CVC3. \\
-QF\_ABV & 	9 & 	6457 & \win{Boolector-j}; Boolector-d; [MathSAT]; \\
-& & & SONOLAR; CVC4; [Z3]; Yices2; \\
-& & & Kleaver-STP; Kleaver-portfolio. \\
-QF\_ALIA & 	5 & 	97 & \win{Yices2}; SMTInterpol; [Z3]; [MathSAT]; CVC4. \\
-QF\_AUFBV & 	4 & 	37 & \win{CVC4}; Yices2; [Z3]; [MathSAT]. \\
-QF\_AUFLIA & 	6 & 	610 & \win{Yices2}; [MathSAT]; [Z3] \\
-& & & SMTInterpol; CVC4; veriT. \\
-QF\_AX & 	5 & 	335 & \win{Yices2}; [MathSAT]; [Z3]; CVC4; \\
-& & & SMTInterpol. \\
-QF\_BV & 	11 & 	2488 & \win{Boolector}; STP-CryptoMiniSat4; \\
-& & & [CVC4-with-bugfix]; [MathSAT]; [Z3]; \\
-& & & CVC4; 4Simp; SONOLAR; Yices2; \\
-& & & abziz\_min\_features; abziz\_all\_features. \\
-QF\_IDL & 	4 & 	1315 & 	[Z3]; \win{Yices2}; CVC4; veriT. \\
-QF\_LIA & 	7 & 	4381 & 	[CVC4-with-bugfix]; [MathSAT]; \\
-& & & \win{SMTInterpol}; Yices2; [Z3]; veriT; CVC4. \\
-QF\_LRA & 	6 & 	1343  & \win{CVC4}; Yices2; [MathSAT]; SMTInterpol; \\
-& & & veriT; [Z3]. \\
-QF\_NIA & 	4 & 	8327 & 	[Z3]; \win{AProVE}; CVC3; CVC4. \\
-QF\_NRA & 	4 & 	10121 & [Z3]; \win{CVC3}; CVC4; raSAT. \\
-QF\_RDL & 	4 & 	132 & 	\win{Yices2}; [Z3]; veriT; CVC4. \\
-QF\_UF & 	7 & 	4124 & 	\win{Yices2}; veriT; CVC4; OpenSMT2; [Z3]; \\
-& & & [MathSAT]; SMTInterpol. \\
-QF\_UFBV & 	4 & 	31 & 	\win{Yices2}; [Z3]; [MathSAT]; CVC4. \\
-QF\_UFIDL & 	4 & 	311 & 	[Z3]; \win{Yices2}; CVC4; veriT. \\
-QF\_UFLIA & 	6 & 	484 & 	[Z3]; \win{Yices2}; CVC4; SMTInterpol; \\
-& & & [MathSAT]; veriT. \\
-QF\_UFLRA & 	6 & 	1176 & 	[Z3]; \win{Yices2}; [MathSAT]; CVC4; \\
-& & & SMTInterpol; veriT. \\
-QF\_UFNIA & 	3 & 	7 & 	\win{CVC4}; [Z3]; CVC3. \\
-QF\_UFNRA & 	3 & 	32 & 	[Z3]; \win{CVC3}; CVC4. \\
-UF & 		4 & 	2830 & 	\win{CVC4}; [Z3]; CVC3; veriT. \\
-UFIDL & 	3 & 	49 & 	[Z3]; \win{CVC4}; CVC3. \\
-UFLIA & 	4 & 	5766 & 	\win{CVC4}; [Z3]; veriT; CVC3. \\
-UFLRA & 	4 & 	25 & 	[Z3]; \win{veriT}; CVC3; CVC4. \\
-UFNIA & 	3 & 	1587 & 	[Z3]; \win{CVC4}; CVC3. \\
-\hline
-\end{tabular}}
-\end{table}
-
-\paragraph{Fastest solvers.} The competition does not weight time to solve a problem significantly.
-However, this is an important characteristic to any user.
-Hence we analyzed the competition results for each division to answer this question:
-for each solver, what fraction of the benchmarks for the division does that solver solve the fastest? 
-The data answering this question is shown in Table \ref{tab:speed}.
-For each division and each benchmark, we determined the solver that solved that benchmark the fastest, and for each solver counted the number of benchmarks for which it was the fastest.
-The table lists the three solvers with the most such benchmarks, with the fraction of benchmarks that it won.
-The winning solvers are a mix of Z3, CVC, Yices2, and a few for veriT.
-In some divisions, the winning solver does dominate the competition.
-Yices2, for example tends to win in those divisions in which it participates, with Z3 winning most of the others.
-Note that this analysis does not take into account the margin by which the times are better.
-The times used here are cpu-times; using wall-clock times changes the fractions and sometimes the order, but not the overall observation.
-
-\begin{table}
-\caption{Fraction of benchmarks solved fastest (cpu-time) by each solver (top 3)}
-\label{tab:speed}
-\centering\begin{tabular}{|l|lll|}
-\hline
-Logic & Fraction solved fastest & & \\ \hline
-ALIA & 51\% [Z3] & 48\% veriT  & \\
-AUFLIA & 66\% [Z3] & 33\% CVC3  & \\
-AUFLIRA & 60\% [Z3] & 37\% veriT & 1\% CVC3 \\
-AUFNIRA & 72\% [Z3] & 23\% CVC3 & 2\% CVC4 \\
-LIA & 43\% CVC4 & 30\% [Z3] & 17\% CVC3 \\
-LRA & 42\% CVC4 & 38\% veriT & 18\% [Z3] \\
-NIA & 66\% [Z3] & 33\% CVC4  & \\
-NRA & 96\% CVC4 & 3\% [Z3]  & \\
-QF\_ABV & 78\% Yices2 & 9\% SONOLAR & 7\% Kleaver-STP \\
-QF\_ALIA & 95\% Yices2 & 4\% [Z3] & \\
-QF\_AUFBV & 81\% Yices2 & 10\% [MathSAT] & 5\% [Z3] \\
-QF\_AUFLIA & 60\% Yices2 & 38\% [Z3] & 1\% CVC4 \\
-QF\_AX & 92\% Yices2 & 6\% [Z3] & 0\% CVC4 \\
-QF\_BV & 33\% Yices2 & 25\% [Z3] & 13\% 4Simp \\
-QF\_IDL & 87\% Yices2 & 11\% [Z3] & 0\% veriT \\
-QF\_LIA & 76\% Yices2 & 11\% [Z3] & 7\% CVC4 \\
-QF\_LRA & 86\% Yices2 & 3\% veriT & 3\% CVC4 \\
-QF\_NIA & 90\% [Z3] & 7\% AProVE & 1\% CVC3 \\
-QF\_NRA & 88\% [Z3] & 6\% CVC4 & 4\% CVC3 \\
-QF\_RDL & 71\% Yices2 & 25\% [Z3] & 3\% veriT \\
-QF\_UF & 96\% Yices2 & 1\% veriT & 1\% [Z3] \\
-QF\_UFBV & 96\% Yices2 & 3\% [MathSAT]  & \\
-QF\_UFIDL & 59\% [Z3] & 36\% Yices2 & 3\% veriT \\
-QF\_UFLIA & 97\% Yices2 & 2\% [Z3] & 0\% CVC4 \\
-QF\_UFLRA & 91\% Yices2 & 4\% [Z3] & 2\% veriT \\
-QF\_UFNIA & 100\% CVC4 & & \\
-QF\_UFNRA & 59\% CVC3 & 37\% [Z3] & 3\% CVC4 \\
-UF & 37\% veriT & 32\% CVC4 & 24\% [Z3] \\
-UFIDL & 57\% CVC4 & 42\% [Z3]  & \\
-UFLIA & 56\% [Z3] & 35\% veriT & 7\% CVC4 \\
-UFLRA & 95\% veriT & 4\% [Z3]  & \\
-UFNIA & 80\% [Z3] & 10\% CVC3 & 9\% CVC4 \\
-
-\hline
-\end{tabular}
-\end{table}
-
-\paragraph{Solver contribution.} A second comparison that can be made is to determine what a solver adds in addition to 
-what other solvers contribute.
-We measure this `solver contribution' as follows.
-For each benchmark in a division, we award each solver that solves the benchmark $1/n$ points, where $n$ is the number of solvers that solved the benchmark (within the timeout).
-These points are then summed over all the benchmarks in the division and scaled by the number of benchmarks.
-The sum is a measure of the
-unique contribution provided by a solver; a value of 1.0 would indicate that that solver was the only solver to solve all of the benchmarks in the division.
-The results are shown in Table \ref{tab:cont}.
-The results show again that no one solver dominates in all categories, but that there are several contributing solvers among which users can choose.
-
-\begin{table}
-\caption{Contribution from each solver (top 3)}
-\label{tab:cont}
-\centering\begin{tabular}{|l|lll|}
-\hline
-Logic & Unique contribution & & \\
-\hline
-ALIA & 0.4253 [Z3] & 0.4080 CVC4 & 0.1667 veriT \\
-AUFLIA & 0.3889 CVC4 & 0.2778 [Z3] & 0.2222 CVC3 \\
-AUFLIRA & 0.2615 [Z3] & 0.2521 CVC4 & 0.2503 CVC3 \\
-AUFNIRA & 0.2509 [Z3] & 0.2506 CVC4 & 0.2497 CVC3 \\
-LIA & 0.3949 [Z3] & 0.3514 CVC4 & 0.2319 CVC3 \\
-LRA & 0.3070 CVC4 & 0.3070 [Z3] & 0.2895 CVC3 \\
-NIA & 0.8333 [Z3] & 0.1667 CVC4 & 0.0000 Yices2 \\
-NRA & 0.5071 [Z3] & 0.4929 CVC4 & 0.0000 Yices2 \\
-QF\_ABV & 0.1147 Yices2 & 0.1146 Boolector-just... & 0.1144 Boolector-dual... \\
-QF\_ALIA & 0.2235 Yices2 & 0.2235 SMTInterpol & 0.2235 [Z3] \\
-QF\_AUFBV & 0.2635 [MathSAT] & 0.2635 CVC4 & 0.2500 Yices2 \\
-QF\_AUFLIA & 0.1996 Yices2 & 0.1996 [MathSAT] & 0.1996 CVC4 \\
-QF\_AX & 0.2000 Yices2 & 0.2000 [MathSAT] & 0.2000 CVC4 \\
-QF\_BV & 0.1051 Boolector & 0.0976 STP-Crypto... & 0.0934 abziz\_min\_f... \\
-QF\_IDL & 0.2893 [Z3] & 0.2731 Yices2 & 0.2395 CVC4 \\
-QF\_LIA & 0.1620 [CVC4-...fix] & 0.1610 [Z3] & 0.1610 SMTInterpol \\
-QF\_LRA & 0.1772 CVC4 & 0.1689 Yices2 & 0.1678 SMTInterpol \\
-QF\_NIA & 0.4990 [Z3] & 0.4912 AProVE & 0.0084 CVC3 \\
-QF\_NRA & 0.7714 [Z3] & 0.1347 CVC3 & 0.0898 CVC4 \\
-QF\_RDL & 0.2734 Yices2 & 0.2431 veriT & 0.2431 [Z3] \\
-QF\_UF & 0.1451 Yices2 & 0.1449 veriT & 0.1446 CVC4 \\
-QF\_UFBV & 0.4140 Yices2 & 0.3172 [Z3] & 0.1720 [MathSAT] \\
-QF\_UFIDL & 0.2708 Yices2 & 0.2708 [Z3] & 0.2309 CVC4 \\
-QF\_UFLIA & 0.1698 Yices2 & 0.1698 [MathSAT] & 0.1698 CVC4 \\
-QF\_UFLRA & 0.1715 [Z3] & 0.1681 Yices2 & 0.1681 [MathSAT] \\
-QF\_UFNIA & 0.5000 CVC4 & 0.5000 [Z3] & 0.0000 Yices2 \\
-QF\_UFNRA & 0.5802 [Z3] & 0.2099 CVC4 & 0.2099 CVC3 \\
-UF & 0.4921 CVC4 & 0.1988 [Z3] & 0.1759 CVC3 \\
-UFIDL & 0.5204 [Z3] & 0.4796 CVC4 & 0.0000 Yices2 \\
-UFLIA & 0.4069 CVC4 & 0.3502 [Z3] & 0.2425 veriT \\
-UFLRA & 0.2857 [Z3] & 0.2381 CVC4 & 0.2381 veriT \\
-UFNIA & 0.4156 [Z3] & 0.3860 CVC4 & 0.1984 CVC3 \\
-\hline
-\end{tabular}
-\end{table}
-
-\paragraph{Effect of timeout.}
-For the main track of the competition, the organizers set a timeout of 40~minutes, much longer than in previous competitions (e.g., 25 minutes in 2012).
-The timeout values cannot be directly compared because the hardware changed as well.
-The larger timeout simply reflected the organizers' goal to allow solvers as much time as possible to complete each benchmark problem.
-A common practical question users have is how much benefit is gained by longer timeouts.
-The data from the competition allows us to analyze this question somewhat.
-
-A first question is how many additional problems are solved if the timeout is lengthened. An approximation
-of an answer is shown in Fig.~\ref{Fig:timeouts}.
-This figure shows the number of benchmarks solved, combined over all the solvers participating in the competition, with a solution time less than given timeout values, for the QF\_BV benchmark set.
-Most of the benchmarks are solved quickly: 39\% in less than a second, more than half in under 3.5 seconds,
-62\% by 10 seconds, and then a slow increase to 88\% by 2400 seconds. There is continual improvement for long timeouts, but the return on time invested certainly decreases.
-
-\begin{figure}
-\begin{center}
-\includegraphics[width=.95\textwidth]{QF_BV-timeout-logscale2.png}
-\end{center}
-\caption{Solver success for QF\_BV benchmarks over time.}
-\label{Fig:timeouts}
-\end{figure}
-
-There are two caveats to this observation.
-First, the results depend heavily on the character of the benchmarks set.
-Some logics have only easy benchmarks, some have purposefully crafted difficult benchmarks, others are a mix.
-The benchmarks are not a representative sampling of problems that might be encountered in practice.
-Second, the results described are obtained by observing the wall-clock solution time when the timeout value is set at 2400 seconds.
-Solvers, if told what the timeout value is, have the option to adjust their search strategies based on the timeout; the solvers might then exhibit better behavior for shorter timeout.\footnote{Though solvers could use the timeout value to alter their processing algorithms, current versions of those queried\textemdash Yices2, Z3, Boolector\textemdash do not do so.
-However, CVC4 and CVC3 do build in the stated timeout into the script used for competition (though it is not used by the core solver) and so might show differences from the behavior stated here.}
-
-Table~\ref{Fig:winners} shows a different view of the same data.
-Here we present the number of problems solved by each solver within a given wall-clock solution time, subject to the same caveats.
-The point to observe is that the winning solver changes depending on the timeout chosen.
-For these benchmarks and this set of solvers Yices2 performs best for timeouts under a second, CVC4 does best in the middle range from 1 to 200 seconds, and Boolector does best above 400 seconds.
-Other logics, but not all, show changes in winning order as well.
-This phenomenon could be a result of differences in engineering of the individual solvers or it could be a result of characteristics of the benchmark set.
-
-The data in Table~\ref{Fig:winners} also shows that most solvers have a similar trend in success as the timeout is increased.
-For example, most solvers solve about 50\% (ranging from 40\% to~62\%) of the benchmarks that solver solves within the timeout by 1.0 second and
-about 75\% (ranging from 65\% to 79\%) of those solved within the timeout by 10 seconds.
-However, some solvers, such as Boolector, are outliers: Boolector is slow off the mark---solving only~33\% and 61\% of the benchmarks it eventually solves
-by 1 second and 10 seconds, respectively, even though by 2400 seconds it solves more benchmarks than any other tool, in this division.
-
-\begin{table}
-\caption{Solver success per individual solver for 2488 QF\_BV benchmarks, for different timeouts (in seconds).}
-\label{Fig:winners}
-\centering
-\input{QF_BV-winners.tex}
-\end{table}
-
-\subsection{Application (incremental) track results}
-\label{sec:application-results}
-
-Most solvers are only concerned with raw performance on single benchmarks. However, an important application area for SMT solvers requires what the SMT-LIB standard calls `incremental' operation.
-In this mode, a user or some application interacts with the solver repeatedly, issuing various commands to define a problem, check for satisfiability, inspect resulting counterexample models, adjust the problem by retracting some assertions and adding other assertions, and so on.
-An example use case is a tool that allows a user to author formal specifications in conjunction with software.
-The tool would
-check using a back-end SMT solver whether the specifications are consistent with the code. If not, it might
-supply a counterexample that could be inspected in conjunction with the source code. As the user edits the source or the specifications, the problem presented to the SMT solver is modified.
-
-The application track of the competition presents to the solver a series of SMT-LIB commands through a driver program; the solver replies to the driver with a
-response to each command.
-The driver presents commands only one at a time to emulate a realistic environment and so that the solver cannot ``work ahead.'' The driver also measures the accumulated time taken for each response.
-Note that the time measured includes the response time to every command, not just to the satisfiability-checking commands; while \lstinline{check-sat} commands might be the most time-consuming, \lstinline{assert} commands, and others, might also instigate significant processing.
-The benchmark text contains \lstinline{(set-info :status ...)} commands that
-indicate the expected result for subsequent \lstinline{check-sat} commands; status information is used only by the driver program and not passed on to the solver.
-Such \lstinline{set-info} command might indicate a status of \lstinline{unknown}; in that case, the driver
-considers the benchmark to end after the \emph{previous} \lstinline{check-sat} command for competition purposes.
-The driver originally used to collect the answers had a bug that was
-detected and reported by Kshitij Bansal~\cite{bansal2015email}, who
-also provided a corrected version of the driver. The results discussed
-in this section were obtained with this new driver and differ from those reported
-earlier, such as at the 2014 SMT Workshop.
-
-The application track was first introduced in 2011; a report on that year's application track and the overall design was presented by Griggio and Bruttomesso at the 2012 COMPARE Workshop~\cite{ag+rb+12}.
-A significantly adapted driver was implemented by the organizers for 2014 on the StarExec framework.
-
-In 2014, the SMT-LIB contains 9,926 benchmarks that  specifically  exercise the incremental solving capability of solvers.
-Table \ref{Fig:apptrack-benchmarks} lists the numbers of benchmarks in various logics; UFLRA, QF\_UFLRA, and QF\_UFLIA are the only logics with significant numbers of benchmarks.
-For now, AUFNIRA does not contain any valid \lstinline{check-sat} command.
-All the benchmarks were used in the competition.
-
-Four solvers participated in this competition track: CVC3, CVC4, SMTInterpol, and Yices2; Z3 was added as a demonstration-only historical comparison.
-The winner is the solver that solved the most \lstinline{check-sat} commands correctly within the timeout period.
-No solver produced an erroneous result.
-The time out (40 minutes) is applied to the entire benchmark, not to individual commands.
-The track was run for 8 divisions; the results are shown in Table \ref{Fig:apptrack-results}.
-Within each division, solvers are listed in winning order: Yices2 won four of the eight divisions, out of six in which it participated.
-CVC3, CVC4 and SMTInterpol won one division each.
-Since the previous execution of the application track was in 2012 and not on StarExec, we did not attempt a comparison with previous results.
-
-\begin{table}[H]
-\caption{Numbers of application benchmarks and distribution of \lstinline{check-sat} commands for different logics.}
-\label{Fig:apptrack-benchmarks}
-\centering
-\begin{tabular}{|l|r|rrrr|}
-\multicolumn{6}{c}{\textbf{All benchmarks}} \\
-\hline
-&  & \multicolumn{4}{c|}{{\small\bfseries\sffamily check--sat} commands} \\
- Logic & Benchmarks & total & min & max & avg. \\
-\hline
-AUFNIRA & 165  & 3452 & 2 & 615 & 20.9 \\
-QF\_AUFLIA & 72 & 4699864 & 5 & 1109912 & 65275.9 \\
-QF\_BV & 18 & 2727 & 101 & 202 & 151.5 \\
-QF\_LIA & 65 & 19690826 & 101 & 2630828 & 302935.8 \\
-QF\_LRA & 10 & 1515 & 101 & 202 & 151.5 \\
-QF\_UFLIA & 905 & 790630 & 1 & 474174 & 873.6 \\
-QF\_UFLRA & 3333 & 22103 & 2 & 3384 & 6.6 \\
-UFLRA & 5358 & 3514613 & 2 & 40758 & 656.0 \\
-\hline
-\multicolumn{6}{c}{}\\
-\multicolumn{6}{c}{\textbf{Eligible benchmarks}} \\
-\hline
-&  & \multicolumn{4}{c|}{{\small\bfseries\sffamily check--sat} commands} \\
- Logic & Benchmarks & total & min & max & avg. \\
-\hline
-AUFNIRA & 165  & 0 & 0 & 0 & 0 \\
-QF\_AUFLIA & 72 & 4699864 & 5 & 1109912 & 65275.9 \\
-QF\_BV & 18 & 2141 & 52 & 202 & 118.9 \\
-QF\_LIA & 65 & 19689957 & 30 & 2630828 & 302922.4 \\
-QF\_LRA & 10 & 795 & 45 & 107 & 79.5 \\
-QF\_UFLIA & 905 & 766079 & 1 & 474174 & 846.5 \\
-QF\_UFLRA & 3333 & 22066 & 0 & 3384 & 6.6 \\
-UFLRA & 5358 & 223820 & 2 & 201 & 41.8 \\
-\hline
-\end{tabular}
-\end{table}
-
-\begin{table}
-\caption{Results of the incremental track, across eight divisions. In each division, solvers are listed in winning order.}
-\label{Fig:apptrack-results}
-\vspace{-\medskipamount}
-\centering
-\resizebox{!}{294pt}{\input{apptrack-results.tex}}
-\end{table}
-
-We can also consider the effect of the choice of timeout on the application track.
-This effect is more complicated than for the main track since an application track benchmark can have partial results.
-For example, if a benchmark contains 100 check-sat commands, a solver may report correct answers on 0 to 100 of them prior to timing out.
-Furthermore the seven divisions that have results show very different characteristics.
-In four of the divisions (QF\_AUFLIA, QF\_UFLIA, QF\_UFLRA, UFLRA) over 90\% of the solver-benchmarks jobs were completed before the timeout; for QF\_UFLRA it was over 99\%.
-The other three divisions (QF\_BV, QF\_LIA, QF\_LRA) had much harder benchmarks.
-For example, for QF\_BV, only 1\% of solver-benchmark pairs were completely solved by 1 second and only 42\% by the timeout.
-These three divisions also have many fewer benchmarks---a few hundred, rather than several thousand.
-Changing the timeouts further might affect the results of these divisions significantly, but not those of the four divisions with many more benchmarks.
-
 \section{FLoC Olympic Games Scoring}
 \label{sec:floc}
-
-The main track and the application track described in previous sections are staples of recent SMT Competitions.
-The 2014 edition was unique in also being associated with the FLoC Olympic Games~\cite{FLoCGames}.
-This association was positive in providing a platform, along with the other competitions, to present the
-rationale, methodology and results of the SMT Competition to a wider audience than just the SMT community.
-
-One additional aspect that resulted from the Olympic Games was the awarding of three medals to the three ``winners'' of the competition.
-Since SMT-COMP is organized into many separate divisions, with winners determined in each division independently, the organizers had to determine how to award three global prizes.
-The metrics for doing so were the subject of significant discussion both before and after the competition.
-The metrics were decided by the organizers before the competition began (and before the deadline for solver registration) and were maintained unchanged after the competition.
-
-The organizers chose to award the bronze medal for the best performance in a single division.
-We chose  the QF\_BV division for this medal because it is significant to applications and because it traditionally received the most solver submissions.
-Indeed in 2014, there were 8 participants.
-Determining the winner was straightforward: we used the same metric as is used for each division\textemdash the most problems solved without errors, with ties broken by speed of solution.
-The Boolector~\cite{boolector} solver won this division and therefore the bronze medal.
-The results for all participating solvers are shown in Table \ref{Table:bronze}.
-
-The organizers chose to award the silver and gold medals for best performance across the most divisions.
-Thus we needed a metric that combined the results across divisions.
-We considered two metrics.
-For a given solver, let
-\begin{itemize}[noitemsep,nolistsep]
-\item $e_i$ be the number of benchmarks in division $i$ for which an incorrect result was produced (that excludes timeouts, runtime errors and \lstinline{unknown} answers);
-\item $c_i$ be the number of benchmarks in division $i$ solved correctly;
-\item $t_i$ be the total time to solve the benchmarks in division $i$ that were solved correctly;
-\item $N_i$ be the total number of benchmarks in division $i$, used in the competition.
-\end{itemize}
-The normal metric for a division is that the winning solver is the one with the
-smallest value of $e_i$, the largest value of $c_i$
-and then the smallest value of $t_i$, for each division taken separately;
-that is, the metric is a lexicographic ordering by smallest value of $\langle e_i, -c_i, t_i \rangle$.
-The two global metrics we considered are
-\begin{itemize}[noitemsep,nolistsep]
-\item Metric A: The winning solver is the one with the smallest value of $\sum_i e_i \log N_i$, then the largest value of $\sum_i (c_i/N_i)^2 \log N_i$, then the smallest value of $\sum_i t_i \log N_i$, where for a given solver the sums are over all competitive divisions in which that solver participated.
-\item Metric B: The winning solver is the one with the largest value of $\sum_i (e_i == 0\,?\,(c_i/N_i)^2 : - e_i ) \log N_i$, then the smallest value of $\sum_i t_i \log N_i$, where for a given solver the sums are over all competitive divisions in which that solver participated.
-\end{itemize}
-
-Note that incorrect results are very rare in SMT-COMP, but do occur; for almost all solvers and divisions the value of $e_i$ is 0 and the competition hinges on the values of $c_i$.
-The speed of the solver is important in two ways.
-First, if the solver is slow, it will time out before a solution is found and thus the value of $c_i$ will be lower.
-Second, if there is a tie in the number of errors and correctly solved problems, the total time taken on the correctly solved problems is used as the tie-breaker (even if the solvers solve different subsets of benchmarks); this is a rare occurrence but does happen if, for example, all the benchmark problems in a division are solvable within the time limit---the only situation in the competition in which tie-breaking has been needed.
-
-Only \emph{competitive divisions} were included in the scoring (although all divisions were run and results reported).
-For determining medals, a division is competitive if there are at least two officially registered, participating solvers \emph{from different teams}.
-This prevents a team from gaming the scoring by submitting multiple solvers to divisions in which no one else is participating.
-This criterion excluded a number of divisions from medal scoring: AUFNIRA, BV, NIA, NRA, QF\_UFNIA, QF\_UFNRA, UFBV, UFIDL, UFNIA.
-
-The log scaling of the scores for each division is a somewhat arbitrary means to adjust the scores for the wide variety of numbers of benchmarks.
-If each division is treated equally, with a score, say, of 1.0 for the division for solving all the benchmarks in the division correctly, then the benchmarks for small divisions would count significantly more toward a composite score than those of divisions with many benchmarks.
-On the other hand, counting each benchmark equally appeared to underweight the effect of a solver's effort to participate in multiple divisions.
-The log scaling seemed a reasonable compromise between these two extremes.
-Similarly, the square of the fraction successfully solved is an approximate mechanism to give more weight to solving the harder problems.
-
-Metrics A and B above differ in how errors are treated.
-If a solver has no errors, it is always better off to participate in as many divisions as possible.
-However, an error in a division penalizes a solver so that it would be better not to have participated in the division; hence the organizers ruled that once the competition had started, a solver could not be withdrawn from a division in which it was registered.
-
-The penalty for an error is globally significant in Metric A: a single error in one division out of many would put the solver behind any other solver with no errors, even if that other solver participated in just one division.
-The penalty for an error is more local for Metric~B: the error results in a large negative score for that division, which might be compensated by good performance in other divisions.
-Both metrics satisfy the criterion of putting heavy weight on correctness of solvers.
-The organizers published the choice of Metric A as the metric for the Olympic Games gold and silver medals in the rules prior to the beginning of the competition, with no objection during the comment period.
-
-Though all solvers were scored for the medal metrics, five solvers participated in more than two divisions and were the most competitive during the course of the competition.
-The final results are shown in Table \ref{Table:medals}.
-The choice of metric did have a significant effect on the result.
-CVC4 and Yices2 participated in the most divisions, solved the most problems, and did so the most efficiently.
-However, Yices2 had a crash on one problem in QF\_ABV, but had emitted an erroneous answer prior to the crash (a simple crash without an answer is scored the same as an `unknown' response, marked neither wrong nor correct).
-CVC4 had bugs that affected AUFNIRA, which was not a competitive division, and QF\_LIA,
-which was competitive. Consequently, by the competition metric, these two otherwise leading solvers placed much further back in the pack.
-
-When the results were published, the resulting winning teams, veriT and SMTInterpol, put an appeal to the organizers to use Metric B instead, arguing that (i)~CVC4 and Yices2 were clearly the more capable solvers and (ii)~there were known bugs in the winning solvers as well, which, simply by good fortune, were not triggered by the competition benchmarks.
-However, after public comment acknowledging the good will of the winners, the appeal was not accepted by the organizers.
-The medal ceremony did highlight the differing contributions of all four teams as well as those of the bronze medal winner.
-Note that the discovered bugs were promptly fixed.
-In fact, CVC4 submitted an additional demonstration-only version, named CVC4-with-bugfix in the result tables, which the organizers ran in conjunction with the rest of the competition.
-
-\begin{table}
-\caption{Gold and silver medal competition, in winning order by Metric A. By Metric B the order is the same except that CVC4 and Yices2 are in first and second place.}
-\label{Table:medals}
-\centering
-\begin{tabular}{|l|r|rr|r|}
-\hline
-Solver  & Competitive & Metric A & & Metric B \\
- & Divisions & Weighted errors & Weighted solved & \\
-\hline
-veriT & 17 &	0.000 	& 	25.325 & 25.325 \\
-SMTInterpol & 8 &	0.000 	& 	22.831 & 22.831 \\
-CVC3 & 10	& 	0.000 	& 	9.618 & 9.618 \\
-SONOLAR 	& 2	&  	0.000 	& 	5.978 & 	5.978\\
-AProVE 		& 1 & 	0.000 	& 	3.776	& 	3.776\\
-Boolector-j & 1	&  	0.000 	& 	3.758	& 	3.758\\
-Boolector-d & 1		&  	0.000 	& 	3.755 & 	3.755\\
-OpenSMT2 	& 1	&  	0.000 &	3.582 &	3.582\\
-Boolector & 1		&  	0.000 &	3.058  &	3.058 \\
-STP-CryptoMiniSat4 	& 1	&  	0.000 &	2.859 &	2.859\\
-4Simp 	& 1	& 	0.000 	& 	2.468  	& 	2.468 \\
-raSAT 	& 1	& 	0.000 	& 	0.000 	& 	0.000 \\
-Yices2 	& 15	&  	3.810 	& 	38.624 & 31.059 \\
-CVC4 		& 25 &  	7.283 	& 	54.152 & 43.509 \\
-abziz\_min\_features 	& 1	& 	30.563 	& 	2.548 & -30.563 \\
-abziz\_all\_features 	& 1	&  	30.563 	& 	2.403 & -30.563 \\
-Kleaver-STP 	& 1	&  	213.362 	& 	3.103 & -213.362 \\
-Kleaver-portfolio & 1		&  	346.713 	& 	3.073  & -346.713 \\
-\hline
-\end{tabular}
-\end{table}
-
-\begin{table}
-\caption{Bronze medal competition (QF\_BV division, 2488 benchmarks), in winning order.}
-\label{Table:bronze}
-\centering
-\begin{tabular}{|l|rrr|}
-\hline
- Solver & Errors & Solved & Time (sec)\\
-\hline
-Boolector &	0  &		2361  &		138077.59 \\
-STP-CryptoMiniSat4 & 0  &		2283  &		190660.82 	\\
-{[}CVC4-with-bugfix] &	0  &		2237 	 &		139205.24 \\
-{[}MathSAT]  &	0  &		2199 	 &		262349.39 \\
-{[}Z3]  & 	0  &		2180 	 &		214087.66 	\\
-CVC4  &	0  &		2166 	 &		87954.62 	\\
-4Simp &	0 &	2121 	 &		187966.86 \\
-SONOLAR &	0  &		2026  &	 	174134.49 \\
-Yices2 &	0  &		1770  &	 	159991.55 \\
-abziz\_min\_features &	9  &		2155 	 &	 	134385.22 \\
-abziz\_all\_features &	9  &		2093 	 &	 	122540.04 \\
-\hline
-\end{tabular}
-\end{table}
 
@@
 
-After the competition, David Cok (competition chair) and Clark Barrett and Morgan Deters (SMT-LIB coordinators) collaborated, with the assistance of Aaron Stump (StarExec lead), in attempting to discover the status of the SMT-LIB benchmarks that were marked as unknown.
-For this computation, the timeout was set to 10 hours.
-This activity required several weeks of computation.
-A result confirmed by at least two solvers was obtained for~75\% of the unknown benchmarks, with another 4\% having a tentative result from just one solver.
-The results are shown in Table~\ref{Fig:post}.
-
-The unknown incremental benchmarks have yet to be resolved.
-
-\begin{table}
-\caption{Benchmarks resolved in post-competition computation}
-\label{Fig:post}
-\centering
-\begin{tabular}{|l|c|r|rr|rr|r|}
-\hline
-Logic & Solvers & {\pbox{1.1in}{Unknown\\Benchmarks}} & \multicolumn{2}{c|}{\pbox{1.1in}{Resolved by\\2+ solvers as}} & \multicolumn{2}{c|}{\pbox{1.1in}{Resolved by \\ 1 solver as}} & \pbox{.6in}{Still\\unknown} \\
- & & & sat & unsat & sat & unsat & \\
-\hline
-AUFLIRA & 2 & 168 & 0 & 3 & 0 & 3 & 162 \\
-AUFNIRA & 2 & 468 & 0 & 23 & 0 & 23 & 422 \\
-BV & 2 & 191 & 29 & 56 & 42 & 37 & 27 \\
-LRA & 2 & 450 & 20 & 148 & 241 & 23 & 18 \\
-NRA & 2 & 66 & 0 & 41 & 0 & 16 & 9 \\
-QF\_ABV & 4 & 4190 & 3629 & 373 & 0 & 1 & 187 \\
-QF\_BV & 4 & 28138 & 8838 & 19166 & 20 & 10 & 100 \\
-QF\_IDL & 3 & 537 & 324 & 118 & 20 & 14 & 61 \\
-QF\_LIA & 3 & 1279 & 743 & 230 & 234 & 4 & 68 \\
-QF\_LRA & 2 & 208 & 127 & 25 & 44 & 8 & 4 \\
-QF\_NIA & 3 & 927 & 2 & 0 & 39 & 246 & 640 \\
-QF\_NRA & 2 & 1392 & 0 & 36 & 283 & 168 & 905 \\
-QF\_RDL & 2 & 85 & 50 & 0 & 2 & 1 & 32 \\
-QF\_UF & 3 & 4 & 0 & 3 & 0 & 1 & 0 \\
-QF\_UFLRA & 3 & 87 & 82 & 2 & 2 & 0 & 1 \\
-QF\_UFNRA & 2 & 11 & 0 & 2 & 7 & 0 & 2 \\
-UF & 2 & 2911 & 0 & 2 & 51 & 50 & 2808 \\
-UFBV & 2 & 191 & 17 & 49 & 51 & 44 & 30 \\
-UFIDL & 2 & 12 & 0 & 0 & 0 & 0 & 12 \\
-UFLIA & 2 & 5499 & 0 & 1765 & 4 & 113 & 3617 \\
-UFNIA & 2 & 1052 & 0 & 20 & 2 & 90 & 940 \\
-\hline
-Total & & 47866 & 13861 & 22062 & 1042 & 852 & 10045 \\
-\hline
-\end{tabular}
-\end{table}
-
 \section{Concluding Observations and Recommendations}
@@
 
-SMT-COMP 2014 successfully executed the comparison among solvers that is the main goal of the competition.
-The new computational infrastructure, StarExec, worked very well for the purpose.
-The competition saw a renewed interest in participation\textemdash there were record numbers of teams participating, solvers entered, teams and solvers that had never before participated, benchmarks used, and amount of computation performed.
-Although the 2014 results are not readily comparable to previous years (because of changes in benchmarks and equipment), the detailed performance of each solver on each benchmark from this first year using StarExec will be a solid baseline to measure improvements in the state-of-the-art of solver performance in future years.
-As a partial comparison, solvers that performed well in previous years were included in this year's competition.
-
-The SMT steering committee proposed that SMT-COMP 2015 be held in association with the SMT Workshop, which itself will be affiliated with CAV 2015 in San Franciso, CA, USA from July 18-24, 2015.
-The SMT Workshop is being organized by Vijay Ganesh and Dejan Jovanovi\'c; the organizers of the competition are Tjark Weber, David D\'eharbe, and Sylvain Conchon.
-
-\paragraph{Observations}
-
-Solver implementors continue to focus primarily on raw numbers of problems solved. We think that future competitions can 
-help broaden the focus to encompass breadth of problems addressed, fast solutions on simple problems, and other features provided by the SMT-LIB command language.
-
-An unexpected observation is that there is indeed a difference in outcome of even a straightforward competition depending on the value of timeout chosen.
-As a result, there might indeed be an interest and valuable result from trying a competition track focused on fast solving of relatively simple problems.
-
-A satisfying observation is that there is reasonable competition among several highly-performing solvers, as measured by the unique contributions each makes and the distribution of fastest times.
-
-\paragraph{Recommendations.} Based on the experience of 2014, the 2014 organizers have the following recommendations or topics for consideration for future competitions.
-\begin{itemize}
-\item The 2014 competition used all available benchmarks; though the computation resources enable using all benchmarks, future competitions should consider how to make a principled selection to avoid over-representing benchmarks of particular types or origin.
-\item The competition has used numbers of solved benchmarks as the primary success criterion.
-Time to solve benchmarks should be considered more strongly.
-In particular, a separate track that emphasizes fast solution of fairly simple problems might be informative.
-\item Related to the previous point, currently if a solver times-out or issues a response of `unknown', the time taken to do so is not counted in the accumulated time.
-Only the time taken to compute correct responses is counted towards the evaluation metric.
-A user's experience, however, is that the time taken for a solver to say ``I don't know'' is just as important as time to produce a useful answer. Thus we recommend that such
-computation time be included in the evaluation metric. Omitting this time has had no effect so far because time was little used in the overall metric.
-\item The comparison to a previous years' results will now be easier because common hardware will be used and benchmark selection is simplified.
-Future organizers might also include a larger selection of the specific solver versions that were entered in previous competitions.
-\item A key improvement needed is better benchmark sets.
-Though the accumulation of benchmark problems since the inception of the competition is impressive, attention now needs to be paid to the quality and distribution of benchmarks.
-Some divisions are represented by only a few benchmarks; others have large numbers of similar benchmarks.
-Benchmarks representative of application scenarios are particularly important.
-\item Subsequent to SMT-COMP 2014, David Cok, Aaron Stump, Morgan Deters, and Clark Barrett collaborated in resolving the status of many previously unknown benchmarks.
-Those new expected results are not yet included in the SMT-LIB benchmarks on StarExec.
-They should be incorporated into SMT-LIB on StarExec prior to the next competition.
-\item If a global metric is needed again in the future (per \S\ref{sec:floc}), a review and re-discussion of the appropriate metric should be instigated.
-\item Solvers with breadth of application across many logics and solvers that address problems in new logics such as string and floating point computations are important to users.
-Future competitions should add tracks or otherwise find means to reward solvers that implement such capabilities.
-\item Various competition tracks used in the past should be rejuvenated: parallel processing, computation of unsat cores, production of proofs, computation of symbolic models, and computation of concrete counterexamples.
-\item One missing tool is a standard SMT-LIB syntax checker.
-jSMTLIB~\cite{cok2011jsmtlib} has been proposed for this purpose, but is not yet integrated into StarExec.
-The tool also needs to be updated to include the proposed new SMT-LIB features.
-\item The difficulty in preparing a new solver for submission to StarExec for participation in SMT-COMP should be reduced.
-\item A general means to resolve questions surrounding partial definitions is needed in SMT-LIB, e.g., for divide-by-zero  (cf.~\S\ref{par:undefined}).
-\item An item for study is the effect of benchmark scrambling on the outcome of solver comparisons.
-\item Clearly define the subset of SMT-LIB~v2 that solvers must support for a competition and that benchmarks must use.
-\end{itemize}
-
-\section*{Acknowledgments}
-
-\begin{itemize}
-\item The organizers were supported by their respective institutions (GrammaTech, Federal University of Rio Grande do Norte, Brazil and Uppsala University, Sweden respectively).
-In addition, Cok received partial support from the U.S.\ National Science Foundation under grant ACI-1314674.
-
-\item Clark Barrett and Morgan Deters assisted with some aspects of benchmark preparation, in their roles as SMT-LIB coordinators.
-
-\item Aaron Stump and the StarExec support team were essential in keeping the competition cluster running; in this first large-scale, public use of the cluster, numerous small details needed correction and were corrected promptly.
-The StarExec cluster is supported by the U.S.\ National Science Foundation under grants \#1058748 and \#1058925.
-
-\item The cost of executing the SMT Competition is underwritten by the SMT Workshop.
-\end{itemize}
-
-Any opinions, findings, and conclusions or recommendations expressed in this material are those of the authors, and do not necessarily reflect the views of the National Science Foundation.
-
 \bibliographystyle{plainbv}
-\bibliography{SMTCOMP}
+%\bibliography{SMT-COMP}
 
 \end{document}
-
-%% Local Variables:
-%% mode: LaTeX
-%% ispell-local-dictionary: "american"
-%% mode: flyspell
-%% LocalWords: Tjark Uppsala
-%% End:

### 2018-09-21 2018/report/SMT-COMP.tex
Add JSAT Call for Papers
First draft of participants section

@@
 %\usepackage{pst-tree}
+
+\usepackage{pifont}
+\usepackage{comment}
 
@@
 \firstpageno{25}
+
+\specialcomment{tjark}{\begingroup\footnotesize\color{red}}{\color{black}\endgroup}
+\newcommand{\TODO}[0]{\textcolor{red}{TODO}}
+
+\renewcommand{\mark}[0]{\ding{51}}
+
+% TODO
+\setcounter{topnumber}{2}
+\setcounter{bottomnumber}{2}
+\setcounter{totalnumber}{4}
+\renewcommand{\topfraction}{0.85}
+\renewcommand{\bottomfraction}{0.85}
+\renewcommand{\textfraction}{0.15}
+\renewcommand{\floatpagefraction}{0.7}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \begin{abstract}
-TODO
+\TODO
 \end{abstract}
@@
 
+%% Expected content according to the JSAT Call for Papers:
+
+%% Full articles by competition organizers reporting on SAT 2018
+%% competitions and evaluation. The articles should describe the
+%% competition, its criteria, why it is interesting to the SAT
+%% research community, execution environment used, analysis of the
+%% results (including how they compare to previous instantiations, if
+%% appropriate), and give a summary of the main technical
+%% contributions to the field, as well as discussions on lessons
+%% learned and suggestions for improvements for future competitions.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{tjark}
+Changes 2015:
+\begin{itemize}
+\item All solvers will be run with $n=4$ cores available.  We will
+  recognize both best sequential and best parallel performance in all
+  main track divisions, using different CPU time limits.
+\item The division scoring will take time spent on unsolved benchmarks
+  into account.  Previous competitions only considered time spent on
+  solved benchmarks.  However, the number of solved benchmarks still
+  takes precedence over run-time.
+\item In addition to recognizing the best solver in each division, we
+  will recognize solvers that perform best according to
+  competition-wide criteria, emphasizing breadth of supported logics.
+  These criteria will be a refinement of the criteria used for the
+  FLoC Olympic Games medals in~2014.
+\item We plan to include new divisions for floating-point arithmetic.
+  These should be considered experimental in~2015, and will not be
+  included in the competition-wide ranking.
+\item We plan to run solvers on all eligible benchmarks.  Previous
+  competitions used a proper subset of eligible benchmarks, causing
+  competition results to be affected by a random selection process.
+\end{itemize}
+
+Changes 2016:
+\begin{itemize}
+\item Benchmarks will use (a subset of) version~2.5 of the SMT-LIB
+  language.  \emph{Rationale:} This is the latest version of the
+  SMT-LIB language.  It was released on 2015-06-28, and is largely
+  backwards-compatible to version~2.0, which was used for SMT-COMP
+  2015.
+\item Solver output may affect the score even when the solver does not
+  terminate within the time limit.  (In 2015, main track solver output
+  was ignored if the solver subsequently timed out.)  Solvers should
+  take care not to accidentally produce output that contains
+  \texttt{sat} or \texttt{unsat} even when they are killed.
+  \emph{Rationale:} Users are likely to trust solver responses even
+  when the solver continues to run for some time.
+\item Divisions for floating-point arithmetic are no longer
+  experimental, and will be considered competitive if the necessary
+  requirements (see Section~\ref{sec:scoring}) are met.
+  \emph{Rationale:} Floating-point divisions were experimental in
+  2015.  By now, their definition is sufficiently stable, and they are
+  supported by several solvers.
+\item Division scores will be based on a weighted sum of scores for
+  benchmark families.  \emph{Rationale:} For some years now, SMT-COMPs
+  have had sufficient computational resources to evaluate all solver
+  entrants on all eligible benchmarks.  As a side-effect, the
+  weighting of benchmark families that was achieved in early SMT-COMPs
+  through a careful selection of benchmarks (based on benchmark
+  difficulty and category) was lost.  Since there are vast differences
+  in size between benchmark families, we believe that a weighting that
+  de-emphasizes large benchmark families (see
+  Section~\ref{sec:division-scoring}) will lead to more meaningful
+  competition results.
+\item The unsat-core track that was introduced in SMT-COMP 2012, but
+  discontinued in 2013-2015 (partly because of the competition's move
+  to StarExec), is back.  It will be experimental in 2016; its results
+  will be reported, but no official winners will be announced.
+  \emph{Rationale:} Unsat cores are important in many applications of
+  SMT solving.  The track was discontinued primarily for
+  infrastructure and resource reasons.  We are pleased that we can
+  finally offer it again, but we ask for your understanding in case of
+  mishaps while we port the required tools.
+\item Best industrial performance will no longer be recognized
+  separately.  \emph{Rationale:} While there is agreement in the SMT
+  community to emphasize problems that come from real applications,
+  industrial performance largely coincided with overall performance in
+  SMT-COMP 2015.  We consider the effort to determine and report it
+  separately no longer justified.
+\end{itemize}
+
+Changes 2017:
+\begin{itemize}
+\item Submission of accompanying information for solvers is via a web
+  form (rather than by email to the organizers).  \emph{Rationale:}
+  Email submissions were often incomplete, leading to ambiguity and
+  further inquiries.  The form provides a more structured way of
+  submitting information.
+\item Benchmarks will use (a subset of) version~2.6 of the SMT-LIB
+  language.  \emph{Rationale:} This is the latest version of the
+  SMT-LIB language.  It is largely backwards-compatible with earlier
+  versions (in particular~2.0 and~2.5).
+\item Benchmarks that use partial bit-vector functions, such as
+  \texttt{bvudiv}, or underspecified floating-point functions, such as
+  \texttt{fp.min}, will be eligible for the competition again.
+  \emph{Rationale:} A conclusion on the semantics of these functions
+  has finally been reached, and the status of affected SMT-LIB
+  benchmarks has been updated accordingly.
+\item Benchmarks with unknown status will be eligible for the
+  competition's main track.  In 2016, solver performance on benchmarks
+  with unknown status was evaluated but reported separately; in 2017,
+  it will directly affect the competition results.  \emph{Rationale:}
+  Using only benchmarks with known status (i.e., benchmarks that have
+  been solved before) to determine the competition results unjustly
+  favors imitation of existing solvers over true innovation.
+\item In the competition-wide scoring, the (per-division) penalty for
+  erroneous results is changed from the number of errors to a fixed
+  constant (multiplied by the weight of the respective division).
+  \emph{Rationale:} The weight already takes the number of benchmarks
+  in the division into account; multiplying it by the number of errors
+  overemphasizes large divisions.
+\item The unsat-core track, which was re-introduced in 2016, is no
+  longer experimental.  Its divisions will be considered competitive
+  if the necessary requirements (see Section~\ref{sec:scoring}) are
+  met.  \emph{Rationale:} Rules and tool support for the unsat-core
+  track proved sufficiently stable in 2016.
+\item The competition will feature experimental divisions for
+  benchmarks that use algebraic datatypes.  \emph{Rationale:}
+  Algebraic datatypes are specified in the draft SMT-LIB~2.6 standard,
+  which is expected to become official in the near future, and are
+  already supported by some solvers.  Benchmarks that use datatypes
+  have recently been added to SMT-LIB.
+\end{itemize}
+
+Changes 2018:
+\begin{itemize}
+\item The time limit per solver/benchmark pair is anticipated to be at
+  most 20 minutes in the main track, and at most 40 minutes in the
+  other tracks.  \emph{Rationale:} Already in 2017, the time limit for
+  the main track was reduced to 20 minutes (down from 40 minutes in
+  earlier years) to cope with the inclusion of a large number of
+  benchmarks with unknown status.
+\item In the unsat-core track, the unsatisfiability check for the
+  returned core will be based on a simple majority vote.  The case
+  that a solver finds its own core satisfiable will no longer be
+  treated specially.  \emph{Rationale:} This allows to simplify the
+  post-processing of unsat-core track results considerably.
+\item In 2017, the competition featured experimental divisions for
+  benchmarks that use algebraic datatypes.  These divisions will be
+  regular (non-experimental) in 2018. \emph{Rationale:} Algebraic
+  datatypes are specified in the latest official release (Version~2.6)
+  of the SMT-LIB standard.
+\item The competition will feature an experimental divisions for
+  benchmarks that use strings.  \emph{Rationale:} Corresponding
+  theories and benchmarks are expected to be added to SMT-LIB in the
+  near future.
+\end{itemize}
+\end{tjark}
+
 \section{Introduction}
 \label{sec:intro}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section{SMT-LIB Logic, Language and Solvers}
 \label{sec:context}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section{Participants}
 \label{sec:participants}
+
+Participants must upload their solvers to StarExec (see
+Section~\ref{sec:starexec}) to enter them into the competition, and
+additionally submit information about each competing solver---such as
+the tracks and divisions into which the solver is being entered---to
+the competition organizers.  Until 2016, this information was
+collected by email.  Since 2017, a web form is being used for this
+purpose.  This has greatly reduced the number of incomplete or
+ambiguous submissions.
+
+Table~\ref{table:participants} lists the solvers that participated
+between~2015 and~2018, together with their submitter(s) and
+institutional affiliations (which may have changed over time).  Note
+that most solvers were developed by a group of people; the table does
+not list all contributors but only submitters.
+%
+Participants are also encouraged to submit a short system description
+of their solver, including a list of its authors and an explanation of
+the SMT solving approach used.  System descriptions are published on
+the SMT-COMP website~\cite{smtcomp-web}.  They were submitted for
+about 60\,\% of all solver versions since 2015.
+
+\begin{table}
+  \caption{Participants (2015--2018)}
+  \label{table:participants}
+  \centering
+  \begin{tabular}{|l|p{13cm}|} %TODO: fix width
+    \hline
+    Solver & Submitters (Affiliations)\\
+    \hline
+    ABC [\TODO]       & Valera Balabanov
+                        (Mentor Graphics)\\
+    Alt-Ergo          & Albin Coquereau
+                        (CNRS and University of Paris-Sud)\\
+    AProVE            & Carsten Fuhs
+                        (University College London; Birkbeck, University of London)\\
+    Boolector         & Mathias Preiner
+                        (Johannes Kepler University)\\
+    COLIBRI           & Fran\c{c}ois Bobot
+                        (French Alternative Energies and Atomic Energy Commission)\\
+    Ctrl-Ergo         & Mohamed Iguernlala
+                        (CNRS and University of Paris-Sud)\\
+    CVC3              & Kshitij Bansal
+                        (New York University)\\
+    CVC4              & Kshitij Bansal, Clark Barrett, Andres N\"otzli, Duligur Ibeling
+                        (New York University; Stanford University)\\
+    MapleSTP          & Jimmy Liang
+                        (University of Waterloo)\\
+    MinkeyRink        & Trevor Hansen
+                        (University of Melbourne)\\
+    OpenSMT2          & Matteo Marescotti, Antti Hyv\"arinen
+                        (University of Lugano)\\
+    ProB              & Sebastian Krings
+                        (University of D\"usseldorf)\\
+    Q3B               & Martin Jon\'a\v{s}
+                        (Masaryk University)\\
+    raSAT             & Tung Vu Xuan
+                        (Japan Advanced Institute of Science and Technology)\\
+    Redlog            & Haniel Barbosa
+                        (Inria Nancy)\\
+    SMT-RAT           & Florian Corzilius, Gereon Kremer
+                        (RWTH Aachen University)\\
+    SMTInterpol       & J\"urgen Christ
+                        (University of Freiburg)\\
+    SPASS-SATT        & Martin Bromberger
+                        (Max Planck Institute for Informatics)\\
+    STP               & Mate Soos, Trevor Hansen, Norbert Manthey
+                        (National University of Singapore; University of Melbourne; Amazon Web Services)\\
+    toysmt            & Masahiro Sakai
+                        (\TODO)\\
+    Vampire           & Giles Reger
+                        (University of Manchester)\\
+    veriT             & David D\'eharbe, Haniel Barbosa, Hans-J\"org Schurr
+                        (Federal University of Rio Grande do Norte; Inria Nancy)\\
+    XSat              & Martin Velez
+                        (University of California, Davis)\\
+    Yices2            & Bruno Dutertre, Dejan Jovanovi\'c
+                        (SRI International)\\
+    Z3                & Christoph Wintersteiger, Aleksandar Zelji\'c
+                        (Microsoft Research; Uppsala University)\\
+    \hline
+  \end{tabular}  
+\end{table}
+
+Many of these solvers were submitted in multiple years.  Additionally,
+to promote a wide comparison between tools, developers are allowed to
+submit multiple versions of a solver, e.g., for different competition
+tracks or with differently tuned internal components.
+Table~\ref{table:participants-history} shows in more detail how many
+versions of each solver were submitted in each year.
+
+\begin{table}
+  \caption{Number of versions submitted for each solver (by year).
+    Numbers in square brackets indicate solver versions that were
+    participating hors concours.}
+  \label{table:participants-history}
+  \centering
+  \begin{tabular}{|l|r@{\,\,}r|r@{\,\,}r|r@{\,\,}r|r@{\,\,}r|}
+    \hline
+    Solver & \multicolumn{2}{c|}{2015} & \multicolumn{2}{c|}{2016} & \multicolumn{2}{c|}{2017} & \multicolumn{2}{c|}{2018} \\
+    \hline
+    ABC               &    &      &  2 &      &    &      &    &      \\
+    Alt-Ergo          &    &      &    &      &    &      &  1 &      \\
+    AProVE            &  1 &      &  1 &      &  1 &      &  1 &      \\
+    Boolector         &  3 & [+1] &  2 &      &  2 &      &  2 &      \\
+    COLIBRI           &    &      &    &      &  1 &      &  1 &      \\
+    Ctrl-Ergo         &    &      &    &      &    &      &  1 &      \\
+    CVC3              &  2 &      &    &      &    &      &    &      \\
+    CVC4              &  4 &      &  1 & [+1] &  3 &      &  3 & [+1] \\
+    MapleSTP          &    &      &  4 &      &    &      &    &      \\
+    {[}MathSAT{]}     &    & [+2] &    & [+3] &    & [+3] &    & [+3] \\
+    MinkeyRink        &    &      &  1 &      &  1 &      &  2 &      \\
+    OpenSMT2          &  2 &      &  1 &      &  1 &      &    & [+1] \\
+    ProB              &    &      &  1 &      &    &      &    &      \\
+    Q3B               &    &      &  1 &      &  1 &      &  1 &      \\
+    raSAT             &  1 &      &  2 &      &    &      &    &      \\
+    Redlog            &    &      &    &      &  1 &      &    &      \\
+    SMT-RAT           &  2 &      &  1 &      &  1 &      &  2 &      \\
+    SMTInterpol       &  1 &      &  1 &      &  1 &      &  1 &      \\
+    SPASS-SATT        &    &      &    &      &    &      &  1 &      \\
+    STP               &  4 &      &  8 &      &  2 &      &  3 &      \\
+    toysmt            &    &      &  1 &      &    &      &    &      \\
+    Vampire           &    &      &  2 &      &  1 &      &  1 &      \\
+    veriT             &  1 &      &  1 &      &  3 &      &  2 &      \\
+    XSat              &    &      &    &      &  1 &      &    &      \\
+    Yices2            &  3 &      &  2 &      &  2 &      &  3 &      \\
+    Z3                &  2 & [+1] &    & [+1] &    & [+1] &    & [+1] \\
+    \hline
+    Total             & 26 & [+4] & 32 & [+5] & 22 & [+4] & 25 & [+6] \\
+    \hline
+  \end{tabular}
+\end{table}
+
+In addition to the solvers that were submitted to the competition by
+their respective developers, the organizers included the most recent
+stable versions of MathSAT and Z3 for comparison purposes.  Both
+solvers are strong tools, but---except for two experimental versions
+of Z3 in 2015---their development teams chose not to prepare
+competition versions.  These solvers were therefore participating hors
+concours.  Moreover, in 2015 a bug was discovered in the application
+track version of Boolector and a fixed version was submitted after the
+deadline; in 2016, the CVC4 team did not enter their solver into the
+application track; and in 2018, an experimental version of CVC4 as
+well as the OpenSMT2 solver were submitted after the deadline.  These
+solvers were also participating hors concours.  In result tables, they
+are listed with their name in square brackets (e.g., [MathSAT]).
+
+Table~\ref{table:participation-by-track} summarizes these figures and
+shows how many solver versions were submitted to each track of the
+competition.  Note that solver versions may be entered into multiple
+tracks.  Therefore, the total number of solver versions for each year
+is typically less than the sum over all tracks.
+
+By number of solver versions submitted, the competitions in 2015--2018
+were the four largest in the history of SMT-COMP.  On average, 26
+solver versions were submitted each year since 2015.  In contrast, the
+competitions from 2005--2014 only received an average of 12
+submissions~\cite{smtcomp-2014}.
+
+\begin{table}
+  \caption{Participation by track and year.  Numbers in square
+    brackets indicate solver versions that were participating hors
+    concours.}
+  \label{table:participation-by-track}
+  \centering
+  \begin{tabular}{|l|r@{\,\,}r|r@{\,\,}r|r@{\,\,}r|r@{\,\,}r|}
+    \hline
+                      & \multicolumn{2}{c|}{2015} & \multicolumn{2}{c|}{2016} & \multicolumn{2}{c|}{2017} & \multicolumn{2}{c|}{2018} \\
+    \hline
+    Main track        & 21 &                [+2] & 25 & [+2] & 19 & [+2] & 20 & [+4] \\
+    Application track & 10 &                [+3] &  8 & [+3] &  4 & [+2] &  4 & [+2] \\
+    Unsat-core track  & \multicolumn{2}{c|}{---} &  1 & [+4] &  2 & [+2] &  3 & [+2] \\
+    \hline
+    Total             & 26 &                [+4] & 32 & [+5] & 22 & [+4] & 25 & [+6] \\
+    \hline
+  \end{tabular}
+\end{table}
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section{Post-Competition Activity}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section{Concluding Observations and Recommendations}
 \label{sec:conclusions}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 \end{document}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+% Local Variables:
+% ispell-local-dictionary: "american"
+% mode: LaTeX
+% mode: flyspell
+% LocalWords: concours hors satisfiability SMT Tjark
+% End:

### 2018-09-24 2018/report/SMT-COMP.tex
Minor progress on organization/timeline

@@
 
+The SMT Competition is organized under the direction of the SMT
+Steering Committee, which appoints the competition chair.  This
+appointment should happen ``within 30 days from the end of the current
+edition of the SMT workshop''~\cite{smt-bylaws} but in practice has
+often happened later.  It is then up to the competition chair to
+assemble a team of organizers, and to distribute the work for the next
+competition.
+
+Each year, the SMT Workshop includes a block of time to present the
+competitors and results of the competition.  The workshop is
+affiliated with a different conference each year: with CAV in 2015,
+with IJCAR in 2016, again with CAV in 2017, and with FLoC in 2018.
+Consequently, its date varies by several weeks.  Competition results
+were presented on July~19 in 2015, on July~2 in 2016, on July~23 in
+2017, and on July~13 in 2018.
+
+Important deadlines are effectively determined by calculating
+backwards from the date of the next SMT Workshop.  The competition's
+computational workload should be completed approximately two weeks
+before the workshop date, to give participants and other parties a
+chance to scrutinize the data for errors, allow partial re-runs of
+competition jobs if necessary, and give the organizers time to prepare
+the results presentation.  While making all data publicly available
+well in advance of the official results presentation may impact the
+suspense, it has on several occasions helped to uncover serious
+problems with the competition tools or the StarExec framework (see
+Section~\ref{sec:starexec}) that could have led to invalid results if
+they had gone unnoticed.
+\begin{tjark}
+  Discuss these issues somewhere, add (forward?) reference here.
+\end{tjark}
+
+It takes up to three weeks to run all competition jobs on the StarExec
+cluster, so the final submission deadline for solvers needs to be
+about five weeks before the workshop date.  The competition imposes a
+separate deadline for first versions of solvers about seven weeks
+before the workshop date.  This deadline has proved useful for the
+organizers to obtain an accurate estimate on the number of competing
+solvers, and to run preliminary tests with some of the submitted
+solvers to identify potential issues.  Participants can still make
+changes to their solver until the final deadline but are encouraged to
+use this period for bug-fixing only.
+
+Around the initial solver deadline, the organizers also aim to publish
+the latest version of the competition tools, and--in collaboration
+with the SMT-LIB maintainers--to release a new version of the SMT
+Library.
+
+\begin{tjark}
+  WIP
+
+  Also: Call for Comments in February/March\\
+  Draft rules in April
+
+  SMT-LIB release dates:\\
+  2015-06-01 (vs. 06-01)\\
+  2016-05-23 (vs. 05-15)\\
+  2017-06-05 (vs. 06-04)\\
+  2018-05-20 (vs. 05-27)
+\end{tjark}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2018-10-08 2018/report/SMT-COMP.tex
Some introduction

@@
 \ShortHeadings{The SMT Competition 2015--2018}
-{TODO et al.}
+{Weber et al.}
 \firstpageno{25}
@@
 
-\author{\name{Sylvain Conchon (co-organizer, 2015--2016)}
+\author{%
+  \name{Tjark Weber (competition chair, 2015--2018)}
+  \email{tjark.weber@it.uu.se} \\
+  \addr Uppsala University \\
+  Uppsala \\
+  Sweden
+  \AND
+  \name{Sylvain Conchon (co-organizer, 2015--2016)}
   \email{Sylvain.Conchon@lri.fr} \\
@@
   City \\
-Country
-\AND
-\name{Tjark Weber (competition chair, 2015--2018)}
-\email{tjark.weber@it.uu.se} \\
-\addr Uppsala University \\
-Uppsala \\
-Sweden}
+  Country}
 
@@
 \begin{abstract}
-\TODO
+  The International Satisfiability Modulo Theories Competition is an
+  annual competition between Satisfiability Modulo Theories solvers.
+  We report on the design and selected results of the competition
+  during the last FLoC Olympiad, from 2015 to 2018. \TODO: some
+  notable observations/conclusions?
 \end{abstract}
@@
 \label{sec:intro}
+
+Satisfiability Modulo Theories (SMT) is a generalization of Boolean
+satisfiability (SAT), the satisfiability decision problem for
+propositional logic.  In place of Boolean variables, SMT formulas may
+contain terms that are built from function and predicate symbols drawn
+from a number of background theories.  Background theories, which are
+typically motivated by application areas, include the theory of
+arrays, integer and real arithmetic, bit-vectors, and floating-point
+numbers among others.  For instance, the following is an SMT formula
+over the combination of integer arithmetic and uninterpreted
+functions:
+$$TODO$$
+Software tools to determine the satisfiability of such formulas are
+called SMT solvers.
+
+Internally, many SMT solvers employ SAT solving techniques to deal
+with the propositional structure of the formula, and combine these
+with (semi-)decision procedures for the background theories that the
+solver supports~\cite{TODO,TODO,TODO}.  Historically, SMT solvers have
+focused on quantifier-free formulas and decidable combinations of
+background theories.  Increasingly, however, SMT solvers also support
+quantified formulas.  Hence there is overlap between SMT solving and
+automated theorem proving for quantified Boolean formulas (QBF),
+first-order logic, and even higher-order logic~\cite{TODO}.
+
+The International Satisfiability Modulo Theories Competition
+(SMT-COMP) is an annual competition between SMT solvers.  It is
+affiliated with the International Workshop on Satisfiability Modulo
+Theories.  Solvers are submitted to the competition by their
+developers, and pitted against each other in a number of tracks and
+divisions.  The SMT Competition was part of the Federated Logic
+Conference (FLoC) Olympic Games in~2014, and again in~2018.  It was
+last described in a 2014 competition report~\cite{TODO}.  In this
+paper, we report on the design and selected results of the competition
+during the last FLoC Olympiad, from 2015 to 2018.
+
+\begin{tjark}
+  WIP
+
+  structure of the paper
+\end{tjark}
 

### 2018-10-08 2018/report/SMT-COMP.tex
Work in progress

@@
   The International Satisfiability Modulo Theories Competition is an
-  annual competition between Satisfiability Modulo Theories solvers.
-  We report on the design and selected results of the competition
-  during the last FLoC Olympiad, from 2015 to 2018. \TODO: some
-  notable observations/conclusions?
+  annual competition between Satisfiability Modulo Theories~(SMT)
+  solvers.  The 2018 edition of the competition was part of the FLoC
+  Olympic Games, which comprised 14 competitions in various areas of
+  computational logic.  We report on the design and selected results
+  of the SMT Competition during the last FLoC Olympiad, from 2015 to
+  2018. \TODO: some notable observations/conclusions?
 \end{abstract}
@@
 from a number of background theories.  Background theories, which are
-typically motivated by application areas, include the theory of
-arrays, integer and real arithmetic, bit-vectors, and floating-point
-numbers among others.  For instance, the following is an SMT formula
-over the combination of integer arithmetic and uninterpreted
-functions:
-$$TODO$$
+typically motivated by application domains, include the theory of
+arrays~\cite{TODO}, integer and real arithmetic~\cite{TODO},
+bit-vectors~\cite{TODO}, and floating-point numbers~\cite{TODO} among
+others.  For instance, the following is an SMT formula over the
+combination of integer arithmetic and uninterpreted functions:
+%
+$$x \leq y \wedge y \leq x \wedge P (f(x) - f(y)) \wedge \neg P(0)$$
+%
 Software tools to determine the satisfiability of such formulas are
-called SMT solvers.
+called SMT solvers.  With its rich input language, SMT has
+applications in software engineering, optimization, and many other
+areas~\cite{DeMoura:2011:SMT}.
 
@@
 divisions.  The SMT Competition was part of the Federated Logic
-Conference (FLoC) Olympic Games in~2014, and again in~2018.  It was
-last described in a 2014 competition report~\cite{TODO}.  In this
-paper, we report on the design and selected results of the competition
-during the last FLoC Olympiad, from 2015 to 2018.
+Conference (FLoC) Olympic Games, which comprised 14 competitions in
+various areas of computational logic, in Vienna in~2014, and again in
+Oxford~(UK) in~2018.  It was last described in a 2014 competition
+report~\cite{DBLP:journals/jsat/CokDW14}.  In this paper, we report on
+the design and selected results of the competition during the last
+FLoC Olympiad, from 2015 to~2018.
 
@@
 affiliated with a different conference each year: with CAV in 2015,
-with IJCAR in 2016, again with CAV in 2017, and with FLoC in 2018.
+with IJCAR in 2016, again with CAV in 2017, and with FLoC in~2018.
 Consequently, its date varies by several weeks.  Competition results
@@
 problems with the competition tools or the StarExec framework (see
-Section~\ref{sec:starexec}) that could have led to invalid results if
-they had gone unnoticed.
+Section~\ref{sec:starexec}) that could have led to invalid results
+otherwise.
 \begin{tjark}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section{Competition Procedure}
 \label{sec:procedure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-\section{Other Competitions}
-\label{sec:OtherCompetitions}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-\section{FLoC Olympic Games Scoring}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{FLoC Olympic Games}
 \label{sec:floc}
+
+In 2014, the SMT Competition was part of the FLoC Olympic Games, which
+sponsored three Kurt G\"odel medals.  After substantial internal
+debate, the competition organizers decided to award these to the
+winner of the QF\_BV logic (which has historically been the logic with
+the largest number of solver submissions), as well as to the two best
+main-track solvers according to a competition-wide ranking that had
+been instituted especially for this
+purpose~\cite{DBLP:journals/jsat/CokDW14}.
+
+The 2018 edition of the competition was again part of the FLoC Olympic
+Games.  After last-minute negotiations with the Olympic Games
+organizers, it was decided that the SMT Competition would award seven
+Kurt G\"odel medals.  The competition organizers gave these to the
+following solvers:
+\begin{itemize}
+\item The best three main-track solvers according to the
+  competition-wide scoring (first place: CVC4, second place:
+  Yices-2.6.0, third place: SMTInterpol);
+\item the solver that won the most competitive divisions in the
+  application track (Yices-2.6.0);
+\item the solver that won the most competitive divisions in the
+  unsat-core track (Yices-2.6.0);
+\item the solver(s) that won the QF\_BV division in the main track
+  (sequential ranking: Boolector, parallel ranking: Minkeyrink-MT)
+\end{itemize}
+
+The competition-wide ranking that was used in~2018 was a refinement of
+the ranking scheme introduced in~2014.  A contentious issue has been
+the treatment of incorrect solver results in this ranking.  While
+incorrect answers cause a solver to be ranked behind all correct
+solvers in the per-division ranking (see \TODO )
 
@@
 
-\section{Concluding Observations and Recommendations}
+\section{Conclusions}
 \label{sec:conclusions}
@@
 
-\bibliographystyle{plainbv}
-%\bibliography{SMT-COMP}
+\bibliographystyle{plainbv} \bibliography{SMT-COMP}
 

### 2018-10-08 2018/report/SMT-COMP.tex
FLoC Olympic Games (work in progress)

@@
 
-In 2014, the SMT Competition was part of the FLoC Olympic Games, which
-sponsored three Kurt G\"odel medals.  After substantial internal
-debate, the competition organizers decided to award these to the
-winner of the QF\_BV logic (which has historically been the logic with
-the largest number of solver submissions), as well as to the two best
-main-track solvers according to a competition-wide ranking that had
-been instituted especially for this
-purpose~\cite{DBLP:journals/jsat/CokDW14}.
+In 2014, the SMT Competition was part of the FLoC Olympic Games.
+These gave the competition increased visibility and sponsored three
+Kurt G\"odel medals.  After substantial internal debate, the 2014
+competition organizers decided to award these to the winner of the
+main track's QF\_BV division (which has historically been the logic
+with the largest number of solver submissions), as well as to the two
+best main-track solvers according to a competition-wide ranking that
+had been instituted especially for this
+purpose~\cite{DBLP:journals/jsat/CokDW14}.  This ranking emphasizes
+breadth of solver participation---a solver participating in many
+logics need not be the best in any one of them to rank highly.
+
+The competition-wide ranking for the main track was retained and
+refined after~2014.  A contentious issue in this ranking has been the
+scoring of incorrect solver responses.  In the per-division rankings,
+an incorrect response causes a solver to be ranked behind all correct
+solvers~\cite{rules18}.  But the competition's main track consists of
+many independent divisions.  To balance the strong interest in correct
+solvers against the risk of stifling innovation, the competition-wide
+ranking was revised in~2017 to use a fixed numeric penalty for each
+division with incorrect responses.  The value of this penalty is
+chosen so that entering a (possibly buggy) solver that can solve all
+benchmarks into a division has a positive expected score if the
+probability of a soundness bug in the solver is below~$20\,\%$.
 
@@
 organizers, it was decided that the SMT Competition would award seven
-Kurt G\"odel medals.  The competition organizers gave these to the
-following solvers:
+Kurt G\"odel medals.  The 2018 competition organizers conferred these
+to the following solvers:
 \begin{itemize}
@@
   Yices-2.6.0, third place: SMTInterpol);
+\item the solver(s) that won the QF\_BV division in the main track
+  (sequential ranking: Boolector, parallel ranking: Minkeyrink-MT);
 \item the solver that won the most competitive divisions in the
@@
 \item the solver that won the most competitive divisions in the
-  unsat-core track (Yices-2.6.0);
-\item the solver(s) that won the QF\_BV division in the main track
-  (sequential ranking: Boolector, parallel ranking: Minkeyrink-MT)
+  unsat-core track (Yices-2.6.0).
 \end{itemize}
 
-The competition-wide ranking that was used in~2018 was a refinement of
-the ranking scheme introduced in~2014.  A contentious issue has been
-the treatment of incorrect solver results in this ranking.  While
-incorrect answers cause a solver to be ranked behind all correct
-solvers in the per-division ranking (see \TODO )
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Post-Competition Activity}
-\label{sec:post}
+\begin{tjark}
+  Discuss competition-wide rankings for application and unsat-core
+  tracks.
+\end{tjark}
 

### 2018-10-09 2018/report/SMT-COMP.tex
Goals, FLoC ranking

@@
 
-The SMT Competition is organized under the direction of the SMT
-Steering Committee, which appoints the competition chair.  This
-appointment should happen ``within 30 days from the end of the current
-edition of the SMT workshop''~\cite{smt-bylaws} but in practice has
-often happened later.  It is then up to the competition chair to
-assemble a team of organizers, and to distribute the work for the next
-competition.
+The SMT Competition was instituted in 2005.  It has been held annually
+since then (with the exception of 2013, when an
+evaluation~\cite{DBLP:journals/jar/CokSW15} was conducted instead of a
+competition).  The main goals of the competition were to spur adoption
+of the common, community-designed SMT-LIB formats (see
+Section~\ref{sec:smtlib}), and to spark further advances in SMT,
+especially for verification~\cite{smtcomp2005}.  These, together with
+providing a useful yardstick for users and developers of SMT solvers,
+are still its main goals today.  The competition has been successful
+in establishing SMT-LIB as the \emph{de facto} standard language for
+SMT solvers.  In recent years, the focus in this regard has shifted
+towards promoting some of the newer extensions of the SMT-LIB
+language, such as a floating-point theory~\cite{TODO} or algebraic
+datatypes~\cite{TODO}.
 
-Each year, the SMT Workshop includes a block of time to present the
-competitors and results of the competition.  The workshop is
-affiliated with a different conference each year: with CAV in 2015,
-with IJCAR in 2016, again with CAV in 2017, and with FLoC in~2018.
-Consequently, its date varies by several weeks.  Competition results
-were presented on July~19 in 2015, on July~2 in 2016, on July~23 in
-2017, and on July~13 in 2018.
+The competition is organized under the direction of the SMT Steering
+Committee, which appoints the competition chair.  This appointment
+should happen ``within 30 days from the end of the current edition of
+the SMT workshop''~\cite{smt-bylaws} but in practice has often
+happened later.  The competition chair then assembles a team of
+organizers, and distributes the work for the next competition.
+%
+The SMT Workshop includes a block of time to present the competitors
+and results of the competition.  The workshop is affiliated with a
+different conference each year: with CAV in 2015, with IJCAR in 2016,
+again with CAV in 2017, and with FLoC in~2018.  Consequently, its date
+varies by several weeks.  Competition results were presented on
+July~19 in 2015, on July~2 in 2016, on July~23 in 2017, and on July~13
+in~2018.
 
@@
 Around the initial solver deadline, the organizers also aim to publish
-the latest version of the competition tools, and--in collaboration
-with the SMT-LIB maintainers--to release a new version of the SMT
-Library.
+the latest version of the competition tools, and---in collaboration
+with the SMT-LIB maintainers---to release a new version of the SMT
+Library.  SMT-LIB releases were made on June~1 in 2015, on May~23 in
+2016, on June~5 in 2017, and on May~20 in 2018.  Anyone may submit new
+benchmarks to the SMT Library, and competitors are permitted to tune
+their solvers accordingly.  Therefore it is important that all
+benchmarks eligible for the competition are released at least some
+time before the final solver submission deadline.  To give the SMT-LIB
+maintainers sufficient time for curation, the deadline for new
+benchmark contributions has usually been about four to six weeks
+before the initial solver deadline, typically in April or early May.
 
-\begin{tjark}
-  WIP
-
-  Also: Call for Comments in February/March\\
-  Draft rules in April
-
-  SMT-LIB release dates:\\
-  2015-06-01 (vs. 06-01)\\
-  2016-05-23 (vs. 05-15)\\
-  2017-06-05 (vs. 06-04)\\
-  2018-05-20 (vs. 05-27)
-\end{tjark}
+The competition rules are revised each year, and a (near final) draft
+version of the rules is made public on the competition web site
+typically around mid-April.  The competition chair has ultimate
+responsibility for the rules, but changes are often preceded by
+discussions among the organizers or within the SMT community.  Such
+discussions are initiated by a Call for Comments that is typically
+sent out to the SMT-COMP mailing list~\cite{TODO} in February or early
+March.  Publicly, this call is the first harbinger of a new edition of
+the SMT Competition.
 
@@
 competitions from 2005--2014 only received an average of 12
-submissions~\cite{smtcomp-2014}.
+submissions~\cite{DBLP:journals/jsat/CokDW14}.
 
@@
 main track's QF\_BV division (which has historically been the logic
-with the largest number of solver submissions), as well as to the two
-best main-track solvers according to a competition-wide ranking that
-had been instituted especially for this
+with the largest number of solver submissions and job pairs), as well
+as to the two best main-track solvers according to a competition-wide
+ranking that had been instituted especially for this
 purpose~\cite{DBLP:journals/jsat/CokDW14}.  This ranking emphasizes
@@
 The competition-wide ranking for the main track was retained and
-refined after~2014.  A contentious issue in this ranking has been the
-scoring of incorrect solver responses.  In the per-division rankings,
-an incorrect response causes a solver to be ranked behind all correct
-solvers~\cite{rules18}.  But the competition's main track consists of
-many independent divisions.  To balance the strong interest in correct
-solvers against the risk of stifling innovation, the competition-wide
-ranking was revised in~2017 to use a fixed numeric penalty for each
-division with incorrect responses.  The value of this penalty is
-chosen so that entering a (possibly buggy) solver that can solve all
-benchmarks into a division has a positive expected score if the
-probability of a soundness bug in the solver is below~$20\,\%$.
+refined after~2014.  A contentious issue with this ranking has been
+the scoring of incorrect solver responses.  In the per-division
+rankings, an incorrect response causes a solver to be ranked behind
+all correct solvers~\cite{rules18}.  But the competition's main track
+consists of many independent divisions.  To balance the strong
+interest in correct solvers against the risk of stifling innovation,
+the competition-wide ranking was revised in~2017 to use a fixed
+numeric penalty for each division with incorrect responses.  The value
+of this penalty is set so that entering a (possibly buggy) solver that
+can solve all benchmarks into a division has a positive expected score
+if the probability of a soundness bug in the solver is below~$20\,\%$.
 
@@
 \item The best three main-track solvers according to the
-  competition-wide scoring (first place: CVC4, second place:
+  competition-wide ranking (first place: CVC4, second place:
   Yices-2.6.0, third place: SMTInterpol);
@@
 
-\begin{tjark}
-  Discuss competition-wide rankings for application and unsat-core
-  tracks.
-\end{tjark}
+In comparison to the competition-wide ranking for the main track, the
+metric used for the application and unsat-core track---simply counting
+the number of competitive divisions that a solver has won---was fairly
+unsophisticated.  Future editions of the competition should perhaps
+refine this to use a ranking scheme that is more similar to the
+main-track ranking, by weighing divisions according to their relative
+importance, and by also rewarding good performance by solvers other
+than division winners.  A difficulty in adapting the main-track
+ranking for the other tracks is that each main-track benchmark is
+worth one point (before weighing) if solved correctly, while
+benchmarks in the application and unsat-core track are worth a varying
+number of points.  Moreover, in the unsat-core track, the size of the
+smallest unsatisfiable core---and hence the number of points
+attainable on any given benchmark---may not be known precisely.
 
@@
 
+\TODO
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-\bibliographystyle{plainbv} \bibliography{SMT-COMP}
+\bibliographystyle{plainbv}
+\bibliography{SMT-COMP}
 

### 2018-10-11 2018/report/SMT-COMP.tex
Work in progress

@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section{Introduction}
-\label{sec:intro}
+\label{sec:introduction}
 
@@
 from a number of background theories.  Background theories, which are
-typically motivated by application domains, include the theory of
+motivated by application domains, include the theory of
 arrays~\cite{TODO}, integer and real arithmetic~\cite{TODO},
@@
 The International Satisfiability Modulo Theories Competition
-(SMT-COMP) is an annual competition between SMT solvers.  It is
-affiliated with the International Workshop on Satisfiability Modulo
-Theories.  Solvers are submitted to the competition by their
-developers, and pitted against each other in a number of tracks and
-divisions.  The SMT Competition was part of the Federated Logic
-Conference (FLoC) Olympic Games, which comprised 14 competitions in
-various areas of computational logic, in Vienna in~2014, and again in
-Oxford~(UK) in~2018.  It was last described in a 2014 competition
+(SMT-COMP) is an annual competition between SMT solvers.  It was
+instituted in~2005~\cite{TODO}, and is affiliated with the
+International Workshop on Satisfiability Modulo Theories.  Solvers are
+submitted to the competition by their developers, and pitted against
+each other in a number of tracks and divisions.  The SMT Competition
+was part of the Federated Logic Conference (FLoC) Olympic Games, which
+comprised 14 competitions in various areas of computational logic, in
+Vienna in~2014, and again in Oxford~(UK) in~2018.  It was last
+described in a 2014 competition
 report~\cite{DBLP:journals/jsat/CokDW14}.  In this paper, we report on
@@
 
-The SMT Competition was instituted in 2005.  It has been held annually
-since then (with the exception of 2013, when an
-evaluation~\cite{DBLP:journals/jar/CokSW15} was conducted instead of a
-competition).  The main goals of the competition were to spur adoption
-of the common, community-designed SMT-LIB formats (see
+The original goals of the competition were to spur adoption of the
+common, community-designed SMT-LIB formats (see
 Section~\ref{sec:smtlib}), and to spark further advances in SMT,
 especially for verification~\cite{smtcomp2005}.  These, together with
-providing a useful yardstick for users and developers of SMT solvers,
-are still its main goals today.  The competition has been successful
-in establishing SMT-LIB as the \emph{de facto} standard language for
-SMT solvers.  In recent years, the focus in this regard has shifted
-towards promoting some of the newer extensions of the SMT-LIB
-language, such as a floating-point theory~\cite{TODO} or algebraic
-datatypes~\cite{TODO}.
+providing a useful yardstick of performance for users and developers
+of SMT solvers, are still its main goals to date.  The competition has
+been successful in establishing SMT-LIB as the de~facto standard
+language for SMT solvers.  In recent years, the focus in this regard
+has shifted towards promoting some of the newer extensions of the
+SMT-LIB language~\cite{BarFT-RR-17}, such as its floating-point theory
+or algebraic datatypes.
 
@@
 happened later.  The competition chair then assembles a team of
-organizers, and distributes the work for the next competition.
+organizers, and distributes the work for the next edition of the
+competition.
 %
@@
 
-Important deadlines are effectively determined by calculating
+Important competition deadlines are determined by calculating
 backwards from the date of the next SMT Workshop.  The competition's
 computational workload should be completed approximately two weeks
-before the workshop date, to give participants and other parties a
-chance to scrutinize the data for errors, allow partial re-runs of
-competition jobs if necessary, and give the organizers time to prepare
-the results presentation.  While making all data publicly available
-well in advance of the official results presentation may impact the
-suspense, it has on several occasions helped to uncover serious
-problems with the competition tools or the StarExec framework (see
-Section~\ref{sec:starexec}) that could have led to invalid results
-otherwise.
-\begin{tjark}
-  Discuss these issues somewhere, add (forward?) reference here.
-\end{tjark}
+before the workshop date.  This gives participants and other parties a
+chance to scrutinize the data for errors, allows partial re-runs of
+competition jobs if necessary, and gives the organizers time to
+prepare the results presentation.  While making all data publicly
+available well in advance of the official results presentation may
+impact the suspense, it has on several occasions helped to uncover
+serious problems with the competition tools or the StarExec framework
+(see Section~\ref{sec:starexec}) that could have led to invalid
+results otherwise.
 
-It takes up to three weeks to run all competition jobs on the StarExec
-cluster, so the final submission deadline for solvers needs to be
-about five weeks before the workshop date.  The competition imposes a
-separate deadline for first versions of solvers about seven weeks
-before the workshop date.  This deadline has proved useful for the
-organizers to obtain an accurate estimate on the number of competing
-solvers, and to run preliminary tests with some of the submitted
-solvers to identify potential issues.  Participants can still make
-changes to their solver until the final deadline but are encouraged to
-use this period for bug-fixing only.
+It typically takes up to three weeks to run all competition jobs on
+the StarExec cluster, so the final submission deadline for solvers
+needs to be about five weeks before the workshop date.  The
+competition imposes a separate deadline for first versions of solvers
+about two weeks before the final submission deadline.  This earlier
+deadline has proved useful for the organizers to obtain an accurate
+estimate on the number of competing solvers, and to run preliminary
+tests with some of the submitted solvers to identify potential issues.
+Participants can still make changes to their solver until the final
+deadline but are encouraged to use this period for bug-fixing only.
 
@@
 version of the rules is made public on the competition web site
-typically around mid-April.  The competition chair has ultimate
+usually around mid-April.  The competition chair has ultimate
 responsibility for the rules, but changes are often preceded by
 discussions among the organizers or within the SMT community.  Such
-discussions are initiated by a Call for Comments that is typically
-sent out to the SMT-COMP mailing list~\cite{TODO} in February or early
-March.  Publicly, this call is the first harbinger of a new edition of
-the SMT Competition.
+discussions are initiated by a Call for Comments that is sent out to
+the SMT-COMP mailing list~\cite{smtcomp-mailinglist} typically in
+February or early March.  Publicly, this call is the first harbinger
+of a new edition of the SMT Competition.
 
@@
 
-\section{SMT-LIB Logic, Language and Solvers}
-\label{sec:context}
+\section{The SMT-LIB Language and Library}
+\label{sec:smtlib}
+
+All problems used in the SMT Competition come from the SMT Library
+(SMT-LIB).  This is a large collection of benchmark problems from
+various sources.  The SMT Library is available from a public
+repository~\cite{smtlib-repository}, and each new release is mirrored
+on StarExec (see Section~\ref{sec:starexec}), the cluster on which the
+competition runs.
+
+Benchmarks in the SMT Library are written in the SMT-LIB
+language~\cite{BarFT-RR-17}, a text-based language that defines the
+syntax and semantics of SMT solver input and output.  This includes a
+language for terms and formulas, and a command language for
+interacting with SMT solvers.  For instance,
+Figure~\ref{fig:smtlib-example} shows a possible representation of the
+example formula from Section~\ref{sec:introduction} as a benchmark in
+SMT-LIB syntax.
+
+\begin{figure}
+\begin{verbatim}
+foo
+\end{verbatim}
+\caption{A benchmark problem in SMT-LIB syntax.}
+\label{fig:smtlib-example}
+\end{figure}
 
@@
 
+\section{StarExec}
+\label{sec:starexec}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section{Participants}
@@
 
-Participants must upload their solvers to StarExec (see
-Section~\ref{sec:starexec}) to enter them into the competition, and
-additionally submit information about each competing solver---such as
-the tracks and divisions into which the solver is being entered---to
-the competition organizers.  Until 2016, this information was
-collected by email.  Since 2017, a web form is being used for this
-purpose.  This has greatly reduced the number of incomplete or
-ambiguous submissions.
+Participants must upload their solvers to StarExec to enter them into
+the competition, and additionally submit information about each
+competing solver---such as the tracks and divisions into which the
+solver is being entered---to the competition organizers.  Until 2016,
+this information was collected by email.  Since 2017, a web form is
+being used for this purpose.  This has greatly reduced the number of
+incomplete or ambiguous submissions.
 
@@
     toysmt            & Masahiro Sakai
-                        (\TODO)\\
+                        (Toshiba Corporation)\\
     Vampire           & Giles Reger
@@
 
-\section{StarExec}
-\label{sec:starexec}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \section{Results}
@@
 numeric penalty for each division with incorrect responses.  The value
-of this penalty is set so that entering a (possibly buggy) solver that
-can solve all benchmarks into a division has a positive expected score
-if the probability of a soundness bug in the solver is below~$20\,\%$.
+of this penalty is currently set so that entering a (possibly buggy)
+solver that can solve all benchmarks into a division has a positive
+expected score if the probability of a soundness bug in the solver is
+below~$20\,\%$.
 
 The 2018 edition of the competition was again part of the FLoC Olympic
-Games.  After last-minute negotiations with the Olympic Games
-organizers, it was decided that the SMT Competition would award seven
-Kurt G\"odel medals.  The 2018 competition organizers conferred these
-to the following solvers:
+Games, which sponsored seven Kurt G\"odel medals.  The competition
+organizers awarded these to the following solvers:
 \begin{itemize}
@@
 metric used for the application and unsat-core track---simply counting
-the number of competitive divisions that a solver has won---was fairly
+the number of competitive divisions that a solver has won---was rather
 unsophisticated.  Future editions of the competition should perhaps
@@
 main-track ranking, by weighing divisions according to their relative
-importance, and by also rewarding good performance by solvers other
+importance, and also by rewarding good performance from solvers other
 than division winners.  A difficulty in adapting the main-track
@@
 worth one point (before weighing) if solved correctly, while
-benchmarks in the application and unsat-core track are worth a varying
-number of points.  Moreover, in the unsat-core track, the size of the
-smallest unsatisfiable core---and hence the number of points
-attainable on any given benchmark---may not be known precisely.
+benchmarks in the application and unsat-core track are worth widely
+varying numbers of points.  Moreover, in the unsat-core track, the
+size of the smallest unsatisfiable core---and hence the number of
+points attainable on any given benchmark---may not be known precisely.
 

### 2018-10-12 2018/report/SMT-COMP.tex
Mainly SMT-LIB (work in progress)

@@
 \usepackage{comment}
+\usepackage{multirow}
 
@@
 (SMT-COMP) is an annual competition between SMT solvers.  It was
-instituted in~2005~\cite{TODO}, and is affiliated with the
+instituted in~2005~\cite{BdMS05}, and is affiliated with the
 International Workshop on Satisfiability Modulo Theories.  Solvers are
@@
 The original goals of the competition were to spur adoption of the
-common, community-designed SMT-LIB formats (see
+common, community-designed SMT-LIB format (see
 Section~\ref{sec:smtlib}), and to spark further advances in SMT,
-especially for verification~\cite{smtcomp2005}.  These, together with
+especially for verification~\cite{BdMS05}.  These, together with
 providing a useful yardstick of performance for users and developers
@@
 has shifted towards promoting some of the newer extensions of the
-SMT-LIB language~\cite{BarFT-RR-17}, such as its floating-point theory
-or algebraic datatypes.
+SMT-LIB language, such as its floating-point theory or algebraic
+datatypes~\cite{BarFT-RR-17}.
 
 The competition is organized under the direction of the SMT Steering
-Committee, which appoints the competition chair.  This appointment
+Committee, which appoints the competition chair.  (This appointment
 should happen ``within 30 days from the end of the current edition of
 the SMT workshop''~\cite{smt-bylaws} but in practice has often
-happened later.  The competition chair then assembles a team of
+happened later.)  The competition chair then assembles a team of
 organizers, and distributes the work for the next edition of the
@@
 with the SMT-LIB maintainers---to release a new version of the SMT
-Library.  SMT-LIB releases were made on June~1 in 2015, on May~23 in
-2016, on June~5 in 2017, and on May~20 in 2018.  Anyone may submit new
-benchmarks to the SMT Library, and competitors are permitted to tune
-their solvers accordingly.  Therefore it is important that all
-benchmarks eligible for the competition are released at least some
-time before the final solver submission deadline.  To give the SMT-LIB
-maintainers sufficient time for curation, the deadline for new
-benchmark contributions has usually been about four to six weeks
-before the initial solver deadline, typically in April or early May.
+Library (see Section~\ref{sec:smtlib}).  SMT-LIB releases were made on
+June~1 in 2015, on May~23 in 2016, on June~5 in 2017, and on May~20 in
+2018.  Anyone may submit new benchmarks to the SMT Library, and
+competitors are permitted to tune their solvers accordingly.
+Therefore all benchmarks eligible for the competition must be released
+at least some time before the final solver submission deadline.  To
+give the SMT-LIB maintainers sufficient time for curation, the
+deadline for new benchmark contributions has usually been about four
+to six weeks before the initial solver deadline, typically in April or
+early May.
 
 The competition rules are revised each year, and a (near final) draft
-version of the rules is made public on the competition web site
-usually around mid-April.  The competition chair has ultimate
-responsibility for the rules, but changes are often preceded by
-discussions among the organizers or within the SMT community.  Such
-discussions are initiated by a Call for Comments that is sent out to
-the SMT-COMP mailing list~\cite{smtcomp-mailinglist} typically in
-February or early March.  Publicly, this call is the first harbinger
-of a new edition of the SMT Competition.
+version of the rules is made public on the competition web site around
+mid-April.  The competition chair has ultimate responsibility for the
+rules, but changes are often preceded by discussions among the
+organizers or within the SMT community.  Such discussions are
+initiated by a Call for Comments that is sent out to the SMT-COMP
+mailing list~\cite{smtcomp-mailinglist} typically in February or early
+March.  Publicly, this call is the first harbinger of a new edition of
+the SMT Competition.
 
@@
 on StarExec (see Section~\ref{sec:starexec}), the cluster on which the
-competition runs.
+competition runs.  Users of SMT solvers are encouraged to submit new
+and interesting benchmarks to the library, which has grown from 1,352
+benchmarks in 2005~\cite{BdMS05} to 347,011 benchmarks in 2018.
 
 Benchmarks in the SMT Library are written in the SMT-LIB
-language~\cite{BarFT-RR-17}, a text-based language that defines the
-syntax and semantics of SMT solver input and output.  This includes a
+language~\cite{BarFT-RR-17}, a text-based format that defines the
+syntax and semantics of solver input and output.  This includes a
 language for terms and formulas, and a command language for
 interacting with SMT solvers.  For instance,
-Figure~\ref{fig:smtlib-example} shows a possible representation of the
-example formula from Section~\ref{sec:introduction} as a benchmark in
-SMT-LIB syntax.
+Figure~\ref{fig:smtlib-example} shows the example formula from
+Section~\ref{sec:introduction} as a benchmark in SMT-LIB syntax.
 
@@
 \begin{verbatim}
-foo
+(set-info :smt-lib-version 2.6)
+(set-logic QF_UFLIA)
+(set-info :status unsat)
+(declare-fun x () Int)
+(declare-fun y () Int)
+(declare-fun f (Int) Int)
+(declare-fun P (Int) Bool)
+(assert (and (<= x y) (<= y x) (P (- (f x) (f y))) (not (P 0))))
+(check-sat)
+(exit)
 \end{verbatim}
@@
 \end{figure}
+
+The SMT Library classifies benchmarks according to their logic, that
+is, according to the specific combination of background theories that
+the benchmark uses.  Logic names are composed of letter groups that
+refer to these background theories: {\tt A} or {\tt AX} for the theory
+of arrays, {\tt BV} for the theory of bit-vectors, {\tt DT} for
+algebraic datatypes, {\tt FP} for the floating-point theory, {\tt IA}
+for integer arithmetic, {\tt RA} for real arithmetic, {\tt IRA} for
+mixed integer and real arithmetic, {\tt S} for the theory of strings,
+{\tt UF} for uninterpreted functions (i.e., free symbols).
+Additionally, logics may impose further syntactic restrictions, such
+as the absence of quantifiers ({\tt QF}), the restriction to
+difference logic over the integers ({\tt IDL}) or reals ({\tt RDL}),
+or to the (non-)linear fragment of arithmetic ({\tt L} or {\tt N},
+respectively, before {\tt IA}, {\tt RA} or {\tt IRA}).  For instance,
+the logic {\tt QF\_UFLIA} contains quantifier-free formulas with
+uninterpreted functions over linear integer arithmetic.  These
+restrictions are typically motivated by the existence of efficient
+decision procedures for certain syntactic fragments.
+
+Additionally, the SMT Library distinguishes between incremental and
+non-incremental benchmarks.  Non-incremental benchmarks contain a
+single {\tt check-sat} command, which instructs the SMT solver to
+determine the satisfiability of the benchmark.  (Valid solver
+responses are {\tt sat}, {\tt unsat}, and {\tt unknown}.)  Incremental
+benchmarks exercise additional solver features, such as the ability to
+retract assertions, and typically contain multiple {\tt check-sat}
+commands.  These benchmarks originate from applications such as
+bounded model checking~\cite{TODO}, where SMT solvers interact with
+other tools in a feedback loop.  The 2018 release of the SMT Library
+contained 336,844 non-incremental benchmarks in 51 logics, as well
+as~10,167 incremental benchmarks (with a total of nearly 32 million
+{\tt check-sat} commands) in 26 logics.  Table~\ref{table:smtlib}
+presents further data on the size of the SMT Library since~2015.
+While the library usually grows from one year to the next due to the
+inclusion of new benchmarks and logics, continuous curation efforts
+may also cause benchmarks to be removed or reclassified on occasion,
+thereby causing individual logics or even the entire library to
+shrink.
+
+\begin{table}
+  \caption{Number of benchmarks and logics in the SMT Library}
+  \label{table:smtlib}
+  \centering
+  \begin{tabular}{|r@{\ \ }l|r|r|r|r|}
+    \hline
+                               & & \multicolumn{1}{c|}{2015} & \multicolumn{1}{c|}{2016} & \multicolumn{1}{c|}{2017} & \multicolumn{1}{c|}{2018} \\
+    \hline
+    \multirow{2}{*}{Non-incremental $\{$} & benchmarks & 196,375 & 196,114 & 258,079 & 336,844 \\
+                                          & logics     &      40 &      40 &      49 &      51 \\
+    \multirow{2}{*}{Incremental $\{$}     & benchmarks &  10,019 &  10,024 &   6,262 &  10,167 \\
+                                          & logics     &      15 &      15 &      22 &      26 \\
+    \hline
+  \end{tabular}  
+\end{table}
+
+Benchmarks in the SMT Library are annotated with additional
+information, such as the source of the benchmark and its status (i.e.,
+whether the benchmark is satisfiable or unsatisfiable) if this is
+known.  (For incremental benchmarks, each {\tt check-sat} command has
+a separate status annotation.)  To prevent solvers from simply looking
+up the benchmark's status in the SMT Library, benchmarks in the
+competition are lightly scrambled before they are presented to
+solvers~\cite{DBLP:conf/cade/Weber16}.
 

### 2018-10-16 2018/report/SMT-COMP.tex
Divisions and Benchmarks (work in progress)

@@
 Section~\ref{sec:introduction} as a benchmark in SMT-LIB syntax.
+In~2016, benchmarks were updated from version~2.0 to version~2.5 of
+the SMT-LIB language, and since~2017, benchmarks are written in
+version~2.6.  Fortunately, versions~2.5 and~2.6 are largely
+backwards-compatible to 2.0, so that older solvers are still able to
+compete with at most minor modifications.
 
@@
 
-The SMT Library classifies benchmarks according to their logic, that
-is, according to the specific combination of background theories that
-the benchmark uses.  Logic names are composed of letter groups that
-refer to these background theories: {\tt A} or {\tt AX} for the theory
-of arrays, {\tt BV} for the theory of bit-vectors, {\tt DT} for
+The SMT Library classifies benchmarks according to their \emph{logic},
+that is, according to the specific combination of background theories
+that the benchmark uses.  Logic names are composed of letter groups
+that refer to these background theories: {\tt A} or {\tt AX} for the
+theory of arrays, {\tt BV} for the theory of bit-vectors, {\tt DT} for
 algebraic datatypes, {\tt FP} for the floating-point theory, {\tt IA}
@@
 
-Additionally, the SMT Library distinguishes between incremental and
-non-incremental benchmarks.  Non-incremental benchmarks contain a
-single {\tt check-sat} command, which instructs the SMT solver to
-determine the satisfiability of the benchmark.  (Valid solver
-responses are {\tt sat}, {\tt unsat}, and {\tt unknown}.)  Incremental
-benchmarks exercise additional solver features, such as the ability to
-retract assertions, and typically contain multiple {\tt check-sat}
-commands.  These benchmarks originate from applications such as
-bounded model checking~\cite{TODO}, where SMT solvers interact with
-other tools in a feedback loop.  The 2018 release of the SMT Library
-contained 336,844 non-incremental benchmarks in 51 logics, as well
-as~10,167 incremental benchmarks (with a total of nearly 32 million
-{\tt check-sat} commands) in 26 logics.  Table~\ref{table:smtlib}
-presents further data on the size of the SMT Library since~2015.
-While the library usually grows from one year to the next due to the
-inclusion of new benchmarks and logics, continuous curation efforts
-may also cause benchmarks to be removed or reclassified on occasion,
-thereby causing individual logics or even the entire library to
-shrink.
+Additionally, the SMT Library distinguishes between \emph{incremental}
+and \emph{non-incremental} benchmarks.  Non-incremental benchmarks
+contain a single {\tt check-sat} command, which instructs the SMT
+solver to determine the satisfiability of the benchmark.  (Valid
+solver responses are {\tt sat}, {\tt unsat}, and {\tt unknown}.)
+Incremental benchmarks exercise additional solver features, such as
+the ability to retract assertions, and typically contain multiple {\tt
+  check-sat} commands.  These benchmarks originate from applications
+such as bounded model checking~\cite{TODO}, where SMT solvers interact
+with other tools in a feedback loop.  The 2018 release of the SMT
+Library contained 336,844 non-incremental benchmarks in 51 logics, as
+well as~10,167 incremental benchmarks (with a total of nearly 32
+million {\tt check-sat} commands) in 26 logics.
+Table~\ref{table:smtlib} presents further data on the size of the SMT
+Library since~2015.  While the library usually grows from one year to
+the next due to the inclusion of new benchmarks and logics, continuous
+curation efforts may also cause benchmarks to be removed or
+reclassified on occasion, thereby causing individual logics or even
+the entire library to shrink.
 
@@
 \label{sec:benchmarks}
+
+The SMT Competition consists of several tracks.  The \emph{main
+  track}, which has been a staple of the competition since its
+inception in 2005, features non-incremental benchmarks.  The
+\emph{application track}, which has been part of the competition since
+2011~\cite{TODO}, features incremental benchmarks.  These benchmarks
+are passed to each solver one command at a time by a trace executor,
+which waits for the solver's response before passing the next
+benchmark command (to prevent look-ahead behavior).  The
+\emph{unsat-core track} uses main-track benchmarks that are known to
+be unsatisfiable, and solvers are evaluated on their ability to find
+small unsatisfiable cores (i.e., a small but unsatisfiable subset of
+the benchmark's assertions).  The unsat-core track had first been part
+of the competition in 2012~\cite{TODO}, but was then discontinued
+partly because of the competition's move to StarExec (see Section~5)
+and lacking tool support.  It was re-introduced as an experimental
+track in 2016, and has been a regular competition track since~2017.
+
+Each track is further split into (logic) \emph{divisions}, where each
+division corresponds to a logic from the SMT Library.  Participants
+can choose which tracks and divisions they want to enter, and
+competition results are reported separately for each track and
+division.  Thus, competing solvers need not support all logics, and
+may or may not support features such as incrementality or unsat-core
+generation.
+
+SMT Competitions until~2014 used a pseudo-random selection process to
+cull the number of benchmarks used in the competition.  However, a
+2013 evaluation found that this ``significantly lessens the ability of
+a competition to determine `best'
+solvers.''~\cite{DBLP:journals/jar/CokSW15} Together with the
+increased computational resources available for the competition since
+its move to StarExec, this prompted a paradigm shift.  Since 2015, the
+competition is evaluating all solvers on all eligible benchmarks.
+Some benchmarks from the SMT Library typically have to be excluded for
+syntactic reasons: in 2015 and 2016, 11,966 benchmarks were excluded
+because they contained partial or underspecified operations (e.g.,
+bit-vector division) whose precise semantics were being debated at the
+time.  Additionally in 2016, one benchmark was excluded because it
+contained incorrect status information.  In 2017, 1,104 benchmarks
+were excluded because their logic had been incorrectly classified, and
+8 benchmarks were excluded because of incorrect or missing status
+information.  In 2018, 3,603 benchmarks were excluded because they
+contained named terms (a feature of the SMT-LIB language that is not
+permitted in competition benchmarks), and 5 benchmarks were excluded
+because of missing status information.
+
+\begin{tjark}
+  WIP: benchmark selection, tables with numbers, excluded benchmarks,
+  unknown benchmarks
+\end{tjark}
 

### 2018-10-19 2018/report/SMT-COMP.tex
Benchmark numbers

@@
 
-The original goals of the competition were to spur adoption of the
-common, community-designed SMT-LIB format (see
-Section~\ref{sec:smtlib}), and to spark further advances in SMT,
-especially for verification~\cite{BdMS05}.  These, together with
-providing a useful yardstick of performance for users and developers
-of SMT solvers, are still its main goals to date.  The competition has
-been successful in establishing SMT-LIB as the de~facto standard
-language for SMT solvers.  In recent years, the focus in this regard
-has shifted towards promoting some of the newer extensions of the
-SMT-LIB language, such as its floating-point theory or algebraic
-datatypes~\cite{BarFT-RR-17}.
+The original goals of the SMT Competition were to spur adoption of the
+community-designed SMT-LIB format (see Section~\ref{sec:smtlib}), and
+to spark further advances in SMT, especially for
+verification~\cite{BdMS05}.  These, together with providing a useful
+yardstick of performance for users and developers of SMT solvers, are
+still its main goals to date.  The competition has been successful in
+establishing SMT-LIB as the de~facto standard language for SMT
+solvers.  In recent years, the focus in this regard has shifted
+towards promoting some of the newer extensions of the SMT-LIB
+language~\cite{BarFT-RR-17}, such as floating-point numbers and
+algebraic datatypes.
 
@@
 and results of the competition.  The workshop is affiliated with a
-different conference each year: with CAV in 2015, with IJCAR in 2016,
-again with CAV in 2017, and with FLoC in~2018.  Consequently, its date
-varies by several weeks.  Competition results were presented on
-July~19 in 2015, on July~2 in 2016, on July~23 in 2017, and on July~13
-in~2018.
+major conference in the field of automated reasoning each year: with
+CAV in 2015, with IJCAR in 2016, again with CAV in 2017, and with FLoC
+in~2018.  Consequently, its date varies.  Competition results were
+presented on July~19 in 2015, on July~2 in 2016, on July~23 in 2017,
+and on July~13 in~2018.
 
@@
 initiated by a Call for Comments that is sent out to the SMT-COMP
-mailing list~\cite{smtcomp-mailinglist} typically in February or early
-March.  Publicly, this call is the first harbinger of a new edition of
-the SMT Competition.
+mailing list~\cite{smtcomp-mailinglist} in February or early March.
+Publicly, this call is the first harbinger of a new edition of the SMT
+Competition.
 
@@
 repository~\cite{smtlib-repository}, and each new release is mirrored
-on StarExec (see Section~\ref{sec:starexec}), the cluster on which the
-competition runs.  Users of SMT solvers are encouraged to submit new
-and interesting benchmarks to the library, which has grown from 1,352
-benchmarks in 2005~\cite{BdMS05} to 347,011 benchmarks in 2018.
+on StarExec, the cluster on which the competition runs.  Users of SMT
+solvers are encouraged to submit new and interesting benchmarks to the
+library, which has grown from 1,352 benchmarks in 2005~\cite{BdMS05}
+to 347,011 benchmarks in 2018.
 
@@
 In~2016, benchmarks were updated from version~2.0 to version~2.5 of
-the SMT-LIB language, and since~2017, benchmarks are written in
+the SMT-LIB language.  Since~2017, benchmarks are written in
 version~2.6.  Fortunately, versions~2.5 and~2.6 are largely
@@
 such as bounded model checking~\cite{TODO}, where SMT solvers interact
-with other tools in a feedback loop.  The 2018 release of the SMT
-Library contained 336,844 non-incremental benchmarks in 51 logics, as
-well as~10,167 incremental benchmarks (with a total of nearly 32
-million {\tt check-sat} commands) in 26 logics.
-Table~\ref{table:smtlib} presents further data on the size of the SMT
-Library since~2015.  While the library usually grows from one year to
-the next due to the inclusion of new benchmarks and logics, continuous
-curation efforts may also cause benchmarks to be removed or
-reclassified on occasion, thereby causing individual logics or even
-the entire library to shrink.
+with other tools in a feedback loop.
+
+The 2018 release of the SMT Library contained 336,844 non-incremental
+benchmarks in 51 logics, as well as~10,167 incremental benchmarks
+(with a total of nearly 32 million {\tt check-sat} commands) in 26
+logics.  Table~\ref{table:smtlib} presents further data on the size of
+the SMT Library since~2015.  While the library usually grows from one
+year to the next because of the inclusion of new benchmarks and
+logics, continuous curation efforts may also cause benchmarks to be
+removed or reclassified on occasion, thereby causing individual logics
+or even the entire library to shrink.  From 2015--2018, the total
+number of benchmarks has increased by 68\,\%.
+Figure~\ref{fig:benchmark-sizes} shows how the file size of individual
+benchmarks is distributed.  The largest benchmark in the 2018 release
+has a size of 993~MiB; the total size of the library is 85~GiB.
 
@@
     \hline
-    \multirow{2}{*}{Non-incremental $\{$} & benchmarks & 196,375 & 196,114 & 258,079 & 336,844 \\
+    \multirow{2}{*}{Non-incremental $\{$} & benchmarks & 196375 & 196114 & 258079 & 336844 \\
                                           & logics     &     40 &     40 &     49 &     51 \\
-    \multirow{2}{*}{Incremental $\{$}     & benchmarks &  10,019 &  10,024 &   6,262 &  10,167 \\
+    \multirow{2}{*}{Incremental $\{$}     & benchmarks &  10019 &  10024 &   6262 &  10167 \\
                                           & logics     &     15 &     15 &     22 &     26 \\
@@
 \end{table}
+
+\begin{figure}
+  \TODO \\
+  \TODO \\
+  \TODO \\
+  \TODO \\
+  \TODO \\
+  \TODO \\
+  \TODO \\
+
+  \caption{Distribution of benchmark sizes in the SMT Library (2018).}
+  \label{fig:benchmark-sizes}
+\end{figure}
 
@@
 be unsatisfiable, and solvers are evaluated on their ability to find
-small unsatisfiable cores (i.e., a small but unsatisfiable subset of
-the benchmark's assertions).  The unsat-core track had first been part
-of the competition in 2012~\cite{TODO}, but was then discontinued
-partly because of the competition's move to StarExec (see Section~5)
-and lacking tool support.  It was re-introduced as an experimental
-track in 2016, and has been a regular competition track since~2017.
+small unsatisfiable cores (i.e., a small but still unsatisfiable
+subset of the benchmark's assertions).  The unsat-core track had first
+been part of the competition in 2012~\cite{TODO}, but was then
+discontinued partly because of the competition's move to StarExec and
+lacking tool support.  It was re-introduced as an experimental track
+in 2016, and has been a regular competition track again since~2017.
 
 Each track is further split into (logic) \emph{divisions}, where each
-division corresponds to a logic from the SMT Library.  Participants
-can choose which tracks and divisions they want to enter, and
-competition results are reported separately for each track and
-division.  Thus, competing solvers need not support all logics, and
-may or may not support features such as incrementality or unsat-core
-generation.
+division corresponds to a logic from the SMT Library.
+Table~\ref{table:divisions} shows the number of divisions in each
+track since~2015.  Participants can choose which tracks and divisions
+they want to enter, and competition results are reported separately
+for each track and division.  Thus, competing solvers need not support
+all logics, and may or may not support features such as incrementality
+or unsat-core generation.
 
-SMT Competitions until~2014 used a pseudo-random selection process to
-cull the number of benchmarks used in the competition.  However, a
-2013 evaluation found that this ``significantly lessens the ability of
-a competition to determine `best'
+There are slightly fewer divisions than logics in the SMT Library
+(Table~\ref{table:smtlib}) because not every logic contains benchmarks
+eligible for the competition.  Some benchmarks typically have to be
+excluded for syntactic reasons: in 2015 and 2016, 11,966 benchmarks
+were excluded because they contained partial or underspecified
+operations (e.g., bit-vector division) whose precise semantics were
+being debated at the time.  Additionally in 2016, one benchmark was
+excluded because it contained incorrect status information.  In 2017,
+1,104 benchmarks were excluded because their logic had been classified
+incorrectly, and 8 benchmarks were excluded because of incorrect or
+missing status information.  Moreover, divisions containing datatypes
+({\tt DT})---which were new in~2017---were excluded from the
+unsat-core track because of lacking tool support.  In 2018, 3,603
+benchmarks were excluded because they contained named terms (a feature
+of the SMT-LIB language that is not permitted in competition
+benchmarks), and 5 benchmarks were excluded because of missing status
+information.
+
+\begin{table}
+  \caption{Number of divisions in each competition track}
+  \label{table:divisions}
+  \centering
+  \begin{tabular}{|l|r|r|r|r|}
+    \hline
+    & \multicolumn{1}{c|}{2015} & \multicolumn{1}{c|}{2016} & \multicolumn{1}{c|}{2017} & \multicolumn{1}{c|}{2018} \\
+    \hline
+    Main track        &  40 & 40 & 49 & 50 \\
+    Application track &  14 & 14 & 16 & 21 \\
+    Unsat-core track  &  -- & 40 & 41 & 44 \\
+    \hline
+  \end{tabular}
+\end{table}
+
+SMT Competitions until~2014 employed a pseudo-random selection process
+to further cull the number of benchmarks used in the competition.
+However, a 2013 evaluation found that this ``significantly lessens the
+ability of a competition to determine `best'
 solvers.''~\cite{DBLP:journals/jar/CokSW15} Together with the
@@
 its move to StarExec, this prompted a paradigm shift.  Since 2015, the
-competition is evaluating all solvers on all eligible benchmarks.
-Some benchmarks from the SMT Library typically have to be excluded for
-syntactic reasons: in 2015 and 2016, 11,966 benchmarks were excluded
-because they contained partial or underspecified operations (e.g.,
-bit-vector division) whose precise semantics were being debated at the
-time.  Additionally in 2016, one benchmark was excluded because it
-contained incorrect status information.  In 2017, 1,104 benchmarks
-were excluded because their logic had been incorrectly classified, and
-8 benchmarks were excluded because of incorrect or missing status
-information.  In 2018, 3,603 benchmarks were excluded because they
-contained named terms (a feature of the SMT-LIB language that is not
-permitted in competition benchmarks), and 5 benchmarks were excluded
-because of missing status information.
+competition is evaluating all solvers on all eligible
+benchmarks. \TODO: benchmark weights
 
-\begin{tjark}
-  WIP: benchmark selection, tables with numbers, excluded benchmarks,
-  unknown benchmarks
-\end{tjark}
+Another paradigm shift concerns the treatment of benchmarks with
+unknown status.  Because of the difficulty to judge solver responses
+for such benchmarks, SMT Competitions until 2015 only used benchmarks
+whose status was known (i.e., that had been solved previously by
+existing SMT solvers).  In 2015, 30,717 non-incremental benchmarks
+from the SMT Library were not used for the competition because their
+status was unknown.  However, this approach was criticized for
+favoring imitation of existing solvers over true innovation.  In~2016,
+the SMT Library contained 29,724 non-incremental benchmarks with
+unknown status; solver performance on these was evaluated but reported
+separately.  Since 2017, all non-incremental benchmarks are eligible
+for the competition's main track regardless of status, and they
+directly affect the competition results.  Solver responses for such
+benchmarks are assumed to be correct, unless there is a disagreement
+between two or more (otherwise sound) solvers.  Benchmarks with
+disagreements are removed from the competition results (see
+Section~\ref{sec:results-disagreements} for further discussion).
+
+For incremental benchmarks, the situation is different: an incremental
+benchmark is ineligible for the application track if its first {\tt
+  check-sat} command has unknown status.  Otherwise, the prefix of the
+benchmark that only contains {\tt check-sat} commands with known
+status is eligible.  The main reason for this difference is that the
+competition tools for the application track (in particular, the trace
+executor) have not been adapted yet to support {\tt check-sat}
+commands with unknown status.
+
+Tables~\ref{table:benchmarks-main-track}--\ref{table:benchmarks-unsat-core-track}
+show the number of benchmarks that were used in each competition track
+and division since 2015.  A dash indicates that no eligible benchmarks
+were available, and hence the corresponding SMT-LIB logic was not
+actually a competition division in that track and year.
+
+\begin{table}
+  \caption{Number of benchmarks used in the main track (by division)}
+  \label{table:benchmarks-main-track}
+  \centering
+  \scalebox{.9}[.83]{\begin{tabular}{|l|r|r|r|r|}
+    \hline
+    Division & \multicolumn{1}{c|}{2015} & \multicolumn{1}{c|}{2016} & \multicolumn{1}{c|}{2017} & \multicolumn{1}{c|}{2018} \\
+    \hline
+    ABVFP      &     -- &     -- &      1 &     1 \\
+    ALIA       &     42 &     42 &     42 &    42 \\
+    AUFBVDTLIA &     -- &     -- &   1709 &  1709 \\
+    AUFDTLIA   &     -- &     -- &    728 &   728 \\
+    AUFLIA     &      4 &      4 &      4 &     4 \\
+    AUFLIRA    &  19849 &  19849 &  20011 & 20011 \\
+    AUFNIRA    &   1050 &   1050 &   1480 &  1480 \\
+    BV         &     85 &     85 &   5151 &  5751 \\
+    BVFP       &     -- &     -- &     24 &    24 \\
+    FP         &     -- &     -- &     61 &    61 \\
+    LIA        &    201 &    201 &    388 &   388 \\
+    LRA        &    339 &    339 &   2419 &  2419 \\
+    NIA        &      9 &      9 &     14 &    14 \\
+    NRA        &   3788 &   3788 &   3811 &  3813 \\
+    QF\_ABV    &  14720 &  14720 &  15061 & 15066 \\
+    QF\_ABVFP  &     -- &     -- &  18129 & 18129 \\
+    QF\_ALIA   &    134 &    139 &    139 &   139 \\
+    QF\_ANIA   &      6 &      8 &      8 &     8 \\
+    QF\_AUFBV  &     37 &     37 &     31 &    31 \\
+    QF\_AUFLIA &   1009 &   1009 &   1009 &  1009 \\
+    QF\_AUFNIA &     21 &     21 &     17 &    17 \\
+    QF\_AX     &    551 &    551 &    551 &   551 \\
+    QF\_BV     &  26414 &  26414 &  40043 & 40102 \\
+    QF\_BVFP   &      7 &      7 &  17215 & 17215 \\
+    QF\_DT     &     -- &     -- &   8000 &  8000 \\
+    QF\_FP     &  34413 &  34413 &  40302 & 40300 \\
+    QF\_IDL    &   2094 &   2094 &   2193 &  2193 \\
+    QF\_LIA    &   5839 &   5839 &   6141 &  6947 \\
+    QF\_LIRA   &      6 &      6 &      7 &     7 \\
+    QF\_LRA    &   1626 &   1626 &   1649 &  1649 \\
+    QF\_NIA    &   8475 &   8593 &  23876 & 23876 \\
+    QF\_NIRA   &      2 &      2 &      3 &     3 \\
+    QF\_NRA    &  10184 &  10245 &  11354 & 11489 \\
+    QF\_RDL    &    220 &    220 &    255 &   255 \\
+    QF\_SLIA   &     -- &     -- &     -- & 72705 \\
+    QF\_UF     &   6649 &   6649 &   6650 &  7423 \\
+    QF\_UFBV   &     31 &     31 &     31 &  1224 \\
+    QF\_UFIDL  &    441 &    441 &    428 &   428 \\
+    QF\_UFLIA  &    598 &    598 &    583 &   583 \\
+    QF\_UFLRA  &   1627 &   1627 &   1284 &  1284 \\
+    QF\_UFNIA  &      7 &      7 &      7 &     7 \\
+    QF\_UFNRA  &     34 &     34 &     36 &    36 \\
+    UF         &   2839 &   2839 &   7562 &  7562 \\
+    UFBV       &     71 &     71 &    200 &   200 \\
+    UFDT       &     -- &     -- &   4535 &  4527 \\
+    UFDTLIA    &     -- &     -- &    303 &   303 \\
+    UFIDL      &     68 &     68 &     68 &    68 \\
+    UFLIA      &   8404 &   8404 &  10137 & 10137 \\
+    UFLRA      &     25 &     25 &     15 &    15 \\
+    UFNIA      &   2319 &   2319 &   3308 &  3308 \\
+    \hline
+    Total      & 154238 & 154424 & 256973 & 333241 \\
+    \hline
+  \end{tabular}}
+\end{table}
+
+\begin{table}
+  \caption{Number of benchmarks used in the application track (by
+    division)}
+  \label{table:benchmarks-application-track}
+  \centering
+  \begin{tabular}{|l|r|r|r|r|}
+    \hline
+    Division & \multicolumn{1}{c|}{2015} & \multicolumn{1}{c|}{2016} & \multicolumn{1}{c|}{2017} & \multicolumn{1}{c|}{2018} \\
+    \hline
+    ALIA       &   24 &   24 &   24 &   24 \\
+    ANIA       &    3 &    3 &    3 &    3 \\
+    AUFNIRA    &   -- &   -- &   -- &  117 \\
+    BV         &   -- &   -- &   -- &   17 \\
+    LIA        &    6 &    6 &    6 &    6 \\
+    QF\_ABV    &   -- &   -- &   -- &   15 \\
+    QF\_ALIA   &   44 &   44 &   44 &   44 \\
+    QF\_ANIA   &    5 &    5 &    5 &    5 \\
+    QF\_AUFBV  &   -- &   -- &   -- &   10 \\
+    QF\_AUFLIA &   72 &   72 &   72 &   72 \\
+    QF\_BV     &   18 &   18 &   18 &  815 \\
+    QF\_BVFP   &   -- &   -- &    2 &    2 \\
+    QF\_FP     &   -- &   -- &    2 &    2 \\
+    QF\_LIA    &   65 &   69 &   68 &   69 \\
+    QF\_LRA    &   10 &   10 &   10 &   10 \\
+    QF\_NIA    &   10 &   10 &   10 &   10 \\
+    QF\_UFBV   &   -- &   -- &   -- & 2327 \\
+    QF\_UFLIA  &  905 &  905 &  780 &  780 \\
+    QF\_UFLRA  & 3331 & 3331 & 3056 & 3058 \\
+    QF\_UFNIA  &    1 &    1 &    1 &    1 \\
+    UFLRA      & 5358 & 5358 & 1870 & 1870 \\
+    \hline
+    Total      & 9852 & 9856 & 5971 & 9257 \\
+    \hline
+  \end{tabular}
+\end{table}
+
+\begin{table}
+  \caption{Number of benchmarks used in the unsat-core track (by
+    division)}
+  \label{table:benchmarks-unsat-core-track}
+  \centering
+  \scalebox{1}[.93]{\begin{tabular}{|l|r|r|r|}
+    \hline
+    Division & \multicolumn{1}{c|}{2016} & \multicolumn{1}{c|}{2017} & \multicolumn{1}{c|}{2018} \\
+    \hline
+    ALIA       &     41 &     41 &     41 \\
+    AUFBVDTLIA &     -- &     -- &     25 \\
+    AUFLIA     &      3 &      3 &      3 \\
+    AUFLIRA    &  19749 &  19771 &  19771 \\
+    AUFNIRA    &   1046 &   1050 &   1053 \\
+    BV         &     56 &     94 &   4937 \\
+    LIA        &    191 &    233 &    233 \\
+    LRA        &    319 &   1106 &   1539 \\
+    NIA        &      3 &      4 &      4 \\
+    NRA        &   3788 &   3801 &   3801 \\
+    QF\_ABV    &   4644 &   4673 &   4677 \\
+    QF\_ABVFP  &     -- &   3934 &   3934 \\
+    QF\_ALIA   &     80 &     80 &     80 \\
+    QF\_ANIA   &      8 &      8 &      8 \\
+    QF\_AUFBV  &     31 &     25 &     25 \\
+    QF\_AUFLIA &    516 &    516 &    516 \\
+    QF\_AUFNIA &     15 &     12 &     12 \\
+    QF\_AX     &    279 &    279 &    279 \\
+    QF\_BV     &  17172 &  23732 &  25700 \\
+    QF\_BVFP   &      6 &   3174 &   3174 \\
+    QF\_DT     &     -- &     -- &   4422 \\
+    QF\_FP     &  17213 &  20028 &  20026 \\
+    QF\_IDL    &    816 &    816 &    816 \\
+    QF\_LIA    &   2840 &   2844 &   3019 \\
+    QF\_LIRA   &      5 &      5 &      5 \\
+    QF\_LRA    &    633 &    671 &    683 \\
+    QF\_NIA    &    316 &   3130 &   4842 \\
+    QF\_NIRA   &      2 &      2 &      2 \\
+    QF\_NRA    &   4948 &   5296 &   5357 \\
+    QF\_RDL    &    113 &    113 &    113 \\
+    QF\_UF     &   4100 &   4101 &   4330 \\
+    QF\_UFBV   &     31 &     31 &    575 \\
+    QF\_UFIDL  &    335 &    322 &    322 \\
+    QF\_UFLIA  &    195 &    183 &    183 \\
+    QF\_UFLRA  &    853 &    511 &    511 \\
+    QF\_UFNIA  &      7 &      7 &      7 \\
+    QF\_UFNRA  &     18 &     11 &     11 \\
+    UF         &   2039 &   3316 &   3442 \\
+    UFBV       &     53 &     97 &     97 \\
+    UFDT       &     -- &     -- &   1863 \\
+    UFIDL      &     62 &     57 &     57 \\
+    UFLIA      &   8377 &   7714 &   7743 \\
+    UFLRA      &     20 &     10 &     10 \\
+    UFNIA      &   2318 &   2432 &   2457 \\
+    \hline
+    Total      &  93241 & 114233 & 130705 \\
+    \hline
+  \end{tabular}}
+\end{table}
 
@@
 % mode: flyspell
-% LocalWords: concours hors satisfiability SMT Tjark
+% LocalWords: concours hors logics satisfiability SMT Tjark
 % End:

### 2018-10-19 2018/report/SMT-COMP.tex
Distribution of benchmarks by file size

@@
 \usepackage{multirow}
+\usepackage{tikz}
 
@@
 solvers are encouraged to submit new and interesting benchmarks to the
-library, which has grown from 1,352 benchmarks in 2005~\cite{BdMS05}
+library, which has grown from 1,352 benchmarks in~2005~\cite{BdMS05}
 to 347,011 benchmarks in 2018.
@@
 that the benchmark uses.  Logic names are composed of letter groups
-that refer to these background theories: {\tt A} or {\tt AX} for the
-theory of arrays, {\tt BV} for the theory of bit-vectors, {\tt DT} for
-algebraic datatypes, {\tt FP} for the floating-point theory, {\tt IA}
-for integer arithmetic, {\tt RA} for real arithmetic, {\tt IRA} for
-mixed integer and real arithmetic, {\tt S} for the theory of strings,
-{\tt UF} for uninterpreted functions (i.e., free symbols).
-Additionally, logics may impose further syntactic restrictions, such
-as the absence of quantifiers ({\tt QF}), the restriction to
-difference logic over the integers ({\tt IDL}) or reals ({\tt RDL}),
-or to the (non-)linear fragment of arithmetic ({\tt L} or {\tt N},
-respectively, before {\tt IA}, {\tt RA} or {\tt IRA}).  For instance,
-the logic {\tt QF\_UFLIA} contains quantifier-free formulas with
-uninterpreted functions over linear integer arithmetic.  These
+that refer to these background theories: {A} or {AX} for the theory of
+arrays, {BV} for the theory of bit-vectors, {DT} for algebraic
+datatypes, {FP} for the floating-point theory, {IA} for integer
+arithmetic, {RA} for real arithmetic, {IRA} for mixed integer and real
+arithmetic, {S} for the theory of strings, {UF} for uninterpreted
+functions (i.e., free symbols).  Additionally, logics may impose
+further syntactic restrictions, such as the absence of quantifiers
+({QF\_}), the restriction to difference logic over the
+integers~({IDL}) or reals ({RDL}), or to the (non-)linear fragment of
+arithmetic ({L} or {N}, respectively, before {IA}, {RA} or {IRA}).
+For instance, the logic QF\_UFLIA contains quantifier-free formulas
+with uninterpreted functions over linear integer arithmetic.  These
 restrictions are typically motivated by the existence of efficient
@@
 removed or reclassified on occasion, thereby causing individual logics
-or even the entire library to shrink.  From 2015--2018, the total
-number of benchmarks has increased by 68\,\%.
+or even the entire library to shrink.  From~2015 to~2018, the total
+number of benchmarks has increased by~68\,\%.
 Figure~\ref{fig:benchmark-sizes} shows how the file size of individual
 benchmarks is distributed.  The largest benchmark in the 2018 release
-has a size of 993~MiB; the total size of the library is 85~GiB.
+had a size of 1,041~MB; the total size of the release was 91~GB.
 
@@
 \begin{figure}
-  \TODO \\
-  \TODO \\
-  \TODO \\
-  \TODO \\
-  \TODO \\
-  \TODO \\
-  \TODO \\
-
-  \caption{Distribution of benchmark sizes in the SMT Library (2018).}
+  \centering
+  \scalebox{.96}[.96]{\begin{tikzpicture}
+    \draw [gray] (0,0) -- (14,0);
+    \draw [gray] (0,.9) -- (14,.9);
+    \draw [gray] (0,1.8) -- (14,1.8);
+    \draw [gray] (0,2.7) -- (14,2.7);
+    \draw [gray] (0,3.6) -- (14,3.6);
+    \draw [gray] (0,4.5) -- (14,4.5);
+    \draw [gray] (0,5.4) -- (14,5.4);
+
+    \node [left] at (0,0) {\footnotesize 0};
+    \node [left] at (0,.9) {\footnotesize 1};
+    \node [left] at (0,1.8) {\footnotesize 10};
+    \node [left] at (0,2.7) {\footnotesize 100};
+    \node [left] at (0,3.6) {\footnotesize 1000};
+    \node [left] at (0,4.5) {\footnotesize 10000};
+    \node [left] at (0,5.4) {\footnotesize 100000};
+
+    \node [rotate=90] at (-1.5,2.7) {\small Number of benchmarks};
+
+    \draw [fill=black] (0.5,0) rectangle (1.5,5.1630077857); % 54535
+    \draw [fill=black] (2.25,0) rectangle (3.25,5.5885514492); % 161995
+    \draw [fill=black] (4,0) rectangle (5,5.3624537158); % 90841
+    \draw [fill=black] (5.75,0) rectangle (6.75,4.9369959734); % 30588
+    \draw [fill=black] (7.5,0) rectangle (8.5,4.4297518088); % 8355
+    \draw [fill=black] (9.25,0) rectangle (10.25,3.3931037653); % 589
+    \draw [fill=black] (11,0) rectangle (12,2.7264453999); % 107
+    \draw [fill=black] (12.75,0) rectangle (13.75,0.9); % 1
+
+    \node [below] at (1,0) {\footnotesize $[10^2, 10^3[$};
+    \node [below] at (2.75,0) {\footnotesize $[10^3, 10^4[$};
+    \node [below] at (4.5,0) {\footnotesize $[10^4, 10^5[$};
+    \node [below] at (6.25,0) {\footnotesize $[10^5, 10^6[$};
+    \node [below] at (8,0) {\footnotesize $[10^6, 10^7[$};
+    \node [below] at (9.75,0) {\footnotesize $[10^7, 10^8[$};
+    \node [below] at (11.5,0) {\footnotesize $[10^8, 10^9[$};
+    \node [below] at (13.25,0) {\footnotesize $[10^9, 10^{10}[$};
+
+    \node [] at (7,-1) {\small File size in bytes};
+  \end{tikzpicture}}
+  \caption{Distribution of SMT-LIB benchmarks by file size (2018).}
   \label{fig:benchmark-sizes}
@@
 show the number of benchmarks that were used in each competition track
-and division since 2015.  A dash indicates that no eligible benchmarks
+and division since~2015.  A dash indicates that no eligible benchmarks
 were available, and hence the corresponding SMT-LIB logic was not
-actually a competition division in that track and year.
+actually a competition division in that track and year.  The size of
+divisions varies widely, from just one benchmark in ABVFP to~72,705
+benchmarks in QF\_SLIA.
 
@@
   \centering
-  \scalebox{.9}[.83]{\begin{tabular}{|l|r|r|r|r|}
+  \scalebox{.9}[.82]{\begin{tabular}{|l|r|r|r|r|}
     \hline
@@
 
+\TODO: explain those aspects of the procedure that are required to
+understand the results (e.g., time limits, scoring)
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2018-10-21 2018/report/SMT-COMP.tex
Infrastructure

@@
 
-    \node [rotate=90] at (-1.5,2.7) {\small Number of benchmarks};
+    \node [rotate=90] at (-1.5,2.7) {\small Benchmarks};
 
@@
 missing status information.  Moreover, divisions containing datatypes
-({\tt DT})---which were new in~2017---were excluded from the
-unsat-core track because of lacking tool support.  In 2018, 3,603
-benchmarks were excluded because they contained named terms (a feature
-of the SMT-LIB language that is not permitted in competition
-benchmarks), and 5 benchmarks were excluded because of missing status
-information.
+({DT})---which were new in~2017---were excluded from the unsat-core
+track because of lacking tool support.  In 2018, 3,603 benchmarks were
+excluded because they contained named terms (a feature of the SMT-LIB
+language that is not permitted in competition benchmarks), and 5
+benchmarks were excluded because of missing status information.
 
@@
 to further cull the number of benchmarks used in the competition.
-However, a 2013 evaluation found that this ``significantly lessens the
-ability of a competition to determine `best'
-solvers.''~\cite{DBLP:journals/jar/CokSW15} Together with the
-increased computational resources available for the competition since
+However, a 2013 evaluation of SMT-COMP and SMT-LIB found that this
+``significantly lessens the ability of a competition to determine
+`best' solvers.''~\cite{DBLP:journals/jar/CokSW15} Together with the
+increased computational resources available to the competition since
 its move to StarExec, this prompted a paradigm shift.  Since 2015, the
@@
 
-\section{StarExec}
+\section{Infrastructure}
 \label{sec:starexec}
+
+Since 2014 (and previously for the evaluation in
+2013~\cite{DBLP:journals/jar/CokSW15}), the computational workload of
+the competition is being run on StarExec, a ``cross-community
+infrastructure for logic solving''~\cite{DBLP:conf/cade/StumpST14}
+developed at the University of Iowa and supported by the National
+Science Foundation.  Each machine in the StarExec cluster is equipped
+with two E5-2609 Intel Xeon processors (10~MiB Cache, 2.4~GHz).  This
+hardware configuration has been unchanged since~2013.  Up to two
+solvers are run simultaneously on each machine: one solver on each
+processor, with four cores available.  Memory usage is limited
+to~60~GiB per solver.
+
+On the software side, the cluster is running Red Hat Enterprise Linux
+Workstation.  The~2015 competition was running on release~6.3
+(Santiago, kernel 2.6.32-431).  This was updated to~7.2 (Maipo, kernel
+3.10.0-327) before the~2016 competition, and the kernel was further
+updated to~3.10.0-514 before the~2017 competition.  The platform
+emphasizes stability over bleeding edge technology.  This has on
+occasion caused problems with solver binaries that had been compiled
+on other Linux distributions and linked against library versions not
+(yet) available on the cluster.  Usually, such problems are easily
+solved by building the solver on StarExec instead.  The StarExec
+developers have made a virtual machine image available to facilitate
+this and similar tasks.
+
+Interaction with StarExec is mostly via its web interface,
+\url{https://www.starexec.org}.  The interface allows registered users
+to upload and share benchmarks and solvers, to create and manage jobs
+that apply selected solvers to a selection of benchmarks, and to view
+and download job results.  Other features, such as pre-processing of
+benchmarks (e.g., for scrambling) and post-processing of solver
+output, are also supported.
+
+Jobs consist of individual \emph{job pairs}.  Each job pair
+corresponds to a specific solver-benchmark combination.
+Figure~\ref{fig:job-pairs} shows the total number of job pairs for the
+SMT Competition from~2015 to~2018.  Over this period, the number has
+grown by~72\,\%, from~1,028,615 job pairs in~2015 to~1,776,062 job
+pairs in~2018.  (This is the number of unique solver-benchmark
+combinations that were part of the competition.  The number of job
+pairs that were actually run is even higher: test jobs and job pairs
+that had to be re-run, e.g., because of issues with the StarExec
+infrastructure, are not included.)  For comparison, the~2014
+competition only ran~339,714 job
+pairs~\cite{DBLP:journals/jsat/CokDW14}.
+
+Also shown in Figure~\ref{fig:job-pairs} is the total wall-clock time
+(summed over all job pairs) for the competition.  This has more than
+doubled, from 3.5~years in~2015 to 7.6~years in~2018.  (These are
+solver run-times only.  Time that the cluster spent on pre- and
+post-processing of benchmarks and solver output or on other auxiliary
+tasks is not included.)  The increase in~2016 is largely due to the
+inclusion of non-incremental benchmarks with unknown status; these
+were evaluated with a wall-clock time limit of 10~minutes.  In~2017,
+when these benchmarks had become eligible for the main track,
+main-track job pairs were first run with a time limit of 10~minutes;
+when it became apparent to the organizers that there were sufficient
+resources to increase this limit, job pairs that had timed out were
+re-run with a time limit of 20~minutes.  Table~\ref{table:time-limits}
+shows the wall-clock time limits that were imposed for each track and
+year.
+
+\begin{table}
+  \caption{Wall-clock time limits}
+  \label{table:time-limits}
+  \centering
+  \begin{tabular}{|l|r|r|r|r|}
+    \hline
+    & \multicolumn{1}{c|}{2015} & \multicolumn{1}{c|}{2016} & \multicolumn{1}{c|}{2017} & \multicolumn{1}{c|}{2018} \\
+    \hline
+    Main track        & 40\,min & 40\,min & 20\,min & 20\,min \\
+    Application track & 40\,min & 40\,min & 40\,min & 40\,min \\
+    Unsat-core track  &      -- & 40\,min & 40\,min & 40\,min \\
+    \hline
+  \end{tabular}
+\end{table}
+
+StarExec typically reserves between~80 and~150 machines for the SMT
+Competition, allowing its workload to be completed within two to three
+weeks.  By these measures, the SMT Competition has become not only one
+of the heaviest users of StarExec, but also one of the largest
+competitions in automated reasoning.
+
+\begin{figure}
+  \centering
+  \begin{tikzpicture}
+    \draw [gray] (0,0) -- (12,0);
+    \draw [gray] (0,1.5) -- (12,1.5);
+    \draw [gray] (0,3) -- (12,3);
+    \draw [gray] (0,4.5) -- (12,4.5);
+    \draw [gray] (0,6) -- (12,6);
+
+    \node [left] at (0,0) {\footnotesize 0};
+    \node [left] at (0,1.5) {\footnotesize 500,000};
+    \node [left] at (0,3) {\footnotesize 1,000,000};
+    \node [left] at (0,4.5) {\footnotesize 1,500,000};
+    \node [left] at (0,6) {\footnotesize 2,000,000};
+
+    \node [rotate=90] at (-2,3) {\small Job pairs};
+
+    \node [right] at (12,0) {\footnotesize 0};
+    \node [right] at (12,1.5) {\footnotesize 2};
+    \node [right] at (12,3) {\footnotesize 4};
+    \node [right] at (12,4.5) {\footnotesize 6};
+    \node [right] at (12,6) {\footnotesize 8};
+
+    \node [rotate=-90] at (12.9,3) {\small Wall-clock time (years)};
+
+    \draw [fill=black] (1,0) rectangle (2,3.085845); % 1,028,615
+    \draw [fill=black] (3.75,0) rectangle (4.75,4.687632); % 1,562,544
+    \draw [fill=black] (6.5,0) rectangle (7.5,4.366839); % 1,455,613
+    \draw [fill=black] (9.25,0) rectangle (10.25,5.328186); % 1,776,062
+
+    \draw [fill=white] (2,0) rectangle (3,2.6088709094); % 3,4784945459
+    \draw [fill=white] (4.75,0) rectangle (5.75,4.3030490392); % 5,7373987189
+    \draw [fill=white] (7.5,0) rectangle (8.5,5.6286127759); % 7,5048170345
+    \draw [fill=white] (10.25,0) rectangle (11.25,5.7280186691); % 7,6373582255
+
+    \node [below] at (2,0) {\footnotesize 2015};
+    \node [below] at (4.75,0) {\footnotesize 2016};
+    \node [below] at (7.5,0) {\footnotesize 2017};
+    \node [below] at (10.25,0) {\footnotesize 2018};
+  \end{tikzpicture}
+  \caption{Number of job pairs ($\blacksquare$) and total wall-clock time ($\square$).}
+  \label{fig:job-pairs}
+\end{figure}
+
+The StarExec infrastructure has been vitally important in allowing the
+competition to grow to its current size.  The competition organizers
+have given the StarExec developers comprehensive feedback, and filed
+dozens of feature requests and bug reports since~2013.  The
+infrastructure has become increasingly stable; serious issues are now
+rare.  When they did surface during an ongoing competition, they
+received a swift response by the StarExec team (under the lead of
+Aaron Stump).  This has been critical to the success of the
+competition on more than one occasion.
 
@@
 
+inclusion of check-sat commands with unknown status in the application track
+
+competition-wide rankings for application and unsat-core track
+
+more benchmarks, especially for underrepresented (i.e., small) logics
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2018-10-22 2018/report/SMT-COMP.tex
affiliation, fixes

@@
   \email{niemetz@cs.stanford.edu} \\
-  \addr Affiliation \\
-  City \\
-  Country
+  \addr Stanford University\\
+  Stanford \\
+  USA
   \AND
@@
     \hline
-    ABC [\TODO]       & Valera Balabanov
+    ABC [\TODO]       & Valeriy Balabanov
                         (Mentor Graphics)\\
@@
 The 2018 edition of the competition was again part of the FLoC Olympic
-Games, which sponsored seven Kurt G\"odel medals.  The competition
+Games, which sponsored seven FLoC 2018 medals.  The competition
 organizers awarded these to the following solvers:

### 2018-10-23 2018/report/SMT-COMP.tex
Nicer typesetting of SMT-LIB syntax; separate file size distributions

@@
 \usepackage{tikz}
+
+\usepackage{listings}
+\lstdefinelanguage{smtlib2}
+  {alsoletter={-, =},
+   morekeywords={set-logic,declare-fun,assert,check-sat,set-info,exit},
+   sensitive=false,
+   morecomment=[l]{;}}
+\lstset{language=smtlib2,
+basicstyle=\sffamily,
+numbers=none,
+keywordstyle=\bfseries\sffamily,
+keywordstyle={[2]\bfseries\sffamily\underbar}
+}
 
@@
   of the SMT Competition during the last FLoC Olympiad, from 2015 to
-  2018. \TODO: some notable observations/conclusions?
+  2018.  These competitions set several new records regarding the
+  number of participants, number of benchmarks used, and amount of
+  computation performed.
 \end{abstract}
@@
 Figure~\ref{fig:smtlib-example} shows the example formula from
-Section~\ref{sec:introduction} as a benchmark in SMT-LIB syntax.
-In~2016, benchmarks were updated from version~2.0 to version~2.5 of
-the SMT-LIB language.  Since~2017, benchmarks are written in
-version~2.6.  Fortunately, versions~2.5 and~2.6 are largely
-backwards-compatible to 2.0, so that older solvers are still able to
-compete with at most minor modifications.
+Section~\ref{sec:introduction} as a benchmark in SMT-LIB syntax, with
+commands to the SMT solver typeset in bold.  In~2016, benchmarks were
+updated from version~2.0 to version~2.5 of the SMT-LIB language.
+Since~2017, benchmarks are written in version~2.6.  Fortunately,
+versions~2.5 and~2.6 are largely backwards-compatible to 2.0, so that
+older solvers are still able to compete with at most minor
+modifications.
 
 \begin{figure}
-\begin{verbatim}
+\begin{lstlisting}
 (set-info :smt-lib-version 2.6)
@@
 (exit)
-\end{verbatim}
+\end{lstlisting}
 \caption{A benchmark problem in SMT-LIB syntax.}
@@
 
-    \draw [fill=black] (0.5,0) rectangle (1.5,5.1630077857); % 54535
-    \draw [fill=black] (2.25,0) rectangle (3.25,5.5885514492); % 161995
-    \draw [fill=black] (4,0) rectangle (5,5.3624537158); % 90841
-    \draw [fill=black] (5.75,0) rectangle (6.75,4.9369959734); % 30588
-    \draw [fill=black] (7.5,0) rectangle (8.5,4.4297518088); % 8355
-    \draw [fill=black] (9.25,0) rectangle (10.25,3.3931037653); % 589
-    \draw [fill=black] (11,0) rectangle (12,2.7264453999); % 107
-    \draw [fill=black] (12.75,0) rectangle (13.75,0.9); % 1
+    \draw [fill=black] (0.5,0) rectangle (1,5.1629791157); % 54531
+    \draw [fill=black] (2.25,0) rectangle (2.75,5.5836542368); % 159978
+    \draw [fill=black] (4,0) rectangle (4.5,5.350394013); % 88081
+    \draw [fill=black] (5.75,0) rectangle (6.25,4.8786283826); % 26345
+    \draw [fill=black] (7.5,0) rectangle (8,4.3889077926); % 7526
+    \draw [fill=black] (9.25,0) rectangle (9.75,3.1918883971); % 352
+    \draw [fill=black] (11,0) rectangle (11.5,2.2422255245); % 31
+    %\draw [fill=black] (12.75,0) rectangle (13.25,0); % 0
+
+    \draw [fill=white] (1,0) rectangle (1.5,1.4418539922); % 4
+    \draw [fill=white] (2.75,0) rectangle (3.25,3.8742353084); % 2017
+    \draw [fill=white] (4.5,0) rectangle (5,3.9968181739); % 2760
+    \draw [fill=white] (6.25,0) rectangle (6.75,4.1649057286); % 4243
+    \draw [fill=white] (8,0) rectangle (8.5,3.5266990775); % 829
+    \draw [fill=white] (9.75,0) rectangle (10.25,3.0372735114); % 237 
+    \draw [fill=white] (11.5,0) rectangle (12,2.5927322331); % 76
+    \draw [fill=white] (13.25,0) rectangle (13.75,0.9); % 1
 
@@
   \end{tikzpicture}}
-  \caption{Distribution of SMT-LIB benchmarks by file size (2018).}
+  \caption{Distribution of SMT-LIB benchmarks by file size (2018), for
+    non-incremental~($\blacksquare$) and incremental~($\square$)
+    benchmarks.}
   \label{fig:benchmark-sizes}
@@
     \hline
-    Main track        & 40\,min & 40\,min & 20\,min & 20\,min \\
-    Application track & 40\,min & 40\,min & 40\,min & 40\,min \\
-    Unsat-core track  &      -- & 40\,min & 40\,min & 40\,min \\
+    Main track        & 40~min & 40~min & 20~min & 20~min \\
+    Application track & 40~min & 40~min & 40~min & 40~min \\
+    Unsat-core track  &     -- & 40~min & 40~min & 40~min \\
     \hline

### 2018-11-20 2018/report/SMT-COMP.tex
medals
Introduction

@@
 %\usepackage{pst-tree}
+
+%\usepackage[numbers,sort&compress]{natbib}
 
@@
 from a number of background theories.  Background theories, which are
-motivated by application domains, include the theory of
-arrays~\cite{TODO}, integer and real arithmetic~\cite{TODO},
-bit-vectors~\cite{TODO}, and floating-point numbers~\cite{TODO} among
-others.  For instance, the following is an SMT formula over the
-combination of integer arithmetic and uninterpreted functions:
+motivated by application domains, include the theory of arrays,
+integer and real arithmetic, bit-vectors, and floating-point numbers
+among others~\cite{BarFT-RR-17}.  For instance, the following is an
+SMT formula over the combination of integer arithmetic and
+uninterpreted functions:
 %
@@
 with (semi-)decision procedures for the background theories that the
-solver supports~\cite{TODO,TODO,TODO}.  Historically, SMT solvers have
-focused on quantifier-free formulas and decidable combinations of
-background theories.  Increasingly, however, SMT solvers also support
-quantified formulas.  Hence there is overlap between SMT solving and
-automated theorem proving for quantified Boolean formulas (QBF),
-first-order logic, and even higher-order logic~\cite{TODO}.
+solver
+supports~\cite{DBLP:conf/cav/BarrettCDHJKRT11,DBLP:conf/cade/BoutonODF09,DBLP:conf/tacas/MouraB08}.
+Historically, SMT solvers have focused on quantifier-free formulas and
+decidable combinations of background theories.  Increasingly, however,
+SMT solvers also support quantified formulas.  Hence there is overlap
+between SMT solving and automated theorem proving for quantified
+Boolean formulas (QBF), first-order logic, and even higher-order
+logic~\cite{DBLP:journals/corr/abs-1712-01486}.
 
 The International Satisfiability Modulo Theories Competition
-(SMT-COMP) is an annual competition between SMT solvers.  It was
-instituted in~2005~\cite{BdMS05}, and is affiliated with the
-International Workshop on Satisfiability Modulo Theories.  Solvers are
-submitted to the competition by their developers, and pitted against
-each other in a number of tracks and divisions.  The SMT Competition
-was part of the Federated Logic Conference (FLoC) Olympic Games, which
-comprised 14 competitions in various areas of computational logic, in
-Vienna in~2014, and again in Oxford~(UK) in~2018.  It was last
-described in a 2014 competition
-report~\cite{DBLP:journals/jsat/CokDW14}.  In this paper, we report on
-the design and selected results of the competition during the last
-FLoC Olympiad, from 2015 to~2018.
-
-\begin{tjark}
-  WIP
-
-  structure of the paper
-\end{tjark}
+(SMT-COMP)~\cite{BdMS05,BdMS07,BDdMOS13,BDOS08,BDOS10,CDW14,CGBD12} is
+an annual competition between SMT solvers.  It was instituted in~2005,
+and is affiliated with the International Workshop on Satisfiability
+Modulo Theories.  Solvers are submitted to the competition by their
+developers, and pitted against each other in a number of tracks and
+divisions.  The SMT Competition was part of the Federated Logic
+Conference (FLoC) Olympic Games, which comprised 14 competitions in
+various areas of computational logic, in Vienna in~2014, and again in
+Oxford~(UK) in~2018.  It was last described in a 2014 competition
+report~\cite{CDW14}.  In this paper, we report on the design and
+selected results of the competition during the last FLoC Olympiad,
+from 2015 to~2018.
+
+For space reasons, the discussion in this paper is necessarily
+limited.  Complete data about past competitions since 2015 (and partly
+for earlier competitions) is available from the competition web site,
+\url{http://www.smtcomp.org}.  This includes detailed results for each
+solver/benchmark combination, totaling nearly 6 million data records
+(about 1.1~GB in CSV format).
+
+The rest of this paper is structured as follows.  In
+Section~\ref{sec:goals}, we present the goals and organization of the
+competition.  Section~\ref{sec:smtlib} introduces the SMT-LIB language
+and library, and Section~\ref{sec:benchmarks} discusses competition
+divisions and benchmarks.  The competition is being run on StarExec,
+which is described in Section~\ref{sec:starexec}.
+Section~\ref{sec:participants} gives an overview of participating
+solvers.  The details of the competition procedure are described in
+Section~\ref{sec:procedure}, and selected results are presented and
+analyzed in Section~\ref{sec:results}.  We conclude with suggestions
+for future SMT Competitions in Section~\ref{sec:conclusions}.
 
@@
 ``significantly lessens the ability of a competition to determine
-`best' solvers.''~\cite{DBLP:journals/jar/CokSW15} Together with the
-increased computational resources available to the competition since
-its move to StarExec, this prompted a paradigm shift.  Since 2015, the
-competition is evaluating all solvers on all eligible
-benchmarks. \TODO: benchmark weights
+`best' solvers.''~\cite{CSW15} rTogether with the increased
+computational resources available to the competition since its move to
+StarExec, this prompted a paradigm shift.  Since 2015, the competition
+is evaluating all solvers on all eligible benchmarks. \TODO: benchmark
+weights
 
@@
 
-Since 2014 (and previously for the evaluation in
-2013~\cite{DBLP:journals/jar/CokSW15}), the computational workload of
-the competition is being run on StarExec, a ``cross-community
-infrastructure for logic solving''~\cite{DBLP:conf/cade/StumpST14}
-developed at the University of Iowa and supported by the National
-Science Foundation.  Each machine in the StarExec cluster is equipped
-with two E5-2609 Intel Xeon processors (10~MiB Cache, 2.4~GHz).  This
-hardware configuration has been unchanged since~2013.  Up to two
-solvers are run simultaneously on each machine: one solver on each
-processor, with four cores available.  Memory usage is limited
-to~60~GiB per solver.
+Since 2014 (and previously for the evaluation in 2013~\cite{CSW15}),
+the computational workload of the competition is being run on
+StarExec, a ``cross-community infrastructure for logic
+solving''~\cite{DBLP:conf/cade/StumpST14} developed at the University
+of Iowa and supported by the National Science Foundation.  Each
+machine in the StarExec cluster is equipped with two E5-2609 Intel
+Xeon processors (10~MiB Cache, 2.4~GHz).  This hardware configuration
+has been unchanged since~2013.  Up to two solvers are run
+simultaneously on each machine: one solver on each processor, with
+four cores available.  Memory usage is limited to~60~GiB per solver.
 
@@
 infrastructure, are not included.)  For comparison, the~2014
-competition only ran~339,714 job
-pairs~\cite{DBLP:journals/jsat/CokDW14}.
+competition only ran~339,714 job pairs~\cite{CDW14}.
 
@@
 competitions from 2005--2014 only received an average of 12
-submissions~\cite{DBLP:journals/jsat/CokDW14}.
+submissions~\cite{CDW14}.
 
@@
 The 2018 edition of the competition was again part of the FLoC Olympic
-Games, which sponsored seven FLoC 2018 medals.  The competition
-organizers awarded these to the following solvers:
+Games, which sponsored seven medals.  The competition organizers
+awarded these to the following solvers:
 \begin{itemize}

### 2018-11-20 2018/report/SMT-COMP.tex
Minor, references, table for competition-wide ranking

@@
 limited.  Complete data about past competitions since 2015 (and partly
-for earlier competitions) is available from the competition web site,
+for earlier competitions) is available from the competition website,
 \url{http://www.smtcomp.org}.  This includes detailed results for each
@@
 happened later.)  The competition chair then assembles a team of
-organizers, and distributes the work for the next edition of the
+organizers, and oversees the work for the next edition of the
 competition.
@@
 The competition rules are revised each year, and a (near final) draft
-version of the rules is made public on the competition web site around
+version of the rules is made public on the competition website around
 mid-April.  The competition chair has ultimate responsibility for the
@@
 repository~\cite{smtlib-repository}, and each new release is mirrored
-on StarExec, the cluster on which the competition runs.  Users of SMT
-solvers are encouraged to submit new and interesting benchmarks to the
-library, which has grown from 1,352 benchmarks in~2005~\cite{BdMS05}
-to 347,011 benchmarks in 2018.
+on StarExec.  Users of SMT solvers are encouraged to submit new and
+interesting benchmarks to the library, which has grown from 1,352
+benchmarks in~2005~\cite{BdMS05} to 347,011 benchmarks in 2018.
 
@@
 Section~\ref{sec:introduction} as a benchmark in SMT-LIB syntax, with
-commands to the SMT solver typeset in bold.  In~2016, benchmarks were
-updated from version~2.0 to version~2.5 of the SMT-LIB language.
-Since~2017, benchmarks are written in version~2.6.  Fortunately,
-versions~2.5 and~2.6 are largely backwards-compatible to 2.0, so that
-older solvers are still able to compete with at most minor
-modifications.
+commands to the SMT solver typeset in bold.
+
+In~2016, benchmarks were updated from version~2.0 to version~2.5 of
+the SMT-LIB language.  Since~2017, benchmarks are written in
+version~2.6.  Fortunately, versions~2.5 and~2.6 are largely
+backwards-compatible to 2.0, so that older solvers are still able to
+compete with at most minor modifications.
 
@@
   check-sat} commands.  These benchmarks originate from applications
-such as bounded model checking~\cite{TODO}, where SMT solvers interact
-with other tools in a feedback loop.
+such as bounded model
+checking~\cite{Gunther:2014:IBS:2632362.2632374}, where SMT solvers
+interact with other tools in a feedback loop.
 
@@
 \emph{application track}, which has been part of the competition since
-2011~\cite{TODO}, features incremental benchmarks.  These benchmarks
-are passed to each solver one command at a time by a trace executor,
-which waits for the solver's response before passing the next
-benchmark command (to prevent look-ahead behavior).  The
+2011~\cite{BDdMOS13}, features incremental benchmarks.  These
+benchmarks are passed to each solver one command at a time by a trace
+executor, which waits for the solver's response before passing the
+next benchmark command (to prevent look-ahead behavior).  The
 \emph{unsat-core track} uses main-track benchmarks that are known to
@@
 subset of the benchmark's assertions).  The unsat-core track had first
-been part of the competition in 2012~\cite{TODO}, but was then
+been part of the competition in 2012~\cite{CGBD12}, but was then
 discontinued partly because of the competition's move to StarExec and
@@
 ``significantly lessens the ability of a competition to determine
-`best' solvers.''~\cite{CSW15} rTogether with the increased
+`best' solvers.''~\cite{CSW15} Together with the increased
 computational resources available to the competition since its move to
@@
 Jobs consist of individual \emph{job pairs}.  Each job pair
-corresponds to a specific solver-benchmark combination.
+corresponds to a specific solver/benchmark combination.
 Figure~\ref{fig:job-pairs} shows the total number of job pairs for the
@@
 grown by~72\,\%, from~1,028,615 job pairs in~2015 to~1,776,062 job
-pairs in~2018.  (This is the number of unique solver-benchmark
+pairs in~2018.  (This is the number of unique solver/benchmark
 combinations that were part of the competition.  The number of job
@@
 resources to increase this limit, job pairs that had timed out were
-re-run with a time limit of 20~minutes.  Table~\ref{table:time-limits}
-shows the wall-clock time limits that were imposed for each track and
-year.
+re-run with a time limit of 20~minutes.  (In this way, about 2.9 years
+of wall-clock time in 2017 were spent on job pairs that were then
+re-run.  This time is not included in Figure~\ref{fig:job-pairs}.)
+Table~\ref{table:time-limits} shows the wall-clock time limits that
+were imposed on job pairs for each track and year.
 
 \begin{table}
-  \caption{Wall-clock time limits}
+  \caption{Wall-clock time limits.}
   \label{table:time-limits}
@@
     \hline
-    Main track        & 40~min & 40~min & 20~min & 20~min \\
-    Application track & 40~min & 40~min & 40~min & 40~min \\
-    Unsat-core track  &     -- & 40~min & 40~min & 40~min \\
+    Main track        & 40~min & 40~min & 20~min\protect\footnotemark & 20~min \\
+    Application track & 40~min & 40~min & 40~min\phantom{$^{1.}$} & 40~min \\
+    Unsat-core track  &     -- & 40~min & 40~min\phantom{$^{1.}$} & 40~min \\
     \hline
@@
 \end{table}
+\footnotetext{These job pairs were first run with a time limit of
+  10~minutes.  See the text for details.}
 
@@
 \end{figure}
-
-The StarExec infrastructure has been vitally important in allowing the
-competition to grow to its current size.  The competition organizers
-have given the StarExec developers comprehensive feedback, and filed
-dozens of feature requests and bug reports since~2013.  The
-infrastructure has become increasingly stable; serious issues are now
-rare.  When they did surface during an ongoing competition, they
-received a swift response by the StarExec team (under the lead of
-Aaron Stump).  This has been critical to the success of the
-competition on more than one occasion.
 
@@
 the SMT solving approach used.  System descriptions are published on
-the SMT-COMP website~\cite{smtcomp-web}.  They were submitted for
-about 60\,\% of all solver versions since 2015.
+the SMT-COMP website.  They were submitted for about 60\,\% of all
+solver versions since 2015.
 
@@
   \centering
-  \begin{tabular}{|l|p{13cm}|} %TODO: fix width
+  \begin{tabular}{|l|p{11.7cm}|} %TODO: fix width
     \hline
@@
     \hline
-    ABC [\TODO]       & Valeriy Balabanov
+    ABC~\cite{DBLP:conf/cav/BraytonM10} & Valeriy Balabanov
                         (Mentor Graphics)\\
@@
                         (CNRS and University of Paris-Sud)\\
-    AProVE            & Carsten Fuhs
+    AProVE~\cite{DBLP:conf/cade/GieslBEFFOPSSST14} & Carsten Fuhs
                         (University College London; Birkbeck, University of London)\\
-    Boolector         & Mathias Preiner
+    Boolector~\cite{DBLP:conf/cav/NiemetzPWB18} & Mathias Preiner
                         (Johannes Kepler University)\\
-    COLIBRI           & Fran\c{c}ois Bobot
+    COLIBRI~\cite{colibri} & Fran\c{c}ois Bobot
                         (French Alternative Energies and Atomic Energy Commission)\\
-    Ctrl-Ergo         & Mohamed Iguernlala
+    Ctrl-Ergo~\cite{ctrl-ergo} & Mohamed Iguernlala
                         (CNRS and University of Paris-Sud)\\
-    CVC3              & Kshitij Bansal
+    CVC3~\cite{cvc3}  & Kshitij Bansal
                         (New York University)\\
-    CVC4              & Kshitij Bansal, Clark Barrett, Andres N\"otzli, Duligur Ibeling
+    CVC4~\cite{DBLP:conf/cav/BarrettCDHJKRT11}  & Kshitij Bansal, Clark Barrett, Andres N\"otzli, Duligur Ibeling
                         (New York University; Stanford University)\\
-    MapleSTP          & Jimmy Liang
+    MapleSTP~\cite{maplestp} & Jimmy Liang
                         (University of Waterloo)\\
-    MinkeyRink        & Trevor Hansen
+    MinkeyRink~\cite{minkeyrink} & Trevor Hansen
                         (University of Melbourne)\\
-    OpenSMT2          & Matteo Marescotti, Antti Hyv\"arinen
+    OpenSMT2~\cite{opensmt2} & Matteo Marescotti, Antti Hyv\"arinen
                         (University of Lugano)\\
-    ProB              & Sebastian Krings
+    ProB~\cite{prob}  & Sebastian Krings
                         (University of D\"usseldorf)\\
-    Q3B               & Martin Jon\'a\v{s}
+    Q3B~\cite{q3b}    & Martin Jon\'a\v{s}
                         (Masaryk University)\\
-    raSAT             & Tung Vu Xuan
+    raSAT~\cite{rasat} & Tung Vu Xuan
                         (Japan Advanced Institute of Science and Technology)\\
-    Redlog            & Haniel Barbosa
+    Redlog~\cite{redlog} & Haniel Barbosa
                         (Inria Nancy)\\
-    SMT-RAT           & Florian Corzilius, Gereon Kremer
+    SMT-RAT~\cite{smt-rat} & Florian Corzilius, Gereon Kremer
                         (RWTH Aachen University)\\
-    SMTInterpol       & J\"urgen Christ
+    SMTInterpol~\cite{} & J\"urgen Christ
                         (University of Freiburg)\\
-    SPASS-SATT        & Martin Bromberger
+    SPASS-SATT~\cite{} & Martin Bromberger
                         (Max Planck Institute for Informatics)\\
-    STP               & Mate Soos, Trevor Hansen, Norbert Manthey
+    STP~\cite{}        & Mate Soos, Trevor Hansen, Norbert Manthey
                         (National University of Singapore; University of Melbourne; Amazon Web Services)\\
-    toysmt            & Masahiro Sakai
+    toysmt~\cite{}     & Masahiro Sakai
                         (Toshiba Corporation)\\
-    Vampire           & Giles Reger
+    Vampire~\cite{}    & Giles Reger
                         (University of Manchester)\\
-    veriT             & David D\'eharbe, Haniel Barbosa, Hans-J\"org Schurr
+    veriT~\cite{DBLP:conf/cade/BoutonODF09} & David D\'eharbe, Haniel Barbosa, Hans-J\"org Schurr
                         (Federal University of Rio Grande do Norte; Inria Nancy)\\
-    XSat              & Martin Velez
+    XSat~\cite{}       & Martin Velez
                         (University of California, Davis)\\
-    Yices2            & Bruno Dutertre, Dejan Jovanovi\'c
+    Yices2~\cite{}     & Bruno Dutertre, Dejan Jovanovi\'c
                         (SRI International)\\
-    Z3                & Christoph Wintersteiger, Aleksandar Zelji\'c
+    Z3~\cite{DBLP:conf/tacas/MouraB08} & Christoph Wintersteiger, Aleksandar Zelji\'c
                         (Microsoft Research; Uppsala University)\\
@@
 \TODO: explain those aspects of the procedure that are required to
-understand the results (e.g., time limits, scoring)
+understand the results (e.g., scoring)
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{FLoC Olympic Games}
+\subsection{Division Rankings}
+\label{sec:division-rankings}
+
+\TODO
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection{Competition-Wide Ranking}
 \label{sec:floc}
@@
 competition organizers decided to award these to the winner of the
-main track's QF\_BV division (which has historically been the logic
+main track's QF\_BV division (which had historically been the logic
 with the largest number of solver submissions and job pairs), as well
@@
 ranking that had been instituted especially for this
-purpose~\cite{DBLP:journals/jsat/CokDW14}.  This ranking emphasizes
-breadth of solver participation---a solver participating in many
-logics need not be the best in any one of them to rank highly.
+purpose~\cite{CDW14}.  This ranking emphasizes breadth of solver
+participation---a solver participating in many logics need not be the
+best in any one of them to rank highly.
 
 The competition-wide ranking for the main track was retained and
-refined after~2014.  A contentious issue with this ranking has been
-the scoring of incorrect solver responses.  In the per-division
-rankings, an incorrect response causes a solver to be ranked behind
-all correct solvers~\cite{rules18}.  But the competition's main track
-consists of many independent divisions.  To balance the strong
-interest in correct solvers against the risk of stifling innovation,
-the competition-wide ranking was revised in~2017 to use a fixed
-numeric penalty for each division with incorrect responses.  The value
-of this penalty is currently set so that entering a (possibly buggy)
-solver that can solve all benchmarks into a division has a positive
-expected score if the probability of a soundness bug in the solver is
-below~$20\,\%$.
+refined after~2014.  Table~\ref{table:competition-wide-ranking} shows
+the best three solvers according to this ranking for 2015--2018.  Also
+shown is Z3, which ranked highly each year but was running hors
+concours.  Sequential and parallel performance are reported
+separately.
+%
+Note that scores are not directly comparable between different years:
+the set of benchmarks changes from one year to the next, and also the
+formula to compute the score changed (see below).  Moreover, readers
+should keep in mind that this ranking---like any method that maps the
+performance of solvers for a broad range of logics to a
+one-dimensional value---is inherently limited.  We refer to the
+individual division rankings (Section~\ref{sec:division-rankings}) for
+more detailed information.
+
+\begin{table}
+  \caption{Competition-wide ranking for the main track: best solvers (by year).}
+  \label{table:competition-wide-ranking}
+  \centering
+  \scalebox{.89}{\begin{tabular}{|c|p{2.2cm}|r|r|p{0cm}|c|p{2.2cm}|r|r|}
+    \cline{1-4} \cline{6-9}
+    \multicolumn{4}{|c|}{2015} & & \multicolumn{4}{c|}{2016} \\ \cline{1-4} \cline{6-9}
+    Rank & Solver & Score  & Score  & & Rank & Solver & Score & Score \\
+         &        & (sequential) & (parallel) & & & & (sequential) & (parallel) \\ \cline{1-4} \cline{6-9}
+         & [Z3]              & 159.36 & 159.36 & &    & [Z3]   & 185.09 & 185.09 \\
+      1. & CVC4              & 144.67 & 144.74 & & 1. & CVC4   & 180.95 & 181.19 \\
+      2. & CVC4(exp)\footnotemark & 140.47 & 140.51 & & 2. & Yices2 & 119.29 & 119.29 \\
+      3. & Yices             & 101.91 & 101.91 & & 3. & veriT  &  75.11 &  75.11 \\ \cline{1-4} \cline{6-9}
+  \end{tabular}}
+
+  \medskip
+
+  \scalebox{.89}{\begin{tabular}{|c|p{2.2cm}|r|r|p{0cm}|c|p{2.2cm}|r|r|}
+    \cline{1-4} \cline{6-9}
+    \multicolumn{4}{|c|}{2017} & & \multicolumn{4}{c|}{2018} \\ \cline{1-4} \cline{6-9}
+    Rank & Solver & Score  & Score  & & Rank & Solver & Score & Score \\
+         &        & (sequential) & (parallel) & & & & (sequential) & (parallel) \\ \cline{1-4} \cline{6-9}
+         & [Z3]        & 171.99 & 171.99 & & 1. & CVC4        & 211.99 & 211.99 \\
+      1. & CVC4        & 161.38 & 161.76 & &    & [Z3]        & 186.19 & 186.19 \\
+      2. & Yices2      & 110.63 & 110.63 & & 2. & Yices2      & 115.26 & 115.26 \\
+      3. & SMTInterpol &  65.96 &  66.00 & & 3. & SMTInterpol &  65.32 &  65.38 \\ \cline{1-4} \cline{6-9}
+  \end{tabular}}
+\end{table}
+\footnotetext{This was a distinct version of CVC4 that was designated as experimental.}
+
+A contentious issue with this ranking has been the scoring of
+incorrect solver responses.  In the division rankings, an incorrect
+response causes a solver to be ranked behind all correct solvers for
+that division.  But the competition's main track consists of many
+independent divisions.  To balance the strong interest in correct
+solvers against the risk of stifling innovation, the competition-wide
+ranking was revised in~2017 to use a fixed numeric penalty for each
+division with incorrect responses.  The value of this penalty is
+currently set so that entering a (possibly buggy) solver that can
+solve all benchmarks into a division has a positive expected score if
+the probability of a soundness bug in the solver is
+below~$20\,\%$.~\cite{rules18}
 
@@
 \item The best three main-track solvers according to the
-  competition-wide ranking (first place: CVC4, second place:
-  Yices-2.6.0, third place: SMTInterpol);
-\item the solver(s) that won the QF\_BV division in the main track
-  (sequential ranking: Boolector, parallel ranking: Minkeyrink-MT);
+  competition-wide ranking (see
+  Table~\ref{table:competition-wide-ranking}),
+\item the solvers that won the QF\_BV division in the main track (see
+  Table~\ref{TODO}),
+  % TODO (sequential ranking: Boolector, parallel ranking: Minkeyrink-MT);
 \item the solver that won the most competitive divisions in the
-  application track (Yices-2.6.0);
+  application track (see Table~\ref{TODO}),
 \item the solver that won the most competitive divisions in the
-  unsat-core track (Yices-2.6.0).
+  unsat-core track (see Table~\ref{TODO}).
 \end{itemize}
+
+%TODO The latter two medals were won by Yices-2.6.0.
 
@@
 ranking for the other tracks is that each main-track benchmark is
-worth one point (before weighing) if solved correctly, while
-benchmarks in the application and unsat-core track are worth widely
-varying numbers of points.  Moreover, in the unsat-core track, the
-size of the smallest unsatisfiable core---and hence the number of
-points attainable on any given benchmark---may not be known precisely.
+worth one point (before benchmark weights are applied) if solved
+correctly, while benchmarks in the application and unsat-core track
+are worth widely varying numbers of points.  Moreover, in the
+unsat-core track, the size of the smallest unsatisfiable core---and
+hence the number of points attainable on any given benchmark---may not
+be known precisely.
+
+\subsection{Improvement Over Time}
+
+\TODO
+
+\subsection{Other Measures}
+
+\TODO
 
@@
 more benchmarks, especially for underrepresented (i.e., small) logics
+
+The StarExec infrastructure has been vitally important in allowing the
+competition to grow to its current size.  The competition organizers
+have given the StarExec developers comprehensive feedback, and filed
+dozens of feature requests and bug reports since~2013.  The
+infrastructure has become increasingly stable; serious issues are now
+rare.  When they did surface during ongoing competitions, they
+received a swift response by the StarExec team (under the lead of
+Aaron Stump).  This has been critical to the success of the
+competition on more than one occasion.
 

### 2018-11-21 2018/report/SMT-COMP.tex
Conclusion

@@
 
-StarExec typically reserves between~80 and~150 machines for the SMT
+StarExec typically reserves between~80 to~150 machines for the SMT
 Competition, allowing its workload to be completed within two to three
@@
 solve all benchmarks into a division has a positive expected score if
-the probability of a soundness bug in the solver is
-below~$20\,\%$.~\cite{rules18}
+the probability that a soundness bug in the solver will be triggered
+is below~$20\,\%$.~\cite{rules18}
 
@@
 
-\TODO
-
-inclusion of check-sat commands with unknown status in the application track
-
-competition-wide rankings for application and unsat-core track
-
-more benchmarks, especially for underrepresented (i.e., small) logics
+After 13 years, the SMT Competition is a well-established event that
+garners wide interest from developers and users of SMT solvers.  The
+competition continues to contribute to its original goals, including
+adoption of the SMT-LIB format and sparking further advances in SMT,
+and it provides a yardstick of performance for SMT solvers.
+
+The last FLoC Olympiad was a period of significant growth for the SMT
+Competition.  The average number of solver submissions increased
+from~12 (for 2005--2014) to~26 (for 2015--2018).  The number of
+SMT-LIB benchmarks used in the competition increased from~77,352
+in~2014~\cite{CDW14} to 342,498 in 2018.  This is partly because new
+benchmarks were added to the SMT Library, but also because benchmarks
+with unknown status are now eligible for the competition, and because
+the earlier culling of benchmarks was abandoned.  Since the
+re-introduction of the unsat-core track in~2016, the competition again
+has three separate tracks.  This, together with new logics in the SMT
+Library, has brought the total number of competition divisions to 115
+in~2018, up from just 40 divisions in~2014~\cite{CDW14}.  The number
+of job pairs increased from 339,714 in~2014 to~1,776,062~in 2018, and
+the total wall-clock time in~2018 exceeded 7.6~years.  By these
+measures, the SMT Competition is one of the largest competitions in
+automated reasoning.
 
@@
 have given the StarExec developers comprehensive feedback, and filed
-dozens of feature requests and bug reports since~2013.  The
+dozens of feature requests and bug reports since 2013.  The
 infrastructure has become increasingly stable; serious issues are now
@@
 competition on more than one occasion.
+
+Despite the substantial amount of computational resources available to
+the competition through StarExec, the competition has reached a size
+where future organizers will have to carefully consider the number of
+participants and benchmarks each year, to determine whether the
+current time limits remain tenable.  (Otherwise, reducing the time
+limits would probably be a better solution than reverting to the
+pre-2014 practice of benchmark culling.)
+
+Further development of the competition should be undertaken with care,
+keeping in mind that any major changes require not just the
+competition organizers, but also participants to adapt.  Immediate
+action items for next year's organizers are
+\begin{itemize}
+\item the inclusion of {\tt check-sat} commands with unknown status in
+  the application track; and
+\item the definition of competition-wide rankings for the application
+  and unsat-core track.
+\end{itemize}
+
+For the inclusion of new tracks or divisions, a two-phase approach has
+proven successful.  A new division is first declared
+\emph{experimental}, meaning that results will be reported but no
+official winner will be announced.  This allows competition organizers
+and participants to gain valuable experience, while reducing the
+impact of mistakes.  If successful, the division may then become
+regular in the following year.
+
+Organizing the competition is a non-trivial amount of work.  Much of
+this happens behind the scenes.  For instance, the competition tools
+(such as the benchmark scrambler and trace executor) often require
+updating when new divisions are added, or when changes are made to
+StarExec.  One could imagine adding further tracks (e.g., for
+proof-producing SMT solvers, or for variants such as max-SMT) to the
+competition, but the effort required to support such tracks will need
+to be balanced against their added value.
+
+To ensure that the competition results are practically relevant, it is
+important that the SMT Library contains benchmarks that cover a wide
+range of applications.  To this end, we again encourage users of SMT
+solvers to submit new and interesting benchmarks to the library,
+especially for underrepresented logics.  This is not just a valuable
+contribution to the community, but also---since these benchmarks will
+then be used in the competition---a straightforward way to get solver
+developers to tune their solvers accordingly.
+
+\paragraph{Acknowledgments}
+
+We would like to thank Aaron Stump for allowing the SMT Competition to
+run on StarExec; the SMT-LIB maintainers, namely Clark Barrett, Pascal
+Fontaine, Aina Niemetz and Mathias Preiner, for preparing the annual
+SMT-LIB release; all contributors of new benchmarks to the SMT
+Library; and last but not least all solver developers who entered
+their solver into the competition.
 

### 2018-11-21 2018/report/SMT-COMP.tex
Minor

@@
   \centering
-  \begin{tikzpicture}
+  \scalebox{.98}{\begin{tikzpicture}
     \draw [gray] (0,0) -- (12,0);
@@
     \node [below] at (10.25,0) {\footnotesize 2018};
-  \end{tikzpicture}
+  \end{tikzpicture}}
   \caption{Number of job pairs ($\blacksquare$) and total wall-clock time ($\square$).}
@@
 adoption of the SMT-LIB format and sparking further advances in SMT,
-and it provides a yardstick of performance for SMT solvers.
+and provides a yardstick of performance for SMT solvers.
 
@@
 Further development of the competition should be undertaken with care,
-keeping in mind that any major changes require not just the
-competition organizers, but also participants to adapt.  Immediate
-action items for next year's organizers are
+keeping in mind that major changes require not just the competition
+organizers, but also participants to adapt.  Immediate action items
+for next year's organizers are
 \begin{itemize}

### 2018-11-22 2018/report/SMT-COMP.tex
Tables with winners

@@
   \name{David D\'{e}harbe (co-organizer, 2015--2016)}
-  \email{david@dimap.ufrn.br} \\
-  \addr Federal University of Rio Grande do Norte \\
-  Natal \\
-  Brazil
+  \email{david.deharbe@clearsy.com} \\
+  \addr ClearSy Systems Engineering \\
+  Aix-en-Provence \\
+  France
   \AND
@@
 
+In tables~\ref{tab:winners-main-1},~\ref{tab:winners-main-2} and
+~\ref{tab:winners-unsat-core}, entries $A/B$ indicate that solver $A$
+is the winner considering sequential performance, while $B$ is the
+winner considering parallel performance. When the same solver has won
+both, which is most often the case, its name appears just once. All
+runs in the application track are sequential and therefore only
+sequential performance is used to determine the winners.
+
+\include{table-winners-main}
+
+\include{table-winners-application}
+
+\include{table-winners-unsat-core}
+
 \TODO

### 2018-11-22 2018/report/table-winners-main.tex
Tables with winners

\begin{table}[]
\begin{center}
\scalebox{.89}{\begin{tabular}{rcccc}
\hline
Logic  & 2015                          & 2016                                & 2017                          & 2018                                  \\
\hline
\multicolumn{1}{l}{}            & \multicolumn{1}{l}{}          & \multicolumn{1}{l}{}                & \multicolumn{1}{l}{}          & \multicolumn{1}{l}{}                  \\ \cline{5-5} 
ABVFP                           & \multicolumn{1}{l}{}          & \multicolumn{1}{l}{}                & \multicolumn{1}{l|}{}         & \multicolumn{1}{c|}{CVC4}             \\ \cline{2-5} 
\multicolumn{1}{r|}{ALIA}       & \multicolumn{4}{c|}{{[}Z3{]}}                                                                                                               \\ \cline{2-5} 
AUFBVDTLIA                      & \multicolumn{1}{l}{}          & \multicolumn{1}{l|}{}               & \multicolumn{2}{c|}{CVC4}                                             \\ \cline{4-5} 
AUFDTLIA                        & \multicolumn{1}{l}{}          & \multicolumn{1}{l|}{}               & \multicolumn{2}{c|}{CVC4}                                             \\ \cline{2-5} 
\multicolumn{1}{r|}{AUFLIA}     & \multicolumn{4}{c|}{CVC4}                                                                                                                   \\ \cline{2-5} 
\multicolumn{1}{r|}{AUFLIRA}    & \multicolumn{4}{c|}{{[}Z3{]}}                                                                                                               \\ \cline{2-5} 
\multicolumn{1}{r|}{AUFNIRA}    & \multicolumn{1}{c|}{CVC4}     & \multicolumn{2}{c|}{vampire}                                        & \multicolumn{1}{c|}{CVC4}             \\ \cline{2-5} 
\multicolumn{1}{r|}{BV}         & \multicolumn{1}{c|}{{[}Z3{]}} & \multicolumn{1}{c|}{Q3B}            & \multicolumn{1}{c|}{{[}Z3{]}} & \multicolumn{1}{c|}{CVC4}             \\ \cline{2-5} 
BVFP                            & \multicolumn{1}{l}{}          & \multicolumn{1}{l}{}                & \multicolumn{1}{l|}{}         & \multicolumn{1}{c|}{CVC4}             \\ \cline{5-5} 
FP                              & \multicolumn{1}{l}{}          & \multicolumn{1}{l}{}                & \multicolumn{1}{l|}{}         & \multicolumn{1}{c|}{CVC4}             \\ \cline{2-5} 
\multicolumn{1}{r|}{LIA}        & \multicolumn{2}{c|}{CVC4}                                           & \multicolumn{2}{c|}{{[}Z3{]}}                                         \\ \cline{2-5} 
\multicolumn{1}{r|}{LRA}        & \multicolumn{2}{c|}{CVC4}                                           & \multicolumn{2}{c|}{{[}Z3{]}}                                         \\ \cline{2-5} 
\multicolumn{1}{r|}{NIA}        & \multicolumn{4}{c|}{{[}Z3{]}}                                                                                                               \\ \cline{2-5} 
\multicolumn{1}{r|}{NRA}        & \multicolumn{1}{c|}{CVC4}     & \multicolumn{1}{c|}{Vampire}        & \multicolumn{1}{c|}{Redlog}   & \multicolumn{1}{l}{{[}Z3{]}/Vampire}  \\ \cline{2-5} 
\multicolumn{1}{r|}{QF\_ABV}    & \multicolumn{4}{c|}{Boolector}                                                                                                              \\ \cline{2-5} 
QF\_ABVFP                       & \multicolumn{1}{l}{}          & \multicolumn{1}{l}{}                & \multicolumn{1}{l|}{}         & \multicolumn{1}{c|}{CVC4}             \\ \cline{2-5} 
\multicolumn{1}{r|}{QF\_ALIA}   & \multicolumn{4}{c|}{Yices2}                                                                                                                 \\ \cline{2-5} 
\multicolumn{1}{r|}{QF\_ANIA}   & \multicolumn{1}{c|}{{[}Z3{]}} & \multicolumn{2}{c|}{CVC4}                                           & \multicolumn{1}{c|}{{[}Z3{]}}         \\ \cline{2-5} 
\multicolumn{1}{r|}{QF\_AUFBV}  & \multicolumn{3}{c|}{{[}MathSAT{]}}                                                                  & \multicolumn{1}{c|}{CVC4}             \\ \cline{2-5} 
\multicolumn{1}{r|}{QF\_AUFLIA} & \multicolumn{4}{c|}{Yices2}                                                                                                                 \\ \cline{2-5} 
\multicolumn{1}{r|}{QF\_AUFNIA} & \multicolumn{2}{c|}{CVC4}                                           & \multicolumn{2}{c|}{{[}Z3{]}}                                         \\ \cline{2-5} 
\multicolumn{1}{r|}{QF\_AX}     & \multicolumn{4}{c|}{Yices2}                                                                                                                 \\ \cline{2-5} 
\multicolumn{1}{r|}{QF\_BV}     & \multicolumn{2}{c|}{Boolector}                                      & \multicolumn{2}{c|}{Boolector/MinkeyRink}                             \\ \cline{2-5} 
\multicolumn{1}{r|}{QF\_BVFP}   & \multicolumn{1}{c|}{Z3 (FP)}  & \multicolumn{2}{c|}{{[}Z3{]}}                                       & \multicolumn{1}{c|}{CVC4}             \\ \cline{2-5} 
QF\_DT                          & \multicolumn{1}{l}{}          & \multicolumn{1}{l|}{}               & \multicolumn{2}{c|}{CVC4}                                             \\ \cline{4-5} 
\end{tabular}}
\end{center}
\caption{\label{tab:winners-main-1} Winners of the main track (part 1).}
\end{table}

\begin{table}[]
\begin{center}
\scalebox{.89}{\begin{tabular}{rcccc}
\hline
Logic  & 2015                          & 2016                                & 2017                          & 2018                                  \\
\hline
\multicolumn{1}{l}{}            & \multicolumn{1}{l}{}          & \multicolumn{1}{l}{}                & \multicolumn{1}{l}{}          & \multicolumn{1}{l}{}                  \\ \cline{2-5} 
\multicolumn{1}{r|}{QF\_FP}     & \multicolumn{1}{c|}{Z3 (FP)}  & \multicolumn{1}{c|}{{[}MathSat5{]}} & \multicolumn{1}{c|}{{[}Z3{]}} & \multicolumn{1}{c|}{COLIBRI}          \\ \cline{2-5} 
\multicolumn{1}{r|}{QF\_IDL}    & \multicolumn{2}{c|}{{[}Z3{]}}                                       & \multicolumn{2}{c|}{Yices2}                                           \\ \cline{2-5} 
\multicolumn{1}{r|}{QF\_LIA}    & \multicolumn{3}{c|}{{[}MathSat{]}}                                                                  & \multicolumn{1}{c|}{SPASS-SATT}       \\ \cline{2-5} 
\multicolumn{1}{r|}{QF\_LIRA}   & \multicolumn{2}{c|}{Yices2}                                         & \multicolumn{2}{c|}{{[}Z3{]}}                                         \\ \cline{2-5} 
\multicolumn{1}{r|}{QF\_LRA}    & \multicolumn{4}{c|}{CVC4}                                                                                                                   \\ \cline{2-5} 
\multicolumn{1}{r|}{QF\_NIA}    & \multicolumn{2}{c|}{{[}Z3{]}}                                       & \multicolumn{2}{c|}{CVC4}                                             \\ \cline{2-5} 
\multicolumn{1}{r|}{QF\_NIRA}   & \multicolumn{2}{c|}{CVC4}                                           & \multicolumn{2}{c|}{SMTRAT}                                           \\ \cline{2-5} 
\multicolumn{1}{r|}{QF\_NRA}    & \multicolumn{2}{c|}{{[}Z3{]}}                                       & \multicolumn{1}{c|}{Yices2}   & \multicolumn{1}{c|}{{[}Z3{]}}         \\ \cline{2-5} 
\multicolumn{1}{r|}{QF\_RDL}    & \multicolumn{4}{c|}{Yices2}                                                                                                                 \\ \cline{2-5} 
QF\_SLIA                        & \multicolumn{1}{l}{}          & \multicolumn{1}{l}{}                & \multicolumn{1}{l|}{}         & \multicolumn{1}{c|}{CVC4}             \\ \cline{2-5} 
\multicolumn{1}{r|}{QF\_UF}     & \multicolumn{4}{c|}{Yices2}                                                                                                                 \\ \cline{2-5} 
\multicolumn{1}{r|}{QF\_UFBV}   & \multicolumn{4}{c|}{Boolector}                                                                                                              \\ \cline{2-5} 
\multicolumn{1}{r|}{QF\_UFIDL}  & \multicolumn{4}{c|}{Yices2}                                                                                                                 \\ \cline{2-5} 
\multicolumn{1}{r|}{QF\_UFLIA}  & \multicolumn{2}{c|}{{[}Z3{]}}                                       & \multicolumn{2}{c|}{Yices2}                                           \\ \cline{2-5} 
\multicolumn{1}{r|}{QF\_UFLRA}  & \multicolumn{4}{c|}{Yices2}                                                                                                                 \\ \cline{2-5} 
\multicolumn{1}{r|}{QF\_UFNIA}  & \multicolumn{1}{c|}{CVC4}     & \multicolumn{1}{c|}{Yices2/CVC4}    & \multicolumn{2}{c|}{Yices2}                                           \\ \cline{2-5} 
\multicolumn{1}{r|}{QF\_UFNRA}  & \multicolumn{1}{c|}{{[}Z3{]}} & \multicolumn{1}{c|}{Yices2}         & \multicolumn{1}{c|}{{[}Z3{]}} & \multicolumn{1}{c|}{Yices2}           \\ \cline{2-5} 
\multicolumn{1}{r|}{UF}         & \multicolumn{2}{c|}{CVC4}                                           & \multicolumn{1}{c|}{Vampire}  & \multicolumn{1}{c|}{CVC4/Vampire}     \\ \cline{2-5} 
\multicolumn{1}{r|}{UFBV}       & \multicolumn{4}{c|}{{[}Z3{]}}                                                                                                               \\ \cline{2-5} 
UFDT                            & \multicolumn{1}{l}{}          & \multicolumn{1}{l|}{}               & \multicolumn{2}{c|}{CVC4}                                             \\ \cline{4-5} 
UFDTLIA                         & \multicolumn{1}{l}{}          & \multicolumn{1}{l|}{}               & \multicolumn{1}{c|}{Vampire}  & \multicolumn{1}{c|}{CVC4}             \\ \cline{2-5} 
\multicolumn{1}{r|}{UFIDL}      & \multicolumn{1}{c|}{{[}Z3{]}} & \multicolumn{2}{c|}{CVC4}                                           & \multicolumn{1}{c|}{{[}Z3{]}}         \\ \cline{2-5} 
\multicolumn{1}{r|}{UFLIA}      & \multicolumn{4}{c|}{CVC4}                                                                                                                   \\ \cline{2-5} 
\multicolumn{1}{r|}{UFLRA}      & \multicolumn{1}{c|}{CVC3}     & \multicolumn{3}{c|}{{[}Z3{]}}                                                                               \\ \cline{2-5} 
\multicolumn{1}{r|}{UFNIA}      & \multicolumn{1}{c|}{CVC4}     & \multicolumn{2}{c|}{Vampire}                                        & \multicolumn{1}{c|}{{[}Z3{]}/Vampire} \\ \cline{2-5} 
\end{tabular}}
\end{center}
\caption{\label{tab:winners-main-2} Winners of the main track (part 2).}
\end{table}

### 2018-11-22 2018/report/table-winners-unsat-core.tex
Tables with winners

  \begin{table}[]
  \begin{center}
\scalebox{.89}{\begin{tabular}{lccc}
      \hline
      & \multicolumn{1}{l}{2016}           & \multicolumn{1}{l}{2017}                  & \multicolumn{1}{l}{2018}         \\
      \hline
      \\
      \cline{2-4}
      \multicolumn{1}{l|}{ALIA}       & \multicolumn{3}{c|}{{[}Z3{]}}                                                                                     \\ \cline{2-4} 
AUFBVDTLIA                      & \multicolumn{1}{l}{}               & \multicolumn{1}{l}{}                      & CVC4                             \\ \cline{2-4} 
\multicolumn{1}{l|}{AUFLIA}     & \multicolumn{2}{c|}{{[}Z3{]}}                                                  & \multicolumn{1}{c|}{CVC4}        \\ \cline{2-4} 
\multicolumn{1}{l|}{AUFLIRA}    & \multicolumn{2}{c|}{{[}Z3{]}}                                                  & \multicolumn{1}{c|}{CVC4}        \\ \cline{2-4} 
\multicolumn{1}{l|}{AUFNIRA}    & \multicolumn{1}{c|}{{[}Z3{]}}      & \multicolumn{2}{c|}{CVC4}                                                    \\ \cline{2-4} 
\multicolumn{1}{l|}{BV}         & \multicolumn{3}{c|}{{[}Z3{]}}                                                                                     \\ \cline{2-4} 
\multicolumn{1}{l|}{LIA}        & \multicolumn{1}{c|}{{[}veriT{]}}   & \multicolumn{1}{c|}{CVC4}                 & \multicolumn{1}{c|}{{[}Z3{]}}    \\ \cline{2-4} 
\multicolumn{1}{l|}{LRA}        & \multicolumn{1}{c|}{{[}veriT{]}}   & \multicolumn{2}{c}{CVC4}                                                     \\ \cline{2-4} 
\multicolumn{1}{l|}{NIA}        & \multicolumn{1}{c|}{{[}Z3{]}}      & \multicolumn{1}{c|}{CVC4/{[}Z3{]}}        & \multicolumn{1}{c|}{CVC4}        \\ \cline{2-4} 
\multicolumn{1}{l|}{NRA}        & \multicolumn{3}{c|}{{[}Z3{]}}                                                                                     \\ \cline{2-4} 
\multicolumn{1}{l|}{QF\_ABV}    & \multicolumn{2}{c|}{{[}Z3{]}}                                                  & \multicolumn{1}{c|}{Yices2}      \\ \cline{2-4} 
                                & \multicolumn{1}{l}{}               & \multicolumn{1}{l|}{}                     & \multicolumn{1}{c|}{CVC4}        \\ \cline{2-4} 
\multicolumn{1}{l|}{QF\_ALIA}   & \multicolumn{3}{c|}{{[}Z3{]}}                                                                                     \\ \cline{2-4} 
\multicolumn{1}{l|}{QF\_ANIA}   & \multicolumn{1}{c|}{{[}Z3{]}}      & \multicolumn{2}{c|}{CVC4}                                                    \\ \cline{2-4} 
\multicolumn{1}{l|}{QF\_AUFBV}  & \multicolumn{1}{c|}{{[}Z3{]}}      & \multicolumn{2}{c|}{{[}MathSAT{]}}                                           \\ \cline{2-4} 
\multicolumn{1}{l|}{QF\_AUFLIA} & \multicolumn{1}{c|}{{[}Z3{]}}      & \multicolumn{2}{c|}{CVC4}                                                    \\ \cline{2-4} 
\multicolumn{1}{l|}{QF\_AUFNIA} & \multicolumn{3}{c|}{{[}Z3{]}}                                                                                     \\ \cline{2-4} 
\multicolumn{1}{l|}{QF\_AX}     & \multicolumn{2}{c|}{{[}Z3{]}}                                                  & \multicolumn{1}{c|}{Yices2}      \\ \cline{2-4} 
\multicolumn{1}{l|}{QF\_BV}     & \multicolumn{2}{c|}{{[}MathSAT{]}}                                             & \multicolumn{1}{c|}{Yices2}      \\ \cline{2-4} 
\multicolumn{1}{l|}{QF\_BVFP}   & \multicolumn{2}{c|}{{[}Z3{]}}                                                  & \multicolumn{1}{c|}{CVC4}        \\ \cline{2-4} 
QF\_DT                          & \multicolumn{1}{l}{}               & \multicolumn{1}{l|}{}                     & \multicolumn{1}{c|}{CVC4}        \\ \cline{2-4} 
\multicolumn{1}{l|}{QF\_FP}     & \multicolumn{1}{c|}{{[}MathSAT{]}} & \multicolumn{1}{c|}{{[}Z3{]}}             & \multicolumn{1}{c|}{CVC4}        \\ \cline{2-4} 
\multicolumn{1}{l|}{QF\_IDL}    & \multicolumn{3}{c|}{{[}Z3{]}}                                                                                     \\ \cline{2-4} 
\multicolumn{1}{l|}{QF\_LIA}    & \multicolumn{1}{c|}{{[}Z3{]}}      & \multicolumn{1}{c|}{SMTInterpol/{[}Z3{]}} & \multicolumn{1}{c|}{SMTInterpol} \\ \cline{2-4} 
\multicolumn{1}{l|}{QF\_LIRA}   & \multicolumn{3}{c|}{{[}Z3{]}}                                                                                     \\ \cline{2-4} 
\multicolumn{1}{l|}{QF\_LRA}    & \multicolumn{3}{c|}{SMTInterpol}                                                                                  \\ \cline{2-4} 
\multicolumn{1}{l|}{QF\_NIA}    & \multicolumn{3}{c|}{{[}Z3{]}}                                                                                     \\ \cline{2-4} 
\multicolumn{1}{l|}{QF\_NIRA}   & \multicolumn{3}{c|}{{[}Z3{]}}                                                                                     \\ \cline{2-4} 
\multicolumn{1}{l|}{QF\_NRA}    & \multicolumn{1}{c|}{{[}Z3{]}}      & \multicolumn{2}{c|}{CVC4}                                                    \\ \cline{2-4} 
\multicolumn{1}{l|}{QF\_RDL}    & \multicolumn{1}{c|}{{[}veriT{]}}   & \multicolumn{2}{c|}{{[}Z3{]}}                                                \\ \cline{2-4} 
\multicolumn{1}{l|}{QF\_UF}     & \multicolumn{1}{c|}{{[}MathSAT{]}} & \multicolumn{2}{c|}{CVC4}                                                    \\ \cline{2-4} 
\multicolumn{1}{l|}{QF\_UFBV}   & \multicolumn{2}{c|}{{[}MathSAT{]}}                                             & \multicolumn{1}{c|}{{[}Z3{]}}    \\ \cline{2-4} 
\multicolumn{1}{l|}{QF\_UFIDL}  & \multicolumn{2}{c|}{{[}Z3{]}}                                                  & \multicolumn{1}{c|}{Yices2}      \\ \cline{2-4} 
\multicolumn{1}{l|}{QF\_UFLIA}  & \multicolumn{1}{c|}{{[}MathSAT{]}} & \multicolumn{2}{c|}{{[}Z3{]}}                                                \\ \cline{2-4} 
\multicolumn{1}{l|}{QF\_UFLRA}  & \multicolumn{1}{c|}{{[}Z3{]}}      & \multicolumn{2}{c}{{[}MathSAT{]}}                                            \\ \cline{2-4} 
\multicolumn{1}{l|}{QF\_UFNIA}  & \multicolumn{3}{c|}{{[}Z3{]}}                                                                                     \\ \cline{2-4} 
\multicolumn{1}{l|}{QF\_UFNRA}  & \multicolumn{3}{c|}{{[}Z3{]}}                                                                                     \\ \cline{2-4} 
\multicolumn{1}{l|}{UF}         & \multicolumn{1}{c|}{{[}Z3{]}}      & \multicolumn{2}{c|}{CVC4}                                                    \\ \cline{2-4} 
\multicolumn{1}{l|}{UFBV}       & \multicolumn{2}{c|}{{[}Z3{]}}                                                  & \multicolumn{1}{c|}{CVC4}        \\ \cline{2-4} 
UFDT                            & \multicolumn{1}{l}{}               & \multicolumn{1}{l|}{}                     & \multicolumn{1}{c|}{CVC4}        \\ \cline{2-4} 
\multicolumn{1}{l|}{UFIDL}      & \multicolumn{1}{c|}{{[}Z3{]}}      & \multicolumn{2}{c|}{CVC4}                                                    \\ \cline{2-4} 
\multicolumn{1}{l|}{UFLIA}      & \multicolumn{1}{c|}{{[}Z3{]}}      & \multicolumn{2}{c|}{CVC4}                                                    \\ \cline{2-4} 
\multicolumn{1}{l|}{UFLRA}      & \multicolumn{3}{c|}{{[}Z3{]}}                                                                                     \\ \cline{2-4} 
\multicolumn{1}{l|}{UFNIA}      & \multicolumn{1}{c|}{{[}Z3{]}}      & \multicolumn{2}{c|}{CVC4}                                                    \\ \cline{2-4} 
\end{tabular}}
\end{center}
\caption{\label{tab:winners-unsat-core} Winners of the unsat-core track.}
\end{table}

### 2018-11-23 2018/report/SMT-COMP.tex
Minor

@@
 integers~({IDL}) or reals ({RDL}), or to the (non-)linear fragment of
-arithmetic ({L} or {N}, respectively, before {IA}, {RA} or {IRA}).
+arithmetic ({N} or {L}, respectively, before {IA}, {RA} or {IRA}).
 For instance, the logic QF\_UFLIA contains quantifier-free formulas
@@
 operations (e.g., bit-vector division) whose precise semantics were
-being debated at the time.  Additionally in 2016, one benchmark was
-excluded because it contained incorrect status information.  In 2017,
+being debated at the time.  Additionally in~2016, one benchmark was
+excluded because it contained incorrect status information.  In~2017,
 1,104 benchmarks were excluded because their logic had been classified
@@
 ({DT})---which were new in~2017---were excluded from the unsat-core
-track because of lacking tool support.  In 2018, 3,603 benchmarks were
+track because of lacking tool support.  In~2018, 3,603 benchmarks were
 excluded because they contained named terms (a feature of the SMT-LIB
@@
 tasks is not included.)  The increase in~2016 is largely due to the
-inclusion of non-incremental benchmarks with unknown status; these
+inclusion of (non-incremental) benchmarks with unknown status; these
 were evaluated with a wall-clock time limit of 10~minutes.  In~2017,
 when these benchmarks had become eligible for the main track,
-main-track job pairs were first run with a time limit of 10~minutes;
-when it became apparent to the organizers that there were sufficient
+main-track job pairs were first run with a time limit of 10~minutes.
+When it became apparent to the organizers that there were sufficient
 resources to increase this limit, job pairs that had timed out were
@@
 \begin{table}
-  \caption{Wall-clock time limits.}
+  \caption{Wall-clock time limits}
   \label{table:time-limits}
@@
 the SMT solving approach used.  System descriptions are published on
-the SMT-COMP website.  They were submitted for about 60\,\% of all
+the competition website.  They were submitted for about 60\,\% of all
 solver versions since 2015.
@@
                         (French Alternative Energies and Atomic Energy Commission)\\
-    Ctrl-Ergo~\cite{ctrl-ergo} & Mohamed Iguernlala
+    Ctrl-Ergo         & Mohamed Iguernlala
                         (CNRS and University of Paris-Sud)\\
@@
 individual division rankings (Section~\ref{sec:division-rankings}) for
-more detailed information.
+more detailed information about each solver.
 
 \begin{table}
-  \caption{Competition-wide ranking for the main track: best solvers (by year).}
+  \caption{Competition-wide ranking for the main track: best solvers (by year)}
   \label{table:competition-wide-ranking}
@@
 
-After 13 years, the SMT Competition is a well-established event that
-garners wide interest from developers and users of SMT solvers.  The
-competition continues to contribute to its original goals, including
-adoption of the SMT-LIB format and sparking further advances in SMT,
-and provides a yardstick of performance for SMT solvers.
+Thirteen years after its inception, the SMT Competition is a
+well-established event that garners wide interest from developers and
+users of SMT solvers.  The competition continues to contribute to its
+original goals, including adoption of the SMT-LIB format and sparking
+further advances in SMT, and provides a yardstick of performance for
+SMT solvers.
 
@@
 with unknown status are now eligible for the competition, and because
-the earlier culling of benchmarks was abandoned.  Since the
-re-introduction of the unsat-core track in~2016, the competition again
-has three separate tracks.  This, together with new logics in the SMT
-Library, has brought the total number of competition divisions to 115
-in~2018, up from just 40 divisions in~2014~\cite{CDW14}.  The number
-of job pairs increased from 339,714 in~2014 to~1,776,062~in 2018, and
-the total wall-clock time in~2018 exceeded 7.6~years.  By these
-measures, the SMT Competition is one of the largest competitions in
-automated reasoning.
+the competition now uses all eligible benchmarks (rather than a
+randomly selected subset).  Since the re-introduction of the
+unsat-core track in~2016, the competition again has three separate
+tracks.  This, together with new logics in the SMT Library, has
+brought the total number of competition divisions to 115 in~2018, up
+from just 40 divisions in~2014~\cite{CDW14}.  The number of job pairs
+increased from 339,714 in~2014 to~1,776,062~in 2018, and the total
+wall-clock time in~2018 exceeded 7.6~years.  By these measures, the
+SMT Competition is one of the largest competitions in automated
+reasoning.
 
@@
 where future organizers will have to carefully consider the number of
-participants and benchmarks each year, to determine whether the
-current time limits remain tenable.  (Otherwise, reducing the time
-limits would probably be a better solution than reverting to the
-pre-2014 practice of benchmark culling.)
+participants and benchmarks each year, to determine time limits that
+will allow the computational workload to complete before the SMT
+Workshop.
 
@@
 \item the inclusion of {\tt check-sat} commands with unknown status in
-  the application track; and
+  the application track, and
 \item the definition of competition-wide rankings for the application
@@
 
-Organizing the competition is a non-trivial amount of work.  Much of
-this happens behind the scenes.  For instance, the competition tools
-(such as the benchmark scrambler and trace executor) often require
-updating when new divisions are added, or when changes are made to
-StarExec.  One could imagine adding further tracks (e.g., for
-proof-producing SMT solvers, or for variants such as max-SMT) to the
-competition, but the effort required to support such tracks will need
-to be balanced against their added value.
+Organizing the competition is a non-trivial amount of work.  For
+instance, the competition tools (such as the benchmark scrambler and
+trace executor) often require updating when new divisions are added,
+or when changes are made to StarExec.  One could imagine adding
+further tracks to the competition (e.g., for proof-producing solvers,
+or for variants such as max-SMT), but the effort required to support
+such tracks will need to be balanced against their added value.
 
@@
 contribution to the community, but also---since these benchmarks will
-then be used in the competition---a straightforward way to get solver
-developers to tune their solvers accordingly.
+then be used in the competition---a straightforward way to incentivize
+solver developers to tune their solvers accordingly.
 

### 2018-11-23 2018/report/SMT-COMP.tex
References for participants

@@
   \centering
-  \begin{tabular}{|l|p{11.7cm}|} %TODO: fix width
+  \begin{tabular}{|l|p{11.5cm}|} %TODO: fix width
     \hline
@@
                         (CNRS and University of Paris-Sud)\\
-    CVC3~\cite{cvc3}  & Kshitij Bansal
+    CVC3~\cite{DBLP:conf/cav/BarrettT07} & Kshitij Bansal
                         (New York University)\\
@@
                         (New York University; Stanford University)\\
-    MapleSTP~\cite{maplestp} & Jimmy Liang
+    MapleSTP          & Jimmy Liang
                         (University of Waterloo)\\
-    MinkeyRink~\cite{minkeyrink} & Trevor Hansen
+    MinkeyRink        & Trevor Hansen
                         (University of Melbourne)\\
-    OpenSMT2~\cite{opensmt2} & Matteo Marescotti, Antti Hyv\"arinen
+    OpenSMT2~\cite{DBLP:conf/sat/HyvarinenMAS16} & Matteo Marescotti, Antti Hyv\"arinen
                         (University of Lugano)\\
-    ProB~\cite{prob}  & Sebastian Krings
+    ProB~\cite{doi:10.1002/9781119002727.ch14} & Sebastian Krings
                         (University of D\"usseldorf)\\
-    Q3B~\cite{q3b}    & Martin Jon\'a\v{s}
+    Q3B               & Martin Jon\'a\v{s}
                         (Masaryk University)\\
@@
                         (Japan Advanced Institute of Science and Technology)\\
-    Redlog~\cite{redlog} & Haniel Barbosa
+    Redlog~\cite{DBLP:journals/cca/Dolzmann097} & Haniel Barbosa
                         (Inria Nancy)\\
-    SMT-RAT~\cite{smt-rat} & Florian Corzilius, Gereon Kremer
+    SMT-RAT~\cite{DBLP:conf/sat/CorziliusKJSA15} & Florian Corzilius, Gereon Kremer
                         (RWTH Aachen University)\\
-    SMTInterpol~\cite{} & J\"urgen Christ
+    SMTInterpol~\cite{DBLP:conf/spin/ChristHN12} & J\"urgen Christ
                         (University of Freiburg)\\
-    SPASS-SATT~\cite{} & Martin Bromberger
+    SPASS-SATT         & Martin Bromberger
                         (Max Planck Institute for Informatics)\\
-    STP~\cite{}        & Mate Soos, Trevor Hansen, Norbert Manthey
+    STP~\cite{ganesh07} & Mate Soos, Trevor Hansen, Norbert Manthey
                         (National University of Singapore; University of Melbourne; Amazon Web Services)\\
-    toysmt~\cite{}     & Masahiro Sakai
+    toysmt             & Masahiro Sakai
                         (Toshiba Corporation)\\
-    Vampire~\cite{}    & Giles Reger
+    Vampire~\cite{DBLP:conf/cav/KovacsV13} & Giles Reger
                         (University of Manchester)\\
@@
                         (Federal University of Rio Grande do Norte; Inria Nancy)\\
-    XSat~\cite{}       & Martin Velez
+    XSat~\cite{DBLP:conf/cav/FuS16} & Martin Velez
                         (University of California, Davis)\\
-    Yices2~\cite{}     & Bruno Dutertre, Dejan Jovanovi\'c
+    Yices2~\cite{Dutertre:cav2014} & Bruno Dutertre, Dejan Jovanovi\'c
                         (SRI International)\\

### 2018-11-24 2018/report/plot/cactus_plot.r
Add scripts to generate plots per division on common benchmarks.

@@ -1,0 +1,63 @@
+library(tools)
+
+if(!dir.exists("pdf")) dir.create("pdf")
+args <- commandArgs(trailingOnly = TRUE)
+
+fname_pdf=paste("pdf/cactus_plot-",args[1],".pdf",sep="")
+pdf(fname_pdf,width=9)
+par(cex=1.2)
+
+colors=c("red2","orange","chartreuse3","dodgerblue1","dodgerblue3",
+		 "cornflowerblue","darkgreen","yellow2","darkorchid2","gray",
+		 "chartreuse2", "darkorange", "darkorchid3","deeppink","blue3",
+		 "darkolivegreen","cyan2","darkcyan","deepskyblue4","deeppink4",
+		 "chartreuse4","chocolate4","darkblue","darkgoldenrod2")
+ncolors=length(colors)
+ltypes=c(1,5,6,4,3,1,5,6,4,3,1,5,6,4,3,1,5,6,4,3,1,5,6)
+lwidth=2
+nfiles=(length(args)-1)/2
+xlegend=vector(length=nfiles)
+xtitles=vector(length=nfiles)
+xpch=vector(length=nfiles)
+xcol=vector(length=nfiles)
+fname_data <- args[2]
+fname <- file_path_sans_ext(basename(fname_data))
+data=read.csv(fname_data,sep=",",head=F,comment.char="#")
+x=sort(ifelse(data[,3] > 1200, 1200, data[,3]))
+max_x=length(x)
+max_y=1450
+xlegend[1] <- as.expression(bquote(bold(.(args[nfiles+2]))))
+xcol[1] <- colors[1]
+
+options("scipen"=100, "digits"=4)
+par(mar=c(5,5.2,2,3))
+plot(x,xlab="# Benchmarks",type="n",xaxt="n",yaxt="n",ann=FALSE,col=colors[1],xlim=c(0, max_x),ylim=c(0, max_y))
+abline(h=1200,col="gray")
+abline(v=max_x,col="gray")
+lines(x,col=colors[1],lwd=lwidth,lty=ltypes[1])
+
+ticks=sapply(axTicks(1), function(i) as.integer(i))
+labels=sprintf("%i",ticks)
+axis(1, at=ticks, labels=labels)
+ticks=sapply(axTicks(2), function(i) as.integer(i))
+labels=sprintf("%i",ticks)
+axis(2, at=ticks, labels=labels)
+
+if (nfiles >= 2)
+{
[…]

### 2018-11-24 2018/report/plot/extract_common_results.py

@@ -1,0 +1,443 @@
+#! /usr/bin/env python3
+
+import os
+import sys
+from argparse import ArgumentParser #, REMAINDER, ArgumentDefaultsHelpFormatter
+
+winners_2018_main  = {
+        "ABVFP" : "master-2018-06-10-b19c840-competition-default",
+        "ALIA" : "master-2018-06-10-b19c840-competition-default",
+        "AUFBVDTLIA" : "master-2018-06-10-b19c840-competition-default",
+        "AUFDTLIA" : "master-2018-06-10-b19c840-competition-default",
+        "AUFLIA" : "master-2018-06-10-b19c840-competition-default",
+        "AUFLIRA" : "master-2018-06-10-b19c840-competition-default",
+        "AUFNIRA" : "master-2018-06-10-b19c840-competition-default",
+        "BV" : "master-2018-06-10-b19c840-competition-default",
+        "BVFP" : "master-2018-06-10-b19c840-competition-default",
+        "FP" : "master-2018-06-10-b19c840-competition-default",
+        "LIA" : "master-2018-06-10-b19c840-competition-default",
+        "LRA" : "master-2018-06-10-b19c840-competition-default",
+        "NIA" : "master-2018-06-10-b19c840-competition-default",
+        "NRA" : "vampire-4.3-smt",
+        "QF_ABV" : "Boolector",
+        "QF_ABVFP" : "master-2018-06-10-b19c840-competition-default",
+        "QF_ALIA" : "Yices 2.6.0",
+        "QF_ANIA" : "master-2018-06-10-b19c840-competition-default",
+        "QF_AUFBV" : "master-2018-06-10-b19c840-competition-default",
+        "QF_AUFLIA" : "Yices 2.6.0",
+        "QF_AUFNIA" : "master-2018-06-10-b19c840-competition-default",
+        "QF_AX" : "Yices 2.6.0",
+        "QF_BV" : "Boolector",
+        "QF_BVFP" : "master-2018-06-10-b19c840-competition-default",
[…]

### 2018-11-24 2018/report/plot/gen_plots.sh

@@ -1,0 +1,9 @@
+#! /bin/sh
+
+base_dir=$(dirname "$0")
+file_2017="$base_dir/2017-Main_Track.csv"
+extract_script="$base_dir/extract_common_results.py"
+
+[ -e $file_2017 ] || tar xvf "$file_2017.tar.xz"
+python $extract_script -w $base_dir/../../csv/Main_Track.csv,$file_2017,$base_dir/../../../2016/csv/Main_Track.csv,$base_dir/../../../2015/csv/Main_Track.csv 2018,2017,2016,2015
+make

### 2018-11-24 2018/report/plot/extract_common_results.py
clean up

@@ -2,7 +2,7 @@
 
 import os
 import sys
-from argparse import ArgumentParser #, REMAINDER, ArgumentDefaultsHelpFormatter
+from argparse import ArgumentParser
 
 winners_2018_main  = {
         "ABVFP" : "master-2018-06-10-b19c840-competition-default",
@@ -398,30 +398,21 @@ if __name__ == "__main__":
                         else (solvers_2017_main if p == "2017" \
                         else (solvers_2016_main if p == "2016" \
                         else solvers_2015_main))
-                #print(f)
-                #print(p)
                 for l in results[f]:
                     if len(common_benchmarks[l]) > 0:
                         if not l in tmp: tmp[l] = {}
                         assert (l in benchmarks)
                         r = results[f][l] if not args.winners_only else [winners[l]]
-                        #print(p)
-                        #print(winners[l])
                         for s in r:
                             s_name = s if not args.winners_only  else solvers[s]
                             outfile_name = "{}/{}-{}-Main_Track-{}.csv".format(
                                     path, p, l, s_name)
-                            #print("{}-{}".format(p,s))
-                            #print(outfile_name)
-                            #print(l + " " + str(len(common_benchmarks[l])))
                             tmp[l]["{}-{}".format(p,s_name)] = outfile_name
                             with open(outfile_name, 'w') as outfile:
                                 outfile.write(
                                     "# 1 solver, 2 benchmark, 3 time (wallclock)\n")
                                 for b in common_benchmarks[l]:
                                     assert (b in results[f][l][s])
-                                    #print(s)
-                                    #print(p)
                                     assert (s in solvers)
                                     outfile.write(
                                         "{},{},{}\n".format(
@@ -429,7 +420,6 @@ if __name__ == "__main__":
                                             b,
                                             results[f][l][s][b]))
             for l in tmp:
-                #print(str(l) + " "  + str(tmp))
                 makefile.write(
                         '\tRscript cactus_plot.r "{}" "{}" "{}"\n'.format(
                             l,

### 2018-11-24 2018/report/SMT-COMP.tex
Affiliations
Weights, disagreements, minor

@@
   \addr Uppsala University \\
-  Uppsala \\
+  %Uppsala \\
   Sweden
@@
   \email{Sylvain.Conchon@lri.fr} \\
-  \addr Affiliation \\
-  City \\
-  Country
+  \addr Paris-Sud University \\
+  France
   \AND
@@
   \addr ClearSy Systems Engineering \\
-  Aix-en-Provence \\
+  %Aix-en-Provence \\
   France
@@
   \email{heizmann@informatik.uni-freiburg.de} \\
-  \addr Affiliation \\
-  City \\
-  Country
+  \addr University of Freiburg \\
+  %City \\
+  Germany
   \AND
@@
   \addr Stanford University\\
-  Stanford \\
+  %Stanford \\
   USA
@@
   \email{giles.reger@manchester.ac.uk} \\
-  \addr Affiliation \\
-  City \\
-  Country}
+  \addr University of Manchester \\
+  UK}
 
@@
 solver/benchmark combination, totaling nearly 6 million data records
-(about 1.1~GB in CSV format).
+(about 1.1~GB in CSV format).  Competition solvers and benchmarks may
+be downloaded from StarExec, \url{https://www.starexec.org}.
 
@@
 Section~\ref{sec:participants} gives an overview of participating
-solvers.  The details of the competition procedure are described in
-Section~\ref{sec:procedure}, and selected results are presented and
-analyzed in Section~\ref{sec:results}.  We conclude with suggestions
-for future SMT Competitions in Section~\ref{sec:conclusions}.
+solvers.  Selected results are presented
+%TODO: and analyzed
+in Section~\ref{sec:results}.  We conclude with suggestions for future
+SMT Competitions in Section~\ref{sec:conclusions}.
 
@@
 computational resources available to the competition since its move to
-StarExec, this prompted a paradigm shift.  Since 2015, the competition
-is evaluating all solvers on all eligible benchmarks. \TODO: benchmark
-weights
+StarExec, this finding prompted a paradigm shift.  Since 2015, the
+competition is evaluating all solvers on all eligible benchmarks.
+This change had an unintended side effect: the pseudo-random selection
+process had been purposely constrained to choose benchmarks from
+different benchmark families (that is, groups of benchmarks with
+similar characteristics).  Since there are vast differences in size
+between benchmark families in the SMT Library, the competition
+since~2016 uses a scoring method that assigns a weight to each
+main-track benchmark in order to de-emphasize large benchmark
+families~\cite{rules18}.
 
@@
 between two or more (otherwise sound) solvers.  Benchmarks with
-disagreements are removed from the competition results (see
-Section~\ref{sec:results-disagreements} for further discussion).
+disagreements are removed from the competition results.  In 2016,
+there were disagreements on 79 benchmarks; in 2017, only one benchmark
+was removed; and in 2018, there were no disagreements between
+otherwise sound solvers.
 
@@
 (summed over all job pairs) for the competition.  This has more than
-doubled, from 3.5~years in~2015 to 7.6~years in~2018.  (These are
-solver run-times only.  Time that the cluster spent on pre- and
+doubled, from 3.5~years in~2015 to 7.6~years in~2018.  These are
+solver run-times only; time that the cluster spent on pre- and
 post-processing of benchmarks and solver output or on other auxiliary
-tasks is not included.)  The increase in~2016 is largely due to the
+tasks is not included.  The increase in~2016 is largely due to the
 inclusion of (non-incremental) benchmarks with unknown status; these
@@
   \centering
-  \begin{tabular}{|l|p{11.5cm}|} %TODO: fix width
+  \begin{tabular}{|l|p{11.5cm}|}
     \hline
@@
 
-\section{Competition Procedure}
-\label{sec:procedure}
-
-\TODO: explain those aspects of the procedure that are required to
-understand the results (e.g., scoring)
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \section{Results}
@@
 \label{sec:division-rankings}
+
+Solvers in each division (of each track) are ranked according to a
+metric that is based, first, on the number of erroneous responses
+(which is usually~0, but solvers that did give erroneous responses are
+ranked behind solvers that did not); second, on the number of correct
+responses; third, on the wall-clock and CPU time that the solver
+process consumed.  For the unsat-core track (which uses unsatisfiable
+benchmarks only), the reduction in the size of the unsatisfiable core
+is used instead of the number of correct responses.  A detailed
+description of the scoring regulations can be found in the competition
+rules~\cite{rules18}.
+
+As discussed in Section~\ref{sec:benchmarks}, main-track benchmarks
+with unknown status are removed from the competition results if two
+(or more) solvers that are sound on benchmarks with known status
+disagree on their result.  Otherwise, solver responses for benchmarks
+with unknown status are assumed to be correct.
+
+All solvers are run with four cores available, and the time limit~$T$
+that is imposed on each job pair (see Table~\ref{table:time-limits})
+is a wall-clock limit.  Thus, solvers that take advantage of
+parallelism might use up to~$4T$ CPU time.  For the main track and the
+unsat-core track, the competition reports parallel and sequential
+performance separately.  The latter is determined by imposing a
+(virtual) CPU time limit of~$T$.
 
@@
 
+\TODO: non-competitive divisions
+
 \include{table-winners-main}
@@
 \include{table-winners-unsat-core}
-
-\TODO
 

### 2018-11-24 2018/report/plot/extract_common_results.py
Minor

@@ -427,6 +427,7 @@ if __name__ == "__main__":
                             '" "'.join(tmp[l].keys())))
             makefile.write("clean:\n")
             makefile.write("\trm -r pdf\n")
+            makefile.write("\trm -r makefile\n")
 
 
     except BrokenPipeError:

### 2018-11-24 2018/report/plot/gen_plots.sh

@@ -1,9 +1,15 @@
 #! /bin/sh
 
 base_dir=$(dirname "$0")
+file_2018="$base_dir/../../csv/Main_Track.csv"
 file_2017="$base_dir/2017-Main_Track.csv"
+file_2016="$base_dir/../../../2016/csv/Main_Track.csv"
+file_2015="$base_dir/../../../2015/csv/Main_Track.csv"
 extract_script="$base_dir/extract_common_results.py"
 
+[ -e $file_2018 ] || tar xvf "${file_2018%.*}.tar.xz" && mv Main_Track.csv $file_2018
 [ -e $file_2017 ] || tar xvf "$file_2017.tar.xz"
-python $extract_script -w $base_dir/../../csv/Main_Track.csv,$file_2017,$base_dir/../../../2016/csv/Main_Track.csv,$base_dir/../../../2015/csv/Main_Track.csv 2018,2017,2016,2015
+[ -e $file_2016 ] || tar xvf "${file_2016%.*}.tar.xz" && mv Main_Track.csv $file_2016
+[ -e $file_2015 ] || tar xvf "${file_2015%.*}.tar.xz" && mv Main_Track.csv $file_2015
+python $extract_script -w $file_2018,$file_2017,$file_2016,$file_2015 2018,2017,2016,2015
 make

### 2018-11-25 2018/report/SMT-COMP.tex
Minor

@@
 \usepackage{pifont}
-\usepackage{comment}
 \usepackage{multirow}
@@
 
-\specialcomment{tjark}{\begingroup\footnotesize\color{red}}{\color{black}\endgroup}
-\newcommand{\TODO}[0]{\textcolor{red}{TODO}}
-
-\renewcommand{\mark}[0]{\ding{51}}
-
-% TODO
+% float layout
 \setcounter{topnumber}{2}
@@
 
-\begin{tjark}
-Changes 2015:
-\begin{itemize}
-\item All solvers will be run with $n=4$ cores available.  We will
-  recognize both best sequential and best parallel performance in all
-  main track divisions, using different CPU time limits.
-\item The division scoring will take time spent on unsolved benchmarks
-  into account.  Previous competitions only considered time spent on
-  solved benchmarks.  However, the number of solved benchmarks still
-  takes precedence over run-time.
-\item In addition to recognizing the best solver in each division, we
-  will recognize solvers that perform best according to
-  competition-wide criteria, emphasizing breadth of supported logics.
-  These criteria will be a refinement of the criteria used for the
-  FLoC Olympic Games medals in~2014.
-\item We plan to include new divisions for floating-point arithmetic.
-  These should be considered experimental in~2015, and will not be
-  included in the competition-wide ranking.
-\item We plan to run solvers on all eligible benchmarks.  Previous
-  competitions used a proper subset of eligible benchmarks, causing
-  competition results to be affected by a random selection process.
-\end{itemize}
-
-Changes 2016:
-\begin{itemize}
-\item Benchmarks will use (a subset of) version~2.5 of the SMT-LIB
-  language.  \emph{Rationale:} This is the latest version of the
-  SMT-LIB language.  It was released on 2015-06-28, and is largely
-  backwards-compatible to version~2.0, which was used for SMT-COMP
-  2015.
-\item Solver output may affect the score even when the solver does not
-  terminate within the time limit.  (In 2015, main track solver output
-  was ignored if the solver subsequently timed out.)  Solvers should
-  take care not to accidentally produce output that contains
-  \texttt{sat} or \texttt{unsat} even when they are killed.
-  \emph{Rationale:} Users are likely to trust solver responses even
-  when the solver continues to run for some time.
-\item Divisions for floating-point arithmetic are no longer
-  experimental, and will be considered competitive if the necessary
-  requirements (see Section~\ref{sec:scoring}) are met.
-  \emph{Rationale:} Floating-point divisions were experimental in
-  2015.  By now, their definition is sufficiently stable, and they are
-  supported by several solvers.
-\item Division scores will be based on a weighted sum of scores for
-  benchmark families.  \emph{Rationale:} For some years now, SMT-COMPs
-  have had sufficient computational resources to evaluate all solver
-  entrants on all eligible benchmarks.  As a side-effect, the
-  weighting of benchmark families that was achieved in early SMT-COMPs
-  through a careful selection of benchmarks (based on benchmark
-  difficulty and category) was lost.  Since there are vast differences
-  in size between benchmark families, we believe that a weighting that
-  de-emphasizes large benchmark families (see
-  Section~\ref{sec:division-scoring}) will lead to more meaningful
-  competition results.
-\item The unsat-core track that was introduced in SMT-COMP 2012, but
-  discontinued in 2013-2015 (partly because of the competition's move
-  to StarExec), is back.  It will be experimental in 2016; its results
-  will be reported, but no official winners will be announced.
-  \emph{Rationale:} Unsat cores are important in many applications of
-  SMT solving.  The track was discontinued primarily for
-  infrastructure and resource reasons.  We are pleased that we can
-  finally offer it again, but we ask for your understanding in case of
-  mishaps while we port the required tools.
-\item Best industrial performance will no longer be recognized
-  separately.  \emph{Rationale:} While there is agreement in the SMT
-  community to emphasize problems that come from real applications,
-  industrial performance largely coincided with overall performance in
-  SMT-COMP 2015.  We consider the effort to determine and report it
-  separately no longer justified.
-\end{itemize}
-
-Changes 2017:
-\begin{itemize}
-\item Submission of accompanying information for solvers is via a web
-  form (rather than by email to the organizers).  \emph{Rationale:}
-  Email submissions were often incomplete, leading to ambiguity and
-  further inquiries.  The form provides a more structured way of
-  submitting information.
-\item Benchmarks will use (a subset of) version~2.6 of the SMT-LIB
-  language.  \emph{Rationale:} This is the latest version of the
-  SMT-LIB language.  It is largely backwards-compatible with earlier
-  versions (in particular~2.0 and~2.5).
-\item Benchmarks that use partial bit-vector functions, such as
-  \texttt{bvudiv}, or underspecified floating-point functions, such as
-  \texttt{fp.min}, will be eligible for the competition again.
-  \emph{Rationale:} A conclusion on the semantics of these functions
-  has finally been reached, and the status of affected SMT-LIB
-  benchmarks has been updated accordingly.
-\item Benchmarks with unknown status will be eligible for the
-  competition's main track.  In 2016, solver performance on benchmarks
-  with unknown status was evaluated but reported separately; in 2017,
-  it will directly affect the competition results.  \emph{Rationale:}
-  Using only benchmarks with known status (i.e., benchmarks that have
-  been solved before) to determine the competition results unjustly
-  favors imitation of existing solvers over true innovation.
-\item In the competition-wide scoring, the (per-division) penalty for
-  erroneous results is changed from the number of errors to a fixed
-  constant (multiplied by the weight of the respective division).
-  \emph{Rationale:} The weight already takes the number of benchmarks
-  in the division into account; multiplying it by the number of errors
-  overemphasizes large divisions.
-\item The unsat-core track, which was re-introduced in 2016, is no
-  longer experimental.  Its divisions will be considered competitive
-  if the necessary requirements (see Section~\ref{sec:scoring}) are
-  met.  \emph{Rationale:} Rules and tool support for the unsat-core
-  track proved sufficiently stable in 2016.
-\item The competition will feature experimental divisions for
-  benchmarks that use algebraic datatypes.  \emph{Rationale:}
-  Algebraic datatypes are specified in the draft SMT-LIB~2.6 standard,
-  which is expected to become official in the near future, and are
-  already supported by some solvers.  Benchmarks that use datatypes
-  have recently been added to SMT-LIB.
-\end{itemize}
-
-Changes 2018:
-\begin{itemize}
-\item The time limit per solver/benchmark pair is anticipated to be at
-  most 20 minutes in the main track, and at most 40 minutes in the
-  other tracks.  \emph{Rationale:} Already in 2017, the time limit for
-  the main track was reduced to 20 minutes (down from 40 minutes in
-  earlier years) to cope with the inclusion of a large number of
-  benchmarks with unknown status.
-\item In the unsat-core track, the unsatisfiability check for the
-  returned core will be based on a simple majority vote.  The case
-  that a solver finds its own core satisfiable will no longer be
-  treated specially.  \emph{Rationale:} This allows to simplify the
-  post-processing of unsat-core track results considerably.
-\item In 2017, the competition featured experimental divisions for
-  benchmarks that use algebraic datatypes.  These divisions will be
-  regular (non-experimental) in 2018. \emph{Rationale:} Algebraic
-  datatypes are specified in the latest official release (Version~2.6)
-  of the SMT-LIB standard.
-\item The competition will feature an experimental divisions for
-  benchmarks that use strings.  \emph{Rationale:} Corresponding
-  theories and benchmarks are expected to be added to SMT-LIB in the
-  near future.
-\end{itemize}
-\end{tjark}
+%% Changes 2015:
+%% \begin{itemize}
+%% \item All solvers will be run with $n=4$ cores available.  We will
+%%   recognize both best sequential and best parallel performance in all
+%%   main track divisions, using different CPU time limits.
+%% \item The division scoring will take time spent on unsolved benchmarks
+%%   into account.  Previous competitions only considered time spent on
+%%   solved benchmarks.  However, the number of solved benchmarks still
+%%   takes precedence over run-time.
+%% \item In addition to recognizing the best solver in each division, we
+%%   will recognize solvers that perform best according to
+%%   competition-wide criteria, emphasizing breadth of supported logics.
+%%   These criteria will be a refinement of the criteria used for the
+%%   FLoC Olympic Games medals in~2014.
+%% \item We plan to include new divisions for floating-point arithmetic.
+%%   These should be considered experimental in~2015, and will not be
+%%   included in the competition-wide ranking.
+%% \item We plan to run solvers on all eligible benchmarks.  Previous
+%%   competitions used a proper subset of eligible benchmarks, causing
+%%   competition results to be affected by a random selection process.
+%% \end{itemize}
+
+%% Changes 2016:
+%% \begin{itemize}
+%% \item Benchmarks will use (a subset of) version~2.5 of the SMT-LIB
+%%   language.  \emph{Rationale:} This is the latest version of the
+%%   SMT-LIB language.  It was released on 2015-06-28, and is largely
+%%   backwards-compatible to version~2.0, which was used for SMT-COMP
+%%   2015.
+%% \item Solver output may affect the score even when the solver does not
+%%   terminate within the time limit.  (In 2015, main track solver output
+%%   was ignored if the solver subsequently timed out.)  Solvers should
+%%   take care not to accidentally produce output that contains
+%%   \texttt{sat} or \texttt{unsat} even when they are killed.
+%%   \emph{Rationale:} Users are likely to trust solver responses even
+%%   when the solver continues to run for some time.
+%% \item Divisions for floating-point arithmetic are no longer
+%%   experimental, and will be considered competitive if the necessary
+%%   requirements (see Section~\ref{sec:scoring}) are met.
+%%   \emph{Rationale:} Floating-point divisions were experimental in
+%%   2015.  By now, their definition is sufficiently stable, and they are
+%%   supported by several solvers.
+%% \item Division scores will be based on a weighted sum of scores for
+%%   benchmark families.  \emph{Rationale:} For some years now, SMT-COMPs
+%%   have had sufficient computational resources to evaluate all solver
+%%   entrants on all eligible benchmarks.  As a side-effect, the
+%%   weighting of benchmark families that was achieved in early SMT-COMPs
+%%   through a careful selection of benchmarks (based on benchmark
+%%   difficulty and category) was lost.  Since there are vast differences
+%%   in size between benchmark families, we believe that a weighting that
+%%   de-emphasizes large benchmark families (see
+%%   Section~\ref{sec:division-scoring}) will lead to more meaningful
+%%   competition results.
+%% \item The unsat-core track that was introduced in SMT-COMP 2012, but
+%%   discontinued in 2013-2015 (partly because of the competition's move
+%%   to StarExec), is back.  It will be experimental in 2016; its results
+%%   will be reported, but no official winners will be announced.
+%%   \emph{Rationale:} Unsat cores are important in many applications of
+%%   SMT solving.  The track was discontinued primarily for
+%%   infrastructure and resource reasons.  We are pleased that we can
+%%   finally offer it again, but we ask for your understanding in case of
+%%   mishaps while we port the required tools.
+%% \item Best industrial performance will no longer be recognized
+%%   separately.  \emph{Rationale:} While there is agreement in the SMT
+%%   community to emphasize problems that come from real applications,
+%%   industrial performance largely coincided with overall performance in
+%%   SMT-COMP 2015.  We consider the effort to determine and report it
+%%   separately no longer justified.
+%% \end{itemize}
+
+%% Changes 2017:
+%% \begin{itemize}
+%% \item Submission of accompanying information for solvers is via a web
+%%   form (rather than by email to the organizers).  \emph{Rationale:}
+%%   Email submissions were often incomplete, leading to ambiguity and
+%%   further inquiries.  The form provides a more structured way of
+%%   submitting information.
+%% \item Benchmarks will use (a subset of) version~2.6 of the SMT-LIB
+%%   language.  \emph{Rationale:} This is the latest version of the
+%%   SMT-LIB language.  It is largely backwards-compatible with earlier
+%%   versions (in particular~2.0 and~2.5).
+%% \item Benchmarks that use partial bit-vector functions, such as
+%%   \texttt{bvudiv}, or underspecified floating-point functions, such as
+%%   \texttt{fp.min}, will be eligible for the competition again.
+%%   \emph{Rationale:} A conclusion on the semantics of these functions
+%%   has finally been reached, and the status of affected SMT-LIB
+%%   benchmarks has been updated accordingly.
+%% \item Benchmarks with unknown status will be eligible for the
+%%   competition's main track.  In 2016, solver performance on benchmarks
+%%   with unknown status was evaluated but reported separately; in 2017,
+%%   it will directly affect the competition results.  \emph{Rationale:}
+%%   Using only benchmarks with known status (i.e., benchmarks that have
+%%   been solved before) to determine the competition results unjustly
+%%   favors imitation of existing solvers over true innovation.
+%% \item In the competition-wide scoring, the (per-division) penalty for
+%%   erroneous results is changed from the number of errors to a fixed
+%%   constant (multiplied by the weight of the respective division).
+%%   \emph{Rationale:} The weight already takes the number of benchmarks
+%%   in the division into account; multiplying it by the number of errors
+%%   overemphasizes large divisions.
+%% \item The unsat-core track, which was re-introduced in 2016, is no
+%%   longer experimental.  Its divisions will be considered competitive
+%%   if the necessary requirements (see Section~\ref{sec:scoring}) are
+%%   met.  \emph{Rationale:} Rules and tool support for the unsat-core
+%%   track proved sufficiently stable in 2016.
+%% \item The competition will feature experimental divisions for
+%%   benchmarks that use algebraic datatypes.  \emph{Rationale:}
+%%   Algebraic datatypes are specified in the draft SMT-LIB~2.6 standard,
+%%   which is expected to become official in the near future, and are
+%%   already supported by some solvers.  Benchmarks that use datatypes
+%%   have recently been added to SMT-LIB.
+%% \end{itemize}
+
+%% Changes 2018:
+%% \begin{itemize}
+%% \item The time limit per solver/benchmark pair is anticipated to be at
+%%   most 20 minutes in the main track, and at most 40 minutes in the
+%%   other tracks.  \emph{Rationale:} Already in 2017, the time limit for
+%%   the main track was reduced to 20 minutes (down from 40 minutes in
+%%   earlier years) to cope with the inclusion of a large number of
+%%   benchmarks with unknown status.
+%% \item In the unsat-core track, the unsatisfiability check for the
+%%   returned core will be based on a simple majority vote.  The case
+%%   that a solver finds its own core satisfiable will no longer be
+%%   treated specially.  \emph{Rationale:} This allows to simplify the
+%%   post-processing of unsat-core track results considerably.
+%% \item In 2017, the competition featured experimental divisions for
+%%   benchmarks that use algebraic datatypes.  These divisions will be
+%%   regular (non-experimental) in 2018. \emph{Rationale:} Algebraic
+%%   datatypes are specified in the latest official release (Version~2.6)
+%%   of the SMT-LIB standard.
+%% \item The competition will feature an experimental divisions for
+%%   benchmarks that use strings.  \emph{Rationale:} Corresponding
+%%   theories and benchmarks are expected to be added to SMT-LIB in the
+%%   near future.
+%% \end{itemize}
 
@@
 Section~\ref{sec:participants} gives an overview of participating
-solvers.  Selected results are presented
-%TODO: and analyzed
-in Section~\ref{sec:results}.  We conclude with suggestions for future
+solvers.  Selected competition results are presented in
+Section~\ref{sec:results}.  We conclude with suggestions for future
 SMT Competitions in Section~\ref{sec:conclusions}.
@@
 (which is usually~0, but solvers that did give erroneous responses are
-ranked behind solvers that did not); second, on the number of correct
+ranked below solvers that did not); second, on the number of correct
 responses; third, on the wall-clock and CPU time that the solver
@@
 is used instead of the number of correct responses.  A detailed
-description of the scoring regulations can be found in the competition
+description of the scoring can be found in the competition
 rules~\cite{rules18}.
@@
 parallelism might use up to~$4T$ CPU time.  For the main track and the
-unsat-core track, the competition reports parallel and sequential
-performance separately.  The latter is determined by imposing a
-(virtual) CPU time limit of~$T$.
-
-In tables~\ref{tab:winners-main-1},~\ref{tab:winners-main-2} and
-~\ref{tab:winners-unsat-core}, entries $A/B$ indicate that solver $A$
-is the winner considering sequential performance, while $B$ is the
-winner considering parallel performance. When the same solver has won
-both, which is most often the case, its name appears just once. All
-runs in the application track are sequential and therefore only
-sequential performance is used to determine the winners.
-
-\TODO: non-competitive divisions
+unsat-core track, the competition reports sequential and parallel
+performance separately.  The former is determined by imposing a
+(virtual) CPU time limit of~$T$.  For the application track,
+sequential performance is not recorded (because response times to
+individual {\tt check-sat} commands are not available).
+
+Tables~\ref{tab:winners-main}--\ref{tab:winners-unsat-core} show the
+highest-ranked solver for each division from 2015--2018.  Entries
+$A/B$ indicate that solver~$A$ ranked first considering sequential
+performance, while~$B$ ranked first considering parallel performance.
+When the same solver ranked first in both, which is most often the
+case, its name appears just once.  Some divisions were not
+\emph{competitive} (that is, no official winner was declared for
+them); we are including all divisions here.  Moreover, we are
+including solvers that were running hors concours (and hence
+ineligible to be recognized as official competition winners).  Full
+division rankings are available from the competition website.
 
@@
 incorrect solver responses.  In the division rankings, an incorrect
-response causes a solver to be ranked behind all correct solvers for
+response causes a solver to be ranked below all correct solvers for
 that division.  But the competition's main track consists of many
@@
 \item The best three main-track solvers according to the
-  competition-wide ranking (see
+  competition-wide ranking (CVC4, Yices2, and SMTInterpol; see
   Table~\ref{table:competition-wide-ranking}),
-\item the solvers that won the QF\_BV division in the main track (see
-  Table~\ref{TODO}),
-  % TODO (sequential ranking: Boolector, parallel ranking: Minkeyrink-MT);
+\item the solvers that won the QF\_BV division in the main track
+  (Boolector and MinkeyRink; see Table~\ref{tab:winners-main}),
 \item the solver that won the most competitive divisions in the
-  application track (see Table~\ref{TODO}),
+  application track (Yices2),
 \item the solver that won the most competitive divisions in the
-  unsat-core track (see Table~\ref{TODO}).
+  unsat-core track (Yices2).
 \end{itemize}
-
-%TODO The latter two medals were won by Yices-2.6.0.
 
@@
 
-\subsection{Improvement Over Time}
-
-\TODO
-
-\subsection{Other Measures}
-
-\TODO
+\medskip
+
+\paragraph{Further analysis.}
+
+A deeper analysis of the competition results, for example with a view
+to improvements in SMT solvers over time, would certainly be
+interesting, but goes beyond the immediate mandate of the competition
+organizers.  We leave it for future work, noting that all data needed
+for such an analysis is publicly available from the competition
+website.
 
@@
 
-Thirteen years after its inception, the SMT Competition is a
-well-established event that garners wide interest from developers and
-users of SMT solvers.  The competition continues to contribute to its
-original goals, including adoption of the SMT-LIB format and sparking
-further advances in SMT, and provides a yardstick of performance for
-SMT solvers.
+The SMT Competition was instituted in~2005.  Thirteen years later, it
+is a well-established event that garners wide interest from developers
+and users of SMT solvers.  The competition continues to contribute to
+its original goals, including adoption of the SMT-LIB format and
+sparking further advances in SMT, and provides a yardstick of
+performance for SMT solvers.
 
@@
 the competition now uses all eligible benchmarks (rather than a
-randomly selected subset).  Since the re-introduction of the
-unsat-core track in~2016, the competition again has three separate
-tracks.  This, together with new logics in the SMT Library, has
-brought the total number of competition divisions to 115 in~2018, up
-from just 40 divisions in~2014~\cite{CDW14}.  The number of job pairs
-increased from 339,714 in~2014 to~1,776,062~in 2018, and the total
-wall-clock time in~2018 exceeded 7.6~years.  By these measures, the
-SMT Competition is one of the largest competitions in automated
-reasoning.
+randomly selected subset).
+
+Since the re-introduction of the unsat-core track in~2016, the
+competition again has three separate tracks.  This, together with new
+logics in the SMT Library, has brought the total number of competition
+divisions to 115 in~2018, up from just 40 divisions
+in~2014~\cite{CDW14}.  The number of job pairs increased from 339,714
+in~2014 to~1,776,062~in 2018, and the total wall-clock time in~2018
+exceeded 7.6~years.  By these measures, the SMT Competition is one of
+the largest competitions in automated reasoning.
 

### 2018-11-25 2018/report/table-winners-main.tex
Weights, disagreements, minor
Minor

@@
-\begin{table}[]
-\begin{center}
-\scalebox{.89}{\begin{tabular}{rcccc}
+\begin{table}
+\caption{Best main-track solvers (by division)}
+\label{tab:winners-main}
+\centering
+\scalebox{.84}{\begin{tabular}{|rcccc|}
 \hline
-Logic  & 2015                          & 2016                                & 2017                          & 2018                                  \\
+Division                         & 2015                          & 2016                                & 2017                          & 2018                                  \\
 \hline
-\multicolumn{1}{l}{}            & \multicolumn{1}{l}{}          & \multicolumn{1}{l}{}                & \multicolumn{1}{l}{}          & \multicolumn{1}{l}{}                  \\ \cline{5-5} 
+%\multicolumn{1}{l}{}            & \multicolumn{1}{l}{}          & \multicolumn{1}{l}{}                & \multicolumn{1}{l}{}          & \multicolumn{1}{l}{}                  \\ \cline{5-5}
 ABVFP                            & \multicolumn{1}{l}{}          & \multicolumn{1}{l}{}                & \multicolumn{1}{l|}{}         & \multicolumn{1}{c|}{CVC4}             \\ \cline{2-5}
-\multicolumn{1}{r|}{ALIA}       & \multicolumn{4}{c|}{{[}Z3{]}}                                                                                                               \\ \cline{2-5} 
+\multicolumn{1}{|r|}{ALIA}       & \multicolumn{4}{c|}{{[}Z3{]}}                                                                                                               \\ \cline{2-5}
 AUFBVDTLIA                       & \multicolumn{1}{l}{}          & \multicolumn{1}{l|}{}               & \multicolumn{2}{c|}{CVC4}                                             \\ \cline{4-5}
 AUFDTLIA                         & \multicolumn{1}{l}{}          & \multicolumn{1}{l|}{}               & \multicolumn{2}{c|}{CVC4}                                             \\ \cline{2-5}
-\multicolumn{1}{r|}{AUFLIA}     & \multicolumn{4}{c|}{CVC4}                                                                                                                   \\ \cline{2-5} 
-\multicolumn{1}{r|}{AUFLIRA}    & \multicolumn{4}{c|}{{[}Z3{]}}                                                                                                               \\ \cline{2-5} 
-\multicolumn{1}{r|}{AUFNIRA}    & \multicolumn{1}{c|}{CVC4}     & \multicolumn{2}{c|}{vampire}                                        & \multicolumn{1}{c|}{CVC4}             \\ \cline{2-5} 
-\multicolumn{1}{r|}{BV}         & \multicolumn{1}{c|}{{[}Z3{]}} & \multicolumn{1}{c|}{Q3B}            & \multicolumn{1}{c|}{{[}Z3{]}} & \multicolumn{1}{c|}{CVC4}             \\ \cline{2-5} 
+\multicolumn{1}{|r|}{AUFLIA}     & \multicolumn{4}{c|}{CVC4}                                                                                                                   \\ \cline{2-5}
+\multicolumn{1}{|r|}{AUFLIRA}    & \multicolumn{4}{c|}{{[}Z3{]}}                                                                                                               \\ \cline{2-5}
+\multicolumn{1}{|r|}{AUFNIRA}    & \multicolumn{1}{c|}{CVC4}     & \multicolumn{2}{c|}{Vampire}                                        & \multicolumn{1}{c|}{CVC4}             \\ \cline{2-5}
+\multicolumn{1}{|r|}{BV}         & \multicolumn{1}{c|}{{[}Z3{]}} & \multicolumn{1}{c|}{Q3B}            & \multicolumn{1}{c|}{{[}Z3{]}} & \multicolumn{1}{c|}{CVC4}             \\ \cline{2-5}
 BVFP                             & \multicolumn{1}{l}{}          & \multicolumn{1}{l}{}                & \multicolumn{1}{l|}{}         & \multicolumn{1}{c|}{CVC4}             \\ \cline{5-5}
 FP                               & \multicolumn{1}{l}{}          & \multicolumn{1}{l}{}                & \multicolumn{1}{l|}{}         & \multicolumn{1}{c|}{CVC4}             \\ \cline{2-5}
-\multicolumn{1}{r|}{LIA}        & \multicolumn{2}{c|}{CVC4}                                           & \multicolumn{2}{c|}{{[}Z3{]}}                                         \\ \cline{2-5} 
-\multicolumn{1}{r|}{LRA}        & \multicolumn{2}{c|}{CVC4}                                           & \multicolumn{2}{c|}{{[}Z3{]}}                                         \\ \cline{2-5} 
-\multicolumn{1}{r|}{NIA}        & \multicolumn{4}{c|}{{[}Z3{]}}                                                                                                               \\ \cline{2-5} 
-\multicolumn{1}{r|}{NRA}        & \multicolumn{1}{c|}{CVC4}     & \multicolumn{1}{c|}{Vampire}        & \multicolumn{1}{c|}{Redlog}   & \multicolumn{1}{l}{{[}Z3{]}/Vampire}  \\ \cline{2-5} 
-\multicolumn{1}{r|}{QF\_ABV}    & \multicolumn{4}{c|}{Boolector}                                                                                                              \\ \cline{2-5} 
+\multicolumn{1}{|r|}{LIA}        & \multicolumn{2}{c|}{CVC4}                                           & \multicolumn{2}{c|}{{[}Z3{]}}                                         \\ \cline{2-5}
+\multicolumn{1}{|r|}{LRA}        & \multicolumn{2}{c|}{CVC4}                                           & \multicolumn{2}{c|}{{[}Z3{]}}                                         \\ \cline{2-5}
+\multicolumn{1}{|r|}{NIA}        & \multicolumn{4}{c|}{{[}Z3{]}}                                                                                                               \\ \cline{2-5}
+\multicolumn{1}{|r|}{NRA}        & \multicolumn{1}{c|}{CVC4}     & \multicolumn{1}{c|}{Vampire}        & \multicolumn{1}{c|}{Redlog}   & \multicolumn{1}{c|}{{[}Z3{]}/Vampire} \\ \cline{2-5}
+\multicolumn{1}{|r|}{QF\_ABV}    & \multicolumn{4}{c|}{Boolector}                                                                                                              \\ \cline{2-5}
 QF\_ABVFP                        & \multicolumn{1}{l}{}          & \multicolumn{1}{l}{}                & \multicolumn{1}{l|}{}         & \multicolumn{1}{c|}{CVC4}             \\ \cline{2-5}
-\multicolumn{1}{r|}{QF\_ALIA}   & \multicolumn{4}{c|}{Yices2}                                                                                                                 \\ \cline{2-5} 
-\multicolumn{1}{r|}{QF\_ANIA}   & \multicolumn{1}{c|}{{[}Z3{]}} & \multicolumn{2}{c|}{CVC4}                                           & \multicolumn{1}{c|}{{[}Z3{]}}         \\ \cline{2-5} 
-\multicolumn{1}{r|}{QF\_AUFBV}  & \multicolumn{3}{c|}{{[}MathSAT{]}}                                                                  & \multicolumn{1}{c|}{CVC4}             \\ \cline{2-5} 
-\multicolumn{1}{r|}{QF\_AUFLIA} & \multicolumn{4}{c|}{Yices2}                                                                                                                 \\ \cline{2-5} 
-\multicolumn{1}{r|}{QF\_AUFNIA} & \multicolumn{2}{c|}{CVC4}                                           & \multicolumn{2}{c|}{{[}Z3{]}}                                         \\ \cline{2-5} 
-\multicolumn{1}{r|}{QF\_AX}     & \multicolumn{4}{c|}{Yices2}                                                                                                                 \\ \cline{2-5} 
-\multicolumn{1}{r|}{QF\_BV}     & \multicolumn{2}{c|}{Boolector}                                      & \multicolumn{2}{c|}{Boolector/MinkeyRink}                             \\ \cline{2-5} 
-\multicolumn{1}{r|}{QF\_BVFP}   & \multicolumn{1}{c|}{Z3 (FP)}  & \multicolumn{2}{c|}{{[}Z3{]}}                                       & \multicolumn{1}{c|}{CVC4}             \\ \cline{2-5} 
-QF\_DT                          & \multicolumn{1}{l}{}          & \multicolumn{1}{l|}{}               & \multicolumn{2}{c|}{CVC4}                                             \\ \cline{4-5} 
-\end{tabular}}
-\end{center}
-\caption{\label{tab:winners-main-1} Winners of the main track (part 1).}
-\end{table}
-
-\begin{table}[]
-\begin{center}
-\scalebox{.89}{\begin{tabular}{rcccc}
-\hline
-Logic  & 2015                          & 2016                                & 2017                          & 2018                                  \\
-\hline
-\multicolumn{1}{l}{}            & \multicolumn{1}{l}{}          & \multicolumn{1}{l}{}                & \multicolumn{1}{l}{}          & \multicolumn{1}{l}{}                  \\ \cline{2-5} 
-\multicolumn{1}{r|}{QF\_FP}     & \multicolumn{1}{c|}{Z3 (FP)}  & \multicolumn{1}{c|}{{[}MathSat5{]}} & \multicolumn{1}{c|}{{[}Z3{]}} & \multicolumn{1}{c|}{COLIBRI}          \\ \cline{2-5} 
-\multicolumn{1}{r|}{QF\_IDL}    & \multicolumn{2}{c|}{{[}Z3{]}}                                       & \multicolumn{2}{c|}{Yices2}                                           \\ \cline{2-5} 
-\multicolumn{1}{r|}{QF\_LIA}    & \multicolumn{3}{c|}{{[}MathSat{]}}                                                                  & \multicolumn{1}{c|}{SPASS-SATT}       \\ \cline{2-5} 
-\multicolumn{1}{r|}{QF\_LIRA}   & \multicolumn{2}{c|}{Yices2}                                         & \multicolumn{2}{c|}{{[}Z3{]}}                                         \\ \cline{2-5} 
-\multicolumn{1}{r|}{QF\_LRA}    & \multicolumn{4}{c|}{CVC4}                                                                                                                   \\ \cline{2-5} 
-\multicolumn{1}{r|}{QF\_NIA}    & \multicolumn{2}{c|}{{[}Z3{]}}                                       & \multicolumn{2}{c|}{CVC4}                                             \\ \cline{2-5} 
-\multicolumn{1}{r|}{QF\_NIRA}   & \multicolumn{2}{c|}{CVC4}                                           & \multicolumn{2}{c|}{SMTRAT}                                           \\ \cline{2-5} 
-\multicolumn{1}{r|}{QF\_NRA}    & \multicolumn{2}{c|}{{[}Z3{]}}                                       & \multicolumn{1}{c|}{Yices2}   & \multicolumn{1}{c|}{{[}Z3{]}}         \\ \cline{2-5} 
-\multicolumn{1}{r|}{QF\_RDL}    & \multicolumn{4}{c|}{Yices2}                                                                                                                 \\ \cline{2-5} 
+\multicolumn{1}{|r|}{QF\_ALIA}   & \multicolumn{4}{c|}{Yices2}                                                                                                                 \\ \cline{2-5}
+\multicolumn{1}{|r|}{QF\_ANIA}   & \multicolumn{1}{c|}{{[}Z3{]}} & \multicolumn{2}{c|}{CVC4}                                           & \multicolumn{1}{c|}{{[}Z3{]}}         \\ \cline{2-5}
+\multicolumn{1}{|r|}{QF\_AUFBV}  & \multicolumn{3}{c|}{{[}MathSAT{]}}                                                                  & \multicolumn{1}{c|}{CVC4}             \\ \cline{2-5}
+\multicolumn{1}{|r|}{QF\_AUFLIA} & \multicolumn{4}{c|}{Yices2}                                                                                                                 \\ \cline{2-5}
+\multicolumn{1}{|r|}{QF\_AUFNIA} & \multicolumn{2}{c|}{CVC4}                                           & \multicolumn{2}{c|}{{[}Z3{]}}                                         \\ \cline{2-5}
+\multicolumn{1}{|r|}{QF\_AX}     & \multicolumn{4}{c|}{Yices2}                                                                                                                 \\ \cline{2-5}
+\multicolumn{1}{|r|}{QF\_BV}     & \multicolumn{2}{c|}{Boolector}                                      & \multicolumn{2}{c|}{Boolector/MinkeyRink}                             \\ \cline{2-5}
+\multicolumn{1}{|r|}{QF\_BVFP}   & \multicolumn{1}{c|}{Z3}       & \multicolumn{2}{c|}{{[}Z3{]}}                                       & \multicolumn{1}{c|}{CVC4}             \\ \cline{2-5}
+QF\_DT                           & \multicolumn{1}{l}{}          & \multicolumn{1}{l|}{}               & \multicolumn{2}{c|}{CVC4}                                             \\ \cline{2-5}
+\multicolumn{1}{|r|}{QF\_FP}     & \multicolumn{1}{c|}{Z3}       & \multicolumn{1}{c|}{{[}MathSAT{]}}  & \multicolumn{1}{c|}{{[}Z3{]}} & \multicolumn{1}{c|}{COLIBRI}          \\ \cline{2-5}
+\multicolumn{1}{|r|}{QF\_IDL}    & \multicolumn{2}{c|}{{[}Z3{]}}                                       & \multicolumn{2}{c|}{Yices2}                                           \\ \cline{2-5}
+\multicolumn{1}{|r|}{QF\_LIA}    & \multicolumn{3}{c|}{{[}MathSAT{]}}                                                                  & \multicolumn{1}{c|}{SPASS-SATT}       \\ \cline{2-5}
+\multicolumn{1}{|r|}{QF\_LIRA}   & \multicolumn{2}{c|}{Yices2}                                         & \multicolumn{2}{c|}{{[}Z3{]}}                                         \\ \cline{2-5}
+\multicolumn{1}{|r|}{QF\_LRA}    & \multicolumn{4}{c|}{CVC4}                                                                                                                   \\ \cline{2-5}
+\multicolumn{1}{|r|}{QF\_NIA}    & \multicolumn{2}{c|}{{[}Z3{]}}                                       & \multicolumn{2}{c|}{CVC4}                                             \\ \cline{2-5}
+\multicolumn{1}{|r|}{QF\_NIRA}   & \multicolumn{2}{c|}{CVC4}                                           & \multicolumn{2}{c|}{SMT-RAT}                                          \\ \cline{2-5}
+\multicolumn{1}{|r|}{QF\_NRA}    & \multicolumn{2}{c|}{{[}Z3{]}}                                       & \multicolumn{1}{c|}{Yices2}   & \multicolumn{1}{c|}{{[}Z3{]}}         \\ \cline{2-5}
+\multicolumn{1}{|r|}{QF\_RDL}    & \multicolumn{4}{c|}{Yices2}                                                                                                                 \\ \cline{2-5}
 QF\_SLIA                         & \multicolumn{1}{l}{}          & \multicolumn{1}{l}{}                & \multicolumn{1}{l|}{}         & \multicolumn{1}{c|}{CVC4}             \\ \cline{2-5}
-\multicolumn{1}{r|}{QF\_UF}     & \multicolumn{4}{c|}{Yices2}                                                                                                                 \\ \cline{2-5} 
-\multicolumn{1}{r|}{QF\_UFBV}   & \multicolumn{4}{c|}{Boolector}                                                                                                              \\ \cline{2-5} 
-\multicolumn{1}{r|}{QF\_UFIDL}  & \multicolumn{4}{c|}{Yices2}                                                                                                                 \\ \cline{2-5} 
-\multicolumn{1}{r|}{QF\_UFLIA}  & \multicolumn{2}{c|}{{[}Z3{]}}                                       & \multicolumn{2}{c|}{Yices2}                                           \\ \cline{2-5} 
-\multicolumn{1}{r|}{QF\_UFLRA}  & \multicolumn{4}{c|}{Yices2}                                                                                                                 \\ \cline{2-5} 
-\multicolumn{1}{r|}{QF\_UFNIA}  & \multicolumn{1}{c|}{CVC4}     & \multicolumn{1}{c|}{Yices2/CVC4}    & \multicolumn{2}{c|}{Yices2}                                           \\ \cline{2-5} 
-\multicolumn{1}{r|}{QF\_UFNRA}  & \multicolumn{1}{c|}{{[}Z3{]}} & \multicolumn{1}{c|}{Yices2}         & \multicolumn{1}{c|}{{[}Z3{]}} & \multicolumn{1}{c|}{Yices2}           \\ \cline{2-5} 
-\multicolumn{1}{r|}{UF}         & \multicolumn{2}{c|}{CVC4}                                           & \multicolumn{1}{c|}{Vampire}  & \multicolumn{1}{c|}{CVC4/Vampire}     \\ \cline{2-5} 
-\multicolumn{1}{r|}{UFBV}       & \multicolumn{4}{c|}{{[}Z3{]}}                                                                                                               \\ \cline{2-5} 
+\multicolumn{1}{|r|}{QF\_UF}     & \multicolumn{4}{c|}{Yices2}                                                                                                                 \\ \cline{2-5}
+\multicolumn{1}{|r|}{QF\_UFBV}   & \multicolumn{4}{c|}{Boolector}                                                                                                              \\ \cline{2-5}
+\multicolumn{1}{|r|}{QF\_UFIDL}  & \multicolumn{4}{c|}{Yices2}                                                                                                                 \\ \cline{2-5}
+\multicolumn{1}{|r|}{QF\_UFLIA}  & \multicolumn{2}{c|}{{[}Z3{]}}                                       & \multicolumn{2}{c|}{Yices2}                                           \\ \cline{2-5}
+\multicolumn{1}{|r|}{QF\_UFLRA}  & \multicolumn{4}{c|}{Yices2}                                                                                                                 \\ \cline{2-5}
+\multicolumn{1}{|r|}{QF\_UFNIA}  & \multicolumn{1}{c|}{CVC4}     & \multicolumn{1}{c|}{Yices2/CVC4}    & \multicolumn{2}{c|}{Yices2}                                           \\ \cline{2-5}
+\multicolumn{1}{|r|}{QF\_UFNRA}  & \multicolumn{1}{c|}{{[}Z3{]}} & \multicolumn{1}{c|}{Yices2}         & \multicolumn{1}{c|}{{[}Z3{]}} & \multicolumn{1}{c|}{Yices2}           \\ \cline{2-5}
+\multicolumn{1}{|r|}{UF}         & \multicolumn{2}{c|}{CVC4}                                           & \multicolumn{1}{c|}{Vampire}  & \multicolumn{1}{c|}{CVC4/Vampire}     \\ \cline{2-5}
+\multicolumn{1}{|r|}{UFBV}       & \multicolumn{4}{c|}{{[}Z3{]}}                                                                                                               \\ \cline{2-5}
 UFDT                             & \multicolumn{1}{l}{}          & \multicolumn{1}{l|}{}               & \multicolumn{2}{c|}{CVC4}                                             \\ \cline{4-5}
 UFDTLIA                          & \multicolumn{1}{l}{}          & \multicolumn{1}{l|}{}               & \multicolumn{1}{c|}{Vampire}  & \multicolumn{1}{c|}{CVC4}             \\ \cline{2-5}
-\multicolumn{1}{r|}{UFIDL}      & \multicolumn{1}{c|}{{[}Z3{]}} & \multicolumn{2}{c|}{CVC4}                                           & \multicolumn{1}{c|}{{[}Z3{]}}         \\ \cline{2-5} 
-\multicolumn{1}{r|}{UFLIA}      & \multicolumn{4}{c|}{CVC4}                                                                                                                   \\ \cline{2-5} 
-\multicolumn{1}{r|}{UFLRA}      & \multicolumn{1}{c|}{CVC3}     & \multicolumn{3}{c|}{{[}Z3{]}}                                                                               \\ \cline{2-5} 
-\multicolumn{1}{r|}{UFNIA}      & \multicolumn{1}{c|}{CVC4}     & \multicolumn{2}{c|}{Vampire}                                        & \multicolumn{1}{c|}{{[}Z3{]}/Vampire} \\ \cline{2-5} 
+\multicolumn{1}{|r|}{UFIDL}      & \multicolumn{1}{c|}{{[}Z3{]}} & \multicolumn{2}{c|}{CVC4}                                           & \multicolumn{1}{c|}{{[}Z3{]}}         \\ \cline{2-5}
+\multicolumn{1}{|r|}{UFLIA}      & \multicolumn{4}{c|}{CVC4}                                                                                                                   \\ \cline{2-5}
+\multicolumn{1}{|r|}{UFLRA}      & \multicolumn{1}{c|}{CVC3}     & \multicolumn{3}{c|}{{[}Z3{]}}                                                                               \\ \cline{2-5}
+\multicolumn{1}{|r|}{UFNIA}      & \multicolumn{1}{c|}{CVC4}     & \multicolumn{2}{c|}{Vampire}                                        & \multicolumn{1}{c|}{{[}Z3{]}/Vampire} \\ \hline
 \end{tabular}}
-\end{center}
-\caption{\label{tab:winners-main-2} Winners of the main track (part 2).}
 \end{table}

### 2018-11-25 2018/report/SMT-COMP.tex
Minor

@@
 
-\jsatheading{1}{2004}{25-30}
+\jsatheading{1}{2004}{1-25}
 \ShortHeadings{The SMT Competition 2015--2018}
 {Weber et al.}
-\firstpageno{25}
+\firstpageno{1}
 
@@
 
-\published{September 2004}{October 2004}{November 2004}
+\published{November 2018}{November 2018}{November 2018}
 
@@
 parallelism might use up to~$4T$ CPU time.  For the main track and the
-unsat-core track, the competition reports sequential and parallel
-performance separately.  The former is determined by imposing a
-(virtual) CPU time limit of~$T$.  For the application track,
-sequential performance is not recorded (because response times to
-individual {\tt check-sat} commands are not available).
+unsat-core track, the competition reports parallel and sequential
+performance separately.  The latter is determined by imposing a
+(virtual) CPU time limit of~$T$.  For the application track, only
+parallel performance is reported (because response times to individual
+{\tt check-sat} commands are not recorded by StarExec).
 

### 2019-01-18 2018/report/SMT-COMP.tex
Fixed Mathias Preiner's affiliation.

@@
     Boolector~\cite{DBLP:conf/cav/NiemetzPWB18} & Mathias Preiner
-                        (Johannes Kepler University)\\
+                        (Johannes Kepler University, Stanford University)\\
     COLIBRI~\cite{colibri} & Fran\c{c}ois Bobot

### 2019-02-01 2018/report/SMT-COMP.tex
Less inaccurate meta-data
Add Alt-Ergo reference

--- 2018-11-25 2018/report/SMT-COMP.tex
@@
 
-\jsatheading{1}{2004}{1-25}
+\jsatheading{?}{2018}{??-??}
 \ShortHeadings{The SMT Competition 2015--2018}
@@
 
-\published{November 2018}{November 2018}{November 2018}
+\published{November 2018}{TBA}{TBA}
 
@@
                         (Mentor Graphics)\\
-    Alt-Ergo          & Albin Coquereau
+    Alt-Ergo~\cite{conchon:hal-01960203} & Albin Coquereau
                         (CNRS and University of Paris-Sud)\\

### 2019-02-01 2018/report/SMT-COMP.tex
Fix affiliation for Ctrl-Ergo (Mohamed Iguernlala)

@@
     Ctrl-Ergo         & Mohamed Iguernlala
-                        (CNRS and University of Paris-Sud)\\
+                        (OCamlPro SAS)\\
     CVC3~\cite{DBLP:conf/cav/BarrettT07} & Kshitij Bansal

### 2019-02-01 2018/report/SMT-COMP.tex
Add Ctrl-Ergo reference

@@
                         (French Alternative Energies and Atomic Energy Commission)\\
-    Ctrl-Ergo         & Mohamed Iguernlala
+    Ctrl-Ergo~\cite{10.1007/978-3-642-31365-3_8} & Mohamed Iguernlala
                         (OCamlPro SAS)\\

### 2019-02-01 2018/report/SMT-COMP.tex
Better AProVE reference

--- 2019-02-01 2018/report/SMT-COMP.tex
@@
                         (CNRS and University of Paris-Sud)\\
-    AProVE~\cite{DBLP:conf/cade/GieslBEFFOPSSST14} & Carsten Fuhs
+    AProVE~\cite{DBLP:journals/jar/GieslABEFFHOPSS17} & Carsten Fuhs
                         (University College London; Birkbeck, University of London)\\

### 2019-02-01 2018/report/SMT-COMP.tex
Fix affiliation for STP (Norbert Manthey)

--- 2019-02-01 2018/report/SMT-COMP.tex
@@
     STP~\cite{ganesh07} & Mate Soos, Trevor Hansen, Norbert Manthey
-                        (National University of Singapore; University of Melbourne; Amazon Web Services)\\
+                        (National University of Singapore; University of Melbourne)\\
     toysmt             & Masahiro Sakai

### 2019-02-01 2018/report/SMT-COMP.tex
Nicer tables (using the booktabs package)

@@
 \usepackage{amsmath, amsthm, amssymb}
+\usepackage{booktabs}
 %\usepackage[pdf]{pstricks}
@@
   \centering
-  \begin{tabular}{|r@{\ \ }l|r|r|r|r|}
-    \hline
-                               & & \multicolumn{1}{c|}{2015} & \multicolumn{1}{c|}{2016} & \multicolumn{1}{c|}{2017} & \multicolumn{1}{c|}{2018} \\
-    \hline
+  \begin{tabular}{r@{\ \ }lrrrr}
+    \toprule
+                               & & \multicolumn{1}{c}{2015} & \multicolumn{1}{c}{2016} & \multicolumn{1}{c}{2017} & \multicolumn{1}{c}{2018} \\
+    \midrule
     \multirow{2}{*}{Non-incremental $\{$} & benchmarks & 196375 & 196114 & 258079 & 336844 \\
@@
                                           & logics     &     15 &     15 &     22 &     26 \\
-    \hline
+    \bottomrule
   \end{tabular}
@@
   \centering
-  \begin{tabular}{|l|r|r|r|r|}
-    \hline
-    & \multicolumn{1}{c|}{2015} & \multicolumn{1}{c|}{2016} & \multicolumn{1}{c|}{2017} & \multicolumn{1}{c|}{2018} \\
-    \hline
+  \begin{tabular}{lcccc}
+    \toprule
+    & 2015 & 2016 & 2017 & 2018 \\
+    \midrule
     Main track        &  40 & 40 & 49 & 50 \\
@@
     Unsat-core track  &  -- & 40 & 41 & 44 \\
-    \hline
+    \bottomrule
   \end{tabular}
@@
   \centering
-  \scalebox{.9}[.82]{\begin{tabular}{|l|r|r|r|r|}
-    \hline
-    Division & \multicolumn{1}{c|}{2015} & \multicolumn{1}{c|}{2016} & \multicolumn{1}{c|}{2017} & \multicolumn{1}{c|}{2018} \\
-    \hline
+  \scalebox{.9}[.8]{\begin{tabular}{lrrrr}
+    \toprule
+    Division & \multicolumn{1}{c}{2015} & \multicolumn{1}{c}{2016} & \multicolumn{1}{c}{2017} & \multicolumn{1}{c}{2018} \\
+    \midrule
     ABVFP      &     -- &     -- &      1 &     1 \\
@@
     UFNIA      &   2319 &   2319 &   3308 &  3308 \\
-    \hline
+    \midrule
     Total      & 154238 & 154424 & 256973 & 333241 \\
-    \hline
+    \bottomrule
   \end{tabular}}
@@
   \centering
-  \begin{tabular}{|l|r|r|r|r|}
-    \hline
-    Division & \multicolumn{1}{c|}{2015} & \multicolumn{1}{c|}{2016} & \multicolumn{1}{c|}{2017} & \multicolumn{1}{c|}{2018} \\
-    \hline
+  \begin{tabular}{lrrrr}
+    \toprule
+    Division & \multicolumn{1}{c}{2015} & \multicolumn{1}{c}{2016} & \multicolumn{1}{c}{2017} & \multicolumn{1}{c}{2018} \\
+    \midrule
     ALIA       &   24 &   24 &   24 &   24 \\
@@
     UFLRA      & 5358 & 5358 & 1870 & 1870 \\
-    \hline
+    \midrule
     Total      & 9852 & 9856 & 5971 & 9257 \\
-    \hline
+    \bottomrule
   \end{tabular}
@@
   \centering
-  \scalebox{1}[.93]{\begin{tabular}{|l|r|r|r|}
-    \hline
-    Division & \multicolumn{1}{c|}{2016} & \multicolumn{1}{c|}{2017} & \multicolumn{1}{c|}{2018} \\
-    \hline
+  \scalebox{1}[.91]{\begin{tabular}{lrrr}
+    \toprule
+    Division & \multicolumn{1}{c}{2016} & \multicolumn{1}{c}{2017} & \multicolumn{1}{c}{2018} \\
+    \midrule
     ALIA       &     41 &     41 &     41 \\
@@
     UFNIA      &   2318 &   2432 &   2457 \\
-    \hline
+    \midrule
     Total      &  93241 & 114233 & 130705 \\
-    \hline
+    \bottomrule
   \end{tabular}}
@@
 \begin{table}
-  \caption{Wall-clock time limits}
+  \caption{Wall-clock time limits (in minutes)}
   \label{table:time-limits}
   \centering
-  \begin{tabular}{|l|r|r|r|r|}
-    \hline
-    & \multicolumn{1}{c|}{2015} & \multicolumn{1}{c|}{2016} & \multicolumn{1}{c|}{2017} & \multicolumn{1}{c|}{2018} \\
-    \hline
-    Main track        & 40~min & 40~min & 20~min\protect\footnotemark & 20~min \\
-    Application track & 40~min & 40~min & 40~min\phantom{$^{1.}$} & 40~min \\
-    Unsat-core track  &     -- & 40~min & 40~min\phantom{$^{1.}$} & 40~min \\
-    \hline
+  \begin{tabular}{lcccc}
+    \toprule
+    & 2015 & 2016 & 2017 & 2018 \\
+    \midrule
+    Main track        & 40 & 40 & 20\protect\footnotemark & 20 \\
+    Application track & 40 & 40 & 40\phantom{$^{1.}$}      & 40 \\
+    Unsat-core track  & -- & 40 & 40\phantom{$^{1.}$}      & 40 \\
+    \bottomrule
   \end{tabular}
@@
   \centering
-  \begin{tabular}{|l|p{11.5cm}|}
-    \hline
+  \begin{tabular}{lp{11.5cm}}
+    \toprule
     Solver & Submitters (Affiliations)\\
-    \hline
+    \midrule
     ABC~\cite{DBLP:conf/cav/BraytonM10} & Valeriy Balabanov
@@
                         (Microsoft Research; Uppsala University)\\
-    \hline
+    \bottomrule
   \end{tabular}
@@
   \centering
-  \begin{tabular}{|l|r@{\,\,}r|r@{\,\,}r|r@{\,\,}r|r@{\,\,}r|}
-    \hline
-    Solver & \multicolumn{2}{c|}{2015} & \multicolumn{2}{c|}{2016} & \multicolumn{2}{c|}{2017} & \multicolumn{2}{c|}{2018} \\
-    \hline
+  \begin{tabular}{lr@{\,\,}rr@{\,\,}rr@{\,\,}rr@{\,\,}r}
+    \toprule
+    Solver & \multicolumn{2}{c}{2015} & \multicolumn{2}{c}{2016} & \multicolumn{2}{c}{2017} & \multicolumn{2}{c}{2018} \\
+    \midrule
     ABC               &    &      &  2 &      &    &      &    &      \\
@@
     Z3                &  2 & [+1] &    & [+1] &    & [+1] &    & [+1] \\
-    \hline
+    \midrule
     Total             & 26 & [+4] & 32 & [+5] & 22 & [+4] & 25 & [+6] \\
-    \hline
+    \bottomrule
   \end{tabular}
@@
   \centering
-  \begin{tabular}{|l|r@{\,\,}r|r@{\,\,}r|r@{\,\,}r|r@{\,\,}r|}
-    \hline
-                      & \multicolumn{2}{c|}{2015} & \multicolumn{2}{c|}{2016} & \multicolumn{2}{c|}{2017} & \multicolumn{2}{c|}{2018} \\
-    \hline
+  \begin{tabular}{lr@{\,\,}rr@{\,\,}rr@{\,\,}rr@{\,\,}r}
+    \toprule
+                      & \multicolumn{2}{c}{2015} & \multicolumn{2}{c}{2016} & \multicolumn{2}{c}{2017} & \multicolumn{2}{c}{2018} \\
+    \midrule
     Main track        & 21 &               [+2] & 25 & [+2] & 19 & [+2] & 20 & [+4] \\
     Application track & 10 &               [+3] &  8 & [+3] &  4 & [+2] &  4 & [+2] \\
-    Unsat-core track  & \multicolumn{2}{c|}{---} &  1 & [+4] &  2 & [+2] &  3 & [+2] \\
-    \hline
+    Unsat-core track  & \multicolumn{2}{c}{---} &  1 & [+4] &  2 & [+2] &  3 & [+2] \\
+    \midrule
     Total             & 26 &               [+4] & 32 & [+5] & 22 & [+4] & 25 & [+6] \\
-    \hline
+    \bottomrule
   \end{tabular}
@@
   \centering
-  \scalebox{.89}{\begin{tabular}{|c|p{2.2cm}|r|r|p{0cm}|c|p{2.2cm}|r|r|}
-    \cline{1-4} \cline{6-9}
-    \multicolumn{4}{|c|}{2015} & & \multicolumn{4}{c|}{2016} \\ \cline{1-4} \cline{6-9}
+  \scalebox{.89}{\begin{tabular}{cp{2.2cm}rrp{0cm}cp{2.2cm}rr}
+    \cmidrule[\heavyrulewidth]{1-4} \cmidrule[\heavyrulewidth]{6-9}
+    \multicolumn{4}{c}{2015} & & \multicolumn{4}{c}{2016} \\ \cmidrule{1-4} \cmidrule{6-9}
     Rank & Solver & Score  & Score  & & Rank & Solver & Score & Score \\
-         &        & (sequential) & (parallel) & & & & (sequential) & (parallel) \\ \cline{1-4} \cline{6-9}
+         &        & (sequential) & (parallel) & & & & (sequential) & (parallel) \\ \cmidrule{1-4} \cmidrule{6-9}
          & [Z3]              & 159.36 & 159.36 & &    & [Z3]   & 185.09 & 185.09 \\
@@
       2. & CVC4(exp)\footnotemark & 140.47 & 140.51 & & 2. & Yices2 & 119.29 & 119.29 \\
-      3. & Yices             & 101.91 & 101.91 & & 3. & veriT  &  75.11 &  75.11 \\ \cline{1-4} \cline{6-9}
+      3. & Yices             & 101.91 & 101.91 & & 3. & veriT  &  75.11 &  75.11 \\ \cmidrule[\heavyrulewidth]{1-4} \cmidrule[\heavyrulewidth]{6-9}
   \end{tabular}}
@@
 
-  \scalebox{.89}{\begin{tabular}{|c|p{2.2cm}|r|r|p{0cm}|c|p{2.2cm}|r|r|}
-    \cline{1-4} \cline{6-9}
-    \multicolumn{4}{|c|}{2017} & & \multicolumn{4}{c|}{2018} \\ \cline{1-4} \cline{6-9}
+  \scalebox{.89}{\begin{tabular}{cp{2.2cm}rrp{0cm}cp{2.2cm}rr}
+    \cmidrule[\heavyrulewidth]{1-4} \cmidrule[\heavyrulewidth]{6-9}
+    \multicolumn{4}{c}{2017} & & \multicolumn{4}{c}{2018} \\ \cmidrule{1-4} \cmidrule{6-9}
     Rank & Solver & Score  & Score  & & Rank & Solver & Score & Score \\
-         &        & (sequential) & (parallel) & & & & (sequential) & (parallel) \\ \cline{1-4} \cline{6-9}
+         &        & (sequential) & (parallel) & & & & (sequential) & (parallel) \\ \cmidrule{1-4} \cmidrule{6-9}
          & [Z3]        & 171.99 & 171.99 & & 1. & CVC4        & 211.99 & 211.99 \\
@@
       2. & Yices2      & 110.63 & 110.63 & & 2. & Yices2      & 115.26 & 115.26 \\
-      3. & SMTInterpol &  65.96 &  66.00 & & 3. & SMTInterpol &  65.32 &  65.38 \\ \cline{1-4} \cline{6-9}
+      3. & SMTInterpol &  65.96 &  66.00 & & 3. & SMTInterpol &  65.32 &  65.38 \\ \cmidrule[\heavyrulewidth]{1-4} \cmidrule[\heavyrulewidth]{6-9}
   \end{tabular}}

### 2019-02-28 2018/report/SMT-COMP.tex
\normalfont for author roles
Minor
Minor (acknowledgments)

@@
 
-\jsatheading{?}{2018}{??-??}
+\jsatheading{?}{2019}{??-??}
 \ShortHeadings{The SMT Competition 2015--2018}
@@
 \author{%
-  \name{Tjark Weber (competition chair, 2015--2018)}
+  \name{Tjark Weber {\normalfont (competition chair, 2015--2018)}}
   \email{tjark.weber@it.uu.se} \\
@@
   \AND
-  \name{Sylvain Conchon (co-organizer, 2015--2016)}
+  \name{Sylvain Conchon {\normalfont (co-organizer, 2015--2016)}}
   \email{Sylvain.Conchon@lri.fr} \\
@@
   \AND
-  \name{David D\'{e}harbe (co-organizer, 2015--2016)}
+  \name{David D\'{e}harbe {\normalfont (co-organizer, 2015--2016)}}
   \email{david.deharbe@clearsy.com} \\
@@
   \AND
-  \name{Matthias Heizmann (co-organizer, 2016--2018)}
+  \name{Matthias Heizmann {\normalfont (co-organizer, 2016--2018)}}
   \email{heizmann@informatik.uni-freiburg.de} \\
@@
   \AND
-  \name{Aina Niemetz (co-organizer, 2018)}
+  \name{Aina Niemetz {\normalfont (co-organizer, 2018)}}
   \email{niemetz@cs.stanford.edu} \\
@@
   \AND
-  \name{Giles Reger (co-organizer, 2017--2018)}
+  \name{Giles Reger {\normalfont (co-organizer, 2017--2018)}}
   \email{giles.reger@manchester.ac.uk} \\
@@
 
-\published{November 2018}{TBA}{TBA}
+\published{November 2018}{March 2019}{TBA}
 
@@
 SMT-LIB release; all contributors of new benchmarks to the SMT
-Library; and last but not least all solver developers who entered
+Library; and, last but not least, all solver developers who entered
 their solver into the competition.

### 2019-02-28 2018/report/SMT-COMP.tex
Unique solutions

@@
 
-\medskip
-
-\paragraph{Further analysis.}
-
-A deeper analysis of the competition results, for example with a view
-to improvements in SMT solvers over time, would certainly be
-interesting, but goes beyond the immediate mandate of the competition
-organizers.  We leave it for future work, noting that all data needed
-for such an analysis is publicly available from the competition
-website.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection{Further Analysis}
+
+Beyond the competition rankings, the competition data provides ample
+opportunity for further analysis.  Here, we report on three additional
+aspects: progress in solver performance, number of uniquely solved
+benchmarks, and use of parallelism in SMT solvers.
+
+\paragraph{Progress in solver performance.}
+
+%TODO
+
+\paragraph{Unique solutions.}
+
+For each SMT solver, the number of uniquely solved benchmarks---that
+is, the number of benchmarks that were solved by this solver only---is
+a measure of how much the solver contributes to the state-of-the-art,
+and the extent to which it is complementary to other solvers.  In
+particular, if a solver that uniquely solves~$n$ benchmarks had not
+participated in the competition, the virtual best solver would have
+been able to solve~$n$ fewer benchmarks.
+Table~\ref{table:unique-solutions} shows the number of uniquely solved
+benchmarks for each main-track solver from 2015--2018.  (Multiple
+versions of a solver are consolidated in this table, and answers that
+were given by unsound solver versions are excluded.)
+
+Solvers that rank highly in the competition-wide ranking
+(Section~\ref{sec:floc}) often also solve many benchmarks uniquely,
+but there are exceptions.  For instance, SMTInterpol has relatively
+few unique solutions, despite achieving third place in the
+competition-wide ranking in~2017 and~2018.  However, almost every
+(sound) solver solves at least some benchmarks uniquely, and hence
+contributes to the state-of-the-art.
+
+The largest numbers in Table~\ref{table:unique-solutions} are due to
+divisions in which there was only one sound solver: in~2016, MathSAT
+was the only solver to support QF\_FP; in~2017, Z3 was the only sound
+solver in QF\_FP; and in~2018, CVC4 was the only solver to support
+QF\_SLIA, as well as the only sound solver in QF\_ABVFP.  Note that
+divisions with fewer than two competing solvers do not affect the
+competition-wide ranking.
+
+\begin{table}
+  \caption{Number of main-track benchmarks uniquely solved by each
+    solver (by year)}
+  \label{table:unique-solutions}
+  \centering
+  \begin{tabular}{lrrrr}
+    \toprule
+    Solver & 2015 & 2016 & 2017 & 2018 \\
+    \midrule
+    ABC               &       & 3     &       &        \\
+    Alt-Ergo          &       &       &       & 1      \\
+    AProVE            & 1     & 0     & 413   & 553    \\
+    Boolector         & 37    & 23    & 97    & 62     \\
+    COLIBRI           &       &       & 3     & 22     \\
+    Ctrl-Ergo         &       &       &       & 12     \\
+    CVC3              & 69    &       &       &        \\
+    CVC4              & 4884  & 116   & 10258 & 100679 \\
+    MapleSTP          &       & 2     &       &        \\
+    {[}MathSAT{]}     & 13    & 28748 & 11    & 5      \\
+    MinkeyRink        &       & 27    & 27    & 16     \\
+    OpenSMT2          & 0     & 0     & 0     & 0      \\
+    ProB              &       & 1     &       &        \\
+    Q3B               &       & 0     & 89    & 0      \\
+    raSAT             & 3     & 14    &       &        \\
+    Redlog            &       &       & 4     &        \\
+    SMT-RAT           & 13    & 0     & 85    & 2      \\
+    SMTInterpol       & 2     & 2     & 5     & 4      \\
+    SPASS-SATT        &       &       &       & 34     \\
+    STP               & 4     & 2     & 4     & 5      \\
+    toysmt            &       & 0     &       &        \\
+    Vampire           &       & 139   & 753   & 652    \\
+    veriT             & 5     & 21    & 55    & 57     \\
+    XSat              &       &       & 0     &        \\
+    Yices2            & 88    & 146   & 2379  & 1535   \\
+    Z3                & 6139  & 242   & 40992 & 888    \\
+    \midrule
+    Total             & 11258 & 29486 & 55175 & 104527 \\
+    \bottomrule
+  \end{tabular}
+\end{table}
 

### 2019-03-01 2018/report/SMT-COMP.tex
Minor (unique solutions)
Unique solutions: more correct numbers; use of parallelism

@@
 competition-wide ranking in~2017 and~2018.  However, almost every
-(sound) solver solves at least some benchmarks uniquely, and hence
-contributes to the state-of-the-art.
+(sound) solver in the competition solves at least some benchmarks
+uniquely, and hence contributes to the state-of-the-art.
 
@@
     \midrule
-    ABC               &       & 3     &       &        \\
+    ABC               &       & 7     &       &        \\
     Alt-Ergo          &       &       &       & 1      \\
-    AProVE            & 1     & 0     & 413   & 553    \\
-    Boolector         & 37    & 23    & 97    & 62     \\
+    AProVE            & 5     & 0     & 413   & 553    \\
+    Boolector         & 37    & 25    & 97    & 62     \\
     COLIBRI           &       &       & 3     & 22     \\
     Ctrl-Ergo         &       &       &       & 12     \\
-    CVC3              & 69    &       &       &        \\
-    CVC4              & 4884  & 116   & 10258 & 100679 \\
-    MapleSTP          &       & 2     &       &        \\
-    {[}MathSAT{]}     & 13    & 28748 & 11    & 5      \\
-    MinkeyRink        &       & 27    & 27    & 16     \\
+    CVC3              & 70    &       &       &        \\
+    CVC4              & 4863  & 113   & 10258 & 100679 \\
+    MapleSTP          &       & 0     &       &        \\
+    {[}MathSAT{]}     & 21    & 28745 & 11    & 5      \\
+    MinkeyRink        &       & 13    & 27    & 16     \\
     OpenSMT2          & 0     & 0     & 0     & 0      \\
-    ProB              &       & 1     &       &        \\
+    ProB              &       & 2     &       &        \\
     Q3B               &       & 0     & 89    & 0      \\
-    raSAT             & 3     & 14    &       &        \\
+    raSAT             & 0     & 14    &       &        \\
     Redlog            &       &       & 4     &        \\
-    SMT-RAT           & 13    & 0     & 85    & 2      \\
-    SMTInterpol       & 2     & 2     & 5     & 4      \\
+    SMT-RAT           & 12    & 0     & 85    & 2      \\
+    SMTInterpol       & 1     & 1     & 5     & 4      \\
     SPASS-SATT        &       &       &       & 34     \\
-    STP               & 4     & 2     & 4     & 5      \\
+    STP               & 4     & 1     & 4     & 5      \\
     toysmt            &       & 0     &       &        \\
-    Vampire           &       & 139   & 753   & 652    \\
-    veriT             & 5     & 21    & 55    & 57     \\
+    Vampire           &       & 130   & 753   & 652    \\
+    veriT             & 7     & 19    & 55    & 57     \\
     XSat              &       &       & 0     &        \\
-    Yices2            & 88    & 146   & 2379  & 1535   \\
-    Z3                & 6139  & 242   & 40992 & 888    \\
-    \midrule
-    Total             & 11258 & 29486 & 55175 & 104527 \\
+    Yices2            & 86    & 128   & 2379  & 1535   \\
+    Z3                & 6118  & 244   & 40992 & 888    \\
+    \midrule
+    Total             & 11224 & 29442 & 55175 & 104527 \\
+    \bottomrule
+  \end{tabular}
+\end{table}
+
+\paragraph{Use of parallelism.}
+
+It is evident both from the division rankings
+(Section~\ref{sec:division-rankings}) and the competition-wide ranking
+(Section~\ref{sec:floc}) that there is very little difference between
+sequential and parallel performance.  Even though parallel solvers may
+use up to four times as much CPU time, sequential and parallel
+division winners are most often identical, as are sequential and
+parallel scores for the competition-wide ranking.
+
+%TODO: discuss whether this can be attributed to the hardness
+%distribution of benchmarks (cf. VBS plot)
+
+In Table~\ref{table:parallelism}, we report the quotient of CPU time
+over wall-clock time (summed up over all main-track benchmarks) for
+each solver, as well as for all solvers combined.  When there were
+multiple versions of a solver (such as a sequential and a parallel
+version), only the highest value is shown.  We note that this quotient
+is close to~1 for most solvers: only about 4--8 main-track solvers
+each year were participating with a version that made use of
+parallelism.
+
+\begin{table}
+  \caption{Quotient of CPU time over wall-clock time for each
+    main-track solver (by year).  Values below~1.1 are shown in gray.}
+  \label{table:parallelism}
+  \centering
+  \begin{tabular}{lrrrr}
+    \toprule
+    Solver & 2015 & 2016 & 2017 & 2018 \\
+    \midrule
+    ABC               &     & \textcolor{gray}{1.0} &     &     \\
+    Alt-Ergo          &     &     &     & 3.0 \\
+    AProVE            & \textcolor{gray}{1.0} & \textcolor{gray}{1.0} & \textcolor{gray}{0.8} & \textcolor{gray}{0.8} \\
+    Boolector         & \textcolor{gray}{1.0} & \textcolor{gray}{1.0} & 1.1 & 1.3 \\
+    COLIBRI           &     &     & \textcolor{gray}{1.0} & \textcolor{gray}{1.0} \\
+    Ctrl-Ergo         &     &     &     & 4.0 \\
+    CVC3              & \textcolor{gray}{1.0} &     &     &     \\
+    CVC4              & 1.2 & 1.1 & 1.1 & \textcolor{gray}{1.0} \\
+    MapleSTP          &     & 3.8 &     &     \\
+    {[}MathSAT{]}     & \textcolor{gray}{1.0} & \textcolor{gray}{1.0} & \textcolor{gray}{1.0} & \textcolor{gray}{1.0} \\
+    MinkeyRink        &     & 3.6 & 2.0 & 3.9 \\
+    OpenSMT2          & 3.7 & \textcolor{gray}{1.0} & \textcolor{gray}{1.0} & \textcolor{gray}{1.0} \\
+    ProB              &     & \textcolor{gray}{1.0} &     &     \\
+    Q3B               &     & 2.9 & 2.9 & 3.0 \\
+    raSAT             & \textcolor{gray}{1.0} & 2.0 &     &     \\
+    Redlog            &     &     & \textcolor{gray}{1.0} &     \\
+    SMT-RAT           & 1.3 & \textcolor{gray}{1.0} & \textcolor{gray}{1.0} & \textcolor{gray}{1.0} \\
+    SMTInterpol       & 1.4 & 1.1 & 1.1 & 1.1 \\
+    SPASS-SATT        &     &     &     & \textcolor{gray}{1.0} \\
+    STP               & \textcolor{gray}{1.0} & 3.6 & 3.8 & 3.8 \\
+    toysmt            &     & \textcolor{gray}{1.0} &     &     \\
+    Vampire           &     & 3.4 & 3.9 & 4.0 \\
+    veriT             & \textcolor{gray}{1.0} & \textcolor{gray}{1.0} & \textcolor{gray}{1.0} & \textcolor{gray}{1.0} \\
+    XSat              &     &     & 1.8 &     \\
+    Yices2            & \textcolor{gray}{1.0} & \textcolor{gray}{1.0} & \textcolor{gray}{1.0} & \textcolor{gray}{1.0} \\
+    Z3                & \textcolor{gray}{1.0} & \textcolor{gray}{1.0} & \textcolor{gray}{1.0} & \textcolor{gray}{1.0} \\
+    \midrule
+    All solvers       & 1.0 & 1.3 & 1.3 & 1.3 \\
     \bottomrule

### 2019-03-14 2018/report/SMT-COMP.tex
Add VBS cactus plots.

@@
 
+%\usepackage{showframe}   % debug
+
 \usepackage{pifont}
@@
 \usepackage{tikz}
+\usepackage{subcaption}
 
@@
 
+\begin{figure}
+  \begin{subfigure}[t]{0.5\textwidth}
+    \scalebox{.35}{\includegraphics{plot/pdf/cactus_plot-Virtual_Best_Solver_(VBS)_2014-2015.pdf}}
+    \caption{2014 vs.~2015}
+  \end{subfigure}
+  \begin{subfigure}[t]{0.5\textwidth}
+    \scalebox{.35}{\includegraphics{plot/pdf/cactus_plot-Virtual_Best_Solver_(VBS)_2015-2016.pdf}}
+    \caption{2015 vs.~2016}
+  \end{subfigure}
+  \\[4ex]
+  \begin{subfigure}[t]{0.5\textwidth}
+    \scalebox{.35}{\includegraphics{plot/pdf/cactus_plot-Virtual_Best_Solver_(VBS)_2016-2017.pdf}}
+    \caption{2016 vs.~2017}
+  \end{subfigure}
+  \begin{subfigure}[t]{0.5\textwidth}
+    \scalebox{.35}{\includegraphics{plot/pdf/cactus_plot-Virtual_Best_Solver_(VBS)_2017-2018.pdf}}
+    \caption{2017 vs.~2018}
+  \end{subfigure}
+  \caption{Virtual Best Solver (VBS) on common benchmarks of all
+  logics in the Main Track.}
+\end{figure}
+
 A contentious issue with this ranking has been the scoring of

### 2019-03-14 2018/report/plot/cactus_plot.r

@@ -4,7 +4,10 @@ if(!dir.exists("pdf")) dir.create("pdf")
 args <- commandArgs(trailingOnly = TRUE)
 
 min_x=as.integer(args[1])
-fname_pdf=paste("pdf/cactus_plot-",args[2],".pdf",sep="")
+
+plot_title=args[2]
+fname=gsub(' ','_',plot_title,fixed=TRUE)
+fname_pdf=paste("pdf/cactus_plot-",fname,".pdf",sep="")
 pdf(fname_pdf,width=9)
 par(cex=1.2)
 
@@ -83,5 +86,5 @@ axis(2, at=ticks, labels=labels)
 
 title(ylab="Time [s]",line=4)
 title(xlab="# Benchmarks",line=3)
-title(args[2],outer=TRUE,line=-1,font.main=2)
+title(plot_title,outer=TRUE,line=-1,font.main=2)
 legend(x="topleft",xlegend,col=xcol,bty="n",lwd=lwidth,lty=ltypes,text.font=1)

### 2019-03-14 2018/report/SMT-COMP.tex
Consistent track names.

@@
 %%   competition results.
-%% \item The unsat-core track that was introduced in SMT-COMP 2012, but
+%% \item The Unsat-Core track that was introduced in SMT-COMP 2012, but
 %%   discontinued in 2013-2015 (partly because of the competition's move
@@
 %%   overemphasizes large divisions.
-%% \item The unsat-core track, which was re-introduced in 2016, is no
+%% \item The Unsat-Core track, which was re-introduced in 2016, is no
 %%   longer experimental.  Its divisions will be considered competitive
@@
 %%   benchmarks with unknown status.
-%% \item In the unsat-core track, the unsatisfiability check for the
+%% \item In the Unsat-Core track, the unsatisfiability check for the
 %%   returned core will be based on a simple majority vote.  The case
@@
 %%   treated specially.  \emph{Rationale:} This allows to simplify the
-%%   post-processing of unsat-core track results considerably.
+%%   post-processing of Unsat-Core track results considerably.
 %% \item In 2017, the competition featured experimental divisions for
@@
 inception in 2005, features non-incremental benchmarks.  The
-\emph{application track}, which has been part of the competition since
+\emph{Application track}, which has been part of the competition since
 2011~\cite{BDdMOS13}, features incremental benchmarks.  These
@@
 next benchmark command (to prevent look-ahead behavior).  The
-\emph{unsat-core track} uses main-track benchmarks that are known to
+\emph{Unsat-Core track} uses Main-track benchmarks that are known to
 be unsatisfiable, and solvers are evaluated on their ability to find
 small unsatisfiable cores (i.e., a small but still unsatisfiable
-subset of the benchmark's assertions).  The unsat-core track had first
+subset of the benchmark's assertions).  The Unsat-Core track had first
 been part of the competition in 2012~\cite{CGBD12}, but was then
@@
     Application track &  14 & 14 & 16 & 21 \\
-    Unsat-core track  &  -- & 40 & 41 & 44 \\
+    Unsat-Core track  &  -- & 40 & 41 & 44 \\
     \bottomrule
@@
 since~2016 uses a scoring method that assigns a weight to each
-main-track benchmark in order to de-emphasize large benchmark
+Main-track benchmark in order to de-emphasize large benchmark
 families~\cite{rules18}.
@@
 separately.  Since 2017, all non-incremental benchmarks are eligible
-for the competition's main track regardless of status, and they
+for the competition's Main track regardless of status, and they
 directly affect the competition results.  Solver responses for such
@@
 For incremental benchmarks, the situation is different: an incremental
-benchmark is ineligible for the application track if its first {\tt
+benchmark is ineligible for the Application track if its first {\tt
   check-sat} command has unknown status.  Otherwise, the prefix of the
@@
 status is eligible.  The main reason for this difference is that the
-competition tools for the application track (in particular, the trace
+competition tools for the Application track (in particular, the trace
 executor) have not been adapted yet to support {\tt check-sat}
@@
 \begin{table}
-  \caption{Number of benchmarks used in the main track (by division)}
+  \caption{Number of benchmarks used in the Main track (by division)}
   \label{table:benchmarks-main-track}
@@
 \begin{table}
-  \caption{Number of benchmarks used in the application track (by
+  \caption{Number of benchmarks used in the Application track (by
     division)}
@@
 \begin{table}
-  \caption{Number of benchmarks used in the unsat-core track (by
+  \caption{Number of benchmarks used in the Unsat-Core track (by
     division)}
@@
 were evaluated with a wall-clock time limit of 10~minutes.  In~2017,
-when these benchmarks had become eligible for the main track,
-main-track job pairs were first run with a time limit of 10~minutes.
+when these benchmarks had become eligible for the Main track,
+Main-track job pairs were first run with a time limit of 10~minutes.
 When it became apparent to the organizers that there were sufficient
@@
     Application track & 40 & 40 & 40\phantom{$^{1.}$}      & 40 \\
-    Unsat-core track  & -- & 40 & 40\phantom{$^{1.}$}      & 40 \\
+    Unsat-Core track  & -- & 40 & 40\phantom{$^{1.}$}      & 40 \\
     \bottomrule
@@
 deadline; in 2016, the CVC4 team did not enter their solver into the
-application track; and in 2018, an experimental version of CVC4 as
+Application track; and in 2018, an experimental version of CVC4 as
 well as the OpenSMT2 solver were submitted after the deadline.  These
@@
     Application track & 10 &               [+3] &  8 & [+3] &  4 & [+2] &  4 & [+2] \\
-    Unsat-core track  & \multicolumn{2}{c}{---} &  1 & [+4] &  2 & [+2] &  3 & [+2] \\
+    Unsat-Core track  & \multicolumn{2}{c}{---} &  1 & [+4] &  2 & [+2] &  3 & [+2] \\
     \midrule
@@
 responses; third, on the wall-clock and CPU time that the solver
-process consumed.  For the unsat-core track (which uses unsatisfiable
+process consumed.  For the Unsat-Core track (which uses unsatisfiable
 benchmarks only), the reduction in the size of the unsatisfiable core
@@
 
-As discussed in Section~\ref{sec:benchmarks}, main-track benchmarks
+As discussed in Section~\ref{sec:benchmarks}, Main-track benchmarks
 with unknown status are removed from the competition results if two
@@
 is a wall-clock limit.  Thus, solvers that take advantage of
-parallelism might use up to~$4T$ CPU time.  For the main track and the
-unsat-core track, the competition reports parallel and sequential
+parallelism might use up to~$4T$ CPU time.  For the Main track and the
+Unsat-Core track, the competition reports parallel and sequential
 performance separately.  The latter is determined by imposing a
-(virtual) CPU time limit of~$T$.  For the application track, only
+(virtual) CPU time limit of~$T$.  For the Application track, only
 parallel performance is reported (because response times to individual
@@
 competition organizers decided to award these to the winner of the
-main track's QF\_BV division (which had historically been the logic
+Main track's QF\_BV division (which had historically been the logic
 with the largest number of solver submissions and job pairs), as well
-as to the two best main-track solvers according to a competition-wide
+as to the two best Main-track solvers according to a competition-wide
 ranking that had been instituted especially for this
@@
 
-The competition-wide ranking for the main track was retained and
+The competition-wide ranking for the Main track was retained and
 refined after~2014.  Table~\ref{table:competition-wide-ranking} shows
@@
 \begin{table}
-  \caption{Competition-wide ranking for the main track: best solvers (by year)}
+  \caption{Competition-wide ranking for the Main track: best solvers (by year)}
   \label{table:competition-wide-ranking}
@@
   \caption{Virtual Best Solver (VBS) on common benchmarks of all
-  logics in the Main Track.}
+  logics in the Main track.}
 \end{figure}
@@
 response causes a solver to be ranked below all correct solvers for
-that division.  But the competition's main track consists of many
+that division.  But the competition's Main track consists of many
 independent divisions.  To balance the strong interest in correct
@@
 \begin{itemize}
-\item The best three main-track solvers according to the
+\item The best three Main-track solvers according to the
   competition-wide ranking (CVC4, Yices2, and SMTInterpol; see
   Table~\ref{table:competition-wide-ranking}),
-\item the solvers that won the QF\_BV division in the main track
+\item the solvers that won the QF\_BV division in the Main track
   (Boolector and MinkeyRink; see Table~\ref{tab:winners-main}),
 \item the solver that won the most competitive divisions in the
-  application track (Yices2),
+  Application track (Yices2),
 \item the solver that won the most competitive divisions in the
-  unsat-core track (Yices2).
+  Unsat-Core track (Yices2).
 \end{itemize}
 
-In comparison to the competition-wide ranking for the main track, the
-metric used for the application and unsat-core track---simply counting
+In comparison to the competition-wide ranking for the Main track, the
+metric used for the application and Unsat-Core track---simply counting
 the number of competitive divisions that a solver has won---was rather
@@
 refine this to use a ranking scheme that is more similar to the
-main-track ranking, by weighing divisions according to their relative
+Main-track ranking, by weighing divisions according to their relative
 importance, and also by rewarding good performance from solvers other
-than division winners.  A difficulty in adapting the main-track
-ranking for the other tracks is that each main-track benchmark is
+than division winners.  A difficulty in adapting the Main-track
+ranking for the other tracks is that each Main-track benchmark is
 worth one point (before benchmark weights are applied) if solved
-correctly, while benchmarks in the application and unsat-core track
+correctly, while benchmarks in the application and Unsat-Core track
 are worth widely varying numbers of points.  Moreover, in the
-unsat-core track, the size of the smallest unsatisfiable core---and
+Unsat-Core track, the size of the smallest unsatisfiable core---and
 hence the number of points attainable on any given benchmark---may not
@@
 Table~\ref{table:unique-solutions} shows the number of uniquely solved
-benchmarks for each main-track solver from 2015--2018.  (Multiple
+benchmarks for each Main-track solver from 2015--2018.  (Multiple
 versions of a solver are consolidated in this table, and answers that
@@
 \begin{table}
-  \caption{Number of main-track benchmarks uniquely solved by each
+  \caption{Number of Main-track benchmarks uniquely solved by each
     solver (by year)}
@@
 In Table~\ref{table:parallelism}, we report the quotient of CPU time
-over wall-clock time (summed up over all main-track benchmarks) for
+over wall-clock time (summed up over all Main-track benchmarks) for
 each solver, as well as for all solvers combined.  When there were
@@
 version), only the highest value is shown.  We note that this quotient
-is close to~1 for most solvers: only about 4--8 main-track solvers
+is close to~1 for most solvers: only about 4--8 Main-track solvers
 each year were participating with a version that made use of
@@
   \caption{Quotient of CPU time over wall-clock time for each
-    main-track solver (by year).  Values below~1.1 are shown in gray.}
+    Main-track solver (by year).  Values below~1.1 are shown in gray.}
   \label{table:parallelism}
@@
 
-Since the re-introduction of the unsat-core track in~2016, the
+Since the re-introduction of the Unsat-Core track in~2016, the
 competition again has three separate tracks.  This, together with new
@@
 \item the inclusion of {\tt check-sat} commands with unknown status in
-  the application track, and
+  the Application track, and
 \item the definition of competition-wide rankings for the application
-  and unsat-core track.
+  and Unsat-Core track.
 \end{itemize}

### 2019-03-14 2018/report/SMT-COMP.tex
Moved figure.

@@
 
-\begin{figure}
-  \begin{subfigure}[t]{0.5\textwidth}
-    \scalebox{.35}{\includegraphics{plot/pdf/cactus_plot-Virtual_Best_Solver_(VBS)_2014-2015.pdf}}
-    \caption{2014 vs.~2015}
-  \end{subfigure}
-  \begin{subfigure}[t]{0.5\textwidth}
-    \scalebox{.35}{\includegraphics{plot/pdf/cactus_plot-Virtual_Best_Solver_(VBS)_2015-2016.pdf}}
-    \caption{2015 vs.~2016}
-  \end{subfigure}
-  \\[4ex]
-  \begin{subfigure}[t]{0.5\textwidth}
-    \scalebox{.35}{\includegraphics{plot/pdf/cactus_plot-Virtual_Best_Solver_(VBS)_2016-2017.pdf}}
-    \caption{2016 vs.~2017}
-  \end{subfigure}
-  \begin{subfigure}[t]{0.5\textwidth}
-    \scalebox{.35}{\includegraphics{plot/pdf/cactus_plot-Virtual_Best_Solver_(VBS)_2017-2018.pdf}}
-    \caption{2017 vs.~2018}
-  \end{subfigure}
-  \caption{Virtual Best Solver (VBS) on common benchmarks of all
-  logics in the Main track.}
-\end{figure}
-
 A contentious issue with this ranking has been the scoring of
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{figure}
+  \begin{subfigure}[t]{0.5\textwidth}
+    \scalebox{.35}{\includegraphics{%
+        plot/pdf/cactus_plot-Virtual_Best_Solver_(VBS)_2014-2015.pdf}}
+    \caption{2014 vs.~2015}
+  \end{subfigure}
+  \begin{subfigure}[t]{0.5\textwidth}
+    \scalebox{.35}{\includegraphics{%
+      plot/pdf/cactus_plot-Virtual_Best_Solver_(VBS)_2015-2016.pdf}}
+    \caption{2015 vs.~2016}
+  \end{subfigure}
+  \\[4ex]
+  \begin{subfigure}[t]{0.5\textwidth}
+    \scalebox{.35}{\includegraphics{%
+      plot/pdf/cactus_plot-Virtual_Best_Solver_(VBS)_2016-2017.pdf}}
+    \caption{2016 vs.~2017}
+  \end{subfigure}
+  \begin{subfigure}[t]{0.5\textwidth}
+    \scalebox{.35}{\includegraphics{%
+    plot/pdf/cactus_plot-Virtual_Best_Solver_(VBS)_2017-2018.pdf}}
+    \caption{2017 vs.~2018}
+  \end{subfigure}
+  \caption{Virtual Best Solver (VBS) on common benchmarks of all
+  logics in the Main track.}
+\end{figure}
 

### 2019-03-15 2018/report/SMT-COMP.tex
Progress analysis.

@@
   logics in the Main track.}
+  \label{fig:progress}
 \end{figure}
@@
 
-%TODO
+The SMT Competition consists of several tracks with a multitude of divisions
+per track.
+Not all participating solvers enter all tracks, and the majority of
+participants participates only in a handful of divisions.
+To give a measure of overall progress in solver performance we
+use the notion of \emph{virtual best solver} (VBS) over all divisions of the
+Main track.
+We determine the VBS as the best wall-clock performance per (correctly solved)
+instance with the time limit of 1200s used in the competitions 2017 and 2018.
+Figure~\ref{fig:progress} visualizes VBS performance on common benchmarks over
+pairs of consecutive years from 2014 to 2018 as a cactus plot.
+It shows the wall-clock solving time per instance over all instances, sorted by
+solving time.
+
+Between 2014 (67426 benchmarks) and 2015 (154238 benchmarks),
+the number of common benchmarks is 67070;
+between 2015 and 2016 (154424 benchmarks) it is 154238;
+between 2016 and 2017 (238758 benchmarks) it is 145236;
+and between 2017 and 2018 (333241 benchmarks) it is 226429.
+The number of solved instances on these sets of common benchmarks
+increased from 2014 to 2015 by 0.1\%, from 2016 to 2017 by 3.9\%,
+and from 2017 to 2018 by 0.3\%.
+Interestingly, it decreased from 2015 to 2016 by 3.5\%.
+This is mainly due to the fact that in 2015, more than 5600 benchmarks of
+division QF\_FP where solved by one of the two participating configurations of
+Z3 that no one else could solve, and in 2016 Z3 did not participate in this
+division.
 

### 2019-03-15 2018/report/table-winners-main-new.tex
New layout for winners table (currently only main).

\begin{table}
\caption{Best main-track solvers (by division)}
\label{tab:winners-main}
\centering
\scalebox{.83}{%
\renewcommand{\arraystretch}{1.01}%
\begin{tabular}{r@{\hskip 3em}c@{\hskip 2em}c@{\hskip 2em}c@{\hskip 2em}c}
\toprule
Division     & 2015            & 2016            & 2017                   & 2018                  \\
\hline \hline
ABVFP        &                 &                 &                        & {CVC4}                \\
ALIA         & {{[}Z3{]}}      & {{[}Z3{]}}      & {{[}Z3{]}}             & {{[}Z3{]}}            \\
AUFBVDTLIA   &                 &                 & {CVC4}                 & {CVC4}                \\
AUFDTLIA     &                 &                 & {CVC4}                 & {CVC4}                \\
AUFLIA       & {CVC4}          & {CVC4}          & {CVC4}                 & {CVC4}                \\
AUFLIRA      & {{[}Z3{]}}      & {{[}Z3{]}}      & {{[}Z3{]}}             & {{[}Z3{]}}            \\
AUFNIRA      & {CVC4}          & {Vampire}       & {Vampire}              & {CVC4}                \\
BV           & {{[}Z3{]}}      & {Q3B}           & {{[}Z3{]}}             & {CVC4}                \\
BVFP         &                 &                 &                        & {CVC4}                \\
FP           &                 &                 &                        & {CVC4}                \\
LIA          & {CVC4}          & {CVC4}          & {{[}Z3{]}}             & {{[}Z3{]}}            \\
LRA          & {CVC4}          & {CVC4}          & {{[}Z3{]}}             & {{[}Z3{]}}            \\
NIA          & {{[}Z3{]}}      & {{[}Z3{]}}      & {{[}Z3{]}}             & {{[}Z3{]}}            \\
NRA          & {CVC4}          & {Vampire}       & {Redlog}               & {{[}Z3{]}/Vampire}    \\
QF\_ABV      & {Boolector}     & {Boolector}     & {Boolector}            & {Boolector}           \\
QF\_ABVFP    &                 &                 & {---}                  & {CVC4}                \\
QF\_ALIA     & {Yices2}        & {Yices2}        & {Yices2}               & {Yices2}              \\
QF\_ANIA     & {{[}Z3{]}}      & {CVC4}          & {CVC4}                 & {{[}Z3{]}}            \\
QF\_AUFBV    & {{[}MathSAT{]}} & {{[}MathSAT{]}} & {{[}MathSAT{]}}        & {CVC4}                \\
QF\_AUFLIA   & {Yices2}        & {Yices2}        & {Yices2}               & {Yices2}              \\
QF\_AUFNIA   & {CVC4}          & {CVC4}          & {{[}Z3{]}}             & {{[}Z3{]}}            \\
QF\_AX       & {Yices2}        & {Yices2}        & {Yices2}               & {Yices2}              \\
QF\_BV       & {Boolector}     & {Boolector}     & {Boolector/MinkeyRink} & {Boolector/MinkeyRink}\\
QF\_BVFP     & {Z3}            & {{[}Z3{]}}      & {{[}Z3{]}}             & {CVC4}                \\
QF\_DT       &                 &                 & {CVC4}                 & {CVC4}                \\
QF\_FP       & {Z3}            & {{[}MathSAT{]}} & {{[}Z3{]}}             & {COLIBRI}             \\
QF\_IDL      & {{[}Z3{]}}      & {{[}Z3{]}}      & {Yices2}               & {Yices2}              \\
QF\_LIA      & {{[}MathSAT{]}} & {{[}MathSAT{]}} & {{[}MathSAT{]}}        & {SPASS-SATT}          \\
QF\_LIRA     & {Yices2}        & {Yices2}        & {{[}Z3{]}}             & {{[}Z3{]}}            \\
QF\_LRA      &  {CVC4}         & {CVC4}          & {CVC4}                 & {CVC4}                \\
QF\_NIA      & {{[}Z3{]}}      & {{[}Z3{]}}      & {CVC4}                 & {CVC4}                \\
QF\_NIRA     & {CVC4}          & {CVC4}          & {SMT-RAT}              & {SMT-RAT}             \\
QF\_NRA      & {{[}Z3{]}}      & {{[}Z3{]}}      & {Yices2}               & {{[}Z3{]}}            \\
QF\_RDL      & {Yices2}        & {Yices2}        & {Yices2}               & {Yices2}              \\
QF\_SLIA     &                 &                 &                        & {CVC4}                \\
QF\_UF       & {Yices2}        & {Yices2}        & {Yices2}               & {Yices2}              \\
QF\_UFBV     & {Boolector}     & {Boolector}     & {Boolector}            & {Boolector}           \\
QF\_UFIDL    & {Yices2}        & {Yices2}        & {Yices2}               & {Yices2}              \\
QF\_UFLIA    & {{[}Z3{]}}      & {{[}Z3{]}}      & {Yices2}               & {Yices2}              \\
QF\_UFLRA    & {Yices2}        & {Yices2}        & {Yices2}               & {Yices2}              \\
QF\_UFNIA    & {CVC4}          & {Yices2/CVC4}   & {Yices2}               & {Yices2}              \\
QF\_UFNRA    & {{[}Z3{]}}      & {Yices2}        & {{[}Z3{]}}             & {Yices2}              \\
UF           & {CVC4}          & {CVC4}          & {Vampire}              & {CVC4/Vampire}        \\
UFBV         & {{[}Z3{]}}      & {{[}Z3{]}}      & {{[}Z3{]}}             & {{[}Z3{]}}            \\
UFDT         &                 &                 & {CVC4}                 & {CVC4}                \\
UFDTLIA      &                 &                 & {Vampire}              & {CVC4}                \\
UFIDL        & {{[}Z3{]}}      & {CVC4}          & {CVC4}                 & {{[}Z3{]}}            \\
UFLIA        & {CVC4}          & {CVC4}          & {CVC4}                 & {CVC4}                \\
UFLRA        & {CVC3}          & {{[}Z3{]}}      & {{[}Z3{]}}             & {{[}Z3{]}}            \\
UFNIA        & {CVC4}          & {Vampire}       & {Vampire}              & {{[}Z3{]}/Vampire}    \\
\bottomrule
\end{tabular}}
\end{table}

### 2019-03-16 2018/report/table-winners-main-new.tex
Beautify layout of main track winners table.

@@
 \renewcommand{\arraystretch}{1.01}%
-\begin{tabular}{r@{\hskip 3em}c@{\hskip 2em}c@{\hskip 2em}c@{\hskip 2em}c}
+  \begin{tabular}{r@{\hskip 3em}>{\columncolor[gray]{.95}[.5em][1em]}c@{\hskip 2em}>{\columncolor[gray]{.95}[1em][1em]}c@{\hskip 2em}>{\columncolor[gray]{.95}[1em][1em]}c@{\hskip 2em}>{\columncolor[gray]{.95}[1em][0.5em]}c}
 \toprule
+\rc
 Division         &  2015           &  2016           &  2017                  &  2018                 \\
 \hline \hline
-ABVFP        &                 &                 &                        & {CVC4}                \\
-ALIA         & {{[}Z3{]}}      & {{[}Z3{]}}      & {{[}Z3{]}}             & {{[}Z3{]}}            \\
-AUFBVDTLIA   &                 &                 & {CVC4}                 & {CVC4}                \\
-AUFDTLIA     &                 &                 & {CVC4}                 & {CVC4}                \\
-AUFLIA       & {CVC4}          & {CVC4}          & {CVC4}                 & {CVC4}                \\
-AUFLIRA      & {{[}Z3{]}}      & {{[}Z3{]}}      & {{[}Z3{]}}             & {{[}Z3{]}}            \\
-AUFNIRA      & {CVC4}          & {Vampire}       & {Vampire}              & {CVC4}                \\
-BV           & {{[}Z3{]}}      & {Q3B}           & {{[}Z3{]}}             & {CVC4}                \\
-BVFP         &                 &                 &                        & {CVC4}                \\
-FP           &                 &                 &                        & {CVC4}                \\
-LIA          & {CVC4}          & {CVC4}          & {{[}Z3{]}}             & {{[}Z3{]}}            \\
-LRA          & {CVC4}          & {CVC4}          & {{[}Z3{]}}             & {{[}Z3{]}}            \\
-NIA          & {{[}Z3{]}}      & {{[}Z3{]}}      & {{[}Z3{]}}             & {{[}Z3{]}}            \\
-NRA          & {CVC4}          & {Vampire}       & {Redlog}               & {{[}Z3{]}/Vampire}    \\
-QF\_ABV      & {Boolector}     & {Boolector}     & {Boolector}            & {Boolector}           \\
-QF\_ABVFP    &                 &                 & {---}                  & {CVC4}                \\
-QF\_ALIA     & {Yices2}        & {Yices2}        & {Yices2}               & {Yices2}              \\
-QF\_ANIA     & {{[}Z3{]}}      & {CVC4}          & {CVC4}                 & {{[}Z3{]}}            \\
-QF\_AUFBV    & {{[}MathSAT{]}} & {{[}MathSAT{]}} & {{[}MathSAT{]}}        & {CVC4}                \\
-QF\_AUFLIA   & {Yices2}        & {Yices2}        & {Yices2}               & {Yices2}              \\
-QF\_AUFNIA   & {CVC4}          & {CVC4}          & {{[}Z3{]}}             & {{[}Z3{]}}            \\
-QF\_AX       & {Yices2}        & {Yices2}        & {Yices2}               & {Yices2}              \\
-QF\_BV       & {Boolector}     & {Boolector}     & {Boolector/MinkeyRink} & {Boolector/MinkeyRink}\\
-QF\_BVFP     & {Z3}            & {{[}Z3{]}}      & {{[}Z3{]}}             & {CVC4}                \\
-QF\_DT       &                 &                 & {CVC4}                 & {CVC4}                \\
-QF\_FP       & {Z3}            & {{[}MathSAT{]}} & {{[}Z3{]}}             & {COLIBRI}             \\
-QF\_IDL      & {{[}Z3{]}}      & {{[}Z3{]}}      & {Yices2}               & {Yices2}              \\
-QF\_LIA      & {{[}MathSAT{]}} & {{[}MathSAT{]}} & {{[}MathSAT{]}}        & {SPASS-SATT}          \\
-QF\_LIRA     & {Yices2}        & {Yices2}        & {{[}Z3{]}}             & {{[}Z3{]}}            \\
-QF\_LRA      &  {CVC4}         & {CVC4}          & {CVC4}                 & {CVC4}                \\
-QF\_NIA      & {{[}Z3{]}}      & {{[}Z3{]}}      & {CVC4}                 & {CVC4}                \\
-QF\_NIRA     & {CVC4}          & {CVC4}          & {SMT-RAT}              & {SMT-RAT}             \\
-QF\_NRA      & {{[}Z3{]}}      & {{[}Z3{]}}      & {Yices2}               & {{[}Z3{]}}            \\
-QF\_RDL      & {Yices2}        & {Yices2}        & {Yices2}               & {Yices2}              \\
-QF\_SLIA     &                 &                 &                        & {CVC4}                \\
-QF\_UF       & {Yices2}        & {Yices2}        & {Yices2}               & {Yices2}              \\
-QF\_UFBV     & {Boolector}     & {Boolector}     & {Boolector}            & {Boolector}           \\
-QF\_UFIDL    & {Yices2}        & {Yices2}        & {Yices2}               & {Yices2}              \\
-QF\_UFLIA    & {{[}Z3{]}}      & {{[}Z3{]}}      & {Yices2}               & {Yices2}              \\
-QF\_UFLRA    & {Yices2}        & {Yices2}        & {Yices2}               & {Yices2}              \\
-QF\_UFNIA    & {CVC4}          & {Yices2/CVC4}   & {Yices2}               & {Yices2}              \\
-QF\_UFNRA    & {{[}Z3{]}}      & {Yices2}        & {{[}Z3{]}}             & {Yices2}              \\
-UF           & {CVC4}          & {CVC4}          & {Vampire}              & {CVC4/Vampire}        \\
-UFBV         & {{[}Z3{]}}      & {{[}Z3{]}}      & {{[}Z3{]}}             & {{[}Z3{]}}            \\
-UFDT         &                 &                 & {CVC4}                 & {CVC4}                \\
-UFDTLIA      &                 &                 & {Vampire}              & {CVC4}                \\
-UFIDL        & {{[}Z3{]}}      & {CVC4}          & {CVC4}                 & {{[}Z3{]}}            \\
-UFLIA        & {CVC4}          & {CVC4}          & {CVC4}                 & {CVC4}                \\
-UFLRA        & {CVC3}          & {{[}Z3{]}}      & {{[}Z3{]}}             & {{[}Z3{]}}            \\
-UFNIA        & {CVC4}          & {Vampire}       & {Vampire}              & {{[}Z3{]}/Vampire}    \\
+\cc ABVFP        & \cc             & \cc             & \cc                    & \cc {CVC4}            \\
+\cc ALIA         & {{[}Z3{]}}      & {{[}Z3{]}}      & {{[}Z3{]}}             & {{[}Z3{]}}            \\
+\drc
+\cc AUFBVDTLIA   & \cc             & \cc             & {CVC4}                 & {CVC4}                \\
+\cc AUFDTLIA     & \cc             & \cc             & {CVC4}                 & {CVC4}                \\
+\drc
+\cc AUFLIA       & {CVC4}          & {CVC4}          & {CVC4}                 & {CVC4}                \\
+\cc AUFLIRA      & {{[}Z3{]}}      & {{[}Z3{]}}      & {{[}Z3{]}}             & {{[}Z3{]}}            \\
+\drc
+\cc AUFNIRA      & \cc {CVC4}      & {Vampire}       & {Vampire}              &\cc  {CVC4}            \\
+\rc
+\cc BV           &  {{[}Z3{]}}     & {Q3B}           & {{[}Z3{]}}             &  {CVC4}               \\
+\cc BVFP         & \cc             & \cc             & \cc                    & \cc {CVC4}            \\
+\cc FP           & \cc             & \cc             & \cc                    & \cc {CVC4}            \\
+\cc LIA          & \dcc {CVC4}     & \dcc{CVC4}      & {{[}Z3{]}}             & {{[}Z3{]}}            \\
+\cc LRA          & {CVC4}          & {CVC4}          & \dcc {{[}Z3{]}}        & \dcc {{[}Z3{]}}       \\
+\cc NIA          & {{[}Z3{]}}      & {{[}Z3{]}}      & {{[}Z3{]}}             & {{[}Z3{]}}            \\
+\rc
+\cc NRA          & {CVC4}          & {Vampire}       & {Redlog}               & {{[}Z3{]}/Vampire}    \\
+\cc QF\_ABV      & {Boolector}     & {Boolector}     & {Boolector}            & {Boolector}           \\
+\cc QF\_ABVFP    & \cc             &  \cc            & \cc {---}              & \cc {CVC4}            \\
+\cc QF\_ALIA     & {Yices2}        & {Yices2}        & {Yices2}               & {Yices2}              \\
+\drc
+\cc QF\_ANIA     & \cc {{[}Z3{]}}  & {CVC4}          & {CVC4}                 & {{[}Z3{]}}            \\
+\cc QF\_AUFBV    & {{[}MathSAT{]}} & {{[}MathSAT{]}} & {{[}MathSAT{]}}        & \cc {CVC4}            \\
+\drc
+\cc QF\_AUFLIA   & {Yices2}        & {Yices2}        & {Yices2}               & {Yices2}              \\
+\cc QF\_AUFNIA   & {CVC4}          & {CVC4}          & \dcc {{[}Z3{]}}        & \dcc {{[}Z3{]}}       \\
+\cc QF\_AX       & {Yices2}        & {Yices2}        & {Yices2}               & {Yices2}              \\
+\drc
+\cc QF\_BV       & {Boolector}     & {Boolector}     & {Boolector/MinkeyRink} & {Boolector/MinkeyRink}\\
+\cc QF\_BVFP     & {Z3}            & {{[}Z3{]}}      & {{[}Z3{]}}             & \cc {CVC4}            \\
+\drc
+\cc QF\_DT       & \cc             & \cc             & {CVC4}                 & {CVC4}                \\
+\rc
+\cc QF\_FP       & {Z3}            & {{[}MathSAT{]}} & {{[}Z3{]}}             & {COLIBRI}             \\
+\cc QF\_IDL      & \dcc {{[}Z3{]}} & \dcc {{[}Z3{]}} & {Yices2}               & {Yices2}              \\
+\cc QF\_LIA      & {{[}MathSAT{]}} & {{[}MathSAT{]}} & {{[}MathSAT{]}}        & \cc {SPASS-SATT}      \\
+\cc QF\_LIRA     & {Yices2}        & {Yices2}        & \dcc {{[}Z3{]}}        & \dcc {{[}Z3{]}}       \\
+\cc QF\_LRA      &  {CVC4}         & {CVC4}          & {CVC4}                 & {CVC4}                \\
+\cc QF\_NIA      & {{[}Z3{]}}      & {{[}Z3{]}}      & {CVC4}                 & {CVC4}                \\
+\cc QF\_NIRA     & {CVC4}          & {CVC4}          & {SMT-RAT}              & {SMT-RAT}             \\
+\cc QF\_NRA      & \dcc {{[}Z3{]}} & \dcc {{[}Z3{]}}      & \cc {Yices2}      & \cc {{[}Z3{]}}        \\
+\cc QF\_RDL      & {Yices2}        & {Yices2}        & {Yices2}               & {Yices2}              \\
+\cc QF\_SLIA     & \cc             & \cc             & \cc                    & \cc {CVC4}            \\
+\cc QF\_UF       & {Yices2}        & {Yices2}        & {Yices2}               & {Yices2}              \\
+\drc
+\cc QF\_UFBV     & {Boolector}     & {Boolector}     & {Boolector}            & {Boolector}           \\
+\cc QF\_UFIDL    & {Yices2}        & {Yices2}        & {Yices2}               & {Yices2}              \\
+\cc QF\_UFLIA    & \dcc {{[}Z3{]}} & \dcc {{[}Z3{]}} & {Yices2}               & {Yices2}              \\
+\cc QF\_UFLRA    & {Yices2}        & {Yices2}        & {Yices2}               & {Yices2}              \\
+\drc
+\cc QF\_UFNIA    & \cc {CVC4}      & {Yices2/CVC4}   & {Yices2}               & {Yices2}              \\
+\rc
+\cc QF\_UFNRA    & {{[}Z3{]}}      & {Yices2}        & {{[}Z3{]}}             & {Yices2}              \\
+\cc UF           & {CVC4}          & {CVC4}          & \dcc {Vampire}         & \dcc {CVC4/Vampire}   \\
+\cc UFBV         & {{[}Z3{]}}      & {{[}Z3{]}}      & {{[}Z3{]}}             & {{[}Z3{]}}            \\
+\cc UFDT         & \cc             & \cc             & {CVC4}                 & {CVC4}                \\
+\rc
+\cc UFDTLIA      &                 &                 & {Vampire}              & {CVC4}                \\
+\cc UFIDL        & \cc {{[}Z3{]}}  & {CVC4}          & {CVC4}                 & \cc {{[}Z3{]}}        \\
+\drc
+\cc UFLIA        & {CVC4}          & {CVC4}          & {CVC4}                 & {CVC4}                \\
+\cc UFLRA        & \cc {CVC3}      & {{[}Z3{]}}      & {{[}Z3{]}}             & {{[}Z3{]}}            \\
+\drc
+\cc UFNIA        & \cc {CVC4}      & {Vampire}       & {Vampire}              & {{[}Z3{]}/Vampire}    \\
 \bottomrule

### 2019-03-16 2018/report/table-winners-main.tex
No solvers were entered into QF_ABVFP in 2017
Nicer tables (using the booktabs package)
Removed old main track winners table.

@@
 \centering
-\scalebox{.84}{\begin{tabular}{|rcccc|}
-\hline
+\scalebox{.83}{%
+\renewcommand{\arraystretch}{1.01}%
+  \begin{tabular}{r@{\hskip 1em}>{\columncolor[gray]{.95}[.25em][.5em]}c@{\hskip 1em}>{\columncolor[gray]{.95}[.5em][.5em]}c@{\hskip 1em}>{\columncolor[gray]{.95}[.5em][.5em]}c@{\hskip 1em}>{\columncolor[gray]{.95}[.5em][0.25em]}c}
+\toprule
+\rc
 Division         &  2015           &  2016           &  2017                  &  2018                 \\
-\hline
-%\multicolumn{1}{l}{}            & \multicolumn{1}{l}{}          & \multicolumn{1}{l}{}                & \multicolumn{1}{l}{}          & \multicolumn{1}{l}{}                  \\ \cline{5-5}
-ABVFP                            & \multicolumn{1}{l}{}          & \multicolumn{1}{l}{}                & \multicolumn{1}{l|}{}         & \multicolumn{1}{c|}{CVC4}             \\ \cline{2-5}
-\multicolumn{1}{|r|}{ALIA}       & \multicolumn{4}{c|}{{[}Z3{]}}                                                                                                               \\ \cline{2-5}
-AUFBVDTLIA                       & \multicolumn{1}{l}{}          & \multicolumn{1}{l|}{}               & \multicolumn{2}{c|}{CVC4}                                             \\ \cline{4-5}
-AUFDTLIA                         & \multicolumn{1}{l}{}          & \multicolumn{1}{l|}{}               & \multicolumn{2}{c|}{CVC4}                                             \\ \cline{2-5}
-\multicolumn{1}{|r|}{AUFLIA}     & \multicolumn{4}{c|}{CVC4}                                                                                                                   \\ \cline{2-5}
-\multicolumn{1}{|r|}{AUFLIRA}    & \multicolumn{4}{c|}{{[}Z3{]}}                                                                                                               \\ \cline{2-5}
-\multicolumn{1}{|r|}{AUFNIRA}    & \multicolumn{1}{c|}{CVC4}     & \multicolumn{2}{c|}{Vampire}                                        & \multicolumn{1}{c|}{CVC4}             \\ \cline{2-5}
-\multicolumn{1}{|r|}{BV}         & \multicolumn{1}{c|}{{[}Z3{]}} & \multicolumn{1}{c|}{Q3B}            & \multicolumn{1}{c|}{{[}Z3{]}} & \multicolumn{1}{c|}{CVC4}             \\ \cline{2-5}
-BVFP                             & \multicolumn{1}{l}{}          & \multicolumn{1}{l}{}                & \multicolumn{1}{l|}{}         & \multicolumn{1}{c|}{CVC4}             \\ \cline{5-5}
-FP                               & \multicolumn{1}{l}{}          & \multicolumn{1}{l}{}                & \multicolumn{1}{l|}{}         & \multicolumn{1}{c|}{CVC4}             \\ \cline{2-5}
-\multicolumn{1}{|r|}{LIA}        & \multicolumn{2}{c|}{CVC4}                                           & \multicolumn{2}{c|}{{[}Z3{]}}                                         \\ \cline{2-5}
-\multicolumn{1}{|r|}{LRA}        & \multicolumn{2}{c|}{CVC4}                                           & \multicolumn{2}{c|}{{[}Z3{]}}                                         \\ \cline{2-5}
-\multicolumn{1}{|r|}{NIA}        & \multicolumn{4}{c|}{{[}Z3{]}}                                                                                                               \\ \cline{2-5}
-\multicolumn{1}{|r|}{NRA}        & \multicolumn{1}{c|}{CVC4}     & \multicolumn{1}{c|}{Vampire}        & \multicolumn{1}{c|}{Redlog}   & \multicolumn{1}{c|}{{[}Z3{]}/Vampire} \\ \cline{2-5}
-\multicolumn{1}{|r|}{QF\_ABV}    & \multicolumn{4}{c|}{Boolector}                                                                                                              \\ \cline{2-5}
-QF\_ABVFP                        & \multicolumn{1}{l}{}          & \multicolumn{1}{l}{}                & \multicolumn{1}{l|}{}         & \multicolumn{1}{c|}{CVC4}             \\ \cline{2-5}
-\multicolumn{1}{|r|}{QF\_ALIA}   & \multicolumn{4}{c|}{Yices2}                                                                                                                 \\ \cline{2-5}
-\multicolumn{1}{|r|}{QF\_ANIA}   & \multicolumn{1}{c|}{{[}Z3{]}} & \multicolumn{2}{c|}{CVC4}                                           & \multicolumn{1}{c|}{{[}Z3{]}}         \\ \cline{2-5}
-\multicolumn{1}{|r|}{QF\_AUFBV}  & \multicolumn{3}{c|}{{[}MathSAT{]}}                                                                  & \multicolumn{1}{c|}{CVC4}             \\ \cline{2-5}
-\multicolumn{1}{|r|}{QF\_AUFLIA} & \multicolumn{4}{c|}{Yices2}                                                                                                                 \\ \cline{2-5}
-\multicolumn{1}{|r|}{QF\_AUFNIA} & \multicolumn{2}{c|}{CVC4}                                           & \multicolumn{2}{c|}{{[}Z3{]}}                                         \\ \cline{2-5}
-\multicolumn{1}{|r|}{QF\_AX}     & \multicolumn{4}{c|}{Yices2}                                                                                                                 \\ \cline{2-5}
-\multicolumn{1}{|r|}{QF\_BV}     & \multicolumn{2}{c|}{Boolector}                                      & \multicolumn{2}{c|}{Boolector/MinkeyRink}                             \\ \cline{2-5}
-\multicolumn{1}{|r|}{QF\_BVFP}   & \multicolumn{1}{c|}{Z3}       & \multicolumn{2}{c|}{{[}Z3{]}}                                       & \multicolumn{1}{c|}{CVC4}             \\ \cline{2-5}
-QF\_DT                           & \multicolumn{1}{l}{}          & \multicolumn{1}{l|}{}               & \multicolumn{2}{c|}{CVC4}                                             \\ \cline{2-5}
-\multicolumn{1}{|r|}{QF\_FP}     & \multicolumn{1}{c|}{Z3}       & \multicolumn{1}{c|}{{[}MathSAT{]}}  & \multicolumn{1}{c|}{{[}Z3{]}} & \multicolumn{1}{c|}{COLIBRI}          \\ \cline{2-5}
-\multicolumn{1}{|r|}{QF\_IDL}    & \multicolumn{2}{c|}{{[}Z3{]}}                                       & \multicolumn{2}{c|}{Yices2}                                           \\ \cline{2-5}
-\multicolumn{1}{|r|}{QF\_LIA}    & \multicolumn{3}{c|}{{[}MathSAT{]}}                                                                  & \multicolumn{1}{c|}{SPASS-SATT}       \\ \cline{2-5}
-\multicolumn{1}{|r|}{QF\_LIRA}   & \multicolumn{2}{c|}{Yices2}                                         & \multicolumn{2}{c|}{{[}Z3{]}}                                         \\ \cline{2-5}
-\multicolumn{1}{|r|}{QF\_LRA}    & \multicolumn{4}{c|}{CVC4}                                                                                                                   \\ \cline{2-5}
-\multicolumn{1}{|r|}{QF\_NIA}    & \multicolumn{2}{c|}{{[}Z3{]}}                                       & \multicolumn{2}{c|}{CVC4}                                             \\ \cline{2-5}
-\multicolumn{1}{|r|}{QF\_NIRA}   & \multicolumn{2}{c|}{CVC4}                                           & \multicolumn{2}{c|}{SMT-RAT}                                          \\ \cline{2-5}
-\multicolumn{1}{|r|}{QF\_NRA}    & \multicolumn{2}{c|}{{[}Z3{]}}                                       & \multicolumn{1}{c|}{Yices2}   & \multicolumn{1}{c|}{{[}Z3{]}}         \\ \cline{2-5}
-\multicolumn{1}{|r|}{QF\_RDL}    & \multicolumn{4}{c|}{Yices2}                                                                                                                 \\ \cline{2-5}
-QF\_SLIA                         & \multicolumn{1}{l}{}          & \multicolumn{1}{l}{}                & \multicolumn{1}{l|}{}         & \multicolumn{1}{c|}{CVC4}             \\ \cline{2-5}
-\multicolumn{1}{|r|}{QF\_UF}     & \multicolumn{4}{c|}{Yices2}                                                                                                                 \\ \cline{2-5}
-\multicolumn{1}{|r|}{QF\_UFBV}   & \multicolumn{4}{c|}{Boolector}                                                                                                              \\ \cline{2-5}
-\multicolumn{1}{|r|}{QF\_UFIDL}  & \multicolumn{4}{c|}{Yices2}                                                                                                                 \\ \cline{2-5}
-\multicolumn{1}{|r|}{QF\_UFLIA}  & \multicolumn{2}{c|}{{[}Z3{]}}                                       & \multicolumn{2}{c|}{Yices2}                                           \\ \cline{2-5}
-\multicolumn{1}{|r|}{QF\_UFLRA}  & \multicolumn{4}{c|}{Yices2}                                                                                                                 \\ \cline{2-5}
-\multicolumn{1}{|r|}{QF\_UFNIA}  & \multicolumn{1}{c|}{CVC4}     & \multicolumn{1}{c|}{Yices2/CVC4}    & \multicolumn{2}{c|}{Yices2}                                           \\ \cline{2-5}
-\multicolumn{1}{|r|}{QF\_UFNRA}  & \multicolumn{1}{c|}{{[}Z3{]}} & \multicolumn{1}{c|}{Yices2}         & \multicolumn{1}{c|}{{[}Z3{]}} & \multicolumn{1}{c|}{Yices2}           \\ \cline{2-5}
-\multicolumn{1}{|r|}{UF}         & \multicolumn{2}{c|}{CVC4}                                           & \multicolumn{1}{c|}{Vampire}  & \multicolumn{1}{c|}{CVC4/Vampire}     \\ \cline{2-5}
-\multicolumn{1}{|r|}{UFBV}       & \multicolumn{4}{c|}{{[}Z3{]}}                                                                                                               \\ \cline{2-5}
-UFDT                             & \multicolumn{1}{l}{}          & \multicolumn{1}{l|}{}               & \multicolumn{2}{c|}{CVC4}                                             \\ \cline{4-5}
-UFDTLIA                          & \multicolumn{1}{l}{}          & \multicolumn{1}{l|}{}               & \multicolumn{1}{c|}{Vampire}  & \multicolumn{1}{c|}{CVC4}             \\ \cline{2-5}
-\multicolumn{1}{|r|}{UFIDL}      & \multicolumn{1}{c|}{{[}Z3{]}} & \multicolumn{2}{c|}{CVC4}                                           & \multicolumn{1}{c|}{{[}Z3{]}}         \\ \cline{2-5}
-\multicolumn{1}{|r|}{UFLIA}      & \multicolumn{4}{c|}{CVC4}                                                                                                                   \\ \cline{2-5}
-\multicolumn{1}{|r|}{UFLRA}      & \multicolumn{1}{c|}{CVC3}     & \multicolumn{3}{c|}{{[}Z3{]}}                                                                               \\ \cline{2-5}
-\multicolumn{1}{|r|}{UFNIA}      & \multicolumn{1}{c|}{CVC4}     & \multicolumn{2}{c|}{Vampire}                                        & \multicolumn{1}{c|}{{[}Z3{]}/Vampire} \\ \hline
+\hline \hline
+\cc ABVFP        & \cc             & \cc             & \cc                    & \cc {CVC4} *          \\
+\cc ALIA         & CVC4 {{[}Z3{]}}      & CVC4 {{[}Z3{]}}      & CVC4 {{[}Z3{]}}             & CVC4 {{[}Z3{]}}            \\
+\cc AUFBVDTLIA   & \cc             & \cc             & {CVC4} *               & {CVC4} *              \\
+\cc AUFDTLIA     & \cc             & \cc             & {CVC4} *               & {CVC4}                \\
+\cc AUFLIA       & {CVC4}          & {CVC4}          & {CVC4}                 & {CVC4}                \\
+\drc
+\cc AUFLIRA      & \cc CVC4 {{[}Z3{]}}      & Vampire {{[}Z3{]}}      & Vampire {{[}Z3{]}}             & \cc CVC4 {{[}Z3{]}}            \\
+\drc
+\cc AUFNIRA      & \cc {CVC4} *    & {Vampire}       & {Vampire}              &\cc  {CVC4}            \\
+\cc BV           & \cc CVC4 {{[}Z3{]}} *    & {Q3B}           & Q3B {{[}Z3{]}}             &  \cc {CVC4}               \\
+\cc BVFP         & \cc             & \cc             & \cc                    & \cc {CVC4} *          \\
+\cc FP           & \cc             & \cc             & \cc                    & \cc {CVC4} *          \\
+\cc LIA          & {CVC4}     & {CVC4}      & CVC4 {{[}Z3{]}}             & CVC4 {{[}Z3{]}}            \\
+\cc LRA          & {CVC4}     & {CVC4}     & CVC4 {{[}Z3{]}}             & CVC4 {{[}Z3{]}}            \\
+\cc NIA          & \cc CVC4 {{[}Z3{]}} *     & \cc ProB {{[}Z3{]}}      & CVC4 {{[}Z3{]}}             & CVC4 {{[}Z3{]}}            \\
+\rc
+\cc NRA          & {CVC4} *        & {Vampire}       & {Redlog}               & Vampire {{[}Z3{]}/Vampire}    \\
+\cc QF\_ABV      & {Boolector}     & {Boolector}     & {Boolector}            & {Boolector}           \\
+\cc QF\_ABVFP    & \cc             &  \cc            & \cc {---}              & \cc {CVC4}            \\
+\cc QF\_ALIA     & {Yices2}        & {Yices2}        & {Yices2}               & {Yices2}              \\
+\drc
+\cc QF\_ANIA     & CVC4 {{[}Z3{]}} *& {CVC4} *        & {CVC4} *               & CVC4 {{[}Z3{]}} *           \\
+\cc QF\_AUFBV    & CVC4 {{[}MathSAT{]}} & CVC4 {{[}MathSAT{]}} & Yices2 {{[}MathSAT{]}}        & \cc {CVC4}            \\
+\drc
+\cc QF\_AUFLIA   & {Yices2}        & {Yices2}        & {Yices2}                 & {Yices2}              \\
+\cc QF\_AUFNIA   & {CVC4} *        & {CVC4} *        & CVC4 {{[}Z3{]}} *        & CVC4 {{[}Z3{]}} *     \\
+\cc QF\_AX       & {Yices2}        & {Yices2}        & {Yices2}                 & {Yices2}              \\
+\drc
+\cc QF\_BV       & {Boolector}     & {Boolector}     & {Boolector/MinkeyRink}   & {Boolector/MinkeyRink}\\
+\cc QF\_BVFP     & {Z3} *          & {{[}Z3{]}} *    & \cc COLIBRI {{[}Z3{]}} * & \cc {CVC4}            \\
+\drc
+\cc QF\_DT       & \cc             & \cc             & {CVC4} *               & {CVC4} *              \\
+\cc QF\_FP       & \cc {Z3} *      & \cc {{[}MathSAT{]}} * & COLIBRI {{[}Z3{]}}             & {COLIBRI}             \\
+\drc
+\cc QF\_IDL      & Yices2 {{[}Z3{]}} & Yices2 {{[}Z3{]}} & {Yices2}               & {Yices2}              \\
+\cc QF\_LIA      & CVC4 {{[}MathSAT{]}} & CVC4 {{[}MathSAT{]}} & CVC4 {{[}MathSAT{]}}        & \cc {SPASS-SATT}      \\
+\drc
+\cc QF\_LIRA     & {Yices2}        & {Yices2}        & Yices2 {{[}Z3{]}}        & Yices2 {{[}Z3{]}}       \\
+\cc QF\_LRA      &  {CVC4}         & {CVC4}          & {CVC4}                 & {CVC4}                \\
+\cc QF\_NIA      & \cc AProVE {{[}Z3{]}} & \cc Yices2 {{[}Z3{]}} & {CVC4}                 & {CVC4}                \\
+\cc QF\_NIRA     & {CVC4}          & {CVC4}          & \dcc {SMT-RAT}         & \dcc {SMT-RAT}        \\
+\cc QF\_NRA      & Yices2 {{[}Z3{]}} & Yices2 {{[}Z3{]}}      & {Yices2}      & Yices2 {{[}Z3{]}}        \\
+\cc QF\_RDL      & {Yices2}        & {Yices2}        & {Yices2}               & {Yices2}              \\
+\cc QF\_SLIA     & \cc             & \cc             & \cc                    & \cc {CVC4} *          \\
+\cc QF\_UF       & {Yices2}        & {Yices2}        & {Yices2}               & {Yices2}              \\
+\drc
+\cc QF\_UFBV     & {Boolector}     & {Boolector}     & {Boolector}            & {Boolector}           \\
+\cc QF\_UFIDL    & {Yices2}        & {Yices2}        & {Yices2}               & {Yices2}              \\
+\cc QF\_UFLIA    & Yices2 {{[}Z3{]}} & Yices2 {{[}Z3{]}} & {Yices2}               & {Yices2}              \\
+\cc QF\_UFLRA    & {Yices2}        & {Yices2}        & {Yices2}               & {Yices2}              \\
+\cc QF\_UFNIA    & \cc {CVC4} *    & {Yices2/CVC4}   & {Yices2}               & {Yices2}              \\
+\cc QF\_UFNRA    & \cc CVC3 {{[}Z3{]}} *     & {Yices2}        & Yices2 {{[}Z3{]}}             & {Yices2}              \\
+\cc UF           & {CVC4}          & {CVC4}          & \dcc {Vampire}         & \dcc {CVC4/Vampire}   \\
+\drc
+\cc UFBV         & CVC4 {{[}Z3{]}} *    & CVC4 {{[}Z3{]}}      & CVC4 {{[}Z3{]}} *            & CVC4 {{[}Z3{]}} *           \\
+\cc UFDT         & \cc             & \cc             & {CVC4} *               & {CVC4}                \\
+\rc
+\cc UFDTLIA      &                 &                 & {Vampire} *            & {CVC4}                \\
+\cc UFIDL        & CVC4 {{[}Z3{]}}  & {CVC4}          & {CVC4}                 & CVC4 {{[}Z3{]}}        \\
+\cc UFLIA        & {CVC4}          & {CVC4}          & {CVC4}                 & {CVC4}                \\
+\cc UFLRA        & \cc {CVC3}      & \cc Vampire {{[}Z3{]}}      & CVC4 {{[}Z3{]}}             & CVC4 {{[}Z3{]}}            \\
+\cc UFNIA        & \cc {CVC4} *    & {Vampire}       & {Vampire}              & Vampire {{[}Z3{]}/Vampire}    \\
+\bottomrule
 \end{tabular}}

### 2019-03-16 2018/report/table-winners-main.tex
Fix format.

@@
 \drc
-\cc QF\_ANIA     & CVC4 {{[}Z3{]}} *& {CVC4} *        & {CVC4} *               & CVC4 {{[}Z3{]}} *           \\
+\cc QF\_ANIA     & CVC4 {{[}Z3{]}} *     & {CVC4} *                 & {CVC4} *               & CVC4 {{[}Z3{]}} *          \\
 \cc QF\_AUFBV    & CVC4 {{[}MathSAT{]}}  & CVC4 {{[}MathSAT{]}}   & Yices2 {{[}MathSAT{]}}   & \cc {CVC4}                 \\
@@
 \drc
-\cc QF\_BV       & {Boolector}     & {Boolector}     & {Boolector/MinkeyRink}   & {Boolector/MinkeyRink}\\
+\cc QF\_BV       & {Boolector}           & {Boolector}            & {Boolector/MinkeyRink}   & {Boolector/MinkeyRink}     \\
 \cc QF\_BVFP     & {Z3} *                & {{[}Z3{]}} *           & \cc COLIBRI {{[}Z3{]}} * & \cc {CVC4}                 \\

### 2019-03-18 2018/report/plot/cactus_plot.r
Use time limit as y limit for vbs plots.

@@ -56,16 +56,17 @@ for (i in 1:nfiles)
   }
 }
 
-max_y=1450
-xlegend[1] <- as.expression(bquote(bold(.(args[nfiles+3]))))
+#max_y=1450
+max_y=1200
 xcol[1] <- colors[1]
 
 options("scipen"=100, "digits"=4)
 par(mar=c(5,5.2,2,3))
 plot(x,xlab="# Benchmarks",type="n",xaxt="n",yaxt="n",ann=FALSE,col=colors[1],xlim=c(min_x, max_x),ylim=c(0, max_y))
-abline(h=1200,col="gray")
-abline(v=max_x,col="gray")
+abline(h=1200,col="lightgray")
+abline(v=max_x,col="lightgray")
 lines(xvalues[[1]],col=colors[1],lwd=lwidth,lty=ltypes[1])
+xlegend[1] <- as.expression(bquote(bold(.(args[nfiles+3]))))
 
 if (nfiles >= 2)
 {
@@ -87,4 +88,4 @@ axis(2, at=ticks, labels=labels)
 title(ylab="Time [s]",line=4)
 title(xlab="# Benchmarks",line=3)
 title(plot_title,outer=TRUE,line=-1,font.main=2)
-legend(x="topleft",xlegend,col=xcol,bty="n",lwd=lwidth,lty=ltypes,text.font=1)
+legend(x="topleft",xlegend,col=xcol,bty="n",lwd=lwidth,lty=ltypes,text.font=1,inset=c(0,.02))

### 2019-03-18 2018/report/plot/cactus_plot.r
Add VBS plot for 2015-2018.

@@ -4,28 +4,29 @@ if(!dir.exists("pdf")) dir.create("pdf")
 args <- commandArgs(trailingOnly = TRUE)
 
 min_x=as.integer(args[1])
+max_x=as.integer(args[2])
 
-plot_title=args[2]
+plot_title=args[3]
 fname=gsub(' ','_',plot_title,fixed=TRUE)
 fname_pdf=paste("pdf/cactus_plot-",fname,".pdf",sep="")
 pdf(fname_pdf,width=9)
 par(cex=1.2)
 
-colors=c("deepskyblue4","red2","orange","chartreuse3","dodgerblue1","dodgerblue3",
+colors=c("red2","deepskyblue4","orange","chartreuse3","dodgerblue1","dodgerblue3",
          "cornflowerblue","darkgreen","yellow2","darkorchid2","gray",
          "chartreuse2", "darkorange", "darkorchid3","deeppink","blue3",
          "darkolivegreen","cyan2","darkcyan","deepskyblue4","deeppink4",
          "chartreuse4","chocolate4","darkblue","darkgoldenrod2")
 ncolors=length(colors)
-ltypes=c(5,1,6,4,3,1,5,6,4,3,1,5,6,4,3,1,5,6,4,3,1,5,6)
+ltypes=c(1,5,6,4,3,1,5,6,4,3,1,5,6,4,3,1,5,6,4,3,1,5,6)
 lwidth=2
-nfiles=(length(args)-2)/2
+nfiles=(length(args)-3)/2
 xlegend=vector(length=nfiles)
 xtitles=vector(length=nfiles)
 xpch=vector(length=nfiles)
 xcol=vector(length=nfiles)
 datacol=10
-fname_data <- args[3]
+fname_data <- args[4]
 fname <- file_path_sans_ext(basename(fname_data))
 
 xvalues <- list()
@@ -38,7 +39,7 @@ if (nfiles >= 2)
 {
   for (i in 2:nfiles)
   {
-    fname_data <- args[i+2]
+    fname_data <- args[i+3]
     fname <- file_path_sans_ext(basename(fname_data))
     data=read.csv(fname_data,sep=",",head=F,comment.char="#")
     x=sort(ifelse(data[,datacol] > 1200, 1200, data[,datacol]))
@@ -46,17 +47,6 @@ if (nfiles >= 2)
   }
 }
 
-max_x=0
[…]

### 2019-03-18 2018/report/plot/gen_common_results.py

@@ -39,9 +39,8 @@ if __name__ == "__main__":
         year = year.split(sep='.')[0]
         years = args.common_benchmarks.split('.')[-2]
         years = years.split('/')[-1]
-        years = years.split('_')
-        outfile_name = "{}/{}_vbs_{}-{}.csv".format(
-                path, year, years[-2], years[-1])
+        years = years.replace('Common_Benchmarks_', '')
+        outfile_name = "{}/{}_vbs_{}.csv".format(path, year, years)
         with open(outfile_name, 'w') as outfile:
             with open(args.vbs_data, 'r') as infile:
                 lines = infile.readlines()

### 2019-03-19 2018/report/SMT-COMP.tex
New layout for winners table (currently only main).
Beautify layout of main track winners table.
Removed old main track winners table.
New layout for application winners table.

@@
-\documentclass[twoside,11pt]{article}
+\documentclass[dvipsnames,table,twoside,11pt]{article}
 
@@
 \renewcommand{\floatpagefraction}{0.7}
+
+\newcommand{\nc}[1]{{[}#1{]}}
+\newcommand{\cc}{\cellcolor{white}}
+\newcommand{\rc}{\rowcolor{white}}
+\newcommand{\drc}{\rowcolor[gray]{.9}}
+\newcommand{\dcc}{\cellcolor[gray]{.9}}
 
@@
 \begin{figure}
+  \centering
+  \scalebox{.45}{\includegraphics{%
+        plot/pdf/cactus_plot-Virtual_Best_Solver_(VBS)_2015-2018.pdf}}
+  \caption{VBS on common benchmarks 2015-2018 of all logics in the Main track.}
+  \label{fig:progress-all}
+\end{figure}
+
+\begin{figure}
   \begin{subfigure}[t]{0.5\textwidth}
@@
   \end{subfigure}
-  \\[4ex]
+  \\[2ex]
   \begin{subfigure}[t]{0.5\textwidth}
@@
   \end{subfigure}
-  \caption{Virtual Best Solver (VBS) on common benchmarks of all
-  logics in the Main track.}
+  \caption{VBS on common benchmarks for pairs of years of all logics in the
+  Main track.}
   \label{fig:progress}

### 2019-03-19 2018/report/table-winners-main.tex
New layout for application winners table.

--- 2019-03-16 2018/report/table-winners-main.tex
@@
 \renewcommand{\arraystretch}{1.01}%
-  \begin{tabular}{r@{\hskip 1em}>{\columncolor[gray]{.95}[.25em][.5em]}c@{\hskip 1em}>{\columncolor[gray]{.95}[.5em][.5em]}c@{\hskip 1em}>{\columncolor[gray]{.95}[.5em][.5em]}c@{\hskip 1em}>{\columncolor[gray]{.95}[.5em][0.25em]}c}
+  \begin{tabular}{r@{\hskip 1em}>{\columncolor[gray]{.95}[.25em][.5em]}c@{\hskip 1em}>{\columncolor[gray]{.95}[.5em][.5em]}c@{\hskip 1em}>{\columncolor[gray]{.95}[.5em][.5em]}c@{\hskip 1em}>{\columncolor[gray]{.95}[.5em][0.5em]}c}
     \toprule
@@
     \cc ABVFP        & \cc                & \cc                 & \cc                   & \cc {CVC4} *            \\
-\cc ALIA         & CVC4 {{[}Z3{]}}      & CVC4 {{[}Z3{]}}      & CVC4 {{[}Z3{]}}             & CVC4 {{[}Z3{]}}            \\
+    \cc ALIA         & CVC4 \nc{Z3}       & CVC4 \nc{Z3}        & CVC4 \nc{Z3}          & CVC4 \nc{Z3}            \\
     \cc AUFBVDTLIA   & \cc                & \cc                 & {CVC4} *              & {CVC4} *                \\
@@
     \drc
-\cc AUFLIRA      & \cc CVC4 {{[}Z3{]}}      & Vampire {{[}Z3{]}}      & Vampire {{[}Z3{]}}             & \cc CVC4 {{[}Z3{]}}            \\
+    \cc AUFLIRA      & \cc CVC4 \nc{Z3}   & Vampire \nc{Z3}     & Vampire \nc{Z3}       & \cc CVC4 \nc{Z3}        \\
     \drc
     \cc AUFNIRA      & \cc {CVC4} *       & {Vampire}           & {Vampire}             &\cc  {CVC4}              \\
-\cc BV           & \cc CVC4 {{[}Z3{]}} *    & {Q3B}           & Q3B {{[}Z3{]}}             &  \cc {CVC4}               \\
+    \cc BV           & \cc CVC4 \nc{Z3} * & {Q3B}               & Q3B \nc{Z3}           &  \cc {CVC4}             \\
     \cc BVFP         & \cc                & \cc                 & \cc                   & \cc {CVC4} *            \\
     \cc FP           & \cc                & \cc                 & \cc                   & \cc {CVC4} *            \\
-\cc LIA          & {CVC4}     & {CVC4}      & CVC4 {{[}Z3{]}}             & CVC4 {{[}Z3{]}}            \\
-\cc LRA          & {CVC4}     & {CVC4}     & CVC4 {{[}Z3{]}}             & CVC4 {{[}Z3{]}}            \\
-\cc NIA          & \cc CVC4 {{[}Z3{]}} *     & \cc ProB {{[}Z3{]}}      & CVC4 {{[}Z3{]}}             & CVC4 {{[}Z3{]}}            \\
+    \cc LIA          & {CVC4}             & {CVC4}              & CVC4 \nc{Z3}          & CVC4 \nc{Z3}            \\
+    \cc LRA          & {CVC4}             & {CVC4}              & CVC4 \nc{Z3}          & CVC4 \nc{Z3}            \\
+    \cc NIA          & \cc CVC4 \nc{Z3} * & \cc ProB \nc{Z3}    & CVC4 \nc{Z3}          & CVC4 \nc{Z3}            \\
     \rc
-\cc NRA          & {CVC4} *        & {Vampire}       & {Redlog}               & Vampire {{[}Z3{]}/Vampire}    \\
+    \cc NRA          & {CVC4} *           & {Vampire}           & {Redlog}              & Vampire \nc{Z3/Vampire} \\
     \cc QF\_ABV      & {Boolector}        & {Boolector}         & {Boolector}           & {Boolector}             \\
@@
     \drc
-\cc QF\_ANIA     & CVC4 {{[}Z3{]}} *& {CVC4} *        & {CVC4} *               & CVC4 {{[}Z3{]}} *           \\
-\cc QF\_AUFBV    & CVC4 {{[}MathSAT{]}} & CVC4 {{[}MathSAT{]}} & Yices2 {{[}MathSAT{]}}        & \cc {CVC4}            \\
+    \cc QF\_ANIA     & CVC4 \nc{Z3} *     & {CVC4} *            & {CVC4} *              & CVC4 \nc{Z3} *          \\
+    \cc QF\_AUFBV    & CVC4 \nc{MathSAT}  & CVC4 \nc{MathSAT}   & Yices2 \nc{MathSAT}   & \cc {CVC4}              \\
     \drc
     \cc QF\_AUFLIA   & {Yices2}           & {Yices2}            & {Yices2}              & {Yices2}                \\
-\cc QF\_AUFNIA   & {CVC4} *        & {CVC4} *        & CVC4 {{[}Z3{]}} *        & CVC4 {{[}Z3{]}} *     \\
+    \cc QF\_AUFNIA   & {CVC4} *           & {CVC4} *            & CVC4 \nc{Z3} *        & CVC4 \nc{Z3} *          \\
     \cc QF\_AX       & {Yices2}           & {Yices2}            & {Yices2}              & {Yices2}                \\
     \drc
-\cc QF\_BV       & {Boolector}     & {Boolector}     & {Boolector/MinkeyRink}   & {Boolector/MinkeyRink}\\
-\cc QF\_BVFP     & {Z3} *          & {{[}Z3{]}} *    & \cc COLIBRI {{[}Z3{]}} * & \cc {CVC4}            \\
+    \cc QF\_BV       & {Boolector}        & {Boolector}         & {Boolector/MinkeyRink}& {Boolector/MinkeyRink}  \\
+    \cc QF\_BVFP     & {Z3} *             & \nc{Z3} *           & \cc COLIBRI \nc{Z3} * & \cc {CVC4}              \\
     \drc
     \cc QF\_DT       & \cc                & \cc                 & {CVC4} *              & {CVC4} *                \\
-\cc QF\_FP       & \cc {Z3} *      & \cc {{[}MathSAT{]}} * & COLIBRI {{[}Z3{]}}             & {COLIBRI}             \\
+    \cc QF\_FP       & \cc {Z3} *         & \cc \nc{MathSAT} *  & COLIBRI \nc{Z3}       & {COLIBRI}               \\
     \drc
-\cc QF\_IDL      & Yices2 {{[}Z3{]}} & Yices2 {{[}Z3{]}} & {Yices2}               & {Yices2}              \\
-\cc QF\_LIA      & CVC4 {{[}MathSAT{]}} & CVC4 {{[}MathSAT{]}} & CVC4 {{[}MathSAT{]}}        & \cc {SPASS-SATT}      \\
+    \cc QF\_IDL      & Yices2 \nc{Z3}     & Yices2 \nc{Z3}      & {Yices2}              & {Yices2}                \\
+    \cc QF\_LIA      & CVC4 \nc{MathSAT}  & CVC4 \nc{MathSAT}   & CVC4 \nc{MathSAT}     & \cc {SPASS-SATT}        \\
     \drc
-\cc QF\_LIRA     & {Yices2}        & {Yices2}        & Yices2 {{[}Z3{]}}        & Yices2 {{[}Z3{]}}       \\
+    \cc QF\_LIRA     & {Yices2}           & {Yices2}            & Yices2 \nc{Z3}        & Yices2 \nc{Z3}          \\
     \cc QF\_LRA      &  {CVC4}            & {CVC4}              & {CVC4}                & {CVC4}                  \\
-\cc QF\_NIA      & \cc AProVE {{[}Z3{]}} & \cc Yices2 {{[}Z3{]}} & {CVC4}                 & {CVC4}                \\
+    \cc QF\_NIA      & \cc AProVE \nc{Z3} & \cc Yices2 \nc{Z3}  & {CVC4}                & {CVC4}                  \\
     \cc QF\_NIRA     & {CVC4}             & {CVC4}              & \dcc {SMT-RAT}        & \dcc {SMT-RAT}          \\
-\cc QF\_NRA      & Yices2 {{[}Z3{]}} & Yices2 {{[}Z3{]}}      & {Yices2}      & Yices2 {{[}Z3{]}}        \\
+    \cc QF\_NRA      & Yices2 \nc{Z3}     & Yices2 \nc{Z3}      & {Yices2}              & Yices2 \nc{Z3}          \\
     \cc QF\_RDL      & {Yices2}           & {Yices2}            & {Yices2}              & {Yices2}                \\
@@
     \cc QF\_UFIDL    & {Yices2}           & {Yices2}            & {Yices2}              & {Yices2}                \\
-\cc QF\_UFLIA    & Yices2 {{[}Z3{]}} & Yices2 {{[}Z3{]}} & {Yices2}               & {Yices2}              \\
+    \cc QF\_UFLIA    & Yices2 \nc{Z3}     & Yices2 \nc{Z3}      & {Yices2}              & {Yices2}                \\
     \cc QF\_UFLRA    & {Yices2}           & {Yices2}            & {Yices2}              & {Yices2}                \\
     \cc QF\_UFNIA    & \cc {CVC4} *       & {Yices2/CVC4}       & {Yices2}              & {Yices2}                \\
-\cc QF\_UFNRA    & \cc CVC3 {{[}Z3{]}} *     & {Yices2}        & Yices2 {{[}Z3{]}}             & {Yices2}              \\
+    \cc QF\_UFNRA    & \cc CVC3 \nc{Z3} * & {Yices2}            & Yices2 \nc{Z3}        & {Yices2}                \\
     \cc UF           & {CVC4}             & {CVC4}              & \dcc {Vampire}        & \dcc {CVC4/Vampire}     \\
     \drc
-\cc UFBV         & CVC4 {{[}Z3{]}} *    & CVC4 {{[}Z3{]}}      & CVC4 {{[}Z3{]}} *            & CVC4 {{[}Z3{]}} *           \\
+    \cc UFBV         & CVC4 \nc{Z3} *     & CVC4 \nc{Z3}        & CVC4 \nc{Z3} *        & CVC4 \nc{Z3} *          \\
     \cc UFDT         & \cc                & \cc                 & {CVC4} *              & {CVC4}                  \\
@@
     \cc UFDTLIA      &                    &                     & {Vampire} *           & {CVC4}                  \\
-\cc UFIDL        & CVC4 {{[}Z3{]}}  & {CVC4}          & {CVC4}                 & CVC4 {{[}Z3{]}}        \\
+    \cc UFIDL        & CVC4 \nc{Z3}       & {CVC4}              & {CVC4}                & CVC4 \nc{Z3}            \\
     \cc UFLIA        & {CVC4}             & {CVC4}              & {CVC4}                & {CVC4}                  \\
-\cc UFLRA        & \cc {CVC3}      & \cc Vampire {{[}Z3{]}}      & CVC4 {{[}Z3{]}}             & CVC4 {{[}Z3{]}}            \\
-\cc UFNIA        & \cc {CVC4} *    & {Vampire}       & {Vampire}              & Vampire {{[}Z3{]}/Vampire}    \\
+    \cc UFLRA        & \cc {CVC3}         & \cc Vampire \nc{Z3} & CVC4 \nc{Z3}          & CVC4 \nc{Z3}            \\
+    \cc UFNIA        & \cc {CVC4} *       & {Vampire}           & {Vampire}             & Vampire \nc{Z3/Vampire} \\
     \bottomrule

### 2019-03-19 2018/report/SMT-COMP.tex
19 (partially)

@@
 motivated by application domains, include the theory of arrays,
-integer and real arithmetic, bit-vectors, and floating-point numbers
+integer and real arithmetic, bit-vectors, and floating-point numbers,
 among others~\cite{BarFT-RR-17}.  For instance, the following is an
@@
 %
-$$x \leq y \wedge y \leq x \wedge P (f(x) - f(y)) \wedge \neg P(0)$$
+$$x \leq y \wedge y \leq x \wedge P (f(x) - f(y)) \wedge \neg P(0).$$
+%
+This formula asserts that~$x$ is less than or equal to~$y$, that~$y$
+is less than or equal to~$x$, that~$P$ holds for the difference
+of~$f(x)$ and~$f(y)$, and that~$P$ does not hold for~$0$.  (Here,~$x$
+and~$y$ are integers,~$f$ is a function from integers to integers,
+and~$P$ is a predicate over integers.)
 %
@@
 solver
-supports~\cite{DBLP:conf/cav/BarrettCDHJKRT11,DBLP:conf/cade/BoutonODF09,DBLP:conf/tacas/MouraB08}.
+supports~\cite{DBLP:conf/cav/BarrettCDHJKRT11,DBLP:conf/cade/BoutonODF09,DBLP:conf/tacas/MouraB08,Nieuwenhuis:2006:SSS:1217856.1217859}.
 Historically, SMT solvers have focused on quantifier-free formulas and

### 2019-03-19 2018/report/SMT-COMP.tex
Remove Figure 2 (Distribution of SMT-LIB benchmarks by file size)
Avoid unfortunate line break

@@
 or even the entire library to shrink.  From~2015 to~2018, the total
-number of benchmarks has increased by~68\,\%.
-Figure~\ref{fig:benchmark-sizes} shows how the file size of individual
-benchmarks is distributed.  The largest benchmark in the 2018 release
-had a size of 1,041~MB; the total size of the release was 91~GB.
+number of benchmarks has increased by~68\,\%.  The largest benchmark
+in the 2018 release had a size of 1,041~MB; the total size of the
+release was 91~GB.
 
@@
 \end{table}
-
-\begin{figure}
-  \centering
-  \scalebox{.96}[.96]{\begin{tikzpicture}
-    \draw [gray] (0,0) -- (14,0);
-    \draw [gray] (0,.9) -- (14,.9);
-    \draw [gray] (0,1.8) -- (14,1.8);
-    \draw [gray] (0,2.7) -- (14,2.7);
-    \draw [gray] (0,3.6) -- (14,3.6);
-    \draw [gray] (0,4.5) -- (14,4.5);
-    \draw [gray] (0,5.4) -- (14,5.4);
-
-    \node [left] at (0,0) {\footnotesize 0};
-    \node [left] at (0,.9) {\footnotesize 1};
-    \node [left] at (0,1.8) {\footnotesize 10};
-    \node [left] at (0,2.7) {\footnotesize 100};
-    \node [left] at (0,3.6) {\footnotesize 1000};
-    \node [left] at (0,4.5) {\footnotesize 10000};
-    \node [left] at (0,5.4) {\footnotesize 100000};
-
-    \node [rotate=90] at (-1.5,2.7) {\small Benchmarks};
-
-    \draw [fill=black] (0.5,0) rectangle (1,5.1629791157); % 54531
-    \draw [fill=black] (2.25,0) rectangle (2.75,5.5836542368); % 159978
-    \draw [fill=black] (4,0) rectangle (4.5,5.350394013); % 88081
-    \draw [fill=black] (5.75,0) rectangle (6.25,4.8786283826); % 26345
-    \draw [fill=black] (7.5,0) rectangle (8,4.3889077926); % 7526
-    \draw [fill=black] (9.25,0) rectangle (9.75,3.1918883971); % 352
-    \draw [fill=black] (11,0) rectangle (11.5,2.2422255245); % 31
-    %\draw [fill=black] (12.75,0) rectangle (13.25,0); % 0
-
-    \draw [fill=white] (1,0) rectangle (1.5,1.4418539922); % 4
-    \draw [fill=white] (2.75,0) rectangle (3.25,3.8742353084); % 2017
-    \draw [fill=white] (4.5,0) rectangle (5,3.9968181739); % 2760
-    \draw [fill=white] (6.25,0) rectangle (6.75,4.1649057286); % 4243
-    \draw [fill=white] (8,0) rectangle (8.5,3.5266990775); % 829
-    \draw [fill=white] (9.75,0) rectangle (10.25,3.0372735114); % 237
-    \draw [fill=white] (11.5,0) rectangle (12,2.5927322331); % 76
-    \draw [fill=white] (13.25,0) rectangle (13.75,0.9); % 1
-
-    \node [below] at (1,0) {\footnotesize $[10^2, 10^3[$};
-    \node [below] at (2.75,0) {\footnotesize $[10^3, 10^4[$};
-    \node [below] at (4.5,0) {\footnotesize $[10^4, 10^5[$};
-    \node [below] at (6.25,0) {\footnotesize $[10^5, 10^6[$};
-    \node [below] at (8,0) {\footnotesize $[10^6, 10^7[$};
-    \node [below] at (9.75,0) {\footnotesize $[10^7, 10^8[$};
-    \node [below] at (11.5,0) {\footnotesize $[10^8, 10^9[$};
-    \node [below] at (13.25,0) {\footnotesize $[10^9, 10^{10}[$};
-
-    \node [] at (7,-1) {\small File size in bytes};
-  \end{tikzpicture}}
-  \caption{Distribution of SMT-LIB benchmarks by file size (2018), for
-    non-incremental~($\blacksquare$) and incremental~($\square$)
-    benchmarks.}
-  \label{fig:benchmark-sizes}
-\end{figure}
 
@@
 1,104 benchmarks were excluded because their logic had been classified
-incorrectly, and 8 benchmarks were excluded because of incorrect or
+incorrectly, and 8~benchmarks were excluded because of incorrect or
 missing status information.  Moreover, divisions containing datatypes
-({DT})---which were new in~2017---were excluded from the unsat-core
-track because of lacking tool support.  In~2018, 3,603 benchmarks were
+({DT})---which were new in~2017---were excluded from the Unsat-Core
+track because of lacking tool support.  In~2018, 3,603~benchmarks were
 excluded because they contained named terms (a feature of the SMT-LIB
-language that is not permitted in competition benchmarks), and 5
-benchmarks were excluded because of missing status information.
+language that is not permitted in competition benchmarks), and
+5~benchmarks were excluded because of missing status information.
 

### 2019-03-19 2018/report/SMT-COMP.tex
Add explanation of competitive divisions

@@
 When the same solver ranked first in both, which is most often the
-case, its name appears just once.  Some divisions were not
-\emph{competitive} (that is, no official winner was declared for
-them); we are including all divisions here.  Moreover, we are
+case, its name appears just once.  A division is \emph{competitive} if
+at least two substantially different solvers (i.e., solvers from two
+different teams) were submitted.  (Experimental divisions are never
+competitive.)  Official winners were declared only for competitive
+divisions; we are including all divisions here.  Moreover, we are
 including solvers that were running hors concours (and hence

### 2019-03-19 2018/report/table-winners-unsat-core.tex
Minor
No solvers were entered into QF_ABVFP in 2017
Nicer tables (using the booktabs package)
Double check application and unsat score application winners table.

@@
-  \begin{table}[]
-  \begin{center}
-\scalebox{.89}{\begin{tabular}{lccc}
-      \hline
-      & \multicolumn{1}{l}{2016}           & \multicolumn{1}{l}{2017}                  & \multicolumn{1}{l}{2018}         \\
-      \hline
-      \\
-      \cline{2-4}
-      \multicolumn{1}{l|}{ALIA}       & \multicolumn{3}{c|}{{[}Z3{]}}                                                                                     \\ \cline{2-4} 
-AUFBVDTLIA                      & \multicolumn{1}{l}{}               & \multicolumn{1}{l}{}                      & CVC4                             \\ \cline{2-4} 
-\multicolumn{1}{l|}{AUFLIA}     & \multicolumn{2}{c|}{{[}Z3{]}}                                                  & \multicolumn{1}{c|}{CVC4}        \\ \cline{2-4} 
-\multicolumn{1}{l|}{AUFLIRA}    & \multicolumn{2}{c|}{{[}Z3{]}}                                                  & \multicolumn{1}{c|}{CVC4}        \\ \cline{2-4} 
-\multicolumn{1}{l|}{AUFNIRA}    & \multicolumn{1}{c|}{{[}Z3{]}}      & \multicolumn{2}{c|}{CVC4}                                                    \\ \cline{2-4} 
-\multicolumn{1}{l|}{BV}         & \multicolumn{3}{c|}{{[}Z3{]}}                                                                                     \\ \cline{2-4} 
-\multicolumn{1}{l|}{LIA}        & \multicolumn{1}{c|}{{[}veriT{]}}   & \multicolumn{1}{c|}{CVC4}                 & \multicolumn{1}{c|}{{[}Z3{]}}    \\ \cline{2-4} 
-\multicolumn{1}{l|}{LRA}        & \multicolumn{1}{c|}{{[}veriT{]}}   & \multicolumn{2}{c}{CVC4}                                                     \\ \cline{2-4} 
-\multicolumn{1}{l|}{NIA}        & \multicolumn{1}{c|}{{[}Z3{]}}      & \multicolumn{1}{c|}{CVC4/{[}Z3{]}}        & \multicolumn{1}{c|}{CVC4}        \\ \cline{2-4} 
-\multicolumn{1}{l|}{NRA}        & \multicolumn{3}{c|}{{[}Z3{]}}                                                                                     \\ \cline{2-4} 
-\multicolumn{1}{l|}{QF\_ABV}    & \multicolumn{2}{c|}{{[}Z3{]}}                                                  & \multicolumn{1}{c|}{Yices2}      \\ \cline{2-4} 
-                                & \multicolumn{1}{l}{}               & \multicolumn{1}{l|}{}                     & \multicolumn{1}{c|}{CVC4}        \\ \cline{2-4} 
-\multicolumn{1}{l|}{QF\_ALIA}   & \multicolumn{3}{c|}{{[}Z3{]}}                                                                                     \\ \cline{2-4} 
-\multicolumn{1}{l|}{QF\_ANIA}   & \multicolumn{1}{c|}{{[}Z3{]}}      & \multicolumn{2}{c|}{CVC4}                                                    \\ \cline{2-4} 
-\multicolumn{1}{l|}{QF\_AUFBV}  & \multicolumn{1}{c|}{{[}Z3{]}}      & \multicolumn{2}{c|}{{[}MathSAT{]}}                                           \\ \cline{2-4} 
-\multicolumn{1}{l|}{QF\_AUFLIA} & \multicolumn{1}{c|}{{[}Z3{]}}      & \multicolumn{2}{c|}{CVC4}                                                    \\ \cline{2-4} 
-\multicolumn{1}{l|}{QF\_AUFNIA} & \multicolumn{3}{c|}{{[}Z3{]}}                                                                                     \\ \cline{2-4} 
-\multicolumn{1}{l|}{QF\_AX}     & \multicolumn{2}{c|}{{[}Z3{]}}                                                  & \multicolumn{1}{c|}{Yices2}      \\ \cline{2-4} 
-\multicolumn{1}{l|}{QF\_BV}     & \multicolumn{2}{c|}{{[}MathSAT{]}}                                             & \multicolumn{1}{c|}{Yices2}      \\ \cline{2-4} 
-\multicolumn{1}{l|}{QF\_BVFP}   & \multicolumn{2}{c|}{{[}Z3{]}}                                                  & \multicolumn{1}{c|}{CVC4}        \\ \cline{2-4} 
-QF\_DT                          & \multicolumn{1}{l}{}               & \multicolumn{1}{l|}{}                     & \multicolumn{1}{c|}{CVC4}        \\ \cline{2-4} 
-\multicolumn{1}{l|}{QF\_FP}     & \multicolumn{1}{c|}{{[}MathSAT{]}} & \multicolumn{1}{c|}{{[}Z3{]}}             & \multicolumn{1}{c|}{CVC4}        \\ \cline{2-4} 
-\multicolumn{1}{l|}{QF\_IDL}    & \multicolumn{3}{c|}{{[}Z3{]}}                                                                                     \\ \cline{2-4} 
-\multicolumn{1}{l|}{QF\_LIA}    & \multicolumn{1}{c|}{{[}Z3{]}}      & \multicolumn{1}{c|}{SMTInterpol/{[}Z3{]}} & \multicolumn{1}{c|}{SMTInterpol} \\ \cline{2-4} 
-\multicolumn{1}{l|}{QF\_LIRA}   & \multicolumn{3}{c|}{{[}Z3{]}}                                                                                     \\ \cline{2-4} 
-\multicolumn{1}{l|}{QF\_LRA}    & \multicolumn{3}{c|}{SMTInterpol}                                                                                  \\ \cline{2-4} 
-\multicolumn{1}{l|}{QF\_NIA}    & \multicolumn{3}{c|}{{[}Z3{]}}                                                                                     \\ \cline{2-4} 
-\multicolumn{1}{l|}{QF\_NIRA}   & \multicolumn{3}{c|}{{[}Z3{]}}                                                                                     \\ \cline{2-4} 
-\multicolumn{1}{l|}{QF\_NRA}    & \multicolumn{1}{c|}{{[}Z3{]}}      & \multicolumn{2}{c|}{CVC4}                                                    \\ \cline{2-4} 
-\multicolumn{1}{l|}{QF\_RDL}    & \multicolumn{1}{c|}{{[}veriT{]}}   & \multicolumn{2}{c|}{{[}Z3{]}}                                                \\ \cline{2-4} 
-\multicolumn{1}{l|}{QF\_UF}     & \multicolumn{1}{c|}{{[}MathSAT{]}} & \multicolumn{2}{c|}{CVC4}                                                    \\ \cline{2-4} 
-\multicolumn{1}{l|}{QF\_UFBV}   & \multicolumn{2}{c|}{{[}MathSAT{]}}                                             & \multicolumn{1}{c|}{{[}Z3{]}}    \\ \cline{2-4} 
-\multicolumn{1}{l|}{QF\_UFIDL}  & \multicolumn{2}{c|}{{[}Z3{]}}                                                  & \multicolumn{1}{c|}{Yices2}      \\ \cline{2-4} 
-\multicolumn{1}{l|}{QF\_UFLIA}  & \multicolumn{1}{c|}{{[}MathSAT{]}} & \multicolumn{2}{c|}{{[}Z3{]}}                                                \\ \cline{2-4} 
-\multicolumn{1}{l|}{QF\_UFLRA}  & \multicolumn{1}{c|}{{[}Z3{]}}      & \multicolumn{2}{c}{{[}MathSAT{]}}                                            \\ \cline{2-4} 
-\multicolumn{1}{l|}{QF\_UFNIA}  & \multicolumn{3}{c|}{{[}Z3{]}}                                                                                     \\ \cline{2-4} 
-\multicolumn{1}{l|}{QF\_UFNRA}  & \multicolumn{3}{c|}{{[}Z3{]}}                                                                                     \\ \cline{2-4} 
-\multicolumn{1}{l|}{UF}         & \multicolumn{1}{c|}{{[}Z3{]}}      & \multicolumn{2}{c|}{CVC4}                                                    \\ \cline{2-4} 
-\multicolumn{1}{l|}{UFBV}       & \multicolumn{2}{c|}{{[}Z3{]}}                                                  & \multicolumn{1}{c|}{CVC4}        \\ \cline{2-4} 
-UFDT                            & \multicolumn{1}{l}{}               & \multicolumn{1}{l|}{}                     & \multicolumn{1}{c|}{CVC4}        \\ \cline{2-4} 
-\multicolumn{1}{l|}{UFIDL}      & \multicolumn{1}{c|}{{[}Z3{]}}      & \multicolumn{2}{c|}{CVC4}                                                    \\ \cline{2-4} 
-\multicolumn{1}{l|}{UFLIA}      & \multicolumn{1}{c|}{{[}Z3{]}}      & \multicolumn{2}{c|}{CVC4}                                                    \\ \cline{2-4} 
-\multicolumn{1}{l|}{UFLRA}      & \multicolumn{3}{c|}{{[}Z3{]}}                                                                                     \\ \cline{2-4} 
-\multicolumn{1}{l|}{UFNIA}      & \multicolumn{1}{c|}{{[}Z3{]}}      & \multicolumn{2}{c|}{CVC4}                                                    \\ \cline{2-4} 
-\end{tabular}}
-\end{center}
-\caption{\label{tab:winners-unsat-core} Winners of the unsat-core track.}
+\begin{table}
+  \caption{Best unsat-core track solvers (by division)}
+  \label{tab:winners-unsat-core}
+  \centering
+  \scalebox{.88}{%
+    \begin{tabular}{r@{\hskip 1em}>{\columncolor[gray]{.95}[.25em][.5em]}c@{\hskip 1em}>{\columncolor[gray]{.95}[.5em][.5em]}c@{\hskip 1em}>{\columncolor[gray]{.95}[.5em][.5em]}c}
+    \toprule
+    \rc
+    Division   & 2016             & 2017            & 2018               \\
+    \hline \hline
+    \cc ALIA       & \cc \nc{Z3} *                  & CVC4 \nc{Z3} *                      & CVC4 \nc{Z3} *           \\
+    \cc AUFBVDTLIA & \cc                            & \cc                                 & CVC4 *                   \\
+    \cc AUFLIA     & \cc \nc{Z3} *                  & CVC4 \nc{Z3} *                      & CVC4 *                   \\
+    \cc AUFLIRA    & \cc \nc{Z3} *                  & CVC4 \nc{Z3} *                      & CVC4 *                   \\
+    \cc AUFNIRA    & \cc \nc{Z3} *                  & CVC4 *                              & CVC4 *                   \\
+    \cc BV         & \cc \nc{Z3} *                  & CVC4 \nc{Z3} *                      & CVC4 \nc{Z3} *           \\
+    \cc LIA        & \cc \nc{veriT} *               & CVC4 *                              & CVC4 \nc{Z3} *           \\
+    \cc LRA        & \cc \nc{veriT} *               & CVC4 *                              & CVC4 *                   \\
+    \cc NIA        & \cc \nc{Z3} *                  & CVC4 / CVC4 \nc{Z3}*                & CVC4 *                   \\
+    \cc NRA        & \cc \nc{Z3} *                  & CVC4 \nc{Z3} *                      & CVC4 \nc{Z3} *           \\
+    \cc QF\_ABV    & \cc \nc{Z3} *                  & CVC4 \nc{Z3} *                      & Yices2                   \\
+    \cc QF\_ABVFP  & \cc                            & \cc ---                             & \cc CVC4 *               \\
+    \rc
+    \cc QF\_ALIA   & SMTInterpol \nc{Z3} *          & SMTInterpol \nc{Z3}                 & Yices2 \nc{Z3}           \\
+    \cc QF\_ANIA   & \cc \nc{Z3} *                  & CVC4 *                              & CVC4 *                   \\
+    \rc
+    \cc QF\_AUFBV  & \nc{Z3} *                      & CVC4 \nc{MathSAT} *                 & Yices2 \nc{MathSAT}      \\
+    \cc QF\_AUFLIA & \cc SMTInterpol \nc{Z3} *      & CVC4                                & CVC4                     \\
+    \cc QF\_AUFNIA & \cc \nc{Z3} *                  & CVC4 \nc{Z3} *                      & CVC4 \nc{Z3} *           \\
+    \drc
+    \cc QF\_AX     & SMTInterpol \nc{Z3} *          & SMTInterpol \nc{Z3}                 & \cc Yices2               \\
+    \rc
+    \cc QF\_BV     & \nc{MathSAT} *                 & CVC4 \nc{MathSAT} *                 & Yices2                   \\
+    \cc QF\_BVFP   & \nc{Z3} *                      & \nc{Z3} *                           & \cc CVC4 \nc{Z3} *       \\
+    \rc
+    \cc QF\_DT     &                                &                                     & CVC4 *                   \\
+    \rc
+    \cc QF\_FP     & \nc{MathSAT} *                 & \nc{Z3} *                           & CVC4 *                   \\
+    \cc QF\_IDL    & \cc SMTInterpol \nc{Z3} *      & CVC4 \nc{Z3}                        & CVC4 \nc{Z3}             \\
+    \drc
+    \cc QF\_LIA    & SMTInterpol \nc{Z3} *          & SMTInterpol / SMTInterpol \nc{Z3}   & SMTInterpol              \\
+    \cc QF\_LIRA   & \cc SMTInterpol \nc{Z3} *      & CVC4 \nc{Z3}                        & CVC4 \nc{Z3}             \\
+    \drc
+    \cc QF\_LRA    & SMTInterpol *                  & SMTInterpol                         & SMTInterpol              \\
+    \cc QF\_NIA    & \cc \nc{Z3} *                  & CVC4 \nc{Z3} *                      & CVC4 \nc{Z3} *           \\
+    \cc QF\_NIRA   & \cc \nc{Z3} *                  & CVC4 \nc{Z3} *                      & CVC4 \nc{Z3} *           \\
+    \cc QF\_NRA    & \cc \nc{Z3} *                  & CVC4 *                              & CVC4 *                   \\
+    \cc QF\_RDL    & \cc SMTInterpol \nc{veriT} *   & CVC4 \nc{Z3}                        & CVC4 \nc{Z3}             \\
+    \cc QF\_UF     & \cc SMTInterpol \nc{MathSAT} * & CVC4                                & CVC4                     \\
+    \rc
+    \cc QF\_UFBV   & \nc{MathSAT} *                 & CVC4 \nc{MathSAT} *                 & Yices2 \nc{Z3}           \\
+    \drc
+    \cc QF\_UFIDL  & SMTInterpol \nc{Z3} *          & SMTInterpol \nc{Z3}                 & \cc Yices2               \\
+    \drc
+    \cc QF\_UFLIA  & SMTInterpol \nc{MathSAT} *     & SMTInterpol \nc{Z3}                 & SMTInterpol \nc{Z3}      \\
+    \drc
+    \cc QF\_UFLRA  & SMTInterpol \nc{Z3} *          & SMTInterpol \nc{MathSAT}            & \cc Yices2 \nc{MathSAT}  \\
+    \cc QF\_UFNIA  & \cc \nc{Z3} *                  & CVC4 \nc{Z3} *                      & CVC4 \nc{Z3} *           \\
+    \cc QF\_UFNRA  & \cc \nc{Z3} *                  & CVC4 \nc{Z3} *                      & CVC4 \nc{Z3} *           \\
+    \cc UF         & \cc \nc{Z3} *                  & CVC4 *                              & CVC4 *                   \\
+    \cc UFBV       & \cc \nc{Z3} *                  & CVC4 \nc{Z3} *                      & CVC4 *                   \\
+    \rc
+    \cc UFDT       &                                &                                     & CVC4 *                   \\
+    \cc UFIDL      & \cc \nc{Z3} *                  & CVC4 *                              & CVC4 *                   \\
+    \cc UFLIA      & \cc \nc{Z3} *                  & CVC4 *                              & CVC4 *                   \\
+    \cc UFLRA      & \cc \nc{Z3} *                  & CVC4 \nc{Z3} *                      & CVC4 \nc{Z3} *           \\
+    \cc UFNIA      & \cc \nc{Z3} *                  & CVC4 *                              & CVC4 *                   \\
+  \end{tabular}
+  }
 \end{table}

### 2019-03-20 2018/report/table-winners-main.tex
Use colors for winners tables.

@@
 \renewcommand{\arraystretch}{1.01}%
-  \begin{tabular}{r@{\hskip 1em}>{\columncolor[gray]{.95}[.25em][.5em]}c@{\hskip 1em}>{\columncolor[gray]{.95}[.5em][.5em]}c@{\hskip 1em}>{\columncolor[gray]{.95}[.5em][.5em]}c@{\hskip 1em}>{\columncolor[gray]{.95}[.5em][0.5em]}c}
+  \begin{tabular}{r@{\hskip 1em}>{\columncolor{white}[.25em][.5em]}c@{\hskip 1em}>{\columncolor{white}[.5em][.5em]}c@{\hskip 1em}>{\columncolor{white}[.5em][.5em]}c@{\hskip 1em}>{\columncolor{white}[.5em][0.5em]}c}
     \toprule
-    \rc
     Division         &  2015                    &  2016                     &  2017                          &  2018                     \\
     \hline \hline
-    \cc ABVFP        & \cc                & \cc                 & \cc                   & \cc {CVC4} *            \\
-    \cc ALIA         & CVC4 \nc{Z3}       & CVC4 \nc{Z3}        & CVC4 \nc{Z3}          & CVC4 \nc{Z3}            \\
-    \cc AUFBVDTLIA   & \cc                & \cc                 & {CVC4} *              & {CVC4} *                \\
-    \cc AUFDTLIA     & \cc                & \cc                 & {CVC4} *              & {CVC4}                  \\
-    \cc AUFLIA       & {CVC4}             & {CVC4}              & {CVC4}                & {CVC4}                  \\
-    \drc
-    \cc AUFLIRA      & \cc CVC4 \nc{Z3}   & Vampire \nc{Z3}     & Vampire \nc{Z3}       & \cc CVC4 \nc{Z3}        \\
-    \drc
-    \cc AUFNIRA      & \cc {CVC4} *       & {Vampire}           & {Vampire}             &\cc  {CVC4}              \\
-    \cc BV           & \cc CVC4 \nc{Z3} * & {Q3B}               & Q3B \nc{Z3}           &  \cc {CVC4}             \\
-    \cc BVFP         & \cc                & \cc                 & \cc                   & \cc {CVC4} *            \\
-    \cc FP           & \cc                & \cc                 & \cc                   & \cc {CVC4} *            \\
-    \cc LIA          & {CVC4}             & {CVC4}              & CVC4 \nc{Z3}          & CVC4 \nc{Z3}            \\
-    \cc LRA          & {CVC4}             & {CVC4}              & CVC4 \nc{Z3}          & CVC4 \nc{Z3}            \\
-    \cc NIA          & \cc CVC4 \nc{Z3} * & \cc ProB \nc{Z3}    & CVC4 \nc{Z3}          & CVC4 \nc{Z3}            \\
-    \rc
-    \cc NRA          & {CVC4} *           & {Vampire}           & {Redlog}              & Vampire \nc{Z3/Vampire} \\
-    \cc QF\_ABV      & {Boolector}        & {Boolector}         & {Boolector}           & {Boolector}             \\
-    \cc QF\_ABVFP    & \cc                &  \cc                & \cc {---}             & \cc {CVC4}              \\
-    \cc QF\_ALIA     & {Yices2}           & {Yices2}            & {Yices2}              & {Yices2}                \\
-    \drc
-    \cc QF\_ANIA     & CVC4 \nc{Z3} *     & {CVC4} *            & {CVC4} *              & CVC4 \nc{Z3} *          \\
-    \cc QF\_AUFBV    & CVC4 \nc{MathSAT}  & CVC4 \nc{MathSAT}   & Yices2 \nc{MathSAT}   & \cc {CVC4}              \\
-    \drc
-    \cc QF\_AUFLIA   & {Yices2}           & {Yices2}            & {Yices2}              & {Yices2}                \\
-    \cc QF\_AUFNIA   & {CVC4} *           & {CVC4} *            & CVC4 \nc{Z3} *        & CVC4 \nc{Z3} *          \\
-    \cc QF\_AX       & {Yices2}           & {Yices2}            & {Yices2}              & {Yices2}                \\
-    \drc
-    \cc QF\_BV       & {Boolector}        & {Boolector}         & {Boolector/MinkeyRink}& {Boolector/MinkeyRink}  \\
-    \cc QF\_BVFP     & {Z3} *             & \nc{Z3} *           & \cc COLIBRI \nc{Z3} * & \cc {CVC4}              \\
-    \drc
-    \cc QF\_DT       & \cc                & \cc                 & {CVC4} *              & {CVC4} *                \\
-    \cc QF\_FP       & \cc {Z3} *         & \cc \nc{MathSAT} *  & COLIBRI \nc{Z3}       & {COLIBRI}               \\
-    \drc
-    \cc QF\_IDL      & Yices2 \nc{Z3}     & Yices2 \nc{Z3}      & {Yices2}              & {Yices2}                \\
-    \cc QF\_LIA      & CVC4 \nc{MathSAT}  & CVC4 \nc{MathSAT}   & CVC4 \nc{MathSAT}     & \cc {SPASS-SATT}        \\
-    \drc
-    \cc QF\_LIRA     & {Yices2}           & {Yices2}            & Yices2 \nc{Z3}        & Yices2 \nc{Z3}          \\
-    \cc QF\_LRA      &  {CVC4}            & {CVC4}              & {CVC4}                & {CVC4}                  \\
-    \cc QF\_NIA      & \cc AProVE \nc{Z3} & \cc Yices2 \nc{Z3}  & {CVC4}                & {CVC4}                  \\
-    \cc QF\_NIRA     & {CVC4}             & {CVC4}              & \dcc {SMT-RAT}        & \dcc {SMT-RAT}          \\
-    \cc QF\_NRA      & Yices2 \nc{Z3}     & Yices2 \nc{Z3}      & {Yices2}              & Yices2 \nc{Z3}          \\
-    \cc QF\_RDL      & {Yices2}           & {Yices2}            & {Yices2}              & {Yices2}                \\
-    \cc QF\_SLIA     & \cc                & \cc                 & \cc                   & \cc {CVC4} *            \\
-    \cc QF\_UF       & {Yices2}           & {Yices2}            & {Yices2}              & {Yices2}                \\
-    \drc
-    \cc QF\_UFBV     & {Boolector}        & {Boolector}         & {Boolector}           & {Boolector}             \\
-    \cc QF\_UFIDL    & {Yices2}           & {Yices2}            & {Yices2}              & {Yices2}                \\
-    \cc QF\_UFLIA    & Yices2 \nc{Z3}     & Yices2 \nc{Z3}      & {Yices2}              & {Yices2}                \\
-    \cc QF\_UFLRA    & {Yices2}           & {Yices2}            & {Yices2}              & {Yices2}                \\
-    \cc QF\_UFNIA    & \cc {CVC4} *       & {Yices2/CVC4}       & {Yices2}              & {Yices2}                \\
-    \cc QF\_UFNRA    & \cc CVC3 \nc{Z3} * & {Yices2}            & Yices2 \nc{Z3}        & {Yices2}                \\
-    \cc UF           & {CVC4}             & {CVC4}              & \dcc {Vampire}        & \dcc {CVC4/Vampire}     \\
-    \drc
-    \cc UFBV         & CVC4 \nc{Z3} *     & CVC4 \nc{Z3}        & CVC4 \nc{Z3} *        & CVC4 \nc{Z3} *          \\
-    \cc UFDT         & \cc                & \cc                 & {CVC4} *              & {CVC4}                  \\
-    \rc
-    \cc UFDTLIA      &                    &                     & {Vampire} *           & {CVC4}                  \\
-    \cc UFIDL        & CVC4 \nc{Z3}       & {CVC4}              & {CVC4}                & CVC4 \nc{Z3}            \\
-    \cc UFLIA        & {CVC4}             & {CVC4}              & {CVC4}                & {CVC4}                  \\
-    \cc UFLRA        & \cc {CVC3}         & \cc Vampire \nc{Z3} & CVC4 \nc{Z3}          & CVC4 \nc{Z3}            \\
-    \cc UFNIA        & \cc {CVC4} *       & {Vampire}           & {Vampire}             & Vampire \nc{Z3/Vampire} \\
+    \wc ABVFP        &                          &                           &                                & \cc{cvc4} {CVC4} *        \\
+    \rc{cvc4}
+    \wc ALIA         & CVC4 \nc{Z3}             & CVC4 \nc{Z3}              & CVC4 \nc{Z3}                   & CVC4 \nc{Z3}              \\
+    \wc AUFBVDTLIA   &                          &                           & \cc{cvc4} {CVC4} *             & \cc{cvc4} {CVC4} *        \\
+    \wc AUFDTLIA     &                          &                           & \cc{cvc4} {CVC4} *             & \cc{cvc4} {CVC4}          \\
+    \rc{cvc4}
+    \wc AUFLIA       & {CVC4}                   & {CVC4}                    & {CVC4}                         & {CVC4}                    \\
+    \rc{vamp}
+    \wc AUFLIRA      & \cc{cvc4} CVC4 \nc{Z3}   & Vampire \nc{Z3}           & Vampire \nc{Z3}                & \cc{cvc4} CVC4 \nc{Z3}    \\
+    \rc{vamp}
+    \wc AUFNIRA      & \cc{cvc4} {CVC4} *       & {Vampire}                 & {Vampire}                      & \cc{cvc4} {CVC4}          \\
+    \rc{q3b}
+    \wc BV           & \cc{cvc4} CVC4 \nc{Z3} * & {Q3B}                     & Q3B \nc{Z3}                    &  \cc{cvc4} {CVC4}         \\
+    \wc BVFP         &                          &                           &                                & \cc{cvc4} {CVC4} *        \\
+    \wc FP           &                          &                           &                                & \cc{cvc4} {CVC4} *        \\
+    \rc{cvc4}
+    \wc LIA          & {CVC4}                   & {CVC4}                    & CVC4 \nc{Z3}                   & CVC4 \nc{Z3}              \\
+    \rc{cvc4}
+    \wc LRA          & {CVC4}                   & {CVC4}                    & CVC4 \nc{Z3}                   & CVC4 \nc{Z3}              \\
+    \rc{cvc4}
+    \wc NIA          & CVC4 \nc{Z3} *           & \cc{prob} ProB \nc{Z3}    & CVC4 \nc{Z3}                   & CVC4 \nc{Z3}              \\
+    \rc{vamp}
+    \wc NRA          & \cc{cvc4} {CVC4} *       & {Vampire}                 & \cc{redl} {Redlog}             & Vampire \nc{Z3} / Vampire \\
+    \rc{bool}
+    \wc QF\_ABV      & {Boolector}              & {Boolector}               & {Boolector}                    & {Boolector}               \\
+    \wc QF\_ABVFP    &                          &                           & {---}                          & \cc{cvc4} {CVC4}          \\
+    \rc{yices}
+    \wc QF\_ALIA     & {Yices2}                 & {Yices2}                  & {Yices2}                       & {Yices2}                  \\
+    \rc{cvc4}
+    \wc QF\_ANIA     & CVC4 \nc{Z3} *           & {CVC4} *                  & {CVC4} *                       & CVC4 \nc{Z3} *            \\
+    \rc{cvc4}
+    \wc QF\_AUFBV    & CVC4 \nc{MathSAT}        & CVC4 \nc{MathSAT}         & \cc{yices} Yices2 \nc{MathSAT} & {CVC4}                    \\
+    \rc{yices}
+    \wc QF\_AUFLIA   & {Yices2}                 & {Yices2}                  & {Yices2}                       & {Yices2}                  \\
+    \rc{cvc4}
+    \wc QF\_AUFNIA   & {CVC4} *                 & {CVC4} *                  & CVC4 \nc{Z3} *                 & CVC4 \nc{Z3} *            \\
+    \rc{yices}
+    \wc QF\_AX       & {Yices2}                 & {Yices2}                  & {Yices2}                       & {Yices2}                  \\
+    \rc{bool}
+    \wc QF\_BV       & {Boolector}              & {Boolector}               & {Boolector/MinkeyRink}         & {Boolector/MinkeyRink}    \\
+    \wc QF\_BVFP     & \cc{z} {Z3} *            & \wc \nc{Z3} *             & \cc{coli} COLIBRI \nc{Z3} *    & \cc{cvc4} {CVC4}          \\
+    \wc QF\_DT       &                          &                           & \cc{cvc4} {CVC4} *             & \cc{cvc4} {CVC4} *        \\
+    \rc{coli}
+    \wc QF\_FP       & \cc{z} {Z3} *            & \wc \nc{MathSAT} *        & COLIBRI \nc{Z3}                & {COLIBRI}                 \\
+    \rc{yices}
+    \wc QF\_IDL      & Yices2 \nc{Z3}           & Yices2 \nc{Z3}            & {Yices2}                       & {Yices2}                  \\
+    \rc{cvc4}
+    \wc QF\_LIA      & CVC4 \nc{MathSAT}        & CVC4 \nc{MathSAT}         & CVC4 \nc{MathSAT}              & \cc{spass} {SPASS-SATT}   \\
+    \rc{yices}
+    \wc QF\_LIRA     & {Yices2}                 & {Yices2}                  & Yices2 \nc{Z3}                 & Yices2 \nc{Z3}            \\
+    \rc{cvc4}
+    \wc QF\_LRA      &  {CVC4}                  & {CVC4}                    & {CVC4}                         & {CVC4}                    \\
+    \rc{cvc4}
+    \wc QF\_NIA      & \cc{apr} AProVE \nc{Z3}  & \cc{yices} Yices2 \nc{Z3} & {CVC4}                         & {CVC4}                    \\
+    \rc{cvc4}
+    \wc QF\_NIRA     & {CVC4}                   & {CVC4}                    & \cc{rat} {SMT-RAT}             & \cc{rat} {SMT-RAT}        \\
+    \rc{yices}
+    \wc QF\_NRA      & Yices2 \nc{Z3}           & Yices2 \nc{Z3}            & {Yices2}                       & Yices2 \nc{Z3}            \\
+    \rc{yices}
+    \wc QF\_RDL      & {Yices2}                 & {Yices2}                  & {Yices2}                       & {Yices2}                  \\
+    \wc QF\_SLIA     &                          &                           &                                & \cc{cvc4} {CVC4} *        \\
+    \rc{yices}
+    \wc QF\_UF       & {Yices2}                 & {Yices2}                  & {Yices2}                       & {Yices2}                  \\
+    \rc{bool}
+    \wc QF\_UFBV     & {Boolector}              & {Boolector}               & {Boolector}                    & {Boolector}               \\
+    \rc{yices}
+    \wc QF\_UFIDL    & {Yices2}                 & {Yices2}                  & {Yices2}                       & {Yices2}                  \\
+    \rc{yices}
+    \wc QF\_UFLIA    & Yices2 \nc{Z3}           & Yices2 \nc{Z3}            & {Yices2}                       & {Yices2}                  \\
+    \rc{yices}
+    \wc QF\_UFLRA    & {Yices2}                 & {Yices2}                  & {Yices2}                       & {Yices2}                  \\
+    \rc{yices}
+    \wc QF\_UFNIA    & \cc{cvc4} {CVC4} *       & {Yices2/CVC4}             & {Yices2}                       & {Yices2}                  \\
+    \rc{yices}
+    \wc QF\_UFNRA    & \cc{cvc3} CVC3 \nc{Z3} * & {Yices2}                  & Yices2 \nc{Z3}                 & {Yices2}                  \\
+    \rc{cvc4}
+    \wc UF           & {CVC4}                   & {CVC4}                    & \cc{vamp} {Vampire}            &  {CVC4/Vampire}           \\
+    \rc{cvc4}
+    \wc UFBV         & CVC4 \nc{Z3} *           & CVC4 \nc{Z3}              & CVC4 \nc{Z3} *                 & CVC4 \nc{Z3} *            \\
+    \wc UFDT         &                          &                           & \cc{cvc4} {CVC4} *             & \cc{cvc4} {CVC4}          \\
+    \wc UFDTLIA      &                          &                           & \cc{vamp} {Vampire} *          & \cc{cvc4} {CVC4}          \\
+    \rc{cvc4}
+    \wc UFIDL        & CVC4 \nc{Z3}             & {CVC4}                    & {CVC4}                         & CVC4 \nc{Z3}              \\
+    \rc{cvc4}
+    \wc UFLIA        & {CVC4}                   & {CVC4}                    & {CVC4}                         & {CVC4}                    \\
+    \rc{cvc4}
+    \wc UFLRA        & \cc{cvc3} {CVC3}         & \cc{vamp} Vampire \nc{Z3} & CVC4 \nc{Z3}                   & CVC4 \nc{Z3}              \\
+    \rc{vamp}
+    \wc UFNIA        & \cc{cvc4} {CVC4} *       & {Vampire}                 & {Vampire}                      & Vampire \nc{Z3} / Vampire \\
     \bottomrule

### 2019-03-20 2018/report/table-winners-unsat-core.tex
Use colors for winners tables.

@@
   \scalebox{.88}{%
-    \begin{tabular}{r@{\hskip 1em}>{\columncolor[gray]{.95}[.25em][.5em]}c@{\hskip 1em}>{\columncolor[gray]{.95}[.5em][.5em]}c@{\hskip 1em}>{\columncolor[gray]{.95}[.5em][.5em]}c}
+    \begin{tabular}{r@{\hskip 1em}>{\columncolor{white}[.25em][.5em]}c@{\hskip 1em}>{\columncolor{white}[.5em][.5em]}c@{\hskip 1em}>{\columncolor{white}[.5em][.5em]}c}
       \toprule
-    \rc
+      \rc{white}
       Division       & 2016                                 & 2017                                & 2018                           \\
       \hline \hline
-    \cc ALIA       & \cc \nc{Z3} *                  & CVC4 \nc{Z3} *                      & CVC4 \nc{Z3} *           \\
-    \cc AUFBVDTLIA & \cc                            & \cc                                 & CVC4 *                   \\
-    \cc AUFLIA     & \cc \nc{Z3} *                  & CVC4 \nc{Z3} *                      & CVC4 *                   \\
-    \cc AUFLIRA    & \cc \nc{Z3} *                  & CVC4 \nc{Z3} *                      & CVC4 *                   \\
-    \cc AUFNIRA    & \cc \nc{Z3} *                  & CVC4 *                              & CVC4 *                   \\
-    \cc BV         & \cc \nc{Z3} *                  & CVC4 \nc{Z3} *                      & CVC4 \nc{Z3} *           \\
-    \cc LIA        & \cc \nc{veriT} *               & CVC4 *                              & CVC4 \nc{Z3} *           \\
-    \cc LRA        & \cc \nc{veriT} *               & CVC4 *                              & CVC4 *                   \\
-    \cc NIA        & \cc \nc{Z3} *                  & CVC4 / CVC4 \nc{Z3}*                & CVC4 *                   \\
-    \cc NRA        & \cc \nc{Z3} *                  & CVC4 \nc{Z3} *                      & CVC4 \nc{Z3} *           \\
-    \cc QF\_ABV    & \cc \nc{Z3} *                  & CVC4 \nc{Z3} *                      & Yices2                   \\
-    \cc QF\_ABVFP  & \cc                            & \cc ---                             & \cc CVC4 *               \\
-    \rc
-    \cc QF\_ALIA   & SMTInterpol \nc{Z3} *          & SMTInterpol \nc{Z3}                 & Yices2 \nc{Z3}           \\
-    \cc QF\_ANIA   & \cc \nc{Z3} *                  & CVC4 *                              & CVC4 *                   \\
-    \rc
-    \cc QF\_AUFBV  & \nc{Z3} *                      & CVC4 \nc{MathSAT} *                 & Yices2 \nc{MathSAT}      \\
-    \cc QF\_AUFLIA & \cc SMTInterpol \nc{Z3} *      & CVC4                                & CVC4                     \\
-    \cc QF\_AUFNIA & \cc \nc{Z3} *                  & CVC4 \nc{Z3} *                      & CVC4 \nc{Z3} *           \\
-    \drc
-    \cc QF\_AX     & SMTInterpol \nc{Z3} *          & SMTInterpol \nc{Z3}                 & \cc Yices2               \\
-    \rc
-    \cc QF\_BV     & \nc{MathSAT} *                 & CVC4 \nc{MathSAT} *                 & Yices2                   \\
-    \cc QF\_BVFP   & \nc{Z3} *                      & \nc{Z3} *                           & \cc CVC4 \nc{Z3} *       \\
-    \rc
-    \cc QF\_DT     &                                &                                     & CVC4 *                   \\
-    \rc
-    \cc QF\_FP     & \nc{MathSAT} *                 & \nc{Z3} *                           & CVC4 *                   \\
-    \cc QF\_IDL    & \cc SMTInterpol \nc{Z3} *      & CVC4 \nc{Z3}                        & CVC4 \nc{Z3}             \\
-    \drc
-    \cc QF\_LIA    & SMTInterpol \nc{Z3} *          & SMTInterpol / SMTInterpol \nc{Z3}   & SMTInterpol              \\
-    \cc QF\_LIRA   & \cc SMTInterpol \nc{Z3} *      & CVC4 \nc{Z3}                        & CVC4 \nc{Z3}             \\
-    \drc
-    \cc QF\_LRA    & SMTInterpol *                  & SMTInterpol                         & SMTInterpol              \\
-    \cc QF\_NIA    & \cc \nc{Z3} *                  & CVC4 \nc{Z3} *                      & CVC4 \nc{Z3} *           \\
-    \cc QF\_NIRA   & \cc \nc{Z3} *                  & CVC4 \nc{Z3} *                      & CVC4 \nc{Z3} *           \\
-    \cc QF\_NRA    & \cc \nc{Z3} *                  & CVC4 *                              & CVC4 *                   \\
-    \cc QF\_RDL    & \cc SMTInterpol \nc{veriT} *   & CVC4 \nc{Z3}                        & CVC4 \nc{Z3}             \\
-    \cc QF\_UF     & \cc SMTInterpol \nc{MathSAT} * & CVC4                                & CVC4                     \\
-    \rc
-    \cc QF\_UFBV   & \nc{MathSAT} *                 & CVC4 \nc{MathSAT} *                 & Yices2 \nc{Z3}           \\
-    \drc
-    \cc QF\_UFIDL  & SMTInterpol \nc{Z3} *          & SMTInterpol \nc{Z3}                 & \cc Yices2               \\
-    \drc
-    \cc QF\_UFLIA  & SMTInterpol \nc{MathSAT} *     & SMTInterpol \nc{Z3}                 & SMTInterpol \nc{Z3}      \\
-    \drc
-    \cc QF\_UFLRA  & SMTInterpol \nc{Z3} *          & SMTInterpol \nc{MathSAT}            & \cc Yices2 \nc{MathSAT}  \\
-    \cc QF\_UFNIA  & \cc \nc{Z3} *                  & CVC4 \nc{Z3} *                      & CVC4 \nc{Z3} *           \\
-    \cc QF\_UFNRA  & \cc \nc{Z3} *                  & CVC4 \nc{Z3} *                      & CVC4 \nc{Z3} *           \\
-    \cc UF         & \cc \nc{Z3} *                  & CVC4 *                              & CVC4 *                   \\
-    \cc UFBV       & \cc \nc{Z3} *                  & CVC4 \nc{Z3} *                      & CVC4 *                   \\
-    \rc
-    \cc UFDT       &                                &                                     & CVC4 *                   \\
-    \cc UFIDL      & \cc \nc{Z3} *                  & CVC4 *                              & CVC4 *                   \\
-    \cc UFLIA      & \cc \nc{Z3} *                  & CVC4 *                              & CVC4 *                   \\
-    \cc UFLRA      & \cc \nc{Z3} *                  & CVC4 \nc{Z3} *                      & CVC4 \nc{Z3} *           \\
-    \cc UFNIA      & \cc \nc{Z3} *                  & CVC4 *                              & CVC4 *                   \\
+      \rc{cvc4}
+      \wc ALIA       & \wc \nc{Z3} *                        & CVC4 \nc{Z3} *                      & CVC4 \nc{Z3} *                 \\
+      \wc AUFBVDTLIA &                                      &                                     & \cc{cvc4} CVC4 *               \\
+      \rc{cvc4}
+      \wc AUFLIA     & \wc \nc{Z3} *                        & CVC4 \nc{Z3} *                      & CVC4 *                         \\
+      \rc{cvc4}
+      \wc AUFLIRA    & \wc \nc{Z3} *                        & CVC4 \nc{Z3} *                      & CVC4 *                         \\
+      \rc{cvc4}
+      \wc AUFNIRA    & \wc \nc{Z3} *                        & CVC4 *                              & CVC4 *                         \\
+      \rc{cvc4}
+      \wc BV         & \wc \nc{Z3} *                        & CVC4 \nc{Z3} *                      & CVC4 \nc{Z3} *                 \\
+      \rc{cvc4}
+      \wc LIA        & \wc \nc{veriT} *                     & CVC4 *                              & CVC4 \nc{Z3} *                 \\
+      \rc{cvc4}
+      \wc LRA        & \wc \nc{veriT} *                     & CVC4 *                              & CVC4 *                         \\
+      \rc{cvc4}
+      \wc NIA        & \wc \nc{Z3} *                        & CVC4 / CVC4 \nc{Z3}*                & CVC4 *                         \\
+      \rc{cvc4}
+      \wc NRA        & \wc \nc{Z3} *                        & CVC4 \nc{Z3} *                      & CVC4 \nc{Z3} *                 \\
+      \wc QF\_ABV    & \wc \nc{Z3} *                        & \cc{cvc4} CVC4 \nc{Z3} *            & \cc{yices} Yices2              \\
+      \wc QF\_ABVFP  &                                      & ---                                 & \cc{cvc4} CVC4 *               \\
+      \rc{smti}
+      \wc QF\_ALIA   & SMTInterpol \nc{Z3} *                & SMTInterpol \nc{Z3}                 & \cc{yices} Yices2 \nc{Z3}      \\
+      \rc{cvc4}
+      \wc QF\_ANIA   & \wc \nc{Z3} *                        & CVC4 *                              & CVC4 *                         \\
+      \wc QF\_AUFBV  & \nc{Z3} *                            & \cc{cvc4} CVC4 \nc{MathSAT} *       & \cc{yices} Yices2 \nc{MathSAT} \\
+      \rc{cvc4}
+      \wc QF\_AUFLIA & \cc{smti} SMTInterpol \nc{Z3} *      & CVC4                                & CVC4                           \\
+      \rc{cvc4}
+      \wc QF\_AUFNIA & \wc \nc{Z3} *                        & CVC4 \nc{Z3} *                      & CVC4 \nc{Z3} *                 \\
+      \rc{smti}
+      \wc QF\_AX     & SMTInterpol \nc{Z3} *                & SMTInterpol \nc{Z3}                 & \cc{yices} Yices2              \\
+      \wc QF\_BV     & \nc{MathSAT} *                       & \cc{cvc4} CVC4 \nc{MathSAT} *       & \cc{yices} Yices2              \\
+      \wc QF\_BVFP   & \nc{Z3} *                            & \nc{Z3} *                           & \cc{cvc4} CVC4 \nc{Z3} *       \\
+      \wc QF\_DT     &                                      &                                     & \cc{cvc4} CVC4 *               \\
+      \wc QF\_FP     & \nc{MathSAT} *                       & \nc{Z3} *                           & \cc{cvc4} CVC4 *               \\
+      \rc{cvc4}
+      \wc QF\_IDL    & \cc{smti} SMTInterpol \nc{Z3} *      & CVC4 \nc{Z3}                        & CVC4 \nc{Z3}                   \\
+      \rc{smti}
+      \wc QF\_LIA    & SMTInterpol \nc{Z3} *                & SMTInterpol / SMTInterpol \nc{Z3}   & SMTInterpol                    \\
+      \rc{cvc4}
+      \wc QF\_LIRA   & \cc{smti} SMTInterpol \nc{Z3} *      & CVC4 \nc{Z3}                        & CVC4 \nc{Z3}                   \\
+      \rc{smti}
+      \wc QF\_LRA    & SMTInterpol *                        & SMTInterpol                         & SMTInterpol                    \\
+      \rc{cvc4}
+      \wc QF\_NIA    & \wc \nc{Z3} *                        & CVC4 \nc{Z3} *                      & CVC4 \nc{Z3} *                 \\
+      \rc{cvc4}
+      \wc QF\_NIRA   & \wc \nc{Z3} *                        & CVC4 \nc{Z3} *                      & CVC4 \nc{Z3} *                 \\
+      \rc{cvc4}
+      \wc QF\_NRA    & \wc \nc{Z3} *                        & CVC4 *                              & CVC4 *                         \\
+      \rc{cvc4}
+      \wc QF\_RDL    & \cc{smti} SMTInterpol \nc{veriT} *   & CVC4 \nc{Z3}                        & CVC4 \nc{Z3}                   \\
+      \rc{cvc4}
+      \wc QF\_UF     & \cc{smti} SMTInterpol \nc{MathSAT} * & CVC4                                & CVC4                           \\
+      \wc QF\_UFBV   & \nc{MathSAT} *                       & \cc{cvc4} CVC4 \nc{MathSAT} *       & \cc{yices} Yices2 \nc{Z3}      \\
+      \rc{smti}
+      \wc QF\_UFIDL  & SMTInterpol \nc{Z3} *                & SMTInterpol \nc{Z3}                 & \cc{yices} Yices2              \\
+      \rc{smti}
+      \wc QF\_UFLIA  & SMTInterpol \nc{MathSAT} *           & SMTInterpol \nc{Z3}                 & SMTInterpol \nc{Z3}            \\
+      \rc{smti}
+      \wc QF\_UFLRA  & SMTInterpol \nc{Z3} *                & SMTInterpol \nc{MathSAT}            & \cc{yices} Yices2 \nc{MathSAT} \\
+      \rc{cvc4}
+      \wc QF\_UFNIA  & \wc \nc{Z3} *                        & CVC4 \nc{Z3} *                      & CVC4 \nc{Z3} *                 \\
+      \rc{cvc4}
+      \wc QF\_UFNRA  & \wc \nc{Z3} *                        & CVC4 \nc{Z3} *                      & CVC4 \nc{Z3} *                 \\
+      \rc{cvc4}
+      \wc UF         & \wc \nc{Z3} *                        & CVC4 *                              & CVC4 *                         \\
+      \rc{cvc4}
+      \wc UFBV       & \wc \nc{Z3} *                        & CVC4 \nc{Z3} *                      & CVC4 *                         \\
+      \wc UFDT       &                                      &                                     & \cc{cvc4} CVC4 *               \\
+      \rc{cvc4}
+      \wc UFIDL      & \wc \nc{Z3} *                        & CVC4 *                              & CVC4 *                         \\
+      \rc{cvc4}
+      \wc UFLIA      & \wc \nc{Z3} *                        & CVC4 *                              & CVC4 *                         \\
+      \rc{cvc4}
+      \wc UFLRA      & \wc \nc{Z3} *                        & CVC4 \nc{Z3} *                      & CVC4 \nc{Z3} *                 \\
+      \rc{cvc4}
+      \wc UFNIA      & \wc \nc{Z3} *                        & CVC4 *                              & CVC4 *                         \\
     \end{tabular}

### 2019-03-20 2018/report/table-winners-main.tex
Use gray text font instead of * for non-competitive divisions.

@@
     \hline \hline
-    \wc ABVFP        &                          &                           &                                & \cc{cvc4} {CVC4} *        \\
+    \wc ABVFP        &                              &                           &                                 & \nonc \cc{cvc4} {CVC4}    \\
     \rc{cvc4}
     \wc ALIA         & CVC4 \nc{Z3}                 & CVC4 \nc{Z3}              & CVC4 \nc{Z3}                    & CVC4 \nc{Z3}              \\
-    \wc AUFBVDTLIA   &                          &                           & \cc{cvc4} {CVC4} *             & \cc{cvc4} {CVC4} *        \\
-    \wc AUFDTLIA     &                          &                           & \cc{cvc4} {CVC4} *             & \cc{cvc4} {CVC4}          \\
+    \wc AUFBVDTLIA   &                              &                           & \nonc \cc{cvc4} {CVC4}          & \nonc \cc{cvc4} {CVC4}    \\
+    \wc AUFDTLIA     &                              &                           & \nonc \cc{cvc4} {CVC4}          & \cc{cvc4} {CVC4}          \\
     \rc{cvc4}
@@
     \rc{vamp}
-    \wc AUFNIRA      & \cc{cvc4} {CVC4} *       & {Vampire}                 & {Vampire}                      & \cc{cvc4} {CVC4}          \\
+    \wc AUFNIRA      & \nonc \cc{cvc4} {CVC4}       & {Vampire}                 & {Vampire}                       & \cc{cvc4} {CVC4}          \\
     \rc{q3b}
-    \wc BV           & \cc{cvc4} CVC4 \nc{Z3} * & {Q3B}                     & Q3B \nc{Z3}                    &  \cc{cvc4} {CVC4}         \\
-    \wc BVFP         &                          &                           &                                & \cc{cvc4} {CVC4} *        \\
-    \wc FP           &                          &                           &                                & \cc{cvc4} {CVC4} *        \\
+    \wc BV           & \nonc \cc{cvc4} CVC4 \nc{Z3} & {Q3B}                     & Q3B \nc{Z3}                     & \cc{cvc4} {CVC4}          \\
+    \wc BVFP         &                              &                           &                                 & \nonc \cc{cvc4} {CVC4}    \\
+    \wc FP           &                              &                           &                                 & \nonc \cc{cvc4} {CVC4}    \\
     \rc{cvc4}
@@
     \rc{cvc4}
-    \wc NIA          & CVC4 \nc{Z3} *           & \cc{prob} ProB \nc{Z3}    & CVC4 \nc{Z3}                   & CVC4 \nc{Z3}              \\
+    \wc NIA          & \nonc CVC4 \nc{Z3}           & \cc{prob} ProB \nc{Z3}    & CVC4 \nc{Z3}                    & CVC4 \nc{Z3}              \\
     \rc{vamp}
-    \wc NRA          & \cc{cvc4} {CVC4} *       & {Vampire}                 & \cc{redl} {Redlog}             & Vampire \nc{Z3} / Vampire \\
+    \wc NRA          & \nonc \cc{cvc4} {CVC4}       & {Vampire}                 & \cc{redl} {Redlog}              & Vampire \nc{Z3} / Vampire \\
     \rc{bool}
@@
     \rc{cvc4}
-    \wc QF\_ANIA     & CVC4 \nc{Z3} *           & {CVC4} *                  & {CVC4} *                       & CVC4 \nc{Z3} *            \\
+    \wc QF\_ANIA     & \nonc CVC4 \nc{Z3}           & \nonc {CVC4}                & \nonc {CVC4}                  & \nonc CVC4 \nc{Z3}        \\
     \rc{cvc4}
@@
     \rc{cvc4}
-    \wc QF\_AUFNIA   & {CVC4} *                 & {CVC4} *                  & CVC4 \nc{Z3} *                 & CVC4 \nc{Z3} *            \\
+    \wc QF\_AUFNIA   & \nonc {CVC4}                 & \nonc {CVC4}              & \nonc CVC4 \nc{Z3}              & \nonc CVC4 \nc{Z3}        \\
     \rc{yices}
@@
     \wc QF\_BV       & {Boolector}                  & {Boolector}               & {Boolector/MinkeyRink}          & {Boolector/MinkeyRink}    \\
-    \wc QF\_BVFP     & \cc{z} {Z3} *            & \wc \nc{Z3} *             & \cc{coli} COLIBRI \nc{Z3} *    & \cc{cvc4} {CVC4}          \\
-    \wc QF\_DT       &                          &                           & \cc{cvc4} {CVC4} *             & \cc{cvc4} {CVC4} *        \\
+    \wc QF\_BVFP     & \nonc \cc{z} {Z3}            & \nonc \wc \nc{Z3}         & \nonc \cc{coli} COLIBRI \nc{Z3} & \cc{cvc4} {CVC4}          \\
+    \wc QF\_DT       &                              &                           & \nonc \cc{cvc4} {CVC4}          & \nonc \cc{cvc4} {CVC4}    \\
     \rc{coli}
-    \wc QF\_FP       & \cc{z} {Z3} *            & \wc \nc{MathSAT} *        & COLIBRI \nc{Z3}                & {COLIBRI}                 \\
+    \wc QF\_FP       & \nonc \cc{z} {Z3}            & \nonc \wc \nc{MathSAT}    & COLIBRI \nc{Z3}                 & {COLIBRI}                 \\
     \rc{yices}
@@
     \wc QF\_RDL      & {Yices2}                     & {Yices2}                  & {Yices2}                        & {Yices2}                  \\
-    \wc QF\_SLIA     &                          &                           &                                & \cc{cvc4} {CVC4} *        \\
+    \wc QF\_SLIA     &                              &                           &                                 & \nonc \cc{cvc4} {CVC4}    \\
     \rc{yices}
@@
     \rc{yices}
-    \wc QF\_UFNIA    & \cc{cvc4} {CVC4} *       & {Yices2/CVC4}             & {Yices2}                       & {Yices2}                  \\
+    \wc QF\_UFNIA    & \nonc \cc{cvc4} {CVC4}       & {Yices2/CVC4}             & {Yices2}                        & {Yices2}                  \\
     \rc{yices}
-    \wc QF\_UFNRA    & \cc{cvc3} CVC3 \nc{Z3} * & {Yices2}                  & Yices2 \nc{Z3}                 & {Yices2}                  \\
+    \wc QF\_UFNRA    & \nonc \cc{cvc3} CVC3 \nc{Z3} & {Yices2}                  & Yices2 \nc{Z3}                  & {Yices2}                  \\
     \rc{cvc4}
@@
     \rc{cvc4}
-    \wc UFBV         & CVC4 \nc{Z3} *           & CVC4 \nc{Z3}              & CVC4 \nc{Z3} *                 & CVC4 \nc{Z3} *            \\
-    \wc UFDT         &                          &                           & \cc{cvc4} {CVC4} *             & \cc{cvc4} {CVC4}          \\
-    \wc UFDTLIA      &                          &                           & \cc{vamp} {Vampire} *          & \cc{cvc4} {CVC4}          \\
+    \wc UFBV         & \nonc CVC4 \nc{Z3}           & CVC4 \nc{Z3}              & \nonc CVC4 \nc{Z3}              & \nonc CVC4 \nc{Z3}        \\
+    \wc UFDT         &                              &                           & \nonc \cc{cvc4} {CVC4}          & \cc{cvc4} {CVC4}          \\
+    \wc UFDTLIA      &                              &                           & \nonc \cc{vamp} {Vampire}       & \cc{cvc4} {CVC4}          \\
     \rc{cvc4}
@@
     \rc{vamp}
-    \wc UFNIA        & \cc{cvc4} {CVC4} *       & {Vampire}                 & {Vampire}                      & Vampire \nc{Z3} / Vampire \\
+    \wc UFNIA        & \nonc \cc{cvc4} {CVC4}       & {Vampire}                 & {Vampire}                       & Vampire \nc{Z3} / Vampire \\
     \bottomrule

### 2019-03-20 2018/report/table-winners-unsat-core.tex
Use gray text font instead of * for non-competitive divisions.

--- 2019-03-19 2018/report/table-winners-unsat-core.tex
@@
   \scalebox{.88}{%
-    \begin{tabular}{r@{\hskip 1em}>{\columncolor[gray]{.95}[.25em][.5em]}c@{\hskip 1em}>{\columncolor[gray]{.95}[.5em][.5em]}c@{\hskip 1em}>{\columncolor[gray]{.95}[.5em][.5em]}c}
+    \begin{tabular}{r@{\hskip 1em}>{\nonc \columncolor{white}[.25em][.5em]}c@{\hskip 1em}>{\columncolor{white}[.5em][.5em]}c@{\hskip 1em}>{\columncolor{white}[.5em][.5em]}c}
       \toprule
-    \rc
+      \rc{white}
       Division       & 2016                                & 2017                              & 2018                           \\
       \hline \hline
-    \cc ALIA       & \cc \nc{Z3} *                  & CVC4 \nc{Z3} *                      & CVC4 \nc{Z3} *           \\
-    \cc AUFBVDTLIA & \cc                            & \cc                                 & CVC4 *                   \\
-    \cc AUFLIA     & \cc \nc{Z3} *                  & CVC4 \nc{Z3} *                      & CVC4 *                   \\
-    \cc AUFLIRA    & \cc \nc{Z3} *                  & CVC4 \nc{Z3} *                      & CVC4 *                   \\
-    \cc AUFNIRA    & \cc \nc{Z3} *                  & CVC4 *                              & CVC4 *                   \\
-    \cc BV         & \cc \nc{Z3} *                  & CVC4 \nc{Z3} *                      & CVC4 \nc{Z3} *           \\
-    \cc LIA        & \cc \nc{veriT} *               & CVC4 *                              & CVC4 \nc{Z3} *           \\
-    \cc LRA        & \cc \nc{veriT} *               & CVC4 *                              & CVC4 *                   \\
-    \cc NIA        & \cc \nc{Z3} *                  & CVC4 / CVC4 \nc{Z3}*                & CVC4 *                   \\
-    \cc NRA        & \cc \nc{Z3} *                  & CVC4 \nc{Z3} *                      & CVC4 \nc{Z3} *           \\
-    \cc QF\_ABV    & \cc \nc{Z3} *                  & CVC4 \nc{Z3} *                      & Yices2                   \\
-    \cc QF\_ABVFP  & \cc                            & \cc ---                             & \cc CVC4 *               \\
-    \rc
-    \cc QF\_ALIA   & SMTInterpol \nc{Z3} *          & SMTInterpol \nc{Z3}                 & Yices2 \nc{Z3}           \\
-    \cc QF\_ANIA   & \cc \nc{Z3} *                  & CVC4 *                              & CVC4 *                   \\
-    \rc
-    \cc QF\_AUFBV  & \nc{Z3} *                      & CVC4 \nc{MathSAT} *                 & Yices2 \nc{MathSAT}      \\
-    \cc QF\_AUFLIA & \cc SMTInterpol \nc{Z3} *      & CVC4                                & CVC4                     \\
-    \cc QF\_AUFNIA & \cc \nc{Z3} *                  & CVC4 \nc{Z3} *                      & CVC4 \nc{Z3} *           \\
-    \drc
-    \cc QF\_AX     & SMTInterpol \nc{Z3} *          & SMTInterpol \nc{Z3}                 & \cc Yices2               \\
-    \rc
-    \cc QF\_BV     & \nc{MathSAT} *                 & CVC4 \nc{MathSAT} *                 & Yices2                   \\
-    \cc QF\_BVFP   & \nc{Z3} *                      & \nc{Z3} *                           & \cc CVC4 \nc{Z3} *       \\
-    \rc
-    \cc QF\_DT     &                                &                                     & CVC4 *                   \\
-    \rc
-    \cc QF\_FP     & \nc{MathSAT} *                 & \nc{Z3} *                           & CVC4 *                   \\
-    \cc QF\_IDL    & \cc SMTInterpol \nc{Z3} *      & CVC4 \nc{Z3}                        & CVC4 \nc{Z3}             \\
-    \drc
-    \cc QF\_LIA    & SMTInterpol \nc{Z3} *          & SMTInterpol / SMTInterpol \nc{Z3}   & SMTInterpol              \\
-    \cc QF\_LIRA   & \cc SMTInterpol \nc{Z3} *      & CVC4 \nc{Z3}                        & CVC4 \nc{Z3}             \\
-    \drc
-    \cc QF\_LRA    & SMTInterpol *                  & SMTInterpol                         & SMTInterpol              \\
-    \cc QF\_NIA    & \cc \nc{Z3} *                  & CVC4 \nc{Z3} *                      & CVC4 \nc{Z3} *           \\
-    \cc QF\_NIRA   & \cc \nc{Z3} *                  & CVC4 \nc{Z3} *                      & CVC4 \nc{Z3} *           \\
-    \cc QF\_NRA    & \cc \nc{Z3} *                  & CVC4 *                              & CVC4 *                   \\
-    \cc QF\_RDL    & \cc SMTInterpol \nc{veriT} *   & CVC4 \nc{Z3}                        & CVC4 \nc{Z3}             \\
-    \cc QF\_UF     & \cc SMTInterpol \nc{MathSAT} * & CVC4                                & CVC4                     \\
-    \rc
-    \cc QF\_UFBV   & \nc{MathSAT} *                 & CVC4 \nc{MathSAT} *                 & Yices2 \nc{Z3}           \\
-    \drc
-    \cc QF\_UFIDL  & SMTInterpol \nc{Z3} *          & SMTInterpol \nc{Z3}                 & \cc Yices2               \\
-    \drc
-    \cc QF\_UFLIA  & SMTInterpol \nc{MathSAT} *     & SMTInterpol \nc{Z3}                 & SMTInterpol \nc{Z3}      \\
-    \drc
-    \cc QF\_UFLRA  & SMTInterpol \nc{Z3} *          & SMTInterpol \nc{MathSAT}            & \cc Yices2 \nc{MathSAT}  \\
-    \cc QF\_UFNIA  & \cc \nc{Z3} *                  & CVC4 \nc{Z3} *                      & CVC4 \nc{Z3} *           \\
-    \cc QF\_UFNRA  & \cc \nc{Z3} *                  & CVC4 \nc{Z3} *                      & CVC4 \nc{Z3} *           \\
-    \cc UF         & \cc \nc{Z3} *                  & CVC4 *                              & CVC4 *                   \\
-    \cc UFBV       & \cc \nc{Z3} *                  & CVC4 \nc{Z3} *                      & CVC4 *                   \\
-    \rc
-    \cc UFDT       &                                &                                     & CVC4 *                   \\
-    \cc UFIDL      & \cc \nc{Z3} *                  & CVC4 *                              & CVC4 *                   \\
-    \cc UFLIA      & \cc \nc{Z3} *                  & CVC4 *                              & CVC4 *                   \\
-    \cc UFLRA      & \cc \nc{Z3} *                  & CVC4 \nc{Z3} *                      & CVC4 \nc{Z3} *           \\
-    \cc UFNIA      & \cc \nc{Z3} *                  & CVC4 *                              & CVC4 *                   \\
+      \rc{cvc4}
+      \wc ALIA       & \wc \nc{Z3}                         & \nonc CVC4 \nc{Z3}                & \nonc CVC4 \nc{Z3}             \\
+      \wc AUFBVDTLIA &                                     &                                   & \nonc \cc{cvc4} CVC4           \\
+      \rc{cvc4}
+      \wc AUFLIA     & \wc \nc{Z3}                         & \nonc CVC4 \nc{Z3}                & \nonc CVC4                     \\
+      \rc{cvc4}
+      \wc AUFLIRA    & \wc \nc{Z3}                         & \nonc CVC4 \nc{Z3}                & \nonc CVC4                     \\
+      \rc{cvc4}
+      \wc AUFNIRA    & \wc \nc{Z3}                         & \nonc CVC4                        & \nonc CVC4                     \\
+      \rc{cvc4}
+      \wc BV         & \wc \nc{Z3}                         & \nonc CVC4 \nc{Z3}                & \nonc CVC4 \nc{Z3}             \\
+      \rc{cvc4}
+      \wc LIA        & \wc \nc{veriT}                      & \nonc CVC4                        & \nonc CVC4 \nc{Z3}             \\
+      \rc{cvc4}
+      \wc LRA        & \wc \nc{veriT}                      & \nonc CVC4                        & \nonc CVC4                     \\
+      \rc{cvc4}
+      \wc NIA        & \wc \nc{Z3}                         & \nonc CVC4 / CVC4 \nc{Z3}         & \nonc CVC4                     \\
+      \rc{cvc4}
+      \wc NRA        & \wc \nc{Z3}                         & \nonc CVC4 \nc{Z3}                & \nonc CVC4 \nc{Z3}             \\
+      \wc QF\_ABV    & \wc \nc{Z3}                         & \nonc \cc{cvc4} CVC4 \nc{Z3}      & \cc{yices} Yices2              \\
+      \wc QF\_ABVFP  &                                      & ---                              & \nonc \cc{cvc4} CVC4           \\
+      \rc{smti}
+      \wc QF\_ALIA   & SMTInterpol \nc{Z3}                 & SMTInterpol \nc{Z3}               & \cc{yices} Yices2 \nc{Z3}      \\
+      \rc{cvc4}
+      \wc QF\_ANIA   & \wc \nc{Z3}                         & \nonc CVC4                        & \nonc CVC4                     \\
+      \wc QF\_AUFBV  & \nc{Z3}                             & \nonc \cc{cvc4} CVC4 \nc{MathSAT} & \cc{yices} Yices2 \nc{MathSAT} \\
+      \rc{cvc4}
+      \wc QF\_AUFLIA & \cc{smti} SMTInterpol \nc{Z3}       & CVC4                              & CVC4                           \\
+      \rc{cvc4}
+      \wc QF\_AUFNIA & \wc \nc{Z3}                         & \nonc CVC4 \nc{Z3}                & \nonc CVC4 \nc{Z3}             \\
+      \rc{smti}
+      \wc QF\_AX     & SMTInterpol \nc{Z3}                 & SMTInterpol \nc{Z3}               & \cc{yices} Yices2              \\
+      \wc QF\_BV     & \nc{MathSAT}                        & \nonc \cc{cvc4} CVC4 \nc{MathSAT} & \cc{yices} Yices2              \\
+      \wc QF\_BVFP   & \nc{Z3}                             & \nonc \nc{Z3}                     & \nonc \cc{cvc4} CVC4 \nc{Z3}   \\
+      \wc QF\_DT     &                                     &                                   & \nonc \cc{cvc4} CVC4           \\
+      \wc QF\_FP     & \nc{MathSAT}                        & \nonc \nc{Z3}                     & \nonc \cc{cvc4} CVC4           \\
+      \rc{cvc4}
+      \wc QF\_IDL    & \cc{smti} SMTInterpol \nc{Z3}       & CVC4 \nc{Z3}                      & CVC4 \nc{Z3}                   \\
+      \rc{smti}
+      \wc QF\_LIA    & SMTInterpol \nc{Z3}                 & SMTInterpol / SMTInterpol \nc{Z3} & SMTInterpol                    \\
+      \rc{cvc4}
+      \wc QF\_LIRA   & \cc{smti} SMTInterpol \nc{Z3}       & CVC4 \nc{Z3}                      & CVC4 \nc{Z3}                   \\
+      \rc{smti}
+      \wc QF\_LRA    & SMTInterpol                         & SMTInterpol                       & SMTInterpol                    \\
+      \rc{cvc4}
+      \wc QF\_NIA    & \wc \nc{Z3}                         & \nonc CVC4 \nc{Z3}                & \nonc CVC4 \nc{Z3}             \\
+      \rc{cvc4}
+      \wc QF\_NIRA   & \wc \nc{Z3}                         & \nonc CVC4 \nc{Z3}                & \nonc CVC4 \nc{Z3}             \\
+      \rc{cvc4}
+      \wc QF\_NRA    & \wc \nc{Z3}                         & \nonc CVC4                        & \nonc CVC4                     \\
+      \rc{cvc4}
+      \wc QF\_RDL    & \cc{smti} SMTInterpol \nc{veriT}    & CVC4 \nc{Z3}                      & CVC4 \nc{Z3}                   \\
+      \rc{cvc4}
+      \wc QF\_UF     & \cc{smti} SMTInterpol \nc{MathSAT}  & CVC4                              & CVC4                           \\
+      \wc QF\_UFBV   & \nc{MathSAT}                        & \nonc \cc{cvc4} CVC4 \nc{MathSAT} & \cc{yices} Yices2 \nc{Z3}      \\
+      \rc{smti}
+      \wc QF\_UFIDL  & SMTInterpol \nc{Z3}                 & SMTInterpol \nc{Z3}               & \cc{yices} Yices2              \\
+      \rc{smti}
+      \wc QF\_UFLIA  & SMTInterpol \nc{MathSAT}            & SMTInterpol \nc{Z3}               & SMTInterpol \nc{Z3}            \\
+      \rc{smti}
+      \wc QF\_UFLRA  & SMTInterpol \nc{Z3}                 & SMTInterpol \nc{MathSAT}          & \cc{yices} Yices2 \nc{MathSAT} \\
+      \rc{cvc4}
+      \wc QF\_UFNIA  & \wc \nc{Z3}                         & \nonc CVC4 \nc{Z3}                & \nonc CVC4 \nc{Z3}             \\
+      \rc{cvc4}
+      \wc QF\_UFNRA  & \wc \nc{Z3}                         & \nonc CVC4 \nc{Z3}                & \nonc CVC4 \nc{Z3}             \\
+      \rc{cvc4}
+      \wc UF         & \wc \nc{Z3}                         & \nonc CVC4                        & \nonc CVC4                     \\
+      \rc{cvc4}
+      \wc UFBV       & \wc \nc{Z3}                         & \nonc CVC4 \nc{Z3}                & \nonc CVC4                     \\
+      \wc UFDT       &                                     &                                   & \nonc \cc{cvc4} CVC4           \\
+      \rc{cvc4}
+      \wc UFIDL      & \wc \nc{Z3}                         & \nonc CVC4                        & \nonc CVC4                     \\
+      \rc{cvc4}
+      \wc UFLIA      & \wc \nc{Z3}                         & \nonc CVC4                        & \nonc CVC4                     \\
+      \rc{cvc4}
+      \wc UFLRA      & \wc \nc{Z3}                         & \nonc CVC4 \nc{Z3}                & \nonc CVC4 \nc{Z3}             \\
+      \rc{cvc4}
+      \wc UFNIA      & \wc \nc{Z3}                         & \nonc CVC4                        & \nonc CVC4                     \\
     \end{tabular}

### 2019-03-20 2018/report/SMT-COMP.tex
Fix
Add winner tables layout description.

@@
 
+\colorlet{bool}{blue!10}
+\colorlet{cvc4}{cyan!10}
+\colorlet{smti}{yellow!10}
+\colorlet{yices}{green!10}
+\colorlet{vamp}{orange!10}
+\colorlet{q3b}{red!10}
+\colorlet{prob}{gray!10}
+\colorlet{z}{Fuchsia!10}
+\colorlet{coli}{Brown!10}
+\colorlet{spass}{Lavender!10}
+\colorlet{apr}{PineGreen!10}
+\colorlet{rat}{Goldenrod!10}
+\colorlet{cvc3}{GreenYellow!10}
+\colorlet{redl}{Yellow!10}
+\colorlet{nonc}{black!55}
+
+\newcommand{\cc}[1]{\cellcolor{#1}}
+\newcommand{\wc}{\cc{white}}
+\newcommand{\rc}[1]{\rowcolor{#1}}
 \newcommand{\nc}[1]{{[}#1{]}}
-\newcommand{\cc}{\cellcolor{white}}
-\newcommand{\rc}{\rowcolor{white}}
-\newcommand{\drc}{\rowcolor[gray]{.9}}
-\newcommand{\dcc}{\cellcolor[gray]{.9}}
+
+\newcommand{\nonc}{\color{nonc}}
 
@@
 Tables~\ref{tab:winners-main}--\ref{tab:winners-unsat-core} show the
-highest-ranked solver for each division from 2015--2018.  Entries
+highest-ranked solver for each division from 2015--2018.
+Non-competitive divisions use gray font.
+Entries $A [B]$ indicate that solver $A$ was the highest competing solver,
+but non-competing solver $B$ actually ranked best if non-competing solvers
+are also taking into consideration.
+Entries
 $A/B$ indicate that solver~$A$ ranked first considering sequential
@@
 When the same solver ranked first in both, which is most often the
-case, its name appears just once.  A division is \emph{competitive} if
+case, its name appears just once.
+Table cell colors (other than white) indicate the best competing sequential
+solver performance, no cell color indicate that the best sequential solver
+performance was by a non-competing solver and no competing solvers participated
+in that division.
+A division is \emph{competitive} if
 at least two substantially different solvers (i.e., solvers from two

### 2019-03-20 2018/report/SMT-COMP.tex
Move and fix.

@@
 
+A division is \emph{competitive} if
+at least two substantially different solvers (i.e., solvers from two
+different teams) were submitted.  (Experimental divisions are never
+competitive.)  Official winners were declared only for competitive
+divisions.
+
 Tables~\ref{tab:winners-main}--\ref{tab:winners-unsat-core} show the
-highest-ranked solver for each division from 2015--2018.
-Non-competitive divisions use gray font.
+highest-ranked solvers for all (competitive and non-competitive) division from
+2015--2018.
+We include solvers that were running hors concours (and hence non-competing
+and ineligible to be recognized as official competition winners).
+Non-com-petitive divisions use gray font.
 Entries $A [B]$ indicate that solver $A$ was the highest competing solver,
@@
 Table cell colors (other than white) indicate the best competing sequential
-solver performance, no cell color indicate that the best sequential solver
+solver performance, no cell color indicates that the best sequential solver
 performance was by a non-competing solver and no competing solvers participated
 in that division.
-A division is \emph{competitive} if
-at least two substantially different solvers (i.e., solvers from two
-different teams) were submitted.  (Experimental divisions are never
-competitive.)  Official winners were declared only for competitive
-divisions; we are including all divisions here.  Moreover, we are
-including solvers that were running hors concours (and hence
-ineligible to be recognized as official competition winners).  Full
-division rankings are available from the competition website.
+Full division rankings are available from the competition website.
 

### 2019-03-21 2018/report/analysis/analysis.sh
Analysis scripts: Add support for application track.

@@ -14,11 +14,16 @@ MAINTRACK_2017="../../../2017/csv/Main_Track.csv"
 MAINTRACK_2017_RERUN="../../../2017/csv/Main_Track_Rerun_Timeouts.csv"
 MAINTRACK_2018="../../../2018/csv/Main_Track.csv"
 
+APPLICATION_2015="../../../2015/csv/Application_Track.csv"
+APPLICATION_2016="../../../2016/csv/Application_Track.csv"
+APPLICATION_2017="../../../2017/csv/Application_Track.csv"
+APPLICATION_2018="../../../2018/csv/Application_Track.csv"
+
 ################################################################################
 # check that all input files exist
 ################################################################################
 
-for FILE in "$MAINTRACK_2014" "$MAINTRACK_2015" "$MAINTRACK_2016" "$MAINTRACK_2017" "$MAINTRACK_2017_RERUN" "$MAINTRACK_2018"
+for FILE in "$MAINTRACK_2014" "$MAINTRACK_2015" "$MAINTRACK_2016" "$MAINTRACK_2017" "$MAINTRACK_2017_RERUN" "$MAINTRACK_2018" "$APPLICATION_2015" "$APPLICATION_2016" "$APPLICATION_2017" "$APPLICATION_2018"
 do
     if [[ ! -f "$FILE" ]]; then
         echo "Error: $FILE is not a regular file."
@@ -36,7 +41,14 @@ MT_2016="2016_Main_Track.csv"
 MT_2017="2017_Main_Track.csv"
 MT_2018="2018_Main_Track.csv"
 
+AP_2015="2015_Application_Track.csv"
+AP_2016="2016_Application_Track.csv"
+AP_2017="2017_Application_Track.csv"
+AP_2018="2018_Application_Track.csv"
+
 ################################################################################
+
+### Main track
 
 # the 2014 data lacks a "memory usage" column; we add one (with value
 # 0.0) for uniformity
@@ -68,57 +80,90 @@ sed -i -e 's:,Rerun Timeouts Datatype Divisions/:,:' "$MT_2017"
 # (for uniformity)
 tail -n +2 "$MAINTRACK_2018"|sed -e 's:,Other Divisions/:,:' > "$MT_2018"
 
+### Application track
+
+# strip column header line of application track files
+tail -n +2 "$APPLICATION_2015" > "$AP_2015"
[…]

### 2019-03-21 2018/report/analysis/unsound-solvers-app.sh

@@ -1,0 +1,15 @@
+#!/bin/bash
+
+set -e
+set -u
+
+# print a list of all solvers that have given an incorrect answer
+# (together with the respective division)
+
+while IFS=, read PAIR_ID BENCHMARK BENCHMARK_ID SOLVER SOLVER_ID CONFIG CONFIG_ID STATUS CPU_TIME WALL_TIME MEMORY RESULT WRONG CORRECT
+do
+    if [[ ("$WRONG" != "0") ]]; then
+        DIVISION=${BENCHMARK%%/*}
+        echo $DIVISION,$SOLVER,$SOLVER_ID
+    fi
+done < "$1"|LC_ALL=C sort -u

### 2019-03-21 2018/report/analysis/virtual-best-solver-app.sh

@@ -1,0 +1,18 @@
+#!/bin/bash
+
+set -e
+set -u
+
+# virtual best solver
+
+# only keep the best (highest number of correct answers) result for each
+# benchmark
+
+# Column  3: benchmark id
+#         8: status
+#        10: wall time
+#        14: correct answers
+
+awk -F , '$8=="complete"' "$1"|
+    sort -t , -k 3,3n -k 10,10n|
+    sort -t , -k 3,3n -u

### 2019-03-21 2018/report/plot/gen_common_results.py
Update plot generation files for application track.

@@ -39,7 +39,8 @@ if __name__ == "__main__":
         year = year.split(sep='.')[0]
         years = args.common_benchmarks.split('.')[-2]
         years = years.split('/')[-1]
-        years = years.replace('Common_Benchmarks_', '')
+        years = years.replace('Main_Track_Common_Benchmarks_', '')
+        years = years.replace('Application_Track_Common_Benchmarks_', '')
         outfile_name = "{}/{}_vbs_{}.csv".format(path, year, years)
         with open(outfile_name, 'w') as outfile:
             with open(args.vbs_data, 'r') as infile:

### 2019-03-21 2018/report/analysis/virtual-best-solver-app.sh
Fix vbs script for app track.

@@ -14,5 +14,5 @@ set -u
 #        14: correct answers
 
 awk -F , '$8=="complete"' "$1"|
-    sort -t , -k 3,3n -k 10,10n|
+    sort -t , -k 3,3n -k 14,14nr|
     sort -t , -k 3,3n -u

### 2019-03-22 2018/report/analysis/virtual-best-solver-app.sh
Fix vbs script for app track.

@@ -13,6 +13,4 @@ set -u
 #        10: wall time
 #        14: correct answers
 
-awk -F , '$8=="complete"' "$1"|
-    sort -t , -k 3,3n -k 14,14nr|
-    sort -t , -k 3,3n -u
+cat "$1"| sort -t , -k 3,3n -k 14,14nr| sort -t , -k 3,3n -u

### 2019-03-22 2018/report/SMT-COMP.tex
Add scripts for application track bar plots.

@@
   \scalebox{.45}{\includegraphics{%
-        plot/pdf/cactus_plot-Virtual_Best_Solver_(VBS)_2015-2018.pdf}}
+        plot/pdf/cactus_plot-Virtual_Best_Solver_(VBS)_Main_Track_2015-2018.pdf}}
   \caption{VBS on common benchmarks 2015-2018 of all logics in the Main track.}
@@
     \scalebox{.35}{\includegraphics{%
-        plot/pdf/cactus_plot-Virtual_Best_Solver_(VBS)_2014-2015.pdf}}
+        plot/pdf/cactus_plot-Virtual_Best_Solver_(VBS)_Main_Track_2014-2015.pdf}}
     \caption{2014 vs.~2015}
@@
     \scalebox{.35}{\includegraphics{%
-      plot/pdf/cactus_plot-Virtual_Best_Solver_(VBS)_2015-2016.pdf}}
+      plot/pdf/cactus_plot-Virtual_Best_Solver_(VBS)_Main_Track_2015-2016.pdf}}
     \caption{2015 vs.~2016}
@@
     \scalebox{.35}{\includegraphics{%
-      plot/pdf/cactus_plot-Virtual_Best_Solver_(VBS)_2016-2017.pdf}}
+      plot/pdf/cactus_plot-Virtual_Best_Solver_(VBS)_Main_Track_2016-2017.pdf}}
     \caption{2016 vs.~2017}
@@
     \scalebox{.35}{\includegraphics{%
-    plot/pdf/cactus_plot-Virtual_Best_Solver_(VBS)_2017-2018.pdf}}
+    plot/pdf/cactus_plot-Virtual_Best_Solver_(VBS)_Main_Track_2017-2018.pdf}}
     \caption{2017 vs.~2018}
@@
 \end{figure}
+
+\iffalse
+\begin{figure}
+  \centering
+  \scalebox{.45}{\includegraphics{%
+        plot/pdf/cactus_plot-Virtual_Best_Solver_(VBS)_Application_Track_2015-2018.pdf}}
+  \caption{VBS on common benchmarks 2015-2018 of all logics in the Application track.}
+  \label{fig:progress-all}
+\end{figure}
+
+\begin{figure}
+  \begin{subfigure}[t]{0.5\textwidth}
+    \scalebox{.35}{\includegraphics{%
+      plot/pdf/cactus_plot-Virtual_Best_Solver_(VBS)_Application_Track_2015-2016.pdf}}
+    \caption{2015 vs.~2016}
+  \end{subfigure}
+  \\[2ex]
+  \begin{subfigure}[t]{0.5\textwidth}
+    \scalebox{.35}{\includegraphics{%
+      plot/pdf/cactus_plot-Virtual_Best_Solver_(VBS)_Application_Track_2016-2017.pdf}}
+    \caption{2016 vs.~2017}
+  \end{subfigure}
+  \begin{subfigure}[t]{0.5\textwidth}
+    \scalebox{.35}{\includegraphics{%
+    plot/pdf/cactus_plot-Virtual_Best_Solver_(VBS)_Application_Track_2017-2018.pdf}}
+    \caption{2017 vs.~2018}
+  \end{subfigure}
+  \caption{VBS on common benchmarks for pairs of years of all logics in the
+  Application track.}
+  \label{fig:progress}
+\end{figure}
+\fi
 

### 2019-03-22 2018/report/plot/bar_plot.r

@@ -1,0 +1,37 @@
+library(tools)
+
+if(!dir.exists("pdf")) dir.create("pdf")
+args <- commandArgs(trailingOnly = TRUE)
+plot_title=args[1]
+fname_data <- args[2]
+
+fname=gsub(' ','_',plot_title,fixed=TRUE)
+fname_pdf=paste("pdf/bar_plot-",fname,".pdf",sep="")
+pdf(fname_pdf,width=9)
+
+colors=c("red2","deepskyblue4","orange","chartreuse3")
+
+par(cex=1.5)
+data=read.csv(fname_data,sep=",",head=F,comment.char="#")
+len=length(data[,1])
+xcol=vector(length=len)
+for(i in 1:len)
+{
+  xcol[i] <- colors[len+1-i]
+}
+
+bp <- barplot(data[,2],
+              col = xcol,
+              ylab="# Correct answers",
+              legend=colnames(data[0,2:2]),
+              las=1,
+              xaxt="n",
+              yaxt="n",
+              ylim=c(0,35000000),
+             )
+text(x=bp, y=data[,2], label=data[,2], pos=3, cex=0.8, col="black")
+axis(side=1, at=bp, labels=data[,1])
+ticks=sapply(axTicks(2), function(i) as.integer(i))
+labels=sprintf("%.0fM",ticks/1000000)
+axis(2, at=ticks, labels=labels)
+title(plot_title,outer=TRUE,line=-1,font.main=2)

### 2019-03-22 2018/report/plot/cactus_plot.r

@@ -27,7 +27,6 @@ xpch=vector(length=nfiles)
 xcol=vector(length=nfiles)
 datacol=10
 fname_data <- args[4]
-fname <- file_path_sans_ext(basename(fname_data))
 
 xvalues <- list()
 
@@ -40,7 +39,6 @@ if (nfiles >= 2)
   for (i in 2:nfiles)
   {
     fname_data <- args[i+3]
-    fname <- file_path_sans_ext(basename(fname_data))
     data=read.csv(fname_data,sep=",",head=F,comment.char="#")
     x=sort(ifelse(data[,datacol] > 1200, 1200, data[,datacol]))
     xvalues[[i]] <- x

### 2019-03-22 rules/rules19.tex
Add initial version of rules 2019 document.

--- 2018-07-14 rules/rules18.tex
@@
 \newcommand{\akey}[1]{\textbf{#1}}
+\newcommand{\todo}[1]{\textcolor{red}{[#1]}}
 
@@
 \author{%
-Matthias Heizmann \\
-University of Freiburg \\
-Germany \\
-{\small\href{mailto:heizmann@informatik.uni-freiburg.de}{\texttt{heizmann@informatik.uni-freiburg.de}}} \\
+Liana Hadarean \\
+Amazon \\
+USA \\
+{\small\href{mailto:hadarean@amazon.com}{\texttt{hadarean@amazon.com}}}\\
+\and
+Antti Hyvarinen \\
+Universita della Svizzera italiana \\
+Switzerland \\
+{\small\href{mailto:tjark.weber@it.uu.se}{\texttt{tjark.weber@it.uu.se}}} \\
 \and
@@
 {\small\href{mailto:giles.reger@manchester.ac.uk}{\texttt{giles.reger@manchester.ac.uk}}} \\
-\and
-Tjark Weber \\
-Uppsala University \\
-Sweden \\
-{\small\href{mailto:tjark.weber@it.uu.se}{\texttt{tjark.weber@it.uu.se}}} \\
 \\
@@
 \noindent Additional material will be made available at the
-competition web site, \url{www.smtcomp.org} or
-\url{smtcomp.sourceforge.net/2018}.
+competition web site, \url{www.smtcomp.org}.
 
@@
 \begin{description}
-\item[April~8] Deadline for new benchmark contributions.
-\item[May~15] Final versions of competition tools (e.g., benchmark
+\item[March~1] Deadline for new benchmark contributions.
+\item[May~1] Final versions of competition tools (e.g., benchmark
   scrambler) are made available.  Benchmark libraries are frozen.
-\item[May~27] Deadline for first versions of solvers (for all tracks),
+\item[May~19] Deadline for first versions of solvers (for all tracks),
   including information about which tracks and divisions are being
   entered, and magic numbers for benchmark scrambling.
-\item[June~10] Deadline for final versions of solvers, including
+\item[June~2] Deadline for final versions of solvers, including
   system descriptions.
-\item[June~11] Opening value of NYSE Composite Index used to complete
+\item[\todo{TODO}] Opening value of NYSE Composite Index used to complete
   random seed for benchmark scrambling.
-\item[July~12/13] SMT Workshop; end of competition, presentation of
+\item[July~7/8] SMT Workshop; end of competition, presentation of
   results.
@@
 
-SMT-COMP~2018 is part of the SMT Workshop~2018
-(\url{http://smt-workshop.cs.uiowa.edu/2018/}),
-which is affiliated with IJCAR~2018 (\url{http://ijcar2018.org/}),
-part of FLoC 2018 (\url{http://www.floc2018.org/}).
+SMT-COMP~2019 is part of the SMT Workshop~2019
+(\url{http://smt2019.galois.com/}),
+which is affiliated with SAT~2019 (\url{http://sat2019.tecnico.ulisboa.pt/}).
 The SMT Workshop will include a block of time to present the results of the
@@
 
-SMT-COMP 2018 will have three tracks: the conventional main track, an
-application (i.e., incremental) track, and an unsat-core track.
+SMT-COMP 2019 will have four tracks: the single problem track (formerly
+known as main track), the incremental track (formerly known as application
+track), the unsat-core track, and the (new) industry challenge track.
 
@@
   Sylvain Conchon, David D{\'e}harbe, Morgan Deters, Alberto Griggio,
-  Matthias Heizmann, Albert Oliveras, Giles Reger, Aaron Stump, and
-  Tjark Weber.}  describes the rules and competition procedures for
-SMT-COMP~2018.  The principal changes from the previous competition
-rules are the following:
+  Matthias Heizmann, Aina Niemetz, Albert Oliveras, Giles Reger, Aaron Stump,
+	and Tjark Weber.}  describes the rules and competition procedures for
+SMT-COMP~2019.
+\todo{update changes vs 2018}
+The principal changes from the previous competition rules are the following:
 \begin{itemize}

### 2019-03-22 rules/rules19.tex
rules 2019: Update submission information.

@@
 \begin{center}
-  \url{https://goo.gl/forms/3pAMFHsfDJqGqucR2}
+  \todo{\url{}submission form url}
 \end{center}
-A submission must also include a 32-bit unsigned integer.  These
-integer numbers, collected from all submissions, are used to seed the
+A submission must also include a \emph{system description} (see below) and a
+\emph{32-bit unsigned integer}.
+ These integer numbers, collected from all submissions, are used to seed the
 benchmark scrambler.
@@
 %
-As part of a submission, SMT-COMP entrants are strongly encouraged to
-provide a short (1--2 pages) description of the system.  This should
-include a list of all authors of the system, their present
+As part of a submission, SMT-COMP entrants \emph{must} provide a short (1--2
+pages) description of the system.
+This should include a list of all authors of the system, their present
 institutional affiliations, and any appropriate acknowledgements.  The

### 2019-03-22 rules/rules19.tex
Rules 2019: Update and add todos for sections up to 5.2.

@@
 \newcommand{\akey}[1]{\textbf{#1}}
-\newcommand{\todo}[1]{\textcolor{red}{[#1]}}
+\newcommand{\rem}[1]{\textcolor{red}{[#1]}}
+\newcommand{\an}[1]{\rem{#1 -- aina}}
+\newcommand{\ah}[1]{\rem{#1 -- antti}}
+\newcommand{\lh}[1]{\rem{#1 -- liana}}
+\newcommand{\gr}[1]{\rem{#1 -- giles}}
 
@@
   system descriptions.
-\item[\todo{TODO}] Opening value of NYSE Composite Index used to complete
+\item[\an{TODO}] Opening value of NYSE Composite Index used to complete
   random seed for benchmark scrambling.
@@
 
-SMT-COMP 2019 will have four tracks: the single problem track (formerly
+SMT-COMP 2019 will have five tracks: the single problem track (formerly
 known as main track), the incremental track (formerly known as application
-track), the unsat-core track, and the (new) industry challenge track.
+track), the unsat-core track, the (new) industry challenge track, and the
+(new) model validation track.
 
@@
 SMT-COMP~2019.
-\todo{update changes vs 2018}
+\an{update changes vs 2018}
 The principal changes from the previous competition rules are the following:
@@
 \begin{center}
-  \todo{\url{}submission form url}
+  \an{\url{}submission form url}
 \end{center}
@@
 SMT-COMP entrants must be submitted via StarExec (solvers) \emph{and}
-the above web form (accompanying information) until the end of {\bf
-  May~27, 2018} anywhere on earth.
-After this date no new entrants will be accepted.
+the above web form (accompanying information) until the end of
+{\bf May~19, 2019} anywhere on earth.
+After this date \emph{no new entrants} will be accepted.
 However, updates to existing entrants on StarExec
-will be accepted until the end of {\bf June~10, 2018} anywhere on earth.
+will be accepted until the end of {\bf June~2, 2019} anywhere on earth.
 
@@
 
+\an{Add information that these solver versions will be made available
+on the smt-comp website for archiving purposes? What are the implications of
+this?}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 The bulk of the computation will take place during the weeks leading
-up to SMT 2018.  Intermediate results will be regularly posted to the
+up to SMT 2019.  Intermediate results will be regularly posted to the
 SMT-COMP website as the competition runs.
@@
 
-\header{Input and output.}
+\header{Input and output. \rem{TODO: update}}
 %
@@
 
-The time limit~$T$ is yet to be determined.  It is anticipated to be
-at most 20~minutes of wall-clock time per solver/benchmark pair in the
-main track, and at most 40~minutes in the other tracks.\footnote{The
-  time limit may be adjusted once we know the number of competition
-  entrants and eligible benchmarks.}  Solvers that take more than this
-time limit will be killed.  Solvers are allowed to spawn other
-processes; these will be killed at approximately the same time as the
-first started process.
+The time limit~$T$ will be 40~minutes of wall-clock time per solver/benchmark
+pair in the single problem, incremental and unsat core tracks, \rem{TODO:
+XX}~minutes in the industry challenge track, and \rem{TODO: XX}~minutes in the
+model validation track \an{TODO: Need to elaborate how time is split? Do we
+need two time limits here, one for solving and one for
+validation?}.\footnote{\an{TODO: Is this obsolete?} The time limit may be
+adjusted once we know the number of competition entrants and eligible
+benchmarks.}  Solvers that take more than this time limit will be killed.
+Solvers are allowed to spawn other processes; these will be killed at
+approximately the same time as the first started process.
 
@@
 The main track competition uses a StarExec post-processor (named
-``SMT-COMP 2018") to accumulate the results.
+``SMT-COMP 2019") to accumulate the results.
 

### 2019-03-22 rules/rules19.tex
Rules 2019: Rename tracks.

@@
 
-SMT-COMP 2019 will have five tracks: the single problem track (formerly
-known as main track), the incremental track (formerly known as application
-track), the unsat-core track, the (new) industry challenge track, and the
-(new) model validation track.
+SMT-COMP 2019 will have five tracks: the single problem track (formerly known
+as Single Problem Track), the incremental track (formerly known as application
+track), the unsat-core track, the (new) industry challenge track, and the (new)
+model validation track.
 
@@
 single benchmark script, whose filename is presented as the solver's
-first command-line argument.  In the application track, a trace
+first command-line argument.  In the incremental track, a trace
 executor will send commands from a benchmark script to the solver's
@@
       previous competitions to run without changes.}
-  \item In the application track, the \akey{:print-success} option
+  \item In the incremental track, the \akey{:print-success} option
     must not be disabled.  The trace executor will send an initial
@@
   \begin{enumerate}
-    \item In the main and application track, named terms (i.e., terms
+    \item In the main and incremental track, named terms (i.e., terms
       with the \akey{:named} attribute) are not used.
@@
     \akey{check-sat} command.
-  \item In the application track, there are one or more
+  \item In the incremental track, there are one or more
     \akey{check-sat} commands.  There may also be zero or more
@@
 \item The script may optionally contain an \akey{exit} command as its
-  last command.  In the application track, this command must not be
+  last command.  In the incremental track, this command must not be
   omitted.
@@
 
-\subsection{Main track}
-\label{sec:exec:main}
+\subsection{Single Problem Track (Previously: Main Track)}
+\label{sec:exec:single}
 
-The main track competition will consist of selected benchmarks in each
+The single problem track competition will consist of selected benchmarks in each
 of the logic divisions.  Each benchmark script will be presented to
@@
 
-The main track competition uses a StarExec post-processor (named
+The single problem track competition uses a StarExec post-processor (named
 ``SMT-COMP 2019") to accumulate the results.
@@
 
-\subsection{Application track}
+\subsection{Incremental Track (Previously: Application Track)}
 
-The application track evaluates SMT solvers when interacting with an
+The incremental track evaluates SMT solvers when interacting with an
 external verification framework, e.g., a model checker. This
@@
 will set up a ``simulation'' of the aforementioned interaction.  Each
-benchmark in the application track represents a realistic
+benchmark in the incremental track represents a realistic
 communication trace, containing multiple \akey{check-sat} commands
@@
 
-The disk space and memory limits for the application track are the
-same as for the main track (see Section~\ref{sec:exec:main}).
+The disk space and memory limits for the incremental track are the
+same as for the single problem track (see Section~\ref{sec:exec:single}).
 
@@
 solver.  The commands will be taken from an SMT-LIB benchmark script
-that satisfies the requirements for application track scripts given in
+that satisfies the requirements for incremental track scripts given in
 Section~\ref{sec:logistics}.
@@
 In order to perform this unsatisfiability check, the organizers will
-use a selection of SMT solvers that participate in the main track of
+use a selection of SMT solvers that participate in the single problem track of
 this competition.  For each division, the organizers will use only
 solvers that have been sound (i.e., not produced any erroneous result)
-in the main track for this division.  The unsatisfiability of a
+in the single problem track for this division.  The unsatisfiability of a
 produced unsatisfiable core is refuted if the number of checking
@@
 Benchmarks for each division will be drawn from the SMT-LIB benchmark
-library.  The main track will use a subset of all
-\emph{non-incremental} benchmarks; the application track will use a
+library.  The single problem track will use a subset of all
+\emph{non-incremental} benchmarks; the incremental track will use a
 subset of all \emph{incremental} benchmarks.  The unsat-core track
-will use unsatisfiable main track benchmarks, modified to use named
+will use unsatisfiable single problem track benchmarks, modified to use named
 top-level assertions.
@@
 results,\footnote{Here, $N$ is the number of \akey{check-sat} commands
-  in the benchmark.  Recall that main track benchmarks have just one
-  \akey{check-sat} command; application track benchmarks may have
+  in the benchmark.  Recall that single problem track benchmarks have just one
+  \akey{check-sat} command; incremental track benchmarks may have
   multiple \akey{check-sat} commands.} $w \in [0,T]$ the (real-valued)
@@
 
-\header{Main track.} More specifically, for the main track, we have
+\header{Single Problem Track.} More specifically, for the single problem track,
+we have
 %
@@
 
-\header{Application track.}
+\header{Incremental Track.}
 %
@@
 or \akey{pop} commands might also entail a reasonable amount of
-processing.  For the application track, we have
+processing.  For the incremental track, we have
 \begin{itemize}
@@
 
-\subsection{Sequential performance (main track)}
+\subsection{Sequential Performance (Single Problem Track)}
 \label{sec:sequential}
@@
 measures both, and we intend to recognize both best sequential and
-best parallel solvers in all competitive main track divisions.
+best parallel solvers in all competitive single problem track divisions.
 
@@
 
-\header{Main track: removal of disagreements.}
+\header{Single Problem Track: Removal of Disagreements.}
 %
-Before division scores are computed for the main track, benchmarks
+Before division scores are computed for the Single Problem Track, benchmarks
 with unknown status are removed from the competition results if two
@@
 
-For main track and unsat-core track divisions, we will separately
+For Single Problem Track and unsat-core track divisions, we will separately
 compute the weighted sum of all raw scores
@@
 weighted sum of all sequential scores (Section~\ref{sec:sequential})
-to assess sequential performance.  For application track divisions,
+to assess sequential performance.  For incremental track divisions,
 division scores will be based on raw scores only.\footnote{Since
-  application track benchmarks may be partially solved, defining a
-  useful sequential score for the application track would require
+  incremental track benchmarks may be partially solved, defining a
+  useful sequential score for the incremental track would require
   information not provided by the raw score, e.g., detailed timing
@@
 
-\subsection{Competition-wide scoring (main track)}
+\subsection{Competition-wide scoring (Single Problem Track)}
 \label{sec:competition-wide}
 
-We define a competition-wide metric for the main track, separately for
+We define a competition-wide metric for the Single Problem Track, separately for
 parallel and sequential performance, as follows.  Let $N_i$ be the
@@
 \item The best three solvers according to the competition-wide scoring
-  (main track);
+  (Single Problem Track);
 \item the solver that wins the most competitive divisions in the
-  application track;
+  incremental track;
 \item the solver that wins the most competitive divisions in the
@@
 \item the solver that wins the QF\_BV division (separately for
-  parallel and sequential performance) in the main track.
+  parallel and sequential performance) in the Single Problem Track.
 \end{itemize}

### 2019-03-22 rules/rules19.tex
Rules 2019: Update and add todos for the remaining sections.

@@
 
-\title{13th International Satisfiability Modulo Theories Competition
-  (SMT-COMP 2018): Rules and Procedures}
+\title{14th International Satisfiability Modulo Theories Competition
+  (SMT-COMP 2019): Rules and Procedures}
 
@@
 
+\rem{TODO: Update accordingly: Do we run only up to the first unknown status
+check-sat or further?}
 The incremental track evaluates SMT solvers when interacting with an
@@
 
+\an{TODO: We do not run non-competitive divisions.}
+
 \header{Benchmark sources.}
@@
 %
-The deadline for submission of new benchmarks is {\bf April~8, 2018}.
+The deadline for submission of new benchmarks is {\bf March~1, 2019}.
 The organizers, in collaboration with the SMT-LIB maintainers, will be
-checking and curating these until {\bf May~15, 2018}.  The SMT-LIB
+checking and curating these until {\bf May~1, 2019}.  The SMT-LIB
 maintainers intend to make a new release of the benchmark library
@@
 
-\header{Benchmark demographics.}
+\header{Benchmark demographics. \rem{TODO: update}}
 %
@@
 
-\header{Benchmark selection.}
+\header{Benchmark selection. \rem{TODO: update}}
 %
@@
 
-\section{Scoring}
+\section{Scoring \rem{TODO: update}}
 \label{sec:scoring}
@@
 \label{sec:sequential}
+
+\rem{TODO: 24s, sat, unsat score description}
 
@@
 
-\subsection{Other recognitions}
+\subsection{Other Recognitions \rem{TODO: Update}}
 
@@
 
-SMT-COMP 2018 is organized under the direction of the SMT Steering
+SMT-COMP 2019 is organized under the direction of the SMT Steering
 Committee. The organizing team is
@@
 \item
-  \href{https://swt.informatik.uni-freiburg.de/staff/heizmann}{Matthias
-    Heizmann}~-- University of Freiburg, Germany (co-organizer)
+		Liana Hadarean~-- Amazon, USA (co-organizer)
+\item \href{http://www.inf.usi.ch/postdoc/hyvarinen/}{Antti Hyvarinen}~--
+		Universita della Svizzera italiana, Switzerland (co-organizer)
 \item
   \href{http://cs.stanford.edu/people/niemetz}{Aina
-    Niemetz}~-- Stanford University, USA (co-organizer)
+    Niemetz}~-- Stanford University, USA (co-chair)
 \item \href{http://www.cs.man.ac.uk/~regerg/}{Giles Reger}~--
-  University of Manchester, UK (co-organizer)
-\item \href{http://user.it.uu.se/~tjawe125/}{Tjark Weber}~-- Uppsala
-  University, Sweden (chair)
+  University of Manchester, UK (co-chair)
 \end{itemize}
 %
-Tjark Weber is responsible for policy and procedure decisions, such as
-these rules, with input from the co-organizers. He is not associated
-with any group creating or submitting solvers.
+The competition charis are responsible for policy and procedure decisions,
+such as these rules, with input from the co-organizers.
 
-Many others have contributed benchmarks, effort, and feedback.  Clark
-Barrett and Pascal Fontaine are maintaining the SMT-LIB benchmark
-library.  The competition uses the
+Many others have contributed benchmarks, effort, and feedback.  Clark Barrett,
+Pascal Fontaine, Aina Niemetz and Mathias Preiner are maintaining the SMT-LIB
+benchmark library.
+The competition uses the
 \href{https://www.starexec.org/}{StarExec} service, which is hosted at
@@
 %
+Liana Hadarean was part of the developing team of the SMT solver
+CVC4~\cite{cvc4} and is currently not associated with any group
+creating or submitting solvers.
 Aina Niemetz is part of the developing teams of the SMT solvers
@@
 and CVC4~\cite{cvc4}.
-Matthias Heizmann is associated with the group producing the
-SMTInterpol~\cite{smtinterpol} solver.
+Antti Hyvarinen is part of the developing team of the SMT solver OpenSMT
+\rem{TODO: cite OpenSMT}.
 Giles Reger is associated with the group

### 2019-03-22 2018/report/SMT-COMP.tex
Include app track plot, amend captions of vbs plots.

@@
         plot/pdf/cactus_plot-Virtual_Best_Solver_(VBS)_Main_Track_2015-2018.pdf}}
-  \caption{VBS on common benchmarks 2015-2018 of all logics in the Main track.}
+  \caption{VBS on common benchmarks 2015-2018 of all logics in the Main track
+  with a time limit of 1200s. Number of common benchmarks is indicated with a
+  gray vertical line.}
   \label{fig:progress-all}
@@
   \caption{VBS on common benchmarks for pairs of years of all logics in the
-  Main track.}
+  Main track with a time limit of 1200s. Number of common benchmarks is
+  indicated with a gray vertical line.}
   \label{fig:progress}
@@
 
-\iffalse
 \begin{figure}
@@
   \scalebox{.45}{\includegraphics{%
-        plot/pdf/cactus_plot-Virtual_Best_Solver_(VBS)_Application_Track_2015-2018.pdf}}
-  \caption{VBS on common benchmarks 2015-2018 of all logics in the Application track.}
-  \label{fig:progress-all}
+  plot/pdf/bar_plot-Virtual_Best_Solver_(VBS)_Application_Track_2015-2018.pdf}}
+  \vspace{-5ex}
+  \caption{VBS in terms of correct \texttt{check-sat} answers
+  (out of 30370517 total)
+  within a time limit of 1200s
+  on common benchmarks 2015-2018 of all logics in the Application
+  track.}
+  \label{fig:progress-all-app}
 \end{figure}
-
-\begin{figure}
-  \begin{subfigure}[t]{0.5\textwidth}
-    \scalebox{.35}{\includegraphics{%
-      plot/pdf/cactus_plot-Virtual_Best_Solver_(VBS)_Application_Track_2015-2016.pdf}}
-    \caption{2015 vs.~2016}
-  \end{subfigure}
-  \\[2ex]
-  \begin{subfigure}[t]{0.5\textwidth}
-    \scalebox{.35}{\includegraphics{%
-      plot/pdf/cactus_plot-Virtual_Best_Solver_(VBS)_Application_Track_2016-2017.pdf}}
-    \caption{2016 vs.~2017}
-  \end{subfigure}
-  \begin{subfigure}[t]{0.5\textwidth}
-    \scalebox{.35}{\includegraphics{%
-    plot/pdf/cactus_plot-Virtual_Best_Solver_(VBS)_Application_Track_2017-2018.pdf}}
-    \caption{2017 vs.~2018}
-  \end{subfigure}
-  \caption{VBS on common benchmarks for pairs of years of all logics in the
-  Application track.}
-  \label{fig:progress}
-\end{figure}
-\fi
 

### 2019-03-22 2018/report/SMT-COMP.tex
Report: Description of app track plot.

@@
   (out of 30370517 total)
-  within a time limit of 1200s
+  within a time limit of 2400s
   on common benchmarks 2015-2018 of all logics in the Application
@@
 To give a measure of overall progress in solver performance we
-use the notion of \emph{virtual best solver} (VBS) over all divisions of the
-Main track.
-We determine the VBS as the best wall-clock performance per (correctly solved)
-instance with the time limit of 1200s used in the competitions 2017 and 2018.
-Figure~\ref{fig:progress} visualizes VBS performance on common benchmarks over
-pairs of consecutive years from 2014 to 2018 as a cactus plot.
-It shows the wall-clock solving time per instance over all instances, sorted by
-solving time.
-
+use the notion of \emph{virtual best solver} (VBS) over all divisions of all
+three tracks.
+
+For the Main track, we determine the VBS as the best wall-clock performance per
+(correctly solved) instance with the time limit of 1200s used in the
+competitions 2017 and 2018. Figure~\ref{fig:progress-all} visualizes VBS
+performance on common benchmarks from 2015-2018 as cactus plot.
+Figure~\ref{fig:progress} shows VBS performance on common benchmarks over pairs
+of consecutive years from 2014 to 2018.  Both plots show the wall-clock solving
+time per instance over all instances, sorted by solving time.
+%
 Between 2014 (67426 benchmarks) and 2015 (154238 benchmarks),
@@
 division.
+
+For the Application track, we determine the VBS as the best performance in
+terms of number of correct \texttt{check-sat} answers within the time limit
+of 2400s (the time limit of the Application track in the competitions
+2015-2018).
+The total number of eligible \texttt{check-sat} queries (i.e., all queries with
+status sat or unsat up to the first query with status unknown) on
+common benchmarks from 2015-2018 is 30370517.
+Figure~\ref{fig:progress-all-app} visualizes VBS performance on these
+benchmarks as a bar plot.
+In 2015, already 99.95\% of the eligible queries were answered correctly,
+which naturally does not leave a lot of room for improvement.
+In 2016, performance decreased by 185625 correct answers (0.61\%),
+which can be entirely attributed to a performance degression
+of Z3 on 2 benchmarks in the QF\_NIA division.
+%(on which in 2016, CVC4 then
+%performed best, and from 2017 onwards even as well as Z3 in 2015).
 

### 2019-03-24 rules/rules19.tex
Fixed a problem on some URLs that resulted at in at least Mac's preview not understanding that it should open a browser.  Added a reference on opensmt and updated my (Antti's) email.  Wrote a suggestion for the benchmark family description.

@@
 Switzerland \\
-{\small\href{mailto:tjark.weber@it.uu.se}{\texttt{tjark.weber@it.uu.se}}} \\
+{\small\href{mailto:antti.hyvaerinen@usi.ch}{\texttt{antti.hyvaerinen@usi.ch}}} \\
 \and
@@
 \item Sign-up site for the mailing list:
-  \url{cs.nyu.edu/mailman/listinfo/smt-comp}
+  \url{http://cs.nyu.edu/mailman/listinfo/smt-comp}
 \end{itemize}
@@
 \noindent Additional material will be made available at the
-competition web site, \url{www.smtcomp.org}.
+competition web site, \url{http://www.smtcomp.org}.
 
@@
 on the history and motivation for SMT-COMP can be found at the
-competition web site, \url{www.smtcomp.org}, and in reports on
+competition web site, \url{http://www.smtcomp.org}, and in reports on
 previous
@@
 
-\header{Benchmark demographics. \rem{TODO: update}}
+\header{Benchmark demographics. \rem{TODO: check}}
 %
-In SMT-LIB, benchmarks are organized according to \emph{families}.  A
-benchmark family contains problems that are similar in some
-significant way.  Typically they come from the same source or
-application, or are all output by the same tool.  Each top-level
-subdirectory within a division represents a distinct family.
+The set of all SMT-LIB benchmarks in a given division can be naturally
+partitioned to sets containing benchmarks that are similar from the user
+community perspective.  Such benchmarks could all come from the same
+application domain, be generated by the same tool, or have some other
+obvious common identity.
+%
+The organizers try to identify a meaningful partitioning based on the
+directory hierarchy in SMT-LIB.  In many cases the hierarchy consists of
+the top-level directories each corresponding to a submitter, who has
+further imposed a hierarchy on the benchmarks.
+%
+The organizers believe that the submitters have the best information on
+the common identity of their benchmarks and therefore partition each
+division based on the bottom-level directory imposed by each submitter.
+These partitions are referred to as \emph{families}.
 
@@
 and CVC4~\cite{cvc4}.
-Antti Hyvarinen is part of the developing team of the SMT solver OpenSMT
-\rem{TODO: cite OpenSMT}.
+Antti Hyvarinen is part of the developing team of the SMT solver
+OpenSMT~\cite{opensmt2}.
 Giles Reger is associated with the group

### 2019-03-24 rules/rules19.tex
Made a pass on the sat/unsat/all/24 sec scores.  I introduced a difference between performance (parallel/sequential) and score (the sat/unsat/all/24 stuff).  I hope you like it, and that it's not overly complicated...

@@
 
-A solver's \emph{raw score} for each benchmark is a quadruple $\langle
+A solver's \emph{parallel performance} for each benchmark is a quadruple $\langle
 e, n, w, c\rangle$, with $e \in \{0, 1\}$ the number of erroneous
@@
 
-\rem{TODO: 24s, sat, unsat score description}
-
+\iffalse
 SMT-COMP has traditionally emphasized sequential performance (i.e.,
@@
 best parallel solvers in all competitive single problem track divisions.
+\fi
 
-The raw score, as defined in Section~\ref{sec:benchmark-scoring},
+The parallel performance, as defined in Section~\ref{sec:benchmark-scoring},
 favors parallel solvers, which may utilize all available processor
 cores.  To evaluate sequential performance, we derive a
-\emph{sequential score} by imposing a (virtual) CPU time limit equal
+\emph{sequential performance} by imposing a (virtual) CPU time limit equal
 to the wall-clock time limit~$T$.  A solver result is taken into
-consideration for the sequential score only if the solver process
+consideration for the sequential performance only if the solver process
 terminates within this CPU time limit.  More specifically, for a given
-raw score $\langle e, n, w, c\rangle$, the corresponding sequential
-score is defined as~$\langle e_S, n_S, c_S\rangle$, where
+parallel performance $\langle e, n, w, c\rangle$, the corresponding sequential
+performance is defined as~$\langle e_S, n_S, c_S\rangle$, where
 \begin{itemize}
@@
 \item $c_S = \min\ \{c, T\}$.\footnote{\emph{Rationale:} Under this
-  score, a solver should not benefit from using multiple processor
-  cores.  Conceptually, the sequential score should be (nearly)
+  measure, a solver should not benefit from using multiple processor
+  cores.  Conceptually, the sequential performance should be (nearly)
   unchanged if the solver was run on a single-core processor, up to a
@@
 \label{sec:division-scoring}
+
+We compute in total eight different {\em scores} for each division based
+on solvers' parallel and sequential performance.  The two performances
+are computed separately for {\em all}, {\em satisfiable}, and {\em
+unsatisfiable instances}.  In addition we compute the performances for a
+\emph{one-minute wonder} track, where each solver is run with a
+24-second timeout.
 
@@
 comparison purposes) is \emph{sound on benchmarks with known status}
-for a division if its raw score (Section~\ref{sec:benchmark-scoring})
+for a division if its parallel performance (Section~\ref{sec:benchmark-scoring})
 is of the form $\langle 0, n, w, c\rangle$ for each benchmark in the
@@
 
-To compute a solver's score for a division, the solver's individual
+To compute a solver's scores for a division, the solver's individual
 benchmark scores for all benchmarks in the division are first
@@
 For Single Problem Track and unsat-core track divisions, we will separately
-compute the weighted sum of all raw scores
-(Section~\ref{sec:benchmark-scoring}) $$\sum_b \alpha'_b \cdot \langle
-e_b \cdot N, n_b \cdot N, w_b, c_b\rangle$$ where the sum is over all
+compute the weighted sum of all benchmarks separately based on the
+parallel performance and sequential performance.
+(Section~\ref{sec:benchmark-scoring})
+%
+These will be computed as
+$$\sum_b \alpha'_b \cdot \langle e_b \cdot N, n_b \cdot N, w_b, c_b\rangle$$
+%
+where the sum $\sum_b$ ranges over all parallel performances when
+computing parallel performance scores, and over all sequential
+performances when computing sequential performance scores.
+\iffalse
 benchmarks in the division to assess parallel performance, and the
-weighted sum of all sequential scores (Section~\ref{sec:sequential})
-to assess sequential performance.  For incremental track divisions,
-division scores will be based on raw scores only.\footnote{Since
+weighted sum of all sequential performances (Section~\ref{sec:sequential})
+to assess sequential performance.
+\fi
+For incremental track divisions,
+division scores will be based on parallel performance only.\footnote{Since
   incremental track benchmarks may be partially solved, defining a
-  useful sequential score for the incremental track would require
-  information not provided by the raw score, e.g., detailed timing
+  useful sequential performance for the incremental track would require
+  information not provided by the parallel performance, e.g., detailed timing
   information for each result.}
@@
 \begin{itemize}
-\item A weighted sum of raw scores $\langle e, n, w, c\rangle$ is
+\item A weighted sum of parallel performances $\langle e, n, w, c\rangle$ is
   better than $\langle e', n', w', c'\rangle$ iff $e < e'$ or ($e =
@@
   CPU time taken.
-\item A weighted sum of sequential scores $\langle e_S, n_S,
+\item A weighted sum of sequential performances $\langle e_S, n_S,
   c_S\rangle$ is better than $\langle e_S', n_S', c_S'\rangle$ iff
@@
 %
-We will not make any comparisons between raw scores and sequential
-scores, as these are intended to measure fundamentally different
+We will not make any comparisons between parallel and sequential
+performances, as these are intended to measure fundamentally different
 performance characteristics.
@@
 \label{sec:competition-wide}
+
+\rem{TODO: Shall we drop the competition-wide scoring?}
 

### 2019-03-27 2018/report/analysis/analysis.sh
Report: Add scripts for unsat core analysis.

@@ -19,6 +19,10 @@ APPLICATION_2016="../../../2016/csv/Application_Track.csv"
 APPLICATION_2017="../../../2017/csv/Application_Track.csv"
 APPLICATION_2018="../../../2018/csv/Application_Track.csv"
 
+UNSAT_CORE_2016="../../../2016/csv/Unsat_Core_Track.csv"
+UNSAT_CORE_2017="../../../2017/csv/Unsat_Core_Track.csv"
+UNSAT_CORE_2018="../../../2018/csv/Unsat_Core_Track.csv"
+
 ################################################################################
 # check that all input files exist
 ################################################################################
@@ -46,148 +50,186 @@ AP_2016="2016_Application_Track.csv"
 AP_2017="2017_Application_Track.csv"
 AP_2018="2018_Application_Track.csv"
 
+UC_2016="2016_Unsat_Core_Track.csv"
+UC_2017="2017_Unsat_Core_Track.csv"
+UC_2018="2018_Unsat_Core_Track.csv"
+
 ################################################################################
 
 ### Main track
 
-# the 2014 data lacks a "memory usage" column; we add one (with value
-# 0.0) for uniformity
-while IFS=, read PAIR_ID BENCHMARK BENCHMARK_ID SOLVER SOLVER_ID CONFIG CONFIG_ID STATUS CPU_TIME WALL_TIME RESULT EXPECTED
-do
-    echo $PAIR_ID,$BENCHMARK,$BENCHMARK_ID,$SOLVER,$SOLVER_ID,$CONFIG,$CONFIG_ID,$STATUS,$CPU_TIME,$WALL_TIME,0.0,$RESULT,$EXPECTED
-done < "$MAINTRACK_2014" > "$MT_2014"
+## the 2014 data lacks a "memory usage" column; we add one (with value
+## 0.0) for uniformity
+#while IFS=, read PAIR_ID BENCHMARK BENCHMARK_ID SOLVER SOLVER_ID CONFIG CONFIG_ID STATUS CPU_TIME WALL_TIME RESULT EXPECTED
+#do
+#    echo $PAIR_ID,$BENCHMARK,$BENCHMARK_ID,$SOLVER,$SOLVER_ID,$CONFIG,$CONFIG_ID,$STATUS,$CPU_TIME,$WALL_TIME,0.0,$RESULT,$EXPECTED
+#done < "$MAINTRACK_2014" > "$MT_2014"
+#
[…]

### 2019-03-27 2018/report/analysis/unsound-solvers-uc.sh

@@ -1,0 +1,15 @@
+#!/bin/bash
+
+set -e
+set -u
+
+# print a list of all solvers that have given an incorrect answer
+# (together with the respective division)
+
+while IFS=, read PAIR_ID BENCHMARK BENCHMARK_ID SOLVER SOLVER_ID STATUS RESULT RESULT_ERR REDUCTION
+do
+    if [[ ("$RESULT" == "sat") ]]; then
+        DIVISION=${BENCHMARK%%/*}
+        echo $DIVISION,$SOLVER,$SOLVER_ID
+    fi
+done < "$1"|LC_ALL=C sort -u

### 2019-03-27 2018/report/analysis/virtual-best-solver-main.sh

@@ -5,8 +5,7 @@ set -u
 
 # virtual best solver
 
-# only keep the best (fastest, based on wall time) result for each
-# benchmark
+# only keep the best (fastest, based on wall time) result for each benchmark
 
 # Column  3: benchmark id
 #         8: status

### 2019-03-27 2018/report/analysis/virtual-best-solver-uc.sh

@@ -1,0 +1,16 @@
+#!/bin/bash
+
+set -e
+set -u
+
+# virtual best solver
+
+# only keep the best (highest number of reduction) result for each benchmark
+
+# Column  3: benchmark id
+#         6: status
+#         7: result
+
+awk -F , '$6=="complete" && $7=="unsat"' "$1"|
+    sort -t , -k 3,3n -k 9,9n|
+    sort -t , -k 3,3n -u

### 2019-03-27 2018/report/plot/bar_plot.r
Report: Add bar plot for unsat core track.

@@ -4,6 +4,10 @@ if(!dir.exists("pdf")) dir.create("pdf")
 args <- commandArgs(trailingOnly = TRUE)
 plot_title=args[1]
 fname_data <- args[2]
+max_y <- as.integer(args[3])
+scaling <- as.integer(args[4])
+y_label <- args[5]
+unit <- args[6]
 
 fname=gsub(' ','_',plot_title,fixed=TRUE)
 fname_pdf=paste("pdf/bar_plot-",fname,".pdf",sep="")
@@ -20,18 +24,23 @@ for(i in 1:len)
   xcol[i] <- colors[len+1-i]
 }
 
+if (max_y == 0)
+{
+  max_y = max(data[,2])
+}
+
 bp <- barplot(data[,2],
               col = xcol,
-              ylab="# Correct answers",
+              ylab=y_label,
               legend=colnames(data[0,2:2]),
               las=1,
               xaxt="n",
               yaxt="n",
-              ylim=c(0,35000000),
+              ylim=c(0,max_y),
              )
 text(x=bp, y=data[,2], label=data[,2], pos=3, cex=0.8, col="black")
 axis(side=1, at=bp, labels=data[,1])
 ticks=sapply(axTicks(2), function(i) as.integer(i))
-labels=sprintf("%.0fM",ticks/1000000)
+labels=sprintf("%.0f%s",ticks/scaling, unit)
 axis(2, at=ticks, labels=labels)
 title(plot_title,outer=TRUE,line=-1,font.main=2)

### 2019-03-27 2018/report/plot/gen_common_results.py

@@ -41,6 +41,7 @@ if __name__ == "__main__":
         years = years.split('/')[-1]
         years = years.replace('Main_Track_Common_Benchmarks_', '')
         years = years.replace('Application_Track_Common_Benchmarks_', '')
+        years = years.replace('Unsat_Core_Track_Common_Benchmarks_', '')
         outfile_name = "{}/{}_vbs_{}.csv".format(path, year, years)
         with open(outfile_name, 'w') as outfile:
             with open(args.vbs_data, 'r') as infile:

### 2019-03-27 2018/report/analysis/eligible-incremental-status.sh
Report: Add script and result file to determine number of eligible application track answers.

@@ -1,0 +1,18 @@
+#!/bin/bash
+
+# the incremental benchmark file
+file=$1
+
+stats=$(grep "set-info" "$file" | grep ":status")
+
+num_stats=$(echo "$stats" | wc -l)
+eligible=$(echo "$stats" | grep "unknown" -m 1 -n)
+
+if [ -z "$eligible" ]; then
+  eligible="$num_stats"
+else
+  eligible=$(echo "$eligible" | cut -d ':' -f 1)
+  eligible=$((eligible - 1))
+fi
+
+echo "$file,$num_stats,$eligible"

### 2019-03-27 2018/report/analysis/analysis.sh
Minor

@@ -58,48 +58,48 @@ UC_2018="2018_Unsat_Core_Track.csv"
 
 ### Main track
 
-## the 2014 data lacks a "memory usage" column; we add one (with value
-## 0.0) for uniformity
-#while IFS=, read PAIR_ID BENCHMARK BENCHMARK_ID SOLVER SOLVER_ID CONFIG CONFIG_ID STATUS CPU_TIME WALL_TIME RESULT EXPECTED
-#do
-#    echo $PAIR_ID,$BENCHMARK,$BENCHMARK_ID,$SOLVER,$SOLVER_ID,$CONFIG,$CONFIG_ID,$STATUS,$CPU_TIME,$WALL_TIME,0.0,$RESULT,$EXPECTED
-#done < "$MAINTRACK_2014" > "$MT_2014"
-#
-## strip column header line
-#tail -n +2 "$MAINTRACK_2015" > "$MT_2015"
-#
-## strip column header line
-#tail -n +2 "$MAINTRACK_2016" > "$MT_2016"
-#
-## in 2017, main track job-pairs that timed out were re-run with a
-## longer time limit, resulting in two separate result files that we
-## merge now
-#./merge-2017-main-track-reruns.sh "$MAINTRACK_2017" "$MAINTRACK_2017_RERUN" > "$MT_2017"
-## some main track job pairs were run in sub-spaces on StarExec; we
-## remove those sub-space names from the benchmark path (for
-## uniformity)
-#sed -i -e 's:,Datatype Divisions/:,:' "$MT_2017"
-#sed -i -e 's:,Other Divisions/:,:' "$MT_2017"
-#sed -i -e 's:,Rerun Timeouts/:,:' "$MT_2017"
-#sed -i -e 's:,Rerun Timeouts Datatype Divisions/:,:' "$MT_2017"
-#
-## in 2018, some main track job pairs were run in sub-spaces on
-## StarExec; we remove those sub-space names from the benchmark path
-## (for uniformity)
-#tail -n +2 "$MAINTRACK_2018"|sed -e 's:,Other Divisions/:,:' > "$MT_2018"
-#
+# the 2014 data lacks a "memory usage" column; we add one (with value
+# 0.0) for uniformity
+while IFS=, read PAIR_ID BENCHMARK BENCHMARK_ID SOLVER SOLVER_ID CONFIG CONFIG_ID STATUS CPU_TIME WALL_TIME RESULT EXPECTED
+do
[…]

### 2019-03-27 2018/report/SMT-COMP.tex
Report: Add bar plot for unsat core track.
Report: Description of unsat-core bar plot.

@@
 
+\begin{figure}
+  \centering
+  \scalebox{.45}{\includegraphics{%
+  plot/pdf/bar_plot-Virtual_Best_Solver_(VBS)_Unsat_Core_Track_2016-2018.pdf}}
+  \vspace{-5ex}
+  \caption{VBS in terms of number of unsat core reductions
+  within a time limit of 2400s
+  on common benchmarks 2016-2018 of all logics in the Unsat Core 
+  track.}
+  \label{fig:progress-all-uc}
+\end{figure}
+
 \subsection{Further Analysis}
@@
 
-For the Main track, we determine the VBS as the best wall-clock performance per
-(correctly solved) instance with the time limit of 1200s used in the
-competitions 2017 and 2018. Figure~\ref{fig:progress-all} visualizes VBS
+For the \emph{Main track}, we determine the VBS as the best wall-clock
+performance per (correctly solved) instance with the time limit of 1200s used
+in the competitions 2017 and 2018. Figure~\ref{fig:progress-all} visualizes VBS
 performance on common benchmarks from 2015-2018 as cactus plot.
@@
 
-For the Application track, we determine the VBS as the best performance in
-terms of number of correct \texttt{check-sat} answers within the time limit
+For the \emph{Application track}, we determine the VBS as the best performance
+in terms of number of correct \texttt{check-sat} answers within the time limit
 of 2400s (the time limit of the Application track in the competitions
@@
 %performed best, and from 2017 onwards even as well as Z3 in 2015).
+
+For the \emph{Unsat-Core track}, we determine the VBS as the best performance in
+terms of \emph{reduction}, i.e., the difference in the number of assertions
+of the input formula and the unsat core, within the time limit
+of 2400s (the time limit of the Unsat-Core track in the competitions
+2016-2018).
+Figure~\ref{fig:progress-all-app} visualizes VBS performance on the common
+benchmarks (91455 total) from 2016-2018 as a bar plot.
+For 32377 of these benchmarks, extracting an unsat core is trivial since
+they contain only one single \texttt{assert} command.
+They are thus also not considered in the bar plot, since their maximum
+possible reduction is trivially 0.
 

### 2019-03-27 2018/report/analysis/unsat-core-asserts.sh
Report: Add script and result file to determine number of asserts in unsat-core track.

@@ -1,0 +1,10 @@
+#!/bin/bash
+
+# the incremental benchmark file
+file=$1
+
+stats=$(grep "\<assert\>" "$file")
+
+num_stats=$(echo "$stats" | wc -l)
+
+echo "$file,$num_stats"

### 2019-04-04 rules/rules19.tex
Rules: Use rm font for urls.
Rules: Remove todo.

@@
 }
+
+\urlstyle{same}
 
@@
 \item SMT-COMP mailing list:
-  \href{mailto:smt-comp@cs.nyu.edu}{\texttt{smt-comp@cs.nyu.edu}}
+  \href{mailto:smt-comp@cs.nyu.edu}{\textrm{smt-comp@cs.nyu.edu}}
 \item Sign-up site for the mailing list:
@@
 need two time limits here, one for solving and one for
-validation?}.\footnote{\an{TODO: Is this obsolete?} The time limit may be
+validation?}.\footnote{The time limit may be
 adjusted once we know the number of competition entrants and eligible

### 2019-04-04 rules/rules19.tex
Rules: Add TODO.

@@
 24-second timeout.
+\rem{TODO: 24-seconds is only a score, not a track}
 
@@
 
-\rem{TODO: Shall we drop the competition-wide scoring?}
+\rem{TODO: Replace notion of competition-wide scoring with a notion of ranking
+based on distance between first and second (based on scoring, and maybe a second
+based on VBS marginal contribution)}
 

### 2019-04-09 2018/report/SMT-COMP.tex
Report: First (refactored) version of participants table.

@@
 \usepackage{booktabs}
+\usepackage{longtable}
 %\usepackage[pdf]{pstricks}
@@
 
-\begin{table}
-  \caption{Participants (2015--2018)}
-  \label{table:participants}
-  \centering
-  \begin{tabular}{lp{11.5cm}}
-    \toprule
-    Solver & Submitters (Affiliations)\\
-    \midrule
-    ABC~\cite{DBLP:conf/cav/BraytonM10} & Valeriy Balabanov
-                        (Mentor Graphics)\\
-    Alt-Ergo~\cite{conchon:hal-01960203} & Albin Coquereau
-                        (CNRS and University of Paris-Sud)\\
-    AProVE~\cite{DBLP:journals/jar/GieslABEFFHOPSS17} & Carsten Fuhs
-                        (University College London; Birkbeck, University of London)\\
-    Boolector~\cite{DBLP:conf/cav/NiemetzPWB18} & Mathias Preiner
-                        (Johannes Kepler University, Stanford University)\\
-    COLIBRI~\cite{colibri} & Fran\c{c}ois Bobot
-                        (French Alternative Energies and Atomic Energy Commission)\\
-    Ctrl-Ergo~\cite{10.1007/978-3-642-31365-3_8} & Mohamed Iguernlala
-                        (OCamlPro SAS)\\
-    CVC3~\cite{DBLP:conf/cav/BarrettT07} & Kshitij Bansal
-                        (New York University)\\
-    CVC4~\cite{DBLP:conf/cav/BarrettCDHJKRT11}  & Kshitij Bansal, Clark Barrett, Andres N\"otzli, Duligur Ibeling
-                        (New York University; Stanford University)\\
-    MapleSTP          & Jimmy Liang
-                        (University of Waterloo)\\
-    MinkeyRink        & Trevor Hansen
-                        (University of Melbourne)\\
-    OpenSMT2~\cite{DBLP:conf/sat/HyvarinenMAS16} & Matteo Marescotti, Antti Hyv\"arinen
-                        (University of Lugano)\\
-    ProB~\cite{doi:10.1002/9781119002727.ch14} & Sebastian Krings
-                        (University of D\"usseldorf)\\
-    Q3B               & Martin Jon\'a\v{s}
-                        (Masaryk University)\\
-    raSAT~\cite{rasat} & Tung Vu Xuan
-                        (Japan Advanced Institute of Science and Technology)\\
-    Redlog~\cite{DBLP:journals/cca/Dolzmann097} & Haniel Barbosa
-                        (Inria Nancy)\\
-    SMT-RAT~\cite{DBLP:conf/sat/CorziliusKJSA15} & Florian Corzilius, Gereon Kremer
-                        (RWTH Aachen University)\\
-    SMTInterpol~\cite{DBLP:conf/spin/ChristHN12} & J\"urgen Christ
-                        (University of Freiburg)\\
-    SPASS-SATT         & Martin Bromberger
-                        (Max Planck Institute for Informatics)\\
-    STP~\cite{ganesh07} & Mate Soos, Trevor Hansen, Norbert Manthey
-                        (National University of Singapore; University of Melbourne)\\
-    toysmt             & Masahiro Sakai
-                        (Toshiba Corporation)\\
-    Vampire~\cite{DBLP:conf/cav/KovacsV13} & Giles Reger
-                        (University of Manchester)\\
-    veriT~\cite{DBLP:conf/cade/BoutonODF09} & David D\'eharbe, Haniel Barbosa, Hans-J\"org Schurr
-                        (Federal University of Rio Grande do Norte; Inria Nancy)\\
-    XSat~\cite{DBLP:conf/cav/FuS16} & Martin Velez
-                        (University of California, Davis)\\
-    Yices2~\cite{Dutertre:cav2014} & Bruno Dutertre, Dejan Jovanovi\'c
-                        (SRI International)\\
-    Z3~\cite{DBLP:conf/tacas/MouraB08} & Christoph Wintersteiger, Aleksandar Zelji\'c
-                        (Microsoft Research; Uppsala University)\\
-    \bottomrule
-  \end{tabular}
-\end{table}
+\include{table-participants}
 

### 2019-04-09 2018/report/SMT-COMP.tex
Report: Split participants table, description.

@@
 \usepackage{booktabs}
-\usepackage{longtable}
 %\usepackage[pdf]{pstricks}
@@
 
-Table~\ref{table:participants} lists the solvers that participated
-between~2015 and~2018, together with their submitter(s) and
-institutional affiliations (which may have changed over time).  Note
-that most solvers were developed by a group of people; the table does
-not list all contributors but only submitters.
+Tables~\ref{table:participants1}-\ref{table:participants3} list the solvers
+that participated between~2015 and~2018, together with contributing team
+members (in alphabetical order) and their institutional affiliations (which may
+have changed over time).
 %

### 2019-04-10 rules/rules19.tex
Added industrial and model validating track.

@@
 
+\subsection{Industry challenge track}
+\label{sec:exec:industry-challenge}
+
+The industry challenge track will follow the same rules as the single problem track,
+with two exceptions: benchmark selection and the time limit. The track will run on
+all SMT-LIB benchmarks that have an unknown status and that have been tagged as being
+ \emph{industrial}. Additionally we will include benchmarks nominated by the community.
+\lh{TODO: benchmark selection still needs discussion}
+\lh{TODO: We didn't decide on what we do if only one solver gives an answer and we don't
+know if the problem is sat/unsat}
+
+\subsection{Model Validation Track (experimental)}
+\label{sec:exec:model}
+The model validation track will evaluate the solver's ability to produce models
+for satisfiable problems. This track will run on all QF\_BV satisfiable benchmarks
+from the single problem track.
+
+The SMT-LIB language accommodates this functionality by providing the ability to
+request a satisfying model after a \akey{check-sat} command returns \texttt{sat}.
+The satisfiable core that is returned must consist of definitions specifying all
+and only the current user-declared function symbols, in the format prescribed by
+the SMT-LIB standard.
+
+The result of a solver is considered erroneous if the response to the
+\akey{checks-sat} command is \texttt{unsat}, if the returned model is not
+well-formed (e.g. does not provide a definition for all the user-declared function
+symbols), or if the returned model does not satisfy the benchmark.
+
+In order to check that the model satisfies the benchmark, the organizers will use
+a model validating tool. The organizers will make this tool available to solver
+developers before the solver submission deadline.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2019-04-10 rules/rules19.tex
Rules: Introduce todo macro.

@@
 \newcommand{\rem}[1]{\textcolor{red}{[#1]}}
+\newcommand{\todo}[1]{\rem{TODO #1}}
 \newcommand{\an}[1]{\rem{#1 -- aina}}
@@
   system descriptions.
-\item[\an{TODO}] Opening value of NYSE Composite Index used to complete
+\item[\todo{}] Opening value of NYSE Composite Index used to complete
   random seed for benchmark scrambling.
@@
 SMT-COMP~2019.
-\an{update changes vs 2018}
+\todo{update changes vs 2018}
 The principal changes from the previous competition rules are the following:
@@
 \begin{center}
-  \an{\url{}submission form url}
+  \todo{\url{}submission form url}
 \end{center}
@@
 
-\an{Add information that these solver versions will be made available
+\todo{Add information that these solver versions will be made available
 on the smt-comp website for archiving purposes? What are the implications of
@@
 
-\header{Input and output. \rem{TODO: update}}
+\header{Input and output. \todo{update}}
 %
@@
 The time limit~$T$ will be 40~minutes of wall-clock time per solver/benchmark
-pair in the single problem, incremental and unsat core tracks, \rem{TODO:
-XX}~minutes in the industry challenge track, and \rem{TODO: XX}~minutes in the
-model validation track \an{TODO: Need to elaborate how time is split? Do we
+pair in the single problem, incremental and unsat core tracks, \todo{XX}~minutes in the industry challenge track, and \todo{XX}~minutes in the
+model validation track \todo{Need to elaborate how time is split? Do we
 need two time limits here, one for solving and one for
@@
 
-\rem{TODO: Update accordingly: Do we run only up to the first unknown status
+\todo{Update accordingly: Do we run only up to the first unknown status
 check-sat or further?}
@@
 
-\an{TODO: We do not run non-competitive divisions.}
+\todo{We do not run non-competitive divisions.}
 
@@
 
-\header{Benchmark demographics. \rem{TODO: check}}
+\header{Benchmark demographics. \todo{check}}
 %
@@
 
-\header{Benchmark selection. \rem{TODO: update}}
+\header{Benchmark selection. \todo{update}}
 %
@@
 
-\section{Scoring \rem{TODO: update}}
+\section{Scoring \todo{update}}
 \label{sec:scoring}
@@
 24-second timeout.
-\rem{TODO: 24-seconds is only a score, not a track}
+\todo{24-seconds is only a score, not a track}
 
@@
 
-\rem{TODO: Replace notion of competition-wide scoring with a notion of ranking
+\todo{Replace notion of competition-wide scoring with a notion of ranking
 based on distance between first and second (based on scoring, and maybe a second
@@
 
-\subsection{Other Recognitions \rem{TODO: Update}}
+\subsection{Other Recognitions \todo{Update}}
 

### 2019-04-11 rules/rules19.tex
Rules: Introduce macros for tracks.

@@
 \usepackage{hyperref}
+\usepackage{xspace}
 
@@
 \newcommand{\gr}[1]{\rem{#1 -- giles}}
+
+\newcommand{\main}{Single Query\xspace}
+\newcommand{\incremental}{Incremental\xspace}
+\newcommand{\ucore}{Unsat Core\xspace}
+\newcommand{\mval}{Model Validation\xspace}
 
@@
 
-SMT-COMP 2019 will have five tracks: the single problem track (formerly known
-as Single Problem Track), the incremental track (formerly known as application
-track), the unsat-core track, the (new) industry challenge track, and the (new)
-model validation track.
+SMT-COMP 2019 will have five tracks: the \main Track (formerly known
+as Main Track), the incremental track (formerly known as application
+track), the \ucore Track, the (new) industry challenge track, and the (new)
+\mval Track.
 
@@
 \item The time limit per solver/benchmark pair is anticipated to be at
-  most 20 minutes in the main track, and at most 40 minutes in the
+  most 20 minutes in the \main Track, and at most 40 minutes in the
   other tracks.  \emph{Rationale:} Already in 2017, the time limit for
-  the main track was reduced to 20 minutes (down from 40 minutes in
+  the \main Track was reduced to 20 minutes (down from 40 minutes in
   earlier years) to cope with the inclusion of a large number of
@@
 
-\item In the unsat-core track, the unsatisfiability check for the
+\item In the \ucore Track, the unsatisfiability check for the
   returned core will be based on a simple majority vote.  The case
@@
   treated specially.  \emph{Rationale:} This allows to simplify the
-  post-processing of unsat-core track results considerably.
+  post-processing of \ucore Track results considerably.
 
@@
 %
-In the main and unsat-core track, a participating solver must read a
+In the \main and \ucore tracks, a participating solver must read a
 single benchmark script, whose filename is presented as the solver's
@@
   \begin{enumerate}
-  \item In the main and unsat-core track, there may be a single
+  \item In the \main and \ucore tracks, there may be a single
     \akey{(set-option :print-success ...)} command.  Note that
@@
   \end{enumerate}
-\item In the unsat-core track, there is a single \akey{(set-option
+\item In the \ucore Track, there is a single \akey{(set-option
   :produce-unsat-cores true)} command.
@@
   \begin{enumerate}
-    \item In the main and incremental track, named terms (i.e., terms
+    \item In the \main and \incremental tracks, named terms (i.e., terms
       with the \akey{:named} attribute) are not used.
-    \item In the unsat core track, top-level assertions may be named.
+    \item In the \ucore Track, top-level assertions may be named.
   \end{enumerate}
@@
   \begin{enumerate}
-  \item In the main and unsat-core track, there is exactly one
+  \item In the \main and \ucore tracks, there is exactly one
     \akey{check-sat} command.
@@
   \end{enumerate}
-\item In the unsat-core track, the \akey{check-sat} command (which is
+\item In the \ucore Track, the \akey{check-sat} command (which is
   always issued in an unsatisfiable context) is followed by a single
@@
 The time limit~$T$ will be 40~minutes of wall-clock time per solver/benchmark
-pair in the single problem, incremental and unsat core tracks, \todo{XX}~minutes in the industry challenge track, and \todo{XX}~minutes in the
-model validation track \todo{Need to elaborate how time is split? Do we
+pair in the \main, \incremental and \ucore tracks, \todo{XX}~minutes in the
+industry challenge track, and \todo{XX}~minutes in the \mval Track
+\todo{Need to elaborate how time is split? Do we
 need two time limits here, one for solving and one for
@@
 
-\subsection{Single Problem Track (Previously: Main Track)}
+\subsection{\main Track (Previously: Main Track)}
 \label{sec:exec:single}
 
-The single problem track competition will consist of selected benchmarks in each
+The \main Track competition will consist of selected benchmarks in each
 of the logic divisions.  Each benchmark script will be presented to
@@
 
-The single problem track competition uses a StarExec post-processor (named
+The \main Track competition uses a StarExec post-processor (named
 ``SMT-COMP 2019") to accumulate the results.
@@
 The disk space and memory limits for the incremental track are the
-same as for the single problem track (see Section~\ref{sec:exec:single}).
+same as for the \main Track (see Section~\ref{sec:exec:single}).
 
@@
 
-\subsection{Unsat-core track}
+\subsection{\ucore Track}
 \label{sec:exec:unsat-core}
 
-The unsat-core track will evaluate the capability of solvers to
+The \ucore Track will evaluate the capability of solvers to
 generate unsatisfiable cores (for problems that are known to be
@@
 
-In order to perform this unsatisfiability check, the organizers will
-use a selection of SMT solvers that participate in the single problem track of
-this competition.  For each division, the organizers will use only
-solvers that have been sound (i.e., not produced any erroneous result)
-in the single problem track for this division.  The unsatisfiability of a
-produced unsatisfiable core is refuted if the number of checking
-solvers whose result is \texttt{sat} exceeds the number of checking
-solvers whose result is \texttt{unsat}.  The time limit for checking
-unsatisfiable cores is yet to be determined, but is anticipated to be
-around 5 minutes of wall-clock time per solver.
+In order to perform this unsatisfiability check, the organizers will use a
+selection of SMT solvers that participate in the \main Track of this
+competition.  For each division, the organizers will use only solvers that have
+been sound (i.e., not produced any erroneous result) in the \main Track for
+this division.  The unsatisfiability of a produced unsatisfiable core is
+refuted if the number of checking solvers whose result is \texttt{sat} exceeds
+the number of checking solvers whose result is \texttt{unsat}.  The time limit
+for checking unsatisfiable cores is yet to be determined, but is anticipated to
+be around 5 minutes of wall-clock time per solver.
 
@@
 
-The industry challenge track will follow the same rules as the single problem track,
+The industry challenge track will follow the same rules as the \main Track,
 with two exceptions: benchmark selection and the time limit. The track will run on
@@
 
-\subsection{Model Validation Track (experimental)}
+\subsection{\mval Track (experimental)}
 \label{sec:exec:model}
-The model validation track will evaluate the solver's ability to produce models
+The \mval Track will evaluate the solver's ability to produce models
 for satisfiable problems. This track will run on all QF\_BV satisfiable benchmarks
-from the single problem track.
+from the \main Track.
 
@@
 Benchmarks for each division will be drawn from the SMT-LIB benchmark
-library.  The single problem track will use a subset of all
+library.  The \main Track will use a subset of all
 \emph{non-incremental} benchmarks; the incremental track will use a
-subset of all \emph{incremental} benchmarks.  The unsat-core track
-will use unsatisfiable single problem track benchmarks, modified to use named
+subset of all \emph{incremental} benchmarks.  The \ucore Track
+will use unsatisfiable \main Track benchmarks, modified to use named
 top-level assertions.
@@
     \akey{check-sat} commands with unknown status in the application
-    track (for the same reasons they are now included in the main
+    track (for the same reasons they are now included in the \main
     track), but this would require substantial changes to the trace
@@
 results,\footnote{Here, $N$ is the number of \akey{check-sat} commands
-  in the benchmark.  Recall that single problem track benchmarks have just one
+  in the benchmark.  Recall that \main Track benchmarks have just one
   \akey{check-sat} command; incremental track benchmarks may have
@@
 
-\header{Single Problem Track.} More specifically, for the single problem track,
-we have
+\header{\main Track.} More specifically, for the \main Track, we have
 %
@@
 
-\header{Unsat-core track.}
-%
-For the unsat-core track, we instead have $0 \leq n \leq A$, where~$A$
+\header{\ucore Track.}
+%
+For the \ucore Track, we instead have $0 \leq n \leq A$, where~$A$
 is the number of named top-level assertions in the benchmark, and
@@
 
-\subsection{Sequential Performance (Single Problem Track)}
+\subsection{Sequential Performance (\main Track)}
 \label{sec:sequential}
@@
 measures both, and we intend to recognize both best sequential and
-best parallel solvers in all competitive single problem track divisions.
+best parallel solvers in all competitive \main Track divisions.
 \fi
@@
 
-\header{Single Problem Track: Removal of Disagreements.}
-%
-Before division scores are computed for the Single Problem Track, benchmarks
+\header{\main Track: Removal of Disagreements.}
+%
+Before division scores are computed for the \main Track, benchmarks
 with unknown status are removed from the competition results if two
@@
 
-For Single Problem Track and unsat-core track divisions, we will separately
+For \main Track and \ucore Track divisions, we will separately
 compute the weighted sum of all benchmarks separately based on the
@@
 
-\subsection{Competition-wide scoring (Single Problem Track)}
+\subsection{Competition-wide scoring (\main Track)}
 \label{sec:competition-wide}
@@
 
-We define a competition-wide metric for the Single Problem Track, separately for
+We define a competition-wide metric for the \main Track, separately for
 parallel and sequential performance, as follows.  Let $N_i$ be the
@@
 \item The best three solvers according to the competition-wide scoring
-  (Single Problem Track);
+  (\main Track);
 \item the solver that wins the most competitive divisions in the
@@
 \item the solver that wins the most competitive divisions in the
-  unsat-core track;
+  \ucore Track;
 \item the solver that wins the QF\_BV division (separately for
-  parallel and sequential performance) in the Single Problem Track.
+  parallel and sequential performance) in the \main Track.
 \end{itemize}

### 2019-04-11 rules/rules19.tex
Rules: Macro for industry challenge track.

@@
 \newcommand{\mval}{Model Validation\xspace}
+\newcommand{\challenge}{Industry Challenge\xspace}
 
@@
 as Main Track), the incremental track (formerly known as application
-track), the \ucore Track, the (new) industry challenge track, and the (new)
+track), the \ucore Track, the (new) \challenge Track, and the (new)
 \mval Track.
@@
 pair in the \main, \incremental and \ucore tracks, \todo{XX}~minutes in the
-industry challenge track, and \todo{XX}~minutes in the \mval Track
+\challenge Track, and \todo{XX}~minutes in the \mval Track
 \todo{Need to elaborate how time is split? Do we
@@
 
-\subsection{Industry challenge track}
+\subsection{\challenge Track}
 \label{sec:exec:industry-challenge}
 
-The industry challenge track will follow the same rules as the \main Track,
+The \challenge Track will follow the same rules as the \main Track,
 with two exceptions: benchmark selection and the time limit. The track will run on

### 2019-04-11 rules/rules19.tex
Rules: Update list of changes (+ TODOs).
+ changes: update time limit section

@@
 SMT-COMP~2019.
-\todo{update changes vs 2018}
 The principal changes from the previous competition rules are the following:
 \begin{itemize}
-\item The time limit per solver/benchmark pair is anticipated to be at
-  most 20 minutes in the \main Track, and at most 40 minutes in the
-  other tracks.  \emph{Rationale:} Already in 2017, the time limit for
-  the \main Track was reduced to 20 minutes (down from 40 minutes in
-  earlier years) to cope with the inclusion of a large number of
-  benchmarks with unknown status.
-
-\item In the \ucore Track, the unsatisfiability check for the
-  returned core will be based on a simple majority vote.  The case
-  that a solver finds its own core satisfiable will no longer be
-  treated specially.  \emph{Rationale:} This allows to simplify the
-  post-processing of \ucore Track results considerably.
-
-\item In 2017, the competition featured experimental divisions for
-  benchmarks that use algebraic datatypes.  These divisions will be
-  regular (non-experimental) in 2018. \emph{Rationale:} Algebraic
-  datatypes are specified in the latest official release (Version~2.6)
-  of the SMT-LIB standard.
-
-\item The competition will feature an experimental divisions for
+  \item {\it Renaming of Tracks.} \todo{}
+
+  \item {\it Mandatory System Descriptions.} \todo{}
+
+  \item {\it Do Not Run Non-Competitive Divisions.} \todo{}
+
+  \item {\it Benchmark Selection.} \todo{}
+
+  \item {\it Time Limit.} The time limit per solver/benchmark pair is
+    anticipated to be at most 40 minutes in the \main (formerly: Main),
+    \incremental (formerly: Application), \ucore and \mval Tracks.  For the
+    \challenge Track, it is anticipated to be at most \todo{xx} minutes.
+    \emph{Rationale:} In 2017 and 2018, the time limit for the Main Track was
+    reduced to 20 minutes (down from 40 minutes in earlier years) to cope with
+    the inclusion of a large number of benchmarks with unknown status.  This
+    year, the reduced number of benchmarks selected per division allows us to
+    increase the time limit back to 40 minutes for the \main Track.
+
+  \item {\it New \mval Track.} \todo{}
+
+  \item {\it New \challenge Track.} \todo{}
+.
+  \item {\it New Scores.} \todo{24 seconds, sat, unsat}
+
+  \item {\it Incremental Track.} \todo{Run beyond the first unknown status query}
+
+  \item {\it Experimental Strings Division.}
+    \todo{point to the current draft of the standard as the set of rules
+    solvers have to agree on}
+    The competition will feature an experimental divisions for
   benchmarks that use strings.  \emph{Rationale:} Corresponding
@@
   near future.
+
+  \item {\it Scoring Scheme.} \todo{}
+
+  \item {\it Competition-Wide Scores/Winners.} \todo{}
+
+  \item {\it Problems with Evaluation Scripts.} \todo{Explain what was the
+    problem and what has been fixed, talk about notion of benchmark family.}
+
 \end{itemize}
@@
 
+\todo{time limit}
 The \challenge Track will follow the same rules as the \main Track,

### 2019-04-11 rules/rules19.tex
Rules: Update incremental track.

@@
 
-\todo{Update accordingly: Do we run only up to the first unknown status
-check-sat or further?}
 The incremental track evaluates SMT solvers when interacting with an
@@
 
-In order to facilitate the evaluation of solvers in this track, we
-will set up a ``simulation'' of the aforementioned interaction.  Each
-benchmark in the incremental track represents a realistic
-communication trace, containing multiple \akey{check-sat} commands
-(possibly with corresponding \akey{push 1} and \akey{pop 1} commands),
-which is parsed by a \emph{trace executor}. The trace executor serves
-the following purposes:
-\begin{itemize}
-\item it simulates the online interaction by sending single queries to
-  the SMT solver (through stdin);
+In order to facilitate the evaluation of solvers in this track, we will set up
+a ``simulation'' of the aforementioned interaction.  Each benchmark represents
+a realistic communication trace, containing multiple \akey{check-sat} commands
+(possibly with corresponding \akey{push 1} and \akey{pop 1} commands). It is
+parsed by a (publicly available) \emph{trace executor}\footnote{\todo{link}},
+which serves the following purposes: \begin{itemize} \item it simulates the
+online interaction by sending single queries to the SMT solver (through stdin);
 \item it prevents ``look-ahead'' behaviors of SMT solvers;
@@
 \end{itemize}
-%
-The trace executor terminates processing the benchmark script upon
-receiving an incorrect response from the solver.
 
@@
 
-\header{\main Track: Removal of Disagreements.}
-%
-Before division scores are computed for the \main Track, benchmarks
-with unknown status are removed from the competition results if two
-(or more) solvers that are sound on benchmarks with known status
-disagree on their result.  More specifically, a solver (including a
-solver that was entered into the competition by the organizers for
-comparison purposes) is \emph{sound on benchmarks with known status}
-for a division if its parallel performance (Section~\ref{sec:benchmark-scoring})
-is of the form $\langle 0, n, w, c\rangle$ for each benchmark in the
-division, i.e., if it did not produce any erroneous results.  Two
-solvers \emph{disagree} on a benchmark if one of them reported
-\texttt{sat} and the other reported \texttt{unsat}.  Only the
-remaining benchmarks are used in the following computation of division
-scores (but the organizers may report disagreements for informational
-purposes).
+\header{\main and \challenge Track: Removal of Disagreements.}
+%
+\todo{do we need to update this notion?}
+Before division scores are computed for the \main and \challenge tracks,
+benchmarks with unknown status are removed from the competition results if two
+(or more) solvers that are sound on benchmarks with known status disagree on
+their result.  More specifically, a solver (including a solver that was entered
+into the competition by the organizers for comparison purposes) is \emph{sound
+on benchmarks with known status} for a division if its parallel performance
+(Section~\ref{sec:benchmark-scoring}) is of the form $\langle 0, n, w,
+c\rangle$ for each benchmark in the division, i.e., if it did not produce any
+erroneous results.  Two solvers \emph{disagree} on a benchmark if one of them
+reported \texttt{sat} and the other reported \texttt{unsat}.  Only the
+remaining benchmarks are used in the following computation of division scores
+(but the organizers may report disagreements for informational purposes).
+
+\header{\incremental Track: Removal of Disagreements.}
+\todo{}
+
+\header{\challenge Track: Removal of Disagreements.}
+\todo{}
 

### 2019-04-11 rules/rules19.tex
Rules: Update changes for the incremental track.

@@
 
-  \item {\it Incremental Track.} \todo{Run beyond the first unknown status query}
+  \item {\it Incremental Track.}
+    In previous years, benchmarks were not eligible for the \incremental Track
+    if their first \akey{check-sat} command had unknown status.  Similarly, the
+    trace executor used to send commands from the benchmark to the solver's
+    standard input channel stopped execution at the first \akey{check-sat}
+    command with unknown status. This year, benchmarks whose first
+    \akey{check-sat} command has unknown status are eligible for the
+    \incremental track and trace execution is only stopped before the solver
+    completes a benchmark if the execution runs into the time limit.
+    \emph{Rationale:} The previous limitations were imposed by the trace
+    executor, which now has been extended to support executing solvers on
+    benchmarks beyond \akey{check-sat} commands with unknown status.
 

### 2019-04-11 rules/rules19.tex
Rules: Update input/output commands section.

@@
 
-\header{Input and output. \todo{update}}
+\header{Input and output.}
 %
@@
   \begin{enumerate}
-    \item In the \main and \incremental tracks, named terms (i.e., terms
+    \item In all tracks except the \ucore Track,  named terms (i.e., terms
       with the \akey{:named} attribute) are not used.
@@
   \begin{enumerate}
-  \item In the \main and \ucore tracks, there is exactly one
-    \akey{check-sat} command.
+  \item In all tracks except the \incremental Track, there is exactly one
+    \akey{check-sat} command. \todo{is that true for the challenge track?}
   \item In the incremental track, there are one or more
@@
   \akey{get-unsat-core} command.
+\item In the \mval Track, the \akey{check-sat} command (which is
+  always issued in a satisfiable context) is followed by a single
+  \akey{get-model} command. \todo{Liana: please verify}
 \item The script may optionally contain an \akey{exit} command as its

### 2019-04-11 rules/rules19.tex
Rules: More incremental track updates.

@@
   of coming from or having some intended application outside SMT.
-\item \emph{Remove incremental benchmarks whose first \akey{check-sat}
-  command has unknown status.}  Incremental benchmarks may contain
-  multiple \akey{check-sat} commands, each with its own status.  If an
-  incremental benchmark contains a \akey{check-sat} command whose
-  status is unknown, only the prefix of the benchmark up to the
-  preceding \akey{check-sat} command is eligible for the application
-  track of the competition; if the benchmark's first \akey{check-sat}
-  command has unknown status, the entire benchmark is
-  ineligible.\footnote{It might be desirable to also include
-    \akey{check-sat} commands with unknown status in the application
-    track (for the same reasons they are now included in the \main
-    track), but this would require substantial changes to the trace
-    executor and scoring tools.}
+\item \todo{\emph{Remove benchmarks solved by all solvers within 1s in the previous year}}
 \end{enumerate}
 %
+\todo{update with the new benchmark selection rules}
 All remaining benchmarks are used for the competition.  There will be

### 2019-04-11 rules/rules19.tex
Rules: Benchmark selection TODOs, incremental updates.
Rules: More TODOs.

@@
 
-SMT-COMP 2019 will have five tracks: the \main Track (formerly known
-as Main Track), the incremental track (formerly known as application
-track), the \ucore Track, the (new) \challenge Track, and the (new)
+SMT-COMP 2019 will have five tracks: the \main Track (previously: Main Track),
+the incremental track (previously: Application Track), the \ucore Track,
+the (new) \challenge Track, and the (new)
 \mval Track.
@@
   \item {\it Time Limit.} The time limit per solver/benchmark pair is
-    anticipated to be at most 40 minutes in the \main (formerly: Main),
-    \incremental (formerly: Application), \ucore and \mval Tracks.  For the
+    anticipated to be at most 40 minutes in the \main (previously: Main),
+    \incremental (previously: Application), \ucore and \mval Tracks.  For the
     \challenge Track, it is anticipated to be at most \todo{xx} minutes.
@@
 top-level assertions.
+\todo{add information about how benchmarks are selected for the \mval,
+\challenge, \ucore tracks, and the 24s, sat and unsat scores -- either here
+or below}
 
@@
 
-\header{Benchmark selection. \todo{update}}
+\header{Benchmark selection.}
 %
@@
 benchmark pool is culled as follows:
+\todo{add information about how benchmarks are selected for the \mval,
+\challenge, \ucore tracks, and the 24s, sat and unsat scores}
 \begin{enumerate}
@@
   information for each result.}
+  \todo{is this only true for the incremental track or also one of the new tracks}
 

### 2019-04-11 rules/rules19.tex
Rules: Added changes information about renaming tracks.

@@
 \begin{itemize}
-  \item {\it Renaming of Tracks.} \todo{}
+  \item {\it Renaming of Tracks.} This year, the track previously known as
+    `Main Track` will be renamed to \emph{\main Track}, and the previous
+    `Application Track' will be renamed to \emph{\incremental Track}.
+    \emph{Rationale:} We believe the current names are misleading, as the
+    previous `Main Track' also contains problems coming from applications.
+    Additionally, having it called `Main' de-emphasizes the importance of the
+    other tracks and use cases of SMT.
 

### 2019-04-11 rules/rules19.tex
Rules: Update system description information.

@@
 
-  \item {\it Mandatory System Descriptions.} \todo{}
+  \item {\it Mandatory System Descriptions.}
+    SMT-COMP entrants are now required to provide a short (1–2 pages)
+    description of the system.  \emph{Rationale:} The main incentive for this
+    change is twofold.  First, we want to improve transparency when submitted
+    solvers are wrapper tools according to the rules of the competition.
+    Second, we want to encourage documentation of technical improvements that
+    lead to the current results.
 
@@
 %
-As part of a submission, SMT-COMP entrants \emph{must} provide a short (1--2
-pages) description of the system.
-This should include a list of all authors of the system, their present
-institutional affiliations, and any appropriate acknowledgements.  The
-programming language(s) and basic SMT solving approach employed should
-be described (e.g., lazy integration of a Nelson-Oppen combination
-with SAT, translation to SAT, etc.).  System descriptions should also
-include a URL for a web site for the submitted tool.  System
-descriptions may be submitted after the solver deadline, but to be
-useful should be sent to the organizers before the competition ends.
-We intend to make system descriptions publicly available.
+As part of the submission, SMT-COMP entrants are \emph{required} to provide a
+short (1–-2 pages) description of the system.  This should include a list of
+all authors of the system, their present institutional affiliations, and any
+appropriate acknowledgements.  The programming language(s) and basic SMT
+solving approach employed should be described (e.g., lazy integration of a
+Nelson-Oppen combination with SAT, translation to SAT, etc.).  System
+descriptions should also include a URL for a web site for the submitted tool.
+System descriptions must be submitted until the final solver deadline System
+descriptions will be made publicly available.
 
@@
 %
+\todo{Giles: update}
 A \emph{wrapper tool} is defined as any solver that calls (or is in

### 2019-04-11 2018/report/SMT-COMP.tex
adding further analysis tables still need to add text

@@
 
+It is interesting to note that the non-competitive solvers MathSAT and Z3 often appear as the best performing solver.
+We do not see this as detracting from the overall significance of results.
+Both solvers are industrial-strength tools, actively maintained and tuned.
+The reasons for non-entry into the competition are orthogonal to their suitability for the competition.
+Indeed, Z3 has been entered into the competition competitively in the past and one can assume was trained on the current problems (as much as any solver is).
+Finally, the fact that industrial-strength solvers perform well in the competition supports the notion that the benchmarks in the competition are industrially relevant.
+
 \include{table-winners-main}
@@
 
-\subsection{Further Analysis}
+\section{Further Analysis}
 
@@
 
-\paragraph{Progress in solver performance.}
+\subsection{Progress in Solver Performance.}
 
@@
 
-\paragraph{Unique solutions.}
+\subsection{Unique Solutions.}
 
@@
 
-\paragraph{Use of parallelism.}
+\subsection{Use of Parallelism.}
 
@@
 
+\subsection{Focussing on Satisfiability or Unsatisfiability}
+
+In the Main-track all divisions contain a mixture of problems that are satisfiable and unsatisfiable.
+However, some solvers may be specialised or optimised for a particular kind of problem.
+Therefore, it is interesting to ask whether the winners of divisions might have changed if benchmarks in that division had been restricted to one of these results.
+Table~\ref{tab:results:sat:unsat} shows the changes in division winners if only satisfiable or unsatisfiable results are given.
+
+\begin{table}
+\caption{Alternative winners if only Satisfiable (top) or Unsatisfiable (bottom) benchmarks had been considered.
+These results are in reference to those given in Table~\ref{tab:winners-main}.\label{tab:results:sat:unsat}}
+\centering
+\begin{tabular}{r@{\hskip 1em}>{\columncolor[gray]{.95}[.25em][.5em]}c@{\hskip 1em}>{\columncolor[gray]{.95}[.5em][.5em]}c@{\hskip 1em}>{\columncolor[gray]{.95}[.5em][.5em]}c@{\hskip 1em}>{\columncolor[gray]{.95}[.5em][0.25em]}c}
+\toprule
+Division         &  2015                 &  2016                    &  2017                  &  2018                      \\
+\hline \hline
+AUFLIA  & CVC3  &   &   & Alt-Ergo  \\
+AUFNIRA & \nc{Z3}  & CVC4 \nc{Z3}  & CVC4 \nc{Z3}  & \nc{Z3}  \\
+NIA     & CVC3  &   &   &   \\
+NRA     & CVC3  & CVC4  & CVC4  & CVC4\nc{Z3}Z3  \\
+QF\_AUFBV        & Yices  & Yices2  &   & Yices2  \\
+QF\_LIA  & \nc{Z3}  &   &   &   \\
+QF\_UFIDL        & \nc{Z3}  & \nc{Z3}  & \nc{Z3}  & \nc{Z3} veriT  \\
+QF\_UFNIA        & CVC3  &   & CVC4  &   \\
+UFLIA   & \nc{Z3}  &   &   &   \\
+UFLRA   & CVC3  & CVC4  &   &   \\
+AUFLIRA &   & CVC4  & CVC4  & Alt-Ergo  \\
+BV      &   & \nc{Z3}  & Boolector  & Boolector  \\
+QF\_ABV  &   & Yices2  & Yices2  &   \\
+QF\_BV   &   & MinkeyRink  &   &   \\
+QF\_NIA  &   & SMT-RAT  &   &   \\
+UF      &   & Vampire  &   &   \\
+UFBV    &   & Boolector  &   &   \\
+UFNIA   &   & CVC4  & CVC4  & CVC4  \\
+LRA     &   &   & veriT+Redlog  &   \\
+QF\_LRA  &   &   & Yices2  & Yices2  \\
+QF\_NIRA &   &   & CVC4  &   \\
+QF\_NRA  &   &   & \nc{Z3}  &   \\
+UFDTLIA &   &   & CVC4  &   \\
+ALIA    &   &   &   & Alt-Ergo  \\
+QF\_FP   &   &   &   & CVC4  \\
+QF\_UFBV &   &   &   & Yices2  \\
+\bottomrule
+\end{tabular}
+
+\begin{tabular}{r@{\hskip 1em}>{\columncolor[gray]{.95}[.25em][.5em]}c@{\hskip 1em}>{\columncolor[gray]{.95}[.5em][.5em]}c@{\hskip 1em}>{\columncolor[gray]{.95}[.5em][.5em]}c@{\hskip 1em}>{\columncolor[gray]{.95}[.5em][0.25em]}c}
+\toprule
+Division         &  2015                 &  2016                    &  2017                  &  2018                      \\
+\hline \hline
+QF\_AUFNIA       & \nc{Z3}  & \nc{Z3}  &   &   \\
+QF\_IDL  & CVC4  &   & \nc{Z3}  & CVC4 \nc{Z3}  \\
+QF\_LIA  & SMTInterpol  & SMTInterpol  & SMTInterpol  & SMTInterpol  \\
+QF\_NIA  & CVC3  &   & Yices2  &   \\
+BV      &   & CVC4  &   &   \\
+NIA     &   & CVC4  & Vampire  & Vampire  \\
+QF\_UFNRA        &   & CVC4 \nc{Z3}  & CVC4  & CVC4 \nc{Z3}  \\
+UFIDL   &   & Vampire \nc{Z3}  & \nc{Z3}  &   \\
+QF\_AUFBV        &   &   & CVC4  &   \\
+QF\_BV   &   &   & Boolector  &   \\
+QF\_UFLIA        &   &   & \nc{Z3}  &   \\
+UF      &   &   & CVC4  & CVC4  \\
+UFLRA   &   &   & veriT  & veriT  \\
+QF\_NRA  &   &   &   & CVC4  \\
+\bottomrule
+\end{tabular}
+
+\end{table}
+
+\subsection{Very Quick Solutions}
+
+Table~\ref{tab:results:24s}
+
+\begin{table}
+\caption{Alternative winners if the time limit had been 24 seconds.\label{tab:results:24s}}
+\centering
+
+\begin{tabular}{r@{\hskip 1em}>{\columncolor[gray]{.95}[.25em][.5em]}c@{\hskip 1em}>{\columncolor[gray]{.95}[.5em][.5em]}c@{\hskip 1em}>{\columncolor[gray]{.95}[.5em][.5em]}c@{\hskip 1em}>{\columncolor[gray]{.95}[.5em][0.25em]}c}
+\toprule
+Division         &  2015                 &  2016                    &  2017                  &  2018                      \\
+\hline \hline
+AUFLIRA & CVC3  &   &   & Alt-Ergo  \\
+AUFNIRA & \nc{Z3}  &   &   & \nc{Z3}  \\
+QF\_BV   & CVC4  & STP \nc{Z3}  &   & Boolector  \\
+QF\_LIA  & Yices  & Yices2  & Yices2  &   \\
+QF\_LRA  & Yices  & Yices2  & Yices2  & Yices2  \\
+QF\_UF   & veriT  & veriT  &   &   \\
+UFNIA   & \nc{Z3}  &   &   & \nc{Z3}  \\
+AUFLIA  &   & Vampire \nc{Z3}  & veriT  &   \\
+QF\_ABV  &   & Yices2  &   &   \\
+QF\_ANIA &   & \nc{Z3}  & \nc{Z3}  &   \\
+QF\_UFNRA        &   & CVC4 \nc{Z3}  & CVC4  & \nc{Z3}  \\
+UF      &   & Vampire  &   &   \\
+UFBV    &   & Boolector  &   &   \\
+UFIDL   &   & Vampire \nc{Z3}  & \nc{Z3}  &   \\
+QF\_NIA  &   &   & Yices2  & Yices2  \\
+QF\_NIRA &   &   & Yices2 Z3  & Yices2 \nc{Z3}  \\
+QF\_NRA  &   &   & \nc{Z3}  &   \\
+UFLRA   &   &   & veriT  & veriT  \\
+BV      &   &   &   & Boolector \nc{Z3}  \\
+NRA     &   &   &   & CVC4 \nc{Z3}  \\
+UFLIA   &   &   &   & \nc{Z3}  \\
+\bottomrule
+\end{tabular}
+\end{table}
+
+\subsection{Do Families Matter?}
+
+Table~\ref{tab:results:total:solved}
+
+\begin{table}
+\caption{Alternative winners if families were not used in computing scores e.g. the 2015 scoring system were used.\label{tab:results:total:solved}}
+\centering
+\begin{tabular}{r@{\hskip 1em}>{\columncolor[gray]{.95}[.25em][.5em]}c@{\hskip 1em}>{\columncolor[gray]{.95}[.5em][.5em]}c@{\hskip 1em}>{\columncolor[gray]{.95}[.5em][.5em]}c@{\hskip 1em}>{\columncolor[gray]{.95}[.5em][0.25em]}c}
+\toprule
+Division         &  2015                 &  2016                    &  2017                  &  2018                      \\
+\hline\hline
+AUFNIRA &   & CVC4  &   &   \\
+UFIDL   &   & \nc{Z3}  &   &   \\
+BV      &   &   & Boolector  &   \\
+QF\_LRA  &   &   & Yices2  & SPASS-SATT  \\
+QF\_NIA  &   &   & Yices2  & Yices2  \\
+QF\_BV   &   &   &   & Boolector  \\
+QF\_FP   &   &   &   & CVC4  \\
+\bottomrule
+\end{tabular}
+\end{table}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2019-04-11 2018/report/SMT-COMP.tex
Add description of further analysis tables

@@
 Table~\ref{tab:results:sat:unsat} shows the changes in division winners if only satisfiable or unsatisfiable results are given.
+This table only lists a solver if the winner has changed.
+A non-competing solver is listed by itself if it now outperforms the winning competitive solver.
+
+It is interesting to note that we see some new solvers winning divisions that did not win any division in the main results.
+For example, Alt-Ergo solves the most satisfiable problems in AUFLIA and ALIA in 2018 and SMTInterpol performs very well on unsatisfiable problems in QF\_LIA.
 
@@
 
+%%%%%%%%%%%%%%%%%%%%
 \subsection{Very Quick Solutions}
 
-Table~\ref{tab:results:24s}
+The time limits used in each year are relatively long (20 or 40 minutes) whereas some applications of SMT solvers (e.g.
+software verification) make use of very short time limits.
+We ask the question \emph{how would the results change if we consider a much shorter time limit of 24 seconds?}\footnote{This time limit was inspired by a conversation with Liana Hadarean as it is a time limit being used in one application of SMT solvers in Amazon.}.
+The results of this analysis are given in Table~\ref{tab:results:24s}.
+As in the previous, this highlights the different winners under this new scheme only.
+Here we see STP winning a division for the first time in our analysis (QF\_BV in 2016) and Yices2 performing well.
 
@@
 
-Table~\ref{tab:results:total:solved}
+In 2016 the Main-track competition scoring was changed to weight the correctness score for benchmarks by the size of the family the benchmark belongs to.
+Here we ask what the winners would have been if this change had not been made.
+The answer to this question is given in Table~\ref{tab:results:total:solved}.
+Relatively few changes would have occurred.
+Unsurprisingly the differences are in the larger and more structured divisions.
+
+Whilst producing these results we noticed that the description of what constitutes a family had been incorrectly interpreted by the scoring scripts in 2016-2018.
+After fixing this misinterpretation we note that only a single division winner changes.
+As this is in the past we are choosing not to retroactively change the winner (and all tables in this paper reflect the previously published results) but the scripts have been fixed for future iterations of the competition.
 

### 2019-04-11 rules/rules19.tex
add todos

@@
 SMT-COMP~2019.
-The principal changes from the previous competition rules are the following:
+The principal changes from the previous competition rules are the following: \todo{Aina in charge of this section}
 \begin{itemize}
@@
 System descriptions must be submitted until the final solver deadline System
-descriptions will be made publicly available.
+descriptions will be made publicly available. \todo{Giles: Include licence information - minimum requirement: licence must allow to run the binary for evaluation purposes}
 
@@
 
-\todo{Add information that these solver versions will be made available
-on the smt-comp website for archiving purposes? What are the implications of
-this?}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 Workshop.
+
+\header{Competition Website}
+
+\todo{Giles: Add text about the fact that we will use the competition website to include links to tools, announce results etc... including archiving}
+%
 
@@
   \item In all tracks except the \incremental Track, there is exactly one
-    \akey{check-sat} command. \todo{is that true for the challenge track?}
+    \akey{check-sat} command.
   \item In the incremental track, there are one or more
@@
   always issued in a satisfiable context) is followed by a single
-  \akey{get-model} command. \todo{Liana: please verify}
+  \akey{get-model} command.
 \item The script may optionally contain an \akey{exit} command as its
@@
 
-\header{Time and memory limits.}
+\header{Time and memory limits.} \todo{Aina: Move all time and memory limits to the individual sections and forward reference from here}
 %
@@
 The time limit~$T$ will be 40~minutes of wall-clock time per solver/benchmark
-pair in the \main, \incremental and \ucore tracks, \todo{XX}~minutes in the
-\challenge Track, and \todo{XX}~minutes in the \mval Track
-\todo{Need to elaborate how time is split? Do we
-need two time limits here, one for solving and one for
-validation?}.\footnote{The time limit may be
+pair in the \main, \incremental and \ucore tracks, \todo{12 hours} in the
+\challenge Track, and \todo{40 + 5 as in Unsat core}~minutes in the \mval Track \footnote{The time limit may be
 adjusted once we know the number of competition entrants and eligible
@@
 (possibly with corresponding \akey{push 1} and \akey{pop 1} commands). It is
-parsed by a (publicly available) \emph{trace executor}\footnote{\todo{link}},
+parsed by a (publicly available) \emph{trace executor},
 which serves the following purposes: \begin{itemize} \item it simulates the
@@
 The \challenge Track will follow the same rules as the \main Track,
-with two exceptions: benchmark selection and the time limit. The track will run on
-all SMT-LIB benchmarks that have an unknown status and that have been tagged as being
- \emph{industrial}. Additionally we will include benchmarks nominated by the community.
+with two exceptions: benchmark selection and the time limit. The track will run on benchmarks nominated by the community.
 \lh{TODO: benchmark selection still needs discussion}
-\lh{TODO: We didn't decide on what we do if only one solver gives an answer and we don't
-know if the problem is sat/unsat}
+\lh{TODO: scored in the same way as main track (mention later not here)}
 
@@
 
+\todo{Liana - check if we can use the SMT-LIB standard and if so say that we will here, or if we need slight changes state them here.}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-\todo{We do not run non-competitive divisions.}
+\todo{Aina: We do not run non-competitive divisions.}
 
@@
 top-level assertions.
-\todo{add information about how benchmarks are selected for the \mval,
-\challenge, \ucore tracks, and the 24s, sat and unsat scores -- either here
-or below}
 
@@
 
-\header{Benchmark selection.}
+\header{Benchmark selection.} \todo{Antti covers this section}
 %
@@
 when the competition begins.
+
+\todo{add information about how benchmarks are selected for the \mval,
+\challenge, \ucore tracks, and the 24s, sat and unsat scores -- either here
+or below}
+
+\todo{For Unsatcore remove all benchmarks with a single assertion, otherwise use same procedure as last year... check what that was}
 

### 2019-04-12 2018/report/SMT-COMP.tex
Report: TODO 22
Report: TODO 19: Minor things

@@
 the SMT Library since~2015.  While the library usually grows from one
-year to the next because of the inclusion of new benchmarks and
+year to the other because of the inclusion of new benchmarks and
 logics, continuous curation efforts may also cause benchmarks to be
@@
 they want to enter, and competition results are reported separately
-for each track and division.  Thus, competing solvers need not support
+for each track and division.  Thus, competing solvers do not need support
 all logics, and may or may not support features such as incrementality
@@
 status was unknown.  However, this approach was criticized for
-favoring imitation of existing solvers over true innovation.  In~2016,
+imitating existing solvers rather than truly innovating.  In~2016,
 the SMT Library contained 29,724 non-incremental benchmarks with
@@
 Competition, allowing its workload to be completed within two to three
-weeks.  By these measures, the SMT Competition has become not only one
-of the heaviest users of StarExec, but also one of the largest
-competitions in automated reasoning.
+weeks.
 
@@
 purpose~\cite{CDW14}.  This ranking emphasizes breadth of solver
-participation---a solver participating in many logics need not be the
+participation---a solver participating in many logics does not need to be the
 best in any one of them to rank highly.
@@
 Note that scores are not directly comparable between different years:
-the set of benchmarks changes from one year to the next, and also the
+the set of benchmarks changes from one year to the other, and also the
 formula to compute the score changed (see below).  Moreover, readers
@@
 Games, which sponsored seven medals.  The competition organizers
-awarded these to the following solvers:
+awarded the following solvers:
 \begin{itemize}

### 2019-04-12 rules/rules19.tex
Rules: More TODOs.

@@
 %
+\todo{add minimum requirement for authorship?}
 As part of the submission, SMT-COMP entrants are \emph{required} to provide a
@@
 \todo{Giles: update}
+\todo{reword? "one or more SMT solvers of which the author of the wrapper tool
+is not an author"}
 A \emph{wrapper tool} is defined as any solver that calls (or is in

### 2019-04-12 2018/report/SMT-COMP.tex
Report: TODO 4

@@
 
+Participants are required to be authors of the tool they submit.
+In 2015--2018, the competition rules did not further define authorship,
+but it is understood that an author contributed code to the tool.
+As a special case of this rule, participants are required to identify
+if their tool is a wrapper tool, i.e., any solver that calls (or is in some
+other way based on) one or more SMT solvers of which the author of the tool
+is not an author.
+
 Tables~\ref{table:participants1}-\ref{table:participants3} list the solvers
@@
 have changed over time).
+
+Further, there was no restriction on the number of solver versions participants
+may submit, but the organizers reserved the right to not accept multiple
+versions of a solver in case the number of solver submissions is too large for
+the computational resources. In the past four years, executing this right was
+not necessary.
 %
-Participants are also encouraged to submit a short system description
-of their solver, including a list of its authors and an explanation of
-the SMT solving approach used.  System descriptions are published on
-the competition website.  They were submitted for about 60\,\% of all
-solver versions since 2015.
-
-\include{table-participants}
-
 Many of these solvers were submitted in multiple years.  Additionally,
@@
 versions of each solver were submitted in each year.
+
+Participants were not required to provide source code with their submission.
+There were no licensing requirements/restrictions for the submitted binaries
+of the participating solvers.
+%
+Participants were encouraged to submit a short system description
+of their solver, including a list of its authors and an explanation of
+the SMT solving approach used.  System descriptions are published on
+the competition website.  They were submitted for about 60\,\% of all
+solver versions since 2015.
+
+\include{table-participants}
 

### 2019-04-13 2018/report/SMT-COMP.tex
Benchmark weights, minor

@@
 Main-track benchmark in order to de-emphasize large benchmark
-families~\cite{rules18}.
+families~\cite{rules18}.  A benchmark's weight is computed as $(1 +
+\ln F)/F$, where~$F\geq 1$ is the size of the benchmark's family.  The
+log scaling seems a reasonable compromise between linearly combining
+numbers of benchmarks, which would overemphasize large families, and
+simply averaging the fraction of benchmarks solved, which would
+overemphasize small families.
 
@@
 that division.  But the competition's Main track consists of many
-independent divisions.  To balance the strong interest in correct
-solvers against the risk of stifling innovation, the competition-wide
-ranking was revised in~2017 to use a fixed numeric penalty for each
-division with incorrect responses.  The value of this penalty is
-currently set so that entering a (possibly buggy) solver that can
-solve all benchmarks into a division has a positive expected score if
-the probability that a soundness bug in the solver will be triggered
-is below~$20\,\%$.~\cite{rules18}
+independent divisions.  A solver bug that affects one division need
+not manifest itself in other divisions.  To balance the strong
+interest in correct solvers against the risk of stifling innovation,
+the competition-wide ranking was revised in~2017 to use a fixed
+numeric penalty for each division with incorrect responses.  The value
+of this penalty is currently set so that entering a (possibly buggy)
+solver that can solve all benchmarks into a division has a positive
+expected score if the probability that a soundness bug in the solver
+will be triggered is below~$20\,\%$.~\cite{rules18}
 

### 2019-04-13 2018/report/SMT-COMP.tex
TODO 16: add brief explanation of competition-wide ranking

@@
 
-In 2014, the SMT Competition was part of the FLoC Olympic Games.
-These gave the competition increased visibility and sponsored three
-Kurt G\"odel medals.  After substantial internal debate, the 2014
-competition organizers decided to award these to the winner of the
-Main track's QF\_BV division (which had historically been the logic
-with the largest number of solver submissions and job pairs), as well
-as to the two best Main-track solvers according to a competition-wide
-ranking that had been instituted especially for this
-purpose~\cite{CDW14}.  This ranking emphasizes breadth of solver
-participation---a solver participating in many logics does not need to be the
-best in any one of them to rank highly.
+In 2014, the SMT Competition was part of the FLoC Olympic Games, which
+sponsored three Kurt G\"odel medals.  These were awarded to the winner
+of the Main track's QF\_BV division (which had historically been the
+logic with the largest number of solver submissions and job pairs), as
+well as to the two best Main-track solvers according to a
+competition-wide ranking that had been instituted especially for this
+purpose~\cite{CDW14}.  This ranking combines each solver's performance
+across all competitive Main-track divisions into a single score,
+giving more weight to larger divisions, and to solvers that solve a
+large fraction of the benchmarks~\cite{rules18}.  It emphasizes
+breadth of solver participation---a solver participating in many
+logics does not need to be the best in any one of them to rank highly.
 

### 2019-04-13 2018/report/SMT-COMP.tex
update tables

@@
 benchmarks are assumed to be correct, unless there is a disagreement
-between two or more (otherwise sound) solvers.  Benchmarks with
-disagreements are removed from the competition results.  In 2016,
+between two or more (otherwise sound e.g. on problems with known status) solvers.  Benchmarks with
+disagreements are removed from the competition results.
+This conservative approach was chosen over a voting system as this situation is expected to be rare as the SMT-LIB organisers go to a significant effort prior to each competition to update the statuses of problems.
+A manual investigation is therefore preferred over an automated resolution.
+Disagreements are reported to the solvers involved and in all cases have led to bugs in solvers being identified and fixed.
+In 2016,
 there were disagreements on 79 benchmarks; in 2017, only one benchmark
@@
 commands with unknown status.
+Even though the trace executor has now been modified, we cannot check what impact this may have had on previous results without rerunning all tracks as the trace executor drives the solver.
 
@@
 
+The use of StarExec ensures the \emph{reproducibility} of the competition.
+The publicly accessible space \url{https://www.starexec.org/starexec/secure/explore/spaces.jsp?id=2641} stores all of the information required to rerun the competition e.g.
+all benchmarks and copies of all tools.
+In addition, a GitHub organisation (\url{https://github.com/SMT-COMP/smt-comp}) has been setup to archive previous results and store the tools used by organisers to run the competition.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \hline \hline
+ALIA    &   &   &   & Alt-Ergo  \\
 AUFLIA  & CVC3  &   &   & Alt-Ergo  \\
+AUFLIRA &   & CVC4  & CVC4  & Alt-Ergo  \\
 AUFNIRA & \nc{Z3}  & CVC4 \nc{Z3}  & CVC4 \nc{Z3}  & \nc{Z3}  \\
+BV      &   & \nc{Z3}  & Boolector  & Boolector  \\
+LRA     &   &   & veriT+Redlog  &   \\
 NIA     & CVC3  &   &   &   \\
-NRA     & CVC3  & CVC4  & CVC4  & CVC4\nc{Z3}Z3  \\
+NRA     & CVC3  & CVC4  & CVC4  & CVC4 \nc{Z3}  \\
+QF\_ABV  &   & Yices2  & Yices2  &   \\
 QF\_AUFBV        & Yices  & Yices2  &   & Yices2  \\
+QF\_BV   &   & \nc{Z3}/MinkeyRink  &   &   \\
+QF\_FP   &   &   &   & CVC4  \\
 QF\_LIA  & \nc{Z3}  &   &   &   \\
+QF\_LRA  &   &   & Yices2  & Yices2  \\
+QF\_NIA  &   & SMT-RAT  &   &   \\
+QF\_NIRA &   &   & CVC4  &   \\
+QF\_NRA  &   &   & \nc{Z3}  &   \\
+QF\_UFBV &   &   &   & Yices2  \\
 QF\_UFIDL        & \nc{Z3}  & \nc{Z3}  & \nc{Z3}  & \nc{Z3} veriT  \\
 QF\_UFNIA        & CVC3  &   & CVC4  &   \\
+UF      &   & Vampire  &   & Vampire/-  \\
+UFBV    &   & Boolector  &   &   \\
+UFDTLIA &   &   & CVC4  &   \\
 UFLIA   & \nc{Z3}  &   &   &   \\
 UFLRA   & CVC3  & CVC4  &   &   \\
-AUFLIRA &   & CVC4  & CVC4  & Alt-Ergo  \\
-BV      &   & \nc{Z3}  & Boolector  & Boolector  \\
-QF\_ABV  &   & Yices2  & Yices2  &   \\
-QF\_BV   &   & MinkeyRink  &   &   \\
-QF\_NIA  &   & SMT-RAT  &   &   \\
-UF      &   & Vampire  &   &   \\
-UFBV    &   & Boolector  &   &   \\
 UFNIA   &   & CVC4  & CVC4  & CVC4  \\
-LRA     &   &   & veriT+Redlog  &   \\
-QF\_LRA  &   &   & Yices2  & Yices2  \\
-QF\_NIRA &   &   & CVC4  &   \\
-QF\_NRA  &   &   & \nc{Z3}  &   \\
-UFDTLIA &   &   & CVC4  &   \\
-ALIA    &   &   &   & Alt-Ergo  \\
-QF\_FP   &   &   &   & CVC4  \\
-QF\_UFBV &   &   &   & Yices2  \\
 \bottomrule
@@
 \hline \hline
+BV      &   & CVC4  &   &   \\
+NIA     &   & CVC4  & Vampire  & Vampire  \\
+QF\_AUFBV        &   &   & CVC4  &   \\
 QF\_AUFNIA       & \nc{Z3}  & \nc{Z3}  &   &   \\
+QF\_BV   &   &   & Boolector  &   \\
 QF\_IDL  & CVC4  &   & \nc{Z3}  & CVC4 \nc{Z3}  \\
@@
 QF\_NIA  & CVC3  &   & Yices2  &   \\
-BV      &   & CVC4  &   &   \\
-NIA     &   & CVC4  & Vampire  & Vampire  \\
+QF\_NRA  &   &   &   & CVC4  \\
+QF\_UFLIA        &   &   & \nc{Z3}  &   \\
 QF\_UFNRA        &   & CVC4 \nc{Z3}  & CVC4  & CVC4 \nc{Z3}  \\
+UF      &   &   & CVC4  & -/CVC4  \\
 UFIDL   &   & Vampire \nc{Z3}  & \nc{Z3}  &   \\
-QF\_AUFBV        &   &   & CVC4  &   \\
-QF\_BV   &   &   & Boolector  &   \\
-QF\_UFLIA        &   &   & \nc{Z3}  &   \\
-UF      &   &   & CVC4  & CVC4  \\
 UFLRA   &   &   & veriT  & veriT  \\
-QF\_NRA  &   &   &   & CVC4  \\
 \bottomrule
@@
 software verification) make use of very short time limits.
-We ask the question \emph{how would the results change if we consider a much shorter time limit of 24 seconds?}\footnote{This time limit was inspired by a conversation with Liana Hadarean as it is a time limit being used in one application of SMT solvers in Amazon.}.
+We ask the question \emph{how would the Main track results change if we consider a much shorter time limit of 24 seconds?}\footnote{This time limit was inspired by a conversation with Liana Hadarean as it is a time limit being used in one application of SMT solvers in Amazon.}.
+We only consider the Main track here as this is the setting where short time limits are most likely to be relevant.
 The results of this analysis are given in Table~\ref{tab:results:24s}.
@@
 \hline \hline
-AUFLIRA & CVC3  &   &   & Alt-Ergo  \\
+AUFLIA  &   & Vampire \nc{Z3}  & veriT  &   \\
+AUFLIRA & CVC3  &   &   & -/Alt-Ergo  \\
 AUFNIRA & \nc{Z3}  &   &   & \nc{Z3}  \\
-QF\_BV   & CVC4  & STP \nc{Z3}  &   & Boolector  \\
+BV      &   &   &   & Boolector/Boolector \nc{Z3}  \\
+NRA     &   &   &   & CVC4/CVC4 \nc{Z3}  \\
+QF\_ABV  &   & Yices2  &   &   \\
+QF\_ANIA &   & \nc{Z3}  & \nc{Z3}  &   \\
+QF\_BV   & CVC4  & STP \nc{Z3}  & Boolector+CaDiCaL/-  & Boolector  \\
 QF\_LIA  & Yices  & Yices2  & Yices2  &   \\
 QF\_LRA  & Yices  & Yices2  & Yices2  & Yices2  \\
+QF\_NIA  &   &   & Yices2  & Yices2  \\
+QF\_NIRA &   &   & Yices2 \nc{Z3}  & Yices2 \nc{Z3}  \\
+QF\_NRA  &   &   & \nc{Z3}  &   \\
 QF\_UF   & veriT  & veriT  &   &   \\
-UFNIA   & \nc{Z3}  &   &   & \nc{Z3}  \\
-AUFLIA  &   & Vampire \nc{Z3}  & veriT  &   \\
-QF\_ABV  &   & Yices2  &   &   \\
-QF\_ANIA &   & \nc{Z3}  & \nc{Z3}  &   \\
 QF\_UFNRA        &   & CVC4 \nc{Z3}  & CVC4  & \nc{Z3}  \\
-UF      &   & Vampire  &   &   \\
+UF      &   & Vampire  &   &  Vampire/- \\
 UFBV    &   & Boolector  &   &   \\
 UFIDL   &   & Vampire \nc{Z3}  & \nc{Z3}  &   \\
-QF\_NIA  &   &   & Yices2  & Yices2  \\
-QF\_NIRA &   &   & Yices2 Z3  & Yices2 \nc{Z3}  \\
-QF\_NRA  &   &   & \nc{Z3}  &   \\
+UFLIA   &   &   &   & \nc{Z3}  \\
 UFLRA   &   &   & veriT  & veriT  \\
-BV      &   &   &   & Boolector \nc{Z3}  \\
-NRA     &   &   &   & CVC4 \nc{Z3}  \\
-UFLIA   &   &   &   & \nc{Z3}  \\
+UFNIA   & \nc{Z3}  &   &   & CVC4/\nc{Z3}  \\
 \bottomrule
@@
 
+%%%%%%%%%%%%%%%%%
 \subsection{Do Families Matter?}
@@
 Whilst producing these results we noticed that the description of what constitutes a family had been incorrectly interpreted by the scoring scripts in 2016-2018.
-After fixing this misinterpretation we note that only a single division winner changes.
+After fixing this misinterpretation we note that only a single division winner changes - in 2017 AUFNIRA should have been won by
+
+.
 As this is in the past we are choosing not to retroactively change the winner (and all tables in this paper reflect the previously published results) but the scripts have been fixed for future iterations of the competition.
@@
 
+%%%%%%%%%%%%%%%%%
+\subsection{What Impact Did Adding Unknowns Have?}
+
+In 2017 the Main track ran with benchmarks with unknown status (removing any that had disagreements).
+An interesting question is to what extent this affected the winners in the Main track.
+Table~\ref{tab:results:unknowns} gives the alternative winners if these benchmarks had not been included.
+
+\begin{table}
+\caption{Alternative winners if benchmarks with unknown status had not bee included in 2017 onwards.\label{tab:results:unknowns}}
+\centering
+\begin{tabular}{r@{\hskip 1em}>{\columncolor[gray]{.95}[.25em][.5em]}c@{\hskip 1em}>{\columncolor[gray]{.95}[.5em][.5em]}c@{\hskip 1em}>{\columncolor[gray]{.95}[.5em][.5em]}c@{\hskip 1em}>{\columncolor[gray]{.95}[.5em][0.25em]}c}
+\toprule
+Division                       &  2017                  &  2018                      \\
+\hline\hline
+AUFNIRA & CVC4 & \\
+QF\_NIRA & \nc{Z3} & CVC4 \nc{Z3} \\
+QF\_NRA & \nc{Z3} & \\
+UFDTLIA & CVC4 & \\
+BV & & Boolector \\
+QF\_FP & & CVC4 \nc{Z3} \\
+UFNIA & & CVC4 \\
+NRA & & -/\nc{Z3} \\
+UF & & -/CVC4\\
+\bottomrule
+\end{tabular}
+\end{table}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2019-04-14 2018/report/SMT-COMP.tex
Report: Layout and clean up sat/unsat/24s tables.

@@
 
-%\usepackage{showframe}   % debug
+\usepackage{showframe}   % debug
 
@@
 \colorlet{rat}{Goldenrod!10}
-\colorlet{cvc3}{GreenYellow!10}
+\colorlet{cvc3}{Melon!10}
 \colorlet{redl}{Yellow!10}
+\colorlet{alt}{LimeGreen!10}
+\colorlet{verit}{MidnightBlue!10}
+\colorlet{stp}{Fuchsia!10}
 \colorlet{nonc}{black!55}
@@
 Therefore, it is interesting to ask whether the winners of divisions might have changed if benchmarks in that division had been restricted to one of these results.
-Table~\ref{tab:results:sat:unsat} shows the changes in division winners if only satisfiable or unsatisfiable results are given.
-This table only lists a solver if the winner has changed.
-A non-competing solver is listed by itself if it now outperforms the winning competitive solver.
+Tables~\ref{tab:results:sat}-\ref{tab:results::unsat} show the changes in division winners if only satisfiable or unsatisfiable results are given.
+This table is in reference to Table~\ref{tab:winners-main} and only lists a solver if the result has changed.
+A non-competing solver is listed by itself if it was not the overall best performing solver of that division but now outperforms the winning competitive solver .
 
@@
 
-\begin{table}
-\caption{Alternative winners if only Satisfiable (top) or Unsatisfiable (bottom) benchmarks had been considered.
-These results are in reference to those given in Table~\ref{tab:winners-main}.\label{tab:results:sat:unsat}}
-\centering
-\begin{tabular}{r@{\hskip 1em}>{\columncolor[gray]{.95}[.25em][.5em]}c@{\hskip 1em}>{\columncolor[gray]{.95}[.5em][.5em]}c@{\hskip 1em}>{\columncolor[gray]{.95}[.5em][.5em]}c@{\hskip 1em}>{\columncolor[gray]{.95}[.5em][0.25em]}c}
-\toprule
-Division         &  2015                 &  2016                    &  2017                  &  2018                      \\
-\hline \hline
-ALIA    &   &   &   & Alt-Ergo  \\
-AUFLIA  & CVC3  &   &   & Alt-Ergo  \\
-AUFLIRA &   & CVC4  & CVC4  & Alt-Ergo  \\
-AUFNIRA & \nc{Z3}  & CVC4 \nc{Z3}  & CVC4 \nc{Z3}  & \nc{Z3}  \\
-BV      &   & \nc{Z3}  & Boolector  & Boolector  \\
-LRA     &   &   & veriT+Redlog  &   \\
-NIA     & CVC3  &   &   &   \\
-NRA     & CVC3  & CVC4  & CVC4  & CVC4 \nc{Z3}  \\
-QF\_ABV  &   & Yices2  & Yices2  &   \\
-QF\_AUFBV        & Yices  & Yices2  &   & Yices2  \\
-QF\_BV   &   & \nc{Z3}/MinkeyRink  &   &   \\
-QF\_FP   &   &   &   & CVC4  \\
-QF\_LIA  & \nc{Z3}  &   &   &   \\
-QF\_LRA  &   &   & Yices2  & Yices2  \\
-QF\_NIA  &   & SMT-RAT  &   &   \\
-QF\_NIRA &   &   & CVC4  &   \\
-QF\_NRA  &   &   & \nc{Z3}  &   \\
-QF\_UFBV &   &   &   & Yices2  \\
-QF\_UFIDL        & \nc{Z3}  & \nc{Z3}  & \nc{Z3}  & \nc{Z3} veriT  \\
-QF\_UFNIA        & CVC3  &   & CVC4  &   \\
-UF      &   & Vampire  &   & Vampire/-  \\
-UFBV    &   & Boolector  &   &   \\
-UFDTLIA &   &   & CVC4  &   \\
-UFLIA   & \nc{Z3}  &   &   &   \\
-UFLRA   & CVC3  & CVC4  &   &   \\
-UFNIA   &   & CVC4  & CVC4  & CVC4  \\
-\bottomrule
-\end{tabular}
-
-\begin{tabular}{r@{\hskip 1em}>{\columncolor[gray]{.95}[.25em][.5em]}c@{\hskip 1em}>{\columncolor[gray]{.95}[.5em][.5em]}c@{\hskip 1em}>{\columncolor[gray]{.95}[.5em][.5em]}c@{\hskip 1em}>{\columncolor[gray]{.95}[.5em][0.25em]}c}
-\toprule
-Division         &  2015                 &  2016                    &  2017                  &  2018                      \\
-\hline \hline
-BV      &   & CVC4  &   &   \\
-NIA     &   & CVC4  & Vampire  & Vampire  \\
-QF\_AUFBV        &   &   & CVC4  &   \\
-QF\_AUFNIA       & \nc{Z3}  & \nc{Z3}  &   &   \\
-QF\_BV   &   &   & Boolector  &   \\
-QF\_IDL  & CVC4  &   & \nc{Z3}  & CVC4 \nc{Z3}  \\
-QF\_LIA  & SMTInterpol  & SMTInterpol  & SMTInterpol  & SMTInterpol  \\
-QF\_NIA  & CVC3  &   & Yices2  &   \\
-QF\_NRA  &   &   &   & CVC4  \\
-QF\_UFLIA        &   &   & \nc{Z3}  &   \\
-QF\_UFNRA        &   & CVC4 \nc{Z3}  & CVC4  & CVC4 \nc{Z3}  \\
-UF      &   &   & CVC4  & -/CVC4  \\
-UFIDL   &   & Vampire \nc{Z3}  & \nc{Z3}  &   \\
-UFLRA   &   &   & veriT  & veriT  \\
-\bottomrule
-\end{tabular}
-
-\end{table}
+\input{table-winners-main-sat-unsat}
 
@@
 
-\begin{table}
-\caption{Alternative winners if the time limit had been 24 seconds.\label{tab:results:24s}}
-\centering
-
-\begin{tabular}{r@{\hskip 1em}>{\columncolor[gray]{.95}[.25em][.5em]}c@{\hskip 1em}>{\columncolor[gray]{.95}[.5em][.5em]}c@{\hskip 1em}>{\columncolor[gray]{.95}[.5em][.5em]}c@{\hskip 1em}>{\columncolor[gray]{.95}[.5em][0.25em]}c}
-\toprule
-Division         &  2015                 &  2016                    &  2017                  &  2018                      \\
-\hline \hline
-AUFLIA  &   & Vampire \nc{Z3}  & veriT  &   \\
-AUFLIRA & CVC3  &   &   & -/Alt-Ergo  \\
-AUFNIRA & \nc{Z3}  &   &   & \nc{Z3}  \\
-BV      &   &   &   & Boolector/Boolector \nc{Z3}  \\
-NRA     &   &   &   & CVC4/CVC4 \nc{Z3}  \\
-QF\_ABV  &   & Yices2  &   &   \\
-QF\_ANIA &   & \nc{Z3}  & \nc{Z3}  &   \\
-QF\_BV   & CVC4  & STP \nc{Z3}  & Boolector+CaDiCaL/-  & Boolector  \\
-QF\_LIA  & Yices  & Yices2  & Yices2  &   \\
-QF\_LRA  & Yices  & Yices2  & Yices2  & Yices2  \\
-QF\_NIA  &   &   & Yices2  & Yices2  \\
-QF\_NIRA &   &   & Yices2 \nc{Z3}  & Yices2 \nc{Z3}  \\
-QF\_NRA  &   &   & \nc{Z3}  &   \\
-QF\_UF   & veriT  & veriT  &   &   \\
-QF\_UFNRA        &   & CVC4 \nc{Z3}  & CVC4  & \nc{Z3}  \\
-UF      &   & Vampire  &   &  Vampire/- \\
-UFBV    &   & Boolector  &   &   \\
-UFIDL   &   & Vampire \nc{Z3}  & \nc{Z3}  &   \\
-UFLIA   &   &   &   & \nc{Z3}  \\
-UFLRA   &   &   & veriT  & veriT  \\
-UFNIA   & \nc{Z3}  &   &   & CVC4/\nc{Z3}  \\
-\bottomrule
-\end{tabular}
-\end{table}
+\input{table-winners-main-24s}
 

### 2019-04-14 2018/report/table-winners-main-24s.tex
Report: Layout and clean up sat/unsat/24s tables.

\begin{table}
  \caption{Alternative best solvers in the Main track if the time limit had been 24 seconds.}
  \label{tab:results:24s}
  \centering

  \begin{tabular}{r@{\hskip 1em}>{\columncolor{white}[.25em][.5em]}c@{\hskip 1em}>{\columncolor{white}[.5em][.5em]}c@{\hskip 1em}>{\columncolor{white}[.5em][.5em]}c@{\hskip 1em}>{\columncolor{white}[.5em][0.5em]}c}
    \toprule
    Division   &  2015             &  2016                      &  2017                     &  2018                                  \\
    \hline \hline
    AUFLIA     &                   & \cc{vamp} Vampire \nc{Z3}  & \cc{verit} veriT          &                                        \\
    AUFLIRA    & \cc{cvc3} CVC3    &                            &                           & -/Alt-Ergo                             \\
    AUFNIRA    & \nonc \nc{Z3}     &                            &                           & \nc{Z3}                                \\
    BV         &                   &                            &                           & \cc{bool} Boolector/Boolector \nc{Z3}  \\
    NRA        &                   &                            &                           & \cc{cvc4} CVC4/CVC4 \nc{Z3}            \\
    QF\_ABV    &                   & \cc{yices} Yices2          &                           &                                        \\
    QF\_ANIA   &                   & \nonc \nc{Z3}              & \nonc \nc{Z3}             &                                        \\
    QF\_BV     & \cc{cvc4} CVC4    & \cc{stp} STP \nc{Z3}       &                           & -/Boolector                            \\
    QF\_LIA    & \cc{yices} Yices2 & \cc{yices} Yices2          & \cc{yices} Yices2         &                                        \\
    QF\_LRA    & \cc{yices} Yices2 & \cc{yices} Yices2          & \cc{yices} Yices2         & \cc{yices} Yices2                      \\
    QF\_NIA    &                   &                            & \cc{yices} Yices2         & \cc{yices} Yices2                      \\
    QF\_NIRA   &                   &                            & \cc{yices} Yices2 \nc{Z3} & \cc{yices} Yices2 \nc{Z3}              \\
    QF\_NRA    &                   &                            & \nc{Z3}                   &                                        \\
    QF\_UF     & \cc{verit} veriT  & \cc{verit} veriT           &                           &                                        \\
    QF\_UFNRA  &                   & \cc{cvc4} CVC4 \nc{Z3}     & \cc{cvc4} CVC4            & \nc{Z3}                                \\
    UF         &                   & \cc{vamp} Vampire          &                           &  \cc{vamp} Vampire/-                   \\
    UFBV       &                   & \cc{bool} Boolector        &                           &                                        \\
    UFIDL      &                   & \cc{vamp} Vampire \nc{Z3}  & \nc{Z3}                   &                                        \\
    UFLIA      &                   &                            &                           & \nc{Z3}                                \\
    UFLRA      &                   &                            & \cc{verit} veriT          & \cc{verit} veriT                       \\
    UFNIA      & \nonc \nc{Z3}     &                            &                           & \cc{cvc4} CVC4/\nc{Z3}                 \\
    \bottomrule
  \end{tabular}
\end{table}

### 2019-04-14 2018/report/table-winners-main-sat-unsat.tex
Report: Layout and clean up sat/unsat/24s tables.

\begin{table}
  \caption{Alternative best solvers in the Main track if only \emph{satisfiable} benchmarks had been considered. These results are in reference to those given in Table~\ref{tab:winners-main}.}
  \label{tab:results:sat}
\centering
  \begin{tabular}{r@{\hskip 1em}>{\columncolor{white}[.25em][.5em]}c@{\hskip 1em}>{\columncolor{white}[.5em][.5em]}c@{\hskip 1em}>{\columncolor{white}[.5em][.5em]}c@{\hskip 1em}>{\columncolor{white}[.5em][0.5em]}c}
    \toprule
    Division         &  2015                &  2016                   &  2017                   &  2018                     \\
    \hline \hline
    ALIA             &                      &                         &                         & \cc{alt} Alt-Ergo         \\
    AUFLIA           & \cc{cvc3} CVC3       &                         &                         & \cc{alt} Alt-Ergo         \\
    AUFLIRA          &                      & \cc{cvc4} CVC4          & \cc{cvc4} CVC4          & \cc{alt} Alt-Ergo         \\
    AUFNIRA          & \nonc\nc{Z3}         & \cc{cvc4} CVC4 \nc{Z3}  & \cc{cvc4} CVC4 \nc{Z3}  & \nc{Z3}                   \\
    BV               &                      & \nc{Z3}                 & \cc{bool} Boolector     & \cc{bool} Boolector       \\
    LRA              &                      &                         & \cc{verit} veriT        &                           \\
    NIA              & \nonc \cc{cvc3} CVC3 &                         &                         &                           \\
    NRA              & \nonc \cc{cvc3} CVC3 & \cc{cvc4} CVC4          & \cc{cvc4} CVC4          & \cc{cvc4} CVC4 \nc{Z3}    \\
    QF\_ABV          &                      & \cc{yices} Yices2       & \cc{yices} Yices2       &                           \\
    QF\_AUFBV        & \cc{yices} Yices     & \cc{yices} Yices2       &                         & \cc{yices} Yices2         \\
    QF\_BV           &                      & \nc{Z3}/MinkeyRink      &                         &                           \\
    QF\_FP           &                      &                         &                         & \cc{cvc4} CVC4            \\
    QF\_LIA          & \nc{Z3}              &                         &                         &                           \\
    QF\_LRA          &                      &                         & \cc{yices} Yices2       & \cc{yices} Yices2         \\
    QF\_NIA          &                      & \cc{rat} SMT-RAT        &                         &                           \\
    QF\_NIRA         &                      &                         & \cc{cvc4} CVC4          &                           \\
    QF\_NRA          &                      &                         & \nc{Z3}                 &                           \\
    QF\_UFBV         &                      &                         &                         & \cc{yices} Yices2         \\
    QF\_UFIDL        & \nc{Z3}              & \nc{Z3}                 & \nc{Z3}                 & \cc{verit} veriT  \nc{Z3} \\
    QF\_UFNIA        & \nonc \cc{cvc3} CVC3 &                         & \cc{cvc4} CVC4          &                           \\
    UF               &                      & \cc{vamp} Vampire       &                         & \cc{vamp}Vampire/-        \\
    UFBV             &                      & \cc{bool} Boolector     &                         &                           \\
    UFDTLIA          &                      &                         & \nonc \cc{cvc4} CVC4    &                           \\
    UFLIA            & \nc{Z3}              &                         &                         &                           \\
    UFLRA            & \cc{cvc3} CVC3       & \cc{cvc4} CVC4          &                         &                           \\
    UFNIA            &                      & \cc{cvc4} CVC4          & \cc{cvc4} CVC4          & \cc{cvc4} CVC4            \\
    \bottomrule
  \end{tabular}
\end{table}

\begin{table}
  \caption{Alternative best solvers in the Main track if only \emph{unsatisfiable} benchmarks had been considered. These results are in reference to those given in Table~\ref{tab:winners-main}.}
  \label{tab:results:unsat}
  \centering
  \begin{tabular}{r@{\hskip 1em}>{\columncolor{white}[.25em][.5em]}c@{\hskip 1em}>{\columncolor{white}[.5em][.5em]}c@{\hskip 1em}>{\columncolor{white}[.5em][.5em]}c@{\hskip 1em}>{\columncolor{white}[.5em][0.5em]}c}
\toprule
Division        &  2015                  &  2016                     &  2017                 &  2018                   \\
\hline \hline
    BV          &                        & \cc{cvc4} CVC4            &                       &                         \\
    NIA         &                        & \cc{cvc4} CVC4            & \cc{vamp} Vampire     & \cc{vamp} Vampire       \\
    QF\_AUFBV   &                        &                           & \cc{cvc4} CVC4        &                         \\
    QF\_AUFNIA  & \nonc \nc{Z3}          & \nonc \nc{Z3}             &                       &                         \\
    QF\_BV      &                        &                           & -/Boolector           &                         \\
    QF\_IDL     & \cc{cvc4} CVC4         &                           & \nc{Z3}               & \cc{cvc4} CVC4 \nc{Z3}  \\
    QF\_LIA     & \cc{smti} SMTInterpol  & \cc{smti} SMTInterpol     & \cc{smti} SMTInterpol & \cc{smti} SMTInterpol   \\
    QF\_NIA     & \cc{cvc3} CVC3         &                           & \cc{yices} Yices2     &                         \\
    QF\_NRA     &                        &                           &                       & \cc{cvc4} CVC4          \\
    QF\_UFLIA   &                        &                           & \nc{Z3}               &                         \\
    QF\_UFNRA   &                        & \cc{cvc4} CVC4 \nc{Z3}    & \cc{cvc4} CVC4        & \cc{cvc4} CVC4 \nc{Z3}  \\
    UF          &                        &                           & \cc{cvc4} CVC4        & -/CVC4                  \\
    UFIDL       &                        & \cc{vamp} Vampire \nc{Z3} & \nc{Z3}               &                         \\
    UFLRA       &                        &                           & \cc{verit} veriT      & \cc{verit} veriT        \\
    \bottomrule
  \end{tabular}

\end{table}

### 2019-04-14 2018/report/SMT-COMP.tex
Report: Layout and clean up main track winners tables for families and unknown.

@@
 
-\begin{table}
-\caption{Alternative winners if families were not used in computing scores e.g. the 2015 scoring system were used.\label{tab:results:total:solved}}
-\centering
-\begin{tabular}{r@{\hskip 1em}>{\columncolor[gray]{.95}[.25em][.5em]}c@{\hskip 1em}>{\columncolor[gray]{.95}[.5em][.5em]}c@{\hskip 1em}>{\columncolor[gray]{.95}[.5em][.5em]}c@{\hskip 1em}>{\columncolor[gray]{.95}[.5em][0.25em]}c}
-\toprule
-Division         &  2015                 &  2016                    &  2017                  &  2018                      \\
-\hline\hline
-AUFNIRA &   & CVC4  &   &   \\
-UFIDL   &   & \nc{Z3}  &   &   \\
-BV      &   &   & Boolector  &   \\
-QF\_LRA  &   &   & Yices2  & SPASS-SATT  \\
-QF\_NIA  &   &   & Yices2  & Yices2  \\
-QF\_BV   &   &   &   & Boolector  \\
-QF\_FP   &   &   &   & CVC4  \\
-\bottomrule
-\end{tabular}
-\end{table}
-
+\input{table-winners-main-families}
 %%%%%%%%%%%%%%%%%
@@
 
-\begin{table}
-\caption{Alternative winners if benchmarks with unknown status had not bee included in 2017 onwards.\label{tab:results:unknowns}}
-\centering
-\begin{tabular}{r@{\hskip 1em}>{\columncolor[gray]{.95}[.25em][.5em]}c@{\hskip 1em}>{\columncolor[gray]{.95}[.5em][.5em]}c@{\hskip 1em}>{\columncolor[gray]{.95}[.5em][.5em]}c@{\hskip 1em}>{\columncolor[gray]{.95}[.5em][0.25em]}c}
-\toprule
-Division                       &  2017                  &  2018                      \\
-\hline\hline
-AUFNIRA & CVC4 & \\
-QF\_NIRA & \nc{Z3} & CVC4 \nc{Z3} \\
-QF\_NRA & \nc{Z3} & \\
-UFDTLIA & CVC4 & \\
-BV & & Boolector \\
-QF\_FP & & CVC4 \nc{Z3} \\
-UFNIA & & CVC4 \\
-NRA & & -/\nc{Z3} \\
-UF & & -/CVC4\\
-\bottomrule
-\end{tabular}
-\end{table}
-
+\input{table-winners-main-unknown}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2019-04-14 2018/report/table-winners-main-families.tex
Report: Layout and clean up main track winners tables for families and unknown.

--- 2019-04-14 2018/report/table-winners-main-sat-unsat.tex
@@
 \begin{table}
-  \caption{Alternative best solvers in the Main track if only \emph{satisfiable} benchmarks had been considered. These results are in reference to those given in Table~\ref{tab:winners-main}.}
-  \label{tab:results:sat}
+  \caption{Alternative best solvers in the Main track if families were not considered in computing scores (i.e., the 2015 scoring system were used).}
+  \label{tab:results:total:solved}
   \centering
@@
     Division & 2015 &  2016           &  2017                &  2018                  \\
-    \hline \hline
-    ALIA             &                      &                         &                         & \cc{alt} Alt-Ergo         \\
-    AUFLIA           & \cc{cvc3} CVC3       &                         &                         & \cc{alt} Alt-Ergo         \\
-    AUFLIRA          &                      & \cc{cvc4} CVC4          & \cc{cvc4} CVC4          & \cc{alt} Alt-Ergo         \\
-    AUFNIRA          & \nonc\nc{Z3}         & \cc{cvc4} CVC4 \nc{Z3}  & \cc{cvc4} CVC4 \nc{Z3}  & \nc{Z3}                   \\
-    BV               &                      & \nc{Z3}                 & \cc{bool} Boolector     & \cc{bool} Boolector       \\
-    LRA              &                      &                         & \cc{verit} veriT        &                           \\
-    NIA              & \nonc \cc{cvc3} CVC3 &                         &                         &                           \\
-    NRA              & \nonc \cc{cvc3} CVC3 & \cc{cvc4} CVC4          & \cc{cvc4} CVC4          & \cc{cvc4} CVC4 \nc{Z3}    \\
-    QF\_ABV          &                      & \cc{yices} Yices2       & \cc{yices} Yices2       &                           \\
-    QF\_AUFBV        & \cc{yices} Yices     & \cc{yices} Yices2       &                         & \cc{yices} Yices2         \\
-    QF\_BV           &                      & \nc{Z3}/MinkeyRink      &                         &                           \\
+    \hline\hline
+    AUFNIRA  &      & \cc{cvc4} CVC4  &                      &                        \\
+    UFIDL    &      & \nc{Z3}         &                      &                        \\
+    BV       &      &                 & \cc{bool} Boolector  &                        \\
+    QF\_LRA  &      &                 & \cc{yices} Yices2    & \cc{spass} SPASS-SATT  \\
+    QF\_NIA  &      &                 & \cc{yices} Yices2    & \cc{yices} Yices2      \\
+    QF\_BV   &      &                 &                      & -/Boolector            \\
     QF\_FP   &      &                 &                      & \cc{cvc4} CVC4         \\
-    QF\_LIA          & \nc{Z3}              &                         &                         &                           \\
-    QF\_LRA          &                      &                         & \cc{yices} Yices2       & \cc{yices} Yices2         \\
-    QF\_NIA          &                      & \cc{rat} SMT-RAT        &                         &                           \\
-    QF\_NIRA         &                      &                         & \cc{cvc4} CVC4          &                           \\
-    QF\_NRA          &                      &                         & \nc{Z3}                 &                           \\
-    QF\_UFBV         &                      &                         &                         & \cc{yices} Yices2         \\
-    QF\_UFIDL        & \nc{Z3}              & \nc{Z3}                 & \nc{Z3}                 & \cc{verit} veriT  \nc{Z3} \\
-    QF\_UFNIA        & \nonc \cc{cvc3} CVC3 &                         & \cc{cvc4} CVC4          &                           \\
-    UF               &                      & \cc{vamp} Vampire       &                         & \cc{vamp}Vampire/-        \\
-    UFBV             &                      & \cc{bool} Boolector     &                         &                           \\
-    UFDTLIA          &                      &                         & \nonc \cc{cvc4} CVC4    &                           \\
-    UFLIA            & \nc{Z3}              &                         &                         &                           \\
-    UFLRA            & \cc{cvc3} CVC3       & \cc{cvc4} CVC4          &                         &                           \\
-    UFNIA            &                      & \cc{cvc4} CVC4          & \cc{cvc4} CVC4          & \cc{cvc4} CVC4            \\
   \bottomrule
@@
 \end{table}
-
-\begin{table}
-  \caption{Alternative best solvers in the Main track if only \emph{unsatisfiable} benchmarks had been considered. These results are in reference to those given in Table~\ref{tab:winners-main}.}
-  \label{tab:results:unsat}
-  \centering
-  \begin{tabular}{r@{\hskip 1em}>{\columncolor{white}[.25em][.5em]}c@{\hskip 1em}>{\columncolor{white}[.5em][.5em]}c@{\hskip 1em}>{\columncolor{white}[.5em][.5em]}c@{\hskip 1em}>{\columncolor{white}[.5em][0.5em]}c}
-\toprule
-Division        &  2015                  &  2016                     &  2017                 &  2018                   \\
-\hline \hline
-    BV          &                        & \cc{cvc4} CVC4            &                       &                         \\
-    NIA         &                        & \cc{cvc4} CVC4            & \cc{vamp} Vampire     & \cc{vamp} Vampire       \\
-    QF\_AUFBV   &                        &                           & \cc{cvc4} CVC4        &                         \\
-    QF\_AUFNIA  & \nonc \nc{Z3}          & \nonc \nc{Z3}             &                       &                         \\
-    QF\_BV      &                        &                           & -/Boolector           &                         \\
-    QF\_IDL     & \cc{cvc4} CVC4         &                           & \nc{Z3}               & \cc{cvc4} CVC4 \nc{Z3}  \\
-    QF\_LIA     & \cc{smti} SMTInterpol  & \cc{smti} SMTInterpol     & \cc{smti} SMTInterpol & \cc{smti} SMTInterpol   \\
-    QF\_NIA     & \cc{cvc3} CVC3         &                           & \cc{yices} Yices2     &                         \\
-    QF\_NRA     &                        &                           &                       & \cc{cvc4} CVC4          \\
-    QF\_UFLIA   &                        &                           & \nc{Z3}               &                         \\
-    QF\_UFNRA   &                        & \cc{cvc4} CVC4 \nc{Z3}    & \cc{cvc4} CVC4        & \cc{cvc4} CVC4 \nc{Z3}  \\
-    UF          &                        &                           & \cc{cvc4} CVC4        & -/CVC4                  \\
-    UFIDL       &                        & \cc{vamp} Vampire \nc{Z3} & \nc{Z3}               &                         \\
-    UFLRA       &                        &                           & \cc{verit} veriT      & \cc{verit} veriT        \\
-    \bottomrule
-  \end{tabular}
-
-\end{table}

### 2019-04-14 2018/report/table-winners-main-unknown.tex
Report: Layout and clean up main track winners tables for families and unknown.

\begin{table}
  \caption{Alternative best solvers if benchmarks with unknown status had not bee included in 2017 onwards.}
  \label{tab:results:unknowns}
  \centering
    \begin{tabular}{r@{\hskip 1em}>{\columncolor{white}[.25em][.5em]}c@{\hskip 1em}>{\columncolor{white}[.5em][.5em]}c@{\hskip 1em}>{\columncolor{white}[.5em][.5em]}c@{\hskip 1em}>{\columncolor{white}[.5em][0.5em]}c}
    \toprule
    Division &  2017          &  2018                  \\
    \hline\hline
    AUFNIRA  & \cc{cvc4} CVC4 &                        \\
    QF\_NIRA & \nc{Z3}        & \cc{cvc4} CVC4 \nc{Z3} \\
    QF\_NRA  & \nc{Z3}        &                        \\
    UFDTLIA  & \cc{cvc4} CVC4 &                        \\
    BV       &                & \cc{bool} Boolector    \\
    QF\_FP   &                & \cc{cvc4} CVC4 \nc{Z3} \\
    UFNIA    &                & \cc{cvc4} CVC4         \\
    NRA      &                & -/\nc{Z3}              \\
    UF       &                & -/CVC4                 \\
  \bottomrule
  \end{tabular}
\end{table}

### 2019-04-14 2018/report/SMT-COMP.tex
Report: Disable frames.
Report: Introduce macros for track names.

@@
 %\usepackage{pst-tree}
+\usepackage{xspace}
 
@@
 
-\usepackage{showframe}   % debug
+%\usepackage{showframe}   % debug
 
@@
 \firstpageno{1}
+
+% macros for tracks for more constistency
+\newcommand{\maintrack}{Main Track\xspace}
+\newcommand{\apptrack}{Application Track\xspace}
+\newcommand{\ucoretrack}{Unsat-Core Track\xspace}
 
@@
 %%   recognize both best sequential and best parallel performance in all
-%%   main track divisions, using different CPU time limits.
+%%   \maintrack divisions, using different CPU time limits.
 %% \item The division scoring will take time spent on unsolved benchmarks
@@
 %% \item Solver output may affect the score even when the solver does not
-%%   terminate within the time limit.  (In 2015, main track solver output
+%%   terminate within the time limit.  (In 2015, \maintrack solver output
 %%   was ignored if the solver subsequently timed out.)  Solvers should
@@
 %%   competition results.
-%% \item The Unsat-Core track that was introduced in SMT-COMP 2012, but
+%% \item The \ucoretrack that was introduced in SMT-COMP 2012, but
 %%   discontinued in 2013-2015 (partly because of the competition's move
@@
 %% \item Benchmarks with unknown status will be eligible for the
-%%   competition's main track.  In 2016, solver performance on benchmarks
+%%   competition's \maintrack.  In 2016, solver performance on benchmarks
 %%   with unknown status was evaluated but reported separately; in 2017,
@@
 %%   overemphasizes large divisions.
-%% \item The Unsat-Core track, which was re-introduced in 2016, is no
+%% \item The \ucoretrack, which was re-introduced in 2016, is no
 %%   longer experimental.  Its divisions will be considered competitive
@@
 %% \item The time limit per solver/benchmark pair is anticipated to be at
-%%   most 20 minutes in the main track, and at most 40 minutes in the
+%%   most 20 minutes in the \maintrack, and at most 40 minutes in the
 %%   other tracks.  \emph{Rationale:} Already in 2017, the time limit for
-%%   the main track was reduced to 20 minutes (down from 40 minutes in
+%%   the \maintrack was reduced to 20 minutes (down from 40 minutes in
 %%   earlier years) to cope with the inclusion of a large number of
 %%   benchmarks with unknown status.
-%% \item In the Unsat-Core track, the unsatisfiability check for the
+%% \item In the \ucoretrack, the unsatisfiability check for the
 %%   returned core will be based on a simple majority vote.  The case
@@
 %%   treated specially.  \emph{Rationale:} This allows to simplify the
-%%   post-processing of Unsat-Core track results considerably.
+%%   post-processing of \ucoretrack results considerably.
 %% \item In 2017, the competition featured experimental divisions for
@@
 
-The SMT Competition consists of several tracks.  The \emph{main
-  track}, which has been a staple of the competition since its
+The SMT Competition consists of several tracks.  The \emph{\maintrack}, which
+has been a staple of the competition since its
 inception in 2005, features non-incremental benchmarks.  The
-\emph{Application track}, which has been part of the competition since
+\emph{\apptrack}, which has been part of the competition since
 2011~\cite{BDdMOS13}, features incremental benchmarks.  These
@@
 next benchmark command (to prevent look-ahead behavior).  The
-\emph{Unsat-Core track} uses Main-track benchmarks that are known to
+\emph{\ucoretrack} uses \maintrack benchmarks that are known to
 be unsatisfiable, and solvers are evaluated on their ability to find
 small unsatisfiable cores (i.e., a small but still unsatisfiable
-subset of the benchmark's assertions).  The Unsat-Core track had first
+subset of the benchmark's assertions).  The \ucoretrack had first
 been part of the competition in 2012~\cite{CGBD12}, but was then
@@
     \midrule
-    Main track        &  40 & 40 & 49 & 50 \\
-    Application track &  14 & 14 & 16 & 21 \\
-    Unsat-Core track  &  -- & 40 & 41 & 44 \\
+    \maintrack   &  40 & 40 & 49 & 50 \\
+    \apptrack    &  14 & 14 & 16 & 21 \\
+    \ucoretrack  &  -- & 40 & 41 & 44 \\
     \bottomrule
@@
 since~2016 uses a scoring method that assigns a weight to each
-Main-track benchmark in order to de-emphasize large benchmark
+\maintrack benchmark in order to de-emphasize large benchmark
 families~\cite{rules18}.  A benchmark's weight is computed as $(1 +
@@
 separately.  Since 2017, all non-incremental benchmarks are eligible
-for the competition's Main track regardless of status, and they
+for the competition's \maintrack regardless of status, and they
 directly affect the competition results.  Solver responses for such
@@
 For incremental benchmarks, the situation is different: an incremental
-benchmark is ineligible for the Application track if its first {\tt
+benchmark is ineligible for the \apptrack if its first {\tt
   check-sat} command has unknown status.  Otherwise, the prefix of the
@@
 status is eligible.  The main reason for this difference is that the
-competition tools for the Application track (in particular, the trace
+competition tools for the \apptrack (in particular, the trace
 executor) have not been adapted yet to support {\tt check-sat}
@@
 \begin{table}
-  \caption{Number of benchmarks used in the Main track (by division)}
+  \caption{Number of benchmarks used in the \maintrack (by division)}
   \label{table:benchmarks-main-track}
@@
 \begin{table}
-  \caption{Number of benchmarks used in the Application track (by
-    division)}
+  \caption{Number of benchmarks used in the \apptrack (by division)}
   \label{table:benchmarks-application-track}
@@
 \begin{table}
-  \caption{Number of benchmarks used in the Unsat-Core track (by
+  \caption{Number of benchmarks used in the \ucoretrack (by
     division)}
@@
 were evaluated with a wall-clock time limit of 10~minutes.  In~2017,
-when these benchmarks had become eligible for the Main track,
-Main-track job pairs were first run with a time limit of 10~minutes.
+when these benchmarks had become eligible for the \maintrack,
+\maintrack job pairs were first run with a time limit of 10~minutes.
 When it became apparent to the organizers that there were sufficient
@@
     \midrule
-    Main track        & 40 & 40 & 20\protect\footnotemark & 20 \\
-    Application track & 40 & 40 & 40\phantom{$^{1.}$}      & 40 \\
-    Unsat-Core track  & -- & 40 & 40\phantom{$^{1.}$}      & 40 \\
+    \maintrack   & 40 & 40 & 20\protect\footnotemark & 20 \\
+    \apptrack    & 40 & 40 & 40\phantom{$^{1.}$}      & 40 \\
+    \ucoretrack  & -- & 40 & 40\phantom{$^{1.}$}      & 40 \\
     \bottomrule
@@
 competition versions.  These solvers were therefore participating hors
-concours.  Moreover, in 2015 a bug was discovered in the application
-track version of Boolector and a fixed version was submitted after the
+concours.  Moreover, in 2015 a bug was discovered in the \apptrack 
+version of Boolector and a fixed version was submitted after the
 deadline; in 2016, the CVC4 team did not enter their solver into the
-Application track; and in 2018, an experimental version of CVC4 as
+\apptrack; and in 2018, an experimental version of CVC4 as
 well as the OpenSMT2 solver were submitted after the deadline.  These
@@
     \midrule
-    Main track        & 21 &               [+2] & 25 & [+2] & 19 & [+2] & 20 & [+4] \\
-    Application track & 10 &               [+3] &  8 & [+3] &  4 & [+2] &  4 & [+2] \\
-    Unsat-Core track  & \multicolumn{2}{c}{---} &  1 & [+4] &  2 & [+2] &  3 & [+2] \\
+    \maintrack   & 21 &               [+2] & 25 & [+2] & 19 & [+2] & 20 & [+4] \\
+    \apptrack    & 10 &               [+3] &  8 & [+3] &  4 & [+2] &  4 & [+2] \\
+    \ucoretrack  & \multicolumn{2}{c}{---} &  1 & [+4] &  2 & [+2] &  3 & [+2] \\
     \midrule
@@
 responses; third, on the wall-clock and CPU time that the solver
-process consumed.  For the Unsat-Core track (which uses unsatisfiable
+process consumed.  For the \ucoretrack (which uses unsatisfiable
 benchmarks only), the reduction in the size of the unsatisfiable core
@@
 
-As discussed in Section~\ref{sec:benchmarks}, Main-track benchmarks
+As discussed in Section~\ref{sec:benchmarks}, \maintrack benchmarks
 with unknown status are removed from the competition results if two
@@
 is a wall-clock limit.  Thus, solvers that take advantage of
-parallelism might use up to~$4T$ CPU time.  For the Main track and the
-Unsat-Core track, the competition reports parallel and sequential
+parallelism might use up to~$4T$ CPU time.  For the \maintrack and the
+\ucoretrack, the competition reports parallel and sequential
 performance separately.  The latter is determined by imposing a
-(virtual) CPU time limit of~$T$.  For the Application track, only
+(virtual) CPU time limit of~$T$.  For the \apptrack, only
 parallel performance is reported (because response times to individual
@@
 sponsored three Kurt G\"odel medals.  These were awarded to the winner
-of the Main track's QF\_BV division (which had historically been the
+of the \maintrack's QF\_BV division (which had historically been the
 logic with the largest number of solver submissions and job pairs), as
-well as to the two best Main-track solvers according to a
+well as to the two best \maintrack solvers according to a
 competition-wide ranking that had been instituted especially for this
 purpose~\cite{CDW14}.  This ranking combines each solver's performance
-across all competitive Main-track divisions into a single score,
+across all competitive \maintrack divisions into a single score,
 giving more weight to larger divisions, and to solvers that solve a
@@
 
-The competition-wide ranking for the Main track was retained and
+The competition-wide ranking for the \maintrack was retained and
 refined after~2014.  Table~\ref{table:competition-wide-ranking} shows
@@
 \begin{table}
-  \caption{Competition-wide ranking for the Main track: best solvers (by year)}
+  \caption{Competition-wide ranking for the \maintrack: best solvers (by year)}
   \label{table:competition-wide-ranking}
@@
 response causes a solver to be ranked below all correct solvers for
-that division.  But the competition's Main track consists of many
+that division.  But the competition's \maintrack consists of many
 independent divisions.  A solver bug that affects one division need
@@
 \begin{itemize}
-\item The best three Main-track solvers according to the
+\item The best three \maintrack solvers according to the
   competition-wide ranking (CVC4, Yices2, and SMTInterpol; see
   Table~\ref{table:competition-wide-ranking}),
-\item the solvers that won the QF\_BV division in the Main track
+\item the solvers that won the QF\_BV division in the \maintrack 
   (Boolector and MinkeyRink; see Table~\ref{tab:winners-main}),
 \item the solver that won the most competitive divisions in the
-  Application track (Yices2),
+  \apptrack (Yices2),
 \item the solver that won the most competitive divisions in the
-  Unsat-Core track (Yices2).
+  \ucoretrack (Yices2).
 \end{itemize}
 
-In comparison to the competition-wide ranking for the Main track, the
-metric used for the application and Unsat-Core track---simply counting
+In comparison to the competition-wide ranking for the \maintrack, the
+metric used for the \apptrack and \ucoretrack---simply counting
 the number of competitive divisions that a solver has won---was rather
@@
 refine this to use a ranking scheme that is more similar to the
-Main-track ranking, by weighing divisions according to their relative
+\maintrack ranking, by weighing divisions according to their relative
 importance, and also by rewarding good performance from solvers other
-than division winners.  A difficulty in adapting the Main-track
-ranking for the other tracks is that each Main-track benchmark is
+than division winners.  A difficulty in adapting the \maintrack
+ranking for the other tracks is that each \maintrack benchmark is
 worth one point (before benchmark weights are applied) if solved
-correctly, while benchmarks in the application and Unsat-Core track
+correctly, while benchmarks in the \apptrack and \ucoretrack
 are worth widely varying numbers of points.  Moreover, in the
-Unsat-Core track, the size of the smallest unsatisfiable core---and
+\ucoretrack, the size of the smallest unsatisfiable core---and
 hence the number of points attainable on any given benchmark---may not
@@
         plot/pdf/cactus_plot-Virtual_Best_Solver_(VBS)_Main_Track_2015-2018.pdf}}
-  \caption{VBS on common benchmarks 2015-2018 of all logics in the Main track
+  \caption{VBS on common benchmarks 2015-2018 of all logics in the \maintrack 
   with a time limit of 1200s. Number of common benchmarks is indicated with a
@@
   \caption{VBS on common benchmarks for pairs of years of all logics in the
-  Main track with a time limit of 1200s. Number of common benchmarks is
+  \maintrack with a time limit of 1200s. Number of common benchmarks is
   indicated with a gray vertical line.}
@@
   within a time limit of 2400s
-  on common benchmarks 2015-2018 of all logics in the Application
-  track.}
+  on common benchmarks 2015-2018 of all logics in the \apptrack.}
   \label{fig:progress-all-app}
@@
   within a time limit of 2400s
-  on common benchmarks 2016-2018 of all logics in the Unsat Core 
-  track.}
+  on common benchmarks 2016-2018 of all logics in the \ucoretrack.}
   \label{fig:progress-all-uc}
@@
 
-For the \emph{Main track}, we determine the VBS as the best wall-clock
+For the \emph{\maintrack}, we determine the VBS as the best wall-clock
 performance per (correctly solved) instance with the time limit of 1200s used
@@
 
-For the \emph{Application track}, we determine the VBS as the best performance
+For the \emph{\apptrack}, we determine the VBS as the best performance
 in terms of number of correct \texttt{check-sat} answers within the time limit
-of 2400s (the time limit of the Application track in the competitions
+of 2400s (the time limit of the \apptrack in the competitions
 2015-2018).
@@
 
-For the \emph{Unsat-Core track}, we determine the VBS as the best performance in
+For the \emph{\ucoretrack}, we determine the VBS as the best performance in
 terms of \emph{reduction}, i.e., the difference in the number of assertions
 of the input formula and the unsat core, within the time limit
-of 2400s (the time limit of the Unsat-Core track in the competitions
+of 2400s (the time limit of the \ucoretrack in the competitions
 2016-2018).
@@
 Table~\ref{table:unique-solutions} shows the number of uniquely solved
-benchmarks for each Main-track solver from 2015--2018.  (Multiple
+benchmarks for each \maintrack solver from 2015--2018.  (Multiple
 versions of a solver are consolidated in this table, and answers that
@@
 \begin{table}
-  \caption{Number of Main-track benchmarks uniquely solved by each
+  \caption{Number of \maintrack benchmarks uniquely solved by each
     solver (by year)}
@@
 In Table~\ref{table:parallelism}, we report the quotient of CPU time
-over wall-clock time (summed up over all Main-track benchmarks) for
+over wall-clock time (summed up over all \maintrack benchmarks) for
 each solver, as well as for all solvers combined.  When there were
@@
 version), only the highest value is shown.  We note that this quotient
-is close to~1 for most solvers: only about 4--8 Main-track solvers
+is close to~1 for most solvers: only about 4--8 \maintrack solvers
 each year were participating with a version that made use of
@@
   \caption{Quotient of CPU time over wall-clock time for each
-    Main-track solver (by year).  Values below~1.1 are shown in gray.}
+    \maintrack solver (by year).  Values below~1.1 are shown in gray.}
   \label{table:parallelism}
@@
 
-In the Main-track all divisions contain a mixture of problems that are satisfiable and unsatisfiable.
+In the \maintrack all divisions contain a mixture of problems that are satisfiable and unsatisfiable.
 However, some solvers may be specialised or optimised for a particular kind of problem.
@@
 software verification) make use of very short time limits.
-We ask the question \emph{how would the Main track results change if we consider a much shorter time limit of 24 seconds?}\footnote{This time limit was inspired by a conversation with Liana Hadarean as it is a time limit being used in one application of SMT solvers in Amazon.}.
-We only consider the Main track here as this is the setting where short time limits are most likely to be relevant.
+We ask the question \emph{how would the \maintrack results change if we consider a much shorter time limit of 24 seconds?}\footnote{This time limit was inspired by a conversation with Liana Hadarean as it is a time limit being used in one application of SMT solvers in Amazon.}.
+We only consider the \maintrack here as this is the setting where short time limits are most likely to be relevant.
 The results of this analysis are given in Table~\ref{tab:results:24s}.
@@
 
-In 2016 the Main-track competition scoring was changed to weight the correctness score for benchmarks by the size of the family the benchmark belongs to.
+In 2016 the \maintrack competition scoring was changed to weight the correctness score for benchmarks by the size of the family the benchmark belongs to.
 Here we ask what the winners would have been if this change had not been made.
@@
 
-In 2017 the Main track ran with benchmarks with unknown status (removing any that had disagreements).
-An interesting question is to what extent this affected the winners in the Main track.
+In 2017 the \maintrack ran with benchmarks with unknown status (removing any that had disagreements).
+An interesting question is to what extent this affected the winners in the \maintrack.
 Table~\ref{tab:results:unknowns} gives the alternative winners if these benchmarks had not been included.
@@
 
-Since the re-introduction of the Unsat-Core track in~2016, the
+Since the re-introduction of the \ucoretrack in~2016, the
 competition again has three separate tracks.  This, together with new
@@
 \item the inclusion of {\tt check-sat} commands with unknown status in
-  the Application track, and
-\item the definition of competition-wide rankings for the application
-  and Unsat-Core track.
+  the \apptrack, and
+\item the definition of competition-wide rankings for the \apptrack 
+  and \ucoretrack.
 \end{itemize}

### 2019-04-14 2018/report/table-winners-main-sat-unsat.tex
Report: Introduce macros for track names.

@@
 \begin{table}
-  \caption{Alternative best solvers in the Main track if only \emph{satisfiable} benchmarks had been considered. These results are in reference to those given in Table~\ref{tab:winners-main}.}
+  \caption{Alternative best solvers in the \maintrack if only \emph{satisfiable} benchmarks had been considered. These results are in reference to those given in Table~\ref{tab:winners-main}.}
   \label{tab:results:sat}
@@
 \begin{table}
-  \caption{Alternative best solvers in the Main track if only \emph{unsatisfiable} benchmarks had been considered. These results are in reference to those given in Table~\ref{tab:winners-main}.}
+  \caption{Alternative best solvers in the \maintrack if only \emph{unsatisfiable} benchmarks had been considered. These results are in reference to those given in Table~\ref{tab:winners-main}.}
   \label{tab:results:unsat}

### 2019-04-14 2018/report/SMT-COMP.tex
Report: Pass over "Very quick solutions".

@@
 
-The time limits used in each year are relatively long (20 or 40 minutes) whereas some applications of SMT solvers (e.g.
-software verification) make use of very short time limits.
-We ask the question \emph{how would the \maintrack results change if we consider a much shorter time limit of 24 seconds?}\footnote{This time limit was inspired by a conversation with Liana Hadarean as it is a time limit being used in one application of SMT solvers in Amazon.}.
-We only consider the \maintrack here as this is the setting where short time limits are most likely to be relevant.
-The results of this analysis are given in Table~\ref{tab:results:24s}.
-As in the previous, this highlights the different winners under this new scheme only.
-Here we see STP winning a division for the first time in our analysis (QF\_BV in 2016) and Yices2 performing well.
+Different application domains of SMT typically impose a wide range of time
+limits (from hours to seconds). In domains with very low time limits, these
+limits are, in the incremental case, usually even defined per incremental
+query.  With 20 and 40 minutes, the time limits used in the competition for all
+tracks in all four years were relatively long and the same for all benchmarks,
+thus agnostic to the application domain of a benchmark.  Hence, it is
+interesting to investigate how the results change if we consider a much shorter
+time limit.  Table~\ref{tab:results:24s} shows the results of virtually
+imposing a time limit of 24 seconds\footnote{This time limit is used for the
+new 24 seconds score introduced in SMT-COMP 2019 and was inspired by a use case
+at Amazon.} in the \maintrack.  As in the previous, this highlights the
+different winners under this new scheme only. Here we see STP winning a
+division for the first time in our analysis (QF\_BV in 2016) and Yices2
+performing well.
+
+We only consider the \maintrack here, since for the other two tracks, the
+results are less interesting.  In the \apptrack, for such low time limits we
+are rather interested in a time limit per query, which we are unable to impose
+on the existing data since it is not possible to extract wallclock run time
+information per incremental query from the data of the competitions (as
+mentioned above, StarExec does not record this information).  In the
+\ucoretrack, the main focus is on producing small unsat-cores and solving times
+are of secondary interest.  Additionally, benchmarks with known unsatisfiable
+status from the \maintrack are used, and thus these results are already
+available from the \maintrack analysis in Table~\ref{tab:results:24s}
+(disregarding the fact that enabling unsat core production may slow down a
+solver, depending on the technique).
 

### 2019-04-14 2018/report/SMT-COMP.tex
Minor

@@
 
-\subsection{Progress in Solver Performance.}
+\subsection{Progress in Solver Performance}
 
@@
 
-\subsection{Unique Solutions.}
+\subsection{Unique Solutions}
 
@@
 
-\subsection{Use of Parallelism.}
+\subsection{Use of Parallelism}
 
@@
 It is interesting to note that we see some new solvers winning divisions that did not win any division in the main results.
-For example, Alt-Ergo solves the most satisfiable problems in AUFLIA and ALIA in 2018 and SMTInterpol performs very well on unsatisfiable problems in QF\_LIA.
+For example, Alt-Ergo solves the most satisfiable problems in AUFLIA and ALIA in 2018, and SMTInterpol performs very well on unsatisfiable problems in QF\_LIA.
 

### 2019-04-14 2018/report/SMT-COMP.tex
TODO 6 (brief explanation added, but not changed to count solvers instead of solver versions)
Minor

@@
 
-For space reasons, the discussion in this paper is necessarily
-limited.  Complete data about past competitions since 2015 (and partly
-for earlier competitions) is available from the competition website,
+Complete data about past competitions since 2015 (and partly for
+earlier competitions) is available from the competition website,
 \url{http://www.smtcomp.org}.  This includes detailed results for each
@@
 solvers.  Selected competition results are presented in
-Section~\ref{sec:results}.  We conclude with suggestions for future
+Section~\ref{sec:results}, and analyzed in more detail in
+Section~\ref{sec:analysis}.  We conclude with suggestions for future
 SMT Competitions in Section~\ref{sec:conclusions}.
@@
 
+It can be easy for developers to create multiple versions of their
+solver, which may differ only in configuration settings or other minor
+details.  We caution against over-interpreting these numbers, which to
+some extent depend on how experimental development teams were in any
+given year.
+
 By number of solver versions submitted, the competitions in 2015--2018
@@
 \section{Further Analysis}
+\label{sec:analysis}
 

### 2019-04-14 2018/report/SMT-COMP.tex
Report: Pass over "Focussing on Sat or Unsat".

@@
 }
+
+\newcommand{\rem}[1]{\textcolor{red}{[#1]}}
+\newcommand{\todo}[1]{\rem{TODO #1}}
 
@@
 
-In the \maintrack all divisions contain a mixture of problems that are satisfiable and unsatisfiable.
-However, some solvers may be specialised or optimised for a particular kind of problem.
-Therefore, it is interesting to ask whether the winners of divisions might have changed if benchmarks in that division had been restricted to one of these results.
-Tables~\ref{tab:results:sat}-\ref{tab:results::unsat} show the changes in division winners if only satisfiable or unsatisfiable results are given.
-This table is in reference to Table~\ref{tab:winners-main} and only lists a solver if the result has changed.
-A non-competing solver is listed by itself if it was not the overall best performing solver of that division but now outperforms the winning competitive solver .
-
+In many cases, an SMT application produces either mainly satisfiable or mainly
+unsatisfiable queries to the SMT solver.  A typical example is model checking,
+where a query is only satisfiable if a property of the model does not hold.  As
+a consequence, some solvers may implement specialized techniques and
+optimizations for the more frequent (the expected) case.
+%
+Therefore, it is interesting to ask whether the winners of divisions of a track
+might have changed if benchmarks in that division had been restricted to one of
+these results.  Tables~\ref{tab:results:sat}-\ref{tab:results:unsat} show the
+changes in division winners if only satisfiable or unsatisfiable results are
+given. This table is in reference to Table~\ref{tab:winners-main} and only
+lists a solver if the result has changed. A non-competing solver is listed by
+itself if it was not the overall best performing solver of that division but
+now outperforms the winning competitive solver, and the winning competing
+solver did not change.
 It is interesting to note that we see some new solvers winning divisions that did not win any division in the main results.
 For example, Alt-Ergo solves the most satisfiable problems in AUFLIA and ALIA in 2018, and SMTInterpol performs very well on unsatisfiable problems in QF\_LIA.
+
+We only consider the \maintrack here, which contains a mixture of problems that
+are satisfiable and unsatisfiable.
+\todo{give numbers in percent for years or refer to table where the numbers should be: {table:benchmarks-main-track}}
+For the \apptrack, this analysis is less meaningful since a benchmarks usually
+contains a multitude of both satisfiable and unsatisfiable incremental queries
+(which may depend on each other).
+For the \ucoretrack, only known unsatisfiable benchmarks from the \maintrack
+are used, which renders this analysis useless for this track.
 

### 2019-04-14 2018/report/SMT-COMP.tex
Report: Add todo
Report: Pass over unknown analysis

@@
 After fixing this misinterpretation we note that only a single division winner changes - in 2017 AUFNIRA should have been won by
-
-.
+\todo{who instead of who?}.
 As this is in the past we are choosing not to retroactively change the winner (and all tables in this paper reflect the previously published results) but the scripts have been fixed for future iterations of the competition.
@@
 %%%%%%%%%%%%%%%%%
-\subsection{What Impact Did Adding Unknowns Have?}
-
-In 2017 the \maintrack ran with benchmarks with unknown status (removing any that had disagreements).
-An interesting question is to what extent this affected the winners in the \maintrack.
-Table~\ref{tab:results:unknowns} gives the alternative winners if these benchmarks had not been included.
+\subsection{What Impact Did Adding Unknowns in the \maintrack Have?}
+
+Until 2016, only benchmarks with known status were used in the \maintrack. In
+2016, benchmarks with unknown status were evaluated separately, but not
+considered in the overall results of the track.  Since 2017, non-incremental
+benchmarks with unknown status were eligible for the \maintrack.
+Table~\ref{tab:results:unknowns} shows alternative winners for 2017 and 2018 if
+benchmarks with unknown status had not been included.
 

### 2019-04-14 2018/report/SMT-COMP.tex
Report: Restructre section 4 to add more detailed scoring information.

@@
 
-The SMT Competition consists of several tracks.  The \emph{\maintrack}, which
+The SMT Competition consists of several tracks.  Each track is further split
+into (logic) \emph{divisions}, where each division corresponds to a logic from
+the SMT Library.  As indicated in
+Tables~\ref{table:smtlib}--\ref{table:divisions}, there are slightly fewer
+divisions (Table~\ref{table:divisions}) than logics in the SMT Library
+(Table~\ref{table:smtlib}) because not every logic contains benchmarks eligible
+for the competition.
+
+\paragraph{Tracks.}
+The \emph{\maintrack}, which
 has been a staple of the competition since its
@@
 
-Each track is further split into (logic) \emph{divisions}, where each
-division corresponds to a logic from the SMT Library.
+\paragraph{Divisions.}
 Table~\ref{table:divisions} shows the number of divisions in each
@@
 they want to enter, and competition results are reported separately
-for each track and division.  Thus, competing solvers do not need support
-all logics, and may or may not support features such as incrementality
+for each track and division.  Thus, competing solvers do not need to support
+all logics, and may or may not support features such as incremental solving
 or unsat-core generation.
 
-There are slightly fewer divisions than logics in the SMT Library
-(Table~\ref{table:smtlib}) because not every logic contains benchmarks
-eligible for the competition.  Some benchmarks typically have to be
+\paragraph{Eligible Benchmarks.}
+Some benchmarks typically have to be
 excluded for syntactic reasons: in 2015 and 2016, 11,966 benchmarks
@@
 
+\paragraph{Benchmark Selection.}
 SMT Competitions until~2014 employed a pseudo-random selection process
@@
 ``significantly lessens the ability of a competition to determine
-`best' solvers.''~\cite{CSW15} Together with the increased
+`best' solvers''~\cite{CSW15}. Together with the increased
 computational resources available to the competition since its move to
@@
 different benchmark families (that is, groups of benchmarks with
-similar characteristics).  Since there are vast differences in size
-between benchmark families in the SMT Library, the competition
-since~2016 uses a scoring method that assigns a weight to each
-\maintrack benchmark in order to de-emphasize large benchmark
-families~\cite{rules18}.  A benchmark's weight is computed as $(1 +
-\ln F)/F$, where~$F\geq 1$ is the size of the benchmark's family.  The
-log scaling seems a reasonable compromise between linearly combining
-numbers of benchmarks, which would overemphasize large families, and
-simply averaging the fraction of benchmarks solved, which would
-overemphasize small families.
-
+similar characteristics).
+
+\paragraph{Benchmarks with Unknown Status.}
 Another paradigm shift concerns the treatment of benchmarks with
@@
 benchmarks in QF\_SLIA.
+
+\subsection{Scoring}
+
+Since there are vast differences in size
+between benchmark families in the SMT Library, the competition
+since~2016 uses a scoring method that assigns a weight to each
+\maintrack benchmark in order to de-emphasize large benchmark
+families~\cite{rules18}.  A benchmark's weight is computed as $(1 +
+\ln F)/F$, where~$F\geq 1$ is the size of the benchmark's family.  The
+log scaling seems a reasonable compromise between linearly combining
+numbers of benchmarks, which would overemphasize large families, and
+simply averaging the fraction of benchmarks solved, which would
+overemphasize small families.
 

### 2019-04-14 2018/report/SMT-COMP.tex
Report: Add scoring information.

@@
 \usepackage{xspace}
+\usepackage{enumitem}
 
@@
 
-Since there are vast differences in size
-between benchmark families in the SMT Library, the competition
-since~2016 uses a scoring method that assigns a weight to each
-\maintrack benchmark in order to de-emphasize large benchmark
-families~\cite{rules18}.  A benchmark's weight is computed as $(1 +
-\ln F)/F$, where~$F\geq 1$ is the size of the benchmark's family.  The
-log scaling seems a reasonable compromise between linearly combining
-numbers of benchmarks, which would overemphasize large families, and
-simply averaging the fraction of benchmarks solved, which would
-overemphasize small families.
+The \emph{raw benchmark score} of a solver is a quadruple $\langle
+e, n, w, c\rangle$, with
+\begin{itemize}[noitemsep]
+  \item \makebox[5em][l]{$e \in \{0, 1\}$} number of erroneous results (usually~$e = 0$)
+  \item \makebox[5em][l]{$0 \leq n \leq N$} number of correct results (resp.~\emph{reduction} for the \ucoretrack)
+  \item \makebox[5em][l]{$w \in [0,T]$} wall-clock time in seconds (real-valued)
+  \item \makebox[5em][l]{$c \in [0, 4T]$} CPU time in seconds (real-valued)
+\end{itemize}
+\noindent
+For the \maintrack and \apptrack,
+$N$ is defined as the number of {\tt check-sat} commands, and
+$n$ is defined as the number of correct results.
+For the \ucoretrack, $N$ is defined as the number of named top-level assertions,
+and $n$ is defined as the \emph{reduction}, i.e., the difference between $N$
+and the size of the unsat core.
+
+This raw score corresponds to the \emph{raw parallel score} (all values are
+determined for solver performance within the wall-clock time limit).  To
+evaluate sequential performance, we derive a \emph{raw sequential score} by
+imposing a (virtual) CPU time limit equal to the wall-clock time limit~$T$.  A
+solver result is taken into consideration for the sequential score only if the
+solver process terminates within this CPU time limit.
+
+Until 2015, the competition used these raw scores for all tracks to determine
+the division score of a solver as the sum of the scores of all benchmarks in
+that division.
+Fewer errors in a division takes precedence over more correct solutions
+(resp.~reduction), which takes precedence over less wall-clock time taken,
+which takes precedence over less CPU time taken.
+However, since there are vast differences in size between benchmark families in
+the SMT Library, the competition since~2016 uses a scoring method that assigns
+a weight to each benchmark in the \maintrack and \ucoretrack in order to
+de-emphasize large benchmark families~\cite{rules16,rules17,rules18}.
+For application track divisions, division scores were still based on raw scores
+only, since application track benchmarks may be partially solved. Defining a
+useful sequential score for the application track would require information not
+provided by the raw score, e.g., detailed timing information for each result.
+
+\paragraph{Benchmark Weights (\maintrack and \ucoretrack 2016-2018).} The \emph{weight} of a
+benchmark in the main track is computed as $\alpha = (1 + \ln F)/F$,
+where~$F\geq 1$ is the size of the benchmark's family.  We then define its
+\emph{normalized weight} as $\alpha' = \alpha / (\sum_{i\in F} \alpha_i)$,
+where the sum is over all benchmarks in the division.  The log scaling seems a
+reasonable compromise between linearly combining numbers of benchmarks, which
+would overemphasize large families, and simply averaging the fraction of
+benchmarks solved, which would overemphasize small families.
+
+\paragraph{Weighted Division Scores (\maintrack and \ucoretrack 2016-2018).}
+The \emph{(weighted) score} of a solver in a division of the \maintrack and
+\ucoretrack is then defined as the weighted sum of all raw scores $$\sum_{i\in
+F} \alpha'_i \cdot \langle e \cdot N, n \cdot N, w, c\rangle$$ where the sum is
+over all benchmarks in the division to assess parallel performance, and the
+weighted sum of all sequential scores to assess sequential performance.
 

### 2019-04-14 2018/report/SMT-COMP.tex
Report: Add competition-wide score.

@@
 weighted sum of all sequential scores to assess sequential performance.
+
+\paragraph{Competition-Wide Score (\maintrack).}
+A competition-wide metric for the main track, separately for
+parallel and sequential performance, was defined as follows.
+
+Let $N_i$ be the total number of benchmarks in division~$i$ that were used in the
+competition (and not removed because of disagreements), and let $\langle e_i, n_i, w_i, c_i\rangle$ be a solver's
+raw score for this division.
+%
+In 2015 and 2016,
+the \emph{competition-wide raw score} for a solver was defined as
+%
+$\sum_i (e_i == 0 \,?\, (n_i/N_i)^2 : -e_i) \log N_i$,
+%
+where the sum is over all competitive
+divisions into which the solver was
+entered.
+%
+In 2017, the (per-division) penalty for erroneous results was changed from the
+number of errors to a fixed constant, since the weight already takes the number
+of benchmarks in the division into account, and multiplying it by the number of
+errors overemphasizes large divisions.
+In 2017 and 2018,
+the \emph{competition-wide raw score} for a solver was thus defined as
+%
+$\sum_i (e_i == 0 \,?\, (n_i/N_i)^2 : -4) \log_e N_i$,
+%
+where the sum is over all competitive divisions into which the solver
+was entered.
 

### 2019-04-14 2018/report/table-winners-main-sat-unsat.tex
Report: Fix sat table

@@
     UFLIA            & \nc{Z3}              &                         &                         &                           \\
-    UFLRA            & \cc{cvc3} CVC3       & \cc{cvc4} CVC4          &                         &                           \\
+    UFLRA            &                      & \cc{cvc4} CVC4          &                         &                           \\
     UFNIA            &                      & \cc{cvc4} CVC4          & \cc{cvc4} CVC4          & \cc{cvc4} CVC4            \\

### 2019-04-14 2018/report/SMT-COMP.tex
update table 3

@@
 \begin{table}
-  \caption{Number of benchmarks used in the \maintrack (by division)}
+  \caption{Number of benchmarks used in the \maintrack (by division).
+Numbers in brackets indicate the (rounded) percentage of problems with different statuses, which are (sat,unsat) in 2015/6 and (sat,unsat,unknown) in 2017/8.}
   \label{table:benchmarks-main-track}
@@
     \midrule
-    ABVFP      &     -- &     -- &      1 &     1 \\
-    ALIA       &     42 &     42 &     42 &    42 \\
-    AUFBVDTLIA &     -- &     -- &   1709 &  1709 \\
-    AUFDTLIA   &     -- &     -- &    728 &   728 \\
-    AUFLIA     &      4 &      4 &      4 &     4 \\
-    AUFLIRA    &  19849 &  19849 &  20011 & 20011 \\
-    AUFNIRA    &   1050 &   1050 &   1480 &  1480 \\
-    BV         &     85 &     85 &   5151 &  5751 \\
-    BVFP       &     -- &     -- &     24 &    24 \\
-    FP         &     -- &     -- &     61 &    61 \\
-    LIA        &    201 &    201 &    388 &   388 \\
-    LRA        &    339 &    339 &   2419 &  2419 \\
-    NIA        &      9 &      9 &     14 &    14 \\
-    NRA        &   3788 &   3788 &   3811 &  3813 \\
-    QF\_ABV    &  14720 &  14720 &  15061 & 15066 \\
-    QF\_ABVFP  &     -- &     -- &  18129 & 18129 \\
-    QF\_ALIA   &    134 &    139 &    139 &   139 \\
-    QF\_ANIA   &      6 &      8 &      8 &     8 \\
-    QF\_AUFBV  &     37 &     37 &     31 &    31 \\
-    QF\_AUFLIA &   1009 &   1009 &   1009 &  1009 \\
-    QF\_AUFNIA &     21 &     21 &     17 &    17 \\
-    QF\_AX     &    551 &    551 &    551 &   551 \\
-    QF\_BV     &  26414 &  26414 &  40043 & 40102 \\
-    QF\_BVFP   &      7 &      7 &  17215 & 17215 \\
-    QF\_DT     &     -- &     -- &   8000 &  8000 \\
-    QF\_FP     &  34413 &  34413 &  40302 & 40300 \\
-    QF\_IDL    &   2094 &   2094 &   2193 &  2193 \\
-    QF\_LIA    &   5839 &   5839 &   6141 &  6947 \\
-    QF\_LIRA   &      6 &      6 &      7 &     7 \\
-    QF\_LRA    &   1626 &   1626 &   1649 &  1649 \\
-    QF\_NIA    &   8475 &   8593 &  23876 & 23876 \\
-    QF\_NIRA   &      2 &      2 &      3 &     3 \\
-    QF\_NRA    &  10184 &  10245 &  11354 & 11489 \\
-    QF\_RDL    &    220 &    220 &    255 &   255 \\
-    QF\_SLIA   &     -- &     -- &     -- & 72705 \\
-    QF\_UF     &   6649 &   6649 &   6650 &  7423 \\
-    QF\_UFBV   &     31 &     31 &     31 &  1224 \\
-    QF\_UFIDL  &    441 &    441 &    428 &   428 \\
-    QF\_UFLIA  &    598 &    598 &    583 &   583 \\
-    QF\_UFLRA  &   1627 &   1627 &   1284 &  1284 \\
-    QF\_UFNIA  &      7 &      7 &      7 &     7 \\
-    QF\_UFNRA  &     34 &     34 &     36 &    36 \\
-    UF         &   2839 &   2839 &   7562 &  7562 \\
-    UFBV       &     71 &     71 &    200 &   200 \\
-    UFDT       &     -- &     -- &   4535 &  4527 \\
-    UFDTLIA    &     -- &     -- &    303 &   303 \\
-    UFIDL      &     68 &     68 &     68 &    68 \\
-    UFLIA      &   8404 &   8404 &  10137 & 10137 \\
-    UFLRA      &     25 &     25 &     15 &    15 \\
-    UFNIA      &   2319 &   2319 &   3308 &  3308 \\
+    ABVFP & - & - & - & 1 (0:0:100)\\
+ALIA & 42 (2:98) & 42 (2:98) & 42 (2:98:0) & 42 (2:98:0)\\
+AUFBVDTLIA & - & - & 1709 (0:1:98) & 1709 (0:1:98)\\
+AUFDTLIA & - & - & 728 (0:0:100) & 728 (0:0:100)\\
+AUFLIA & 4 (25:75) & 4 (25:75) & 4 (25:75:0) & 4 (25:75:0)\\
+AUFLIRA & 19849 (1:99) & 19849 (1:99) & 20011 (0:99:1) & 20011 (0:99:1)\\
+AUFNIRA & 1050 (0:100) & 1050 (0:100) & 1480 (0:71:29) & 1480 (0:71:29)\\
+BV & 85 (34:66) & 85 (34:66) & 5151 (2:2:97) & 5751 (10:86:4)\\
+BVFP & - & - & - & 24 (0:0:100)\\
+FP & - & - & - & 61 (0:0:100)\\
+LIA & 201 (5:95) & 201 (5:95) & 388 (38:60:2) & 388 (38:60:2)\\
+LRA & 339 (6:94) & 339 (6:94) & 2419 (17:46:38) & 2419 (29:64:8)\\
+NIA & 9 (67:33) & 9 (67:33) & 14 (43:29:29) & 14 (43:29:29)\\
+NRA & 3788 (0:100) & 3788 (0:100) & 3811 (0:100:0) & 3813 (0:100:0)\\
+QF\_ABV & 14720 (68:32) & 14720 (68:32) & 15061 (69:31:0) & 15066 (69:31:0)\\
+QF\_ABVFP & - & - & - & 18129 (78:22:1)\\
+QF\_ALIA & 134 (40:60) & 139 (42:58) & 139 (42:58:0) & 139 (42:58:0)\\
+QF\_ANIA & 6 (0:100) & 8 (0:100) & 8 (0:100:0) & 8 (0:100:0)\\
+QF\_AUFBV & 37 (16:84) & 37 (16:84) & 31 (19:81:0) & 31 (19:81:0)\\
+QF\_AUFLIA & 1009 (49:51) & 1009 (49:51) & 1009 (49:51:0) & 1009 (49:51:0)\\
+QF\_AUFNIA & 21 (29:71) & 21 (29:71) & 17 (29:71:0) & 17 (29:71:0)\\
+QF\_AX & 551 (49:51) & 551 (49:51) & 551 (49:51:0) & 551 (49:51:0)\\
+QF\_BV & 26414 (35:65) & 26414 (35:65) & 40043 (32:59:8) & 40102 (36:64:0)\\
+QF\_BVFP & 7 (14:86) & 7 (14:86) & 17215 (81:18:0) & 17215 (81:18:0)\\
+QF\_DT & - & - & 8000 (0:0:100) & 8000 (45:55:0)\\
+QF\_FP & 34413 (50:50) & 34413 (50:50) & 40302 (50:50:1) & 40300 (50:50:1)\\
+QF\_IDL & 2094 (61:39) & 2094 (61:39) & 2193 (58:37:5) & 2193 (58:37:4)\\
+QF\_LIA & 5839 (51:49) & 5839 (51:49) & 6141 (52:46:2) & 6947 (55:43:1)\\
+QF\_LIRA & 6 (17:83) & 6 (17:83) & 7 (14:71:14) & 7 (14:71:14)\\
+QF\_LRA & 1626 (61:39) & 1626 (61:39) & 1649 (57:41:2) & 1649 (57:41:1)\\
+QF\_NIA & 8475 (98:2) & 8593 (96:4) & 23876 (59:13:28) & 23876 (59:20:20)\\
+QF\_NIRA & 2 (0:100) & 2 (0:100) & 3 (0:67:33) & 3 (0:67:33)\\
+QF\_NRA & 10184 (52:48) & 10245 (52:48) & 11354 (44:47:10) & 11489 (44:47:9)\\
+QF\_RDL & 220 (49:51) & 220 (49:51) & 255 (43:44:13) & 255 (43:44:13)\\
+QF\_SLIA & - & - & - & 72705 (0:0:100)\\
+QF\_UF & 6649 (38:62) & 6649 (38:62) & 6650 (38:62:0) & 7423 (42:58:0)\\
+QF\_UFBV & 31 (0:100) & 31 (0:100) & 31 (0:100:0) & 1224 (53:47:0)\\
+QF\_UFIDL & 441 (24:76) & 441 (24:76) & 428 (25:75:0) & 428 (25:75:0)\\
+QF\_UFLIA & 598 (67:33) & 598 (67:33) & 583 (69:31:0) & 583 (69:31:0)\\
+QF\_UFLRA & 1627 (48:52) & 1627 (48:52) & 1284 (60:40:0) & 1284 (60:40:0)\\
+QF\_UFNIA & 7 (0:100) & 7 (0:100) & 7 (0:100:0) & 7 (0:100:0)\\
+QF\_UFNRA & 34 (47:53) & 34 (47:53) & 36 (58:31:11) & 36 (58:31:11)\\
+UF & 2839 (28:72) & 2839 (28:72) & 7562 (10:44:46) & 7562 (10:46:44)\\
+UFBV & 71 (25:75) & 71 (25:75) & 200 (34:48:17) & 200 (34:48:17)\\
+UFDT & - & - & 4535 (0:9:90) & 4527 (1:41:58)\\
+UFDTLIA & - & - & 303 (0:0:100) & 303 (0:0:100)\\
+UFIDL & 68 (9:91) & 68 (9:91) & 68 (4:84:12) & 68 (4:84:12)\\
+UFLIA & 8404 (0:100) & 8404 (0:100) & 10137 (0:76:24) & 10137 (0:76:23)\\
+UFLRA & 25 (20:80) & 25 (20:80) & 15 (33:67:0) & 15 (33:67:0)\\
+UFNIA & 2319 (0:100) & 2319 (0:100) & 3308 (0:74:26) & 3308 (0:74:26)\\
+\iffalse
+ ABVFP & - & - & - & 1 (0:0)\\
+ALIA & 42 (2:98) & 42 (2:98) & 42 (2:98) & 42 (2:98)\\
+AUFBVDTLIA & - & - & 1709 (0:1) & 1709 (0:1)\\
+AUFDTLIA & - & - & 728 (0:0) & 728 (0:0)\\
+AUFLIA & 4 (25:75) & 4 (25:75) & 4 (25:75) & 4 (25:75)\\
+AUFLIRA & 19849 (1:99) & 19849 (1:99) & 20011 (0:99) & 20011 (0:99)\\
+AUFNIRA & 1050 (0:100) & 1050 (0:100) & 1480 (0:71) & 1480 (0:71)\\
+BV & 85 (34:66) & 85 (34:66) & 5151 (2:2) & 5751 (10:86)\\
+BVFP & - & - & - & 24 (0:0)\\
+FP & - & - & - & 61 (0:0)\\
+LIA & 201 (5:95) & 201 (5:95) & 388 (38:60) & 388 (38:60)\\
+LRA & 339 (6:94) & 339 (6:94) & 2419 (17:46) & 2419 (29:64)\\
+NIA & 9 (67:33) & 9 (67:33) & 14 (43:29) & 14 (43:29)\\
+NRA & 3788 (0:100) & 3788 (0:100) & 3811 (0:100) & 3813 (0:100)\\
+QF\_ABV & 14720 (68:32) & 14720 (68:32) & 15061 (69:31) & 15066 (69:31)\\
+QF\_ABVFP & - & - & - & 18129 (78:22)\\
+QF\_ALIA & 134 (40:60) & 139 (42:58) & 139 (42:58) & 139 (42:58)\\
+QF\_ANIA & 6 (0:100) & 8 (0:100) & 8 (0:100) & 8 (0:100)\\
+QF\_AUFBV & 37 (16:84) & 37 (16:84) & 31 (19:81) & 31 (19:81)\\
+QF\_AUFLIA & 1009 (49:51) & 1009 (49:51) & 1009 (49:51) & 1009 (49:51)\\
+QF\_AUFNIA & 21 (29:71) & 21 (29:71) & 17 (29:71) & 17 (29:71)\\
+QF\_AX & 551 (49:51) & 551 (49:51) & 551 (49:51) & 551 (49:51)\\
+QF\_BV & 26414 (35:65) & 26414 (35:65) & 40043 (32:59) & 40102 (36:64)\\
+QF\_BVFP & 7 (14:86) & 7 (14:86) & 17215 (81:18) & 17215 (81:18)\\
+QF\_DT & - & - & 8000 (0:0) & 8000 (45:55)\\
+QF\_FP & 34413 (50:50) & 34413 (50:50) & 40302 (50:50) & 40300 (50:50)\\
+QF\_IDL & 2094 (61:39) & 2094 (61:39) & 2193 (58:37) & 2193 (58:37)\\
+QF\_LIA & 5839 (51:49) & 5839 (51:49) & 6141 (52:46) & 6947 (55:43)\\
+QF\_LIRA & 6 (17:83) & 6 (17:83) & 7 (14:71) & 7 (14:71)\\
+QF\_LRA & 1626 (61:39) & 1626 (61:39) & 1649 (57:41) & 1649 (57:41)\\
+QF\_NIA & 8475 (98:2) & 8593 (96:4) & 23876 (59:13) & 23876 (59:20)\\
+QF\_NIRA & 2 (0:100) & 2 (0:100) & 3 (0:67) & 3 (0:67)\\
+QF\_NRA & 10184 (52:48) & 10245 (52:48) & 11354 (44:47) & 11489 (44:47)\\
+QF\_RDL & 220 (49:51) & 220 (49:51) & 255 (43:44) & 255 (43:44)\\
+QF\_SLIA & - & - & - & 72705 (0:0)\\
+QF\_UF & 6649 (38:62) & 6649 (38:62) & 6650 (38:62) & 7423 (42:58)\\
+QF\_UFBV & 31 (0:100) & 31 (0:100) & 31 (0:100) & 1224 (53:47)\\
+QF\_UFIDL & 441 (24:76) & 441 (24:76) & 428 (25:75) & 428 (25:75)\\
+QF\_UFLIA & 598 (67:33) & 598 (67:33) & 583 (69:31) & 583 (69:31)\\
+QF\_UFLRA & 1627 (48:52) & 1627 (48:52) & 1284 (60:40) & 1284 (60:40)\\
+QF\_UFNIA & 7 (0:100) & 7 (0:100) & 7 (0:100) & 7 (0:100)\\
+QF\_UFNRA & 34 (47:53) & 34 (47:53) & 36 (58:31) & 36 (58:31)\\
+UF & 2839 (28:72) & 2839 (28:72) & 7562 (10:44) & 7562 (10:46)\\
+UFBV & 71 (25:75) & 71 (25:75) & 200 (34:48) & 200 (34:48)\\
+UFDT & - & - & 4535 (0:9) & 4527 (1:41)\\
+UFDTLIA & - & - & 303 (0:0) & 303 (0:0)\\
+UFIDL & 68 (9:91) & 68 (9:91) & 68 (4:84) & 68 (4:84)\\
+UFLIA & 8404 (0:100) & 8404 (0:100) & 10137 (0:76) & 10137 (0:76)\\
+UFLRA & 25 (20:80) & 25 (20:80) & 15 (33:67) & 15 (33:67)\\
+UFNIA & 2319 (0:100) & 2319 (0:100) & 3308 (0:74) & 3308 (0:74)\\
+\fi
     \midrule
-    Total      & 154238 & 154424 & 256973 & 333241 \\
+    Total      & 154238 (40:60) & 154424 (40:60) & 256973 (37:46:17) & 333241 (33:39:28)\\
     \bottomrule

### 2019-04-15 2018/report/SMT-COMP.tex
Report: Layout of benchmarks table

--- 2019-04-14 2018/report/SMT-COMP.tex
@@
 \newcommand{\nonc}{\color{nonc}}
+
+\newcommand{\gray}[1]{\textcolor{gray}{#1}}
 
@@
 \begin{table}
-  \caption{Number of benchmarks used in the \maintrack (by division)}
+  \caption{Number of benchmarks used in the \maintrack (by division).
+Numbers in brackets indicate the (rounded) percentage of problems with different statuses, which are (sat/unsat) in 2015 and 2016, and (sat/unsat/unknown) in 2017 and 2018.}
   \label{table:benchmarks-main-track}
   \centering
-  \scalebox{.9}[.8]{\begin{tabular}{lrrrr}
+  \scalebox{.9}[.775]{\begin{tabular}{lrrrr}
     \toprule
@@
     \midrule
-    ABVFP      &     -- &     -- &      1 &     1 \\
-    ALIA       &     42 &     42 &     42 &    42 \\
-    AUFBVDTLIA &     -- &     -- &   1709 &  1709 \\
-    AUFDTLIA   &     -- &     -- &    728 &   728 \\
-    AUFLIA     &      4 &      4 &      4 &     4 \\
-    AUFLIRA    &  19849 &  19849 &  20011 & 20011 \\
-    AUFNIRA    &   1050 &   1050 &   1480 &  1480 \\
-    BV         &     85 &     85 &   5151 &  5751 \\
-    BVFP       &     -- &     -- &     24 &    24 \\
-    FP         &     -- &     -- &     61 &    61 \\
-    LIA        &    201 &    201 &    388 &   388 \\
-    LRA        &    339 &    339 &   2419 &  2419 \\
-    NIA        &      9 &      9 &     14 &    14 \\
-    NRA        &   3788 &   3788 &   3811 &  3813 \\
-    QF\_ABV    &  14720 &  14720 &  15061 & 15066 \\
-    QF\_ABVFP  &     -- &     -- &  18129 & 18129 \\
-    QF\_ALIA   &    134 &    139 &    139 &   139 \\
-    QF\_ANIA   &      6 &      8 &      8 &     8 \\
-    QF\_AUFBV  &     37 &     37 &     31 &    31 \\
-    QF\_AUFLIA &   1009 &   1009 &   1009 &  1009 \\
-    QF\_AUFNIA &     21 &     21 &     17 &    17 \\
-    QF\_AX     &    551 &    551 &    551 &   551 \\
-    QF\_BV     &  26414 &  26414 &  40043 & 40102 \\
-    QF\_BVFP   &      7 &      7 &  17215 & 17215 \\
-    QF\_DT     &     -- &     -- &   8000 &  8000 \\
-    QF\_FP     &  34413 &  34413 &  40302 & 40300 \\
-    QF\_IDL    &   2094 &   2094 &   2193 &  2193 \\
-    QF\_LIA    &   5839 &   5839 &   6141 &  6947 \\
-    QF\_LIRA   &      6 &      6 &      7 &     7 \\
-    QF\_LRA    &   1626 &   1626 &   1649 &  1649 \\
-    QF\_NIA    &   8475 &   8593 &  23876 & 23876 \\
-    QF\_NIRA   &      2 &      2 &      3 &     3 \\
-    QF\_NRA    &  10184 &  10245 &  11354 & 11489 \\
-    QF\_RDL    &    220 &    220 &    255 &   255 \\
-    QF\_SLIA   &     -- &     -- &     -- & 72705 \\
-    QF\_UF     &   6649 &   6649 &   6650 &  7423 \\
-    QF\_UFBV   &     31 &     31 &     31 &  1224 \\
-    QF\_UFIDL  &    441 &    441 &    428 &   428 \\
-    QF\_UFLIA  &    598 &    598 &    583 &   583 \\
-    QF\_UFLRA  &   1627 &   1627 &   1284 &  1284 \\
-    QF\_UFNIA  &      7 &      7 &      7 &     7 \\
-    QF\_UFNRA  &     34 &     34 &     36 &    36 \\
-    UF         &   2839 &   2839 &   7562 &  7562 \\
-    UFBV       &     71 &     71 &    200 &   200 \\
-    UFDT       &     -- &     -- &   4535 &  4527 \\
-    UFDTLIA    &     -- &     -- &    303 &   303 \\
-    UFIDL      &     68 &     68 &     68 &    68 \\
-    UFLIA      &   8404 &   8404 &  10137 & 10137 \\
-    UFLRA      &     25 &     25 &     15 &    15 \\
-    UFNIA      &   2319 &   2319 &   3308 &  3308 \\
+    ABVFP & - & - & - & 1 \gray{(0/0/100)}\\
+    ALIA & 42 \gray{(2/98)} & 42 \gray{(2/98)} & 42 \gray{(2/98/0)} & 42 \gray{(2/98/0)}\\
+    AUFBVDTLIA & - & - & 1709 \gray{(0/1/98)} & 1709 \gray{(0/1/98)}\\
+    AUFDTLIA & - & - & 728 \gray{(0/0/100)} & 728 \gray{(0/0/100)}\\
+    AUFLIA & 4 \gray{(25/75)} & 4 \gray{(25/75)} & 4 \gray{(25/75/0)} & 4 \gray{(25/75/0)}\\
+    AUFLIRA & 19849 \gray{(1/99)} & 19849 \gray{(1/99)} & 20011 \gray{(0/99/1)} & 20011 \gray{(0/99/1)}\\
+    AUFNIRA & 1050 \gray{(0/100)} & 1050 \gray{(0/100)} & 1480 \gray{(0/71/29)} & 1480 \gray{(0/71/29)}\\
+    BV & 85 \gray{(34/66)} & 85 \gray{(34/66)} & 5151 \gray{(2/2/97)} & 5751 \gray{(10/86/4)}\\
+    BVFP & - & - & - & 24 \gray{(0/0/100)}\\
+    FP & - & - & - & 61 \gray{(0/0/100)}\\
+    LIA & 201 \gray{(5/95)} & 201 \gray{(5/95)} & 388 \gray{(38/60/2)} & 388 \gray{(38/60/2)}\\
+    LRA & 339 \gray{(6/94)} & 339 \gray{(6/94)} & 2419 \gray{(17/46/38)} & 2419 \gray{(29/64/8)}\\
+    NIA & 9 \gray{(67/33)} & 9 \gray{(67/33)} & 14 \gray{(43/29/29)} & 14 \gray{(43/29/29)}\\
+    NRA & 3788 \gray{(0/100)} & 3788 \gray{(0/100)} & 3811 \gray{(0/100/0)} & 3813 \gray{(0/100/0)}\\
+    QF\_ABV & 14720 \gray{(68/32)} & 14720 \gray{(68/32)} & 15061 \gray{(69/31/0)} & 15066 \gray{(69/31/0)}\\
+    QF\_ABVFP & - & - & - & 18129 \gray{(78/22/1)}\\
+    QF\_ALIA & 134 \gray{(40/60)} & 139 \gray{(42/58)} & 139 \gray{(42/58/0)} & 139 \gray{(42/58/0)}\\
+    QF\_ANIA & 6 \gray{(0/100)} & 8 \gray{(0/100)} & 8 \gray{(0/100/0)} & 8 \gray{(0/100/0)}\\
+    QF\_AUFBV & 37 \gray{(16/84)} & 37 \gray{(16/84)} & 31 \gray{(19/81/0)} & 31 \gray{(19/81/0)}\\
+    QF\_AUFLIA & 1009 \gray{(49/51)} & 1009 \gray{(49/51)} & 1009 \gray{(49/51/0)} & 1009 \gray{(49/51/0)}\\
+    QF\_AUFNIA & 21 \gray{(29/71)} & 21 \gray{(29/71)} & 17 \gray{(29/71/0)} & 17 \gray{(29/71/0)}\\
+    QF\_AX & 551 \gray{(49/51)} & 551 \gray{(49/51)} & 551 \gray{(49/51/0)} & 551 \gray{(49/51/0)}\\
+    QF\_BV & 26414 \gray{(35/65)} & 26414 \gray{(35/65)} & 40043 \gray{(32/59/8)} & 40102 \gray{(36/64/0)}\\
+    QF\_BVFP & 7 \gray{(14/86)} & 7 \gray{(14/86)} & 17215 \gray{(81/18/0)} & 17215 \gray{(81/18/0)}\\
+    QF\_DT & - & - & 8000 \gray{(0/0/100)} & 8000 \gray{(45/55/0)}\\
+    QF\_FP & 34413 \gray{(50/50)} & 34413 \gray{(50/50)} & 40302 \gray{(50/50/1)} & 40300 \gray{(50/50/1)}\\
+    QF\_IDL & 2094 \gray{(61/39)} & 2094 \gray{(61/39)} & 2193 \gray{(58/37/5)} & 2193 \gray{(58/37/4)}\\
+    QF\_LIA & 5839 \gray{(51/49)} & 5839 \gray{(51/49)} & 6141 \gray{(52/46/2)} & 6947 \gray{(55/43/1)}\\
+    QF\_LIRA & 6 \gray{(17/83)} & 6 \gray{(17/83)} & 7 \gray{(14/71/14)} & 7 \gray{(14/71/14)}\\
+    QF\_LRA & 1626 \gray{(61/39)} & 1626 \gray{(61/39)} & 1649 \gray{(57/41/2)} & 1649 \gray{(57/41/1)}\\
+    QF\_NIA & 8475 \gray{(98/2)} & 8593 \gray{(96/4)} & 23876 \gray{(59/13/28)} & 23876 \gray{(59/20/20)}\\
+    QF\_NIRA & 2 \gray{(0/100)} & 2 \gray{(0/100)} & 3 \gray{(0/67/33)} & 3 \gray{(0/67/33)}\\
+    QF\_NRA & 10184 \gray{(52/48)} & 10245 \gray{(52/48)} & 11354 \gray{(44/47/10)} & 11489 \gray{(44/47/9)}\\
+    QF\_RDL & 220 \gray{(49/51)} & 220 \gray{(49/51)} & 255 \gray{(43/44/13)} & 255 \gray{(43/44/13)}\\
+    QF\_SLIA & - & - & - & 72705 \gray{(0/0/100)}\\
+    QF\_UF & 6649 \gray{(38/62)} & 6649 \gray{(38/62)} & 6650 \gray{(38/62/0)} & 7423 \gray{(42/58/0)}\\
+    QF\_UFBV & 31 \gray{(0/100)} & 31 \gray{(0/100)} & 31 \gray{(0/100/0)} & 1224 \gray{(53/47/0)}\\
+    QF\_UFIDL & 441 \gray{(24/76)} & 441 \gray{(24/76)} & 428 \gray{(25/75/0)} & 428 \gray{(25/75/0)}\\
+    QF\_UFLIA & 598 \gray{(67/33)} & 598 \gray{(67/33)} & 583 \gray{(69/31/0)} & 583 \gray{(69/31/0)}\\
+    QF\_UFLRA & 1627 \gray{(48/52)} & 1627 \gray{(48/52)} & 1284 \gray{(60/40/0)} & 1284 \gray{(60/40/0)}\\
+    QF\_UFNIA & 7 \gray{(0/100)} & 7 \gray{(0/100)} & 7 \gray{(0/100/0)} & 7 \gray{(0/100/0)}\\
+    QF\_UFNRA & 34 \gray{(47/53)} & 34 \gray{(47/53)} & 36 \gray{(58/31/11)} & 36 \gray{(58/31/11)}\\
+    UF & 2839 \gray{(28/72)} & 2839 \gray{(28/72)} & 7562 \gray{(10/44/46)} & 7562 \gray{(10/46/44)}\\
+    UFBV & 71 \gray{(25/75)} & 71 \gray{(25/75)} & 200 \gray{(34/48/17)} & 200 \gray{(34/48/17)}\\
+    UFDT & - & - & 4535 \gray{(0/9/90)} & 4527 \gray{(1/41/58)}\\
+    UFDTLIA & - & - & 303 \gray{(0/0/100)} & 303 \gray{(0/0/100)}\\
+    UFIDL & 68 \gray{(9/91)} & 68 \gray{(9/91)} & 68 \gray{(4/84/12)} & 68 \gray{(4/84/12)}\\
+    UFLIA & 8404 \gray{(0/100)} & 8404 \gray{(0/100)} & 10137 \gray{(0/76/24)} & 10137 \gray{(0/76/23)}\\
+    UFLRA & 25 \gray{(20/80)} & 25 \gray{(20/80)} & 15 \gray{(33/67/0)} & 15 \gray{(33/67/0)}\\
+    UFNIA & 2319 \gray{(0/100)} & 2319 \gray{(0/100)} & 3308 \gray{(0/74/26)} & 3308 \gray{(0/74/26)}\\
     \midrule
-    Total      & 154238 & 154424 & 256973 & 333241 \\
+    Total      & 154238 \gray{(40:60)} & 154424 \gray{(40:60)} & 256973 \gray{(37:46:17)} & 333241 \gray{(33:39:28)}\\
     \bottomrule

### 2019-04-15 2018/report/SMT-COMP.tex
Report: Remove frames
Report: Fix weighted division score

@@
 \ucoretrack is then defined as the weighted sum of all raw scores $$\sum_{i\in
-F} \alpha'_i \cdot \langle e \cdot N, n \cdot N, w, c\rangle$$ where the sum is
-over all benchmarks in the division to assess parallel performance, and the
-weighted sum of all sequential scores to assess sequential performance.
+F} \alpha'_i \cdot \langle e_i \cdot N_i, n_i \cdot N_i, w_i, c_i\rangle$$
+where the sum is over all benchmarks in the division to assess parallel
+performance, and the weighted sum of all sequential scores to assess sequential
+performance.
 

### 2019-04-15 2018/report/SMT-COMP.tex
conclusion

@@
 
-Further development of the competition should be undertaken with care,
-keeping in mind that major changes require not just the competition
-organizers, but also participants to adapt.  Immediate action items
-for next year's organizers are
+\paragraph{The Next Competition}
+
+Preparations for the 2019 iteration of the competition are underway and a number of changes have already been decided. These include
+
 \begin{itemize}
 	\item the inclusion of {\tt check-sat} commands with unknown status in
-  the \apptrack, and
-\item the definition of competition-wide rankings for the \apptrack 
-  and \ucoretrack.
+  the \apptrack, 
+  	\item the removal of non-competitive divisions and the filtering of benchmarks to exclude those seen as \emph{trivial} (taken as those solved by all competitors in the previous competition in less than 1 second)
+  	\item the introduction of a new experimental \emph{model validation track} with a single QF\_BV division where the models produced by solvers are checked,
+	\item the introduction of a new \emph{industrial challenge track} consisting of unsolved benchmarks submitted specifically for the track, and
+	\item the removal of the notion of competition-wide scoring.
 \end{itemize}
+
+\paragraph{The Future}
+
+Looking to the future of the competition, it is clear that further development should be undertaken with care,
+keeping in mind that major changes require not just the competition
+organizers, but also participants to adapt.
 

### 2019-04-15 2018/report/SMT-COMP.tex
small fix in table 3
Report: Fix weighted score

@@
 The \emph{(weighted) score} of a solver in a division of the \maintrack and
-\ucoretrack is then defined as the weighted sum of all raw scores $$\sum_{i\in
-F} \alpha'_i \cdot \langle e_i \cdot N_i, n_i \cdot N_i, w_i, c_i\rangle$$
-where the sum is over all benchmarks in the division to assess parallel
-performance, and the weighted sum of all sequential scores to assess sequential
-performance.
+\ucoretrack with $M$ benchmarks is then defined as the weighted sum of all raw
+scores $$\sum_{b\in M} \alpha'_b \cdot \langle e_b \cdot N_b, n_b \cdot N_b,
+w_b, c_b\rangle$$ where the sum is over all benchmarks in the division to
+assess parallel performance, and the weighted sum of all sequential scores to
+assess sequential performance.
 
@@
     \midrule
-    Total      & 154238 \gray{(40:60)} & 154424 \gray{(40:60)} & 256973 \gray{(37:46:17)} & 333241 \gray{(33:39:28)}\\
+    Total      & 154238 \gray{(40/60)} & 154424 \gray{(40/60)} & 256973 \gray{(37/46/17)} & 333241 \gray{(33/39/28)}\\
     \bottomrule

### 2019-04-15 2018/report/SMT-COMP.tex
resolved TODO 7

@@
 \noindent
+For the \maintrack and \apptrack, $e$ is the number of returned statuses that disagree with the given expected status (as described above, disagreements on benchmarks with unknown status lead to the benchmark being disregarded).
+For the \ucoretrack, $e$ includes, in addition, the number of returned unsat cores that are ill-formed or are not, in fact, unsatisfiable (as validated by a selection of other solvers selected by organizers).
+
 For the \maintrack and \apptrack,

### 2019-04-15 2018/report/SMT-COMP.tex
small fix in division scoring

@@
 \ucoretrack with $M$ benchmarks is then defined as the weighted sum of all raw
-scores $$\sum_{b\in M} \alpha'_b \cdot \langle e_b \cdot N_b, n_b \cdot N_b,
+scores $$\sum_{b\in M} \alpha'_b \cdot \langle e_b \cdot N, n_b \cdot N,
 w_b, c_b\rangle$$ where the sum is over all benchmarks in the division to

### 2019-04-15 2018/report/SMT-COMP.tex
Report: More outlook

@@
 \begin{itemize}
+  \item the introduction of new \emph{additional scores} for
+    satisfiable/unsatisfiable benchmarks and benchmarks solved within 24
+    seconds in the \maintrack,
 	\item the inclusion of {\tt check-sat} commands with unknown status in
   the \apptrack,
-  	\item the removal of non-competitive divisions and the filtering of benchmarks to exclude those seen as \emph{trivial} (taken as those solved by all competitors in the previous competition in less than 1 second)
-  	\item the introduction of a new experimental \emph{model validation track} with a single QF\_BV division where the models produced by solvers are checked,
-	\item the introduction of a new \emph{industrial challenge track} consisting of unsolved benchmarks submitted specifically for the track, and
-	\item the removal of the notion of competition-wide scoring.
+  \item the removal of \emph{non-competitive divisions} and the filtering of
+    benchmarks to exclude those seen as \emph{trivial} (taken as those solved
+    by all competitors in the previous competition in less than 1 second),
+  \item the introduction of a new experimental \emph{model validation track}
+    with a single QF\_BV division where the models produced by solvers are
+    checked,
+  \item the introduction of a new \emph{industrial challenge track} consisting
+    of unsolved benchmarks submitted specifically for the track,
+  \item the replacement of the notion of \emph{competition-wide scoring} with
+    awards that do not attempt to compare divisions.
 \end{itemize}

### 2019-04-15 2018/report/SMT-COMP.tex
Report: Addressed todo for sat/unsat tables

@@
 We only consider the \maintrack here, which contains a mixture of problems that
-are satisfiable and unsatisfiable.
-\todo{give numbers in percent for years or refer to table where the numbers should be: {table:benchmarks-main-track}}
-For the \apptrack, this analysis is less meaningful since a benchmarks usually
-contains a multitude of both satisfiable and unsatisfiable incremental queries
+are satisfiable and unsatisfiable. A percentage of satisfiable, unsatisfiable
+and unknown status benchmarks per division and year is given in
+Table~\ref{table:benchmarks-main-track}.  For the \apptrack, this analysis is
+less meaningful since a benchmarks usually contains a multitude of both
+satisfiable and unsatisfiable incremental queries
 (which may depend on each other).

### 2019-04-15 2018/report/SMT-COMP.tex
changes

@@
 developers, and pitted against each other in a number of tracks and
-divisions.  The SMT Competition was part of the Federated Logic
+divisions.
+
+The SMT Competition is one of a growing number of tool competitions in the broad area of formal methods, which are summarised in a recent review of the area~\cite{toolympics}.
+The two closest competitions in terms of goals and design are the SAT competition (\url{https://www.satcompetition.org/}), which evaluates SAT solvers, and CASC (\url{http://www.tptp.org/CASC/}), which evaluates automated theorem provers (ATPs).
+In recent years, we have seen a blurring of lines between SMT-COMP and CASC with SMT solvers competing in CASC and ATPs competing in SMT-COMP.
+The main (informal) distinction remains that SMT-COMP focusses on problems that are heavy in theories, whereas CASC focusses on problems heavy in quantifiers.
+Another closely related competition is SV-COMP (\url{https://sv-comp.sosy-lab.org}) where many tools rely on advanced in SMT solving technology.
+
+The SMT Competition was part of the Federated Logic
 Conference (FLoC) Olympic Games, which comprised 14 competitions in

### 2019-04-15 rules/rules19.tex
Minor edits to industry challenge track.

@@
 \todo{time limit}
-The \challenge Track will follow the same rules as the \main Track,
-with two exceptions: benchmark selection and the time limit. The track will run on benchmarks nominated by the community.
-\lh{TODO: benchmark selection still needs discussion}
-\lh{TODO: scored in the same way as main track (mention later not here)}
+The \challenge Track will include both incremental and single query benchmarks and it will follow the same rules as the \incremental and  \main Track, respectively with two exceptions: benchmark selection and the time limit.
+The track will run on challenging industrial benchmarks provided by the community.
 

### 2019-04-15 2018/report/SMT-COMP.tex
Report: Fix typo
fix remaining todo

@@
 The main (informal) distinction remains that SMT-COMP focusses on problems that are heavy in theories, whereas CASC focusses on problems heavy in quantifiers.
-Another closely related competition is SV-COMP (\url{https://sv-comp.sosy-lab.org}) where many tools rely on advanced in SMT solving technology.
+Another closely related competition is SV-COMP (\url{https://sv-comp.sosy-lab.org}) where many tools rely on advances in SMT solving technology.
 
@@
 Whilst producing these results we noticed that the description of what constitutes a family had been incorrectly interpreted by the scoring scripts in 2016-2018.
-After fixing this misinterpretation we note that only a single division winner changes - in 2017 AUFNIRA should have been won by
-\todo{who instead of who?}.
-As this is in the past we are choosing not to retroactively change the winner (and all tables in this paper reflect the previously published results) but the scripts have been fixed for future iterations of the competition.
+After fixing this misinterpretation we note that only a single division winner changes - in 2017 AUFNIRA should have been won by CVC4 and not Vampire.
+
+The combination of the small changes in winners and the lack of difference a misinterpretation of the notion of family made suggests that families do not have a significant impact on the competition.
 

### 2019-04-15 rules/rules19.tex
Rules: Update time limit in changes section.

@@
 
-\newcommand{\main}{Single Query\xspace}
-\newcommand{\incremental}{Incremental\xspace}
-\newcommand{\ucore}{Unsat Core\xspace}
-\newcommand{\mval}{Model Validation\xspace}
-\newcommand{\challenge}{Industry Challenge\xspace}
+\newcommand{\maintrack}{Single Query Track\xspace}
+\newcommand{\inctrack}{Incremental Track\xspace}
+\newcommand{\ucoretrack}{Unsat Core Track\xspace}
+\newcommand{\mvaltrack}{Model Validation Track\xspace}
+\newcommand{\challtrack}{Industry Challenge Track\xspace}
 
@@
 
-SMT-COMP 2019 will have five tracks: the \main Track (previously: Main Track),
-the incremental track (previously: Application Track), the \ucore Track,
-the (new) \challenge Track, and the (new)
-\mval Track.
+SMT-COMP 2019 will have five tracks: the \maintrack (previously: Main Track),
+the incremental track (previously: Application Track), the \ucoretrack,
+the (new) \challtrack, and the (new)
+\mvaltrack.
 
@@
   \item {\it Renaming of Tracks.} This year, the track previously known as
-    `Main Track` will be renamed to \emph{\main Track}, and the previous
-    `Application Track' will be renamed to \emph{\incremental Track}.
+    `Main Track` will be renamed to \emph{\maintrack}, and the previous
+    `Application Track' will be renamed to \emph{\inctrack}.
     \emph{Rationale:} We believe the current names are misleading, as the
@@
   \item {\it Time Limit.} The time limit per solver/benchmark pair is
-    anticipated to be at most 40 minutes in the \main (previously: Main),
-    \incremental (previously: Application), \ucore and \mval Tracks.  For the
-    \challenge Track, it is anticipated to be at most \todo{xx} minutes.
+    anticipated to be at most 40 minutes in the \maintrack (previously: Main Track),
+    \inctrack, \ucoretrack and \mvaltrack.  For the
+    \challtrack, it is anticipated to be at most 720 (12 hours) minutes.
     \emph{Rationale:} In 2017 and 2018, the time limit for the Main Track was
@@
     year, the reduced number of benchmarks selected per division allows us to
-    increase the time limit back to 40 minutes for the \main Track.
-
-  \item {\it New \mval Track.} \todo{}
-
-  \item {\it New \challenge Track.} \todo{}
+    increase the time limit back to 40 minutes for the \maintrack.  For the
+    \challtrack, 12 hours seem to be a reasonable compromise for the
+    expected number of participants and benchmarks submitted to this track.
+
+  \item {\it New \mvaltrack.} \todo{}
+
+  \item {\it New \challtrack.} \todo{}
 .
@@
   \item {\it Incremental Track.}
-    In previous years, benchmarks were not eligible for the \incremental Track
+    In previous years, benchmarks were not eligible for the \inctrack
     if their first \akey{check-sat} command had unknown status.  Similarly, the
@@
     \akey{check-sat} command has unknown status are eligible for the
-    \incremental track and trace execution is only stopped before the solver
+    \inctrack and trace execution is only stopped before the solver
     completes a benchmark if the execution runs into the time limit.
@@
 %
-In the \main and \ucore tracks, a participating solver must read a
+In the \maintrack and \ucoretrack, a participating solver must read a
 single benchmark script, whose filename is presented as the solver's
@@
   \begin{enumerate}
-  \item In the \main and \ucore tracks, there may be a single
+  \item In the \maintrack and \ucoretrack, there may be a single
     \akey{(set-option :print-success ...)} command.  Note that
@@
   \end{enumerate}
-\item In the \ucore Track, there is a single \akey{(set-option
+\item In the \ucoretrack, there is a single \akey{(set-option
   :produce-unsat-cores true)} command.
@@
   \begin{enumerate}
-    \item In all tracks except the \ucore Track,  named terms (i.e., terms
+    \item In all tracks except the \ucoretrack,  named terms (i.e., terms
       with the \akey{:named} attribute) are not used.
-    \item In the \ucore Track, top-level assertions may be named.
+    \item In the \ucoretrack, top-level assertions may be named.
   \end{enumerate}
@@
   \begin{enumerate}
-  \item In all tracks except the \incremental Track, there is exactly one
+  \item In all tracks except the \inctrack, there is exactly one
     \akey{check-sat} command.
@@
   \end{enumerate}
-\item In the \ucore Track, the \akey{check-sat} command (which is
+\item In the \ucoretrack, the \akey{check-sat} command (which is
   always issued in an unsatisfiable context) is followed by a single
   \akey{get-unsat-core} command.
-\item In the \mval Track, the \akey{check-sat} command (which is
+\item In the \mvaltrack, the \akey{check-sat} command (which is
   always issued in a satisfiable context) is followed by a single
@@
 The time limit~$T$ will be 40~minutes of wall-clock time per solver/benchmark
-pair in the \main, \incremental and \ucore tracks, \todo{12 hours} in the
-\challenge Track, and \todo{40 + 5 as in Unsat core}~minutes in the \mval Track \footnote{The time limit may be
+pair in the \maintrack, \inctrack and \ucoretrack, \todo{12 hours} in the
+\challtrack, and \todo{40 + 5 as in Unsat core}~minutes in the \mvaltrack \footnote{The time limit may be
 adjusted once we know the number of competition entrants and eligible
@@
 
-\subsection{\main Track (Previously: Main Track)}
+\subsection{\maintrack (Previously: Main Track)}
 \label{sec:exec:single}
 
-The \main Track competition will consist of selected benchmarks in each
+The \maintrack competition will consist of selected benchmarks in each
 of the logic divisions.  Each benchmark script will be presented to
@@
 
-The \main Track competition uses a StarExec post-processor (named
+The \maintrack competition uses a StarExec post-processor (named
 ``SMT-COMP 2019") to accumulate the results.
@@
 The disk space and memory limits for the incremental track are the
-same as for the \main Track (see Section~\ref{sec:exec:single}).
+same as for the \maintrack (see Section~\ref{sec:exec:single}).
 
@@
 
-\subsection{\ucore Track}
+\subsection{\ucoretrack}
 \label{sec:exec:unsat-core}
 
-The \ucore Track will evaluate the capability of solvers to
+The \ucoretrack will evaluate the capability of solvers to
 generate unsatisfiable cores (for problems that are known to be
@@
 In order to perform this unsatisfiability check, the organizers will use a
-selection of SMT solvers that participate in the \main Track of this
+selection of SMT solvers that participate in the \maintrack of this
 competition.  For each division, the organizers will use only solvers that have
-been sound (i.e., not produced any erroneous result) in the \main Track for
+been sound (i.e., not produced any erroneous result) in the \maintrack for
 this division.  The unsatisfiability of a produced unsatisfiable core is
@@
 
-\subsection{\challenge Track}
+\subsection{\challtrack}
 \label{sec:exec:industry-challenge}
@@
 \todo{time limit}
-The \challenge Track will include both incremental and single query benchmarks and it will follow the same rules as the \incremental and  \main Track, respectively with two exceptions: benchmark selection and the time limit.
+The \challtrack will include both incremental and single query benchmarks and it will follow the same rules as the \inctrack and  \maintrack, respectively with two exceptions: benchmark selection and the time limit.
 The track will run on challenging industrial benchmarks provided by the community.
 
-\subsection{\mval Track (experimental)}
+\subsection{\mvaltrack (experimental)}
 \label{sec:exec:model}
-The \mval Track will evaluate the solver's ability to produce models
+The \mvaltrack will evaluate the solver's ability to produce models
 for satisfiable problems. This track will run on all QF\_BV satisfiable benchmarks
-from the \main Track.
+from the \maintrack.
 
@@
 Benchmarks for each division will be drawn from the SMT-LIB benchmark
-library.  The \main Track will use a subset of all
+library.  The \maintrack will use a subset of all
 \emph{non-incremental} benchmarks; the incremental track will use a
-subset of all \emph{incremental} benchmarks.  The \ucore Track
-will use unsatisfiable \main Track benchmarks, modified to use named
+subset of all \emph{incremental} benchmarks.  The \ucoretrack
+will use unsatisfiable \maintrack benchmarks, modified to use named
 top-level assertions.
@@
 benchmark pool is culled as follows:
-\todo{add information about how benchmarks are selected for the \mval,
-\challenge, \ucore tracks, and the 24s, sat and unsat scores}
+\todo{add information about how benchmarks are selected for the \mvaltrack,
+\challtrack, \ucoretrack, and the 24s, sat and unsat scores}
 \begin{enumerate}
@@
 
-\todo{add information about how benchmarks are selected for the \mval,
-\challenge, \ucore tracks, and the 24s, sat and unsat scores -- either here
+\todo{add information about how benchmarks are selected for the \mvaltrack,
+\challtrack, \ucoretrack, and the 24s, sat and unsat scores -- either here
 or below}
@@
 results,\footnote{Here, $N$ is the number of \akey{check-sat} commands
-  in the benchmark.  Recall that \main Track benchmarks have just one
+  in the benchmark.  Recall that \maintrack benchmarks have just one
   \akey{check-sat} command; incremental track benchmarks may have
@@
 
-\header{\main Track.} More specifically, for the \main Track, we have
+\header{\maintrack.} More specifically, for the \maintrack, we have
 %
@@
 
-\header{\ucore Track.}
-%
-For the \ucore Track, we instead have $0 \leq n \leq A$, where~$A$
+\header{\ucoretrack.}
+%
+For the \ucoretrack, we instead have $0 \leq n \leq A$, where~$A$
 is the number of named top-level assertions in the benchmark, and
@@
 
-\subsection{Sequential Performance (\main Track)}
+\subsection{Sequential Performance (\maintrack)}
 \label{sec:sequential}
@@
 measures both, and we intend to recognize both best sequential and
-best parallel solvers in all competitive \main Track divisions.
+best parallel solvers in all competitive \maintrack divisions.
 \fi
@@
 
-\header{\main and \challenge Track: Removal of Disagreements.}
+\header{\maintrack and \challtrack: Removal of Disagreements.}
 %
 \todo{do we need to update this notion?}
-Before division scores are computed for the \main and \challenge tracks,
+Before division scores are computed for the \maintrack and \challtrack,
 benchmarks with unknown status are removed from the competition results if two
@@
 
-\header{\incremental Track: Removal of Disagreements.}
+\header{\inctrack: Removal of Disagreements.}
 \todo{}
 
-\header{\challenge Track: Removal of Disagreements.}
+\header{\challtrack: Removal of Disagreements.}
 \todo{}
@@
 
-For \main Track and \ucore Track divisions, we will separately
+For \maintrack and \ucoretrack divisions, we will separately
 compute the weighted sum of all benchmarks separately based on the
@@
 
-\subsection{Competition-wide scoring (\main Track)}
+\subsection{Competition-wide scoring (\maintrack)}
 \label{sec:competition-wide}
@@
 
-We define a competition-wide metric for the \main Track, separately for
+We define a competition-wide metric for the \maintrack, separately for
 parallel and sequential performance, as follows.  Let $N_i$ be the
@@
 \item The best three solvers according to the competition-wide scoring
-  (\main Track);
+  (\maintrack);
 \item the solver that wins the most competitive divisions in the
@@
 \item the solver that wins the most competitive divisions in the
-  \ucore Track;
+  \ucoretrack;
 \item the solver that wins the QF\_BV division (separately for
-  parallel and sequential performance) in the \main Track.
+  parallel and sequential performance) in the \maintrack.
 \end{itemize}

### 2019-04-16 rules/rules19.tex
Rules: Reorder
Benchmark selection section updated

@@
 \begin{itemize}
+  \item {\it Mandatory System Descriptions.}
+    SMT-COMP entrants are now required to provide a short (1–2 pages)
+    description of the system.  \emph{Rationale:} The main incentive for this
+    change is twofold.  First, we want to improve transparency when submitted
+    solvers are wrapper tools according to the rules of the competition.
+    Second, we want to encourage documentation of technical improvements that
+    lead to the current results.
+
   \item {\it Renaming of Tracks.} This year, the track previously known as
@@
     other tracks and use cases of SMT.
-
-  \item {\it Mandatory System Descriptions.}
-    SMT-COMP entrants are now required to provide a short (1–2 pages)
-    description of the system.  \emph{Rationale:} The main incentive for this
-    change is twofold.  First, we want to improve transparency when submitted
-    solvers are wrapper tools according to the rules of the competition.
-    Second, we want to encourage documentation of technical improvements that
-    lead to the current results.
-
-  \item {\it Do Not Run Non-Competitive Divisions.} \todo{}
-
-  \item {\it Benchmark Selection.} \todo{}
-
-  \item {\it Time Limit.} The time limit per solver/benchmark pair is
-    anticipated to be at most 40 minutes in the \maintrack (previously: Main Track),
-    \inctrack, \ucoretrack and \mvaltrack.  For the
-    \challtrack, it is anticipated to be at most 720 (12 hours) minutes.
-    \emph{Rationale:} In 2017 and 2018, the time limit for the Main Track was
-    reduced to 20 minutes (down from 40 minutes in earlier years) to cope with
-    the inclusion of a large number of benchmarks with unknown status.  This
-    year, the reduced number of benchmarks selected per division allows us to
-    increase the time limit back to 40 minutes for the \maintrack.  For the
-    \challtrack, 12 hours seem to be a reasonable compromise for the
-    expected number of participants and benchmarks submitted to this track.
-
-  \item {\it New \mvaltrack.} \todo{}
-
-  \item {\it New \challtrack.} \todo{}
-.
-  \item {\it New Scores.} \todo{24 seconds, sat, unsat}
 
@@
 
+  \item {\it New \mvaltrack.} \todo{}
+
+  \item {\it New \challtrack.} \todo{}
+.
+  \item {\it Time Limit.} The time limit per solver/benchmark pair is
+    anticipated to be at most 40 minutes in the \maintrack (previously: Main Track),
+    \inctrack, \ucoretrack and \mvaltrack.  For the
+    \challtrack, it is anticipated to be at most 720 (12 hours) minutes.
+    \emph{Rationale:} In 2017 and 2018, the time limit for the Main Track was
+    reduced to 20 minutes (down from 40 minutes in earlier years) to cope with
+    the inclusion of a large number of benchmarks with unknown status.  This
+    year, the reduced number of benchmarks selected per division allows us to
+    increase the time limit back to 40 minutes for the \maintrack.  For the
+    \challtrack, 12 hours seem to be a reasonable compromise for the
+    expected number of participants and benchmarks submitted to this track.
+
+  \item {\it Benchmark Selection.} \todo{}
+
+  \item {\it Scoring Scheme.} \todo{}
+
+  \item {\it New Scores in the \maintrack.} \todo{24 seconds, sat, unsat}
+
+  \item {\it Do Not Run Non-Competitive Divisions.} \todo{}
+
   \item {\it Experimental Strings Division.}
@@
   near future.
-
-  \item {\it Scoring Scheme.} \todo{}
 
@@
 %
-The competition will use a large subset of SMT-LIB benchmarks.  The
-benchmark pool is culled as follows:
-\todo{add information about how benchmarks are selected for the \mvaltrack,
-\challtrack, \ucoretrack, and the 24s, sat and unsat scores}
+The competition will use a large subset of SMT-LIB benchmarks.  In all
+tracks the following process will be used for culling the benchmark
+pool.
 \begin{enumerate}
@@
   of coming from or having some intended application outside SMT.
-\item \todo{\emph{Remove benchmarks solved by all solvers within 1s in the previous year}}
+\item \emph{Remove easy benchmarks.} The competition organizers will
+  remove all benchmarks that were solved by all solvers (including the
+  non-competitive solvers) in the 2018 SMT competition.
+\item \emph{Cap the number of instances in a division.} The competition
+  organizers will limit the number of benchmarks in a division as
+  follows:
+  \begin{enumerate}
+  \item If a division contains less than 300 instances, all
+        the instances will selected.
+  \item If a division contains between 300 and 600 instances, a
+        random selection of 300 instances from the set will be used.
+  \item If a division contains more than 600 instances, 50\% of
+        the benchmarks will be randomly selected.
   \end{enumerate}
-%
-\todo{update with the new benchmark selection rules}
-All remaining benchmarks are used for the competition.  There will be
-no further selection of benchmarks, e.g., based on benchmark
-difficulty or benchmark category.
-
-The set of benchmarks selected for the competition will be published
-when the competition begins.
-
-\todo{add information about how benchmarks are selected for the \mvaltrack,
-\challtrack, \ucoretrack, and the 24s, sat and unsat scores -- either here
-or below}
-
-\todo{For Unsatcore remove all benchmarks with a single assertion, otherwise use same procedure as last year... check what that was}
+\item \emph{\ucoretrack{}.} In addition, for the \ucoretrack{}, all
+  benchmarks with a single assertion will be removed.
+\end{enumerate}
+%
+The culling script will be publicly available and use the same random
+seed as the rest of the competition, and the set of benchmarks selected
+for the competition will be published when the competition begins.
 

### 2019-04-16 rules/rules19.tex
Rules: New layout for changes.

@@
 
-\newcommand{\akey}[1]{\textbf{#1}}
+\newcommand{\akey}[1]{\texttt{#1}}
+
 \newcommand{\rem}[1]{\textcolor{red}{[#1]}}
@@
 \newcommand{\challtrack}{Industry Challenge Track\xspace}
+
+\newcommand{\rationale}[1]{\hskip .5em{\textit{Rationale:} #1}\xspace}
 
@@
 
+\todo{does this paragraph need rewriting?}
 The annual Satisfiability Modulo Theories Competition~(SMT-COMP) is
@@
 \begin{itemize}
-  \item {\it Mandatory System Descriptions.}
+  \item {\bf Mandatory System Descriptions.}
     SMT-COMP entrants are now required to provide a short (1–2 pages)
-    description of the system.  \emph{Rationale:} The main incentive for this
+    description of the system.
+    \rationale{The main incentive for this
     change is twofold.  First, we want to improve transparency when submitted
@@
     Second, we want to encourage documentation of technical improvements that
-    lead to the current results.
-
-  \item {\it Renaming of Tracks.} This year, the track previously known as
+    lead to the current results.}
+
+  \item {\bf Renaming of Tracks.} This year, the track previously known as
     `Main Track` will be renamed to \emph{\maintrack}, and the previous
     `Application Track' will be renamed to \emph{\inctrack}.
-    \emph{Rationale:} We believe the current names are misleading, as the
+    \rationale{We believe the current names are misleading, as the
     previous `Main Track' also contains problems coming from applications.
     Additionally, having it called `Main' de-emphasizes the importance of the
-    other tracks and use cases of SMT.
-
-  \item {\it Incremental Track.}
+    other tracks and use cases of SMT.}
+
+  \item {\bf Incremental Track.}
     In previous years, benchmarks were not eligible for the \inctrack
@@
     completes a benchmark if the execution runs into the time limit.
-    \emph{Rationale:} The previous limitations were imposed by the trace
+    \rationale{The previous limitations were imposed by the trace
     executor, which now has been extended to support executing solvers on
-    benchmarks beyond \akey{check-sat} commands with unknown status.
-
-  \item {\it New \mvaltrack.} \todo{}
-
-  \item {\it New \challtrack.} \todo{}
-.
-  \item {\it Time Limit.} The time limit per solver/benchmark pair is
-    anticipated to be at most 40 minutes in the \maintrack (previously: Main Track),
-    \inctrack, \ucoretrack and \mvaltrack.  For the
-    \challtrack, it is anticipated to be at most 720 (12 hours) minutes.
-    \emph{Rationale:} In 2017 and 2018, the time limit for the Main Track was
+    benchmarks beyond \akey{check-sat} commands with unknown status.}
+
+  \item {\bf New \mvaltrack.} \todo{}
+
+  \item {\bf New \challtrack.} \todo{}
+
+  \item {\bf Time Limit.} The time limit per solver/benchmark pair is
+    anticipated to be at most 40 minutes in the \maintrack (previously: Main
+    Track), \inctrack, \ucoretrack and \mvaltrack.  For the \challtrack, it is
+    anticipated to be at most 720 (12 hours) minutes.
+    \rationale{In 2017 and 2018, the time limit for the Main Track was
     reduced to 20 minutes (down from 40 minutes in earlier years) to cope with
@@
     \challtrack, 12 hours seem to be a reasonable compromise for the
-    expected number of participants and benchmarks submitted to this track.
-
-  \item {\it Benchmark Selection.} \todo{}
-
-  \item {\it Scoring Scheme.} \todo{}
-
-  \item {\it New Scores in the \maintrack.} \todo{24 seconds, sat, unsat}
-
-  \item {\it Do Not Run Non-Competitive Divisions.} \todo{}
-
-  \item {\it Experimental Strings Division.}
+    expected number of participants and benchmarks submitted to this track.}
+
+  \item {\bf Benchmark Selection.} \todo{}
+
+  \item {\bf Scoring Scheme.} \todo{}
+
+  \item {\bf New Scores in the \maintrack.} \todo{24 seconds, sat, unsat}
+
+  \item {\bf Do Not Run Non-Competitive Divisions.} \todo{}
+
+  \item {\bf Experimental Strings Division.}
     \todo{point to the current draft of the standard as the set of rules
     solvers have to agree on}
-    The competition will feature an experimental divisions for
-  benchmarks that use strings.  \emph{Rationale:} Corresponding
-  theories and benchmarks are expected to be added to SMT-LIB in the
-  near future.
-
-  \item {\it Competition-Wide Scores/Winners.} \todo{}
-
-  \item {\it Problems with Evaluation Scripts.} \todo{Explain what was the
+    The competition will feature an experimental divisions for benchmarks that
+    use strings.
+    \rationale{Corresponding theories and benchmarks are expected to be added
+    to SMT-LIB in the near future.}
+
+  \item {\bf Competition-Wide Scores/Winners.} \todo{}
+
+  \item {\bf Problems with Evaluation Scripts.} \todo{Explain what was the
     problem and what has been fixed, talk about notion of benchmark family.}

### 2019-04-16 rules/rules19.tex
Rules: Update changes with model validation track info.

@@
 
-  \item {\bf New \mvaltrack.} \todo{}
+  \item {\bf New \mvaltrack.}
+    This year, we introduce a new experimental \mvaltrack for logic QF\_BV.
+    The benchmarks for this track will include all eligible \emph{non-incremental}
+    QF\_BV benchmarks with known satisfiable status in SMT-LIB.
+    Participating solvers are required to support the \akey{get-model} command.
+    \rationale{In many SMT applications, model generation is an essential
+    feature.  Previously, none of the SMT-COMP tracks required model
+    generation. One of the challenges is that the model format is not
+    consistent across different solvers. While imposing a standard over all
+    logics is challenging, there are several logics (e.g., QF\_BV) where it is
+    straightforward.  In the future we hope to expand this track to other
+    logics as a way of pushing for model standardization.  Since the QF\_BV
+    division was the one with the largest number of participants in previous
+    years,  we hope for a high number of participants in this track.  }
 

### 2019-04-16 rules/rules19.tex
Rules: Alphabetical order in disclosure.
Rules: Update changes with industry challenge track info.

@@
 
-  \item {\bf New \mvaltrack.}
+  \item {\bf New \mvaltrack for QF\_BV.}
     This year, we introduce a new experimental \mvaltrack for logic QF\_BV.
@@
 
-  \item {\bf New \challtrack.} \todo{}
+  \item {\bf New \challtrack.}
+    This year, we further introduce a new \challtrack.  This track will contain
+    new challenging SMT-LIB benchmarks (with an emphasis on industrial
+    applications) that are either unsolved or unsolved within some reasonable
+    time limit, as indicated by the benchmark submitters.  We will also include
+    benchmarks nominated by the community as challenging and of interest. In
+    this track, solvers will run with a significantly longer time limit.
+    \rationale{ Different application domains require different time limits.
+    For example software verification traditionally requires much lower time
+    limits, compared to hardware verification.  To reward solvers optimized for
+    different use cases, we propose this new track and a new score for
+    benchmarks solved within a very low time limit (see item ``New Scores in
+    the \maintrack'').  }
+    \todo{how do we provide information about which benchmarks and which logics?}
 
@@
 %
+
+\header{Tools} \todo{link to scrambler, trace executor, benchmark selection script, postprocessors}
 
@@
 creating or submitting solvers.
+Antti Hyvarinen is part of the developing team of the SMT solver
+OpenSMT~\cite{opensmt2}.
 Aina Niemetz is part of the developing teams of the SMT solvers
@@
 and CVC4~\cite{cvc4}.
-Antti Hyvarinen is part of the developing team of the SMT solver
-OpenSMT~\cite{opensmt2}.
 Giles Reger is associated with the group

### 2019-04-16 rules/rules19.tex
Rules: Update changes with new scores info.

@@
   \item {\bf Time Limit.} The time limit per solver/benchmark pair is
-    anticipated to be at most 40 minutes in the \maintrack (previously: Main
-    Track), \inctrack, \ucoretrack and \mvaltrack.  For the \challtrack, it is
-    anticipated to be at most 720 (12 hours) minutes.
+    anticipated to be at most 40 minutes in the \maintrack, \inctrack,
+    \ucoretrack and \mvaltrack.  For the \challtrack, it is anticipated to be
+    at most 720 (12 hours) minutes.
     \rationale{In 2017 and 2018, the time limit for the Main Track was
@@
 
-  \item {\bf New Scores in the \maintrack.} \todo{24 seconds, sat, unsat}
+  \item {\bf New Scores in the \maintrack.}
+    This year, additionally to the separate scores given for sequential and
+    parallel performance, we will reward three new scores in the \maintrack.
+    The \emph{24-second score} will reward solving performance within a time
+    limit of 24 seconds (wall clock time), the \emph{sat score} will reward
+    performance on satisfiable instances, and the \emph{unsat score} will
+    reward performance on unsatisfiable instances.
+    \rationale{ Different application domains of SMT typically impose a wide
+    range of time limits (from hours to seconds).  Previous time limits used in
+    the competition were the same for all benchmarks and thus agnostic to the
+    application domain of a benchmark.  The new \challtrack and the new
+    24-second score try to address use cases on both extreme ends of the
+    spectrum.  Further, in many cases an SMT application produces either mainly
+    satisfiable or mainly unsatisfiable queries to the SMT solver.  The new sat
+    and unsat scores are intended to reward solvers that implement specialized
+    techniques and optimizations for either case.}
 

### 2019-04-16 rules/rules19.tex
Rules: Update changes with benchmark selection info.

@@
 
-  \item {\bf Benchmark Selection.} \todo{}
+  \item {\bf Benchmark Selection.} Since 2015, the competition evaluated all
+    solvers on all eligible benchmarks in SMT-LIB.  This year, we will use an
+    alternative benchmark selection scheme that selects a subset of the
+    eligible benchmarks. The upper bound for the size of each division,
+    however, is not fixed, but depends on the size of the corresponding logic.
+    Prior to this selection, we will remove all benchmarks in a division that
+    were solved by all solvers (including non-competing solvers) in this
+    division in under a second during last year's competition.
+    \rationale{Evaluating solvers on all eligible benchmarks in SMT-LIB makes
+    results more predictable and seems to be more of an evaluation than a
+    competition.  In the Main track of last year's competition, 78\% of the 258,741
+    benchmarks were solved by all supported solvers within the time
+    limit (71\% within 1 second). In 7 (out of 46) logics, over 99\% of
+    benchmarks were solved by all solvers.  Removing `easy' (or at least
+    `unsurprising') benchmarks attempts to shift the focus towards challenging
+    benchmarks, in particular since we now use an alternative benchmark
+    selection scheme.  It can be argued that the size of a logic in SMT-LIB can
+    be seen as an indicator of its relevance.  We thus do not use a fixed upper
+    bound for the size of a division in order to reflect the suggested
+    importance of a division.}
 

### 2019-04-16 rules/rules19.tex
Rules: Update changes with scoring scheme info.

@@
     results more predictable and seems to be more of an evaluation than a
-    competition.  In the Main track of last year's competition, 78\% of the 258,741
-    benchmarks were solved by all supported solvers within the time
+    competition.  In the Main track of last year's competition, 78\% of the
+    258,741 benchmarks were solved by all supported solvers within the time
     limit (71\% within 1 second). In 7 (out of 46) logics, over 99\% of
@@
 
-  \item {\bf Scoring Scheme.} \todo{}
+  \item {\bf Scoring Scheme.}
+    This year, we will abandon the weighted scoring scheme that was introduced
+    for the Main Track and \ucoretrack in 2016. We will fall back to the
+    scoring scheme based on the number of solved instances that was last used
+    in 2015.
+    \rationale{ Since 2016, the competition has used a scoring scheme based on
+    benchmark weights in order to de-emphasize large benchmark families.  The
+    scoring scheme is fairly complicated and not necessarily intuitive.  It
+    further makes comparing results in papers with results from the competition
+    more difficult.  A recent analysis of competition data from 2015-2018 for a
+    report on the competition of these years (currently under submission to
+    JSAT) suggests that benchmark families do not have a significant impact on
+    the (weighted) scores.  When determining winners for each division using
+    the scoring scheme of 2015, the winners for only 7 divisions (out of 139)
+    over all three years would have changed.  While producing these results we
+    further noticed that the description of what constitutes a benchmark family
+    (as stated in the rules documents) had been incorrectly interpreted by the
+    scoring scripts in 2016-2018. After fixing this misinterpretation, only one
+    single division winner changes - in 2017 AUFNIRA should have been won by
+    CVC4 and not Vampire.}
 

### 2019-04-17 rules/rules19.tex
Started working on implementing the instance selection that prefers the new instances.

--- 2019-04-16 rules/rules19.tex
@@
 
-\newcommand{\akey}[1]{\texttt{#1}}
-
+\newcommand{\akey}[1]{\textbf{#1}}
 \newcommand{\rem}[1]{\textcolor{red}{[#1]}}
@@
 \newcommand{\challtrack}{Industry Challenge Track\xspace}
-
-\newcommand{\rationale}[1]{\hskip .5em{\textit{Rationale:} #1}\xspace}
 
@@
 
-\todo{does this paragraph need rewriting?}
 The annual Satisfiability Modulo Theories Competition~(SMT-COMP) is
@@
 \begin{itemize}
-  \item {\bf Mandatory System Descriptions.}
+  \item {\it Mandatory System Descriptions.}
     SMT-COMP entrants are now required to provide a short (1–2 pages)
-    description of the system.
-    \rationale{The main incentive for this
+    description of the system.  \emph{Rationale:} The main incentive for this
     change is twofold.  First, we want to improve transparency when submitted
@@
     Second, we want to encourage documentation of technical improvements that
-    lead to the current results.}
-
-  \item {\bf Renaming of Tracks.} This year, the track previously known as
+    lead to the current results.
+
+  \item {\it Renaming of Tracks.} This year, the track previously known as
     `Main Track` will be renamed to \emph{\maintrack}, and the previous
     `Application Track' will be renamed to \emph{\inctrack}.
-    \rationale{We believe the current names are misleading, as the
+    \emph{Rationale:} We believe the current names are misleading, as the
     previous `Main Track' also contains problems coming from applications.
     Additionally, having it called `Main' de-emphasizes the importance of the
-    other tracks and use cases of SMT.}
-
-  \item {\bf Incremental Track.}
+    other tracks and use cases of SMT.
+
+  \item {\it Incremental Track.}
     In previous years, benchmarks were not eligible for the \inctrack
@@
     completes a benchmark if the execution runs into the time limit.
-    \rationale{The previous limitations were imposed by the trace
+    \emph{Rationale:} The previous limitations were imposed by the trace
     executor, which now has been extended to support executing solvers on
-    benchmarks beyond \akey{check-sat} commands with unknown status.}
-
-  \item {\bf New \mvaltrack for QF\_BV.}
-    This year, we introduce a new experimental \mvaltrack for logic QF\_BV.
-    The benchmarks for this track will include all eligible \emph{non-incremental}
-    QF\_BV benchmarks with known satisfiable status in SMT-LIB.
-    Participating solvers are required to support the \akey{get-model} command.
-    \rationale{In many SMT applications, model generation is an essential
-    feature.  Previously, none of the SMT-COMP tracks required model
-    generation. One of the challenges is that the model format is not
-    consistent across different solvers. While imposing a standard over all
-    logics is challenging, there are several logics (e.g., QF\_BV) where it is
-    straightforward.  In the future we hope to expand this track to other
-    logics as a way of pushing for model standardization.  Since the QF\_BV
-    division was the one with the largest number of participants in previous
-    years,  we hope for a high number of participants in this track.  }
-
-  \item {\bf New \challtrack.}
-    This year, we further introduce a new \challtrack.  This track will contain
-    new challenging SMT-LIB benchmarks (with an emphasis on industrial
-    applications) that are either unsolved or unsolved within some reasonable
-    time limit, as indicated by the benchmark submitters.  We will also include
-    benchmarks nominated by the community as challenging and of interest. In
-    this track, solvers will run with a significantly longer time limit.
-    \rationale{ Different application domains require different time limits.
-    For example software verification traditionally requires much lower time
-    limits, compared to hardware verification.  To reward solvers optimized for
-    different use cases, we propose this new track and a new score for
-    benchmarks solved within a very low time limit (see item ``New Scores in
-    the \maintrack'').  }
-    \todo{how do we provide information about which benchmarks and which logics?}
-
-  \item {\bf Time Limit.} The time limit per solver/benchmark pair is
-    anticipated to be at most 40 minutes in the \maintrack, \inctrack,
-    \ucoretrack and \mvaltrack.  For the \challtrack, it is anticipated to be
-    at most 720 (12 hours) minutes.
-    \rationale{In 2017 and 2018, the time limit for the Main Track was
+    benchmarks beyond \akey{check-sat} commands with unknown status.
+
+  \item {\it New \mvaltrack.} \todo{}
+
+  \item {\it New \challtrack.} \todo{}
+.
+  \item {\it Time Limit.} The time limit per solver/benchmark pair is
+    anticipated to be at most 40 minutes in the \maintrack (previously: Main Track),
+    \inctrack, \ucoretrack and \mvaltrack.  For the
+    \challtrack, it is anticipated to be at most 720 (12 hours) minutes.
+    \emph{Rationale:} In 2017 and 2018, the time limit for the Main Track was
     reduced to 20 minutes (down from 40 minutes in earlier years) to cope with
@@
     \challtrack, 12 hours seem to be a reasonable compromise for the
-    expected number of participants and benchmarks submitted to this track.}
-
-  \item {\bf Benchmark Selection.} \todo{}
-
-  \item {\bf Scoring Scheme.} \todo{}
-
-  \item {\bf New Scores in the \maintrack.}
-    This year, additionally to the separate scores given for sequential and
-    parallel performance, we will reward three new scores in the \maintrack.
-    The \emph{24-second score} will reward solving performance within a time
-    limit of 24 seconds (wall clock time), the \emph{sat score} will reward
-    performance on satisfiable instances, and the \emph{unsat score} will
-    reward performance on unsatisfiable instances.
-    \rationale{ Different application domains of SMT typically impose a wide
-    range of time limits (from hours to seconds).  Previous time limits used in
-    the competition were the same for all benchmarks and thus agnostic to the
-    application domain of a benchmark.  The new \challtrack and the new
-    24-second score try to address use cases on both extreme ends of the
-    spectrum.  Further, in many cases an SMT application produces either mainly
-    satisfiable or mainly unsatisfiable queries to the SMT solver.  The new sat
-    and unsat scores are intended to reward solvers that implement specialized
-    techniques and optimizations for either case.}
-
-  \item {\bf Do Not Run Non-Competitive Divisions.} \todo{}
-
-  \item {\bf Experimental Strings Division.}
+    expected number of participants and benchmarks submitted to this track.
+
+  \item {\it Benchmark Selection.} \todo{}
+
+  \item {\it Scoring Scheme.} \todo{}
+
+  \item {\it New Scores in the \maintrack.} \todo{24 seconds, sat, unsat}
+
+  \item {\it Do Not Run Non-Competitive Divisions.} \todo{}
+
+  \item {\it Experimental Strings Division.}
     \todo{point to the current draft of the standard as the set of rules
     solvers have to agree on}
-    The competition will feature an experimental divisions for benchmarks that
-    use strings.
-    \rationale{Corresponding theories and benchmarks are expected to be added
-    to SMT-LIB in the near future.}
-
-  \item {\bf Competition-Wide Scores/Winners.} \todo{}
-
-  \item {\bf Problems with Evaluation Scripts.} \todo{Explain what was the
+    The competition will feature an experimental divisions for
+  benchmarks that use strings.  \emph{Rationale:} Corresponding
+  theories and benchmarks are expected to be added to SMT-LIB in the
+  near future.
+
+  \item {\it Competition-Wide Scores/Winners.} \todo{}
+
+  \item {\it Problems with Evaluation Scripts.} \todo{Explain what was the
     problem and what has been fixed, talk about notion of benchmark family.}
@@
 %
-
-\header{Tools} \todo{link to scrambler, trace executor, benchmark selection script, postprocessors}
 
@@
 %
-The competition will use a large subset of SMT-LIB benchmarks.  In all
-tracks the following process will be used for culling the benchmark
-pool.
+The competition will use a large subset of SMT-LIB benchmarks, with a
+preference to the new benchmarks.  In all tracks the following process
+will be used for culling the benchmark pool.
 \begin{enumerate}
@@
 creating or submitting solvers.
-Antti Hyvarinen is part of the developing team of the SMT solver
-OpenSMT~\cite{opensmt2}.
 Aina Niemetz is part of the developing teams of the SMT solvers
@@
 and CVC4~\cite{cvc4}.
+Antti Hyvarinen is part of the developing team of the SMT solver
+OpenSMT~\cite{opensmt2}.
 Giles Reger is associated with the group

### 2019-04-17 rules/rules19.tex
Added the part on ensuring at least one benchmark from each new benchmark family

--- 2019-04-16 rules/rules19.tex
@@
 
-\header{Benchmark demographics. \todo{check}}
+\header{Benchmark demographics.}
 %
@@
 
-\header{Benchmark selection.} \todo{Antti covers this section}
-%
-The competition will use a large subset of SMT-LIB benchmarks.  In all
-tracks the following process will be used for culling the benchmark
-pool.
+\header{Benchmark selection.}
+%
+The competition will use a large subset of SMT-LIB benchmarks, with some
+guarantees on including new benchmarks.  In all tracks the following
+process will be used for culling the benchmark pool.
 \begin{enumerate}
@@
         the instances will selected.
-  \item If a division contains between 300 and 600 instances, a
-        random selection of 300 instances from the set will be used.
+  \item If a division contains between 300 and 600 instances,
+        a selection of 300 instances from the set will be selected.
   \item If a division contains more than 600 instances, 50\% of
-        the benchmarks will be randomly selected.
+        the benchmarks will be selected.
   \end{enumerate}
@@
 %
-The culling script will be publicly available and use the same random
-seed as the rest of the competition, and the set of benchmarks selected
-for the competition will be published when the competition begins.
+The selection process in cases (b) and (c) above will guarantee the
+inclusion of new benchmarks by first picking randomly one benchmark from
+each new benchmark family.  The rest of the benchmarks will be chosen
+randomly from the remaining benchmarks using a uniform distribution.
+%
+The culling script will be publicly available and will use the same
+random seed as the rest of the competition.  The set of benchmarks
+selected for the competition will be published when the competition
+begins.
 

### 2019-04-17 rules/rules19.tex
Added a note on the special handling of new families in benchmark selection in the changes

@@
   \item {\bf Benchmark Selection.} Since 2015, the competition evaluated all
-    solvers on all eligible benchmarks in SMT-LIB.  This year, we will use an
-    alternative benchmark selection scheme that selects a subset of the
-    eligible benchmarks. The upper bound for the size of each division,
-    however, is not fixed, but depends on the size of the corresponding logic.
-    Prior to this selection, we will remove all benchmarks in a division that
-    were solved by all solvers (including non-competing solvers) in this
+    solvers on all eligible benchmarks in SMT-LIB.  This year, we will
+    use an alternative benchmark selection scheme that selects a subset
+    of the eligible benchmarks. The benchmark selection will be random,
+    but will guarantee inclusion of newly submitted benchmarks.  The upper
+    bound for the size of each division is not fixed, but
+    depends on the size of the corresponding logic.  Prior to this
+    selection, we will remove all benchmarks in a division that were
+    solved by all solvers (including non-competing solvers) in this
     division in under a second during last year's competition.
-    \rationale{Evaluating solvers on all eligible benchmarks in SMT-LIB makes
-    results more predictable and seems to be more of an evaluation than a
-    competition.  In the Main track of last year's competition, 78\% of the
-    258,741 benchmarks were solved by all supported solvers within the time
-    limit (71\% within 1 second). In 7 (out of 46) logics, over 99\% of
-    benchmarks were solved by all solvers.  Removing `easy' (or at least
-    `unsurprising') benchmarks attempts to shift the focus towards challenging
-    benchmarks, in particular since we now use an alternative benchmark
-    selection scheme.  It can be argued that the size of a logic in SMT-LIB can
-    be seen as an indicator of its relevance.  We thus do not use a fixed upper
-    bound for the size of a division in order to reflect the suggested
+    \rationale{Evaluating solvers on all eligible benchmarks in SMT-LIB
+    makes results more predictable and seems to be more of an evaluation
+    than a competition.  In the Main track of last year's competition,
+    78\% of the 258,741 benchmarks were solved by all supported solvers
+    within the time limit (71\% within 1 second). In 7 (out of 46)
+    logics, over 99\% of benchmarks were solved by all solvers.
+    Removing `easy' (or at least `unsurprising') benchmarks attempts to
+    shift the focus towards challenging benchmarks, in particular since
+    we now use an alternative benchmark selection scheme.  It can be
+    argued that the size of a logic in SMT-LIB can be seen as an
+    indicator of its relevance.  We thus do not use a fixed upper bound
+    for the size of a division in order to reflect the suggested
     importance of a division.}

### 2019-04-17 rules/rules19.tex
Rules: Update changes with non-competitive divisions.

@@
     solved by all solvers (including non-competing solvers) in this
-    division in under a second during last year's competition.
+    division in under 1 second during last year's competition.
     \rationale{Evaluating solvers on all eligible benchmarks in SMT-LIB
@@
 
-  \item {\bf Do Not Run Non-Competitive Divisions.} \todo{}
+  \item {\bf Do Not Run Non-Competitive Divisions.}
+    This year, we will not run non-competitive divions.
+    \rationale{Evaluating solvers in non-competitive divisions is more in the
+    spirit of an evaluation than a competition.}
 

### 2019-04-18 rules/rules19.tex
Rules: Add comments.

@@
 descriptions will be made publicly available. \todo{Giles: Include licence information - minimum requirement: licence must allow to run the binary for evaluation purposes}
+\an{This todo should actually go into section 5, intro of the section maybe, we should add there that solvers will be archived on the website and so on.
+Interestingly, we replied to the reviewer in the report that the solvers are publicly available in the StarExec space when asked about reproducability, but in the past it was never defined under which terms.}
 
@@
 %
-The organizers' intent is to promote as wide a comparison among
+The intent of the organizers is to promote as wide a comparison among
 solvers and solver options as possible.  However, if the number of
@@
 %
-In the \maintrack and \ucoretrack, a participating solver must read a
-single benchmark script, whose filename is presented as the solver's
-first command-line argument.  In the incremental track, a trace
-executor will send commands from a benchmark script to the solver's
-standard input channel.
+In the \maintrack, \mvaltrack, \ucoretrack and \challtrack, a participating
+solver must read a single benchmark script, whose filename is presented as the
+solver's first command-line argument.  In the \inctrack, a trace
+executor will send commands from a benchmark script to the solver's standard
+input channel.
 

### 2019-04-18 rules/rules19.tex
describe website and tools

@@
 
-\header{Competition Website}
-
-\todo{Giles: Add text about the fact that we will use the competition website to include links to tools, announce results etc... including archiving}
-%
-
-\header{Tools} \todo{link to scrambler, trace executor, benchmark selection script, postprocessors}
+\header{Competition Website.} 
+The competition website (\url{www.smtcomp.org}) will be used as the main form of communication for the competition.
+The website will be used to post updates, link to these rules and other relevant information (e.g.
+the benchmarks), and to announce the results.
+We also use the website to archive previous competitions.
+Starting from 2019 we will include the submitted solvers in this archive to allow reproduction of the competition results in the future.
+%
+
+\header{Tools.} 
+The competition uses a number of its own tools/scripts to run the competition.
+We briefly describe these tools.
+Unless stated otherwise the tools are found at \url{https://github.com/SMT-COMP/smt-comp/tree/master/tools}.
+{\color{red} Some tools have not been released yet.}
+\begin{itemize}
+	\item \textbf{Benchmark Selection.} This script implements the benchmark selection policy described on page~\pageref{benchmark-selection}.
+It takes a seed for the random benchmark selection.
+The same seed is used for all tools requiring randomisation.
+	\item \textbf{Scramber.} This tool is used to scramble benchmarks during the competition to ensure that tools do not rely on syntactic features to identify benchmarks.
+The scramber can be found at \url{https://github.com/SMT-COMP/scrambler}.
+	\item \textbf{Trace Executor.} This tool is used in the interactive track to emulate an on-line interaction between an SMT solver and a client application and is available at \url{https://github.com/SMT-COMP/trace-executor}
+	\item \textbf{Postprocessors.} These are used by StarExec to translate the output of tools to the format required for scoring.
+The postprocessors (per track) are available at \url{https://github.com/SMT-COMP/postprocessors}.
+	\item \textbf{Scoring.} This script implements the scoring computation described on in Section~\ref{sec:scoring}. It also includes the scoring computations used in previous competitions (since 2015).
+\end{itemize}
 
@@
 
-\header{Benchmark selection.}
+\header{Benchmark selection.} \label{benchmark-selection}
 %

### 2019-04-18 rules/rules19.tex
Rules: Update section "Entrants" until (incl) "System Descriptions".

@@
     JSAT) suggests that benchmark families do not have a significant impact on
-    the (weighted) scores.  When determining winners for each division using
+    the (weighted) scores  When determining winners for each division using
     the scoring scheme of 2015, the winners for only 7 divisions (out of 139)
@@
 
-\header{Solver submission.}
-%
-An entrant to SMT-COMP is an SMT solver submitted by its authors using
-the StarExec (\url{http://www.starexec.org}) service.  The execution
+\header{SMT Solver.} A solver that can enter SMT-COMP is a tool that allows to
+determine (un)satisfiability of benchmarks from the SMT-LIB benchmark library
+(\url{http://www.smt-lib.org/benchmarks.shtml}).
+
+\header{SMT Solver Submission.}
+An entrant to SMT-COMP is a solver submitted by its authors using
+the StarExec (\url{http://www.starexec.org}) service.
+
+\header{Solver execution.}
+The StarExec execution
 service enables members of the SMT research community to run solvers
@@
 Jobs are run on a shared computer cluster.  The execution service is
-provided free of charge, but it does require registration to create a
-login account.  Registered users may then upload their own solvers to
+provided free of charge, but requires registration to create a
+login account.  Registered users may then upload solvers to
 run, or may run public solvers already uploaded to the service.
@@
 
+\header{Participation in the Competition.}
 For participation in SMT-COMP, a solver must be uploaded to StarExec
@@
 \begin{center}
-  \todo{\url{}submission form url}
+  \rem{submission form url}
 \end{center}
-A submission must also include a \emph{system description} (see below) and a
-\emph{32-bit unsigned integer}.
- These integer numbers, collected from all submissions, are used to seed the
-benchmark scrambler.
+A submission \textbf{must} also include a \emph{system description} (see below)
+and a \emph{32-bit unsigned integer}.
+ These integer numbers, collected from all submissions, are used to seed
+ competition tools.
 
 \header{System description.}
-%
-\todo{add minimum requirement for authorship?}
-As part of the submission, SMT-COMP entrants are \emph{required} to provide a
-short (1–-2 pages) description of the system.  This should include a list of
-all authors of the system, their present institutional affiliations, and any
-appropriate acknowledgements.  The programming language(s) and basic SMT
-solving approach employed should be described (e.g., lazy integration of a
-Nelson-Oppen combination with SAT, translation to SAT, etc.).  System
-descriptions should also include a URL for a web site for the submitted tool.
-System descriptions must be submitted until the final solver deadline System
-descriptions will be made publicly available. \todo{Giles: Include licence information - minimum requirement: licence must allow to run the binary for evaluation purposes}
-\an{This todo should actually go into section 5, intro of the section maybe, we should add there that solvers will be archived on the website and so on.
-Interestingly, we replied to the reviewer in the report that the solvers are publicly available in the StarExec space when asked about reproducability, but in the past it was never defined under which terms.}
+As part of the submission, SMT-COMP entrants are \textbf{required} to provide a
+short (1-2 pages) description of the system, which \textbf{must} explicitly
+acknowledge any solver it wraps in case of a \emph{wrapper tool} (see below).
+It \emph{should} further include
+\begin{itemize}[itemsep=0ex]
+  \item a list of all authors of the system and their present institutional
+    affiliations,
+  \item the basic SMT solving approach employed,
+  \item details of any non-standard algorithmic techniques as well as
+    references to relevant literature (by the authors or others),
+  \item appropriate acknowledgement of tools other than SMT solvers called by
+    the system (e.g., SAT solvers) that are not written by the authors of the
+    submitted solver, and
+  \item a link to a website for the submitted tool.
+\end{itemize}
+System descriptions \textbf{must} be submitted \textbf{until the final solver
+deadline}, and will be made publicly available on the competition website.
 
@@
 made public.
+\todo{Giles: Include licence information - minimum requirement: licence must allow to run the binary for evaluation purposes}
+\an{intro of the section maybe, we should add there that solvers will be archived on the website and so on.
+Interestingly, we replied to the reviewer in the report that the solvers are publicly available in the StarExec space when asked about reproducability, but in the past it was never defined under which terms.}
 

### 2019-04-19 rules/rules19.tex
Rules: Finish up section 4.

@@
     lead to the current results.}
+
+  \item {\bf Naming Convention for Derived Tools.} \todo{}
 
@@
 
-\header{SMT Solver.} A solver that can enter SMT-COMP is a tool that allows to
+\header{SMT Solver.}
+%
+A solver that can enter SMT-COMP is a tool that allows to
 determine (un)satisfiability of benchmarks from the SMT-LIB benchmark library
@@
 
+\header{Wrapper Tool.}
+%
+A \emph{wrapper tool} is defined as any solver that calls one or more SMT
+solvers (the \emph{wrapped solvers}) of which the author of the wrapper tool is
+not an author.  Its system description \textbf{must} explicitly acknowledge any
+solvers that it wraps.  It \emph{should} further make clear technical
+innovations by which the wrapper tool expects to improve on the wrapped
+solvers.
+
+\header{Derived Tool.}
+%
+A \emph{derived tool} is defined as any solver that is \emph{based on and
+extends} an SMT solver (the \emph{base solver}) not written by the authors of
+the derived tool.  Its system description \textbf{must} explicitly acknowledge
+the solver it is based on and extends.  It \emph{should} further make clear
+technical innovations by which the wrapper tool expects to improve on the
+wrapped solvers.  A derived tool should follow the \emph{naming convention}
+{[name of base solver]-[my solver name]}.
+
 \header{SMT Solver Submission.}
+%
 An entrant to SMT-COMP is a solver submitted by its authors using
@@
 \header{Solver execution.}
+%
 The StarExec execution
@@
 \header{Participation in the Competition.}
+%
 For participation in SMT-COMP, a solver must be uploaded to StarExec
@@
 \header{System description.}
+%
 As part of the submission, SMT-COMP entrants are \textbf{required} to provide a
 short (1-2 pages) description of the system, which \textbf{must} explicitly
-acknowledge any solver it wraps in case of a \emph{wrapper tool} (see below).
+acknowledge any solver it wraps or is based on in case of a \emph{wrapper} or
+\emph{derived} tool (see above).
 It \emph{should} further include
@@
     references to relevant literature (by the authors or others),
+  \item in case of a \emph{wrapped} or \emph{derived tool}: details of
+    technical innovations by which a wrapper or derived tool expects to improve
+    on the wrapped,
+    solvers or base solver
   \item appropriate acknowledgement of tools other than SMT solvers called by
@@
 
-\header{Wrapper tools.}
-%
-\todo{Giles: update}
-\todo{reword? "one or more SMT solvers of which the author of the wrapper tool
-is not an author"}
-A \emph{wrapper tool} is defined as any solver that calls (or is in
-some other way based on) one or more SMT solvers not written by the
-author of the wrapper tool.  The other solvers are called the
-\emph{wrapped} solvers.  A wrapper tool must explicitly acknowledge
-any solvers that it wraps.  Its system description should make clear
-the technical innovations by which the wrapper tool expects to improve
-on the wrapped solvers.
-
 \header{Attendance.}
 %
-Submitters of an SMT-COMP entrant need not be physically present at
-the competition or the SMT Workshop to participate or win.
+Submitters of an SMT-COMP entrant are not required (but encouraged) to be
+physically present at the competition or the SMT Workshop to participate or
+win.
 

### 2019-04-19 rules/rules19.tex
Rules: Pass over tools

@@
 
-\header{Dates of competition.}
+\header{Dates of Competition.}
 %
@@
 SMT-COMP website as the competition runs.
-
+%
 The organizers reserve the right to prioritize certain competition
@@
 \header{Competition Website.}
-The competition website (\url{www.smtcomp.org}) will be used as the main form of communication for the competition.
-The website will be used to post updates, link to these rules and other relevant information (e.g.
-the benchmarks), and to announce the results.
-We also use the website to archive previous competitions.
-Starting from 2019 we will include the submitted solvers in this archive to allow reproduction of the competition results in the future.
+The competition website (\url{www.smtcomp.org}) will be used as the main form
+of communication for the competition. The website will be used to post updates,
+link to these rules and other relevant information (e.g. the benchmarks), and
+to announce the results. We also use the website to archive previous
+competitions. Starting from 2019 we will include the submitted solvers in this
+archive to allow reproduction of the competition results in the future.
 %
@@
 \header{Tools.}
-The competition uses a number of its own tools/scripts to run the competition.
-We briefly describe these tools.
-Unless stated otherwise the tools are found at \url{https://github.com/SMT-COMP/smt-comp/tree/master/tools}.
+The competition uses a number of tools/scripts to run the competition. In the
+following, we briefly describe these tools. Unless stated otherwise, these
+tools are found at \url{https://github.com/SMT-COMP/smt-comp/tree/master/tools}.
 {\color{red} Some tools have not been released yet.}
 \begin{itemize}
-	\item \textbf{Benchmark Selection.} This script implements the benchmark selection policy described on page~\pageref{benchmark-selection}.
-It takes a seed for the random benchmark selection.
-The same seed is used for all tools requiring randomisation.
-	\item \textbf{Scramber.} This tool is used to scramble benchmarks during the competition to ensure that tools do not rely on syntactic features to identify benchmarks.
-The scramber can be found at \url{https://github.com/SMT-COMP/scrambler}.
-	\item \textbf{Trace Executor.} This tool is used in the interactive track to emulate an on-line interaction between an SMT solver and a client application and is available at \url{https://github.com/SMT-COMP/trace-executor}
-	\item \textbf{Postprocessors.} These are used by StarExec to translate the output of tools to the format required for scoring.
-The postprocessors (per track) are available at \url{https://github.com/SMT-COMP/postprocessors}.
-	\item \textbf{Scoring.} This script implements the scoring computation described on in Section~\ref{sec:scoring}. It also includes the scoring computations used in previous competitions (since 2015).
+  \item \textbf{Benchmark Selection.} We use a script to implement the
+    benchmark selection policy described on page~\pageref{benchmark-selection}.
+    It takes a seed for the random benchmark selection. The same seed is used
+    for all tools requiring randomisation.
+  \item \textbf{Scrambler.} This tool is used to scramble benchmarks during the
+    competition to ensure that tools do not rely on syntactic features to
+    identify benchmarks. The scrambler can be found at
+    \url{https://github.com/SMT-COMP/scrambler}.
+  \item \textbf{Trace Executor.} This tool is used in the \inctrack to emulate
+    an on-line interaction between an SMT solver and a client application and
+    is available at \url{https://github.com/SMT-COMP/trace-executor}
+  \item \textbf{Postprocessors.} These are used by StarExec to translate the
+    output of tools to the format required for scoring. All postprocessors (per
+    track) are available at \url{https://github.com/SMT-COMP/postprocessors}.
+  \item \textbf{Scoring.} We use a script to implement the scoring computation
+    described on in Section~\ref{sec:scoring}. It also includes the scoring
+    computations used in previous competitions (since 2015).
 \end{itemize}

### 2019-04-19 rules/rules19.tex
Rules: Fix

@@
 \header{Competition Website.}
+%
 The competition website (\url{www.smtcomp.org}) will be used as the main form
@@
 archive to allow reproduction of the competition results in the future.
-%
 
 \header{Tools.}
+%
 The competition uses a number of tools/scripts to run the competition. In the
@@
   \item \textbf{Scoring.} We use a script to implement the scoring computation
-    described on in Section~\ref{sec:scoring}. It also includes the scoring
+    described in Section~\ref{sec:scoring}. It also includes the scoring
     computations used in previous competitions (since 2015).

### 2019-04-19 rules/rules19.tex
Minor edits to rules.

--- 2019-04-19 rules/rules19.tex
@@
 SMT-COMP 2019 will have five tracks: the \maintrack (previously: Main Track),
-the incremental track (previously: Application Track), the \ucoretrack,
+the \inctrack (previously: Application Track), the \ucoretrack,
 the (new) \challtrack, and the (new)
@@
     solvers are wrapper tools according to the rules of the competition.
-    Second, we want to encourage documentation of technical improvements that
+    Second, we want to encourage documenting technical improvements that
     lead to the current results.}
@@
   \item {\bf New \mvaltrack for QF\_BV.}
-    This year, we introduce a new experimental \mvaltrack for logic QF\_BV.
+    This year, we introduce a new experimental \mvaltrack for the QF\_BV logic.
     The benchmarks for this track will include all eligible \emph{non-incremental}
@@
   \item {\bf New \challtrack.}
-    This year, we further introduce a new \challtrack.  This track will contain
+    This year, we introduce a new \challtrack.  This track will contain
     new challenging SMT-LIB benchmarks (with an emphasis on industrial
@@
     benchmarks solved within a very low time limit (see item ``New Scores in
-    the \maintrack'').  }
-    \todo{how do we provide information about which benchmarks and which logics?}
+    the \maintrack'').  } See ~\ref{sec:exec:industry-challenge} for the list of
+    benchmark families included in \challtrack for this year.
 
@@
 %
-A solver that can enter SMT-COMP is a tool that allows to
-determine (un)satisfiability of benchmarks from the SMT-LIB benchmark library
+A SMT solver that can enter SMT-COMP is a tool that can
+determine the (un)satisfiability of benchmarks from the SMT-LIB benchmark library
 (\url{http://www.smt-lib.org/benchmarks.shtml}).
@@
 A \emph{wrapper tool} is defined as any solver that calls one or more SMT
-solvers (the \emph{wrapped solvers}) of which the author of the wrapper tool is
-not an author.  Its system description \textbf{must} explicitly acknowledge any
+solvers (the \emph{wrapped solvers}) that do not have the same author as the
+wrapper tool itself. Its system description \textbf{must} explicitly acknowledge any
 solvers that it wraps.  It \emph{should} further make clear technical
@@
 The track will run on challenging industrial benchmarks provided by the community.
+This year, the \challtrack will include all the benchmarks from the \lh{TODO families} families, in the \lh{TODO logics}.
 
@@
 developers before the solver submission deadline.
-
-\todo{Liana - check if we can use the SMT-LIB standard and if so say that we will here, or if we need slight changes state them here.}
 

### 2019-04-19 rules/rules19.tex
Added challenge track logics.

@@
     benchmarks solved within a very low time limit (see item ``New Scores in
-    the \maintrack'').  } See ~\ref{sec:exec:industry-challenge} for the list of
-    benchmark families included in \challtrack for this year.
+    the \maintrack'').  } See ~\ref{sec:exec:industry-challenge} for the logics
+    included in \challtrack for this year.
 
@@
 \todo{time limit}
-The \challtrack will include both incremental and single query benchmarks and it will follow the same rules as the \inctrack and  \maintrack, respectively with two exceptions: benchmark selection and the time limit.
-The track will run on challenging industrial benchmarks provided by the community.
-This year, the \challtrack will include all the benchmarks from the \lh{TODO families} families, in the \lh{TODO logics}.
+The \challtrack will include both incremental and single query benchmarks and
+it will follow the same rules as the \inctrack and  \maintrack, respectively
+with two exceptions: benchmark selection and the time limit. The track will
+run on challenging industrial benchmarks provided by the community. This year,
+the \challtrack will include both incremental and single query benchmarks in the
+following logics QF\_BV, QF\_ABV and QF\_AUFBV. The complete list of benchmarks
+along with instructions on how to access them will be provided on the SMT-COMP
+website as soon as the benchmarks are released.
 

### 2019-04-19 rules/rules19.tex
Rules: First pass over input/output.

@@
 %
-A \emph{wrapper tool} is defined as any solver that calls one or more SMT
-solvers (the \emph{wrapped solvers}) that do not have the same author as the
-wrapper tool itself. Its system description \textbf{must} explicitly acknowledge any
+A \emph{wrapper tool} is defined as any solver that calls one or more other SMT
+solvers (the \emph{wrapped solvers}). Its system description \textbf{must} explicitly acknowledge any
 solvers that it wraps.  It \emph{should} further make clear technical
@@
 A \emph{derived tool} is defined as any solver that is \emph{based on and
-extends} an SMT solver (the \emph{base solver}) not written by the authors of
-the derived tool.  Its system description \textbf{must} explicitly acknowledge
+extends} another SMT solver (the \emph{base solver}).  Its system description
+\textbf{must} explicitly acknowledge
 the solver it is based on and extends.  It \emph{should} further make clear
-technical innovations by which the wrapper tool expects to improve on the
-wrapped solvers.  A derived tool should follow the \emph{naming convention}
+technical innovations by which the derived tool expects to improve on the
+original solver.  A derived tool should follow the \emph{naming convention}
 {[name of base solver]-[my solver name]}.
@@
 %
-In the \maintrack, \mvaltrack, \ucoretrack and \challtrack, a participating
-solver must read a single benchmark script, whose filename is presented as the
-solver's first command-line argument.  In the \inctrack, a trace
-executor will send commands from a benchmark script to the solver's standard
-input channel.
-
-The benchmark script is in the concrete syntax of the SMT-LIB format,
-version~2.6, though with a restricted set of commands.  A benchmark
-script is a text file containing a sequence of SMT-LIB commands that
+In the \emph{\inctrack}, the \emph{trace executor} will send commands from an
+(incremental) benchmark file to the standard input channel of the solver.  In
+\emph{all other tracks}, a participating solver must read a \emph{single}
+benchmark file, whose filename is presented as the first command-line argument
+of the solver.
+
+Benchmark files are in the concrete syntax of the SMT-LIB format
+version~2.6, though with a \emph{restricted} set of commands.  A benchmark
+file is a text file containing a sequence of SMT-LIB commands that
 satisfies the following requirements:
@@
     \begin{enumerate}
-  \item In the \maintrack and \ucoretrack, there may be a single
+      \item In the \textbf{\maintrack} and \textbf{\ucoretrack}, there may be a single
       \akey{(set-option :print-success ...)} command.  Note that
@@
         previous competitions to run without changes.}
-  \item In the incremental track, the \akey{:print-success} option
+      \item In the \textbf{\inctrack}, the \akey{:print-success} option
       must not be disabled.  The trace executor will send an initial
         \akey{(set-option :print-success true)} command to the solver.
+      \item In the \textbf{\ucoretrack}, there is a single \akey{(set-option
+        :produce-unsat-cores true)} command.
     \end{enumerate}
-\item In the \ucoretrack, there is a single \akey{(set-option
-  :produce-unsat-cores true)} command.
-\item The (single) \akey{set-logic} command setting the benchmark's
-  logic is the first command after any \akey{set-option} commands.
-\item The script may contain any number of \akey{set-info} commands.
-\item The script may contain any number of \akey{declare-sort} and
+  \item A (single) \akey{set-logic} command is the \emph{first} command after
+    any \akey{set-option} commands.
+  \item It may contain any number of \akey{set-info} commands.
+  \item It may contain any number of \akey{declare-sort} and
     \akey{define-sort} commands.  All sorts declared or defined with
     these commands must have zero arity.
-\item The script may contain any number of \akey{declare-fun} and
-  \akey{define-fun} commands.
-\item If the benchmark's logic features algebraic datatypes, the
-  script may contain any number of \akey{declare-datatype(s)}
+  \item It may contain any number of \akey{declare-fun} and \akey{define-fun}
     commands.
-\item The script may contain any number of \akey{assert} commands.
-  All formulas in the script belong to the benchmark's logic, with any
-  free symbols declared in the script.
+  \item If the logic features algebraic datatypes, the benchmark file may
+    contain any number of \akey{declare-datatype(s)} commands.
+  \item It may contain any number of \akey{assert} commands.  All formulas in
+    the file belong in the declared logic, with any free symbols declared in
+    the file.
   \item
     \begin{enumerate}
-    \item In all tracks except the \ucoretrack,  named terms (i.e., terms
-      with the \akey{:named} attribute) are not used.
-    \item In the \ucoretrack, top-level assertions may be named.
+      \item In \textbf{all} tracks \textbf{except} the \ucoretrack,  named
+        terms (i.e., terms with the \akey{:named} attribute) are \emph{not}
+        used.
+      \item In the \textbf{\ucoretrack}, top-level assertions may be named.
     \end{enumerate}
@@
     \begin{enumerate}
-  \item In all tracks except the \inctrack, there is exactly one
-    \akey{check-sat} command.
-  \item In the incremental track, there are one or more
+      \item In \textbf{all} tracks \textbf{except} the \inctrack, there is
+        \emph{exactly one} \akey{check-sat} command.
+      \item In the \textbf{\inctrack}, there are one or more
       \akey{check-sat} commands.  There may also be zero or more
@@
     \end{enumerate}
-\item In the \ucoretrack, the \akey{check-sat} command (which is
+  \item In the \textbf{\ucoretrack}, the \akey{check-sat} command (which is
     always issued in an unsatisfiable context) is followed by a single
     \akey{get-unsat-core} command.
-\item In the \mvaltrack, the \akey{check-sat} command (which is
+  \item In the \textbf{\mvaltrack}, the \akey{check-sat} command (which is
     always issued in a satisfiable context) is followed by a single
     \akey{get-model} command.
-\item The script may optionally contain an \akey{exit} command as its
-  last command.  In the incremental track, this command must not be
+  \item It may \emph{optionally} contain an \akey{exit} command as its
+    last command.  In the \textbf{\inctrack}, this command must not be
     omitted.

### 2019-04-19 rules/rules19.tex
Rules: Try different layout for input/output.

--- 2019-04-19 rules/rules19.tex
@@
 
-\newcommand{\akey}[1]{\texttt{#1}}
+\newcommand{\akey}[1]{\textbf{#1}}
+\newcommand{\bkey}[1]{\textbf{\texttt{#1}}}
 
@@
 
-\header{Input and output.}
+\header{Input and Output.}
 %
@@
 file is a text file containing a sequence of SMT-LIB commands that
-satisfies the following requirements:
+satisfies the following \emph{requirements}:
 %
@@
   \item
+    \bkey{(set-option :print-success ...)}
     \begin{enumerate}
-      \item In the \textbf{\maintrack} and \textbf{\ucoretrack}, there may be a single
-      \akey{(set-option :print-success ...)} command.  Note that
-      \texttt{success} outputs are ignored by the post-processor used by
-      the competition.\footnote{SMT-LIB~2.6 requires solvers to produce
-        a \texttt{success} answer after each \akey{set-logic},
-        \akey{declare-sort}, \akey{declare-fun} and \akey{assert}
-        command (among others), unless the option \akey{:print-success}
-        is set to false.  Ignoring the \texttt{success} outputs allows
-        for submitting fully SMT-LIB~2.6 compliant solvers without the
-        need for a wrapper script, while still allowing entrants of
-        previous competitions to run without changes.}
+      \vspace{-1ex}
+      \item In the \textbf{\maintrack} and \textbf{\ucoretrack}, there may be a
+        single \akey{set-option} command.  Note that \texttt{success} outputs
+        are ignored by the post-processor used by the
+        competition.\footnote{SMT-LIB~2.6 requires solvers to produce a
+        \texttt{success} answer after each \akey{set-logic},
+        \akey{declare-sort}, \akey{declare-fun} and \akey{assert} command
+        (among others), unless the option \akey{:print-success} is set to
+        false.  Ignoring the \texttt{success} outputs allows for submitting
+        fully SMT-LIB~2.6 compliant solvers without the need for a wrapper
+        script, while still allowing entrants of previous competitions to run
+        without changes.}
       \item In the \textbf{\inctrack}, the \akey{:print-success} option
@@
     \end{enumerate}
-  \item A (single) \akey{set-logic} command is the \emph{first} command after
+  \item \bkey{(set-logic ...)}\\
+    A (single) \akey{set-logic} command is the \emph{first} command after
     any \akey{set-option} commands.
-  \item It may contain any number of \akey{set-info} commands.
-  \item It may contain any number of \akey{declare-sort} and
-    \akey{define-sort} commands.  All sorts declared or defined with
-    these commands must have zero arity.
-  \item It may contain any number of \akey{declare-fun} and \akey{define-fun}
-    commands.
-  \item If the logic features algebraic datatypes, the benchmark file may
+  \item \bkey{(set-info ...)}\\
+    A benchmark file may contain any number of \akey{set-info} commands.
+  \item \bkey{(declare-sort ...)}\\
+    A benchmark file may contain any number of \akey{declare-sort} and
+    \akey{define-sort} commands.  All sorts declared or defined with these
+    commands must have zero arity.
+  \item \bkey{(declare-fun ...)} and \bkey{(define-fun ...)}\\
+    A benchmark file may contain any number of \akey{declare-fun} and
+    \akey{define-fun} commands.
+  \item \bkey{(declare-datatype ...)} and \bkey{(declare-datatypes ...)}\\
+    If the logic features algebraic datatypes, the benchmark file may
     contain any number of \akey{declare-datatype(s)} commands.
-  \item It may contain any number of \akey{assert} commands.  All formulas in
-    the file belong in the declared logic, with any free symbols declared in
-    the file.
+  \item \bkey{(assert ...)}\\
+    A benchmark file may contain any number of \akey{assert} commands.  All
+    formulas in the file belong in the declared logic, with any free symbols
+    declared in the file.
   \item
+    \bkey{:named}
     \begin{enumerate}
+      \vspace{-1ex}
       \item In \textbf{all} tracks \textbf{except} the \ucoretrack,  named
@@
     \item
+      \bkey{(check-sat)}
       \begin{enumerate}
+        \vspace{-1ex}
         \item In \textbf{all} tracks \textbf{except} the \inctrack, there is
@@
     \end{enumerate}
-  \item In the \textbf{\ucoretrack}, the \akey{check-sat} command (which is
+    \item \bkey{(get-unsat-core)}\\
+    In the \textbf{\ucoretrack}, the \akey{check-sat} command (which is
       always issued in an unsatisfiable context) is followed by a single
       \akey{get-unsat-core} command.
-  \item In the \textbf{\mvaltrack}, the \akey{check-sat} command (which is
+    \item \bkey{(get-model)}\\
+      In the \textbf{\mvaltrack}, the \akey{check-sat} command (which is
       always issued in a satisfiable context) is followed by a single
     \akey{get-model} command.
-  \item It may \emph{optionally} contain an \akey{exit} command as its
+  \item \bkey{(exit)}\\
+    It may \emph{optionally} contain an \akey{exit} command as its
     last command.  In the \textbf{\inctrack}, this command must not be

### 2019-04-19 rules/rules19.tex
Rules: Remove competition-wide score.

@@
 
-  \item {\bf Competition-Wide Scores/Winners.} \todo{}
+  \item {\bf Competition-Wide Recognitions.} \todo{}
 
@@
 \subsection{Incremental Track (Previously: Application Track)}
+\label{sec:exec:app}
 
@@
 because of disagreements).  We define the weight for benchmark~$b$ as
-$\alpha_b = (1 + \log_e F_b) / F_b$.\footnote{See
-  Section~\ref{sec:competition-wide} for a motivating discussion of
-  log scaling.}  We define the \emph{normalized weight} for
+$\alpha_b = (1 + \log_e F_b) / F_b$.  We define the \emph{normalized weight} for
 benchmark~$b$ as $\alpha'_b = \alpha_b / (\sum_{b'} \alpha_{b'})$,
@@
 
-\subsection{Competition-wide scoring (\maintrack)}
-\label{sec:competition-wide}
-
-\todo{Replace notion of competition-wide scoring with a notion of ranking
-based on distance between first and second (based on scoring, and maybe a second
-based on VBS marginal contribution)}
-
-We define a competition-wide metric for the \maintrack, separately for
-parallel and sequential performance, as follows.  Let $N_i$ be the
-total number of benchmarks in division~$i$ that were used in the
-competition (and not removed because of disagreements), and let
-$\langle e_i, n_i, w_i, c_i\rangle$ be a solver's raw score for this
-division (Section~\ref{sec:division-scoring}).  The solver's
-competition-wide raw score is
-%
-$$\sum_i (e_i == 0 \,?\, (n_i/N_i)^2 : -4) \log_e N_i$$
-%
-where the sum is over all competitive divisions into which the solver
-was entered.\footnote{\emph{Rationale:} This metric purposely
-  emphasizes breadth of solver participation---a solver participating
-  in many logics need not be the best in any one of them.  The use of
-  the square in the metric limits this somewhat---a solver still needs
-  to do reasonably well compared to winners to be able to catch up by
-  breadth of participation.  The non-linear metric also gives added
-  weight to completing close to all benchmarks in a division.
-
-  The constant penalty for errors reflects the fact that any error (in
-  a particular division) renders a solver untrustworthy for that
-  division.  The value~$4$ balances the community's strong interest in
-  correct (thoroughly tested) solvers against the risk of stifling
-  innovation: entering a (possibly buggy) solver that can solve all
-  benchmarks into a division has a positive expected value if the
-  probability of a soundness bug is below $\frac{1}{1+4} = 20$\,\%.
-
-  The log scaling is a (somewhat arbitrary) means to adjust the scores
-  for the wide variety of numbers of benchmarks in different
-  divisions.  It seems a reasonable compromise between linearly
-  combining numbers of benchmarks, which would overweigh large
-  divisions, and simply summing the fraction of benchmarks solved,
-  which would overweigh small divisions.
-
-  The metric is also quite simple, and the metric for a solver is
-  independent of the performance of other solvers.  Time is omitted
-  from the metric because it is only of third importance in the
-  regular competition metric, and is difficult to compare across
-  divisions.}  The solver's competition-wide sequential score is
-computed from its sequential division scores
-(Section~\ref{sec:division-scoring}) according to the same formula.
-We will recognize the best three solvers according to these metrics.
-
 \subsection{Other Recognitions \todo{Update}}
@@
   solver implementation team, as measured by the competition-wide
-  metric.
+    metric. \todo{}
 \item \emph{Benchmarks}. Contributors of new benchmarks.
@@
 \begin{itemize}
-\item The best three solvers according to the competition-wide scoring
-  (\maintrack);
 \item the solver that wins the most competitive divisions in the

### 2019-04-19 rules/rules19.tex
Rules: Pass over Single Query Track.

@@
 
-The \maintrack competition will consist of selected benchmarks in each
-of the logic divisions.  Each benchmark script will be presented to
-the solver as its first command-line argument.  The solver is then
-expected to attempt to report on its standard output channel whether
-the formula is satisfiable (\texttt{sat}, in lowercase) or
-unsatisfiable (\texttt{unsat}).  A solver may also report
-\texttt{unknown} to indicate that it cannot determine satisfiability
-of the formula.
-
-The \maintrack competition uses a StarExec post-processor (named
-``SMT-COMP 2019") to accumulate the results.
+\header{Input/Output.}
+This track will consist of selected non-incremental benchmarks in each of
+the logic divisions.  Each benchmark will be presented to the solver as its
+first command-line argument.  The solver is then expected to report on its
+standard output channel whether the formula is satisfiable (\texttt{sat}) or
+unsatisfiable (\texttt{unsat}).  A solver may also report \texttt{unknown} to
+indicate that it cannot determine satisfiability of the formula.
+
+\header{Time Limit.}
+This track will use a wall-clock time limit of 40 minutes per solver/benchmark
+pair.
+
+\header{Postprocessor.}
+This track uses a StarExec post-processor (named \rem{tba}) to accumulate the
+results.
 

### 2019-04-19 rules/rules19.tex
Removed track specific time limits.

@@
 
-\header{Time and memory limits.} \todo{Aina: Move all time and memory limits to the individual sections and forward reference from here}
+\header{Time and memory limits.}
 %
@@
 competition machine, for each given benchmark, up to a fixed
-wall-clock time limit~$T$.  Each processor has 4 cores.  Detailed
+wall-clock time limit~$T$. The individual track description specifies
+the time limit for each track. Each processor has 4 cores.  Detailed
 machine specifications are available on the competition web site.
-
-The time limit~$T$ will be 40~minutes of wall-clock time per solver/benchmark
-pair in the \maintrack, \inctrack and \ucoretrack, \todo{12 hours} in the
-\challtrack, and \todo{40 + 5 as in Unsat core}~minutes in the \mvaltrack \footnote{The time limit may be
-adjusted once we know the number of competition entrants and eligible
-benchmarks.}  Solvers that take more than this time limit will be killed.
-Solvers are allowed to spawn other processes; these will be killed at
-approximately the same time as the first started process.
 
@@
 variables.  See the StarExec user guide for more information.
+
+% The time limit~$T$ will be 40~minutes of wall-clock time per solver/benchmark
+% pair in the \maintrack, \inctrack and \ucoretrack, \todo{12 hours} in the
+% \challtrack, and \todo{40 + 5 as in Unsat core}~minutes in the \mvaltrack \footnote{The time limit may be
+% adjusted once we know the number of competition entrants and eligible
+% benchmarks.}  Solvers that take more than this time limit will be killed.
+% Solvers are allowed to spawn other processes; these will be killed at
+% approximately the same time as the first started process.
 

### 2019-04-19 rules/rules19.tex
Rules: Competitive divisions.

@@
 
-% The time limit~$T$ will be 40~minutes of wall-clock time per solver/benchmark
-% pair in the \maintrack, \inctrack and \ucoretrack, \todo{12 hours} in the
-% \challtrack, and \todo{40 + 5 as in Unsat core}~minutes in the \mvaltrack \footnote{The time limit may be
-% adjusted once we know the number of competition entrants and eligible
-% benchmarks.}  Solvers that take more than this time limit will be killed.
-% Solvers are allowed to spawn other processes; these will be killed at
-% approximately the same time as the first started process.
-
-\subsection{\maintrack (Previously: Main Track)}
-\label{sec:exec:single}
-
-\header{Input/Output.}
-This track will consist of selected non-incremental benchmarks in each of
-the logic divisions.  Each benchmark will be presented to the solver as its
-first command-line argument.  The solver is then expected to report on its
-standard output channel whether the formula is satisfiable (\texttt{sat}) or
-unsatisfiable (\texttt{unsat}).  A solver may also report \texttt{unknown} to
-indicate that it cannot determine satisfiability of the formula.
-
-\header{Time Limit.}
-This track will use a wall-clock time limit of 40 minutes per solver/benchmark
-pair.
-
-\header{Postprocessor.}
-This track uses a StarExec post-processor (named \rem{tba}) to accumulate the
-results.
-
 \header{Aborts and unparsable output.}
@@
 exhausting memory or crashing) \emph{and} do not produce output that
-includes \texttt{sat}, \texttt{unsat} or \texttt{unknown} will be
-considered to have aborted.
+includes \texttt{sat}, \texttt{unsat}, \texttt{unknown} or other track
+specific output as specified in the individual track sections e.g. unsat
+cores or models, will be considered to have aborted.
 
@@
 machines, e.g., over the network.
+
+\subsection{\maintrack (Previously: Main Track)}
+\label{sec:exec:single}
+
+\header{Input/Output.}
+This track will consist of selected non-incremental benchmarks in each of
+the logic divisions.  Each benchmark will be presented to the solver as its
+first command-line argument.  The solver is then expected to report on its
+standard output channel whether the formula is satisfiable (\texttt{sat}) or
+unsatisfiable (\texttt{unsat}).  A solver may also report \texttt{unknown} to
+indicate that it cannot determine satisfiability of the formula.
+
+\header{Time Limit.}
+This track will use a wall-clock time limit of 40 minutes per solver/benchmark
+pair.
+
+\header{Postprocessor.}
+This track uses a StarExec post-processor (named \rem{tba}) to accumulate the
+results.
 
@@
 
-The disk space and memory limits for the incremental track are the
-same as for the \maintrack (see Section~\ref{sec:exec:single}).
-
 \header{Input and output.}
@@
 
+\header{Time Limit.}
+This track will use a wall-clock time limit of 40 minutes per solver/benchmark
+pair.
+
 \subsection{\ucoretrack}
@@
 refuted if the number of checking solvers whose result is \texttt{sat} exceeds
-the number of checking solvers whose result is \texttt{unsat}.  The time limit
-for checking unsatisfiable cores is yet to be determined, but is anticipated to
-be around 5 minutes of wall-clock time per solver.
+the number of checking solvers whose result is \texttt{unsat}.
 
@@
 
+\header{Time Limit.}
+This track will use a wall-clock time limit of 40 minutes per solver/benchmark
+pair. The time limit for checking unsatisfiable cores is yet to be determined, but is anticipated to
+be around 5 minutes of wall-clock time per solver.
+
 \subsection{\challtrack}
@@
 
-\todo{time limit}
 The \challtrack will include both incremental and single query benchmarks and
@@
 
+\header{Time Limit.}
+This track will use a wall-clock time limit of 12 hours per solver/benchmark
+pair.
+
 \subsection{\mvaltrack (experimental)}
@@
 
+\header{Time Limit.}
+This track will use a wall-clock time limit of 40 minutes per solver/benchmark
+pair. The time limit for checking the satisfying assignment is yet to be
+determined, but is anticipated to be around 5 minutes of wall-clock time per solver.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-\todo{Aina: We do not run non-competitive divisions.}
+\header{Competitive Divisions.}
+A division in a track is competitive if at least two substantially
+different solvers (i.e., solvers from two different teams) were
+submitted.  Although the organizers may enter other solvers for
+comparison purposes, only solvers that are explicitly submitted by
+their authors determine whether a division is competitive, and are
+eligible to be designated as winners.
+We will \textbf{not} run \emph{non-competitive} divisions.
 
@@
 
-\subsection{Competitive divisions}
-
-Scores will be computed for all solvers and divisions.  However,
-winners will be declared only for \emph{competitive} divisions.  A
-division in a track is competitive if at least two substantially
-different solvers (i.e., solvers from two different teams) were
-submitted.  Although the organizers may enter other solvers for
-comparison purposes, only solvers that are explicitly submitted by
-their authors determine whether a division is competitive, and are
-eligible to be designated as winners.
-
 \subsection{Benchmark scoring}

### 2019-04-19 rules/rules19.tex
Moved scoring to individual tracks.

@@
 
-\header{Competitive Divisions.}
-A division in a track is competitive if at least two substantially
-different solvers (i.e., solvers from two different teams) were
-submitted.  Although the organizers may enter other solvers for
-comparison purposes, only solvers that are explicitly submitted by
-their authors determine whether a division is competitive, and are
-eligible to be designated as winners.
-We will \textbf{not} run \emph{non-competitive} divisions.
+\todo{Aina: We do not run non-competitive divisions.}
 
@@
 
+\subsection{Competitive divisions}
+
+Scores will be computed for all solvers and divisions.  However,
+winners will be declared only for \emph{competitive} divisions.  A
+division in a track is competitive if at least two substantially
+different solvers (i.e., solvers from two different teams) were
+submitted.  Although the organizers may enter other solvers for
+comparison purposes, only solvers that are explicitly submitted by
+their authors determine whether a division is competitive, and are
+eligible to be designated as winners.
+
 \subsection{Benchmark scoring}

### 2019-04-19 rules/rules19.tex
Rules: Benchmark scoring.

--- 2019-04-19 rules/rules19.tex
@@
 
-A solver's \emph{parallel performance} for each benchmark is a quadruple $\langle
-e, n, w, c\rangle$, with $e \in \{0, 1\}$ the number of erroneous
-results (usually~$e = 0$), $0 \leq n \leq N$ the number of correct
-results,\footnote{Here, $N$ is the number of \akey{check-sat} commands
-  in the benchmark.  Recall that \maintrack benchmarks have just one
-  \akey{check-sat} command; incremental track benchmarks may have
-  multiple \akey{check-sat} commands.} $w \in [0,T]$ the (real-valued)
-wall-clock time in seconds, and $c \in [0, 4T]$ the (real-valued) CPU
-time in seconds, measured across all cores and sub-processes, until
-the solver process terminates.
-
-\header{\maintrack.} More specifically, for the \maintrack, we have
-%
+The \textbf{parallel benchmark score} of a solver is a quadruple $\langle
+e, n, w, c\rangle$, with
+\begin{itemize}[noitemsep]
+  \vspace{-1ex}
+  \item \makebox[5em][l]{$e \in \{0, 1\}$}
+    number of erroneous results (usually~$e = 0$)
+  \item \makebox[5em][l]{$0 \leq n \leq N$}
+    number of correct results (resp.~\emph{reduction} for the \ucoretrack)
+  \item \makebox[5em][l]{$w \in [0,T]$}
+    wall-clock time in seconds (real-valued)
+  \item \makebox[5em][l]{$c \in [0, 4T]$}
+    CPU time in seconds (real-valued)
+\end{itemize}
+
+\header{Error Score ($\mathbf{e}$).}
+For the \maintrack, \inctrack and \challtrack, $e$ is the number of returned
+statuses that disagree with the given expected status (as described above,
+disagreements on benchmarks with unknown status lead to the benchmark being
+disregarded). For the \ucoretrack, $e$ includes, in addition, the number of
+returned unsat cores that are ill-formed or are not, in fact, unsatisfiable (as
+validated by a selection of other solvers selected by organizers).  For the
+\mvaltrack, $e$ includes, in addition, the number of returned models that are
+ill-formed or not full satisfiable models.
+
+\header{Correctly Solved Score ($\mathbf{n}$).}
+For the \maintrack, \inctrack, \challtrack and \mvaltrack,
+$N$ is defined as the number of \akey{check-sat} commands, and
+$n$ is defined as the number of correct results.
+For the \ucoretrack, $N$ is defined as the number of named top-level assertions,
+and $n$ is defined as the \emph{reduction}, i.e., the difference between $N$
+and the size of the unsat core.
+
+\header{Wall-Clock Time Score ($\mathbf{w}$).}
+The (real-valued) wall-clock time in seconds, until time limit $T$ or the
+solver process terminates.
+
+\header{CPU Time Score ($\mathbf{c}$).}
+The (real-valued) CPU time in seconds, measured across all cores and
+sub-processes, until time limit $4T$ or the solver process terminates.
+
+\subsubsection{Sequential Benchmark Score}
+\label{sec:sequential}
+
+The parallel score as defined above favors parallel solvers, which may utilize
+all available processor cores.  To evaluate sequential performance, we derive a
+\emph{sequential score} by imposing a (virtual) CPU time limit equal to the
+wall-clock time limit~$T$.  A solver result is taken into consideration for the
+sequential score only if the solver process terminates within this CPU time
+limit.  More specifically, for a given parallel performance $\langle e, n, w,
+c\rangle$, the corresponding sequential performance is defined as~$\langle e_S,
+n_S, c_S\rangle$, where
 \begin{itemize}
-\item $e=0$, $n=0$ if the solver aborts without a response, or the
-  result of the \akey{check-sat} command is \texttt{unknown},
-\item $e=0$, $n=1$ if the result of the \akey{check-sat} command is
-  \texttt{sat} or \texttt{unsat}, and the result either agrees with
-  the benchmark status or the benchmark status is unknown,\footnote{If
-    the benchmark status is unknown, we thus treat the solver's answer
-    as correct.  Disagreements between different solvers on benchmarks
-    with unknown status are governed in
+\item $e_S = 0$ and $n_S = 0$ if $c > T$, and $e_S = e$ and $n_S = n$
+  otherwise,
+\item $c_S = \min\ \{c, T\}$.\footnote{Under this
+  measure, a solver should not benefit from using multiple processor
+  cores.  Conceptually, the sequential performance should be (nearly)
+  unchanged if the solver was run on a single-core processor, up to a
+  time limit of~$T$.}
+\end{itemize}
+
+\subsubsection{\maintrack and \challtrack.}
+  For the \maintrack and \challtrack, the error score $e$ and the correctly
+  solved score $n$ are defined as
+  \begin{itemize}
+  \item $e=0$ and $n=0$ if the solver
+    \begin{itemize}[noitemsep,nolistsep]
+      \item aborts without a response, or
+      \item  the result of the \akey{check-sat} command is \texttt{unknown},
+    \end{itemize}
+  \item $e=0$ and $n=1$ if the result of the \akey{check-sat} command is
+      \texttt{sat} or \texttt{unsat} and either
+    \begin{itemize}[noitemsep,nolistsep]
+      \item agrees with the benchmark status,
+      \item or the benchmark status
+        is unknown,\footnote{If the benchmark status is unknown, we thus treat
+        the solver's answer as correct.  Disagreements between different
+        solvers on benchmarks with unknown status are governed in
         Section~\ref{sec:division-scoring}.}
-\item $e=1$, $n=0$ if the result of the \akey{check-sat} command is
+    \end{itemize}
+  \item $e=1$ and $n=0$ if the result of the \akey{check-sat} command is
     incorrect.
@@
 
-\header{Incremental Track.}
+\subsubsection{Incremental Track.}
 %
@@
 or \akey{pop} commands might also entail a reasonable amount of
-processing.  For the incremental track, we have
+processing.  For the \inctrack, we have
 \begin{itemize}
-\item $e=1$, $n=0$ if the solver returns an incorrect result for any
+\item $e=1$ and $n=0$ if the solver returns an incorrect result for any
   \akey{check-sat} command within the time limit,
-\item otherwise, $e=0$, and $n$ is the number of correct results for
+\item otherwise, $e=0$ and $n$ is the number of correct results for
   \akey{check-sat} commands returned by the solver before the time
@@
 
-\header{\ucoretrack.}
-%
-For the \ucoretrack, we instead have $0 \leq n \leq A$, where~$A$
-is the number of named top-level assertions in the benchmark, and
+\subsubsection{\ucoretrack.}
+  For the \ucoretrack, the error score $e$ and the correctly solved score $n$
+  are defined as
   \begin{itemize}
-\item $e=0$, $n=0$ if the solver aborts without a response, or the
-  result of the \akey{check-sat} command is \texttt{unknown},
-\item $e=1$, $n=0$ if the result is erroneous according to
+  \item $e=0$ and $n=0$ if the solver
+    \begin{itemize}[noitemsep,nolistsep]
+      \item aborts without a response, or
+      \item the result of the \akey{check-sat} command is \texttt{unknown},
+    \end{itemize}
+  \item $e=1$and  $n=0$ if the result is erroneous according to
     Section~\ref{sec:exec:unsat-core},
-\item otherwise, $e=0$, and $n$ is the reduction in the number of
-  formulas, i.e., $n = A$ minus the number of formula names in the
+  \item otherwise, $e=0$ and $n$ is the \emph{reduction} in the number of
+    formulas, i.e., $n = N$ minus the number of formula names in the
     reported unsatisfiable core.
-\end{itemize}
-
-\subsection{Sequential Performance (\maintrack)}
-\label{sec:sequential}
-
-\iffalse
-SMT-COMP has traditionally emphasized sequential performance (i.e.,
-CPU time) over parallel performance (i.e., wall-clock time).  StarExec
-measures both, and we intend to recognize both best sequential and
-best parallel solvers in all competitive \maintrack divisions.
-\fi
-
-The parallel performance, as defined in Section~\ref{sec:benchmark-scoring},
-favors parallel solvers, which may utilize all available processor
-cores.  To evaluate sequential performance, we derive a
-\emph{sequential performance} by imposing a (virtual) CPU time limit equal
-to the wall-clock time limit~$T$.  A solver result is taken into
-consideration for the sequential performance only if the solver process
-terminates within this CPU time limit.  More specifically, for a given
-parallel performance $\langle e, n, w, c\rangle$, the corresponding sequential
-performance is defined as~$\langle e_S, n_S, c_S\rangle$, where
-\begin{itemize}
-\item $e_S = 0$ and $n_S = 0$ if $c > T$, $e_S = e$ and $n_S = n$
-  otherwise,
-\item $c_S = \min\ \{c, T\}$.\footnote{\emph{Rationale:} Under this
-  measure, a solver should not benefit from using multiple processor
-  cores.  Conceptually, the sequential performance should be (nearly)
-  unchanged if the solver was run on a single-core processor, up to a
-  time limit of~$T$.}
   \end{itemize}

### 2019-04-19 rules/rules19.tex
Rules: Clean up

@@
     benchmarks solved within a very low time limit (see item ``New Scores in
-    the \maintrack'').  } See ~\ref{sec:exec:industry-challenge} for the logics
-    included in \challtrack for this year.
+    the \maintrack''). See Section~\ref{sec:exec:industry-challenge} for the
+    logics included in the \challtrack for this year. }
 
@@
   \item {\bf Competition-Wide Recognitions.} \todo{}
-
-  \item {\bf Problems with Evaluation Scripts.} \todo{Explain what was the
-    problem and what has been fixed, talk about notion of benchmark family.}
 
@@
     omitted.
-  \item No other commands besides the ones just mentioned may be used.
+  \item \textbf{No other commands} besides the ones just mentioned may be used.
 \end{enumerate}
@@
 
-\section{Scoring \todo{update}}
+\section{Scoring}
 \label{sec:scoring}
@@
 
-\subsection{Division scoring}
+\subsection{Division scoring \todo{update}}
 \label{sec:division-scoring}

### 2019-04-19 rules/rules19.tex
Fixed the text on removal of easy benchmarks.

@@
     remove all benchmarks that were solved by all solvers (including the
-  non-competitive solvers) in the 2018 SMT competition.
+        non-competitive solvers) in less than one second in the 2018 SMT
+        competition.
 \item \emph{Cap the number of instances in a division.} The competition

### 2019-04-19 rules/rules19.tex
Rules: Fix and improve input/output.

@@
 
-\newcommand{\akey}[1]{\textbf{#1}}
-\newcommand{\bkey}[1]{\textbf{\texttt{#1}}}
+\newcommand{\akey}[1]{\textbf{#1}\xspace}
+\newcommand{\bkey}[1]{\textbf{{#1}}\xspace}
 
@@
     solved by all solvers (including non-competing solvers) in this
-    division in under 1 second during last year's competition.
+    division in under one second in last year's competition.
     \rationale{Evaluating solvers on all eligible benchmarks in SMT-LIB
     makes results more predictable and seems to be more of an evaluation
-    than a competition.  In the Main track of last year's competition,
+    than a competition.  In the Main track last year,
     78\% of the 258,741 benchmarks were solved by all supported solvers
@@
     is available at \url{https://github.com/SMT-COMP/trace-executor}
-  \item \textbf{Postprocessors.} These are used by StarExec to translate the
-    output of tools to the format required for scoring. All postprocessors (per
+  \item \textbf{Post-Processors.} These are used by StarExec to translate the
+    output of tools to the format required for scoring. All post-processors (per
     track) are available at \url{https://github.com/SMT-COMP/postprocessors}.
@@
 %
-\begin{enumerate}
+\begin{itemize}
+  \item \bkey{(set-logic ...)}\\
+    A (single) \akey{set-logic} command is the \emph{first} command after
+    any \akey{set-option} commands.
+  \item \bkey{(set-info ...)}\\
+    A benchmark file may contain any number of \akey{set-info} commands.
   \item
     \bkey{(set-option :print-success ...)}
-    \begin{enumerate}
+    \begin{enumerate}[label=(\alph*)]
       \vspace{-1ex}
-      \item In the \textbf{\maintrack} and \textbf{\ucoretrack}, there may be a
-        single \akey{set-option} command.  Note that \texttt{success} outputs
-        are ignored by the post-processor used by the
-        competition.\footnote{SMT-LIB~2.6 requires solvers to produce a
-        \texttt{success} answer after each \akey{set-logic},
+    \item In the \emph{\maintrack}, \emph{\challtrack}, \emph{\mvaltrack} and
+        \emph{\ucoretrack}, there may be a single \akey{set-option} command.
+        Note that \texttt{success} outputs are ignored by the post-processors
+        used by the competition.\footnote{SMT-LIB~2.6 requires solvers to
+        produce a \texttt{success} answer after each \akey{set-logic},
         \akey{declare-sort}, \akey{declare-fun} and \akey{assert} command
@@
         without changes.}
-      \item In the \textbf{\inctrack}, the \akey{:print-success} option
+      \item In the \emph{\inctrack}, the \akey{:print-success} option
         must not be disabled.  The trace executor will send an initial
         \akey{(set-option :print-success true)} command to the solver.
-      \item In the \textbf{\ucoretrack}, there is a single \akey{(set-option
-        :produce-unsat-cores true)} command.
+      \item In the \emph{\mvaltrack}, a benchmark file contains a single
+        \akey{(set-option :produce-models true)} command.
+      \item In the \emph{\ucoretrack}, a benchmark file contains a single
+        \akey{(set-option :produce-unsat-cores true)} command.
     \end{enumerate}
-  \item \bkey{(set-logic ...)}\\
-    A (single) \akey{set-logic} command is the \emph{first} command after
-    any \akey{set-option} commands.
-  \item \bkey{(set-info ...)}\\
-    A benchmark file may contain any number of \akey{set-info} commands.
   \item \bkey{(declare-sort ...)}\\
@@
     \bkey{:named}
-    \begin{enumerate}
+    \begin{enumerate}[label=(\alph*)]
       \vspace{-1ex}
-      \item In \textbf{all} tracks \textbf{except} the \ucoretrack,  named
+      \item In \emph{all} tracks \emph{except} the \ucoretrack,  named
         terms (i.e., terms with the \akey{:named} attribute) are \emph{not}
         used.
-      \item In the \textbf{\ucoretrack}, top-level assertions may be named.
+      \item In the \emph{\ucoretrack}, top-level assertions may be named.
     \end{enumerate}
@@
       \bkey{(check-sat)}
-      \begin{enumerate}
+      \begin{enumerate}[label=(\alph*)]
         \vspace{-1ex}
-        \item In \textbf{all} tracks \textbf{except} the \inctrack, there is
+        \item In \emph{all} tracks \emph{except} the \inctrack, there is
           \emph{exactly one} \akey{check-sat} command.
-        \item In the \textbf{\inctrack}, there are one or more
+        \item In the \emph{\inctrack}, there are one or more
         \akey{check-sat} commands.  There may also be zero or more
-        \akey{push 1} commands, and zero or more \akey{pop 1} commands,
+        \akey{(push 1)} commands, and zero or more \akey{(pop 1)} commands,
         consistent with the use of those commands in the SMT-LIB standard.
@@
     \item \bkey{(get-unsat-core)}\\
-    In the \textbf{\ucoretrack}, the \akey{check-sat} command (which is
+      In the \emph{\ucoretrack}, the \akey{check-sat} command (which is
       always issued in an unsatisfiable context) is followed by a single
@@
     \item \bkey{(get-model)}\\
-      In the \textbf{\mvaltrack}, the \akey{check-sat} command (which is
+      In the \emph{\mvaltrack}, the \akey{check-sat} command (which is
       always issued in a satisfiable context) is followed by a single
@@
     It may \emph{optionally} contain an \akey{exit} command as its
-    last command.  In the \textbf{\inctrack}, this command must not be
+    last command.  In the \emph{\inctrack}, this command must not be
     omitted.
   \item \textbf{No other commands} besides the ones just mentioned may be used.
-\end{enumerate}
+\end{itemize}
 %
@@
 
-\header{Postprocessor.}
+\header{Post-Processor.}
 This track uses a StarExec post-processor (named \rem{tba}) to accumulate the

### 2019-04-19 rules/rules19.tex
Rules: Add pageref for time limit reference.
Rules: Move challenge track

@@
 competition machine, for each given benchmark, up to a fixed
-wall-clock time limit~$T$. The individual track description specifies
+wall-clock time limit~$T$. The individual track descriptions on
+pages~\pageref{sec:exec:single}-\pageref{sec:exec:model} specify
 the time limit for each track. Each processor has 4 cores.  Detailed
@@
 
+\subsection{\challtrack}
+\label{sec:exec:industry-challenge}
+
+The \challtrack will include both non-incremental and incremental benchmarks and
+it will follow the same rules as the \inctrack and  \maintrack, respectively
+with two exceptions: benchmark selection and the time limit. The track will
+run on challenging industrial benchmarks provided by the community. This year,
+the \challtrack will include both incremental and single query benchmarks in the
+following logics QF\_BV, QF\_ABV and QF\_AUFBV. The complete list of benchmarks
+along with instructions on how to access them will be provided on the SMT-COMP
+website as soon as the benchmarks are released.
+
+\header{Time Limit.}
+This track will use a wall-clock time limit of 12 hours per solver/benchmark
+pair.
+
 \subsection{\ucoretrack}
@@
 be around 5 minutes of wall-clock time per solver.
-
-\subsection{\challtrack}
-\label{sec:exec:industry-challenge}
-
-The \challtrack will include both incremental and single query benchmarks and
-it will follow the same rules as the \inctrack and  \maintrack, respectively
-with two exceptions: benchmark selection and the time limit. The track will
-run on challenging industrial benchmarks provided by the community. This year,
-the \challtrack will include both incremental and single query benchmarks in the
-following logics QF\_BV, QF\_ABV and QF\_AUFBV. The complete list of benchmarks
-along with instructions on how to access them will be provided on the SMT-COMP
-website as soon as the benchmarks are released.
-
-\header{Time Limit.}
-This track will use a wall-clock time limit of 12 hours per solver/benchmark
-pair.
 

### 2019-04-19 rules/rules19.tex
Rules: More in tracks.

@@
 
-\header{Input/Output.}
-This track will consist of selected non-incremental benchmarks in each of
-the logic divisions.  Each benchmark will be presented to the solver as its
-first command-line argument.  The solver is then expected to report on its
-standard output channel whether the formula is satisfiable (\texttt{sat}) or
-unsatisfiable (\texttt{unsat}).  A solver may also report \texttt{unknown} to
-indicate that it cannot determine satisfiability of the formula.
+The \maintrack track will consist of selected non-incremental benchmarks in
+each of the competitive logic divisions.  Each benchmark will be presented to
+the solver as its first command-line argument.  The solver is then expected to
+report on its standard output channel whether the formula is satisfiable
+(\texttt{sat}) or unsatisfiable (\texttt{unsat}).  A solver may also report
+\texttt{unknown} to indicate that it cannot determine satisfiability of the
+formula.
+
+\header{Benchmark Selection.} See page~\pageref{benchmark-selection}.
 
@@
 
+\header{Post-Processor.}
+This track uses the post-processor at \rem{link tba} to accumulate the results.
+
 \subsection{\challtrack}
@@
 
-The \challtrack will include both non-incremental and incremental benchmarks and
-it will follow the same rules as the \inctrack and  \maintrack, respectively
-with two exceptions: benchmark selection and the time limit. The track will
-run on challenging industrial benchmarks provided by the community. This year,
-the \challtrack will include both incremental and single query benchmarks in the
-following logics QF\_BV, QF\_ABV and QF\_AUFBV. The complete list of benchmarks
-along with instructions on how to access them will be provided on the SMT-COMP
-website as soon as the benchmarks are released.
+The \challtrack will include both non-incremental and incremental benchmarks.
+It will follow the same rules as the \maintrack and \inctrack, respectively,
+with two exceptions: benchmark selection and the time limit.
+
+\header{Benchmark Selection.}
+This track will run on challenging industrial benchmarks provided by the
+community. This year, the \challtrack will include the complete set of provided
+benchmarks dedicated to this track, which consist of both incremental and
+single query benchmarks in the logics QF\_BV, QF\_ABV and QF\_AUFBV. The
+complete list of benchmarks along with instructions on how to access them will
+be provided on the SMT-COMP website as soon as the benchmark library is
+released.
 
@@
 pair.
+
+\header{Post-Processor.}
+This track uses the post-processors from the \maintrack (for non-incremental
+benchmarks) and the \inctrack (for incremental benchmarks) to accumulate the
+results.
 
@@
 The competition will use a large subset of SMT-LIB benchmarks, with some
-guarantees on including new benchmarks.  In all tracks the following
-process will be used for culling the benchmark pool.
+guarantees on including new benchmarks.  In \textbf{all} tracks \textbf{except}
+the \challtrack, the following selection process will be used.
 \begin{enumerate}

### 2019-04-19 rules/rules19.tex
fix a todo

@@
 made public.
-\todo{Giles: Include licence information - minimum requirement: licence must allow to run the binary for evaluation purposes}
-\an{intro of the section maybe, we should add there that solvers will be archived on the website and so on.
+Solvers will be made publicly available after the competition and it is a minimum licence requirement that (i) solvers can be distributed in this way, and (ii) all submitted solvers may be freely used for academic evaluation purposes.
+
+%\an{intro of the section maybe, we should add there that solvers will be archived on the website and so on.
 Interestingly, we replied to the reviewer in the report that the solvers are publicly available in the StarExec space when asked about reproducability, but in the past it was never defined under which terms.}

### 2019-04-19 rules/rules19.tex
Rules: More in Unsat-Core Track.

@@
 \newcommand{\inctrack}{Incremental Track\xspace}
-\newcommand{\ucoretrack}{Unsat Core Track\xspace}
-\newcommand{\mvaltrack}{Model Validation Track\xspace}
-\newcommand{\challtrack}{Industry Challenge Track\xspace}
+\newcommand{\ucoretrack}{Unsat-Core Track\xspace}
+\newcommand{\mvaltrack}{Model-Validation Track\xspace}
+\newcommand{\challtrack}{Industry-Challenge Track\xspace}
 
@@
 
-\header{Tools.}
+\header{Tools.} \label{tools}
 The competition uses a number of tools/scripts to run the competition. In the
@@
 parsed by a (publicly available) \emph{trace executor},
-which serves the following purposes: \begin{itemize} \item it simulates the
-online interaction by sending single queries to the SMT solver (through stdin);
-\item it prevents ``look-ahead'' behaviors of SMT solvers;
-\item it records time and answers for each command;
-\item it guarantees a fair execution for all solvers by abstracting
+which serves the following purposes:
+
+\begin{itemize}
+  \item simulating online interaction by sending single queries to the SMT
+    solver (through stdin),
+  \item preventing ``look-ahead'' behaviors of SMT solvers,
+  \item recording time and answers for each command,
+  \item guaranteeing a fair execution for all solvers by abstracting
   from any possible crash, misbehavior, etc.\ that might happen in the
@@
 \header{Input and output.}
-%
 Participating solvers will be connected to a trace executor, which
@@
 Section~\ref{sec:logistics}.
-
+%
 Solvers must respond to each command sent by the trace executor with
@@
 
+\header{Trace Executor.} This track will use the trace executor at \rem{link tba}
+to execute solvers on an incremental benchmark file.
+
 \header{Post-Processor.}
-This track uses the post-processor at \rem{link tba} to accumulate the results.
+This track will use the post-processor at \rem{link tba} to accumulate the
+results.
 
@@
 \header{Post-Processor.}
-This track uses the post-processors from the \maintrack (for non-incremental
+This track uses the post-processors from the \maintrack (for non-incremen-tal
 benchmarks) and the \inctrack (for incremental benchmarks) to accumulate the
@@
 
-The \ucoretrack will evaluate the capability of solvers to
-generate unsatisfiable cores (for problems that are known to be
-unsatisfiable).  Solvers will be measured by the smallness of the
-unsatisfiable core they return.
-
-The SMT-LIB language accommodates this functionality by providing two
-features: the ability to name top-level (asserted) formulas, and the
-ability to request an unsatisfiable core after a \akey{check-sat}
-command returns \texttt{unsat}.  The unsatisfiable core that is
-returned must consist of a list of names of formulas, in the format
-prescribed by the SMT-LIB standard.
-
+The \ucoretrack will evaluate the capability of solvers to generate
+unsatisfiable cores.  Performance of solvers will be measured by the smallness
+of the unsatisfiable core they provide.
+
+\header{Input/Output.}
+The SMT-LIB language provides a command \akey{(get-unsat-core)}, which asks
+a solver to identify an unsatisfiable core after a \akey{check-sat}
+command returns \texttt{unsat}.
+This unsat core must consist of a list of all named top-level
+assertions in the format prescribed by the SMT-LIB standard.
+%
+Solvers must respond to each command in the benchmark script with the
+answers defined in the SMT-LIB format specification.  In particular,
+solvers that respond \texttt{unknown} to the \akey{check-sat} command
+must respond with an error to the following \akey{get-unsat-core}
+command.
+
+\header{Result.}
 The result of a solver is considered erroneous if the response to the
@@
 
-In order to perform this unsatisfiability check, the organizers will use a
-selection of SMT solvers that participate in the \maintrack of this
-competition.  For each division, the organizers will use only solvers that have
-been sound (i.e., not produced any erroneous result) in the \maintrack for
-this division.  The unsatisfiability of a produced unsatisfiable core is
-refuted if the number of checking solvers whose result is \texttt{sat} exceeds
-the number of checking solvers whose result is \texttt{unsat}.
-
-Solvers must respond to each command in the benchmark script with the
-answers defined in the SMT-LIB format specification.  In particular,
-solvers that respond \texttt{unknown} to the \akey{check-sat} command
-must respond with an error to the following \akey{get-unsat-core}
-command.
+\header{Validation.}
+The organizers will use a selection of SMT solvers (the \emph{validation
+solvers}) that participate in the \maintrack of this competition in order to
+validate if a given unsat core is indeed unsatisfiable.  For each division, the
+organizers will use only solvers that have been sound (i.e., they did not
+produce any erroneous result) in the \maintrack for this division.  The
+unsatisfiability of an unsat core is refuted if the number of validation
+solvers whose result is \texttt{sat} exceeds the number of checking solvers
+whose result is \texttt{unsat}.
 
@@
 This track will use a wall-clock time limit of 40 minutes per solver/benchmark
-pair. The time limit for checking unsatisfiable cores is yet to be determined, but is anticipated to
-be around 5 minutes of wall-clock time per solver.
+pair. The time limit for checking unsatisfiable cores is yet to be determined,
+but is anticipated to be around 5 minutes of wall-clock time per solver.
+
+\header{Post-Processor.}
+This track will use the post-processor at \rem{link tba} to accumulate the
+results.
 

### 2019-04-19 rules/rules19.tex
Rules: Fix
Rules: More in Model-Validation Track.

@@
 
-\header{Time and memory limits.}
+\header{Time and Memory Limits.}
 %
@@
 
-\header{Aborts and unparsable output.}
-%
-Any \texttt{success} outputs will be ignored.  Solvers that exit
-before the time limit without reporting a result (e.g., due to
-exhausting memory or crashing) \emph{and} do not produce output that
-includes \texttt{sat}, \texttt{unsat}, \texttt{unknown} or other track
-specific output as specified in the individual track sections e.g. unsat
-cores or models, will be considered to have aborted.
-
-\header{Persistent state.}
+\header{Aborts and Unparsable Output.}
+%
+In all tracks except the \inctrack, any \texttt{success} outputs will be
+ignored.  Solvers that exit before the time limit without reporting a result
+(e.g., due to exhausting memory or crashing) \emph{and} do not produce output
+that includes \texttt{sat}, \texttt{unsat}, \texttt{unknown} or other track
+specific output as specified in the individual track sections e.g. unsat cores
+or models, will be considered to have aborted.
+
+\header{Persistent State.}
 %
@@
 The \ucoretrack will evaluate the capability of solvers to generate
-unsatisfiable cores.  Performance of solvers will be measured by the smallness
-of the unsatisfiable core they provide.
+unsatisfiable cores.  Performance of solvers will be measured by correctness
+and size of the unsatisfiable core they provide.
+
+\header{Benchmark Selection.}
+This track will run on all benchmarks from the \maintrack with status
+\texttt{unsat}.
 
@@
 \label{sec:exec:model}
-The \mvaltrack will evaluate the solver's ability to produce models
-for satisfiable problems. This track will run on all QF\_BV satisfiable benchmarks
-from the \maintrack.
-
-The SMT-LIB language accommodates this functionality by providing the ability to
-request a satisfying model after a \akey{check-sat} command returns \texttt{sat}.
-The satisfiable core that is returned must consist of definitions specifying all
-and only the current user-declared function symbols, in the format prescribed by
-the SMT-LIB standard.
-
+The \mvaltrack will evaluate the capability of solvers to produce models for
+satisfiable problems.  Performance of solvers will be measured by correctness
+and well-formedness of the model they provide.
+
+\header{Benchmark Selection.}
+This track will run on all QF\_BV benchmarks from the \maintrack with status
+\texttt{sat}.
+
+\header{Input/Output.}
+The SMT-LIB language provides a command \akey{(get-model)} to request a
+satisfying model after a \akey{check-sat} command returns \texttt{sat}.  This
+model must consist of definitions specifying all and only the current
+user-declared function symbols, in the format prescribed by the SMT-LIB
+standard.
+
+\header{Result.}
 The result of a solver is considered erroneous if the response to the
 \akey{checks-sat} command is \texttt{unsat}, if the returned model is not
-well-formed (e.g. does not provide a definition for all the user-declared function
-symbols), or if the returned model does not satisfy the benchmark.
-
-In order to check that the model satisfies the benchmark, the organizers will use
-a model validating tool. The organizers will make this tool available to solver
-developers before the solver submission deadline.
+well-formed (e.g. does not provide a definition for all the user-declared
+function symbols), or if the returned model does not satisfy the benchmark.
+
+\header{Validation.}
+In order to check that the model satisfies the benchmark, the organizers will
+use a model validating tool. The organizers will make this tool available to
+solver developers before the solver submission deadline.
 
@@
 pair. The time limit for checking the satisfying assignment is yet to be
-determined, but is anticipated to be around 5 minutes of wall-clock time per solver.
+determined, but is anticipated to be around 5 minutes of wall-clock time per
+solver.
+
+\header{Post-Processor.}
+This track will use the post-processor at \rem{link tba} to accumulate the
+results.
 

### 2019-04-19 rules/rules19.tex
Rules: Fix

@@
 \header{Benchmark Selection.}
-This track will run on all benchmarks from the \maintrack with status
-\texttt{unsat}.
+This track will run on all \emph{unsatisfiable} benchmarks from the \maintrack.
 
@@
 \header{Benchmark Selection.}
-This track will run on all QF\_BV benchmarks from the \maintrack with status
-\texttt{sat}.
+This experimental track only has one division, QF\_BV. It will run on all
+\emph{satisfiable} benchmarks from this division in the \maintrack.
 

### 2019-04-19 rules/rules19.tex
Rules: Pass over first half of benchmarks section.

@@
 \header{Benchmark Selection.}
-This track will run on all \emph{unsatisfiable} benchmarks from the \maintrack.
+This track will run on all \emph{unsatisfiable} benchmarks from the \maintrack,
+modified to use named top-level assertions of the form \akey{(assert (! t
+:named f ))}.
+\todo{what if removing all benchmarks with one assertion doesn't leave enough benchmarks in a division?}
 
@@
 
+\header{Division}
+Within each track there are multiple divisions, and each division selects
+benchmarks from a specific SMT-LIB logic in the SMT-LIB benchmark library.
+
 \header{Competitive Divisions.}
@@
 \header{Benchmark sources.}
-%
-Benchmarks for each division will be drawn from the SMT-LIB benchmark
-library.  The \maintrack will use a subset of all
-\emph{non-incremental} benchmarks; the incremental track will use a
-subset of all \emph{incremental} benchmarks.  The \ucoretrack
-will use unsatisfiable \maintrack benchmarks, modified to use named
-top-level assertions.
+Benchmarks for each division will be drawn from the SMT-LIB benchmark library.
+The \maintrack will use a subset of all \emph{non-incremental} benchmarks and
+the \inctrack will use a subset of all \emph{incremental} benchmarks. The
+\challtrack will use all incremental and non-incremental benchmarks dedicated
+to this track by their submitters. The \ucoretrack will use all unsatisfiable
+\maintrack benchmarks, modified to use named top-level assertions.  The
+\mvaltrack will use all satisfiable \maintrack benchmarks from the QF\_BV
+division.
 
 \header{New benchmarks.}
-%
 The deadline for submission of new benchmarks is {\bf March~1, 2019}.
@@
 \header{Benchmark demographics.}
-%
 The set of all SMT-LIB benchmarks in a given division can be naturally
@@
 \header{Benchmark selection.} \label{benchmark-selection}
-%
 The competition will use a large subset of SMT-LIB benchmarks, with some
@@
 \begin{enumerate}
-\item \emph{Remove inappropriate benchmarks.} The competition
+\item \emph{Remove inappropriate benchmarks.} The
   organizers may remove benchmarks that are deemed inappropriate or
@@
   of coming from or having some intended application outside SMT.
-\item \emph{Remove easy benchmarks.} The competition organizers will
-    remove all benchmarks that were solved by all solvers (including the
-        non-competitive solvers) in less than one second in the 2018 SMT
-        competition.
-\item \emph{Cap the number of instances in a division.} The competition
-  organizers will limit the number of benchmarks in a division as
-  follows:
+\item \emph{Remove easy benchmarks.} The organizers will remove all
+  benchmarks that were solved by all solvers (including non-competitive
+  solvers) in less than one second in 2018.
+\item \emph{\ucoretrack.} In addition, for the \ucoretrack, all
+  benchmarks with a single assertion will be removed.
+\item \emph{Cap the number of instances in a division.} The organizers will
+  limit the number of benchmarks in a division based on the size of the
+  corresponding logic in SMT-LIB as follows:
   \begin{enumerate}
-  \item If a division contains less than 300 instances, all
-        the instances will selected.
-  \item If a division contains between 300 and 600 instances,
-        a selection of 300 instances from the set will be selected.
-  \item If a division contains more than 600 instances, 50\% of
-        the benchmarks will be selected.
+  \vspace{-1ex}
+    \item \label{bench-sel-300} If a logic contains less than 300 instances,
+      all instances will selected.
+  \item \label{bench-sel-600} If a logic contains between 300 and 600
+    instances, a subset of 300 instances from the set will be selected.
+  \item \label{bench-sel-more} If a logic contains more than 600 instances,
+    50\% of the benchmarks will be selected.
   \end{enumerate}
-\item \emph{\ucoretrack{}.} In addition, for the \ucoretrack{}, all
-  benchmarks with a single assertion will be removed.
 \end{enumerate}
 %
-The selection process in cases (b) and (c) above will guarantee the
-inclusion of new benchmarks by first picking randomly one benchmark from
-each new benchmark family.  The rest of the benchmarks will be chosen
-randomly from the remaining benchmarks using a uniform distribution.
-%
-The culling script will be publicly available and will use the same
-random seed as the rest of the competition.  The set of benchmarks
-selected for the competition will be published when the competition
+The selection process in cases \ref{bench-sel-600} and \ref{bench-sel-more}
+above will guarantee the inclusion of new benchmarks by first picking randomly
+one benchmark from each new benchmark family.  The rest of the benchmarks will
+be chosen randomly from the remaining benchmarks using a uniform distribution.
+%
+The benchmark selection script will be publicly available at \rem{link tba} and
+will use the same random seed as the rest of the competition.  The set of
+benchmarks selected for the competition will be published when the competition
 begins.

### 2019-04-19 rules/rules19.tex
Rules: Fix benchmark selection for UC and MV tracks.

@@
 
+\header{Benchmark Selection.} See page~\pageref{benchmark-selection}.
+
 \header{Time Limit.}
@@
 \header{Benchmark Selection.}
-This track will run on all \emph{unsatisfiable} benchmarks from the \maintrack,
-modified to use named top-level assertions of the form \akey{(assert (! t
-:named f ))}.
-\todo{what if removing all benchmarks with one assertion doesn't leave enough benchmarks in a division?}
+This track will run on a selection of non-incremental benchmarks with status
+\texttt{unsat} (as described on page~\pageref{benchmark-selection}), modified
+to use named top-level assertions of the form \akey{(assert (! t :named f ))}.
 
@@
 This experimental track only has one division, QF\_BV. It will run on all
-\emph{satisfiable} benchmarks from this division in the \maintrack.
+selection of non-incremental benchmarks with status \texttt{sat} from logic
+QF\_BV (as described on page~\pageref{benchmark-selection}).
 
@@
 \challtrack will use all incremental and non-incremental benchmarks dedicated
-to this track by their submitters. The \ucoretrack will use all unsatisfiable
-\maintrack benchmarks, modified to use named top-level assertions.  The
-\mvaltrack will use all satisfiable \maintrack benchmarks from the QF\_BV
-division.
+to this track by their submitters. The \ucoretrack will use a selection of
+non-incremental benchmarks with status \texttt{unsat} and more than one
+top-level assertion, modified to use named top-level assertions.  The
+\mvaltrack will use a selection of non-incremental benchmarks with status
+\texttt{sat} from logic QF\_BV.
 

### 2019-04-19 rules/rules19.tex
Rules: Finished pass over benchmarks section.
Rules: Generalize parallel time limit.

@@
 %
-Benchmarks will be slightly scrambled before the competition, using a
-simple benchmark scrambler.  The benchmark scrambler will be made
-publicly available before the competition.
-
+Benchmarks will be slightly scrambled before the competition, using a simple
+benchmark scrambler available at \rem{link tba}.  The benchmark scrambler will
+be made publicly available before the competition.
+%
 Naturally, solvers must not rely on previously determined identifying
@@
     wall-clock time in seconds (real-valued)
-  \item \makebox[5em][l]{$c \in [0, 4T]$}
+  \item \makebox[5em][l]{$c \in [0, mT]$}
     CPU time in seconds (real-valued)
@@
 \header{CPU Time Score ($\mathbf{c}$).}
-The (real-valued) CPU time in seconds, measured across all cores and
-sub-processes, until time limit $4T$ or the solver process terminates.
+The (real-valued) CPU time in seconds, measured across all $m$ cores
+until time limit $mT$ is reached or the solver process
+terminates.
 
@@
 all available processor cores.  To evaluate sequential performance, we derive a
-\emph{sequential score} by imposing a (virtual) CPU time limit equal to the
-wall-clock time limit~$T$.  A solver result is taken into consideration for the
-sequential score only if the solver process terminates within this CPU time
-limit.  More specifically, for a given parallel performance $\langle e, n, w,
-c\rangle$, the corresponding sequential performance is defined as~$\langle e_S,
-n_S, c_S\rangle$, where
+\textbf{sequential score} by imposing a \emph{virtual} CPU time limit equal to
+the wall-clock time limit~$T$.  A solver result is taken into consideration for
+the sequential score only if the solver process terminates \emph{within} this
+CPU time limit.  More specifically, for a given parallel performance $\langle
+e, n, w, c\rangle$, the corresponding sequential performance is defined
+as~$\langle e_S, n_S, c_S\rangle$, where
 \begin{itemize}
@@
 
-\subsubsection{\maintrack and \challtrack.}
+\subsubsection{\maintrack and \challtrack}
   For the \maintrack and \challtrack, the error score $e$ and the correctly

### 2019-04-20 rules/rules19.tex
Rules: Division scoring.

@@
 
-\subsubsection{Incremental Track.}
+\subsubsection{Incremental Track}
 %
@@
 
-\subsubsection{\ucoretrack.}
+\subsubsection{\ucoretrack}
   For the \ucoretrack, the error score $e$ and the correctly solved score $n$
@@
 
-\subsection{Division scoring \todo{update}}
+\subsection{Division scoring}
 \label{sec:division-scoring}
 
-We compute in total eight different {\em scores} for each division based
-on solvers' parallel and sequential performance.  The two performances
-are computed separately for {\em all}, {\em satisfiable}, and {\em
-unsatisfiable instances}.  In addition we compute the performances for a
-\emph{one-minute wonder} track, where each solver is run with a
-24-second timeout.
-\todo{24-seconds is only a score, not a track}
-
-\header{\maintrack and \challtrack: Removal of Disagreements.}
-%
-\todo{do we need to update this notion?}
+For each track and division, we compute a division score based on the parallel
+performance of a solver (the \emph{parallel division score}).  For the
+\maintrack, \challtrack, \ucoretrack and \mvaltrack we also compute a division
+score based on the sequential performance of a solver (the \emph{sequential
+division score}).  Additionally, for the \maintrack, we further determine three
+additional scores based on parallel performance: The \emph{24-second score}
+will reward solving performance within a time limit of 24 seconds (wall clock
+time), the \emph{sat score} will reward (parallel) performance on satisfiable
+instances, and the \emph{unsat score} will reward (parallel) performance on
+unsatisfiable instances.
+
+\header{Sound Solver.}
+A solver is \emph{sound} on benchmarks with \emph{known status} for a division
+if its parallel performance (Section~\ref{sec:benchmark-scoring}) is of the
+form $\langle 0, n, w, c\rangle$ for each benchmark in the division, i.e., if
+it did not produce any erroneous results.
+
+\header{Disagreeing Solvers.}
+Two solvers \emph{disagree} on a benchmark if one of them reported \texttt{sat}
+and the other reported \texttt{unsat}.
+
+\header{Removal of Disagreements.}
 Before division scores are computed for the \maintrack and \challtrack,
-benchmarks with unknown status are removed from the competition results if two
-(or more) solvers that are sound on benchmarks with known status disagree on
-their result.  More specifically, a solver (including a solver that was entered
-into the competition by the organizers for comparison purposes) is \emph{sound
-on benchmarks with known status} for a division if its parallel performance
-(Section~\ref{sec:benchmark-scoring}) is of the form $\langle 0, n, w,
-c\rangle$ for each benchmark in the division, i.e., if it did not produce any
-erroneous results.  Two solvers \emph{disagree} on a benchmark if one of them
-reported \texttt{sat} and the other reported \texttt{unsat}.  Only the
-remaining benchmarks are used in the following computation of division scores
-(but the organizers may report disagreements for informational purposes).
-
-\header{\inctrack: Removal of Disagreements.}
-\todo{}
-
-\header{\challtrack: Removal of Disagreements.}
-\todo{}
-
-\medskip
-
-To compute a solver's scores for a division, the solver's individual
-benchmark scores for all benchmarks in the division are first
-multiplied by a scalar weight that depends on the benchmark's family,
-and then summed component-wise.
-
-For a given competition benchmark~$b$, let~$F_b \geq 1$ be the total
-number of benchmarks in $b$'s benchmark family that were used in the
-competition track to which the division belongs (and not removed
-because of disagreements).  We define the weight for benchmark~$b$ as
-$\alpha_b = (1 + \log_e F_b) / F_b$.  We define the \emph{normalized weight} for
-benchmark~$b$ as $\alpha'_b = \alpha_b / (\sum_{b'} \alpha_{b'})$,
-where the sum is over all benchmarks in the division.  Let~$N$ be the
-total number of benchmarks in the division.
-
-For \maintrack and \ucoretrack divisions, we will separately
-compute the weighted sum of all benchmarks separately based on the
-parallel performance and sequential performance.
-(Section~\ref{sec:benchmark-scoring})
-%
-These will be computed as
-$$\sum_b \alpha'_b \cdot \langle e_b \cdot N, n_b \cdot N, w_b, c_b\rangle$$
-%
-where the sum $\sum_b$ ranges over all parallel performances when
-computing parallel performance scores, and over all sequential
-performances when computing sequential performance scores.
-\iffalse
-benchmarks in the division to assess parallel performance, and the
-weighted sum of all sequential performances (Section~\ref{sec:sequential})
-to assess sequential performance.
-\fi
-For incremental track divisions,
-division scores will be based on parallel performance only.\footnote{Since
-  incremental track benchmarks may be partially solved, defining a
-  useful sequential performance for the incremental track would require
-  information not provided by the parallel performance, e.g., detailed timing
-  information for each result.}
-  \todo{is this only true for the incremental track or also one of the new tracks}
-
-Division scores are compared lexicographically:
-\begin{itemize}
-\item A weighted sum of parallel performances $\langle e, n, w, c\rangle$ is
-  better than $\langle e', n', w', c'\rangle$ iff $e < e'$ or ($e =
-  e'$ and $n > n'$) or ($e = e'$ and $n = n'$ and $w < w'$) or ($e =
-  e'$ and $n = n'$ and $w = w'$ and $c < c'$).  That is, fewer errors
-  takes precedence over more correct solutions, which takes precedence
-  over less wall-clock time taken, which takes precedence over less
-  CPU time taken.
-\item A weighted sum of sequential performances $\langle e_S, n_S,
-  c_S\rangle$ is better than $\langle e_S', n_S', c_S'\rangle$ iff
-  $e_S < e_S'$ or ($e_S = e_S'$ and $n_S > n_S'$) or ($e_S = e_S'$ and
-  $n_S = n_S'$ and $c_S < c_S'$).  That is, fewer errors takes
-  precedence over more correct solutions, which takes precedence over
-  less CPU time taken.
-\end{itemize}
-%
-We will not make any comparisons between parallel and sequential
-performances, as these are intended to measure fundamentally different
-performance characteristics.
+benchmarks with \emph{unknown status} are removed from the competition results
+if two (or more) solvers that are sound on benchmarks with known status
+disagree on their result.
+%
+Only the remaining benchmarks are used in the following computation of division
+scores (but the organizers \emph{will report disagreements} for informational
+purposes).
+
+\subsubsection{Parallel Division Score}
+
+The parallel score for a division is computed for \emph{all} tracks.  It is
+defined for a participating solver in a division with $M$ benchmarks as the sum
+of all the individual parallel benchmark scores:
+$$\sum_{b\in M} \langle e_b \cdot N, n_b \cdot N, w_b, c_b\rangle$$.
+
+\noindent
+A parallel division score $\langle e, n, w, c\rangle$ is better than a parallel
+division score $\langle e', n', w', c'\rangle$ iff $e < e'$ or ($e = e'$ and $n
+> n'$) or ($e = e'$ and $n = n'$ and $w < w'$) or ($e = e'$ and $n = n'$ and $w
+= w'$ and $c < c'$).  That is, fewer errors takes precedence over more correct
+solutions, which takes precedence over less wall-clock time taken, which takes
+precedence over less CPU time taken.
+
+\subsubsection{Sequential Division Score}
+
+The sequential score for a division is computed for \emph{all} tracks
+\emph{except} the \inctrack and incremental benchmarks in the
+\challtrack\footnote{Since incremental track benchmarks may be partially
+solved, defining a useful sequential performance for the incremental track
+would require information not provided by the parallel performance, e.g.,
+detailed timing information for each result.}.  It is defined for a
+participating solver in a division with $M$ benchmarks as the sum of all the
+individual sequential benchmark scores:
+$$\sum_{b\in M} \langle e_{S_b} \cdot N, n_{S_b} \cdot N, w_{S_b}, c_{S_b}\rangle$$.
+
+\noindent
+A sequential division score $\langle e_S, n_S, c_S\rangle$ is better than a
+sequential division score $\langle e_S', n_S', c_S'\rangle$ iff $e_S < e_S'$ or
+($e_S = e_S'$ and $n_S > n_S'$) or ($e_S = e_S'$ and $n_S = n_S'$ and $c_S <
+c_S'$).  That is, fewer errors takes precedence over more correct solutions,
+which takes precedence over less CPU time taken.
+
+We will not make any comparisons between parallel and sequential performances,
+as these are intended to measure fundamentally different performance
+characteristics.
+
+\subsubsection{24-Seconds Score (\maintrack)}
+
+The 24-seconds score for a division is computed for the \maintrack as the
+parallel division score with a wall-clock time limit $T$ of 24 seconds.
+
+\subsubsection{Sat Score (\maintrack)}
+
+The sat score for a division is computed for the \maintrack as the
+parallel division score when only satisfiable instances are considered.
+
+\subsubsection{Unsat Score (\maintrack)}
+The unsat score for a division is computed for the \maintrack as the
+parallel division score when only unsatisfiable instances are considered.
 

### 2019-04-20 rules/rules19.tex
Rules: Competition-wide recognitions (still not finalized).

@@
 
-  \item {\bf Competition-Wide Recognitions.} \todo{}
+  \item {\bf Competition-Wide Recognitions.}
+    This year, we will replace the previous notion of competition-wide scoring
+    as introduced for the Main Track in 2014 (and improved over the years)
+    with recognitions for all tracks that do not directly compare divisions.
+    {\color{red} Details to be announced.}
+    \rationale{Competition-wide scoring was introduced as a metric to
+    compare solver performance across all divisions. By definition, this metric
+    is biased towards solvers that enter a large number of divisions.}
 
@@
 
-\subsection{Other Recognitions \todo{Update}}
+\subsection{Competition-Wide Recognitions}
+
+{\color{red} Details to be announced.}
+
+\subsection{Other Recognitions}
 

### 2019-04-20 rules/rules19.tex
Rules: Finalize draft.

@@
   system descriptions.
-\item[\todo{}] Opening value of NYSE Composite Index used to complete
-  random seed for benchmark scrambling.
+\item[June~3] Opening value of NYSE Composite Index used to compute
+  random seed for competition tools.
 \item[July~7/8] SMT Workshop; end of competition, presentation of
@@
 competition.
-
+%
 Accordingly, researchers are highly encouraged to submit both new
@@
 \mvaltrack.
-
+%
 Within each track there are multiple divisions, where each division
@@
 SMT-COMP~2019.
-The principal changes from the previous competition rules are the following: \todo{Aina in charge of this section}
+The principal changes from the previous competition rules are the following:
 \begin{itemize}
@@
 
-  \item {\bf Naming Convention for Derived Tools.} \todo{}
+  \item {\bf Naming Convention for Derived Tools.}
+    This year, we require that a derived tool (a tool based on and extending
+    another SMT solver) should follow the \emph{naming convention} {[name of
+    base solver]-[my solver name]}.
+    \rationale{Give credit where credit is due.}
 
@@
   \item {\bf Experimental Strings Division.}
-    \todo{point to the current draft of the standard as the set of rules
-    solvers have to agree on}
     The competition will feature an experimental divisions for benchmarks that
-    use strings.
+    use strings. Participating solvers must implement the semantics of the
+    current SMT-LIB draft for the theory of unicode strings
+    (\url{http://smtlib.cs.uiowa.edu/theories-UnicodeStrings.shtml}).
     \rationale{Corresponding theories and benchmarks are expected to be added
@@
 
+\pagebreak
 \header{Time and Memory Limits.}
@@
 
+{\color{red} Details to be announced.}
+\iffalse
 The organizers will also recognize the following contributions:
@@
 contributions that become apparent in the competition results.
-
-As part of the FLoC Olympic Games, Kurt G{\"o}del medals will be
-awarded to:
-%
-\begin{itemize}
-\item the solver that wins the most competitive divisions in the
-  incremental track;
-\item the solver that wins the most competitive divisions in the
-  \ucoretrack;
-\item the solver that wins the QF\_BV division (separately for
-  parallel and sequential performance) in the \maintrack.
-\end{itemize}
+\fi
 
@@
 
+\pagebreak
 \section{Acknowledgments}

### 2019-04-20 rules/rules19.tex
Rules: Add draft watermark.
Rules: Fix typos.

@@
   \item {\bf Experimental Strings Division.}
-    The competition will feature an experimental divisions for benchmarks that
+    The competition will feature experimental divisions for benchmarks that
     use strings. Participating solvers must implement the semantics of the
@@
 %
-The competition charis are responsible for policy and procedure decisions,
+The competition chairs are responsible for policy and procedure decisions,
 such as these rules, with input from the co-organizers.

### 2019-04-24 rules/rules19.tex
Rules: Fix line breaking for URLs
Rules: Wrapper tools must state solver versions

@@
 \urlstyle{same}
+% add chars ~,-,*,'," to break line at for long URLs
+\makeatletter
+\g@addto@macro{\UrlBreaks}{\UrlOrds}
+\makeatother
 
@@
     change is twofold.  First, we want to improve transparency when submitted
-    solvers are wrapper tools according to the rules of the competition.
-    Second, we want to encourage documenting technical improvements that
-    lead to the current results.}
+    solvers are wrapper or derived tools according to the rules of the
+    competition.  Second, we want to encourage documenting technical
+    improvements that lead to the current results.}
 
@@
 A \emph{wrapper tool} is defined as any solver that calls one or more other SMT
-solvers (the \emph{wrapped solvers}). Its system description \textbf{must} explicitly acknowledge any
-solvers that it wraps.  It \emph{should} further make clear technical
-innovations by which the wrapper tool expects to improve on the wrapped
-solvers.
+solvers (the \emph{wrapped solvers}). Its system description \textbf{must}
+explicitly acknowledge and state the \textbf{exact} version of any solvers that
+it wraps.  It \emph{should} further make clear technical innovations by which
+the wrapper tool expects to improve on the wrapped solvers.
 
@@
 \emph{derived} tool (see above).
+In case of a \emph{wrapper} tool, it \textbf{must} also explicitly state
+the exact version of each wrapped solver.
 It \emph{should} further include
@@
     references to relevant literature (by the authors or others),
-  \item in case of a \emph{wrapped} or \emph{derived tool}: details of
+  \item in case of a \emph{wrapper} or \emph{derived tool}: details of
     technical innovations by which a wrapper or derived tool expects to improve
-    on the wrapped,
-    solvers or base solver
+    on the wrapped solvers or base solver
   \item appropriate acknowledgement of tools other than SMT solvers called by

### 2019-04-29 rules/rules19.tex
Rules: more in system descriptions
first draft competition wide recognition

@@
 the exact version of each wrapped solver.
-It \emph{should} further include
+A system description \emph{should} further include the following information
+(unless there is a good reason otherwise):
 \begin{itemize}[itemsep=0ex]
@@
 deadline}, and will be made publicly available on the competition website.
+Organizers will check that they contain sufficient information
+and may withdraw a system if its description is not sufficiently updated upon
+request
 
@@
 
-\header{Division}
+\header{Divisions.}
 Within each track there are multiple divisions, and each division selects
@@
 
-\subsubsection{Parallel Division Score}
+\subsubsection{Parallel Score}
 
@@
 
-\subsubsection{Sequential Division Score}
+\subsubsection{Sequential Score}
 
@@
 
-{\color{red} Details to be announced.}
+In 2014 the SMT competition introduced a competition-wide scoring to allow it to award medals in the FLoC Olympic Games and has been awarded each year since.
+This scoring purposefully emphasized the breadth of solver participation by summing up a score for each (competitive) division a solver competed in.
+Whilst this rationale is reasonable, we observed that this score had become dictated by the number of divisions being entered by a solver.
+
+This year we will replace the competition-wide score with two new \emph{rankings} that select one solver per division and then rank those solvers.
+The rationale here is to take the focus away from the number of divisions entered and focus on measures that make sense to use to compare different divisions.
+
+\subsubsection{Biggest Lead Ranking}
+
+This ranking aims to select the solver that \emph{won by the most} in some competitive division.
+The winners of each division are ranked by the distance between them and the next competitive solver in that division.
+
+Let $\mathit{solved}(D,i)$ be the number of problems solved by the $i$th solver in division $D$. The rank of division $D$ is given as
+\[
+\frac{\mathit{solved}(D,1)+1}{\mathit{solved}(D,2)+1}
+\]
+The biggest lead winner is the winner of the division with the highest (largest) rank. This can be computed per scoring system e.g. separately for the sat and unsat score.
+
+\subsubsection{Largest Contribution Ranking}
+
+This ranking aims to select the solver that \emph{uniquely contributed} the most in some division, or to put another way, the solver that would be most missed.
+This is achieved by computing a solvers contribution to the \emph{virtual best solver} for a division.
+
+The virtual best solver score for a division $D$ containing solvers $S$ is given as 
+\[
+\mathit{vbss}(D,S) = \sum_{b \in D} {\sf min}\{ \mathit{solvedIn}(s,b) \mid s \in S ~\mathit{and}~\mathit{solved}(s,b) \}
+\]
+where $\mathit{solved}(s,b)$ is true if solver $s$ solves benchmark $b$ and $\mathit{solvedIn}(s,b)$ is the amount of time solver $s$ takes to solve benchmark $b$.
+E.g.
+$\mathit{vbss}(D,S)$ is the smallest amount of time taken to solve all benchmarks solved in division $D$ using solvers in $S$.
+
+Let $S$ be the set of competitive solvers competing in division $D$. The rank of solver $s \in S$ in division $D$ is then
+\[
+1- \frac{\mathit{vbss}(D,S-s) }{ \mathit{vbss}(D,S)}
+\]
+e.g.
+the difference in virtual best solver score when removing $s$ from the computation.
+This will be a number between 0 and 1 with 0 indicating that $s$ made no impact on the \emph{vbss} and 1 indicating that $s$ is the only solver that solved anything in the division.
+
+The largest contribution winner is the solver across all divisions with the highest (largest) rank. Again, this can be computed per scoring system.
 

### 2019-05-07 rules/rules19.tex
updates

@@
 of all the individual parallel benchmark scores:
-$$\sum_{b\in M} \langle e_b \cdot N, n_b \cdot N, w_b, c_b\rangle$$.
+$$\sum_{b\in M} \langle e_b , n_b , w_b, c_b\rangle$$.
 
@@
 individual sequential benchmark scores:
-$$\sum_{b\in M} \langle e_{S_b} \cdot N, n_{S_b} \cdot N, w_{S_b}, c_{S_b}\rangle$$.
+$$\sum_{b\in M} \langle e_{S_b}, n_{S_b}, w_{S_b}, c_{S_b}\rangle$$.
 
@@
 
-Let $\mathit{solved}(D,i)$ be the number of problems solved by the $i$th solver in division $D$. The rank of division $D$ is given as
+Let $n_i^D$ be the correctness score of the $i$th solver (for a given scoring system e.g. number of correct results or reduction) in division $D$. The rank of division $D$ is given as
 \[
-\frac{\mathit{solved}(D,1)+1}{\mathit{solved}(D,2)+1}
+\frac{n_1^D+1}{n_2^D+1}
 \]
-The biggest lead winner is the winner of the division with the highest (largest) rank. This can be computed per scoring system e.g. separately for the sat and unsat score.
+The \emph{biggest lead winner} is the winner of the division with the highest (largest) rank. This can be computed per scoring system.
 
@@
 This ranking aims to select the solver that \emph{uniquely contributed} the most in some division, or to put another way, the solver that would be most missed.
-This is achieved by computing a solvers contribution to the \emph{virtual best solver} for a division.
-
-The virtual best solver score for a division $D$ containing solvers $S$ is given as 
+This is achieved by computing a solver's contribution to the \emph{virtual best solver} for a division.
+
+Let $\langle e_b^s, n_b^s, w_b^s, c_b^s \rangle$ be the parallel benchmark score for benchmark $b$ and solver $s$ (for a given scoring system e.g.
+$n$ is either number of correct results or reduction).
+The virtual best solver score for a division $D$ using solvers $S$ is given as 
 \[
-\mathit{vbss}(D,S) = \sum_{b \in D} {\sf min}\{ \mathit{solvedIn}(s,b) \mid s \in S ~\mathit{and}~\mathit{solved}(s,b) \}
+\mathit{vbss}(D,S) = \sum_{b \in D} {\sf min}\{ n_b^s \times c_b^s \mid s \in S ~\mathit{and}~ n_b^s > 0  \}
 \]
-where $\mathit{solved}(s,b)$ is true if solver $s$ solves benchmark $b$ and $\mathit{solvedIn}(s,b)$ is the amount of time solver $s$ takes to solve benchmark $b$.
-E.g.
-$\mathit{vbss}(D,S)$ is the smallest amount of time taken to solve all benchmarks solved in division $D$ using solvers in $S$.
+where the minimum of an empty set is 0 (e.g.
+no contribution if a benchmark is unsolved).
+In other words, for the single query track, $\mathit{vbss}(D,S)$ is the smallest amount of time taken to solve all benchmarks solved in division $D$ using solvers in $S$.
 
@@
 This will be a number between 0 and 1 with 0 indicating that $s$ made no impact on the \emph{vbss} and 1 indicating that $s$ is the only solver that solved anything in the division.
-
-The largest contribution winner is the solver across all divisions with the highest (largest) rank. Again, this can be computed per scoring system.
+%
+The \emph{largest contribution winner} is the solver across all divisions with the highest (largest) rank. Again, this can be computed per scoring system.
 
@@
 
-{\color{red} Details to be announced.}
-\iffalse
 The organizers will also recognize the following contributions:
@@
 \begin{itemize}
-\item \emph{Best new entrant}. The best performing entrant from a new
-  solver implementation team, as measured by the competition-wide
-    metric. \todo{}
-\item \emph{Benchmarks}. Contributors of new benchmarks.
-\end{itemize}
-%
+\item \emph{New entrants}.
+All new entrants (to be interpreted by the organisers, but broadly a significantly new tool that has not competed in the competition before) that beat an existing solver in some division will be awarded special commendations.
+\item \emph{Benchmarks}. Contributors of new benchmarks used in the competition will receive a special mention.
+\end{itemize}
+%
+These recognitions will be announced at the SMT workshop and published on the competition website. 
 The organizers reserve the right to recognize other outstanding
 contributions that become apparent in the competition results.
-\fi
 

### 2019-05-07 tools/scoring/score.py
add scoring script and config files

@@ -1,0 +1,454 @@
+# This script has been written to compute the scores of SMT-COMP
+# It is purposefully trying to be flexible to changes in the scoring
+# mechanisms. It can be used to apply scoring schemes from different
+# years of the competition to different sets of data.
+#
+# This script requires the pandas data analysis framework
+#
+# @author Giles Reger
+# @date May 2019
+
+# Data processing library pandas
+import numpy as np
+import pandas as pd
+
+# Options parsing
+import optparse
+
+import sys
+import csv
+import math
+
+
+############################
+# Helper functions
+
+all_solved_verdicts = pd.Series(['sat','unsat'])
+sat_solved_verdicts = pd.Series(['sat'])
+unsat_solved_verdicts = pd.Series(['unsat'])
+
+
+def log(string):
+  # turn this on to debug stuff 
+  if(False):
+    print(string)
+
+# project out the main columns for printing
+def view(data):
+  return data[['benchmark','solver','result']]
+
+
+# adds columns for division and family to data
+# also does some tidying of benchmark column for specific years of the competition
+# edit this function if you want to edit how families are added
+def addDivisonFamilyInfo(data,fam):
+
+  # Remove OtherDivision from benchmark name (2018)
+  data['benchmark'] = data['benchmark'].str.replace('Other Divisions/','')
+  # Remove Datatype divisions from benchmark name (2017)
+  data['benchmark'] = data['benchmark'].str.replace('Datatype Divisions/','')
+
+  # Extract divisions and as another column
+  data['division'] = data['benchmark'].str.split('/').str[0]
+  # Extract family as another column
+  # This depends on the fam option. The 'top' option takes the top directory and the 'bot' option takes the
+  # bottom directory. The rules have always specified 'top' but the scoring scripts for many years actually
+  # implemented 'top'. The scripts allow you to choose.
+  if fam=="top":
+    log("Using top-level directories for fam")
+    # Take top-level sub-directories as family
+    data['family'] = np.where(data['benchmark'].str.count('/')>1,data['benchmark'].str.split('/').str[1], '-')
+  elif fam=="bot":
+    log("Using bottom-level directories for fam")
+    # Take immediate super-directory as family
+    data['family'] = data.benchmark.apply(lambda x : x[(1+x.index('/')):(x.rfind('/'))])
+  else:
[…]

### 2019-05-07 tools/scoring/count_status.py
Update to scoring files

@@ -1,0 +1,103 @@
+# A script that counts the ratio of different status problems appearing
+# in results files. This was used to prepare the SMT-COMP journal paper
+# and could form the basis of other similar analyses.
+#
+# This script requires the pandas data analysis framework
+#
+# @author Giles Reger
+# @date May 2019
+
+# Data processing library pandas
+import numpy as np
+import pandas as pd
+import sys
+import csv
+
+# Options parsing
+import optparse
+
+import math
+
+
+############################
+def addDivisionInfo(data):
+
+  # Remove OtherDivision from benchmark name (2018)
+  data['benchmark'] = data['benchmark'].str.replace('Other Divisions/','')
+  # Remove Datatype divisions from benchmark name (2017)
+  data['benchmark'] = data['benchmark'].str.replace('Datatype Divisions/','')
+  # Extract divisions and as another column
+  data['division'] = data['benchmark'].str.split('/').str[0]
+  return data
+
+def process_csv(csv,year,unknown):
+
+  # Load CSV file
+  data = pd.read_csv(csv)
+
+  # Remove spaces from columns for ease
+  cols = data.columns
+  cols = cols.map(lambda x: x.replace(' ', '_'))
+  data.columns = cols
+
+  #only grab the benchmarks and their expected value
+  data = data[['benchmark','expected']]
+  data = data.drop_duplicates(subset='benchmark',keep='first')
+
+  # extract division as separate column
+  data = addDivisionInfo(data)
+  
+  print(year)
+  total = len(data)
+  round_it = lambda x : str(int(round(100*(x/total))))
+  if unknown:
+    print("("+round_it(len(data[(data.expected=="sat")]))+":"+round_it(len(data[(data.expected=="unsat")]))+":"+round_it(len(data[(data.expected=="starexec-unknown")]))+")")
+  else:
+    print("("+round_it(len(data[(data.expected=="sat")]))+":"+round_it(len(data[(data.expected=="unsat")]))+")")
+
+  all = data.groupby('division').count()[['expected']]
+  unsat = data[(data.expected=="unsat")].groupby('division').count()[['expected']]
+  sat = data[(data.expected=="sat")].groupby('division').count()[['expected']]
+
+  all.columns=['all']
+  unsat.columns=['unsat']
[…]

### 2019-05-07 tools/scoring/score.py

@@ -334,6 +334,7 @@ def process_csv(csv,family,division,disagreements,year,time_limit,verdicts,use_f
 
 # This function runs with specific values for certain years but keeps some options open to allow
 # us to try diferent things
+# Assumes csv files for different years are stored in a hardcoded place. TODO: make more generic
 def run(family,division,verdicts,tlimit,bytotal,sequential,skip_unknowns):
 
   df15 = process_csv("csvs/2015.csv",family,division,False,2015,min(2400,tlimit),verdicts,False,skip_unknowns,sequential)

### 2019-05-10 rules/rules19.tex
Rules: Finalize as much as possible

@@
 
-\usepackage{draftwatermark}
+%\usepackage{draftwatermark}
+%\usepackage{showframe}   % debug
 
@@
   \item {\bf Competition-Wide Recognitions.}
-    This year, we will replace the previous notion of competition-wide scoring
+    This year, we will replace the previous notion of competi\-tion-wide scoring
     as introduced for the Main Track in 2014 (and improved over the years)
     with recognitions for all tracks that do not directly compare divisions.
-    {\color{red} Details to be announced.}
     \rationale{Competition-wide scoring was introduced as a metric to
@@
 %
-A SMT solver that can enter SMT-COMP is a tool that can
-determine the (un)satisfiability of benchmarks from the SMT-LIB benchmark library
+A Satisfiability Modulo Theories (SMT) solver that can enter SMT-COMP is a tool that can determine the
+(un)satisfia\-bility of benchmarks from the SMT-LIB benchmark library
 (\url{http://www.smt-lib.org/benchmarks.shtml}).
@@
 \begin{center}
-  \rem{submission form url}
+  \url{https://docs.google.com/forms/d/1gJ_9ztIzwsgeyR0R4H_yIg5lBxxxDBwSy8ZodXt5xKk}
 \end{center}
@@
 tools are found at \url{https://github.com/SMT-COMP/smt-comp/tree/master/tools}.
-{\color{red} Some tools have not been released yet.}
 \begin{itemize}
@@
 \header{Post-Processor.}
-This track uses a StarExec post-processor (named \rem{tba}) to accumulate the
-results.
+This track will use
+{\url{https://github.com/SMT-COMP/postprocessors/tree/master/single-query-track/process}}
+as a post-processor
+to validate and accumulate the results.
 
@@
 
-\header{Trace Executor.} This track will use the trace executor at \rem{link tba}
-to execute solvers on an incremental benchmark file.
+\header{Trace Executor.} This track will use the trace executor
+to execute a solver on an incremental benchmark file.
 
 \header{Post-Processor.}
-This track will use the post-processor at \rem{link tba} to accumulate the
-results.
+This track will use
+{\url{https://github.com/SMT-COMP/postprocessors/tree/master/incremental-track/process}}
+as a post-processor
+to validate and accumulate the results.
 
@@
 \header{Post-Processor.}
-This track uses the post-processors from the \maintrack (for non-incremen-tal
-benchmarks) and the \inctrack (for incremental benchmarks) to accumulate the
-results.
+This track will use the post-processors from the \maintrack (for
+non-incremen\-tal benchmarks) and the \inctrack (for incremental benchmarks)
+to accumulate the results.
 
@@
 \header{Post-Processor.}
-This track will use the post-processor at \rem{link tba} to accumulate the
-results.
+This track will use
+{\url{https://github.com/SMT-COMP/postprocessors/tree/master/unsat-core-track/process}}
+as a post-processor
+to validate and accumulate the results.
 
@@
 In order to check that the model satisfies the benchmark, the organizers will
-use a model validating tool. The organizers will make this tool available to
-solver developers before the solver submission deadline.
+use the model validating tool available at
+{\url{https://github.com/SMT-COMP/postprocessors/tree/master/model-validation-track}}.
 
@@
 \header{Post-Processor.}
-This track will use the post-processor at \rem{link tba} to accumulate the
-results.
+This track will use
+{\url{https://github.com/SMT-COMP/postprocessors/tree/master/model-validation-track/process}}
+as a post-processor
+to validate and accumulate the results.
 
@@
 Benchmarks will be slightly scrambled before the competition, using a simple
-benchmark scrambler available at \rem{link tba}.  The benchmark scrambler will
-be made publicly available before the competition.
+benchmark scrambler available at \url{https://github.com/SMT-COMP/scrambler}.
+The benchmark scrambler will be made publicly available before the competition.
 %

### 2019-05-11 rules/rules19.tex
Rules: Add link for benchmark selection script

@@
 %
-The benchmark selection script will be publicly available at \rem{link tba} and
+The benchmark selection script will be publicly available at
+\url{https://github.com/SMT-COMP/smt-comp/tree/master/tools} and
 will use the same random seed as the rest of the competition.  The set of

### 2019-05-11 rules/rules19.tex
Minor
Rules: Update submission form link

@@
 \begin{center}
-  \url{https://docs.google.com/forms/d/1gJ_9ztIzwsgeyR0R4H_yIg5lBxxxDBwSy8ZodXt5xKk}
+  \url{https://forms.gle/y8xB4C8TB2WkdKPx9}
 \end{center}
@@
 {\url{https://github.com/SMT-COMP/postprocessors/tree/master/model-validation-track}}.
+The tool will output VALID for full satisfying models, and INVALID for partial models,
+malformed models, models that do not satisfy the benchmark or if the solver returns
+\texttt{unsat}. If the solver provides no output or returns \texttt{unknown} the model
+validating tool will output UNKNOWN.
 
@@
 
+\subsubsection{\mvaltrack}
+  For the \mvaltrack, the error score $e$ and the correctly solved score $n$
+  are defined as
+  \begin{itemize}
+  \item $e=0$ and $n=0$ if the solver
+    \begin{itemize}[noitemsep,nolistsep]
+      \item aborts without a response, or
+      \item the result of the \akey{check-sat} command is \texttt{unknown},
+    \end{itemize}
+  \item $e=1$ and $n=0$ if the result is invalid according to the output of
+    the model validating tool described in Section~\ref{sec:exec:model},
+  \item otherwise, $e=0$ and $n=1$.
+  \end{itemize}
+
 \subsection{Division scoring}
@@
 
-\pagebreak
 \section{Acknowledgments}
@@
 
+\pagebreak
 \bibliographystyle{plain}

### 2019-05-15 rules/rules19.tex
Added scoring for model validation track.
Rules: Fix benchmark selection.

@@
 \header{Benchmark Selection.}
-This experimental track only has one division, QF\_BV. It will run on all
+This experimental track only has one division, QF\_BV. It will run on a
 selection of non-incremental benchmarks with status \texttt{sat} from logic
@@
   of coming from or having some intended application outside SMT.
-\item \emph{Remove easy benchmarks.} The organizers will remove all
-  benchmarks that were solved by all solvers (including non-competitive
-  solvers) in less than one second in 2018.
-\item \emph{\ucoretrack.} In addition, for the \ucoretrack, all
-  benchmarks with a single assertion will be removed.
-\item \emph{Cap the number of instances in a division.} The organizers will
-  limit the number of benchmarks in a division based on the size of the
-  corresponding logic in SMT-LIB as follows:
+\item \emph{Remove easy / uninteresting benchmarks.}
+  For the following tracks, all benchmarks that can be
+  considered as easy or uninteresting based on the following criteria
+  will be removed.
+  \begin{itemize}
+    \item \emph{\maintrack.} All benchmarks that were solved by all
+      solvers (including non-competitive solvers) in less than one second in
+      the corresponding track in 2018.
+    \item \emph{\ucoretrack.} All benchmarks with only a single assertion.
+  \end{itemize}
+\item \emph{Cap the number of instances in a division.}
+  The number of benchmarks in a division based on the size of the
+  corresponding logic in SMT-LIB will be limited as follows.
+  Let $n$ be the number of benchmarks in an SMT-LIB logic, then
   \begin{enumerate}
   \vspace{-1ex}
-    \item \label{bench-sel-300} If a logic contains less than 300 instances,
-      all instances will selected.
-  \item \label{bench-sel-600} If a logic contains between 300 and 600
-    instances, a subset of 300 instances from the set will be selected.
-  \item \label{bench-sel-more} If a logic contains more than 600 instances,
-    50\% of the benchmarks will be selected.
+    \item \label{bench-sel-300} if $n <= 300$, all instances will be selected;
+  \item \label{bench-sel-600} if $300 < n \leq 600$, a subset of 300 instances
+    from the logic will be selected;
+  \item \label{bench-sel-more} and if $n > 600$,
+    50\% of the benchmarks of the logic will be selected.
   \end{enumerate}

### 2019-05-16 rules/rules19.tex
Fixed <= to \le
Rules: Update scoring and validation info for model-val/unsat-core.

@@
 \header{Result.}
-The result of a solver is considered erroneous if the response to the
+The result of a solver is considered \emph{erroneous} if the response to the
 \akey{check-sat} command is \texttt{sat}, or if the returned
@@
 unsatisfiable core is not, in fact, unsatisfiable.
+Note that an \texttt{unsat} response to \akey{check-sat} but no response to
+\akey{get-model} is considered as a special case of the last case
+(the empty formula is satisfiable).
 
@@
 {\url{https://github.com/SMT-COMP/postprocessors/tree/master/model-validation-track}}.
-The tool will output VALID for full satisfying models, and INVALID for partial models,
-malformed models, models that do not satisfy the benchmark or if the solver returns
-\texttt{unsat}. If the solver provides no output or returns \texttt{unknown} the model
-validating tool will output UNKNOWN.
+It expects as model input a file with the answer to the \akey{check-sat}
+command followed by the solver response to the \akey{get-model} command.
+The model validator tool will output 
+\begin{enumerate}
+  \item VALID\hskip .5em for a \texttt{sat} solver response
+        followed by a full satisfying model;
+  \item INVALID\hskip .5em for
+    \begin{itemize}[noitemsep,topsep=0pt]
+      \item an \texttt{unsat} solver response to \akey{check-sat},
+      \item a \texttt{sat} response to \akey{check-sat} without a response to
+        \akey{get-model},
+      \item partial models,
+      \item malformed models,
+      \item models that do not satisfy the input problem; and
+    \end{itemize}
+  \item UNKNOWN\hskip .5em for
+    \begin{itemize}[noitemsep,topsep=0pt]
+      \item no solver output (no response to both commands),
+      \item an \texttt{unknown} response to \akey{check-sat}.
+    \end{itemize}
+\end{enumerate}
 
@@
   \vspace{-1ex}
-    \item \label{bench-sel-300} if $n <= 300$, all instances will be selected;
+    \item \label{bench-sel-300} if $n \le 300$, all instances will be selected;
   \item \label{bench-sel-600} if $300 < n \leq 600$, a subset of 300 instances
@@
 
-\subsubsection{Incremental Track}
+\subsubsection{\inctrack}
 %
@@
     \begin{itemize}[noitemsep,nolistsep]
-      \item aborts without a response, or
+      \item aborts without a response to \akey{check-sat}, or
       \item the result of the \akey{check-sat} command is \texttt{unknown},
@@
   \begin{itemize}
-  \item $e=0$ and $n=0$ if the solver
-    \begin{itemize}[noitemsep,nolistsep]
-      \item aborts without a response, or
-      \item the result of the \akey{check-sat} command is \texttt{unknown},
-    \end{itemize}
-  \item $e=1$ and $n=0$ if the result is invalid according to the output of
+  \item $e=0$ and $n=0$ if the result is UNKNOWN according to the output of
+    the model validating tool described in Section~\ref{sec:exec:model},
+  \item $e=1$ and $n=0$ if the result is INVALID according to the output of
     the model validating tool described in Section~\ref{sec:exec:model},

### 2019-05-18 rules/rules19.tex
Fixed a missing space
Update rules

@@
 \header{Result.}
-The result of a solver is considered \emph{erroneous} if the response to the
-\akey{check-sat} command is \texttt{sat}, or if the returned
-unsatisfiable core is not well-formed (e.g., contains names of
-formulas that have not been asserted before), or if the returned
+The result of a solver is considered \emph{erroneous} if (i) the
+response to the \akey{check-sat} command is \texttt{sat}, (ii) the
+returned unsatisfiable core is not well-formed (e.g., contains names of
+formulas that have not been asserted before), or (iii) the returned
 unsatisfiable core is not, in fact, unsatisfiable.
-Note that an \texttt{unsat} response to \akey{check-sat} but no response to
-\akey{get-model} is considered as a special case of the last case
-(the empty formula is satisfiable).
+%
+If the solver replies \texttt{unsat} to \akey{check-sat} but gives no
+response to \akey{get-model}, this is considered as no reduction, i.e.,
+as if the solver would have returned the entire benchmark as an unsat
+core.
 
@@
       \item an \texttt{unsat} solver response to \akey{check-sat},
-      \item a \texttt{sat} response to \akey{check-sat} without a response to
-        \akey{get-model},
       \item partial models,
-      \item malformed models,
+      \item malformed models (except if this due to reaching the time limit
+        while printing),
       \item models that do not satisfy the input problem; and
@@
     \begin{itemize}[noitemsep,topsep=0pt]
-      \item no solver output (no response to both commands),
+      \item no solver output (no response to either both commands or
+        \akey{get-model}),
       \item an \texttt{unknown} response to \akey{check-sat}.
@@
     \end{itemize}
-  \item $e=1$and  $n=0$ if the result is erroneous according to
+  \item $e=1$ and  $n=0$ if the result is erroneous according to
     Section~\ref{sec:exec:unsat-core},

### 2019-07-03 tools/scoring/score.py
Add normalization for Largest Contribution Ranking.

@@ -288,6 +288,8 @@ def get_family_scores(data):
 
 def map_solver_id(row, column):
     global g_competitive, g_solver_names
+    if column not in row:
+        return
     solver_id = int(row[column]) if not pandas.isnull(row[column]) else None
     if solver_id:
         g_competitive[solver_id] = row[COL_COMPETING] == 'yes'
@@ -782,7 +784,7 @@ def biggest_lead_ranking(data, sequential):
         scores = []
         for division, div_data in ydata.groupby('division'):
             # Skip non-competitive divisions
-            if not is_competitive_division(div_data.solver.unique()):
+            if not is_competitive_division(div_data.solver_id.unique()):
                 continue
 
             assert len(div_data) >= 2
@@ -795,7 +797,10 @@ def biggest_lead_ranking(data, sequential):
 
             # Compute distance between first and second in the division.
             score = ((1 + first.score_correct) / (1 + second.score_correct))
-            scores.append((score, first.solver, second.solver, division))
+            scores.append((score,
+                           get_solver_name(first.solver_id),
+                           get_solver_name(second.solver_id),
+                           division))
 
         scores_sorted = sorted(scores, reverse=True)
         print('{} Biggest Lead Ranking'.format(year) +
@@ -805,6 +810,8 @@ def biggest_lead_ranking(data, sequential):
 
     if g_args.show_timestamps:
         log('time biggest_lead_ranking: {}'.format(time.time() - start))
+
+    return scores_sorted
 
 
 # Largest Contribution Ranking.
@@ -848,6 +855,7 @@ def largest_contribution_ranking(data, time_limit):
 
     data = data[(data.competitive == True)]
 
+    num_job_pairs_total = 0
     scores_top = []
     for division, div_data in data.groupby('division'):
         solvers = div_data.solver_id.unique()
@@ -855,6 +863,9 @@ def largest_contribution_ranking(data, time_limit):
         # Skip non-competitive divisions
         if not is_competitive_division(solvers):
             continue
+
+        division_size = div_data.division_size.iloc[0]
+        num_job_pairs_total += division_size * len(solvers)
 
         # Compute the scores for the virtual best solver
         vbs_score_correct, vbs_cpu_time = vbss(div_data, '')
@@ -868,20 +879,35 @@ def largest_contribution_ranking(data, time_limit):
             impact_score = 1 - cur_score_correct / vbs_score_correct
             impact_time = 1 - vbs_cpu_time / cur_cpu_time
 
-            scores_div.append((impact_score, impact_time,
[…]

### 2019-07-03 tools/scoring/score.py
Use biggest lead time if solvers have the same biggest lead score.

@@ -795,9 +795,14 @@ def biggest_lead_ranking(data, sequential):
             first = first.iloc[0]
             second = second.iloc[0]
 
-            # Compute distance between first and second in the division.
+            # Compute score and time distance between first and second in the
+            # division.
+            # Note: The time score is only used if solvers have the same score
+            # lead.
             score = ((1 + first.score_correct) / (1 + second.score_correct))
+            time = ((1 + second.score_cpu_time) / (1 + first.score_cpu_time))
             scores.append((score,
+                           time,
                            get_solver_name(first.solver_id),
                            get_solver_name(second.solver_id),
                            division))

### 2019-07-03 tools/scoring/score.py
Fix

@@ -440,7 +440,10 @@ def score(division,
                          | ((data_new.result == filter_result)
                             & (data_new.expected.isin(expected)))]
             benchmarks = set(data_with_result.benchmark.unique())
-            data_new = data_new[data_new.benchmark.isin(benchmarks)]
+            #data_new = data_new[data_new.benchmark.isin(benchmarks)]
+            data_new.loc[~data_new.benchmark.isin(benchmarks),
+                         ['cpu_time', 'wallclock_time', 'result']] = \
+                            [0.0, 0.0, RESULT_UNKNOWN]
 
         # Select benchmarks with results sat/unsat.
         solved = data_new[(data_new.result == RESULT_SAT)

### 2019-07-03 tools/scoring/score.py
Add timeout/memout columns.

@@ -323,6 +323,8 @@ def group_and_rank_solver(data, sequential):
         'score_error': sum,
         'score_cpu_time': sum,
         'score_wallclock_time': sum,
+        'timeout' : sum,
+        'memout' : sum,
         'competitive': 'first',
         'division_size': 'first',
         })
@@ -401,6 +403,8 @@ def score(division,
     data_new['correct_unsat'] = 0 # Number of correctly solved unsat benchmarks
     data_new['division_size'] = num_benchmarks
     data_new['competitive'] = data_new.solver_id.map(is_competitive_solver)
+    data_new['timeout'] = 0
+    data_new['memout'] = 0
 
     # Set the column that is used to determine if a benchmark was solved
     # within the time limit.
@@ -415,6 +419,10 @@ def score(division,
     data_new.loc[data_new[time_column] > wclock_limit,
                  ['cpu_time', 'wallclock_time', 'status', 'result']] = \
                     [wclock_limit, wclock_limit, 'timeout', RESULT_UNKNOWN]
+
+    # Determine memouts/timeouts based on status.
+    data_new.loc[data_new.status.str.startswith('timeout'), 'timeout'] = 1
+    data_new.loc[data_new.status == 'memout', 'memout'] = 1
 
     # Column 'wrong-answers' only exists in incremental tracks.
     incremental = 'wrong-answers' in data.columns
@@ -950,6 +958,10 @@ def md_table_details(df, track, scoring, n_benchmarks):
                 row.correct_unsat))
             lines.append("  unsolved: {}".format(
                 n_benchmarks - row.correct))
+            lines.append("  timeout: {}".format(
+                row.timeout))
+            lines.append("  memout: {}".format(
+                row.memout))
     return '\n'.join(lines)
 
 def write_md_file_sq(division,

### 2019-07-03 rules/rules19.tex
Clarified the unsat-core track scoring
Add single query results.

@@
     with recognitions for all tracks that do not directly compare divisions.
-    \rationale{Competition-wide scoring was introduced as a metric to
-    compare solver performance across all divisions. By definition, this metric
-    is biased towards solvers that enter a large number of divisions.}
+    \rationale{Competi\-tion-wide scoring was introduced as a metric to
+    compare solver performance across all divisions. It is, by definition,
+    biased towards solvers that enter a large number of divisions.}
 

### 2019-07-03 tools/scoring/score.py
Fix

@@ -958,10 +958,10 @@ def md_table_details(df, track, scoring, n_benchmarks):
                 row.correct_unsat))
             lines.append("  unsolved: {}".format(
                 n_benchmarks - row.correct))
-            lines.append("  timeout: {}".format(
-                row.timeout))
-            lines.append("  memout: {}".format(
-                row.memout))
+        lines.append("  timeout: {}".format(
+            row.timeout))
+        lines.append("  memout: {}".format(
+            row.memout))
     return '\n'.join(lines)
 
 def write_md_file_sq(division,

### 2019-07-04 tools/scoring/score.py
Fix biggest lead and largest contribution rankings.
Only consider sound solvers for largest contribution ranking. For both
rankings use cpu_time for sequential and wallclock_time for parallel
scoring.

@@ -556,6 +556,13 @@ def process_csv(csv,
     if 'expected' not in data.columns:
         data['expected'] = None
 
+    # Make sure that the expected column contains RESULT_SAT, RESULT_UNSAT or
+    # RESULT_UNKNOWN. For some exported StarExec data, the expected column is
+    # '-', which can happen when extracting the status of a benchmark fails
+    # while uploading the benchmark to StarExec.
+    data.loc[~data.expected.isin({RESULT_SAT, RESULT_UNSAT}),
+             'expected'] = RESULT_UNKNOWN
+
     start = time.time() if g_args.show_timestamps else None
     data = add_division_family_info(data, g_args.family)
     if g_args.show_timestamps:
@@ -806,12 +813,24 @@ def biggest_lead_ranking(data, sequential):
             first = first.iloc[0]
             second = second.iloc[0]
 
+            # If no solver was able to solve a single instance, there is no
+            # winner for this division.
+            if first.score_correct == 0:
+                continue
+
+            if sequential:
+                time_first =  first.score_cpu_time
+                time_second = second.score_cpu_time
+            else:
+                time_first =  first.score_wallclock_time
+                time_second = second.score_wallclock_time
+
             # Compute score and time distance between first and second in the
             # division.
             # Note: The time score is only used if solvers have the same score
             # lead.
             score = ((1 + first.score_correct) / (1 + second.score_correct))
-            time = ((1 + second.score_cpu_time) / (1 + first.score_cpu_time))
+            time = (1 + time_second) / (1 + time_first)
             scores.append((score,
                            time,
                            get_solver_name(first.solver_id),
@@ -836,14 +855,18 @@ def biggest_lead_ranking(data, sequential):
 # division if the results of 'solver' are excluded. This function corresponds
 # to function vbss(D,S) as defined in section 7.3.2 of the SMT-COMP'19 rules.
 #
-def vbss(division_data, solver_id):
+def vbss(division_data, solver_id, sequential):
 
-    # For VBS we only consider correctly solved benchmarks
-    data = division_data[(division_data.solver_id != solver_id)
-                         & (division_data.error == 0)]
+    # Remove 'solver_id' and compute the virtual best score and cpu_time.
+    data = division_data[division_data.solver_id != solver_id]
 
-    sort_columns = ['benchmark', 'score_correct', 'cpu_time']
+    sort_columns = ['benchmark', 'score_correct']
[…]

### 2019-07-04 rules/rules19.tex
Rules: Refine competition-wide recognitions.

@@
 individual sequential benchmark scores:
-$$\sum_{b\in M} \langle e_{S_b}, n_{S_b}, w_{S_b}, c_{S_b}\rangle$$.
+$$\sum_{b\in M} \langle e_b^s, n_b^s, w_b^s, c_b^s\rangle$$.
 
 \noindent
-A sequential division score $\langle e_S, n_S, c_S\rangle$ is better than a
-sequential division score $\langle e_S', n_S', c_S'\rangle$ iff $e_S < e_S'$ or
-($e_S = e_S'$ and $n_S > n_S'$) or ($e_S = e_S'$ and $n_S = n_S'$ and $c_S <
-c_S'$).  That is, fewer errors takes precedence over more correct solutions,
+A sequential division score $\langle e^s, n^s, c^s\rangle$ is better than a
+sequential division score $\langle e^{s'}, n^{s'}, c^{s'}\rangle$ iff
+$e^s < e^{s'}$ or ($e^s = e^{s'}$ and $n^s > n^{s'}$) or ($e^s = e^{s'}$ and
+$n_S = n^{s'}$ and $c^s < c^{s'}$).
+That is, fewer errors takes precedence over more correct solutions,
 which takes precedence over less CPU time taken.
@@
 
-Let $n_i^D$ be the correctness score of the $i$th solver (for a given scoring system e.g. number of correct results or reduction) in division $D$. The rank of division $D$ is given as
+Let $n_i^D$ be the correctness score of the $i$th solver (for a given scoring
+system e.g. number of correct results or reduction) in division $D$.
+The \emph{correctness rank} of division $D$ is given as
 \[
@@
 \]
-The \emph{biggest lead winner} is the winner of the division with the highest (largest) rank. This can be computed per scoring system.
+Let $c_i^D$ be the CPU time score of the $i$th solver in division $D$.
+The \emph{CPU time rank} of division $D$ is given as
+\vspace{-1ex}
+\[
+\frac{c_2^D+1}{c_1^D+1}
+\]
+Let $w_i^D$ be the wall-clock time score of the $i$th solver in division $D$.
+The \emph{wall-clock time rank} of division $D$ is given as
+\vspace{-1ex}
+\[
+\frac{w_2^D+1}{w_1^D+1}
+\]
+The \emph{biggest lead winner} is the winner of the division with the highest
+(largest) correctness rank. In case of a tie, the winner is determined as the
+solver with the higher corresponding CPU (resp. wall-clock) time rank for
+sequantial (resp. parallel) scoring.
+This can be computed per scoring system.
 
@@
 
-Let $\langle e_b^s, n_b^s, w_b^s, c_b^s \rangle$ be the parallel benchmark score for benchmark $b$ and solver $s$ (for a given scoring system e.g.
-$n$ is either number of correct results or reduction).
-The virtual best solver score for a division $D$ using solvers $S$ is given as 
+Let $\langle e^s, n^s, w^s, c^s \rangle$ be the parallel division score
+for solver $s$ (for a given scoring system, i.e., $n$ is either number of correct
+results or reduction).
+If the division error score $e^s > 0$, then solver $s$ is considered unsound
+and excluded from the ranking.
+If the number of sound competitive solvers~$S$ in a division $D$ is $|S| < 2$, 
+the division is excluded from the ranking.
+
+Let $\langle e_b^s, n_b^s, w_b^s, c_b^s \rangle$ be the parallel benchmark
+score for benchmark $b$ and solver $s$ (for a given scoring system). 
+The virtual best solver \emph{correctness score} for a division $D$ with 
+competitive sound solvers $S$ is given as 
 \[
-\mathit{vbss}(D,S) = \sum_{b \in D} {\sf min}\{ n_b^s \times c_b^s \mid s \in S ~\mathit{and}~ n_b^s > 0  \}
+\mathit{vbss}_n(D,S) = \sum_{b \in D} {\sf max}\{ n_b^s \mid s \in S ~\mathit{and}~ n_b^s > 0 \}
 \]
-where the minimum of an empty set is 0 (e.g.
-no contribution if a benchmark is unsolved).
-In other words, for the single query track, $\mathit{vbss}(D,S)$ is the smallest amount of time taken to solve all benchmarks solved in division $D$ using solvers in $S$.
-
-Let $S$ be the set of competitive solvers competing in division $D$. The rank of solver $s \in S$ in division $D$ is then
+where the maximum of an empty set is 0 (i.e., no contribution if a benchmark
+is unsolved).
+
+The virtual best solver \emph{CPU time score} $\mathit{vbss}_c$ and
+the virtual best solver \emph{wall-clock time score} $\mathit{vbss}_w$ for a
+division $D$ with competitive sound solvers $S$ is given as 
 \[
-1- \frac{\mathit{vbss}(D,S-s) }{ \mathit{vbss}(D,S)}
+\mathit{vbss}_c(D,S) = \sum_{b \in D} {\sf min}\{ c_b^s \mid s \in S ~\mathit{and}~ n_b^s > 0 \}
 \]
-e.g.
-the difference in virtual best solver score when removing $s$ from the computation.
-This will be a number between 0 and 1 with 0 indicating that $s$ made no impact on the \emph{vbss} and 1 indicating that $s$ is the only solver that solved anything in the division.
-%
-The \emph{largest contribution winner} is the solver across all divisions with the highest (largest) rank. Again, this can be computed per scoring system.
+\[
+\mathit{vbss}_w(D,S) = \sum_{b \in D} {\sf min}\{ w_b^s \mid s \in S ~\mathit{and}~ n_b^s > 0 \}
+\]
+where the minimum of an empty set is 2400 seconds
+(no solver was able to solve the benchmark).
+
+In other words, for the single query track,
+$\mathit{vbss}_c(D,S)$  and $\mathit{vbss}_w(D,S)$ is the
+smallest amount of CPU time and wall-clock time taken to solve all benchmarks
+solved in division $D$ using all sound competitive solvers in $S$.
+
+Let $S$ be the set of competitive solvers competing in division $D$.
+The \emph{correctness rank} $\mathit{vbss}_n$, the \emph{CPU time rank}
+$\mathit{vbss}_c$ and the \emph{wall-clock time rank} $\mathit{vbss}_w$
+of solver $s \in S$ in division $D$ are then defined as
+\[
+1- \frac{\mathit{vbss}_n(D,S-s) }{ \mathit{vbss}_n (D,S)}
+\hspace{3em}
+1- \frac{\mathit{vbss}_c(D,S) }{ \mathit{vbss}_c(D,S-s)}
+\hspace{3em}
+1- \frac{\mathit{vbss}_w(D,S) }{ \mathit{vbss}_w(D,S-s)}
+\]
+i.e., the difference in virtual best solver score when removing $s$ from the
+computation.
+
+These ranks will be numbers between 0 and 1 with 0 indicating that $s$ made no
+impact on the \emph{vbss} and 1 indicating that $s$ is the only solver that
+solved anything in the division.
+%
+The ranks for a division $D$ in a given track will be normalized by multiplying
+with $\frac{n_D}{N}$, where $n_D$ corresponds to the number of competitive
+solver/benchmark pairs in division $D$ and $N$ being the overall number of
+competitive solver/benchmark pairs of this track.
+
+The \emph{largest contribution winner} is the solver across all divisions with
+the highest (largest) normalized correctness rank. Again, this can be computed
+per scoring system. In case of a tie, the winner is determined as the solver
+with the higher corresponding normalized CPU (resp. wall-clock) time rank for
+sequential (resp. parallel) scoring.
 

### 2019-07-04 2019/prep/submitted/make_spaces.sh

@@ -11,6 +11,7 @@ IN_SPACE_INC="../incremental-space.xml"
 
 ### Benchmark selection
 SELECT_SQ="$SCRIPTDIR/../selection/single_query/benchmark_selection_single_query_2019_no_strings"
+SELECT_SQ_STRINGS="$SCRIPTDIR/../selection/single_query/benchmark_selection_single_query_2019_strings"
 
 SELECT_INC="$SCRIPTDIR/../selection/incremental/benchmark_selection_incremental_2019"
 SELECT_INC_UNKNOWN="$SCRIPTDIR/../selection/incremental/benchmark_selection_incremental_2019_status_unknown"
@@ -55,6 +56,7 @@ OUT_SPACE_SQ=
 OUT_SPACE_SQ_FIXED=
 OUT_SPACE_SQ_FIXED_NC=
 OUT_SPACE_SQ_2018=
+OUT_SPACE_SQ_STRINGS=
 # Challenge Track - non-incremental
 OUT_SPACE_CHALL_NON_INC=
 OUT_SPACE_CHALL_NON_INC_FIXED=
@@ -85,11 +87,13 @@ do
       echo
       echo "  options:"
       echo "    -h, --help           Print this message and exit"
-      echo "    --sq          <file> Single Query track output xml"
-      echo "    --sq-fixed    <file> Single Query track output xml for fixed"
-      echo "                         (non-competing) solvers"
-      echo "    --sq-2018     <file> Single Query track output xml for best "
-      echo "                         solvers 2018"
+      echo "    --sq          <file> Single Query track (no strings) output xml"
+      echo "    --sq-fixed    <file> Single Query track (no strings) output xml"
+      echo "                         for fixed (non-competing) solvers"
+      echo "    --sq-2018     <file> Single Query track (no strings) output xml"
+      echo "                         for best solvers 2018"
+      echo "    --sq-strings  <file> Single Query track (strings only) "
+      echo "                         output xml"
       echo "    --inc         <file> Incremental track output xml"
       echo "    --inc-unknown <file> Incremental track for benchmarks with"
[…]

### 2019-07-04 tools/prep/prepare_space_xml.py

@@ -203,6 +203,8 @@ def add_solvers_in_space(space, solvers):
 # Currently, this only considers non-competing solvers as given via '--nc'.
 def is_competitive(solvers):
     global g_args
+    if g_args.include_non_competitive:
+        return True
     count = len(solvers)
     for nc in g_args.non_competing:
         for s in solvers:
@@ -301,6 +303,10 @@ def main():
                         dest="excluded_solvers",
                         help="generate space excluding the listed "\
                              "solvers (StarExec IDs, wrapped IDs if -w)")
+    parser.add_argument("--include-non-competitive",
+                        default=False,
+                        action="store_true",
+                        help="include non-competitive divisions")
     g_args = parser.parse_args()
 
     if not os.path.exists(g_args.space_xml):

### 2019-07-04 tools/scoring/score.py
scoring script: Do not select winners with correct score 0.

@@ -976,9 +976,12 @@ def largest_contribution_ranking(data, time_limit, sequential):
 # Generate competition results and .md files for website
 
 def md_get_winner(df):
-    solver_id = df[(df.competitive == True) \
-                & (df['rank'] == 1)].iloc[0].solver_id
-    return get_solver_name(solver_id)
+    winner = df[(df.competitive == True) & (df['rank'] == 1)].iloc[0]
+    # If the first ranked solver has a score of 0, there are no winners for
+    # this division.
+    if winner.score_correct == 0:
+        return ''
+    return get_solver_name(winner.solver_id)
 
 def md_table_details(df, track, scoring, n_benchmarks):
     lines = ["{}:".format(scoring)]

### 2019-07-04 tools/process-results/merge_rerun_job_output.py
scoring script: Add support to write .md files for unsat core.

@@ -35,7 +35,7 @@ def main():
             print("error: given file does not exist: {}".format(csv))
             sys.exit(1)
         data.append(pandas.read_csv(csv, dtype=str, engine='python'))
-    result = pandas.concat(data, ignore_index=True)
+    result = pandas.concat(data, ignore_index=True, sort=True)
     result.sort_values('pair id', ascending=True, inplace=True)
     result.drop_duplicates(
                     keep='last',

### 2019-07-04 tools/scoring/score.py

@@ -998,7 +998,7 @@ def md_table_details(df, track, scoring, n_benchmarks):
             round(row.score_cpu_time, 3)))
         lines.append("  WallScore: {}".format(
             round(row.score_wallclock_time, 3)))
-        if track != OPT_TRACK_INC and track != OPT_TRACK_CHALL_INC:
+        if track == OPT_TRACK_SQ and track == OPT_TRACK_CHALL_SQ:
             lines.append("  solved: {}".format(
                 row.correct))
             lines.append("  solved_sat: {}".format(
@@ -1101,6 +1101,47 @@ def write_md_file_inc(division,
     outfile.write("\n".join([str_div, str_par, '---\n']))
 
 
+def write_md_file_uc(division,
+                     n_benchmarks,
+                     data_seq, data_par,
+                     year,
+                     path,
+                     ext_str,
+                     track,
+                     track_str,
+                     time):
+    # general info about the current division
+    str_div = \
+            "---\n"\
+            "layout: result_uc\n"\
+            "resultdate: {}\n"\
+            "division: {}\n"\
+            "track: {}\n"\
+            "n_benchmarks: {}\n"\
+            "time_limit: {}\n"\
+            "\n"\
+            "winner_seq: {}\n"\
+            "winner_par: {}\n"\
+            .format(datetime.datetime.now().strftime("%Y-%m-%d %H:%M:%S"),
+                    division,
+                    track_str,
+                    n_benchmarks,
+                    time,
+                    md_get_winner(data_seq),
+                    md_get_winner(data_par))
+    # division scores
+    str_seq   = md_table_details(data_seq, track, 'sequential', n_benchmarks)
+    str_par   = md_table_details(data_par, track, 'parallel', n_benchmarks)
+    # write md file
+    year_path = os.path.join(path, year)
+    if not os.path.exists(year_path): os.mkdir(year_path)
+    track_path = os.path.join(year_path, track)
+    if not os.path.exists(track_path): os.mkdir(track_path)
+    outfile = open(
+            os.path.join(track_path, "{}{}".format(division, ext_str)), "w")
+    outfile.write("\n".join([str_div, str_seq, str_par, '---\n']))
+
+
 def to_md_files(results_seq,
                 results_par,
                 results_sat,
@@ -1161,8 +1202,15 @@ def to_md_files(results_seq,
                               TRACK_INC,
                               time)
         elif track == OPT_TRACK_UC:
-            ext = EXT_UC
[…]

### 2019-07-04 tools/scoring/score.py
Fix

@@ -39,12 +39,12 @@ RESULT_SAT = 'sat'
 RESULT_UNSAT = 'unsat'
 
 # Tracks
-TRACK_SQ = "Single Query Track"
-TRACK_INC = "Incremental Track"
-TRACK_CHALL_SQ = "Challenge Track (non-incremental)"
-TRACK_CHALL_INC = "Challenge Track (incremental)"
-TRACK_UC = "Unsat Core Track"
-TRACK_MV = "Model Validation Track"
+TRACK_SQ = "track_single_query"
+TRACK_INC = "track_incremental"
+TRACK_CHALL_SQ = "track_single_query_challenge"
+TRACK_CHALL_INC = "track_incremental_challenge"
+TRACK_UC = "track_unsat_core"
+TRACK_MV = "track_model_validation"
 
 # Track options
 OPT_TRACK_SQ = "sq"
@@ -998,7 +998,7 @@ def md_table_details(df, track, scoring, n_benchmarks):
             round(row.score_cpu_time, 3)))
         lines.append("  WallScore: {}".format(
             round(row.score_wallclock_time, 3)))
-        if track == OPT_TRACK_SQ and track == OPT_TRACK_CHALL_SQ:
+        if track == OPT_TRACK_SQ or track == OPT_TRACK_CHALL_SQ:
             lines.append("  solved: {}".format(
                 row.correct))
             lines.append("  solved_sat: {}".format(

### 2019-07-04 tools/scoring/score.py
Add support for model validation track.

@@ -430,11 +430,22 @@ def score(division,
     unsat_core = 'reduction' in data.columns
     assert not unsat_core or 'result-is-erroneous' in data.columns
 
+    # Column 'model_validator_status' only exists in the model validation track.
+    model_validation = 'model_validator_status' in data.columns
+
     # Note: For incremental tracks we have to consider all benchmarks (also
     #       the ones that run into resource limits).
     if incremental:
         data_new['correct'] = data['correct-answers']
         data_new['error'] = data['wrong-answers']
+    # Note: The model validator reports INVALID if a solver crashes on an
+    #       instance. Hence, only when a solver reports statisfiable, we
+    #       check the status of the model validator.
+    elif model_validation:
+        data_new.loc[(data.result == RESULT_SAT)
+                     & (data.model_validator_status == 'VALID'), 'correct'] = 1
+        data_new.loc[(data.result == RESULT_SAT)
+                     & (data.model_validator_status == 'INVALID'), 'error'] = 1
     # Set correct/error column for solved benchmarks.
     else:
         # Filter job pairs based on given verdict. For the sat/unsat scoring

### 2019-07-04 tools/scoring/score.py
Add unsolved column.

@@ -325,6 +325,7 @@ def group_and_rank_solver(data, sequential):
         'score_wallclock_time': sum,
         'timeout' : sum,
         'memout' : sum,
+        'unsolved': sum,
         'competitive': 'first',
         'division_size': 'first',
         })
@@ -405,6 +406,7 @@ def score(division,
     data_new['competitive'] = data_new.solver_id.map(is_competitive_solver)
     data_new['timeout'] = 0
     data_new['memout'] = 0
+    data_new['unsolved'] = 0
 
     # Set the column that is used to determine if a benchmark was solved
     # within the time limit.
@@ -493,6 +495,8 @@ def score(division,
             data_new.loc[solved_sat.index, 'correct_sat'] = 1
             data_new.loc[solved_unsat.index, 'correct_unsat'] = 1
 
+    # Determine unsolved benchmarks.
+    data_new.loc[data_new.correct == 0, 'unsolved'] = 1
 
     # Set alpha_prime_b for each benchmark, set to 1 if family is not in the
     # 'family_scores' dictionary (use_families == False).
@@ -1017,7 +1021,7 @@ def md_table_details(df, track, scoring, n_benchmarks):
             lines.append("  solved_unsat: {}".format(
                 row.correct_unsat))
             lines.append("  unsolved: {}".format(
-                n_benchmarks - row.correct))
+                row.unsolved))
         lines.append("  timeout: {}".format(
             row.timeout))
         lines.append("  memout: {}".format(

### 2019-07-04 tools/scoring/score.py
scoring script: Add support for generating .md files for model validation track.

@@ -1149,19 +1149,20 @@ def write_md_file_inc(division,
     outfile.write("\n".join([str_div, str_par, '---\n']))
 
 
-def write_md_file_uc(division,
-                     n_benchmarks,
-                     data_seq, data_par,
-                     year,
-                     path,
-                     ext_str,
-                     track,
-                     track_str,
-                     time):
+def write_md_file_others(division,
+                         n_benchmarks,
+                         data_seq, data_par,
+                         year,
+                         path,
+                         ext_str,
+                         track,
+                         track_str,
+                         time,
+                         is_experimental=False):
     # general info about the current division
     str_div = \
             "---\n"\
-            "layout: result_uc\n"\
+            "layout: result_{}\n"\
             "resultdate: {}\n"\
             "division: {}\n"\
             "track: {}\n"\
@@ -1170,7 +1171,8 @@ def write_md_file_uc(division,
             "\n"\
             "winner_seq: {}\n"\
             "winner_par: {}\n"\
-            .format(datetime.datetime.now().strftime("%Y-%m-%d %H:%M:%S"),
+            .format('exp' if is_experimental else 'others',
+                    datetime.datetime.now().strftime("%Y-%m-%d %H:%M:%S"),
                     division,
                     track_str,
                     n_benchmarks,
@@ -1250,7 +1252,7 @@ def to_md_files(results_seq,
                               TRACK_INC,
                               time)
         elif track == OPT_TRACK_UC:
-            write_md_file_uc(division,
+            write_md_file_others(division,
                              n_benchmarks,
                              data_seq, data_par,
                              year,
@@ -1260,8 +1262,16 @@ def to_md_files(results_seq,
                              TRACK_UC,
                              time)
         elif track == OPT_TRACK_MV:
-            ext = EXT_MV
-            track_str = TRACK_MV
+            write_md_file_others(division,
+                                 n_benchmarks,
+                                 data_seq, data_par,
+                                 year,
+                                 path,
+                                 EXT_MV,
+                                 track,
+                                 TRACK_MV,
+                                 time,
+                                 OPT_TRACK_MV in g_args.exp_tracks)
         elif track == OPT_TRACK_CHALL_SQ:
             write_md_file_sq(division,
                              n_benchmarks,
@@ -1427,6 +1437,11 @@ def parse_args():
                                  OPT_TRACK_MV, OPT_TRACK_CHALL_SQ,
[…]

### 2019-07-04 tools/scoring/score.py
Fix sequential/parallel for model validation track. (#14)

@@ -432,20 +432,14 @@ def score(division,
 
     # Column 'model_validator_status' only exists in the model validation track.
     model_validation = 'model_validator_status' in data.columns
+    if model_validation:
+        data_new['model_validator_status'] = data['model_validator_status']
 
     # Note: For incremental tracks we have to consider all benchmarks (also
     #       the ones that run into resource limits).
     if incremental:
         data_new['correct'] = data['correct-answers']
         data_new['error'] = data['wrong-answers']
-    # Note: The model validator reports INVALID if a solver crashes on an
-    #       instance. Hence, only when a solver reports statisfiable, we
-    #       check the status of the model validator.
-    elif model_validation:
-        data_new.loc[(data.result == RESULT_SAT)
-                     & (data.model_validator_status == 'VALID'), 'correct'] = 1
-        data_new.loc[(data.result == RESULT_SAT)
-                     & (data.model_validator_status == 'INVALID'), 'error'] = 1
     # Set correct/error column for solved benchmarks.
     else:
         # Filter job pairs based on given verdict. For the sat/unsat scoring
@@ -479,6 +473,15 @@ def score(division,
         if unsat_core:
             data_new.loc[solved.index, 'correct'] = data['reduction']
             data_new.loc[solved.index, 'error'] = data['result-is-erroneous']
+        # Note: The model validator reports INVALID if a solver crashes on an
+        #       instance. Hence, only when a solver reports statisfiable, we
+        #       check the status of the model validator.
+        elif model_validation:
+            solved = solved[solved.result == RESULT_SAT]
+            solved_valid = solved[solved.model_validator_status == 'VALID']
+            solved_invalid = solved[solved.model_validator_status == 'INVALID']
+            data_new.loc[solved_valid.index, 'correct'] = 1
+            data_new.loc[solved_invalid.index, 'error'] = 1
         else:
             data_new.loc[solved.index, 'correct'] = 1
 

### 2019-07-04 tools/scoring/score.py
Add unsolved column. (#13)

@@ -325,6 +325,7 @@ def group_and_rank_solver(data, sequential):
         'score_wallclock_time': sum,
         'timeout' : sum,
         'memout' : sum,
+        'unsolved': sum,
         'competitive': 'first',
         'division_size': 'first',
         })
@@ -405,6 +406,7 @@ def score(division,
     data_new['competitive'] = data_new.solver_id.map(is_competitive_solver)
     data_new['timeout'] = 0
     data_new['memout'] = 0
+    data_new['unsolved'] = 0
 
     # Set the column that is used to determine if a benchmark was solved
     # within the time limit.
@@ -496,6 +498,8 @@ def score(division,
             data_new.loc[solved_sat.index, 'correct_sat'] = 1
             data_new.loc[solved_unsat.index, 'correct_unsat'] = 1
 
+    # Determine unsolved benchmarks.
+    data_new.loc[data_new.correct == 0, 'unsolved'] = 1
 
     # Set alpha_prime_b for each benchmark, set to 1 if family is not in the
     # 'family_scores' dictionary (use_families == False).
@@ -1020,7 +1024,7 @@ def md_table_details(df, track, scoring, n_benchmarks):
             lines.append("  solved_unsat: {}".format(
                 row.correct_unsat))
             lines.append("  unsolved: {}".format(
-                n_benchmarks - row.correct))
+                row.unsolved))
         lines.append("  timeout: {}".format(
             row.timeout))
         lines.append("  memout: {}".format(

### 2019-07-05 tools/process-results/merge_rerun_job_output.py
Fix

@@ -35,7 +35,7 @@ def main():
             print("error: given file does not exist: {}".format(csv))
             sys.exit(1)
         data.append(pandas.read_csv(csv, dtype=str, engine='python'))
-    result = pandas.concat(data, ignore_index=True, sort=True)
+    result = pandas.concat(data, ignore_index=True, sort=False)
     result.sort_values('pair id', ascending=True, inplace=True)
     result.drop_duplicates(
                     keep='last',

### 2019-07-09 2019/slides/SMT-COMP-2019-slides.tex
Add slides.

\documentclass[10pt]{beamer}
%\usepackage[sfdefault,light]{FiraSans}
%\usepackage{FiraSans}
%\usepackage{FiraMono}
\usetheme{metropolis}

\usepackage{xspace}
\usepackage{tikz}
\usepackage{amsmath}
\usepackage{pdfpages}
\usepackage{graphics}

\usetikzlibrary{shapes,arrows,positioning,decorations.markings,matrix,fit}
\tikzstyle{line} = [draw,line width=.7pt,fill=none]
\tikzstyle{node} = [draw,circle,minimum width=2em]
\tikzstyle{leaf} = [draw,rectangle,minimum width=2em,minimum height=2em]

\newcommand{\trib}{{\small\raisebox{.75pt}{$\triangleright$}}\xspace}
\newcommand{\tribb}{{\small\raisebox{.75pt}{$\blacktriangleright$}}\xspace}
\newcommand{\tribo}{{\small\raisebox{.75pt}{\textcolor{mLightBrown}{$\blacktriangleright$}}}}

\newcommand{\indtrib}{\hspace*{1em}\trib}
\newcommand{\indtribb}{\hspace*{1em}\tribb}

\definecolor{mBlue}{RGB}{4,110,152}
\definecolor{mGreen}{RGB}{115,180,85}
\definecolor{mRed}{RGB}{205,90,80}
\definecolor{mYellow}{RGB}{230,195,35}
\definecolor{mOrange}{HTML}{EB811B}
\definecolor{mGrey}{RGB}{125,130,140}

\newcommand{\red}[1]{\textcolor{mRed}{#1\xspace}}
\newcommand{\orange}[1]{\textcolor{mLightBrown}{#1}}
\newcommand{\green}[1]{\textcolor{mGreen}{#1\xspace}}
\newcommand{\blue}[1]{\textcolor{mBlue}{#1\xspace}}
\newcommand{\gray}[1]{\textcolor{mGrey}{#1\xspace}}

\newcommand{\akey}[1]{\texttt{#1}\xspace}

\newcommand{\orangea}{\ensuremath{\textcolor{mLightBrown}{\longrightarrow}}\xspace}

\usetikzlibrary{shapes,arrows,positioning,decorations.markings,matrix,fit}
\tikzstyle{line} = [draw, -latex',line width=.7pt,fill=none]
\pgfdeclarelayer{background}
\pgfdeclarelayer{foreground}
\pgfsetlayers{background,main,foreground}

\setbeamertemplate{itemize subitem}{$\circ$}

\title{SMT-COMP 2019\\[2ex]
{\normalsize 14th International
Satisfiability Modulo Theories Competition}}

\author{
  Liana Hadarean \and
  Antti Hyv\"{a}rinen \and
  \underline{Aina Niemetz} \and
  Giles Reger
}

\institute{}

\date{
  \vspace{10ex}
  SMT Workshop, July 7-8, 2019, Lisbon, Portugal
}

\begin{document}
  \maketitle

  \begin{frame}{SMT-COMP}
    \begin{itemize}
      \setbeamertemplate{itemize items}{\orangea}
      \item annual competition for \orange{SMT solvers}
      \item on (a selection of) benchmarks from \orange{SMT-LIB}
    \end{itemize}
    \vspace{1ex}
    \begin{itemize}
      \item first held in \orange{2005}
      \item \orange{2013}: evaluation instead of competition
      \item since \orange{2014}: hosted by StarExec
    \end{itemize}
    \vspace{1ex}
    \textbf{Goals}
    {\vspace{-1ex}\small
    \begin{itemize}
      \setbeamertemplate{itemize items}{$\circ$}
      \item encourage \orange{scientific advances} in SMT solvers
      \item stimulate community to explore \orange{shared challenges}
      \item promote \orange{tools} and their usage
      \item engage and include \orange{new members} of the community
      \item support the \orange{SMT-LIB} project to promote and develop the
        SMT-LIB format and collect relevant benchmarks
    \end{itemize}
    }
  \end{frame}

  \begin{frame}{Participants}
    \textbf{SMT solver:} determine (un)satisfiability 
    of benchmarks from SMT-LIB
    {\small
    \begin{itemize}
      \item \textbf{SMT Solvers} in the `classical' sense
      \item \textbf{Wrapper Tools:} call one or more other SMT solvers
      \item \textbf{Derived Tools:} based on and extends another SMT solver
      \item \textbf{Automated Theorem Provers} (e.g., Vampire)
    \end{itemize}
    }
    \vspace{2ex}
    \begin{itemize}
      \setbeamertemplate{itemize items}{\orangea}
      \item \orange{New} system description mandatory 
      \item \orange{New} naming convention for derived tools
    \end{itemize}
  \end{frame}

  \begin{frame}{Tracks}
    \begin{itemize}
      \item \textbf{Single Query Track} (previously: Main Track)
        \begin{itemize}
          \item one \textbf{single} \akey{check-sat} command,
            no \akey{push}/\akey{pop} commands
          \item \orange{New} \textbf{remove} benchmarks solved by all solvers 
            in 2018 in $\leq 1s$
          \item \orange{New} \textbf{selection} of benchmarks
          \item \orange{New} \textbf{time limit:} 2400s (40 min)
        \end{itemize}
      \vspace{4ex}
      \item \textbf{Incremental Track} (previously: Application Track)
        \begin{itemize}
          \item \textbf{multiple} \akey{check-sat} and \akey{push}/\akey{pop} commands
          \item solvers are executed on benchmarks via \textbf{trace executor}
          \item \orange{New} \textbf{selection} of benchmarks
          \item \orange{New} \textbf{keep} benchmarks with first \akey{check-sat}
            status \akey{unknown}
          \item \orange{New} execute solver \textbf{beyond} first status
            \akey{unknown} \akey{check-sat} call
          \item \textbf{time limit:} 2400s (40 min)
        \end{itemize}
    \end{itemize}
  \end{frame}

  \begin{frame}{Tracks}
    \begin{itemize}
      \item \textbf{Unsat Core Track}
        \begin{itemize}
          \item one \textbf{single} \akey{check-sat} command,
                \textbf{multiple} \akey{assert} commands
          \item benchmarks with \textbf{status \akey{unsat}}
          \item extract \textbf{unsat core} as set of top-level assertions
          \item \orange{New} \textbf{remove} benchmarks with a single \akey{assert} command
          \item \orange{New} \textbf{selection} of benchmarks
          \item \textbf{time limit:} 2400s (40 min)
        \end{itemize}
    \end{itemize}
  \end{frame}

  \begin{frame}{Tracks}
    \begin{itemize}
      \item \orange{New:} \textbf{Challenge Track}
        \begin{itemize}
          \item two subtracks: \orange{non-incremental} and \orange{incremental}
          \item benchmarks that were \textbf{nominated} by their submitters for
            this track
          \item \textbf{time limit:} 43200s (12 hours)
        \end{itemize}
      \vspace{4ex}
      \item \orange{New:} \textbf{Model Validation Track} (\orange{experimental})
        \begin{itemize}
          \item one \textbf{single} \akey{check-sat} command,
          \item \textbf{selection} of benchmarks with \textbf{status \akey{sat}}
          \item produce full, correct, well-formed
            \textbf{model} in SMT-LIB format
          \item \textbf{only} for division QF\_BV
          \item \textbf{time limit:} 2400s (40 min)
        \end{itemize}
      \end{itemize}
  \end{frame}

  \begin{frame}{Divisions}
    \begin{itemize}
      \setbeamertemplate{itemize items}{\orangea}
      \item \textbf{Tracks} are split into divisions
      \item \textbf{Divisions} correspond to \orange{logics} in SMT-LIB
    \end{itemize}
    \begin{itemize}
      \item solvers are submitted to divisions in a track
      \item \textbf{winners} are declared
        \begin{itemize}
          \item per division and track
          \item with respect to different scoring schemes per track
        \end{itemize}
      \vspace{1ex}
      \item \orange{New} do not run \textbf{non-competitive} divisions
    \end{itemize}
  \end{frame}

  \begin{frame}{Benchmark Selection}
    \begin{itemize}
      \item \orange{2015-2018}: \textbf{all} eligible benchmarks in a division
        \begin{itemize}
          \setbeamertemplate{itemize items}{$\longrightarrow$}
          \item results more predictable
          \item more of an evaluation than a competition
          \item Main Track (2018):
            \begin{itemize}
              \setbeamertemplate{itemize items}{$\circ$}
              \item 78\% solved by all participating solvers
              \item 71\% solved in $\leq 1s$
              \item in 7 out of 46 divisions $> 99\%$ solved by all solvers
            \end{itemize}
        \end{itemize}
      \vspace{1ex}
      \item \orange{New} alternative benchmark selection
        \begin{itemize}
          \item \textbf{remove} easy/uninteresting benchmarks
            \begin{itemize}
              \item SQ:
                all benchmarks solved by all solvers in $\leq 1 s$ in 2018
              \item UC: all benchmarks with only a single assertion
            \end{itemize}

          \item \textbf{cap} number of instances in a division
            \begin{itemize}
              \item $n \leq 300$: all instances
              \item $300 < n \leq 600$: 300 instances
              \item $n > 600$: 50\% of the logic
            \end{itemize}

          \item guarantee inclusion of \textbf{new} benchmarks
            (at least one per family)

          \item select benchmarks randomly using a uniform distribution
        \end{itemize}
    \end{itemize}
  \end{frame}

  \begin{frame}{Single Query and Unsat Core Track Scoring}
    \begin{itemize}
      \item \orange{2016-2018}:
        \textbf{weighted} with respect to benchmark family size
        \begin{itemize}
          \setbeamertemplate{itemize items}{$\longrightarrow$}
          \item \textbf{goal:} de-emphasize large benchmark families
          \item fairly complicated, not necessarily intuitive
          \item complicates comparing paper and competition results
        \end{itemize}
      \vspace{2ex}
      \item \textbf{Competition report} for 2015-2018 (under review):
        \begin{itemize}
          \setbeamertemplate{itemize items}{\orangea}
          \item families \textbf{no significant impact} on the (weighted)
            scores
            \begin{itemize}
              \setbeamertemplate{itemize items}{$\circ$}
              \item problems with scoring script (2016-2018)
              \item incorrect interpretation of benchmark family 
              \item \textbf{after fix:} only one change
              (2017 AUFNIRA: CVC4 over Vampire)
            \end{itemize}
          \item \textbf{unweighted:} only 7 out of 139 winners in
            2016-2018 change
      \end{itemize}
      \vspace{2ex}
      \item \orange{New} drop weighted scoring, use \textbf{unweighted} scheme
        from 2015
    \end{itemize}
  \end{frame}

  \begin{frame}{Scores}
    \begin{itemize}
      \item \textbf{Single Query, Challenge (non-incremental):}\\
        number of correctly solved instances
      \vspace{1ex}
      \item \textbf{Incremental, Challenge (incremental):}\\
        number of correctly solved \akey{check-sat} calls
      \vspace{1ex}
      \item \textbf{Unsat Core:}\\
        reduction in terms of top-level assertions
      \vspace{1ex}
      \item \textbf{Model Validation:}\\
        number of correctly solved instances with validated models
    \end{itemize}
  \end{frame}

  \begin{frame}{Scores}
    \begin{itemize}
      \item \textbf{sequential score} (SQ, CHSQ, UC, MV)\\
        time limit applied to CPU time
      \vspace{1ex}
      \item \textbf{parallel score} (all)\\
        time limit applied to wall-clock time
      \vspace{1ex}
      \item \orange{New} \textbf{sat score} (SQ, CHSQ)\\
        parallel score for satisfiable instances
      \vspace{1ex}
      \item \orange{New} \textbf{unsat score} (SQ, CHSQ)\\
        parallel score for unsatisfiable instances
      \vspace{1ex}
      \item \orange{New} \textbf{24s score} (SQ, CHSQ)\\
        parallel score for time limit of 24s
    \end{itemize}
  \end{frame}

  \begin{frame}{Competition-Wide Recognitions}
    \begin{itemize}
      \item \orange{2014-2018}:
        \begin{itemize}
          \setbeamertemplate{itemize items}{$\circ$}
          \item \textbf{competition-wide scores} as weighted sum of division
            scores
          \item emphasis on number of entered divisions
        \end{itemize}
      \vspace{1ex}
    \item \orange{New} replace with \textbf{two new competition-wide
      rankings}
      \begin{itemize}
        \setbeamertemplate{itemize items}{$\longrightarrow$}
        \item focus on measures that make sense to compare between divisions
        \item for all scores in a track
        \setbeamertemplate{itemize items}{$\circ$}
      \end{itemize}
      \vspace{1ex}
      \item \orange{\textbf{biggest lead}}
        \begin{itemize}
          \item in terms of \textbf{score} over the solver in the second place
          \item \textbf{tie:} ranked by biggest lead in CPU/wall-clock time
        \end{itemize}
      \vspace{1ex}
        \item \orange{\textbf{largest contribution}}
          \begin{itemize}
            \item ranked by contribution to \textbf{virtual best solver}
              in terms of \textbf{score}
            \item \textbf{tie:} ranked by largest contribution in terms of
              CPU/wall-clock time
          \end{itemize}
    \end{itemize}
  \end{frame}

  \begin{frame}{Competition Overview}

    {\footnotesize
      \begin{tabular}{r|r@{\hspace{.75em}}r|r@{\hspace{.75em}}r|r@{\hspace{.75em}}r@{\hspace{.75em}}r}
        & \multicolumn{2}{c}{\textbf{Solvers}}
        & \multicolumn{2}{|c}{\textbf{Divisions}}
        & \multicolumn{3}{|c}{\textbf{Benchmarks}} \\
        \textbf{Track}
        & \textbf{Total}
        & \textbf{C/NC}
        & \textbf{Total}
        & \textbf{C/NC/Exp}
        & \textbf{C}
        & \textbf{Selected}
        & \textbf{Total}
        \\
        \hline
        SQ    & 51 (\orange{+27}) &  37/\gray{14} & 57 (\orange{+7}) & 49/\gray{6}/2 & 64156 & 89817 & 327041 \\
        Inc   & 22 (\orange{+16}) &  14/\gray{8}  & 29 (\orange{+8}) & 24/\gray{5}/0 &  6835 &  7567 & 14030 \\
        CHSQ  & 21 (\orange{+21}) &  15/\gray{6}  &  3 (\orange{+3}) &  3/\gray{0}/0 &    29 &    29 & 29 \\
        CHInc & 12 (\orange{+12}) &   7/\gray{5}  &  3 (\orange{+3}) &  3/\gray{0}/0 &    22 &    22 & 22 \\
        UC    & 14 (\orange{+9})  &   8/\gray{6}  & 38 (\orange{-6}) & 33/\gray{5}/0 & 29808 & 44341 & 136012\\
        MV    & 10 (\orange{+10}) &  10/\gray{0}  &  1 (\orange{+1}) &  1/\gray{0}/0 &  7191 &  7191 & 14382 \\
      \end{tabular}
      \begin{center}
        C \ldots Competitive
        \hspace{1.5em}NC \ldots Non-Competitive
        \hspace{1.5em}Exp \ldots Experimental\\
      \end{center}
    }

    \vfill
    \textbf{Teams}: 23 (\alert{+6})\\
    \textbf{StarExec Stats}: 21.4 years CPU time; 1,022,802 job pairs
    \vfill
  \end{frame}

  \begin{frame}{Non-Competitive Solvers}
    \textbf{Total:} \textbf{\orange{14}} (SQ), \textbf{\orange{8}} (Inc),
    \textbf{\orange{6}} (CHSQ),
    \textbf{\orange{5}} (CHINC), \textbf{\orange{6}} (UC)
    \begin{itemize}
      \item submitted by \textbf{organizers}
        \begin{itemize}
          \item Z3 4.8.4
          \item best solvers 2018 (SQ: 9, Inc: 5, CHSQ: 3, CHINC: 3, UC: 5)
        \end{itemize}
      \vspace{1ex}
      \item submitted by \textbf{participants}
        \begin{itemize}
          \item 2 derived tools (Boolector-ReasonLS, CVC4-SymBreak)
          \item 3 fixed solver versions (1 x CVC4, 2 x STP)
        \end{itemize}
    \end{itemize}
  \end{frame}

\begin{frame}{Solver Presentations}
  \begin{center}
    Boolector, COLIBRI, CVC4, MathSAT, OpenSMT, SPASS-SATT,
    Vampire,
    VeriT
    Yices
  \end{center}
\end{frame}

{
  \setbeamercolor{background canvas}{bg=}
  \includepdf[pages=1-]{solvers/boolector.pdf}
  \includepdf[pages=1-2]{solvers/colibri.pdf}
  \includepdf[pages=1-]{solvers/cvc4.pdf}
  \includepdf[pages=1-]{solvers/opensmt.pdf}
  \includepdf[pages=1-]{solvers/SPASS-SATT2.pdf}
  \includepdf[pages=1-]{solvers/vampire.pdf}
  \includepdf[pages=1-]{solvers/verit.pdf}
  \includepdf[pages=1-]{solvers/yices.pdf}
  \includepdf[pages=1]{solvers/mathsat.pdf}
  \includepdf[pages=4]{solvers/mathsat.pdf}
}

  \begin{frame}{Results}
    \begin{center}
    \resizebox{.9\textwidth}{!}{
      \includegraphics{results.png}
    }
    \end{center}
  \end{frame}

  \begin{frame}{Competition-Wide Recognitions}
    \begin{center}
      {\Huge Trophies}
    \end{center}
  \end{frame}

  \begin{frame}{Trophies: Largest Contribution}

    \begin{tabular}{rrr}
      \hline
      \textbf{Single Query}
      & \textbf{1\textsuperscript{st} Place}
      & \textbf{2\textsuperscript{nd} Place} \\
      seq   & \textbf{\orange{CVC4}} (QF\_NIA)  & \textbf{Vampire} (UF) \\
      par   & \textbf{\orange{CVC4}} (QF\_NIA)  & \textbf{Vampire} (UF) \\
      sat   & \textbf{\orange{Par4}} (AUFLIRA)  & \textbf{SMTInterpol} (UFLIA) \\
      unsat & \textbf{\orange{Par4}} (UFNIA)    & \textbf{Vampire} (UF) \\
      24s   & \textbf{\orange{Vampire}} (UF)    & \textbf{Par4} (UFNIA) \\
      \hline
      \hline

      \textbf{Incremental}
      & \textbf{1\textsuperscript{st} Place}
      & \textbf{2\textsuperscript{nd} Place} \\
      par &  \textbf{\orange{CVC4}} (UFLRA) & \textbf{Boolector} (QF\_BV) \\
      \hline
      \hline

      \textbf{Unsat Core}
      & \textbf{1\textsuperscript{st} Place}
      & \textbf{2\textsuperscript{nd} Place} \\
      seq & \textbf{\orange{CVC4}} (AUFLIRA) & \textbf{MathSAT} (QF\_NIA) \\
      par & \textbf{\orange{CVC4}} (AUFLIRA) & \textbf{MathSAT} (QF\_NIA) \\
      \hline
      \hline

      \textbf{Challenge}
      & \textbf{1\textsuperscript{st} Place}
      & \textbf{2\textsuperscript{nd} Place} \\
      par & \textbf{\orange{Yices}} (QF\_AUFBV) & \textbf{Boolector} (QF\_ABV) \\
      \hline

    \end{tabular}
  \end{frame}

  \begin{frame}{Trophies: Biggest Lead}

    \begin{tabular}{rrr}
      \hline
      \textbf{Single Query}
      & \textbf{1\textsuperscript{st} Place}
      & \textbf{2\textsuperscript{nd} Place} \\
      seq   &  \textbf{\orange{CVC4}} (FP)       &  \textbf{Par4} (UFBV) \\
      par   &  \textbf{\orange{CVC4}} (FP)       &  \textbf{Par4} (UFBV) \\
      sat   &  \textbf{\orange{CVC4}} (AUFDTLIA) &  \textbf{Par4} (AUFLIRA) \\
      unsat &  \textbf{\orange{CVC4}} (BVFP)     &  \textbf{SMT-RAT} (QF\_NIRA) \\
      24s   &  \textbf{\orange{CVC4}} (BVFP)     &  \textbf{Par4} (UFBV) \\
      \hline
      \hline

      \textbf{Incremental}
      & \textbf{1\textsuperscript{st} Place}
      & \textbf{2\textsuperscript{nd} Place} \\
      par & \textbf{\orange{CVC4}} (ANIA)  & \textbf{Yices} (QF\_AUFBV) \\
      \hline
      \hline

      \textbf{Unsat Core}
      & \textbf{1\textsuperscript{st} Place}
      & \textbf{2\textsuperscript{nd} Place} \\
      seq & \textbf{\orange{CVC4}} (UFLIA) &  \textbf{Yices} (QF\_AX) \\
      par & \textbf{\orange{CVC4}} (UFLIA) &  \textbf{Yices} (QF\_AX) \\
      \hline
      \hline

      \textbf{Challenge}
      & \textbf{1\textsuperscript{st} Place}
      & \textbf{2\textsuperscript{nd} Place} \\
      par & \textbf{\orange{Yices}} (QF\_AUFBV) & \textbf{Boolector} (QF\_ABV) \\
      \hline
    \end{tabular}
  \end{frame}

  \begin{frame}{Discussion}
    \begin{itemize}
      \item \textbf{time limit}
        \begin{itemize}
          \item increased back to 2400s (from 1200s 2017-2018) in SQ track
          \item only \orange{$-3953$} instances if cut off at \textbf{1200s}
            (sequential score)
          \item \orange{$\sim50\%$} of the timeouts in \textbf{quantified}
            divisions
          \vspace{2ex}
          \setbeamertemplate{itemize items}{\orangea}
          \item run selected challenging benchmarks in the \textbf{challenge track}
          \vspace{1ex}
          \item \textbf{decrease} time limit (maybe even further) for \textbf{other tracks}
          \vspace{1ex}
          \item shorter time limit for \textbf{quantified divisions}?
            \\
            (typically: solved within short time or ``never")
        \end{itemize}
    \end{itemize}
  \end{frame}

  \begin{frame}{Discussion}
    \begin{itemize}
      \item \textbf{divisions}
        \begin{itemize}
          \item size of competitions is getting out of hand
          \item this year we didn't run non-competitive divisions
          \vspace{2ex}
          \setbeamertemplate{itemize items}{\orangea}
          \item \textbf{don't run} if less than 3? 4? competitive participants?
        \end{itemize}
      \vspace{2ex}
      \item \textbf{parallel score}
        \begin{itemize}
          \setbeamertemplate{itemize items}{$\circ$}
          \item StarExec only offers 4 cores per job
          \item not interesting for real parallelism
          \vspace{1ex}
          \setbeamertemplate{itemize items}{\orangea}
          \item \textbf{future plans:} dedicated \textbf{parallel track}
          \item would require to move away from StarExec
        \end{itemize}
      \end{itemize}
  \end{frame}

  \begin{frame}{Discussion}
    \begin{itemize}
      \item \textbf{portfolio wrapper tools}
        \begin{itemize}
          \item wrapper tools allowed to participate without restrictions
          \vspace{1ex}
          \item problems with portfolio
            (not author of the wrapped solvers)
            \begin{itemize}
              \setbeamertemplate{itemize items}{$\rightarrow$}
              \item win with simple script and work of other teams
              \item negative/unfair impact on competition-wide rankings
              \item progress of non-portfolio tools harder to distinguish
            \end{itemize}
          \vspace{1ex}
          \item disallowing wrapper tools entirely is problematic (example: Vampire)
          \vspace{2ex}
          \setbeamertemplate{itemize items}{\orangea}
          \item \textbf{disallow} portfolio with wrapped solvers from other teams?
          \vspace{1ex}
          \item only allow \textbf{non-competitive} submission?
          \vspace{1ex}
          \item at least \textbf{exclude} them from competition-wide recognitions
          \vspace{1ex}
          \item \textbf{similar issues} with SATzilla-style systems
        \end{itemize}
    \end{itemize}
  \end{frame}

  \begin{frame}{Ackknowledgements}
    \begin{itemize}
      \item Mathias Preiner (benchmark selection and scoring scripts)
      \item Aaron Stump (StarExec)
      \item Andres N\"{o}tzli (trace executor extension)
      \item Marco Gario and Andrea Micheli (PySMT)
      \item Martin Riener (certificates/trophies logistics)
    \end{itemize}
  \end{frame}
\end{document}

### 2019-07-09 tools/scoring/score.py

@@ -851,7 +851,6 @@ def biggest_lead_ranking(data, sequential):
     data = data[data['competitive'] == True]
     scores = dict()
     for year, ydata in data.groupby('year'):
-        scores[year] = []
         for division, div_data in ydata.groupby('division'):
             # Skip non-competitive divisions
             if not is_competitive_division(div_data.solver_id.unique()):
@@ -883,12 +882,14 @@ def biggest_lead_ranking(data, sequential):
             # lead.
             score = ((1 + first.score_correct) / (1 + second.score_correct))
             time = (1 + time_second) / (1 + time_first)
+            if year not in scores: scores[year] = []
             scores[year].append((score,
                            time,
                            get_solver_name(first.solver_id),
                            get_solver_name(second.solver_id),
                            division))
-        scores[year] = sorted(scores[year], reverse=True)
+        if year in scores:
+            scores[year] = sorted(scores[year], reverse=True)
 
 #        scores_sorted = sorted(scores[year], reverse=True)
 #        print('{} Biggest Lead Ranking'.format(year) +
@@ -1017,14 +1018,15 @@ def largest_contribution_ranking(data, time_limit, sequential):
 
         # Normalize scores based on division job pairs/total job pairs as defined
         # in section 7.3.2 of the SMT-COMP'19 rules.
-        weighted_scores[year] = []
         for tup in scores_top:
             impact_score, impact_time, n_solvers, n_benchmarks = tup[:4]
             weight = n_solvers * n_benchmarks / num_job_pairs_total
             w_score, w_time = impact_score * weight, impact_time * weight
+            if year not in weighted_scores: weighted_scores[year] = []
             weighted_scores[year].append(
                 (w_score, w_time, n_solvers, n_benchmarks, tup[4], tup[5]))
-        weighted_scores[year] = sorted(weighted_scores[year], reverse=True)
+        if year in weighted_scores:
+            weighted_scores[year] = sorted(weighted_scores[year], reverse=True)
         #print('Largest Contribution Ranking')
         #for s in sorted(weighted_scores[year], reverse=True):
         #    print(s)
@@ -1094,6 +1096,7 @@ def write_md_file_sq(division,
             "track: {}\n"\
             "n_benchmarks: {}\n"\
             "time_limit: {}\n"\
[…]

### 2019-07-09 tools/scoring/score.py
Fix unsolved column for sat/unsat scoring tables.

@@ -463,13 +463,15 @@ def score(division,
         # either the expected status is sat/unsat or a solver solves the
         # instance.
         if filter_result:
+            # Save original result for  determining unsolved benchmarks
+            data_new['result_orig'] = data_new['result']
+
             expected = set([filter_result, RESULT_UNKNOWN])
             data_with_result = \
                 data_new[(data_new.expected == filter_result)
                          | ((data_new.result == filter_result)
                             & (data_new.expected.isin(expected)))]
             benchmarks = set(data_with_result.benchmark.unique())
-            #data_new = data_new[data_new.benchmark.isin(benchmarks)]
             data_new.loc[~data_new.benchmark.isin(benchmarks),
                          ['cpu_time', 'wallclock_time', 'result']] = \
                             [0.0, 0.0, RESULT_UNKNOWN]
@@ -513,7 +515,28 @@ def score(division,
             data_new.loc[solved_unsat.index, 'correct_unsat'] = 1
 
         # Determine unsolved benchmarks.
-        data_new.loc[data_new.correct == 0, 'unsolved'] = 1
+        # If 'filter_result' is given, a benchmark is unsolved if:
+        # 1) expected is 'filter_result' and the benchmark is unsolved
+        # 2) expected is RESULT_UNKNOWN and at least one solver was able to
+        #    solve the benchmark with result != 'filter_result'.
+        # For example, for the sat score we don't consider benchmarks as
+        # unsolved if they are either expected to be unsatisfiable or solved as
+        # unsatisfiable
+        if filter_result:
+            # Filter solved unknown benchmarks with a result other than
+            # 'filter_result'.
+            solved_unknowns =
+                data_new[(data_new.expected == RESULT_UNKNOWN)
+                         & (data_new.result_orig != filter_result)
+                         & (data_new.result_orig != RESULT_UNKNOWN)]
+            benchmarks = set(solved_unknowns.benchmark.unique())
+            expected = set([filter_result, RESULT_UNKNOWN])
+            data_new.loc[(data_new.correct == 0)
+                         & data_new.expected.isin(expected)
+                         & ~data_new.benchmark.isin(unknowns),
+                         'unsolved'] = 1
+        else:
+            data_new.loc[data_new.correct == 0, 'unsolved'] = 1
 
     # Set alpha_prime_b for each benchmark, set to 1 if family is not in the
     # 'family_scores' dictionary (use_families == False).

### 2019-08-16 2018/report/SMT-COMP.tex
Fix broken reference to www.satcompetition.org

@@
 The SMT Competition is one of a growing number of tool competitions in the broad area of formal methods, which are summarised in a recent review of the area~\cite{toolympics}.
-The two closest competitions in terms of goals and design are the SAT competition (\url{https://www.satcompetition.org/}), which evaluates SAT solvers, and CASC (\url{http://www.tptp.org/CASC/}), which evaluates automated theorem provers (ATPs).
+The two closest competitions in terms of goals and design are the SAT competition (\url{http://www.satcompetition.org/}), which evaluates SAT solvers, and CASC (\url{http://www.tptp.org/CASC/}), which evaluates automated theorem provers (ATPs).
 In recent years, we have seen a blurring of lines between SMT-COMP and CASC with SMT solvers competing in CASC and ATPs competing in SMT-COMP.

### 2019-08-16 2018/report/SMT-COMP.tex
Delete trailing whitespace
permitted -> allowed
lacking -> inadequate

@@
 2018.  Anyone may submit new benchmarks to the SMT Library, and
-competitors are permitted to tune their solvers accordingly.
+competitors are allowed to tune their solvers accordingly.
 Therefore all benchmarks eligible for the competition must be released
@@
 discontinued partly because of the competition's move to StarExec and
-lacking tool support.  It was re-introduced as an experimental track
+inadequate tool support.  It was re-introduced as an experimental track
 in 2016, and has been a regular competition track again since~2017.
@@
 ({DT})---which were new in~2017---were excluded from the Unsat-Core
-track because of lacking tool support.  In~2018, 3,603~benchmarks were
+track because of inadequate tool support.  In~2018, 3,603~benchmarks were
 excluded because they contained named terms (a feature of the SMT-LIB

### 2019-08-16 2018/report/SMT-COMP.tex
Comma

@@
 were excluded because they contained partial or underspecified
-operations (e.g., bit-vector division) whose precise semantics were
+operations (e.g., bit-vector division), whose precise semantics were
 being debated at the time.  Additionally in~2016, one benchmark was

### 2019-08-16 2018/report/SMT-COMP.tex
Affiliated with IJCAR in 2018

@@
 major conference in the field of automated reasoning each year: with
-CAV in 2015, with IJCAR in 2016, again with CAV in 2017, and with FLoC
-in~2018.  Consequently, its date varies.  Competition results were
-presented on July~19 in 2015, on July~2 in 2016, on July~23 in 2017,
-and on July~13 in~2018.
+CAV in 2015, with IJCAR in 2016, again with CAV in 2017, and with
+IJCAR (as part of FLoC) in~2018.  Consequently, its date varies.
+Competition results were presented on July~19 in 2015, on July~2 in
+2016, on July~23 in 2017, and on July~13 in~2018.
 

### 2019-08-16 2018/report/SMT-COMP.tex
Add parentheses for clarity

@@
 been part of the competition in 2012~\cite{CGBD12}, but was then
-discontinued partly because of the competition's move to StarExec and
-inadequate tool support.  It was re-introduced as an experimental track
+discontinued (partly because of the competition's move to StarExec and
+inadequate tool support).  It was re-introduced as an experimental track
 in 2016, and has been a regular competition track again since~2017.

### 2019-08-16 2018/report/SMT-COMP.tex
and -> while

@@
 there were disagreements on 79 benchmarks; in 2017, only one benchmark
-was removed; and in 2018, there were no disagreements between
+was removed; while in 2018, there were no disagreements between
 otherwise sound solvers.

### 2019-08-16 2018/report/SMT-COMP.tex
executing -> exercising
are also taking -> were taken

@@
 versions of a solver in case the number of solver submissions is too large for
-the computational resources. In the past four years, executing this right was
+the computational resources. In the past four years, exercising this right was
 not necessary.
@@
 but non-competing solver $B$ actually ranked best if non-competing solvers
-are also taking into consideration.
+were taken into consideration.
 Entries

### 2019-08-16 2018/report/SMT-COMP.tex
Add "that it"

@@
 The reasons for non-entry into the competition are orthogonal to their suitability for the competition.
-Indeed, Z3 has been entered into the competition competitively in the past and one can assume was trained on the current problems (as much as any solver is).
+Indeed, Z3 has been entered into the competition competitively in the past and one can assume that it was trained on the current problems (as much as any solver is).
 Finally, the fact that industrial-strength solvers perform well in the competition supports the notion that the benchmarks in the competition are industrially relevant.

### 2019-08-16 2018/report/SMT-COMP.tex
Comma

@@
 Interestingly, it decreased from 2015 to 2016 by 3.5\%.
-This is mainly due to the fact that in 2015, more than 5600 benchmarks of
+This is mainly due to the fact that, in 2015, more than 5600 benchmarks of
 division QF\_FP where solved by one of the two participating configurations of

### 2019-08-16 2018/report/SMT-COMP.tex
degression -> regression

@@
 In 2016, performance decreased by 185625 correct answers (0.61\%),
-which can be entirely attributed to a performance degression
+which can be entirely attributed to a performance regression
 of Z3 on 2 benchmarks in the QF\_NIA division.

### 2019-08-16 2018/report/SMT-COMP.tex
highly -> in high position

@@
 breadth of solver participation---a solver participating in many
-logics does not need to be the best in any one of them to rank highly.
+logics does not need to be the best in any one of them to rank in high
+position.
 
@@
 the best three solvers according to this ranking for 2015--2018.  Also
-shown is Z3, which ranked highly each year but was running hors
-concours.  Sequential and parallel performance are reported
+shown is Z3, which ranked in high position each year but was running
+hors concours.  Sequential and parallel performance are reported
 separately.
@@
 
-Solvers that rank highly in the competition-wide ranking
+Solvers that rank in high position in the competition-wide ranking
 (Section~\ref{sec:floc}) often also solve many benchmarks uniquely,

### 2019-08-16 2018/report/SMT-COMP.tex
has relatively few -> has few
a benchmarks -> a benchmark

@@
 (Section~\ref{sec:floc}) often also solve many benchmarks uniquely,
-but there are exceptions.  For instance, SMTInterpol has relatively
-few unique solutions, despite achieving third place in the
-competition-wide ranking in~2017 and~2018.  However, almost every
-(sound) solver in the competition solves at least some benchmarks
-uniquely, and hence contributes to the state-of-the-art.
+but there are exceptions.  For instance, SMTInterpol has few unique
+solutions, despite achieving third place in the competition-wide
+ranking in~2017 and~2018.  However, almost every (sound) solver in the
+competition solves at least some benchmarks uniquely, and hence
+contributes to the state-of-the-art.
 
@@
 Table~\ref{table:benchmarks-main-track}.  For the \apptrack, this analysis is
-less meaningful since a benchmarks usually contains a multitude of both
+less meaningful since a benchmark usually contains a multitude of both
 satisfiable and unsatisfiable incremental queries

### 2019-08-16 2018/report/SMT-COMP.tex
Add "analysis"
Comma

@@
 new 24 seconds score introduced in SMT-COMP 2019 and was inspired by a use case
-at Amazon.} in the \maintrack.  As in the previous, this highlights the
+at Amazon.} in the \maintrack.  As in the previous analysis, this highlights the
 different winners under this new scheme only. Here we see STP winning a
@@
 Relatively few changes would have occurred.
-Unsurprisingly the differences are in the larger and more structured divisions.
+Unsurprisingly, the differences are in the larger and more structured divisions.
 

### 2019-08-16 2018/report/SMT-COMP.tex
not Vampire -> not by Vampire

@@
 Whilst producing these results we noticed that the description of what constitutes a family had been incorrectly interpreted by the scoring scripts in 2016-2018.
-After fixing this misinterpretation we note that only a single division winner changes - in 2017 AUFNIRA should have been won by CVC4 and not Vampire.
+After fixing this misinterpretation we note that only a single division winner changes---in 2017 AUFNIRA should have been won by CVC4 and not by Vampire.
 

### 2019-08-16 2018/report/SMT-COMP.tex
figures -> numbers
reproducibility -> replicability; minor other changes

@@
 
-The use of StarExec ensures the \emph{reproducibility} of the competition.
-The publicly accessible space \url{https://www.starexec.org/starexec/secure/explore/spaces.jsp?id=2641} stores all of the information required to rerun the competition e.g.
-all benchmarks and copies of all tools.
-In addition, a GitHub organisation (\url{https://github.com/SMT-COMP/smt-comp}) has been setup to archive previous results and store the tools used by organisers to run the competition.
+The use of StarExec ensures the \emph{replicability} of the competition.
+The publicly accessible space \url{https://www.starexec.org/starexec/secure/explore/spaces.jsp?id=2641} stores all of the information required to rerun the competition, e.g., all benchmarks and copies of all tools.
+In addition, a GitHub organization (\url{https://github.com/SMT-COMP/smt-comp}) has been set up to archive previous results and store the tools used by organizers to run the competition.
 
@@
 
-Table~\ref{table:participation-by-track} summarizes these figures and
+Table~\ref{table:participation-by-track} summarizes these numbers and
 shows how many solver versions were submitted to each track of the

### 2019-08-16 2018/report/Reviews_67398_Revised_Response.txt
Add response to the reviews for the revised version

> *** Review 1 ***
>
>  The paper overall improved since the first submission, but there are still issues to be fixed, some of them already reported in the review of the first version.
>
>  * Organization
>
> - information about ranking should all stay in the related section, while
> there are related information, e.g. in the first part of Section 7 - Results.

TODO

> - outline of the content of Section 8 describes only part of its content (the first three sub-sections).

TODO

> * Quality
>
> - The paper still contains a number of issues, minor or not, detailed at the end of this review.
>
> -  In Section 2 the fact that "appointment should happen ... " is of relative interest and could be omitted. The same holds for the day in which the events took place.

TODO

> * Rules
>
> - basically incorrect results are "ignored" by omitting the benchmark if the status is not known - this comment still remains. The authors updated the text. I see their points and analysis, which I appreciated, through I think that this is an issue that should be dealt with more care. Correctness is very important for solvers when checking in particular real benchmarks (HW- and SW-verification, etc).

TODO

> * Significance of the results
>
>  - the paper and its analysis now contain many numbers and data, which is very appropriate for e competition report in my opinion. But, basically, no explanation is in place. What I expect to get out of a report, other than commenting the numbers, is their explanation, e.g.: what are the techniques implemented in solvers that overall performed better? Rr better, what techniques implemented in solvers led to an efficient solvers on a particular benchmark? why such techniques led to positive results on benchmarks with (a) given structure/characteristics?

TODO

>  - last paragraph of Section 7.1 that gives motivations for MathTSAT and Z3 to be industrial-strenght tool, and states Z3 training, are either not clear or somehow not convincing as motivations. The paragraph should be clarified, or can be omitted.

TODO

>  - Table 16 should not consider, in my opinion, divisions in which there was only one sound solvers, otherwise the concept of "solved uniquely" is trivially true.

TODO

>  * Relation to other competitions
>
>  - in the conclusions section authors mention the changes that will be implemented in 2019: it would be interesting to state which of the changes mentioned are already in place in other related solver's competitions (e.g., SAT, ASP, QBF, SV ...) .

TODO

>  * Minor points
>
>  Introduction
>
>  - "Hence there is" ->  - "Hence there is" ->

WONTFIX (comment is unclear)

>  - there is reference broken at pg. 2

DONE (http:// instead of https:// for www.satcompetition.org)

>  Section 2
>
>  - does the event was co-located with any conference in particular in 2018?

DONE (affiliated with IJCAR in 2018)

>  - "permitted" -> "allowed"

DONE

>  Section 3
>
>  - "increased by" -> "increased of" ?

WONTFIX

>  Section 4
>
>  - "discontinued partly" -> "partly discontinued" ?

DONE (added parentheses for clarity)

>  - "lacking tool support" -> "lacking of tool support" (This recurs later.)

DONE (lacking -> inadequate)

>  - "whose precise" ->  ", whose precise"

DONE

>  - "DT" looks not to be introduced

TODO

>  - the concept of "benchmarks families" is used at the beginning of pg. 7 but it has not been introduced

TODO

>  - "and in 2018, there were" ->   "while in 2018, there were"

DONE

> - e \in \{0,1 \} is defined, but than it is said to be the number of returned statuses...are they aligned? Please clarify

TODO

> Section 6
>
> - "executing" -> "performing"

DONE (executing -> exercising)

> - there is an huge space at pg. 14

TODO

> - Table 9: there are two team members for solver STP that miss affiliation

TODO

> - "Table 11 summarizes these figures". It would be probably useful to explicitly mention the figure numbers

DONE (figures -> numbers)

> Section 7
>
> - "are also taking" -> "were taken"

DONE

> - referring in the text to colors may not be a good choice for b/w printing

TODO

> - In Sec. 7.1 "assume was trained" -> "assume that it was trained"

DONE

> Section 8
>
> - "the fact that in 2015," ->  "the fact that, in 2015,"

DONE

>  - "degression of Z3" ?

DONE

>  - "rank highly" -> "rank in high position" ? (This recurs later.)

DONE

>  - "has relatively few" -> "has few"

DONE

>  - "quotient" -> "ratio" ?

TODO

>  - "a benchmarks" ->  "a benchmark"

DONE

>  - "problem" and "benchmark" are used for the same concept here. Maybe they can be unified

TODO

>  - in Table 17, does 1.0 means they are sequential? In case these numbers could be omitted

WONTFIX (we do not know for sure if those solvers are sequential; and
with these numbers present, the table also indicates whether a solver
was submitted in a given year)

>  - "As in the previous, this" -> "As in the previous analysis, this"

DONE

>  - "Unsurprisingly the" ->   "Unsurprisingly, the"

DONE

>  - "and not Vampire." -> - "and not by Vampire."

DONE

>  Section 9
>
> - "The last FLoC Olympiad was a period of ..." -> are you referring to "the time between the two FLoC Olympiads" ?

WONTFIX (yes; and this is correct usage of the word Olympiad)

>  References
>
>  They could be made more uniform, e.g.
>
>  - [7] vs. [12], where the same journal is referred with contracted form or full name

DONE

>  - Isn't [13] a CADE paper? In case, the way the conference name is mentioned is very different to [14], which is a CADE paper as well

DONE

>  - [38] contains the only acronym for journal name

DONE

> ============================================
>
> *** Review 2 ***
>
> ummary: This is a much improved revision of this paper. I'm very happy to see
> the additional sections and paragraphs, especially Sec 8! I think this paper is
> ready for publication, modulo a few minor (essentially typesetting) issues (see
> below).
>
> Details:
>
> 4.1 Scoring: A good addition. I think it would be great if the changes to the
> scoring system over the years would be analyzed, to see whether they did indeed
> have the intended effect. This has been started in 8.6, but a more
> comprehensive analysis would be great (possibly as a separate submission here
> or elsewhere).

TODO

> (28), Tbl 7: Thanks for the revision of the table, but I'm not sure listing
> more team members to "the best of our knowledge" is a good idea. If I were to
> do that, I would be bound to miss someone... Maybe just list the main
> institution? Or perhaps ask the submitter who they would want to be listed? I
> think there should be enough time to do that.

TODO

> General: Gray and grey are the worst colors to use. On my (Xerox color-laser)
> printer, all of the gray text in tables and figures are almost or completely
> unreadable. For instance, on white (bleached) paper there is not even a faint
> trace of the gray vertical line in Figures 3/4; I had to switch to the screen
> to see what this refers to.

TODO

> Fig 5/6: These could be significantly smaller :)

TODO

> Fig 3/4: Starting the X-axis at an arbitrary point is always a bit fishy. This
> way, any tiny difference can be overemphasized to achieve any level of
> impressiveness that the author choses. For instance, 144k vs 136k instances
> (casually read off the plot) is a 3.5% increase, but this is an irrelevant
> detail as explained in the text. All four series are also of exactly the same
> shape. I think a cactus plot is simply not the right tool for this job.

TODO

> ============================================
>
> *** Review 3 ***
>
>
> This is a revised version of a paper describing
> the years 2015-2018 of the SMT competition.
> The important changes requested last time were addressed,
> and new content was added in Section 8,
> which discusses interesting questions
> and adds substantial value to the paper.
>
> There are only a few minor improvements that should be made before publication:
>
> In the definition of the raw benchmark score (Sect. 4.1),
> it is not clear why CPU time is bounded at 4T
> (the fact that only 4 cores are available only comes later).

TODO

> In the remainder of Sect. 4.1, the term "benchmark family" is used,
> but this is never defined.
> This could be added to the definitions part in the beginning of Sect. 4.

TODO

> In the definition of "Competition-Wide Score (Main Track)",
> it says "since the weight already takes".
> This seems like the weighted division score is used as input for this computation,
> but another sentence of this definition explicitly uses
> the solver's raw score for this computation.
> So what weight is referred to here?

TODO

> In tables 3-5, please keep the regular numbers right-aligned.
> In LaTeX, the easiest way to do this is probably to use separate columns
> for the regular numbers and the number in brackets,
> and potentially shrink the space between each pair of columns.

TODO

> It is said that "StarExec ensures the reproducibility of the competition".
> If we use the terminology of ACM
> (https://www.acm.org/publications/policies/artifact-review-badging),
> the better term would be "replicability" instead of "reproducibility",
> because StarExec allows a different team to replicate the results
> with the same experimental setup.

DONE

> In the next sentence, commas should be placed before and after "e.g.".

DONE

> For tables 7-9, a smaller font size could be used
> (like in Table 12).

TODO

> The first paragraph of Sect. 8 mentions only three aspects,
> but more aspects are analyzed.

TODO

> Figure 5 seems unnecessary, because the difference is not visible anyway.
> Just listing the numbers would be sufficient.

TODO

> Especially in Sect. 8, there are many larger numbers.
> For readability, it would be better if all numbers larger than 9999
> would use a thin space as thousand separator,
> e.g., $1\,000\,000$ or using siunitx which can do this automatically
> with \num{1000000}.
> (Please do not use other characters as thousand separator
> because this can be confusing for international readers.)

TODO

> In Sect. 8.4, it would be better to refer to bounded model checking
> instead of just model checking.
> Other model checking algorithms use many SMT queries
> where the discussed property does not hold.

DONE

> On the middle of page 2, there is an unresolved reference ([?]).

DONE

> Footnote 1 is on the wrong page.

TODO

### 2019-08-19 2018/report/SMT-COMP.tex
Focussing -> Focusing
model checking -> bounded model checking
Participants tables (minor)
Use siunitx's \num command

@@
 \usepackage{enumitem}
+\usepackage{siunitx}
 
@@
 on StarExec.  Users of SMT solvers are encouraged to submit new and
-interesting benchmarks to the library, which has grown from 1,352
-benchmarks in~2005~\cite{BdMS05} to 347,011 benchmarks in 2018.
+interesting benchmarks to the library, which has grown from \num{1352}
+benchmarks in~2005~\cite{BdMS05} to \num{347011} benchmarks in 2018.
 
@@
 
-The 2018 release of the SMT Library contained 336,844 non-incremental
-benchmarks in 51 logics, as well as~10,167 incremental benchmarks
+The 2018 release of the SMT Library contained \num{336844} non-incremental
+benchmarks in 51 logics, as well as~\num{10167} incremental benchmarks
 (with a total of nearly 32 million {\tt check-sat} commands) in 26
@@
 number of benchmarks has increased by~68\,\%.  The largest benchmark
-in the 2018 release had a size of 1,041~MB; the total size of the
+in the 2018 release had a size of \num{1041}~MB; the total size of the
 release was 91~GB.
@@
 Some benchmarks typically have to be
-excluded for syntactic reasons: in 2015 and 2016, 11,966 benchmarks
+excluded for syntactic reasons: in 2015 and 2016, \num{11966} benchmarks
 were excluded because they contained partial or underspecified
@@
 excluded because it contained incorrect status information.  In~2017,
-1,104 benchmarks were excluded because their logic had been classified
+\num{1104} benchmarks were excluded because their logic had been classified
 incorrectly, and 8~benchmarks were excluded because of incorrect or
@@
 ({DT})---which were new in~2017---were excluded from the Unsat-Core
-track because of inadequate tool support.  In~2018, 3,603~benchmarks were
+track because of inadequate tool support.  In~2018, \num{3603}~benchmarks were
 excluded because they contained named terms (a feature of the SMT-LIB
@@
 
-\paragraph{Benchmark Weights (\maintrack and \ucoretrack 2016-2018).} The \emph{weight} of a
+\paragraph{Benchmark Weights (\maintrack and \ucoretrack 2016--2018).} The \emph{weight} of a
 benchmark in the main track is computed as $\alpha = (1 + \ln F)/F$,
@@
 
-\paragraph{Weighted Division Scores (\maintrack and \ucoretrack 2016-2018).}
+\paragraph{Weighted Division Scores (\maintrack and \ucoretrack 2016--2018).}
 The \emph{(weighted) score} of a solver in a division of the \maintrack and
@@
 SMT Competition from~2015 to~2018.  Over this period, the number has
-grown by~72\,\%, from~1,028,615 job pairs in~2015 to~1,776,062 job
+grown by~72\,\%, from~\num{1028615} job pairs in~2015 to~\num{1776062} job
 pairs in~2018.  (This is the number of unique solver/benchmark
@@
 infrastructure, are not included.)  For comparison, the~2014
-competition only ran~339,714 job pairs~\cite{CDW14}.
+competition only ran~\num{339714} job pairs~\cite{CDW14}.
 
@@
         plot/pdf/cactus_plot-Virtual_Best_Solver_(VBS)_Main_Track_2015-2018.pdf}}
-  \caption{VBS on common benchmarks 2015-2018 of all logics in the \maintrack
+  \caption{VBS on common benchmarks 2015--2018 of all logics in the \maintrack
   with a time limit of 1200s. Number of common benchmarks is indicated with a
@@
   within a time limit of 2400s
-  on common benchmarks 2016-2018 of all logics in the \ucoretrack.}
+  on common benchmarks 2016--2018 of all logics in the \ucoretrack.}
   \label{fig:progress-all-uc}
@@
 %
-Between 2014 (67426 benchmarks) and 2015 (154238 benchmarks),
-the number of common benchmarks is 67070;
-between 2015 and 2016 (154424 benchmarks) it is 154238;
-between 2016 and 2017 (238758 benchmarks) it is 145236;
-and between 2017 and 2018 (333241 benchmarks) it is 226429.
+Between 2014 (\num{67426} benchmarks) and 2015 (\num{154238} benchmarks),
+the number of common benchmarks is \num{67070};
+between 2015 and 2016 (\num{154424} benchmarks) it is \num{154238};
+between 2016 and 2017 (\num{238758} benchmarks) it is \num{145236};
+and between 2017 and 2018 (\num{333241} benchmarks) it is \num{226429}.
 The number of solved instances on these sets of common benchmarks
@@
 Interestingly, it decreased from 2015 to 2016 by 3.5\%.
-This is mainly due to the fact that, in 2015, more than 5600 benchmarks of
+This is mainly due to the fact that, in 2015, more than \num{5600} benchmarks of
 division QF\_FP where solved by one of the two participating configurations of
-Z3 that no one else could solve, and in 2016 Z3 did not participate in this
+Z3 that no one else could solve, and in~2016 Z3 did not participate in this
 division.
@@
 of 2400s (the time limit of the \apptrack in the competitions
-2015-2018).
+2015--2018).
 The total number of eligible \texttt{check-sat} queries (i.e., all queries with
 status sat or unsat up to the first query with status unknown) on
-common benchmarks from 2015-2018 is 30370517.
+common benchmarks from 2015--2018 is \num{30370517}.
 Figure~\ref{fig:progress-all-app} visualizes VBS performance on these
@@
 which naturally does not leave a lot of room for improvement.
-In 2016, performance decreased by 185625 correct answers (0.61\%),
+In 2016, performance decreased by \num{185625} correct answers (0.61\%),
 which can be entirely attributed to a performance regression
@@
 of 2400s (the time limit of the \ucoretrack in the competitions
-2016-2018).
+2016--2018).
 Figure~\ref{fig:progress-all-app} visualizes VBS performance on the common
-benchmarks (91455 total) from 2016-2018 as a bar plot.
-For 32377 of these benchmarks, extracting an unsat core is trivial since
+benchmarks (\num{91455} total) from 2016--2018 as a bar plot.
+For \num{32377} of these benchmarks, extracting an unsat core is trivial since
 they contain only one single \texttt{assert} command.
@@
 
-\subsection{Focussing on Satisfiability or Unsatisfiability}
+\subsection{Focusing on Satisfiability or Unsatisfiability}
 
 In many cases, an SMT application produces either mainly satisfiable or mainly
-unsatisfiable queries to the SMT solver.  A typical example is model checking,
+unsatisfiable queries to the SMT solver.  A typical example is bounded model checking,
 where a query is only satisfiable if a property of the model does not hold.  As
@@
 
-Whilst producing these results we noticed that the description of what constitutes a family had been incorrectly interpreted by the scoring scripts in 2016-2018.
+Whilst producing these results we noticed that the description of what constitutes a family had been incorrectly interpreted by the scoring scripts in 2016--2018.
 After fixing this misinterpretation we note that only a single division winner changes---in 2017 AUFNIRA should have been won by CVC4 and not by Vampire.
@@
 from~12 (for 2005--2014) to~26 (for 2015--2018).  The number of
-SMT-LIB benchmarks used in the competition increased from~77,352
-in~2014~\cite{CDW14} to 342,498 in 2018.  This is partly because new
+SMT-LIB benchmarks used in the competition increased from~\num{77352}
+in~2014~\cite{CDW14} to \num{342498} in 2018.  This is partly because new
 benchmarks were added to the SMT Library, but also because benchmarks
@@
 divisions to 115 in~2018, up from just 40 divisions
-in~2014~\cite{CDW14}.  The number of job pairs increased from 339,714
-in~2014 to~1,776,062~in 2018, and the total wall-clock time in~2018
+in~2014~\cite{CDW14}.  The number of job pairs increased from \num{339714}
+in~2014 to~\num{1776062} in 2018, and the total wall-clock time in~2018
 exceeded 7.6~years.  By these measures, the SMT Competition is one of

### 2019-08-19 2018/report/SMT-COMP.tex
Complete outline for Section 8 (Further Analysis)

@@
 Beyond the competition rankings, the competition data provides ample
-opportunity for further analysis.  Here, we report on three additional
-aspects: progress in solver performance, number of uniquely solved
-benchmarks, and use of parallelism in SMT solvers.
+opportunity for further analysis.  Here, we report on several
+additional aspects: progress in solver performance, number of uniquely
+solved benchmarks, use of parallelism in SMT solvers, performance on
+satisfiable versus unsatisfiable benchmarks, performance for a low
+time limit, and the impact of benchmark families and of benchmarks
+with unknown status.
 

### 2019-08-19 2018/report/SMT-COMP.tex
Table 3 (Main Track benchmarks): right-aligned numbers

@@
   \caption{Number of benchmarks used in the \maintrack (by division).
-Numbers in brackets indicate the (rounded) percentage of problems with different statuses, which are (sat/unsat) in 2015 and 2016, and (sat/unsat/unknown) in 2017 and 2018.}
+Numbers in parentheses indicate the (rounded) percentage of problems with different statuses, which are (sat/unsat) in 2015 and 2016, and (sat/unsat/unknown) in 2017 and 2018.}
   \label{table:benchmarks-main-track}
   \centering
-  \scalebox{.9}[.775]{\begin{tabular}{lrrrr}
+  \scalebox{.9}[.775]{\begin{tabular}{lr@{\hskip3pt}cr@{\hskip3pt}cr@{\hskip3pt}cr@{\hskip3pt}c}
     \toprule
-    Division & \multicolumn{1}{c}{2015} & \multicolumn{1}{c}{2016} & \multicolumn{1}{c}{2017} & \multicolumn{1}{c}{2018} \\
+    Division & \multicolumn{2}{c}{2015} & \multicolumn{2}{c}{2016} & \multicolumn{2}{c}{2017} & \multicolumn{2}{c}{2018} \\
     \midrule
-    ABVFP & - & - & - & 1 \gray{(0/0/100)}\\
-    ALIA & 42 \gray{(2/98)} & 42 \gray{(2/98)} & 42 \gray{(2/98/0)} & 42 \gray{(2/98/0)}\\
-    AUFBVDTLIA & - & - & 1709 \gray{(0/1/98)} & 1709 \gray{(0/1/98)}\\
-    AUFDTLIA & - & - & 728 \gray{(0/0/100)} & 728 \gray{(0/0/100)}\\
-    AUFLIA & 4 \gray{(25/75)} & 4 \gray{(25/75)} & 4 \gray{(25/75/0)} & 4 \gray{(25/75/0)}\\
-    AUFLIRA & 19849 \gray{(1/99)} & 19849 \gray{(1/99)} & 20011 \gray{(0/99/1)} & 20011 \gray{(0/99/1)}\\
-    AUFNIRA & 1050 \gray{(0/100)} & 1050 \gray{(0/100)} & 1480 \gray{(0/71/29)} & 1480 \gray{(0/71/29)}\\
-    BV & 85 \gray{(34/66)} & 85 \gray{(34/66)} & 5151 \gray{(2/2/97)} & 5751 \gray{(10/86/4)}\\
-    BVFP & - & - & - & 24 \gray{(0/0/100)}\\
-    FP & - & - & - & 61 \gray{(0/0/100)}\\
-    LIA & 201 \gray{(5/95)} & 201 \gray{(5/95)} & 388 \gray{(38/60/2)} & 388 \gray{(38/60/2)}\\
-    LRA & 339 \gray{(6/94)} & 339 \gray{(6/94)} & 2419 \gray{(17/46/38)} & 2419 \gray{(29/64/8)}\\
-    NIA & 9 \gray{(67/33)} & 9 \gray{(67/33)} & 14 \gray{(43/29/29)} & 14 \gray{(43/29/29)}\\
-    NRA & 3788 \gray{(0/100)} & 3788 \gray{(0/100)} & 3811 \gray{(0/100/0)} & 3813 \gray{(0/100/0)}\\
-    QF\_ABV & 14720 \gray{(68/32)} & 14720 \gray{(68/32)} & 15061 \gray{(69/31/0)} & 15066 \gray{(69/31/0)}\\
-    QF\_ABVFP & - & - & - & 18129 \gray{(78/22/1)}\\
-    QF\_ALIA & 134 \gray{(40/60)} & 139 \gray{(42/58)} & 139 \gray{(42/58/0)} & 139 \gray{(42/58/0)}\\
-    QF\_ANIA & 6 \gray{(0/100)} & 8 \gray{(0/100)} & 8 \gray{(0/100/0)} & 8 \gray{(0/100/0)}\\
-    QF\_AUFBV & 37 \gray{(16/84)} & 37 \gray{(16/84)} & 31 \gray{(19/81/0)} & 31 \gray{(19/81/0)}\\
-    QF\_AUFLIA & 1009 \gray{(49/51)} & 1009 \gray{(49/51)} & 1009 \gray{(49/51/0)} & 1009 \gray{(49/51/0)}\\
-    QF\_AUFNIA & 21 \gray{(29/71)} & 21 \gray{(29/71)} & 17 \gray{(29/71/0)} & 17 \gray{(29/71/0)}\\
-    QF\_AX & 551 \gray{(49/51)} & 551 \gray{(49/51)} & 551 \gray{(49/51/0)} & 551 \gray{(49/51/0)}\\
-    QF\_BV & 26414 \gray{(35/65)} & 26414 \gray{(35/65)} & 40043 \gray{(32/59/8)} & 40102 \gray{(36/64/0)}\\
-    QF\_BVFP & 7 \gray{(14/86)} & 7 \gray{(14/86)} & 17215 \gray{(81/18/0)} & 17215 \gray{(81/18/0)}\\
-    QF\_DT & - & - & 8000 \gray{(0/0/100)} & 8000 \gray{(45/55/0)}\\
-    QF\_FP & 34413 \gray{(50/50)} & 34413 \gray{(50/50)} & 40302 \gray{(50/50/1)} & 40300 \gray{(50/50/1)}\\
-    QF\_IDL & 2094 \gray{(61/39)} & 2094 \gray{(61/39)} & 2193 \gray{(58/37/5)} & 2193 \gray{(58/37/4)}\\
-    QF\_LIA & 5839 \gray{(51/49)} & 5839 \gray{(51/49)} & 6141 \gray{(52/46/2)} & 6947 \gray{(55/43/1)}\\
-    QF\_LIRA & 6 \gray{(17/83)} & 6 \gray{(17/83)} & 7 \gray{(14/71/14)} & 7 \gray{(14/71/14)}\\
-    QF\_LRA & 1626 \gray{(61/39)} & 1626 \gray{(61/39)} & 1649 \gray{(57/41/2)} & 1649 \gray{(57/41/1)}\\
-    QF\_NIA & 8475 \gray{(98/2)} & 8593 \gray{(96/4)} & 23876 \gray{(59/13/28)} & 23876 \gray{(59/20/20)}\\
-    QF\_NIRA & 2 \gray{(0/100)} & 2 \gray{(0/100)} & 3 \gray{(0/67/33)} & 3 \gray{(0/67/33)}\\
-    QF\_NRA & 10184 \gray{(52/48)} & 10245 \gray{(52/48)} & 11354 \gray{(44/47/10)} & 11489 \gray{(44/47/9)}\\
-    QF\_RDL & 220 \gray{(49/51)} & 220 \gray{(49/51)} & 255 \gray{(43/44/13)} & 255 \gray{(43/44/13)}\\
-    QF\_SLIA & - & - & - & 72705 \gray{(0/0/100)}\\
-    QF\_UF & 6649 \gray{(38/62)} & 6649 \gray{(38/62)} & 6650 \gray{(38/62/0)} & 7423 \gray{(42/58/0)}\\
-    QF\_UFBV & 31 \gray{(0/100)} & 31 \gray{(0/100)} & 31 \gray{(0/100/0)} & 1224 \gray{(53/47/0)}\\
-    QF\_UFIDL & 441 \gray{(24/76)} & 441 \gray{(24/76)} & 428 \gray{(25/75/0)} & 428 \gray{(25/75/0)}\\
-    QF\_UFLIA & 598 \gray{(67/33)} & 598 \gray{(67/33)} & 583 \gray{(69/31/0)} & 583 \gray{(69/31/0)}\\
-    QF\_UFLRA & 1627 \gray{(48/52)} & 1627 \gray{(48/52)} & 1284 \gray{(60/40/0)} & 1284 \gray{(60/40/0)}\\
-    QF\_UFNIA & 7 \gray{(0/100)} & 7 \gray{(0/100)} & 7 \gray{(0/100/0)} & 7 \gray{(0/100/0)}\\
-    QF\_UFNRA & 34 \gray{(47/53)} & 34 \gray{(47/53)} & 36 \gray{(58/31/11)} & 36 \gray{(58/31/11)}\\
-    UF & 2839 \gray{(28/72)} & 2839 \gray{(28/72)} & 7562 \gray{(10/44/46)} & 7562 \gray{(10/46/44)}\\
-    UFBV & 71 \gray{(25/75)} & 71 \gray{(25/75)} & 200 \gray{(34/48/17)} & 200 \gray{(34/48/17)}\\
-    UFDT & - & - & 4535 \gray{(0/9/90)} & 4527 \gray{(1/41/58)}\\
-    UFDTLIA & - & - & 303 \gray{(0/0/100)} & 303 \gray{(0/0/100)}\\
-    UFIDL & 68 \gray{(9/91)} & 68 \gray{(9/91)} & 68 \gray{(4/84/12)} & 68 \gray{(4/84/12)}\\
-    UFLIA & 8404 \gray{(0/100)} & 8404 \gray{(0/100)} & 10137 \gray{(0/76/24)} & 10137 \gray{(0/76/23)}\\
-    UFLRA & 25 \gray{(20/80)} & 25 \gray{(20/80)} & 15 \gray{(33/67/0)} & 15 \gray{(33/67/0)}\\
-    UFNIA & 2319 \gray{(0/100)} & 2319 \gray{(0/100)} & 3308 \gray{(0/74/26)} & 3308 \gray{(0/74/26)}\\
+    ABVFP & -- & & -- & & -- & & 1 & \gray{(0/0/100)}\\
+    ALIA & 42 & \gray{(2/98)} & 42 & \gray{(2/98)} & 42 & \gray{(2/98/0)} & 42 & \gray{(2/98/0)}\\
+    AUFBVDTLIA & -- & & -- & & 1709 & \gray{(0/1/98)} & 1709 & \gray{(0/1/98)}\\
+    AUFDTLIA & -- & & -- & & 728 & \gray{(0/0/100)} & 728 & \gray{(0/0/100)}\\
+    AUFLIA & 4 & \gray{(25/75)} & 4 & \gray{(25/75)} & 4 & \gray{(25/75/0)} & 4 & \gray{(25/75/0)}\\
+    AUFLIRA & 19849 & \gray{(1/99)} & 19849 & \gray{(1/99)} & 20011 & \gray{(0/99/1)} & 20011 & \gray{(0/99/1)}\\
+    AUFNIRA & 1050 & \gray{(0/100)} & 1050 & \gray{(0/100)} & 1480 & \gray{(0/71/29)} & 1480 & \gray{(0/71/29)}\\
+    BV & 85 & \gray{(34/66)} & 85 & \gray{(34/66)} & 5151 & \gray{(2/2/97)} & 5751 & \gray{(10/86/4)}\\
+    BVFP & -- & & -- & & -- & & 24 & \gray{(0/0/100)}\\
+    FP & -- & & -- & & -- & & 61 & \gray{(0/0/100)}\\
+    LIA & 201 & \gray{(5/95)} & 201 & \gray{(5/95)} & 388 & \gray{(38/60/2)} & 388 & \gray{(38/60/2)}\\
+    LRA & 339 & \gray{(6/94)} & 339 & \gray{(6/94)} & 2419 & \gray{(17/46/38)} & 2419 & \gray{(29/64/8)}\\
+    NIA & 9 & \gray{(67/33)} & 9 & \gray{(67/33)} & 14 & \gray{(43/29/29)} & 14 & \gray{(43/29/29)}\\
+    NRA & 3788 & \gray{(0/100)} & 3788 & \gray{(0/100)} & 3811 & \gray{(0/100/0)} & 3813 & \gray{(0/100/0)}\\
+    QF\_ABV & 14720 & \gray{(68/32)} & 14720 & \gray{(68/32)} & 15061 & \gray{(69/31/0)} & 15066 & \gray{(69/31/0)}\\
+    QF\_ABVFP & -- & & -- & & -- & & 18129 & \gray{(78/22/1)}\\
+    QF\_ALIA & 134 & \gray{(40/60)} & 139 & \gray{(42/58)} & 139 & \gray{(42/58/0)} & 139 & \gray{(42/58/0)}\\
+    QF\_ANIA & 6 & \gray{(0/100)} & 8 & \gray{(0/100)} & 8 & \gray{(0/100/0)} & 8 & \gray{(0/100/0)}\\
+    QF\_AUFBV & 37 & \gray{(16/84)} & 37 & \gray{(16/84)} & 31 & \gray{(19/81/0)} & 31 & \gray{(19/81/0)}\\
+    QF\_AUFLIA & 1009 & \gray{(49/51)} & 1009 & \gray{(49/51)} & 1009 & \gray{(49/51/0)} & 1009 & \gray{(49/51/0)}\\
+    QF\_AUFNIA & 21 & \gray{(29/71)} & 21 & \gray{(29/71)} & 17 & \gray{(29/71/0)} & 17 & \gray{(29/71/0)}\\
+    QF\_AX & 551 & \gray{(49/51)} & 551 & \gray{(49/51)} & 551 & \gray{(49/51/0)} & 551 & \gray{(49/51/0)}\\
+    QF\_BV & 26414 & \gray{(35/65)} & 26414 & \gray{(35/65)} & 40043 & \gray{(32/59/8)} & 40102 & \gray{(36/64/0)}\\
+    QF\_BVFP & 7 & \gray{(14/86)} & 7 & \gray{(14/86)} & 17215 & \gray{(81/18/0)} & 17215 & \gray{(81/18/0)}\\
+    QF\_DT & -- & & -- & & 8000 & \gray{(0/0/100)} & 8000 & \gray{(45/55/0)}\\
+    QF\_FP & 34413 & \gray{(50/50)} & 34413 & \gray{(50/50)} & 40302 & \gray{(50/50/1)} & 40300 & \gray{(50/50/1)}\\
+    QF\_IDL & 2094 & \gray{(61/39)} & 2094 & \gray{(61/39)} & 2193 & \gray{(58/37/5)} & 2193 & \gray{(58/37/4)}\\
+    QF\_LIA & 5839 & \gray{(51/49)} & 5839 & \gray{(51/49)} & 6141 & \gray{(52/46/2)} & 6947 & \gray{(55/43/1)}\\
+    QF\_LIRA & 6 & \gray{(17/83)} & 6 & \gray{(17/83)} & 7 & \gray{(14/71/14)} & 7 & \gray{(14/71/14)}\\
+    QF\_LRA & 1626 & \gray{(61/39)} & 1626 & \gray{(61/39)} & 1649 & \gray{(57/41/2)} & 1649 & \gray{(57/41/1)}\\
+    QF\_NIA & 8475 & \gray{(98/2)} & 8593 & \gray{(96/4)} & 23876 & \gray{(59/13/28)} & 23876 & \gray{(59/20/20)}\\
+    QF\_NIRA & 2 & \gray{(0/100)} & 2 & \gray{(0/100)} & 3 & \gray{(0/67/33)} & 3 & \gray{(0/67/33)}\\
+    QF\_NRA & 10184 & \gray{(52/48)} & 10245 & \gray{(52/48)} & 11354 & \gray{(44/47/10)} & 11489 & \gray{(44/47/9)}\\
+    QF\_RDL & 220 & \gray{(49/51)} & 220 & \gray{(49/51)} & 255 & \gray{(43/44/13)} & 255 & \gray{(43/44/13)}\\
+    QF\_SLIA & -- & & -- & & -- & & 72705 & \gray{(0/0/100)}\\
+    QF\_UF & 6649 & \gray{(38/62)} & 6649 & \gray{(38/62)} & 6650 & \gray{(38/62/0)} & 7423 & \gray{(42/58/0)}\\
+    QF\_UFBV & 31 & \gray{(0/100)} & 31 & \gray{(0/100)} & 31 & \gray{(0/100/0)} & 1224 & \gray{(53/47/0)}\\
+    QF\_UFIDL & 441 & \gray{(24/76)} & 441 & \gray{(24/76)} & 428 & \gray{(25/75/0)} & 428 & \gray{(25/75/0)}\\
+    QF\_UFLIA & 598 & \gray{(67/33)} & 598 & \gray{(67/33)} & 583 & \gray{(69/31/0)} & 583 & \gray{(69/31/0)}\\
+    QF\_UFLRA & 1627 & \gray{(48/52)} & 1627 & \gray{(48/52)} & 1284 & \gray{(60/40/0)} & 1284 & \gray{(60/40/0)}\\
+    QF\_UFNIA & 7 & \gray{(0/100)} & 7 & \gray{(0/100)} & 7 & \gray{(0/100/0)} & 7 & \gray{(0/100/0)}\\
+    QF\_UFNRA & 34 & \gray{(47/53)} & 34 & \gray{(47/53)} & 36 & \gray{(58/31/11)} & 36 & \gray{(58/31/11)}\\
+    UF & 2839 & \gray{(28/72)} & 2839 & \gray{(28/72)} & 7562 & \gray{(10/44/46)} & 7562 & \gray{(10/46/44)}\\
+    UFBV & 71 & \gray{(25/75)} & 71 & \gray{(25/75)} & 200 & \gray{(34/48/17)} & 200 & \gray{(34/48/17)}\\
+    UFDT & -- & & -- & & 4535 & \gray{(0/9/90)} & 4527 & \gray{(1/41/58)}\\
+    UFDTLIA & -- & & -- & & 303 & \gray{(0/0/100)} & 303 & \gray{(0/0/100)}\\
+    UFIDL & 68 & \gray{(9/91)} & 68 & \gray{(9/91)} & 68 & \gray{(4/84/12)} & 68 & \gray{(4/84/12)}\\
+    UFLIA & 8404 & \gray{(0/100)} & 8404 & \gray{(0/100)} & 10137 & \gray{(0/76/24)} & 10137 & \gray{(0/76/23)}\\
+    UFLRA & 25 & \gray{(20/80)} & 25 & \gray{(20/80)} & 15 & \gray{(33/67/0)} & 15 & \gray{(33/67/0)}\\
+    UFNIA & 2319 & \gray{(0/100)} & 2319 & \gray{(0/100)} & 3308 & \gray{(0/74/26)} & 3308 & \gray{(0/74/26)}\\
     \midrule
-    Total      & 154238 \gray{(40/60)} & 154424 \gray{(40/60)} & 256973 \gray{(37/46/17)} & 333241 \gray{(33/39/28)}\\
+    Total      & 154238 & \gray{(40/60)} & 154424 & \gray{(40/60)} & 256973 & \gray{(37/46/17)} & 333241 & \gray{(33/39/28)}\\
     \bottomrule
@@
   within a time limit of 2400s
-  on common benchmarks 2015-2018 of all logics in the \apptrack.}
+  on common benchmarks 2015--2018 of all logics in the \apptrack.}
   \label{fig:progress-all-app}
@@
 in the competitions 2017 and 2018. Figure~\ref{fig:progress-all} visualizes VBS
-performance on common benchmarks from 2015-2018 as cactus plot.
+performance on common benchmarks from 2015--2018 as cactus plot.
 Figure~\ref{fig:progress} shows VBS performance on common benchmarks over pairs

### 2019-08-21 2018/report/Reviews_67398_Revised_Response.txt
Participants tables (minor)
Use siunitx's \num command
Complete outline for Section 8 (Further Analysis)
Table 3 (Main Track benchmarks): right-aligned numbers
WONTFIX: unique solutions (Table 16)

@@
 
-TODO
+DONE
 
@@
 
-TODO
+WONTFIX (a unique solution is a unique solution, regardless of *why*
+no other solver found a solution; the definition suggested by the
+reviewer is not stable under adding a dummy solver that always
+responds "unknown"; and some divisions/years in which there was only
+one sound solver are explicitly mentioned in the text)
 
@@
 
-TODO
+WONTFIX (there is no reference to colors other than an explanation of
+what they mean)
 
@@
 
-TODO
+WONTFIX (I tried but didn't manage to make the participants tables fit
+on two pages instead of three)
 
@@
 
-TODO
+DONE (in the text only, not in tables)
 

### 2019-08-21 2018/report/SMT-COMP.tex
Clarify scoring rules

@@
 \begin{itemize}[noitemsep]
-  \item \makebox[5em][l]{$e \in \{0, 1\}$} number of erroneous results (usually~$e = 0$)
+  \item \makebox[5em][l]{$e\geq 0$} number of erroneous results (usually~$e = 0$)
   \item \makebox[5em][l]{$0 \leq n \leq N$} number of correct results (resp.~\emph{reduction} for the \ucoretrack)
@@
 \noindent
-For the \maintrack and \apptrack, $e$ is the number of returned statuses that disagree with the given expected status (as described above, disagreements on benchmarks with unknown status lead to the benchmark being disregarded).
-For the \ucoretrack, $e$ includes, in addition, the number of returned unsat cores that are ill-formed or are not, in fact, unsatisfiable (as validated by a selection of other solvers selected by organizers).
+For the \maintrack and \apptrack, $e$ is the number of returned statuses that disagree with the given expected status; $e \in \{0,1\}$ for the \maintrack.
+(As described above, disagreements between solvers on benchmarks with unknown status lead to the benchmark being disregarded.)  For the \ucoretrack, $e$ includes, in addition, the number of returned unsat cores that are ill-formed or are not, in fact, unsatisfiable (as validated by a selection of other solvers selected by organizers).
 
 For the \maintrack and \apptrack,
-$N$ is defined as the number of {\tt check-sat} commands, and
+$N$ is defined as the number of {\tt check-sat} commands ($N=1$ for the \maintrack), and
 $n$ is defined as the number of correct results.
 For the \ucoretrack, $N$ is defined as the number of named top-level assertions,
-and $n$ is defined as the \emph{reduction}, i.e., the difference between $N$
-and the size of the unsat core.
+and~$n$ is defined as the \emph{reduction}, i.e., the difference between $N$
+and the size of the unsat core returned by the solver.
 

### 2019-08-21 2018/report/Reviews_67398_Revised_Response.txt
Clarify scoring rules
Motivate removal of disagreements

@@
 
-TODO
+DONE (updated to better motivate the removal of benchmarks with
+disagreements; of course we agree that correctness is important)
 
@@
 
-TODO
+DONE (changed to clarify that e \in \{0,1\} only for the Main Track)
 
@@
 
-WONTFIX (yes; and this is correct usage of the word Olympiad)
+WONTFIX (we are referring to the time between the two FLoC Olympic
+Games; this is correct usage of the word Olympiad)
 

### 2019-08-21 2018/report/SMT-COMP.tex
Motivate removal of disagreements

@@
 whose status was known (i.e., that had been solved previously by
-existing SMT solvers).  In 2015, 30,717 non-incremental benchmarks
+existing SMT solvers).  In 2015, \num{30717} non-incremental benchmarks
 from the SMT Library were not used for the competition because their
@@
 imitating existing solvers rather than truly innovating.  In~2016,
-the SMT Library contained 29,724 non-incremental benchmarks with
+the SMT Library contained \num{29724} non-incremental benchmarks with
 unknown status; solver performance on these was evaluated but reported
@@
 benchmarks are assumed to be correct, unless there is a disagreement
-between two or more (otherwise sound e.g. on problems with known status) solvers.  Benchmarks with
-disagreements are removed from the competition results.
-This conservative approach was chosen over a voting system as this situation is expected to be rare as the SMT-LIB organisers go to a significant effort prior to each competition to update the statuses of problems.
-A manual investigation is therefore preferred over an automated resolution.
-Disagreements are reported to the solvers involved and in all cases have led to bugs in solvers being identified and fixed.
-In 2016,
-there were disagreements on 79 benchmarks; in 2017, only one benchmark
-was removed; while in 2018, there were no disagreements between
-otherwise sound solvers.
+between two or more solvers that are otherwise (i.e., on problems with
+known status) sound.  Benchmarks with disagreements are removed from
+the competition results.  This conservative approach was chosen over a
+voting system as the latter is unreliable (especially in divisions
+with few solvers), could lead to a solver being punished wrongly, and
+could be gamed by entering multiple copies of a solver into the
+competition.  Moreover, the size and time frame of the competition
+demand an automated resolution.  Disagreements are reported to the
+solver developers involved, who typically perform a manual
+investigation at their leisure, and in all cases have led to bugs in
+solvers being identified and fixed.  In 2016, there were disagreements
+on 79 benchmarks; in 2017, only one benchmark was removed; while in
+2018, there were no disagreements between otherwise sound solvers.
 

### 2019-08-21 2018/report/SMT-COMP.tex
Clarify discussion of MathSAT/Z3 performance and industrial relevance

@@
 Table cell colors (other than white) indicate the best competing sequential
-solver performance, no cell color indicates that the best sequential solver
+solver performance; no cell color indicates that the best sequential solver
 performance was by a non-competing solver and no competing solvers participated
@@
 
-It is interesting to note that the non-competitive solvers MathSAT and Z3 often appear as the best performing solver.
-We do not see this as detracting from the overall significance of results.
-Both solvers are industrial-strength tools, actively maintained and tuned.
-The reasons for non-entry into the competition are orthogonal to their suitability for the competition.
-Indeed, Z3 has been entered into the competition competitively in the past and one can assume that it was trained on the current problems (as much as any solver is).
-Finally, the fact that industrial-strength solvers perform well in the competition supports the notion that the benchmarks in the competition are industrially relevant.
+It is interesting to note that the non-competing solvers MathSAT and
+Z3 often appear as the best performing solver.  We view this as
+confirmation of the industrial significance of competition results.
+Both solvers are industrial-strength tools, actively maintained and
+tuned.  The reasons for non-entry into the competition are orthogonal
+to their suitability for the competition.  Indeed, Z3 has been entered
+into the competition competitively in the past, and one can assume
+that it was trained on the current problems.  The fact that
+industrial-strength solvers perform well in the competition supports
+the notion that the benchmarks in the competition are industrially
+relevant.
 

### 2019-08-21 2018/report/Reviews_67398_Revised_Response.txt
Clarify discussion of MathSAT/Z3 performance and industrial relevance
WONTFIX: explanation of results

@@
 
-TODO
+WONTFIX (while interesting, this is way out of scope for this paper.
+We, as organizers, are not the developers of most of the solvers (nor
+the source of most benchmarks), so there is no practical way for us to
+determine what exactly was the cause for improvement)
 
@@
 
-TODO
+DONE (the paragraph was added in response to earlier reviewer feedback
+and has been rephrased)
 
@@
 
-DONE
+DONE (degression -> regression)
 

### 2019-08-21 2018/report/SMT-COMP.tex
Remove less interesting organizational details

@@
 The competition is organized under the direction of the SMT Steering
-Committee, which appoints the competition chair.  (This appointment
-should happen ``within 30 days from the end of the current edition of
-the SMT workshop''~\cite{smt-bylaws} but in practice has often
-happened later.)  The competition chair then assembles a team of
-organizers, and oversees the work for the next edition of the
-competition.
+Committee, which appoints the competition chair~\cite{smt-bylaws}.
+The competition chair then assembles a team of organizers, and
+oversees the work for the next edition of the competition.
 %
@@
 IJCAR (as part of FLoC) in~2018.  Consequently, its date varies.
-Competition results were presented on July~19 in 2015, on July~2 in
-2016, on July~23 in 2017, and on July~13 in~2018.
+During 2015--2018, the workshop always took place in July.
 
@@
 actually a competition division in that track and year.  The size of
-divisions varies widely, from just one benchmark in ABVFP to~72,705
+divisions varies widely, from just one benchmark in ABVFP to~\num{72705}
 benchmarks in QF\_SLIA.

### 2019-08-21 2018/report/SMT-COMP.tex
Minor

@@
 Z3 often appear as the best performing solver.  We view this as
-confirmation of the industrial significance of competition results.
-Both solvers are industrial-strength tools, actively maintained and
-tuned.  The reasons for non-entry into the competition are orthogonal
-to their suitability for the competition.  Indeed, Z3 has been entered
-into the competition competitively in the past, and one can assume
-that it was trained on the current problems.  The fact that
-industrial-strength solvers perform well in the competition supports
-the notion that the benchmarks in the competition are industrially
-relevant.
+confirmation of the industrial significance of the competition
+results.  Both solvers are industrial-strength tools, actively
+maintained and tuned for applications.  The reasons for non-entry into
+the competition are orthogonal to their suitability for the
+competition.  Indeed, Z3 has been entered into the competition
+competitively in the past, and one can assume that it was trained on
+the current problems.  The fact that industrial-strength solvers
+perform well in the competition supports the notion that the
+benchmarks in the competition are industrially relevant.
 

### 2019-08-21 2018/report/Reviews_67398_Revised_Response.txt
Remove less interesting organizational details
WONTFIX: "DT"
Minor

--- 2019-08-21 2018/report/Reviews_67398_Revised_Response.txt
@@
 
-TODO
+WONTFIX (while interesting, this is way out of scope for this paper:
+we, as organizers, are not the developers of most of the solvers (nor
+the source of most benchmarks), so there is no practical way for us to
+determine what exactly was the cause for improvement)
 
@@
 
-TODO
+WONTFIX ("DT" for algebraic datatypes is introduced in Section 3)
 

### 2019-08-22 2018/report/SMT-COMP.tex
Move Scoring into its own section; minor

@@
 solver/benchmark combination, totaling nearly 6 million data records
-(about 1.1~GB in CSV format).  Competition solvers and benchmarks may
-be downloaded from StarExec, \url{https://www.starexec.org}.
+(about \SI{1.1}{GB} in CSV format).  Competition solvers and
+benchmarks may be downloaded from StarExec,
+\url{https://www.starexec.org}.
 
@@
 Section~\ref{sec:participants} gives an overview of participating
-solvers.  Selected competition results are presented in
+solvers, and Section~\ref{sec:scoring} discusses the scoring rules.
+Selected competition results are presented in
 Section~\ref{sec:results}, and analyzed in more detail in
@@
 
-The 2018 release of the SMT Library contained \num{336844} non-incremental
-benchmarks in 51 logics, as well as~\num{10167} incremental benchmarks
-(with a total of nearly 32 million {\tt check-sat} commands) in 26
-logics.  Table~\ref{table:smtlib} presents further data on the size of
-the SMT Library since~2015.  While the library usually grows from one
-year to the other because of the inclusion of new benchmarks and
-logics, continuous curation efforts may also cause benchmarks to be
-removed or reclassified on occasion, thereby causing individual logics
-or even the entire library to shrink.  From~2015 to~2018, the total
-number of benchmarks has increased by~68\,\%.  The largest benchmark
-in the 2018 release had a size of \num{1041}~MB; the total size of the
-release was 91~GB.
+The 2018 release of the SMT Library contained \num{336844}
+non-incremental benchmarks in 51 logics, as well as~\num{10167}
+incremental benchmarks (with a total of nearly 32 million {\tt
+  check-sat} commands) in 26 logics.  Table~\ref{table:smtlib}
+presents further data on the size of the SMT Library since~2015.
+While the library usually grows from one year to the other because of
+the inclusion of new benchmarks and logics, continuous curation
+efforts may also cause benchmarks to be removed or reclassified on
+occasion, thereby causing individual logics or even the entire library
+to shrink.  From~2015 to~2018, the total number of benchmarks has
+increased by~68\,\%.  The largest benchmark in the 2018 release had a
+size of \SI{1041}{MB}; the total size of the release was \SI{91}{GB}.
 
@@
 benchmarks in QF\_SLIA.
-
-\subsection{Scoring}
-
-The \emph{raw benchmark score} of a solver is a quadruple $\langle
-e, n, w, c\rangle$, with
-\begin{itemize}[noitemsep]
-  \item \makebox[5em][l]{$e\geq 0$} number of erroneous results (usually~$e = 0$)
-  \item \makebox[5em][l]{$0 \leq n \leq N$} number of correct results (resp.~\emph{reduction} for the \ucoretrack)
-  \item \makebox[5em][l]{$w \in [0,T]$} wall-clock time in seconds (real-valued)
-  \item \makebox[5em][l]{$c \in [0, 4T]$} CPU time in seconds (real-valued)
-\end{itemize}
-\noindent
-For the \maintrack and \apptrack, $e$ is the number of returned statuses that disagree with the given expected status; $e \in \{0,1\}$ for the \maintrack.
-(As described above, disagreements between solvers on benchmarks with unknown status lead to the benchmark being disregarded.)  For the \ucoretrack, $e$ includes, in addition, the number of returned unsat cores that are ill-formed or are not, in fact, unsatisfiable (as validated by a selection of other solvers selected by organizers).
-
-For the \maintrack and \apptrack,
-$N$ is defined as the number of {\tt check-sat} commands ($N=1$ for the \maintrack), and
-$n$ is defined as the number of correct results.
-For the \ucoretrack, $N$ is defined as the number of named top-level assertions,
-and~$n$ is defined as the \emph{reduction}, i.e., the difference between $N$
-and the size of the unsat core returned by the solver.
-
-This raw score corresponds to the \emph{raw parallel score} (all values are
-determined for solver performance within the wall-clock time limit).  To
-evaluate sequential performance, we derive a \emph{raw sequential score} by
-imposing a (virtual) CPU time limit equal to the wall-clock time limit~$T$.  A
-solver result is taken into consideration for the sequential score only if the
-solver process terminates within this CPU time limit.
-
-Until 2015, the competition used these raw scores for all tracks to determine
-the division score of a solver as the sum of the scores of all benchmarks in
-that division.
-Fewer errors in a division takes precedence over more correct solutions
-(resp.~reduction), which takes precedence over less wall-clock time taken,
-which takes precedence over less CPU time taken.
-However, since there are vast differences in size between benchmark families in
-the SMT Library, the competition since~2016 uses a scoring method that assigns
-a weight to each benchmark in the \maintrack and \ucoretrack in order to
-de-emphasize large benchmark families~\cite{rules16,rules17,rules18}.
-For application track divisions, division scores were still based on raw scores
-only, since application track benchmarks may be partially solved. Defining a
-useful sequential score for the application track would require information not
-provided by the raw score, e.g., detailed timing information for each result.
-
-\paragraph{Benchmark Weights (\maintrack and \ucoretrack 2016--2018).} The \emph{weight} of a
-benchmark in the main track is computed as $\alpha = (1 + \ln F)/F$,
-where~$F\geq 1$ is the size of the benchmark's family.  We then define its
-\emph{normalized weight} as $\alpha' = \alpha / (\sum_{i\in F} \alpha_i)$,
-where the sum is over all benchmarks in the division.  The log scaling seems a
-reasonable compromise between linearly combining numbers of benchmarks, which
-would overemphasize large families, and simply averaging the fraction of
-benchmarks solved, which would overemphasize small families.
-
-\paragraph{Weighted Division Scores (\maintrack and \ucoretrack 2016--2018).}
-The \emph{(weighted) score} of a solver in a division of the \maintrack and
-\ucoretrack with $M$ benchmarks is then defined as the weighted sum of all raw
-scores $$\sum_{b\in M} \alpha'_b \cdot \langle e_b \cdot N, n_b \cdot N,
-w_b, c_b\rangle$$ where the sum is over all benchmarks in the division to
-assess parallel performance, and the weighted sum of all sequential scores to
-assess sequential performance.
-
-\paragraph{Competition-Wide Score (\maintrack).}
-A competition-wide metric for the main track, separately for
-parallel and sequential performance, was defined as follows.
-
-Let $N_i$ be the total number of benchmarks in division~$i$ that were used in the
-competition (and not removed because of disagreements), and let $\langle e_i, n_i, w_i, c_i\rangle$ be a solver's
-raw score for this division.
-%
-In 2015 and 2016,
-the \emph{competition-wide raw score} for a solver was defined as
-%
-$\sum_i (e_i == 0 \,?\, (n_i/N_i)^2 : -e_i) \log N_i$,
-%
-where the sum is over all competitive
-divisions into which the solver was
-entered.
-%
-In 2017, the (per-division) penalty for erroneous results was changed from the
-number of errors to a fixed constant, since the weight already takes the number
-of benchmarks in the division into account, and multiplying it by the number of
-errors overemphasizes large divisions.
-In 2017 and 2018,
-the \emph{competition-wide raw score} for a solver was thus defined as
-%
-$\sum_i (e_i == 0 \,?\, (n_i/N_i)^2 : -4) \log_e N_i$,
-%
-where the sum is over all competitive divisions into which the solver
-was entered.
 
@@
 
+\section{Scoring}
+\label{sec:scoring}
+
+The \emph{raw benchmark score} of a solver is a quadruple $\langle
+e, n, w, c\rangle$, with
+\begin{itemize}[noitemsep]
+  \item \makebox[5em][l]{$e\geq 0$} number of erroneous results (usually~$e = 0$)
+  \item \makebox[5em][l]{$0 \leq n \leq N$} number of correct results (resp.~\emph{reduction} for the \ucoretrack)
+  \item \makebox[5em][l]{$w \in [0,T]$} wall-clock time in seconds (real-valued)
+  \item \makebox[5em][l]{$c \in [0, 4T]$} CPU time in seconds (real-valued)
+\end{itemize}
+\noindent
+For the \maintrack and \apptrack, $e$ is the number of returned statuses that disagree with the given expected status; $e \in \{0,1\}$ for the \maintrack.
+(As described above, disagreements between solvers on benchmarks with unknown status lead to the benchmark being disregarded.)  For the \ucoretrack, $e$ includes, in addition, the number of returned unsat cores that are ill-formed or are not, in fact, unsatisfiable (as validated by a selection of other solvers selected by organizers).
+
+For the \maintrack and \apptrack,
+$N$ is defined as the number of {\tt check-sat} commands ($N=1$ for the \maintrack), and
+$n$ is defined as the number of correct results.
+For the \ucoretrack, $N$ is defined as the number of named top-level assertions,
+and~$n$ is defined as the \emph{reduction}, i.e., the difference between $N$
+and the size of the unsat core returned by the solver.
+
+This raw score corresponds to the \emph{raw parallel score} (all values are
+determined for solver performance within the wall-clock time limit).  To
+evaluate sequential performance, we derive a \emph{raw sequential score} by
+imposing a (virtual) CPU time limit equal to the wall-clock time limit~$T$.  A
+solver result is taken into consideration for the sequential score only if the
+solver process terminates within this CPU time limit.
+
+Until 2015, the competition used these raw scores for all tracks to determine
+the division score of a solver as the sum of the scores of all benchmarks in
+that division.
+Fewer errors in a division takes precedence over more correct solutions
+(resp.~reduction), which takes precedence over less wall-clock time taken,
+which takes precedence over less CPU time taken.
+However, since there are vast differences in size between benchmark families in
+the SMT Library, the competition since~2016 uses a scoring method that assigns
+a weight to each benchmark in the \maintrack and \ucoretrack in order to
+de-emphasize large benchmark families~\cite{rules16,rules17,rules18}.
+For application track divisions, division scores were still based on raw scores
+only, since application track benchmarks may be partially solved. Defining a
+useful sequential score for the application track would require information not
+provided by the raw score, e.g., detailed timing information for each result.
+
+\paragraph{Benchmark Weights (\maintrack and \ucoretrack 2016--2018).} The \emph{weight} of a
+benchmark in the main track is computed as $\alpha = (1 + \ln F)/F$,
+where~$F\geq 1$ is the size of the benchmark's family.  We then define its
+\emph{normalized weight} as $\alpha' = \alpha / (\sum_{i\in F} \alpha_i)$,
+where the sum is over all benchmarks in the division.  The log scaling seems a
+reasonable compromise between linearly combining numbers of benchmarks, which
+would overemphasize large families, and simply averaging the fraction of
+benchmarks solved, which would overemphasize small families.
+
+\paragraph{Weighted Division Scores (\maintrack and \ucoretrack 2016--2018).}
+The \emph{(weighted) score} of a solver in a division of the \maintrack and
+\ucoretrack with $M$ benchmarks is then defined as the weighted sum of all raw
+scores $$\sum_{b\in M} \alpha'_b \cdot \langle e_b \cdot N, n_b \cdot N,
+w_b, c_b\rangle$$ where the sum is over all benchmarks in the division to
+assess parallel performance, and the weighted sum of all sequential scores to
+assess sequential performance.
+
+\paragraph{Competition-Wide Score (\maintrack).}
+A competition-wide metric for the main track, separately for
+parallel and sequential performance, was defined as follows.
+
+Let $N_i$ be the total number of benchmarks in division~$i$ that were used in the
+competition (and not removed because of disagreements), and let $\langle e_i, n_i, w_i, c_i\rangle$ be a solver's
+raw score for this division.
+%
+In 2015 and 2016,
+the \emph{competition-wide raw score} for a solver was defined as
+%
+$\sum_i (e_i == 0 \,?\, (n_i/N_i)^2 : -e_i) \log N_i$,
+%
+where the sum is over all competitive
+divisions into which the solver was
+entered.
+%
+In 2017, the (per-division) penalty for erroneous results was changed from the
+number of errors to a fixed constant, since the weight already takes the number
+of benchmarks in the division into account, and multiplying it by the number of
+errors overemphasizes large divisions.
+In 2017 and 2018,
+the \emph{competition-wide raw score} for a solver was thus defined as
+%
+$\sum_i (e_i == 0 \,?\, (n_i/N_i)^2 : -4) \log_e N_i$,
+%
+where the sum is over all competitive divisions into which the solver
+was entered.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section{Results}
@@
         plot/pdf/cactus_plot-Virtual_Best_Solver_(VBS)_Main_Track_2015-2018.pdf}}
-  \caption{VBS on common benchmarks 2015--2018 of all logics in the \maintrack
-  with a time limit of 1200s. Number of common benchmarks is indicated with a
-  gray vertical line.}
+  \caption{VBS on common benchmarks 2015--2018 of all logics in the
+    \maintrack with a time limit of \SI{1200}{s}.  Number of common
+    benchmarks is indicated with a gray vertical line.}
   \label{fig:progress-all}
@@
   \end{subfigure}
-  \caption{VBS on common benchmarks for pairs of years of all logics in the
-  \maintrack with a time limit of 1200s. Number of common benchmarks is
-  indicated with a gray vertical line.}
+  \caption{VBS on common benchmarks for pairs of years of all logics
+    in the \maintrack with a time limit of \SI{1200}{s}.  Number of
+    common benchmarks is indicated with a gray vertical line.}
   \label{fig:progress}
@@
   \vspace{-5ex}
-  \caption{VBS in terms of correct \texttt{check-sat} answers
-  (out of 30370517 total)
-  within a time limit of 2400s
-  on common benchmarks 2015--2018 of all logics in the \apptrack.}
+  \caption{VBS in terms of correct \texttt{check-sat} answers (out of
+    \num{30370517} total) within a time limit of \SI{2400}{s} on
+    common benchmarks 2015--2018 of all logics in the \apptrack.}
   \label{fig:progress-all-app}
@@
   \vspace{-5ex}
-  \caption{VBS in terms of number of unsat core reductions
-  within a time limit of 2400s
-  on common benchmarks 2016--2018 of all logics in the \ucoretrack.}
+  \caption{VBS in terms of number of unsat core reductions within a
+    time limit of \SI{2400}{s} on common benchmarks 2016--2018 of all
+    logics in the \ucoretrack.}
   \label{fig:progress-all-uc}

### 2019-08-22 2018/report/SMT-COMP.tex
Remove \rem and \todo commands
Shorter discussion of benchmark selection (no families mentioned)
Explanation of families in Section 7

@@
 }
-
-\newcommand{\rem}[1]{\textcolor{red}{[#1]}}
-\newcommand{\todo}[1]{\rem{TODO #1}}
 
@@
 competition is evaluating all solvers on all eligible benchmarks.
-This change had an unintended side effect: the pseudo-random selection
-process had been purposely constrained to choose benchmarks from
-different benchmark families (that is, groups of benchmarks with
-similar characteristics).
 
@@
 
-Until 2015, the competition used these raw scores for all tracks to determine
-the division score of a solver as the sum of the scores of all benchmarks in
-that division.
-Fewer errors in a division takes precedence over more correct solutions
-(resp.~reduction), which takes precedence over less wall-clock time taken,
-which takes precedence over less CPU time taken.
-However, since there are vast differences in size between benchmark families in
-the SMT Library, the competition since~2016 uses a scoring method that assigns
-a weight to each benchmark in the \maintrack and \ucoretrack in order to
-de-emphasize large benchmark families~\cite{rules16,rules17,rules18}.
-For application track divisions, division scores were still based on raw scores
-only, since application track benchmarks may be partially solved. Defining a
-useful sequential score for the application track would require information not
-provided by the raw score, e.g., detailed timing information for each result.
+Until 2015, the competition used these raw scores for all tracks to
+determine the division score of a solver as the sum of the scores of
+all benchmarks in that division.  Fewer errors in a division takes
+precedence over more correct solutions (resp.~reduction), which takes
+precedence over less wall-clock time taken, which takes precedence
+over less CPU time taken.  However, since there are vast differences
+in size between benchmark families (i.e., groups of benchmarks with
+similar characteristics) in the SMT Library, the competition
+since~2016 uses a scoring method that assigns a weight to each
+benchmark in the \maintrack and \ucoretrack in order to de-emphasize
+large benchmark families~\cite{rules16,rules17,rules18}.  For
+application track divisions, division scores were still based on raw
+scores only, since application track benchmarks may be partially
+solved.  Defining a useful sequential score for the application track
+would require information not provided by the raw score, e.g.,
+detailed timing information for each result.
 

### 2019-08-22 2018/report/Reviews_67398_Revised_Response.txt
WONTFIX: quotient
Explanation of families in Section 7
Layout
WONTFIX: additional analysis

@@
 
-TODO
+DONE (reference to benchmark families removed on page 7; they are now
+discussed in Section 7)
 
@@
 
-TODO
+WONTFIX (quotient is the correct word here)
 
@@
 
-TODO
+WONTFIX (we have carried out some analysis to answer this question;
+there is certainly ample opportunity for further analysis, but the
+present paper already covers a lot of material and we cannot expand
+its scope forevermore)
 

### 2019-08-22 2018/report/SMT-COMP.tex
Minor

@@
 which can be entirely attributed to a performance regression
-of Z3 on 2 benchmarks in the QF\_NIA division.
-%(on which in 2016, CVC4 then
-%performed best, and from 2017 onwards even as well as Z3 in 2015).
+of Z3 on two benchmarks in the QF\_NIA division.
 

### 2019-08-22 2018/report/Reviews_67398_Revised_Response.txt
WONTFIX: gray color, cactus plots

@@
 
-TODO
+WONTFIX (we concede that gray text can be problematic with certain
+printers; however, other colors can be equally problematic, and some
+of the tables and figures contain a lot of information, which we find
+difficult to condense without the use of color)
 
@@
 
-TODO
+WONTFIX (starting the x-axis at 0 would render the plots unexpressive;
+a cactus plot may not be ideal but we haven't been able to find a
+better tool)
 

### 2019-08-22 2018/report/SMT-COMP.tex
focusses -> focuses

@@
 In recent years, we have seen a blurring of lines between SMT-COMP and CASC with SMT solvers competing in CASC and ATPs competing in SMT-COMP.
-The main (informal) distinction remains that SMT-COMP focusses on problems that are heavy in theories, whereas CASC focusses on problems heavy in quantifiers.
+The main (informal) distinction remains that SMT-COMP focuses on problems that are heavy in theories, whereas CASC focuses on problems heavy in quantifiers.
 Another closely related competition is SV-COMP (\url{https://sv-comp.sosy-lab.org}) where many tools rely on advances in SMT solving technology.

### 2019-08-27 2018/report/SMT-COMP.tex
Reduce the size of Figures 5 and 6

@@
   \centering
-  \scalebox{.45}{\includegraphics{%
+  \begin{minipage}{0.47\textwidth}
+    \centering
+    \scalebox{.31}{\includegraphics{%
         plot/pdf/bar_plot-Virtual_Best_Solver_(VBS)_Application_Track_2015-2018.pdf}}
     \vspace{-5ex}
-  \caption{VBS in terms of correct \texttt{check-sat} answers (out of
-    \num{30370517} total) within a time limit of \SI{2400}{s} on
+    \caption{VBS in terms of correct \texttt{check-sat} answers (out
+      of \num{30370517} total) within a time limit of \SI{2400}{s} on
       common benchmarks 2015--2018 of all logics in the \apptrack.}
     \label{fig:progress-all-app}
-\end{figure}
-
-\begin{figure}
+  \end{minipage}\hfill
+  \begin{minipage}{0.47\textwidth}
     \centering
-  \scalebox{.45}{\includegraphics{%
+    \scalebox{.31}{\includegraphics{%
         plot/pdf/bar_plot-Virtual_Best_Solver_(VBS)_Unsat_Core_Track_2016-2018.pdf}}
@@
     \caption{VBS in terms of number of unsat core reductions within a
-    time limit of \SI{2400}{s} on common benchmarks 2016--2018 of all
-    logics in the \ucoretrack.}
+      time limit of \SI{2400}{s} on common benchmarks 2016--2018 of
+      all logics in the \ucoretrack.}
     \label{fig:progress-all-uc}
+  \end{minipage}
 \end{figure}

### 2019-08-27 2018/report/SMT-COMP.tex
Moving the scoring explanation

@@
 
+\subsection{Division Rankings}
+\label{sec:scoring-division-rankings}
+
+Solvers in each division (of each track) are ranked according to a
+metric that is based, first, on the number of erroneous responses
+(which is usually~0, but solvers that did give erroneous responses are
+ranked below solvers that did not); second, on the number of correct
+responses; third and fourth, on the wall-clock and CPU time,
+respectively, that the solver process consumed.  For the \ucoretrack
+(which uses unsatisfiable benchmarks only), the reduction in the size
+of the unsatisfiable core is used instead of the number of correct
+responses.  A detailed description of the scoring can be found in the
+competition rules~\cite{rules18}.
+
+As discussed in Section~\ref{sec:benchmarks}, \maintrack benchmarks
+with unknown status are removed from the competition results if two
+(or more) solvers that are sound on benchmarks with known status
+disagree on their result.  Otherwise, solver responses for benchmarks
+with unknown status are assumed to be correct.
+
+All solvers are run with four cores available, and the time limit~$T$
+that is imposed on each job pair (see Table~\ref{table:time-limits})
+is a wall-clock limit.  Thus, solvers that take advantage of
+parallelism might use up to~$4T$ CPU time.  For the \maintrack and the
+\ucoretrack, the competition reports parallel and sequential
+performance separately.  The latter is determined by imposing a
+(virtual) CPU time limit of~$T$.  For the \apptrack, only
+parallel performance is reported (because response times to individual
+{\tt check-sat} commands are not recorded by StarExec).
+
+A division is \emph{competitive} if
+at least two substantially different solvers (i.e., solvers from two
+different teams) were submitted.  (Experimental divisions are never
+competitive.)  Official winners were declared only for competitive
+divisions.
+
 The \emph{raw benchmark score} of a solver is a quadruple $\langle
@@
 assess sequential performance.
+
+\subsection{Competition-Wide Ranking}
+\label{sec:scoring:floc}
+
+In 2014, the SMT Competition was part of the FLoC Olympic Games, which
+sponsored three Kurt G\"odel medals.  These were awarded to the winner
+of the \maintrack's QF\_BV division (which had historically been the
+logic with the largest number of solver submissions and job pairs), as
+well as to the two best \maintrack solvers according to a
+competition-wide ranking that had been instituted especially for this
+purpose~\cite{CDW14}.  This ranking combines each solver's performance
+across all competitive \maintrack divisions into a single score,
+giving more weight to larger divisions, and to solvers that solve a
+large fraction of the benchmarks~\cite{rules18}.  It emphasizes
+breadth of solver participation---a solver participating in many
+logics does not need to be the best in any one of them to rank in high
+position.
+
+The competition-wide ranking for the \maintrack was retained and
+refined after~2014.  Table~\ref{table:competition-wide-ranking} shows
+the best three solvers according to this ranking for 2015--2018.  Also
+shown is Z3, which ranked in high position each year but was running
+hors concours.  Sequential and parallel performance are reported
+separately.
 
@@
 
-Solvers in each division (of each track) are ranked according to a
-metric that is based, first, on the number of erroneous responses
-(which is usually~0, but solvers that did give erroneous responses are
-ranked below solvers that did not); second, on the number of correct
-responses; third, on the wall-clock and CPU time that the solver
-process consumed.  For the \ucoretrack (which uses unsatisfiable
-benchmarks only), the reduction in the size of the unsatisfiable core
-is used instead of the number of correct responses.  A detailed
-description of the scoring can be found in the competition
-rules~\cite{rules18}.
-
-As discussed in Section~\ref{sec:benchmarks}, \maintrack benchmarks
-with unknown status are removed from the competition results if two
-(or more) solvers that are sound on benchmarks with known status
-disagree on their result.  Otherwise, solver responses for benchmarks
-with unknown status are assumed to be correct.
-
-All solvers are run with four cores available, and the time limit~$T$
-that is imposed on each job pair (see Table~\ref{table:time-limits})
-is a wall-clock limit.  Thus, solvers that take advantage of
-parallelism might use up to~$4T$ CPU time.  For the \maintrack and the
-\ucoretrack, the competition reports parallel and sequential
-performance separately.  The latter is determined by imposing a
-(virtual) CPU time limit of~$T$.  For the \apptrack, only
-parallel performance is reported (because response times to individual
-{\tt check-sat} commands are not recorded by StarExec).
-
-A division is \emph{competitive} if
-at least two substantially different solvers (i.e., solvers from two
-different teams) were submitted.  (Experimental divisions are never
-competitive.)  Official winners were declared only for competitive
-divisions.
-
 Tables~\ref{tab:winners-main}--\ref{tab:winners-unsat-core} show the
@@
 
-In 2014, the SMT Competition was part of the FLoC Olympic Games, which
-sponsored three Kurt G\"odel medals.  These were awarded to the winner
-of the \maintrack's QF\_BV division (which had historically been the
-logic with the largest number of solver submissions and job pairs), as
-well as to the two best \maintrack solvers according to a
-competition-wide ranking that had been instituted especially for this
-purpose~\cite{CDW14}.  This ranking combines each solver's performance
-across all competitive \maintrack divisions into a single score,
-giving more weight to larger divisions, and to solvers that solve a
-large fraction of the benchmarks~\cite{rules18}.  It emphasizes
-breadth of solver participation---a solver participating in many
-logics does not need to be the best in any one of them to rank in high
-position.
-
-The competition-wide ranking for the \maintrack was retained and
-refined after~2014.  Table~\ref{table:competition-wide-ranking} shows
-the best three solvers according to this ranking for 2015--2018.  Also
-shown is Z3, which ranked in high position each year but was running
-hors concours.  Sequential and parallel performance are reported
-separately.
+Table~\ref{table:competition-wide-ranking} shows the best three
+solvers according to the competition-wide ranking for 2015--2018.
+Also shown is Z3, which ranked in high position each year but was
+running hors concours.  Sequential and parallel performance are
+reported separately.
 %

### 2019-08-27 2018/report/SMT-COMP.tex
Minor

@@
 %\usepackage[numbers,sort&compress]{natbib}
-
-%\usepackage{showframe}   % debug
 
@@
 competition tools for the \apptrack (in particular, the trace
-executor) have not been adapted yet to support {\tt check-sat}
+executor) had not been adapted yet to support {\tt check-sat}
 commands with unknown status.
-Even though the trace executor has now been modified, we cannot check what impact this may have had on previous results without rerunning all tracks as the trace executor drives the solver.
+Even though the trace executor has now been modified, we cannot check what impact this may have had on previous results without rerunning the \apptrack as the trace executor drives the solver.
 

### 2019-08-27 2018/report/SMT-COMP.tex
Minor (fewer \cmidrules)

@@
   \scalebox{.89}{\begin{tabular}{cp{2.2cm}rrp{0cm}cp{2.2cm}rr}
-    \cmidrule[\heavyrulewidth]{1-4} \cmidrule[\heavyrulewidth]{6-9}
-    \multicolumn{4}{c}{2015} & & \multicolumn{4}{c}{2016} \\ \cmidrule{1-4} \cmidrule{6-9}
+    %\cmidrule[\heavyrulewidth]{1-4} \cmidrule[\heavyrulewidth]{6-9}
+    \multicolumn{4}{c}{2015} & & \multicolumn{4}{c}{2016} \\ \cmidrule[\heavyrulewidth]{1-4} \cmidrule[\heavyrulewidth]{6-9}
     Rank & Solver & Score  & Score  & & Rank & Solver & Score & Score \\
@@
   \scalebox{.89}{\begin{tabular}{cp{2.2cm}rrp{0cm}cp{2.2cm}rr}
-    \cmidrule[\heavyrulewidth]{1-4} \cmidrule[\heavyrulewidth]{6-9}
-    \multicolumn{4}{c}{2017} & & \multicolumn{4}{c}{2018} \\ \cmidrule{1-4} \cmidrule{6-9}
+    %\cmidrule[\heavyrulewidth]{1-4} \cmidrule[\heavyrulewidth]{6-9}
+    \multicolumn{4}{c}{2017} & & \multicolumn{4}{c}{2018} \\ \cmidrule[\heavyrulewidth]{1-4} \cmidrule[\heavyrulewidth]{6-9}
     Rank & Solver & Score  & Score  & & Rank & Solver & Score & Score \\

### 2019-08-27 2018/report/SMT-COMP.tex
problem -> benchmark; more work on Scoring

@@
 benchmarks are assumed to be correct, unless there is a disagreement
-between two or more solvers that are otherwise (i.e., on problems with
+between two or more solvers that are otherwise (i.e., on benchmarks with
 known status) sound.  Benchmarks with disagreements are removed from
@@
   \caption{Number of benchmarks used in the \maintrack (by division).
-Numbers in parentheses indicate the (rounded) percentage of problems with different statuses, which are (sat/unsat) in 2015 and 2016, and (sat/unsat/unknown) in 2017 and 2018.}
+Numbers in parentheses indicate the (rounded) percentage of benchmarks with different statuses, which are (sat/unsat) in 2015 and 2016, and (sat/unsat/unknown) in 2017 and 2018.}
   \label{table:benchmarks-main-track}
@@
 
+The \emph{raw benchmark score} of a solver is thus a quadruple
+$\langle e, n, w, c\rangle$, with
+\begin{itemize}[noitemsep]
+  \item \makebox[5em][l]{$e\geq 0$} number of erroneous responses (usually~$e = 0$),
+  \item \makebox[5em][l]{$0 \leq n \leq N$} number of correct responses (resp.~\emph{reduction} for the \ucoretrack),
+  \item \makebox[5em][l]{$w \in [0,T]$} wall-clock time in seconds (real-valued),
+  \item \makebox[5em][l]{$c \in [0, 4T]$} CPU time in seconds (real-valued).
+\end{itemize}
+%
+For the \maintrack and \apptrack, $e$ is the number of returned
+statuses that disagree with the given expected status; $e \in \{0,1\}$
+for the \maintrack.  (As described in Section~\ref{sec:benchmarks},
+disagreements between otherwise sound solvers on benchmarks with
+unknown status lead to the benchmark being disregarded.)  For the
+\ucoretrack, $e$ includes, in addition, the number of returned unsat
+cores that are ill-formed or are not, in fact, unsatisfiable (as
+validated by a selection of other solvers selected by organizers).
+
+For the \maintrack and \apptrack,
+$N$ is defined as the number of {\tt check-sat} commands ($N=1$ for the \maintrack), and
+$n$ is defined as the number of correct results.
+For the \ucoretrack, $N$ is defined as the number of named top-level assertions,
+and~$n$ is defined as the \emph{reduction}, i.e., the difference between $N$
+and the size of the unsat core returned by the solver.
+
+This raw score corresponds to the \emph{raw parallel score} (all values are
+determined for solver performance within the wall-clock time limit).  To
+evaluate sequential performance, we derive a \emph{raw sequential score} by
+imposing a (virtual) CPU time limit equal to the wall-clock time limit~$T$.  A
+solver result is taken into consideration for the sequential score only if the
+solver process terminates within this CPU time limit.
+
 As discussed in Section~\ref{sec:benchmarks}, \maintrack benchmarks
@@
 divisions.
-
-The \emph{raw benchmark score} of a solver is a quadruple $\langle
-e, n, w, c\rangle$, with
-\begin{itemize}[noitemsep]
-  \item \makebox[5em][l]{$e\geq 0$} number of erroneous results (usually~$e = 0$)
-  \item \makebox[5em][l]{$0 \leq n \leq N$} number of correct results (resp.~\emph{reduction} for the \ucoretrack)
-  \item \makebox[5em][l]{$w \in [0,T]$} wall-clock time in seconds (real-valued)
-  \item \makebox[5em][l]{$c \in [0, 4T]$} CPU time in seconds (real-valued)
-\end{itemize}
-\noindent
-For the \maintrack and \apptrack, $e$ is the number of returned statuses that disagree with the given expected status; $e \in \{0,1\}$ for the \maintrack.
-(As described above, disagreements between solvers on benchmarks with unknown status lead to the benchmark being disregarded.)  For the \ucoretrack, $e$ includes, in addition, the number of returned unsat cores that are ill-formed or are not, in fact, unsatisfiable (as validated by a selection of other solvers selected by organizers).
-
-For the \maintrack and \apptrack,
-$N$ is defined as the number of {\tt check-sat} commands ($N=1$ for the \maintrack), and
-$n$ is defined as the number of correct results.
-For the \ucoretrack, $N$ is defined as the number of named top-level assertions,
-and~$n$ is defined as the \emph{reduction}, i.e., the difference between $N$
-and the size of the unsat core returned by the solver.
-
-This raw score corresponds to the \emph{raw parallel score} (all values are
-determined for solver performance within the wall-clock time limit).  To
-evaluate sequential performance, we derive a \emph{raw sequential score} by
-imposing a (virtual) CPU time limit equal to the wall-clock time limit~$T$.  A
-solver result is taken into consideration for the sequential score only if the
-solver process terminates within this CPU time limit.
 
@@
 \subsection{Competition-Wide Ranking}
-\label{sec:scoring:floc}
+\label{sec:scoring-floc}
 
@@
 
+A contentious issue with this ranking has been the scoring of
+incorrect solver responses.  In the division rankings, an incorrect
+response causes a solver to be ranked below all correct solvers for
+that division.  But the competition's \maintrack consists of many
+independent divisions.  A solver bug that affects one division need
+not manifest itself in other divisions.  To balance the strong
+interest in correct solvers against the risk of stifling innovation,
+the competition-wide ranking was revised in~2017 to use a fixed
+numeric penalty for each division with incorrect responses.  The value
+of this penalty is currently set so that entering a (possibly buggy)
+solver that can solve all benchmarks into a division has a positive
+expected score if the probability that a soundness bug in the solver
+will be triggered is below~$20\,\%$.~\cite{rules18}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 competitively in the past, and one can assume that it was trained on
-the current problems.  The fact that industrial-strength solvers
+the current benchmarks.  The fact that industrial-strength solvers
 perform well in the competition supports the notion that the
@@
 Table~\ref{table:competition-wide-ranking} shows the best three
-solvers according to the competition-wide ranking for 2015--2018.
-Also shown is Z3, which ranked in high position each year but was
-running hors concours.  Sequential and parallel performance are
-reported separately.
+\maintrack solvers according to the competition-wide ranking for
+2015--2018.  Also shown is Z3, which ranked in high position each year
+but was running hors concours.  Sequential and parallel performance
+are reported separately.
 %
@@
 the set of benchmarks changes from one year to the other, and also the
-formula to compute the score changed (see below).  Moreover, readers
-should keep in mind that this ranking---like any method that maps the
-performance of solvers for a broad range of logics to a
-one-dimensional value---is inherently limited.  We refer to the
-individual division rankings (Section~\ref{sec:division-rankings}) for
-more detailed information about each solver.
+formula to compute the score changed (see
+Section~\ref{sec:scoring-floc}).  Moreover, readers should keep in
+mind that this ranking---like any method that maps the performance of
+solvers for a broad range of logics to a one-dimensional value---is
+inherently limited.  We refer to the individual division rankings
+(Section~\ref{sec:division-rankings}) for more detailed information
+about each solver.
 
@@
 
-A contentious issue with this ranking has been the scoring of
-incorrect solver responses.  In the division rankings, an incorrect
-response causes a solver to be ranked below all correct solvers for
-that division.  But the competition's \maintrack consists of many
-independent divisions.  A solver bug that affects one division need
-not manifest itself in other divisions.  To balance the strong
-interest in correct solvers against the risk of stifling innovation,
-the competition-wide ranking was revised in~2017 to use a fixed
-numeric penalty for each division with incorrect responses.  The value
-of this penalty is currently set so that entering a (possibly buggy)
-solver that can solve all benchmarks into a division has a positive
-expected score if the probability that a soundness bug in the solver
-will be triggered is below~$20\,\%$.~\cite{rules18}
-
-The 2018 edition of the competition was again part of the FLoC Olympic
+The 2018 edition of the competition was part of the FLoC Olympic
 Games, which sponsored seven medals.  The competition organizers
@@
 \item the solver that won the most competitive divisions in the
-  \apptrack (Yices2),
+  \apptrack (Yices2; see Table~\ref{tab:winners-application}),
 \item the solver that won the most competitive divisions in the
-  \ucoretrack (Yices2).
+  \ucoretrack (Yices2; see Table~\ref{tab:winners-unsat-core}).
 \end{itemize}
@@
 
-For the \emph{\maintrack}, we determine the VBS as the best wall-clock
-performance per (correctly solved) instance with the time limit of 1200s used
+For the \maintrack, we determine the VBS as the best wall-clock
+performance per (correctly solved) instance with the time limit of \SI{1200}{s} used
 in the competitions 2017 and 2018. Figure~\ref{fig:progress-all} visualizes VBS
@@
 %
-Between 2014 (\num{67426} benchmarks) and 2015 (\num{154238} benchmarks),
+Between 2014 (\num{67426} benchmarks) and~2015 (\num{154238} benchmarks),
 the number of common benchmarks is \num{67070};
@@
 
-For the \emph{\apptrack}, we determine the VBS as the best performance
+For the \apptrack, we determine the VBS as the best performance
 in terms of number of correct \texttt{check-sat} answers within the time limit
-of 2400s (the time limit of the \apptrack in the competitions
+of \SI{2400}{s} (the time limit of the \apptrack in the competitions
 2015--2018).
@@
 
-For the \emph{\ucoretrack}, we determine the VBS as the best performance in
-terms of \emph{reduction}, i.e., the difference in the number of assertions
+For the \ucoretrack, we determine the VBS as the best performance in
+terms of reduction, i.e., the difference in the number of assertions
 of the input formula and the unsat core, within the time limit
-of 2400s (the time limit of the \ucoretrack in the competitions
+of \SI{2400}{s} (the time limit of the \ucoretrack in the competitions
 2016--2018).
@@
 they contain only one single \texttt{assert} command.
-They are thus also not considered in the bar plot, since their maximum
+They are thus not considered in the bar plot, since their maximum
 possible reduction is trivially 0.
@@
 It is interesting to note that we see some new solvers winning divisions that did not win any division in the main results.
-For example, Alt-Ergo solves the most satisfiable problems in AUFLIA and ALIA in 2018, and SMTInterpol performs very well on unsatisfiable problems in QF\_LIA.
-
-We only consider the \maintrack here, which contains a mixture of problems that
+For example, Alt-Ergo solves the most satisfiable benchmarks in AUFLIA and ALIA in 2018, and SMTInterpol performs very well on unsatisfiable benchmarks in QF\_LIA.
+
+We only consider the \maintrack here, which contains a mixture of benchmarks that
 are satisfiable and unsatisfiable. A percentage of satisfiable, unsatisfiable

### 2019-08-27 2018/report/Reviews_67398_Revised_Response.txt
WONTFIX: Figure 5
Minor
Reduce the size of Figures 5 and 6
Footnote 1 now happens to be on the correct page
problem -> benchmark; more work on Scoring
Scoring

@@
 
-TODO
+DONE (all information about the scoring rules was moved into a new
+Section 7)
 
@@
 
-TODO
+DONE (raw benchmark scores are now introduced in a new Section 7)
 
@@
 
-TODO
+DONE (benchmark families are now introduced in a new Section 7)
 
@@
 
-TODO
+DONE (the division weight, log N_i)
 
@@
 
-TODO
+WONTFIX (we have a similar figure for each track; omitting it for the
+Application Track merely for space reasons seems unnecessary, and it
+serves to show that the difference is hardly visible---however, we
+reduced the size of the figure)
 
@@
 
-TODO
+DONE

### 2019-08-27 2018/report/SMT-COMP.tex
Scoring

@@
 
-\paragraph{Eligible Benchmarks.}
+\paragraph{Eligible benchmarks.}
 Some benchmarks typically have to be
@@
 
-\paragraph{Benchmark Selection.}
+\paragraph{Benchmark selection.}
 SMT Competitions until~2014 employed a pseudo-random selection process
@@
 
-\paragraph{Benchmarks with Unknown Status.}
+\paragraph{Benchmarks with unknown status.}
 Another paradigm shift concerns the treatment of benchmarks with
@@
 
+A detailed description of the scoring can be found in the competition
+rules~\cite{rules18}.  We summarize the most important aspects in this
+section.
+
 \subsection{Division Rankings}
@@
 responses; third and fourth, on the wall-clock and CPU time,
-respectively, that the solver process consumed.  For the \ucoretrack
-(which uses unsatisfiable benchmarks only), the reduction in the size
-of the unsatisfiable core is used instead of the number of correct
-responses.  A detailed description of the scoring can be found in the
-competition rules~\cite{rules18}.
-
+respectively, that the solver process consumed.
+%
 The \emph{raw benchmark score} of a solver is thus a quadruple
@@
 statuses that disagree with the given expected status; $e \in \{0,1\}$
-for the \maintrack.  (As described in Section~\ref{sec:benchmarks},
-disagreements between otherwise sound solvers on benchmarks with
-unknown status lead to the benchmark being disregarded.)  For the
-\ucoretrack, $e$ includes, in addition, the number of returned unsat
-cores that are ill-formed or are not, in fact, unsatisfiable (as
-validated by a selection of other solvers selected by organizers).
-
-For the \maintrack and \apptrack,
-$N$ is defined as the number of {\tt check-sat} commands ($N=1$ for the \maintrack), and
-$n$ is defined as the number of correct results.
-For the \ucoretrack, $N$ is defined as the number of named top-level assertions,
-and~$n$ is defined as the \emph{reduction}, i.e., the difference between $N$
-and the size of the unsat core returned by the solver.
-
-This raw score corresponds to the \emph{raw parallel score} (all values are
-determined for solver performance within the wall-clock time limit).  To
-evaluate sequential performance, we derive a \emph{raw sequential score} by
-imposing a (virtual) CPU time limit equal to the wall-clock time limit~$T$.  A
-solver result is taken into consideration for the sequential score only if the
-solver process terminates within this CPU time limit.
+for the \maintrack.  For the \ucoretrack, $e$ includes, in addition,
+the number of returned unsat cores that are ill-formed or are not, in
+fact, unsatisfiable (as validated by a selection of solvers selected
+by the organizers).
+
+For the \maintrack and \apptrack, $N$ is defined as the number of {\tt
+  check-sat} commands ($N=1$ for the \maintrack), and $n$ is defined
+as the number of correct responses.  For the \ucoretrack (which uses
+unsatisfiable benchmarks only), $N$ is defined as the number of named
+top-level assertions, and~$n$ is defined as the \emph{reduction},
+i.e., the difference between $N$ and the size of the unsat core
+returned by the solver.
 
@@
 
+A division is \emph{competitive} if at least two substantially
+different solvers (i.e., solvers from two different teams) were
+submitted.  (Experimental divisions are never competitive.)  Official
+winners were declared only for competitive divisions.
+
+\paragraph{Parallel vs.\ sequential performance.}
+
 All solvers are run with four cores available, and the time limit~$T$
@@
 \ucoretrack, the competition reports parallel and sequential
-performance separately.  The latter is determined by imposing a
-(virtual) CPU time limit of~$T$.  For the \apptrack, only
+performance separately.  The raw benchmark score corresponds to the
+\emph{raw parallel score}---all values are determined for solver
+performance within the wall-clock time limit.  We derive a \emph{raw
+  sequential score} by imposing a (virtual) CPU time limit equal to
+the wall-clock time limit~$T$.  A solver response is taken into
+consideration for the sequential score only if the solver process
+terminates within this CPU time limit.  For the \apptrack, only
 parallel performance is reported (because response times to individual
@@
 
-A division is \emph{competitive} if
-at least two substantially different solvers (i.e., solvers from two
-different teams) were submitted.  (Experimental divisions are never
-competitive.)  Official winners were declared only for competitive
-divisions.
+\paragraph{Benchmark weights.}
 
@@
 determine the division score of a solver as the sum of the scores of
-all benchmarks in that division.  Fewer errors in a division takes
-precedence over more correct solutions (resp.~reduction), which takes
-precedence over less wall-clock time taken, which takes precedence
-over less CPU time taken.  However, since there are vast differences
-in size between benchmark families (i.e., groups of benchmarks with
-similar characteristics) in the SMT Library, the competition
-since~2016 uses a scoring method that assigns a weight to each
-benchmark in the \maintrack and \ucoretrack in order to de-emphasize
-large benchmark families~\cite{rules16,rules17,rules18}.  For
-application track divisions, division scores were still based on raw
-scores only, since application track benchmarks may be partially
-solved.  Defining a useful sequential score for the application track
-would require information not provided by the raw score, e.g.,
-detailed timing information for each result.
-
-\paragraph{Benchmark Weights (\maintrack and \ucoretrack 2016--2018).} The \emph{weight} of a
-benchmark in the main track is computed as $\alpha = (1 + \ln F)/F$,
-where~$F\geq 1$ is the size of the benchmark's family.  We then define its
-\emph{normalized weight} as $\alpha' = \alpha / (\sum_{i\in F} \alpha_i)$,
-where the sum is over all benchmarks in the division.  The log scaling seems a
-reasonable compromise between linearly combining numbers of benchmarks, which
-would overemphasize large families, and simply averaging the fraction of
-benchmarks solved, which would overemphasize small families.
-
-\paragraph{Weighted Division Scores (\maintrack and \ucoretrack 2016--2018).}
-The \emph{(weighted) score} of a solver in a division of the \maintrack and
-\ucoretrack with $M$ benchmarks is then defined as the weighted sum of all raw
-scores $$\sum_{b\in M} \alpha'_b \cdot \langle e_b \cdot N, n_b \cdot N,
-w_b, c_b\rangle$$ where the sum is over all benchmarks in the division to
-assess parallel performance, and the weighted sum of all sequential scores to
-assess sequential performance.
-
-\subsection{Competition-Wide Ranking}
+all benchmarks in that division.  However, there are vast differences
+in size between benchmark \emph{families} (i.e., groups of benchmarks
+with similar characteristics) in the SMT Library.  The pseudo-random
+selection process of benchmarks that was used until~2014 (see
+Section~\ref{sec:benchmarks}) ensured that large families were not
+overemphasized in the competition.  Since~2016, the competition uses a
+scoring method that assigns a weight to each benchmark in the
+\maintrack and \ucoretrack to achieve the same
+goal~\cite{rules16,rules17,rules18}.
+
+The \emph{weight} of a benchmark~$b$ in the \maintrack is computed as
+$\alpha_b = (1 + \ln F_b)/F_b$, where $F_b \geq 1$ is the size of the
+benchmark's family.  We then define its \emph{normalized weight} as
+$\alpha'_b = \alpha_b / (\sum_{b'} \alpha_{b'})$, where the sum is
+over all benchmarks in the division.  The logarithmic scaling seems a
+reasonable compromise between linearly combining numbers of
+benchmarks, which would overemphasize large families, and simply
+averaging the fraction of benchmarks solved, which would overemphasize
+small families.
+
+The \emph{(weighted) score} of a solver in a (\maintrack or
+\ucoretrack) division~$D$ is then defined as the weighted sum of all
+raw scores
+%
+$$\sum_{b\in D} \alpha'_b \cdot \langle e_b \cdot |D|, n_b \cdot |D|, w_b,
+  c_b\rangle$$
+%
+where the sum is over all benchmarks in the division, and~$|D|$ is the
+number of benchmarks in~$D$.  This is computed separately for parallel
+and sequential performance.
+
+For \apptrack divisions, division scores were still based on raw
+scores only, since \apptrack benchmarks may be partially solved.
+
+\subsection{Competition-Wide Ranking (\maintrack)}
 \label{sec:scoring-floc}
@@
 The competition-wide ranking for the \maintrack was retained and
-refined after~2014.  Table~\ref{table:competition-wide-ranking} shows
-the best three solvers according to this ranking for 2015--2018.  Also
-shown is Z3, which ranked in high position each year but was running
-hors concours.  Sequential and parallel performance are reported
-separately.
-
-\paragraph{Competition-Wide Score (\maintrack).}
-A competition-wide metric for the main track, separately for
-parallel and sequential performance, was defined as follows.
-
-Let $N_i$ be the total number of benchmarks in division~$i$ that were used in the
-competition (and not removed because of disagreements), and let $\langle e_i, n_i, w_i, c_i\rangle$ be a solver's
-raw score for this division.
+refined after~2014.  Sequential and parallel performance are reported
+separately.  Let $N_i$ be the total number of benchmarks in
+division~$i$ that were used in the competition (and not removed
+because of disagreements), and let $\langle e_i, n_i, w_i, c_i\rangle$
+be a solver's raw score for this division.
 %
-In 2015 and 2016,
-the \emph{competition-wide raw score} for a solver was defined as
+In 2015 and~2016, the \emph{competition-wide raw score} for a solver
+was defined as
 %
-$\sum_i (e_i == 0 \,?\, (n_i/N_i)^2 : -e_i) \log N_i$,
-%
-where the sum is over all competitive
-divisions into which the solver was
-entered.
-%
-In 2017, the (per-division) penalty for erroneous results was changed from the
-number of errors to a fixed constant, since the weight already takes the number
-of benchmarks in the division into account, and multiplying it by the number of
-errors overemphasizes large divisions.
-In 2017 and 2018,
-the \emph{competition-wide raw score} for a solver was thus defined as
-%
-$\sum_i (e_i == 0 \,?\, (n_i/N_i)^2 : -4) \log_e N_i$,
+$$\sum_i (e_i == 0 \,?\, (n_i/N_i)^2 : -e_i) \log N_i$$
 %
@@
 was entered.
-
-A contentious issue with this ranking has been the scoring of
-incorrect solver responses.  In the division rankings, an incorrect
-response causes a solver to be ranked below all correct solvers for
-that division.  But the competition's \maintrack consists of many
-independent divisions.  A solver bug that affects one division need
-not manifest itself in other divisions.  To balance the strong
-interest in correct solvers against the risk of stifling innovation,
-the competition-wide ranking was revised in~2017 to use a fixed
-numeric penalty for each division with incorrect responses.  The value
-of this penalty is currently set so that entering a (possibly buggy)
-solver that can solve all benchmarks into a division has a positive
-expected score if the probability that a soundness bug in the solver
-will be triggered is below~$20\,\%$.~\cite{rules18}
+%
+In 2017, the (per-division) penalty for erroneous results was changed
+from the number of errors to a fixed constant, since the division
+weight~$\log N_i$ already takes the number of benchmarks in the
+division into account, and multiplying it by the number of errors
+overemphasizes large divisions.  In 2017 and 2018, the
+\emph{competition-wide raw score} for a solver was thus defined as
+%
+$$\sum_i (e_i == 0 \,?\, (n_i/N_i)^2 : -4) \log_e N_i$$
+%
+The value of this constant was chosen to balance the strong interest
+in correct solvers against the risk of stifling innovation.  In the
+division rankings (Section~\ref{sec:scoring-division-rankings}), an
+incorrect response causes a solver to be ranked below all correct
+solvers for that division.  But the competition's \maintrack consists
+of many independent divisions; a solver bug that affects one division
+need not manifest itself in other divisions.  With the current value,
+entering a (possibly buggy) solver that can solve all benchmarks into
+a division has a positive expected score if the probability that a
+soundness bug in the solver will be triggered is below~$20\,\%$.
 

### 2019-08-27 2018/report/SMT-COMP.tex
Fix reference to Figure 6
Layout

@@
       time limit of \SI{2400}{s} on common benchmarks 2016--2018 of
-      all logics in the \ucoretrack.}
+      all logics in the \ucoretrack.\\${}$}
     \label{fig:progress-all-uc}
@@
 2016--2018).
-Figure~\ref{fig:progress-all-app} visualizes VBS performance on the common
+Figure~\ref{fig:progress-all-uc} visualizes VBS performance on the common
 benchmarks (\num{91455} total) from 2016--2018 as a bar plot.

### 2019-08-27 2018/report/SMT-COMP.tex
Minor

@@
 
-Tables~\ref{table:participants1}-\ref{table:participants3} list the solvers
+Tables~\ref{table:participants1}--\ref{table:participants3} list the solvers
 that participated between~2015 and~2018, together with contributing team

### 2019-08-27 2018/report/SMT-COMP.tex
log -> ln

@@
 %
-$$\sum_i (e_i == 0 \,?\, (n_i/N_i)^2 : -e_i) \log N_i$$
+$$\sum_i (e_i == 0 \,?\, (n_i/N_i)^2 : -e_i) \ln N_i$$
 %
@@
 from the number of errors to a fixed constant, since the division
-weight~$\log N_i$ already takes the number of benchmarks in the
+weight~$\ln N_i$ already takes the number of benchmarks in the
 division into account, and multiplying it by the number of errors
@@
 %
-$$\sum_i (e_i == 0 \,?\, (n_i/N_i)^2 : -4) \log_e N_i$$
+$$\sum_i (e_i == 0 \,?\, (n_i/N_i)^2 : -4) \ln N_i$$
 %

### 2019-08-27 2018/report/SMT-COMP.tex
Minor
Clarify that we list team members as reported by the development teams

@@
 members (in alphabetical order) and their institutional affiliations (which may
-have changed over time).
+have changed over time) as reported by the development teams.
 
@@
 number of benchmarks in~$D$.  This is computed separately for parallel
-and sequential performance.
+and sequential scores.
 

### 2019-08-27 2018/report/SMT-COMP.tex
Institutional affiliations are optional

@@
 
-Tables~\ref{table:participants1}--\ref{table:participants3} list the solvers
-that participated between~2015 and~2018, together with contributing team
-members (in alphabetical order) and their institutional affiliations (which may
-have changed over time) as reported by the development teams.
+Tables~\ref{table:participants1}--\ref{table:participants3} list the
+solvers that participated between~2015 and~2018, together with
+contributing team members (in alphabetical order) and their
+institutional affiliations (if any; these may have changed over time)
+as reported by the development teams.
 

### 2019-08-27 2018/report/SMT-COMP.tex
Grammar

@@
 Tables~\ref{tab:winners-main}--\ref{tab:winners-unsat-core} show the
-highest-ranked solvers for all (competitive and non-competitive) division from
+highest-ranked solvers for all (competitive and non-competitive) divisions from
 2015--2018.

### 2019-08-29 2018/report/SMT-COMP.tex
Minor
Report: Consistent table layout for App and UC.

@@
 
-% macros for tracks for more constistency
+% macros for tracks for more consistency
 \newcommand{\maintrack}{Main Track\xspace}
@@
 \colorlet{stp}{Fuchsia!10}
+\colorlet{mink}{Magenta!10}
 \colorlet{nonc}{black!55}
@@
 and ineligible to be recognized as official competition winners).
-Non-com-petitive divisions use gray font.
+Non-com-petitive divisions use gray font. % TODO superscript?
 Entries $A [B]$ indicate that solver $A$ was the highest competing solver,
@@
 Entries
-$A/B$ indicate that solver~$A$ ranked first considering sequential
+$A|B$ indicate that solver~$A$ ranked first considering sequential
 performance, while~$B$ ranked first considering parallel performance.
@@
 case, its name appears just once.
-Table cell colors (other than white) indicate the best competing sequential
-solver performance; no cell color indicates that the best sequential solver
+Table cell colors (other than white) indicate the best competing
+solver performance; no cell color indicates that the best solver
 performance was by a non-competing solver and no competing solvers participated

### 2019-08-29 2018/report/table-winners-unsat-core.tex
Update caption of winners tables.
Fix.
Remove period
Revert "Remove period"
This reverts commit 642caca4681cb9f17cf171ea2072f96ac1473901.
Minor
Report: Consistent table layout for App and UC.

--- 2019-03-19 2018/report/table-winners-unsat-core.tex
@@
 \begin{table}
-  \caption{Best unsat-core track solvers (by division)}
+  \caption{Best \ucoretrack solvers (by division)}
   \label{tab:winners-unsat-core}
@@
   \scalebox{.88}{%
-    \begin{tabular}{r@{\hskip 1em}>{\columncolor[gray]{.95}[.25em][.5em]}c@{\hskip 1em}>{\columncolor[gray]{.95}[.5em][.5em]}c@{\hskip 1em}>{\columncolor[gray]{.95}[.5em][.5em]}c}
+    \renewcommand{\arraystretch}{1.01}%
+    \begin{tabular}{r>{\columncolor{white}[.25em][.8em]}r@{\hskip .8em}|@{\hskip .5em}>{\columncolor{white}[.5em][.5em]}l>{\columncolor{white}[.5em][.8em]}r@{\hskip .8em}|@{\hskip .5em}>{\columncolor{white}[.5em][.5em]}l>{\columncolor{white}[.5em][.8em]}r@{\hskip .8em}|@{\hskip .5em}>{\columncolor{white}[.5em][0.5em]}l}
       \toprule
-    \rc
-    Division   & 2016             & 2017            & 2018               \\
-    \hline \hline
-    \cc ALIA       & \cc \nc{Z3} *                  & CVC4 \nc{Z3} *                      & CVC4 \nc{Z3} *           \\
-    \cc AUFBVDTLIA & \cc                            & \cc                                 & CVC4 *                   \\
-    \cc AUFLIA     & \cc \nc{Z3} *                  & CVC4 \nc{Z3} *                      & CVC4 *                   \\
-    \cc AUFLIRA    & \cc \nc{Z3} *                  & CVC4 \nc{Z3} *                      & CVC4 *                   \\
-    \cc AUFNIRA    & \cc \nc{Z3} *                  & CVC4 *                              & CVC4 *                   \\
-    \cc BV         & \cc \nc{Z3} *                  & CVC4 \nc{Z3} *                      & CVC4 \nc{Z3} *           \\
-    \cc LIA        & \cc \nc{veriT} *               & CVC4 *                              & CVC4 \nc{Z3} *           \\
-    \cc LRA        & \cc \nc{veriT} *               & CVC4 *                              & CVC4 *                   \\
-    \cc NIA        & \cc \nc{Z3} *                  & CVC4 / CVC4 \nc{Z3}*                & CVC4 *                   \\
-    \cc NRA        & \cc \nc{Z3} *                  & CVC4 \nc{Z3} *                      & CVC4 \nc{Z3} *           \\
-    \cc QF\_ABV    & \cc \nc{Z3} *                  & CVC4 \nc{Z3} *                      & Yices2                   \\
-    \cc QF\_ABVFP  & \cc                            & \cc ---                             & \cc CVC4 *               \\
-    \rc
-    \cc QF\_ALIA   & SMTInterpol \nc{Z3} *          & SMTInterpol \nc{Z3}                 & Yices2 \nc{Z3}           \\
-    \cc QF\_ANIA   & \cc \nc{Z3} *                  & CVC4 *                              & CVC4 *                   \\
-    \rc
-    \cc QF\_AUFBV  & \nc{Z3} *                      & CVC4 \nc{MathSAT} *                 & Yices2 \nc{MathSAT}      \\
-    \cc QF\_AUFLIA & \cc SMTInterpol \nc{Z3} *      & CVC4                                & CVC4                     \\
-    \cc QF\_AUFNIA & \cc \nc{Z3} *                  & CVC4 \nc{Z3} *                      & CVC4 \nc{Z3} *           \\
-    \drc
-    \cc QF\_AX     & SMTInterpol \nc{Z3} *          & SMTInterpol \nc{Z3}                 & \cc Yices2               \\
-    \rc
-    \cc QF\_BV     & \nc{MathSAT} *                 & CVC4 \nc{MathSAT} *                 & Yices2                   \\
-    \cc QF\_BVFP   & \nc{Z3} *                      & \nc{Z3} *                           & \cc CVC4 \nc{Z3} *       \\
-    \rc
-    \cc QF\_DT     &                                &                                     & CVC4 *                   \\
-    \rc
-    \cc QF\_FP     & \nc{MathSAT} *                 & \nc{Z3} *                           & CVC4 *                   \\
-    \cc QF\_IDL    & \cc SMTInterpol \nc{Z3} *      & CVC4 \nc{Z3}                        & CVC4 \nc{Z3}             \\
-    \drc
-    \cc QF\_LIA    & SMTInterpol \nc{Z3} *          & SMTInterpol / SMTInterpol \nc{Z3}   & SMTInterpol              \\
-    \cc QF\_LIRA   & \cc SMTInterpol \nc{Z3} *      & CVC4 \nc{Z3}                        & CVC4 \nc{Z3}             \\
-    \drc
-    \cc QF\_LRA    & SMTInterpol *                  & SMTInterpol                         & SMTInterpol              \\
-    \cc QF\_NIA    & \cc \nc{Z3} *                  & CVC4 \nc{Z3} *                      & CVC4 \nc{Z3} *           \\
-    \cc QF\_NIRA   & \cc \nc{Z3} *                  & CVC4 \nc{Z3} *                      & CVC4 \nc{Z3} *           \\
-    \cc QF\_NRA    & \cc \nc{Z3} *                  & CVC4 *                              & CVC4 *                   \\
-    \cc QF\_RDL    & \cc SMTInterpol \nc{veriT} *   & CVC4 \nc{Z3}                        & CVC4 \nc{Z3}             \\
-    \cc QF\_UF     & \cc SMTInterpol \nc{MathSAT} * & CVC4                                & CVC4                     \\
-    \rc
-    \cc QF\_UFBV   & \nc{MathSAT} *                 & CVC4 \nc{MathSAT} *                 & Yices2 \nc{Z3}           \\
-    \drc
-    \cc QF\_UFIDL  & SMTInterpol \nc{Z3} *          & SMTInterpol \nc{Z3}                 & \cc Yices2               \\
-    \drc
-    \cc QF\_UFLIA  & SMTInterpol \nc{MathSAT} *     & SMTInterpol \nc{Z3}                 & SMTInterpol \nc{Z3}      \\
-    \drc
-    \cc QF\_UFLRA  & SMTInterpol \nc{Z3} *          & SMTInterpol \nc{MathSAT}            & \cc Yices2 \nc{MathSAT}  \\
-    \cc QF\_UFNIA  & \cc \nc{Z3} *                  & CVC4 \nc{Z3} *                      & CVC4 \nc{Z3} *           \\
-    \cc QF\_UFNRA  & \cc \nc{Z3} *                  & CVC4 \nc{Z3} *                      & CVC4 \nc{Z3} *           \\
-    \cc UF         & \cc \nc{Z3} *                  & CVC4 *                              & CVC4 *                   \\
-    \cc UFBV       & \cc \nc{Z3} *                  & CVC4 \nc{Z3} *                      & CVC4 *                   \\
-    \rc
-    \cc UFDT       &                                &                                     & CVC4 *                   \\
-    \cc UFIDL      & \cc \nc{Z3} *                  & CVC4 *                              & CVC4 *                   \\
-    \cc UFLIA      & \cc \nc{Z3} *                  & CVC4 *                              & CVC4 *                   \\
-    \cc UFLRA      & \cc \nc{Z3} *                  & CVC4 \nc{Z3} *                      & CVC4 \nc{Z3} *           \\
-    \cc UFNIA      & \cc \nc{Z3} *                  & CVC4 *                              & CVC4 *                   \\
+       Division       & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{2016                          } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{2017                              } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{2018                          } \\
+      \midrule
+       ALIA       & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nc{Z3}                          } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 \nc{Z3}      } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 \nc{Z3}  } \\
+       AUFBVDTLIA & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{                                  } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{                                  } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4          } \\
+       AUFLIA     & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nc{Z3}                          } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 \nc{Z3}      } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4          } \\
+       AUFLIRA    & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nc{Z3}                          } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 \nc{Z3}      } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4          } \\
+       AUFNIRA    & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nc{Z3}                          } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4              } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4          } \\
+       BV         & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nc{Z3}                          } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 \nc{Z3}      } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 \nc{Z3}  } \\
+       LIA        & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nc{veriT}                       } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4              } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 \nc{Z3}  } \\
+       LRA        & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nc{veriT}                       } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4              } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4          } \\
+       NIA        & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nc{Z3}                          } & \nonc \cc{cvc4} CVC4 & \nonc \cc{cvc4} CVC4 \nc{Z3}                                      & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4          } \\
+       NRA        & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nc{Z3}                          } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 \nc{Z3}      } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 \nc{Z3}  } \\
+       QF\_ABV    & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nc{Z3}                          } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 \nc{Z3}      } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices2             } \\
+       QF\_ABVFP  & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{                                  } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{---                               } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4          } \\
+       QF\_ALIA   & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{smti} SMTInterpol \nc{Z3}     } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{smti} SMTInterpol \nc{Z3}     } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices2 \nc{Z3}     } \\
+       QF\_ANIA   & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nc{Z3}                          } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4              } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4          } \\
+       QF\_AUFBV  & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nc{Z3}                           } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 \nc{MathSAT} } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices2 \nc{MathSAT}} \\
+       QF\_AUFLIA & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{smti} SMTInterpol \nc{Z3}     } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4                    } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4                } \\
+       QF\_AUFNIA & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nc{Z3}                          } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 \nc{Z3}      } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 \nc{Z3}  } \\
+       QF\_AX     & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{smti} SMTInterpol \nc{Z3}     } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{smti} SMTInterpol \nc{Z3}     } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices2             } \\
+       QF\_BV     & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nc{MathSAT}                      } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 \nc{MathSAT} } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices2             } \\
+       QF\_BVFP   & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nc{Z3}                           } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \nc{Z3}                     } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 \nc{Z3}  } \\
+       QF\_DT     & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{                                  } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{                                  } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4          } \\
+       QF\_FP     & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nc{MathSAT}                      } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \nc{Z3}                     } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4          } \\
+       QF\_IDL    & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{smti} SMTInterpol \nc{Z3}     } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4 \nc{Z3}            } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4 \nc{Z3}        } \\
+       QF\_LIA    & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{smti} SMTInterpol \nc{Z3}     } & \cc{smti} SMTInterpol & \cc{smti} SMTInterpol \nc{Z3}                                    & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{smti} SMTInterpol         } \\
+       QF\_LIRA   & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{smti} SMTInterpol \nc{Z3}     } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4 \nc{Z3}            } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4 \nc{Z3}        } \\
+       QF\_LRA    & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{smti} SMTInterpol             } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{smti} SMTInterpol             } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{smti} SMTInterpol         } \\
+       QF\_NIA    & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nc{Z3}                          } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 \nc{Z3}      } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 \nc{Z3}  } \\
+       QF\_NIRA   & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nc{Z3}                          } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 \nc{Z3}      } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 \nc{Z3}  } \\
+       QF\_NRA    & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nc{Z3}                          } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4              } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4          } \\
+       QF\_RDL    & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{smti} SMTInterpol \nc{veriT}  } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4 \nc{Z3}            } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4 \nc{Z3}        } \\
+       QF\_UF     & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{smti} SMTInterpol \nc{MathSAT}} & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4                    } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4                } \\
+       QF\_UFBV   & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nc{MathSAT}                      } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 \nc{MathSAT} } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices2 \nc{Z3}     } \\
+       QF\_UFIDL  & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{smti} SMTInterpol \nc{Z3}     } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{smti} SMTInterpol \nc{Z3}     } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices2             } \\
+       QF\_UFLIA  & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{smti} SMTInterpol \nc{MathSAT}} & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{smti} SMTInterpol \nc{Z3}     } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{smti} SMTInterpol \nc{Z3} } \\
+       QF\_UFLRA  & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{smti} SMTInterpol \nc{Z3}     } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{smti} SMTInterpol \nc{MathSAT}} & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices2 \nc{MathSAT}} \\
+       QF\_UFNIA  & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nc{Z3}                          } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 \nc{Z3}      } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 \nc{Z3}  } \\
+       QF\_UFNRA  & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nc{Z3}                          } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 \nc{Z3}      } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 \nc{Z3}  } \\
+       UF         & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nc{Z3}                          } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4              } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4          } \\
+       UFBV       & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nc{Z3}                          } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 \nc{Z3}      } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4          } \\
+       UFDT       & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{                                  } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{                                  } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4          } \\
+       UFIDL      & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nc{Z3}                          } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4              } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4          } \\
+       UFLIA      & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nc{Z3}                          } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4              } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4          } \\
+       UFLRA      & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nc{Z3}                          } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 \nc{Z3}      } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 \nc{Z3}  } \\
+       UFNIA      & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nc{Z3}                          } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4              } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4          } \\
+      \bottomrule
     \end{tabular}

### 2019-08-29 2018/report/table-winners-main.tex
Update caption of winners tables.
Fix.
Report: Layout and clean up sat/unsat/24s tables.
Remove period
Revert "Remove period"
This reverts commit 642caca4681cb9f17cf171ea2072f96ac1473901.
Minor
Report: Update layout of winners main table.

@@
 \begin{table}
-\caption{Best main-track solvers (by division)}
+\caption{Best \maintrack solvers (by division)}
 \label{tab:winners-main}
 \centering
-\scalebox{.83}{%
+\scalebox{.82}{%
 \renewcommand{\arraystretch}{1.01}%
@@
     Division         &  2015                        &  2016                     &  2017                           &  2018                     \\
-    \hline \hline
+    \midrule
     \wc ABVFP        &                              &                           &                                 & \nonc \cc{cvc4} {CVC4}    \\
@@
 \end{table}
+
+\begin{table}
+\caption{Best \maintrack solvers (by division). NEW}
+\label{tab:winners-main}
+\centering
+\scalebox{.82}{%
+\renewcommand{\arraystretch}{1.01}%
+
+\begin{tabular}{r>{\columncolor{white}[.25em][.8em]}r@{\hskip .8em}|@{\hskip .5em}>{\columncolor{white}[.5em][.5em]}l>{\columncolor{white}[.5em][.8em]}r@{\hskip .8em}|@{\hskip .5em}>{\columncolor{white}[.5em][.5em]}l>{\columncolor{white}[.5em][.8em]}r@{\hskip .8em}|@{\hskip .5em}>{\columncolor{white}[.5em][0.5em]}l>{\columncolor{white}[.5em][.8em]}r@{\hskip .8em}|@{\hskip .5em}>{\columncolor{white}[.5em][0.5em]}l}
+\toprule
+Division &                      \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{2015} &                      \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{2016} &                        \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{2017} &                   \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{2018} \\
+\midrule
+ABVFP      &                          \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                          \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                            \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &         \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4} \\
+ALIA       &       \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4 [Z3]} &       \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4 [Z3]} &         \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4 [Z3]} &    \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4 [Z3]} \\
+AUFBVDTLIA &                          \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                          \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &              \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4} &         \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4} \\
+AUFDTLIA   &                          \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                          \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &              \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4} &         \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4} \\
+AUFLIA     &            \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4} &            \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4} &              \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4} &         \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4} \\
+AUFLIRA    &       \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4 [Z3]} &    \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{vamp} Vampire [Z3]} &      \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{vamp} Vampire [Z3]} &    \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4 [Z3]} \\
+AUFNIRA    &            \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4} &         \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{vamp} Vampire} &           \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{vamp} Vampire} &         \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4} \\
+BV         &       \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 [Z3]} &              \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{q3b} Q3B} &           \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{q3b} Q3B [Z3]} &         \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4} \\
+BVFP       &                          \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                          \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                            \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &         \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4} \\
+FP         &                          \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                          \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                            \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &         \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4} \\
+LIA        &            \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4} &            \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4} &         \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4 [Z3]} &    \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4 [Z3]} \\
+LRA        &            \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4} &            \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4} &         \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4 [Z3]} &    \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4 [Z3]} \\
+NIA        &       \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 [Z3]} &       \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{prob} ProB [Z3]} &         \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4 [Z3]} &    \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4 [Z3]} \\
+NRA        &            \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4} &         \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{vamp} Vampire} &            \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{redl} Redlog} &                                   \cc{vamp} Vampire [Z3] & \cc{vamp} Vampire \\
+QF\_ABV     &       \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{bool} Boolector} &       \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{bool} Boolector} &         \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{bool} Boolector} &    \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{bool} Boolector} \\
+QF\_ABVFP   &                          \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                          \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                            \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{---} &         \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4} \\
+QF\_ALIA    &          \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices} &          \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices} &            \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices} &       \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices} \\
+QF\_ANIA    &       \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 [Z3]} &            \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4} &              \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4} &    \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 [Z3]} \\
+QF\_AUFBV   &  \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4 [MathSAT]} &  \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4 [MathSAT]} &  \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices [MathSAT]} &         \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4} \\
+QF\_AUFLIA  &          \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices} &          \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices} &            \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices} &       \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices} \\
+QF\_AUFNIA  &            \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4} &            \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4} &         \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 [Z3]} &    \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 [Z3]} \\
+QF\_AX      &          \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices} &          \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices} &            \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices} &       \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices} \\
+QF\_BV      &       \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{bool} Boolector} &       \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{bool} Boolector} &                                        \cc{bool} Boolector & \cc{mink} Minkeyrink &                                   \cc{bool} Boolector & \cc{mink} Minkeyrink \\
+QF\_BVFP    &                 \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{z} Z3} &          \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc [Z3]} &      \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{coli} COLIBRI [Z3]} &         \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4} \\
+QF\_DT      &                          \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                          \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &              \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4} &         \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4} \\
+  QF\_FP      &                 \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{z} Z3} &                 \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc [MathSAT]} &      \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{coli} COLIBRI [Z3]} &      \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{coli} COLIBRI} \\
+QF\_IDL     &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices [Z3]} &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices [Z3]} &            \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices} &       \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices} \\
+QF\_LIA     &  \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4 [MathSAT]} &  \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4 [MathSAT]} &    \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4 [MathSAT]} &  \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{spass} SPASS-SATT} \\
+QF\_LIRA    &          \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices} &          \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices} &       \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices [Z3]} &  \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices [Z3]} \\
+QF\_LRA     &            \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4} &            \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4} &              \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4} &         \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4} \\
+QF\_NIA     &      \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{apr} AProVE [Z3]} &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices [Z3]} &              \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4} &         \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4} \\
+QF\_NIRA    &            \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4} &            \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4} &            \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{rat} SMT-RAT} &       \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{rat} SMT-RAT} \\
+QF\_NRA     &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices [Z3]} &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices [Z3]} &            \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices} &  \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices [Z3]} \\
+QF\_RDL     &          \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices} &          \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices} &            \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices} &       \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices} \\
+QF\_SLIA    &                          \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                          \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                            \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &         \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4} \\
+QF\_UF      &          \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices} &          \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices} &            \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices} &       \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices} \\
+QF\_UFBV    &       \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{bool} Boolector} &       \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{bool} Boolector} &         \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{bool} Boolector} &    \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{bool} Boolector} \\
+QF\_UFIDL   &          \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices} &          \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices} &            \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices} &       \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices} \\
+QF\_UFLIA   &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices [Z3]} &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices [Z3]} &            \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices} &       \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices} \\
+QF\_UFLRA   &          \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices} &          \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices} &            \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices} &       \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices} \\
+QF\_UFNIA   &            \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4} &                                               \cc{yices} Yices & \cc{cvc4} CVC4 &            \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices} &       \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices} \\
+QF\_UFNRA   &       \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc3} CVC3 [Z3]} &          \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices} &       \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices [Z3]} &       \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices} \\
+UF         &            \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4} &            \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4} &           \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{vamp} Vampire} &                                           \cc{cvc4} CVC4 & \cc{vamp} Vampire \\
+UFBV       &       \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 [Z3]} &       \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4 [Z3]} &         \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 [Z3]} &    \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 [Z3]} \\
+UFDT       &                          \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                          \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &              \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4} &         \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4} \\
+UFDTLIA    &                          \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                          \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &           \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{vamp} Vampire} &         \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4} \\
+UFIDL      &       \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4 [Z3]} &            \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4} &              \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4} &    \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4 [Z3]} \\
+UFLIA      &            \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4} &            \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4} &              \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4} &         \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4} \\
+UFLRA      &            \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc3} CVC3} &    \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{vamp} Vampire [Z3]} &         \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4 [Z3]} &    \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4 [Z3]} \\
+UFNIA      &            \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4} &         \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{vamp} Vampire} &           \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{vamp} Vampire} &                                   \cc{vamp} Vampire [Z3] & \cc{vamp} Vampire \\
+\bottomrule
+\end{tabular}
+}
+
+\end{table}

### 2019-08-29 2018/report/table-winners-main-sat-unsat.tex
Report: Fix results and layout for sat/unsat score table.

@@
 \begin{table}
+  \caption{Alternative best solvers in the \maintrack if only \emph{satisfiable} benchmarks had been considered. These results are in reference to those given in Table~\ref{tab:winners-main}. NEW}
+  \label{tab:results:sat}
+  \centering
+  \scalebox{.82}{%
+    \renewcommand{\arraystretch}{1.01}%
+\begin{tabular}{r>{\columncolor{white}[.25em][.8em]}r@{\hskip .8em}|@{\hskip .5em}>{\columncolor{white}[.5em][.5em]}l>{\columncolor{white}[.5em][.8em]}r@{\hskip .8em}|@{\hskip .5em}>{\columncolor{white}[.5em][.5em]}l>{\columncolor{white}[.5em][.8em]}r@{\hskip .8em}|@{\hskip .5em}>{\columncolor{white}[.5em][0.5em]}l>{\columncolor{white}[.5em][.8em]}r@{\hskip .8em}|@{\hskip .5em}>{\columncolor{white}[.5em][0.5em]}l}
+\toprule
+Division &                 \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{2015} &                      \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{2016} &                      \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{2017} &                   \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{2018} \\
+\midrule
+ALIA      &                     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                          \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                          \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                   \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{[Z3]} \\
+AUFLIRA   &                     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                      \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{[Z3]} &                      \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{[Z3]} &                   \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{[Z3]} \\
+AUFNIRA   &  \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 [Z3]} &       \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4 [Z3]} &       \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4 [Z3]} &    \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4 [Z3]} \\
+BV        &                     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &         \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{q3b} Q3B [Z3]} &  \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{bool} Boolector [Z3]} &    \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{bool} Boolector} \\
+NIA       &           \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc [Z3]} &                          \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                          \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                       \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} \\
+NRA       &                     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                          \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                          \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                   \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{[Z3]} \\
+QF\_ABV    &                     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &          \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices} &          \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices} &                       \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} \\
+QF\_AUFBV  &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices} &          \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices} &          \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices} &       \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices} \\
+QF\_AUFNIA &                     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                          \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &            \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4} &         \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4} \\
+QF\_BV     &                     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                                 \cc{bool} Boolector [Z3] & \cc{mink} Minkeyrink &                                                         \cc{mink} Minkeyrink &  &                       \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} \\
+QF\_FP     &                     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                          \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                          \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &         \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4} \\
+QF\_IDL    &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices} &          \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices} &                          \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                       \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} \\
+QF\_LIRA   &                     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                          \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &          \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices} &       \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices} \\
+QF\_LRA    &                     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                          \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                          \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &       \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices} \\
+QF\_NIA    &      \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{apr} AProVE} &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{rat} SMT-RAT [Z3]} &                          \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                       \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} \\
+QF\_NRA    &                     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                          \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices [Z3]} &                       \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} \\
+QF\_UFBV   &                     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                          \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                          \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &       \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices} \\
+QF\_UFIDL  &                    \hspace*{3em}                   & \cc{yices} Yices [Z3] &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices [Z3]} &                                                         & \cc{yices} Yices [Z3] &  \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{verit} veriT [Z3]} \\
+QF\_UFLIA  &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices} &          \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices} &                          \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                       \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} \\
+UF        &                     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &         \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{vamp} Vampire} &                          \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                                                         \cc{vamp} Vampire & \hspace*{3em} \\
+UFBV      &                     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &  \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{bool} Boolector [Z3]} &                          \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                       \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} \\
+UFLIA     &  \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4 [Z3]} &                          \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                          \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                       \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} \\
+UFLRA     &                     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                      \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{[Z3]} &                          \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                       \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} \\
+UFNIA     &                     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                          \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &            \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4} &         \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4} \\
+\bottomrule
+\end{tabular}
+  }
+\end{table}
+
+\begin{table}
   \caption{Alternative best solvers in the \maintrack if only \emph{unsatisfiable} benchmarks had been considered. These results are in reference to those given in Table~\ref{tab:winners-main}.}
@@
 \end{table}
+
+\begin{table}
+  \caption{Alternative best solvers in the \maintrack if only \emph{unsatisfiable} benchmarks had been considered. These results are in reference to those given in Table~\ref{tab:winners-main}. NEW}
+  \label{tab:results:unsat}
+  \centering
+  \scalebox{.82}{%
+    \renewcommand{\arraystretch}{1.01}%
+\begin{tabular}{r>{\columncolor{white}[.25em][.5em]}c|>{\columncolor{white}[.5em][.5em]}c>{\columncolor{white}[.5em][.5em]}c|>{\columncolor{white}[.5em][.5em]}c>{\columncolor{white}[.5em][.5em]}c|>{\columncolor{white}[.5em][.5em]}c>{\columncolor{white}[.5em][.5em]}c|>{\columncolor{white}[.5em][0.5em]}c}
+\toprule
+Division &                   \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{2015} &                    \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{2016} &                      \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{2017} &                    \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{2018} \\
+\midrule
+AUFLIRA   &                       \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                        \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &         \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{vamp} Vampire} &                        \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} \\
+BV        &                       \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &          \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4} &              \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{q3b} Q3B} &                        \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} \\
+LIA       &                       \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                        \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &            \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4} &          \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4} \\
+NIA       &         \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4} &          \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4} &         \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{vamp} Vampire} &  \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{vamp} Vampire [Z3]} \\
+QF\_AUFBV  &                       \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                        \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &  \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4 [MathSAT]} &                        \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} \\
+QF\_AUFNIA &    \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 [Z3]} &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 [Z3]} &                          \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                        \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} \\
+QF\_BV     &                       \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                        \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                  \hspace*{3em}                            & \cc{bool} Boolector &                        \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} \\
+QF\_FP     &                       \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                        \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &         \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{coli} COLIBRI} &                        \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} \\
+QF\_IDL    &    \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4 [Z3]} &                        \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &       \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4 [Z3]} &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4 [Z3]} \\
+QF\_LIA    &  \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{smti} SMTInterpol} &   \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{smti} SMTInterpol} &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{smti} SMTInterpol} &   \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{smti} SMTInterpol} \\
+QF\_NIA    &    \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc3} CVC3 [Z3]} &                        \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &          \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices} &                        \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} \\
+QF\_NRA    &                       \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &        \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices} &                          \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &          \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4} \\
+QF\_UFLIA  &                       \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                        \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices [Z3]} &                        \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} \\
+QF\_UFNRA  &                       \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4 [Z3]} &                                                           & \cc{cvc4} CVC4 [Z3] &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4 [Z3]} \\
+UF        &                       \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                        \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &            \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4} &                          \hspace*{3em}                       & \cc{cvc4} CVC4 \\
+UFBV      &                       \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &          \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4} &                          \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                        \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} \\
+UFIDL     &                       \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &  \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{vamp} Vampire [Z3]} &       \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4 [Z3]} &                        \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} \\
+UFLRA     &       \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{verit} veriT} &        \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{verit} veriT} &          \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{verit} veriT} &        \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{verit} veriT} \\
+\bottomrule
+\end{tabular}
+
+  }
+\end{table}

### 2019-08-29 2018/report/table-winners-main-24s.tex
Report: Introduce macros for track names.
Report: Fix results and layout for 24s score table.

@@
 \begin{table}
-  \caption{Alternative best solvers in the Main track if the time limit had been 24 seconds.}
+  \caption{Alternative best solvers in the \maintrack if the time limit had been 24 seconds.}
   \label{tab:results:24s}
@@
 \end{table}
+
+\begin{table}
+  \caption{Alternative best solvers in the \maintrack if the time limit had been 24 seconds. NEW}
+  \label{tab:results:24s}
+  \centering
+  \scalebox{.82}{%
+    \renewcommand{\arraystretch}{1.01}%
+\begin{tabular}{r>{\columncolor{white}[.25em][.8em]}r@{\hskip .8em}|@{\hskip .5em}>{\columncolor{white}[.5em][.5em]}l>{\columncolor{white}[.5em][.8em]}r@{\hskip .8em}|@{\hskip .5em}>{\columncolor{white}[.5em][.5em]}l>{\columncolor{white}[.5em][.8em]}r@{\hskip .8em}|@{\hskip .5em}>{\columncolor{white}[.5em][0.5em]}l>{\columncolor{white}[.5em][.8em]}r@{\hskip .8em}|@{\hskip .5em}>{\columncolor{white}[.5em][0.5em]}l}
+\toprule
+Division &                 \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{2015} &                        \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{2016} &                        \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{2017} &                   \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{2018} \\
+\midrule
+AUFLIA   &                     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &      \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{vamp} Vampire [Z3]} &            \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{verit} veriT} &                       \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} \\
+AUFLIRA  &  \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc3} CVC3 [Z3]} &                            \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                            \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                                                     & \cc{alt} Alt-Ergo [Z3] \\
+AUFNIRA  &  \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc3} CVC3 [Z3]} &                            \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                            \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &    \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4 [Z3]} \\
+BV       &                     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                            \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                            \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                               \cc{cvc4} CVC4 [Z3] & \cc{bool} Boolector [Z3] \\
+NRA      &                     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                            \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                            \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &    \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4 [Z3]} \\
+QF\_ABV   &                     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &            \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices} &                            \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                       \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} \\
+QF\_ANIA  &                     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &         \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \nonc \cc{cvc4} CVC4 [Z3]} &         \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 [Z3]} &                       \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} \\
+QF\_BV    &              \hspace*{3em}                                & \cc{cvc4} CVC4 &           \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{stp} STP [Z3]} &                            \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                                                        & \cc{bool} Boolector \\
+QF\_IDL   &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices} &            \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices} &                            \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                       \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} \\
+QF\_LIA   &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices} &  \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices [MathSAT]} &  \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices [MathSAT]} &                       \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} \\
+QF\_LIRA  &                     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                            \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &            \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices} &       \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices} \\
+QF\_LRA   &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices} &            \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices} &            \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices} &       \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices} \\
+QF\_NIA   &                     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                            \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &            \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices} &       \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices} \\
+QF\_NIRA  &                     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                            \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &       \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices [Z3]} &  \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices [Z3]} \\
+QF\_NRA   &                     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                            \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &       \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices [Z3]} &                       \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} \\
+QF\_UF    &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{verit} veriT} &            \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{verit} veriT} &                            \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                       \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} \\
+QF\_UFLIA &                                                         & \cc{yices} Yices &            \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices} &                            \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                       \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} \\
+QF\_UFNRA &  \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 [Z3]} &         \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4 [Z3]} &         \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4 [Z3]} &  \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices [Z3]} \\
+UF       &                     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &           \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{vamp} Vampire} &                            \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                                                         \cc{vamp} Vampire &  \\
+UFBV     &                     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &    \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{bool} Boolector [Z3]} &                            \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                       \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} \\
+UFIDL    &                     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &         \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4 [Z3]} &         \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4 [Z3]} &                       \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} \\
+UFLIA    &                     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                            \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                            \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &    \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4 [Z3]} \\
+UFLRA    &                     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &           \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{vamp} Vampire} &       \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{verit} veriT [Z3]} &       \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{verit} veriT} \\
+UFNIA    &  \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 [Z3]} &                            \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                            \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                                 \cc{cvc4} CVC4 [Z3] & \cc{vamp} Vampire [Z3] \\
+\bottomrule
+\end{tabular}
+  }
+\end{table}

### 2019-08-30 2018/report/table-winners-main-families.tex
Report: Introduce macros for track names.
Remove period
Report: Fix results and layout for families table.

@@
 \begin{table}
-  \caption{Alternative best solvers in the Main track if families were not considered in computing scores (i.e., the 2015 scoring system were used).}
+  \caption{Alternative best solvers in the \maintrack if families were not considered in computing scores (i.e., the 2015 scoring system were used)}
   \label{tab:results:total:solved}
@@
 \end{table}
+
+\begin{table}
+  \caption{Alternative best solvers in the \maintrack if families were not considered in computing scores (i.e., the 2015 scoring system were used). NEW}
+  \label{tab:results:total:solved}
+  \centering
+  {%
+    \renewcommand{\arraystretch}{1.01}%
+
+\begin{tabular}{r>{\columncolor{white}[.25em][.8em]}r@{\hskip .8em}|@{\hskip .5em}>{\columncolor{white}[.5em][.5em]}l>{\columncolor{white}[.5em][.8em]}r@{\hskip .8em}|@{\hskip .5em}>{\columncolor{white}[.5em][.5em]}l>{\columncolor{white}[.5em][.8em]}r@{\hskip .8em}|@{\hskip .5em}>{\columncolor{white}[.5em][0.5em]}l>{\columncolor{white}[.5em][.8em]}r@{\hskip .8em}|@{\hskip .5em}>{\columncolor{white}[.5em][0.5em]}l}
+\toprule
+Division & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{2015}              &                 \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{2016} &                      \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{2017} &                   \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{2018} \\
+\midrule
+AUFNIRA  &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\hspace*{5em}} &       \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4} &                          \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                       \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} \\
+BV       &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{}              &                     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &  \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{bool} Boolector [Z3]} &                       \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} \\
+QF\_BV    &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{}             &                     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                                     \cc{mink} Minkeyrink &  \hspace*{3em}       &                           \hspace*{3em}                & \cc{bool} Boolector \\
+QF\_FP    &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{}             &                     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                          \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &         \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4} \\
+QF\_IDL   &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{}             &                     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices [Z3]} &                       \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} \\
+QF\_LRA   &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{}             &                     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                          \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &  \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{spass} SPASS-SATT} \\
+QF\_NIA   &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{}             &                     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &          \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices} &       \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices} \\
+QF\_NRA   &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{}             &                     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                          \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &       \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices} \\
+UFIDL    &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{}              &  \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4 [Z3]} &                          \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                       \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} \\
+\bottomrule
+\end{tabular}
+  }
+\end{table}

### 2019-08-30 2018/report/table-winners-main-unknown.tex
Report: Introduce macros for track names.
Report: Fix results and layout for no-unknowns table.

@@
 \begin{table}
-  \caption{Alternative best solvers if benchmarks with unknown status had not bee included in 2017 onwards.}
+  \caption{Alternative best solvers in the \maintrack if benchmarks with unknown status had not bee included in 2017 onwards.}
   \label{tab:results:unknowns}
@@
 \end{table}
+
+\begin{table}
+  \caption{Alternative best solvers in the \maintrack if benchmarks with unknown status had not bee included in 2017 onwards. NEW}
+  \label{tab:results:unknowns}
+  \centering
+  {%
+    \renewcommand{\arraystretch}{1.01}%
+\begin{tabular}{r>{\columncolor{white}[.25em][.8em]}r@{\hskip .8em}|@{\hskip .5em}>{\columncolor{white}[.5em][.5em]}l>{\columncolor{white}[.5em][.8em]}r@{\hskip .8em}|@{\hskip .5em}>{\columncolor{white}[.5em][.5em]}l>{\columncolor{white}[.5em][.8em]}r@{\hskip .8em}|@{\hskip .5em}>{\columncolor{white}[.5em][0.5em]}l>{\columncolor{white}[.5em][.8em]}r@{\hskip .8em}|@{\hskip .5em}>{\columncolor{white}[.5em][0.5em]}l}
+\toprule
+Division & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{2015} & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{2016} &                   \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{2017} &                 \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{2018} \\
+\midrule
+AUFLIRA  &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                                 \cc{cvc4} CVC4 [Z3] &  \hspace*{3em}         &                     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} \\
+AUFNIRA  &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &         \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4} &                     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} \\
+BV       &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &           \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{q3b} Q3B} &  \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{bool} Boolector} \\
+LRA      &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &         \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4} &                     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} \\
+NRA      &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                       \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                                                   & \cc{vamp} Vampire [Z3] \\
+QF\_FP    &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                       \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &       \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4} \\
+QF\_NRA   &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &  \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices [Z3]} &                     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} \\
+UF       &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                                                            \cc{cvc4} CVC4 &  &                                                           & \cc{cvc4} CVC4 \\
+UFNIA    &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                       \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                                                     \cc{cvc4} CVC4 [Z3] &  \\
+\bottomrule
+\end{tabular}
+  }
+\end{table}

### 2019-08-30 2018/report/table-winners-main-24s.tex
Report: Tweak winners table layout.

@@
   \centering
-
-  \begin{tabular}{r@{\hskip 1em}>{\columncolor{white}[.25em][.5em]}c@{\hskip 1em}>{\columncolor{white}[.5em][.5em]}c@{\hskip 1em}>{\columncolor{white}[.5em][.5em]}c@{\hskip 1em}>{\columncolor{white}[.5em][0.5em]}c}
-    \toprule
-    Division   &  2015             &  2016                      &  2017                     &  2018                                  \\
-    \hline \hline
-    AUFLIA     &                   & \cc{vamp} Vampire \nc{Z3}  & \cc{verit} veriT          &                                        \\
-    AUFLIRA    & \cc{cvc3} CVC3    &                            &                           & -/Alt-Ergo                             \\
-    AUFNIRA    & \nonc \nc{Z3}     &                            &                           & \nc{Z3}                                \\
-    BV         &                   &                            &                           & \cc{bool} Boolector/Boolector \nc{Z3}  \\
-    NRA        &                   &                            &                           & \cc{cvc4} CVC4/CVC4 \nc{Z3}            \\
-    QF\_ABV    &                   & \cc{yices} Yices2          &                           &                                        \\
-    QF\_ANIA   &                   & \nonc \nc{Z3}              & \nonc \nc{Z3}             &                                        \\
-    QF\_BV     & \cc{cvc4} CVC4    & \cc{stp} STP \nc{Z3}       &                           & -/Boolector                            \\
-    QF\_LIA    & \cc{yices} Yices2 & \cc{yices} Yices2          & \cc{yices} Yices2         &                                        \\
-    QF\_LRA    & \cc{yices} Yices2 & \cc{yices} Yices2          & \cc{yices} Yices2         & \cc{yices} Yices2                      \\
-    QF\_NIA    &                   &                            & \cc{yices} Yices2         & \cc{yices} Yices2                      \\
-    QF\_NIRA   &                   &                            & \cc{yices} Yices2 \nc{Z3} & \cc{yices} Yices2 \nc{Z3}              \\
-    QF\_NRA    &                   &                            & \nc{Z3}                   &                                        \\
-    QF\_UF     & \cc{verit} veriT  & \cc{verit} veriT           &                           &                                        \\
-    QF\_UFNRA  &                   & \cc{cvc4} CVC4 \nc{Z3}     & \cc{cvc4} CVC4            & \nc{Z3}                                \\
-    UF         &                   & \cc{vamp} Vampire          &                           &  \cc{vamp} Vampire/-                   \\
-    UFBV       &                   & \cc{bool} Boolector        &                           &                                        \\
-    UFIDL      &                   & \cc{vamp} Vampire \nc{Z3}  & \nc{Z3}                   &                                        \\
-    UFLIA      &                   &                            &                           & \nc{Z3}                                \\
-    UFLRA      &                   &                            & \cc{verit} veriT          & \cc{verit} veriT                       \\
-    UFNIA      & \nonc \nc{Z3}     &                            &                           & \cc{cvc4} CVC4/\nc{Z3}                 \\
-    \bottomrule
-  \end{tabular}
-\end{table}
-
-\begin{table}
-  \caption{Alternative best solvers in the \maintrack if the time limit had been 24 seconds. NEW}
-  \label{tab:results:24s}
-  \centering
-  \scalebox{.82}{%
+  \scalebox{.755}{%
     \renewcommand{\arraystretch}{1.01}%

### 2019-08-30 2018/report/table-winners-main-families.tex
Report: Tweak winners table layout.

@@
 \begin{table}
-  \caption{Alternative best solvers in the \maintrack if families were not considered in computing scores (i.e., the 2015 scoring system were used)}
+  \caption{Alternative best solvers in the \maintrack if families were not considered in computing scores (i.e., the 2015 scoring system were used).}
   \label{tab:results:total:solved}
   \centering
-  \begin{tabular}{r@{\hskip 1em}>{\columncolor{white}[.25em][.5em]}c@{\hskip 1em}>{\columncolor{white}[.5em][.5em]}c@{\hskip 1em}>{\columncolor{white}[.5em][.5em]}c@{\hskip 1em}>{\columncolor{white}[.5em][0.5em]}c}
-    \toprule
-    Division & 2015 &  2016           &  2017                &  2018                  \\
-    \hline\hline
-    AUFNIRA  &      & \cc{cvc4} CVC4  &                      &                        \\
-    UFIDL    &      & \nc{Z3}         &                      &                        \\
-    BV       &      &                 & \cc{bool} Boolector  &                        \\
-    QF\_LRA  &      &                 & \cc{yices} Yices2    & \cc{spass} SPASS-SATT  \\
-    QF\_NIA  &      &                 & \cc{yices} Yices2    & \cc{yices} Yices2      \\
-    QF\_BV   &      &                 &                      & -/Boolector            \\
-    QF\_FP   &      &                 &                      & \cc{cvc4} CVC4         \\
-  \bottomrule
-  \end{tabular}
-\end{table}
-
-\begin{table}
-  \caption{Alternative best solvers in the \maintrack if families were not considered in computing scores (i.e., the 2015 scoring system were used). NEW}
-  \label{tab:results:total:solved}
-  \centering
-  {%
+  \scalebox{.755}{%
     \renewcommand{\arraystretch}{1.01}%

### 2019-08-30 2018/report/table-winners-main-sat-unsat.tex
Report: Tweak winners table layout.

@@
   \centering
-  \begin{tabular}{r@{\hskip 1em}>{\columncolor{white}[.25em][.5em]}c@{\hskip 1em}>{\columncolor{white}[.5em][.5em]}c@{\hskip 1em}>{\columncolor{white}[.5em][.5em]}c@{\hskip 1em}>{\columncolor{white}[.5em][0.5em]}c}
-    \toprule
-    Division         &  2015                &  2016                   &  2017                   &  2018                     \\
-    \hline \hline
-    ALIA             &                      &                         &                         & \cc{alt} Alt-Ergo         \\
-    AUFLIA           & \cc{cvc3} CVC3       &                         &                         & \cc{alt} Alt-Ergo         \\
-    AUFLIRA          &                      & \cc{cvc4} CVC4          & \cc{cvc4} CVC4          & \cc{alt} Alt-Ergo         \\
-    AUFNIRA          & \nonc\nc{Z3}         & \cc{cvc4} CVC4 \nc{Z3}  & \cc{cvc4} CVC4 \nc{Z3}  & \nc{Z3}                   \\
-    BV               &                      & \nc{Z3}                 & \cc{bool} Boolector     & \cc{bool} Boolector       \\
-    LRA              &                      &                         & \cc{verit} veriT        &                           \\
-    NIA              & \nonc \cc{cvc3} CVC3 &                         &                         &                           \\
-    NRA              & \nonc \cc{cvc3} CVC3 & \cc{cvc4} CVC4          & \cc{cvc4} CVC4          & \cc{cvc4} CVC4 \nc{Z3}    \\
-    QF\_ABV          &                      & \cc{yices} Yices2       & \cc{yices} Yices2       &                           \\
-    QF\_AUFBV        & \cc{yices} Yices     & \cc{yices} Yices2       &                         & \cc{yices} Yices2         \\
-    QF\_BV           &                      & \nc{Z3}/MinkeyRink      &                         &                           \\
-    QF\_FP           &                      &                         &                         & \cc{cvc4} CVC4            \\
-    QF\_LIA          & \nc{Z3}              &                         &                         &                           \\
-    QF\_LRA          &                      &                         & \cc{yices} Yices2       & \cc{yices} Yices2         \\
-    QF\_NIA          &                      & \cc{rat} SMT-RAT        &                         &                           \\
-    QF\_NIRA         &                      &                         & \cc{cvc4} CVC4          &                           \\
-    QF\_NRA          &                      &                         & \nc{Z3}                 &                           \\
-    QF\_UFBV         &                      &                         &                         & \cc{yices} Yices2         \\
-    QF\_UFIDL        & \nc{Z3}              & \nc{Z3}                 & \nc{Z3}                 & \cc{verit} veriT  \nc{Z3} \\
-    QF\_UFNIA        & \nonc \cc{cvc3} CVC3 &                         & \cc{cvc4} CVC4          &                           \\
-    UF               &                      & \cc{vamp} Vampire       &                         & \cc{vamp}Vampire/-        \\
-    UFBV             &                      & \cc{bool} Boolector     &                         &                           \\
-    UFDTLIA          &                      &                         & \nonc \cc{cvc4} CVC4    &                           \\
-    UFLIA            & \nc{Z3}              &                         &                         &                           \\
-    UFLRA            &                      & \cc{cvc4} CVC4          &                         &                           \\
-    UFNIA            &                      & \cc{cvc4} CVC4          & \cc{cvc4} CVC4          & \cc{cvc4} CVC4            \\
-    \bottomrule
-  \end{tabular}
-\end{table}
-
-\begin{table}
-  \caption{Alternative best solvers in the \maintrack if only \emph{satisfiable} benchmarks had been considered. These results are in reference to those given in Table~\ref{tab:winners-main}. NEW}
-  \label{tab:results:sat}
-  \centering
-  \scalebox{.82}{%
+  \scalebox{.747}{%
     \renewcommand{\arraystretch}{1.01}%
@@
   \centering
-  \begin{tabular}{r@{\hskip 1em}>{\columncolor{white}[.25em][.5em]}c@{\hskip 1em}>{\columncolor{white}[.5em][.5em]}c@{\hskip 1em}>{\columncolor{white}[.5em][.5em]}c@{\hskip 1em}>{\columncolor{white}[.5em][0.5em]}c}
-\toprule
-Division        &  2015                  &  2016                     &  2017                 &  2018                   \\
-\hline \hline
-    BV          &                        & \cc{cvc4} CVC4            &                       &                         \\
-    NIA         &                        & \cc{cvc4} CVC4            & \cc{vamp} Vampire     & \cc{vamp} Vampire       \\
-    QF\_AUFBV   &                        &                           & \cc{cvc4} CVC4        &                         \\
-    QF\_AUFNIA  & \nonc \nc{Z3}          & \nonc \nc{Z3}             &                       &                         \\
-    QF\_BV      &                        &                           & -/Boolector           &                         \\
-    QF\_IDL     & \cc{cvc4} CVC4         &                           & \nc{Z3}               & \cc{cvc4} CVC4 \nc{Z3}  \\
-    QF\_LIA     & \cc{smti} SMTInterpol  & \cc{smti} SMTInterpol     & \cc{smti} SMTInterpol & \cc{smti} SMTInterpol   \\
-    QF\_NIA     & \cc{cvc3} CVC3         &                           & \cc{yices} Yices2     &                         \\
-    QF\_NRA     &                        &                           &                       & \cc{cvc4} CVC4          \\
-    QF\_UFLIA   &                        &                           & \nc{Z3}               &                         \\
-    QF\_UFNRA   &                        & \cc{cvc4} CVC4 \nc{Z3}    & \cc{cvc4} CVC4        & \cc{cvc4} CVC4 \nc{Z3}  \\
-    UF          &                        &                           & \cc{cvc4} CVC4        & -/CVC4                  \\
-    UFIDL       &                        & \cc{vamp} Vampire \nc{Z3} & \nc{Z3}               &                         \\
-    UFLRA       &                        &                           & \cc{verit} veriT      & \cc{verit} veriT        \\
-    \bottomrule
-  \end{tabular}
-
-\end{table}
-
-\begin{table}
-  \caption{Alternative best solvers in the \maintrack if only \emph{unsatisfiable} benchmarks had been considered. These results are in reference to those given in Table~\ref{tab:winners-main}. NEW}
-  \label{tab:results:unsat}
-  \centering
-  \scalebox{.82}{%
+  \scalebox{.755}{%
     \renewcommand{\arraystretch}{1.01}%
-\begin{tabular}{r>{\columncolor{white}[.25em][.5em]}c|>{\columncolor{white}[.5em][.5em]}c>{\columncolor{white}[.5em][.5em]}c|>{\columncolor{white}[.5em][.5em]}c>{\columncolor{white}[.5em][.5em]}c|>{\columncolor{white}[.5em][.5em]}c>{\columncolor{white}[.5em][.5em]}c|>{\columncolor{white}[.5em][0.5em]}c}
+\begin{tabular}{r>{\columncolor{white}[.25em][.8em]}r@{\hskip .8em}|@{\hskip .5em}>{\columncolor{white}[.5em][.5em]}l>{\columncolor{white}[.5em][.8em]}r@{\hskip .8em}|@{\hskip .5em}>{\columncolor{white}[.5em][.5em]}l>{\columncolor{white}[.5em][.8em]}r@{\hskip .8em}|@{\hskip .5em}>{\columncolor{white}[.5em][0.5em]}l>{\columncolor{white}[.5em][.8em]}r@{\hskip .8em}|@{\hskip .5em}>{\columncolor{white}[.5em][0.5em]}l}
 \toprule

### 2019-08-30 2018/report/table-winners-main-unknown.tex
Report: Tweak winners table layout.

--- 2019-04-14 2018/report/table-winners-main-unknown.tex
@@
 \begin{table}
-  \caption{Alternative best solvers if benchmarks with unknown status had not bee included in 2017 onwards.}
+  \caption{Alternative best solvers in the \maintrack if benchmarks with unknown status had not bee included in 2017 onwards.}
   \label{tab:results:unknowns}
   \centering
-    \begin{tabular}{r@{\hskip 1em}>{\columncolor{white}[.25em][.5em]}c@{\hskip 1em}>{\columncolor{white}[.5em][.5em]}c@{\hskip 1em}>{\columncolor{white}[.5em][.5em]}c@{\hskip 1em}>{\columncolor{white}[.5em][0.5em]}c}
+  \scalebox{.755}{%
+    \renewcommand{\arraystretch}{1.01}%
+\begin{tabular}{r>{\columncolor{white}[.25em][.8em]}r@{\hskip .8em}|@{\hskip .5em}>{\columncolor{white}[.5em][.5em]}l>{\columncolor{white}[.5em][.8em]}r@{\hskip .8em}|@{\hskip .5em}>{\columncolor{white}[.5em][.5em]}l>{\columncolor{white}[.5em][.8em]}r@{\hskip .8em}|@{\hskip .5em}>{\columncolor{white}[.5em][0.5em]}l>{\columncolor{white}[.5em][.8em]}r@{\hskip .8em}|@{\hskip .5em}>{\columncolor{white}[.5em][0.5em]}l}
 \toprule
-    Division &  2017          &  2018                  \\
-    \hline\hline
-    AUFNIRA  & \cc{cvc4} CVC4 &                        \\
-    QF\_NIRA & \nc{Z3}        & \cc{cvc4} CVC4 \nc{Z3} \\
-    QF\_NRA  & \nc{Z3}        &                        \\
-    UFDTLIA  & \cc{cvc4} CVC4 &                        \\
-    BV       &                & \cc{bool} Boolector    \\
-    QF\_FP   &                & \cc{cvc4} CVC4 \nc{Z3} \\
-    UFNIA    &                & \cc{cvc4} CVC4         \\
-    NRA      &                & -/\nc{Z3}              \\
-    UF       &                & -/CVC4                 \\
+Division & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{2015} & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{2016} &                   \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{2017} &                 \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{2018} \\
+\midrule
+AUFLIRA  &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\hspace*{5em}} &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\hspace*{5em}} &                                 \cc{cvc4} CVC4 [Z3] &  \hspace*{3em}         &                     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} \\
+AUFNIRA  &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &         \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4} &                     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} \\
+BV       &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &           \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{q3b} Q3B} &  \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{bool} Boolector} \\
+LRA      &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &         \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4} &                     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} \\
+NRA      &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                       \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                                                   & \cc{vamp} Vampire [Z3] \\
+QF\_FP    &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                       \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &       \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4} \\
+QF\_NRA   &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &  \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices [Z3]} &                     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} \\
+UF       &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                                                            \cc{cvc4} CVC4 &  &                                                           & \cc{cvc4} CVC4 \\
+UFNIA    &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                       \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                                                     \cc{cvc4} CVC4 [Z3] &  \\
 \bottomrule
 \end{tabular}
+  }
 \end{table}

### 2019-08-30 2018/report/table-winners-main.tex
Report: Tweak winners table layout.

@@
 \begin{table}
-\caption{Best \maintrack solvers (by division)}
+\caption{Best \maintrack solvers (by division).}
 \label{tab:winners-main}
 \centering
-\scalebox{.82}{%
-\renewcommand{\arraystretch}{1.01}%
-  \begin{tabular}{r@{\hskip 1em}>{\columncolor{white}[.25em][.5em]}c@{\hskip 1em}>{\columncolor{white}[.5em][.5em]}c@{\hskip 1em}>{\columncolor{white}[.5em][.5em]}c@{\hskip 1em}>{\columncolor{white}[.5em][0.5em]}c}
-    \toprule
-    Division         &  2015                        &  2016                     &  2017                           &  2018                     \\
-    \midrule
-    \wc ABVFP        &                              &                           &                                 & \nonc \cc{cvc4} {CVC4}    \\
-    \rc{cvc4}
-    \wc ALIA         & CVC4 \nc{Z3}                 & CVC4 \nc{Z3}              & CVC4 \nc{Z3}                    & CVC4 \nc{Z3}              \\
-    \wc AUFBVDTLIA   &                              &                           & \nonc \cc{cvc4} {CVC4}          & \nonc \cc{cvc4} {CVC4}    \\
-    \wc AUFDTLIA     &                              &                           & \nonc \cc{cvc4} {CVC4}          & \cc{cvc4} {CVC4}          \\
-    \rc{cvc4}
-    \wc AUFLIA       & {CVC4}                       & {CVC4}                    & {CVC4}                          & {CVC4}                    \\
-    \rc{vamp}
-    \wc AUFLIRA      & \cc{cvc4} CVC4 \nc{Z3}       & Vampire \nc{Z3}           & Vampire \nc{Z3}                 & \cc{cvc4} CVC4 \nc{Z3}    \\
-    \rc{vamp}
-    \wc AUFNIRA      & \nonc \cc{cvc4} {CVC4}       & {Vampire}                 & {Vampire}                       & \cc{cvc4} {CVC4}          \\
-    \rc{q3b}
-    \wc BV           & \nonc \cc{cvc4} CVC4 \nc{Z3} & {Q3B}                     & Q3B \nc{Z3}                     & \cc{cvc4} {CVC4}          \\
-    \wc BVFP         &                              &                           &                                 & \nonc \cc{cvc4} {CVC4}    \\
-    \wc FP           &                              &                           &                                 & \nonc \cc{cvc4} {CVC4}    \\
-    \rc{cvc4}
-    \wc LIA          & {CVC4}                       & {CVC4}                    & CVC4 \nc{Z3}                    & CVC4 \nc{Z3}              \\
-    \rc{cvc4}
-    \wc LRA          & {CVC4}                       & {CVC4}                    & CVC4 \nc{Z3}                    & CVC4 \nc{Z3}              \\
-    \rc{cvc4}
-    \wc NIA          & \nonc CVC4 \nc{Z3}           & \cc{prob} ProB \nc{Z3}    & CVC4 \nc{Z3}                    & CVC4 \nc{Z3}              \\
-    \rc{vamp}
-    \wc NRA          & \nonc \cc{cvc4} {CVC4}       & {Vampire}                 & \cc{redl} {Redlog}              & Vampire \nc{Z3} / Vampire \\
-    \rc{bool}
-    \wc QF\_ABV      & {Boolector}                  & {Boolector}               & {Boolector}                     & {Boolector}               \\
-    \wc QF\_ABVFP    &                              &                           & {---}                           & \cc{cvc4} {CVC4}          \\
-    \rc{yices}
-    \wc QF\_ALIA     & {Yices2}                     & {Yices2}                  & {Yices2}                        & {Yices2}                  \\
-    \rc{cvc4}
-    \wc QF\_ANIA     & \nonc CVC4 \nc{Z3}           & \nonc {CVC4}                & \nonc {CVC4}                  & \nonc CVC4 \nc{Z3}        \\
-    \rc{cvc4}
-    \wc QF\_AUFBV    & CVC4 \nc{MathSAT}            & CVC4 \nc{MathSAT}         & \cc{yices} Yices2 \nc{MathSAT}  & {CVC4}                    \\
-    \rc{yices}
-    \wc QF\_AUFLIA   & {Yices2}                     & {Yices2}                  & {Yices2}                        & {Yices2}                  \\
-    \rc{cvc4}
-    \wc QF\_AUFNIA   & \nonc {CVC4}                 & \nonc {CVC4}              & \nonc CVC4 \nc{Z3}              & \nonc CVC4 \nc{Z3}        \\
-    \rc{yices}
-    \wc QF\_AX       & {Yices2}                     & {Yices2}                  & {Yices2}                        & {Yices2}                  \\
-    \rc{bool}
-    \wc QF\_BV       & {Boolector}                  & {Boolector}               & {Boolector/MinkeyRink}          & {Boolector/MinkeyRink}    \\
-    \wc QF\_BVFP     & \nonc \cc{z} {Z3}            & \nonc \wc \nc{Z3}         & \nonc \cc{coli} COLIBRI \nc{Z3} & \cc{cvc4} {CVC4}          \\
-    \wc QF\_DT       &                              &                           & \nonc \cc{cvc4} {CVC4}          & \nonc \cc{cvc4} {CVC4}    \\
-    \rc{coli}
-    \wc QF\_FP       & \nonc \cc{z} {Z3}            & \nonc \wc \nc{MathSAT}    & COLIBRI \nc{Z3}                 & {COLIBRI}                 \\
-    \rc{yices}
-    \wc QF\_IDL      & Yices2 \nc{Z3}               & Yices2 \nc{Z3}            & {Yices2}                        & {Yices2}                  \\
-    \rc{cvc4}
-    \wc QF\_LIA      & CVC4 \nc{MathSAT}            & CVC4 \nc{MathSAT}         & CVC4 \nc{MathSAT}               & \cc{spass} {SPASS-SATT}   \\
-    \rc{yices}
-    \wc QF\_LIRA     & {Yices2}                     & {Yices2}                  & Yices2 \nc{Z3}                  & Yices2 \nc{Z3}            \\
-    \rc{cvc4}
-    \wc QF\_LRA      &  {CVC4}                      & {CVC4}                    & {CVC4}                          & {CVC4}                    \\
-    \rc{cvc4}
-    \wc QF\_NIA      & \cc{apr} AProVE \nc{Z3}      & \cc{yices} Yices2 \nc{Z3} & {CVC4}                          & {CVC4}                    \\
-    \rc{cvc4}
-    \wc QF\_NIRA     & {CVC4}                       & {CVC4}                    & \cc{rat} {SMT-RAT}              & \cc{rat} {SMT-RAT}        \\
-    \rc{yices}
-    \wc QF\_NRA      & Yices2 \nc{Z3}               & Yices2 \nc{Z3}            & {Yices2}                        & Yices2 \nc{Z3}            \\
-    \rc{yices}
-    \wc QF\_RDL      & {Yices2}                     & {Yices2}                  & {Yices2}                        & {Yices2}                  \\
-    \wc QF\_SLIA     &                              &                           &                                 & \nonc \cc{cvc4} {CVC4}    \\
-    \rc{yices}
-    \wc QF\_UF       & {Yices2}                     & {Yices2}                  & {Yices2}                        & {Yices2}                  \\
-    \rc{bool}
-    \wc QF\_UFBV     & {Boolector}                  & {Boolector}               & {Boolector}                     & {Boolector}               \\
-    \rc{yices}
-    \wc QF\_UFIDL    & {Yices2}                     & {Yices2}                  & {Yices2}                        & {Yices2}                  \\
-    \rc{yices}
-    \wc QF\_UFLIA    & Yices2 \nc{Z3}               & Yices2 \nc{Z3}            & {Yices2}                        & {Yices2}                  \\
-    \rc{yices}
-    \wc QF\_UFLRA    & {Yices2}                     & {Yices2}                  & {Yices2}                        & {Yices2}                  \\
-    \rc{yices}
-    \wc QF\_UFNIA    & \nonc \cc{cvc4} {CVC4}       & {Yices2/CVC4}             & {Yices2}                        & {Yices2}                  \\
-    \rc{yices}
-    \wc QF\_UFNRA    & \nonc \cc{cvc3} CVC3 \nc{Z3} & {Yices2}                  & Yices2 \nc{Z3}                  & {Yices2}                  \\
-    \rc{cvc4}
-    \wc UF           & {CVC4}                       & {CVC4}                    & \cc{vamp} {Vampire}             &  {CVC4/Vampire}           \\
-    \rc{cvc4}
-    \wc UFBV         & \nonc CVC4 \nc{Z3}           & CVC4 \nc{Z3}              & \nonc CVC4 \nc{Z3}              & \nonc CVC4 \nc{Z3}        \\
-    \wc UFDT         &                              &                           & \nonc \cc{cvc4} {CVC4}          & \cc{cvc4} {CVC4}          \\
-    \wc UFDTLIA      &                              &                           & \nonc \cc{vamp} {Vampire}       & \cc{cvc4} {CVC4}          \\
-    \rc{cvc4}
-    \wc UFIDL        & CVC4 \nc{Z3}                 & {CVC4}                    & {CVC4}                          & CVC4 \nc{Z3}              \\
-    \rc{cvc4}
-    \wc UFLIA        & {CVC4}                       & {CVC4}                    & {CVC4}                          & {CVC4}                    \\
-    \rc{cvc4}
-    \wc UFLRA        & \cc{cvc3} {CVC3}             & \cc{vamp} Vampire \nc{Z3} & CVC4 \nc{Z3}                    & CVC4 \nc{Z3}              \\
-    \rc{vamp}
-    \wc UFNIA        & \nonc \cc{cvc4} {CVC4}       & {Vampire}                 & {Vampire}                       & Vampire \nc{Z3} / Vampire \\
-    \bottomrule
-  \end{tabular}}
-\end{table}
-
-\begin{table}
-\caption{Best \maintrack solvers (by division). NEW}
-\label{tab:winners-main}
-\centering
-\scalebox{.82}{%
+\scalebox{.755}{%
 \renewcommand{\arraystretch}{1.01}%

### 2019-08-30 tools/scoring/score.py
scoring script: Fix and refactor functionality for 2015-2018 report.

@@ -71,6 +71,7 @@ g_args = None
 
 g_competitive = {}
 g_solver_names = {}
+g_solver_variants = {}
 
 g_tracks = { OPT_TRACK_SQ: TRACK_SQ,
              OPT_TRACK_INC: TRACK_INC,
@@ -116,15 +117,15 @@ def get_family_top(benchmark):
 def get_family_bot(benchmark):
     return benchmark.rsplit('/', 1)[0]
 
-# adds columns for division and family to data
-# also does some tidying of benchmark column for specific years of the competition
-# edit this function if you want to edit how families are added
+# Add columns for division and family.
+# Also does some tidying of benchmark column for specific years of the
+# competition. Edit this function if you want to edit how families are added.
 def add_division_family_info(data, family_definition):
-
     # Select family extraction functions.
     # This depends on the family_definition option:
     #   - 'top' interprets the top-most directory, and
-    #   - 'bot' interprets the bottom-most directory as benchmark family.
+    #   - 'bot' interprets the bottom-most directory
+    # as benchmark family.
     # The rules have always specified 'top' but the scoring scripts for many
     # years actually implemented 'bot'. The scripts allow you to choose.
     fam_func = None
@@ -140,6 +141,29 @@ def add_division_family_info(data, family_definition):
     data['benchmark'] = split.str[0]
     data['division'] = split.str[1]
     data['family'] = split.str[2]
+
+#    print('##########################################################')
+#    print(data['family'].unique())
+#    print('***********************************')
+#
+#    if family_definition == "top":
+#        if g_args.log:
+#            log("Using top-level directories for fam")
+#            # Take top-level sub-directories as family
+#            data['family'] = numpy.where(
+#                                data['benchmark'].str.count('/') > 1,
+#                                data['benchmark'].str.split('/').str[1],
+#                                '-')
+#    elif family_definition == "bot":
+#        if g_args.log:
+#            log("Using bottom-level directories for fam")
+#            # Take immediate super-directory as family
+#            data['family'] = data.benchmark.apply(lambda x : x[(1+x.index('/')):(x.rfind('/'))])
+#    else:
+#        die ("family option not supported: {}".format(fam))
+#
+#    print(data['family'].unique())
+#    print('------------------------------------------------------')
 
     return data
 
@@ -169,7 +193,7 @@ def remove_disagreements(data):
[…]

### 2019-08-30 2018/report/table-winners-main-24s.tex
Minor

@@
     \renewcommand{\arraystretch}{1.01}%
-\begin{tabular}{r>{\columncolor{white}[.25em][.8em]}r@{\hskip .8em}|@{\hskip .5em}>{\columncolor{white}[.5em][.5em]}l>{\columncolor{white}[.5em][.8em]}r@{\hskip .8em}|@{\hskip .5em}>{\columncolor{white}[.5em][.5em]}l>{\columncolor{white}[.5em][.8em]}r@{\hskip .8em}|@{\hskip .5em}>{\columncolor{white}[.5em][0.5em]}l>{\columncolor{white}[.5em][.8em]}r@{\hskip .8em}|@{\hskip .5em}>{\columncolor{white}[.5em][0.5em]}l}
+\begin{tabular}{r>{\columncolor{white}[.25em][.8em]}r@{\hskip .8em}|@{\hskip .5em}>{\columncolor{white}[.5em][.5em]}l>{\columncolor{white}[.5em][.8em]}r@{\hskip .8em}|@{\hskip .5em}>{\columncolor{white}[.5em][.5em]}l>{\columncolor{white}[.5em][.8em]}r@{\hskip .8em}|@{\hskip .5em}>{\columncolor{white}[.5em][.5em]}l>{\columncolor{white}[.5em][.8em]}r@{\hskip .8em}|@{\hskip .5em}>{\columncolor{white}[.5em][.5em]}l}
 \toprule

### 2019-08-30 2018/report/table-winners-main-families.tex
Minor

@@
 
-\begin{tabular}{r>{\columncolor{white}[.25em][.8em]}r@{\hskip .8em}|@{\hskip .5em}>{\columncolor{white}[.5em][.5em]}l>{\columncolor{white}[.5em][.8em]}r@{\hskip .8em}|@{\hskip .5em}>{\columncolor{white}[.5em][.5em]}l>{\columncolor{white}[.5em][.8em]}r@{\hskip .8em}|@{\hskip .5em}>{\columncolor{white}[.5em][0.5em]}l>{\columncolor{white}[.5em][.8em]}r@{\hskip .8em}|@{\hskip .5em}>{\columncolor{white}[.5em][0.5em]}l}
+\begin{tabular}{r>{\columncolor{white}[.25em][.8em]}r@{\hskip .8em}|@{\hskip .5em}>{\columncolor{white}[.5em][.5em]}l>{\columncolor{white}[.5em][.8em]}r@{\hskip .8em}|@{\hskip .5em}>{\columncolor{white}[.5em][.5em]}l>{\columncolor{white}[.5em][.8em]}r@{\hskip .8em}|@{\hskip .5em}>{\columncolor{white}[.5em][.5em]}l>{\columncolor{white}[.5em][.8em]}r@{\hskip .8em}|@{\hskip .5em}>{\columncolor{white}[.5em][.5em]}l}
 \toprule

### 2019-08-30 2018/report/table-winners-unsat-core.tex
Report: Tweak winners table layout.
Minor

@@
   \centering
-  \scalebox{.88}{%
+  \scalebox{.755}{%
     \renewcommand{\arraystretch}{1.01}%
-    \begin{tabular}{r>{\columncolor{white}[.25em][.8em]}r@{\hskip .8em}|@{\hskip .5em}>{\columncolor{white}[.5em][.5em]}l>{\columncolor{white}[.5em][.8em]}r@{\hskip .8em}|@{\hskip .5em}>{\columncolor{white}[.5em][.5em]}l>{\columncolor{white}[.5em][.8em]}r@{\hskip .8em}|@{\hskip .5em}>{\columncolor{white}[.5em][0.5em]}l}
+    \begin{tabular}{r>{\columncolor{white}[.25em][.8em]}r@{\hskip .8em}|@{\hskip .5em}>{\columncolor{white}[.5em][.5em]}l>{\columncolor{white}[.5em][.8em]}r@{\hskip .8em}|@{\hskip .5em}>{\columncolor{white}[.5em][.5em]}l>{\columncolor{white}[.5em][.8em]}r@{\hskip .8em}|@{\hskip .5em}>{\columncolor{white}[.5em][.5em]}l}
       \toprule

### 2019-08-30 2018/report/SMT-COMP.tex
Report: Tweak winners table layout.
Report: Update text after table updates.

@@
 }
+
+%\usepackage{showframe}   % debug
 
@@
         plot/pdf/cactus_plot-Virtual_Best_Solver_(VBS)_Main_Track_2015-2018.pdf}}
-  \caption{VBS on common benchmarks 2015--2018 of all logics in the
+  \caption{VBS on common benchmarks 2015--2018 of all divisions in the
     \maintrack with a time limit of \SI{1200}{s}.  Number of common
@@
   \end{subfigure}
-  \caption{VBS on common benchmarks for pairs of years of all logics
-    in the \maintrack with a time limit of \SI{1200}{s}.  Number of
-    common benchmarks is indicated with a gray vertical line.}
+  \caption{VBS on common benchmarks for pairs of years of all \maintrack
+  divisions with a time limit of \SI{1200}{s}.  Number of common benchmarks is
+  indicated with a gray vertical line.}
   \label{fig:progress}
@@
       of \num{30370517} total) within a time limit of \SI{2400}{s} on
-      common benchmarks 2015--2018 of all logics in the \apptrack.}
+      common benchmarks 2015--2018 of all divisions in the \apptrack.}
     \label{fig:progress-all-app}
@@
       time limit of \SI{2400}{s} on common benchmarks 2016--2018 of
-      all logics in the \ucoretrack.\\${}$}
+      all divisions in the \ucoretrack.\\${}$}
     \label{fig:progress-all-uc}
@@
 changes in division winners if only satisfiable or unsatisfiable results are
-given. This table is in reference to Table~\ref{tab:winners-main} and only
-lists a solver if the result has changed. A non-competing solver is listed by
-itself if it was not the overall best performing solver of that division but
-now outperforms the winning competitive solver, and the winning competing
-solver did not change.
-It is interesting to note that we see some new solvers winning divisions that did not win any division in the main results.
-For example, Alt-Ergo solves the most satisfiable benchmarks in AUFLIA and ALIA in 2018, and SMTInterpol performs very well on unsatisfiable benchmarks in QF\_LIA.
+given. These tables only lists the result for a division if it has changed
+with respect to Table~\ref{tab:winners-main}. A non-competing solver is listed
+by itself if there was no competing solver with a positive division score under
+the given constraints.
+It is interesting to note that we see some new solvers winning divisions that
+did not win any division in the main results. For example, veriT solves the
+most satisfiable benchmarks in QF\_UFIDL in 2018 and the most unsatisfiable
+benchmarks in all four years in UFLRA, and SMTInterpol performs very well on
+unsatisfiable benchmarks in QF\_LIA.
 
@@
 at Amazon.} in the \maintrack.  As in the previous analysis, this highlights the
-different winners under this new scheme only. Here we see STP winning a
-division for the first time in our analysis (QF\_BV in 2016) and Yices2
-performing well.
+different winners under this new scheme only. Here we see Alt-Ergo (AUFLIRA in
+2018) and STP (QF\_BV in 2016) winning a division for the first time in our
+analysis, and Yices performing well.
 

### 2019-08-30 tools/scoring/score.py
scoring script: cleanup

@@ -141,30 +141,6 @@ def add_division_family_info(data, family_definition):
     data['benchmark'] = split.str[0]
     data['division'] = split.str[1]
     data['family'] = split.str[2]
-
-#    print('##########################################################')
-#    print(data['family'].unique())
-#    print('***********************************')
-#
-#    if family_definition == "top":
-#        if g_args.log:
-#            log("Using top-level directories for fam")
-#            # Take top-level sub-directories as family
-#            data['family'] = numpy.where(
-#                                data['benchmark'].str.count('/') > 1,
-#                                data['benchmark'].str.split('/').str[1],
-#                                '-')
-#    elif family_definition == "bot":
-#        if g_args.log:
-#            log("Using bottom-level directories for fam")
-#            # Take immediate super-directory as family
-#            data['family'] = data.benchmark.apply(lambda x : x[(1+x.index('/')):(x.rfind('/'))])
-#    else:
-#        die ("family option not supported: {}".format(fam))
-#
-#    print(data['family'].unique())
-#    print('------------------------------------------------------')
-
     return data
 
 # Drop any rows that contain benchmarks with status unknown where two otherwise
@@ -228,6 +204,12 @@ def get_solver_variant(solver_id):
         return '[{}]'.format(name)
     return name
 
+# Do not consider solver variants for determining if a division is
+# competitive.
+# Uses get_solver_name(solver) to get the base version of solver.
+def is_competitive_division(solvers):
+    return len(set([get_solver_name(x) for x in solvers])) > 1
+
 # Compute family score modifiers.
 # This is based on the presentation in the SMT-COMP 2017 rules document
 # and is basically the same in all rules documents.
@@ -249,85 +231,6 @@ def get_family_scores(data):
                             for family, alpha_b in raw_fam_scores.items())
 
     return family_scores
-
-# Selects the winners (e.g. rank 0) from the results for a division and year
-# Returns these as a list (there may be more than one)
-# TODO: needs to be refactored with new dataframe layout
-#def select(results, division, year):
-#    return results[(results.year == year)
-#                   & (results.division == division)].groupby(
-#                        ['year', 'division']).first()['solver'].tolist()
-
-# The same as select but turns the winners into a pretty string
-# TODO: needs to be refactored with new dataframe layout
[…]

### 2019-08-30 2018/report/SMT-COMP.tex
Report: Add table for family top.

@@
 
-Whilst producing these results we noticed that the description of what constitutes a family had been incorrectly interpreted by the scoring scripts in 2016--2018.
-After fixing this misinterpretation we note that only a single division winner changes---in 2017 AUFNIRA should have been won by CVC4 and not by Vampire.
+Whilst producing these results we noticed that the description of what
+constitutes a family had been incorrectly interpreted by the scoring scripts in
+2016--2018. The scoring scripts interpreted the bottom most directory
+containing benchmarks in a logic as family, while the rules stated that the top
+most subdirectory in a logic is to be interpreted as family. After fixing this
+misinterpretation we note that only five division winners change---in 2018,
+division AUFLIRA should have been won by Vampire instead of CVC4; in 2016,
+AUFNIRA should have been won by CVC4 instead of Vampire; in 2016 and 2017,
+QF\_LIA should have been won by Yices instead of CVC4; and in 2018, QF\_NRA
+should have been won by CVC4 instead of Yices.
+Table~\ref{tab:results:total:top} shows the results in the Main Track when
+the top most subdirectory in a logic is interpreted as family in reference
+to the competition results in Table~\ref{tab:winners-main}, where the bottom
+most directory was interpreted as family.
 

### 2019-08-30 2018/report/table-winners-main-families.tex
Report: Add table for family top.

@@
 \end{table}
+
+\begin{table}
+  \caption{Alternative best solvers in the \maintrack if the notion of families were implemented as stated in the rules, i.e., top most directory instead of bottom most.}
+  \label{tab:results:total:top}
+  \centering
+  \scalebox{.755}{%
+    \renewcommand{\arraystretch}{1.01}%
+
+\begin{tabular}{r>{\columncolor{white}[.25em][.8em]}r@{\hskip .8em}|@{\hskip .5em}>{\columncolor{white}[.5em][.5em]}l>{\columncolor{white}[.5em][.8em]}r@{\hskip .8em}|@{\hskip .5em}>{\columncolor{white}[.5em][.5em]}l>{\columncolor{white}[.5em][.8em]}r@{\hskip .8em}|@{\hskip .5em}>{\columncolor{white}[.5em][.5em]}l>{\columncolor{white}[.5em][.8em]}r@{\hskip .8em}|@{\hskip .5em}>{\columncolor{white}[.5em][.5em]}l}
+\toprule
+Division & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{2015} &                        \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{2016} &                        \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{2017} &                    \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{2018} \\
+\midrule
+  AUFLIRA  &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\hspace*{5em}} &                            \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                            \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &  \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{vamp} Vampire [Z3]} \\
+AUFNIRA  &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &              \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4} &                            \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                        \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} \\
+BV       &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                            \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{q3b} Q3B} &                        \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} \\
+QF\_IDL   &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                            \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &       \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices [Z3]} &   \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices [Z3]} \\
+QF\_LIA   &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &  \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices [MathSAT]} &  \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices [MathSAT]} &                        \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} \\
+QF\_NRA   &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                            \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                            \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4 [Z3]} \\
+UFBV     &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &              \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4} &                            \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                        \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} \\
+UFIDL    &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &         \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4 [Z3]} &                            \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                        \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} \\
+UFLIA    &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                            \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                            \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4 [Z3]} \\
+UFNIA    &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                            \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                            \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                                 \hspace*{3em}        & \cc{vamp} Vampire [Z3] \\
+\bottomrule
+\end{tabular}
+  }
+\end{table}

### 2019-08-30 2018/report/SMT-COMP.tex
Report: Use consistent name for Yices.

@@
     XSat              &    &      &    &      &  1 &      &    &      \\
-    Yices2            &  3 &      &  2 &      &  2 &      &  3 &      \\
+    Yices            &  3 &      &  2 &      &  2 &      &  3 &      \\
     Z3                &  2 & [+1] &    & [+1] &    & [+1] &    & [+1] \\
@@
       1. & CVC4              & 144.67 & 144.74 & & 1. & CVC4   & 180.95 & 181.19 \\
-      2. & CVC4(exp)\footnotemark & 140.47 & 140.51 & & 2. & Yices2 & 119.29 & 119.29 \\
+      2. & CVC4(exp)\footnotemark & 140.47 & 140.51 & & 2. & Yices & 119.29 & 119.29 \\
       3. & Yices             & 101.91 & 101.91 & & 3. & veriT  &  75.11 &  75.11 \\ \cmidrule[\heavyrulewidth]{1-4} \cmidrule[\heavyrulewidth]{6-9}
@@
       1. & CVC4        & 161.38 & 161.76 & &    & [Z3]        & 186.19 & 186.19 \\
-      2. & Yices2      & 110.63 & 110.63 & & 2. & Yices2      & 115.26 & 115.26 \\
+      2. & Yices      & 110.63 & 110.63 & & 2. & Yices      & 115.26 & 115.26 \\
       3. & SMTInterpol &  65.96 &  66.00 & & 3. & SMTInterpol &  65.32 &  65.38 \\ \cmidrule[\heavyrulewidth]{1-4} \cmidrule[\heavyrulewidth]{6-9}
@@
 \item The best three \maintrack solvers according to the
-  competition-wide ranking (CVC4, Yices2, and SMTInterpol; see
+  competition-wide ranking (CVC4, Yices, and SMTInterpol; see
   Table~\ref{table:competition-wide-ranking}),
@@
 \item the solver that won the most competitive divisions in the
-  \apptrack (Yices2; see Table~\ref{tab:winners-application}),
+  \apptrack (Yices; see Table~\ref{tab:winners-application}),
 \item the solver that won the most competitive divisions in the
-  \ucoretrack (Yices2; see Table~\ref{tab:winners-unsat-core}).
+  \ucoretrack (Yices; see Table~\ref{tab:winners-unsat-core}).
 \end{itemize}
@@
     XSat              &       &       & 0     &        \\
-    Yices2            & 86    & 128   & 2379  & 1535   \\
+    Yices            & 86    & 128   & 2379  & 1535   \\
     Z3                & 6118  & 244   & 40992 & 888    \\
@@
     XSat              &     &     & 1.8 &     \\
-    Yices2            & \textcolor{gray}{1.0} & \textcolor{gray}{1.0} & \textcolor{gray}{1.0} & \textcolor{gray}{1.0} \\
+    Yices            & \textcolor{gray}{1.0} & \textcolor{gray}{1.0} & \textcolor{gray}{1.0} & \textcolor{gray}{1.0} \\
     Z3                & \textcolor{gray}{1.0} & \textcolor{gray}{1.0} & \textcolor{gray}{1.0} & \textcolor{gray}{1.0} \\

### 2019-08-30 2018/report/table-winners-unsat-core.tex
Report: Use consistent name for Yices.

@@
        NRA        & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nc{Z3}                          } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 \nc{Z3}      } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 \nc{Z3}  } \\
-       QF\_ABV    & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nc{Z3}                          } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 \nc{Z3}      } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices2             } \\
+       QF\_ABV    & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nc{Z3}                          } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 \nc{Z3}      } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices             } \\
        QF\_ABVFP  & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{                                  } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{---                               } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4          } \\
-       QF\_ALIA   & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{smti} SMTInterpol \nc{Z3}     } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{smti} SMTInterpol \nc{Z3}     } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices2 \nc{Z3}     } \\
+       QF\_ALIA   & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{smti} SMTInterpol \nc{Z3}     } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{smti} SMTInterpol \nc{Z3}     } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices \nc{Z3}     } \\
        QF\_ANIA   & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nc{Z3}                          } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4              } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4          } \\
-       QF\_AUFBV  & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nc{Z3}                           } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 \nc{MathSAT} } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices2 \nc{MathSAT}} \\
+       QF\_AUFBV  & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nc{Z3}                           } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 \nc{MathSAT} } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices \nc{MathSAT}} \\
        QF\_AUFLIA & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{smti} SMTInterpol \nc{Z3}     } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4                    } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4                } \\
        QF\_AUFNIA & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nc{Z3}                          } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 \nc{Z3}      } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 \nc{Z3}  } \\
-       QF\_AX     & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{smti} SMTInterpol \nc{Z3}     } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{smti} SMTInterpol \nc{Z3}     } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices2             } \\
-       QF\_BV     & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nc{MathSAT}                      } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 \nc{MathSAT} } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices2             } \\
+       QF\_AX     & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{smti} SMTInterpol \nc{Z3}     } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{smti} SMTInterpol \nc{Z3}     } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices             } \\
+       QF\_BV     & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nc{MathSAT}                      } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 \nc{MathSAT} } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices             } \\
        QF\_BVFP   & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nc{Z3}                           } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \nc{Z3}                     } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 \nc{Z3}  } \\
@@
        QF\_UF     & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{smti} SMTInterpol \nc{MathSAT}} & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4                    } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4                } \\
-       QF\_UFBV   & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nc{MathSAT}                      } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 \nc{MathSAT} } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices2 \nc{Z3}     } \\
-       QF\_UFIDL  & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{smti} SMTInterpol \nc{Z3}     } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{smti} SMTInterpol \nc{Z3}     } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices2             } \\
+       QF\_UFBV   & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nc{MathSAT}                      } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 \nc{MathSAT} } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices \nc{Z3}     } \\
+       QF\_UFIDL  & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{smti} SMTInterpol \nc{Z3}     } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{smti} SMTInterpol \nc{Z3}     } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices             } \\
        QF\_UFLIA  & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{smti} SMTInterpol \nc{MathSAT}} & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{smti} SMTInterpol \nc{Z3}     } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{smti} SMTInterpol \nc{Z3} } \\
-       QF\_UFLRA  & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{smti} SMTInterpol \nc{Z3}     } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{smti} SMTInterpol \nc{MathSAT}} & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices2 \nc{MathSAT}} \\
+       QF\_UFLRA  & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{smti} SMTInterpol \nc{Z3}     } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{smti} SMTInterpol \nc{MathSAT}} & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices \nc{MathSAT}} \\
        QF\_UFNIA  & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nc{Z3}                          } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 \nc{Z3}      } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 \nc{Z3}  } \\

### 2019-08-30 2018/report/table-winners-main-families.tex
Minkeyrink -> MinkeyRink

@@
 BV       &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{}              &                     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &  \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{bool} Boolector [Z3]} &                       \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} \\
-QF\_BV    &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{}             &                     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                                     \cc{mink} Minkeyrink &  \hspace*{3em}       &                           \hspace*{3em}                & \cc{bool} Boolector \\
+QF\_BV    &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{}             &                     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                                     \cc{mink} MinkeyRink &  \hspace*{3em}       &                           \hspace*{3em}                & \cc{bool} Boolector \\
 QF\_FP    &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{}             &                     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                          \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &         \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4} \\

### 2019-08-30 2018/report/table-winners-main-sat-unsat.tex
Minkeyrink -> MinkeyRink

@@
 QF\_AUFNIA &                     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                          \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &            \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4} &         \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4} \\
-QF\_BV     &                     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                                 \cc{bool} Boolector [Z3] & \cc{mink} Minkeyrink &                                                         \cc{mink} Minkeyrink &  &                       \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} \\
+QF\_BV     &                     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                                 \cc{bool} Boolector [Z3] & \cc{mink} MinkeyRink &                                                         \cc{mink} MinkeyRink &  &                       \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} \\
 QF\_FP     &                     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                          \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                          \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &         \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4} \\

### 2019-08-30 2018/report/table-winners-main.tex
Minkeyrink -> MinkeyRink

@@
 QF\_AX      &          \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices} &          \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices} &            \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices} &       \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices} \\
-QF\_BV      &       \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{bool} Boolector} &       \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{bool} Boolector} &                                        \cc{bool} Boolector & \cc{mink} Minkeyrink &                                   \cc{bool} Boolector & \cc{mink} Minkeyrink \\
+QF\_BV      &       \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{bool} Boolector} &       \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{bool} Boolector} &                                        \cc{bool} Boolector & \cc{mink} MinkeyRink &                                   \cc{bool} Boolector & \cc{mink} MinkeyRink \\
 QF\_BVFP    &                 \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{z} Z3} &          \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc [Z3]} &      \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{coli} COLIBRI [Z3]} &         \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4} \\

### 2019-08-30 2018/report/table-winners-main.tex
Division without solvers was non-competitive

@@
 \begin{table}
-\caption{Best \maintrack solvers (by division).}
+\caption{Best \maintrack solvers (by division)}
 \label{tab:winners-main}
@@
 QF\_ABV     &       \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{bool} Boolector} &       \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{bool} Boolector} &         \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{bool} Boolector} &    \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{bool} Boolector} \\
-QF\_ABVFP   &                          \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                          \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                            \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{---} &         \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4} \\
+QF\_ABVFP   &                          \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                          \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                            \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc ---} &         \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4} \\
 QF\_ALIA    &          \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices} &          \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices} &            \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices} &       \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices} \\

### 2019-08-30 2018/report/table-winners-unsat-core.tex
UC track was experimental (hence non-competitive) in 2016

@@
       \toprule
-       Division       & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{2016                          } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{2017                              } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{2018                          } \\
+       Division       & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc 2016                          } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{2017                              } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{2018                          } \\
       \midrule
-       ALIA       & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nc{Z3}                          } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 \nc{Z3}      } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 \nc{Z3}  } \\
+       ALIA       & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nonc \nc{Z3}                          } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 \nc{Z3}      } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 \nc{Z3}  } \\
        AUFBVDTLIA & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{                                  } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{                                  } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4          } \\
-       AUFLIA     & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nc{Z3}                          } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 \nc{Z3}      } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4          } \\
-       AUFLIRA    & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nc{Z3}                          } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 \nc{Z3}      } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4          } \\
-       AUFNIRA    & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nc{Z3}                          } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4              } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4          } \\
-       BV         & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nc{Z3}                          } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 \nc{Z3}      } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 \nc{Z3}  } \\
-       LIA        & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nc{veriT}                       } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4              } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 \nc{Z3}  } \\
-       LRA        & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nc{veriT}                       } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4              } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4          } \\
-       NIA        & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nc{Z3}                          } & \nonc \cc{cvc4} CVC4 & \nonc \cc{cvc4} CVC4 \nc{Z3}                                      & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4          } \\
-       NRA        & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nc{Z3}                          } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 \nc{Z3}      } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 \nc{Z3}  } \\
-       QF\_ABV    & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nc{Z3}                          } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 \nc{Z3}      } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices             } \\
+       AUFLIA     & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nonc \nc{Z3}                          } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 \nc{Z3}      } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4          } \\
+       AUFLIRA    & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nonc \nc{Z3}                          } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 \nc{Z3}      } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4          } \\
+       AUFNIRA    & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nonc \nc{Z3}                          } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4              } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4          } \\
+       BV         & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nonc \nc{Z3}                          } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 \nc{Z3}      } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 \nc{Z3}  } \\
+       LIA        & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nonc \nc{veriT}                       } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4              } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 \nc{Z3}  } \\
+       LRA        & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nonc \nc{veriT}                       } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4              } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4          } \\
+       NIA        & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nonc \nc{Z3}                          } & \nonc \cc{cvc4} CVC4 & \nonc \cc{cvc4} CVC4 \nc{Z3}                                      & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4          } \\
+       NRA        & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nonc \nc{Z3}                          } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 \nc{Z3}      } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 \nc{Z3}  } \\
+       QF\_ABV    & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nonc \nc{Z3}                          } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 \nc{Z3}      } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices             } \\
        QF\_ABVFP  & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{                                  } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{---                               } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4          } \\
-       QF\_ALIA   & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{smti} SMTInterpol \nc{Z3}     } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{smti} SMTInterpol \nc{Z3}     } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices \nc{Z3}     } \\
-       QF\_ANIA   & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nc{Z3}                          } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4              } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4          } \\
-       QF\_AUFBV  & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nc{Z3}                           } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 \nc{MathSAT} } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices \nc{MathSAT}} \\
-       QF\_AUFLIA & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{smti} SMTInterpol \nc{Z3}     } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4                    } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4                } \\
-       QF\_AUFNIA & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nc{Z3}                          } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 \nc{Z3}      } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 \nc{Z3}  } \\
-       QF\_AX     & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{smti} SMTInterpol \nc{Z3}     } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{smti} SMTInterpol \nc{Z3}     } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices             } \\
-       QF\_BV     & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nc{MathSAT}                      } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 \nc{MathSAT} } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices             } \\
-       QF\_BVFP   & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nc{Z3}                           } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \nc{Z3}                     } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 \nc{Z3}  } \\
+       QF\_ALIA   & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nonc \cc{smti} SMTInterpol \nc{Z3}    } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{smti} SMTInterpol \nc{Z3}     } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices \nc{Z3}     } \\
+       QF\_ANIA   & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nonc \nc{Z3}                          } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4              } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4          } \\
+       QF\_AUFBV  & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nonc \nc{Z3}                          } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 \nc{MathSAT} } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices \nc{MathSAT}} \\
+       QF\_AUFLIA & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nonc \cc{smti} SMTInterpol \nc{Z3}    } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4                    } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4                } \\
+       QF\_AUFNIA & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nonc \nc{Z3}                          } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 \nc{Z3}      } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 \nc{Z3}  } \\
+       QF\_AX     & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nonc \cc{smti} SMTInterpol \nc{Z3}    } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{smti} SMTInterpol \nc{Z3}     } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices             } \\
+       QF\_BV     & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nonc \nc{MathSAT}                     } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 \nc{MathSAT} } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices             } \\
+       QF\_BVFP   & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nonc \nc{Z3}                          } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \nc{Z3}                     } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 \nc{Z3}  } \\
        QF\_DT     & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{                                  } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{                                  } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4          } \\
-       QF\_FP     & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nc{MathSAT}                      } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \nc{Z3}                     } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4          } \\
-       QF\_IDL    & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{smti} SMTInterpol \nc{Z3}     } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4 \nc{Z3}            } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4 \nc{Z3}        } \\
-       QF\_LIA    & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{smti} SMTInterpol \nc{Z3}     } & \cc{smti} SMTInterpol & \cc{smti} SMTInterpol \nc{Z3}                                    & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{smti} SMTInterpol         } \\
-       QF\_LIRA   & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{smti} SMTInterpol \nc{Z3}     } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4 \nc{Z3}            } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4 \nc{Z3}        } \\
-       QF\_LRA    & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{smti} SMTInterpol             } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{smti} SMTInterpol             } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{smti} SMTInterpol         } \\
-       QF\_NIA    & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nc{Z3}                          } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 \nc{Z3}      } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 \nc{Z3}  } \\
-       QF\_NIRA   & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nc{Z3}                          } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 \nc{Z3}      } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 \nc{Z3}  } \\
-       QF\_NRA    & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nc{Z3}                          } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4              } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4          } \\
-       QF\_RDL    & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{smti} SMTInterpol \nc{veriT}  } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4 \nc{Z3}            } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4 \nc{Z3}        } \\
-       QF\_UF     & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{smti} SMTInterpol \nc{MathSAT}} & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4                    } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4                } \\
-       QF\_UFBV   & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nc{MathSAT}                      } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 \nc{MathSAT} } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices \nc{Z3}     } \\
-       QF\_UFIDL  & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{smti} SMTInterpol \nc{Z3}     } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{smti} SMTInterpol \nc{Z3}     } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices             } \\
-       QF\_UFLIA  & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{smti} SMTInterpol \nc{MathSAT}} & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{smti} SMTInterpol \nc{Z3}     } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{smti} SMTInterpol \nc{Z3} } \\
-       QF\_UFLRA  & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{smti} SMTInterpol \nc{Z3}     } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{smti} SMTInterpol \nc{MathSAT}} & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices \nc{MathSAT}} \\
-       QF\_UFNIA  & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nc{Z3}                          } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 \nc{Z3}      } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 \nc{Z3}  } \\
-       QF\_UFNRA  & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nc{Z3}                          } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 \nc{Z3}      } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 \nc{Z3}  } \\
-       UF         & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nc{Z3}                          } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4              } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4          } \\
-       UFBV       & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nc{Z3}                          } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 \nc{Z3}      } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4          } \\
+       QF\_FP     & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nonc \nc{MathSAT}                     } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \nc{Z3}                     } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4          } \\
+       QF\_IDL    & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nonc \cc{smti} SMTInterpol \nc{Z3}    } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4 \nc{Z3}            } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4 \nc{Z3}        } \\
+       QF\_LIA    & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nonc \cc{smti} SMTInterpol \nc{Z3}    } & \cc{smti} SMTInterpol & \cc{smti} SMTInterpol \nc{Z3}                                    & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{smti} SMTInterpol         } \\
+       QF\_LIRA   & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nonc \cc{smti} SMTInterpol \nc{Z3}    } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4 \nc{Z3}            } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4 \nc{Z3}        } \\
+       QF\_LRA    & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nonc \cc{smti} SMTInterpol            } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{smti} SMTInterpol             } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{smti} SMTInterpol         } \\
+       QF\_NIA    & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nonc \nc{Z3}                         } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 \nc{Z3}      } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 \nc{Z3}  } \\
+       QF\_NIRA   & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nonc \nc{Z3}                         } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 \nc{Z3}      } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 \nc{Z3}  } \\
+       QF\_NRA    & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nonc \nc{Z3}                         } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4              } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4          } \\
+       QF\_RDL    & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nonc \cc{smti} SMTInterpol \nc{veriT}  } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4 \nc{Z3}            } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4 \nc{Z3}        } \\
+       QF\_UF     & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nonc \cc{smti} SMTInterpol \nc{MathSAT}} & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4                    } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4                } \\
+       QF\_UFBV   & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nonc \nc{MathSAT}                      } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 \nc{MathSAT} } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices \nc{Z3}     } \\
+       QF\_UFIDL  & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nonc \cc{smti} SMTInterpol \nc{Z3}     } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{smti} SMTInterpol \nc{Z3}     } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices             } \\
+       QF\_UFLIA  & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nonc \cc{smti} SMTInterpol \nc{MathSAT}} & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{smti} SMTInterpol \nc{Z3}     } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{smti} SMTInterpol \nc{Z3} } \\
+       QF\_UFLRA  & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nonc \cc{smti} SMTInterpol \nc{Z3}     } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{smti} SMTInterpol \nc{MathSAT}} & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices \nc{MathSAT}} \\
+       QF\_UFNIA  & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nonc \nc{Z3}                          } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 \nc{Z3}      } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 \nc{Z3}  } \\
+       QF\_UFNRA  & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nonc \nc{Z3}                          } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 \nc{Z3}      } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 \nc{Z3}  } \\
+       UF         & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nonc \nc{Z3}                          } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4              } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4          } \\
+       UFBV       & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nonc \nc{Z3}                          } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 \nc{Z3}      } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4          } \\
        UFDT       & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{                                  } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{                                  } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4          } \\
-       UFIDL      & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nc{Z3}                          } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4              } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4          } \\
-       UFLIA      & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nc{Z3}                          } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4              } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4          } \\
-       UFLRA      & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nc{Z3}                          } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 \nc{Z3}      } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 \nc{Z3}  } \\
-       UFNIA      & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nc{Z3}                          } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4              } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4          } \\
+       UFIDL      & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nonc \nc{Z3}                          } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4              } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4          } \\
+       UFLIA      & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nonc \nc{Z3}                          } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4              } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4          } \\
+       UFLRA      & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nonc \nc{Z3}                          } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 \nc{Z3}      } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 \nc{Z3}  } \\
+       UFNIA      & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nonc \nc{Z3}                          } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4              } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4          } \\
       \bottomrule

### 2019-08-31 2018/report/SMT-COMP.tex
Minor

@@
 between SMT solving and automated theorem proving for quantified
-Boolean formulas (QBF), first-order logic, and even higher-order
+Boolean formulas~(QBF), first-order logic, and even higher-order
 logic~\cite{DBLP:journals/corr/abs-1712-01486}.
@@
 status was unknown.  However, this approach was criticized for
-imitating existing solvers rather than truly innovating.  In~2016,
+rewarding imitation of existing solvers rather than true innovation.  In~2016,
 the SMT Library contained \num{29724} non-incremental benchmarks with
@@
 for the competition's \maintrack regardless of status, and they
-directly affect the competition results.  Solver responses for such
+directly affect the competition results.
+
+Solver responses for such
 benchmarks are assumed to be correct, unless there is a disagreement
@@
 
-The use of StarExec ensures the \emph{replicability} of the competition.
+The use of StarExec ensures the replicability of the competition.
 The publicly accessible space \url{https://www.starexec.org/starexec/secure/explore/spaces.jsp?id=2641} stores all of the information required to rerun the competition, e.g., all benchmarks and copies of all tools.
@@
 
-Further, there was no restriction on the number of solver versions participants
-may submit, but the organizers reserved the right to not accept multiple
-versions of a solver in case the number of solver submissions is too large for
-the computational resources. In the past four years, exercising this right was
-not necessary.
-%
-Many of these solvers were submitted in multiple years.  Additionally,
-to promote a wide comparison between tools, developers are allowed to
-submit multiple versions of a solver, e.g., for different competition
-tracks or with differently tuned internal components.
+Further, to promote a wide comparison between tools, there was no
+restriction on the number of solver versions participants may submit,
+e.g., for different competition tracks or with differently tuned
+internal components.  Organizers reserved the right to not accept
+multiple versions of a solver in case the number of solver submissions
+is too large given the computational resources, but in the past four
+years, exercising this right was not necessary.
 Table~\ref{table:participants-history} shows in more detail how many
@@
 solver versions since 2015.
+
+In addition to the solvers that were submitted to the competition by
+their respective developers, the organizers included the most recent
+stable versions of MathSAT and Z3 for comparison purposes.  Both
+solvers are strong tools, but---except for two experimental versions
+of Z3 in 2015---their development teams chose not to prepare
+competition versions.  These solvers were therefore participating hors
+concours.  Moreover, in 2015 a bug was discovered in the \apptrack
+version of Boolector and a fixed version was submitted after the
+deadline; in 2016, the CVC4 team did not enter their solver into the
+\apptrack; and in 2018, an experimental version of CVC4 as
+well as the OpenSMT2 solver were submitted after the deadline.  These
+solvers were also participating hors concours.  In result tables, they
+are listed with their name in square brackets (e.g., [MathSAT]).
 
@@
 
-In addition to the solvers that were submitted to the competition by
-their respective developers, the organizers included the most recent
-stable versions of MathSAT and Z3 for comparison purposes.  Both
-solvers are strong tools, but---except for two experimental versions
-of Z3 in 2015---their development teams chose not to prepare
-competition versions.  These solvers were therefore participating hors
-concours.  Moreover, in 2015 a bug was discovered in the \apptrack
-version of Boolector and a fixed version was submitted after the
-deadline; in 2016, the CVC4 team did not enter their solver into the
-\apptrack; and in 2018, an experimental version of CVC4 as
-well as the OpenSMT2 solver were submitted after the deadline.  These
-solvers were also participating hors concours.  In result tables, they
-are listed with their name in square brackets (e.g., [MathSAT]).
-
 Table~\ref{table:participation-by-track} summarizes these numbers and
@@
 details.  We caution against over-interpreting these numbers, which to
-some extent depend on how experimental development teams were in any
+some extent depend on how adventurous development teams were in any
 given year.
@@
 solver versions were submitted each year since 2015.  In contrast, the
-competitions from 2005--2014 only received an average of 12
+competitions from 2005--2014 only received an average of~12
 submissions~\cite{CDW14}.
@@
 The \emph{(weighted) score} of a solver in a (\maintrack or
-\ucoretrack) division~$D$ is then defined as the weighted sum of all
+\ucoretrack) division~$i$ is then defined as the weighted sum of all
 raw scores
 %
-$$\sum_{b\in D} \alpha'_b \cdot \langle e_b \cdot |D|, n_b \cdot |D|, w_b,
-  c_b\rangle$$
+$$\sum_{b\in i} \alpha'_b \cdot \langle e_b \cdot N_i, n_b \cdot N_i, w_b, c_b\rangle$$
 %
-where the sum is over all benchmarks in the division, and~$|D|$ is the
-number of benchmarks in~$D$.  This is computed separately for parallel
+where the sum is over all benchmarks in the division, and~$N_i$ is the
+number of benchmarks in~$i$.  This is computed separately for parallel
 and sequential scores.
@@
 %
-The value of this constant was chosen to balance the strong interest
-in correct solvers against the risk of stifling innovation.  In the
-division rankings (Section~\ref{sec:scoring-division-rankings}), an
-incorrect response causes a solver to be ranked below all correct
-solvers for that division.  But the competition's \maintrack consists
-of many independent divisions; a solver bug that affects one division
-need not manifest itself in other divisions.  With the current value,
-entering a (possibly buggy) solver that can solve all benchmarks into
-a division has a positive expected score if the probability that a
-soundness bug in the solver will be triggered is below~$20\,\%$.
+The value~$-4$ was chosen to balance the strong interest in correct
+solvers against the risk of stifling innovation.  In the division
+rankings (Section~\ref{sec:scoring-division-rankings}), an incorrect
+response causes a solver to be ranked below all correct solvers for
+that division.  But the competition's \maintrack consists of many
+independent divisions; a solver bug that affects one division need not
+manifest itself in other divisions.  With this value, entering a
+(possibly buggy) solver that can solve all benchmarks into a division
+has a positive expected score if the probability that a soundness bug
+in the solver will be triggered is below~$20\,\%$.
 
@@
 
-The SMT Competition consists of several tracks with a multitude of divisions
-per track.
-Not all participating solvers enter all tracks, and the majority of
-participants participates only in a handful of divisions.
-To give a measure of overall progress in solver performance we
-use the notion of \emph{virtual best solver} (VBS) over all divisions of all
-three tracks.
+The SMT Competition consists of several tracks with a multitude of
+divisions per track.  Not all participating solvers enter all tracks,
+and the majority of solvers participates only in a handful of
+divisions.  To give a measure of overall progress in solver
+performance we use, for each of the three tracks, the notion of a
+\emph{virtual best solver} (VBS) over all divisions.
 
@@
 %
-Between 2014 (\num{67426} benchmarks) and~2015 (\num{154238} benchmarks),
-the number of common benchmarks is \num{67070};
-between 2015 and 2016 (\num{154424} benchmarks) it is \num{154238};
-between 2016 and 2017 (\num{238758} benchmarks) it is \num{145236};
-and between 2017 and 2018 (\num{333241} benchmarks) it is \num{226429}.
+Between 2014 (\num{67426} benchmarks) and~2015 (\num{154238}
+benchmarks), the number of common benchmarks is \num{67070}; between
+2015 and 2016 (\num{154424} benchmarks) it is \num{154238}; between
+2016 and 2017 (\num{238758} benchmarks) it is \num{145236}; and
+between 2017 and 2018 (\num{333241} benchmarks) it is \num{226429}.
 The number of solved instances on these sets of common benchmarks
-increased from 2014 to 2015 by 0.1\%, from 2016 to 2017 by 3.9\%,
-and from 2017 to 2018 by 0.3\%.
-Interestingly, it decreased from 2015 to 2016 by 3.5\%.
-This is mainly due to the fact that, in 2015, more than \num{5600} benchmarks of
-division QF\_FP where solved by one of the two participating configurations of
-Z3 that no one else could solve, and in~2016 Z3 did not participate in this
-division.
+increased from 2014 to 2015 by 0.1\%, from 2016 to 2017 by 3.9\%, and
+from 2017 to 2018 by 0.3\%.  Interestingly, it decreased from 2015 to
+2016 by 3.5\%.  This is mainly due to the fact that, in 2015, more
+than \num{5600} benchmarks of division QF\_FP were solved by one of
+the two participating configurations of Z3 but by no other solver, and
+in~2016 Z3 did not participate in this division.
 
@@
 QF\_SLIA, as well as the only sound solver in QF\_ABVFP.  Note that
-divisions with fewer than two competing solvers do not affect the
-competition-wide ranking.
+divisions with fewer than two competing solvers are non-competitive
+and do not affect the competition-wide ranking.
 
@@
 
-%TODO: discuss whether this can be attributed to the hardness
-%distribution of benchmarks (cf. VBS plot)
-
 In Table~\ref{table:parallelism}, we report the quotient of CPU time
-over wall-clock time (summed up over all \maintrack benchmarks) for
-each solver, as well as for all solvers combined.  When there were
-multiple versions of a solver (such as a sequential and a parallel
-version), only the highest value is shown.  We note that this quotient
-is close to~1 for most solvers: only about 4--8 \maintrack solvers
-each year were participating with a version that made use of
+over wall-clock time (summed up over all benchmarks) for each
+\maintrack solver, as well as for all solvers combined.  When there
+were multiple versions of a solver (such as a sequential and a
+parallel version), only the highest value is shown.  We note that this
+quotient is close to~1 for most solvers: only about 4--8 \maintrack
+solvers each year were participating with a version that made use of
 parallelism.
@@
 
-In many cases, an SMT application produces either mainly satisfiable or mainly
-unsatisfiable queries to the SMT solver.  A typical example is bounded model checking,
-where a query is only satisfiable if a property of the model does not hold.  As
-a consequence, some solvers may implement specialized techniques and
-optimizations for the more frequent (the expected) case.
+In many cases, an SMT application produces either mainly satisfiable
+or mainly unsatisfiable queries to the SMT solver.  A typical example
+is bounded model checking, where a query is only satisfiable if a
+property of the model does not hold.  As a consequence, some solvers
+may implement specialized techniques and optimizations for the more
+frequent (the expected) case.
 %
-Therefore, it is interesting to ask whether the winners of divisions of a track
-might have changed if benchmarks in that division had been restricted to one of
-these results.  Tables~\ref{tab:results:sat}-\ref{tab:results:unsat} show the
-changes in division winners if only satisfiable or unsatisfiable results are
-given. These tables only lists the result for a division if it has changed
-with respect to Table~\ref{tab:winners-main}. A non-competing solver is listed
-by itself if there was no competing solver with a positive division score under
-the given constraints.
-It is interesting to note that we see some new solvers winning divisions that
-did not win any division in the main results. For example, veriT solves the
-most satisfiable benchmarks in QF\_UFIDL in 2018 and the most unsatisfiable
-benchmarks in all four years in UFLRA, and SMTInterpol performs very well on
-unsatisfiable benchmarks in QF\_LIA.
-
-We only consider the \maintrack here, which contains a mixture of benchmarks that
-are satisfiable and unsatisfiable. A percentage of satisfiable, unsatisfiable
-and unknown status benchmarks per division and year is given in
-Table~\ref{table:benchmarks-main-track}.  For the \apptrack, this analysis is
-less meaningful since a benchmark usually contains a multitude of both
-satisfiable and unsatisfiable incremental queries
-(which may depend on each other).
-For the \ucoretrack, only known unsatisfiable benchmarks from the \maintrack
-are used, which renders this analysis useless for this track.
+Therefore, it is interesting to ask whether the winners of divisions
+of a track might have changed if benchmarks in that division had been
+restricted to one of these results.
+Tables~\ref{tab:results:sat}--\ref{tab:results:unsat} show the changes
+in division winners if only satisfiable or unsatisfiable results are
+considered.  These tables only lists the result for a division if it
+has changed with respect to Table~\ref{tab:winners-main}.  A
+non-competing solver is listed by itself if there was no competing
+solver with a positive division score under the given constraints.  It
+is interesting to note that we see some new solvers winning divisions
+that did not win any division in the main results.  For example, veriT
+solves the most satisfiable benchmarks in QF\_UFIDL in 2018 and the
+most unsatisfiable benchmarks in all four years in UFLRA, and
+SMTInterpol performs very well on unsatisfiable benchmarks in QF\_LIA.
+
+We only consider the \maintrack here, which contains a mixture of
+benchmarks that are satisfiable and unsatisfiable.  A percentage of
+satisfiable, unsatisfiable and unknown status benchmarks per division
+and year is given in Table~\ref{table:benchmarks-main-track}.  For the
+\apptrack, this analysis is less meaningful since a benchmark usually
+contains a multitude of both satisfiable and unsatisfiable incremental
+queries (which may depend on each other).  For the \ucoretrack, only
+known unsatisfiable benchmarks from the \maintrack are used, which
+renders this analysis useless for this track.
 

### 2019-08-31 2018/report/SMT-COMP.tex
Source file cleanup

@@
 \usepackage{booktabs}
-%\usepackage[pdf]{pstricks}
-%\usepackage{pst-tree}
 \usepackage{xspace}
@@
 \usepackage{siunitx}
-
-%\usepackage[numbers,sort&compress]{natbib}
 
@@
 }
-
-%\usepackage{showframe}   % debug
 
@@
   \addr Uppsala University \\
-  %Uppsala \\
   Sweden
@@
   \addr ClearSy Systems Engineering \\
-  %Aix-en-Provence \\
   France
@@
   \addr University of Freiburg \\
-  %City \\
   Germany
@@
   \addr Stanford University\\
-  %Stanford \\
   USA
@@
 %% learned and suggestions for improvements for future competitions.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%% Changes 2015:
-%% \begin{itemize}
-%% \item All solvers will be run with $n=4$ cores available.  We will
-%%   recognize both best sequential and best parallel performance in all
-%%   \maintrack divisions, using different CPU time limits.
-%% \item The division scoring will take time spent on unsolved benchmarks
-%%   into account.  Previous competitions only considered time spent on
-%%   solved benchmarks.  However, the number of solved benchmarks still
-%%   takes precedence over run-time.
-%% \item In addition to recognizing the best solver in each division, we
-%%   will recognize solvers that perform best according to
-%%   competition-wide criteria, emphasizing breadth of supported logics.
-%%   These criteria will be a refinement of the criteria used for the
-%%   FLoC Olympic Games medals in~2014.
-%% \item We plan to include new divisions for floating-point arithmetic.
-%%   These should be considered experimental in~2015, and will not be
-%%   included in the competition-wide ranking.
-%% \item We plan to run solvers on all eligible benchmarks.  Previous
-%%   competitions used a proper subset of eligible benchmarks, causing
-%%   competition results to be affected by a random selection process.
-%% \end{itemize}
-
-%% Changes 2016:
-%% \begin{itemize}
-%% \item Benchmarks will use (a subset of) version~2.5 of the SMT-LIB
-%%   language.  \emph{Rationale:} This is the latest version of the
-%%   SMT-LIB language.  It was released on 2015-06-28, and is largely
-%%   backwards-compatible to version~2.0, which was used for SMT-COMP
-%%   2015.
-%% \item Solver output may affect the score even when the solver does not
-%%   terminate within the time limit.  (In 2015, \maintrack solver output
-%%   was ignored if the solver subsequently timed out.)  Solvers should
-%%   take care not to accidentally produce output that contains
-%%   \texttt{sat} or \texttt{unsat} even when they are killed.
-%%   \emph{Rationale:} Users are likely to trust solver responses even
-%%   when the solver continues to run for some time.
-%% \item Divisions for floating-point arithmetic are no longer
-%%   experimental, and will be considered competitive if the necessary
-%%   requirements (see Section~\ref{sec:scoring}) are met.
-%%   \emph{Rationale:} Floating-point divisions were experimental in
-%%   2015.  By now, their definition is sufficiently stable, and they are
-%%   supported by several solvers.
-%% \item Division scores will be based on a weighted sum of scores for
-%%   benchmark families.  \emph{Rationale:} For some years now, SMT-COMPs
-%%   have had sufficient computational resources to evaluate all solver
-%%   entrants on all eligible benchmarks.  As a side-effect, the
-%%   weighting of benchmark families that was achieved in early SMT-COMPs
-%%   through a careful selection of benchmarks (based on benchmark
-%%   difficulty and category) was lost.  Since there are vast differences
-%%   in size between benchmark families, we believe that a weighting that
-%%   de-emphasizes large benchmark families (see
-%%   Section~\ref{sec:division-scoring}) will lead to more meaningful
-%%   competition results.
-%% \item The \ucoretrack that was introduced in SMT-COMP 2012, but
-%%   discontinued in 2013-2015 (partly because of the competition's move
-%%   to StarExec), is back.  It will be experimental in 2016; its results
-%%   will be reported, but no official winners will be announced.
-%%   \emph{Rationale:} Unsat cores are important in many applications of
-%%   SMT solving.  The track was discontinued primarily for
-%%   infrastructure and resource reasons.  We are pleased that we can
-%%   finally offer it again, but we ask for your understanding in case of
-%%   mishaps while we port the required tools.
-%% \item Best industrial performance will no longer be recognized
-%%   separately.  \emph{Rationale:} While there is agreement in the SMT
-%%   community to emphasize problems that come from real applications,
-%%   industrial performance largely coincided with overall performance in
-%%   SMT-COMP 2015.  We consider the effort to determine and report it
-%%   separately no longer justified.
-%% \end{itemize}
-
-%% Changes 2017:
-%% \begin{itemize}
-%% \item Submission of accompanying information for solvers is via a web
-%%   form (rather than by email to the organizers).  \emph{Rationale:}
-%%   Email submissions were often incomplete, leading to ambiguity and
-%%   further inquiries.  The form provides a more structured way of
-%%   submitting information.
-%% \item Benchmarks will use (a subset of) version~2.6 of the SMT-LIB
-%%   language.  \emph{Rationale:} This is the latest version of the
-%%   SMT-LIB language.  It is largely backwards-compatible with earlier
-%%   versions (in particular~2.0 and~2.5).
-%% \item Benchmarks that use partial bit-vector functions, such as
-%%   \texttt{bvudiv}, or underspecified floating-point functions, such as
-%%   \texttt{fp.min}, will be eligible for the competition again.
-%%   \emph{Rationale:} A conclusion on the semantics of these functions
-%%   has finally been reached, and the status of affected SMT-LIB
-%%   benchmarks has been updated accordingly.
-%% \item Benchmarks with unknown status will be eligible for the
-%%   competition's \maintrack.  In 2016, solver performance on benchmarks
-%%   with unknown status was evaluated but reported separately; in 2017,
-%%   it will directly affect the competition results.  \emph{Rationale:}
-%%   Using only benchmarks with known status (i.e., benchmarks that have
-%%   been solved before) to determine the competition results unjustly
-%%   favors imitation of existing solvers over true innovation.
-%% \item In the competition-wide scoring, the (per-division) penalty for
-%%   erroneous results is changed from the number of errors to a fixed
-%%   constant (multiplied by the weight of the respective division).
-%%   \emph{Rationale:} The weight already takes the number of benchmarks
-%%   in the division into account; multiplying it by the number of errors
-%%   overemphasizes large divisions.
-%% \item The \ucoretrack, which was re-introduced in 2016, is no
-%%   longer experimental.  Its divisions will be considered competitive
-%%   if the necessary requirements (see Section~\ref{sec:scoring}) are
-%%   met.  \emph{Rationale:} Rules and tool support for the unsat-core
-%%   track proved sufficiently stable in 2016.
-%% \item The competition will feature experimental divisions for
-%%   benchmarks that use algebraic datatypes.  \emph{Rationale:}
-%%   Algebraic datatypes are specified in the draft SMT-LIB~2.6 standard,
-%%   which is expected to become official in the near future, and are
-%%   already supported by some solvers.  Benchmarks that use datatypes
-%%   have recently been added to SMT-LIB.
-%% \end{itemize}
-
-%% Changes 2018:
-%% \begin{itemize}
-%% \item The time limit per solver/benchmark pair is anticipated to be at
-%%   most 20 minutes in the \maintrack, and at most 40 minutes in the
-%%   other tracks.  \emph{Rationale:} Already in 2017, the time limit for
-%%   the \maintrack was reduced to 20 minutes (down from 40 minutes in
-%%   earlier years) to cope with the inclusion of a large number of
-%%   benchmarks with unknown status.
-%% \item In the \ucoretrack, the unsatisfiability check for the
-%%   returned core will be based on a simple majority vote.  The case
-%%   that a solver finds its own core satisfiable will no longer be
-%%   treated specially.  \emph{Rationale:} This allows to simplify the
-%%   post-processing of \ucoretrack results considerably.
-%% \item In 2017, the competition featured experimental divisions for
-%%   benchmarks that use algebraic datatypes.  These divisions will be
-%%   regular (non-experimental) in 2018. \emph{Rationale:} Algebraic
-%%   datatypes are specified in the latest official release (Version~2.6)
-%%   of the SMT-LIB standard.
-%% \item The competition will feature an experimental divisions for
-%%   benchmarks that use strings.  \emph{Rationale:} Corresponding
-%%   theories and benchmarks are expected to be added to SMT-LIB in the
-%%   near future.
-%% \end{itemize}
 
@@
 
-The SMT Competition is one of a growing number of tool competitions in the broad area of formal methods, which are summarised in a recent review of the area~\cite{toolympics}.
-The two closest competitions in terms of goals and design are the SAT competition (\url{http://www.satcompetition.org/}), which evaluates SAT solvers, and CASC (\url{http://www.tptp.org/CASC/}), which evaluates automated theorem provers (ATPs).
-In recent years, we have seen a blurring of lines between SMT-COMP and CASC with SMT solvers competing in CASC and ATPs competing in SMT-COMP.
-The main (informal) distinction remains that SMT-COMP focuses on problems that are heavy in theories, whereas CASC focuses on problems heavy in quantifiers.
-Another closely related competition is SV-COMP (\url{https://sv-comp.sosy-lab.org}) where many tools rely on advances in SMT solving technology.
-
-The SMT Competition was part of the Federated Logic
-Conference (FLoC) Olympic Games, which comprised 14 competitions in
-various areas of computational logic, in Vienna in~2014, and again in
-Oxford~(UK) in~2018.  It was last described in a 2014 competition
+The SMT Competition is one of a growing number of tool competitions in
+the broad area of formal methods, which are summarised in a recent
+review of the area~\cite{toolympics}. The two closest competitions in
+terms of goals and design are the SAT competition
+(\url{http://www.satcompetition.org/}), which evaluates SAT solvers,
+and CASC (\url{http://www.tptp.org/CASC/}), which evaluates automated
+theorem provers (ATPs). In recent years, we have seen a blurring of
+lines between SMT-COMP and CASC with SMT solvers competing in CASC and
+ATPs competing in SMT-COMP. The main (informal) distinction remains
+that SMT-COMP focuses on problems that are heavy in theories, whereas
+CASC focuses on problems heavy in quantifiers.  Another closely
+related competition is SV-COMP (\url{https://sv-comp.sosy-lab.org})
+where many tools rely on advances in SMT solving technology.
+
+The SMT Competition was part of the Federated Logic Conference (FLoC)
+Olympic Games, which comprised 14 competitions in various areas of
+computational logic, in Vienna in~2014, and again in Oxford~(UK)
+in~2018.  It was last described in a 2014 competition
 report~\cite{CDW14}.  In this paper, we report on the design and
@@
 2018.  Anyone may submit new benchmarks to the SMT Library, and
-competitors are allowed to tune their solvers accordingly.
-Therefore all benchmarks eligible for the competition must be released
-at least some time before the final solver submission deadline.  To
-give the SMT-LIB maintainers sufficient time for curation, the
-deadline for new benchmark contributions has usually been about four
-to six weeks before the initial solver deadline, typically in April or
-early May.
+competitors are allowed to tune their solvers accordingly.  Therefore
+all benchmarks eligible for the competition must be released at least
+some time before the final solver submission deadline.  To give the
+SMT-LIB maintainers sufficient time for curation, the deadline for new
+benchmark contributions has usually been about four to six weeks
+before the initial solver deadline, typically in April or early May.
 
@@
 
-The SMT Competition consists of several tracks.  Each track is further split
-into (logic) \emph{divisions}, where each division corresponds to a logic from
-the SMT Library.  As indicated in
-Tables~\ref{table:smtlib}--\ref{table:divisions}, there are slightly fewer
-divisions (Table~\ref{table:divisions}) than logics in the SMT Library
-(Table~\ref{table:smtlib}) because not every logic contains benchmarks eligible
-for the competition.
+The SMT Competition consists of several tracks.  Each track is further
+split into (logic) \emph{divisions}, where each division corresponds
+to a logic from the SMT Library.  As indicated in
+Tables~\ref{table:smtlib}--\ref{table:divisions}, there are slightly
+fewer divisions (Table~\ref{table:divisions}) than logics in the SMT
+Library (Table~\ref{table:smtlib}) because not every logic contains
+benchmarks eligible for the competition.
 
 \paragraph{Tracks.}
-The \emph{\maintrack}, which
-has been a staple of the competition since its
-inception in 2005, features non-incremental benchmarks.  The
+The \emph{\maintrack}, which has been a staple of the competition
+since its inception in 2005, features non-incremental benchmarks.  The
 \emph{\apptrack}, which has been part of the competition since
@@
 next benchmark command (to prevent look-ahead behavior).  The
-\emph{\ucoretrack} uses \maintrack benchmarks that are known to
-be unsatisfiable, and solvers are evaluated on their ability to find
+\emph{\ucoretrack} uses \maintrack benchmarks that are known to be
+unsatisfiable, and solvers are evaluated on their ability to find
 small unsatisfiable cores (i.e., a small but still unsatisfiable
-subset of the benchmark's assertions).  The \ucoretrack had first
-been part of the competition in 2012~\cite{CGBD12}, but was then
+subset of the benchmark's assertions).  The \ucoretrack had first been
+part of the competition in 2012~\cite{CGBD12}, but was then
 discontinued (partly because of the competition's move to StarExec and
-inadequate tool support).  It was re-introduced as an experimental track
-in 2016, and has been a regular competition track again since~2017.
+inadequate tool support).  It was re-introduced as an experimental
+track in 2016, and has been a regular competition track again
+since~2017.
 
@@
 they want to enter, and competition results are reported separately
-for each track and division.  Thus, competing solvers do not need to support
-all logics, and may or may not support features such as incremental solving
-or unsat-core generation.
+for each track and division.  Thus, competing solvers do not need to
+support all logics, and may or may not support features such as
+incremental solving or unsat-core generation.
 
 \paragraph{Eligible benchmarks.}
-Some benchmarks typically have to be
-excluded for syntactic reasons: in 2015 and 2016, \num{11966} benchmarks
-were excluded because they contained partial or underspecified
-operations (e.g., bit-vector division), whose precise semantics were
-being debated at the time.  Additionally in~2016, one benchmark was
-excluded because it contained incorrect status information.  In~2017,
-\num{1104} benchmarks were excluded because their logic had been classified
-incorrectly, and 8~benchmarks were excluded because of incorrect or
-missing status information.  Moreover, divisions containing datatypes
-({DT})---which were new in~2017---were excluded from the Unsat-Core
-track because of inadequate tool support.  In~2018, \num{3603}~benchmarks were
-excluded because they contained named terms (a feature of the SMT-LIB
-language that is not permitted in competition benchmarks), and
-5~benchmarks were excluded because of missing status information.
+Some benchmarks typically have to be excluded for syntactic reasons:
+in 2015 and 2016, \num{11966} benchmarks were excluded because they
+contained partial or underspecified operations (e.g., bit-vector
+division), whose precise semantics were being debated at the time.
+Additionally in~2016, one benchmark was excluded because it contained
+incorrect status information.  In~2017, \num{1104} benchmarks were
+excluded because their logic had been classified incorrectly, and
+8~benchmarks were excluded because of incorrect or missing status
+information.  Moreover, divisions containing datatypes ({DT})---which
+were new in~2017---were excluded from the Unsat-Core track because of
+inadequate tool support.  In~2018, \num{3603}~benchmarks were excluded
+because they contained named terms (a feature of the SMT-LIB language
+that is not permitted in competition benchmarks), and 5~benchmarks
+were excluded because of missing status information.
 
@@
 whose status was known (i.e., that had been solved previously by
-existing SMT solvers).  In 2015, \num{30717} non-incremental benchmarks
-from the SMT Library were not used for the competition because their
-status was unknown.  However, this approach was criticized for
-rewarding imitation of existing solvers rather than true innovation.  In~2016,
-the SMT Library contained \num{29724} non-incremental benchmarks with
-unknown status; solver performance on these was evaluated but reported
-separately.  Since 2017, all non-incremental benchmarks are eligible
-for the competition's \maintrack regardless of status, and they
-directly affect the competition results.
-
-Solver responses for such
-benchmarks are assumed to be correct, unless there is a disagreement
-between two or more solvers that are otherwise (i.e., on benchmarks with
-known status) sound.  Benchmarks with disagreements are removed from
-the competition results.  This conservative approach was chosen over a
-voting system as the latter is unreliable (especially in divisions
-with few solvers), could lead to a solver being punished wrongly, and
-could be gamed by entering multiple copies of a solver into the
-competition.  Moreover, the size and time frame of the competition
-demand an automated resolution.  Disagreements are reported to the
-solver developers involved, who typically perform a manual
-investigation at their leisure, and in all cases have led to bugs in
-solvers being identified and fixed.  In 2016, there were disagreements
-on 79 benchmarks; in 2017, only one benchmark was removed; while in
-2018, there were no disagreements between otherwise sound solvers.
+existing SMT solvers).  In 2015, \num{30717} non-incremental
+benchmarks from the SMT Library were not used for the competition
+because their status was unknown.  However, this approach was
+criticized for rewarding imitation of existing solvers rather than
+true innovation.  In~2016, the SMT Library contained \num{29724}
+non-incremental benchmarks with unknown status; solver performance on
+these was evaluated but reported separately.  Since 2017, all
+non-incremental benchmarks are eligible for the competition's
+\maintrack regardless of status, and they directly affect the
+competition results.
+
+Solver responses for such benchmarks are assumed to be correct, unless
+there is a disagreement between two or more solvers that are otherwise
+(i.e., on benchmarks with known status) sound.  Benchmarks with
+disagreements are removed from the competition results.  This
+conservative approach was chosen over a voting system as the latter is
+unreliable (especially in divisions with few solvers), could lead to a
+solver being punished wrongly, and could be gamed by entering multiple
+copies of a solver into the competition.  Moreover, the size and time
+frame of the competition demand an automated resolution.
+Disagreements are reported to the solver developers involved, who
+typically perform a manual investigation at their leisure, and in all
+cases have led to bugs in solvers being identified and fixed.  In
+2016, there were disagreements on 79 benchmarks; in 2017, only one
+benchmark was removed; while in 2018, there were no disagreements
+between otherwise sound solvers.
 
 For incremental benchmarks, the situation is different: an incremental
-benchmark is ineligible for the \apptrack if its first {\tt
-  check-sat} command has unknown status.  Otherwise, the prefix of the
-benchmark that only contains {\tt check-sat} commands with known
-status is eligible.  The main reason for this difference is that the
-competition tools for the \apptrack (in particular, the trace
-executor) had not been adapted yet to support {\tt check-sat}
-commands with unknown status.
-Even though the trace executor has now been modified, we cannot check what impact this may have had on previous results without rerunning the \apptrack as the trace executor drives the solver.
+benchmark is ineligible for the \apptrack if its first {\tt check-sat}
+command has unknown status.  Otherwise, the prefix of the benchmark
+that only contains {\tt check-sat} commands with known status is
+eligible.  The main reason for this difference is that the competition
+tools for the \apptrack (in particular, the trace executor) had not
+been adapted yet to support {\tt check-sat} commands with unknown
+status. Even though the trace executor has now been modified, we
+cannot check what impact this may have had on previous results without
+rerunning the \apptrack as the trace executor drives the solver.
 
@@
 actually a competition division in that track and year.  The size of
-divisions varies widely, from just one benchmark in ABVFP to~\num{72705}
-benchmarks in QF\_SLIA.
+divisions varies widely, from just one benchmark in ABVFP
+to~\num{72705} benchmarks in QF\_SLIA.
 
@@
 SMT Competition from~2015 to~2018.  Over this period, the number has
-grown by~72\,\%, from~\num{1028615} job pairs in~2015 to~\num{1776062} job
-pairs in~2018.  (This is the number of unique solver/benchmark
+grown by~72\,\%, from~\num{1028615} job pairs in~2015 to~\num{1776062}
+job pairs in~2018.  (This is the number of unique solver/benchmark
 combinations that were part of the competition.  The number of job
@@
 
-The use of StarExec ensures the replicability of the competition.
-The publicly accessible space \url{https://www.starexec.org/starexec/secure/explore/spaces.jsp?id=2641} stores all of the information required to rerun the competition, e.g., all benchmarks and copies of all tools.
-In addition, a GitHub organization (\url{https://github.com/SMT-COMP/smt-comp}) has been set up to archive previous results and store the tools used by organizers to run the competition.
+The use of StarExec ensures the replicability of the competition. The
+publicly accessible space
+\url{https://www.starexec.org/starexec/secure/explore/spaces.jsp?id=2641}
+stores all of the information required to rerun the competition, e.g.,
+all benchmarks and copies of all tools. In addition, a GitHub
+organization (\url{https://github.com/SMT-COMP/smt-comp}) has been set
+up to archive previous results and store the tools used by organizers
+to run the competition.
 
@@
 
-Participants are required to be authors of the tool they submit.
-In 2015--2018, the competition rules did not further define authorship,
-but it is understood that an author contributed code to the tool.
-As a special case of this rule, participants are required to identify
-if their tool is a wrapper tool, i.e., any solver that calls (or is in some
-other way based on) one or more SMT solvers of which the author of the tool
-is not an author.
+Participants are required to be authors of the tool they submit.  In
+2015--2018, the competition rules did not further define authorship,
+but it is understood that an author contributed code to the tool.  As
+a special case of this rule, participants are required to identify if
+their tool is a wrapper tool, i.e., any solver that calls (or is in
+some other way based on) one or more SMT solvers of which the author
+of the tool is not an author.
 
@@
 
-Participants were not required to provide source code with their submission.
-There were no licensing requirements/restrictions for the submitted binaries
-of the participating solvers.
+Participants were not required to provide source code with their
+submission.  There were no licensing requirements/restrictions for the
+submitted binaries of the participating solvers.
 %
-Participants were encouraged to submit a short system description
-of their solver, including a list of its authors and an explanation of
+Participants were encouraged to submit a short system description of
+their solver, including a list of its authors and an explanation of
 the SMT solving approach used.  System descriptions are published on
@@
 deadline; in 2016, the CVC4 team did not enter their solver into the
-\apptrack; and in 2018, an experimental version of CVC4 as
-well as the OpenSMT2 solver were submitted after the deadline.  These
-solvers were also participating hors concours.  In result tables, they
-are listed with their name in square brackets (e.g., [MathSAT]).
+\apptrack; and in 2018, an experimental version of CVC4 as well as the
+OpenSMT2 solver were submitted after the deadline.  These solvers were
+also participating hors concours.  In result tables, they are listed
+with their name in square brackets (e.g., [MathSAT]).
 
@@
 \begin{itemize}[noitemsep]
-  \item \makebox[5em][l]{$e\geq 0$} number of erroneous responses (usually~$e = 0$),
-  \item \makebox[5em][l]{$0 \leq n \leq N$} number of correct responses (resp.~\emph{reduction} for the \ucoretrack),
-  \item \makebox[5em][l]{$w \in [0,T]$} wall-clock time in seconds (real-valued),
-  \item \makebox[5em][l]{$c \in [0, 4T]$} CPU time in seconds (real-valued).
+  \item \makebox[5em][l]{$e\geq 0$} number of erroneous responses
+    (usually~$e = 0$),
+  \item \makebox[5em][l]{$0 \leq n \leq N$} number of correct
+    responses (resp.~\emph{reduction} for the \ucoretrack),
+  \item \makebox[5em][l]{$w \in [0,T]$} wall-clock time in seconds
+    (real-valued),
+  \item \makebox[5em][l]{$c \in [0, 4T]$} CPU time in seconds
+    (real-valued).
 \end{itemize}
@@
 Tables~\ref{tab:winners-main}--\ref{tab:winners-unsat-core} show the
-highest-ranked solvers for all (competitive and non-competitive) divisions from
-2015--2018.
-We include solvers that were running hors concours (and hence non-competing
-and ineligible to be recognized as official competition winners).
-Non-com-petitive divisions use gray font. % TODO superscript?
-Entries $A [B]$ indicate that solver $A$ was the highest competing solver,
-but non-competing solver $B$ actually ranked best if non-competing solvers
-were taken into consideration.
-Entries
-$A|B$ indicate that solver~$A$ ranked first considering sequential
+highest-ranked solvers for all (competitive and non-competitive)
+divisions from 2015--2018.  We include solvers that were running hors
+concours (and hence non-competing and ineligible to be recognized as
+official competition winners).  Non-com-petitive divisions use gray
+font.  Entries $A [B]$ indicate that solver $A$ was the highest
+competing solver, but non-competing solver $B$ actually ranked best if
+non-competing solvers were taken into consideration.  Entries $A|B$
+indicate that solver~$A$ ranked first considering sequential
 performance, while~$B$ ranked first considering parallel performance.
 When the same solver ranked first in both, which is most often the
-case, its name appears just once.
-Table cell colors (other than white) indicate the best competing
-solver performance; no cell color indicates that the best solver
-performance was by a non-competing solver and no competing solvers participated
-in that division.
-Full division rankings are available from the competition website.
+case, its name appears just once.  Table cell colors (other than
+white) indicate the best competing solver performance; no cell color
+indicates that the best solver performance was by a non-competing
+solver and no competing solvers participated in that division.  Full
+division rankings are available from the competition website.
 
@@
 In comparison to the competition-wide ranking for the \maintrack, the
-metric used for the \apptrack and \ucoretrack---simply counting
-the number of competitive divisions that a solver has won---was rather
+metric used for the \apptrack and \ucoretrack---simply counting the
+number of competitive divisions that a solver has won---was rather
 unsophisticated.  Future editions of the competition should perhaps
@@
 worth one point (before benchmark weights are applied) if solved
-correctly, while benchmarks in the \apptrack and \ucoretrack
-are worth widely varying numbers of points.  Moreover, in the
-\ucoretrack, the size of the smallest unsatisfiable core---and
-hence the number of points attainable on any given benchmark---may not
-be known precisely.
+correctly, while benchmarks in the \apptrack and \ucoretrack are worth
+widely varying numbers of points.  Moreover, in the \ucoretrack, the
+size of the smallest unsatisfiable core---and hence the number of
+points attainable on any given benchmark---may not be known precisely.
 
@@
 For the \maintrack, we determine the VBS as the best wall-clock
-performance per (correctly solved) instance with the time limit of \SI{1200}{s} used
-in the competitions 2017 and 2018. Figure~\ref{fig:progress-all} visualizes VBS
-performance on common benchmarks from 2015--2018 as cactus plot.
-Figure~\ref{fig:progress} shows VBS performance on common benchmarks over pairs
-of consecutive years from 2014 to 2018.  Both plots show the wall-clock solving
-time per instance over all instances, sorted by solving time.
+performance per (correctly solved) instance with the time limit of
+\SI{1200}{s} used in the competitions 2017 and 2018.
+Figure~\ref{fig:progress-all} visualizes VBS performance on common
+benchmarks from 2015--2018 as cactus plot.  Figure~\ref{fig:progress}
+shows VBS performance on common benchmarks over pairs of consecutive
+years from 2014 to 2018.  Both plots show the wall-clock solving time
+per instance over all instances, sorted by solving time.
 %
@@
 
-For the \apptrack, we determine the VBS as the best performance
-in terms of number of correct \texttt{check-sat} answers within the time limit
-of \SI{2400}{s} (the time limit of the \apptrack in the competitions
-2015--2018).
-The total number of eligible \texttt{check-sat} queries (i.e., all queries with
-status sat or unsat up to the first query with status unknown) on
-common benchmarks from 2015--2018 is \num{30370517}.
-Figure~\ref{fig:progress-all-app} visualizes VBS performance on these
-benchmarks as a bar plot.
-In 2015, already 99.95\% of the eligible queries were answered correctly,
-which naturally does not leave a lot of room for improvement.
-In 2016, performance decreased by \num{185625} correct answers (0.61\%),
-which can be entirely attributed to a performance regression
-of Z3 on two benchmarks in the QF\_NIA division.
+For the \apptrack, we determine the VBS as the best performance in
+terms of number of correct \texttt{check-sat} answers within the time
+limit of \SI{2400}{s} (the time limit of the \apptrack in the
+competitions 2015--2018).  The total number of eligible
+\texttt{check-sat} queries (i.e., all queries with status sat or unsat
+up to the first query with status unknown) on common benchmarks from
+2015--2018 is \num{30370517}.  Figure~\ref{fig:progress-all-app}
+visualizes VBS performance on these benchmarks as a bar plot.  In
+2015, already 99.95\% of the eligible queries were answered correctly,
+which naturally does not leave a lot of room for improvement.  In
+2016, performance decreased by \num{185625} correct answers (0.61\%),
+which can be entirely attributed to a performance regression of Z3 on
+two benchmarks in the QF\_NIA division.
 
@@
 terms of reduction, i.e., the difference in the number of assertions
-of the input formula and the unsat core, within the time limit
-of \SI{2400}{s} (the time limit of the \ucoretrack in the competitions
-2016--2018).
-Figure~\ref{fig:progress-all-uc} visualizes VBS performance on the common
-benchmarks (\num{91455} total) from 2016--2018 as a bar plot.
-For \num{32377} of these benchmarks, extracting an unsat core is trivial since
-they contain only one single \texttt{assert} command.
-They are thus not considered in the bar plot, since their maximum
-possible reduction is trivially 0.
+of the input formula and the unsat core, within the time limit of
+\SI{2400}{s} (the time limit of the \ucoretrack in the competitions
+2016--2018).  Figure~\ref{fig:progress-all-uc} visualizes VBS
+performance on the common benchmarks (\num{91455} total) from
+2016--2018 as a bar plot.  For \num{32377} of these benchmarks,
+extracting an unsat core is trivial since they contain only one single
+\texttt{assert} command.  They are thus not considered in the bar
+plot, since their maximum possible reduction is trivially 0.
 
@@
 %%%%%%%%%%%%%%%%%%%%
+
 \subsection{Very Quick Solutions}
 
-Different application domains of SMT typically impose a wide range of time
-limits (from hours to seconds). In domains with very low time limits, these
-limits are, in the incremental case, usually even defined per incremental
-query.  With 20 and 40 minutes, the time limits used in the competition for all
-tracks in all four years were relatively long and the same for all benchmarks,
-thus agnostic to the application domain of a benchmark.  Hence, it is
-interesting to investigate how the results change if we consider a much shorter
-time limit.  Table~\ref{tab:results:24s} shows the results of virtually
-imposing a time limit of 24 seconds\footnote{This time limit is used for the
-new 24 seconds score introduced in SMT-COMP 2019 and was inspired by a use case
-at Amazon.} in the \maintrack.  As in the previous analysis, this highlights the
-different winners under this new scheme only. Here we see Alt-Ergo (AUFLIRA in
-2018) and STP (QF\_BV in 2016) winning a division for the first time in our
+Different application domains of SMT typically impose a wide range of
+time limits (from hours to seconds). In domains with very low time
+limits, these limits are, in the incremental case, usually even
+defined per incremental query.  With 20 and 40 minutes, the time
+limits used in the competition for all tracks in all four years were
+relatively long and the same for all benchmarks, thus agnostic to the
+application domain of a benchmark.  Hence, it is interesting to
+investigate how the results change if we consider a much shorter time
+limit.  Table~\ref{tab:results:24s} shows the results of virtually
+imposing a time limit of 24 seconds\footnote{This time limit is used
+  for the new 24 seconds score introduced in SMT-COMP 2019 and was
+  inspired by a use case at Amazon.} in the \maintrack.  As in the
+previous analysis, this highlights the different winners under this
+new scheme only. Here we see Alt-Ergo (AUFLIRA in 2018) and STP
+(QF\_BV in 2016) winning a division for the first time in our
 analysis, and Yices performing well.
 
-We only consider the \maintrack here, since for the other two tracks, the
-results are less interesting.  In the \apptrack, for such low time limits we
-are rather interested in a time limit per query, which we are unable to impose
-on the existing data since it is not possible to extract wallclock run time
-information per incremental query from the data of the competitions (as
-mentioned above, StarExec does not record this information).  In the
-\ucoretrack, the main focus is on producing small unsat-cores and solving times
-are of secondary interest.  Additionally, benchmarks with known unsatisfiable
-status from the \maintrack are used, and thus these results are already
-available from the \maintrack analysis in Table~\ref{tab:results:24s}
-(disregarding the fact that enabling unsat core production may slow down a
-solver, depending on the technique).
+We only consider the \maintrack here, since for the other two tracks,
+the results are less interesting.  In the \apptrack, for such low time
+limits we are rather interested in a time limit per query, which we
+are unable to impose on the existing data since it is not possible to
+extract wallclock run time information per incremental query from the
+data of the competitions (as mentioned above, StarExec does not record
+this information).  In the \ucoretrack, the main focus is on producing
+small unsat-cores and solving times are of secondary interest.
+Additionally, benchmarks with known unsatisfiable status from the
+\maintrack are used, and thus these results are already available from
+the \maintrack analysis in Table~\ref{tab:results:24s} (disregarding
+the fact that enabling unsat core production may slow down a solver,
+depending on the technique).
 
@@
 %%%%%%%%%%%%%%%%%
+
 \subsection{Do Families Matter?}
 
-In 2016 the \maintrack competition scoring was changed to weight the correctness score for benchmarks by the size of the family the benchmark belongs to.
-Here we ask what the winners would have been if this change had not been made.
-The answer to this question is given in Table~\ref{tab:results:total:solved}.
-Relatively few changes would have occurred.
-Unsurprisingly, the differences are in the larger and more structured divisions.
+In 2016 the \maintrack competition scoring was changed to weight the
+correctness score for benchmarks by the size of the family the
+benchmark belongs to. Here we ask what the winners would have been if
+this change had not been made. The answer to this question is given in
+Table~\ref{tab:results:total:solved}. Relatively few changes would
+have occurred. Unsurprisingly, the differences are in the larger and
+more structured divisions.
 
 Whilst producing these results we noticed that the description of what
-constitutes a family had been incorrectly interpreted by the scoring scripts in
-2016--2018. The scoring scripts interpreted the bottom most directory
-containing benchmarks in a logic as family, while the rules stated that the top
-most subdirectory in a logic is to be interpreted as family. After fixing this
-misinterpretation we note that only five division winners change---in 2018,
-division AUFLIRA should have been won by Vampire instead of CVC4; in 2016,
-AUFNIRA should have been won by CVC4 instead of Vampire; in 2016 and 2017,
-QF\_LIA should have been won by Yices instead of CVC4; and in 2018, QF\_NRA
-should have been won by CVC4 instead of Yices.
-Table~\ref{tab:results:total:top} shows the results in the Main Track when
-the top most subdirectory in a logic is interpreted as family in reference
-to the competition results in Table~\ref{tab:winners-main}, where the bottom
-most directory was interpreted as family.
-
-The combination of the small changes in winners and the lack of difference a misinterpretation of the notion of family made suggests that families do not have a significant impact on the competition.
+constitutes a family had been incorrectly interpreted by the scoring
+scripts in 2016--2018. The scoring scripts interpreted the bottom most
+directory containing benchmarks in a logic as family, while the rules
+stated that the top most subdirectory in a logic is to be interpreted
+as family. After fixing this misinterpretation we note that only five
+division winners change---in 2018, division AUFLIRA should have been
+won by Vampire instead of CVC4; in 2016, AUFNIRA should have been won
+by CVC4 instead of Vampire; in 2016 and 2017, QF\_LIA should have been
+won by Yices instead of CVC4; and in 2018, QF\_NRA should have been
+won by CVC4 instead of Yices.  Table~\ref{tab:results:total:top} shows
+the results in the Main Track when the top most subdirectory in a
+logic is interpreted as family in reference to the competition results
+in Table~\ref{tab:winners-main}, where the bottom most directory was
+interpreted as family.
+
+The combination of the small changes in winners and the lack of
+difference a misinterpretation of the notion of family made suggests
+that families do not have a significant impact on the competition.
 
 \input{table-winners-main-families}
+
 %%%%%%%%%%%%%%%%%
+
 \subsection{What Impact Did Adding Unknowns in the \maintrack Have?}
 
-Until 2016, only benchmarks with known status were used in the \maintrack. In
-2016, benchmarks with unknown status were evaluated separately, but not
-considered in the overall results of the track.  Since 2017, non-incremental
-benchmarks with unknown status were eligible for the \maintrack.
-Table~\ref{tab:results:unknowns} shows alternative winners for 2017 and 2018 if
-benchmarks with unknown status had not been included.
+Until 2016, only benchmarks with known status were used in the
+\maintrack. In 2016, benchmarks with unknown status were evaluated
+separately, but not considered in the overall results of the track.
+Since 2017, non-incremental benchmarks with unknown status were
+eligible for the \maintrack.  Table~\ref{tab:results:unknowns} shows
+alternative winners for 2017 and 2018 if benchmarks with unknown
+status had not been included.
 
 \input{table-winners-main-unknown}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 SMT-LIB benchmarks used in the competition increased from~\num{77352}
-in~2014~\cite{CDW14} to \num{342498} in 2018.  This is partly because new
-benchmarks were added to the SMT Library, but also because benchmarks
-with unknown status are now eligible for the competition, and because
-the competition now uses all eligible benchmarks (rather than a
-randomly selected subset).
-
-Since the re-introduction of the \ucoretrack in~2016, the
-competition again has three separate tracks.  This, together with new
-logics in the SMT Library, has brought the total number of competition
-divisions to 115 in~2018, up from just 40 divisions
-in~2014~\cite{CDW14}.  The number of job pairs increased from \num{339714}
-in~2014 to~\num{1776062} in 2018, and the total wall-clock time in~2018
+in~2014~\cite{CDW14} to \num{342498} in 2018.  This is partly because
+new benchmarks were added to the SMT Library, but also because
+benchmarks with unknown status are now eligible for the competition,
+and because the competition now uses all eligible benchmarks (rather
+than a randomly selected subset).
+
+Since the re-introduction of the \ucoretrack in~2016, the competition
+again has three separate tracks.  This, together with new logics in
+the SMT Library, has brought the total number of competition divisions
+to 115 in~2018, up from just 40 divisions in~2014~\cite{CDW14}.  The
+number of job pairs increased from \num{339714} in~2014
+to~\num{1776062} in 2018, and the total wall-clock time in~2018
 exceeded 7.6~years.  By these measures, the SMT Competition is one of

### 2019-08-31 2018/report/table-winners-main-families.tex
Minor
Remove 2015 column

@@
 \begin{table}
-  \caption{Alternative best solvers in the \maintrack if families were not considered in computing scores (i.e., the 2015 scoring system were used).}
+  \caption{Alternative best solvers in the \maintrack if families were not considered in computing scores (i.e., if the 2015 scoring system were used)}
   \label{tab:results:total:solved}
@@
 
-\begin{tabular}{r>{\columncolor{white}[.25em][.8em]}r@{\hskip .8em}|@{\hskip .5em}>{\columncolor{white}[.5em][.5em]}l>{\columncolor{white}[.5em][.8em]}r@{\hskip .8em}|@{\hskip .5em}>{\columncolor{white}[.5em][.5em]}l>{\columncolor{white}[.5em][.8em]}r@{\hskip .8em}|@{\hskip .5em}>{\columncolor{white}[.5em][.5em]}l>{\columncolor{white}[.5em][.8em]}r@{\hskip .8em}|@{\hskip .5em}>{\columncolor{white}[.5em][.5em]}l}
+\begin{tabular}{r>{\columncolor{white}[.5em][.8em]}r@{\hskip .8em}|@{\hskip .5em}>{\columncolor{white}[.5em][.5em]}l>{\columncolor{white}[.5em][.8em]}r@{\hskip .8em}|@{\hskip .5em}>{\columncolor{white}[.5em][.5em]}l>{\columncolor{white}[.5em][.8em]}r@{\hskip .8em}|@{\hskip .5em}>{\columncolor{white}[.5em][.5em]}l}
 \toprule
-Division & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{2015}              &                 \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{2016} &                      \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{2017} &                   \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{2018} \\
+Division &  \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{2016} &                      \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{2017} &                   \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{2018} \\
 \midrule
-AUFNIRA  &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\hspace*{5em}} &       \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4} &                          \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                       \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} \\
-BV       &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{}              &                     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &  \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{bool} Boolector [Z3]} &                       \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} \\
-QF\_BV    &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{}             &                     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                                     \cc{mink} MinkeyRink &  \hspace*{3em}       &                           \hspace*{3em}                & \cc{bool} Boolector \\
-QF\_FP    &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{}             &                     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                          \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &         \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4} \\
-QF\_IDL   &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{}             &                     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices [Z3]} &                       \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} \\
-QF\_LRA   &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{}             &                     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                          \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &  \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{spass} SPASS-SATT} \\
-QF\_NIA   &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{}             &                     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &          \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices} &       \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices} \\
-QF\_NRA   &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{}             &                     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                          \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &       \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices} \\
-UFIDL    &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{}              &  \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4 [Z3]} &                          \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                       \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} \\
+AUFNIRA   & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4} &                          \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                       \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} \\
+BV        & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &  \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{bool} Boolector [Z3]} &                       \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} \\
+QF\_BV    & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                                     \cc{mink} MinkeyRink &  \hspace*{3em}       &                           \hspace*{3em}                & \cc{bool} Boolector \\
+QF\_FP    & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                          \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &         \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4} \\
+QF\_IDL   & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices [Z3]} &                       \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} \\
+QF\_LRA   & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                          \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &  \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{spass} SPASS-SATT} \\
+QF\_NIA   & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &          \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices} &       \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices} \\
+QF\_NRA   & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                          \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &       \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices} \\
+UFIDL     & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4 [Z3]} &                          \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                       \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} \\
 \bottomrule

### 2019-08-31 2018/report/table-winners-main-families.tex
Remove 2015 column

@@
 \begin{table}
-  \caption{Alternative best solvers in the \maintrack if the notion of families were implemented as stated in the rules, i.e., top most directory instead of bottom most.}
+  \caption{Alternative best solvers in the \maintrack if the notion of families had been implemented as stated in the rules, i.e., top most directory instead of bottom most}
   \label{tab:results:total:top}
@@
 
-\begin{tabular}{r>{\columncolor{white}[.25em][.8em]}r@{\hskip .8em}|@{\hskip .5em}>{\columncolor{white}[.5em][.5em]}l>{\columncolor{white}[.5em][.8em]}r@{\hskip .8em}|@{\hskip .5em}>{\columncolor{white}[.5em][.5em]}l>{\columncolor{white}[.5em][.8em]}r@{\hskip .8em}|@{\hskip .5em}>{\columncolor{white}[.5em][.5em]}l>{\columncolor{white}[.5em][.8em]}r@{\hskip .8em}|@{\hskip .5em}>{\columncolor{white}[.5em][.5em]}l}
+\begin{tabular}{r>{\columncolor{white}[.5em][.8em]}r@{\hskip .8em}|@{\hskip .5em}>{\columncolor{white}[.5em][.5em]}l>{\columncolor{white}[.5em][.8em]}r@{\hskip .8em}|@{\hskip .5em}>{\columncolor{white}[.5em][.5em]}l>{\columncolor{white}[.5em][.8em]}r@{\hskip .8em}|@{\hskip .5em}>{\columncolor{white}[.5em][.5em]}l}
 \toprule
-Division & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{2015} &                        \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{2016} &                        \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{2017} &                    \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{2018} \\
+Division &                         \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{2016} &                        \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{2017} &                    \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{2018} \\
 \midrule
-  AUFLIRA  &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\hspace*{5em}} &                            \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                            \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &  \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{vamp} Vampire [Z3]} \\
-AUFNIRA  &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &              \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4} &                            \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                        \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} \\
-BV       &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                            \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{q3b} Q3B} &                        \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} \\
-QF\_IDL   &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                            \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &       \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices [Z3]} &   \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices [Z3]} \\
-QF\_LIA   &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &  \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices [MathSAT]} &  \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices [MathSAT]} &                        \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} \\
-QF\_NRA   &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                            \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                            \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4 [Z3]} \\
-UFBV     &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &              \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4} &                            \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                        \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} \\
-UFIDL    &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &         \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4 [Z3]} &                            \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                        \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} \\
-UFLIA    &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                            \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                            \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4 [Z3]} \\
-UFNIA    &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                            \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                            \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                                 \hspace*{3em}        & \cc{vamp} Vampire [Z3] \\
+AUFLIRA  &                             \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                            \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &  \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{vamp} Vampire [Z3]} \\
+AUFNIRA  &               \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4} &                            \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                        \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} \\
+BV       &                             \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{q3b} Q3B} &                        \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} \\
+QF\_IDL  &                             \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &       \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices [Z3]} &   \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices [Z3]} \\
+QF\_LIA  &   \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices [MathSAT]} &  \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices [MathSAT]} &                        \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} \\
+QF\_NRA  &                             \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                            \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4 [Z3]} \\
+UFBV     &               \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4} &                            \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                        \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} \\
+UFIDL    &          \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4 [Z3]} &                            \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                        \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} \\
+UFLIA    &                             \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                            \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4 [Z3]} \\
+UFNIA    &                             \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                            \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                                 \hspace*{3em}        & \cc{vamp} Vampire [Z3] \\
 \bottomrule

### 2019-08-31 2018/report/table-winners-main-unknown.tex
Report: Add table for family top.
Minor
Remove 2015 and 2016 columns

@@
 \begin{table}
-  \caption{Alternative best solvers in the \maintrack if benchmarks with unknown status had not bee included in 2017 onwards.}
+  \caption{Alternative best solvers in the \maintrack if benchmarks with unknown status had not been included in 2017 onwards}
   \label{tab:results:unknowns}
@@
     \renewcommand{\arraystretch}{1.01}%
-\begin{tabular}{r>{\columncolor{white}[.25em][.8em]}r@{\hskip .8em}|@{\hskip .5em}>{\columncolor{white}[.5em][.5em]}l>{\columncolor{white}[.5em][.8em]}r@{\hskip .8em}|@{\hskip .5em}>{\columncolor{white}[.5em][.5em]}l>{\columncolor{white}[.5em][.8em]}r@{\hskip .8em}|@{\hskip .5em}>{\columncolor{white}[.5em][.5em]}l>{\columncolor{white}[.5em][.8em]}r@{\hskip .8em}|@{\hskip .5em}>{\columncolor{white}[.5em][.5em]}l}
+\begin{tabular}{r>{\columncolor{white}[.5em][.8em]}r@{\hskip .8em}|@{\hskip .5em}>{\columncolor{white}[.5em][.5em]}l>{\columncolor{white}[.5em][.8em]}r@{\hskip .8em}|@{\hskip .5em}>{\columncolor{white}[.5em][.5em]}l}
 \toprule
-Division & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{2015} & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{2016} &                   \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{2017} &                 \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{2018} \\
+Division &                  \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{2017} &                 \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{2018} \\
 \midrule
-AUFLIRA  &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\hspace*{5em}} &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\hspace*{5em}} &                                 \cc{cvc4} CVC4 [Z3] &  \hspace*{3em}         &                     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} \\
-AUFNIRA  &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &         \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4} &                     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} \\
-BV       &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &           \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{q3b} Q3B} &  \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{bool} Boolector} \\
-LRA      &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &         \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4} &                     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} \\
-NRA      &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                       \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                                                   & \cc{vamp} Vampire [Z3] \\
-QF\_FP    &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                       \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &       \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4} \\
-QF\_NRA   &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &  \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices [Z3]} &                     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} \\
-UF       &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                                                            \cc{cvc4} CVC4 &  &                                                           & \cc{cvc4} CVC4 \\
-UFNIA    &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                       \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                                                     \cc{cvc4} CVC4 [Z3] &  \\
+AUFLIRA  &                                \cc{cvc4} CVC4 [Z3] &  \hspace*{3em}         &                     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} \\
+AUFNIRA  &        \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4} &                     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} \\
+BV       &          \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{q3b} Q3B} &  \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{bool} Boolector} \\
+LRA      &        \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4} &                     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} \\
+NRA      &                      \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                                                   & \cc{vamp} Vampire [Z3] \\
+QF\_FP   &                      \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &       \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4} \\
+QF\_NRA  & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices [Z3]} &                     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} \\
+UF       &                                                           \cc{cvc4} CVC4 &  &                                                           & \cc{cvc4} CVC4 \\
+UFNIA    &                      \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                                                     \cc{cvc4} CVC4 [Z3] &  \\
 \bottomrule

### 2019-08-31 2018/report/SMT-COMP.tex
Minor

@@
 multiple versions of a solver in case the number of solver submissions
-is too large given the computational resources, but in the past four
+is too large for the computational resources, but in the past four
 years, exercising this right was not necessary.

### 2019-08-31 2018/report/SMT-COMP.tex
Layout (avoid overfull hboxes)
Layout: increase floatpagefraction, \include -> \input, \% -> \percent

@@
 \renewcommand{\textfraction}{0.15}
-\renewcommand{\floatpagefraction}{0.7}
+\renewcommand{\floatpagefraction}{0.75}
 
@@
 to shrink.  From~2015 to~2018, the total number of benchmarks has
-increased by~68\,\%.  The largest benchmark in the 2018 release had a
-size of \SI{1041}{MB}; the total size of the release was \SI{91}{GB}.
+increased by~\SI{68}{\percent}.  The largest benchmark in the 2018
+release had a size of \SI{1041}{MB}; the total size of the release was
+\SI{91}{GB}.
 
@@
 SMT Competition from~2015 to~2018.  Over this period, the number has
-grown by~72\,\%, from~\num{1028615} job pairs in~2015 to~\num{1776062}
-job pairs in~2018.  (This is the number of unique solver/benchmark
-combinations that were part of the competition.  The number of job
-pairs that were actually run is even higher: test jobs and job pairs
-that had to be re-run, e.g., because of issues with the StarExec
-infrastructure, are not included.)  For comparison, the~2014
+grown by~\SI{72}{\percent}, from~\num{1028615} job pairs in~2015
+to~\num{1776062} job pairs in~2018.  (This is the number of unique
+solver/benchmark combinations that were part of the competition.  The
+number of job pairs that were actually run is even higher: test jobs
+and job pairs that had to be re-run, e.g., because of issues with the
+StarExec infrastructure, are not included.)  For comparison, the~2014
 competition only ran~\num{339714} job pairs~\cite{CDW14}.
@@
 the SMT solving approach used.  System descriptions are published on
-the competition website.  They were submitted for about 60\,\% of all
-solver versions since 2015.
+the competition website.  They were submitted for about
+\SI{60}{\percent} of all solver versions since 2015.
 
@@
 
-\include{table-participants}
+\input{table-participants}
 
@@
 has a positive expected score if the probability that a soundness bug
-in the solver will be triggered is below~$20\,\%$.
+in the solver will be triggered is below~\SI{20}{\percent}.
 
@@
 
-\include{table-winners-main}
-
-\include{table-winners-application}
-
-\include{table-winners-unsat-core}
+\input{table-winners-main}
+
+\input{table-winners-application}
+
+\input{table-winners-unsat-core}
 
@@
 \item the solvers that won the QF\_BV division in the \maintrack
-  (Boolector and MinkeyRink; see Table~\ref{tab:winners-main}),
+  (Boolector and Minkey\-Rink; see Table~\ref{tab:winners-main}),
 \item the solver that won the most competitive divisions in the
@@
     \caption{2014 vs.~2015}
-  \end{subfigure}
+  \end{subfigure}%
   \begin{subfigure}[t]{0.5\textwidth}
@@
     \caption{2016 vs.~2017}
-  \end{subfigure}
+  \end{subfigure}%
   \begin{subfigure}[t]{0.5\textwidth}
@@
 The number of solved instances on these sets of common benchmarks
-increased from 2014 to 2015 by 0.1\%, from 2016 to 2017 by 3.9\%, and
-from 2017 to 2018 by 0.3\%.  Interestingly, it decreased from 2015 to
-2016 by 3.5\%.  This is mainly due to the fact that, in 2015, more
-than \num{5600} benchmarks of division QF\_FP were solved by one of
-the two participating configurations of Z3 but by no other solver, and
-in~2016 Z3 did not participate in this division.
+increased from 2014 to 2015 by \SI{0.1}{\percent}, from 2016 to 2017
+by \SI{3.9}{\percent}, and from 2017 to 2018 by \SI{0.3}{\percent}.
+Interestingly, it decreased from 2015 to 2016 by \SI{3.5}{\percent}.
+This is mainly due to the fact that, in 2015, more than \num{5600}
+benchmarks of division QF\_FP were solved by one of the two
+participating configurations of Z3 but by no other solver, and in~2016
+Z3 did not participate in this division.
 
@@
 visualizes VBS performance on these benchmarks as a bar plot.  In
-2015, already 99.95\% of the eligible queries were answered correctly,
-which naturally does not leave a lot of room for improvement.  In
-2016, performance decreased by \num{185625} correct answers (0.61\%),
-which can be entirely attributed to a performance regression of Z3 on
-two benchmarks in the QF\_NIA division.
+2015, already \SI{99.95}{\percent} of the eligible queries were
+answered correctly, which naturally does not leave a lot of room for
+improvement.  In 2016, performance decreased by \num{185625} correct
+answers (\SI{0.61}{\percent}), which can be entirely attributed to a
+performance regression of Z3 on two benchmarks in the QF\_NIA
+division.
 

### 2019-09-02 2018/report/SMT-COMP.tex
Fix the position of footnote 2
Giles changes in conclusion

@@
 \end{table}
-\footnotetext{This was a distinct version of CVC4 that was designated as experimental.}
 
@@
 with unknown status.
+
+% manually placed here so that it ends up on the correct page
+\footnotetext{This was a distinct version of CVC4 that was designated as experimental.}
 
@@
 
-Preparations for the 2019 iteration of the competition are underway and a number of changes have already been decided. These include
-
+At the time of writing, the 2019 iteration of the competition has just come to a close.
+It was too late to be included in this report but certain changes were made, partly influenced by the writing of this report.
+The three main changes were:
 \begin{itemize}
-  \item the introduction of new \emph{additional scores} for
+    \item \emph{Additional Scores.} This report made it clear that simply looking at the number of problems solved was a simplified view.
+In 2019 the competition introduced new \emph{additional scores} for
     satisfiable/unsatisfiable benchmarks and benchmarks solved within 24
-    seconds in the \maintrack,
+    seconds in the \maintrack.
+Organising results by satisfiability is not new.
+The SAT competition previously split satisfiable and unsatisfiable benchmarks into separate tracks, but merged them completely from 2016.
+The CASC competition separates \emph{theorems} and \emph{non-theorems} for most tracks.
+However, other competitions do not tend to look at short time limits (CASC had the SLH division in 2017).
+
+  \item \emph{Benchmarks.}  Partly to combat the growing size of SMT-LIB, and partly to inject more competition-like variability and focus into the results, in 2019 the competition removed \emph{non-competitive divisions} and then filtered
+    benchmarks to exclude those seen as \emph{trivial} (taken as those solved
+    by all competitors in the previous competition in less than 1 second).
+This brings it closer to the CASC competition where a small subset of problems are chosen based on difficultly, although there was no inclusion of a difficultly measure in benchmark selection beyond the initial filtering.
+The SAT competition takes a different approach to benchmark selection with a \emph{bring your own benchmark} approach.
+
+\item \emph{Competition-Wide Scoring.} Motivated by the need to avoid competition-wide scoring becoming overly focussed on the \emph{breadth} of a solver, in 2019 the competition replaced the notion of \emph{competition-wide scoring} with awards that do not attempt to compare divisions.
+Two awards were introduced -- the \emph{Largest Contribution} award looked at the contribution a solver made to the virtual best solver, and the \emph{Biggest Lead} award measured the distance between the winner and second place.
+No other competition (that we are aware of) attempts to rank solvers across multiple areas in this way.
+However, the CASC competition does have a notion of \emph{State of the Art Contribution}, similar to the largest contribution measure.
+
+\end{itemize}
+Other changes include
+\begin{itemize}
+
 	\item the inclusion of {\tt check-sat} commands with unknown status in
   the \apptrack,
-  \item the removal of \emph{non-competitive divisions} and the filtering of
-    benchmarks to exclude those seen as \emph{trivial} (taken as those solved
-    by all competitors in the previous competition in less than 1 second),
+
   \item the introduction of a new experimental \emph{model validation track}
@@
   \item the introduction of a new \emph{industrial challenge track} consisting
-    of unsolved benchmarks submitted specifically for the track,
-  \item the replacement of the notion of \emph{competition-wide scoring} with
-    awards that do not attempt to compare divisions.
+    of unsolved benchmarks submitted specifically for the track.
 \end{itemize}

### 2019-09-02 2018/report/SMT-COMP.tex
Minor

@@
     \vspace{-5ex}
-    \caption{VBS in terms of correct \texttt{check-sat} answers (out
-      of \num{30370517} total) within a time limit of \SI{2400}{s} on
-      common benchmarks 2015--2018 of all divisions in the \apptrack.}
+    \caption{VBS in terms of correct \texttt{check-\allowbreak sat}
+      answers (out of \num{30370517} total) within a time limit of
+      \SI{2400}{s} on common benchmarks 2015--2018 of all divisions in
+      the \apptrack.}
     \label{fig:progress-all-app}
@@
 \paragraph{The Next Competition}
-
-At the time of writing, the 2019 iteration of the competition has just come to a close.
-It was too late to be included in this report but certain changes were made, partly influenced by the writing of this report.
-The three main changes were:
+%
+At the time of writing, the 2019 iteration of the competition has just
+come to a close.  It was too late to be included in this report but
+certain changes were made, partly influenced by the writing of this
+report.  The three main changes were:
 \begin{itemize}
-    \item \emph{Additional Scores.} This report made it clear that simply looking at the number of problems solved was a simplified view.
-In 2019 the competition introduced new \emph{additional scores} for
+\item \emph{Additional Scores.}  This report made it clear that simply
+  looking at the number of problems solved was a simplified view.  In
+  2019 the competition introduced new \emph{additional scores} for
   satisfiable/unsatisfiable benchmarks and benchmarks solved within 24
-    seconds in the \maintrack.
-Organising results by satisfiability is not new.
-The SAT competition previously split satisfiable and unsatisfiable benchmarks into separate tracks, but merged them completely from 2016.
-The CASC competition separates \emph{theorems} and \emph{non-theorems} for most tracks.
-However, other competitions do not tend to look at short time limits (CASC had the SLH division in 2017).
-
-  \item \emph{Benchmarks.}  Partly to combat the growing size of SMT-LIB, and partly to inject more competition-like variability and focus into the results, in 2019 the competition removed \emph{non-competitive divisions} and then filtered
-    benchmarks to exclude those seen as \emph{trivial} (taken as those solved
-    by all competitors in the previous competition in less than 1 second).
-This brings it closer to the CASC competition where a small subset of problems are chosen based on difficultly, although there was no inclusion of a difficultly measure in benchmark selection beyond the initial filtering.
-The SAT competition takes a different approach to benchmark selection with a \emph{bring your own benchmark} approach.
-
-\item \emph{Competition-Wide Scoring.} Motivated by the need to avoid competition-wide scoring becoming overly focussed on the \emph{breadth} of a solver, in 2019 the competition replaced the notion of \emph{competition-wide scoring} with awards that do not attempt to compare divisions.
-Two awards were introduced -- the \emph{Largest Contribution} award looked at the contribution a solver made to the virtual best solver, and the \emph{Biggest Lead} award measured the distance between the winner and second place.
-No other competition (that we are aware of) attempts to rank solvers across multiple areas in this way.
-However, the CASC competition does have a notion of \emph{State of the Art Contribution}, similar to the largest contribution measure.
-
+  seconds in the \maintrack.  Organizing results by satisfiability is
+  not new.  The SAT competition previously split satisfiable and
+  unsatisfiable benchmarks into separate tracks, but merged them
+  completely from 2016.  The CASC competition separates
+  \emph{theorems} and \emph{non-theorems} for most tracks.  However,
+  other competitions do not tend to look at short time limits (CASC
+  had the SLH division in 2017).
+\item \emph{Benchmarks.}  Partly to combat the growing size of
+  SMT-LIB, and partly to inject more competition-like variability and
+  focus into the results, in 2019 the competition removed
+  \emph{non-competitive divisions} and then filtered benchmarks to
+  exclude those seen as \emph{trivial} (taken as those solved by all
+  competitors in the previous competition in less than 1 second).
+  This brings it closer to the CASC competition where a small subset
+  of problems are chosen based on difficulty, although there was no
+  inclusion of a difficulty measure in benchmark selection beyond the
+  initial filtering.  The SAT competition takes a different approach
+  to benchmark selection with a \emph{bring your own benchmark}
+  approach.
+\item \emph{Competition-Wide Scoring.}  Motivated by the need to avoid
+  competition-wide scoring becoming overly focused on the
+  \emph{breadth} of a solver, in 2019 the competition replaced the
+  notion of \emph{competition-wide scoring} with awards that do not
+  attempt to compare divisions.  Two awards were introduced---the
+  \emph{Largest Contribution} award looked at the contribution a
+  solver made to the virtual best solver, and the \emph{Biggest Lead}
+  award measured the distance between the winner and second place. No
+  other competition (that we are aware of) attempts to rank solvers
+  across multiple areas in this way.  However, the CASC competition
+  does have a notion of \emph{State of the Art Contribution}, similar
+  to the largest contribution measure.
 \end{itemize}
-Other changes include
+Other changes included
 \begin{itemize}
-
 \item the inclusion of {\tt check-sat} commands with unknown status in
   the \apptrack,
-
-  \item the introduction of a new experimental \emph{model validation track}
-    with a single QF\_BV division where the models produced by solvers are
-    checked,
-  \item the introduction of a new \emph{industrial challenge track} consisting
-    of unsolved benchmarks submitted specifically for the track.
+\item the introduction of a new experimental \emph{model validation
+  track} with a single QF\_BV division where the models produced by
+  solvers are checked,
+\item the introduction of a new \emph{industrial challenge track}
+  consisting of unsolved benchmarks submitted specifically for the
+  track.
 \end{itemize}
@@
 \paragraph{The Future}
-
-Looking to the future of the competition, it is clear that further development should be undertaken with care,
-keeping in mind that major changes require not just the competition
-organizers, but also participants to adapt.
+%
+Looking to the future of the competition, it is clear that further
+development should be undertaken with care, keeping in mind that major
+changes require not just the competition organizers, but also
+participants to adapt.
 

### 2020-04-01 rules/rules20.tex
Preliminary rules for 2020 (work in progress).

--- 2019-07-04 rules/rules19.tex
@@
 \author{%
-Liana Hadarean \\
-Amazon \\
-USA \\
-{\small\href{mailto:hadarean@amazon.com}{\texttt{hadarean@amazon.com}}}\\
+\todo{check}
+Haniel Barbosa\\
+Universidade Federal de Minas Gerais\\
+Brazil\\
+{\small\href{mailto:hbarbosa@dcc.ufmg.br}{\texttt{hbarbosa@dcc.ufmg.br}}}\\
 \and
-Antti Hyvarinen \\
+Jochen Hoenicke\\
+Universit\"at Freiburg\\
+Germany
+{\small\href{mailto:hoenicke@informatik.uni-freiburg.de}{\texttt{hoenicke@informatik.uni-freiburg.de}}}\\
+\and
+Antti Hyvarinen (chair)\\
 Universita della Svizzera italiana \\
@@
 {\small\href{mailto:antti.hyvaerinen@usi.ch}{\texttt{antti.hyvaerinen@usi.ch}}} \\
-\and
-Aina Niemetz \\
-Stanford University\\
-USA\\
-{\small\href{mailto:niemetz@cs.stanford.edu}{\texttt{niemetz@cs.stanford.edu}}}\\
-\and
-Giles Reger \\
-University of Manchester \\
-UK \\
-{\small\href{mailto:giles.reger@manchester.ac.uk}{\texttt{giles.reger@manchester.ac.uk}}} \\
-\\
 }
@@
   scrambler) are made available.  Benchmark libraries are frozen.
-\item[May~19] Deadline for first versions of solvers (for all tracks),
+\item[May~4] Deadline for first versions of solvers (for all tracks),
   including information about which tracks and divisions are being
   entered, and magic numbers for benchmark scrambling.
-\item[June~2] Deadline for final versions of solvers, including
+\item[May~18] Deadline for final versions of solvers, including
   system descriptions.
-\item[June~3] Opening value of NYSE Composite Index used to compute
-  random seed for competition tools.
-\item[July~7/8] SMT Workshop; end of competition, presentation of
+\item[May~19] Opening value of NYSE Composite Index used to compute
+  random seed for competition tools. \todo{Okay?}
+\item[July~5/6] SMT Workshop; end of competition, presentation of
   results.
@@
 
-SMT-COMP~2019 is part of the SMT Workshop~2019
-(\url{http://smt2019.galois.com/}),
-which is affiliated with SAT~2019 (\url{http://sat2019.tecnico.ulisboa.pt/}).
+SMT-COMP~2020 is part of the SMT Workshop~2020
+(\url{http://smt-workshop.cs.uiowa.edu/2020/index.shtml}),
+which is affiliated with IJCAR~2020 (\url{https://ijcar2020.org/}).
 The SMT Workshop will include a block of time to present the results of the
@@
 
-SMT-COMP 2019 will have five tracks: the \maintrack (previously: Main Track),
-the \inctrack (previously: Application Track), the \ucoretrack,
-the (new) \challtrack, and the (new)
-\mvaltrack.
+SMT-COMP 2020 will have five tracks: the \maintrack (before 2019: Main Track),
+the \inctrack (before 2019: Application Track), the \ucoretrack,
+the \challtrack, and the \mvaltrack.
 %
@@
   Sylvain Conchon, David D{\'e}harbe, Morgan Deters, Alberto Griggio,
+  Liana Hadarean,
   Matthias Heizmann, Aina Niemetz, Albert Oliveras, Giles Reger, Aaron Stump,
 	and Tjark Weber.}  describes the rules and competition procedures for
-SMT-COMP~2019.
+SMT-COMP~2020.
 The principal changes from the previous competition rules are the following:
 \begin{itemize}
+  \item {\bf Portfolio Solvers are Forbidden.} \todo{check}
+    This year we explicitly forbid the submission of so-called
+    portfolio solvers as competition entries.  We acknowledge that
+    judging what constitutes a portfolio SMT solver is difficult.
+    However, we are not the first in history to face a similar
+    challenge, and plan to apply an equally historical approach where
+    we write down a ``law'', act as its ``judges'', and have a few
+    ``precedents''.
+
+    Here we define a portfolio solver as ``a solver using a combination of
+    two or more sub-solvers, developed by different groups of authors, on
+    the same component or abstraction of the input problem.'' For example, a
+    solver using one subsolver to solve the ground abstraction of a
+    quantified problem is allowed, while a solver using two or more
+    subsolvers from different groups of authors is not.
+    \todo{Something about  hybrid solvers?}
+
+    \todo{rationale}
+
   \item {\bf Mandatory System Descriptions.}
@@
 
+  \item {\bf Limit the Number of Solvers.} \todo{NEW}
+    This year solver development teams may only submit more than one
+    entry if they are substantially different.  A justification must
+    be provided for the difference.  We strongly encourage the teams
+    to keep the number of solvers per team per category at at most
+    two.
+
+    \rationale{The organizers wishes to keep the total run-time of the
+      competition small, in case of unforeseen problems that require
+      to rerun the whole competition.  The idea in allowing up to two
+      submissions is to encourage the development of new, experimental
+      techniques by allowing an “alternative solver” to be submitted
+      while keeping the competition manageable.}
+
   \item {\bf Naming Convention for Derived Tools.}
@@
 
-  \item {\bf Renaming of Tracks.} This year, the track previously known as
-    `Main Track` will be renamed to \emph{\maintrack}, and the previous
-    `Application Track' will be renamed to \emph{\inctrack}.
-    \rationale{We believe the current names are misleading, as the
-    previous `Main Track' also contains problems coming from applications.
-    Additionally, having it called `Main' de-emphasizes the importance of the
-    other tracks and use cases of SMT.}
-
-  \item {\bf Incremental Track.}
-    In previous years, benchmarks were not eligible for the \inctrack
-    if their first \akey{check-sat} command had unknown status.  Similarly, the
-    trace executor used to send commands from the benchmark to the solver's
-    standard input channel stopped execution at the first \akey{check-sat}
-    command with unknown status. This year, benchmarks whose first
-    \akey{check-sat} command has unknown status are eligible for the
-    \inctrack and trace execution is only stopped before the solver
-    completes a benchmark if the execution runs into the time limit.
-    \rationale{The previous limitations were imposed by the trace
-    executor, which now has been extended to support executing solvers on
-    benchmarks beyond \akey{check-sat} commands with unknown status.}
+  \item {\bf Combine stdout and stderr.}
+    This year, output to the standard error channel is not ignored, but
+    treated the same as output to the standard output channel.
+
+    \rationale{Due to limitations of starexec, the standard error channel
+      and standard output channel are not separated.  The previous year the
+      organizers had to work around the limitation by wrapping the submitted
+      solvers in a script that ignored stderr.  By changing the rule we avoid
+      that the organizers have to change the submitted solvers.}
+
+%  \item {\bf Incremental Track.}
+%    In previous years, benchmarks were not eligible for the \inctrack
+%    if their first \akey{check-sat} command had unknown status.  Similarly, the
+%    trace executor used to send commands from the benchmark to the solver's
+%    standard input channel stopped execution at the first \akey{check-sat}
+%    command with unknown status. This year, benchmarks whose first
+%    \akey{check-sat} command has unknown status are eligible for the
+%    \inctrack and trace execution is only stopped before the solver
+%    completes a benchmark if the execution runs into the time limit.
+%    \rationale{The previous limitations were imposed by the trace
+%    executor, which now has been extended to support executing solvers on
+%    benchmarks beyond \akey{check-sat} commands with unknown status.}
 
@@
   \item {\bf Time Limit.} The time limit per solver/benchmark pair is
-    anticipated to be at most 40 minutes in the \maintrack, \inctrack,
+    anticipated to be at most 20 minutes in the \maintrack, \inctrack,
     \ucoretrack and \mvaltrack.  For the \challtrack, it is anticipated to be
     at most 720 (12 hours) minutes.
-    \rationale{In 2017 and 2018, the time limit for the Main Track was
-    reduced to 20 minutes (down from 40 minutes in earlier years) to cope with
-    the inclusion of a large number of benchmarks with unknown status.  This
-    year, the reduced number of benchmarks selected per division allows us to
-    increase the time limit back to 40 minutes for the \maintrack.  For the
-    \challtrack, 12 hours seem to be a reasonable compromise for the
+    \rationale{The time limit for the Main Track is
+    reduced to 20 minutes (down from 40 minutes in earlier years) \todo{rationale}.
+    For the \challtrack, 12 hours seem to be a reasonable compromise for the
     expected number of participants and benchmarks submitted to this track.}
 
-  \item {\bf Benchmark Selection.} Since 2015, the competition evaluated all
+  \item {\bf Benchmark Selection.} \todo{update}
+    Since 2015, the competition evaluated all
     solvers on all eligible benchmarks in SMT-LIB.  This year, we will
@@
 
+\todo{Portfolio Tool}
+
 \header{Wrapper Tool.}
@@
 \begin{center}
-  \url{https://forms.gle/y8xB4C8TB2WkdKPx9}
+  \todo{\url{https://forms.gle/todo}}
 \end{center}
@@
 
-\header{Multiple versions.}
+\header{Multiple versions.}\todo{check}
 %
 The intent of the organizers is to promote as wide a comparison among
-solvers and solver options as possible.  However, if the number of
-solver submissions is too large for the computational resources
-available to the competition, the organizers reserve the right not to
-accept multiple versions of solvers from the same solver team.
+solvers and solver options as possible.  However, to keep the number of
+solver submissions low, each team should only provide multiple solvers,
+if they are  substantially different.  A justification must be provided
+for the difference.  We strongly encourage the teams to keep the number
+of solvers per team per category at at most two.  The idea in allowing
+up to two submissions is to encourage the development of new,
+experimental techniques by allowing an ``alternative solver'' to be
+submitted while keeping the competition manageable.
 
@@
 
-\header{Attendance.}
+\header{Attendance.}\todo{fix this!}
 %
@@
 the above web form (accompanying information) until the end of
-{\bf May~19, 2019} anywhere on earth.
+{\bf May~4, 2020} anywhere on earth.
 After this date \emph{no new entrants} will be accepted.
 However, updates to existing entrants on StarExec
-will be accepted until the end of {\bf June~2, 2019} anywhere on earth.
+will be accepted until the end of {\bf May~18, 2020} anywhere on earth.
 
@@
 The bulk of the computation will take place during the weeks leading
-up to SMT 2019.  Intermediate results will be regularly posted to the
+up to SMT 2020.  Intermediate results will be regularly posted to the
 SMT-COMP website as the competition runs.
@@
 
-\pagebreak
 \header{Time and Memory Limits.}
@@
 \texttt{unknown} to indicate that it cannot determine satisfiability of the
-formula.
+formula.  Note that output sent to the standard error channel is treated the
+same way as output sent to the standard output channel. \todo{okay?}
 
@@
 \header{Time Limit.}
-This track will use a wall-clock time limit of 40 minutes per solver/benchmark
-pair.
+This track will use a wall-clock time limit of 20 minutes per solver/benchmark
+pair.\todo{we said 20 minutes, right?}
 
@@
 will incrementally send commands to the standard input channel of the
-solver and read responses from the standard output channel of the
+solver and read responses from both the standard output channel of the
 solver.  The commands will be taken from an SMT-LIB benchmark script
@@
 other commands.
+Solver must not write anything to the standard error channel. \todo{okay?}
 
@@
 \header{Time Limit.}
-This track will use a wall-clock time limit of 40 minutes per solver/benchmark
-pair.
+This track will use a wall-clock time limit of 20 minutes per solver/benchmark
+pair.\todo{20 min}
 
@@
 
-\header{Benchmark Selection.}
+\header{Benchmark Selection.}\todo{fixme}
 This track will run on challenging industrial benchmarks provided by the
@@
 benchmarks dedicated to this track, which consist of both incremental and
-single query benchmarks in the logics QF\_BV, QF\_ABV and QF\_AUFBV. The
+single query benchmarks in the logics \todo{QF\_BV, QF\_ABV and QF\_AUFBV}. The
 complete list of benchmarks along with instructions on how to access them will
@@
 \header{Time Limit.}
-This track will use a wall-clock time limit of 40 minutes per solver/benchmark
+This track will use a wall-clock time limit of 20 minutes per solver/benchmark
 pair. The time limit for checking unsatisfiable cores is yet to be determined,
@@
 \header{Benchmark Selection.}
-This experimental track only has one division, QF\_BV. It will run on a
-selection of non-incremental benchmarks with status \texttt{sat} from logic
-QF\_BV (as described on page~\pageref{benchmark-selection}).
+This experimental track only has the divisions
+\todo{QF\_BV, QF\_IDL, QF\_RDL, QF\_LIA, QF\_LRA, QF\_LIRA}. It will run on a
+selection of non-incremental benchmarks with status \texttt{sat} from these
+logics (as described on page~\pageref{benchmark-selection}).
 
@@
 \header{Time Limit.}
-This track will use a wall-clock time limit of 40 minutes per solver/benchmark
+This track will use a wall-clock time limit of 20 minutes per solver/benchmark
 pair. The time limit for checking the satisfying assignment is yet to be
@@
 \header{New benchmarks.}
-The deadline for submission of new benchmarks is {\bf March~1, 2019}.
+The deadline for submission of new benchmarks is {\bf March~1, 2020}.
 The organizers, in collaboration with the SMT-LIB maintainers, will be
-checking and curating these until {\bf May~1, 2019}.  The SMT-LIB
+checking and curating these until {\bf April~20, 2020}~\todo{check date}.  The SMT-LIB
 maintainers intend to make a new release of the benchmark library
@@
   Let $n$ be the number of benchmarks in an SMT-LIB logic, then
+  \todo{How do we cap?}
   \begin{enumerate}
@@
 entrants other than the organizers'.  Additionally, the integer part
-of the opening value of the New York Stock Exchange Composite Index on
+of \todo{one hundred times} the opening value of the New York Stock Exchange Composite Index on
 the first day the exchange is open on or after the date specified in
 the timeline (Section~\ref{sec:important}) will be added to the other
-seeding values.  This helps provide transparency, by guaranteeing that
+seeding values. \todo{Should we provide more randomness by multiplying it with 100?  It has two or three trailing digits}  This helps provide transparency, by guaranteeing that
 the organizers cannot manipulate the seed in favor of or against any
@@
 and excluded from the ranking.
-If the number of sound competitive solvers~$S$ in a division $D$ is $|S| < 2$, 
+If the number of sound competitive solvers~$S$ in a division $D$ is $|S| \leq 2$, 
 the division is excluded from the ranking.
@@
 \]
-where the minimum of an empty set is 2400 seconds
+where the minimum of an empty set is 1200 seconds \todo{changed from 2400 to 1200, correct?}
 (no solver was able to solve the benchmark).
@@
 
-SMT-COMP 2019 is organized under the direction of the SMT Steering
+SMT-COMP 2020 is organized under the direction of the SMT Steering
 Committee. The organizing team is
 %
+\todo{check your affiliations}
 \begin{itemize}
 \setlength{\itemsep}{0pt}
-\item
-		Liana Hadarean~-- Amazon, USA (co-organizer)
+\item Haniel Barbosa~-- Universidade Federal de Minas Gerais, Brazil
 \item \href{http://www.inf.usi.ch/postdoc/hyvarinen/}{Antti Hyvarinen}~--
-		Universita della Svizzera italiana, Switzerland (co-organizer)
-\item
-  \href{http://cs.stanford.edu/people/niemetz}{Aina
-    Niemetz}~-- Stanford University, USA (co-chair)
-\item \href{http://www.cs.man.ac.uk/~regerg/}{Giles Reger}~--
-  University of Manchester, UK (co-chair)
+		Universita della Svizzera italiana, Switzerland (chair)
+\item Jochen Hoenicke~-- Universit\"at Freiburg, Germany
 \end{itemize}
@@
 Pascal Fontaine, Aina Niemetz and Mathias Preiner are maintaining the SMT-LIB
-benchmark library.
+benchmark library. \todo{check if still current}
 The competition uses the
@@
 %
-Liana Hadarean was part of the developing team of the SMT solver
-CVC4~\cite{cvc4} and is currently not associated with any group
-creating or submitting solvers.
+\todo{add disclosure}
 Antti Hyvarinen is part of the developing team of the SMT solver
 OpenSMT~\cite{opensmt2}.
-Aina Niemetz is part of the developing teams of the SMT solvers
-Boolector~\cite{boolector}
-and CVC4~\cite{cvc4}.
-Giles Reger is associated with the group
-producing the Vampire system~\cite{vampire}.
+Jochen Hoenicke is part of the developing teams of the SMT solver
+SMTInterpol~\cite{smtinterpol}.
 

### 2020-04-01 rules/rules20.tex
some updates, especially new rules

@@
 \author{%
-\todo{check}
 Haniel Barbosa\\
@@
 Universit\"at Freiburg\\
-Germany
+Germany\\
 {\small\href{mailto:hoenicke@informatik.uni-freiburg.de}{\texttt{hoenicke@informatik.uni-freiburg.de}}}\\
@@
 \item[March~1] Deadline for new benchmark contributions.
-\item[May~1] Final versions of competition tools (e.g., benchmark
+\item[April~20] Final versions of competition tools (e.g., benchmark
   scrambler) are made available.  Benchmark libraries are frozen.
@@
 \begin{itemize}
-  \item {\bf Portfolio Solvers are Forbidden.} \todo{check}
+  \item {\bf Portfolio Solvers are Forbidden.}
     This year we explicitly forbid the submission of so-called
@@
     ``precedents''.
-
     Here we define a portfolio solver as ``a solver using a combination of
@@
     subsolvers from different groups of authors is not.
-    \todo{Something about  hybrid solvers?}
-
-    \todo{rationale}
-
-  \item {\bf Mandatory System Descriptions.}
-    SMT-COMP entrants are now required to provide a short (1–2 pages)
-    description of the system.
-    \rationale{The main incentive for this
-    change is twofold.  First, we want to improve transparency when submitted
-    solvers are wrapper or derived tools according to the rules of the
-    competition.  Second, we want to encourage documenting technical
-    improvements that lead to the current results.}
-
-  \item {\bf Limit the Number of Solvers.} \todo{NEW}
+    \rationale{The goal of the competition is to evaluate and improve
+      the state of the art of SMT solving. By just combining existing
+      solvers and running them in parallel it is possible to win the
+      competition without contributing anything new.}
+
+  \item {\bf Limit the Number of Solvers.}
     This year solver development teams may only submit more than one
@@
     two.
-
+%
     \rationale{The organizers wishes to keep the total run-time of the
@@
       submissions is to encourage the development of new, experimental
-      techniques by allowing an “alternative solver” to be submitted
+      techniques by allowing an ``alternative solver'' to be submitted
       while keeping the competition manageable.}
-
-  \item {\bf Naming Convention for Derived Tools.}
-    This year, we require that a derived tool (a tool based on and extending
-    another SMT solver) should follow the \emph{naming convention} {[name of
-    base solver]-[my solver name]}.
-    \rationale{Give credit where credit is due.}
 
@@
     treated the same as output to the standard output channel.
-
+    Solvers should not write anything to the standard error channel.
+%
     \rationale{Due to limitations of starexec, the standard error channel
-      and standard output channel are not separated.  The previous year the
+      and standard output channel are not separated.  In the previous year, the
       organizers had to work around the limitation by wrapping the submitted
@@
 
-%  \item {\bf Incremental Track.}
-%    In previous years, benchmarks were not eligible for the \inctrack
-%    if their first \akey{check-sat} command had unknown status.  Similarly, the
-%    trace executor used to send commands from the benchmark to the solver's
-%    standard input channel stopped execution at the first \akey{check-sat}
-%    command with unknown status. This year, benchmarks whose first
-%    \akey{check-sat} command has unknown status are eligible for the
-%    \inctrack and trace execution is only stopped before the solver
-%    completes a benchmark if the execution runs into the time limit.
-%    \rationale{The previous limitations were imposed by the trace
-%    executor, which now has been extended to support executing solvers on
-%    benchmarks beyond \akey{check-sat} commands with unknown status.}
-
-  \item {\bf New \mvaltrack for QF\_BV.}
-    This year, we introduce a new experimental \mvaltrack for the QF\_BV logic.
-    The benchmarks for this track will include all eligible \emph{non-incremental}
-    QF\_BV benchmarks with known satisfiable status in SMT-LIB.
-    Participating solvers are required to support the \akey{get-model} command.
-    \rationale{In many SMT applications, model generation is an essential
-    feature.  Previously, none of the SMT-COMP tracks required model
-    generation. One of the challenges is that the model format is not
-    consistent across different solvers. While imposing a standard over all
-    logics is challenging, there are several logics (e.g., QF\_BV) where it is
-    straightforward.  In the future we hope to expand this track to other
-    logics as a way of pushing for model standardization.  Since the QF\_BV
-    division was the one with the largest number of participants in previous
-    years,  we hope for a high number of participants in this track.  }
-
-  \item {\bf New \challtrack.}
-    This year, we introduce a new \challtrack.  This track will contain
-    new challenging SMT-LIB benchmarks (with an emphasis on industrial
-    applications) that are either unsolved or unsolved within some reasonable
-    time limit, as indicated by the benchmark submitters.  We will also include
-    benchmarks nominated by the community as challenging and of interest. In
-    this track, solvers will run with a significantly longer time limit.
-    \rationale{ Different application domains require different time limits.
-    For example software verification traditionally requires much lower time
-    limits, compared to hardware verification.  To reward solvers optimized for
-    different use cases, we propose this new track and a new score for
-    benchmarks solved within a very low time limit (see item ``New Scores in
-    the \maintrack''). See Section~\ref{sec:exec:industry-challenge} for the
-    logics included in the \challtrack for this year. }
+%  \item {\bf The \mvaltrack is extended to other logics.}
+%    This year, we introduce a new experimental \mvaltrack for the logics QF\_IDL, QF\_RDL, QF\_LIA, QF\_LRA, QF\_LIRA.
+%    The benchmarks for this track will include all eligible \emph{non-incremental}
+%    QF\_BV benchmarks with known satisfiable status in SMT-LIB.
+%    Participating solvers are required to support the \akey{get-model} command.
+%    \rationale{In many SMT applications, model generation is an essential
+%    feature.  Previously, none of the SMT-COMP tracks required model
+%    generation. One of the challenges is that the model format is not
+%    consistent across different solvers. While imposing a standard over all
+%    logics is challenging, there are several logics (e.g., QF\_BV) where it is
+%    straightforward.  In the future we hope to expand this track to other
+%    logics as a way of pushing for model standardization.  Since the QF\_BV
+%    division was the one with the largest number of participants in previous
+%    years,  we hope for a high number of participants in this track.  }
+
+  \item \todo{\challtrack}
 
@@
     anticipated to be at most 20 minutes in the \maintrack, \inctrack,
-    \ucoretrack and \mvaltrack.  For the \challtrack, it is anticipated to be
-    at most 720 (12 hours) minutes.
+    \ucoretrack and \mvaltrack.
     \rationale{The time limit for the Main Track is
-    reduced to 20 minutes (down from 40 minutes in earlier years) \todo{rationale}.
-    For the \challtrack, 12 hours seem to be a reasonable compromise for the
-    expected number of participants and benchmarks submitted to this track.}
-
-  \item {\bf Benchmark Selection.} \todo{update}
-    Since 2015, the competition evaluated all
-    solvers on all eligible benchmarks in SMT-LIB.  This year, we will
-    use an alternative benchmark selection scheme that selects a subset
-    of the eligible benchmarks. The benchmark selection will be random,
-    but will guarantee inclusion of newly submitted benchmarks.  The upper
-    bound for the size of each division is not fixed, but
-    depends on the size of the corresponding logic.  Prior to this
-    selection, we will remove all benchmarks in a division that were
-    solved by all solvers (including non-competing solvers) in this
-    division in under one second in last year's competition.
-    \rationale{Evaluating solvers on all eligible benchmarks in SMT-LIB
-    makes results more predictable and seems to be more of an evaluation
-    than a competition.  In the Main track last year,
-    78\% of the 258,741 benchmarks were solved by all supported solvers
-    within the time limit (71\% within 1 second). In 7 (out of 46)
-    logics, over 99\% of benchmarks were solved by all solvers.
-    Removing `easy' (or at least `unsurprising') benchmarks attempts to
-    shift the focus towards challenging benchmarks, in particular since
-    we now use an alternative benchmark selection scheme.  It can be
-    argued that the size of a logic in SMT-LIB can be seen as an
-    indicator of its relevance.  We thus do not use a fixed upper bound
-    for the size of a division in order to reflect the suggested
-    importance of a division.}
-
-  \item {\bf Scoring Scheme.}
-    This year, we will abandon the weighted scoring scheme that was introduced
-    for the Main Track and \ucoretrack in 2016. We will fall back to the
-    scoring scheme based on the number of solved instances that was last used
-    in 2015.
-    \rationale{ Since 2016, the competition has used a scoring scheme based on
-    benchmark weights in order to de-emphasize large benchmark families.  The
-    scoring scheme is fairly complicated and not necessarily intuitive.  It
-    further makes comparing results in papers with results from the competition
-    more difficult.  A recent analysis of competition data from 2015-2018 for a
-    report on the competition of these years (currently under submission to
-    JSAT) suggests that benchmark families do not have a significant impact on
-    the (weighted) scores  When determining winners for each division using
-    the scoring scheme of 2015, the winners for only 7 divisions (out of 139)
-    over all three years would have changed.  While producing these results we
-    further noticed that the description of what constitutes a benchmark family
-    (as stated in the rules documents) had been incorrectly interpreted by the
-    scoring scripts in 2016-2018. After fixing this misinterpretation, only one
-    single division winner changes - in 2017 AUFNIRA should have been won by
-    CVC4 and not Vampire.}
-
-  \item {\bf New Scores in the \maintrack.}
-    This year, additionally to the separate scores given for sequential and
-    parallel performance, we will reward three new scores in the \maintrack.
-    The \emph{24-second score} will reward solving performance within a time
-    limit of 24 seconds (wall clock time), the \emph{sat score} will reward
-    performance on satisfiable instances, and the \emph{unsat score} will
-    reward performance on unsatisfiable instances.
-    \rationale{ Different application domains of SMT typically impose a wide
-    range of time limits (from hours to seconds).  Previous time limits used in
-    the competition were the same for all benchmarks and thus agnostic to the
-    application domain of a benchmark.  The new \challtrack and the new
-    24-second score try to address use cases on both extreme ends of the
-    spectrum.  Further, in many cases an SMT application produces either mainly
-    satisfiable or mainly unsatisfiable queries to the SMT solver.  The new sat
-    and unsat scores are intended to reward solvers that implement specialized
-    techniques and optimizations for either case.}
-
-  \item {\bf Do Not Run Non-Competitive Divisions.}
-    This year, we will not run non-competitive divions.
-    \rationale{Evaluating solvers in non-competitive divisions is more in the
-    spirit of an evaluation than a competition.}
-
-  \item {\bf Experimental Strings Division.}
-    The competition will feature experimental divisions for benchmarks that
-    use strings. Participating solvers must implement the semantics of the
-    current SMT-LIB draft for the theory of unicode strings
-    (\url{http://smtlib.cs.uiowa.edu/theories-UnicodeStrings.shtml}).
-    \rationale{Corresponding theories and benchmarks are expected to be added
-    to SMT-LIB in the near future.}
-
-  \item {\bf Competition-Wide Recognitions.}
-    This year, we will replace the previous notion of competi\-tion-wide scoring
-    as introduced for the Main Track in 2014 (and improved over the years)
-    with recognitions for all tracks that do not directly compare divisions.
-    \rationale{Competi\-tion-wide scoring was introduced as a metric to
-    compare solver performance across all divisions. It is, by definition,
-    biased towards solvers that enter a large number of divisions.}
+      reduced to 20 minutes (down from 40 minutes in the previous years),
+      to make running the competition more manageable}
+
+  \item {\bf Benchmark Selection.}
+    This year we reduce the percentage of the benchmarks that are run in the competition.
+    \rationale{The goal is to make running the competition more managable.}
+
+  \item {\bf The Strings Division is not experimental.}
+    The last years competition introduced a experimental divisions for benchmarks that
+    use strings. This year, the String division is no longer experimental.
+
+    \rationale{The final specification of the string theory has been officially released.}
 
@@
 
-\todo{Portfolio Tool}
+\header{Portfolio Solver.}
+%
+A \emph{portfolio solver} is a solver using a combination of two or
+more sub-solvers, developed by different groups of authors, on the
+same component or abstraction of the input problem.  For example, a
+solver using one subsolver to solve the ground abstraction of a
+quantified problem is allowed, while a solver using two or more
+subsolvers from different groups of authors is not.
+Porfolio solver are in general \textbf{not allowed}.
+If you are unsure if your tool is a portfolio solver according to this
+definition and you feel that it should be allowed contact the
+organizers of the SMT-COMP for clarification.
 
@@
 
-\header{Attendance.}\todo{fix this!}
-%
-Submitters of an SMT-COMP entrant are not required (but encouraged) to be
-physically present at the competition or the SMT Workshop to participate or
-win.
+%\header{Attendance.}
+%
+%Submitters of an SMT-COMP entrant are not required (but encouraged) to be
+%physically present at the competition or the SMT Workshop to participate or
+%win.
 
@@
 specific output as specified in the individual track sections e.g. unsat cores
-or models, will be considered to have aborted.
+or models, will be considered to have aborted.  Note that there is no
+distinction between output and error channel and tools should not write any
+message to the error channel that could be misinterpreted as a wrong result.
 
@@
 This track will use a wall-clock time limit of 20 minutes per solver/benchmark
-pair.\todo{we said 20 minutes, right?}
+pair.
 
@@
 other commands.
-Solver must not write anything to the standard error channel. \todo{okay?}
+Solvers must not write anything to the standard error channel.
 
@@
 This track will use a wall-clock time limit of 20 minutes per solver/benchmark
-pair.\todo{20 min}
+pair.
 
@@
 If the solver replies \texttt{unsat} to \akey{check-sat} but gives no
-response to \akey{get-model}, this is considered as no reduction, i.e.,
+response to \akey{get-unsat-core}, this is considered as no reduction, i.e.,
 as if the solver would have returned the entire benchmark as an unsat

### 2020-04-01 rules/rules20.tex
ordered organizing team alphabetically

@@
 \item Haniel Barbosa~-- Universidade Federal de Minas Gerais, Brazil
+\item Jochen Hoenicke~-- Universit\"at Freiburg, Germany
 \item \href{http://www.inf.usi.ch/postdoc/hyvarinen/}{Antti Hyvarinen}~--
 		Universita della Svizzera italiana, Switzerland (chair)
-\item Jochen Hoenicke~-- Universit\"at Freiburg, Germany
 \end{itemize}
@@
 \todo{add disclosure}
+Jochen Hoenicke is part of the developing teams of the SMT solver
+SMTInterpol~\cite{smtinterpol}.
 Antti Hyvarinen is part of the developing team of the SMT solver
 OpenSMT~\cite{opensmt2}.
-Jochen Hoenicke is part of the developing teams of the SMT solver
-SMTInterpol~\cite{smtinterpol}.
 

### 2020-04-01 rules/rules20.tex
adding disclosure

@@
     two.
-%
-    \rationale{The organizers wishes to keep the total run-time of the
+
+    \rationale{The organizers wish to keep the total run-time of the
       competition small, in case of unforeseen problems that require
@@
 %
-\todo{add disclosure}
-Jochen Hoenicke is part of the developing teams of the SMT solver
+Haniel Barbosa is part of the developing teams of the SMT solvers
+CVC4~\cite{cvc4-smtcomp18} and veriT~\cite{verit}.
+%
+Jochen Hoenicke is part of the developing team of the SMT solver
 SMTInterpol~\cite{smtinterpol}.

### 2020-04-02 rules/rules20.tex
Some comments and text on rules20

@@
 SMT-COMP~2020.
+%
+\ah{As in previous years, we have revised the rules slightly.  Some rule
+changes in 2020 aim specifically at making the competition more
+manageable to run, as both the popularity of the competition and the
+benchmark library have grown over time.}
+%
 The principal changes from the previous competition rules are the following:
@@
 %
-    \rationale{Due to limitations of starexec, the standard error channel
-      and standard output channel are not separated.  In the previous year, the
+    \rationale{Starexec does not distinguish between the standard error
+      and output channels.  In the previous year, the
       organizers had to work around the limitation by wrapping the submitted
@@
   \item {\bf The Strings Division is not experimental.}
-    The last years competition introduced a experimental divisions for benchmarks that
+    The last year's competition introduced a experimental divisions for benchmarks that
     use strings. This year, the String division is no longer experimental.
@@
     \rationale{The final specification of the string theory has been officially released.}
-
+\item \ah{{\bf Model validation track for QF\_BV is not
+        experimental.}
+        Last year's competition introduced the experimental model
+        validation track for QF\_BV.  This year this will be a standard
+        track.}
+
+        \rationale{There was no issues with the track, so there is no
+        reason to keep it experimental.}
 \end{itemize}
@@
 
-\subsection{\mvaltrack (experimental)}
+\subsection{\mvaltrack (experimental)}\ah{Experimental and non
+experimental?}
 \label{sec:exec:model}
@@
 The result of a solver is considered erroneous if the response to the
-\akey{checks-sat} command is \texttt{unsat}, if the returned model is not
+\akey{check-sat} command is \texttt{unsat}, if the returned model is not
 well-formed (e.g. does not provide a definition for all the user-declared
@@
       \item partial models,
-      \item malformed models (except if this due to reaching the time limit
+      \item malformed models (except if this is due to reaching the time limit
         while printing),
@@
       solvers (including non-competitive solvers) in less than one second in
-      the corresponding track in 2018.
+          the corresponding track in 2018 \ah{or 2019}.
     \item \emph{\ucoretrack.} All benchmarks with only a single assertion.
@@
   \item \label{bench-sel-more} and if $n > 600$,
-    50\% of the benchmarks of the logic will be selected.
+      \ah{40\%} of the benchmarks of the logic will be selected.
   \end{enumerate}
@@
 the timeline (Section~\ref{sec:important}) will be added to the other
-seeding values. \todo{Should we provide more randomness by multiplying it with 100?  It has two or three trailing digits}  This helps provide transparency, by guaranteeing that
+seeding values. \todo{Should we provide more randomness by multiplying
+it with 100?  It has two or three trailing digits} \ah{Two.  Does it
+sometimes have three?} This helps provide transparency, by guaranteeing that
 the organizers cannot manipulate the seed in favor of or against any

### 2020-04-03 rules/rules20.tex
minor changes to rules 2020 document

@@
 \newcommand{\ah}[1]{\rem{#1 -- antti}}
+\newcommand{\hb}[1]{\rem{#1 -- haniel}}
 \newcommand{\lh}[1]{\rem{#1 -- liana}}
@@
 
-        \rationale{There was no issues with the track, so there is no
+        \rationale{There were no issues with the track, so there is no
         reason to keep it experimental.}
@@
 solvers and solver options as possible.  However, to keep the number of
-solver submissions low, each team should only provide multiple solvers,
+solver submissions low, each team should only provide multiple solvers
 if they are  substantially different.  A justification must be provided
 for the difference.  We strongly encourage the teams to keep the number
-of solvers per team per category at at most two.  The idea in allowing
-up to two submissions is to encourage the development of new,
-experimental techniques by allowing an ``alternative solver'' to be
-submitted while keeping the competition manageable.
+of solvers per team per category at at most two. By allowing
+up to two submissions we want to encourage the development of new,
+experimental techniques via an ``alternative solver'' while keeping
+the competition manageable.
 
@@
       solvers (including non-competitive solvers) in less than one second in
-          the corresponding track in 2018 \ah{or 2019}.
+          the corresponding track in \hb{previous years}.%  2018 \ah{or 2019}.
     \item \emph{\ucoretrack.} All benchmarks with only a single assertion.

### 2020-04-03 rules/rules20.tex
changes to rules document as discussed

@@
 \item[May~19] Opening value of NYSE Composite Index used to compute
-  random seed for competition tools. \todo{Okay?}
+  random seed for competition tools.
 \item[July~5/6] SMT Workshop; end of competition, presentation of
@@
 
-SMT-COMP 2020 will have five tracks: the \maintrack (before 2019: Main Track),
-the \inctrack (before 2019: Application Track), the \ucoretrack,
-the \challtrack, and the \mvaltrack.
+SMT-COMP 2020 will have four tracks: the \maintrack (before 2019: Main Track),
+the \inctrack (before 2019: Application Track), the \ucoretrack, and the
+\mvaltrack.
 %
@@
 %
-\ah{As in previous years, we have revised the rules slightly.  Some rule
+As in previous years, we have revised the rules slightly.  Some rule
 changes in 2020 aim specifically at making the competition more
 manageable to run, as both the popularity of the competition and the
-benchmark library have grown over time.}
+benchmark library have grown over time.
 %
@@
 
-  \item \todo{\challtrack}
+  \item {\bf The \challtrack will not run this year.}
+
+  \rationale{Since there were no new benchmarks submitted to SMT-LIB intended
+    for the SMT-COMP \challtrack, we will not run the track in 2020, as
+    previously announced.}
 
@@
   \rationale{The final specification of the string theory has been officially released.}
-\item \ah{{\bf Model validation track for QF\_BV is not
-        experimental.}
-        Last year's competition introduced the experimental model
-        validation track for QF\_BV.  This year this will be a standard
-        track.}
-
-        \rationale{There were no issues with the track, so there is no
-        reason to keep it experimental.}
+
+  \item {\bf \mvaltrack.}  Last year's competition introduced the experimental
+  model validation track for QF\_BV.  This year this will be a standard
+  track. Moreover, the divisions QF\_IDL, QF\_RDL, QF\_LIA, QF\_LRA, QF\_LIRA
+  will be included and will be experimental.
+
+  \rationale{There were no issues with the track for QF\_BV, so there is no
+    reason to keep it experimental. For the new divisions, as before, given the
+    inconsistencies across different model producing solvers, we proceed in an
+    experimental fashion to push for model standardization.}
 \end{itemize}
@@
 
-\header{Input and Output.}
+\header{Input.}
 %
@@
       \vspace{-1ex}
-    \item In the \emph{\maintrack}, \emph{\challtrack}, \emph{\mvaltrack} and
+    \item In the \emph{\maintrack}, \emph{\mvaltrack} and
         \emph{\ucoretrack}, there may be a single \akey{set-option} command.
-        Note that \texttt{success} outputs are ignored by the post-processors
-        used by the competition.\footnote{SMT-LIB~2.6 requires solvers to
-        produce a \texttt{success} answer after each \akey{set-logic},
-        \akey{declare-sort}, \akey{declare-fun} and \akey{assert} command
-        (among others), unless the option \akey{:print-success} is set to
-        false.  Ignoring the \texttt{success} outputs allows for submitting
-        fully SMT-LIB~2.6 compliant solvers without the need for a wrapper
-        script, while still allowing entrants of previous competitions to run
-        without changes.}
       \item In the \emph{\inctrack}, the \akey{:print-success} option
@@
 
+\header{Output.}
+%
+In all tracks except the \inctrack, any \texttt{success} outputs will be
+ignored\footnote{SMT-LIB~2.6 requires solvers to produce a \texttt{success}
+  answer after each \akey{set-logic}, \akey{declare-sort}, \akey{declare-fun}
+  and \akey{assert} command (among others), unless the option
+  \akey{:print-success} is set to false.  Ignoring the \texttt{success} outputs
+  allows for submitting fully SMT-LIB~2.6 compliant solvers without the need for
+  a wrapper script, while still allowing entrants of previous competitions to
+  run without changes.}.  Solvers that exit before the time limit without
+reporting a result (e.g., due to exhausting memory or crashing) \emph{and} do
+not produce output that includes \texttt{sat}, \texttt{unsat}, \texttt{unknown}
+or other track specific output as specified in the individual track sections
+e.g. unsat cores or models, will be considered to have aborted.  Note that there
+is no distinction between output and error channel and tools should not write
+any message to the error channel because it could be misinterpreted as a wrong
+result.
+
 \header{Time and Memory Limits.}
@@
 variables.  See the StarExec user guide for more information.
-
-\header{Aborts and Unparsable Output.}
-%
-In all tracks except the \inctrack, any \texttt{success} outputs will be
-ignored.  Solvers that exit before the time limit without reporting a result
-(e.g., due to exhausting memory or crashing) \emph{and} do not produce output
-that includes \texttt{sat}, \texttt{unsat}, \texttt{unknown} or other track
-specific output as specified in the individual track sections e.g. unsat cores
-or models, will be considered to have aborted.  Note that there is no
-distinction between output and error channel and tools should not write any
-message to the error channel that could be misinterpreted as a wrong result.
 
@@
 \texttt{unknown} to indicate that it cannot determine satisfiability of the
-formula.  Note that output sent to the standard error channel is treated the
-same way as output sent to the standard output channel. \todo{okay?}
+formula.
 
@@
 
-\subsection{\challtrack}
-\label{sec:exec:industry-challenge}
-
-The \challtrack will include both non-incremental and incremental benchmarks.
-It will follow the same rules as the \maintrack and \inctrack, respectively,
-with two exceptions: benchmark selection and the time limit.
-
-\header{Benchmark Selection.}\todo{fixme}
-This track will run on challenging industrial benchmarks provided by the
-community. This year, the \challtrack will include the complete set of provided
-benchmarks dedicated to this track, which consist of both incremental and
-single query benchmarks in the logics \todo{QF\_BV, QF\_ABV and QF\_AUFBV}. The
-complete list of benchmarks along with instructions on how to access them will
-be provided on the SMT-COMP website as soon as the benchmark library is
-released.
-
-\header{Time Limit.}
-This track will use a wall-clock time limit of 12 hours per solver/benchmark
-pair.
-
-\header{Post-Processor.}
-This track will use the post-processors from the \maintrack (for
-non-incremen\-tal benchmarks) and the \inctrack (for incremental benchmarks)
-to accumulate the results.
+% \subsection{\challtrack}
+% \label{sec:exec:industry-challenge}
+
+% The \challtrack will include both non-incremental and incremental benchmarks.
+% It will follow the same rules as the \maintrack and \inctrack, respectively,
+% with two exceptions: benchmark selection and the time limit.
+
+% \header{Benchmark Selection.}\todo{fixme}
+% This track will run on challenging industrial benchmarks provided by the
+% community. This year, the \challtrack will include the complete set of provided
+% benchmarks dedicated to this track, which consist of both incremental and
+% single query benchmarks in the logics \todo{QF\_BV, QF\_ABV and QF\_AUFBV}. The
+% complete list of benchmarks along with instructions on how to access them will
+% be provided on the SMT-COMP website as soon as the benchmark library is
+% released.
+
+% \header{Time Limit.}
+% This track will use a wall-clock time limit of 12 hours per solver/benchmark
+% pair.
+
+% \header{Post-Processor.}
+% This track will use the post-processors from the \maintrack (for
+% non-incremen\-tal benchmarks) and the \inctrack (for incremental benchmarks)
+% to accumulate the results.
 
@@
 
-\subsection{\mvaltrack (experimental)}\ah{Experimental and non
-experimental?}
+\subsection{\mvaltrack}
 \label{sec:exec:model}
@@
 \header{Benchmark Selection.}
-This experimental track only has the divisions
-\todo{QF\_BV, QF\_IDL, QF\_RDL, QF\_LIA, QF\_LRA, QF\_LIRA}. It will run on a
+This track only has the divisions
+QF\_BV, QF\_IDL, QF\_RDL, QF\_LIA, QF\_LRA, QF\_LIRA.
+%
+This year all but the first are experimental divisions.
+%
+It will run on a
 selection of non-incremental benchmarks with status \texttt{sat} from these
@@
 The \maintrack will use a subset of all \emph{non-incremental} benchmarks and
-the \inctrack will use a subset of all \emph{incremental} benchmarks. The
-\challtrack will use all incremental and non-incremental benchmarks dedicated
-to this track by their submitters. The \ucoretrack will use a selection of
+the \inctrack will use a subset of all \emph{incremental} benchmarks.
+%
+% The \challtrack will use all incremental and non-incremental benchmarks
+% dedicated to this track by their submitters.
+%
+The \ucoretrack will use a selection of
 non-incremental benchmarks with status \texttt{unsat} and more than one
@@
 The organizers, in collaboration with the SMT-LIB maintainers, will be
-checking and curating these until {\bf April~20, 2020}~\todo{check date}.  The SMT-LIB
+checking and curating these until {\bf April~20, 2020}.  The SMT-LIB
 maintainers intend to make a new release of the benchmark library
@@
 The competition will use a large subset of SMT-LIB benchmarks, with some
-guarantees on including new benchmarks.  In \textbf{all} tracks \textbf{except}
-the \challtrack, the following selection process will be used.
+guarantees on including new benchmarks.  In \textbf{all} tracks
+% \textbf{except} the \challtrack,
+the following selection process will be used.
 \begin{enumerate}
@@
       solvers (including non-competitive solvers) in less than one second in
-          the corresponding track in \hb{previous years}.%  2018 \ah{or 2019}.
+          the corresponding track in 2018 or 2019.
     \item \emph{\ucoretrack.} All benchmarks with only a single assertion.
@@
   Let $n$ be the number of benchmarks in an SMT-LIB logic, then
-  \todo{How do we cap?}
   \begin{enumerate}
@@
   \item \label{bench-sel-more} and if $n > 600$,
-      \ah{40\%} of the benchmarks of the logic will be selected.
+      40\% of the benchmarks of the logic will be selected.
   \end{enumerate}
@@
 entrants other than the organizers'.  Additionally, the integer part
-of \todo{one hundred times} the opening value of the New York Stock Exchange Composite Index on
+of one hundred times the opening value of the New York Stock Exchange
+Composite Index on
 the first day the exchange is open on or after the date specified in
 the timeline (Section~\ref{sec:important}) will be added to the other
-seeding values. \todo{Should we provide more randomness by multiplying
-it with 100?  It has two or three trailing digits} \ah{Two.  Does it
-sometimes have three?} This helps provide transparency, by guaranteeing that
+seeding values. This helps provide transparency, by guaranteeing that
 the organizers cannot manipulate the seed in favor of or against any
@@
 \header{Error Score ($\mathbf{e}$).}
-For the \maintrack, \inctrack and \challtrack, $e$ is the number of returned
+For the \maintrack, and \inctrack,%
+% and \challtrack
+$e$ is the number of returned
 statuses that disagree with the given expected status (as described above,
@@
 \header{Correctly Solved Score ($\mathbf{n}$).}
-For the \maintrack, \inctrack, \challtrack and \mvaltrack,
+For the \maintrack, \inctrack, and \mvaltrack,
 $N$ is defined as the number of \akey{check-sat} commands, and
@@
 
-\subsubsection{\maintrack and \challtrack}
-  For the \maintrack and \challtrack, the error score $e$ and the correctly
+\subsubsection{\maintrack}% and \challtrack}
+  For the \maintrack the error score $e$ and the correctly
   solved score $n$ are defined as
@@
 performance of a solver (the \emph{parallel division score}).  For the
-\maintrack, \challtrack, \ucoretrack and \mvaltrack we also compute a division
+\maintrack, \ucoretrack and \mvaltrack we also compute a division
 score based on the sequential performance of a solver (the \emph{sequential
@@
 \header{Removal of Disagreements.}
-Before division scores are computed for the \maintrack and \challtrack,
+Before division scores are computed for the \maintrack,% and \challtrack,
 benchmarks with \emph{unknown status} are removed from the competition results
@@
 The sequential score for a division is computed for \emph{all} tracks
-\emph{except} the \inctrack and incremental benchmarks in the
-\challtrack\footnote{Since incremental track benchmarks may be partially
+\emph{except} the \inctrack
+% and incremental benchmarks in the \challtrack
+\footnote{Since incremental track benchmarks may be partially
 solved, defining a useful sequential performance for the incremental track
@@
 \]
-where the minimum of an empty set is 1200 seconds \todo{changed from 2400 to 1200, correct?}
+where the minimum of an empty set is 1200 seconds
 (no solver was able to solve the benchmark).
@@
 %
-\todo{check your affiliations}
 \begin{itemize}
 \setlength{\itemsep}{0pt}
-\item Haniel Barbosa~-- Universidade Federal de Minas Gerais, Brazil
-\item Jochen Hoenicke~-- Universit\"at Freiburg, Germany
-\item \href{http://www.inf.usi.ch/postdoc/hyvarinen/}{Antti Hyvarinen}~--
-		Universita della Svizzera italiana, Switzerland (chair)
+\item \href{http://homepages.dcc.ufmg.br/~hbarbosa/}{Haniel Barbosa}~-- Universidade Federal de Minas Gerais, Brazil
+\item \href{https://jochen-hoenicke.de/}{Jochen Hoenicke}~-- Universit\"at Freiburg, Germany
+\item \href{http://www.inf.usi.ch/postdoc/hyvarinen/}{Antti Hyv\"arinen}~--
+    Universit\`a della Svizzera italiana, Switzerland (chair)
 \end{itemize}
@@
 Pascal Fontaine, Aina Niemetz and Mathias Preiner are maintaining the SMT-LIB
-benchmark library. \todo{check if still current}
+benchmark library.
 The competition uses the

### 2020-04-03 rules/rules20.tex
Some last edits on the rules.  Added the draft watermark

@@
 
-%\usepackage{draftwatermark}
+\usepackage{draftwatermark}
 %\usepackage{showframe}   % debug
@@
 presence \emph{and the tracks and divisions in which it is
-  participating} via the web form at
+  participating} via the web form at a location we will disclose on a
+  later date.
+  \iffalse
 \begin{center}
@@
 \end{center}
+\fi
 A submission \textbf{must} also include a \emph{system description} (see below)
@@
 
-\header{Multiple versions.}\todo{check}
+\header{Multiple versions.}
 %
@@
 \header{Removal of Disagreements.}
-Before division scores are computed for the \maintrack,% and \challtrack,
+Before division scores are computed for the \maintrack{},
 benchmarks with \emph{unknown status} are removed from the competition results

### 2020-04-27 rules/rules20.tex
Added the draft watermark.  Fixed the year and edition number
fix
no longer draft, adding form link

@@
 
-\usepackage{draftwatermark}
+% \usepackage{draftwatermark}
 %\usepackage{showframe}   % debug
@@
 
-\title{14th International Satisfiability Modulo Theories Competition
-  (SMT-COMP 2019): Rules and Procedures}
+\title{15th International Satisfiability Modulo Theories Competition
+  (SMT-COMP 2020): Rules and Procedures}
 
@@
   later date.
-  \iffalse
 \begin{center}
-  \todo{\url{https://forms.gle/todo}}
+  \url{https://forms.gle/WRbJrawdb1Sko6uz5}
 \end{center}
-\fi
 A submission \textbf{must} also include a \emph{system description} (see below)
@@
 \mvaltrack will use a selection of non-incremental benchmarks with status
-\texttt{sat} from logic QF\_BV.
+\texttt{sat} from logics QF\_BV, QF\_IDL, QF\_RDL, QF\_LIA, QF\_LRA, QF\_LIRA.
 

### 2020-04-27 rules/rules20.tex
fix

@@
 presence \emph{and the tracks and divisions in which it is
-  participating} via the web form at a location we will disclose on a
-  later date.
+  participating} via the web form at
 \begin{center}

### 2020-04-27 tools/prep/extract_data_from_submission.py
Adjust registration scripts to 2020 competition and new form

@@ -48,15 +48,17 @@ g_logics_all = {
         'track_model_validation' : ['QF_BV']
         }
 
-COL_SINGLE_QUERY_TRACK = 'Select all divisions in the Single-Query (previously: Main) Track and the Unsat-Core Track to submit the solver to (use checkbox ALL for all divisions): '
-COL_INCREMENTAL_TRACK = 'Select all divisions in the Incremental Track to submit the solver to (use checkbox ALL for all divisions):'
-COL_MODEL_VALIDATION_TRACK = 'Select all divisions in the Model-Validation Track (experimental) to submit the solver to:'
-COL_CHALLENGE_TRACK = 'Select all divisions in the Industry-Challenge Track to submit the solver to (use checkbox ALL for all divisions):'
+COL_SINGLE_QUERY_TRACK = 'Select all divisions in the Single-Query (previously: Main) Track and the Unsat-Core Track to submit the solver to: '
+COL_INCREMENTAL_TRACK = 'Select all divisions in the Incremental Track to submit the solver to:'
+COL_MODEL_VALIDATION_TRACK = 'Select all divisions in the Model-Validation Track to submit the solver to:'
 COL_VARIANT = 'If this solver is a VARIANT of another submission, e.g. an experimental version, provide the name and the StarExec ID of the main solver, otherwise leave blank.'
-COL_WRAPPER = 'If this solver is a WRAPPER TOOL (i.e., it includes and calls one or more other SMT solvers, see Section 4 of the competition rules at https://smt-comp.github.io/2019/rules19.pdf), list ALL wrapped solvers and their exact version here, otherwise leave blank.'
-COL_DERIVED = 'If this solver is a DERIVED TOOL (i.e., any solver that is based on or extends another SMT solver, see Section 4 of the competition rules at https://smt-comp.github.io/2019/rules19.pdf), provide the name of the original tool here. A derived tool should follow the naming convention [name-of-base-solver]-[my-solver-name].'
-COL_CERTIFICATES = 'Certificates will be awarded to winning teams. To allow us to print the correct number, please indicate how many certificates you would need.'
+COL_WRAPPER = 'If this solver is a WRAPPER TOOL (i.e., it includes and calls one or more other SMT solvers, see Section 4 of the competition rules at https://smt-comp.github.io/2020/rules20.pdf), list ALL wrapped solvers and their exact version here, otherwise leave blank.'
[…]

### 2020-04-27 tools/prep/extract_data_from_solvers_divisions.py
Adjust registration scripts to 2020 competition and new form

@@ -14,8 +14,6 @@ g_submissions = None
 
 TRACK_SINGLE_QUERY_RAW = 'track_single_query'
 TRACK_INCREMENTAL_RAW = 'track_incremental'
-TRACK_SINGLE_QUERY_CHALLENGE_RAW = 'track_single_query_challenge'
-TRACK_INCREMENTAL_CHALLENGE_RAW = 'track_incremental_challenge'
 TRACK_UNSAT_CORE_RAW = 'track_unsat_core'
 TRACK_MODEL_VALIDATION_RAW = 'track_model_validation'
 
@@ -37,16 +35,6 @@ g_logics_all = {
             'QF_LRA','QF_NIA','QF_UF','QF_UFBV','QF_UFBVLIA','QF_UFLIA',
             'QF_UFLRA','QF_UFNIA','UFLRA',
             ],
-        TRACK_SINGLE_QUERY_CHALLENGE_RAW        : [
-            'QF_BV',
-            'QF_ABV',
-            'QF_AUFBV',
-            ],
-        TRACK_INCREMENTAL_CHALLENGE_RAW        : [
-            'QF_BV',
-            'QF_ABV',
-            'QF_AUFBV',
-            ],
         TRACK_UNSAT_CORE_RAW       : [
             'ABVFP','ALIA','AUFBVDTLIA','AUFDTLIA','AUFLIA','AUFLIRA','AUFNIA',
             'AUFNIRA','BV','BVFP','FP','LIA','LRA','NIA','NRA','QF_ABV',
@@ -57,7 +45,8 @@ g_logics_all = {
             'QF_UFLRA','QF_UFNIA','QF_UFNRA','UF','UFBV','UFDT','UFDTLIA',
             'UFDTNIA','UFIDL','UFLIA','UFLRA','UFNIA',
             ],
-        TRACK_MODEL_VALIDATION_RAW : ['QF_BV']
+        TRACK_MODEL_VALIDATION_RAW : ['QF_BV', 'QF_IDL', 'QF_RDL', 'QF_LIA',
+            'QF_LRA', 'QF_LIRA']
         }
 
 
@@ -81,16 +70,12 @@ COL_COMPETING = 'Competing'
 # Tracks
 COL_SINGLE_QUERY_TRACK = 'Single Query Track'
 COL_INCREMENTAL_TRACK = 'Incremental Track'
[…]

### 2020-05-06 rules/rules20.tex
Made the constants in selection compatible with the 40% rule.  Changed the definition of derived tool to allow authors to rename their own tool.

@@
 A \emph{derived tool} is defined as any solver that is \emph{based on and
-extends} another SMT solver (the \emph{base solver}).  Its system description
+extends} another SMT solver (the \emph{base solver}) from a different
+group of authors.  Its system description
 \textbf{must} explicitly acknowledge
@@
     \item \label{bench-sel-300} if $n \le 300$, all instances will be selected;
-  \item \label{bench-sel-600} if $300 < n \leq 600$, a subset of 300 instances
+  \item \label{bench-sel-600} if $300 < n \leq 750$, a subset of 300 instances
     from the logic will be selected;
-  \item \label{bench-sel-more} and if $n > 600$,
+  \item \label{bench-sel-more} and if $n > 750$,
       40\% of the benchmarks of the logic will be selected.

### 2020-05-06 tools/selection/selection.py
Updated the constants in the selection rule according to the 40% also in the selection script

@@ -16,12 +16,12 @@ NUM_ASSERTS = 2
 
 # The rules give the following rules for the number of selected benchmarks
 # (a) If a logic contains < 300 instances, all instances will be selected
-# (b) If a logic contains between 300 and 600, a subset of 300 will be selected
-# (c) If a logic contains > 600 then 40% will be selected
+# (b) If a logic contains between 300 and 750, a subset of 300 will be selected
+# (c) If a logic contains > 750 then 40% will be selected
 # The following three variables represent the parameters in these rules so that
 # they can be modified if needed
 NUM_LOWER = 300
-NUM_UPPER = 600
+NUM_UPPER = 750
 PERCENT = 0.4
 
 #==============================================================================

### 2020-05-06 tools/selection/selection.py
Selection rule constants updated in selection.py

@@ -17,12 +17,12 @@ NUM_ASSERTS = 2
 
 # The rules give the following rules for the number of selected benchmarks
 # (a) If a logic contains < 300 instances, all instances will be selected
-# (b) If a logic contains between 300 and 600, a subset of 300 will be selected
-# (c) If a logic contains > 600 then 40% will be selected
+# (b) If a logic contains between 300 and 750, a subset of 300 will be selected
+# (c) If a logic contains > 750 then 40% will be selected
 # The following three variables represent the parameters in these rules so that
 # they can be modified if needed
 NUM_LOWER = 300
-NUM_UPPER = 600
+NUM_UPPER = 750
 PERCENT = 0.4
 
 #==============================================================================

### 2020-05-13 rules/rules20.tex
Extended solver deadline

@@
   entered, and magic numbers for benchmark scrambling.
-\item[May~18] Deadline for final versions of solvers, including
+\item[May~25] Deadline for final versions of solvers, including
   system descriptions.
-\item[May~19] Opening value of NYSE Composite Index used to compute
+\item[May~26] Opening value of NYSE Composite Index used to compute
   random seed for competition tools.
@@
 However, updates to existing entrants on StarExec
-will be accepted until the end of {\bf May~18, 2020} anywhere on earth.
+will be accepted until the end of {\bf May~25, 2020} anywhere on earth.
 

### 2020-05-13 tools/wrap-solvers/wrap_solver.sh
Update to wrapper scripts for SMTCOMP 2020 (#20)
Wrapper scripts for SMTCOMP 2020

- Added option for unzip_only
- Fix calling wrap_solver script for incremental.
- Added option to wrap preliminary solvers.
- Work around to not use starexec to download solvers
- do not require login.sh
- Handle solvers where config ist not named "default"
- updated README
- check if trace-executor was copied and bail out otherwise

@@ -4,17 +4,19 @@
 
 
 SCRIPTDIR=`dirname $(readlink -f "$0")`
-source "$SCRIPTDIR/login.sh"
+#source "$SCRIPTDIR/login.sh"
 
 if [ $# -eq 5 ]
 then
   WRAP=yes
   DOWNLOAD=yes
+  UNZIP=yes
   UPLOAD=yes
   ZIP=yes
 else
   WRAP=no
   DOWNLOAD=no
+  UNZIP=no
   UPLOAD=no
   ZIP=no
 fi
@@ -31,6 +33,7 @@ do
       echo "  options:"
       echo "    -h, --help    print this message and exit"
       echo "    -d            download only"
+      echo "    -x            unzip only"
       echo "    -w            wrap solver only"
       echo "    -u            upload solver only"
       echo "    -z            only zip solver from existing wrapped dir when wrapping"
@@ -39,6 +42,9 @@ do
       ;;
     -d)
       DOWNLOAD=yes
+      ;;
+    -x)
+      UNZIP=yes
       ;;
     -w)
       WRAP=yes
@@ -74,11 +80,13 @@ upload_solver()
 
   SOLVER=$1
   SOLVER_NAME=$2
-  COMMAND="pushsolver f=${SOLVER} n=${SOLVER_NAME} id=${SPACE_ID} downloadable="
-  java -jar ${SCRIPTDIR}/StarexecCommand.jar <<EOF
-login u=${USERNAME} p=${PASSWORD}
-${COMMAND}
-EOF
+#  COMMAND="pushsolver f=${SOLVER} n=${SOLVER_NAME} id=${SPACE_ID} downloadable="
+#  java -jar ${SCRIPTDIR}/StarexecCommand.jar <<EOF
+#login u=${USERNAME} p=${PASSWORD}
+#${COMMAND}
+#EOF
+  mkdir -p upload
+  cp "${SOLVER}" upload
 }
 
 get_solver_info()
@@ -86,11 +94,14 @@ get_solver_info()
   echo ">> get solver info"
 
   ID=$1
-  COMMAND="viewsolver id=${ID}"
-  java -jar ${SCRIPTDIR}/StarexecCommand.jar <<EOF
-login u=${USERNAME} p=${PASSWORD}
-${COMMAND}
[…]

### 2020-05-13 tools/wrap-solvers/wrap_solvers.py

@@ -6,6 +6,7 @@ import subprocess
 import os
 
 COL_SOLVER_ID = 'Solver ID'
+COL_PRELIM_SOLVER_ID = 'Preliminary Solver ID'
 COL_SOLVER_NAME = 'Solver Name'
 COL_SINGLE_QUERY_TRACK = 'Single Query Track'
 COL_INCREMENTAL_TRACK = 'Incremental Track'
@@ -29,6 +30,9 @@ if __name__ == '__main__':
     parser.add_argument ("-d", dest="download_only", action="store_true",
                          default=False,
                          help="download solvers only")
+    parser.add_argument ("-x", dest="unzip_only", action="store_true",
+                         default=False,
+                         help="unzip solvers only")
     parser.add_argument ("-w", dest="wrap_only", action="store_true",
                          default=False,
                          help="wrap solvers only")
@@ -50,10 +54,18 @@ if __name__ == '__main__':
             help="the StarExec space id for model validation track wrapped solvers")
     parser.add_argument ("--uc", dest="space_id_uc",
             help="the StarExec space id for unsat core track wrapped solvers")
+    parser.add_argument ("--prelim", dest="preliminary", action="store_true",
+            help="wrap the preliminary solvers")
     args = parser.parse_args()
+    if args.preliminary:
+        COL_SOLVER_ID = COL_PRELIM_SOLVER_ID
 
     if not os.path.exists(args.csv):
         die("file not found: {}".format(args.csv))
+
+    if args.space_id_inc and \
+       not os.path.exists("wrapper_inc/smtlib2_trace_executor"):
+        die("Please, copy the smtlib2_trace_executor binary to wrapper_inc")
 
     with open(args.csv, 'r') as csvfile:
         reader = csv.reader(csvfile, delimiter=',', quotechar='"')
@@ -72,6 +84,8 @@ if __name__ == '__main__':
             add_args = []
             if args.download_only:
                 add_args.append("-d")
+            if args.unzip_only:
+                add_args.append("-x")
             if args.wrap_only:
                 add_args.append("-w")
             if args.upload_only:
@@ -103,7 +117,7 @@ if __name__ == '__main__':
             if args.space_id_inc and incremental_track:
                 print('wrapping for incremental track')
                 script_args.extend(add_args)
-                script_args.extend(['./wrap_solver.sh', 'wrapped-inc', 'wrapper_inc', solver_id, args.space_id_inc, "solvers-inc"])
[…]

### 2020-05-26 2020/registration/update_web_pages.sh
Added small script to update web-pages from csv

@@ -1,0 +1,10 @@
+#!/bin/sh
+
+# Update the web pages from the solvers_division_final.csv.
+# You should have checked out the smt-comp.github.io repository into the
+# same directory as smt-comp
+
+NYSE_ON_MAY26="0"
+
+../../tools/prep/extract_data_from_solvers_divisions.py solvers_divisions_final.csv ../../../smt-comp.github.io/_participants_2020 2020
+../../tools/prep/make_participants_md.py -y 2020 -n "2020-05-26;$NYSE_ON_MAY26" ../../../smt-comp.github.io/2020/

### 2020-05-26 rules/rules20.tex
another deadline extension

@@
   entered, and magic numbers for benchmark scrambling.
-\item[May~25] Deadline for final versions of solvers, including
+\item[May~26] Deadline for final versions of solvers, including
   system descriptions.
-\item[May~26] Opening value of NYSE Composite Index used to compute
+\item[May~27] Opening value of NYSE Composite Index used to compute
   random seed for competition tools.
@@
 However, updates to existing entrants on StarExec
-will be accepted until the end of {\bf May~25, 2020} anywhere on earth.
+will be accepted until the end of {\bf May~26, 2020} anywhere on earth.
 

### 2020-12-01 rules/rules21.tex
Added preliminary rules for 2021

--- 2020-05-26 rules/rules20.tex
@@
 
-% \usepackage{draftwatermark}
+\usepackage{draftwatermark}
 %\usepackage{showframe}   % debug
@@
 \begin{itemize}
-  \item {\bf Portfolio Solvers are Forbidden.}
-    This year we explicitly forbid the submission of so-called
-    portfolio solvers as competition entries.  We acknowledge that
-    judging what constitutes a portfolio SMT solver is difficult.
-    However, we are not the first in history to face a similar
-    challenge, and plan to apply an equally historical approach where
-    we write down a ``law'', act as its ``judges'', and have a few
-    ``precedents''.
-    Here we define a portfolio solver as ``a solver using a combination of
-    two or more sub-solvers, developed by different groups of authors, on
-    the same component or abstraction of the input problem.'' For example, a
-    solver using one subsolver to solve the ground abstraction of a
-    quantified problem is allowed, while a solver using two or more
-    subsolvers from different groups of authors is not.
-    \rationale{The goal of the competition is to evaluate and improve
-      the state of the art of SMT solving. By just combining existing
-      solvers and running them in parallel it is possible to win the
-      competition without contributing anything new.}
-
-  \item {\bf Limit the Number of Solvers.}
+  \item {\bf The option \akey{:print-success} is explicitly set to true or false.}
+    Previous competitions set this option to \akey{true} for the incremental track.
+    In addition, this competition will set the option to \akey{false} for all
+    other tracks.
+
+    \rationale{According to the standard the default value of
+      \akey{:print-success} is true.  So a conforming solver would
+      unnecessarily print \akey{success} after each command that needs
+      to be stored and skipped by the post-processors.
+      Additionally, solvers can use this option as indication whether
+      incremental checking is desired.}
+
+  \item {\bf Error result is for unsoundness, only.}
+    Previous competitions marked malformed output in the unsat core and
+    the model validation track as errors.  These errors basically disqualify
+    a solver that outputs a slightly malformed model.  This year the error
+    result is only given for unsat cores that are not unsatifiable or models
+    that don't satisfy the formula. Of courses, answering sat in unsat
+    core track or unsat in model validation track is still considered an
+    error.
+    \rationale{An error result is very punishing and should be reserved
+      for problems that cannot be easily detected.  Giving a syntactically
+      wrong output, e.g. an error message, should just be considered as
+      not solving the task, not as providing an unsound result.}
+
+  \item {\bf The organizers may manually check unsound results.}
+    If solvers disagree on a result, the organizers reserve the right
+    to play the judge and determine which solver is unsound.  The unsound
+    solver is punished, the sound solver gets the point.
+    Previous competitions would take benchmark out of the scoring.
+    \rationale{Often, it can be decided which solver is unsound, even when
+      the benchmark has no status.  For example, when a solver was unsound in
+      other divisions and the authors submitted a fixed version, or because
+      a solver returning sat can be asked for a model.  In that case it would
+      be bad if solver that is known to be unsound
+      won the competition, just because the benchmarks it was unsound
+      on had no status.}
+
+  \item {\bf Punishment of unsound results is adapted to fix sat/unsat scores.}
+
+  \item {\bf TODO LIFT? Limit the Number of Solvers.}
     This year solver development teams may only submit more than one
@@
 
-  \item {\bf Combine stdout and stderr.}
-    This year, output to the standard error channel is not ignored, but
-    treated the same as output to the standard output channel.
-    Solvers should not write anything to the standard error channel.
-%
-    \rationale{Starexec does not distinguish between the standard error
-      and output channels.  In the previous year, the
-      organizers had to work around the limitation by wrapping the submitted
-      solvers in a script that ignored stderr.  By changing the rule we avoid
-      that the organizers have to change the submitted solvers.}
-
-%  \item {\bf The \mvaltrack is extended to other logics.}
-%    This year, we introduce a new experimental \mvaltrack for the logics QF\_IDL, QF\_RDL, QF\_LIA, QF\_LRA, QF\_LIRA.
-%    The benchmarks for this track will include all eligible \emph{non-incremental}
-%    QF\_BV benchmarks with known satisfiable status in SMT-LIB.
-%    Participating solvers are required to support the \akey{get-model} command.
-%    \rationale{In many SMT applications, model generation is an essential
-%    feature.  Previously, none of the SMT-COMP tracks required model
-%    generation. One of the challenges is that the model format is not
-%    consistent across different solvers. While imposing a standard over all
-%    logics is challenging, there are several logics (e.g., QF\_BV) where it is
-%    straightforward.  In the future we hope to expand this track to other
-%    logics as a way of pushing for model standardization.  Since the QF\_BV
-%    division was the one with the largest number of participants in previous
-%    years,  we hope for a high number of participants in this track.  }
-
-  \item {\bf The \challtrack will not run this year.}
-
-  \rationale{Since there were no new benchmarks submitted to SMT-LIB intended
-    for the SMT-COMP \challtrack, we will not run the track in 2020, as
-    previously announced.}
-
-  \item {\bf Time Limit.} The time limit per solver/benchmark pair is
+  \item {\bf TODO: Time Limit.} The time limit per solver/benchmark pair is
     anticipated to be at most 20 minutes in the \maintrack, \inctrack,
@@
 
+  \item {\bf Model syntax in \mvaltrack.}  The syntax used in the
+    model validation track did not conform to the SMTLIB standard.
+    The difference is that the syntax used previously included an
+    additional keyword \texttt{model} after the opening parenthesis in
+    the output.  This year we support both the SMTLIB syntax and the
+    old syntax.  We urge solver writers to upgrade their solver to use
+    the new syntax.
+
   \item {\bf \mvaltrack.}  Last year's competition introduced the experimental
-  model validation track for QF\_BV.  This year this will be a standard
-  track. Moreover, the divisions QF\_IDL, QF\_RDL, QF\_LIA, QF\_LRA, QF\_LIRA
-  will be included and will be experimental.
-
-  \rationale{There were no issues with the track for QF\_BV, so there is no
+    divisions QF\_IDL, QF\_RDL, QF\_LIA, QF\_LRA, QF\_LIRA in the
+    model validation track.  This year these will no longer be experimental.
+
+  \rationale{There were only small issues with these divisions, so there is no
     reason to keep it experimental. For the new divisions, as before, given the
@@
   \item
-    \bkey{(set-option :print-success ...)}
+    \bkey{(set-option ...)}
     \begin{enumerate}[label=(\alph*)]
       \vspace{-1ex}
-    \item In the \emph{\maintrack}, \emph{\mvaltrack} and
-        \emph{\ucoretrack}, there may be a single \akey{set-option} command.
+    \item The Input may contain the following \akey{set-option} commands.
     \item In the \emph{\inctrack}, the \akey{:print-success} option
@@
       \akey{(set-option :print-success true)} command to the solver.
+    \item In all other tracks, the scrambler will add an initial
+      \akey{(set-option :print-success false)} command to the solver.
     \item In the \emph{\mvaltrack}, a benchmark file contains a single
-        \akey{(set-option :produce-models true)} command.
-      \item In the \emph{\ucoretrack}, a benchmark file contains a single
-        \akey{(set-option :produce-unsat-cores true)} command.
+      \akey{(set-option :produce-models true)} command as the second command.
+    \item In the \emph{\ucoretrack}, a benchmark file contains a
+      single \akey{(set-option :produce-unsat-cores true)} command as
+      the second command.
     \end{enumerate}
@@
 response to the \akey{check-sat} command is \texttt{sat}, (ii) the
-returned unsatisfiable core is not well-formed (e.g., contains names of
-formulas that have not been asserted before), or (iii) the returned
-unsatisfiable core is not, in fact, unsatisfiable.
+returned unsatisfiable core is not, in fact, unsatisfiable.
 %
@@
     \begin{itemize}[noitemsep,topsep=0pt]
-      \item an \texttt{unsat} solver response to \akey{check-sat},
-      \item partial models,
-      \item malformed models (except if this is due to reaching the time limit
-        while printing),
-      \item models that do not satisfy the input problem; and
+      \item an \texttt{unsat} solver response to \akey{check-sat} or
+      \item models that do not satisfy the input problem.
     \end{itemize}
@@
         \akey{get-model}),
-      \item an \texttt{unknown} response to \akey{check-sat}.
+      \item an \texttt{unknown} response to \akey{check-sat}, or
+      \item malformed models, e.g., partial models.
     \end{itemize}
@@
 disregarded). For the \ucoretrack, $e$ includes, in addition, the number of
-returned unsat cores that are ill-formed or are not, in fact, unsatisfiable (as
+returned unsat cores that are not, in fact, unsatisfiable (as
 validated by a selection of other solvers selected by organizers).  For the
 \mvaltrack, $e$ includes, in addition, the number of returned models that are
-ill-formed or not full satisfiable models.
+not full satisfiable models.
 
@@
       \item the result of the \akey{check-sat} command is \texttt{unknown},
+      \item the result of the \akey{get-unsat-core} command is not wellformed.
     \end{itemize}

### 2021-01-13 rules/rules21.tex
no ref in page limit

@@
 As part of the submission, SMT-COMP entrants are \textbf{required} to provide a
-short (1-2 pages) description of the system, which \textbf{must} explicitly
+short (1-2 pages, excluding references) description of the system, which \textbf{must} explicitly
 acknowledge any solver it wraps or is based on in case of a \emph{wrapper} or

### 2021-05-01 rules/rules21.tex
various changes

@@
 \begin{itemize}
-  \item {\bf The option \akey{:print-success} is explicitly set to true or false.}
-    Previous competitions set this option to \akey{true} for the incremental track.
-    In addition, this competition will set the option to \akey{false} for all
-    other tracks.
-
+  \item {\bf The option \akey{:print-success} is explicitly set to
+    true or false.}  Previous competitions set this option to
+    \akey{true} for the incremental track.  In addition, this
+    competition will set the option to \akey{false} for all other
+    tracks.
     \rationale{According to the standard the default value of
@@
       unnecessarily print \akey{success} after each command that needs
-      to be stored and skipped by the post-processors.
-      Additionally, solvers can use this option as indication whether
-      incremental checking is desired.}
+      to be stored and skipped by the post-processors.  Additionally,
+      solvers can use this option as indication whether incremental
+      checking is desired.}
+
+    We were asked to set the \akey{:incremental} option to true for
+    the incremental track.  However this is problematic, because it is
+    not a standard option and solvers may not support it.
 
@@
 
-  \item {\bf TODO LIFT? Limit the Number of Solvers.}
-    This year solver development teams may only submit more than one
-    entry if they are substantially different.  A justification must
-    be provided for the difference.  We strongly encourage the teams
-    to keep the number of solvers per team per category at at most
-    two.
-
-    \rationale{The organizers wish to keep the total run-time of the
-      competition small, in case of unforeseen problems that require
-      to rerun the whole competition.  The idea in allowing up to two
-      submissions is to encourage the development of new, experimental
-      techniques by allowing an ``alternative solver'' to be submitted
-      while keeping the competition manageable.}
-
-  \item {\bf TODO: Time Limit.} The time limit per solver/benchmark pair is
-    anticipated to be at most 20 minutes in the \maintrack, \inctrack,
-    \ucoretrack and \mvaltrack.
-    \rationale{The time limit for the Main Track is
-      reduced to 20 minutes (down from 40 minutes in the previous years),
-      to make running the competition more manageable}
+    Previously an unsound response for a benchmark did punish the
+    score corresponding to the benchmark status.  We fix it to count
+    errors to the score that correspond to the solver output, not the
+    benchmark status.
+    \rationale{If a solver returns \texttt{unsat} for a
+      satisfiable benchmark, all other \texttt{unsat} responses of the
+      solver are no longer trustworthy.  So it is the unsat score of
+      the solver that must be punished.  The \texttt{sat} responses
+      may still be trustworthy.  In the extreme case, a solver that
+      always return \texttt{unsat} would a high error score for the
+      unsat category under the new rules, and would get no points at
+      all for the sat category.}
 
   \item {\bf Benchmark Selection.}
-    This year we reduce the percentage of the benchmarks that are run in the competition.
-    \rationale{The goal is to make running the competition more managable.}
+    This year we increase the percentage of the benchmarks that are run in the competition back to 50 \%.
+    \rationale{We feel that increasing the number of benchmarks is managable and 50 \% is a more round number than 40 \%.}
 
@@
     model validation track.  This year these will no longer be experimental.
+    In addition, new experimental divisions QF\_UF, QF\_UFBV,
+    QF\_UFIDL, QF\_UFLIA, QF\_UFLRA will be added.
 
@@
 subsolvers from different groups of authors is not.
-Porfolio solver are in general \textbf{not allowed}.
+Portfolio solver are in general \textbf{not allowed}.
 If you are unsure if your tool is a portfolio solver according to this

### 2021-05-01 rules/rules21.tex
model syntax, single query track check

@@
 
-  \item {\bf The Strings Division is not experimental.}
-    The last year's competition introduced a experimental divisions for benchmarks that
-    use strings. This year, the String division is no longer experimental.
-
-  \rationale{The final specification of the string theory has been officially released.}
-
-  \item {\bf Model syntax in \mvaltrack.}  The syntax used in the
-    model validation track did not conform to the SMTLIB standard.
-    The difference is that the syntax used previously included an
-    additional keyword \texttt{model} after the opening parenthesis in
-    the output.  This year we support both the SMTLIB syntax and the
-    old syntax.  We urge solver writers to upgrade their solver to use
-    the new syntax.
+  \item {\bf Stricter checks for output in single query track.}
+    It is now checked that the output in the single query track starts with
+    sat or unsat.  Error messages before such an output is no longer ignored
+    and are treated as an \texttt{unknown} result.
+    {\bf Note:} Solver authors should make sure not to print any debugging
+    output.  This includes debugging output on stderr, because the
+    post-processors cannot distinguish between stderr and stdout.
+
+  \rationale{A solver that does not support the full logic may
+    report errors and then continue ignoring the failed assertion.  This
+    way, it may be flagged as unsound under the old rules, even though it
+    clearly indicated the error.}
 
@@
     experimental fashion to push for model standardization.}
+
+  \item {\bf Model syntax in \mvaltrack.}  The syntax used in the
+    model validation track did not conform to the SMT-LIB standard.
+    The difference is that the syntax used previously included an
+    additional keyword \texttt{model} after the opening parenthesis in
+    the output.  This year we support both the SMT-LIB syntax and the
+    old syntax.  We urge solver writers to upgrade their solver to use
+    the new syntax.
+
+    We added new tracks for UF logics. According to the SMT-LIB standard,
+    model values of uninterpreted sorts should use the syntax
+    \texttt{(as @name Sort)}.
+    In particular the model validator needs to know the sort of the model
+    value.  Furthermore, it is implicitly assumed that model values
+    differ if they have different names.
+
 \end{itemize}

### 2021-05-01 rules/rules21.tex
updated logics in model validation

@@
 \header{Benchmark Selection.}
-This track only has the divisions
-QF\_BV, QF\_IDL, QF\_RDL, QF\_LIA, QF\_LRA, QF\_LIRA.
-%
-This year all but the first are experimental divisions.
+This track has the divisions
+QF\_BV, QF\_IDL, QF\_RDL, QF\_LIA, QF\_LRA, QF\_LIRA,
+QF\_UFIDL, QF\_UFLIA, and QF\_UFLRA.
+%
+This year all UF logics (with uninterpreted functions) are experimental divisions.
 %

### 2021-05-01 rules/rules21.tex
Updated dates

@@
 \title{15th International Satisfiability Modulo Theories Competition
-  (SMT-COMP 2020): Rules and Procedures}
+  (SMT-COMP 2021): Rules and Procedures}
 
@@
 \begin{description}
-\item[March~1] Deadline for new benchmark contributions.
-\item[April~20] Final versions of competition tools (e.g., benchmark
+\item[March~15] Deadline for new benchmark contributions.
+\item[May~7] Final versions of competition tools (e.g., benchmark
   scrambler) are made available.  Benchmark libraries are frozen.
-\item[May~4] Deadline for first versions of solvers (for all tracks),
+\item[May~30] Deadline for first versions of solvers (for all tracks),
   including information about which tracks and divisions are being
   entered, and magic numbers for benchmark scrambling.
-\item[May~26] Deadline for final versions of solvers, including
+\item[June~13] Deadline for final versions of solvers, including
   system descriptions.
-\item[May~27] Opening value of NYSE Composite Index used to compute
+\item[June~15] Opening value of NYSE Composite Index used to compute
   random seed for competition tools.
-\item[July~5/6] SMT Workshop; end of competition, presentation of
+\item[July~18/19] SMT Workshop; end of competition, presentation of
   results.
@@
 
-SMT-COMP~2020 is part of the SMT Workshop~2020
-(\url{http://smt-workshop.cs.uiowa.edu/2020/index.shtml}),
-which is affiliated with IJCAR~2020 (\url{https://ijcar2020.org/}).
+SMT-COMP~2021 is part of the SMT Workshop~2021
+(\url{http://smt-workshop.cs.uiowa.edu/2021/}),
+which is affiliated with CAV~2021 (\url{http://i-cav.org/2021/}).
 The SMT Workshop will include a block of time to present the results of the
@@
 
-SMT-COMP 2020 will have four tracks: the \maintrack (before 2019: Main Track),
+SMT-COMP 2021 will have four tracks: the \maintrack (before 2019: Main Track),
 the \inctrack (before 2019: Application Track), the \ucoretrack, and the
@@
   and Tjark Weber.}  describes the rules and competition procedures for
-SMT-COMP~2020.
+SMT-COMP~2021.
 %
 As in previous years, we have revised the rules slightly.  Some rule
-changes in 2020 aim specifically at making the competition more
-manageable to run, as both the popularity of the competition and the
-benchmark library have grown over time.
+changes in 2021 are designed to not overly punish solvers producing
+syntactically wrong output, by treating those outputs as unknown and
+not as unsoundness.  Moreover, we added more divisions to the model
+validation track.
 %
@@
 the above web form (accompanying information) until the end of
-{\bf May~4, 2020} anywhere on earth.
+{\bf May~30, 2021} anywhere on earth.
 After this date \emph{no new entrants} will be accepted.
 However, updates to existing entrants on StarExec
-will be accepted until the end of {\bf May~26, 2020} anywhere on earth.
+will be accepted until the end of {\bf June~13, 2021} anywhere on earth.
 
@@
 The bulk of the computation will take place during the weeks leading
-up to SMT 2020.  Intermediate results will be regularly posted to the
+up to SMT 2021.  Intermediate results will be regularly posted to the
 SMT-COMP website as the competition runs.
@@
 \header{New benchmarks.}
-The deadline for submission of new benchmarks is {\bf March~1, 2020}.
+The deadline for submission of new benchmarks was {\bf March~15, 2021}.
 The organizers, in collaboration with the SMT-LIB maintainers, will be
-checking and curating these until {\bf April~20, 2020}.  The SMT-LIB
+checking and curating these until {\bf May~7, 2021}.  The SMT-LIB
 maintainers intend to make a new release of the benchmark library
@@
 
-SMT-COMP 2020 is organized under the direction of the SMT Steering
+SMT-COMP 2021 is organized under the direction of the SMT Steering
 Committee. The organizing team is
@@
 \item \href{http://homepages.dcc.ufmg.br/~hbarbosa/}{Haniel Barbosa}~-- Universidade Federal de Minas Gerais, Brazil
-\item \href{https://jochen-hoenicke.de/}{Jochen Hoenicke}~-- Universit\"at Freiburg, Germany
+\item \href{https://jochen-hoenicke.de/}{Jochen Hoenicke}~-- Universit\"at Freiburg, Germany (chair)
 \item \href{http://www.inf.usi.ch/postdoc/hyvarinen/}{Antti Hyv\"arinen}~--
-    Universit\`a della Svizzera italiana, Switzerland (chair)
+    Universit\`a della Svizzera italiana, Switzerland
 \end{itemize}

### 2021-05-04 rules/rules21.tex
some more trivial updates for this year

@@
 \and
-Jochen Hoenicke\\
+Jochen Hoenicke (chair)\\
 Universit\"at Freiburg\\
@@
 \and
-Antti Hyvarinen (chair)\\
+Antti Hyvarinen\\
 Universita della Svizzera italiana \\
@@
       solvers (including non-competitive solvers) in less than one second in
-          the corresponding track in 2018 or 2019.
+          the corresponding track in 2018, 2019, and 2020.
     \item \emph{\ucoretrack.} All benchmarks with only a single assertion.

### 2021-05-06 rules/rules21.tex
formatting
adding new MV logics to section 6

@@
 %
-The \ucoretrack will use a selection of
-non-incremental benchmarks with status \texttt{unsat} and more than one
-top-level assertion, modified to use named top-level assertions.  The
-\mvaltrack will use a selection of non-incremental benchmarks with status
-\texttt{sat} from logics QF\_BV, QF\_IDL, QF\_RDL, QF\_LIA, QF\_LRA, QF\_LIRA.
+The \ucoretrack will use a selection of non-incremental benchmarks with status
+\texttt{unsat} and more than one top-level assertion, modified to use named
+top-level assertions.  The \mvaltrack will use a selection of non-incremental
+benchmarks with status \texttt{sat} from logics QF\_BV, QF\_IDL, QF\_RDL,
+QF\_LIA, QF\_LRA, QF\_LIRA, QF\_UF, QF\_UFBV, QF\_UFIDL, QF\_UFLIA, QF\_UFLRA.
 

### 2021-05-06 rules/rules21.tex
udpating text about old overall ranking change
updating rules with new divisions change

@@
 Within each track there are multiple divisions, where each division
-uses benchmarks from a specific SMT-LIB logic (or group of logics).
+uses benchmarks from a specific group of SMT-LIB logics.
 We will recognize winners as measured by number of benchmarks solved
@@
 \begin{itemize}
+  \item {\bf \maintrack.} Previously, every logic in the \maintrack was its own
+  division.  There are currently over 60 logics in SMT-LIB, which makes a short
+  summary of the results impossible.  On the other hand the competition-wide
+  scoring does a comparison between solvers that cannot be sensibly compared as
+  they support completely disjoint logics. To get a better overview, this year
+  we have in the \maintrack divisions combining related logics, thus reducing
+  the number of divisions and obtaining more manageable and meaningful results.
+  Rather than logics, solvers will declare the divisions they enter in the
+  \maintrack. They will be ranked by the number of benchmarks they solve across
+  all logics in the divisions entered.
+  \begin{itemize}
+    \item Quantifier-free divisions:
+    \begin{itemize}
+      \item QF\_Equality\\
+Logics: QF\_UF, QF\_AX, QF\_DT
+\item QF\_Equality+LinearArith\\
+Logics: QF\_ALIA, QF\_AUFLIA, QF\_UFLIA, QF\_UFLRA, QF\_UFIDL
+\item QF\_Equality+NonLinearArith\\
+Logics: QF\_UFNRA, QF\_UFNIA, QF\_ANIA, QF\_AUFNIA
+\item QF\_Equality+BVArith\\
+Logics: QF\_ABV, QF\_UFBV, QF\_AUFBV
+\item QF\_LinearIntArith\\
+Logics: QF\_LIA, QF\_LIRA, QF\_IDL
+\item QF\_LinearRealArith\\
+Logics: QF\_LRA, QF\_RDL
+\item QF\_BV
+\item QF\_FPArith\\
+Logics: QF\_FP, QF\_UFFP, QF\_FPLRA, QF\_BVFP, QF\_ABVFP, QF\_BVFPLRA, QF\_ABVFPLRA
+\item QF\_NonLinearIntArith\\
+Logics: QF\_NIA, QF\_NIRA
+\item QF\_NRA
+\item QF\_Strings\\
+Logics: QF\_S, QF\_SLIA
+
+    \end{itemize}
+    \item Divisions with quantifiers:
+    \begin{itemize}
+      \item Equality\\
+Logics: UF, UFDT
+\item Equality+LinearArith\\
+Logics: ALIA, AUFLIA, UFLIA, UFIDL, AUFLIRA, UFLRA, UFDTLIA, UFDTLIRA, AUFDTLIA, AUFDTLIRA
+\item Equality+MachineArith\\
+Logics: AUFFPDTLIRA, UFFPDTLIRA, UFFPDTNIRA, ABVFP, ABVFPLRA, UFBV, AUFBVDTLIA
+\item Equality+NonLinearArith\\
+Logics: AUFDTNIRA, UFDTNIA, UFDTNIRA, AUFNIA, AUFNIRA, UFNIA
+\item Arith\\
+Logics: LRA, LIA, NIA, NRA
+\item BV
+\item FPArith\\
+Logics: BVFP, FP, BVFPLRA, FPLRA
+    \end{itemize}
+  \end{itemize}
+
+  \rationale{We are aware that any partitioning of logics into divisions can be
+    disadvantageous to some solvers that support some but not all logics in the
+    division. We believe however that to a lesser extent this situation is already
+    common, thinking of different features among problems in the same logic. So in
+    our view the disadvantages are offset by the benefit of having a better
+    presentation of the results. Regardless, results per logic will still be
+    accessible within the results page of a given division, similarly to how one can
+    now see the different scores other than sequential for a given logic.
+
+    The divisions above were defined according to the following rationale:
+
+    \begin{itemize}
+      \item Similar logics that do not standout by themselves were combined.
+      \item Integer and real, as well as bit-vector and floating-point,
+      arithmetics are separated
+      \begin{itemize}
+        \item Note that the ``Arith'' division goes against this. However, its
+        composing logics do not standout out by themselves as currently
+        represented in SMT-LIB.
+      \end{itemize}
+      \item Arrays and datatypes are handled in a similar enough way to UF to be combined with it.
+        \item Floating-point logics are combined since generally this is the dominating component for any logic contaning FP.
+    \end{itemize}
+  }
+
   \item {\bf The option \akey{:print-success} is explicitly set to
@@
 The \maintrack track will consist of selected non-incremental benchmarks in
-each of the competitive logic divisions.  Each benchmark will be presented to
+each of the competitive divisions.  Each benchmark will be presented to
 the solver as its first command-line argument.  The solver is then expected to
@@
 \header{Divisions.}
+
 Within each track there are multiple divisions, and each division selects
-benchmarks from a specific SMT-LIB logic in the SMT-LIB benchmark library.
+benchmarks from a specific group of SMT-LIB logics in the SMT-LIB benchmark
+library.
 
@@
 \header{Benchmark demographics.}
-The set of all SMT-LIB benchmarks in a given division can be naturally
-partitioned to sets containing benchmarks that are similar from the user
-community perspective.  Such benchmarks could all come from the same
+%
+The set of all SMT-LIB benchmarks in the logics of a given division can be
+naturally partitioned to sets containing benchmarks that are similar from the
+user community perspective.
+%
+Such benchmarks could all come from the same
 application domain, be generated by the same tool, or have some other
@@
 %
-The organizers believe that the submitters have the best information on
-the common identity of their benchmarks and therefore partition each
-division based on the bottom-level directory imposed by each submitter.
-These partitions are referred to as \emph{families}.
+The organizers believe that the submitters have the best information on the
+common identity of their benchmarks and therefore partition each logic in a
+division based on the bottom-level directory imposed by each submitter.  These
+partitions are referred to as \emph{families}.
 
@@
   The number of benchmarks in a division based on the size of the
-  corresponding logic in SMT-LIB will be limited as follows.
+  corresponding logics in SMT-LIB will be limited as follows.
   Let $n$ be the number of benchmarks in an SMT-LIB logic, then
@@
 unsatisfiable instances.
+%
+Finally, for the \maintrack all the above scores, in divisions composed by more
+than one logic, will be presented not only for the overall division but also for
+each logic composing the division.
 
@@
 
-This year we will replace the competition-wide score with two new \emph{rankings} that select one solver per division and then rank those solvers.
+This score has been replaced the competition-wide score with two \emph{rankings} that select one solver per division and then rank those solvers.
 The rationale here is to take the focus away from the number of divisions entered and focus on measures that make sense to use to compare different divisions.

### 2021-05-06 rules/rules21.tex
parallel and cloud tracks

@@
 \newcommand{\challtrack}{Industry-Challenge Track\xspace}
+\newcommand{\paralleltrack}{Parallel Track\xspace}
+\newcommand{\cloudtrack}{Cloud Track\xspace}
 
@@
 the \inctrack (before 2019: Application Track), the \ucoretrack, and the
-\mvaltrack.
+\mvaltrack.  In addition there will be two experimental tracks sponsored
+by AWS: the \paralleltrack{} and the \cloudtrack{}.
 %
@@
     a solver that outputs a slightly malformed model.  This year the error
-    result is only given for unsat cores that are not unsatifiable or models
+    result is only given for unsat cores that are not unsatisfiable or models
     that don't satisfy the formula. Of courses, answering sat in unsat
@@
   \item {\bf Benchmark Selection.}
-    This year we increase the percentage of the benchmarks that are run in the competition back to 50 \%.
-    \rationale{We feel that increasing the number of benchmarks is managable and 50 \% is a more round number than 40 \%.}
+      Apart from the \cloudtrack{} and the \paralleltrack{}, this year we
+        increase the percentage of the benchmarks that are run in the
+        competition back to 50 \%.
+    \rationale{We feel that increasing the number of benchmarks is
+    manageable and 50 \% is a more round number than 40 \%.  The
+    \cloudtrack{} and \paralleltrack{} need to be run on a more
+    restricted set because of the amount of parallel resources we
+    provide for the tracks.}
 
@@
 subsolvers from different groups of authors is not.
-Portfolio solver are in general \textbf{not allowed}.
+Portfolio solver are in general \textbf{allowed only in the
+\paralleltrack{} and \cloudtrack{}}.
 If you are unsure if your tool is a portfolio solver according to this
@@
 An entrant to SMT-COMP is a solver submitted by its authors using
-the StarExec (\url{http://www.starexec.org}) service.
+the StarExec (\url{http://www.starexec.org}) service, or, for
+\paralleltrack{} and \cloudtrack{}, otherwise communicated to the
+organisers.
 
@@
 For participation in SMT-COMP, a solver must be uploaded to StarExec
-and made publicly available.  StarExec supports solver configurations;
+and made publicly available, or communicated separately to the
+organisers for the \cloudtrack{} and \paralleltrack{}.  StarExec supports solver configurations;
 for clarity, \emph{each submitted solver must have one configuration
@@
     on the wrapped solvers or base solver
-  \item appropriate acknowledgement of tools other than SMT solvers called by
+  \item appropriate acknowledgment of tools other than SMT solvers called by
     the system (e.g., SAT solvers) that are not written by the authors of the
@@
 
-SMT-COMP entrants must be submitted via StarExec (solvers) \emph{and}
+SMT-COMP entrants must be submitted via StarExec (solvers), or
+communicated separately to the organisers for the \paralleltrack{} and
+\cloudtrack{}, \emph{and}
 the above web form (accompanying information) until the end of
@@
 After this date \emph{no new entrants} will be accepted.
-However, updates to existing entrants on StarExec
+However, updates to existing entrants on StarExec or \paralleltrack{}
+and \cloudtrack{}
 will be accepted until the end of {\bf June~13, 2021} anywhere on earth.
@@
 and not for adding new features, as there may be no opportunity to do
-extensive testing using StarExec after the initial deadline.
-
-The solver versions that are present on StarExec at the conclusion of
+extensive testing using StarExec or other means after the initial deadline.
+
+The solver versions that are present on StarExec or communicated
+otherwise to the organisers for \paralleltrack{}and \cloudtrack{} at the conclusion of
 the grace period will be the ones used for the competition.  Versions
@@
 made public.
-Solvers will be made publicly available after the competition and it is a minimum licence requirement that (i) solvers can be distributed in this way, and (ii) all submitted solvers may be freely used for academic evaluation purposes.
+Solvers will be made publicly available after the competition and it is a minimum license requirement that (i) solvers can be distributed in this way, and (ii) all submitted solvers may be freely used for academic evaluation purposes.
 
 %\an{intro of the section maybe, we should add there that solvers will be archived on the website and so on.
-Interestingly, we replied to the reviewer in the report that the solvers are publicly available in the StarExec space when asked about reproducability, but in the past it was never defined under which terms.}
+Interestingly, we replied to the reviewer in the report that the solvers are publicly available in the StarExec space when asked about reproducibility, but in the past it was never defined under which terms.}
 
@@
 
+The limits for \paralleltrack{} and \cloudtrack{} are available at
+\url{https://smt-comp.github.io/2021/news/2021-02-05-parallel-and-cloud-tracks}.
+
 \header{Persistent State.}
@@
 
+\subsection{\paralleltrack{}}
+The \paralleltrack{} will evaluate the capability of solvers to
+determine the satisfiability of problems in a shared-memory parallel
+computing environment.  The track will be experimental.
+
+\header{Benchmark Selection.}
+We will select non-incremental benchmarks from the smt-lib divisions
+based on the participating solvers.  In total 500 instances will be
+chosen such that their run times are sufficiently high based on our
+estimation.  The track will be experimental.
+
+\header{Time Limit.}
+This track will use a wall-clock time limit of 20 minutes per
+solver/benchmark pair.
+
+\subsection{\cloudtrack{}}
+The \cloudtrack{} will evaluate the capability of solvers to determine
+the satisfiability of problems in a distributed computing environment.
+
+\header{Benchmark Selection.}
+We will select non-incremental benchmarks from the smt-lib divisions
+based on the participating solvers.  In total 500 instances will be
+chosen such that their run times are sufficiently high based on our
+estimation.
+
+\header{Time Limit.}
+This track will use a wall-clock time limit of 20 minutes per
+solver/benchmark pair.
+
 \section{Benchmarks and Problem Divisions}
@@
 \header{Benchmark sources.}
-Benchmarks for each division will be drawn from the SMT-LIB benchmark library.
-The \maintrack will use a subset of all \emph{non-incremental} benchmarks and
-the \inctrack will use a subset of all \emph{incremental} benchmarks.
+Benchmarks for each division will be drawn from the SMT-LIB benchmark
+library.  The \maintrack, \paralleltrack{} and \cloudtrack{} will use a
+subset of all \emph{non-incremental} benchmarks and the \inctrack will
+use a subset of all \emph{incremental} benchmarks.
 %
@@
 
-\subsubsection{\maintrack}% and \challtrack}
-  For the \maintrack the error score $e$ and the correctly
-  solved score $n$ are defined as
+\subsubsection{\maintrack, \paralleltrack, and \cloudtrack}
+  For the \maintrack, \paralleltrack, and \cloudtrack the error score
+  $e$ and the correctly solved score $n$ are defined as
   \begin{itemize}
@@
 The sequential score for a division is computed for \emph{all} tracks
-\emph{except} the \inctrack
-% and incremental benchmarks in the \challtrack
+\emph{except} the \inctrack, \paralleltrack, and \cloudtrack.
 \footnote{Since incremental track benchmarks may be partially
@@
 would require information not provided by the parallel performance, e.g.,
-detailed timing information for each result.}.  It is defined for a
+detailed timing information for each result.  Due to the nature of
+\paralleltrack and \cloudtrack we will not consider the sequential
+scores}.  It is defined for a
 participating solver in a division with $M$ benchmarks as the sum of all the
@@
 solver with the higher corresponding CPU (resp. wall-clock) time rank for
-sequantial (resp. parallel) scoring.
+sequential (resp. parallel) scoring.
 This can be computed per scoring system.

### 2021-05-07 rules/rules21.tex
Cloud track explicitly marked experimental
Added notes on cloud & parallel tracks in benchmark scoring

@@
 chosen such that their run times are sufficiently high based on our
-estimation.  The track will be experimental.
+estimation.
 
@@
 the satisfiability of problems in a distributed computing environment.
+The track will be experimental.
 
@@
 \header{Divisions.}
-
+%
 Within each track there are multiple divisions, and each division selects
@@
 guarantees on including new benchmarks.  In \textbf{all} tracks
-% \textbf{except} the \challtrack,
+\textbf{except} the \paralleltrack and \cloudtrack
 the following selection process will be used.
@@
 \header{Error Score ($\mathbf{e}$).}
-For the \maintrack, and \inctrack,%
-% and \challtrack
+For the \maintrack, \inctrack, \paralleltrack, and \cloudtrack
 $e$ is the number of returned
@@
 \header{Correctly Solved Score ($\mathbf{n}$).}
-For the \maintrack, \inctrack, and \mvaltrack,
+For the \maintrack, \inctrack, \mvaltrack, \paralleltrack, and
+\cloudtrack,
 $N$ is defined as the number of \akey{check-sat} commands, and

### 2021-05-07 rules/rules21.tex
updating divisions with new logics

@@
       \item QF\_Equality\\
-Logics: QF\_UF, QF\_AX, QF\_DT
+Logics: QF\_UF, QF\_AX, QF\_DT, QF\_UFDT
 \item QF\_Equality+LinearArith\\
@@
 Logics: QF\_UFNRA, QF\_UFNIA, QF\_ANIA, QF\_AUFNIA
-\item QF\_Equality+BVArith\\
+\item QF\_Equality+Bitvec\\
 Logics: QF\_ABV, QF\_UFBV, QF\_AUFBV
+\item QF\_Equality+Bitvec+Arith\\
+Logics: QF\_AUFBVLIA, QF\_AUFBVNIA, QF\_UFBVLIA
 \item QF\_LinearIntArith\\
@@
 Logics: QF\_LRA, QF\_RDL
-\item QF\_BV
+\item QF\_Bitvec\\
+Logics: QF\_BV
 \item QF\_FPArith\\
-Logics: QF\_FP, QF\_UFFP, QF\_FPLRA, QF\_BVFP, QF\_ABVFP, QF\_BVFPLRA, QF\_ABVFPLRA
+Logics: QF\_FP, QF\_UFFP, QF\_FPLRA, QF\_BVFP, QF\_ABVFP, QF\_AUFBVFP, QF\_BVFPLRA, QF\_ABVFPLRA
 \item QF\_NonLinearIntArith\\
 Logics: QF\_NIA, QF\_NIRA
-\item QF\_NRA
+\item QF\_NonLinearRealArith\\
+Logics: QF\_NRA
 \item QF\_Strings\\
-Logics: QF\_S, QF\_SLIA
+Logics: QF\_S, QF\_SLIA, QF\_SNIA
 
@@
 \item Equality+MachineArith\\
-Logics: AUFFPDTLIRA, UFFPDTLIRA, UFFPDTNIRA, ABVFP, ABVFPLRA, UFBV, AUFBVDTLIA
+Logics: AUFFPDTLIRA, UFFPDTLIRA, UFFPDTNIRA, ABVFP, ABVFPLRA, AUFBV, AUFBVFP,
+AUFBVDTLIA, UFBV, UFBVFP, UFBVLIA
 \item Equality+NonLinearArith\\
-Logics: AUFDTNIRA, UFDTNIA, UFDTNIRA, AUFNIA, AUFNIRA, UFNIA
+Logics: ANIA, AUFDTNIRA, UFDTNIA, UFDTNIRA, AUFNIA, AUFNIRA, UFNIA, UFNRA
 \item Arith\\
 Logics: LRA, LIA, NIA, NRA
-\item BV
+\item Bitvec\\
+Logics: BV
 \item FPArith\\

### 2021-05-07 rules/rules21.tex
updating division split for all tracks

@@
 \begin{itemize}
-  \item {\bf \maintrack.} Previously, every logic in the \maintrack was its own
-  division.  There are currently over 60 logics in SMT-LIB, which makes a short
-  summary of the results impossible.  On the other hand the competition-wide
-  scoring does a comparison between solvers that cannot be sensibly compared as
-  they support completely disjoint logics. To get a better overview, this year
-  we have in the \maintrack divisions combining related logics, thus reducing
-  the number of divisions and obtaining more manageable and meaningful results.
-  Rather than logics, solvers will declare the divisions they enter in the
-  \maintrack. They will be ranked by the number of benchmarks they solve across
-  all logics in the divisions entered.
+  \item {\bf Divisions now may contain more than one logic.} Previously, every
+  division was comprised of a single logic. There are currently over 60 logics
+  in SMT-LIB, which makes a short summary of the results impossible.  On the
+  other hand the competition-wide scoring does a comparison between solvers that
+  cannot be sensibly compared as they support completely disjoint logics. To get
+  a better overview, this year divisions will combine related logics, thus
+  reducing the number of divisions and obtaining more manageable and meaningful
+  results.  Rather than logics, solvers will declare the divisions they
+  enter. They will be ranked by the number of benchmarks they solve across all
+  logics in the divisions entered.
   \begin{itemize}
@@
   \item {\bf \mvaltrack.}  Last year's competition introduced the experimental
-    divisions QF\_IDL, QF\_RDL, QF\_LIA, QF\_LRA, QF\_LIRA in the
-    model validation track.  This year these will no longer be experimental.
-    In addition, new experimental divisions QF\_UF, QF\_UFBV,
-    QF\_UFIDL, QF\_UFLIA, QF\_UFLRA will be added.
-
-  \rationale{There were only small issues with these divisions, so there is no
-    reason to keep it experimental. For the new divisions, as before, given the
+  divisions QF\_IDL, QF\_RDL, QF\_LIA, QF\_LRA, QF\_LIRA in the model validation
+  track.  This year, the divisions containing these logics will no longer be
+  experimental.  In addition, we will add this year new experimental divisions
+  QF\_Equality (only with QF\_UF benchmarks), QF\_Equality+LinearArith (only with
+  QF\_UFIDL, QF\_UFLIA, and QF\_UFLRA benchmarks), and QF\_Equality+Bitvec (only with
+  QF\_UFBV benchmarks).
+
+  \rationale{There were only small issues with last year's divisions, so there is no
+    reason to keep them experimental. For the new divisions, as before, given the
     inconsistencies across different model producing solvers, we proceed in an
@@
 %
-Finally, for the \maintrack all the above scores, in divisions composed by more
-than one logic, will be presented not only for the overall division but also for
-each logic composing the division.
+Finally, in divisions composed by more than one logic, all the above scores will
+be presented not only for the overall division but also for each logic composing
+the division.
 

### 2021-05-07 rules/rules21.tex
updating model validation track with new divisions

@@
 
-  \rationale{There were only small issues with last year's divisions, so there is no
-    reason to keep them experimental. For the new divisions, as before, given the
-    inconsistencies across different model producing solvers, we proceed in an
-    experimental fashion to push for model standardization.}
+  \rationale{There were only small issues with last year's divisions, so there
+    is no reason to keep them experimental. For the new divisions, as before,
+    given the inconsistencies across different model producing solvers, we
+    proceed in an experimental fashion to push for model standardization. Since
+    both arrays and datatypes add further complications on top of uninterpreted
+    functions, we exclude benchmarks containing those.}
 
@@
 
-\header{Benchmark Selection.}
-This track has the divisions
-QF\_BV, QF\_IDL, QF\_RDL, QF\_LIA, QF\_LRA, QF\_LIRA,
-QF\_UFIDL, QF\_UFLIA, and QF\_UFLRA.
-%
-This year all UF logics (with uninterpreted functions) are experimental divisions.
-%
-It will run on a
+\header{Benchmark Selection.}  This track has the divisions QF\_Bitvec,
+QF\_LinearIntArith, QF\_LinearRealArith, QF\_Equality (only with QF\_UF
+benchmarks), QF\_Equality+LinearArith (only with QF\_UFIDL, QF\_UFLIA, and
+QF\_UFLRA benchmarks), and QF\_Equality+Bitvec (only with QF\_UFBV benchmarks).
+%
+This year all divisions with UF logics (with uninterpreted functions) are
+experimental divisions.
+%
+The track will run on a
 selection of non-incremental benchmarks with status \texttt{sat} from these
 logics (as described on page~\pageref{benchmark-selection}).
+%
+We exclude from the selection all benchmarks containing arrays or datatypes.
 

### 2021-05-07 rules/rules21.tex
Clarify what happens when running on some logics
Solver specifies which logics it supports per Track.
Solver is entered in all divisions where it supports a logic,
but only run on the logics it supports. Unsupported benchmarks
are scored as if the solver returns `unknown` in zero time.

Fix 40%/50% occurrence.

@@
 \begin{center}
-  \url{https://forms.gle/WRbJrawdb1Sko6uz5}
+  \url{https://forms.gle/9Eged2txtvJxGXeD9}
 \end{center}
-A submission \textbf{must} also include a \emph{system description} (see below)
-and a \emph{32-bit unsigned integer}.
- These integer numbers, collected from all submissions, are used to seed
- competition tools.
+For each track the submission should specify the logics which are
+supported by the solver.  A submission \textbf{must} also include a
+link to the \emph{system description} (see below) and a \emph{32-bit
+  unsigned integer}.  These integer numbers, collected from all
+submissions, are used to seed competition tools.
 
@@
 Solvers will be publicly evaluated in all tracks and divisions into
-which they have been entered.  All results of the competition will be
-made public.
-Solvers will be made publicly available after the competition and it is a minimum license requirement that (i) solvers can be distributed in this way, and (ii) all submitted solvers may be freely used for academic evaluation purposes.
+which they have been entered.
+%
+A solver enters a division in a track if it supports at least one
+logics in this division.
+%
+A solver not supporting all logics in a division will not be run on
+the benchmarks from the unsupported logics and will be scored as if it
+returned the result \texttt{unknown} within zero time.
+%
+All results of the competition will be made public. Solvers will be
+made publicly available after the competition and it is a minimum
+license requirement that (i) solvers can be distributed in this way,
+and (ii) all submitted solvers may be freely used for academic
+evaluation purposes.
 
@@
     \item \label{bench-sel-300} if $n \le 300$, all instances will be selected;
-  \item \label{bench-sel-600} if $300 < n \leq 750$, a subset of 300 instances
+  \item \label{bench-sel-600} if $300 < n \leq 600$, a subset of 300 instances
     from the logic will be selected;
-  \item \label{bench-sel-more} and if $n > 750$,
-      40\% of the benchmarks of the logic will be selected.
+  \item \label{bench-sel-more} and if $n > 600$,
+      50\% of the benchmarks of the logic will be selected.
   \end{enumerate}

### 2021-05-07 rules/rules21.tex
Use "enter" for division instead of participate
Also mention that a solver enters a division if it supports a logic
in the submission section

@@
   only}.  Moreover, the organizers must be informed of the solver's
-presence \emph{and the tracks and divisions in which it is
-  participating} via the web form at
+presence \emph{and the tracks and divisions which it enters} via the
+web form at
 \begin{center}
@@
 \end{center}
-For each track the submission should specify the logics which are
-supported by the solver.  A submission \textbf{must} also include a
+For each track the submission must specify the logics which are
+supported by the solver.  The solver will enter all divisions where it
+supports at least one logic.  A submission \textbf{must} also include a
 link to the \emph{system description} (see below) and a \emph{32-bit
@@
 A solver enters a division in a track if it supports at least one
-logics in this division.
+logic in this division.
 %

### 2021-05-07 rules/rules21.tex
fix the worst line breaks

@@
 \item Equality+LinearArith\\
-Logics: ALIA, AUFLIA, UFLIA, UFIDL, AUFLIRA, UFLRA, UFDTLIA, UFDTLIRA, AUFDTLIA, AUFDTLIRA
+Logics: \sloppy ALIA, AUFLIA, UFLIA, UFIDL, AUFLIRA, UFLRA, UFDTLIA, UFDTLIRA, AUFDTLIA, AUFDTLIRA
 \item Equality+MachineArith\\
@@
 
-  \item {\bf \mvaltrack.}  Last year's competition introduced the experimental
+  \item {\bf \mvaltrack.}  \emergencystretch.5cm Last year's competition introduced the experimental
   divisions QF\_IDL, QF\_RDL, QF\_LIA, QF\_LRA, QF\_LIRA in the model validation
@@
 \header{Benchmark Selection.}  This track has the divisions QF\_Bitvec,
-QF\_LinearIntArith, QF\_LinearRealArith, QF\_Equality (only with QF\_UF
+QF\_LinearIntArith, QF\_LinearReal\-Arith, QF\_Equality (only with QF\_UF
 benchmarks), QF\_Equality+LinearArith (only with QF\_UFIDL, QF\_UFLIA, and

### 2021-05-07 rules/rules21.tex
Updated the link for cloud & parallel track info
remove draft
Fix title

@@
 
-\usepackage{draftwatermark}
+%\usepackage{draftwatermark}
 %\usepackage{showframe}   % debug
@@
 
-\title{15th International Satisfiability Modulo Theories Competition
+\title{16th International Satisfiability Modulo Theories Competition
   (SMT-COMP 2021): Rules and Procedures}
@@
 The limits for \paralleltrack{} and \cloudtrack{} are available at
-\url{https://smt-comp.github.io/2021/news/2021-02-05-parallel-and-cloud-tracks}.
+\url{https://smt-comp.github.io/2021/parallel-and-cloud-tracks.html}.
 

### 2021-05-07 rules/rules21.tex
Fixed the number of instances in cloud & parallel tracks

@@
 The solver versions that are present on StarExec or communicated
-otherwise to the organisers for \paralleltrack{}and \cloudtrack{} at the conclusion of
+otherwise to the organisers for \paralleltrack{} and \cloudtrack{} at the conclusion of
 the grace period will be the ones used for the competition.  Versions
@@
 We will select non-incremental benchmarks from the smt-lib divisions
-based on the participating solvers.  In total 500 instances will be
+based on the participating solvers.  In total 400 instances will be
 chosen such that their run times are sufficiently high based on our

### 2021-07-18 tools/scoring/score.py
Update scoring script to give number of benchmarks in used logics

@@ -1401,9 +1401,13 @@ def md_write_file(division,
     if g_args.divisions_map and not division in allLogics:
       assert usedLogics
       allLogicsStr = ""
-      for logic in sorted(usedLogics):
-        allLogicsStr += "\n- %s" % (logic)
-
+      # sort by logic
+      usedlogics = sorted(usedLogics.items(), key = lambda x: x[0])
+      first = True
+      for logic, nBench in usedLogics.items():
+        allLogicsStr += "\n" + ("- " if first else "  ")
+        first = False
+        allLogicsStr += "%s: %s" % (logic, nBench)
       str_div += "logics:%s\n" % allLogicsStr
 
     # winners
@@ -1500,13 +1504,14 @@ def to_md_files(results_seq,
         # track string
         track_str = ""
         ext_str = ".md"
-        usedLogics = []
+        usedLogics = {}
         if g_args.divisions_map and not division in allLogics:
           tmpDf = results_seq.reset_index()
           divLogics = divisionInfo[g_tracks[track]][division]
           for logic in divLogics:
-            if len(tmpDf[tmpDf['division'] == logic] ) > 0:
-             usedLogics.append(logic)
+            logicDf = tmpDf[tmpDf['division'] == logic]
+            if len(logicDf) > 0:
+             usedLogics[logic] = logicDf['division_size'].iloc[0]
         if track == OPT_TRACK_SQ:
             md_write_file(division,
                           n_benchmarks,

### 2021-07-19 2021/presentation/slides.tex
added slides of the presentation

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%   SMT-COMP 2021 - Presentation on SMT-Workshop
%                   virtual conference in "Los Angeles"
%
%   1 hour
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[table]{beamer}
\usepackage[utf8]{inputenc}
\usepackage{xcolor}
\usepackage{tikz}
\usetikzlibrary{shapes,shapes.callouts,automata,trees}
\usetikzlibrary{decorations.pathmorphing,external,fit}
\usetikzlibrary{calc}
\usetikzlibrary{backgrounds} %used for the CEGAR figure
\usepackage{amssymb}
\usepackage{clrscode}
\usepackage{pifont}
\usepackage{pdfpages}
\geometry{papersize={16cm,9cm}}
%\tikzexternalize

\colorlet{MYred}{red!70!black}
\definecolor{MYgreen}{rgb}{.1,.5,0}
\definecolor{MYblue}{rgb}{0,.42,.714}
\colorlet{MYgray}{white!95!MYblue}
\colorlet{MYorange}{orange!80!black}
\definecolor{gold}{rgb}{.8,.6,0}
\colorlet{silver}{white!55!black}
\colorlet{bronze}{brown!70!black}
\def\tick{\ding{52}}
\def\cross{\ding{54}}

%%%%%%%%%%%%%%%%%%%%
%%% Beamer stuff %%%
%%%%%%%%%%%%%%%%%%%%
\usetheme{default}
\useinnertheme{rounded}
\setbeamertemplate{frametitle}[default][center]
\setbeamertemplate{footline}{\quad\hfill\footnotesize\insertframenumber\strut\kern1em\vskip2pt}
\setbeamertemplate{navigation symbols}{}
\setbeamertemplate{itemize/enumerate subbody begin}{\normalsize}
\usefonttheme[onlymath]{serif} % Nicer formulas
\setbeamercolor{block body}{bg=black!10}
\setbeamercolor{block title}{bg=black!20}

\AtBeginSection[]{
  \begin{frame}
  \vfill
  \centering
  \begin{beamercolorbox}[sep=8pt,center,shadow=true,rounded=true]{title}
    \usebeamerfont{title}\insertsectionhead\par%
  \end{beamercolorbox}
  \vfill
  \end{frame}
}

\def\emph#1{\textcolor{MYblue}{#1}}

%%% Titel, Autor und Datum des Vortrags:
\title{SMT-COMP 2021\\
16th International Satisfiability Modulo Theory Competition}
\author{Haniel Barbosa \and \emph{Jochen Hoenicke} \and Antti Hyv\"arinen}
\date{July 18, 2021}

%% Institut
\institute{
  Universidade Federal de Minas Gerais, Brazil \and
  Albert-Ludwigs-Universit\"at Freiburg, Germany \and
  Universita della Svizzera italiana, Switzerland
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% MACROS

% database symbol (from stackexchange)

\makeatletter
\tikzset{
    database/.style={
        path picture={
            \draw (0, 1.5*\database@segmentheight) circle [x radius=\database@radius,y radius=\database@aspectratio*\database@radius];
            \draw (-\database@radius, 0.5*\database@segmentheight) arc [start angle=180,end angle=360,x radius=\database@radius, y radius=\database@aspectratio*\database@radius];
            \draw (-\database@radius,-0.5*\database@segmentheight) arc [start angle=180,end angle=360,x radius=\database@radius, y radius=\database@aspectratio*\database@radius];
            \draw (-\database@radius,1.5*\database@segmentheight) -- ++(0,-3*\database@segmentheight) arc [start angle=180,end angle=360,x radius=\database@radius, y radius=\database@aspectratio*\database@radius] -- ++(0,3*\database@segmentheight);
        },
        minimum width=2*\database@radius + \pgflinewidth,
        minimum height=3*\database@segmentheight + 2*\database@aspectratio*\database@radius + \pgflinewidth,
    },
    database segment height/.store in=\database@segmentheight,
    database radius/.store in=\database@radius,
    database aspect ratio/.store in=\database@aspectratio,
    database segment height=0.1cm,
    database radius=0.25cm,
    database aspect ratio=0.35,
}
\makeatother

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\begin{frame}
  \titlepage
\end{frame}

\begin{frame}
  \frametitle{SMT-COMP}

  \begin{minipage}[b]{.6\textwidth}
    Annual competition for \emph{SMT solvers}\\
    on (a selection of) benchmarks from \emph{SMT-LIB}
  \end{minipage}%
  \begin{minipage}{.4\textwidth}
    \begin{block}{History}
      \begin{tabular}{rp{3cm}}
        \textbf{2005} & first competition \\
        \textbf{2013} & evaluation instead \\
        & of competition\\
        \textbf{2014} & since then hosted\\
        & by \emph{StarExec}\\
        \textbf{2021} & 16th competition
      \end{tabular}
    \end{block}
  \end{minipage}

  Goals:
  \begin{itemize}
  \item spur development of SMT solver implementations
  \item promote SMT solvers and their usage
  \item support the SMT-LIB project
    \begin{itemize}
    \item to promote and develop the SMT-LIB format
    \item to collect relevant benchmarks
    \end{itemize}
  \item engage and include new members
  \end{itemize}

\end{frame}

\begin{frame}
  \frametitle{SMT Solvers and SMT-LIB}
  SMT Solver
  \begin{itemize}
  \item checks formulas 
    in \emph{SMT-LIB} format
    for \emph{satisfiability modulo theories}
  \end{itemize}
  \bigskip

  SMT-LIB is
  \begin{enumerate}
  \item a \emph{language} in which benchmarks are written
  \item a community effort to \emph{collect benchmarks}
  \end{enumerate}
  \medskip

  \begin{columns}
    \begin{column}{0.4\textwidth}
      \begin{block}{Non-incremental}
        381\,683 instances {\small (+5082)} \\
        with 1 query each \\
        in 79 logics {\small (+9)}.
      \end{block}
    \end{column}
    \begin{column}{0.4\textwidth}
      \begin{block}{Incremental}
        43\,284 instances {\small (+19\,073)}\\
        with 33\,998\,794 queries {\small (+554\,499)} \\
        in 35 logics {\small (+2)}.
      \end{block}
    \end{column}
    \begin{column}{0.08\textwidth}
    \end{column}
  \end{columns}
\end{frame}

\begin{frame}
  \frametitle{SMT-LIB Logics}

  \noindent\makebox[\textwidth]{%
  \begin{tikzpicture}[xscale=2.55,yscale=.39]
    \uncover<1-3> {
    % Arith
    \node at (3,14) {\small LIA};
    \node at (3,13) {\small LRA};
    \node at (3,12) {\small NIA};
    \node at (3,11) {\small NRA};
    % Equality
    \node at (3,9) {\small UF};
    \node at (3,8) {\small UFDT};
    % Bitvec
    \node at (3,6) {\small BV};
    % FPArith
    \node at (3,4) {\small BVFP};
    \node at (3,3) {\small BVFPLRA};
    \node at (3,2) {\small FP};
    \node at (3,1) {\small FPLRA};
    % Equality+LinearArith
    \node at (4,15) {\small ALIA};
    \node at (4,14) {\small AUFLIA};
    \node at (4,13) {\small AUFLIRA};
    \node at (4,12) {\small AUFDTLIA};
    \node at (4,11) {\small AUFDTLIRA};
    \node at (5,15) {\small UFDTLIA};
    \node at (5,14) {\small UFDTLIRA};
    \node at (5,13) {\small UFIDL};
    \node at (5,12) {\small UFLIA};
    \node at (5,11) {\small UFLRA};
    % Equality+NonLinearArith
    \node at (4,10) {\small ANIA};
    \node at (4,9) {\small AUFNIA};
    \node at (4,8) {\small AUFNIRA};
    \node at (4,7) {\small AUFDTNIRA};
    \node at (5,10) {\small UFDTNIA};
    \node at (5,9) {\small UFDTNIRA};
    \node at (5,8) {\small UFNIA};
    \node at (5,7) {\small UFNRA};
    % Equality+MachinedArith
    \node at (4,6) {\small ABV};
    \node at (4,5) {\small ABVFP};
    \node at (4,4) {\small ABVFPLRA};
    \node at (4,3) {\small AUFBV};
    \node at (4,2) {\small AUFBVFP};
    \node at (4,1) {\small AUFBVDTLIA};
    \node at (4,0) {\small AUFBVDTNIA};
    \node at (5,6) {\small AUFFPDTLIRA};
    \node at (5,5) {\small AUFFPDTNIRA};
    \node at (5,4) {\small UFBV};
    \node at (5,3) {\small UFBVFP};
    \node at (5,2) {\small UFBVLIA};
    \node at (5,1) {\small UFFPDTLIRA};
    \node at (5,0) {\small UFFPDTNIRA};

    %QF_LinearIntArith
    \node at (0,14) {\small QF\_IDL};
    \node at (0,13) {\small QF\_LIA};
    \node at (0,12) {\small QF\_LIRA};
    %QF_LinearRealArith
    \node at (0,11) {\small QF\_RDL};
    \node at (0,10) {\small QF\_LRA};
    %QF_NonLinearIntArith
    \node at (0,9) {\small QF\_NIA};
    \node at (0,8) {\small QF\_NIRA};
    %QF_NonLinearRealArith
    \node at (0,7) {\small QF\_NRA};
    %QF_Equality
    \node at (0,6) {\small QF\_AX};
    \node at (0,5) {\small QF\_DT};
    \node at (0,4) {\small QF\_UF};
    \node at (0,3) {\small QF\_UFDT};
    %QF_Bitvec
    \node at (0,2) {\small QF\_BV};
    %QF_Strings
    \node at (0,1) {\small QF\_S};
    \node at (1,1) {\small QF\_SLIA};
    \node at (2.05,1) {\small QF\_SNIA};
    %QF_Equality+LinearArith
    \node at (1,14) {\small QF\_ALIA};
    \node at (1,13) {\small QF\_AUFLIA};
    \node at (1,12) {\small QF\_UFIDL};
    \node at (1,11) {\small QF\_UFLIA};
    \node at (1,10) {\small QF\_UFDTLIRA};
    \node at (1,9) {\small QF\_UFLRA};
    %QF_Equality+NonLinearArith
    \node at (1,8) {\small QF\_ANIA};
    \node at (1,7) {\small QF\_AUFNIA};
    \node at (1,6) {\small QF\_UFNIA};
    \node at (1,5) {\small QF\_UFNRA};
    %QF_Equality+Bitvec
    \node at (1,4) {\small QF\_ABV};
    \node at (1,3) {\small QF\_AUFBV};
    \node at (1,2) {\small QF\_UFBV};
    %QF_Equality+Bitvec+Arith
    \node at (2.05,4) {\small QF\_AUFBVLIA};
    \node at (2.05,3) {\small QF\_AUFBVNIA};
    \node at (2.05,2) {\small QF\_UFBVLIA};
    %QF_FPArith
    \node at (2.05,14) {\small QF\_ABVFP};
    \node at (2.05,13) {\small QF\_ABVFPLRA};
    \node at (2.05,12) {\small QF\_AUFBVFP};
    \node at (2.05,11) {\small QF\_BVFP};
    \node at (2.05,10) {\small QF\_BVFPLRA};
    \node at (2.05,9) {\small QF\_FP};
    \node at (2.05,8) {\small QF\_FPLRA};
    \node at (2.05,7) {\small QF\_UFFP};
    \node at (2.05,6) {\small QF\_UFFPDTLIRA};
    }
    %
    \uncover<2-> {
      \draw (2.6,-0.5) -- (2.6,17);
      \node at (1,16.5) {Quantifier-free};
      \node at (4,16.5) {Quantified};
    }
    \uncover<3-> {
      \draw (-.5,.5) rectangle (2.6,1.5);
      \draw (-.5,1.5) rectangle (.5,2.5);
      \draw (-.5,2.5) rectangle (.5,6.5);
      \draw (-.5,6.5) rectangle (.5,7.5);
      \draw (-.5,7.5) rectangle (.5,9.5);
      \draw (-.5,9.5) rectangle (.5,11.5);
      \draw (-.5,11.5) rectangle (.5,14.5);
      \draw (.5,1.5) rectangle (1.5,4.5);
      \draw (.5,4.5) rectangle (1.5,8.5);
      \draw (.5,8.5) rectangle (1.5,14.5);
      \draw (1.5,1.5) rectangle (2.6,5);
      \draw (1.5,5) rectangle (2.6,14.5);

      \draw (2.6,0) rectangle (3.5,5);
      \draw (2.6,5) rectangle (3.5,7);
      \draw (2.6,7) rectangle (3.5,10);
      \draw (2.6,10) rectangle (3.5,15);
      \draw (3.5,-.5) rectangle (5.6,6.5);
      \draw (3.5,6.5) rectangle (5.6,10.5);
      \draw (3.5,10.5) rectangle (5.6,15.5);
    }
    \uncover<4-> {
      \node at (1,15) {QF\_};
      \node at (0,13) {LinearInt};
      \node at (0,10.5) {LinearReal};
      \node at (0,8.5) {NonLinearInt};
      \node at (0,7) {NonLinearReal};
      \node at (0,4.5) {Equality};
      \node at (0,2) {Bitvec};
      \node at (1,11.5) {\begin{tabular}{c}Equality+\\LinearArith\end{tabular}};
      \node at (1,6.5) {\begin{tabular}{c}Equality+\\NonLinearArith\end{tabular}};
      \node at (1,3) {\begin{tabular}{c}Equality+\\Bitvec\end{tabular}};
      \node at (1,1) {String};
      \node at (2,10) {FPArith};
      \node at (2,3) {\begin{tabular}{c}Equality+\\Bitvec+Arith\end{tabular}};
      \node at (1,15) {QF\_};

      \node at (3,12.5) {Arith};
      \node at (3,8.5) {Equality};
      \node at (3,6) {Bitvec};
      \node at (3,2.5) {FPArith};

      \node at (4.5,13) {\begin{tabular}{c}Equality+\\LinearArith\end{tabular}};
      \node at (4.5,8.5) {\begin{tabular}{c}Equality+\\NonLinearArith\end{tabular}};
      \node at (4.5,3){\begin{tabular}{c}Equality+\\MachineArith\end{tabular}};
    }
  \end{tikzpicture}
  }

  \uncover<2-3>{
    \small
    \textbf{Q}uantifier \textbf{F}ree
    \textbf{A}rray
    \textbf{U}ninterpreted \textbf{F}unction
    \textbf{B}it\textbf{V}ector
    \textbf{F}loating\textbf{P}oint
    \textbf{D}ata\textbf{T}ype
    \textbf{S}trings
    \textbf{N}onlinear/\textbf{L}inear
    \textbf{I}nteger \textbf{R}eal
    \textbf{A}rithmetic
    \textbf{D}ifference \textbf{L}ogic
    }
\end{frame}

\begin{frame}
  \frametitle{Competition Overview}

  \begin{tikzpicture}
    \node at (0,6) {SMT-LIB};
    \node at (3,6) {Tracks};
    \node[anchor=west] at (5,6) {Divisions};
    \node[anchor=west] at (9,6) {Logics};

    \node[database,label=below:{\begin{tabular}{c}non-\\incremental\end{tabular}}] (nonincbench) at (0,2) {};
    \node[database,label=below:{incremental}] (incbench) at (0,0) {};

    \node[draw,text width=1.8cm,align=center](sq) at (3,5) {single que.};
    \node[draw,text width=1.8cm,align=center](uc) at (3,4) {unsat core};
    \node[draw,text width=1.8cm,align=center](mv) at (3,3) {model val.};
    \node[draw,text width=1.8cm,align=center](par) at (3,2) {parallel};
    \node[draw,text width=1.8cm,align=center](cloud) at (3,1) {cloud};
    \node[draw,text width=1.8cm,align=center](inc) at (3,0) {incremental};

    \node[anchor=west] (div1) at (5,5) {Arith};
    \node[anchor=west] at (9,5) {\small LIA};
    \node[anchor=west] at (9,4.6) {\small LRA};
    \node[anchor=west] at (10,5) {\small NIA};
    \node[anchor=west] at (10,4.6) {\small NRA};
    \node[anchor=west] (div2) at (5,4) {Bitvec};
    \node[anchor=west] at (9,4) {\small BV};
    \node[anchor=west] (div3) at (5,3.4) {Equality};
    \node[anchor=west] at (9,3.4) {\small UF};
    \node[anchor=west] at (9,3) {\small UFDT};
    \node[anchor=west] (div4) at (5,2.4) {Equality+LinearArith};
    \node[anchor=west] at (9,2.4) {\small UFIDL};
    \node[anchor=west] at (9,2) {\small UFLIA};
    \node[anchor=west] at (9,1.6) {\small UFLRA};
    \node[anchor=west] at (10.5,2.4) {\small ALIA};
    \node[anchor=west] at (10.5,2) {\small AUFLIA};
    \node[anchor=west] at (10.5,1.6) {\small AUFLIRA};
    \node[anchor=west] at (12.5,2) {$\hdots$};
    \node[anchor=west] (div5) at (5,1) {Equality+MachineArith};
    \node[anchor=west] at (9,1) {\small ABV};
    \node[anchor=west] at (9,.6) {\small ABVFP};
    \node[anchor=west] at (9,.2) {\small AUFBV};
    \node[anchor=west] at (10.5,1) {\small AUFBVFP};
    \node[anchor=west] at (10.5,.6) {\small AUFBVDTLIA};
    \node[anchor=west] at (10.5,.2) {\small AUFBVDTNIA};
    \node[anchor=west] at (12.5,1) {$\hdots$};
    \node[anchor=west] (div6)  at (5,-.2) {$\vdots$};

    \draw[->,shorten <=.3em] (nonincbench) to[bend left=15] (sq.west);
    \draw[->,shorten <=.3em] (nonincbench) to[bend left=7] (uc.west);
    \draw[->,shorten <=.3em] (nonincbench) to[bend left=5] (mv.west);
    \draw[->,shorten <=.3em] (nonincbench) to (par.west);
    \draw[->,shorten <=.3em] (nonincbench) to[bend right=4] (cloud.west);
    \draw[->,shorten <=.3em] (incbench) to (inc.west);

    \draw (sq.east) to (div1.west);
    \draw (sq.east) to (div2.west);
    \draw (sq.east) to (div3.west);
    \draw (sq.east) to (div4.west);
    \draw (sq.east) to (div5.west);
    \draw (sq.east) to (div6.west);

    \draw (uc.east) to (div1.west);
    \draw (uc.east) to (div2.west);
    \draw (uc.east) to (div3.west);
    \draw (uc.east) to (div4.west);
    \draw (uc.east) to (div5.west);
    \draw (uc.east) to (div6.west);

    \draw (mv.east) to (div1.west);
    \draw (mv.east) to (div2.west);
    \draw (mv.east) to (div3.west);
    \draw (mv.east) to (div4.west);
    \draw (mv.east) to (div5.west);
    \draw (mv.east) to (div6.west);

    \draw (cloud.east) to (div1.west);
    \draw (cloud.east) to (div2.west);
    \draw (cloud.east) to (div3.west);
    \draw (cloud.east) to (div4.west);
    \draw (cloud.east) to (div5.west);
    \draw (cloud.east) to (div6.west);

    \draw (par.east) to (div1.west);
    \draw (par.east) to (div2.west);
    \draw (par.east) to (div3.west);
    \draw (par.east) to (div4.west);
    \draw (par.east) to (div5.west);
    \draw (par.east) to (div6.west);

    \draw (inc.east) to (div1.west);
    \draw (inc.east) to (div2.west);
    \draw (inc.east) to (div3.west);
    \draw (inc.east) to (div4.west);
    \draw (inc.east) to (div5.west);
    \draw (inc.east) to (div6.west);
  \end{tikzpicture}

\end{frame}

\begin{frame}[fragile]{SMT-COMP Tracks (traditional)}
  \emph{Single Query Track}
  \begin{itemize}
  \item Determine satisfiability of one problem
  \item Solver answers sat/unsat/unknown
  \end{itemize}
  \medskip

  \emph{Unsat Core Track}
  \begin{itemize}
  \item Find small unsatisfiable subset of input.
  \item Solver answers unsat + list of formulas.
  \end{itemize}
  \medskip

  \emph{Model Validation Track}
  \begin{itemize}
  \item Find a model for a satisfiable problem.
  \item Solver answers sat + value for each non-logical symbol.
  \end{itemize}
  \medskip

  \emph{Incremental Track}
  \begin{itemize}
  \item Solve many small problems interactively.
  \item Solver acks commands and answers sat/unsat for each check.
  \end{itemize}
\end{frame}

\begin{frame}[fragile]{SMT-COMP Tracks (new)}
  SMT-COMP 2021 has two new experimental tracks (sponsored by AWS).
  \bigskip

  \emph{Parallel Track}
  \begin{itemize}
  \item Solve a large problem on a big computer
    \begin{itemize}
    \item 64 cores, 256 GB of memory
    \end{itemize}
  \item Solver answers sat/unsat/unknown
  \end{itemize}
  \bigskip
  \emph{Cloud Track}
  \begin{itemize}
  \item Solve a large problem on a network of computers
    \begin{itemize}
    \item 100 machines, 1600 cores, 6400 GB of memory
    \end{itemize}
  \item Solver answers sat/unsat/unknown
  \end{itemize}
\end{frame}

\begin{frame}{Tracks, Solvers, Divisions, and Benchmarks}
  Teams: 18 (+2)
  \bigskip

  \begin{tabular}{c|r@{}l|r@{}l|c}
    Track & \multicolumn{2}{c|}{Solvers} & \multicolumn{2}{c|}{Divisions}  & Benchmarks \\
    \hline
    Single Query  &  19&(-1)  & 18&(-49)  & 101300/381683 \\
    Incremental &  7&(-2)   & 15&(-11)  & 22233/43284   \\
    Unsat Core  &  7&(+2)   & 17&(-23)  & 55463/108188  \\
    Model Validation  &  7&(=)    &  3&(+2) + 3 exp.  & 13301/21251  \\
    Parallel &   &3      &   &14 exp.  & 413/20705 \\
    Cloud & &5      &   &14 exp.  & 405/20669 \\
  \end{tabular}
  \bigskip

  Number in parenthesis shows changes from 2020
\end{frame}

\begin{frame}
  \frametitle{Participants}

  SMT-COMP 2021 participants:
  \begin{itemize}
  \item classic CDCL(T)-based SMT solvers
  \item mcSAT-based solvers
  \item automated theorem provers
  \item finite domain solver
  \item local search techniques
  \item wrapper extending the scope of existing solvers
  \end{itemize}

  \bigskip
  Four new solvers participated:
  \begin{itemize}
  \item iProver (Konstantin Korovin, Andre Duarte, Edvard K Holden)
  \item mc2 (Simon Cruanes, Guillaume Bury)
  \item YicesLS (Bohan Li, Shaowei Cai, Xindi Zhang)
  \item YicesQS (Stéphane Graham-Lengrand)
  \end{itemize}

\end{frame}

\section{Solver Presentation}

{
\begin{frame}
  \vspace*{-1pt}%
  \noindent\makebox[\textwidth]{%
    \includegraphics[height=\paperheight]{bitwuzla-nonumber.pdf}}
\end{frame}
}

{
\begin{frame}
  \vspace*{-1pt}%
  \noindent\makebox[\textwidth]{%
    \includegraphics[height=\paperheight]{COLIBRI-nonumber.pdf}}
\end{frame}
}

{
\begin{frame}
  \vspace*{-1pt}%
  \noindent\makebox[\textwidth]{%
    \includegraphics[height=\paperheight]{cvc5-nonumber.pdf}}
\end{frame}
}

{
\begin{frame}
  \vspace*{-1pt}%
  \noindent\makebox[\textwidth]{%
    \includegraphics[height=\paperheight]{cvc5-gg-nonumber.pdf}}
\end{frame}
}

{
\begin{frame}
  \vspace*{-1pt}%
  \noindent\makebox[\textwidth]{%
    \includegraphics[height=\paperheight]{iprover-nonumber.pdf}}
\end{frame}
}

{
\setbeamertemplate{footline}{\quad\hfill\footnotesize\textcolor{white}{\insertframenumber}\strut\kern1em\vskip1pt}
\begin{frame}
  \vspace*{-1pt}%
  \noindent\makebox[\textwidth]{%
    \includegraphics[height=\paperheight]{mc2-nonumber.pdf}}
\end{frame}
}

{
\begin{frame}
  \vspace*{-1pt}%
  \noindent\makebox[\textwidth]{%
    \includegraphics[height=\paperheight]{opensmt-nonumber.pdf}}
\end{frame}
}

{
\begin{frame}
  \vspace*{-1pt}%
  \noindent\makebox[\textwidth]{%
    \includegraphics[height=\paperheight]{smtinterpol-nonumber.pdf}}
\end{frame}
}

{
%\setbeamertemplate{footline}{\quad\hfill\footnotesize\textcolor{white}{\insertframenumber}\strut\kern1em\vskip1pt}
\begin{frame}<1,3>
  \vspace*{-1pt}%
  \noindent\makebox[\textwidth]{%
    \only<1>{%
      \includegraphics[height=\paperheight,page=1]{smt-rat-nonumber.pdf}
    }\only<2>{%
      \includegraphics[height=\paperheight,page=2]{smt-rat-nonumber.pdf}
    }\only<3>{%
      \includegraphics[height=\paperheight,page=3]{smt-rat-nonumber.pdf}
    }}%
\end{frame}
}

{
\begin{frame}
  \vspace*{-1pt}%
  \noindent\makebox[\textwidth]{%
    \includegraphics[height=\paperheight]{UltimateEliminator-nonumber.pdf}}
\end{frame}
}

{
\begin{frame}
  \vspace*{-1pt}%
  \noindent\makebox[\textwidth]{%
    \includegraphics[height=\paperheight]{vampire-nonumber.pdf}}
\end{frame}
}

{
\begin{frame}
  \vspace*{-1pt}%
  \noindent\makebox[\textwidth]{%
    \includegraphics[height=\paperheight]{verit-nonumber.pdf}}
\end{frame}
}

{
\begin{frame}
  \vspace*{-1pt}\vspace*{-.1\paperheight}%
  \noindent\makebox[\textwidth]{%
    \includegraphics[height=1.2\paperheight]{Yices-nonumber.pdf}}
\end{frame}
}

{
\begin{frame}
  \vspace*{-1pt}%
  \noindent\makebox[\textwidth]{%
    \includegraphics[height=\paperheight]{YicesQS-nonumber.pdf}}
\end{frame}
}

{
\begin{frame}
  \vspace*{-1pt}%
  \noindent\makebox[\textwidth]{%
    \includegraphics[height=\paperheight]{YicesLS-nonumber.pdf}}
\end{frame}
}

\begin{frame}
  \frametitle{Non-Competitive Solvers}

  Submitted by Organisers
  \begin{itemize}
  \item z3-4.8.11
  \item MathSAT 5.6.6
  \item Par4 (for Parallel Track)
  \item Division winners from last year (32 Solvers)
  \end{itemize}
  \bigskip

  Submitted by Participants
  \begin{itemize}
  \item Fixed solvers (Bitwuzla, COLIBRI, cvc5, iProver, OpenSMT, Vampire)
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{New in 2021}

  \begin{itemize}
  \item model validation track extended
  \item manually checking and resolving disagreements
  \item multiple logics per division
  \item we will create an artifact
  \end{itemize}
\end{frame}

\begin{frame}[fragile]
  \frametitle{Model Validation Track}

  Solvers print model for each constant/uninterpreted function
\begin{verbatim}
sat
(model
  (define-fun x15 () Int 5)
  (define-fun x24 () x135 (as @1 x135))
  (define-fun x10 ((?X1 Int)) Int (ite (and (= ?X1 10)) 2 (ite...
\end{verbatim}

  \begin{itemize}
  \item model validator based on pySMT
  \item all models of the competitors were accepted
  \item validator is still inefficient ($>$ 15 minutes)
  \end{itemize}

  \bigskip

  Many thanks to \emph{Andrea Micheli}
\end{frame}

\begin{frame}{Checking Disagreements}

  \begin{itemize}
  \item 111285 instances of 381683 have no status
  \item we checked disagreements between solvers
  \item 209 non-incremental instances
    and 65 incremental instances
  \item only 28 had known sat/unsat status
  \item tactics to resolve status:
    \begin{itemize}
    \item similar disagreements on instances with known status
    \item confirmed with fixed version of participants
    \item analyzed model from solver claiming sat
    \item majority vote
    \item in rare cases manually analyzed instances
    \end{itemize}
  \item solvers found unsound: (Bitwuzla, COLIBRI, cvc5, iProver, MathSAT, OpenSMT, Par4, UltimateEliminator+MathSAT, Vampire, Z3str4)
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{Divisions}
  Tracks are split into \emph{divisions}.

  \begin{itemize}
  \item \emph{before 2021}: Division = SMT-LIB logic
  \item \emph{2021}: 19 Divisions subdivided in 84 logics
  \end{itemize}

  This implied more changes:
  \begin{itemize}
  \item solver authors select supported logics
    \begin{itemize}
    \item[$\Rightarrow$] solvers may run on only a part of a division.
    \end{itemize}
  \item fewer winners (1--5 winners per division)
  \item two solvers won a logic but not a division
    \begin{itemize}
    \item YicesQS won NRA
    \item YicesLS won QF\_IDL
    \end{itemize}
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{Statistics}
  Solver Size
  \begin{itemize}
  \item range from 930~kB to 196~MB (compressed)
  \item total 436 MB
  \item unsat core post-processor: 361~MB
  \end{itemize}
  \bigskip
  \pause

  Job statistics
  \begin{itemize}
  \item Total Job Size: $\sim$ 85 GB
    \begin{itemize}
    \item 35~GB YicesLS temporary files
    \item 29~GB z3 models
    \end{itemize}
  \item 1\,371\,593 pairs (+428\,000)
  \item 16.3 CPU years (+6.4), 9.22 computer years on StarExec
  \item excludes result processors, StarExec overhead, glitches
  \end{itemize}
\end{frame}

\begin{frame}{Scoring}
  Computing scores:
  \begin{itemize}
  \item \emph{Single Query/Parallel/Cloud}: number of solved \emph{instances}
  \item \emph{Incremental}: number of solved \emph{queries}
  \item \emph{Unsat Core}: number of top-level assertions \emph{removed}
  \item \emph{Model Validation}: number of solved instances with correct \emph{models}
  \end{itemize}

  \bigskip
  Error scores:
  \begin{itemize}
  \item \emph{All Tracks}: given for sat reply for unsat instance, or vice versa
  \item \emph{Unsat Core}: given if returned core is satisfiable.
  \item \emph{Model Validation}: given if given model evaluates formula to \emph{false}
  \end{itemize}
  Error scores are draconian.
\end{frame}

\begin{frame}{Score and Ranking}
  In each track we collect different scores:
  \begin{itemize}
  \item \emph{Sequential score} (SQ, UC, MV): all time limits apply to cpu time
  \item \emph{Parallel score} (all): all time limits apply to wallclock time
  \item \emph{SAT score} (SQ): parallel score for \emph{satisfiable} instances
  \item \emph{UNSAT score} (SQ): parallel score for \emph{unsatisfiable} instances
  \item \emph{24s} (SQ): parallel score with time limit of \emph{24s}
  \end{itemize}
  \bigskip

  Division ranking (for each score)
  \begin{itemize}
  \item For each division, one winner is declared
  \end{itemize}

  \bigskip

  Two competition-wide rankings (for each score)
  \begin{itemize}
  \item \emph{Biggest lead}: division winner with most score difference to second place
  \item \emph{Largest contribution}: improvement each solver provided to a virtual best solver
  \end{itemize}

\end{frame}

\begin{frame}{Division Winners}
  \pause
  \emph{Single Query}
  \begin{itemize}
  \item \emph{Bitwuzla}: {\small QF\_Bitvec, QF\_Equality+Bitvec}
  \item \emph{cvc5}: \begin{minipage}{.8\textwidth}\raggedright \tiny Arith, Bitvec, Equality, Equality+LinearArith, Equality+MachineArith, Equality+NonLinearArith, FPArith, QF\_Equality, QF\_Equality+LinearArith, QF\_Equality+NonLinearArith, QF\_FPArith, QF\_LinearIntArith, QF\_LinearRealArith, QF\_NonLinearIntArith, QF\_NonLinearRealArith, QF\_Strings\end{minipage}
  \item \emph{iProver}: {\small Equality+NonLinearArith}
  \item \emph{SMTInterpol}: {\small QF\_Equality+LinearArith}
  \item \emph{UltimateEliminator+MathSAT}: {\small Equality+NonLinearArith}
  \item \emph{Vampire}: {\small Arith, Equality, Equality+NonLinearArith}
  \item \emph{Yices2}: {\tiny QF\_Bitvec, QF\_Equality, QF\_LinearIntArith, QF\_LinearRealArith, QF\_NonLinearIntArith}
  \end{itemize}

  \medskip

  \pause
  \emph{Unsat Core}
  \begin{itemize}
  \item \emph{Bitwuzla}: {\small QF\_Bitvec, QF\_Equality+Bitvec, QF\_FPArith}
  \item \emph{cvc5}: \begin{minipage}{.8\textwidth}\raggedright \tiny Arith, Bitvec, Equality, Equality+LinearArith, Equality+MachineArith, Equality+NonLinearArith, FPArith, QF\_Equality, QF\_Equality+NonLinearArith, QF\_LinearIntrArith, QF\_NonLinearIntArith, QF\_NonLinearRealArith \end{minipage}
  \item \emph{Yices2}: {\small QF\_Equality+LinearArith, QF\_LinearRealArith}
  \end{itemize}

\end{frame}

\begin{frame}{Division Winners}
  \emph{Incremental}
  \begin{itemize}
  \item \emph{cvc5}: \begin{minipage}{.8\textwidth}\raggedright \tiny Arith, Bitvec, Equality, Equality+LinearArith, Equality+NonLinearArith, FPArith, QF\_Equality, QF\_Equality+LinearArith, QF\_FPArith\end{minipage}
  \item \emph{OpenSMT}: {\small QF\_LinearRealArith}
  \item \emph{SMTInterpol}: {\small QF\_Equality+NonLinearArith,QF\_NonLinearIntArith}
  \item \emph{STP}: {\small QF\_Bitvec}
  \item \emph{Yices2}: {\small QF\_Equality+Bitvec,QF\_LinearIntArith}
  \end{itemize}
  \medskip

  \pause
  \emph{Model Validation (competitive only)}
  \begin{itemize}
  \item \emph{Bitwuzla}: {\small QF\_Bitvec}
  \item \emph{cvc5}: {\small QF\_LinearIntArith}
  \item \emph{Yices2}: {\small QF\_LinearRealArith}
  \end{itemize}
\end{frame}

\begin{frame}{Largest contribution}
  \begin{tabular}{r|c@{}lc@{}lc@{}l}
    &\textcolor{gold}{\textbf{1st Place}} &&
    \textcolor{silver}{\textbf{2nd Place}} &&
    \textcolor{bronze}{\textbf{3rd Place}}\\
    \hline
    \emph{Single Query}\\
    seq & Vampire&{\tiny(Eq+NA)} & cvc5&{\tiny(Eq+LA)} & Yices2&{\tiny(QF\_NIA)} \\
    par & iProver&{\tiny(Eq+NA)} & Vampire&{\tiny(Eq)} & cvc5&{\tiny(Eq+LA)} \\
    sat & cvc5&{\tiny(Eq+LA)} & UltimateElim&{\tiny(Eq+NA)} & Vampire&{\tiny(Eq)}\\
    unsat & cvc5&{\tiny(Eq+NA)} & Yices2&{\tiny(QF\_NIA)} & Vampire&{\tiny(Eq)}\\
    24 &  Vampire&{\tiny(Eq+NA)} & cvc5&{\tiny(Eq+LA)} & Yices2&{\tiny(QF\_LIA)}\\[3pt]
    \pause
    \emph{Incremental}\\
    par & cvc5&{\tiny(Eq)} &Yices2&{\tiny(QF\_Eq+LA)}
    &SMTInterpol&{\tiny(QF\_Eq+NA)}\\[3pt]
    \pause
    \emph{Unsat Core}\\
    seq & cvc5&{\tiny(Eq+LA)} &
    Yices2&{\tiny(QF\_Eq+LA)}\\
    par &  cvc5&{\tiny(Eq+LA)}&
    Yices2&{\tiny(QF\_Eq+LA)}\\[3pt]
    \pause
    \emph{Model Validation}\\
    seq &  cvc5&{\tiny(QF\_LIA)} & Bitwuzla&{\tiny(QF\_BV)}
        & Yices2&{\tiny(QF\_LRA)}\\
    par &  cvc5&{\tiny(QF\_LIA)} & Bitwuzla&{\tiny(QF\_BV)}
        & Yices2&{\tiny(QF\_LRA)}\\
  \end{tabular}
\end{frame}

\begin{frame}{Biggest Lead}
  \begin{tabular}{r|c@{}lc@{}lc@{}l}
    &\textcolor{gold}{\textbf{1st Place}} &&
    \textcolor{silver}{\textbf{2nd Place}} &&
    \textcolor{bronze}{\textbf{3rd Place}}\\
    \hline
    \emph{Single Query}\\
    seq & cvc5&{\tiny(Eq+MA)} & Vampire&{\tiny(Eq+NA)} & Bitwuzla&{\tiny(QF\_Eq+BV)} \\
    par & cvc5&{\tiny(Eq+MA)} & iProver&{\tiny(Eq+NA)} & Vampire&{\tiny(Eq)} \\
    sat & cvc5&{\tiny(Eq+MA)} & UltimateElim&{\tiny(Eq+NA)} & Vampire&{\tiny(Eq)}\\
    unsat & cvc5&{\tiny(Eq+MA)} & Yices2&{\tiny(QF\_NIA)} & Vampire&{\tiny(Arith)}\\
    24 &  cvc5&{\tiny(Eq+MA)} & Yices2&{\tiny(QF\_LIA)} & Vampire&{\tiny(Eq+NA)}\\[3pt]
    \pause
    \emph{Incremental}\\
    par & cvc5&{\tiny(BV)} &SMTInterpol&{\tiny(QF\_NIA)}
    &Yices2&{\tiny(QF\_LIA)}\\[3pt]
    \pause
    \emph{Unsat Core}\\
    seq & cvc5&{\tiny(QF\_NRA)} &
    Yices2&{\tiny(QF\_Eq+LA)} &
    Bitwuzla&{\tiny(QF\_Eq+BV)} \\
    par & cvc5&{\tiny(QF\_NRA)} &
    Yices2&{\tiny(QF\_Eq+LA)} &
    Bitwuzla&{\tiny(QF\_Eq+BV)} \\[3pt]
    \pause
    \emph{Model Validation}\\
    seq &  cvc5&{\tiny(QF\_LIA)} & Yices2&{\tiny(QF\_LRA)}
        & Bitwuzla&{\tiny(QF\_BV)} \\
    par &  cvc5&{\tiny(QF\_LIA)} & Yices2&{\tiny(QF\_LRA)}
        & Bitwuzla&{\tiny(QF\_BV)} \\
  \end{tabular}
\end{frame}

\begin{frame}{Plans for SMT-COMP 2022}
  \begin{itemize}
  \item Extend Model Validator to \emph{new logics}?
%    \begin{itemize}
%    \item Non-Linear Arithmetic -- what about div by 0?
%    \item Data Types -- partially defined functions?
%    \item Floating-Point, String
%    \item Arrays -- how to specify lambda arrays?
%    \end{itemize}

  \item Run Model Validator on \emph{unknown} benchmarks?
  \item New \emph{Proof Validation} Track
  \end{itemize}

\end{frame}

\begin{frame}{Proof Validation Track}
  We plan to introduce a proof validation track
  \begin{enumerate}
  \item define \emph{solver independent} proof format
    \begin{itemize}
    \item probably resolution based %Encode resolution dag as SMT-LIB let term
    \item atoms are SMT-LIB formulas
%    \item Input formulas are unit-clauses
%    \item Tseitin-style Axioms provide meaning to logical symbols
    \item fine-grain proofs
    \end{itemize}
  \item implement proof validator
  \item run solvers on unsat \emph{and unknown} benchmarks
  \end{enumerate}
  \bigskip

  Contact us, if you're interested in SMT-LIB proofs.
\end{frame}

\begin{frame}{SMT-COMP organizing committee}
  Three people organize the SMT-COMP.  In 2021:
  \begin{itemize}
  \item Haniel Barbosa
  \item Jochen Hoenicke
  \item Antti Hyvärinen
  \end{itemize}

  Antti's three-year term is ending now.
  \bigskip

  We need a successor for next year's competition.
  Contact us if you would like to volunteer!
\end{frame}

\begin{frame}{Acknowledgements}
  \begin{itemize}
  \item \emph{Andrea Micheli}: Model Validator
  \item \emph{Clark Barrett, Pascal Fontaine, Aina Niemetz, Mathias Preiner, Hans-Jörg Schurr}: SMT-LIB benchmarks
  \item \emph{Aaron Stump}: StarExec support
  \item \emph{Mike Whalen, Jonathan Eidelman}: Cloud/Parallel Track
  \end{itemize}
  \bigskip

  \begin{columns}
    \begin{column}{.3\textwidth}
      \includegraphics[width=\textwidth]{starlogo}
    \end{column}
    \begin{column}{.17\textwidth}
      \includegraphics[width=\textwidth]{powered-by-aws}
    \end{column}
  \end{columns}
\end{frame}

\begin{frame}[shrink=0.95]{Benchmark contributors}
  In 2021 \emph{new benchmarks} were contributed by:

  \small
  \begin{itemize}
  \item Andrew V. Jones
  \item Nuno Lopes
  \item Pierre Bouvier
  \item Alexey Vishnyakov, Andrey Fedotov, Daniil Kuts, Alexander Novikov, Darya Parygina, Eli Kobrin, Vlada Logunova, Pavel Belecky, Shamil Kurmangaleev
  \item Hernán Ponce de León
  \item Anastasiia Izycheva, Eva Darulova
  \item Da Shen, Yuliya Lierler
  \item Maria A Schett, Julian Nagele
  \item Mathias Preiner, Aina Niemetz
  \item Clark Berrett
  \item Johannes Schoisswohl
  \item Jackson Melchert, Nestan Tsiskaridze
  \item Wei-Cheng Wu
  \item Matteo Favaro, Peter Garba
  \item Tjark Weber
  \end{itemize}
\end{frame}

\begin{frame}

  \begin{center}
    \Large\emph{Thanks}
  \end{center}

  \begin{center}
    to all participants
  \end{center}

  \bigskip
  \pause

  \begin{center}
    and to you for listening
  \end{center}

\end{frame}

\end{document}

### 2022-02-01 rules/rules22.tex
new rules

--- 2021-05-07 rules/rules21.tex
@@
 
-\title{16th International Satisfiability Modulo Theories Competition
-  (SMT-COMP 2021): Rules and Procedures}
+\title{17th International Satisfiability Modulo Theories Competition
+  (SMT-COMP 2022): Rules and Procedures}
 
@@
 \author{%
-Haniel Barbosa\\
+Haniel Barbosa (chair)\\
 Universidade Federal de Minas Gerais\\
@@
 \and
-Jochen Hoenicke (chair)\\
+Fran\c{c}ois Bobot\\
+CEA List \\
+France \\
+{\small\href{mailto:Francois.BOBOT@cea.fr}{\texttt{https://github.com/bobot}}} \\
+\and
+Jochen Hoenicke\\
 Universit\"at Freiburg\\
 Germany\\
-{\small\href{mailto:hoenicke@informatik.uni-freiburg.de}{\texttt{hoenicke@informatik.uni-freiburg.de}}}\\
-\and
-Antti Hyvarinen\\
-Universita della Svizzera italiana \\
-Switzerland \\
-{\small\href{mailto:antti.hyvaerinen@usi.ch}{\texttt{antti.hyvaerinen@usi.ch}}} \\
+{\small\href{mailto:hoenicke@informatik.uni-freiburg.de}{\texttt{hoenicke@informatik.uni-freiburg.de}}}
 }
@@
 \begin{description}
-\item[March~15] Deadline for new benchmark contributions.
-\item[May~7] Final versions of competition tools (e.g., benchmark
+\item[TDB] Deadline for new benchmark contributions.
+\item[May~28] Final versions of competition tools (e.g., benchmark
   scrambler) are made available.  Benchmark libraries are frozen.
-\item[May~30] Deadline for first versions of solvers (for all tracks),
+\item[June~18] Deadline for first versions of solvers (for all tracks),
   including information about which tracks and divisions are being
   entered, and magic numbers for benchmark scrambling.
-\item[June~13] Deadline for final versions of solvers, including
+\item[July~2] Deadline for final versions of solvers, including
   system descriptions.
-\item[June~15] Opening value of NYSE Composite Index used to compute
+\item[TDB] Opening value of NYSE Composite Index used to compute
   random seed for competition tools.
-\item[July~18/19] SMT Workshop; end of competition, presentation of
+\item[August 11/12] SMT Workshop; end of competition, presentation of
   results.
@@
 
-SMT-COMP~2021 is part of the SMT Workshop~2021
-(\url{http://smt-workshop.cs.uiowa.edu/2021/}),
-which is affiliated with CAV~2021 (\url{http://i-cav.org/2021/}).
+SMT-COMP~2022 is part of the SMT Workshop~2022
+(\url{http://smt-workshop.cs.uiowa.edu/2022/}) \hb{check},
+which is affiliated with IJCAR~2022 (\url{https://easychair.org/smart-program/IJCAR2022/}).
 The SMT Workshop will include a block of time to present the results of the
@@
 benchmarks and new or improved solvers to raise the level of
-competition and advance the state-of-the-art in automated SMT problem
+competition and advance the state of the art in automated SMT problem
 solving.
 
-SMT-COMP 2021 will have four tracks: the \maintrack (before 2019: Main Track),
+SMT-COMP 2022 will have five \hb{check} tracks: the \maintrack (before 2019: Main Track),
 the \inctrack (before 2019: Application Track), the \ucoretrack, and the
@@
   Liana Hadarean,
-  Matthias Heizmann, Aina Niemetz, Albert Oliveras, Giles Reger, Aaron Stump,
+  Matthias Heizmann, Antti Hyvarinen, Aina Niemetz, Albert Oliveras, Giles Reger, Aaron Stump,
   and Tjark Weber.}  describes the rules and competition procedures for
-SMT-COMP~2021.
-%
+SMT-COMP~2022.
+%
+
+\hb{change more from here}
 As in previous years, we have revised the rules slightly.  Some rule
@@
 the above web form (accompanying information) until the end of
-{\bf May~30, 2021} anywhere on earth.
+{\bf June~18, 2022} anywhere on earth.
 After this date \emph{no new entrants} will be accepted.
@@
 and \cloudtrack{}
-will be accepted until the end of {\bf June~13, 2021} anywhere on earth.
+will be accepted until the end of {\bf July~2, 2022} anywhere on earth.
 
@@
 The bulk of the computation will take place during the weeks leading
-up to SMT 2021.  Intermediate results will be regularly posted to the
+up to SMT 2022.  Intermediate results will be regularly posted to the
 SMT-COMP website as the competition runs.
@@
 
-The limits for \paralleltrack{} and \cloudtrack{} are available at
+The limits for \paralleltrack{} and \cloudtrack{} are available at \hb{check}
 \url{https://smt-comp.github.io/2021/parallel-and-cloud-tracks.html}.
@@
 \header{New benchmarks.}
-The deadline for submission of new benchmarks was {\bf March~15, 2021}.
+The deadline for submission of new benchmarks was {\bf March~15, 2021}
+\hb{update when we have date}.
+%
 The organizers, in collaboration with the SMT-LIB maintainers, will be
-checking and curating these until {\bf May~7, 2021}.  The SMT-LIB
+checking and curating these until {\bf June~18, 2022}.
+
+The SMT-LIB
 maintainers intend to make a new release of the benchmark library
@@
 
-SMT-COMP 2021 is organized under the direction of the SMT Steering
+SMT-COMP 2022 is organized under the direction of the SMT Steering
 Committee. The organizing team is
@@
 \setlength{\itemsep}{0pt}
-\item \href{http://homepages.dcc.ufmg.br/~hbarbosa/}{Haniel Barbosa}~-- Universidade Federal de Minas Gerais, Brazil
-\item \href{https://jochen-hoenicke.de/}{Jochen Hoenicke}~-- Universit\"at Freiburg, Germany (chair)
-\item \href{http://www.inf.usi.ch/postdoc/hyvarinen/}{Antti Hyv\"arinen}~--
-    Universit\`a della Svizzera italiana, Switzerland
+\item \href{http://homepages.dcc.ufmg.br/~hbarbosa/}{Haniel Barbosa}~--
+Universidade Federal de Minas Gerais, Brazil (chair)
+\item \href{https://github.com/bobot}{Fran\c{c}ois Bobot}~-- CEA List, France
+\item \href{https://jochen-hoenicke.de/}{Jochen Hoenicke}~-- Universit\"at Freiburg, Germany
 \end{itemize}
@@
 Haniel Barbosa is part of the developing teams of the SMT solvers
-CVC4~\cite{cvc4-smtcomp18} and veriT~\cite{verit}.
+cvc5~\cite{cvc4-smtcomp18} and veriT~\cite{verit}.
+%
+Fran\c{c}ois is part of the developing team of the SMT solver COLIBRI~\cite{colibri}.
 %
@@
 SMTInterpol~\cite{smtinterpol}.
-Antti Hyvarinen is part of the developing team of the SMT solver
-OpenSMT~\cite{opensmt2}.
 

### 2022-02-08 rules/rules22.tex
more
[rules] adding changes for this year

@@
 \newcommand{\cloudtrack}{Cloud Track\xspace}
+\newcommand{\prooftrack}{Proof Exhibition Track\xspace}
 
@@
 SMT-COMP~2022 is part of the SMT Workshop~2022
-(\url{http://smt-workshop.cs.uiowa.edu/2022/}) \hb{check},
+(\url{http://smt-workshop.cs.uiowa.edu/2022/}),
 which is affiliated with IJCAR~2022 (\url{https://easychair.org/smart-program/IJCAR2022/}).
@@
 
-SMT-COMP 2022 will have five \hb{check} tracks: the \maintrack (before 2019: Main Track),
-the \inctrack (before 2019: Application Track), the \ucoretrack, and the
-\mvaltrack.  In addition there will be two experimental tracks sponsored
-by AWS: the \paralleltrack{} and the \cloudtrack{}.
+SMT-COMP 2022 will have seven tracks: the \maintrack (before 2019: Main Track),
+the \inctrack (before 2019: Application Track), the \ucoretrack, the \mvaltrack,
+the \paralleltrack{} and the \cloudtrack{} (both sponsered by Amazon Web
+Services), and an experimental \prooftrack{} focused on a qualitative evaluation
+of different proof formats, proof checkers and proof-producing solvers.
 %
@@
 uses benchmarks from a specific group of SMT-LIB logics.
-We will recognize winners as measured by number of benchmarks solved
-(taking into account the weighting detailed in
-Section~\ref{sec:scoring}); we will also recognize solvers based on
-additional criteria.
+%
+We will recognize winners in all tracks but the \prooftrack{}.
+%
+They will be determined by the number of benchmarks solved (taking into account
+the weighting detailed in Section~\ref{sec:scoring}); we will also recognize
+solvers based on additional criteria.
 
@@
 
-\hb{change more from here}
 As in previous years, we have revised the rules slightly.  Some rule
-changes in 2021 are designed to not overly punish solvers producing
-syntactically wrong output, by treating those outputs as unknown and
-not as unsoundness.  Moreover, we added more divisions to the model
-validation track.
+changes in 2022 are designed to improve how logics are organized into
+divisions. We have also added more divisions to the \mvaltrack and have defined a
+new \prooftrack.
 %
@@
 \begin{itemize}
-  \item {\bf Divisions now may contain more than one logic.} Previously, every
-  division was comprised of a single logic. There are currently over 60 logics
-  in SMT-LIB, which makes a short summary of the results impossible.  On the
-  other hand the competition-wide scoring does a comparison between solvers that
-  cannot be sensibly compared as they support completely disjoint logics. To get
-  a better overview, this year divisions will combine related logics, thus
-  reducing the number of divisions and obtaining more manageable and meaningful
-  results.  Rather than logics, solvers will declare the divisions they
-  enter. They will be ranked by the number of benchmarks they solve across all
-  logics in the divisions entered.
-  \begin{itemize}
-    \item Quantifier-free divisions:
-    \begin{itemize}
-      \item QF\_Equality\\
-Logics: QF\_UF, QF\_AX, QF\_DT, QF\_UFDT
-\item QF\_Equality+LinearArith\\
-Logics: QF\_ALIA, QF\_AUFLIA, QF\_UFLIA, QF\_UFLRA, QF\_UFIDL
-\item QF\_Equality+NonLinearArith\\
-Logics: QF\_UFNRA, QF\_UFNIA, QF\_ANIA, QF\_AUFNIA
-\item QF\_Equality+Bitvec\\
-Logics: QF\_ABV, QF\_UFBV, QF\_AUFBV
-\item QF\_Equality+Bitvec+Arith\\
-Logics: QF\_AUFBVLIA, QF\_AUFBVNIA, QF\_UFBVLIA
-\item QF\_LinearIntArith\\
-Logics: QF\_LIA, QF\_LIRA, QF\_IDL
-\item QF\_LinearRealArith\\
-Logics: QF\_LRA, QF\_RDL
-\item QF\_Bitvec\\
-Logics: QF\_BV
-\item QF\_FPArith\\
-Logics: QF\_FP, QF\_UFFP, QF\_FPLRA, QF\_BVFP, QF\_ABVFP, QF\_AUFBVFP, QF\_BVFPLRA, QF\_ABVFPLRA
-\item QF\_NonLinearIntArith\\
-Logics: QF\_NIA, QF\_NIRA
-\item QF\_NonLinearRealArith\\
-Logics: QF\_NRA
-\item QF\_Strings\\
-Logics: QF\_S, QF\_SLIA, QF\_SNIA
-
-    \end{itemize}
-    \item Divisions with quantifiers:
-    \begin{itemize}
-      \item Equality\\
-Logics: UF, UFDT
-\item Equality+LinearArith\\
-Logics: \sloppy ALIA, AUFLIA, UFLIA, UFIDL, AUFLIRA, UFLRA, UFDTLIA, UFDTLIRA, AUFDTLIA, AUFDTLIRA
-\item Equality+MachineArith\\
-Logics: AUFFPDTLIRA, UFFPDTLIRA, UFFPDTNIRA, ABVFP, ABVFPLRA, AUFBV, AUFBVFP,
-AUFBVDTLIA, UFBV, UFBVFP, UFBVLIA
-\item Equality+NonLinearArith\\
-Logics: ANIA, AUFDTNIRA, UFDTNIA, UFDTNIRA, AUFNIA, AUFNIRA, UFNIA, UFNRA
-\item Arith\\
-Logics: LRA, LIA, NIA, NRA
-\item Bitvec\\
-Logics: BV
-\item FPArith\\
-Logics: BVFP, FP, BVFPLRA, FPLRA
-    \end{itemize}
-  \end{itemize}
-
-  \rationale{We are aware that any partitioning of logics into divisions can be
-    disadvantageous to some solvers that support some but not all logics in the
-    division. We believe however that to a lesser extent this situation is already
-    common, thinking of different features among problems in the same logic. So in
-    our view the disadvantages are offset by the benefit of having a better
-    presentation of the results. Regardless, results per logic will still be
-    accessible within the results page of a given division, similarly to how one can
-    now see the different scores other than sequential for a given logic.
-
-    The divisions above were defined according to the following rationale:
-
-    \begin{itemize}
-      \item Similar logics that do not standout by themselves were combined.
-      \item Integer and real, as well as bit-vector and floating-point,
-      arithmetics are separated
-      \begin{itemize}
-        \item Note that the ``Arith'' division goes against this. However, its
-        composing logics do not standout out by themselves as currently
-        represented in SMT-LIB.
-      \end{itemize}
-      \item Arrays and datatypes are handled in a similar enough way to UF to be combined with it.
-        \item Floating-point logics are combined since generally this is the dominating component for any logic contaning FP.
-    \end{itemize}
+  \item {\bf Changes in divisions.} Last year we changed
+  divisions to be composed of one or more related logics.
+  %
+  This year we will keep this organization but we will separate logics into
+  divisions slightly differently: we will have a QF\_Datatypes division with the
+  logics QF\_DT, QF\_UFDT and the QF\_Equality division now only contains the
+  QF\_UF and QF\_AX logics.
+
+  \rationale{The feedback from the participants in last year's competition was
+    that datatypes were too dissimilar from QF\_UF and QF\_AX to be organized in
+    the same division.}
+
+  \item {\bf Logics can be non-competitive in competitive divisions.} Last year
+  we considered every logic within a division to competitive unless the division
+  as whole was non-competitive. This year if a logic is non-competitive within a
+  division (i.e., only one competitive solver enrolled in it), it will not be
+  ran.
+
+  \rationale{We believe the previous setup could benefit too much a solver that
+    supports more logics that its competitor.
+    %
+    In particular there was a whose winner was defined by the benchmarks of a
+    non-competitive logic, which we believe is not ideal.
+    %
+    Note that the incentive for solvers to support more logics continues since
+    as soon as there is more than one solver supporting a logic it will be
+    competitive and the solver that does not support it will be disadvantaged.
   }
 
-  \item {\bf The option \akey{:print-success} is explicitly set to
-    true or false.}  Previous competitions set this option to
-    \akey{true} for the incremental track.  In addition, this
-    competition will set the option to \akey{false} for all other
-    tracks.
-    \rationale{According to the standard the default value of
-      \akey{:print-success} is true.  So a conforming solver would
-      unnecessarily print \akey{success} after each command that needs
-      to be stored and skipped by the post-processors.  Additionally,
-      solvers can use this option as indication whether incremental
-      checking is desired.}
-
-    We were asked to set the \akey{:incremental} option to true for
-    the incremental track.  However this is problematic, because it is
-    not a standard option and solvers may not support it.
-
-  \item {\bf Error result is for unsoundness, only.}
-    Previous competitions marked malformed output in the unsat core and
-    the model validation track as errors.  These errors basically disqualify
-    a solver that outputs a slightly malformed model.  This year the error
-    result is only given for unsat cores that are not unsatisfiable or models
-    that don't satisfy the formula. Of courses, answering sat in unsat
-    core track or unsat in model validation track is still considered an
-    error.
-    \rationale{An error result is very punishing and should be reserved
-      for problems that cannot be easily detected.  Giving a syntactically
-      wrong output, e.g. an error message, should just be considered as
-      not solving the task, not as providing an unsound result.}
-
-  \item {\bf The organizers may manually check unsound results.}
-    If solvers disagree on a result, the organizers reserve the right
-    to play the judge and determine which solver is unsound.  The unsound
-    solver is punished, the sound solver gets the point.
-    Previous competitions would take benchmark out of the scoring.
-    \rationale{Often, it can be decided which solver is unsound, even when
-      the benchmark has no status.  For example, when a solver was unsound in
-      other divisions and the authors submitted a fixed version, or because
-      a solver returning sat can be asked for a model.  In that case it would
-      be bad if solver that is known to be unsound
-      won the competition, just because the benchmarks it was unsound
-      on had no status.}
-
-  \item {\bf Punishment of unsound results is adapted to fix sat/unsat scores.}
-
-    Previously an unsound response for a benchmark did punish the
-    score corresponding to the benchmark status.  We fix it to count
-    errors to the score that correspond to the solver output, not the
-    benchmark status.
-    \rationale{If a solver returns \texttt{unsat} for a
-      satisfiable benchmark, all other \texttt{unsat} responses of the
-      solver are no longer trustworthy.  So it is the unsat score of
-      the solver that must be punished.  The \texttt{sat} responses
-      may still be trustworthy.  In the extreme case, a solver that
-      always return \texttt{unsat} would a high error score for the
-      unsat category under the new rules, and would get no points at
-      all for the sat category.}
-
-  \item {\bf Benchmark Selection.}
-      Apart from the \cloudtrack{} and the \paralleltrack{}, this year we
-        increase the percentage of the benchmarks that are run in the
-        competition back to 50 \%.
-    \rationale{We feel that increasing the number of benchmarks is
-    manageable and 50 \% is a more round number than 40 \%.  The
-    \cloudtrack{} and \paralleltrack{} need to be run on a more
-    restricted set because of the amount of parallel resources we
-    provide for the tracks.}
-
-  \item {\bf Stricter checks for output in single query track.}
-    It is now checked that the output in the single query track starts with
-    sat or unsat.  Error messages before such an output is no longer ignored
-    and are treated as an \texttt{unknown} result.
-    {\bf Note:} Solver authors should make sure not to print any debugging
-    output.  This includes debugging output on stderr, because the
-    post-processors cannot distinguish between stderr and stdout.
-
-  \rationale{A solver that does not support the full logic may
-    report errors and then continue ignoring the failed assertion.  This
-    way, it may be flagged as unsound under the old rules, even though it
-    clearly indicated the error.}
-
   \item {\bf \mvaltrack.}  \emergencystretch.5cm Last year's competition introduced the experimental
-  divisions QF\_IDL, QF\_RDL, QF\_LIA, QF\_LRA, QF\_LIRA in the model validation
-  track.  This year, the divisions containing these logics will no longer be
-  experimental.  In addition, we will add this year new experimental divisions
-  QF\_Equality (only with QF\_UF benchmarks), QF\_Equality+LinearArith (only with
+  divisions QF\_Equality (only with QF\_UF benchmarks), QF\_Equality+LinearArith (only with
   QF\_UFIDL, QF\_UFLIA, and QF\_UFLRA benchmarks), and QF\_Equality+Bitvec (only with
   QF\_UFBV benchmarks).
-
-  \rationale{There were only small issues with last year's divisions, so there
-    is no reason to keep them experimental. For the new divisions, as before,
-    given the inconsistencies across different model producing solvers, we
-    proceed in an experimental fashion to push for model standardization. Since
-    both arrays and datatypes add further complications on top of uninterpreted
-    functions, we exclude benchmarks containing those.}
-
-  \item {\bf Model syntax in \mvaltrack.}  The syntax used in the
-    model validation track did not conform to the SMT-LIB standard.
-    The difference is that the syntax used previously included an
-    additional keyword \texttt{model} after the opening parenthesis in
-    the output.  This year we support both the SMT-LIB syntax and the
-    old syntax.  We urge solver writers to upgrade their solver to use
-    the new syntax.
-
-    We added new tracks for UF logics. According to the SMT-LIB standard,
-    model values of uninterpreted sorts should use the syntax
-    \texttt{(as @name Sort)}.
-    In particular the model validator needs to know the sort of the model
-    value.  Furthermore, it is implicitly assumed that model values
-    differ if they have different names.
+  %
+  This year these divisions will no longer be experimental.
+  %
+  In addition, we add this year the new experimental division QF\_FPArith
+  (excluding the logics QF\_ABVFP, QF\_AUFBVFP, and QF\_ABVFPLRA).
+
+  \rationale{Last year's divisions ran successfully, so there
+    is no reason to keep them experimental.
+    %
+    For the new divisions, as before, given the inconsistencies across different
+    model producing solvers, we proceed in an experimental fashion to push for
+    model standardization. We exclude logics containing arrays since their model
+    production adds further complications which we only intend to tackle in the
+    future.}
+
+  \item {\bf \prooftrack.}  \todo{after we iron it out.}
 
@@
 
+\subsection{\prooftrack}
+
+\todo{}
+
 \section{Benchmarks and Problem Divisions}
@@
 Haniel Barbosa is part of the developing teams of the SMT solvers
-cvc5~\cite{cvc4-smtcomp18} and veriT~\cite{verit}.
+cvc5~\cite{cvc4-smtcomp18} \hb{update reference} and veriT~\cite{verit}.
 %

### 2022-03-22 rules/rules22.tex
todo for benchmarks
Updated rules: sat/unsat selection and proof track

@@
 \header{Benchmark Selection.}
-This track will run on a selection of non-incremental benchmarks with status
-\texttt{unsat} (as described on page~\pageref{benchmark-selection}), modified
+This track will run on a selection of non-incremental \emph{unsat} benchmarks
+(as described on page~\pageref{benchmark-selection}), modified
 to use named top-level assertions of the form \akey{(assert (! t :named f ))}.
@@
 The track will run on a
-selection of non-incremental benchmarks with status \texttt{sat} from these
+selection of non-incremental \emph{sat} benchmarks from these
 logics (as described on page~\pageref{benchmark-selection}).
@@
 \subsection{\prooftrack}
-
-\todo{}
+\label{sec:exec:proof}
+
+In the \prooftrack, teams can submit proof-producing solvers together
+with a proof checker for their proof format.  We will compile and
+present the results, as well as assemble a panel of non-organizer
+experts to do a qualitative assessment for each proof-producing
+solver, proof format, and proof checker.
+
+\header{Benchmark Selection.}
+This track will run on a selection of non-incremental \emph{unsat} benchmarks
+(as described on page~\pageref{benchmark-selection}).
+
+\header{Input/Output.}
+The SMT-LIB language provides a command \akey{(get-proof)}, which asks
+a solver to output the proof after a \akey{check-sat}
+command returns \texttt{unsat}.
+This proof must be an s-expression according to the SMT-LIB standard, but
+the format is not specified further.
+%
+Solvers must respond to each command in the benchmark script with the
+answers defined in the SMT-LIB format specification.  In particular,
+solvers that respond \texttt{unknown} to the \akey{check-sat} command
+must respond with an error to the following \akey{get-proof}
+command.
+
+The output of the solver is then fed to a proof checker, which also
+needs be provided by the solver authors.  The input to the proof
+checker is the whole output of the solver including the \texttt{unsat}
+reply to the \akey{check-sat} command.  The proof checker should
+output either \texttt{valid} or \texttt{invalid} to indicate that the
+proof was valid.  \todo{Further statistics?}
+
+\header{Result.}
+The result of a solver is considered \emph{erroneous} if (i) the
+response to the \akey{check-sat} command is \texttt{sat}, (ii) the
+proof checker returns \akey{invalid} to the given proof.  Because the
+\prooftrack is non-competitive and because there is no common
+definition of a valid proof, there will be no score computed for this
+track.
+
+\header{Time Limit.}
+This track will use a wall-clock time limit of 20 minutes per solver/benchmark
+pair. This time limit includes the time for proof checking.
+
+\header{Post-Processor.}
+\todo{This track will use
+{\url{https://github.com/SMT-COMP/postprocessors/tree/master/proof-track/process}}
+as a post-processor
+to validate and accumulate the results.}
 
@@
 %
-The \ucoretrack will use a selection of non-incremental benchmarks with status
-\texttt{unsat} and more than one top-level assertion, modified to use named
+The \ucoretrack will use a selection of non-incremental
+\emph{unsat} benchmarks
+and more than one top-level assertion, modified to use named
 top-level assertions.  The \mvaltrack will use a selection of non-incremental
@@
 QF\_LIA, QF\_LRA, QF\_LIRA, QF\_UF, QF\_UFBV, QF\_UFIDL, QF\_UFLIA, QF\_UFLRA.
+The \prooftrack will use a selection of non-incremental
+\emph{unsat} benchmarks.
+To determine whether a benchmark is sat or unsat, a combination of
+the benchmark's status and the result of the \maintrack{} will be used.
 
@@
   \end{itemize}
+
+\item \todo{excluding and including benchmarks based on statuses and runs}
+  For the \prooftrack and \ucoretrack, all benchmark with status
+  \texttt{sat} are removed.  We further remove benchmarks with status
+  \texttt{unknown} for which no solver reported them to be
+  \texttt{unsat}.
+  %
+  For the \mvaltrack,  all benchmark with status \texttt{unsat} are removed,
+  as well as benchmarks with status
+  \texttt{unknown} for which no solver reported them to be
+  \texttt{sat}.
+
+  In case of a dispute (some solver marks a benchmark as \texttt{sat}
+  and some other solver as \texttt{unsat}), the benchmark may be retained in
+  the selection.
+
 \item \emph{Cap the number of instances in a division.}

### 2022-03-22 rules/rules22.tex
updated benchmark syntax (mainly for proof track)

@@
 \begin{itemize}
-  \item \bkey{(set-logic ...)}\\
-    A (single) \akey{set-logic} command is the \emph{first} command after
-    any \akey{set-option} commands.
-  \item \bkey{(set-info ...)}\\
-    A benchmark file may contain any number of \akey{set-info} commands.
   \item
     \bkey{(set-option ...)}
+    The input contains the following \akey{set-option} commands.
     \begin{enumerate}[label=(\alph*)]
-      \vspace{-1ex}
-    \item The Input may contain the following \akey{set-option} commands.
     \item In the \emph{\inctrack}, the \akey{:print-success} option
@@
       the second command.
+    \item In the \emph{\prooftrack}, a benchmark file contains a
+      single \akey{(set-option :produce-proofs true)} command as
+      the second command.
     \end{enumerate}
+  \item \bkey{(set-logic ...)}\\
+    A (single) \akey{set-logic} command is the \emph{first} command after
+    any \akey{set-option} commands.
+  \item \bkey{(set-info ...)}\\
+    A benchmark file may contain any number of \akey{set-info} commands.
+    During the competition all \akey{set-info} commands are removed from
+    the benchmark by the scrambler.
   \item \bkey{(declare-sort ...)}\\
@@
     \akey{get-model} command.
+  \item \bkey{(get-proof)}\\
+    In the \emph{\prooftrack}, the \akey{check-sat} command (which is
+    always issued in an unsatisfiable context) is followed by a single
+    \akey{get-proof} command.
   \item \bkey{(exit)}\\

### 2022-04-08 rules/rules22.tex
addressing todos

@@
 
-  \item {\bf \prooftrack.}  \todo{after we iron it out.}
+  \item {\bf \prooftrack.}  This track will be introduced this year.
+  %
+  Teams can submit proof-producing solvers together with proof checkers for
+  their proof formats. The checker and format do not need to be from the same
+  team as the solver.
+  %
+  We will compile and present the results, as well as assemble a panel of
+  non-organizer experts to do a qualitative assessment for each proof-producing
+  solver, proof format, and proof checker.
+  %
+  The solver, proof format and checker should be described in a system
+  description (total of 4 pages rather than 2).
+
+  \rationale{Given the many competing visions on how SMT proofs or a proof
+    competition should look like, we decided to be less prescriptive and more
+    descriptive for how SMT-COMP will approach proofs.
+    %
+    We will host a ``proof exhibition'' rather than a ``proof competition''
+    track. The format would be with teams submitting both a proof-producing SMT
+    solver and a proof checker for its proofs.
+ }
 
@@
 
-The output of the solver is then fed to a proof checker, which also
-needs be provided by the solver authors.  The input to the proof
-checker is the whole output of the solver including the \texttt{unsat}
-reply to the \akey{check-sat} command.  The proof checker should
-output either \texttt{valid} or \texttt{invalid} to indicate that the
-proof was valid.  \todo{Further statistics?}
+The output of the solver is then fed to a proof checker, which also needs to be
+provided by the solver authors (but it does not need to authored by them).
+%
+The input to the proof checker is the whole output of the solver including the
+\texttt{unsat} reply to the \akey{check-sat} command.
+%
+The proof checker's output should start with a line containing either
+\texttt{valid} or \texttt{invalid} to indicate that the proof was valid.
+%
+The rest of the output can be arbitrary (for example the proof checker may print
+out statistics).
 
@@
 \header{New benchmarks.}
-The deadline for submission of new benchmarks was {\bf March~15, 2021}
-\hb{update when we have date}.
+The deadline for submission of new benchmarks was {\bf March~15, 2021}.
 %
@@
 
-\item \todo{excluding and including benchmarks based on statuses and runs}
-  For the \prooftrack and \ucoretrack, all benchmark with status
+\item
+  For the \prooftrack and \ucoretrack, all benchmarks with status
   \texttt{sat} are removed.  We further remove benchmarks with status
-  \texttt{unknown} for which no solver reported them to be
+  \texttt{unknown} for which no sound solver reported them to be
   \texttt{unsat}.
   %
-  For the \mvaltrack,  all benchmark with status \texttt{unsat} are removed,
+  For the \mvaltrack,  all benchmarks with status \texttt{unsat} are removed,
   as well as benchmarks with status
-  \texttt{unknown} for which no solver reported them to be
+  \texttt{unknown} for which no sound solver reported them to be
   \texttt{sat}.
@@
 Haniel Barbosa is part of the developing teams of the SMT solvers
-cvc5~\cite{cvc4-smtcomp18} \hb{update reference} and veriT~\cite{verit}.
+cvc5~\cite{cvc5} and veriT~\cite{verit}.
 %

### 2022-04-19 rules/rules22.tex
remove todo

@@
 \header{Post-Processor.}
-\todo{This track will use
+This track will use
 {\url{https://github.com/SMT-COMP/postprocessors/tree/master/proof-track/process}}
 as a post-processor
-to validate and accumulate the results.}
+to validate and accumulate the results.
 

### 2022-05-16 rules/rules22.tex
Proof track description

@@
 
-\header{Input/Output.}
-The SMT-LIB language provides a command \akey{(get-proof)}, which asks
-a solver to output the proof after a \akey{check-sat}
-command returns \texttt{unsat}.
-This proof must be an s-expression according to the SMT-LIB standard, but
-the format is not specified further.
-%
+\header{Input/Output Solver.}
+For the \prooftrack, solver authors should provide two new scripts
+with their solver.  The first script
+\texttt{starexec\_solver\_default} takes the name of the benchmark file as
+single argument and should run the solver on the benchmark.
+As describe in Section~\ref{sec:logistics}, the benchmark
+contains the commands \akey{(check-sat)} and \akey{(get-proof)}.
+The solver must output the answers to both of these commands to stdout.
+Output to stderr is ignored by the toolchain.
+
 Solvers must respond to each command in the benchmark script with the
-answers defined in the SMT-LIB format specification.  In particular,
-solvers that respond \texttt{unknown} to the \akey{check-sat} command
-must respond with an error to the following \akey{get-proof}
-command.
-
-The output of the solver is then fed to a proof checker, which also needs to be
-provided by the solver authors (but it does not need to authored by them).
-%
-The input to the proof checker is the whole output of the solver including the
-\texttt{unsat} reply to the \akey{check-sat} command.
-%
-The proof checker's output should start with a line containing either
-\texttt{valid} or \texttt{invalid} to indicate that the proof was valid.
-%
-The rest of the output can be arbitrary (for example the proof checker may print
-out statistics).
+answers defined in the SMT-LIB format specification.  If the solver
+outputs a proof, this proof must be an s-expression according to the
+SMT-LIB standard, but the format is not specified further.  Solvers
+that respond \texttt{unknown} to the \akey{check-sat} command should
+respond with an error to the following \akey{get-proof} command.  Note
+that the SMT-LIB conformant error result should be output to stdout.
+
+\header{Input/Output Checker.}
+The second script \texttt{starexec\_checker\_default} takes as input
+the benchmark file name as first argument and the proof output of the
+solver script as second argument.  Note that this proof output will
+usually start with the \akey{unsat} result of the \akey{(check-sat)}
+command, which the checker must either parse or skip.
+
+The checker should check the provided proof and provide the result to
+stdout.  Result printed to stderr is ignored.  The first line of the
+proof checker should be one of \akey{valid}, \akey{invalid},
+\akey{holey}, \akey{sat}, \akey{unknown}.  The answer \akey{valid}
+must only be given, if the checker made sure using the proof that the
+benchmark is unsat.  A checker that returns \akey{valid} to a
+satisfiable benchmark is deemed to be unsound.  The answer
+\akey{invalid} should be returned if the proof is errorneous or
+otherwise malformed.  If the proof is correct but skips some proof
+steps or if side-conditions for a rule are not checked by the proof
+checker, the answer should be \akey{holey}.  The answer \akey{sat}
+should be given if the solver claimed that the benchmark is
+satisfiable and \akey{unknown} should be given, if the solver answered
+\akey{unknown} or if it did not give a proof or gave an error result.
+
+After this firsts line, the proof checker can give arbitrary key/value
+pairs of the form \akey{key=value} after the results.  These will be
+collected in the final result table and can include information about
+the number of proof steps, the number of nodes in the proof, the number
+of holes, the number of different proof rules, etc.
 
@@
 The result of a solver is considered \emph{erroneous} if (i) the
-response to the \akey{check-sat} command is \texttt{sat}, (ii) the
-proof checker returns \akey{invalid} to the given proof.  Because the
-\prooftrack is non-competitive and because there is no common
-definition of a valid proof, there will be no score computed for this
-track.
+response to the \akey{check-sat} command is \texttt{sat} and the
+benchmark is unsat, (ii) the proof checker returns \akey{invalid} to
+the given proof.  Because the \prooftrack is non-competitive and
+because there is no common definition of a valid proof, there will be
+no score computed for this track.
+
+A proof checker is considered unsound if it returns \akey{valid} for
+an invalid proof or for a proof containing unchecked steps.  In
+particular, if a proof checker can be tricked to return \akey{valid}
+for a satisfiable benchmark, it is unsound.  Thus, a proof checker
+must also check that the formula that was proved corresponds to the
+benchmark given.  Soundness of the proof checker is a central
+criterion by which the participants will be judged.
 
@@
 
-\header{Post-Processor.}
-This track will use
+\header{Wrapper and Post-Processor.}
+
+Solvers in this track will be wrapped in the competition to include the script
+{\url{https://github.com/SMT-COMP/postprocessors/tree/master/proof-track/starexec_run_default}}, which calls the solver and checker script.
+The track will use
 {\url{https://github.com/SMT-COMP/postprocessors/tree/master/proof-track/process}}

### 2022-05-16 rules/rules22.tex
Minor changes

@@
 \header{Input/Output Solver.}
-For the \prooftrack, solver authors should provide two new scripts
+For the \prooftrack, solver authors should provide two scripts
 with their solver.  The first script
@@
 single argument and should run the solver on the benchmark.
-As describe in Section~\ref{sec:logistics}, the benchmark
+As described in Section~\ref{sec:logistics}, the benchmark
 contains the commands \akey{(check-sat)} and \akey{(get-proof)}.
@@
 solver script as second argument.  Note that this proof output will
-usually start with the \akey{unsat} result of the \akey{(check-sat)}
+usually start with the \texttt{unsat} result of the \akey{(check-sat)}
 command, which the checker must either parse or skip.
@@
 stdout.  Result printed to stderr is ignored.  The first line of the
-proof checker should be one of \akey{valid}, \akey{invalid},
-\akey{holey}, \akey{sat}, \akey{unknown}.  The answer \akey{valid}
+proof checker should be one of \texttt{valid}, \texttt{invalid},
+\texttt{holey}, \texttt{sat}, \texttt{unknown}.  The answer \texttt{valid}
 must only be given, if the checker made sure using the proof that the
-benchmark is unsat.  A checker that returns \akey{valid} to a
+benchmark is unsat.  A checker that returns \texttt{valid} to a
 satisfiable benchmark is deemed to be unsound.  The answer
-\akey{invalid} should be returned if the proof is errorneous or
+\texttt{invalid} should be returned if the proof is errorneous or
 otherwise malformed.  If the proof is correct but skips some proof
 steps or if side-conditions for a rule are not checked by the proof
-checker, the answer should be \akey{holey}.  The answer \akey{sat}
+checker, the answer should be \texttt{holey}.  The answer \texttt{sat}
 should be given if the solver claimed that the benchmark is
-satisfiable and \akey{unknown} should be given, if the solver answered
-\akey{unknown} or if it did not give a proof or gave an error result.
-
-After this firsts line, the proof checker can give arbitrary key/value
-pairs of the form \akey{key=value} after the results.  These will be
-collected in the final result table and can include information about
-the number of proof steps, the number of nodes in the proof, the number
-of holes, the number of different proof rules, etc.
+satisfiable and \texttt{unknown} should be given, if the solver answered
+\texttt{unknown} or if it did not give a proof or gave an error result.
+
+After this firsts line, the proof checker can give arbitrary
+\texttt{key=value} pairs after the results.  These will
+be collected in the final result table and can include information
+about the number of proof steps, the number of nodes in the proof, the
+number of holes, the number of different proof rules, etc.
 
@@
 response to the \akey{check-sat} command is \texttt{sat} and the
-benchmark is unsat, (ii) the proof checker returns \akey{invalid} to
+benchmark is unsat, (ii) the proof checker returns \texttt{invalid} to
 the given proof.  Because the \prooftrack is non-competitive and
@@
 
-A proof checker is considered unsound if it returns \akey{valid} for
+A proof checker is considered unsound if it returns \texttt{valid} for
 an invalid proof or for a proof containing unchecked steps.  In
-particular, if a proof checker can be tricked to return \akey{valid}
+particular, if a proof checker can be tricked to return \texttt{valid}
 for a satisfiable benchmark, it is unsound.  Thus, a proof checker
@@
 \header{Wrapper and Post-Processor.}
-
 Solvers in this track will be wrapped in the competition to include the script

### 2022-05-16 rules/rules22.tex
pass over proof track section

@@
 
-In the \prooftrack, teams can submit proof-producing solvers together
-with a proof checker for their proof format.  We will compile and
-present the results, as well as assemble a panel of non-organizer
-experts to do a qualitative assessment for each proof-producing
-solver, proof format, and proof checker.
+In the \prooftrack, teams can submit a proof-producing solver together with a
+proof checker for its proof format.  We will compile and present the results, as
+well as assemble a panel of experts (not necessarily organizers) to do a
+qualitative assessment for each proof-producing solver, proof format, and proof
+checker.
 
@@
 For the \prooftrack, solver authors should provide two scripts
-with their solver.  The first script
-\texttt{starexec\_solver\_default} takes the name of the benchmark file as
-single argument and should run the solver on the benchmark.
+with their solver.  The first script,
+\texttt{starexec\_solver\_default}, should take the name of the benchmark file as
+a single argument and run the solver on the benchmark.
+%
 As described in Section~\ref{sec:logistics}, the benchmark
-contains the commands \akey{(check-sat)} and \akey{(get-proof)}.
+will contains the commands \akey{(check-sat)} and \akey{(get-proof)}.
+%
 The solver must output the answers to both of these commands to stdout.
@@
 outputs a proof, this proof must be an s-expression according to the
-SMT-LIB standard, but the format is not specified further.  Solvers
-that respond \texttt{unknown} to the \akey{check-sat} command should
-respond with an error to the following \akey{get-proof} command.  Note
-that the SMT-LIB conformant error result should be output to stdout.
+SMT-LIB standard, but otherwise the format is not specified.
+%
+Solvers that respond \texttt{unknown} to the \akey{check-sat} command should
+respond with an error to the following \akey{get-proof} command.  Note that the
+SMT-LIB conformant error result should be output to stdout.
 
 \header{Input/Output Checker.}
-The second script \texttt{starexec\_checker\_default} takes as input
-the benchmark file name as first argument and the proof output of the
-solver script as second argument.  Note that this proof output will
+The second script, \texttt{starexec\_checker\_default}, takes as input
+the benchmark file name as first argument and the stdout output of the
+solver script as second argument.  Note that this output will
 usually start with the \texttt{unsat} result of the \akey{(check-sat)}
@@
 
-The checker should check the provided proof and provide the result to
-stdout.  Result printed to stderr is ignored.  The first line of the
-proof checker should be one of \texttt{valid}, \texttt{invalid},
-\texttt{holey}, \texttt{sat}, \texttt{unknown}.  The answer \texttt{valid}
-must only be given, if the checker made sure using the proof that the
-benchmark is unsat.  A checker that returns \texttt{valid} to a
-satisfiable benchmark is deemed to be unsound.  The answer
-\texttt{invalid} should be returned if the proof is errorneous or
-otherwise malformed.  If the proof is correct but skips some proof
-steps or if side-conditions for a rule are not checked by the proof
-checker, the answer should be \texttt{holey}.  The answer \texttt{sat}
-should be given if the solver claimed that the benchmark is
-satisfiable and \texttt{unknown} should be given, if the solver answered
-\texttt{unknown} or if it did not give a proof or gave an error result.
-
-After this firsts line, the proof checker can give arbitrary
-\texttt{key=value} pairs after the results.  These will
-be collected in the final result table and can include information
-about the number of proof steps, the number of nodes in the proof, the
-number of holes, the number of different proof rules, etc.
+The checker should check the proof within the output and provide the result to
+stdout.
+%
+A result printed to stderr is ignored.
+%
+The first line of the proof checker result should be either \texttt{valid},
+\texttt{invalid}, \texttt{holey}, \texttt{sat}, or \texttt{unknown}.
+%
+The answer \texttt{valid} must only be given when the checker certifies the
+given proof justifies the unsatisfiability of the given benchmark.
+%
+A checker that returns \texttt{valid} to a satisfiable benchmark is deemed to be
+unsound.
+%
+The answer \texttt{invalid} should be returned if the proof is errorneous or
+otherwise malformed.
+%
+If the proof checker determines that the proof is valid but it contains holes,
+i.e., steps that are not checked for correctness, the answer should be
+\texttt{holey}.
+%
+The answer \texttt{sat} should be given if the solver claimed that the benchmark
+is satisfiable, and \texttt{unknown} should be given if the solver answered
+\texttt{unknown}, if it answered \texttt{unsat} but did not give a proof, or if
+the solver gave an error result.
+
+After the first line, the proof checker can provide arbitrary
+\texttt{key=value} pairs.
+%
+These will be collected in the final result table and can include for example
+information about the number of proof steps, the number of nodes in the proof,
+the number of holes, the number of different proof rules, etc.
 
 \header{Result.}
+%
 The result of a solver is considered \emph{erroneous} if (i) the
-response to the \akey{check-sat} command is \texttt{sat} and the
-benchmark is unsat, (ii) the proof checker returns \texttt{invalid} to
-the given proof.  Because the \prooftrack is non-competitive and
-because there is no common definition of a valid proof, there will be
-no score computed for this track.
+response to the \akey{check-sat} command is \texttt{sat} (as the
+benchmark is necessarily unsatisfiable), or
+%
+(ii) the proof checker returns \texttt{invalid} to
+the given proof.
+%
+Since the \prooftrack is non-competitive and we are not fixing a definition of a
+valid proof, there will be no score computed for this track.
 

### 2022-05-17 rules/rules22.tex
adding Jochen suggestion

@@
 
-A proof checker is considered unsound if it returns \texttt{valid} for
-an invalid proof or for a proof containing unchecked steps.  In
-particular, if a proof checker can be tricked to return \texttt{valid}
-for a satisfiable benchmark, it is unsound.  Thus, a proof checker
-must also check that the formula that was proved corresponds to the
-benchmark given.  Soundness of the proof checker is a central
+A proof checker is unsound if it returns \texttt{valid} for an (invalid) proof
+of a satisfiable benchmark.
+%
+Thus, a proof checker must also check that the formula that was proved
+corresponds to the benchmark given.  Soundness of the proof checker is a central
 criterion by which the participants will be judged.

### 2022-05-23 rules/rules22.tex
read over the proof section again

@@
 As described in Section~\ref{sec:logistics}, the benchmark
-will contains the commands \akey{(check-sat)} and \akey{(get-proof)}.
+will contain the commands \akey{(check-sat)} and \akey{(get-proof)}.
 %
@@
 \header{Input/Output Checker.}
-The second script, \texttt{starexec\_checker\_default}, takes as input
+The second script, \texttt{starexec\_checker\_default}, should take
 the benchmark file name as first argument and the stdout output of the
@@
 %
-A result printed to stderr is ignored.
+Output printed to stderr is ignored.
 %
@@
 %
-The answer \texttt{valid} must only be given when the checker certifies the
+The answer \texttt{valid} must only be given when the checker certifies that the
 given proof justifies the unsatisfiability of the given benchmark.
@@
 The answer \texttt{sat} should be given if the solver claimed that the benchmark
-is satisfiable, and \texttt{unknown} should be given if the solver answered
-\texttt{unknown}, if it answered \texttt{unsat} but did not give a proof, or if
-the solver gave an error result.
+is satisfiable, and \texttt{unknown} should be given if (1) the solver answered
+\texttt{unknown}, (2) it answered \texttt{unsat} but did not give a proof, or 
+(3) if the solver gave an error result.
 
@@
 The result of a solver is considered \emph{erroneous} if (i) the
-response to the \akey{check-sat} command is \texttt{sat} (as the
+proof checker returns \texttt{sat} (as the
 benchmark is necessarily unsatisfiable), or

### 2022-05-26 rules/rules22.tex
Added missing dates.
Benchmark Deadline was in March (according to SMT-COMP website)
NYSE is July 5th, since July 4th is a holiday.

@@
 \begin{description}
-\item[TDB] Deadline for new benchmark contributions.
+\item[Mar~15] Deadline for new benchmark contributions.
 \item[May~28] Final versions of competition tools (e.g., benchmark
@@
   system descriptions.
-\item[TDB] Opening value of NYSE Composite Index used to compute
+\item[July~5] Opening value of NYSE Composite Index used to compute
   random seed for competition tools.

### 2022-05-27 rules/rules22.tex
remove todo
Change script names for proof track.

@@
 
-The limits for \paralleltrack{} and \cloudtrack{} are available at \hb{check}
-\url{https://smt-comp.github.io/2021/parallel-and-cloud-tracks.html}.
+The limits for \paralleltrack{} and \cloudtrack{} are available at
+\url{https://smt-comp.github.io/2022/parallel-and-cloud-tracks.html}.
 
@@
 pair. The time limit for checking the satisfying assignment is yet to be
-determined, but is anticipated to be around 5 minutes of wall-clock time per
-solver.
+determined, but is anticipated to be around 15 minutes of wall-clock time.
 
@@
 with their solver.  The first script,
-\texttt{starexec\_solver\_default}, should take the name of the benchmark file as
+\texttt{smtcomp\_solver}, should take the name of the benchmark file as
 a single argument and run the solver on the benchmark.
@@
 \header{Input/Output Checker.}
-The second script, \texttt{starexec\_checker\_default}, should take
+The second script, \texttt{smtcomp\_checker}, should take
 the benchmark file name as first argument and the stdout output of the
@@
 Solvers in this track will be wrapped in the competition to include the script
-{\url{https://github.com/SMT-COMP/postprocessors/tree/master/proof-track/starexec_run_default}}, which calls the solver and checker script.
+{\url{https://github.com/SMT-COMP/postprocessors/tree/master/proof-track/starexec_run_proof}}, which calls the solver and checker script.
 The track will use

### 2022-05-27 rules/rules22.tex
Updated system description to include proof format

@@
 As part of the submission, SMT-COMP entrants are \textbf{required} to provide a
-short (1-2 pages, excluding references) description of the system, which \textbf{must} explicitly
+short (1-2 pages, excluding references; plus 2 pages for proof format) description of the system, which \textbf{must} explicitly
 acknowledge any solver it wraps or is based on in case of a \emph{wrapper} or
@@
   \item a link to a website for the submitted tool.
+  \item for participants of the \prooftrack{} a short description
+    of their proof format of up to two extra pages.
 \end{itemize}

### 2022-05-28 2022/prep/find_benchmarks.sh
2022 benchmarks and starexec spaces

@@ -1,0 +1,26 @@
+#!/bin/bash
+
+SCRAMBLER=`dirname $(readlink -f "$0")`/../../../scrambler/scrambler
+YEAR=2022
+LANG=C  # fix sorting
+export LANG
+
+if [ "$#" == 0 -o \! -d "$1" ]; then
+  echo "USAGE: find_benchmarks.sh <path-to-smtlib>"
+  echo "<path-to-smtlib> with three sub-directories"
+  echo "  incremental: directory with of all directory benchmarks"
+  echo "  non-incremental: directory with of all directory benchmarks"
+  echo "  benchmarks-pending: directory with the benchmarks-pending directory"
+  exit
+fi
+
+for track in incremental non-incremental; do
+  utrack=$(echo $track | tr '-' '_')
+  # find benchmarks and convert logic to upper-case
+  (cd $1/$track; find -name \*.smt2) | perl -pe 's!^./[^/]*/!\U$&\E!' | sort > SMT-LIB_${utrack}_benchmarks_all.txt
+  # find new benchmarks
+  #(cd $1/pending-$YEAR/DONE/$track; find -name \*.smt2) | sort > SMT-LIB_${utrack}_benchmarks_new.txt
+done
+
+../../tools/selection/make_statuses_and_asserts.sh $SCRAMBLER $1/non-incremental > SMT-LIB_non_incremental_benchmarks_all_assertions.csv
+../../tools/scoring/make_num_check_sat.sh $1/incremental > SMT-LIB_incremental_benchmarks_num_check_sat.csv

### 2022-05-31 rules/rules22.tex
clarifying

@@
 As part of the submission, SMT-COMP entrants are \textbf{required} to provide a
-short (1-2 pages, excluding references; plus 2 pages for proof format) description of the system, which \textbf{must} explicitly
+short (1-2 pages, excluding references; plus 2 pages for proof format and proof
+checker if the entrant is for the proof exhibition track) description of the system, which \textbf{must} explicitly
 acknowledge any solver it wraps or is based on in case of a \emph{wrapper} or

### 2022-06-01 2022/prep/jobs/make_all_jobs.sh
Added some README files

@@ -1,0 +1,6 @@
+#!/bin/bash
+
+for track in sq inc uc mv pe; do
+    ./make_job.sh --$track
+done
+

### 2022-06-21 tools/prep/download.py
Move download tools to generic directory

@@ -2,7 +2,7 @@
 
 import gitlab
 import subprocess
-import os
+import os,sys
 
 gl = gitlab.Gitlab('https://clc-gitlab.cs.uiowa.edu:2443')
 
@@ -28,6 +28,10 @@ def clone_group(name,dir):
         else:
             subprocess.run(["git", "clone", "--depth=1", project.http_url_to_repo, path])
 
+if len(sys.argv)<2:
+    print("download.py <DIR>")
+    exit(1)
 
-clone_group("SMT-LIB-benchmarks","non-incremental")
-clone_group("SMT-LIB-benchmarks-inc","incremental")
+dst=sys.argv[1]
+clone_group("SMT-LIB-benchmarks",os.path.join(dst,"non-incremental"))
+clone_group("SMT-LIB-benchmarks-inc",os.path.join(dst,"incremental"))

### 2022-06-21 rules/rules22.tex
update link
fix

@@
 (un)satisfia\-bility of benchmarks from the SMT-LIB benchmark library
-(\url{http://www.smt-lib.org/benchmarks.shtml}).
+(\url{https://smtlib.cs.uiowa.edu/benchmarks.shtml}).
 
@@
 \begin{center}
-  \url{https://forms.gle/9Eged2txtvJxGXeD9}
+  \url{https://forms.gle/ewNQdFJbmQ12GxpX8}
 \end{center}

### 2022-06-23 2022/prep/jobs/make_job.sh
Update mv postproc id, set smtcomp.q

@@ -97,12 +97,14 @@ if [ "$TESTING" = "1" ]; then
     POST_SQ=692
     POST_INC=691
     POST_UC=727
-    POST_MV=672
+    POST_MV=742
     POST_PE=741
+    QUEUE=1   # all.q
 else
     SEED=`cat $SCRIPTDIR/../../COMPETITION_SEED`
     TIMEOUT="1200"    # 20 minutes
     KIND=final
+    QUEUE=169969 # smtcomp.q
 fi
 
 mkdir -p $KIND
@@ -110,7 +112,6 @@ mkdir -p $KIND
 PRETR=PRE_${TRACK}
 POSTTR=POST_${TRACK}
 
-QUEUE=1   # FIXME: smtcomp.q
 MEMLIMIT="60.0"
 
 SELECTION="$SCRIPTDIR/../selection/$KIND/benchmark_selection_${!TRACK}"
@@ -131,6 +132,7 @@ fi
 python3 $SCRIPTDIR/../../../tools/prep/prepare_job_xml.py \
 	-t ${!TRACK} --name "$JOBNAME" --queue $QUEUE --pre $PRE --post $POST \
 	--wall $TIMEOUT --seed $SEED --memlimit $MEMLIMIT \
-	-s $SELECTION $IN_SPACE $SOLVERS_CSV $KIND/$OUTFILE.xml
+	-s $SELECTION $IN_SPACE $SOLVERS_CSV $KIND/$OUTFILE.xml \
+	$INCLUDE_NONCOMPETITIVE
 
 (cd $KIND; zip $OUTFILE.zip $OUTFILE.xml)

### 2022-06-23 rules/rules22.tex
Clarified rules for starexec configurations

@@
 and made publicly available, or communicated separately to the
-organisers for the \cloudtrack{} and \paralleltrack{}.  StarExec supports solver configurations;
-for clarity, \emph{each submitted solver must have one configuration
-  only}.  Moreover, the organizers must be informed of the solver's
-presence \emph{and the tracks and divisions which it enters} via the
-web form at
+organisers for the \cloudtrack{} and \paralleltrack{}.  StarExec
+supports solver configurations.  You can have at most one configuration
+for each track (named after the track) and a default configuration used
+for tracks without a track-specific configuration.
+Moreover, the organizers must be informed of the solver's presence
+\emph{and the tracks and divisions which it enters} via the web form
+at
 \begin{center}
@@
 \header{Input and output.}
-Participating solvers will be connected to a trace executor, which
+Participating solvers should include a script
+\texttt{smtcomp\_run\_incremental} (if this is not present the script
+for the default configuration will be used). This script will be called
+without arguments and will be connected to a trace executor, which
 will incrementally send commands to the standard input channel of the
@@
 
-\header{Trace Executor.} This track will use the trace executor
+\header{Trace Executor.} This track will use the trace executor from
+{\url{https://github.com/SMT-COMP/trace-executor}}
 to execute a solver on an incremental benchmark file.

### 2022-06-24 tools/wrap-solvers/wrap_incremental.sh
Reworked wrapper for incremental/proof.
Wrap for all tracks at the same time.  Use wrapping scripts.

@@ -1,0 +1,12 @@
+#!/bin/sh
+
+SOLVER_DIR=$1
+
+test -e "${SOLVER_DIR}/bin/smtcomp_run_incremental" || cp -a "${SOLVER_DIR}/bin/starexec_run_"* "${SOLVER_DIR}/bin/smtcomp_run_incremental"
+res=$?
+cp -a wrapper_inc/* "${SOLVER_DIR}/bin"
+if [ $res -ne 0 ]
+then
+    echo "ERROR: no default config"
+    exit 1
+fi

### 2022-06-24 tools/wrap-solvers/wrap_incremental_proof.sh

@@ -1,0 +1,13 @@
+#!/bin/sh
+
+SOLVER_DIR=$1
+
+test -e "${SOLVER_DIR}/bin/smtcomp_run_incremental" || cp -a "${SOLVER_DIR}/bin/starexec_run_"* "${SOLVER_DIR}/bin/smtcomp_run_incremental"
+res=$?
+cp -a wrapper_inc/* "${SOLVER_DIR}/bin"
+cp -a wrapper_pe/* "${SOLVER_DIR}/bin"
+if [ $res -ne 0 ]
+then
+    echo "ERROR: no default config"
+    exit 1
+fi

### 2022-06-24 tools/wrap-solvers/wrap_proof.sh

@@ -1,0 +1,3 @@
+#!/bin/sh
+
+cp -a wrapper_pe/* "$1/bin"

### 2022-06-24 tools/wrap-solvers/wrap_solver.sh

@@ -5,7 +5,7 @@
 SCRIPTDIR=`dirname $(readlink -f "$0")`
 #source "$SCRIPTDIR/login.sh"
 
-if [ $# -eq 5 ]
+if [ $# -eq 4 ]
 then
   WRAP=yes
   DOWNLOAD=yes
@@ -24,7 +24,7 @@ while [ $# -gt 0 ]
 do
   case $1 in
     -h|--help)
-      echo -n "usage: $(basename $0) [<option>] <wrapped name> <wrapper directory> <solver id> <space id> <solver-dir>"
+      echo -n "usage: $(basename $0) [<option>] <wrapped name> <wrapper script> <solver id> <space id> <solver-dir>"
       echo ""
       echo "Download, wrap and upload solver from and to StarExec."
       echo "If no options are given, all actions are performed."
@@ -67,11 +67,10 @@ done
 [ $WRAP == "yes" ] && ZIP=yes
 
 WRAPPED_NAME=$1
-WRAPPER_DIR=$2
+WRAPPER_SCRIPT=$2
 SOLVER_ID=$3
-SPACE_ID=$4
-SOLVER_DIR=$5
-WRAPPED_SOLVER_DIR=$5-wrapped
+SOLVER_DIR=$4
+WRAPPED_SOLVER_DIR=$4-wrapped
 
 upload_solver()
 {
@@ -109,6 +108,7 @@ download_solver()
 
   ID=$1
   OUT=$2
+  test -s download/${ID}.zip || curl -o download/${ID}.zip 'https://www.starexec.org/starexec/secure/download?type=solver&id='${ID}
 #  COMMAND="getsolver id=${ID} out=${OUT}"
 #  java -jar ${SCRIPTDIR}/StarexecCommand.jar <<EOF
 #login u=${USERNAME} p=${PASSWORD}
@@ -131,17 +131,10 @@ wrap_solver()
   echo ">> wrap solver"
   SOLVER_DIR=$1
   NEW_SOLVER_DIR=$2
+  
   rm -rf "${NEW_SOLVER_DIR}"
-  cp -a "${SOLVER_DIR}/${NAME}" "${NEW_SOLVER_DIR}"
-  echo "${NEW_SOLVER_DIR}/bin/starexec_run_default"
[…]

### 2022-06-24 tools/wrap-solvers/wrap_solvers.py

@@ -13,6 +13,7 @@ COL_SINGLE_QUERY_TRACK = 'Single Query Track'
 COL_INCREMENTAL_TRACK = 'Incremental Track'
 COL_MODEL_VALIDATION_TRACK = 'Model Validation Track'
 COL_UNSAT_CORE_TRACK = 'Unsat Core Track'
+COL_PROOF_EXHIBITION_TRACK = 'Proof Exhibition Track'
 
 # Print error message and exit.
 def die(msg):
@@ -32,13 +33,32 @@ def find_solver_id(solverid, track):
         return m.group(1)
     die(f"cannot find solver id for {track}: {solverid}")
 
+def run_wrapper(args, wrap_script, solver_id):
+    mydir = os.path.dirname(os.path.abspath(__file__)) + '/'
+    script_args = [ mydir + 'wrap_solver.sh']
+    if args.download_only:
+        script_args.append("-d")
+    if args.unzip_only:
+        script_args.append("-x")
+    if args.wrap_only:
+        script_args.append("-w")
+    if args.upload_only:
+        script_args.append("-u")
+    if args.wrap:
+        script_args.append("-W")
+    if args.zip_only:
+        script_args.append("-z")
+    script_args.extend(['wrapped', mydir + wrap_script, solver_id, "solvers"])
+    print(script_args)
+    p = subprocess.Popen(script_args)
+    p.communicate()
 
 if __name__ == '__main__':
     parser = ArgumentParser(
             usage="wrap_solvers [options] <solvers: csv>\n\n"
 
-                  "Download, wrap and upload solvers for non-incremental and "
-                  "incremental tracks.")
+                  "Download, wrap and upload solvers for incremental and "
+                  "proof tracks.")
     parser.add_argument ("csv",
             help="the input csv with solvers and divisions as generated from"\
                  "tools/prep/extract_data_from_submission.py")
@@ -61,14 +81,6 @@ if __name__ == '__main__':
                          default=False,
                          help="only zip solvers from existing wrapped "
                               "directories when wrapping")
-    parser.add_argument ("--sq", dest="space_id",
-            help="the StarExec space id for non-incremental wrapped solvers")
-    parser.add_argument ("--inc", dest="space_id_inc",
-            help="the StarExec space id for incremental wrapped solvers")
-    parser.add_argument ("--mv", dest="space_id_mv",
-            help="the StarExec space id for model validation track wrapped solvers")
[…]

### 2022-08-11 tools/results_visualization/aggregations.py
Add competitive information in pivot table

@@ -191,7 +191,7 @@ def add_division_family_info(data, family_definition):
 # Return true if the solver with given id is competitive.
 def is_competitive_solver(solver_config_id):
     global g_competitive
-    return g_competitive[solver_config_id]
+    return g_competitive[solver_config_id] == 'yes'
 
 # Return solver name of solver with given solver id.
 def get_solver_name(solver_id):
@@ -207,7 +207,7 @@ def map_solver_id(row, column):
     solver_id_str = row[column]
     solver_id = int(solver_id_str) if isinstance(solver_id_str, int) or solver_id_str.isnumeric() else None
     if solver_id:
-        g_competitive[solver_id] = row[COL_COMPETING] == 'yes'
+        g_competitive[solver_id] = row[COL_COMPETING]
         g_solver_names[solver_id] = row[COL_SOLVER_NAME]
         g_solver_variants[solver_id] = row[COL_VARIANT_OF_ID] \
                 if row[COL_VARIANT_OF_ID] else row[COL_SOLVER_NAME]
@@ -347,7 +347,7 @@ def score(
           use_families,
           skip_unknowns,
           sequential):
-    global g_args
+    global g_args, g_competitive
     assert not filter_result or filter_result in [RESULT_SAT, RESULT_UNSAT]
 
     if g_args.log: log("Score for {} in {}".format(year, "ALL"))
@@ -370,7 +370,7 @@ def score(
     data_new['correct_sat'] = 0   # Number of correctly solved sat benchmarks
     data_new['correct_unsat'] = 0 # Number of correctly solved unsat benchmarks
     data_new['division_size'] = num_benchmarks
-    data_new['competitive'] = data_new.solver_id.map(is_competitive_solver)
+    data_new['competitive'] = data_new.solver_id.map(lambda x: g_competitive[x])
     data_new['timeout'] = 0
     data_new['memout'] = 0
     data_new['unsolved'] = 0
@@ -582,12 +582,12 @@ def main():
 
     data["nb"] = 1
 
-    data.drop(columns=["benchmark","solver","configuration_id","status","competitive","score_error","score_cpu_time","score_wallclock_time","year","correct","error","correct_sat","correct_unsat","division_size","timeout","memout","unsolved","score_correct"],inplace=True)
[…]

### 2022-08-11 2022/slides/smtWorkshop/slides.tex
slides

--- 2021-07-19 2021/presentation/slides.tex
@@
 \title{SMT-COMP 2021\\
-16th International Satisfiability Modulo Theory Competition}
-\author{Haniel Barbosa \and \emph{Jochen Hoenicke} \and Antti Hyv\"arinen}
-\date{July 18, 2021}
+17th International Satisfiability Modulo Theory Competition}
+\author{\emph{Haniel Barbosa} \and Jochen Hoenicke \and Fran\c{c}ois Bobot}
+\date{Aug 11, 2022}
 
@@
   Albert-Ludwigs-Universit\"at Freiburg, Germany \and
-  Universita della Svizzera italiana, Switzerland
+  CEA List, France
 }
@@
 
+\newcommand\vitem{\vfill\item}
+
 \begin{document}
@@
         \textbf{2014} & since then hosted\\
-        & by \emph{StarExec}\\
-        \textbf{2021} & 16th competition
+        & by \emph{StarExec}
       \end{tabular}
@@
     \item to promote and develop the SMT-LIB format
+    \begin{itemize}
+      \item model validation
+      \item proof checking
+    \end{itemize}
     \item to collect relevant benchmarks
@@
       \begin{block}{Non-incremental}
-        381\,683 instances {\small (+5082)} \\
+        391\,363 instances {\small (+9680)}\\
         with 1 query each \\
-        in 79 logics {\small (+9)}.
+        in 81 logics {\small (+2)}.
       \end{block}
@@
       \begin{block}{Incremental}
-        43\,284 instances {\small (+19\,073)}\\
-        with 33\,998\,794 queries {\small (+554\,499)} \\
-        in 35 logics {\small (+2)}.
+        43\,285 instances {\small (+1)}\\
+        with 33\,998\,935 queries {\small (+141)} \\
+        in 39 logics.
       \end{block}
@@
   \end{columns}
-\end{frame}
+  \pause
+    \begin{columns}
+    \begin{column}{0.4\textwidth}
+      \begin{block}{Selected Non-incremental}
+        \only<2>{206\,932 instances}\only<3>{\textcolor{red}{206\,932}
+          instances\\
+          \textcolor{red}{We mistakenly ignored 9466 new benchmarks}
+        }
+      \end{block}
+    \end{column}
+    \begin{column}{0.4\textwidth}
+      \begin{block}{Selected Incremental}
+        22\,300 instances
+      \end{block}
+    \end{column}
+    \begin{column}{0.08\textwidth}
+    \end{column}
+  \end{columns}
 
-\begin{frame}
-  \frametitle{SMT-LIB Logics}
-
-  \noindent\makebox[\textwidth]{%
-  \begin{tikzpicture}[xscale=2.55,yscale=.39]
-    \uncover<1-3> {
-    % Arith
-    \node at (3,14) {\small LIA};
-    \node at (3,13) {\small LRA};
-    \node at (3,12) {\small NIA};
-    \node at (3,11) {\small NRA};
-    % Equality
-    \node at (3,9) {\small UF};
-    \node at (3,8) {\small UFDT};
-    % Bitvec
-    \node at (3,6) {\small BV};
-    % FPArith
-    \node at (3,4) {\small BVFP};
-    \node at (3,3) {\small BVFPLRA};
-    \node at (3,2) {\small FP};
-    \node at (3,1) {\small FPLRA};
-    % Equality+LinearArith
-    \node at (4,15) {\small ALIA};
-    \node at (4,14) {\small AUFLIA};
-    \node at (4,13) {\small AUFLIRA};
-    \node at (4,12) {\small AUFDTLIA};
-    \node at (4,11) {\small AUFDTLIRA};
-    \node at (5,15) {\small UFDTLIA};
-    \node at (5,14) {\small UFDTLIRA};
-    \node at (5,13) {\small UFIDL};
-    \node at (5,12) {\small UFLIA};
-    \node at (5,11) {\small UFLRA};
-    % Equality+NonLinearArith
-    \node at (4,10) {\small ANIA};
-    \node at (4,9) {\small AUFNIA};
-    \node at (4,8) {\small AUFNIRA};
-    \node at (4,7) {\small AUFDTNIRA};
-    \node at (5,10) {\small UFDTNIA};
-    \node at (5,9) {\small UFDTNIRA};
-    \node at (5,8) {\small UFNIA};
-    \node at (5,7) {\small UFNRA};
-    % Equality+MachinedArith
-    \node at (4,6) {\small ABV};
-    \node at (4,5) {\small ABVFP};
-    \node at (4,4) {\small ABVFPLRA};
-    \node at (4,3) {\small AUFBV};
-    \node at (4,2) {\small AUFBVFP};
-    \node at (4,1) {\small AUFBVDTLIA};
-    \node at (4,0) {\small AUFBVDTNIA};
-    \node at (5,6) {\small AUFFPDTLIRA};
-    \node at (5,5) {\small AUFFPDTNIRA};
-    \node at (5,4) {\small UFBV};
-    \node at (5,3) {\small UFBVFP};
-    \node at (5,2) {\small UFBVLIA};
-    \node at (5,1) {\small UFFPDTLIRA};
-    \node at (5,0) {\small UFFPDTNIRA};
-
-    %QF_LinearIntArith
-    \node at (0,14) {\small QF\_IDL};
-    \node at (0,13) {\small QF\_LIA};
-    \node at (0,12) {\small QF\_LIRA};
-    %QF_LinearRealArith
-    \node at (0,11) {\small QF\_RDL};
-    \node at (0,10) {\small QF\_LRA};
-    %QF_NonLinearIntArith
-    \node at (0,9) {\small QF\_NIA};
-    \node at (0,8) {\small QF\_NIRA};
-    %QF_NonLinearRealArith
-    \node at (0,7) {\small QF\_NRA};
-    %QF_Equality
-    \node at (0,6) {\small QF\_AX};
-    \node at (0,5) {\small QF\_DT};
-    \node at (0,4) {\small QF\_UF};
-    \node at (0,3) {\small QF\_UFDT};
-    %QF_Bitvec
-    \node at (0,2) {\small QF\_BV};
-    %QF_Strings
-    \node at (0,1) {\small QF\_S};
-    \node at (1,1) {\small QF\_SLIA};
-    \node at (2.05,1) {\small QF\_SNIA};
-    %QF_Equality+LinearArith
-    \node at (1,14) {\small QF\_ALIA};
-    \node at (1,13) {\small QF\_AUFLIA};
-    \node at (1,12) {\small QF\_UFIDL};
-    \node at (1,11) {\small QF\_UFLIA};
-    \node at (1,10) {\small QF\_UFDTLIRA};
-    \node at (1,9) {\small QF\_UFLRA};
-    %QF_Equality+NonLinearArith
-    \node at (1,8) {\small QF\_ANIA};
-    \node at (1,7) {\small QF\_AUFNIA};
-    \node at (1,6) {\small QF\_UFNIA};
-    \node at (1,5) {\small QF\_UFNRA};
-    %QF_Equality+Bitvec
-    \node at (1,4) {\small QF\_ABV};
-    \node at (1,3) {\small QF\_AUFBV};
-    \node at (1,2) {\small QF\_UFBV};
-    %QF_Equality+Bitvec+Arith
-    \node at (2.05,4) {\small QF\_AUFBVLIA};
-    \node at (2.05,3) {\small QF\_AUFBVNIA};
-    \node at (2.05,2) {\small QF\_UFBVLIA};
-    %QF_FPArith
-    \node at (2.05,14) {\small QF\_ABVFP};
-    \node at (2.05,13) {\small QF\_ABVFPLRA};
-    \node at (2.05,12) {\small QF\_AUFBVFP};
-    \node at (2.05,11) {\small QF\_BVFP};
-    \node at (2.05,10) {\small QF\_BVFPLRA};
-    \node at (2.05,9) {\small QF\_FP};
-    \node at (2.05,8) {\small QF\_FPLRA};
-    \node at (2.05,7) {\small QF\_UFFP};
-    \node at (2.05,6) {\small QF\_UFFPDTLIRA};
-    }
-    %
-    \uncover<2-> {
-      \draw (2.6,-0.5) -- (2.6,17);
-      \node at (1,16.5) {Quantifier-free};
-      \node at (4,16.5) {Quantified};
-    }
-    \uncover<3-> {
-      \draw (-.5,.5) rectangle (2.6,1.5);
-      \draw (-.5,1.5) rectangle (.5,2.5);
-      \draw (-.5,2.5) rectangle (.5,6.5);
-      \draw (-.5,6.5) rectangle (.5,7.5);
-      \draw (-.5,7.5) rectangle (.5,9.5);
-      \draw (-.5,9.5) rectangle (.5,11.5);
-      \draw (-.5,11.5) rectangle (.5,14.5);
-      \draw (.5,1.5) rectangle (1.5,4.5);
-      \draw (.5,4.5) rectangle (1.5,8.5);
-      \draw (.5,8.5) rectangle (1.5,14.5);
-      \draw (1.5,1.5) rectangle (2.6,5);
-      \draw (1.5,5) rectangle (2.6,14.5);
-
-      \draw (2.6,0) rectangle (3.5,5);
-      \draw (2.6,5) rectangle (3.5,7);
-      \draw (2.6,7) rectangle (3.5,10);
-      \draw (2.6,10) rectangle (3.5,15);
-      \draw (3.5,-.5) rectangle (5.6,6.5);
-      \draw (3.5,6.5) rectangle (5.6,10.5);
-      \draw (3.5,10.5) rectangle (5.6,15.5);
-    }
-    \uncover<4-> {
-      \node at (1,15) {QF\_};
-      \node at (0,13) {LinearInt};
-      \node at (0,10.5) {LinearReal};
-      \node at (0,8.5) {NonLinearInt};
-      \node at (0,7) {NonLinearReal};
-      \node at (0,4.5) {Equality};
-      \node at (0,2) {Bitvec};
-      \node at (1,11.5) {\begin{tabular}{c}Equality+\\LinearArith\end{tabular}};
-      \node at (1,6.5) {\begin{tabular}{c}Equality+\\NonLinearArith\end{tabular}};
-      \node at (1,3) {\begin{tabular}{c}Equality+\\Bitvec\end{tabular}};
-      \node at (1,1) {String};
-      \node at (2,10) {FPArith};
-      \node at (2,3) {\begin{tabular}{c}Equality+\\Bitvec+Arith\end{tabular}};
-      \node at (1,15) {QF\_};
-
-      \node at (3,12.5) {Arith};
-      \node at (3,8.5) {Equality};
-      \node at (3,6) {Bitvec};
-      \node at (3,2.5) {FPArith};
-
-      \node at (4.5,13) {\begin{tabular}{c}Equality+\\LinearArith\end{tabular}};
-      \node at (4.5,8.5) {\begin{tabular}{c}Equality+\\NonLinearArith\end{tabular}};
-      \node at (4.5,3){\begin{tabular}{c}Equality+\\MachineArith\end{tabular}};
-    }
-  \end{tikzpicture}
-  }
-
-  \uncover<2-3>{
-    \small
-    \textbf{Q}uantifier \textbf{F}ree
-    \textbf{A}rray
-    \textbf{U}ninterpreted \textbf{F}unction
-    \textbf{B}it\textbf{V}ector
-    \textbf{F}loating\textbf{P}oint
-    \textbf{D}ata\textbf{T}ype
-    \textbf{S}trings
-    \textbf{N}onlinear/\textbf{L}inear
-    \textbf{I}nteger \textbf{R}eal
-    \textbf{A}rithmetic
-    \textbf{D}ifference \textbf{L}ogic
-    }
 \end{frame}
@@
 
-\begin{frame}[fragile]{SMT-COMP Tracks (new)}
-  SMT-COMP 2021 has two new experimental tracks (sponsored by AWS).
+\begin{frame}[fragile]{SMT-COMP Tracks (experimental)}
+
+  \emph{Model Validation}
+  \begin{itemize}
+    \item Division with quantifier-free floating-point logics
+    \item Model validation with Dolmen (thanks to Gillaume Bury and Fran\c{c}ois
+    Bobot)
+  \end{itemize}
   \bigskip
 
-  \emph{Parallel Track}
+  \emph{Cloud and Parallel Track} (sponsored by AWS, led by Mike Whalen)
   \begin{itemize}
-  \item Solve a large problem on a big computer
+  \item Solve a large problem over the cloud (or a big computer)
   \begin{itemize}
-    \item 64 cores, 256 GB of memory
+    \item 100 machines, 1600 cores, 6400 GB of memory (cloud)
+    \item 64 cores, 256 GB of memory (parallel)
   \end{itemize}
@@
   \end{itemize}
-  \bigskip
-  \emph{Cloud Track}
+
+  \pause\bigskip
+
+  \emph{Proof Exhibition Track}
   \begin{itemize}
-  \item Solve a large problem on a network of computers
-    \begin{itemize}
-    \item 100 machines, 1600 cores, 6400 GB of memory
+  \item Solver submitted together with a checker for unsatisfiability proofs
+  \item No predefined format or checker
+  \item No ranking
+  \item Qualitative assessment
   \end{itemize}
-  \item Solver answers sat/unsat/unknown
-  \end{itemize}
+
 \end{frame}
@@
 \begin{frame}{Tracks, Solvers, Divisions, and Benchmarks}
-  Teams: 18 (+2)
+  Teams: 21 (+3)
   \bigskip
@@
     \hline
-    Single Query  &  19&(-1)  & 18&(-49)  & 101300/381683 \\
-    Incremental &  7&(-2)   & 15&(-11)  & 22233/43284   \\
-    Unsat Core  &  7&(+2)   & 17&(-23)  & 55463/108188  \\
-    Model Validation  &  7&(=)    &  3&(+2) + 3 exp.  & 13301/21251  \\
-    Parallel &   &3      &   &14 exp.  & 413/20705 \\
-    Cloud & &5      &   &14 exp.  & 405/20669 \\
+    Single Query  &  22&(+3)  & 19&(+1)  & 93\,945 \\
+    Incremental &  8&(+1)   & 17&(+2)  & 22\,300   \\
+    Unsat Core  &  6&(-1)   & 18&(+1)  & 57\,245  \\
+    Model Validation  &  8&(+1)    &  7& (+ 1 exp.)  & 32\,766  \\
+    Proof Exhibition  &  &4    &  & 18 exp.  & 57\,245  \\
+    \hline
+    Parallel &   4&(+1)      &   &14 exp.  & 400 \\
+    Cloud & 4&(-1)      &  &14 exp.  & 400 \\
+
   \end{tabular}
@@
 
-  Number in parenthesis shows changes from 2020
+  Number in parenthesis shows changes from 2021
 \end{frame}
@@
 
-  SMT-COMP 2021 participants:
+  SMT-COMP 2022 participants rely on multiple reasoning frameworks:
   \begin{itemize}
-  \item classic CDCL(T)-based SMT solvers
-  \item mcSAT-based solvers
-  \item automated theorem provers
-  \item finite domain solver
-  \item local search techniques
-  \item wrapper extending the scope of existing solvers
+  \item CDCL(T)
+  \item mcSAT
+  \item saturation
+  \item automata
+  \item finite domain
+  \item CP
+  \item local search
+  \item besides wrappers extending the scope of existing solvers
   \end{itemize}
@@
   \bigskip
-  Four new solvers participated:
+  Six new solvers participated:
   \begin{itemize}
-  \item iProver (Konstantin Korovin, Andre Duarte, Edvard K Holden)
-  \item mc2 (Simon Cruanes, Guillaume Bury)
-  \item YicesLS (Bohan Li, Shaowei Cai, Xindi Zhang)
-  \item YicesQS (Stéphane Graham-Lengrand)
+  \item NRA-LS   {\footnotesize (Liu et al.)}
+  \item OSTRICH {\footnotesize (Chen et al.)}
+  \item Yices-ismt {\footnotesize (Jia et al.)}
+  \item Z3++ {\footnotesize (Cai et al.)}
+  \item solsmt {\footnotesize (Reitwiessner and Soos)}
   \end{itemize}
@@
   \noindent\makebox[\textwidth]{%
-    \includegraphics[height=\paperheight]{bitwuzla-nonumber.pdf}}
+    \includegraphics[height=\paperheight]{slide-bitwuzla.pdf}}
 \end{frame}
@@
   \noindent\makebox[\textwidth]{%
-    \includegraphics[height=\paperheight]{COLIBRI-nonumber.pdf}}
+    \includegraphics[height=\paperheight]{slide-colibri.pdf}}
 \end{frame}
@@
   \noindent\makebox[\textwidth]{%
-    \includegraphics[height=\paperheight]{cvc5-nonumber.pdf}}
+    \includegraphics[height=\paperheight]{slide-cvc5.pdf}}
 \end{frame}
@@
   \noindent\makebox[\textwidth]{%
-    \includegraphics[height=\paperheight]{cvc5-gg-nonumber.pdf}}
+    \includegraphics[height=\paperheight]{slide-cvc5-cloud.pdf}}
 \end{frame}
@@
   \noindent\makebox[\textwidth]{%
-    \includegraphics[height=\paperheight]{iprover-nonumber.pdf}}
-\end{frame}
-}
-
-{
-\setbeamertemplate{footline}{\quad\hfill\footnotesize\textcolor{white}{\insertframenumber}\strut\kern1em\vskip1pt}
-\begin{frame}
-  \vspace*{-1pt}%
-  \noindent\makebox[\textwidth]{%
-    \includegraphics[height=\paperheight]{mc2-nonumber.pdf}}
+    \includegraphics[height=\paperheight]{slide-nra-ls.pdf}}
 \end{frame}
@@
   \noindent\makebox[\textwidth]{%
-    \includegraphics[height=\paperheight]{opensmt-nonumber.pdf}}
+    \includegraphics[height=\paperheight]{slide-opensmt.pdf}}
 \end{frame}
@@
   \noindent\makebox[\textwidth]{%
-    \includegraphics[height=\paperheight]{smtinterpol-nonumber.pdf}}
-\end{frame}
-}
-
-{
-%\setbeamertemplate{footline}{\quad\hfill\footnotesize\textcolor{white}{\insertframenumber}\strut\kern1em\vskip1pt}
-\begin{frame}<1,3>
-  \vspace*{-1pt}%
-  \noindent\makebox[\textwidth]{%
-    \only<1>{%
-      \includegraphics[height=\paperheight,page=1]{smt-rat-nonumber.pdf}
-    }\only<2>{%
-      \includegraphics[height=\paperheight,page=2]{smt-rat-nonumber.pdf}
-    }\only<3>{%
-      \includegraphics[height=\paperheight,page=3]{smt-rat-nonumber.pdf}
-    }}%
+    \includegraphics[height=\paperheight]{slide-smtinterpol.pdf}}
 \end{frame}
@@
   \noindent\makebox[\textwidth]{%
-    \includegraphics[height=\paperheight]{UltimateEliminator-nonumber.pdf}}
+    \includegraphics[height=\paperheight]{slide-solsmt.pdf}}
 \end{frame}
@@
   \noindent\makebox[\textwidth]{%
-    \includegraphics[height=\paperheight]{vampire-nonumber.pdf}}
+    \includegraphics[height=\paperheight]{slide-stp.pdf}}
 \end{frame}
@@
   \noindent\makebox[\textwidth]{%
-    \includegraphics[height=\paperheight]{verit-nonumber.pdf}}
-\end{frame}
-}
-
-{
-\begin{frame}
-  \vspace*{-1pt}\vspace*{-.1\paperheight}%
-  \noindent\makebox[\textwidth]{%
-    \includegraphics[height=1.2\paperheight]{Yices-nonumber.pdf}}
+    \includegraphics[height=\paperheight]{slide-verit.pdf}}
 \end{frame}
@@
   \noindent\makebox[\textwidth]{%
-    \includegraphics[height=\paperheight]{YicesQS-nonumber.pdf}}
+    \includegraphics[height=\paperheight]{slide-yices.pdf}}
 \end{frame}
@@
   \noindent\makebox[\textwidth]{%
-    \includegraphics[height=\paperheight]{YicesLS-nonumber.pdf}}
+    \includegraphics[height=\paperheight]{slide-yices-ismt.pdf}}
+\end{frame}
+}
+
+{
+\begin{frame}
+  \vspace*{-1pt}%
+  \noindent\makebox[\textwidth]{%
+    \includegraphics[height=\paperheight]{slide-yices-qs.pdf}}
+\end{frame}
+}
+
+{
+\begin{frame}
+  \vspace*{-1pt}%
+  \noindent\makebox[\textwidth]{%
+    \includegraphics[height=\paperheight]{slide-z3pp.pdf}}
+\end{frame}
+}
+
+{
+  \begin{frame}
+    \frametitle{Other participants}
+    \begin{itemize}
+      \item Q3B
+      \vitem SMT-RAT
+      \vitem SMTS
+      \vitem UltimateEliminatior+MathSAT
+      \vitem Vampire
+      \vitem Z3str4
+    \end{itemize}
   \end{frame}
@@
 
-  Submitted by Organisers
+  Submitted by organisers
   \begin{itemize}
-  \item z3-4.8.11
-  \item MathSAT 5.6.6
-  \item Par4 (for Parallel Track)
-  \item Division winners from last year (32 Solvers)
+  \item z3-4.8.17
+  \item MathSAT 5.6.8
+  \item Best solvers, per division, from previous years (23 Solvers)
   \end{itemize}
@@
 
-  Submitted by Participants
+  Submitted by participants
   \begin{itemize}
-  \item Fixed solvers (Bitwuzla, COLIBRI, cvc5, iProver, OpenSMT, Vampire)
-  \end{itemize}
-\end{frame}
-
-\begin{frame}
-  \frametitle{New in 2021}
-
-  \begin{itemize}
-  \item model validation track extended
-  \item manually checking and resolving disagreements
-  \item multiple logics per division
-  \item we will create an artifact
-  \end{itemize}
-\end{frame}
-
-\begin{frame}[fragile]
-  \frametitle{Model Validation Track}
-
-  Solvers print model for each constant/uninterpreted function
-\begin{verbatim}
-sat
-(model
-  (define-fun x15 () Int 5)
-  (define-fun x24 () x135 (as @1 x135))
-  (define-fun x10 ((?X1 Int)) Int (ite (and (= ?X1 10)) 2 (ite...
-\end{verbatim}
-
-  \begin{itemize}
-  \item model validator based on pySMT
-  \item all models of the competitors were accepted
-  \item validator is still inefficient ($>$ 15 minutes)
-  \end{itemize}
-
-  \bigskip
-
-  Many thanks to \emph{Andrea Micheli}
-\end{frame}
-
-\begin{frame}{Checking Disagreements}
-
-  \begin{itemize}
-  \item 111285 instances of 381683 have no status
-  \item we checked disagreements between solvers
-  \item 209 non-incremental instances
-    and 65 incremental instances
-  \item only 28 had known sat/unsat status
-  \item tactics to resolve status:
-    \begin{itemize}
-    \item similar disagreements on instances with known status
-    \item confirmed with fixed version of participants
-    \item analyzed model from solver claiming sat
-    \item majority vote
-    \item in rare cases manually analyzed instances
-    \end{itemize}
-  \item solvers found unsound: (Bitwuzla, COLIBRI, cvc5, iProver, MathSAT, OpenSMT, Par4, UltimateEliminator+MathSAT, Vampire, Z3str4)
-  \end{itemize}
-\end{frame}
-
-\begin{frame}
-  \frametitle{Divisions}
-  Tracks are split into \emph{divisions}.
-
-  \begin{itemize}
-  \item \emph{before 2021}: Division = SMT-LIB logic
-  \item \emph{2021}: 19 Divisions subdivided in 84 logics
-  \end{itemize}
-
-  This implied more changes:
-  \begin{itemize}
-  \item solver authors select supported logics
-    \begin{itemize}
-    \item[$\Rightarrow$] solvers may run on only a part of a division.
-    \end{itemize}
-  \item fewer winners (1--5 winners per division)
-  \item two solvers won a logic but not a division
-    \begin{itemize}
-    \item YicesQS won NRA
-    \item YicesLS won QF\_IDL
-    \end{itemize}
-  \end{itemize}
-\end{frame}
-
-\begin{frame}
-  \frametitle{Statistics}
-  Solver Size
-  \begin{itemize}
-  \item range from 930~kB to 196~MB (compressed)
-  \item total 436 MB
-  \item unsat core post-processor: 361~MB
-  \end{itemize}
-  \bigskip
-  \pause
-
-  Job statistics
-  \begin{itemize}
-  \item Total Job Size: $\sim$ 85 GB
-    \begin{itemize}
-    \item 35~GB YicesLS temporary files
-    \item 29~GB z3 models
-    \end{itemize}
-  \item 1\,371\,593 pairs (+428\,000)
-  \item 16.3 CPU years (+6.4), 9.22 computer years on StarExec
-  \item excludes result processors, StarExec overhead, glitches
+  \item Fixed solvers (OpenSMT, STP, Yices-ismt, Z3++,smtinterpol)
   \end{itemize}
@@
   \pause
-  \emph{Single Query}
+  \emph{Single Query, sequential score}
   \begin{itemize}
-  \item \emph{Bitwuzla}: {\small QF\_Bitvec, QF\_Equality+Bitvec}
-  \item \emph{cvc5}: \begin{minipage}{.8\textwidth}\raggedright \tiny Arith, Bitvec, Equality, Equality+LinearArith, Equality+MachineArith, Equality+NonLinearArith, FPArith, QF\_Equality, QF\_Equality+LinearArith, QF\_Equality+NonLinearArith, QF\_FPArith, QF\_LinearIntArith, QF\_LinearRealArith, QF\_NonLinearIntArith, QF\_NonLinearRealArith, QF\_Strings\end{minipage}
-  \item \emph{iProver}: {\small Equality+NonLinearArith}
+  \item \emph{Bitwuzla}: {\small FPArith, QF\_Bitvec, QF\_Equality+Bitvec, QF\_FPArith}
+
+  \item \emph{cvc5}: \begin{minipage}{.8\textwidth}\raggedright \tiny Arith,
+    Bitvec, Equality, Equality+LinearArith, Equality+MachineArith,
+    Equality+NonLinearArith, QF\_Datatypes, QF\_Equality+NonLinearArith, QF\_NonLinearIntArith, QF\_NonLinearRealArith, QF\_Strings\end{minipage}
+
+  \item \emph{OpenSMT}: {\small QF\_LinearIntArith}
+
   \item \emph{SMTInterpol}: {\small QF\_Equality+LinearArith}
-  \item \emph{UltimateEliminator+MathSAT}: {\small Equality+NonLinearArith}
-  \item \emph{Vampire}: {\small Arith, Equality, Equality+NonLinearArith}
-  \item \emph{Yices2}: {\tiny QF\_Bitvec, QF\_Equality, QF\_LinearIntArith, QF\_LinearRealArith, QF\_NonLinearIntArith}
+
+  \item \emph{Yices2}: {\small QF\_Equality, QF\_LinearRealArith}
   \end{itemize}
@@
   \begin{itemize}
-  \item \emph{cvc5}: \begin{minipage}{.8\textwidth}\raggedright \tiny Arith, Bitvec, Equality, Equality+LinearArith, Equality+NonLinearArith, FPArith, QF\_Equality, QF\_Equality+LinearArith, QF\_FPArith\end{minipage}
-  \item \emph{OpenSMT}: {\small QF\_LinearRealArith}
-  \item \emph{SMTInterpol}: {\small QF\_Equality+NonLinearArith,QF\_NonLinearIntArith}
-  \item \emph{STP}: {\small QF\_Bitvec}
-  \item \emph{Yices2}: {\small QF\_Equality+Bitvec,QF\_LinearIntArith}
+\item \emph{cvc5}: Arith, Bitvec, Equality+LinearArith,EqualityNonLinearArith,Equality
+\item \emph{UltimateEliminator+MathSAT}: Equality+MachineArith
+\item \emph{Bitwuzla}: FPArith, QF\_Bitvec, QF\_FPArith
+\item \emph{Yices2}: QF\_Equality+Bitvec, QF\_Equality, QF\_LinearIntArith
+\item \emph{SMTInterpol}: QF\_Equality+LinearArith, QF\_Equality+NonLinearArith, QF\_NonLinearIntArith
+\item \emph{OpenSMT}: QF\_LinearRealArith
   \end{itemize}
@@
   \begin{itemize}
-  \item \emph{Bitwuzla}: {\small QF\_Bitvec}
-  \item \emph{cvc5}: {\small QF\_LinearIntArith}
-  \item \emph{Yices2}: {\small QF\_LinearRealArith}
+\item \emph{Bitwuzla}: QF\_Bitvec, QF\_Equality+Bitvec,
+\item \emph{smtinterpol}: QF\_Equality+LinearArith
+\item \emph{Yices2}: QF\_Equality
+\item \emph{Z3++}: QF\_LinearIntArith
+\item \emph{OpenSMT}: QF\_LinearRealArith
+
+\item experimental: QF\_FPArith : Bitwuzla, cvc5
+
   \end{itemize}
@@
     \emph{Single Query}\\
-    seq & Vampire&{\tiny(Eq+NA)} & cvc5&{\tiny(Eq+LA)} & Yices2&{\tiny(QF\_NIA)} \\
-    par & iProver&{\tiny(Eq+NA)} & Vampire&{\tiny(Eq)} & cvc5&{\tiny(Eq+LA)} \\
-    sat & cvc5&{\tiny(Eq+LA)} & UltimateElim&{\tiny(Eq+NA)} & Vampire&{\tiny(Eq)}\\
-    unsat & cvc5&{\tiny(Eq+NA)} & Yices2&{\tiny(QF\_NIA)} & Vampire&{\tiny(Eq)}\\
-    24 &  Vampire&{\tiny(Eq+NA)} & cvc5&{\tiny(Eq+LA)} & Yices2&{\tiny(QF\_LIA)}\\[3pt]
+    seq & cvc5&{\tiny(Eq+MA)} & YicesQS&{\tiny(Arith)} & Bitwuzla&{\tiny(FPArith)} \\
+    par & cvc5&{\tiny(Eq+MA)} & YicesQS&{\tiny(Arith)} & Bitwuzla&{\tiny(FPArith)} \\
+    sat & cvc5&{\tiny(Eq+LA)} & YicesQS&{\tiny(Arith)} & Bitwuzla&{\tiny(FPArith)} \\
+    unsat & cvc5&{\tiny(Eq+MA)} & Z3++&{\tiny(QF\_NonLIA)} & OSTRICH&{\tiny(QF\_Strings)}\\
+    24 &  Vampire&{\tiny(Eq+NA)} & Vampire&{\tiny(Equality)} & Yices2&{\tiny(QF\_LinIA)}\\[3pt]
     \pause
     \emph{Incremental}\\
-    par & cvc5&{\tiny(Eq)} &Yices2&{\tiny(QF\_Eq+LA)}
+    par & cvc5&{\tiny(Eq+NA)} &Yices2&{\tiny(QF\_Eq+LA)}
     &SMTInterpol&{\tiny(QF\_Eq+NA)}\\[3pt]
     \pause
+
     \emph{Unsat Core}\\
     seq & cvc5&{\tiny(Eq+LA)} &
-    Yices2&{\tiny(QF\_Eq+LA)}\\
-    par &  cvc5&{\tiny(Eq+LA)}&
-    Yices2&{\tiny(QF\_Eq+LA)}\\[3pt]
+    Bitwuzla&{\tiny(QF\_Eq+Bitvec)}\\
+
+    par &  cvc5&{\tiny(Eq+NA)}&
+    Bitwuzla&{\tiny(QF\_Eq+Bitvec)}\\
+\\[3pt]
     \pause
     \emph{Model Validation}\\
-    seq &  cvc5&{\tiny(QF\_LIA)} & Bitwuzla&{\tiny(QF\_BV)}
-        & Yices2&{\tiny(QF\_LRA)}\\
-    par &  cvc5&{\tiny(QF\_LIA)} & Bitwuzla&{\tiny(QF\_BV)}
-        & Yices2&{\tiny(QF\_LRA)}\\
+    seq &  Z3++&{\tiny(QF\_LinIA)} & Bitwuzla&{\tiny(QF\_Bitvec)}
+        & smtinterpol&{\tiny(QF\_Eq+LIA)}\\
+    par &  Z3++&{\tiny(QF\_LinIA)} & Bitwuzla&{\tiny(QF\_Bitvec)}
+        & smtinterpol&{\tiny(QF\_Eq+LIA)}\\
   \end{tabular}
@@
     \emph{Single Query}\\
-    seq & cvc5&{\tiny(Eq+MA)} & Vampire&{\tiny(Eq+NA)} & Bitwuzla&{\tiny(QF\_Eq+BV)} \\
-    par & cvc5&{\tiny(Eq+MA)} & iProver&{\tiny(Eq+NA)} & Vampire&{\tiny(Eq)} \\
-    sat & cvc5&{\tiny(Eq+MA)} & UltimateElim&{\tiny(Eq+NA)} & Vampire&{\tiny(Eq)}\\
-    unsat & cvc5&{\tiny(Eq+MA)} & Yices2&{\tiny(QF\_NIA)} & Vampire&{\tiny(Arith)}\\
-    24 &  cvc5&{\tiny(Eq+MA)} & Yices2&{\tiny(QF\_LIA)} & Vampire&{\tiny(Eq+NA)}\\[3pt]
+    seq & cvc5&{\tiny(QF\_DT)} & Bitwuzla&{\tiny(FPArith)} & Yices2&{\tiny(QF\_LinRA)} \\
+    par & cvc5&{\tiny(QF\_DT)} & Bitwuzla&{\tiny(FPArith)} & Yices2&{\tiny(QF\_LinRA)} \\
+    sat & cvc5&{\tiny(QF\_DT)} & Bitwuzla&{\tiny(FPArith)} & Z3++&{\tiny(QF\_NonRA)} \\
+    unsat & cvc5&{\tiny(QF\_DT)} & Z3++&{\tiny(QF\_NonIA)} & Bitwuzla&{\tiny(FPArith)} \\
+    24 &  cvc5&{\tiny(Eq+MA)} & smtinterpol&{\tiny(QF\_DT)} & Vampire&{\tiny(Equality)}\\[3pt]
     \pause
     \emph{Incremental}\\
-    par & cvc5&{\tiny(BV)} &SMTInterpol&{\tiny(QF\_NIA)}
-    &Yices2&{\tiny(QF\_LIA)}\\[3pt]
+    par & SMTInterpol&{\tiny(QF\_NIA)}
+    &Yices2&{\tiny(QF\_LinIA)} & cvc5&{\tiny(Eq+NonLA)} \\[3pt]
     \pause
     \emph{Unsat Core}\\
-    seq & cvc5&{\tiny(QF\_NRA)} &
-    Yices2&{\tiny(QF\_Eq+LA)} &
-    Bitwuzla&{\tiny(QF\_Eq+BV)} \\
-    par & cvc5&{\tiny(QF\_NRA)} &
-    Yices2&{\tiny(QF\_Eq+LA)} &
-    Bitwuzla&{\tiny(QF\_Eq+BV)} \\[3pt]
+    seq & cvc5&{\tiny(Eq+MA)} &    Yices2&{\tiny(QF\_Eq+LA)} &    smtinterpol&{\tiny(QF\_Eq+NA)} \\
+    par & cvc5&{\tiny(Eq+MA)} &    Yices2&{\tiny(QF\_Eq+LA)} &    smtinterpol&{\tiny(QF\_Eq+NA)} \\
     \pause
     \emph{Model Validation}\\
-    seq &  cvc5&{\tiny(QF\_LIA)} & Yices2&{\tiny(QF\_LRA)}
-        & Bitwuzla&{\tiny(QF\_BV)} \\
-    par &  cvc5&{\tiny(QF\_LIA)} & Yices2&{\tiny(QF\_LRA)}
-        & Bitwuzla&{\tiny(QF\_BV)} \\
+    seq &  Z3++&{\tiny(QF\_LinIA)} & smtinterpol&{\tiny(QF\_LinA)}        & OpenSMT&{\tiny(QF\_LinRA)} \\
+    par &  Z3++&{\tiny(QF\_LinIA)} & smtinterpol&{\tiny(QF\_LinA)}        & OpenSMT&{\tiny(QF\_LinRA)} \\
   \end{tabular}
+\end{frame}
+
+\begin{frame}{Checking Disagreements}
+
+  \begin{itemize}
+  \item  instances of 391\,363 have no status
+
+  \vitem Only 18 benchmarks with disagreements (AUFDTLIA, QF\_NIA)
+
+  \vitem We manually resolved the disagreements
+  \begin{itemize}
+    \item Authors confirmed solver unsoundness
+    \item Sound solvers agreed on result
+  \end{itemize}
+
+  \vitem We had only three solvers with soundness issues: SMTIinterpol, Z3++,
+  yices-ismt
+  \begin{itemize}
+    \item Down from 10 last year
+  \end{itemize}
+  \end{itemize}
 \end{frame}
@@
   \begin{itemize}
-  \item Extend Model Validator to \emph{new logics}?
-%    \begin{itemize}
-%    \item Non-Linear Arithmetic -- what about div by 0?
-%    \item Data Types -- partially defined functions?
-%    \item Floating-Point, String
-%    \item Arrays -- how to specify lambda arrays?
-%    \end{itemize}
+    \item Move to Dolmen as single model validator
 
-  \item Run Model Validator on \emph{unknown} benchmarks?
-  \item New \emph{Proof Validation} Track
+      \vitem Dolmen worked well in QF\_FP (minor issue with empty output, simple
+      to fix)
+      \vitem pysmt timed out in two cases (locally with more time one of them
+      succeeded)
+      \vitem pysmt could not understand the model in 9 cases
+      \vitem Dolmen is easy to extend to new theories
+      \vitem Easy to integrate with correct-by-construction code extracted from
+      Coq
+      \vitem Should be more efficient for handling function call
+
   \end{itemize}
@@
 
-\begin{frame}{Proof Validation Track}
-  We plan to introduce a proof validation track
-  \begin{enumerate}
-  \item define \emph{solver independent} proof format
+\begin{frame}{Plans for SMT-COMP 2022}
   \begin{itemize}
-    \item probably resolution based %Encode resolution dag as SMT-LIB let term
-    \item atoms are SMT-LIB formulas
-%    \item Input formulas are unit-clauses
-%    \item Tseitin-style Axioms provide meaning to logical symbols
-    \item fine-grain proofs
+    \item Proof \textit{validation} track
+
+      \vitem Hopefully proof exhibition this year will help
+
+      \vitem We have to analyze the data still
+      \begin{itemize}
+        \item Job only finished last week (took 18 days to run)
+        \item 830gb
       \end{itemize}
-  \item implement proof validator
-  \item run solvers on unsat \emph{and unknown} benchmarks
-  \end{enumerate}
-  \bigskip
 
-  Contact us, if you're interested in SMT-LIB proofs.
+  \end{itemize}
+
 \end{frame}
@@
   \item Jochen Hoenicke
-  \item Antti Hyvärinen
+  \item Fran\c{c}ois Bobot
   \end{itemize}
 
-  Antti's three-year term is ending now.
+  Both Haniel and Jochen have been organizers for three-years. One of them
+  should be replaced.
   \bigskip
@@
   \begin{itemize}
-  \item \emph{Andrea Micheli}: Model Validator
+    \item \emph{Andrea Micheli}: pysmt
+    \item \emph{Guillaume Bury}: Model Validator
     \item \emph{Clark Barrett, Pascal Fontaine, Aina Niemetz, Mathias Preiner, Hans-Jörg Schurr}: SMT-LIB benchmarks
     \item \emph{Aaron Stump}: StarExec support
-  \item \emph{Mike Whalen, Jonathan Eidelman}: Cloud/Parallel Track
+    \item \emph{Mike Whalen and team}: Cloud/Parallel Track
   \end{itemize}
@@
 \begin{frame}[shrink=0.95]{Benchmark contributors}
-  In 2021 \emph{new benchmarks} were contributed by:
+  In 2022 \emph{new benchmarks} were contributed by:
 
@@
   \begin{itemize}
-  \item Andrew V. Jones
-  \item Nuno Lopes
-  \item Pierre Bouvier
-  \item Alexey Vishnyakov, Andrey Fedotov, Daniil Kuts, Alexander Novikov, Darya Parygina, Eli Kobrin, Vlada Logunova, Pavel Belecky, Shamil Kurmangaleev
-  \item Hernán Ponce de León
-  \item Anastasiia Izycheva, Eva Darulova
-  \item Da Shen, Yuliya Lierler
-  \item Maria A Schett, Julian Nagele
-  \item Mathias Preiner, Aina Niemetz
-  \item Clark Berrett
-  \item Johannes Schoisswohl
-  \item Jackson Melchert, Nestan Tsiskaridze
-  \item Wei-Cheng Wu
-  \item Matteo Favaro, Peter Garba
-  \item Tjark Weber
+    \item  Alex Coffin
+    \item  Alex Ozdemir
+    \item  Ali Uncu, James Davenport and Matthew England
+    \item  Bohan Li
+    \item  Elizabeth Polgreen
+    \item  Fuqi Jia
+    \item  Johann-Tobias Aaron and Raphael Schäg
+    \item  Matthew England and Miguel Del Rio Almajano
+    \item  Nicolas Amat
+    \item  Yannick Moy
+    \item  Yoni Zohar
   \end{itemize}

### 2022-08-12 2022/slides/smtWorkshop/slides.tex
fixes

@@
 %
-%   SMT-COMP 2021 - Presentation on SMT-Workshop
+%   SMT-COMP 2022 - Presentation on SMT-Workshop
 %                   virtual conference in "Los Angeles"
@@
 %%% Titel, Autor und Datum des Vortrags:
-\title{SMT-COMP 2021\\
+\title{SMT-COMP 2022\\
 17th International Satisfiability Modulo Theory Competition}
@@
 \begin{frame}[fragile]{SMT-COMP Tracks (traditional)}
-  \emph{Single Query Track}
+  \emph{Single Query (SQ) Track}
   \begin{itemize}
@@
 \end{itemize}
+
+\medskip
+\pause
+  \emph{This year} the sat/unsat results from sound solvers in SQ were used to
+  include benchmarks on the MV, UC and PE tracks.
 
@@
     \includegraphics[height=\paperheight]{slide-smtinterpol.pdf}}
+\end{frame}
+}
+
+{
+\begin{frame}
+  \vspace*{-1pt}%
+  \noindent\makebox[\textwidth]{%
+    \includegraphics[height=\paperheight]{slide-smtrat.pdf}}
 \end{frame}
@@
   \begin{itemize}
-  \item \emph{Bitwuzla}: {\small QF\_Bitvec, QF\_Equality+Bitvec, QF\_FPArith}
-  \item \emph{cvc5}: \begin{minipage}{.8\textwidth}\raggedright \tiny Arith, Bitvec, Equality, Equality+LinearArith, Equality+MachineArith, Equality+NonLinearArith, FPArith, QF\_Equality, QF\_Equality+NonLinearArith, QF\_LinearIntrArith, QF\_NonLinearIntArith, QF\_NonLinearRealArith \end{minipage}
-  \item \emph{Yices2}: {\small QF\_Equality+LinearArith, QF\_LinearRealArith}
+\item \emph{cvc5}: Arith, Bitvec, Equality+LinearArith, Equality+MachineArith,Equality+NonLinearArith,Equality(Seq), QF\_Datatypes
+\item \emph{Vampire}: Equality(Par)
+\item \emph{Bitwuzla}: QF\_EqualityBitvec, QF\_FPArith
+\item \emph{Yices2}: QF\_Bitvec, QF\_Equality+LinearArith, QF\_Equality, QF\_LinearIntArith, QF\_LinearRealArith
+\item \emph{SMTInterpol}: QF\_Equality+NonLinearArith
+\item \emph{UltimateEliminator+MathSAT}: FPArith
+
   \end{itemize}
@@
 \item \emph{UltimateEliminator+MathSAT}: Equality+MachineArith
-\item \emph{Bitwuzla}: FPArith, QF\_Bitvec, QF\_FPArith
-\item \emph{Yices2}: QF\_Equality+Bitvec, QF\_Equality, QF\_LinearIntArith
+\item \emph{Bitwuzla}: FPArith, QF\_FPArith
+\item \emph{Yices2}: QF\_Bitvec, QF\_Equality+Bitvec, QF\_Equality, QF\_LinearIntArith
 \item \emph{SMTInterpol}: QF\_Equality+LinearArith, QF\_Equality+NonLinearArith, QF\_NonLinearIntArith
@@
   \begin{itemize}
-  \item  instances of 391\,363 have no status
+  \item  111\,451 instances of 391\,363 have no status
 
@@
     \item Down from 10 last year
+    \pause
+    {\tiny (but note that this may be because of our issue with ignoring most of the
+    new benchmarks in the selection)}
+
   \end{itemize}
@@
 \begin{frame}{SMT-COMP organizing committee}
-  Three people organize the SMT-COMP.  In 2021:
+  Three people organize the SMT-COMP.  In 2022:
   \begin{itemize}

### 2023-01-03 2022/slides/flocOlympics/slides.tex
missing slides

--- 2022-08-11 2022/slides/smtWorkshop/slides.tex
@@
 %%% Titel, Autor und Datum des Vortrags:
-\title{SMT-COMP 2021\\
+\title{SMT-COMP 2022\\
 17th International Satisfiability Modulo Theory Competition}
 \author{\emph{Haniel Barbosa} \and Jochen Hoenicke \and Fran\c{c}ois Bobot}
-\date{Aug 11, 2022}
+\date{Aug 9, 2022\\[2ex]      \includegraphics[width=\textwidth]{floc}
+}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\newcommand{\yell}[1]{{\color{red} [#1]}}
+
+% 2952bfff
+\definecolor{ceruleanblue}{rgb}{0.16, 0.32, 0.75}
 
@@
       \begin{block}{Non-incremental}
-        391\,363 instances {\small (+9680)}\\
+        391\,363 instances\\
         with 1 query each \\
-        in 81 logics {\small (+2)}.
+        in 81 logics.
       \end{block}
@@
       \begin{block}{Incremental}
-        43\,285 instances {\small (+1)}\\
-        with 33\,998\,935 queries {\small (+141)} \\
+        43\,285 instances\\
+        with 33\,998\,935 queries \\
         in 39 logics.
@@
       \begin{block}{Selected Non-incremental}
-        \only<2>{206\,932 instances}\only<3>{\textcolor{red}{206\,932}
-          instances\\
-          \textcolor{red}{We mistakenly ignored 9466 new benchmarks}
-        }
+        206\,932 instances
       \end{block}
@@
   \item OSTRICH {\footnotesize (Chen et al.)}
+  \item Q3B {\footnotesize (Jon\'a\v{s} and Strej\v{c}ek)}
   \item Yices-ismt {\footnotesize (Jia et al.)}
@@
 \end{frame}
-
-\section{Solver Presentation}
-
-{
-\begin{frame}
-  \vspace*{-1pt}%
-  \noindent\makebox[\textwidth]{%
-    \includegraphics[height=\paperheight]{slide-bitwuzla.pdf}}
-\end{frame}
-}
-
-{
-\begin{frame}
-  \vspace*{-1pt}%
-  \noindent\makebox[\textwidth]{%
-    \includegraphics[height=\paperheight]{slide-colibri.pdf}}
-\end{frame}
-}
-
-{
-\begin{frame}
-  \vspace*{-1pt}%
-  \noindent\makebox[\textwidth]{%
-    \includegraphics[height=\paperheight]{slide-cvc5.pdf}}
-\end{frame}
-}
-
-{
-\begin{frame}
-  \vspace*{-1pt}%
-  \noindent\makebox[\textwidth]{%
-    \includegraphics[height=\paperheight]{slide-cvc5-cloud.pdf}}
-\end{frame}
-}
-
-{
-\begin{frame}
-  \vspace*{-1pt}%
-  \noindent\makebox[\textwidth]{%
-    \includegraphics[height=\paperheight]{slide-nra-ls.pdf}}
-\end{frame}
-}
-
-{
-\begin{frame}
-  \vspace*{-1pt}%
-  \noindent\makebox[\textwidth]{%
-    \includegraphics[height=\paperheight]{slide-opensmt.pdf}}
-\end{frame}
-}
-
-{
-\begin{frame}
-  \vspace*{-1pt}%
-  \noindent\makebox[\textwidth]{%
-    \includegraphics[height=\paperheight]{slide-smtinterpol.pdf}}
-\end{frame}
-}
-
-{
-\begin{frame}
-  \vspace*{-1pt}%
-  \noindent\makebox[\textwidth]{%
-    \includegraphics[height=\paperheight]{slide-solsmt.pdf}}
-\end{frame}
-}
-
-{
-\begin{frame}
-  \vspace*{-1pt}%
-  \noindent\makebox[\textwidth]{%
-    \includegraphics[height=\paperheight]{slide-stp.pdf}}
-\end{frame}
-}
-
-{
-\begin{frame}
-  \vspace*{-1pt}%
-  \noindent\makebox[\textwidth]{%
-    \includegraphics[height=\paperheight]{slide-verit.pdf}}
-\end{frame}
-}
-
-{
-\begin{frame}
-  \vspace*{-1pt}%
-  \noindent\makebox[\textwidth]{%
-    \includegraphics[height=\paperheight]{slide-yices.pdf}}
-\end{frame}
-}
-
-{
-\begin{frame}
-  \vspace*{-1pt}%
-  \noindent\makebox[\textwidth]{%
-    \includegraphics[height=\paperheight]{slide-yices-ismt.pdf}}
-\end{frame}
-}
-
-{
-\begin{frame}
-  \vspace*{-1pt}%
-  \noindent\makebox[\textwidth]{%
-    \includegraphics[height=\paperheight]{slide-yices-qs.pdf}}
-\end{frame}
-}
-
-{
-\begin{frame}
-  \vspace*{-1pt}%
-  \noindent\makebox[\textwidth]{%
-    \includegraphics[height=\paperheight]{slide-z3pp.pdf}}
-\end{frame}
-}
-
-{
-  \begin{frame}
-    \frametitle{Other participants}
-    \begin{itemize}
-      \item Q3B
-      \vitem SMT-RAT
-      \vitem SMTS
-      \vitem UltimateEliminatior+MathSAT
-      \vitem Vampire
-      \vitem Z3str4
-    \end{itemize}
-  \end{frame}
-}
 
@@
   \item MathSAT 5.6.8
-  \item Best solvers, per division, from previous years (23 Solvers)
+  \item Division winners from previous years (23 Solvers)
   \end{itemize}
@@
 
-\begin{frame}{Division Winners}
-  \pause
-  \emph{Single Query, sequential score}
+\begin{frame}{FLoC Medalists}
+
+  \begin{columns}
+    \begin{column}{0.6\textwidth}
+
+  \Large 8 medals
   \begin{itemize}
-  \item \emph{Bitwuzla}: {\small FPArith, QF\_Bitvec, QF\_Equality+Bitvec, QF\_FPArith}
+    \bigskip
+    \vitem Biggest Lead
+    \begin{itemize}
+      \item Single Query: Gold and Silver
+      \item Model Validation: Gold
+      \item Incremental: Gold
+    \end{itemize}
+    \bigskip
 
-  \item \emph{cvc5}: \begin{minipage}{.8\textwidth}\raggedright \tiny Arith,
-    Bitvec, Equality, Equality+LinearArith, Equality+MachineArith,
-    Equality+NonLinearArith, QF\_Datatypes, QF\_Equality+NonLinearArith, QF\_NonLinearIntArith, QF\_NonLinearRealArith, QF\_Strings\end{minipage}
-
-  \item \emph{OpenSMT}: {\small QF\_LinearIntArith}
-
-  \item \emph{SMTInterpol}: {\small QF\_Equality+LinearArith}
-
-  \item \emph{Yices2}: {\small QF\_Equality, QF\_LinearRealArith}
+    \vitem Largest Contribution
+    \begin{itemize}
+      \item Single Query: Gold and Silver
+      \item Model Validation: Gold
+      \item Incremental: Gold
     \end{itemize}
-
-  \medskip
-
-  \pause
-  \emph{Unsat Core}
-  \begin{itemize}
-  \item \emph{Bitwuzla}: {\small QF\_Bitvec, QF\_Equality+Bitvec, QF\_FPArith}
-  \item \emph{cvc5}: \begin{minipage}{.8\textwidth}\raggedright \tiny Arith, Bitvec, Equality, Equality+LinearArith, Equality+MachineArith, Equality+NonLinearArith, FPArith, QF\_Equality, QF\_Equality+NonLinearArith, QF\_LinearIntrArith, QF\_NonLinearIntArith, QF\_NonLinearRealArith \end{minipage}
-  \item \emph{Yices2}: {\small QF\_Equality+LinearArith, QF\_LinearRealArith}
   \end{itemize}
+\end{column}
+\hfill
+\begin{column}{0.4\textwidth}
+  \begin{center}
+    \includegraphics[width=.3\textwidth]{medalgold}
+    \includegraphics[width=.3\textwidth]{medalgold}
+    \includegraphics[width=.3\textwidth]{medalgold}
+    \includegraphics[width=.3\textwidth]{medalgold}
+    \includegraphics[width=.3\textwidth]{medalgold}
+    \includegraphics[width=.3\textwidth]{medalgold}\\
+    \includegraphics[width=.3\textwidth]{medalsilver}
+    \includegraphics[width=.3\textwidth]{medalsilver}
+  \end{center}
+\end{column}
+\end{columns}
 
@@
 
-\begin{frame}{Division Winners}
-  \emph{Incremental}
+\begin{frame}{FLoC Medalists}
+
+  \begin{columns}
+    \begin{column}{0.6\textwidth}
+
+  \Large cvc5 wins three gold medals:
   \begin{itemize}
-\item \emph{cvc5}: Arith, Bitvec, Equality+LinearArith,EqualityNonLinearArith,Equality
-\item \emph{UltimateEliminator+MathSAT}: Equality+MachineArith
-\item \emph{Bitwuzla}: FPArith, QF\_Bitvec, QF\_FPArith
-\item \emph{Yices2}: QF\_Equality+Bitvec, QF\_Equality, QF\_LinearIntArith
-\item \emph{SMTInterpol}: QF\_Equality+LinearArith, QF\_Equality+NonLinearArith, QF\_NonLinearIntArith
-\item \emph{OpenSMT}: QF\_LinearRealArith
+    \bigskip
+    \vitem Single Query, Biggest Lead
+    \bigskip
+
+    \vitem Single Query, Largest Contribution
+    \bigskip
+
+    \vitem Incremental, Largest Contribution
   \end{itemize}
-  \medskip
-
-  \pause
-  \emph{Model Validation (competitive only)}
-  \begin{itemize}
-\item \emph{Bitwuzla}: QF\_Bitvec, QF\_Equality+Bitvec,
-\item \emph{smtinterpol}: QF\_Equality+LinearArith
-\item \emph{Yices2}: QF\_Equality
-\item \emph{Z3++}: QF\_LinearIntArith
-\item \emph{OpenSMT}: QF\_LinearRealArith
-
-\item experimental: QF\_FPArith : Bitwuzla, cvc5
-
-  \end{itemize}
-\end{frame}
-
-\begin{frame}{Largest contribution}
-  \begin{tabular}{r|c@{}lc@{}lc@{}l}
-    &\textcolor{gold}{\textbf{1st Place}} &&
-    \textcolor{silver}{\textbf{2nd Place}} &&
-    \textcolor{bronze}{\textbf{3rd Place}}\\
-    \hline
-    \emph{Single Query}\\
-    seq & cvc5&{\tiny(Eq+MA)} & YicesQS&{\tiny(Arith)} & Bitwuzla&{\tiny(FPArith)} \\
-    par & cvc5&{\tiny(Eq+MA)} & YicesQS&{\tiny(Arith)} & Bitwuzla&{\tiny(FPArith)} \\
-    sat & cvc5&{\tiny(Eq+LA)} & YicesQS&{\tiny(Arith)} & Bitwuzla&{\tiny(FPArith)} \\
-    unsat & cvc5&{\tiny(Eq+MA)} & Z3++&{\tiny(QF\_NonLIA)} & OSTRICH&{\tiny(QF\_Strings)}\\
-    24 &  Vampire&{\tiny(Eq+NA)} & Vampire&{\tiny(Equality)} & Yices2&{\tiny(QF\_LinIA)}\\[3pt]
-    \pause
-    \emph{Incremental}\\
-    par & cvc5&{\tiny(Eq+NA)} &Yices2&{\tiny(QF\_Eq+LA)}
-    &SMTInterpol&{\tiny(QF\_Eq+NA)}\\[3pt]
-    \pause
-
-    \emph{Unsat Core}\\
-    seq & cvc5&{\tiny(Eq+LA)} &
-    Bitwuzla&{\tiny(QF\_Eq+Bitvec)}\\
-
-    par &  cvc5&{\tiny(Eq+NA)}&
-    Bitwuzla&{\tiny(QF\_Eq+Bitvec)}\\
-\\[3pt]
-    \pause
-    \emph{Model Validation}\\
-    seq &  Z3++&{\tiny(QF\_LinIA)} & Bitwuzla&{\tiny(QF\_Bitvec)}
-        & smtinterpol&{\tiny(QF\_Eq+LIA)}\\
-    par &  Z3++&{\tiny(QF\_LinIA)} & Bitwuzla&{\tiny(QF\_Bitvec)}
-        & smtinterpol&{\tiny(QF\_Eq+LIA)}\\
-  \end{tabular}
-\end{frame}
-
-\begin{frame}{Biggest Lead}
-  \begin{tabular}{r|c@{}lc@{}lc@{}l}
-    &\textcolor{gold}{\textbf{1st Place}} &&
-    \textcolor{silver}{\textbf{2nd Place}} &&
-    \textcolor{bronze}{\textbf{3rd Place}}\\
-    \hline
-    \emph{Single Query}\\
-    seq & cvc5&{\tiny(QF\_DT)} & Bitwuzla&{\tiny(FPArith)} & Yices2&{\tiny(QF\_LinRA)} \\
-    par & cvc5&{\tiny(QF\_DT)} & Bitwuzla&{\tiny(FPArith)} & Yices2&{\tiny(QF\_LinRA)} \\
-    sat & cvc5&{\tiny(QF\_DT)} & Bitwuzla&{\tiny(FPArith)} & Z3++&{\tiny(QF\_NonRA)} \\
-    unsat & cvc5&{\tiny(QF\_DT)} & Z3++&{\tiny(QF\_NonIA)} & Bitwuzla&{\tiny(FPArith)} \\
-    24 &  cvc5&{\tiny(Eq+MA)} & smtinterpol&{\tiny(QF\_DT)} & Vampire&{\tiny(Equality)}\\[3pt]
-    \pause
-    \emph{Incremental}\\
-    par & SMTInterpol&{\tiny(QF\_NIA)}
-    &Yices2&{\tiny(QF\_LinIA)} & cvc5&{\tiny(Eq+NonLA)} \\[3pt]
-    \pause
-    \emph{Unsat Core}\\
-    seq & cvc5&{\tiny(Eq+MA)} &    Yices2&{\tiny(QF\_Eq+LA)} &    smtinterpol&{\tiny(QF\_Eq+NA)} \\
-    par & cvc5&{\tiny(Eq+MA)} &    Yices2&{\tiny(QF\_Eq+LA)} &    smtinterpol&{\tiny(QF\_Eq+NA)} \\
-    \pause
-    \emph{Model Validation}\\
-    seq &  Z3++&{\tiny(QF\_LinIA)} & smtinterpol&{\tiny(QF\_LinA)}        & OpenSMT&{\tiny(QF\_LinRA)} \\
-    par &  Z3++&{\tiny(QF\_LinIA)} & smtinterpol&{\tiny(QF\_LinA)}        & OpenSMT&{\tiny(QF\_LinRA)} \\
-  \end{tabular}
-\end{frame}
-
-\begin{frame}{Checking Disagreements}
-
-  \begin{itemize}
-  \item  instances of 391\,363 have no status
-
-  \vitem Only 18 benchmarks with disagreements (AUFDTLIA, QF\_NIA)
-
-  \vitem We manually resolved the disagreements
-  \begin{itemize}
-    \item Authors confirmed solver unsoundness
-    \item Sound solvers agreed on result
-  \end{itemize}
-
-  \vitem We had only three solvers with soundness issues: SMTIinterpol, Z3++,
-  yices-ismt
-  \begin{itemize}
-    \item Down from 10 last year
-  \end{itemize}
-  \end{itemize}
-\end{frame}
-
-\begin{frame}{Plans for SMT-COMP 2022}
-  \begin{itemize}
-    \item Move to Dolmen as single model validator
-
-      \vitem Dolmen worked well in QF\_FP (minor issue with empty output, simple
-      to fix)
-      \vitem pysmt timed out in two cases (locally with more time one of them
-      succeeded)
-      \vitem pysmt could not understand the model in 9 cases
-      \vitem Dolmen is easy to extend to new theories
-      \vitem Easy to integrate with correct-by-construction code extracted from
-      Coq
-      \vitem Should be more efficient for handling function call
-
-  \end{itemize}
+\end{column}
+\hfill
+\begin{column}{0.4\textwidth}
+  \begin{center}
+    \includegraphics[width=.3\textwidth]{medalgold}
+    \includegraphics[width=.3\textwidth]{medalgold}
+    \includegraphics[width=.3\textwidth]{medalgold}
+  \end{center}
+\end{column}
+\end{columns}
 
@@
 
-\begin{frame}{Plans for SMT-COMP 2022}
+\begin{frame}{FLoC Medalists}
+
+  \begin{columns}
+    \begin{column}{0.6\textwidth}
+
+  \Large Z3++ wins two gold medals:
   \begin{itemize}
-    \item Proof \textit{validation} track
+    \bigskip
+    \vitem Model Validation, Biggest Lead
+    \bigskip
 
-      \vitem Hopefully proof exhibition this year will help
-
-      \vitem We have to analyze the data still
-      \begin{itemize}
-        \item Job only finished last week (took 18 days to run)
-        \item 830gb
+    \vitem Model Validation, Largest Contribution
   \end{itemize}
-
-  \end{itemize}
+\end{column}
+\hfill
+\begin{column}{0.4\textwidth}
+  \begin{center}
+    \includegraphics[width=.3\textwidth]{medalgold}
+    \includegraphics[width=.3\textwidth]{medalgold}
+  \end{center}
+\end{column}
+\end{columns}
 
@@
 
-\begin{frame}{SMT-COMP organizing committee}
-  Three people organize the SMT-COMP.  In 2021:
+\begin{frame}{FLoC Medalists}
+
+  \begin{columns}
+    \begin{column}{0.6\textwidth}
+
+  \Large SMTInterpol wins one gold medal:
   \begin{itemize}
-  \item Haniel Barbosa
-  \item Jochen Hoenicke
-  \item Fran\c{c}ois Bobot
+    \bigskip
+    \vitem Incremental, Biggest Lead
   \end{itemize}
+\end{column}
+\hfill
+\begin{column}{0.4\textwidth}
+  \begin{center}
+    \includegraphics[width=.3\textwidth]{medalgold}
+  \end{center}
+\end{column}
+\end{columns}
 
-  Both Haniel and Jochen have been organizers for three-years. One of them
-  should be replaced.
-  \bigskip
-
-  We need a successor for next year's competition.
-  Contact us if you would like to volunteer!
 \end{frame}
 
-\begin{frame}{Acknowledgements}
-  \begin{itemize}
-    \item \emph{Andrea Micheli}: pysmt
-    \item \emph{Guillaume Bury}: Model Validator
-    \item \emph{Clark Barrett, Pascal Fontaine, Aina Niemetz, Mathias Preiner, Hans-Jörg Schurr}: SMT-LIB benchmarks
-    \item \emph{Aaron Stump}: StarExec support
-    \item \emph{Mike Whalen and team}: Cloud/Parallel Track
-  \end{itemize}
-  \bigskip
+\begin{frame}{FLoC Medalists}
 
   \begin{columns}
-    \begin{column}{.3\textwidth}
-      \includegraphics[width=\textwidth]{starlogo}
+    \begin{column}{0.6\textwidth}
+
+  \Large Bitwuzla wins one silver medal:
+  \begin{itemize}
+    \bigskip
+    \vitem Single Query, Biggest Lead
+  \end{itemize}
 \end{column}
-    \begin{column}{.17\textwidth}
-      \includegraphics[width=\textwidth]{powered-by-aws}
+\hfill
+\begin{column}{0.4\textwidth}
+  \begin{center}
+    \includegraphics[width=.3\textwidth]{medalsilver}
+  \end{center}
 \end{column}
 \end{columns}
+
 \end{frame}
 
-\begin{frame}[shrink=0.95]{Benchmark contributors}
-  In 2022 \emph{new benchmarks} were contributed by:
+\begin{frame}{FLoC Medalists}
 
-  \small
+  \begin{columns}
+    \begin{column}{0.6\textwidth}
+
+  \Large YicesQS wins one silver medal:
   \begin{itemize}
-    \item  Alex Coffin
-    \item  Alex Ozdemir
-    \item  Ali Uncu, James Davenport and Matthew England
-    \item  Bohan Li
-    \item  Elizabeth Polgreen
-    \item  Fuqi Jia
-    \item  Johann-Tobias Aaron and Raphael Schäg
-    \item  Matthew England and Miguel Del Rio Almajano
-    \item  Nicolas Amat
-    \item  Yannick Moy
-    \item  Yoni Zohar
+    \bigskip
+    \vitem Single Query, Largest Contribution
   \end{itemize}
+\end{column}
+\hfill
+\begin{column}{0.4\textwidth}
+  \begin{center}
+    \includegraphics[width=.3\textwidth]{medalsilver}
+  \end{center}
+\end{column}
+\end{columns}
+
 \end{frame}
@@
   \begin{center}
-    \Large\emph{Thanks}
-  \end{center}
-
-  \begin{center}
-    to all participants
-  \end{center}
-
-  \bigskip
-  \pause
-
-  \begin{center}
-    and to you for listening
+    \Large For full results please come to the SMT workshop Thursday 4pm.
   \end{center}

### 2023-01-03 2022/slides/proofs/slides.tex
missing slides

--- 2022-08-11 2022/slides/smtWorkshop/slides.tex
@@
 \begin{frame}
-  \titlepage
-\end{frame}
+  \frametitle{SMT Proofs}
 
-\begin{frame}
-  \frametitle{SMT-COMP}
-
-  \begin{minipage}[b]{.6\textwidth}
-    Annual competition for \emph{SMT solvers}\\
-    on (a selection of) benchmarks from \emph{SMT-LIB}
-  \end{minipage}%
-  \begin{minipage}{.4\textwidth}
-    \begin{block}{History}
-      \begin{tabular}{rp{3cm}}
-        \textbf{2005} & first competition \\
-        \textbf{2013} & evaluation instead \\
-        & of competition\\
-        \textbf{2014} & since then hosted\\
-        & by \emph{StarExec}
-      \end{tabular}
-    \end{block}
-  \end{minipage}
-
-  Goals:
   \begin{itemize}
-  \item spur development of SMT solver implementations
-  \item promote SMT solvers and their usage
-  \item support the SMT-LIB project
+    \item In first meeting we discussed:
     \begin{itemize}
-    \item to promote and develop the SMT-LIB format
+      \item Detailed vs coarse proofs (for scalability)
       \begin{itemize}
-      \item model validation
-      \item proof checking
-    \end{itemize}
-    \item to collect relevant benchmarks
-    \end{itemize}
-  \item engage and include new members
+        \item Similarly, to dump proofs as solving goes rather than store and
+        emit in the end
       \end{itemize}
 
-\end{frame}
+      \item Logical framework or predefined proof calculus
 
-\begin{frame}
-  \frametitle{SMT Solvers and SMT-LIB}
-  SMT Solver
-  \begin{itemize}
-  \item checks formulas
-    in \emph{SMT-LIB} format
-    for \emph{satisfiability modulo theories}
-  \end{itemize}
-  \bigskip
-
-  SMT-LIB is
-  \begin{enumerate}
-  \item a \emph{language} in which benchmarks are written
-  \item a community effort to \emph{collect benchmarks}
-  \end{enumerate}
-  \medskip
-
-  \begin{columns}
-    \begin{column}{0.4\textwidth}
-      \begin{block}{Non-incremental}
-        391\,363 instances {\small (+9680)}\\
-        with 1 query each \\
-        in 81 logics {\small (+2)}.
-      \end{block}
-    \end{column}
-    \begin{column}{0.4\textwidth}
-      \begin{block}{Incremental}
-        43\,285 instances {\small (+1)}\\
-        with 33\,998\,935 queries {\small (+141)} \\
-        in 39 logics.
-      \end{block}
-    \end{column}
-    \begin{column}{0.08\textwidth}
-    \end{column}
-  \end{columns}
-  \pause
-    \begin{columns}
-    \begin{column}{0.4\textwidth}
-      \begin{block}{Selected Non-incremental}
-        \only<2>{206\,932 instances}\only<3>{\textcolor{red}{206\,932}
-          instances\\
-          \textcolor{red}{We mistakenly ignored 9466 new benchmarks}
-        }
-      \end{block}
-    \end{column}
-    \begin{column}{0.4\textwidth}
-      \begin{block}{Selected Incremental}
-        22\,300 instances
-      \end{block}
-    \end{column}
-    \begin{column}{0.08\textwidth}
-    \end{column}
-  \end{columns}
-
-\end{frame}
-
-\begin{frame}
-  \frametitle{Competition Overview}
-
-  \begin{tikzpicture}
-    \node at (0,6) {SMT-LIB};
-    \node at (3,6) {Tracks};
-    \node[anchor=west] at (5,6) {Divisions};
-    \node[anchor=west] at (9,6) {Logics};
-
-    \node[database,label=below:{\begin{tabular}{c}non-\\incremental\end{tabular}}] (nonincbench) at (0,2) {};
-    \node[database,label=below:{incremental}] (incbench) at (0,0) {};
-
-    \node[draw,text width=1.8cm,align=center](sq) at (3,5) {single que.};
-    \node[draw,text width=1.8cm,align=center](uc) at (3,4) {unsat core};
-    \node[draw,text width=1.8cm,align=center](mv) at (3,3) {model val.};
-    \node[draw,text width=1.8cm,align=center](par) at (3,2) {parallel};
-    \node[draw,text width=1.8cm,align=center](cloud) at (3,1) {cloud};
-    \node[draw,text width=1.8cm,align=center](inc) at (3,0) {incremental};
-
-    \node[anchor=west] (div1) at (5,5) {Arith};
-    \node[anchor=west] at (9,5) {\small LIA};
-    \node[anchor=west] at (9,4.6) {\small LRA};
-    \node[anchor=west] at (10,5) {\small NIA};
-    \node[anchor=west] at (10,4.6) {\small NRA};
-    \node[anchor=west] (div2) at (5,4) {Bitvec};
-    \node[anchor=west] at (9,4) {\small BV};
-    \node[anchor=west] (div3) at (5,3.4) {Equality};
-    \node[anchor=west] at (9,3.4) {\small UF};
-    \node[anchor=west] at (9,3) {\small UFDT};
-    \node[anchor=west] (div4) at (5,2.4) {Equality+LinearArith};
-    \node[anchor=west] at (9,2.4) {\small UFIDL};
-    \node[anchor=west] at (9,2) {\small UFLIA};
-    \node[anchor=west] at (9,1.6) {\small UFLRA};
-    \node[anchor=west] at (10.5,2.4) {\small ALIA};
-    \node[anchor=west] at (10.5,2) {\small AUFLIA};
-    \node[anchor=west] at (10.5,1.6) {\small AUFLIRA};
-    \node[anchor=west] at (12.5,2) {$\hdots$};
-    \node[anchor=west] (div5) at (5,1) {Equality+MachineArith};
-    \node[anchor=west] at (9,1) {\small ABV};
-    \node[anchor=west] at (9,.6) {\small ABVFP};
-    \node[anchor=west] at (9,.2) {\small AUFBV};
-    \node[anchor=west] at (10.5,1) {\small AUFBVFP};
-    \node[anchor=west] at (10.5,.6) {\small AUFBVDTLIA};
-    \node[anchor=west] at (10.5,.2) {\small AUFBVDTNIA};
-    \node[anchor=west] at (12.5,1) {$\hdots$};
-    \node[anchor=west] (div6)  at (5,-.2) {$\vdots$};
-
-    \draw[->,shorten <=.3em] (nonincbench) to[bend left=15] (sq.west);
-    \draw[->,shorten <=.3em] (nonincbench) to[bend left=7] (uc.west);
-    \draw[->,shorten <=.3em] (nonincbench) to[bend left=5] (mv.west);
-    \draw[->,shorten <=.3em] (nonincbench) to (par.west);
-    \draw[->,shorten <=.3em] (nonincbench) to[bend right=4] (cloud.west);
-    \draw[->,shorten <=.3em] (incbench) to (inc.west);
-
-    \draw (sq.east) to (div1.west);
-    \draw (sq.east) to (div2.west);
-    \draw (sq.east) to (div3.west);
-    \draw (sq.east) to (div4.west);
-    \draw (sq.east) to (div5.west);
-    \draw (sq.east) to (div6.west);
-
-    \draw (uc.east) to (div1.west);
-    \draw (uc.east) to (div2.west);
-    \draw (uc.east) to (div3.west);
-    \draw (uc.east) to (div4.west);
-    \draw (uc.east) to (div5.west);
-    \draw (uc.east) to (div6.west);
-
-    \draw (mv.east) to (div1.west);
-    \draw (mv.east) to (div2.west);
-    \draw (mv.east) to (div3.west);
-    \draw (mv.east) to (div4.west);
-    \draw (mv.east) to (div5.west);
-    \draw (mv.east) to (div6.west);
-
-    \draw (cloud.east) to (div1.west);
-    \draw (cloud.east) to (div2.west);
-    \draw (cloud.east) to (div3.west);
-    \draw (cloud.east) to (div4.west);
-    \draw (cloud.east) to (div5.west);
-    \draw (cloud.east) to (div6.west);
-
-    \draw (par.east) to (div1.west);
-    \draw (par.east) to (div2.west);
-    \draw (par.east) to (div3.west);
-    \draw (par.east) to (div4.west);
-    \draw (par.east) to (div5.west);
-    \draw (par.east) to (div6.west);
-
-    \draw (inc.east) to (div1.west);
-    \draw (inc.east) to (div2.west);
-    \draw (inc.east) to (div3.west);
-    \draw (inc.east) to (div4.west);
-    \draw (inc.east) to (div5.west);
-    \draw (inc.east) to (div6.west);
-  \end{tikzpicture}
-
-\end{frame}
-
-\begin{frame}[fragile]{SMT-COMP Tracks (traditional)}
-  \emph{Single Query Track}
-  \begin{itemize}
-  \item Determine satisfiability of one problem
-  \item Solver answers sat/unsat/unknown
-  \end{itemize}
-  \medskip
-
-  \emph{Unsat Core Track}
-  \begin{itemize}
-  \item Find small unsatisfiable subset of input.
-  \item Solver answers unsat + list of formulas.
-  \end{itemize}
-  \medskip
-
-  \emph{Model Validation Track}
-  \begin{itemize}
-  \item Find a model for a satisfiable problem.
-  \item Solver answers sat + value for each non-logical symbol.
-  \end{itemize}
-  \medskip
-
-  \emph{Incremental Track}
-  \begin{itemize}
-  \item Solve many small problems interactively.
-  \item Solver acks commands and answers sat/unsat for each check.
-  \end{itemize}
-\end{frame}
-
-\begin{frame}[fragile]{SMT-COMP Tracks (experimental)}
-
-  \emph{Model Validation}
-  \begin{itemize}
-    \item Division with quantifier-free floating-point logics
-    \item Model validation with Dolmen (thanks to Gillaume Bury and Fran\c{c}ois
-    Bobot)
-  \end{itemize}
-  \bigskip
-
-  \emph{Cloud and Parallel Track} (sponsored by AWS, led by Mike Whalen)
-  \begin{itemize}
-  \item Solve a large problem over the cloud (or a big computer)
-  \begin{itemize}
-    \item 100 machines, 1600 cores, 6400 GB of memory (cloud)
-    \item 64 cores, 256 GB of memory (parallel)
-  \end{itemize}
-  \item Solver answers sat/unsat/unknown
-  \end{itemize}
-
-  \pause\bigskip
-
-  \emph{Proof Exhibition Track}
-  \begin{itemize}
-  \item Solver submitted together with a checker for unsatisfiability proofs
-  \item No predefined format or checker
-  \item No ranking
-  \item Qualitative assessment
-  \end{itemize}
-
-\end{frame}
-
-\begin{frame}{Tracks, Solvers, Divisions, and Benchmarks}
-  Teams: 21 (+3)
-  \bigskip
-
-  \begin{tabular}{c|r@{}l|r@{}l|c}
-    Track & \multicolumn{2}{c|}{Solvers} & \multicolumn{2}{c|}{Divisions}  & Benchmarks \\
-    \hline
-    Single Query  &  22&(+3)  & 19&(+1)  & 93\,945 \\
-    Incremental &  8&(+1)   & 17&(+2)  & 22\,300   \\
-    Unsat Core  &  6&(-1)   & 18&(+1)  & 57\,245  \\
-    Model Validation  &  8&(+1)    &  7& (+ 1 exp.)  & 32\,766  \\
-    Proof Exhibition  &  &4    &  & 18 exp.  & 57\,245  \\
-    \hline
-    Parallel &   4&(+1)      &   &14 exp.  & 400 \\
-    Cloud & 4&(-1)      &  &14 exp.  & 400 \\
-
-  \end{tabular}
-  \bigskip
-
-  Number in parenthesis shows changes from 2021
-\end{frame}
-
-\begin{frame}
-  \frametitle{Participants}
-
-  SMT-COMP 2022 participants rely on multiple reasoning frameworks:
-  \begin{itemize}
-  \item CDCL(T)
-  \item mcSAT
-  \item saturation
-  \item automata
-  \item finite domain
-  \item CP
-  \item local search
-  \item besides wrappers extending the scope of existing solvers
-  \end{itemize}
-
-  \bigskip
-  Six new solvers participated:
-  \begin{itemize}
-  \item NRA-LS   {\footnotesize (Liu et al.)}
-  \item OSTRICH {\footnotesize (Chen et al.)}
-  \item Yices-ismt {\footnotesize (Jia et al.)}
-  \item Z3++ {\footnotesize (Cai et al.)}
-  \item solsmt {\footnotesize (Reitwiessner and Soos)}
-  \end{itemize}
-
-\end{frame}
-
-\section{Solver Presentation}
-
-{
-\begin{frame}
-  \vspace*{-1pt}%
-  \noindent\makebox[\textwidth]{%
-    \includegraphics[height=\paperheight]{slide-bitwuzla.pdf}}
-\end{frame}
-}
-
-{
-\begin{frame}
-  \vspace*{-1pt}%
-  \noindent\makebox[\textwidth]{%
-    \includegraphics[height=\paperheight]{slide-colibri.pdf}}
-\end{frame}
-}
-
-{
-\begin{frame}
-  \vspace*{-1pt}%
-  \noindent\makebox[\textwidth]{%
-    \includegraphics[height=\paperheight]{slide-cvc5.pdf}}
-\end{frame}
-}
-
-{
-\begin{frame}
-  \vspace*{-1pt}%
-  \noindent\makebox[\textwidth]{%
-    \includegraphics[height=\paperheight]{slide-cvc5-cloud.pdf}}
-\end{frame}
-}
-
-{
-\begin{frame}
-  \vspace*{-1pt}%
-  \noindent\makebox[\textwidth]{%
-    \includegraphics[height=\paperheight]{slide-nra-ls.pdf}}
-\end{frame}
-}
-
-{
-\begin{frame}
-  \vspace*{-1pt}%
-  \noindent\makebox[\textwidth]{%
-    \includegraphics[height=\paperheight]{slide-opensmt.pdf}}
-\end{frame}
-}
-
-{
-\begin{frame}
-  \vspace*{-1pt}%
-  \noindent\makebox[\textwidth]{%
-    \includegraphics[height=\paperheight]{slide-smtinterpol.pdf}}
-\end{frame}
-}
-
-{
-\begin{frame}
-  \vspace*{-1pt}%
-  \noindent\makebox[\textwidth]{%
-    \includegraphics[height=\paperheight]{slide-solsmt.pdf}}
-\end{frame}
-}
-
-{
-\begin{frame}
-  \vspace*{-1pt}%
-  \noindent\makebox[\textwidth]{%
-    \includegraphics[height=\paperheight]{slide-stp.pdf}}
-\end{frame}
-}
-
-{
-\begin{frame}
-  \vspace*{-1pt}%
-  \noindent\makebox[\textwidth]{%
-    \includegraphics[height=\paperheight]{slide-verit.pdf}}
-\end{frame}
-}
-
-{
-\begin{frame}
-  \vspace*{-1pt}%
-  \noindent\makebox[\textwidth]{%
-    \includegraphics[height=\paperheight]{slide-yices.pdf}}
-\end{frame}
-}
-
-{
-\begin{frame}
-  \vspace*{-1pt}%
-  \noindent\makebox[\textwidth]{%
-    \includegraphics[height=\paperheight]{slide-yices-ismt.pdf}}
-\end{frame}
-}
-
-{
-\begin{frame}
-  \vspace*{-1pt}%
-  \noindent\makebox[\textwidth]{%
-    \includegraphics[height=\paperheight]{slide-yices-qs.pdf}}
-\end{frame}
-}
-
-{
-\begin{frame}
-  \vspace*{-1pt}%
-  \noindent\makebox[\textwidth]{%
-    \includegraphics[height=\paperheight]{slide-z3pp.pdf}}
-\end{frame}
-}
-
-{
-  \begin{frame}
-    \frametitle{Other participants}
-    \begin{itemize}
-      \item Q3B
-      \vitem SMT-RAT
-      \vitem SMTS
-      \vitem UltimateEliminatior+MathSAT
-      \vitem Vampire
-      \vitem Z3str4
-    \end{itemize}
-  \end{frame}
-}
-
-\begin{frame}
-  \frametitle{Non-Competitive Solvers}
-
-  Submitted by organisers
-  \begin{itemize}
-  \item z3-4.8.17
-  \item MathSAT 5.6.8
-  \item Best solvers, per division, from previous years (23 Solvers)
-  \end{itemize}
-  \bigskip
-
-  Submitted by participants
-  \begin{itemize}
-  \item Fixed solvers (OpenSMT, STP, Yices-ismt, Z3++,smtinterpol)
-  \end{itemize}
-\end{frame}
-
-\begin{frame}{Scoring}
-  Computing scores:
-  \begin{itemize}
-  \item \emph{Single Query/Parallel/Cloud}: number of solved \emph{instances}
-  \item \emph{Incremental}: number of solved \emph{queries}
-  \item \emph{Unsat Core}: number of top-level assertions \emph{removed}
-  \item \emph{Model Validation}: number of solved instances with correct \emph{models}
-  \end{itemize}
-
-  \bigskip
-  Error scores:
-  \begin{itemize}
-  \item \emph{All Tracks}: given for sat reply for unsat instance, or vice versa
-  \item \emph{Unsat Core}: given if returned core is satisfiable.
-  \item \emph{Model Validation}: given if given model evaluates formula to \emph{false}
-  \end{itemize}
-  Error scores are draconian.
-\end{frame}
-
-\begin{frame}{Score and Ranking}
-  In each track we collect different scores:
-  \begin{itemize}
-  \item \emph{Sequential score} (SQ, UC, MV): all time limits apply to cpu time
-  \item \emph{Parallel score} (all): all time limits apply to wallclock time
-  \item \emph{SAT score} (SQ): parallel score for \emph{satisfiable} instances
-  \item \emph{UNSAT score} (SQ): parallel score for \emph{unsatisfiable} instances
-  \item \emph{24s} (SQ): parallel score with time limit of \emph{24s}
-  \end{itemize}
-  \bigskip
-
-  Division ranking (for each score)
-  \begin{itemize}
-  \item For each division, one winner is declared
-  \end{itemize}
-
-  \bigskip
-
-  Two competition-wide rankings (for each score)
-  \begin{itemize}
-  \item \emph{Biggest lead}: division winner with most score difference to second place
-  \item \emph{Largest contribution}: improvement each solver provided to a virtual best solver
-  \end{itemize}
-
-\end{frame}
-
-\begin{frame}{Division Winners}
-  \pause
-  \emph{Single Query, sequential score}
-  \begin{itemize}
-  \item \emph{Bitwuzla}: {\small FPArith, QF\_Bitvec, QF\_Equality+Bitvec, QF\_FPArith}
-
-  \item \emph{cvc5}: \begin{minipage}{.8\textwidth}\raggedright \tiny Arith,
-    Bitvec, Equality, Equality+LinearArith, Equality+MachineArith,
-    Equality+NonLinearArith, QF\_Datatypes, QF\_Equality+NonLinearArith, QF\_NonLinearIntArith, QF\_NonLinearRealArith, QF\_Strings\end{minipage}
-
-  \item \emph{OpenSMT}: {\small QF\_LinearIntArith}
-
-  \item \emph{SMTInterpol}: {\small QF\_Equality+LinearArith}
-
-  \item \emph{Yices2}: {\small QF\_Equality, QF\_LinearRealArith}
-  \end{itemize}
-
-  \medskip
-
-  \pause
-  \emph{Unsat Core}
-  \begin{itemize}
-  \item \emph{Bitwuzla}: {\small QF\_Bitvec, QF\_Equality+Bitvec, QF\_FPArith}
-  \item \emph{cvc5}: \begin{minipage}{.8\textwidth}\raggedright \tiny Arith, Bitvec, Equality, Equality+LinearArith, Equality+MachineArith, Equality+NonLinearArith, FPArith, QF\_Equality, QF\_Equality+NonLinearArith, QF\_LinearIntrArith, QF\_NonLinearIntArith, QF\_NonLinearRealArith \end{minipage}
-  \item \emph{Yices2}: {\small QF\_Equality+LinearArith, QF\_LinearRealArith}
-  \end{itemize}
-
-\end{frame}
-
-\begin{frame}{Division Winners}
-  \emph{Incremental}
-  \begin{itemize}
-\item \emph{cvc5}: Arith, Bitvec, Equality+LinearArith,EqualityNonLinearArith,Equality
-\item \emph{UltimateEliminator+MathSAT}: Equality+MachineArith
-\item \emph{Bitwuzla}: FPArith, QF\_Bitvec, QF\_FPArith
-\item \emph{Yices2}: QF\_Equality+Bitvec, QF\_Equality, QF\_LinearIntArith
-\item \emph{SMTInterpol}: QF\_Equality+LinearArith, QF\_Equality+NonLinearArith, QF\_NonLinearIntArith
-\item \emph{OpenSMT}: QF\_LinearRealArith
-  \end{itemize}
-  \medskip
-
-  \pause
-  \emph{Model Validation (competitive only)}
-  \begin{itemize}
-\item \emph{Bitwuzla}: QF\_Bitvec, QF\_Equality+Bitvec,
-\item \emph{smtinterpol}: QF\_Equality+LinearArith
-\item \emph{Yices2}: QF\_Equality
-\item \emph{Z3++}: QF\_LinearIntArith
-\item \emph{OpenSMT}: QF\_LinearRealArith
-
-\item experimental: QF\_FPArith : Bitwuzla, cvc5
+      \item Proof structure and BNF for a proof format
 
     \end{itemize}
-\end{frame}
-
-\begin{frame}{Largest contribution}
-  \begin{tabular}{r|c@{}lc@{}lc@{}l}
-    &\textcolor{gold}{\textbf{1st Place}} &&
-    \textcolor{silver}{\textbf{2nd Place}} &&
-    \textcolor{bronze}{\textbf{3rd Place}}\\
-    \hline
-    \emph{Single Query}\\
-    seq & cvc5&{\tiny(Eq+MA)} & YicesQS&{\tiny(Arith)} & Bitwuzla&{\tiny(FPArith)} \\
-    par & cvc5&{\tiny(Eq+MA)} & YicesQS&{\tiny(Arith)} & Bitwuzla&{\tiny(FPArith)} \\
-    sat & cvc5&{\tiny(Eq+LA)} & YicesQS&{\tiny(Arith)} & Bitwuzla&{\tiny(FPArith)} \\
-    unsat & cvc5&{\tiny(Eq+MA)} & Z3++&{\tiny(QF\_NonLIA)} & OSTRICH&{\tiny(QF\_Strings)}\\
-    24 &  Vampire&{\tiny(Eq+NA)} & Vampire&{\tiny(Equality)} & Yices2&{\tiny(QF\_LinIA)}\\[3pt]
-    \pause
-    \emph{Incremental}\\
-    par & cvc5&{\tiny(Eq+NA)} &Yices2&{\tiny(QF\_Eq+LA)}
-    &SMTInterpol&{\tiny(QF\_Eq+NA)}\\[3pt]
-    \pause
-
-    \emph{Unsat Core}\\
-    seq & cvc5&{\tiny(Eq+LA)} &
-    Bitwuzla&{\tiny(QF\_Eq+Bitvec)}\\
-
-    par &  cvc5&{\tiny(Eq+NA)}&
-    Bitwuzla&{\tiny(QF\_Eq+Bitvec)}\\
-\\[3pt]
-    \pause
-    \emph{Model Validation}\\
-    seq &  Z3++&{\tiny(QF\_LinIA)} & Bitwuzla&{\tiny(QF\_Bitvec)}
-        & smtinterpol&{\tiny(QF\_Eq+LIA)}\\
-    par &  Z3++&{\tiny(QF\_LinIA)} & Bitwuzla&{\tiny(QF\_Bitvec)}
-        & smtinterpol&{\tiny(QF\_Eq+LIA)}\\
-  \end{tabular}
-\end{frame}
-
-\begin{frame}{Biggest Lead}
-  \begin{tabular}{r|c@{}lc@{}lc@{}l}
-    &\textcolor{gold}{\textbf{1st Place}} &&
-    \textcolor{silver}{\textbf{2nd Place}} &&
-    \textcolor{bronze}{\textbf{3rd Place}}\\
-    \hline
-    \emph{Single Query}\\
-    seq & cvc5&{\tiny(QF\_DT)} & Bitwuzla&{\tiny(FPArith)} & Yices2&{\tiny(QF\_LinRA)} \\
-    par & cvc5&{\tiny(QF\_DT)} & Bitwuzla&{\tiny(FPArith)} & Yices2&{\tiny(QF\_LinRA)} \\
-    sat & cvc5&{\tiny(QF\_DT)} & Bitwuzla&{\tiny(FPArith)} & Z3++&{\tiny(QF\_NonRA)} \\
-    unsat & cvc5&{\tiny(QF\_DT)} & Z3++&{\tiny(QF\_NonIA)} & Bitwuzla&{\tiny(FPArith)} \\
-    24 &  cvc5&{\tiny(Eq+MA)} & smtinterpol&{\tiny(QF\_DT)} & Vampire&{\tiny(Equality)}\\[3pt]
-    \pause
-    \emph{Incremental}\\
-    par & SMTInterpol&{\tiny(QF\_NIA)}
-    &Yices2&{\tiny(QF\_LinIA)} & cvc5&{\tiny(Eq+NonLA)} \\[3pt]
-    \pause
-    \emph{Unsat Core}\\
-    seq & cvc5&{\tiny(Eq+MA)} &    Yices2&{\tiny(QF\_Eq+LA)} &    smtinterpol&{\tiny(QF\_Eq+NA)} \\
-    par & cvc5&{\tiny(Eq+MA)} &    Yices2&{\tiny(QF\_Eq+LA)} &    smtinterpol&{\tiny(QF\_Eq+NA)} \\
-    \pause
-    \emph{Model Validation}\\
-    seq &  Z3++&{\tiny(QF\_LinIA)} & smtinterpol&{\tiny(QF\_LinA)}        & OpenSMT&{\tiny(QF\_LinRA)} \\
-    par &  Z3++&{\tiny(QF\_LinIA)} & smtinterpol&{\tiny(QF\_LinA)}        & OpenSMT&{\tiny(QF\_LinRA)} \\
-  \end{tabular}
-\end{frame}
-
-\begin{frame}{Checking Disagreements}
-
+    \item In the second meeting we mostly discussed the last point
     \begin{itemize}
-  \item  instances of 391\,363 have no status
-
-  \vitem Only 18 benchmarks with disagreements (AUFDTLIA, QF\_NIA)
-
-  \vitem We manually resolved the disagreements
+      \item Tentative consensus towards using SMT-LIB 3.0
+      \item Same language for proofs and (regular) terms? Could help to separate syntactically.
+      \item Expectation of proof as sequence of steps towards proving something
       \begin{itemize}
-    \item Authors confirmed solver unsoundness
-    \item Sound solvers agreed on result
+        \item $(c_1 \dots c_n\ p)$ as the response to get proof, with $c_i$ as
+        preamble, $p$ the proof
+        \item A proof could be $(\mathrm{someRule} :\mathrm{conclusion}\ t :\mathrm{premises}\ (\mathrm{list}\
+        p_1 \dots p_n\ p) :\mathrm{args}\ (\mathrm{list}\ t_1\dots t_n))$
+        \item Proof can be flattened (so not just a big proof term) by naming
+        proofs in the preamble
       \end{itemize}
-
-  \vitem We had only three solvers with soundness issues: SMTIinterpol, Z3++,
-  yices-ismt
-  \begin{itemize}
-    \item Down from 10 last year
     \end{itemize}
@@
 
-\begin{frame}{Plans for SMT-COMP 2022}
-  \begin{itemize}
-    \item Move to Dolmen as single model validator
+\begin{frame}[fragile,t,fragile]
+  \frametitle{SMT Proofs}
 
-      \vitem Dolmen worked well in QF\_FP (minor issue with empty output, simple
-      to fix)
-      \vitem pysmt timed out in two cases (locally with more time one of them
-      succeeded)
-      \vitem pysmt could not understand the model in 9 cases
-      \vitem Dolmen is easy to extend to new theories
-      \vitem Easy to integrate with correct-by-construction code extracted from
-      Coq
-      \vitem Should be more efficient for handling function call
+  Two suggestions by Andrew Reynolds for defining a rule via SMT-LIB 3.0. One
+  with simple types:
 
-  \end{itemize}
+\begin{verbatim}
+(declare-type Proof ())
+...
+(declare-const proof.res (-> Proof Proof Bool Proof))
+\end{verbatim}
 
-\end{frame}
+Another with more structured types:
 
-\begin{frame}{Plans for SMT-COMP 2022}
-  \begin{itemize}
-    \item Proof \textit{validation} track
+\begin{verbatim}
+(declare-type Proof (Bool))
+...
+(declare-const proof.eq_symm
+  (-> (! Type :var T :implicit)
+      (! T :var x :implicit)
+      (! T :var y :implicit)
+      (Proof (= x y))
+      (Proof (= y x))))
+\end{verbatim}
 
-      \vitem Hopefully proof exhibition this year will help
+    \medskip
 
-      \vitem We have to analyze the data still
-      \begin{itemize}
-        \item Job only finished last week (took 18 days to run)
-        \item 830gb
-      \end{itemize}
-
-  \end{itemize}
-
-\end{frame}
-
-\begin{frame}{SMT-COMP organizing committee}
-  Three people organize the SMT-COMP.  In 2021:
-  \begin{itemize}
-  \item Haniel Barbosa
-  \item Jochen Hoenicke
-  \item Fran\c{c}ois Bobot
-  \end{itemize}
-
-  Both Haniel and Jochen have been organizers for three-years. One of them
-  should be replaced.
-  \bigskip
-
-  We need a successor for next year's competition.
-  Contact us if you would like to volunteer!
-\end{frame}
-
-\begin{frame}{Acknowledgements}
-  \begin{itemize}
-    \item \emph{Andrea Micheli}: pysmt
-    \item \emph{Guillaume Bury}: Model Validator
-    \item \emph{Clark Barrett, Pascal Fontaine, Aina Niemetz, Mathias Preiner, Hans-Jörg Schurr}: SMT-LIB benchmarks
-    \item \emph{Aaron Stump}: StarExec support
-    \item \emph{Mike Whalen and team}: Cloud/Parallel Track
-  \end{itemize}
-  \bigskip
-
-  \begin{columns}
-    \begin{column}{.3\textwidth}
-      \includegraphics[width=\textwidth]{starlogo}
-    \end{column}
-    \begin{column}{.17\textwidth}
-      \includegraphics[width=\textwidth]{powered-by-aws}
-    \end{column}
-  \end{columns}
-\end{frame}
-
-\begin{frame}[shrink=0.95]{Benchmark contributors}
-  In 2022 \emph{new benchmarks} were contributed by:
-
-  \small
-  \begin{itemize}
-    \item  Alex Coffin
-    \item  Alex Ozdemir
-    \item  Ali Uncu, James Davenport and Matthew England
-    \item  Bohan Li
-    \item  Elizabeth Polgreen
-    \item  Fuqi Jia
-    \item  Johann-Tobias Aaron and Raphael Schäg
-    \item  Matthew England and Miguel Del Rio Almajano
-    \item  Nicolas Amat
-    \item  Yannick Moy
-    \item  Yoni Zohar
-  \end{itemize}
-\end{frame}
-
-\begin{frame}
-
-  \begin{center}
-    \Large\emph{Thanks}
-  \end{center}
-
-  \begin{center}
-    to all participants
-  \end{center}
-
-  \bigskip
-  \pause
-
-  \begin{center}
-    and to you for listening
-  \end{center}
+    so that for example the proof \verb|(proof.eq_symm P)| proves \verb|(= y x)| when \verb|P| proves \verb|(= x y)|.
 

### 2023-01-23 rules/rules23.tex
Started new rules file.

--- 2022-06-23 rules/rules22.tex
@@
 
-\title{17th International Satisfiability Modulo Theories Competition
-  (SMT-COMP 2022): Rules and Procedures}
+\title{18th International Satisfiability Modulo Theories Competition
+  (SMT-COMP 2023): Rules and Procedures}
 
@@
 \author{%
-Haniel Barbosa (chair)\\
-Universidade Federal de Minas Gerais\\
-Brazil\\
-{\small\href{mailto:hbarbosa@dcc.ufmg.br}{\texttt{hbarbosa@dcc.ufmg.br}}}\\
-\and
 Fran\c{c}ois Bobot\\
@@
 \and
+Martin Bromberger\\
+TODO\\
+Germany\\
+{\small\href{mailto:TODO}{\texttt{TODO}}}\\
+\and
 Jochen Hoenicke\\
-Universit\"at Freiburg\\
+Certora\\
 Germany\\
-{\small\href{mailto:hoenicke@informatik.uni-freiburg.de}{\texttt{hoenicke@informatik.uni-freiburg.de}}}
+{\small\href{mailto:jochen@certora.com}{\texttt{jochen@certora.com}}}
 }
@@
 \begin{description}
-\item[Mar~15] Deadline for new benchmark contributions.
-\item[May~28] Final versions of competition tools (e.g., benchmark
+\item[Mar~??] Deadline for new benchmark contributions.
+\item[May~??] Final versions of competition tools (e.g., benchmark
   scrambler) are made available.  Benchmark libraries are frozen.
-\item[June~18] Deadline for first versions of solvers (for all tracks),
+\item[June~??] Deadline for first versions of solvers (for all tracks),
   including information about which tracks and divisions are being
   entered, and magic numbers for benchmark scrambling.
-\item[July~2] Deadline for final versions of solvers, including
+\item[July~?] Deadline for final versions of solvers, including
   system descriptions.
-\item[July~5] Opening value of NYSE Composite Index used to compute
+\item[July~?] Opening value of NYSE Composite Index used to compute
   random seed for competition tools.
-\item[August 11/12] SMT Workshop; end of competition, presentation of
+\item[August~??] SMT Workshop; end of competition, presentation of
   results.
@@
 \header{New benchmarks.}
-The deadline for submission of new benchmarks was {\bf March~15, 2021}.
+The deadline for submission of new benchmarks was {\bf March~15, 2022}.
 %
@@
       solvers (including non-competitive solvers) in less than one second in
-          the corresponding track in 2018, 2019, and 2020.
+          the corresponding track in 2018--2022.
     \item \emph{\ucoretrack.} All benchmarks with only a single assertion.
@@
 \setlength{\itemsep}{0pt}
-\item \href{http://homepages.dcc.ufmg.br/~hbarbosa/}{Haniel Barbosa}~--
-Universidade Federal de Minas Gerais, Brazil (chair)
-\item \href{https://github.com/bobot}{Fran\c{c}ois Bobot}~-- CEA List, France
-\item \href{https://jochen-hoenicke.de/}{Jochen Hoenicke}~-- Universit\"at Freiburg, Germany
+\item \href{https://github.com/bobot}{Fran\c{c}ois Bobot}~-- CEA List, France (chair)
+\item \href{TODO}{Martin Bromberger}~-- TODO
+\item \href{https://jochen-hoenicke.de/}{Jochen Hoenicke}~-- Certora, Germany
 \end{itemize}
@@
 \header{Disclosure.}
-%
-Haniel Barbosa is part of the developing teams of the SMT solvers
-cvc5~\cite{cvc5} and veriT~\cite{verit}.
-%
 Fran\c{c}ois is part of the developing team of the SMT solver COLIBRI~\cite{colibri}.
 %
-Jochen Hoenicke is part of the developing team of the SMT solver
+Martin TODO
+%
+Jochen is part of the developing team of the SMT solver
 SMTInterpol~\cite{smtinterpol}.

### 2023-03-16 rules/rules23.tex
Updated affiliations in the new rule file.
SMT-COMP23 rules: what's new and proof track

@@
 Martin Bromberger\\
-TODO\\
+Max Planck Institute for Informatics\\
+Saarland Informatics Campus\\
 Germany\\
-{\small\href{mailto:TODO}{\texttt{TODO}}}\\
+{\small\href{mailto:mbromber@mpi-inf.mpg.de}{\texttt{mbromber@mpi-inf.mpg.de}}}\\
 \and
@@
 \begin{itemize}
-  \item {\bf Changes in divisions.} Last year we changed
-  divisions to be composed of one or more related logics.
-  %
-  This year we will keep this organization but we will separate logics into
-  divisions slightly differently: we will have a QF\_Datatypes division with the
-  logics QF\_DT, QF\_UFDT and the QF\_Equality division now only contains the
-  QF\_UF and QF\_AX logics.
-
-  \rationale{The feedback from the participants in last year's competition was
-    that datatypes were too dissimilar from QF\_UF and QF\_AX to be organized in
-    the same division.}
-
-  \item {\bf Logics can be non-competitive in competitive divisions.} Last year
-  we considered every logic within a division to competitive unless the division
-  as whole was non-competitive. This year if a logic is non-competitive within a
-  division (i.e., only one competitive solver enrolled in it), it will not be
-  ran.
-
-  \rationale{We believe the previous setup could benefit too much a solver that
-    supports more logics that its competitor.
-    %
-    In particular there was a whose winner was defined by the benchmarks of a
-    non-competitive logic, which we believe is not ideal.
-    %
-    Note that the incentive for solvers to support more logics continues since
-    as soon as there is more than one solver supporting a logic it will be
-    competitive and the solver that does not support it will be disadvantaged.
-  }
-
-  \item {\bf \mvaltrack.}  \emergencystretch.5cm Last year's competition introduced the experimental
-  divisions QF\_Equality (only with QF\_UF benchmarks), QF\_Equality+LinearArith (only with
-  QF\_UFIDL, QF\_UFLIA, and QF\_UFLRA benchmarks), and QF\_Equality+Bitvec (only with
-  QF\_UFBV benchmarks).
+  \item {\bf System description must be submitted with preliminary
+      solver.} \todo{what}
+%
+  \rationale{\todo{reason}}
+
+  \item {\bf \mvaltrack.}  \emergencystretch.5cm Last year's
+    competition introduced the experimental divisions QF\_FPArith
+    (excluding the logics QF\_ABVFP, QF\_AUFBVFP, and QF\_ABVFPLRA).
   %
@@
   %
-  In addition, we add this year the new experimental division QF\_FPArith
-  (excluding the logics QF\_ABVFP, QF\_AUFBVFP, and QF\_ABVFPLRA).
-
+  In addition, we add this year the new experimental division for
+  non-linear arithmetic and for datatypes.  These include the divisions
+  QF\_NonLinearIntArith, QF\_NonLinearRealArith,
+  QF\_Equality+NonLinearArithm,
+  and QF\_Datatypes
+  (excluding all logics involving Arrays).  \todo{root-obj,
+    partially defined functions}
+%
   \rationale{Last year's divisions ran successfully, so there
@@
     model producing solvers, we proceed in an experimental fashion to push for
-    model standardization. We exclude logics containing arrays since their model
-    production adds further complications which we only intend to tackle in the
-    future.}
-
-  \item {\bf \prooftrack.}  This track will be introduced this year.
-  %
-  Teams can submit proof-producing solvers together with proof checkers for
-  their proof formats. The checker and format do not need to be from the same
-  team as the solver.
-  %
-  We will compile and present the results, as well as assemble a panel of
-  non-organizer experts to do a qualitative assessment for each proof-producing
-  solver, proof format, and proof checker.
-  %
-  The solver, proof format and checker should be described in a system
-  description (total of 4 pages rather than 2).
-
-  \rationale{Given the many competing visions on how SMT proofs or a proof
-    competition should look like, we decided to be less prescriptive and more
-    descriptive for how SMT-COMP will approach proofs.
-    %
-    We will host a ``proof exhibition'' rather than a ``proof competition''
-    track. The format would be with teams submitting both a proof-producing SMT
-    solver and a proof checker for its proofs.
+    model standardization. We exclude logics containing arrays since
+    there is no standardized way of expressing array model values and
+    we do not want to add too many new logics.}
+
+\item {\bf \prooftrack.}
+  Last year we added this as experimental track. We will continue with
+  this track in more or less the same format.  We will reduce the
+  number of benchmarks, though.
+%  
+  \rationale{We received several submissions that showed that there is
+    interest in a proof track.
+
+    We are still far away from a common proof format, so changing the
+    track to a competition track or making it non-experimental is not
+    feasible at this time.
+
+    The number of benchmarks and the size of the produced proofs
+    turned out to be a major stress to the StarExec infrastructure,
+    while not giving only little insight.  Therefore, we will reduce
+    the number of benchmarks in this track.
   }
@@
 the number of holes, the number of different proof rules, etc.
+Each proof checker can define its own key/value pairs, but we suggest
+to implement the following:
+\begin{itemize}
+\item \texttt{holes} -- number of unchecked axioms or rewrite rules (that
+  can introduce unsoundness),
+\item \texttt{axioms} -- number of checked axioms or rewrite rules,
+\item \texttt{steps} -- number of proof steps (in some proof-specific
+  granularity),
+\item \texttt{assertions} -- number of asserted formulas used in the proof.
+\end{itemize}
 
@@
 
+\header{Evaluation Criteria.}
+%
+Since different proof formats are not easily comparable we will not do
+any scoring by counting solved benchmarks.  Instead we will evaluate
+both solvers and proof checkers using different criteria:
+\begin{itemize}
+\item \emph{soundness}: does the proof checker only accept correct
+  proofs?  In particular, does it check that the proof proves the formula
+  in the benchmark, and does it warn about unchecked rewrite rules?
+\item \emph{trust-base}: how big is the trusted code and how much is
+  shared between proof checker and solver?
+\item \emph{proof overhead}: what is the performance of the solver and
+  the proof checker compared to running the solver without proof
+  production?
+\item \emph{granularity}: what is the granularity of the proof?
+\item \emph{readability}: is the proof easy to digest for a human?
+\item \emph{extractability}: is the proof suitable for automatic
+  processing?  Are there some implicit rewrites that one has to be
+  aware of?
+\item \emph{stability}: Is the proof checker specific to the current
+  version of the solver and needs to be updated with each solver
+  release, or is the proof checker fixed (except when adding new
+  theories)?
+\end{itemize}
+
 \header{Time Limit.}
@@
 Solvers in this track will be wrapped in the competition to include the script
-{\url{https://github.com/SMT-COMP/postprocessors/tree/master/proof-track/starexec_run_proof}}, which calls the solver and checker script.
+{\url{https://github.com/SMT-COMP/postprocessors/tree/master/proof-track/starexec_run_proof}},
+which calls the solver and checker script.
+Participants are encouraged to wrap their solvers themselves to test
+their submission.
 The track will use
@@
   Let $n$ be the number of benchmarks in an SMT-LIB logic, then
+  the number of chosen benchmarks is $min(n, max(300, 50n/100))$:
   \begin{enumerate}
@@
     \end{enumerate}
+    For the \prooftrack, we will only run $min(n, max(150,
+    25n/100)))$ benchmarks.
 \end{enumerate}

### 2023-03-21 rules/rules23.tex
SMT-COMP23 rules: refining formulations for system description requirements.

@@
 
+  \item {\bf System descriptions.}  \emergencystretch.5cm Some formulations 
+  in the requirements for the system descriptions have been updated from 
+  \emph{should} to \textbf{must} to make it clearer that these requirements 
+  are mandatory and not just recommended/optional.
+%
+  \rationale{We did this to ensure that derived tools are more easily recognizable and 
+  that it is always clear in which way wrapper tools and derived tools improve 
+  on the original solvers. 
+  Our changes follow the key words for use in RFCs to indicate requirement levels 
+  as proposed by \url{https://www.ietf.org/rfc/rfc2119.txt}.}
+
   \item {\bf \mvaltrack.}  \emergencystretch.5cm Last year's
@@
 explicitly acknowledge and state the \textbf{exact} version of any solvers that
-it wraps.  It \emph{should} further make clear technical innovations by which
+it wraps.  It \textbf{must} further make clear technical innovations by which
 the wrapper tool expects to improve on the wrapped solvers.
@@
 \textbf{must} explicitly acknowledge
-the solver it is based on and extends.  It \emph{should} further make clear
+the solver it is based on and extends.  It \textbf{must} further make clear
 technical innovations by which the derived tool expects to improve on the
-original solver.  A derived tool should follow the \emph{naming convention}
+original solver.  A derived tool \textbf{must} follow the \emph{naming convention}
 {[name of base solver]-[my solver name]}.
@@
 the exact version of each wrapped solver.
+A system description \textbf{must} further include the following information:
+\begin{itemize}[itemsep=0ex]
+  \item a list of all (current) authors of the system and their present institutional
+    affiliations,
+  \item the basic SMT solving approach employed,
+  \item in case of a \emph{wrapper} or \emph{derived tool}: details of
+    technical innovations by which a wrapper or derived tool expects to improve
+    on the wrapped solvers or base solver,
+  \item appropriate acknowledgment of tools other than SMT solvers called by
+    the system (e.g., SAT solvers) that are not written by the authors of the
+    submitted solver, and
+  \item for participants of the \prooftrack{} a short description
+    of their proof format of up to two extra pages.
+\end{itemize}
 A system description \emph{should} further include the following information
@@
 \begin{itemize}[itemsep=0ex]
-  \item a list of all authors of the system and their present institutional
-    affiliations,
-  \item the basic SMT solving approach employed,
   \item details of any non-standard algorithmic techniques as well as
-    references to relevant literature (by the authors or others),
-  \item in case of a \emph{wrapper} or \emph{derived tool}: details of
-    technical innovations by which a wrapper or derived tool expects to improve
-    on the wrapped solvers or base solver
-  \item appropriate acknowledgment of tools other than SMT solvers called by
-    the system (e.g., SAT solvers) that are not written by the authors of the
-    submitted solver, and
+    references to relevant literature (by the authors or others), and
   \item a link to a website for the submitted tool.
-  \item for participants of the \prooftrack{} a short description
-    of their proof format of up to two extra pages.
 \end{itemize}

### 2023-04-12 rules/rules23.tex
SMT-COMP23 rules: updated dates and new submission time for system descriptions.

@@
 \begin{description}
-\item[Mar~??] Deadline for new benchmark contributions.
-\item[May~??] Final versions of competition tools (e.g., benchmark
+\item[Mar~31] Deadline for new benchmark contributions.
+\item[April~29] Final versions of competition tools (e.g., benchmark
   scrambler) are made available.  Benchmark libraries are frozen.
-\item[June~??] Deadline for first versions of solvers (for all tracks),
+\item[May~13] Deadline for first versions of solvers (for all tracks),
   including information about which tracks and divisions are being
   entered, and magic numbers for benchmark scrambling.
-\item[July~?] Deadline for final versions of solvers, including
+\item[May~27] Deadline for final versions of solvers, including
   system descriptions.
-\item[July~?] Opening value of NYSE Composite Index used to compute
+\item[May~30] Opening value of NYSE Composite Index used to compute
   random seed for competition tools.
-\item[August~??] SMT Workshop; end of competition, presentation of
+\item[July~5-6] SMT Workshop; end of competition, presentation of
   results.
@@
 
-SMT-COMP~2022 is part of the SMT Workshop~2022
-(\url{http://smt-workshop.cs.uiowa.edu/2022/}),
-which is affiliated with IJCAR~2022 (\url{https://easychair.org/smart-program/IJCAR2022/}).
+SMT-COMP~2023 is part of the SMT Workshop~2023
+(\url{http://smt-workshop.cs.uiowa.edu/2023/}),
+which is affiliated with CADE~29 (\url{https://easyconferences.eu/cade2023/}).
 The SMT Workshop will include a block of time to present the results of the
@@
 
-SMT-COMP 2022 will have seven tracks: the \maintrack (before 2019: Main Track),
+SMT-COMP 2023 will have seven tracks: the \maintrack (before 2019: Main Track),
 the \inctrack (before 2019: Application Track), the \ucoretrack, the \mvaltrack,
@@
   and Tjark Weber.}  describes the rules and competition procedures for
-SMT-COMP~2022.
+SMT-COMP~2023.
 %
@@
 As in previous years, we have revised the rules slightly.  Some rule
-changes in 2022 are designed to improve how logics are organized into
+changes in 2023 are designed to improve how logics are organized into
 divisions. We have also added more divisions to the \mvaltrack and have defined a
@@
 \begin{itemize}
-  \item {\bf System description must be submitted with preliminary
-      solver.} \todo{what}
-%
-  \rationale{\todo{reason}}
+  \item {\bf System descriptions.}  \emergencystretch.5cm The system description 
+  for a participating solver must be submitted by the deadline for the preliminary 
+  solver versions. In the case a system description contains not all necessary information,
+  participants will be asked to submit an updated version of their 
+  system description as part of the submission of the final version of their solver.
+%
+  \rationale{We need this time to check whether the system descriptions contain all
+  necessary information and to give participants the chance to fix their system 
+  descriptions if necessary.}
 
@@
 \emph{and the tracks and divisions which it enters} via the web form
-at
+at \todo{Needs to be updated!}
 \begin{center}
@@
 \end{itemize}
-System descriptions \textbf{must} be submitted \textbf{until the final solver
-deadline}, and will be made publicly available on the competition website.
+System descriptions \textbf{must} be submitted \textbf{by the preliminary solver
+submission deadline}, and will be made publicly available on the competition website.
 Organizers will check that they contain sufficient information
 and may withdraw a system if its description is not sufficiently updated upon
-request
+request. The updates must happen \textbf{by the final solver submission deadline}.
 
@@
 the above web form (accompanying information) until the end of
-{\bf June~18, 2022} anywhere on earth.
+{\bf May~13, 2023} anywhere on earth.
 After this date \emph{no new entrants} will be accepted.
@@
 and \cloudtrack{}
-will be accepted until the end of {\bf July~2, 2022} anywhere on earth.
+will be accepted until the end of {\bf May~27, 2023} anywhere on earth.
 
@@
 The bulk of the computation will take place during the weeks leading
-up to SMT 2022.  Intermediate results will be regularly posted to the
+up to SMT 2023.  Intermediate results will be regularly posted to the
 SMT-COMP website as the competition runs.
@@
 The limits for \paralleltrack{} and \cloudtrack{} are available at
-\url{https://smt-comp.github.io/2022/parallel-and-cloud-tracks.html}.
+\url{https://smt-comp.github.io/2023/parallel-and-cloud-tracks.html}.
 
@@
 \header{New benchmarks.}
-The deadline for submission of new benchmarks was {\bf March~15, 2022}.
+The deadline for submission of new benchmarks was {\bf March~31, 2023}.
 %
 The organizers, in collaboration with the SMT-LIB maintainers, will be
-checking and curating these until {\bf June~18, 2022}.
+checking and curating these until {\bf May~13, 2023}.
 
@@
 
-SMT-COMP 2022 is organized under the direction of the SMT Steering
+SMT-COMP 2023 is organized under the direction of the SMT Steering
 Committee. The organizing team is
@@
 \item \href{https://github.com/bobot}{Fran\c{c}ois Bobot}~-- CEA List, France (chair)
-\item \href{TODO}{Martin Bromberger}~-- TODO
+\item \href{https://www.mpi-inf.mpg.de/departments/automation-of-logic/people/martin-bromberger}{Martin Bromberger}~-- MPI-INF, Germany
 \item \href{https://jochen-hoenicke.de/}{Jochen Hoenicke}~-- Certora, Germany
@@
 %
-Martin TODO
+Martin is part of the developing team of the SMT solver
+SPASS-SATT~\cite{spass-satt}.
 %

### 2023-04-13 rules/rules23.tex
proof track script

@@
 
+\item {\bf Wrapper Script for \prooftrack.}
+   The wrapper script is changed to remove very large proofs and
+   to cut very large error/debug output.
+%
+   \rationale{Last Year, the \prooftrack produced 800~GB of output, most
+   of that stemming from a few benchmark/solver pairs. These cannot be
+   removed without losing the whole proof track job.   It also makes
+   downloading and sharing the result much harder.}
 \end{itemize}
@@
 %
-The answer \texttt{invalid} should be returned if the proof is errorneous or
+The answer \texttt{invalid} should be returned if the proof is erroneous or
 otherwise malformed.

### 2023-04-26 rules/rules23.tex
SMT-COMP23 rules: changes to the wall-clock and CPU time scores.

@@
    downloading and sharing the result much harder.}
+
+\item {\bf Scoring.}  \emergencystretch.5cm We adjusted the wall-clock and 
+CPU time scores so only the benchmarks that are correctly solved within the 
+time limit $T$ are counted.
+%
+  \rationale{We noticed that in the previous scoring unintended results 
+  did occur because timeouts were scored worse than aborts and could 
+  overshadow the times of correctly solved problems. For instance, 
+  solver A that never aborts could lose to solver B that frequently aborts 
+  although A solved exactly the same problems B could solve and A was always 
+  faster on the solved problems than B.}
 \end{itemize}
@@
   \vspace{-1ex}
-  \item \makebox[5em][l]{$e \in \{0, 1\}$}
+  \item \makebox[6em][l]{$e \in \{0, 1\}$}
     number of erroneous results (usually~$e = 0$)
-  \item \makebox[5em][l]{$0 \leq n \leq N$}
+  \item \makebox[6em][l]{$0 \leq n \leq N$}
     number of correct results (resp.~\emph{reduction} for the \ucoretrack)
-  \item \makebox[5em][l]{$w \in [0,T]$}
-    wall-clock time in seconds (real-valued)
-  \item \makebox[5em][l]{$c \in [0, mT]$}
-    CPU time in seconds (real-valued)
+  \item \makebox[6em][l]{$\it{aw} \in [0,T]$}
+    actual wall-clock time in seconds (real-valued)
+  \item \makebox[6em][l]{$w \in [0,T]$}
+    wall-clock time score in seconds (real-valued)
+  \item \makebox[6em][l]{$\it{ac} \in [0, mT]$}
+    actual CPU time in seconds (real-valued)
+  \item \makebox[6em][l]{$c \in [0, mT]$}
+    CPU time score in seconds (real-valued)
 \end{itemize}
@@
 
+\header{Actual Wall-Clock Time ($\mathbf{aw}$).}
+The actual (real-valued) wall-clock time in seconds, until time limit $T$ or the
+solver process terminates.
+
 \header{Wall-Clock Time Score ($\mathbf{w}$).}
-The (real-valued) wall-clock time in seconds, until time limit $T$ or the
-solver process terminates.
-
-\header{CPU Time Score ($\mathbf{c}$).}
+For the \maintrack, \ucoretrack, \mvaltrack, \paralleltrack, and
+\cloudtrack, the wall-clock time score $w$ is the same as 
+the actual (real-valued) wall-clock time $\it{aw}$, 
+except that it is zero if the benchmark was not correctly solved within the time limit $T$, i.e., 
+$w = 0$ if $e = 1$, the process did not terminate within the time limit $T$, or 
+it did return unknown or an unknown result.
+For the \inctrack, the wall-clock time score $w$ 
+is the (real-valued) wall-clock time in seconds until the process returned the last correct result for a \akey{check-sat} command within the time limit;
+this means especially that $w = 0$ is zero if no (correct) result was returned for the first \akey{check-sat} command within the time limit.
+
+\header{Actual CPU Time ($\mathbf{ac}$).}
 The (real-valued) CPU time in seconds, measured across all $m$ cores
@@
 terminates.
+
+\header{CPU Time Score ($\mathbf{c}$).}
+For the \maintrack, \ucoretrack, \mvaltrack, \paralleltrack, and
+\cloudtrack, the CPU time score $c$ is the same as 
+the actual (real-valued) CPU time $\it{ac}$, 
+except that it is zero if the benchmark was not correctly solved within the time limit $mT$, i.e., 
+$c = 0$ if $e = 1$, the process did not terminate within the time limit $mT$, or 
+it did return unknown or an unknown result.
+For the \inctrack, the CPU time score $c$ 
+is the (real-valued) CPU time in seconds until the process returned the last correct result for a \akey{check-sat} command within the time limit;
+this means especially that $c = 0$ is zero if no (correct) result was returned for the first \akey{check-sat} command within the time limit.
 
@@
 CPU time limit.  More specifically, for a given parallel performance $\langle
-e, n, w, c\rangle$, the corresponding sequential performance is defined
+e, n, \it{aw}, w, \it{ac}, c\rangle$, the corresponding sequential performance is defined
 as~$\langle e_S, n_S, c_S\rangle$, where
 \begin{itemize}
-\item $e_S = 0$ and $n_S = 0$ if $c > T$, and $e_S = e$ and $n_S = n$
-  otherwise,
-\item $c_S = \min\ \{c, T\}$.\footnote{Under this
+\item $e_S = 0$, $n_S = 0$, and $c_S = 0$ if $c > T$;
+\item $e_S = e$, $n_S = n$, and $c_S = c$
+  otherwise.\footnote{Under this
   measure, a solver should not benefit from using multiple processor
@@
 if its parallel performance (Section~\ref{sec:benchmark-scoring}) is of the
-form $\langle 0, n, w, c\rangle$ for each benchmark in the division, i.e., if
+form $\langle 0, n, \it{aw}, w, \it{ac}, c\rangle$ for each benchmark in the division, i.e., if
 it did not produce any erroneous results.
@@
 of all the individual parallel benchmark scores:
-$$\sum_{b\in M} \langle e_b , n_b , w_b, c_b\rangle$$.
+$$\sum_{b\in M} \langle e_b , n_b , \it{aw}_b, w_b, \it{ac}_b, c_b\rangle$$.
 
 \noindent
-A parallel division score $\langle e, n, w, c\rangle$ is better than a parallel
-division score $\langle e', n', w', c'\rangle$ iff $e < e'$ or ($e = e'$ and $n
+A parallel division score $\langle
+e, n, \it{aw}, w, \it{ac}, c\rangle$ is better than a parallel
+division score\newline $\langle e', n', \it{aw}', w', \it{ac}', c'\rangle$ iff $e < e'$ or ($e = e'$ and $n
 > n'$) or ($e = e'$ and $n = n'$ and $w < w'$) or ($e = e'$ and $n = n'$ and $w
@@
 individual sequential benchmark scores:
-$$\sum_{b\in M} \langle e_b^s, n_b^s, w_b^s, c_b^s\rangle$$.
+$$\sum_{b\in M} \langle e_b^s, n_b^s, \it{aw}_b^s, w_b^s, \it{ac}_b^s, c_b^s\rangle$$.
 
@@
 
-Let $\langle e^s, n^s, w^s, c^s \rangle$ be the parallel division score
+Let $\langle e^s, n^s, \it{aw}^s, w^s, \it{ac}^s, c^s \rangle$ be the parallel division score
 for solver $s$ (for a given scoring system, i.e., $n$ is either number of correct
@@
 
-Let $\langle e_b^s, n_b^s, w_b^s, c_b^s \rangle$ be the parallel benchmark
+Let $\langle e_b^s, n_b^s, \it{aw}_b^s, w_b^s, \it{ac}_b^s, c_b^s \rangle$ be the parallel benchmark
 score for benchmark $b$ and solver $s$ (for a given scoring system).

### 2023-04-26 rules/rules23.tex
Model validation plus form link

@@
   In addition, we add this year the new experimental division for
-  non-linear arithmetic and for datatypes.  These include the divisions
+  arrays, non-linear arithmetic and for datatypes.  These include the divisions
   QF\_NonLinearIntArith, QF\_NonLinearRealArith,
   QF\_Equality+NonLinearArithm,
-  and QF\_Datatypes
-  (excluding all logics involving Arrays).  \todo{root-obj,
-    partially defined functions}
+  and QF\_Datatypes.
 %
@@
 \emph{and the tracks and divisions which it enters} via the web form
-at \todo{Needs to be updated!}
+at
 \begin{center}
-  \url{https://forms.gle/ewNQdFJbmQ12GxpX8}
+  \url{https://forms.gle/xhUDQaTynbS3mccE7}
 \end{center}
@@
 \header{Benchmark Selection.}  This track has the divisions QF\_Bitvec,
-QF\_LinearIntArith, QF\_LinearReal\-Arith, QF\_Equality (only with QF\_UF
-benchmarks), QF\_Equality+LinearArith (only with QF\_UFIDL, QF\_UFLIA, and
-QF\_UFLRA benchmarks), and QF\_Equality+Bitvec (only with QF\_UFBV benchmarks).
-%
-This year all divisions with UF logics (with uninterpreted functions) are
-experimental divisions.
+QF\_DataTypes, QF\_Equality,
+QF\_Equality+Bitvec,
+QF\_Equality+(Non)LinearArith,  
+QF\_(Non)LinearIntArith, and QF\_(Non)\-LinearRealArith.
+%
+This year all divisions with non-linear arithmetic, arrays, and data
+types are experimental divisions.
 %
@@
 \end{enumerate}
+
+The new experimental divisions require additional syntax to represent
+their models.  We propose the new syntax on the SMT-COMP website
+{\url{https://smt-comp.github.io/2023/model.html}}.
 

### 2023-04-26 rules/rules23.tex
SMT-COMP23 rules: changes to the wall-clock and CPU time scores for the incremental track.

--- 2023-04-26 rules/rules23.tex
@@
 For the \inctrack, the wall-clock time score $w$ 
-is the (real-valued) wall-clock time in seconds until the process returned the last correct result for a \akey{check-sat} command within the time limit;
-this means especially that $w = 0$ is zero if no (correct) result was returned for the first \akey{check-sat} command within the time limit.
+is the (real-valued) wall-clock time in seconds until the process returned the last time sat/unsat within the time limit;
+this means especially that $w = 0$ if the process never returned sat/unsat within the time limit.
 
@@
 For the \inctrack, the CPU time score $c$ 
-is the (real-valued) CPU time in seconds until the process returned the last correct result for a \akey{check-sat} command within the time limit;
-this means especially that $c = 0$ is zero if no (correct) result was returned for the first \akey{check-sat} command within the time limit.
+is the (real-valued) CPU time in seconds until the process returned the last time sat/unsat within the time limit;
+this means especially that $c = 0$ if the process never returned sat/unsat within the time limit.
 

### 2023-04-26 rules/rules23.tex
SMT-COMP23 rules removed draft and restored accidentally deleted changes.

--- 2023-04-26 rules/rules23.tex
@@
  %
-This year all divisions with non-linear arithmetic, arrays, and data
-types are experimental divisions.
+This year all divisions with non-linear arithmetic, arrays, and datatypes 
+are experimental divisions.
 %

### 2023-05-21 rules/rules23.tex
Clarified the model validation changes and the different types of participating tools.

@@
   %
-  This year these divisions will no longer be experimental.
-  %
-  In addition, we add this year the new experimental division for
+  This year these divisions will be officially counted and no longer be experimental.
+  %
+  In addition, we add this year new experimental divisions for
   arrays, non-linear arithmetic and for datatypes.  These include the divisions
@@
     model producing solvers, we proceed in an experimental fashion to push for
-    model standardization. We exclude logics containing arrays since
-    there is no standardized way of expressing array model values and
-    we do not want to add too many new logics.}
+    model standardization.}
 
@@
 A \emph{wrapper tool} is defined as any solver that calls one or more other SMT
-solvers (the \emph{wrapped solvers}). Its system description \textbf{must}
+solvers (the \emph{wrapped solvers}) from a different
+group of authors to solve distinct subtasks. 
+Examples of such subtasks are preprocessing steps or solving a subproblem that belongs to a strict sublogic of the input logic.
+For example, a solver using one subsolver to solve the ground abstraction of a
+quantified problem would be a wrapper tool.
+However, a wrapper tool solving a benchmark of logic A is not allowed to call an SMT solver 
+to solve a problem for logic A; even if the problem is just a subproblem.
+The system description of a wrapper tool \textbf{must}
 explicitly acknowledge and state the \textbf{exact} version of any solvers that
@@
 extends} another SMT solver (the \emph{base solver}) from a different
-group of authors.  Its system description
+group of authors.  
+In contrast to a wrapper tool, 
+a derived tool solving a benchmark of logic A is allowed to call an SMT solver 
+to solve a problem for logic A.
+However, it is not allowed to call more than one different SMT solver to solve a problem over the input logic.
+Examples of derived tools are tools that change the strategy selection for the base solver,
+tools that add new preprocessing steps on top of the base solver,
+tools that add new heuristics or incomplete procedures to a base solver.
+The system description of a derived tool
 \textbf{must} explicitly acknowledge
@@
 logics (as described on page~\pageref{benchmark-selection}).
-%
-We exclude from the selection all benchmarks containing arrays or datatypes.
 

### 2023-06-23 2023/certificates/gen_certificates_ornament.tex
Add template for certificate

\documentclass[landscape,12pt]{article}
\usepackage[svgnames]{xcolor}
\usepackage{wallpaper}
\usepackage{ragged2e}
\usepackage{ulem}
\usepackage[object=pgfhan]{pgfornament}
\usetikzlibrary{chains}
\usetikzlibrary{calc}
\usetikzlibrary{decorations}
\usetikzlibrary{decorations.text,decorations.markings}
\usetikzlibrary {decorations.pathmorphing,shadows}

\usepackage{geometry}
\geometry{hmargin=1in,vmargin=0.8in,headheight=10pt}

\usepackage{fancyhdr}
\fancyhf{}
\renewcommand{\headrule}{}

\fancyhead[L]{%
\newpgfornamentfamily{pgfhan}
\begin{tikzpicture}[overlay,remember picture]
    \tikzset{every node/.append style={inner sep=0pt,color=MidnightBlue!50}}
    \tikzset{pgfornamentstyle/.style={draw=green!20!black,
    fill=orange,fill opacity=.5,thick}}%
    \newbox{\fortyseven}
\savebox{\fortyseven}{\pgfornament[scale=0.50]{32}}
    \node[anchor=north west,shift={(14.5pt,-14.5pt)}] at (current page.north west)
  (nw) {\pgfornament[scale=0.5]{12}};
    \node[anchor=north east,shift={(-14.5pt,-14.5pt)}] at (current page.north east)
    (ne) {\pgfornament[scale=0.5,symmetry=v]{12}};
  \node[anchor=south west,shift={(14.5pt,14.5pt)}] at (current page.south west)
    (sw) {\pgfornament[scale=0.5,symmetry=h]{12}};
  \node[anchor=south east,shift={(-14.5pt,14.5pt)}] at (current page.south east)
    (se) {\pgfornament[scale=0.5,symmetry=c]{12}};
%    \pgfornamentline[scale=0.25,shift={(0pt,-14.5pt)}]{nw.north west}{ne}{20}{32};
% \begin{scope}[start chain,node distance=-1pt]
%     \node[anchor=north west,on chain] at (nw.north east)
%     {\usebox{\fortyseven}};
%     \foreach \i in {1,...,9} {\node[on chain]{\usebox{\fortyseven}};}
%     \end{scope}
\foreach \i in {0,...,5}
   \node[anchor=north west,shift={($\i*(100bp,0)$)}] at (nw.north east)
    {\usebox{\fortyseven}};
\foreach \i in {0,...,3}
    \node[anchor=south east,shift={($\i*(0,-100bp)$)},rotate=90] at (ne.south east)
     {\usebox{\fortyseven}};
\foreach \i in {0,...,5}
     \node[anchor=south west,shift={($\i*(100bp,0)$)}] at (sw.south east)
      {\usebox{\fortyseven}};
\foreach \i in {0,...,3}
      \node[anchor=south west,shift={($\i*(0,-100bp)$)},rotate=-90] at (nw.south west)
       {\usebox{\fortyseven}};
   %         \foreach \i in {0,...,22}
% \node[anchor=south west,rotate=-90,
% shift={($\i*(31bp,0)$)}] at (nw.south west)
% {\usebox{\fortyseven}};
    %   \node[anchor=north west] at (nw.north east) {\pgfornament[scale=0.25]{32}};
%    \draw [scale=0.25] (nw) to [ornament=12] (ne);
%   \node[anchor=north west] at (nw.north east)%
%     {\pgfornament[scale=0.25]{32}};
%     \node[anchor=south west] at (sw.south east)%
%     {\pgfornament[scale=0.25]{32}};
%     \node[anchor=south west,rotate=-90] at (nw.south west)
%     {\pgfornament[scale=0.25]{32}};
%     \node[anchor=south east,rotate=90] at (ne.south east)
%     {\pgfornament[scale=0.25]{32}};
%     \node[anchor=center,shift={(25bp,-25bp)}] at (nw.south east)
%     {\pgfornament[scale=0.5]{57}};
\end{tikzpicture}
}

% \node[anchor=north west,shift={(14.5pt,-14.5pt)}] at (current page.north west)
%   (nw) {\pgfornamenthan[scale=0.2]{25}};

\pagestyle{fancy}
\fancypagestyle{plain}{\pagestyle{fancy}}

\usepackage{environ}

\NewEnviron{myframe}{%
\newpgfornamentfamily{vectorian}
    \begin{tikzpicture}[color=Maroon,
        every node/.style={inner sep=0pt}]
        \node[minimum size=12cm](vecbox){%
            \begin{minipage}{\textwidth}
            \centering
        \BODY
    \end{minipage}};
        \node[anchor=north west] at (vecbox.north west)
        {\pgfornament[width=2.5cm,symmetry=h]{3}};
        \node[anchor=north east] at (vecbox.north east)
        {\pgfornament[width=2.5cm,symmetry=c]{3}};
        \node[anchor=south west] at (vecbox.south west)
        {\pgfornament[width=2.5cm,symmetry=none]{3}};
        \node[anchor=south east] at (vecbox.south east)
        {\pgfornament[width=2.5cm,symmetry=v]{3}};
        \end{tikzpicture}    
}

\newcommand{\seq}{\texttt{;}}
\newcommand{\paral}{\textbardbl}
\newcommand{\sat}{$\top$}
\newcommand{\unsat}{$\bot$}
\newcommand{\fast}{\texttt{24}}
\newcommand{\inc}{inc}
\newcommand{\uc}{uc\textsuperscript}
\newcommand{\mv}{mv}

\begin{document}
\TileWallPaper{4cm}{2cm}{tiling.png}

{\centering
{

\begin{minipage}{\textwidth}
\centering

\begin{tikzpicture}
  \node [circular drop shadow={shadow scale=1.05},
         decorate, decoration=zigzag,
         fill=blue!20,draw,thick,circle,text width=3.5cm,align=center,xshift=2cm]
          {\large\textbf{SMT-COMP\\ 2023}};
\end{tikzpicture}
\end{minipage}

\begin{myframe}

\textcolor{red!10!black!90}
{\Huge Solver Name}\\

\textcolor{green!10!black!90}{
\large In honor of the results achieved in the SMT-competition}

\medskip

\textcolor{red!30!black!90}
{\textit{Certificate for overall performance}}

\newcommand{\all}{{\footnotesize (\seq,\paral,\sat,\unsat,\fast,\inc,\uc\seq,\uc\paral,\mv)}}

\textcolor{black}{\large
 \textsc{Largest Contribution}\all,
 \textsc{Biggest Lead}\all}

 \medskip
\textcolor{red!30!black!90} {\textit{Certificate for category}}

 \textcolor{black}{\large
 \textsc{FParith}
Bitvec\all,
 Equality+LinearArith~\all,
 Equality+MachineArith~\all,
 Equality+NonLinearArith~\all,
 Equality~\all,
 FPArith~\all,
 QF\_Bitvec~\all,
 QF\_Datatypes~\all,
 QF\_Equality+Bitvec+Arith~\all,
 QF\_Equality+Bitvec~\all,
 QF\_Equality+LinearArith~\all,
 QF\_Equality+NonLinearArith~\all,
 QF\_Equality~\all,
 QF\_FPArith~\all,
 QF\_LinearIntArith~\all,
 QF\_LinearRealArith~\all,
 QF\_NonLinearIntArith~\all,
 QF\_NonLinearRealArith~\all,
 QF\_Strings~\all
 }

 \medskip
 \textcolor{red!30!black!90}  {\textit{Certificate for logic}}

 \textcolor{black}{\large QF\_ABVFP\all
 }

\vspace{2mm}

\vspace{1cm}

{\color{blue!40!black}
\scalebox{.7}{
\begin{tabular}{ccccc}
\cline{1-1} 
\cline{3-3}
\cline{5-5}
\\ \
Jochen Hoenicke  & &  Bobot François & & Martin Bromberger \\
Organizer & & Chair & & Organizer \\ 
\end{tabular}
}}
\end{myframe}

}}

\newpage

Lorem ipsum dolor sit amet, consectetur adipiscing elit. Ut in mollis libero, eget sagittis lectus. Curabitur cursus diam nec elit tincidunt dapibus. Quisque elementum lorem eget felis pulvinar sodales. Donec quis ipsum quis nibh venenatis finibus. Suspendisse potenti. Aenean scelerisque rutrum felis ut gravida. Donec tortor ex, auctor condimentum lectus et, tincidunt porttitor nisl.

Fusce eu nunc nisl. Integer mauris neque, egestas id malesuada ac, dignissim nec enim. Quisque vulputate elit justo, eget sodales libero maximus non. Vestibulum gravida vitae nunc blandit finibus. Donec sit amet nulla vitae justo vestibulum iaculis accumsan et sem. Praesent non dolor nec elit lobortis porttitor. Nunc a posuere elit. Mauris condimentum augue et vehicula malesuada.

Nullam eros quam, vestibulum in consequat id, eleifend at dolor. Phasellus fringilla, ante eget ornare condimentum, risus magna semper augue, id venenatis odio risus nec eros. Duis sed ante lectus. Mauris non imperdiet enim, id maximus augue. Vestibulum tincidunt felis neque, eget mollis massa semper ac. In ultrices risus in urna mollis sodales. Curabitur eget consequat dui. Donec ornare convallis convallis. Donec laoreet aliquam laoreet. Maecenas sit amet nisl sagittis, consectetur magna eu, dignissim mi. Curabitur lobortis velit quis lectus condimentum, eget hendrerit nisl malesuada. Integer tincidunt, tellus eu egestas aliquam, sapien enim aliquam lacus, vel posuere nulla augue vitae odio. Vivamus porttitor nisi nec libero tristique, quis congue eros mattis.

Fusce mi nisi, pretium eget metus tristique, mollis efficitur nulla. Vestibulum et interdum risus. Sed venenatis pretium ultrices. Cras odio sapien, interdum convallis maximus at, sagittis et leo. Aenean tincidunt, orci vestibulum interdum condimentum, nibh urna euismod risus, sit amet sodales nisl libero quis sapien. Donec euismod erat a pellentesque pulvinar. Aliquam a nulla massa. Quisque id elit sit amet nibh lacinia pulvinar eget sit amet orci. Etiam finibus mi eu consectetur sodales. Aenean sed nulla leo. Maecenas odio est, rutrum rutrum fringilla et, maximus vel tortor. Donec sit amet lorem magna. In suscipit pharetra justo quis tempor. Sed sit amet ipsum mi. Phasellus vel luctus nulla, quis ornare augue. Phasellus ut elit sit amet magna fermentum ullamcorper.

Sed imperdiet sem neque, sed lacinia libero congue scelerisque. Curabitur sollicitudin orci ullamcorper sem consectetur dapibus. Mauris sit amet erat in enim imperdiet molestie vel lobortis leo. Pellentesque luctus efficitur quam, sit amet malesuada arcu faucibus condimentum. Fusce sapien dolor, blandit ac faucibus gravida, facilisis rutrum nulla. Nam vestibulum feugiat erat sit amet rhoncus. Vivamus egestas justo sit amet euismod tincidunt. Phasellus facilisis ornare volutpat. Cras dignissim in felis eget placerat.

\end{document}

### 2023-06-23 tools/scoring/score.py
Updated scoring script to match new method of scoring cpu and wallclock time.

@@ -454,9 +454,13 @@ def score(division,
     # Column 'wrong-answers' only exists in incremental tracks.
     incremental = 'wrong-answers' in data.columns
     assert not incremental or 'correct-answers' in data.columns
+    if int(year) >= 2023:
+        assert not incremental or 'solver-cpu-time' in data.columns
+        assert not incremental or 'solver-wall-time' in data.columns
+    
     unsat_core = 'reduction' in data.columns
     assert not unsat_core or 'result-is-erroneous' in data.columns
-
+    
     # Column 'model_validator_status' only exists in the model validation track.
     model_validation = 'model_validator_status' in data.columns
     if model_validation:
@@ -467,6 +471,17 @@ def score(division,
     proof_exhibition = 'reason' in data.columns
     if proof_exhibition:
         data_new['reason'] = data['reason']
+
+    # Set alpha_prime_b for each benchmark, set to 1 if family is not in the
+    # 'family_scores' dictionary (use_families == False).
+    data_new['alpha_prime_b'] = \
+        data_new.family.map(lambda x: family_scores.get(x, 1))
+
+    if use_families:
+        data_new['score_modifier'] = \
+            data_new.alpha_prime_b * data_new.division_size
+    else:
+        data_new['score_modifier'] = 1
 
     # Note: For incremental tracks we have to consider all benchmarks (also
     #       the ones that run into resource limits).
@@ -523,6 +538,15 @@ def score(division,
         if unsat_core:
             data_new.loc[solved.index, 'correct'] = data['reduction']
             data_new.loc[solved.index, 'error'] = data['result-is-erroneous']
+
+            # Calculate time scores
+            if int(year) >= 2023:
+                data_new['score_cpu_time'] = 0.0
+                data_new['score_wallclock_time'] = 0.0
+                data_new.loc[solved.index,'score_cpu_time'] = \
+                    data_new.cpu_time * data_new.alpha_prime_b
+                data_new.loc[solved.index,'score_wallclock_time'] = \
+                    data_new.wallclock_time * data_new.alpha_prime_b
         # Note: The model validator reports INVALID if a solver crashes on an
         #       instance. Hence, only when a solver reports statisfiable, we
         #       check the status of the model validator.
@@ -548,10 +572,29 @@ def score(division,
                                              | (incomplete_model == False))]
[…]

### 2023-06-23 2023/scoring/clean_result_csvs.sh
Added scoring scripts

@@ -1,0 +1,32 @@
+#!/bin/bash
+
+SCRIPTDIR=`dirname $(readlink -f "$0")`
+
+PROCESS_CSV="$SCRIPTDIR/../../tools/process-results/process_results.py"
+RESULT_DIR="$SCRIPTDIR/../results"
+NONINC_DECISION="$SCRIPTDIR/../results/sq-disagreements-decision.csv"
+EXCLUDED="$SCRIPTDIR/../prep/SMT-LIB_excluded.txt"
+
+TMPDIR=$(mktemp -d)
+trap "rm -rf $TMPDIR" EXIT
+
+grep ^incremental $EXCLUDED | cut -d/ -f2- > excluded_incremental.txt
+grep ^non-incremental $EXCLUDED | cut -d/ -f2- > excluded_nonincremental.txt
+
+for i in inc mv sq uc pe cloud parallel; do
+    if [ "$i" == "inc" ]; then
+        EXCLUDED=excluded_incremental.txt
+        DECISION=""
+    else
+        EXCLUDED=excluded_nonincremental.txt
+        DECISION="-d $NONINC_DECISION"
+    fi
+
+    FILTER=""
+    if [ "$i" == "uc" ]; then
+        FILTER="| grep -v -e ',post-processor error,' -e 'run script error'"
+    fi
+
+    echo $PROCESS_CSV -x ${EXCLUDED} ${DECISION} $RESULT_DIR/raw-results-$i.csv
+    eval $PROCESS_CSV -x ${EXCLUDED} ${DECISION} $RESULT_DIR/raw-results-$i.csv  $FILTER > results-$i.csv
+done

### 2023-06-23 2023/scoring/make_mds.sh

@@ -1,0 +1,103 @@
+#! /bin/bash
+
+SCRIPTDIR=`dirname $(readlink -f "$0")`
+
+YEAR=2023
+SCORE="$SCRIPTDIR/../../tools/scoring/score.py"
+SOLVERS_CSV="$SCRIPTDIR/../registration/solvers_divisions_all.csv"
+OUTPUT="$SCRIPTDIR/../../../smt-comp.github.io/_results_$YEAR"
+TIME=1200
+INC_NUM_CHECK_SAT="$SCRIPTDIR/../prep/SMT-LIB_incremental_benchmarks_num_check_sat.csv"
+
+GEN_SQ=
+GEN_INC=
+GEN_UC=
+GEN_MV=
+GEN_PE=
+GEN_CT=
+GEN_PT=
+
+while [ $# -gt 0 ]
+do
+  case $1 in
+    -h|--help)
+      echo -n "usage: $(basename $0) [<option>]"
+      echo
+      echo "Generate results .md files for website."
+      echo
+      echo "  options:"
+      echo "    -h, --help     Print this message and exit"
+      echo "    --all          All tracks"
+      echo "    --sq           Single Query track (no strings)"
+      echo "    --inc          Incremental track "
+      echo "    --uc           Unsat Core track "
+      echo "    --mv           Model Validation track "
+      echo "    --pe           Proof Exhibition track "
+      echo "    --cloud        Cloud track "
+      echo "    --parallel     Parallel track "
+      echo
+      exit
+      ;;
+    --all)
+      GEN_SQ=yes
+      GEN_INC=yes
+      GEN_UC=yes
+      GEN_MV=yes
+      GEN_PE=yes
+      GEN_CT=yes
+      GEN_PT=yes
+      ;;
+    --sq)
+      GEN_SQ=yes
+      ;;
+    --inc)
+      GEN_INC=yes
+      ;;
+    --uc)
+      GEN_UC=yes
+      ;;
+    --mv)
+      GEN_MV=yes
+      ;;
+    --pe)
+      GEN_PE=yes
+      ;;
+    --cloud)
+      GEN_CT=yes
+      ;;
+    --parallel)
+      GEN_PT=yes
+      ;;
+    -*)
[…]

### 2023-06-23 2023/scoring/make_pivot_table_csv.sh

@@ -1,0 +1,3 @@
+#/bin/sh -eu
+
+python3 ../../tools/results_visualization/aggregations.py --csv results-sq.csv --solvers ../registration/solvers_divisions_all.csv --out ../../../smt-comp.github.io/2022/sq.csv --divisions-map ../new-divisions.json --time 1200

### 2023-06-26 2023/certificates/gen_certificates_ornament.tex
[Results] Use the results with the fixed version of dolmen

@@
-\documentclass[landscape,12pt]{article}
+\documentclass[a4paper,landscape,12pt]{article}
 \usepackage[svgnames]{xcolor}
@@
 %     \end{scope}
-\foreach \i in {0,...,5}
-   \node[anchor=north west,shift={($\i*(100bp,0)$)}] at (nw.north east)
+\foreach \i in {0,...,6}
+   \node[anchor=north west,shift={($\i*(100bp,0)-(50bp,0)$)}] at (nw.north east)
     {\usebox{\fortyseven}};
@@
      {\usebox{\fortyseven}};
-\foreach \i in {0,...,5}
-     \node[anchor=south west,shift={($\i*(100bp,0)$)}] at (sw.south east)
+\foreach \i in {0,...,6}
+     \node[anchor=south west,shift={($\i*(100bp,0)-(50bp,0)$)}] at (sw.south east)
       {\usebox{\fortyseven}};
@@
  \medskip
-\textcolor{red!30!black!90} {\textit{Certificate for category}}
+\textcolor{red!30!black!90} {\textit{Certificate for divisions}}
 

### 2023-06-26 2023/results/fix_starexec_custom_column.py

@@ -1,0 +1,37 @@
+#!/bin/python3
+
+## Some cell are in column with header "foo=bar" and value "baz" which should
+## be in column "foo" with value "barbaz"
+## starexec cut the last = instead of the first
+
+import csv
+import sys
+
+csv.field_size_limit(sys.maxsize)
+
+def main():
+    with open(sys.argv[1], newline='') as csvin:
+        csvin = csv.reader(csvin)
+        header=next(csvin)
+        clean_header=[]
+        conv=[]
+        for head in header:
+            split=head.split(sep="=",maxsplit=1)
+            if split[0] not in clean_header:
+                clean_header.append(split[0])
+            conv.append(split[0])
+            # print(head)
+            # print(split[0])
+            # print(spurious)
+
+        with open(sys.argv[2], 'w', newline='') as csvout:
+            csvout = csv.DictWriter(csvout,quoting=csv.QUOTE_MINIMAL,fieldnames=clean_header)
+            csvout.writeheader()
+            for row in csvin:
+                new_row={}
+                for col,head in zip(row,conv):
+                    new_row[head]=col
+                csvout.writerow(new_row)
+                
+main()
+        

### 2023-06-26 2023/results/join.sh

@@ -26,9 +26,25 @@ for track in sq inc mv uc pe; do
         fi
         INPUT="Job${id}/Job${id}_info.csv"
         echo -n " Job${id}"
+
+        if [ "$track" == "mv" ]; then
+            TMPINPUT_FIXED=${TMPDIR}/input_fixed.csv
+            echo -n "(fix column)"
+            ./fix_starexec_custom_column.py $INPUT $TMPINPUT_FIXED
+            if [ -e ./fix-results-$id.csv.gz ]; then
+                TMPINPUT=${TMPDIR}/input_merged.csv
+                echo -n "(merge with fixed dolmen)"
+                ./merge_local_results_mv.py ./fix-results-$id.csv.gz $TMPINPUT_FIXED $TMPINPUT
+            else
+                TMPINPUT=$TMPINPUT_FIXED
+            fi
+        else
+            TMPINPUT=$INPUT
+        fi
+
         if [ -e $OUTPUT ]; then
             TMPFILE=${TMPDIR}/job.csv
-            $COLORDER -o $OUTPUT -a $INPUT > $TMPFILE
+            $COLORDER -o $OUTPUT -a $TMPINPUT > $TMPFILE
 
             # sanity check: head must be equal now
             diff <(head -1 $TMPFILE) <(head -1 $OUTPUT)
@@ -36,7 +52,7 @@ for track in sq inc mv uc pe; do
             rm $TMPFILE
         else
             # convert all files to same line ending
-            cat $INPUT > $OUTPUT
+            cat $TMPINPUT > $OUTPUT
         fi
     done
     echo

### 2023-06-26 2023/results/merge_local_results_mv.py

@@ -1,0 +1,41 @@
+#!/usr/bin/python3
+
+## Merge local result with fixed dolmen
+
+import csv
+import sys
+import gzip
+
+def main():
+    local_result = sys.argv[1] #gzipped file
+    raw_result = sys.argv[2]
+    new_result = sys.argv[3]
+    
+    not_proved_locally={}
+    
+    with gzip.open(local_result, newline='',mode='rt') as csvfile:
+        reader = csv.reader(csvfile)
+        for row in reader:
+            not_proved_locally[(row[0],row[1],row[2])]=True
+
+    with open(raw_result, newline='') as inputcsvfile:
+        reader = csv.DictReader(inputcsvfile)
+
+        with open(new_result, 'w', newline='') as outputcsvfile:
+            writer = csv.DictWriter(outputcsvfile, fieldnames=reader.fieldnames)
+
+            writer.writeheader()
+
+            for row in reader:
+                key=(row["benchmark"],row["solver"],row["configuration"])
+                if not key in not_proved_locally:
+                    row["result"]="sat"
+                    row["dolmenexit"]="0"
+                    row["model_validator_error"]="-"
+                    row["model_validator_status"]="VALID"
+                
+                writer.writerow(row)
+    
+    
+main()
+

### 2023-06-26 2023/certificates/gen_certificates_ornament.tex
Generate certificate using yamll from website (example with 2022)

@@
 \usepackage{ulem}
+\usepackage{etoolbox}
 \usepackage[object=pgfhan]{pgfornament}
@@
 \newcommand{\uc}{uc\textsuperscript}
-\newcommand{\mv}{mv}
+\newcommand{\mv}{mv\textsuperscript}
+\newcommand{\cloud}{cloud}
+\newcommand{\all}{{\footnotesize (\seq,\paral,\sat,\unsat,\fast,\inc,\uc\seq,\uc\paral,\mv)}}
+\newcommand{\withtrack}[2]{\textsc{#1}{{\footnotesize (#2)}}}
 
-\begin{document}
-\TileWallPaper{4cm}{2cm}{tiling.png}
-
+\newcommand{\MakeOnePage}[4]{
     {\centering
@@
     \textcolor{red!10!black!90}
-{\Huge Solver Name}\\
+    {\Huge #1}\\
 
@@
     \medskip
-
+    \ifstrempty{#2}{}{
     \textcolor{red!30!black!90}
@@
 
-\newcommand{\all}{{\footnotesize (\seq,\paral,\sat,\unsat,\fast,\inc,\uc\seq,\uc\paral,\mv)}}
-
-\textcolor{black}{\large
- \textsc{Largest Contribution}\all,
- \textsc{Biggest Lead}\all}
+    \textcolor{black}{\large #2}
 
      \medskip
+    }
+
+    \ifstrempty{#3}{}{
     \textcolor{red!30!black!90} {\textit{Certificate for divisions}}
 
- \textcolor{black}{\large
- \textsc{FParith}
-Bitvec\all,
- Equality+LinearArith~\all,
- Equality+MachineArith~\all,
- Equality+NonLinearArith~\all,
- Equality~\all,
- FPArith~\all,
- QF\_Bitvec~\all,
- QF\_Datatypes~\all,
- QF\_Equality+Bitvec+Arith~\all,
- QF\_Equality+Bitvec~\all,
- QF\_Equality+LinearArith~\all,
- QF\_Equality+NonLinearArith~\all,
- QF\_Equality~\all,
- QF\_FPArith~\all,
- QF\_LinearIntArith~\all,
- QF\_LinearRealArith~\all,
- QF\_NonLinearIntArith~\all,
- QF\_NonLinearRealArith~\all,
- QF\_Strings~\all
+     \textcolor{black}{\large#3}
+
+     \medskip
     }
 
- \medskip
+    \ifstrempty{#4}{}{
      \textcolor{red!30!black!90}  {\textit{Certificate for logic}}
 
- \textcolor{black}{\large QF\_ABVFP\all
+     \textcolor{black}{\large #4}
     }
-
     \vspace{2mm}
@@
 
-\newpage
+}
 
-Lorem ipsum dolor sit amet, consectetur adipiscing elit.
-Ut in mollis libero, eget sagittis lectus.
-Curabitur cursus diam nec elit tincidunt dapibus.
-Quisque elementum lorem eget felis pulvinar sodales.
-Donec quis ipsum quis nibh venenatis finibus.
-Suspendisse potenti.
-Aenean scelerisque rutrum felis ut gravida.
-Donec tortor ex, auctor condimentum lectus et, tincidunt porttitor nisl.
+\begin{document}
+\TileWallPaper{4cm}{2cm}{tiling.png}
 
-Fusce eu nunc nisl.
-Integer mauris neque, egestas id malesuada ac, dignissim nec enim.
-Quisque vulputate elit justo, eget sodales libero maximus non.
-Vestibulum gravida vitae nunc blandit finibus.
-Donec sit amet nulla vitae justo vestibulum iaculis accumsan et sem.
-Praesent non dolor nec elit lobortis porttitor.
-Nunc a posuere elit.
-Mauris condimentum augue et vehicula malesuada.
-
-Nullam eros quam, vestibulum in consequat id, eleifend at dolor.
-Phasellus fringilla, ante eget ornare condimentum, risus magna semper augue, id venenatis odio risus nec eros.
-Duis sed ante lectus.
-Mauris non imperdiet enim, id maximus augue.
-Vestibulum tincidunt felis neque, eget mollis massa semper ac.
-In ultrices risus in urna mollis sodales.
-Curabitur eget consequat dui.
-Donec ornare convallis convallis.
-Donec laoreet aliquam laoreet.
-Maecenas sit amet nisl sagittis, consectetur magna eu, dignissim mi.
-Curabitur lobortis velit quis lectus condimentum, eget hendrerit nisl malesuada.
-Integer tincidunt, tellus eu egestas aliquam, sapien enim aliquam lacus, vel posuere nulla augue vitae odio.
-Vivamus porttitor nisi nec libero tristique, quis congue eros mattis.
-
-Fusce mi nisi, pretium eget metus tristique, mollis efficitur nulla.
-Vestibulum et interdum risus.
-Sed venenatis pretium ultrices.
-Cras odio sapien, interdum convallis maximus at, sagittis et leo.
-Aenean tincidunt, orci vestibulum interdum condimentum, nibh urna euismod risus, sit amet sodales nisl libero quis sapien.
-Donec euismod erat a pellentesque pulvinar.
-Aliquam a nulla massa.
-Quisque id elit sit amet nibh lacinia pulvinar eget sit amet orci.
-Etiam finibus mi eu consectetur sodales.
-Aenean sed nulla leo.
-Maecenas odio est, rutrum rutrum fringilla et, maximus vel tortor.
-Donec sit amet lorem magna.
-In suscipit pharetra justo quis tempor.
-Sed sit amet ipsum mi.
-Phasellus vel luctus nulla, quis ornare augue.
-Phasellus ut elit sit amet magna fermentum ullamcorper.
-
-Sed imperdiet sem neque, sed lacinia libero congue scelerisque.
-Curabitur sollicitudin orci ullamcorper sem consectetur dapibus.
-Mauris sit amet erat in enim imperdiet molestie vel lobortis leo.
-Pellentesque luctus efficitur quam, sit amet malesuada arcu faucibus condimentum.
-Fusce sapien dolor, blandit ac faucibus gravida, facilisis rutrum nulla.
-Nam vestibulum feugiat erat sit amet rhoncus.
-Vivamus egestas justo sit amet euismod tincidunt.
-Phasellus facilisis ornare volutpat.
-Cras dignissim in felis eget placerat.
+\input{input_for_certificates.tex}
 

### 2023-06-26 2023/certificates/input_for_certificates.tex
Generate certificate using yamll from website (example with 2022)

\MakeOnePage{Bitwuzla}{}{\withtrack{QF\_Equality+Bitvec}{\seq,\paral,\sat,\unsat,\fast,\uc\seq,\uc\paral,\mv\seq,\mv\paral}, \withtrack{QF\_FPArith}{\seq,\paral,\sat,\unsat,\fast,\inc,\uc\seq,\uc\paral,\mv\seq,\mv\paral}, \withtrack{QF\_Bitvec}{\seq,\paral,\sat,\uc\seq,\uc\paral,\mv\seq,\mv\paral}, \withtrack{FPArith}{\seq,\paral,\sat,\unsat,\fast,\inc}}{\withtrack{QF\_UFBV}{\inc}, \withtrack{AUFBV}{\seq,\paral,\unsat,\fast}, \withtrack{AUFBVFP}{\seq,\paral,\unsat,\fast}, \withtrack{UFBV}{\unsat,\fast}}
\newpage
\MakeOnePage{OpenSMT}{}{\withtrack{QF\_LinearIntArith}{\seq,\paral}, \withtrack{QF\_LinearRealArith}{\inc,\mv\seq,\mv\paral}}{\withtrack{QF\_LIA}{\unsat}, \withtrack{QF\_UFLIA}{\unsat}, \withtrack{QF\_LRA}{\seq,\paral,\unsat,\fast}}
\newpage
\MakeOnePage{Z3++}{\withtrack{Biggest Lead}{\mv\seq,\mv\paral}, \withtrack{Largest Contribution}{\mv\seq,\mv\paral}}{\withtrack{QF\_LinearIntArith}{\sat,\mv\seq,\mv\paral}, \withtrack{QF\_NonLinearIntArith}{\unsat}, \withtrack{QF\_NonLinearRealArith}{\sat}}{\withtrack{QF\_IDL}{\seq,\paral,\unsat}}
\newpage
\MakeOnePage{cvc5}{\withtrack{Biggest Lead}{\seq,\paral,\sat,\unsat,\fast,\uc\seq,\uc\paral}, \withtrack{Largest Contribution}{\seq,\paral,\sat,\unsat,\fast,\inc,\uc\seq,\uc\paral}}{\withtrack{QF\_LinearIntArith}{\unsat}, \withtrack{QF\_Strings}{\seq,\paral,\sat,\unsat,\fast}, \withtrack{QF\_Datatypes}{\seq,\paral,\sat,\unsat,\uc\seq,\uc\paral}, \withtrack{Equality+MachineArith}{\seq,\paral,\sat,\unsat,\fast,\uc\seq,\uc\paral}, \withtrack{Equality}{\seq,\paral,\sat,\unsat,\inc,\uc\seq}, \withtrack{Equality+LinearArith}{\seq,\paral,\sat,\unsat,\fast,\inc,\uc\seq,\uc\paral}, \withtrack{Arith}{\seq,\paral,\unsat,\inc,\uc\seq,\uc\paral}, \withtrack{QF\_NonLinearIntArith}{\seq,\paral,\sat}, \withtrack{Bitvec}{\seq,\paral,\sat,\unsat,\inc,\uc\seq,\uc\paral}, \withtrack{QF\_Equality+NonLinearArith}{\seq,\paral,\sat,\unsat,\fast}, \withtrack{Equality+NonLinearArith}{\seq,\paral,\sat,\unsat,\fast,\inc,\uc\seq,\uc\paral}, \withtrack{QF\_NonLinearRealArith}{\seq,\paral,\unsat,\fast}, \withtrack{QF\_LinearRealArith}{\unsat}}{\withtrack{QF\_IDL}{\uc\seq,\uc\paral}, \withtrack{QF\_UFNIA}{\inc,\uc\seq,\uc\paral}, \withtrack{QF\_ABVFPLRA}{\seq,\paral,\unsat,\inc,\uc\seq,\uc\paral}, \withtrack{LIA}{\sat,\fast}, \withtrack{UFDT}{\fast}, \withtrack{QF\_UFLRA}{\uc\seq,\uc\paral}, \withtrack{QF\_BVFPLRA}{\unsat,\inc}, \withtrack{NIA}{\sat,\fast}, \withtrack{QF\_NIRA}{\unsat}, \withtrack{QF\_UFDTLIRA}{\seq,\paral,\sat,\unsat,\fast,\uc\seq,\uc\paral}, \withtrack{QF\_AUFLIA}{\uc\seq,\uc\paral}, \withtrack{QF\_UFNRA}{\inc,\uc\seq,\uc\paral}, \withtrack{BVFP}{\seq,\paral,\sat}}
\newpage
\MakeOnePage{Yices2}{}{\withtrack{QF\_LinearIntArith}{\fast,\inc,\uc\seq,\uc\paral}, \withtrack{QF\_Bitvec}{\inc}, \withtrack{QF\_Equality}{\seq,\paral,\sat,\unsat,\fast,\inc,\uc\seq,\uc\paral,\mv\seq,\mv\paral}, \withtrack{QF\_LinearRealArith}{\seq,\paral,\sat,\fast,\uc\seq,\uc\paral}, \withtrack{QF\_NonLinearIntArith}{\fast}, \withtrack{QF\_Equality+LinearArith}{\unsat,\fast,\uc\seq,\uc\paral}, \withtrack{QF\_Equality+Bitvec}{\inc}}{\withtrack{QF\_LIRA}{\seq,\paral,\sat,\unsat,\mv\seq,\mv\paral}, \withtrack{QF\_UFNIA}{\sat}, \withtrack{QF\_UFLIA}{\seq,\paral,\sat,\inc,\mv\seq,\mv\paral}, \withtrack{QF\_UFLRA}{\seq,\paral,\inc,\mv\seq}, \withtrack{QF\_UFBV}{\sat}, \withtrack{QF\_UFIDL}{\seq,\paral}, \withtrack{QF\_RDL}{\unsat,\mv\seq,\mv\paral}, \withtrack{QF\_ALIA}{\seq,\paral,\sat}, \withtrack{QF\_AUFLIA}{\seq,\paral,\sat}, \withtrack{QF\_AUFBV}{\seq,\paral,\sat,\unsat,\fast,\uc\seq,\uc\paral}, \withtrack{QF\_UFNRA}{\seq,\paral,\sat,\unsat,\fast}}
\newpage
\MakeOnePage{Vampire}{\withtrack{Biggest Lead}{\cloud}}{\withtrack{Equality}{\fast,\uc\paral,\cloud}, \withtrack{Equality+NonLinearArith}{\cloud}, \withtrack{Arith}{\cloud}, \withtrack{Equality+LinearArith}{\cloud}}{\withtrack{AUFLIA}{\unsat,\fast}, \withtrack{UFLIA}{\uc\paral}, \withtrack{UF}{\seq,\paral,\sat}, \withtrack{UFDTNIA}{\seq,\paral,\unsat,\fast,\uc\seq,\uc\paral}, \withtrack{UFDTLIA}{\fast,\uc\seq,\uc\paral}, \withtrack{AUFNIRA}{\seq,\paral,\unsat,\fast,\uc\seq,\uc\paral}, \withtrack{UFNIA}{\uc\paral}, \withtrack{AUFLIRA}{\fast}}
\newpage
\MakeOnePage{SMTS portfolio}{}{\withtrack{QF\_LinearRealArith}{\cloud}}{}
\newpage
\MakeOnePage{COLIBRI}{}{}{\withtrack{QF\_FP}{\unsat,\fast}, \withtrack{QF\_FPLRA}{\seq,\paral,\unsat,\fast}, \withtrack{QF\_ABVFPLRA}{\sat,\fast}}
\newpage
\MakeOnePage{UltimateEliminator+MathSAT}{}{\withtrack{Equality+MachineArith}{\inc}}{\withtrack{BVFPLRA}{\unsat}}
\newpage
\MakeOnePage{YicesQS}{}{\withtrack{Arith}{\sat,\fast}}{\withtrack{LRA}{\seq,\paral,\unsat}, \withtrack{NRA}{\seq,\paral,\unsat}}
\newpage
\MakeOnePage{-}{}{\withtrack{FPArith}{\uc\seq,\uc\paral}, \withtrack{QF\_Equality+LinearArith}{\cloud}}{\withtrack{AUFLIRA}{\sat,\cloud}, \withtrack{QF\_RDL}{\cloud}, \withtrack{UFDTNIA}{\sat}, \withtrack{AUFBVDTNIRA}{\sat}, \withtrack{UFDTNIRA}{\sat}, \withtrack{QF\_AUFBVFP}{\unsat}, \withtrack{AUFNIA}{\seq,\paral,\sat,\unsat,\fast,\uc\seq,\uc\paral}, \withtrack{UFDTLIA}{\sat,\cloud}, \withtrack{UFBVFP}{\sat}, \withtrack{QF\_NIRA}{\sat,\fast}, \withtrack{AUFBVDTNIA}{\sat}, \withtrack{QF\_SNIA}{\unsat}, \withtrack{AUFBVFP}{\sat}, \withtrack{QF\_LIRA}{\uc\seq,\uc\paral}, \withtrack{ABVFP}{\uc\seq,\uc\paral}, \withtrack{ABVFPLRA}{\uc\seq,\uc\paral}, \withtrack{QF\_UFDT}{\fast}, \withtrack{AUFFPDTNIRA}{\sat}, \withtrack{QF\_UFFP}{\uc\seq,\uc\paral}, \withtrack{UFBVLIA}{\sat,\fast}, \withtrack{AUFDTNIRA}{\sat,\cloud}, \withtrack{AUFDTLIRA}{\sat}, \withtrack{UFLRA}{\sat}}
\newpage
\MakeOnePage{cvc5-cloud}{}{}{\withtrack{UFDTNIRA}{\cloud}, \withtrack{QF\_IDL}{\cloud}, \withtrack{AUFDTLIRA}{\cloud}, \withtrack{NRA}{\cloud}, \withtrack{UFDTLIRA}{\cloud}}
\newpage
\MakeOnePage{smtinterpol}{\withtrack{Biggest Lead}{\inc}}{\withtrack{QF\_Equality+LinearArith}{\seq,\paral,\sat,\inc,\mv\seq,\mv\paral}, \withtrack{QF\_Equality+NonLinearArith}{\inc,\uc\seq,\uc\paral}, \withtrack{QF\_NonLinearIntArith}{\inc}, \withtrack{QF\_Datatypes}{\fast}}{\withtrack{QF\_AUFNIA}{\seq,\paral,\sat,\unsat,\fast}, \withtrack{ALIA}{\seq,\paral,\sat,\fast}, \withtrack{QF\_ANIA}{\seq,\paral,\sat,\unsat,\fast}, \withtrack{QF\_ALIA}{\uc\seq,\uc\paral}, \withtrack{UFLIA}{\sat}, \withtrack{QF\_UF}{\uc\paral}, \withtrack{AUFDTLIA}{\uc\seq,\uc\paral}, \withtrack{UFDTLIRA}{\uc\seq,\uc\paral}}
\newpage
\MakeOnePage{Q3B}{}{\withtrack{Bitvec}{\fast}}{}
\newpage
\MakeOnePage{veriT}{}{}{\withtrack{UFLIA}{\fast}, \withtrack{UFLRA}{\seq,\paral,\unsat,\fast}}
\newpage
\MakeOnePage{SMTS cube-and-conquer (fixed)}{}{\withtrack{QF\_LinearIntArith}{\cloud}}{}
\newpage
\MakeOnePage{Z3str4}{}{}{\withtrack{QF\_S}{\unsat}}
\newpage
\MakeOnePage{STP}{}{\withtrack{QF\_Bitvec}{\unsat,\fast}}{}
\newpage

### 2023-06-26 2023/certificates/compute_from_yaml.py

@@ -1,0 +1,159 @@
+#!/usr/bin/python3
+
+import sys
+import csv
+from typing import Any
+import frontmatter
+import os
+from collections import defaultdict
+ 
+
+    
+track= {
+    "track_incremental": "\\inc",   
+}
+
+class category(dict):
+    def latex(self):
+        l=[]
+        if self.get("sq_seq"): l.append("\\seq")
+        if self.get("sq_par"): l.append("\\paral")
+        if self.get("sq_sat"): l.append("\\sat")
+        if self.get("sq_unsat"): l.append("\\unsat")
+        if self.get("sq_24"): l.append("\\fast")
+        if self.get("inc"): l.append("\\inc")
+        if self.get("uc_seq"): l.append("\\uc\\seq")
+        if self.get("uc_par"): l.append("\\uc\\paral")
+        if self.get("mv_seq"): l.append("\\mv\\seq")
+        if self.get("mv_par"): l.append("\\mv\\paral")
+        if self.get("cloud"): l.append("\\cloud")
+        return ",".join(l)
+    
+    def isNotEmpty(self):
+        for _,v in self.items():
+            if v:
+                return True
+        return False
+    
+    def update (self, name, value) -> None:
+        if self.get(name,False) is None:
+            return
+        else:
+            self[name] = value
+
+
+def withtrack(l,name,category):
+    if category.isNotEmpty():
+      l.append("\\withtrack{{{name}}}{{{category}}}"\
+            .format(name=name.replace("_","\\_"),category=category.latex()))
+
+class overall:
+    
+    def __init__(self) -> None:
+        self.biggest = category()
+        self.largest = category()
+
+    def latex(self):
+        l=[]
+        withtrack(l,"Biggest Lead",self.biggest)
+        withtrack(l,"Largest Contribution",self.largest)
+        return ", ".join(l)
+    
+    def __str__(self):
+        return self.latex()
+
+class info:
+    def __init__(self) -> None:
+        self.overall = overall()
+        self.divisions = defaultdict(category)
+        self.logics = defaultdict(category)
+    
+    def latex(self,name):
+        l=[]
+        for (k,v) in self.divisions.items():
+            withtrack(l,k,v)
+        divisions = ", ".join(l)
+
+        l=[]
+        for (k,v) in self.logics.items():
+            withtrack(l,k,v)
+        logics = ", ".join(l)
+        
+        return "\\MakeOnePage{{{name}}}{{{overall}}}{{{divisions}}}{{{logics}}}"\
[…]

### 2023-06-27 2023/results/join.sh
Add fixed jobs

@@ -5,9 +5,9 @@ FORCE_DOWNLOAD=0
 
 # Jobs in the order "competition best-of non-competing"
 sq="59410 59554 59586 59599"
-inc="59572 59598"
-mv="59579 59619"
-uc="59592 59620"
+inc="59572 59598 59666"
+mv="59579 59619 59702"
+uc="59592 59620 59700"
 pe="59571"
 
 COLORDER=../../tools/process-results/unify_column_order.py

### 2023-06-27 2023/results/fix_starexec_custom_column.py
Use /usr/bin/env python3

@@ -1,4 +1,4 @@
-#!/bin/python3
+#!/usr/bin/env python3
 
 ## Some cell are in column with header "foo=bar" and value "baz" which should
 ## be in column "foo" with value "barbaz"

### 2023-06-27 2023/results/merge_local_results_mv.py
[Results] model validation fix fix results

@@ -29,6 +29,7 @@ def main():
             for row in reader:
                 key=(row["benchmark"],row["solver"],row["configuration"])
                 if not key in not_proved_locally:
+                    row["status"]="complete"
                     row["result"]="sat"
                     row["dolmenexit"]="0"
                     row["model_validator_error"]="-"

### 2023-06-27 2023/results/join.sh
Remove wrong quotes from mv input

@@ -28,9 +28,11 @@ for track in sq inc mv uc pe; do
         echo -n " Job${id}"
 
         if [ "$track" == "mv" ]; then
+            TMPINPUT_NOQUOTE=${TMPDIR}/input_noquote.csv
             TMPINPUT_FIXED=${TMPDIR}/input_fixed.csv
             echo -n "(fix column)"
-            ./fix_starexec_custom_column.py $INPUT $TMPINPUT_FIXED
+            tr -d '"' < $INPUT > $TMPINPUT_NOQUOTE
+            ./fix_starexec_custom_column.py $TMPINPUT_NOQUOTE $TMPINPUT_FIXED
             if [ -e ./fix-results-$id.csv.gz ]; then
                 TMPINPUT=${TMPDIR}/input_merged.csv
                 echo -n "(merge with fixed dolmen)"

### 2023-06-27 2023/prep/create-divisions.sh
Fix experimental mv tracks

@@ -34,6 +34,11 @@ for track in $TRACKS; do
     echo "\"track_$track\":{"
     COMMA2=""
     > logics/all
+    if [ "$track" = "model_validation" ];then
+        TRACKS_REGEX=divisions-regex-mv.txt
+    else
+        TRACKS_REGEX=divisions-regex.txt
+    fi
     while read division regex
     do
         if grep -E "^$regex$" < logics/track_${track} > logics/division; then
@@ -44,29 +49,7 @@ for track in $TRACKS; do
             cat logics/division >> logics/all
         fi
         rm -f logics/division
-    done <<EOF
-QF_Datatypes QF_(AX|UF|AUF)?DT
-QF_Equality QF_(AX|UF|AUF)
-QF_Equality+LinearArith QF_(A|UF|AUF)(DT)?(L[IR]*A|[IR]DL)
-QF_Equality+NonLinearArith QF_(A|UF|AUF)(DT)?(N[IR]*A)
-QF_Equality+Bitvec QF_(A|UF|AUF)(DT)?BV(DT)?
-QF_Equality+Bitvec+Arith QF_(A|UF|AUF)(DT)?BV(DT)?([NL][IR]*A)
-QF_LinearIntArith QF_(LIR?A|IDL)
-QF_LinearRealArith QF_(LRA|RDL)
-QF_Bitvec QF_BV
-QF_FPArith QF_(A|UF|AUF)?(BV)?FP(DT)?([NL][IR]*A)?
-QF_NonLinearIntArith QF_NIR?A
-QF_NonLinearRealArith QF_NRA
-QF_Strings QF_S.*
-Equality (AX?)?(UF)?(DT)?
-Equality+LinearArith (A|UF|AUF)(DT)?(L[IR]*A|[IR]DL)
-Equality+MachineArith (A|UF|AUF)(DT)?(BV|(BV)?FP)(DT)?([NL][IR]*A|[IR]DL)?
-Equality+NonLinearArith (A|UF|AUF)(DT)?(N[IR]*A)
-Arith ([LN][IR]*A|[IR]DL)
-Bitvec BV
-FPArith (BV)?FP(L[IR]*A|[IR]DL)?
-EOF
-
+    done < $TRACKS_REGEX
     echo '}'
     COMMA1=","
     # the following command checks whether each logic occurs exactly once.

### 2023-06-27 2023/scoring/make_mds.sh

@@ -6,6 +6,7 @@ YEAR=2023
 SCORE="$SCRIPTDIR/../../tools/scoring/score.py"
 SOLVERS_CSV="$SCRIPTDIR/../registration/solvers_divisions_all.csv"
 OUTPUT="$SCRIPTDIR/../../../smt-comp.github.io/_results_$YEAR"
+EXPERIMENTAL="$SCRIPTDIR/../experimental.csv"
 TIME=1200
 INC_NUM_CHECK_SAT="$SCRIPTDIR/../prep/SMT-LIB_incremental_benchmarks_num_check_sat.csv"
 
@@ -88,10 +89,11 @@ $PYTHON $SCORE -y $YEAR --csv results-sq.csv  -t $TIME --gen-md $OUTPUT -T sq -S
 $PYTHON $SCORE -y $YEAR --csv results-inc.csv -t $TIME --gen-md $OUTPUT -T inc -S $SOLVERS_CSV -i $INC_NUM_CHECK_SAT -D ../new-divisions.json
 [[ -n $GEN_UC ]] && echo UC && \
 $PYTHON $SCORE -y $YEAR --csv results-uc.csv  -t $TIME --gen-md $OUTPUT -T uc -S $SOLVERS_CSV -D ../new-divisions.json
+MV_EXPDIVS=$(grep ^model_validation $EXPERIMENTAL | cut -d , -f2)
 [[ -n $GEN_MV ]] && echo MV && \
 $PYTHON $SCORE -y $YEAR --csv results-mv.csv  -t $TIME \
     --gen-md $OUTPUT -T mv -S $SOLVERS_CSV -D ../new-divisions.json \
-    --expdivs QF_FPArith
+    --expdivs $(echo $MV_EXPDIVS | tr ' ' ',')
 [[ -n $GEN_PE ]] && echo PE && \
 $PYTHON $SCORE -y $YEAR --csv results-pe.csv  -t $TIME \
     --gen-md $OUTPUT -T pe -S $SOLVERS_CSV -D ../new-divisions.json \

### 2023-06-27 tools/selection/prepare_benchmark_ymls.py

@@ -68,7 +68,7 @@ def fillDivision(division_data, track, bm_files, noncomp_files):
             els = row.split('/')
             if len(els) == 1:
                 continue # empty line
-            division_data[logic2division[els[2]]][track][3][els[2]][0] += 1
+            division_data[logic2division[track][els[2]]][track][3][els[2]][0] += 1
     for noncomp_file in noncomp_files:
         noncomp_rows = open(noncomp_file).readlines()
         for logic in noncomp_rows:
@@ -77,10 +77,10 @@ def fillDivision(division_data, track, bm_files, noncomp_files):
                 if comment[1] in division_data:
                     # Comments where first word is a logic name comment
                     # on this track's logic
-                    division_data[logic2division[comment[1]]][track][3][comment[1]][2].append(logic[1:].strip())
+                    division_data[logic2division[track][comment[1]]][track][3][comment[1]][2].append(logic[1:].strip())
             else:
                 logic = logic.strip()
-                division_data[logic2division[logic]][track][0] = 'non-competitive'
+                division_data[logic2division[track][logic]][track][0] = 'non-competitive'
 
     for division in division_data:
       for track in division_data[division]:
@@ -246,6 +246,7 @@ if __name__ == '__main__':
             division_logics = { logic : [logic]
                                 for logic in division_info[track] }
 
+        logic2division[trackName] = {}
         for division,logics in division_logics.items():
             all_divisions += [division]
             if not division in division_data.keys():
@@ -254,7 +255,7 @@ if __name__ == '__main__':
             division_data[division][trackName] = ["competitive", 0, 0, {}]
             for logic in logics:
                 division_data[division][trackName][3][logic] = [0,0,[]]
-                logic2division[logic] = division
+                logic2division[trackName][logic] = division
     all_divisions = set(all_divisions)
 
     for tr in tracks:
@@ -268,9 +269,9 @@ if __name__ == '__main__':
 
             for row in reader:
                 drow = dict(zip(iter(header), iter(row)))
-                logic = drow['logic']
+                division = drow['division']
                 track = drow['track']
-                division_data[logic2division[logic]][track][0] = 'experimental'
+                division_data[division][track][0] = 'experimental'
 
     for division in all_divisions:
         printYaml(args.year, division, division_data[division], args.output_dir)

### 2023-06-29 tools/scoring/score.py
Use only the validator_result, except for 2020

@@ -466,7 +466,8 @@ def score(division,
     if model_validation:
         data_new['model_validator_status'] = data['model_validator_status']
         data_new['model_validator_error'] = data['model_validator_error']
-        data_new['model_validator_exception'] = data['model_validator_exception']
+        if int(year) == 2020:
+            data_new['model_validator_exception'] = data['model_validator_exception']
     # Column 'reason' only exists in proof exhibition track.
     proof_exhibition = 'reason' in data.columns
     if proof_exhibition:
@@ -554,8 +555,8 @@ def score(division,
             solved = solved[solved.result == RESULT_SAT]
             solved_valid = solved[solved.model_validator_status == 'VALID']
 
-            if int(year) <= 2019:
-                solved_invalid = solved[solved.model_validator_status == 'INVALID']
+            if int(year) != 2020:
+                solved_invalid = data_new[data_new.model_validator_status == 'INVALID']
             else:
                 # Note: The model validator does not report a result, even if
                 #       the solver produces an invalid model or the solver

### 2023-06-29 2023/results/find-disagreements.sh
Fix script to find disagreements

@@ -2,7 +2,7 @@
 
 #benchmark,solver,configuration,status,cpu time,wallclock time,memory usage,result,expected
 
-cat raw-results-sq.csv | cut -d, -f 1,8 | grep -v -e starexec-unknown -e '--' | sort |uniq | cut -d, -f1 |uniq -c |grep -v ' 1 '  | cut -c 9- > disagreeing-sq.txt
+cat raw-results-sq.csv | csvcut -c benchmark,result | grep -v -e starexec-unknown -e '--' | sort |uniq | cut -d, -f1 |uniq -c |grep -v ' 1 '  | cut -c 9- > disagreeing-sq.txt
 
 COMMA=""
 PATTERN=""
@@ -11,7 +11,7 @@ while read bench; do
     COMMA="|"
 done < disagreeing-sq.txt
 # remove the non informative result and select the problematic files
-cat raw-results-sq.csv | grep -v -e ",starexec-unknown," | grep -E "^($PATTERN)," | LANG=C sort -t, -k 1 | cut -d, -f 2,8
+cat raw-results-sq.csv | grep -v -e ",starexec-unknown," | grep -E ",($PATTERN)," | LANG=C sort -t, -k 1 | cut -d, -f2,4,12,13
 
 
 # Solver with answers different from the others

### 2023-06-29 2023/certificates/input_for_certificates.tex
certificates remove solver without members, experimental divisions

@@
-\MakeOnePage{Bitwuzla}{}{\withtrack{QF\_Equality+Bitvec}{\seq,\paral,\sat,\unsat,\fast,\uc\seq,\uc\paral,\mv\seq,\mv\paral}, \withtrack{QF\_FPArith}{\seq,\paral,\sat,\unsat,\fast,\inc,\uc\seq,\uc\paral,\mv\seq,\mv\paral}, \withtrack{QF\_Bitvec}{\seq,\paral,\sat,\uc\seq,\uc\paral,\mv\seq,\mv\paral}, \withtrack{FPArith}{\seq,\paral,\sat,\unsat,\fast,\inc}}{\withtrack{QF\_UFBV}{\inc}, \withtrack{AUFBV}{\seq,\paral,\unsat,\fast}, \withtrack{AUFBVFP}{\seq,\paral,\unsat,\fast}, \withtrack{UFBV}{\unsat,\fast}}
+\MakeOnePage{COLIBRI}{}{}{\withtrack{QF\_FP}{\unsat,\fast}, \withtrack{QF\_FPLRA}{\unsat,\fast}, \withtrack{QF\_ABVFPLRA}{\seq,\paral,\unsat,\fast}}
 \newpage
-\MakeOnePage{OpenSMT}{}{\withtrack{QF\_LinearIntArith}{\seq,\paral}, \withtrack{QF\_LinearRealArith}{\inc,\mv\seq,\mv\paral}}{\withtrack{QF\_LIA}{\unsat}, \withtrack{QF\_UFLIA}{\unsat}, \withtrack{QF\_LRA}{\seq,\paral,\unsat,\fast}}
+\MakeOnePage{Z3++}{\withtrack{Biggest Lead}{\mv}, \withtrack{Largest Contribution}{\mv}}{\withtrack{QF\_LinearIntArith}{\seq,\paral,\sat,\mv}, \withtrack{QF\_NonLinearIntArith}{\seq,\paral,\sat,\unsat,\fast}, \withtrack{QF\_NonLinearRealArith}{\seq,\paral,\sat}}{\withtrack{QF\_IDL}{\unsat}}
 \newpage
-\MakeOnePage{Z3++}{\withtrack{Biggest Lead}{\mv\seq,\mv\paral}, \withtrack{Largest Contribution}{\mv\seq,\mv\paral}}{\withtrack{QF\_LinearIntArith}{\sat,\mv\seq,\mv\paral}, \withtrack{QF\_NonLinearIntArith}{\unsat}, \withtrack{QF\_NonLinearRealArith}{\sat}}{\withtrack{QF\_IDL}{\seq,\paral,\unsat}}
+\MakeOnePage{OSTRICH}{}{}{\withtrack{QF\_S}{\seq,\paral,\unsat}}
 \newpage
-\MakeOnePage{cvc5}{\withtrack{Biggest Lead}{\seq,\paral,\sat,\unsat,\fast,\uc\seq,\uc\paral}, \withtrack{Largest Contribution}{\seq,\paral,\sat,\unsat,\fast,\inc,\uc\seq,\uc\paral}}{\withtrack{QF\_LinearIntArith}{\unsat}, \withtrack{QF\_Strings}{\seq,\paral,\sat,\unsat,\fast}, \withtrack{QF\_Datatypes}{\seq,\paral,\sat,\unsat,\uc\seq,\uc\paral}, \withtrack{Equality+MachineArith}{\seq,\paral,\sat,\unsat,\fast,\uc\seq,\uc\paral}, \withtrack{Equality}{\seq,\paral,\sat,\unsat,\inc,\uc\seq}, \withtrack{Equality+LinearArith}{\seq,\paral,\sat,\unsat,\fast,\inc,\uc\seq,\uc\paral}, \withtrack{Arith}{\seq,\paral,\unsat,\inc,\uc\seq,\uc\paral}, \withtrack{QF\_NonLinearIntArith}{\seq,\paral,\sat}, \withtrack{Bitvec}{\seq,\paral,\sat,\unsat,\inc,\uc\seq,\uc\paral}, \withtrack{QF\_Equality+NonLinearArith}{\seq,\paral,\sat,\unsat,\fast}, \withtrack{Equality+NonLinearArith}{\seq,\paral,\sat,\unsat,\fast,\inc,\uc\seq,\uc\paral}, \withtrack{QF\_NonLinearRealArith}{\seq,\paral,\unsat,\fast}, \withtrack{QF\_LinearRealArith}{\unsat}}{\withtrack{QF\_IDL}{\uc\seq,\uc\paral}, \withtrack{QF\_UFNIA}{\inc,\uc\seq,\uc\paral}, \withtrack{QF\_ABVFPLRA}{\seq,\paral,\unsat,\inc,\uc\seq,\uc\paral}, \withtrack{LIA}{\sat,\fast}, \withtrack{UFDT}{\fast}, \withtrack{QF\_UFLRA}{\uc\seq,\uc\paral}, \withtrack{QF\_BVFPLRA}{\unsat,\inc}, \withtrack{NIA}{\sat,\fast}, \withtrack{QF\_NIRA}{\unsat}, \withtrack{QF\_UFDTLIRA}{\seq,\paral,\sat,\unsat,\fast,\uc\seq,\uc\paral}, \withtrack{QF\_AUFLIA}{\uc\seq,\uc\paral}, \withtrack{QF\_UFNRA}{\inc,\uc\seq,\uc\paral}, \withtrack{BVFP}{\seq,\paral,\sat}}
+\MakeOnePage{SMTInterpol}{\withtrack{Biggest Lead}{\fast}}{\withtrack{QF\_Datatypes}{\fast,\uc\textsuperscript\paral}, \withtrack{QF\_Equality+LinearArith}{\seq,\paral,\sat,\inc,\mv}, \withtrack{QF\_NonLinearIntArith}{\inc}}{\withtrack{QF\_UFDT}{\uc\textsuperscript\seq}, \withtrack{QF\_UFDTLIA}{\unsat,\fast,\uc}, \withtrack{QF\_LIA}{\unsat}, \withtrack{QF\_AUFNIA}{\seq,\paral,\sat,\unsat,\fast,\uc}, \withtrack{ALIA}{\sat,\uc}, \withtrack{QF\_ANIA}{\seq,\paral,\sat,\unsat,\fast,\inc,\uc}, \withtrack{QF\_ALIA}{\uc}, \withtrack{UFLIA}{\sat}, \withtrack{QF\_UF}{\uc\textsuperscript\paral}, \withtrack{UFIDL}{\sat}, \withtrack{AUFDTLIA}{\uc}}
 \newpage
-\MakeOnePage{Yices2}{}{\withtrack{QF\_LinearIntArith}{\fast,\inc,\uc\seq,\uc\paral}, \withtrack{QF\_Bitvec}{\inc}, \withtrack{QF\_Equality}{\seq,\paral,\sat,\unsat,\fast,\inc,\uc\seq,\uc\paral,\mv\seq,\mv\paral}, \withtrack{QF\_LinearRealArith}{\seq,\paral,\sat,\fast,\uc\seq,\uc\paral}, \withtrack{QF\_NonLinearIntArith}{\fast}, \withtrack{QF\_Equality+LinearArith}{\unsat,\fast,\uc\seq,\uc\paral}, \withtrack{QF\_Equality+Bitvec}{\inc}}{\withtrack{QF\_LIRA}{\seq,\paral,\sat,\unsat,\mv\seq,\mv\paral}, \withtrack{QF\_UFNIA}{\sat}, \withtrack{QF\_UFLIA}{\seq,\paral,\sat,\inc,\mv\seq,\mv\paral}, \withtrack{QF\_UFLRA}{\seq,\paral,\inc,\mv\seq}, \withtrack{QF\_UFBV}{\sat}, \withtrack{QF\_UFIDL}{\seq,\paral}, \withtrack{QF\_RDL}{\unsat,\mv\seq,\mv\paral}, \withtrack{QF\_ALIA}{\seq,\paral,\sat}, \withtrack{QF\_AUFLIA}{\seq,\paral,\sat}, \withtrack{QF\_AUFBV}{\seq,\paral,\sat,\unsat,\fast,\uc\seq,\uc\paral}, \withtrack{QF\_UFNRA}{\seq,\paral,\sat,\unsat,\fast}}
+\MakeOnePage{Bitwuzla}{\withtrack{Biggest Lead}{\inc}}{\withtrack{QF\_Bitvec}{\inc}, \withtrack{QF\_FPArith}{\seq,\paral,\sat,\unsat,\fast,\inc}, \withtrack{FPArith}{\seq,\paral,\sat,\unsat,\fast,\inc,\uc}, \withtrack{QF\_Equality+Bitvec}{\seq,\paral,\sat,\unsat,\fast,\inc,\mv}, \withtrack{Equality+MachineArith}{\inc}, \withtrack{Bitvec}{\sat}}{\withtrack{QF\_ABVFPLRA}{\uc}, \withtrack{ABVFP}{\sat,\fast}, \withtrack{AUFBV}{\seq,\paral,\sat,\unsat,\fast}, \withtrack{QF\_ABVFP}{\uc}, \withtrack{QF\_BVFPLRA}{\uc}, \withtrack{QF\_BVFP}{\uc}, \withtrack{ABVFPLRA}{\fast}, \withtrack{UFBVFP}{\seq,\paral,\unsat}, \withtrack{AUFBVFP}{\seq,\paral,\sat,\unsat,\fast}, \withtrack{UFBV}{\seq,\paral,\sat,\unsat,\fast}}
 \newpage
-\MakeOnePage{Vampire}{\withtrack{Biggest Lead}{\cloud}}{\withtrack{Equality}{\fast,\uc\paral,\cloud}, \withtrack{Equality+NonLinearArith}{\cloud}, \withtrack{Arith}{\cloud}, \withtrack{Equality+LinearArith}{\cloud}}{\withtrack{AUFLIA}{\unsat,\fast}, \withtrack{UFLIA}{\uc\paral}, \withtrack{UF}{\seq,\paral,\sat}, \withtrack{UFDTNIA}{\seq,\paral,\unsat,\fast,\uc\seq,\uc\paral}, \withtrack{UFDTLIA}{\fast,\uc\seq,\uc\paral}, \withtrack{AUFNIRA}{\seq,\paral,\unsat,\fast,\uc\seq,\uc\paral}, \withtrack{UFNIA}{\uc\paral}, \withtrack{AUFLIRA}{\fast}}
+\MakeOnePage{Vampire}{}{\withtrack{Equality}{\fast}}{\withtrack{UFDTNIA}{\seq,\paral,\unsat,\fast,\uc}, \withtrack{AUFLIA}{\unsat,\fast}, \withtrack{ALIA}{\seq,\paral,\unsat,\fast}, \withtrack{UFDTLIA}{\fast,\uc}, \withtrack{AUFNIRA}{\paral,\unsat,\fast}, \withtrack{UF}{\seq,\paral,\sat}, \withtrack{AUFLIRA}{\fast}}
 \newpage
-\MakeOnePage{SMTS portfolio}{}{\withtrack{QF\_LinearRealArith}{\cloud}}{}
-\newpage
-\MakeOnePage{COLIBRI}{}{}{\withtrack{QF\_FP}{\unsat,\fast}, \withtrack{QF\_FPLRA}{\seq,\paral,\unsat,\fast}, \withtrack{QF\_ABVFPLRA}{\sat,\fast}}
-\newpage
-\MakeOnePage{UltimateEliminator+MathSAT}{}{\withtrack{Equality+MachineArith}{\inc}}{\withtrack{BVFPLRA}{\unsat}}
+\MakeOnePage{Yices2}{}{\withtrack{QF\_LinearIntArith}{\fast,\inc,\uc}, \withtrack{QF\_Equality+Bitvec}{\uc}, \withtrack{QF\_Equality}{\seq,\paral,\sat,\unsat,\fast,\uc,\mv}, \withtrack{QF\_LinearRealArith}{\seq,\paral,\fast,\uc}, \withtrack{QF\_Bitvec}{\uc}, \withtrack{QF\_Equality+LinearArith}{\fast,\uc}, \withtrack{QF\_Equality+NonLinearArith}{\sat}}{\withtrack{QF\_LIRA}{\seq,\paral,\sat,\unsat,\mv}, \withtrack{QF\_UFLIA}{\unsat,\inc}, \withtrack{QF\_AUFBV}{\fast}, \withtrack{QF\_AUFBVLIA}{\inc}, \withtrack{QF\_UFLRA}{\seq,\paral,\sat,\unsat,\inc,\mv}, \withtrack{QF\_UFNRA}{\seq,\paral,\unsat,\fast,\inc,\mv}, \withtrack{QF\_UFBVLIA}{\inc}, \withtrack{QF\_RDL}{\sat,\unsat,\mv}, \withtrack{QF\_ALIA}{\unsat}, \withtrack{QF\_AUFLIA}{\seq,\paral,\sat,\unsat}}
 \newpage
@@
 \newpage
-\MakeOnePage{-}{}{\withtrack{FPArith}{\uc\seq,\uc\paral}, \withtrack{QF\_Equality+LinearArith}{\cloud}}{\withtrack{AUFLIRA}{\sat,\cloud}, \withtrack{QF\_RDL}{\cloud}, \withtrack{UFDTNIA}{\sat}, \withtrack{AUFBVDTNIRA}{\sat}, \withtrack{UFDTNIRA}{\sat}, \withtrack{QF\_AUFBVFP}{\unsat}, \withtrack{AUFNIA}{\seq,\paral,\sat,\unsat,\fast,\uc\seq,\uc\paral}, \withtrack{UFDTLIA}{\sat,\cloud}, \withtrack{UFBVFP}{\sat}, \withtrack{QF\_NIRA}{\sat,\fast}, \withtrack{AUFBVDTNIA}{\sat}, \withtrack{QF\_SNIA}{\unsat}, \withtrack{AUFBVFP}{\sat}, \withtrack{QF\_LIRA}{\uc\seq,\uc\paral}, \withtrack{ABVFP}{\uc\seq,\uc\paral}, \withtrack{ABVFPLRA}{\uc\seq,\uc\paral}, \withtrack{QF\_UFDT}{\fast}, \withtrack{AUFFPDTNIRA}{\sat}, \withtrack{QF\_UFFP}{\uc\seq,\uc\paral}, \withtrack{UFBVLIA}{\sat,\fast}, \withtrack{AUFDTNIRA}{\sat,\cloud}, \withtrack{AUFDTLIRA}{\sat}, \withtrack{UFLRA}{\sat}}
-\newpage
-\MakeOnePage{cvc5-cloud}{}{}{\withtrack{UFDTNIRA}{\cloud}, \withtrack{QF\_IDL}{\cloud}, \withtrack{AUFDTLIRA}{\cloud}, \withtrack{NRA}{\cloud}, \withtrack{UFDTLIRA}{\cloud}}
-\newpage
-\MakeOnePage{smtinterpol}{\withtrack{Biggest Lead}{\inc}}{\withtrack{QF\_Equality+LinearArith}{\seq,\paral,\sat,\inc,\mv\seq,\mv\paral}, \withtrack{QF\_Equality+NonLinearArith}{\inc,\uc\seq,\uc\paral}, \withtrack{QF\_NonLinearIntArith}{\inc}, \withtrack{QF\_Datatypes}{\fast}}{\withtrack{QF\_AUFNIA}{\seq,\paral,\sat,\unsat,\fast}, \withtrack{ALIA}{\seq,\paral,\sat,\fast}, \withtrack{QF\_ANIA}{\seq,\paral,\sat,\unsat,\fast}, \withtrack{QF\_ALIA}{\uc\seq,\uc\paral}, \withtrack{UFLIA}{\sat}, \withtrack{QF\_UF}{\uc\paral}, \withtrack{AUFDTLIA}{\uc\seq,\uc\paral}, \withtrack{UFDTLIRA}{\uc\seq,\uc\paral}}
+\MakeOnePage{STP}{}{\withtrack{QF\_Bitvec}{\seq,\paral,\sat,\unsat,\fast,\mv}}{}
 \newpage
@@
 \newpage
-\MakeOnePage{veriT}{}{}{\withtrack{UFLIA}{\fast}, \withtrack{UFLRA}{\seq,\paral,\unsat,\fast}}
+\MakeOnePage{cvc5}{\withtrack{Biggest Lead}{\seq,\paral,\sat,\unsat,\uc}, \withtrack{Largest Contribution}{\seq,\paral,\sat,\unsat,\fast,\inc,\uc}}{\withtrack{QF\_LinearIntArith}{\unsat}, \withtrack{QF\_Strings}{\seq,\paral,\sat,\unsat}, \withtrack{QF\_Datatypes}{\seq,\paral,\sat,\unsat,\uc\textsuperscript\seq}, \withtrack{Equality+MachineArith}{\seq,\paral,\sat,\unsat,\fast,\uc}, \withtrack{Equality}{\seq,\paral,\sat,\unsat,\inc,\uc}, \withtrack{Equality+LinearArith}{\seq,\paral,\sat,\unsat,\fast,\inc,\uc}, \withtrack{Arith}{\seq,\paral,\unsat,\inc,\uc}, \withtrack{QF\_Equality+NonLinearArith}{\seq,\paral,\unsat,\fast,\inc,\uc}, \withtrack{Bitvec}{\seq,\paral,\unsat,\inc,\uc}, \withtrack{QF\_Equality+Bitvec+Arith}{\inc}, \withtrack{Equality+NonLinearArith}{\seq,\paral,\sat,\unsat,\fast,\inc,\uc}, \withtrack{QF\_FPArith}{\uc}, \withtrack{QF\_NonLinearRealArith}{\unsat,\fast}, \withtrack{QF\_Equality}{\inc}, \withtrack{QF\_LinearRealArith}{\unsat}}{\withtrack{QF\_FP}{\sat,\mv}, \withtrack{QF\_IDL}{\uc}, \withtrack{QF\_UFNIA}{\sat}, \withtrack{LIA}{\sat,\fast}, \withtrack{UFDT}{\fast}, \withtrack{QF\_UFLRA}{\uc}, \withtrack{NIA}{\sat,\fast}, \withtrack{QF\_UFDTLIRA}{\seq,\paral,\sat,\unsat,\fast,\uc}, \withtrack{QF\_ALIA}{\inc}, \withtrack{QF\_NIRA}{\seq,\paral,\unsat}, \withtrack{QF\_UFBVDT}{\seq,\paral,\sat,\unsat,\fast}, \withtrack{QF\_AUFLIA}{\uc,\mv}, \withtrack{QF\_BVFPLRA}{\inc}, \withtrack{QF\_AX}{\mv}}
 \newpage
-\MakeOnePage{SMTS cube-and-conquer (fixed)}{}{\withtrack{QF\_LinearIntArith}{\cloud}}{}
+\MakeOnePage{OpenSMT}{}{\withtrack{QF\_LinearRealArith}{\sat,\inc,\mv}, \withtrack{QF\_Equality+LinearArith}{\unsat}}{\withtrack{QF\_LIA}{\seq,\paral}, \withtrack{QF\_LRA}{\seq,\paral,\unsat,\fast}, \withtrack{QF\_UFIDL}{\seq,\paral,\sat,\mv}}
 \newpage
-\MakeOnePage{Z3str4}{}{}{\withtrack{QF\_S}{\unsat}}
+\MakeOnePage{z3-alpha}{}{\withtrack{QF\_Strings}{\fast}}{\withtrack{QF\_S}{\sat}, \withtrack{QF\_SNIA}{\seq,\paral,\sat}}
 \newpage
-\MakeOnePage{STP}{}{\withtrack{QF\_Bitvec}{\unsat,\fast}}{}
+\MakeOnePage{iProver}{}{}{\withtrack{ANIA}{\unsat}}
 \newpage

### 2023-06-29 2023/certificates/compute_from_yaml.py

@@ -22,11 +22,16 @@ class category(dict):
         if self.get("sq_unsat"): l.append("\\unsat")
         if self.get("sq_24"): l.append("\\fast")
         if self.get("inc"): l.append("\\inc")
-        if self.get("uc_seq"): l.append("\\uc\\seq")
-        if self.get("uc_par"): l.append("\\uc\\paral")
-        if self.get("mv_seq"): l.append("\\mv\\seq")
-        if self.get("mv_par"): l.append("\\mv\\paral")
+        if self.get("uc_seq") and self.get("uc_par"): l.append("\\uc")
+        else:
+            if self.get("uc_seq"): l.append("\\uc\\textsuperscript\\seq")
+            if self.get("uc_par"): l.append("\\uc\\textsuperscript\\paral")
+        if self.get("mv_seq") and self.get("mv_par"): l.append("\\mv")
+        else:
+            if self.get("mv_seq"): l.append("\\mv\\seq")
+            if self.get("mv_par"): l.append("\\mv\\paral")
         if self.get("cloud"): l.append("\\cloud")
+        if self.get("parallel"): l.append("\\paralTrack")
         return ",".join(l)
     
     def isNotEmpty(self):
@@ -61,6 +66,9 @@ class overall:
     
     def __str__(self):
         return self.latex()
+    
+    def isNotEmpty(self):
+        return self.biggest.isNotEmpty() and self.largest.isNotEmpty()
 
 class info:
     def __init__(self) -> None:
@@ -81,6 +89,11 @@ class info:
         
         return "\\MakeOnePage{{{name}}}{{{overall}}}{{{divisions}}}{{{logics}}}"\
             .format(name=name,overall=self.overall.latex(),divisions=divisions,logics=logics)
+    
+    def isNotEmpty(self):
+        return self.overall.isNotEmpty() \
+        or any(cat.isNotEmpty() for _,cat in self.divisions.items()) \
+        or any(cat.isNotEmpty() for _,cat in self.logics.items())
     
     def __str__(self) -> str:
         return str(self.overall)
@@ -107,8 +120,12 @@ def update(solvers,select,yaml):
         select(solvers[yaml["winner_par"]],"mv_par")
         select(solvers[yaml["winner_seq"]],"mv_seq")
     
-    if yaml["track"] == "track_cloud":
-        select(solvers[yaml["winner_par"]],"cloud")
+    # if yaml["track"] == "track_cloud":
[…]

### 2023-06-29 2023/results/join.sh

@@ -1,4 +1,4 @@
-#!/bin/bash
+#!/bin/bash -eu
 
 # Download Jobs from StarExec even if they already exist
 FORCE_DOWNLOAD=0
@@ -24,6 +24,7 @@ for track in sq inc mv uc pe; do
             curl -o Job${id}_info.zip "https://www.starexec.org/starexec/secure/download?type=job&id=${id}&returnids=true&getcompleted=false"
             unzip Job${id}_info.zip
         fi
+        test -d "Job${id}"
         INPUT="Job${id}/Job${id}_info.csv"
         echo -n " Job${id}"
 
@@ -50,7 +51,7 @@ for track in sq inc mv uc pe; do
 
             # sanity check: head must be equal now
             diff <(head -1 $TMPFILE) <(head -1 $OUTPUT)
-            eval tail -n +2 $TMPFILE $FILTER >> $OUTPUT
+            eval tail -n +2 $TMPFILE >> $OUTPUT
             rm $TMPFILE
         else
             # convert all files to same line ending

### 2023-06-29 2023/certificates/gen_certificates_ornament.tex
certificates remove solver without members, experimental divisions
remove experimental logic

@@
 \usepackage{ulem}
+\usepackage{graphicx}
 \usepackage{etoolbox}
@@
 \usetikzlibrary{decorations.text,decorations.markings}
-\usetikzlibrary {decorations.pathmorphing,shadows}
+\usetikzlibrary{decorations.pathmorphing,shadows}
 
 \usepackage{geometry}
-\geometry{hmargin=1in,vmargin=0.8in,headheight=10pt}
+\geometry{hmargin=1in,vmargin=0.8in,headheight=25pt}
 
@@
 \newcommand{\inc}{inc}
-\newcommand{\uc}{uc\textsuperscript}
-\newcommand{\mv}{mv\textsuperscript}
+\newcommand{\uc}{uc}
+\newcommand{\mv}{mv}
 \newcommand{\cloud}{cloud}
-\newcommand{\all}{{\footnotesize (\seq,\paral,\sat,\unsat,\fast,\inc,\uc\seq,\uc\paral,\mv)}}
+\newcommand{\paralTrack}{parallel}
+%\newcommand{\all}{{\footnotesize (\seq,\paral,\sat,\unsat,\fast,\inc,\uc\seq,\uc\paral,\mv)}}
 \newcommand{\withtrack}[2]{\textsc{#1}{{\footnotesize (#2)}}}
@@
     \textcolor{red!30!black!90}
-    {\textit{Certificate for overall performance}}
+    {\textit{Solver won overall}}
 
@@
     \ifstrempty{#3}{}{
-    \textcolor{red!30!black!90} {\textit{Certificate for divisions}}
+    \textcolor{red!30!black!90} {\textit{Solver won division}}
 
@@
     \ifstrempty{#4}{}{
-     \textcolor{red!30!black!90}  {\textit{Certificate for logic}}
+     \textcolor{red!30!black!90}  {\textit{Solver won logic \ifstrempty{#3}{}{(but not the corresponding division)}}}
 
@@
     {\color{blue!40!black}
-    \scalebox{.7}{
+%    \scalebox{.7}{
+    {\tiny
     \begin{tabular}{ccccc}
+        \includegraphics[scale=0.5]{signature-blank-crop-jochen.pdf} && && \includegraphics{MB-Signature.png} \\
     \cline{1-1} 

### 2023-06-29 2023/certificates/input_for_certificates.tex
remove experimental logic

@@
-\MakeOnePage{COLIBRI}{}{}{\withtrack{QF\_FP}{\unsat,\fast}, \withtrack{QF\_FPLRA}{\unsat,\fast}, \withtrack{QF\_ABVFPLRA}{\seq,\paral,\unsat,\fast}}
+\MakeOnePage{COLIBRI}{}{}{\withtrack{QF\_ABVFPLRA}{\seq,\paral,\unsat,\fast}, \withtrack{QF\_FP}{\unsat,\fast}, \withtrack{QF\_FPLRA}{\unsat,\fast}}
 \newpage
@@
 \newpage
-\MakeOnePage{SMTInterpol}{\withtrack{Biggest Lead}{\fast}}{\withtrack{QF\_Datatypes}{\fast,\uc\textsuperscript\paral}, \withtrack{QF\_Equality+LinearArith}{\seq,\paral,\sat,\inc,\mv}, \withtrack{QF\_NonLinearIntArith}{\inc}}{\withtrack{QF\_UFDT}{\uc\textsuperscript\seq}, \withtrack{QF\_UFDTLIA}{\unsat,\fast,\uc}, \withtrack{QF\_LIA}{\unsat}, \withtrack{QF\_AUFNIA}{\seq,\paral,\sat,\unsat,\fast,\uc}, \withtrack{ALIA}{\sat,\uc}, \withtrack{QF\_ANIA}{\seq,\paral,\sat,\unsat,\fast,\inc,\uc}, \withtrack{QF\_ALIA}{\uc}, \withtrack{UFLIA}{\sat}, \withtrack{QF\_UF}{\uc\textsuperscript\paral}, \withtrack{UFIDL}{\sat}, \withtrack{AUFDTLIA}{\uc}}
+\MakeOnePage{SMTInterpol}{\withtrack{Biggest Lead}{\fast}}{\withtrack{QF\_Datatypes}{\fast,\uc\textsuperscript\paral}, \withtrack{QF\_Equality+LinearArith}{\seq,\paral,\sat,\inc,\mv}, \withtrack{QF\_NonLinearIntArith}{\inc}}{\withtrack{ALIA}{\sat,\uc}, \withtrack{AUFDTLIA}{\uc}, \withtrack{QF\_ALIA}{\uc}, \withtrack{QF\_ANIA}{\seq,\paral,\sat,\unsat,\fast,\inc,\uc}, \withtrack{QF\_AUFNIA}{\seq,\paral,\sat,\unsat,\fast,\uc}, \withtrack{QF\_LIA}{\unsat}, \withtrack{QF\_UF}{\uc\textsuperscript\paral}, \withtrack{QF\_UFDT}{\uc\textsuperscript\seq}, \withtrack{QF\_UFDTLIA}{\unsat,\fast,\uc}, \withtrack{UFIDL}{\sat}, \withtrack{UFLIA}{\sat}}
 \newpage
-\MakeOnePage{Bitwuzla}{\withtrack{Biggest Lead}{\inc}}{\withtrack{QF\_Bitvec}{\inc}, \withtrack{QF\_FPArith}{\seq,\paral,\sat,\unsat,\fast,\inc}, \withtrack{FPArith}{\seq,\paral,\sat,\unsat,\fast,\inc,\uc}, \withtrack{QF\_Equality+Bitvec}{\seq,\paral,\sat,\unsat,\fast,\inc,\mv}, \withtrack{Equality+MachineArith}{\inc}, \withtrack{Bitvec}{\sat}}{\withtrack{QF\_ABVFPLRA}{\uc}, \withtrack{ABVFP}{\sat,\fast}, \withtrack{AUFBV}{\seq,\paral,\sat,\unsat,\fast}, \withtrack{QF\_ABVFP}{\uc}, \withtrack{QF\_BVFPLRA}{\uc}, \withtrack{QF\_BVFP}{\uc}, \withtrack{ABVFPLRA}{\fast}, \withtrack{UFBVFP}{\seq,\paral,\unsat}, \withtrack{AUFBVFP}{\seq,\paral,\sat,\unsat,\fast}, \withtrack{UFBV}{\seq,\paral,\sat,\unsat,\fast}}
+\MakeOnePage{Bitwuzla}{\withtrack{Biggest Lead}{\inc}}{\withtrack{Bitvec}{\sat}, \withtrack{Equality+MachineArith}{\inc}, \withtrack{FPArith}{\seq,\paral,\sat,\unsat,\fast,\inc,\uc}, \withtrack{QF\_Bitvec}{\inc}, \withtrack{QF\_Equality+Bitvec}{\seq,\paral,\sat,\unsat,\fast,\inc,\mv}, \withtrack{QF\_FPArith}{\seq,\paral,\sat,\unsat,\fast,\inc}}{\withtrack{ABVFP}{\sat,\fast}, \withtrack{ABVFPLRA}{\fast}, \withtrack{AUFBV}{\seq,\paral,\sat,\unsat,\fast}, \withtrack{AUFBVFP}{\seq,\paral,\sat,\unsat,\fast}, \withtrack{QF\_ABVFP}{\uc}, \withtrack{QF\_ABVFPLRA}{\uc}, \withtrack{QF\_BVFP}{\uc}, \withtrack{QF\_BVFPLRA}{\uc}, \withtrack{UFBV}{\seq,\paral,\sat,\unsat,\fast}, \withtrack{UFBVFP}{\seq,\paral,\unsat}}
 \newpage
-\MakeOnePage{Vampire}{}{\withtrack{Equality}{\fast}}{\withtrack{UFDTNIA}{\seq,\paral,\unsat,\fast,\uc}, \withtrack{AUFLIA}{\unsat,\fast}, \withtrack{ALIA}{\seq,\paral,\unsat,\fast}, \withtrack{UFDTLIA}{\fast,\uc}, \withtrack{AUFNIRA}{\paral,\unsat,\fast}, \withtrack{UF}{\seq,\paral,\sat}, \withtrack{AUFLIRA}{\fast}}
+\MakeOnePage{Vampire}{}{\withtrack{Equality}{\fast}}{\withtrack{ALIA}{\seq,\paral,\unsat,\fast}, \withtrack{AUFLIA}{\unsat,\fast}, \withtrack{AUFLIRA}{\fast}, \withtrack{AUFNIRA}{\paral,\unsat,\fast}, \withtrack{UF}{\seq,\paral,\sat}, \withtrack{UFDTLIA}{\fast,\uc}, \withtrack{UFDTNIA}{\seq,\paral,\unsat,\fast,\uc}}
 \newpage
-\MakeOnePage{Yices2}{}{\withtrack{QF\_LinearIntArith}{\fast,\inc,\uc}, \withtrack{QF\_Equality+Bitvec}{\uc}, \withtrack{QF\_Equality}{\seq,\paral,\sat,\unsat,\fast,\uc,\mv}, \withtrack{QF\_LinearRealArith}{\seq,\paral,\fast,\uc}, \withtrack{QF\_Bitvec}{\uc}, \withtrack{QF\_Equality+LinearArith}{\fast,\uc}, \withtrack{QF\_Equality+NonLinearArith}{\sat}}{\withtrack{QF\_LIRA}{\seq,\paral,\sat,\unsat,\mv}, \withtrack{QF\_UFLIA}{\unsat,\inc}, \withtrack{QF\_AUFBV}{\fast}, \withtrack{QF\_AUFBVLIA}{\inc}, \withtrack{QF\_UFLRA}{\seq,\paral,\sat,\unsat,\inc,\mv}, \withtrack{QF\_UFNRA}{\seq,\paral,\unsat,\fast,\inc,\mv}, \withtrack{QF\_UFBVLIA}{\inc}, \withtrack{QF\_RDL}{\sat,\unsat,\mv}, \withtrack{QF\_ALIA}{\unsat}, \withtrack{QF\_AUFLIA}{\seq,\paral,\sat,\unsat}}
+\MakeOnePage{Yices2}{}{\withtrack{QF\_Bitvec}{\uc}, \withtrack{QF\_Equality}{\seq,\paral,\sat,\unsat,\fast,\uc,\mv}, \withtrack{QF\_Equality+Bitvec}{\uc}, \withtrack{QF\_Equality+LinearArith}{\fast,\uc}, \withtrack{QF\_Equality+NonLinearArith}{\sat}, \withtrack{QF\_LinearIntArith}{\fast,\inc,\uc}, \withtrack{QF\_LinearRealArith}{\seq,\paral,\fast,\uc}}{\withtrack{QF\_ALIA}{\unsat}, \withtrack{QF\_AUFBV}{\fast}, \withtrack{QF\_AUFBVLIA}{\inc}, \withtrack{QF\_AUFLIA}{\seq,\paral,\sat,\unsat}, \withtrack{QF\_LIRA}{\seq,\paral,\sat,\unsat,\mv}, \withtrack{QF\_RDL}{\sat,\unsat,\mv}, \withtrack{QF\_UFBVLIA}{\inc}, \withtrack{QF\_UFLIA}{\unsat,\inc}, \withtrack{QF\_UFLRA}{\seq,\paral,\sat,\unsat,\inc,\mv}, \withtrack{QF\_UFNRA}{\seq,\paral,\unsat,\fast,\inc}}
 \newpage
@@
 \newpage
-\MakeOnePage{cvc5}{\withtrack{Biggest Lead}{\seq,\paral,\sat,\unsat,\uc}, \withtrack{Largest Contribution}{\seq,\paral,\sat,\unsat,\fast,\inc,\uc}}{\withtrack{QF\_LinearIntArith}{\unsat}, \withtrack{QF\_Strings}{\seq,\paral,\sat,\unsat}, \withtrack{QF\_Datatypes}{\seq,\paral,\sat,\unsat,\uc\textsuperscript\seq}, \withtrack{Equality+MachineArith}{\seq,\paral,\sat,\unsat,\fast,\uc}, \withtrack{Equality}{\seq,\paral,\sat,\unsat,\inc,\uc}, \withtrack{Equality+LinearArith}{\seq,\paral,\sat,\unsat,\fast,\inc,\uc}, \withtrack{Arith}{\seq,\paral,\unsat,\inc,\uc}, \withtrack{QF\_Equality+NonLinearArith}{\seq,\paral,\unsat,\fast,\inc,\uc}, \withtrack{Bitvec}{\seq,\paral,\unsat,\inc,\uc}, \withtrack{QF\_Equality+Bitvec+Arith}{\inc}, \withtrack{Equality+NonLinearArith}{\seq,\paral,\sat,\unsat,\fast,\inc,\uc}, \withtrack{QF\_FPArith}{\uc}, \withtrack{QF\_NonLinearRealArith}{\unsat,\fast}, \withtrack{QF\_Equality}{\inc}, \withtrack{QF\_LinearRealArith}{\unsat}}{\withtrack{QF\_FP}{\sat,\mv}, \withtrack{QF\_IDL}{\uc}, \withtrack{QF\_UFNIA}{\sat}, \withtrack{LIA}{\sat,\fast}, \withtrack{UFDT}{\fast}, \withtrack{QF\_UFLRA}{\uc}, \withtrack{NIA}{\sat,\fast}, \withtrack{QF\_UFDTLIRA}{\seq,\paral,\sat,\unsat,\fast,\uc}, \withtrack{QF\_ALIA}{\inc}, \withtrack{QF\_NIRA}{\seq,\paral,\unsat}, \withtrack{QF\_UFBVDT}{\seq,\paral,\sat,\unsat,\fast}, \withtrack{QF\_AUFLIA}{\uc,\mv}, \withtrack{QF\_BVFPLRA}{\inc}, \withtrack{QF\_AX}{\mv}}
+\MakeOnePage{cvc5}{\withtrack{Biggest Lead}{\seq,\paral,\sat,\unsat,\uc}, \withtrack{Largest Contribution}{\seq,\paral,\sat,\unsat,\fast,\inc,\uc}}{\withtrack{Arith}{\seq,\paral,\unsat,\inc,\uc}, \withtrack{Bitvec}{\seq,\paral,\unsat,\inc,\uc}, \withtrack{Equality}{\seq,\paral,\sat,\unsat,\inc,\uc}, \withtrack{Equality+LinearArith}{\seq,\paral,\sat,\unsat,\fast,\inc,\uc}, \withtrack{Equality+MachineArith}{\seq,\paral,\sat,\unsat,\fast,\uc}, \withtrack{Equality+NonLinearArith}{\seq,\paral,\sat,\unsat,\fast,\inc,\uc}, \withtrack{QF\_Datatypes}{\seq,\paral,\sat,\unsat,\uc\textsuperscript\seq}, \withtrack{QF\_Equality}{\inc}, \withtrack{QF\_Equality+Bitvec+Arith}{\inc}, \withtrack{QF\_Equality+NonLinearArith}{\seq,\paral,\unsat,\fast,\inc,\uc}, \withtrack{QF\_FPArith}{\uc}, \withtrack{QF\_LinearIntArith}{\unsat}, \withtrack{QF\_LinearRealArith}{\unsat}, \withtrack{QF\_NonLinearRealArith}{\unsat,\fast}, \withtrack{QF\_Strings}{\seq,\paral,\sat,\unsat}}{\withtrack{LIA}{\sat,\fast}, \withtrack{NIA}{\sat,\fast}, \withtrack{QF\_ALIA}{\inc}, \withtrack{QF\_AUFLIA}{\uc}, \withtrack{QF\_BVFPLRA}{\inc}, \withtrack{QF\_FP}{\sat}, \withtrack{QF\_IDL}{\uc}, \withtrack{QF\_NIRA}{\seq,\paral,\unsat}, \withtrack{QF\_UFBVDT}{\seq,\paral,\sat,\unsat,\fast}, \withtrack{QF\_UFDTLIRA}{\seq,\paral,\sat,\unsat,\fast,\uc}, \withtrack{QF\_UFLRA}{\uc}, \withtrack{QF\_UFNIA}{\sat}, \withtrack{UFDT}{\fast}}
 \newpage
-\MakeOnePage{OpenSMT}{}{\withtrack{QF\_LinearRealArith}{\sat,\inc,\mv}, \withtrack{QF\_Equality+LinearArith}{\unsat}}{\withtrack{QF\_LIA}{\seq,\paral}, \withtrack{QF\_LRA}{\seq,\paral,\unsat,\fast}, \withtrack{QF\_UFIDL}{\seq,\paral,\sat,\mv}}
+\MakeOnePage{OpenSMT}{}{\withtrack{QF\_Equality+LinearArith}{\unsat}, \withtrack{QF\_LinearRealArith}{\sat,\inc,\mv}}{\withtrack{QF\_LIA}{\seq,\paral}, \withtrack{QF\_LRA}{\seq,\paral,\unsat,\fast}, \withtrack{QF\_UFIDL}{\seq,\paral,\sat,\mv}}
 \newpage

### 2023-06-29 2023/certificates/compute_from_yaml.py

@@ -78,12 +78,12 @@ class info:
     
     def latex(self,name):
         l=[]
-        for (k,v) in self.divisions.items():
+        for (k,v) in sorted(self.divisions.items()):
             withtrack(l,k,v)
         divisions = ", ".join(l)
 
         l=[]
-        for (k,v) in self.logics.items():
+        for (k,v) in sorted(self.logics.items()):
             withtrack(l,k,v)
         logics = ", ".join(l)
         
@@ -134,6 +134,11 @@ def select_division(division,logics):
         solver.divisions[division].update(track,True)
     return select
 
+def add_logic(logics,list,track):
+    for v,_ in list[0].items():
+        logics[v,track] = True
+    
+
 def parse_pretty_names(solvers,pretty_names):
     with open(pretty_names, newline='') as input:
         input = csv.DictReader(input)
@@ -141,23 +146,30 @@ def parse_pretty_names(solvers,pretty_names):
         for row in input:
             solvers[row["Solver Name"]].members = int(row["Members"])
 
-def remove_experimental_division(solvers,experimental_division):
+def parse_experimental_division(solvers,experimental_division):
+    res={}
     with open(experimental_division, newline='') as input:
-        input = list(csv.DictReader(input))
+        input = csv.DictReader(input)
         
-        for _,solver in solvers.items():
-            for row in input:
-                assert (row["track"] == "model_validation")
-                solver.divisions[row["division"]]["mv_par"] = None
-                solver.divisions[row["division"]]["mv_seq"] = None
+        for row in input:
+            res[(row["division"],"track_"+row["track"])] = True
+    return res
 
 def main(website_results,input_for_certificates,pretty_names,experimental_division):
     solvers=defaultdict(info)
     
     parse_pretty_names(solvers,pretty_names)
     solvers["-"].members = 0
+    
+    # Remove experimental division
+    experimental_divisions=parse_experimental_division(solvers,experimental_division)
+
+    existing_logics={}
+    delayed_logic=[] #we wait to know which logic are competitive
  
-    for result in os.listdir(website_results):
+    list_dir = list(os.listdir(website_results))
+    list_dir.sort()
+    for result in list_dir:
         file = os.path.join(website_results,result)
         if not os.path.isfile(file):
             break
@@ -177,13 +189,20 @@ def main(website_results,input_for_certificates,pretty_names,experimental_divisi
             
         else:          
             if "logics" in result:
[…]

### 2023-06-29 2023/certificates/gen_certificates_ornament.tex
reword the certificate

@@
 
-\newcommand{\MakeOnePage}[4]{
+\newcommand{\MakeOnePage}[6]{
     {\centering
@@
     \textcolor{red!30!black!90}
-    {\textit{Solver won overall}}
+    {\textit{Overall Winner}}
 
@@
     \ifstrempty{#3}{}{
-    \textcolor{red!30!black!90} {\textit{Solver won division}}
+    \textcolor{red!30!black!90} {\textit{Winner of the Division#5}}
 
@@
     \ifstrempty{#4}{}{
-     \textcolor{red!30!black!90}  {\textit{Solver won logic \ifstrempty{#3}{}{(but not the corresponding division)}}}
+     \textcolor{red!30!black!90}  {\textit{Winner of the Logic#6
+      \ifstrempty{#3}{}{(where it did not win the corresponding division)}}}
 

### 2023-06-29 2023/certificates/input_for_certificates.tex
reword the certificate

@@
-\MakeOnePage{COLIBRI}{}{}{\withtrack{QF\_ABVFPLRA}{\seq,\paral,\unsat,\fast}, \withtrack{QF\_FP}{\unsat,\fast}, \withtrack{QF\_FPLRA}{\unsat,\fast}}
+\MakeOnePage{COLIBRI}{}{}{\withtrack{QF\_ABVFPLRA}{\seq,\paral,\unsat,\fast}, \withtrack{QF\_FP}{\unsat,\fast}, \withtrack{QF\_FPLRA}{\unsat,\fast}}{}{s}
 \newpage
-\MakeOnePage{Z3++}{\withtrack{Biggest Lead}{\mv}, \withtrack{Largest Contribution}{\mv}}{\withtrack{QF\_LinearIntArith}{\seq,\paral,\sat,\mv}, \withtrack{QF\_NonLinearIntArith}{\seq,\paral,\sat,\unsat,\fast}, \withtrack{QF\_NonLinearRealArith}{\seq,\paral,\sat}}{\withtrack{QF\_IDL}{\unsat}}
+\MakeOnePage{Z3++}{\withtrack{Biggest Lead}{\mv}, \withtrack{Largest Contribution}{\mv}}{\withtrack{QF\_LinearIntArith}{\seq,\paral,\sat,\mv}, \withtrack{QF\_NonLinearIntArith}{\seq,\paral,\sat,\unsat,\fast}, \withtrack{QF\_NonLinearRealArith}{\seq,\paral,\sat}}{\withtrack{QF\_IDL}{\unsat}}{s}{}
 \newpage
-\MakeOnePage{OSTRICH}{}{}{\withtrack{QF\_S}{\seq,\paral,\unsat}}
+\MakeOnePage{OSTRICH}{}{}{\withtrack{QF\_S}{\seq,\paral,\unsat}}{}{}
 \newpage
-\MakeOnePage{SMTInterpol}{\withtrack{Biggest Lead}{\fast}}{\withtrack{QF\_Datatypes}{\fast,\uc\textsuperscript\paral}, \withtrack{QF\_Equality+LinearArith}{\seq,\paral,\sat,\inc,\mv}, \withtrack{QF\_NonLinearIntArith}{\inc}}{\withtrack{ALIA}{\sat,\uc}, \withtrack{AUFDTLIA}{\uc}, \withtrack{QF\_ALIA}{\uc}, \withtrack{QF\_ANIA}{\seq,\paral,\sat,\unsat,\fast,\inc,\uc}, \withtrack{QF\_AUFNIA}{\seq,\paral,\sat,\unsat,\fast,\uc}, \withtrack{QF\_LIA}{\unsat}, \withtrack{QF\_UF}{\uc\textsuperscript\paral}, \withtrack{QF\_UFDT}{\uc\textsuperscript\seq}, \withtrack{QF\_UFDTLIA}{\unsat,\fast,\uc}, \withtrack{UFIDL}{\sat}, \withtrack{UFLIA}{\sat}}
+\MakeOnePage{SMTInterpol}{\withtrack{Biggest Lead}{\fast}}{\withtrack{QF\_Datatypes}{\fast,\uc\textsuperscript\paral}, \withtrack{QF\_Equality+LinearArith}{\seq,\paral,\sat,\inc,\mv}, \withtrack{QF\_NonLinearIntArith}{\inc}}{\withtrack{ALIA}{\sat,\uc}, \withtrack{AUFDTLIA}{\uc}, \withtrack{QF\_ALIA}{\uc}, \withtrack{QF\_ANIA}{\seq,\paral,\sat,\unsat,\fast,\inc,\uc}, \withtrack{QF\_AUFNIA}{\seq,\paral,\sat,\unsat,\fast,\uc}, \withtrack{QF\_LIA}{\unsat}, \withtrack{QF\_UF}{\uc\textsuperscript\paral}, \withtrack{QF\_UFDT}{\uc\textsuperscript\seq}, \withtrack{QF\_UFDTLIA}{\unsat,\fast,\uc}, \withtrack{UFIDL}{\sat}, \withtrack{UFLIA}{\sat}}{s}{s}
 \newpage
-\MakeOnePage{Bitwuzla}{\withtrack{Biggest Lead}{\inc}}{\withtrack{Bitvec}{\sat}, \withtrack{Equality+MachineArith}{\inc}, \withtrack{FPArith}{\seq,\paral,\sat,\unsat,\fast,\inc,\uc}, \withtrack{QF\_Bitvec}{\inc}, \withtrack{QF\_Equality+Bitvec}{\seq,\paral,\sat,\unsat,\fast,\inc,\mv}, \withtrack{QF\_FPArith}{\seq,\paral,\sat,\unsat,\fast,\inc}}{\withtrack{ABVFP}{\sat,\fast}, \withtrack{ABVFPLRA}{\fast}, \withtrack{AUFBV}{\seq,\paral,\sat,\unsat,\fast}, \withtrack{AUFBVFP}{\seq,\paral,\sat,\unsat,\fast}, \withtrack{QF\_ABVFP}{\uc}, \withtrack{QF\_ABVFPLRA}{\uc}, \withtrack{QF\_BVFP}{\uc}, \withtrack{QF\_BVFPLRA}{\uc}, \withtrack{UFBV}{\seq,\paral,\sat,\unsat,\fast}, \withtrack{UFBVFP}{\seq,\paral,\unsat}}
+\MakeOnePage{Bitwuzla}{\withtrack{Biggest Lead}{\inc}}{\withtrack{Bitvec}{\sat}, \withtrack{Equality+MachineArith}{\inc}, \withtrack{FPArith}{\seq,\paral,\sat,\unsat,\fast,\inc,\uc}, \withtrack{QF\_Bitvec}{\inc}, \withtrack{QF\_Equality+Bitvec}{\seq,\paral,\sat,\unsat,\fast,\inc,\mv}, \withtrack{QF\_FPArith}{\seq,\paral,\sat,\unsat,\fast,\inc}}{\withtrack{ABVFP}{\sat,\fast}, \withtrack{ABVFPLRA}{\fast}, \withtrack{AUFBV}{\seq,\paral,\sat,\unsat,\fast}, \withtrack{AUFBVFP}{\seq,\paral,\sat,\unsat,\fast}, \withtrack{QF\_ABVFP}{\uc}, \withtrack{QF\_ABVFPLRA}{\uc}, \withtrack{QF\_BVFP}{\uc}, \withtrack{QF\_BVFPLRA}{\uc}, \withtrack{UFBV}{\seq,\paral,\sat,\unsat,\fast}, \withtrack{UFBVFP}{\seq,\paral,\unsat}}{s}{s}
 \newpage
-\MakeOnePage{Vampire}{}{\withtrack{Equality}{\fast}}{\withtrack{ALIA}{\seq,\paral,\unsat,\fast}, \withtrack{AUFLIA}{\unsat,\fast}, \withtrack{AUFLIRA}{\fast}, \withtrack{AUFNIRA}{\paral,\unsat,\fast}, \withtrack{UF}{\seq,\paral,\sat}, \withtrack{UFDTLIA}{\fast,\uc}, \withtrack{UFDTNIA}{\seq,\paral,\unsat,\fast,\uc}}
+\MakeOnePage{Vampire}{}{\withtrack{Equality}{\fast}}{\withtrack{ALIA}{\seq,\paral,\unsat,\fast}, \withtrack{AUFLIA}{\unsat,\fast}, \withtrack{AUFLIRA}{\fast}, \withtrack{AUFNIRA}{\paral,\unsat,\fast}, \withtrack{UF}{\seq,\paral,\sat}, \withtrack{UFDTLIA}{\fast,\uc}, \withtrack{UFDTNIA}{\seq,\paral,\unsat,\fast,\uc}}{}{s}
 \newpage
-\MakeOnePage{Yices2}{}{\withtrack{QF\_Bitvec}{\uc}, \withtrack{QF\_Equality}{\seq,\paral,\sat,\unsat,\fast,\uc,\mv}, \withtrack{QF\_Equality+Bitvec}{\uc}, \withtrack{QF\_Equality+LinearArith}{\fast,\uc}, \withtrack{QF\_Equality+NonLinearArith}{\sat}, \withtrack{QF\_LinearIntArith}{\fast,\inc,\uc}, \withtrack{QF\_LinearRealArith}{\seq,\paral,\fast,\uc}}{\withtrack{QF\_ALIA}{\unsat}, \withtrack{QF\_AUFBV}{\fast}, \withtrack{QF\_AUFBVLIA}{\inc}, \withtrack{QF\_AUFLIA}{\seq,\paral,\sat,\unsat}, \withtrack{QF\_LIRA}{\seq,\paral,\sat,\unsat,\mv}, \withtrack{QF\_RDL}{\sat,\unsat,\mv}, \withtrack{QF\_UFBVLIA}{\inc}, \withtrack{QF\_UFLIA}{\unsat,\inc}, \withtrack{QF\_UFLRA}{\seq,\paral,\sat,\unsat,\inc,\mv}, \withtrack{QF\_UFNRA}{\seq,\paral,\unsat,\fast,\inc}}
+\MakeOnePage{Yices2}{}{\withtrack{QF\_Bitvec}{\uc}, \withtrack{QF\_Equality}{\seq,\paral,\sat,\unsat,\fast,\uc,\mv}, \withtrack{QF\_Equality+Bitvec}{\uc}, \withtrack{QF\_Equality+LinearArith}{\fast,\uc}, \withtrack{QF\_Equality+NonLinearArith}{\sat}, \withtrack{QF\_LinearIntArith}{\fast,\inc,\uc}, \withtrack{QF\_LinearRealArith}{\seq,\paral,\fast,\uc}}{\withtrack{QF\_ALIA}{\unsat}, \withtrack{QF\_AUFBV}{\fast}, \withtrack{QF\_AUFBVLIA}{\inc}, \withtrack{QF\_AUFLIA}{\seq,\paral,\sat,\unsat}, \withtrack{QF\_LIRA}{\seq,\paral,\sat,\unsat,\mv}, \withtrack{QF\_RDL}{\sat,\unsat,\mv}, \withtrack{QF\_UFBVLIA}{\inc}, \withtrack{QF\_UFLIA}{\unsat,\inc}, \withtrack{QF\_UFLRA}{\seq,\paral,\sat,\unsat,\inc,\mv}, \withtrack{QF\_UFNRA}{\seq,\paral,\unsat,\fast,\inc}}{s}{s}
 \newpage
-\MakeOnePage{YicesQS}{}{\withtrack{Arith}{\sat,\fast}}{\withtrack{LRA}{\seq,\paral,\unsat}, \withtrack{NRA}{\seq,\paral,\unsat}}
+\MakeOnePage{YicesQS}{}{\withtrack{Arith}{\sat,\fast}}{\withtrack{LRA}{\seq,\paral,\unsat}, \withtrack{NRA}{\seq,\paral,\unsat}}{}{s}
 \newpage
-\MakeOnePage{STP}{}{\withtrack{QF\_Bitvec}{\seq,\paral,\sat,\unsat,\fast,\mv}}{}
+\MakeOnePage{STP}{}{\withtrack{QF\_Bitvec}{\seq,\paral,\sat,\unsat,\fast,\mv}}{}{}{}
 \newpage
-\MakeOnePage{Q3B}{}{\withtrack{Bitvec}{\fast}}{}
+\MakeOnePage{Q3B}{}{\withtrack{Bitvec}{\fast}}{}{}{}
 \newpage
-\MakeOnePage{cvc5}{\withtrack{Biggest Lead}{\seq,\paral,\sat,\unsat,\uc}, \withtrack{Largest Contribution}{\seq,\paral,\sat,\unsat,\fast,\inc,\uc}}{\withtrack{Arith}{\seq,\paral,\unsat,\inc,\uc}, \withtrack{Bitvec}{\seq,\paral,\unsat,\inc,\uc}, \withtrack{Equality}{\seq,\paral,\sat,\unsat,\inc,\uc}, \withtrack{Equality+LinearArith}{\seq,\paral,\sat,\unsat,\fast,\inc,\uc}, \withtrack{Equality+MachineArith}{\seq,\paral,\sat,\unsat,\fast,\uc}, \withtrack{Equality+NonLinearArith}{\seq,\paral,\sat,\unsat,\fast,\inc,\uc}, \withtrack{QF\_Datatypes}{\seq,\paral,\sat,\unsat,\uc\textsuperscript\seq}, \withtrack{QF\_Equality}{\inc}, \withtrack{QF\_Equality+Bitvec+Arith}{\inc}, \withtrack{QF\_Equality+NonLinearArith}{\seq,\paral,\unsat,\fast,\inc,\uc}, \withtrack{QF\_FPArith}{\uc}, \withtrack{QF\_LinearIntArith}{\unsat}, \withtrack{QF\_LinearRealArith}{\unsat}, \withtrack{QF\_NonLinearRealArith}{\unsat,\fast}, \withtrack{QF\_Strings}{\seq,\paral,\sat,\unsat}}{\withtrack{LIA}{\sat,\fast}, \withtrack{NIA}{\sat,\fast}, \withtrack{QF\_ALIA}{\inc}, \withtrack{QF\_AUFLIA}{\uc}, \withtrack{QF\_BVFPLRA}{\inc}, \withtrack{QF\_FP}{\sat}, \withtrack{QF\_IDL}{\uc}, \withtrack{QF\_NIRA}{\seq,\paral,\unsat}, \withtrack{QF\_UFBVDT}{\seq,\paral,\sat,\unsat,\fast}, \withtrack{QF\_UFDTLIRA}{\seq,\paral,\sat,\unsat,\fast,\uc}, \withtrack{QF\_UFLRA}{\uc}, \withtrack{QF\_UFNIA}{\sat}, \withtrack{UFDT}{\fast}}
+\MakeOnePage{cvc5}{\withtrack{Biggest Lead}{\seq,\paral,\sat,\unsat,\uc}, \withtrack{Largest Contribution}{\seq,\paral,\sat,\unsat,\fast,\inc,\uc}}{\withtrack{Arith}{\seq,\paral,\unsat,\inc,\uc}, \withtrack{Bitvec}{\seq,\paral,\unsat,\inc,\uc}, \withtrack{Equality}{\seq,\paral,\sat,\unsat,\inc,\uc}, \withtrack{Equality+LinearArith}{\seq,\paral,\sat,\unsat,\fast,\inc,\uc}, \withtrack{Equality+MachineArith}{\seq,\paral,\sat,\unsat,\fast,\uc}, \withtrack{Equality+NonLinearArith}{\seq,\paral,\sat,\unsat,\fast,\inc,\uc}, \withtrack{QF\_Datatypes}{\seq,\paral,\sat,\unsat,\uc\textsuperscript\seq}, \withtrack{QF\_Equality}{\inc}, \withtrack{QF\_Equality+Bitvec+Arith}{\inc}, \withtrack{QF\_Equality+NonLinearArith}{\seq,\paral,\unsat,\fast,\inc,\uc}, \withtrack{QF\_FPArith}{\uc}, \withtrack{QF\_LinearIntArith}{\unsat}, \withtrack{QF\_LinearRealArith}{\unsat}, \withtrack{QF\_NonLinearRealArith}{\unsat,\fast}, \withtrack{QF\_Strings}{\seq,\paral,\sat,\unsat}}{\withtrack{LIA}{\sat,\fast}, \withtrack{NIA}{\sat,\fast}, \withtrack{QF\_ALIA}{\inc}, \withtrack{QF\_AUFLIA}{\uc}, \withtrack{QF\_BVFPLRA}{\inc}, \withtrack{QF\_FP}{\sat}, \withtrack{QF\_IDL}{\uc}, \withtrack{QF\_NIRA}{\seq,\paral,\unsat}, \withtrack{QF\_UFBVDT}{\seq,\paral,\sat,\unsat,\fast}, \withtrack{QF\_UFDTLIRA}{\seq,\paral,\sat,\unsat,\fast,\uc}, \withtrack{QF\_UFLRA}{\uc}, \withtrack{QF\_UFNIA}{\sat}, \withtrack{UFDT}{\fast}}{s}{s}
 \newpage
-\MakeOnePage{OpenSMT}{}{\withtrack{QF\_Equality+LinearArith}{\unsat}, \withtrack{QF\_LinearRealArith}{\sat,\inc,\mv}}{\withtrack{QF\_LIA}{\seq,\paral}, \withtrack{QF\_LRA}{\seq,\paral,\unsat,\fast}, \withtrack{QF\_UFIDL}{\seq,\paral,\sat,\mv}}
+\MakeOnePage{OpenSMT}{}{\withtrack{QF\_Equality+LinearArith}{\unsat}, \withtrack{QF\_LinearRealArith}{\sat,\inc,\mv}}{\withtrack{QF\_LIA}{\seq,\paral}, \withtrack{QF\_LRA}{\seq,\paral,\unsat,\fast}, \withtrack{QF\_UFIDL}{\seq,\paral,\sat,\mv}}{s}{s}
 \newpage
-\MakeOnePage{z3-alpha}{}{\withtrack{QF\_Strings}{\fast}}{\withtrack{QF\_S}{\sat}, \withtrack{QF\_SNIA}{\seq,\paral,\sat}}
+\MakeOnePage{z3-alpha}{}{\withtrack{QF\_Strings}{\fast}}{\withtrack{QF\_S}{\sat}, \withtrack{QF\_SNIA}{\seq,\paral,\sat}}{}{s}
 \newpage
-\MakeOnePage{iProver}{}{}{\withtrack{ANIA}{\unsat}}
+\MakeOnePage{iProver}{}{}{\withtrack{ANIA}{\unsat}}{}{}
 \newpage

### 2023-06-29 2023/certificates/compute_from_yaml.py

@@ -80,15 +80,18 @@ class info:
         l=[]
         for (k,v) in sorted(self.divisions.items()):
             withtrack(l,k,v)
+        s_for_divisions=("s" if len(l)>=2 else "")
         divisions = ", ".join(l)
 
         l=[]
         for (k,v) in sorted(self.logics.items()):
             withtrack(l,k,v)
+        s_for_logics=("s" if len(l)>=2 else "")
         logics = ", ".join(l)
         
-        return "\\MakeOnePage{{{name}}}{{{overall}}}{{{divisions}}}{{{logics}}}"\
-            .format(name=name,overall=self.overall.latex(),divisions=divisions,logics=logics)
+        return "\\MakeOnePage{{{name}}}{{{overall}}}{{{divisions}}}{{{logics}}}{{{s_for_divisions}}}{{{s_for_logics}}}"\
+            .format(name=name,overall=self.overall.latex(),divisions=divisions,logics=logics,
+                    s_for_divisions=s_for_divisions,s_for_logics=s_for_logics)
     
     def isNotEmpty(self):
         return self.overall.isNotEmpty() \

### 2023-07-04 2023/certificates/gen_certificates_ornament.tex
Slides future of SMTCOMP

@@
 \usepackage[svgnames]{xcolor}
+\usepackage{adjustbox}
 \usepackage{wallpaper}
@@
 
-\fancyhead[L]{%
+\newpgfornamentfamily{pgfhan}
+\newbox{\fortyseven}
+\savebox{\fortyseven}{
+    \tikzset{every node/.append style={inner sep=0pt,color=MidnightBlue!50}}
+    \tikzset{pgfornamentstyle/.style={draw=green!20!black,
+    fill=orange,fill opacity=.5,thick}}% 
+\pgfornament[scale=0.50]{32}}
+
+\newbox{\myfancyhead}
+\AtBeginDocument{
+\savebox{\myfancyhead}{
 \newpgfornamentfamily{pgfhan}
@@
     fill=orange,fill opacity=.5,thick}}%
-    \newbox{\fortyseven}
-\savebox{\fortyseven}{\pgfornament[scale=0.50]{32}}
     \node[anchor=north west,shift={(14.5pt,-14.5pt)}] at (current page.north west)
@@
 \foreach \i in {0,...,3}
-    \node[anchor=south east,shift={($\i*(0,-100bp)$)},rotate=90] at (ne.south east)
+    \node[anchor=south east,shift={($\i*(0,-100bp)+(0,25bp)$)},rotate=90] at (ne.south east)
      {\usebox{\fortyseven}};
@@
 \foreach \i in {0,...,3}
-      \node[anchor=south west,shift={($\i*(0,-100bp)$)},rotate=-90] at (nw.south west)
+      \node[anchor=south west,shift={($\i*(0,-100bp)+(0,25bp)$)},rotate=-90] at (nw.south west)
        {\usebox{\fortyseven}};
@@
 \end{tikzpicture}
-}
+}}
+
+\fancyhead[L]{\usebox{\myfancyhead}}
 
@@
     \begin{tabular}{ccccc}
-        \includegraphics[scale=0.5]{signature-blank-crop-jochen.pdf} && && \includegraphics{MB-Signature.png} \\
+        \includegraphics[scale=0.5,trim=0pt 0.60cm 0pt 0pt]{signature-blank-crop-jochen.pdf} &&
+        \includegraphics[scale=0.25,trim=1.5cm 2.75cm 0pt 0pt]{signature_bobot.png} &&
+        \includegraphics[trim=0pt 0.10cm 0pt 0pt]{MB-Signature.png} \\
     \cline{1-1} 
@@
 \begin{document}
+
 \TileWallPaper{4cm}{2cm}{tiling.png}

### 2023-07-04 2023/certificates/input_for_certificates.tex
Slides future of SMTCOMP

--- 2023-06-29 2023/certificates/input_for_certificates.tex
@@
-\MakeOnePage{COLIBRI}{}{}{\withtrack{QF\_ABVFPLRA}{\seq,\paral,\unsat,\fast}, \withtrack{QF\_FP}{\unsat,\fast}, \withtrack{QF\_FPLRA}{\unsat,\fast}}
+\MakeOnePage{Z3-Z3++}{\withtrack{Biggest Lead}{\mv}, \withtrack{Largest Contribution}{\mv}}{\withtrack{QF\_LinearIntArith}{\seq,\paral,\sat,\mv}, \withtrack{QF\_NonLinearIntArith}{\seq,\paral,\sat,\unsat,\fast}, \withtrack{QF\_NonLinearRealArith}{\seq,\paral,\sat}}{\withtrack{QF\_IDL}{\unsat}}{s}{}
 \newpage
-\MakeOnePage{Z3++}{\withtrack{Biggest Lead}{\mv}, \withtrack{Largest Contribution}{\mv}}{\withtrack{QF\_LinearIntArith}{\seq,\paral,\sat,\mv}, \withtrack{QF\_NonLinearIntArith}{\seq,\paral,\sat,\unsat,\fast}, \withtrack{QF\_NonLinearRealArith}{\seq,\paral,\sat}}{\withtrack{QF\_IDL}{\unsat}}
+\MakeOnePage{Z3-Z3++}{\withtrack{Biggest Lead}{\mv}, \withtrack{Largest Contribution}{\mv}}{\withtrack{QF\_LinearIntArith}{\seq,\paral,\sat,\mv}, \withtrack{QF\_NonLinearIntArith}{\seq,\paral,\sat,\unsat,\fast}, \withtrack{QF\_NonLinearRealArith}{\seq,\paral,\sat}}{\withtrack{QF\_IDL}{\unsat}}{s}{}
 \newpage
-\MakeOnePage{OSTRICH}{}{}{\withtrack{QF\_S}{\seq,\paral,\unsat}}
+\MakeOnePage{Z3-Z3++}{\withtrack{Biggest Lead}{\mv}, \withtrack{Largest Contribution}{\mv}}{\withtrack{QF\_LinearIntArith}{\seq,\paral,\sat,\mv}, \withtrack{QF\_NonLinearIntArith}{\seq,\paral,\sat,\unsat,\fast}, \withtrack{QF\_NonLinearRealArith}{\seq,\paral,\sat}}{\withtrack{QF\_IDL}{\unsat}}{s}{}
 \newpage
-\MakeOnePage{SMTInterpol}{\withtrack{Biggest Lead}{\fast}}{\withtrack{QF\_Datatypes}{\fast,\uc\textsuperscript\paral}, \withtrack{QF\_Equality+LinearArith}{\seq,\paral,\sat,\inc,\mv}, \withtrack{QF\_NonLinearIntArith}{\inc}}{\withtrack{ALIA}{\sat,\uc}, \withtrack{AUFDTLIA}{\uc}, \withtrack{QF\_ALIA}{\uc}, \withtrack{QF\_ANIA}{\seq,\paral,\sat,\unsat,\fast,\inc,\uc}, \withtrack{QF\_AUFNIA}{\seq,\paral,\sat,\unsat,\fast,\uc}, \withtrack{QF\_LIA}{\unsat}, \withtrack{QF\_UF}{\uc\textsuperscript\paral}, \withtrack{QF\_UFDT}{\uc\textsuperscript\seq}, \withtrack{QF\_UFDTLIA}{\unsat,\fast,\uc}, \withtrack{UFIDL}{\sat}, \withtrack{UFLIA}{\sat}}
+\MakeOnePage{Z3-Z3++}{\withtrack{Biggest Lead}{\mv}, \withtrack{Largest Contribution}{\mv}}{\withtrack{QF\_LinearIntArith}{\seq,\paral,\sat,\mv}, \withtrack{QF\_NonLinearIntArith}{\seq,\paral,\sat,\unsat,\fast}, \withtrack{QF\_NonLinearRealArith}{\seq,\paral,\sat}}{\withtrack{QF\_IDL}{\unsat}}{s}{}
 \newpage
-\MakeOnePage{Bitwuzla}{\withtrack{Biggest Lead}{\inc}}{\withtrack{Bitvec}{\sat}, \withtrack{Equality+MachineArith}{\inc}, \withtrack{FPArith}{\seq,\paral,\sat,\unsat,\fast,\inc,\uc}, \withtrack{QF\_Bitvec}{\inc}, \withtrack{QF\_Equality+Bitvec}{\seq,\paral,\sat,\unsat,\fast,\inc,\mv}, \withtrack{QF\_FPArith}{\seq,\paral,\sat,\unsat,\fast,\inc}}{\withtrack{ABVFP}{\sat,\fast}, \withtrack{ABVFPLRA}{\fast}, \withtrack{AUFBV}{\seq,\paral,\sat,\unsat,\fast}, \withtrack{AUFBVFP}{\seq,\paral,\sat,\unsat,\fast}, \withtrack{QF\_ABVFP}{\uc}, \withtrack{QF\_ABVFPLRA}{\uc}, \withtrack{QF\_BVFP}{\uc}, \withtrack{QF\_BVFPLRA}{\uc}, \withtrack{UFBV}{\seq,\paral,\sat,\unsat,\fast}, \withtrack{UFBVFP}{\seq,\paral,\unsat}}
-\newpage
-\MakeOnePage{Vampire}{}{\withtrack{Equality}{\fast}}{\withtrack{ALIA}{\seq,\paral,\unsat,\fast}, \withtrack{AUFLIA}{\unsat,\fast}, \withtrack{AUFLIRA}{\fast}, \withtrack{AUFNIRA}{\paral,\unsat,\fast}, \withtrack{UF}{\seq,\paral,\sat}, \withtrack{UFDTLIA}{\fast,\uc}, \withtrack{UFDTNIA}{\seq,\paral,\unsat,\fast,\uc}}
-\newpage
-\MakeOnePage{Yices2}{}{\withtrack{QF\_Bitvec}{\uc}, \withtrack{QF\_Equality}{\seq,\paral,\sat,\unsat,\fast,\uc,\mv}, \withtrack{QF\_Equality+Bitvec}{\uc}, \withtrack{QF\_Equality+LinearArith}{\fast,\uc}, \withtrack{QF\_Equality+NonLinearArith}{\sat}, \withtrack{QF\_LinearIntArith}{\fast,\inc,\uc}, \withtrack{QF\_LinearRealArith}{\seq,\paral,\fast,\uc}}{\withtrack{QF\_ALIA}{\unsat}, \withtrack{QF\_AUFBV}{\fast}, \withtrack{QF\_AUFBVLIA}{\inc}, \withtrack{QF\_AUFLIA}{\seq,\paral,\sat,\unsat}, \withtrack{QF\_LIRA}{\seq,\paral,\sat,\unsat,\mv}, \withtrack{QF\_RDL}{\sat,\unsat,\mv}, \withtrack{QF\_UFBVLIA}{\inc}, \withtrack{QF\_UFLIA}{\unsat,\inc}, \withtrack{QF\_UFLRA}{\seq,\paral,\sat,\unsat,\inc,\mv}, \withtrack{QF\_UFNRA}{\seq,\paral,\unsat,\fast,\inc}}
-\newpage
-\MakeOnePage{YicesQS}{}{\withtrack{Arith}{\sat,\fast}}{\withtrack{LRA}{\seq,\paral,\unsat}, \withtrack{NRA}{\seq,\paral,\unsat}}
-\newpage
-\MakeOnePage{STP}{}{\withtrack{QF\_Bitvec}{\seq,\paral,\sat,\unsat,\fast,\mv}}{}
-\newpage
-\MakeOnePage{Q3B}{}{\withtrack{Bitvec}{\fast}}{}
-\newpage
-\MakeOnePage{cvc5}{\withtrack{Biggest Lead}{\seq,\paral,\sat,\unsat,\uc}, \withtrack{Largest Contribution}{\seq,\paral,\sat,\unsat,\fast,\inc,\uc}}{\withtrack{Arith}{\seq,\paral,\unsat,\inc,\uc}, \withtrack{Bitvec}{\seq,\paral,\unsat,\inc,\uc}, \withtrack{Equality}{\seq,\paral,\sat,\unsat,\inc,\uc}, \withtrack{Equality+LinearArith}{\seq,\paral,\sat,\unsat,\fast,\inc,\uc}, \withtrack{Equality+MachineArith}{\seq,\paral,\sat,\unsat,\fast,\uc}, \withtrack{Equality+NonLinearArith}{\seq,\paral,\sat,\unsat,\fast,\inc,\uc}, \withtrack{QF\_Datatypes}{\seq,\paral,\sat,\unsat,\uc\textsuperscript\seq}, \withtrack{QF\_Equality}{\inc}, \withtrack{QF\_Equality+Bitvec+Arith}{\inc}, \withtrack{QF\_Equality+NonLinearArith}{\seq,\paral,\unsat,\fast,\inc,\uc}, \withtrack{QF\_FPArith}{\uc}, \withtrack{QF\_LinearIntArith}{\unsat}, \withtrack{QF\_LinearRealArith}{\unsat}, \withtrack{QF\_NonLinearRealArith}{\unsat,\fast}, \withtrack{QF\_Strings}{\seq,\paral,\sat,\unsat}}{\withtrack{LIA}{\sat,\fast}, \withtrack{NIA}{\sat,\fast}, \withtrack{QF\_ALIA}{\inc}, \withtrack{QF\_AUFLIA}{\uc}, \withtrack{QF\_BVFPLRA}{\inc}, \withtrack{QF\_FP}{\sat}, \withtrack{QF\_IDL}{\uc}, \withtrack{QF\_NIRA}{\seq,\paral,\unsat}, \withtrack{QF\_UFBVDT}{\seq,\paral,\sat,\unsat,\fast}, \withtrack{QF\_UFDTLIRA}{\seq,\paral,\sat,\unsat,\fast,\uc}, \withtrack{QF\_UFLRA}{\uc}, \withtrack{QF\_UFNIA}{\sat}, \withtrack{UFDT}{\fast}}
-\newpage
-\MakeOnePage{OpenSMT}{}{\withtrack{QF\_Equality+LinearArith}{\unsat}, \withtrack{QF\_LinearRealArith}{\sat,\inc,\mv}}{\withtrack{QF\_LIA}{\seq,\paral}, \withtrack{QF\_LRA}{\seq,\paral,\unsat,\fast}, \withtrack{QF\_UFIDL}{\seq,\paral,\sat,\mv}}
-\newpage
-\MakeOnePage{z3-alpha}{}{\withtrack{QF\_Strings}{\fast}}{\withtrack{QF\_S}{\sat}, \withtrack{QF\_SNIA}{\seq,\paral,\sat}}
-\newpage
-\MakeOnePage{iProver}{}{}{\withtrack{ANIA}{\unsat}}
-\newpage

### 2023-07-04 2023/certificates/compute_from_yaml.py

@@ -212,10 +212,11 @@ def main(website_results,input_for_certificates,pretty_names,experimental_divisi
         for (key,value) in solvers.items():
             if value.isNotEmpty() and value.members != 0:
                 print("solver: ",key,"(",value.members,")")
-#                for i in range(1,value.members):
-                output.write(value.latex(key))
-                output.write("\n\\newpage\n")
-                output.flush()
+                if True:
+#                for i in range(0,value.members):
+                    output.write(value.latex(key))
+                    output.write("\n\\newpage\n")
+                    output.flush()
             else:
                 print("solver: ",key,"( no certificate )")
             

### 2023-07-04 2023/slides/future/smtcomp_futur.tex
cloud and parallel result

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%   SMT-COMP 2023 - Futur of SMTCOMP without starexec
%
%   1 hour
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[table]{beamer}
\usepackage[utf8]{inputenc}
\usepackage{xcolor}
\usepackage{tikz}
\usetikzlibrary{shapes,shapes.callouts,automata,trees}
\usetikzlibrary{decorations.pathmorphing,external,fit}
\usetikzlibrary{calc}
\usetikzlibrary{backgrounds} %used for the CEGAR figure
\usepackage{amssymb}
\usepackage{clrscode}
\usepackage{pifont}
\usepackage{pdfpages}
\usepackage{graphicx}
\usepackage{listings}
\geometry{papersize={16cm,9cm}}
%\tikzexternalize

\colorlet{MYred}{red!70!black}
\definecolor{MYgreen}{rgb}{.1,.5,0}
\definecolor{MYblue}{rgb}{0,.42,.714}
\colorlet{MYgray}{white!95!MYblue}
\colorlet{MYorange}{orange!80!black}
\definecolor{gold}{rgb}{.8,.6,0}
\colorlet{silver}{white!55!black}
\colorlet{bronze}{brown!70!black}
\def\tick{\ding{52}}
\def\cross{\ding{54}}

%%%%%%%%%%%%%%%%%%%%
%%% Beamer stuff %%%
%%%%%%%%%%%%%%%%%%%%
\usetheme{default}
\useinnertheme{rounded}
\setbeamertemplate{frametitle}[default][center]
\setbeamertemplate{footline}{\quad\hfill\footnotesize\insertframenumber\strut\kern1em\vskip2pt}
\setbeamertemplate{navigation symbols}{}
\setbeamertemplate{itemize/enumerate subbody begin}{\normalsize}
\usefonttheme[onlymath]{serif} % Nicer formulas
\setbeamercolor{block body}{bg=black!10}
\setbeamercolor{block title}{bg=black!20}

\AtBeginSection[]{
  \begin{frame}
  \vfill
  \centering
  \begin{beamercolorbox}[sep=8pt,center,shadow=true,rounded=true]{title}
    \usebeamerfont{title}\insertsectionhead\par%
  \end{beamercolorbox}
  \vfill
  \end{frame}
}

\def\emph#1{\textcolor{MYblue}{#1}}

%%% Titel, Autor und Datum des Vortrags:
\title{Discussion on Future of SMT-COMP}
\author{Martin Bromberger \and Jochen Hoenicke \and \emph{Fran\c{c}ois Bobot}}
\date{July 5, 2023}

%% Institut
\institute{
CEA List, France \and
MPI für Informatik, Germany \and
Certora, Israel
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% MACROS

% database symbol (from stackexchange)

\makeatletter
\tikzset{
    database/.style={
        path picture={
            \draw (0, 1.5*\database@segmentheight) circle [x radius=\database@radius,y radius=\database@aspectratio*\database@radius];
            \draw (-\database@radius, 0.5*\database@segmentheight) arc [start angle=180,end angle=360,x radius=\database@radius, y radius=\database@aspectratio*\database@radius];
            \draw (-\database@radius,-0.5*\database@segmentheight) arc [start angle=180,end angle=360,x radius=\database@radius, y radius=\database@aspectratio*\database@radius];
            \draw (-\database@radius,1.5*\database@segmentheight) -- ++(0,-3*\database@segmentheight) arc [start angle=180,end angle=360,x radius=\database@radius, y radius=\database@aspectratio*\database@radius] -- ++(0,3*\database@segmentheight);
        },
        minimum width=2*\database@radius + \pgflinewidth,
        minimum height=3*\database@segmentheight + 2*\database@aspectratio*\database@radius + \pgflinewidth,
    },
    database segment height/.store in=\database@segmentheight,
    database radius/.store in=\database@radius,
    database aspect ratio/.store in=\database@aspectratio,
    database segment height=0.1cm,
    database radius=0.25cm,
    database aspect ratio=0.35,
}
\makeatother

%%%%% json lstlisting %%%%%%%%%

\definecolor{eclipseStrings}{RGB}{42,0.0,255}
\definecolor{eclipseKeywords}{RGB}{127,0,85}
\colorlet{numb}{magenta!60!black}

\lstdefinelanguage{json}{
    basicstyle=\normalfont\ttfamily,
    commentstyle=\color{eclipseStrings}, % style of comment
    stringstyle=\color{eclipseKeywords}, % style of strings
 %   numbers=left,
    numberstyle=\scriptsize,
    stepnumber=1,
    numbersep=8pt,
    showstringspaces=false,
    breaklines=true,
    frame=lines,
%    backgroundcolor=\color{gray}, %only if you like
    string=[s]{"}{"},
    comment=[l]{:\ "},
    morecomment=[l]{:"},
    literate=
        *{0}{{{\color{numb}0}}}{1}
         {1}{{{\color{numb}1}}}{1}
         {2}{{{\color{numb}2}}}{1}
         {3}{{{\color{numb}3}}}{1}
         {4}{{{\color{numb}4}}}{1}
         {5}{{{\color{numb}5}}}{1}
         {6}{{{\color{numb}6}}}{1}
         {7}{{{\color{numb}7}}}{1}
         {8}{{{\color{numb}8}}}{1}
         {9}{{{\color{numb}9}}}{1}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand\vitem{\vfill\item}

\begin{document}

\begin{frame}
  \titlepage
\end{frame}

\newcommand{\mylogo}[1]{\includegraphics[height=1.5em]{#1}}

\newbox{\logostarexec}
\savebox{\logostarexec}{\mylogo{starlogo.png}}

\newcommand{\logolaptop}{\mylogo{512px-OOjs_UI_icon_laptop-progressive.svg.png}}

\begin{frame}
    \frametitle{Current infrastructure}
    \pause
    \begin{tabular}{cl}
        \mylogo{iowa_university.png}\usebox{\logostarexec} & Benchmark uploaded to StarExec from Iowa Gitlab \\\pause
        \mylogo{Google__G__Logo.svg.png} & Applications through Google form \\\pause
        \usebox{\logostarexec} & Solvers are uploaded to StarExec \\\pause
        \mylogo{You've_got_mail.png} & Modification of the applications handled by mail \\\pause
        \logolaptop & Solvers downloaded, wrapped locally, uploaded to StarExec \\\pause
        \logolaptop & Benchmark selection and job created locally \\\pause
        \usebox{\logostarexec} & Jobs sent to StarExec and run \\\pause
        \usebox{\logostarexec} & Download results from StarExec \\\pause
        \logolaptop \usebox{\logostarexec} & Fix benchmark selection, add fixed
         version of the solvers, run jobs on Starexec \\\pause
        \logolaptop & Score the results, generate data for the website \\
    \end{tabular}
\end{frame}

\newcommand{\onlystarexec}{\only<1>{\usebox{\logostarexec}}}
\newcommand{\onlylaptop}{\only<1-4>{\logolaptop}}
\newcommand{\logocloud}{\mylogo{1280px-Amazon_Web_Services_Logo.svg.png}
\mylogo{Google-Cloud-Emblem.png}
\mylogo{Microsoft-Azure.png}}
\newcommand{\onlycloudfirst}{\only<4->{\logocloud}}
\newcommand{\onlycloudsecond}{\only<5->{\logocloud}}
\newcommand{\logogithub}{\mylogo{free-github-163-761603.png}}
\newcommand{\logozenodo}{\mylogo{zenodo.png}}

\frame<1>[label=summary]{
    \frametitle{Needed infrastructure}
    \begin{itemize}
        \item Store benchmark : \mylogo{iowa_university.png}\onlystarexec %iowa and starexec
        \item Participants registration : \only<-4>{\mylogo{Google__G__Logo.svg.png}\mylogo{You've_got_mail.png}}
        \only<5->{\logogithub}
        %google and starexec
        \item Select the benchmarks: \onlylaptop\onlycloudsecond
        \item Run the jobs : \onlystarexec\onlycloudfirst%starexec
        \item Store the datas : \onlystarexec\onlycloudfirst%starexec
        \item Archive the datas : \onlystarexec\only<3->{\logozenodo}%starexec
%        \item Store the raw results (sq csv 148Mo, 16Mo compressed) : \usebox{\logostarexec}%starexec
%        \item Store the artifacts (mv Go proof Go) : \usebox{\logostarexec} %starexec
        \item Run scoring script and generate website : \onlylaptop\onlycloudsecond\logogithub%localy and github
    \end{itemize}
}

\begin{frame}
    \frametitle{StarExec}
    Since 2013, StarExec has run 80 competitions and events across its 16 registered communities(SAT, TPTP, Termination,...).  
    StarExec is supported by a \$1.85 million USD grant (NSF)

%Several people have contributed in various capacities to the StarExec project
%so far.
\vfill
Shepherded by Aaron Stump
\vfill
Involved in the development: {\small Eric Burns, Todd Elvers,
Albert Giegerich, Pat Hawks, Tyler Jensen, Wyatt Kaiser, Ben McCune, Muhammad
Nassar, CJ Palmer, Vivek Sardeshmukh, Skylar Stark, and Ruoyu Zhang.}
\vfill
Computer system support and assistance: {\small Hugh Brown, Dan Holstad, Jamie
Tisdale, and JJ Ulrich}

%In addition to the members of the Advisory Board, the following people have
%provided useful feedback and input: Clark Barrett, Christoph Benzmüller, Armin
%Biere, David Cok, Morgan Deters, Jürgen Giesl, Alberto Griggio, Thomas
%Krennwallner, Jens Otten, Andrei Paskevich, Olivier Roussel, Martina Seidl,
%Stephan Schulz, Michael Tautschnig, Christoph Wintersteiger, and Harald Zankl.
\end{frame}

\begin{frame}
    \frametitle{StarExec: job pairs}
\begin{center}
    \includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{statistics_starexec.png}    
\end{center}

\end{frame}
\begin{frame}
    \frametitle{StarExec is closing}

    \begin{center}

        \huge{Decommissioned starting August 2024}
    \end{center}

\end{frame}

\againframe<2>{summary}

\begin{frame}
    \frametitle{Archive: Past results and Artifacts}

    \begin{itemize}
        \item Solvers
        \item Raw results
        \item Solver output 
    \end{itemize}
    \vfill
    \pause
    \logozenodo: EC funded research. Leveraging CERN developed tools for Big Data management and extended Digital Library capabilities for Open Data
    \begin{itemize}
        \item Open
        \item Max 50 GB per dataset
        \item DOI
    \end{itemize}
\vfill
    NB: StarExec should do the upload (because downloading from StarExec is very slow)

\end{frame}

\againframe<3>{summary}

% \begin{frame}
%     \frametitle{Future competition}

% \begin{itemize}
%     \item CPU
%     \item Intermediate Data-storage
%     \item Permanent Data-storage (like past competition)
% \end{itemize}

% \end{frame}

\begin{frame}
    \frametitle{Future competitions: Cloud? \logocloud}
\begin{columns}
    \column{0.5\textwidth}
    Slurm (open-source job scheduler):
    \begin{itemize}
        \item Available in cloud providers
        \item Could be available in academic clusters
        \item Allows to do the selection in the cloud
    \end{itemize}
    \column{0.5\textwidth}
    Batch
    \begin{itemize}
        \item Each provider as its own API 
        \item Simpler
        \item e.g. \url{https://github.com/Z3Prover/PerformanceTest}
    \end{itemize}
\end{columns}
    \pause
    \vfill
    \begin{center}
        \large
        Who already used cloud for benchmarking?
    \end{center}
\end{frame}

\againframe<4>{summary}

\begin{frame}
    \frametitle{Participant registration}
    Github MR with \lstinline{bub4.json}:

    \lstinputlisting[language=json]{prover.json}
\end{frame}

\againframe<5>{summary}

\begin{frame}
    \frametitle{Other simplifications}
    \begin{itemize}
        \item Currently 3 repositories $\implies$ 1 repository
        \item Bash, sed, awk, python $\implies$ python
    \end{itemize}
\pause
\vfill
    \begin{center}
        {\large Is the secrecy of the result important to keep?}
    \end{center}
\end{frame}

\begin{frame}
    \frametitle{Questions?}

    \begin{itemize}
        \item Zenodo? For longterm archive
        \item Reproducibility of the result?
        \item Experience with cloud computing?
        \item Need for sponsorship
    \end{itemize}
\end{frame}

\end{document}

### 2023-07-04 2023/results/aws/join.py

@@ -1,0 +1,151 @@
+#!/usr/bin/env python3
+
+# Data processing library pandas
+import numpy
+import pandas
+
+# We need higher precisions for some of the reduction scores of the unsat-core
+# track.
+pandas.set_option('display.precision', 16)
+
+# Options parsing
+from argparse import ArgumentParser
+
+import json
+import os
+import sys
+import csv
+import math
+import time
+import datetime
+
+# StarExec result strings
+RESULT_UNKNOWN = 'starexec-unknown'
+RESULT_SAT = 'sat'
+RESULT_UNSAT = 'unsat'
+
+columns = [ "benchmark", "millisecond", "result" ]
+
+# cvc5, vampire, iprover, z3-owl
+
+vampire = {
+    "solver_id": "44484",
+    "configuration_id": "741777",
+    "name": "Vampire"
+}
+
+cvc5 = {
+    "solver_id": "44737",
+    "configuration_id": "741788",
+    "name": "cvc5"
+}
+
+iprover = {
+    "solver_id": "44768",
+    "configuration_id": "741808",
+    "name": "iProver"  
+}
+
+z3owl = {
+    "solver_id": "44715",
+    "configuration_id": "741784",
+    "name": "Z3-Owl"  
+}
+
+
+files = [
+    {
+      "name" : "cloud",
+      "dst" : "../raw-results-cloud.csv",
+      "pairs" : "cloud-pairs.csv.gz",
+      "solvers" : [
+        { "file": "cloud-vampire.adjust-smt.csv.gz",
+          "solver": vampire
+        },
+        { "file": "cloud-cvc5.adjust-smt.csv.gz",
+          "solver": cvc5
+        },
+
+    ]},
+  {
+      "name" : "parallel",
+      "dst" : "../raw-results-parallel.csv",
+      "pairs" : "parallel-pairs.csv.gz",
+      "solvers" : [
+        { "file": "parallel-vampire.adjust-smt.csv.gz",
+          "solver": vampire
+        },
+        { "file": "parallel-iprover.adjust-smt.csv.gz",
+          "solver": iprover
+        },
+        { "file": "parallel-z3-owl.adjust-smt.csv.gz",
+          "solver": z3owl
+        },
+  ]}
+]
+#AWS side:
+# SAT, UNSAT represent SAT and UNSAT answers, respectively.
+# TIMED_OUT is a timeout
+# UNKNOWN means that the solver explicitly reported UNKNOWN.
[…]

### 2023-07-05 2023/slides/presresults/input_for_certificates.tex
Start of presentation result 2023

\MakeOnePage{COLIBRI}{}{}{\withtrack{QF\_ABVFPLRA}{\seq,\paral,\unsat,\fast}, \withtrack{QF\_FP}{\unsat,\fast}, \withtrack{QF\_FPLRA}{\unsat,\fast}}{}{s}
\newpage
\MakeOnePage{Z3++}{\withtrack{Biggest Lead}{\mv}, \withtrack{Largest Contribution}{\mv}}{\withtrack{QF\_LinearIntArith}{\seq,\paral,\sat,\mv}, \withtrack{QF\_NonLinearIntArith}{\seq,\paral,\sat,\unsat,\fast}, \withtrack{QF\_NonLinearRealArith}{\seq,\paral,\sat}}{\withtrack{QF\_IDL}{\unsat}}{s}{}
\newpage
\MakeOnePage{OSTRICH}{}{}{\withtrack{QF\_S}{\seq,\paral,\unsat}}{}{}
\newpage
\MakeOnePage{SMTInterpol}{\withtrack{Biggest Lead}{\fast}}{\withtrack{QF\_Datatypes}{\fast,\uc\textsuperscript\paral}, \withtrack{QF\_Equality+LinearArith}{\seq,\paral,\sat,\inc,\mv}, \withtrack{QF\_NonLinearIntArith}{\inc}}{\withtrack{ALIA}{\sat,\uc}, \withtrack{AUFDTLIA}{\uc}, \withtrack{QF\_ALIA}{\uc}, \withtrack{QF\_ANIA}{\seq,\paral,\sat,\unsat,\fast,\inc,\uc}, \withtrack{QF\_AUFNIA}{\seq,\paral,\sat,\unsat,\fast,\uc}, \withtrack{QF\_LIA}{\unsat}, \withtrack{QF\_UF}{\uc\textsuperscript\paral}, \withtrack{QF\_UFDT}{\uc\textsuperscript\seq}, \withtrack{QF\_UFDTLIA}{\unsat,\fast,\uc}, \withtrack{UFIDL}{\sat}, \withtrack{UFLIA}{\sat}}{s}{s}
\newpage
\MakeOnePage{Bitwuzla}{\withtrack{Biggest Lead}{\inc}}{\withtrack{Bitvec}{\sat,\fast}, \withtrack{Equality+MachineArith}{\inc}, \withtrack{FPArith}{\seq,\paral,\sat,\unsat,\fast,\inc,\uc}, \withtrack{QF\_Bitvec}{\inc}, \withtrack{QF\_Equality+Bitvec}{\seq,\paral,\sat,\unsat,\fast,\inc,\mv}, \withtrack{QF\_FPArith}{\seq,\paral,\sat,\unsat,\fast,\inc}}{\withtrack{ABVFP}{\sat,\fast}, \withtrack{ABVFPLRA}{\fast}, \withtrack{AUFBV}{\seq,\paral,\sat,\unsat,\fast}, \withtrack{AUFBVFP}{\seq,\paral,\sat,\unsat,\fast}, \withtrack{QF\_ABVFP}{\uc}, \withtrack{QF\_ABVFPLRA}{\uc}, \withtrack{QF\_BVFP}{\uc}, \withtrack{QF\_BVFPLRA}{\uc}, \withtrack{UFBV}{\seq,\paral,\sat,\unsat,\fast}, \withtrack{UFBVFP}{\seq,\paral,\unsat}}{s}{s}
\newpage
\MakeOnePage{Vampire}{}{\withtrack{Equality}{\fast}}{\withtrack{ALIA}{\seq,\paral,\unsat,\fast}, \withtrack{AUFLIA}{\unsat,\fast}, \withtrack{AUFLIRA}{\fast}, \withtrack{AUFNIRA}{\paral,\unsat,\fast}, \withtrack{UF}{\seq,\paral,\sat}, \withtrack{UFDTLIA}{\fast,\uc}, \withtrack{UFDTNIA}{\seq,\paral,\unsat,\fast,\uc}}{}{s}
\newpage
\MakeOnePage{Yices2}{}{\withtrack{QF\_Bitvec}{\uc}, \withtrack{QF\_Equality}{\seq,\paral,\sat,\unsat,\fast,\uc,\mv}, \withtrack{QF\_Equality+Bitvec}{\uc}, \withtrack{QF\_Equality+LinearArith}{\fast,\uc}, \withtrack{QF\_Equality+NonLinearArith}{\sat}, \withtrack{QF\_LinearIntArith}{\fast,\inc,\uc}, \withtrack{QF\_LinearRealArith}{\seq,\paral,\fast,\uc}}{\withtrack{QF\_ALIA}{\unsat}, \withtrack{QF\_AUFBV}{\fast}, \withtrack{QF\_AUFBVLIA}{\inc}, \withtrack{QF\_AUFLIA}{\seq,\paral,\sat,\unsat}, \withtrack{QF\_LIRA}{\seq,\paral,\sat,\unsat,\mv}, \withtrack{QF\_RDL}{\sat,\unsat,\mv}, \withtrack{QF\_UFBVLIA}{\inc}, \withtrack{QF\_UFLIA}{\unsat,\inc}, \withtrack{QF\_UFLRA}{\seq,\paral,\sat,\unsat,\inc,\mv}, \withtrack{QF\_UFNRA}{\seq,\paral,\unsat,\fast,\inc}}{s}{s}
\newpage
\MakeOnePage{YicesQS}{}{\withtrack{Arith}{\sat,\fast}}{\withtrack{LRA}{\seq,\paral,\unsat}, \withtrack{NRA}{\seq,\paral,\unsat}}{}{s}
\newpage
\MakeOnePage{STP}{}{\withtrack{QF\_Bitvec}{\seq,\paral,\sat,\unsat,\fast,\mv}}{}{}{}
\newpage
\MakeOnePage{cvc5}{\withtrack{Biggest Lead}{\seq,\paral,\sat,\unsat,\uc}, \withtrack{Largest Contribution}{\seq,\paral,\sat,\unsat,\fast,\inc,\uc}}{\withtrack{Arith}{\seq,\paral,\unsat,\inc,\uc}, \withtrack{Bitvec}{\seq,\paral,\unsat,\inc,\uc}, \withtrack{Equality}{\seq,\paral,\sat,\unsat,\inc,\uc}, \withtrack{Equality+LinearArith}{\seq,\paral,\sat,\unsat,\fast,\inc,\uc}, \withtrack{Equality+MachineArith}{\seq,\paral,\sat,\unsat,\fast,\uc}, \withtrack{Equality+NonLinearArith}{\seq,\paral,\sat,\unsat,\fast,\inc,\uc}, \withtrack{QF\_Datatypes}{\seq,\paral,\sat,\unsat,\uc\textsuperscript\seq}, \withtrack{QF\_Equality}{\inc}, \withtrack{QF\_Equality+Bitvec+Arith}{\inc}, \withtrack{QF\_Equality+NonLinearArith}{\seq,\paral,\unsat,\fast,\inc,\uc}, \withtrack{QF\_FPArith}{\uc}, \withtrack{QF\_LinearIntArith}{\unsat}, \withtrack{QF\_LinearRealArith}{\unsat}, \withtrack{QF\_NonLinearRealArith}{\unsat,\fast}, \withtrack{QF\_Strings}{\seq,\paral,\sat,\unsat}}{\withtrack{LIA}{\sat,\fast}, \withtrack{NIA}{\sat,\fast}, \withtrack{QF\_ALIA}{\inc}, \withtrack{QF\_AUFLIA}{\uc}, \withtrack{QF\_BVFPLRA}{\inc}, \withtrack{QF\_FP}{\sat}, \withtrack{QF\_IDL}{\uc}, \withtrack{QF\_NIRA}{\seq,\paral,\unsat}, \withtrack{QF\_UFBVDT}{\seq,\paral,\sat,\unsat,\fast}, \withtrack{QF\_UFDTLIRA}{\seq,\paral,\sat,\unsat,\fast,\uc}, \withtrack{QF\_UFLRA}{\uc}, \withtrack{QF\_UFNIA}{\sat}, \withtrack{UFDT}{\fast}}{s}{s}
\newpage
\MakeOnePage{OpenSMT}{}{\withtrack{QF\_Equality+LinearArith}{\unsat}, \withtrack{QF\_LinearRealArith}{\sat,\inc,\mv}}{\withtrack{QF\_LIA}{\seq,\paral}, \withtrack{QF\_LRA}{\seq,\paral,\unsat,\fast}, \withtrack{QF\_UFIDL}{\seq,\paral,\sat,\mv}}{s}{s}
\newpage
\MakeOnePage{z3-alpha}{}{\withtrack{QF\_Strings}{\fast}}{\withtrack{QF\_S}{\sat}, \withtrack{QF\_SNIA}{\seq,\paral,\sat}}{}{s}
\newpage
\MakeOnePage{iProver}{}{}{\withtrack{ANIA}{\unsat}}{}{}
\newpage

### 2023-07-05 2023/slides/presresults/slides.tex
Start of presentation result 2023

--- 2022-08-12 2022/slides/smtWorkshop/slides.tex
@@
 %
-%   SMT-COMP 2022 - Presentation on SMT-Workshop
-%                   virtual conference in "Los Angeles"
+%   SMT-COMP 2023 - 
 %
@@
 %%% Titel, Autor und Datum des Vortrags:
-\title{SMT-COMP 2022\\
-17th International Satisfiability Modulo Theory Competition}
-\author{\emph{Haniel Barbosa} \and Jochen Hoenicke \and Fran\c{c}ois Bobot}
-\date{Aug 11, 2022}
+\title{SMT-COMP 2023\\
+18th International Satisfiability Modulo Theory Competition}
+\author{Martin Bromberger \and Jochen Hoenicke \and \emph{Fran\c{c}ois Bobot}}
+\date{July 5, 2023}
 
@@
 \institute{
-  Universidade Federal de Minas Gerais, Brazil \and
-  Albert-Ludwigs-Universit\"at Freiburg, Germany \and
-  CEA List, France
+CEA List, France \and
+MPI für Informatik, Germany \and
+Certora, Israel
 }
@@
       \begin{block}{Non-incremental}
-        391\,363 instances {\small (+9680)}\\
+        434\,212 instances {\small (+42849)}\\ % 434212-391363=42849
         with 1 query each \\
-        in 81 logics {\small (+2)}.
+        in 83 logics {\small (+2)}.
       \end{block}
@@
       \begin{block}{Incremental}
-        43\,285 instances {\small (+1)}\\
-        with 33\,998\,935 queries {\small (+141)} \\
-        in 39 logics.
+        43\,287 instances {\small (+2)}\\
+        with 34\,036\,491 queries {\small (+37\,556)} \\ %34036491-33998935=37556
+        in 38 logics. % -1 ???
       \end{block}
@@
       \begin{block}{Selected Non-incremental}
-        \only<2>{206\,932 instances}\only<3>{\textcolor{red}{206\,932}
-          instances\\
-          \textcolor{red}{We mistakenly ignored 9466 new benchmarks}
-        }
+        227\,940 instances
       \end{block}
@@
       \begin{block}{Selected Incremental}
-        22\,300 instances
+        22\,302 instances
       \end{block}
@@
 \begin{frame}{Tracks, Solvers, Divisions, and Benchmarks}
-  Teams: 21 (+3)
+  Teams: 25 (+4) %2022 21
   \bigskip
@@
     \hline
-    Single Query  &  22&(+3)  & 19&(+1)  & 93\,945 \\
-    Incremental &  8&(+1)   & 17&(+2)  & 22\,300   \\
-    Unsat Core  &  6&(-1)   & 18&(+1)  & 57\,245  \\
-    Model Validation  &  8&(+1)    &  7& (+ 1 exp.)  & 32\,766  \\
-    Proof Exhibition  &  &4    &  & 18 exp.  & 57\,245  \\
+    Single Query  &  22&(=)  & 19&(=)  & 113\,139 \\
+    Incremental &  7&(-1)   & 17&(=)  & 22\,301   \\
+    Unsat Core  &  6&(=)   & 16&(-1)  & 72\,958  \\
+    Model Validation  &  11&(+3)    &  13& (+ 6 exp.)  & 61\,083  \\
+    Proof Exhibition  &  4&(=)    &  & 19 exp.  & 59\,114  \\
     \hline
-    Parallel &   4&(+1)      &   &14 exp.  & 400 \\
-    Cloud & 4&(-1)      &  &14 exp.  & 400 \\
+    Parallel &   3&(-1)      &   &4 exp.  & 400 \\
+    Cloud & 2&(-2)      &  &4 exp.  & 400 \\
 
@@
 
-  Number in parenthesis shows changes from 2021
+  Number in parenthesis shows changes from 2022
 \end{frame}
@@
   \begin{itemize}
-  \item CDCL(T)
-  \item mcSAT
-  \item saturation
+  \item CDCL(T), Saturation, MCSAT, CP
   \item automata
   \item finite domain
-  \item CP
   \item local search
@@
   \bigskip
-  Six new solvers participated:
+  Seven new solvers participated:
   \begin{itemize}
-  \item NRA-LS   {\footnotesize (Liu et al.)}
-  \item OSTRICH {\footnotesize (Chen et al.)}
-  \item Yices-ismt {\footnotesize (Jia et al.)}
-  \item Z3++ {\footnotesize (Cai et al.)}
-  \item solsmt {\footnotesize (Reitwiessner and Soos)}
+\item iProver {\footnotesize (Korovin et al.)}
+\item SMT-RAT-MCSAT {\footnotesize (Jasper Nalbach et al.)}
+\item UltimateIntBlastingWrapper+SMTInterpol {\footnotesize (Max Barth et al.)}
+\item Yaga {\footnotesize (Hanák et al.)}
+\item Z3-alpha {\footnotesize (Lu et al.)}
+\item Z3-Noodler {\footnotesize (Havlena et al.)}
+\item Z3-Owl {\footnotesize (Ma et al.)}
 \end{itemize}
@@
 
-{
+\newcommand{\myincludepdf}[1]{
 \begin{frame}
@@
   \noindent\makebox[\textwidth]{%
-    \includegraphics[height=\paperheight]{slide-bitwuzla.pdf}}
+    \includegraphics[height=\paperheight]{#1}}
 \end{frame}
@@
 
-{
-\begin{frame}
-  \vspace*{-1pt}%
-  \noindent\makebox[\textwidth]{%
-    \includegraphics[height=\paperheight]{slide-colibri.pdf}}
-\end{frame}
-}
-
-{
-\begin{frame}
-  \vspace*{-1pt}%
-  \noindent\makebox[\textwidth]{%
-    \includegraphics[height=\paperheight]{slide-cvc5.pdf}}
-\end{frame}
-}
-
-{
-\begin{frame}
-  \vspace*{-1pt}%
-  \noindent\makebox[\textwidth]{%
-    \includegraphics[height=\paperheight]{slide-cvc5-cloud.pdf}}
-\end{frame}
-}
-
-{
-\begin{frame}
-  \vspace*{-1pt}%
-  \noindent\makebox[\textwidth]{%
-    \includegraphics[height=\paperheight]{slide-nra-ls.pdf}}
-\end{frame}
-}
-
-{
-\begin{frame}
-  \vspace*{-1pt}%
-  \noindent\makebox[\textwidth]{%
-    \includegraphics[height=\paperheight]{slide-opensmt.pdf}}
-\end{frame}
-}
-
-{
-\begin{frame}
-  \vspace*{-1pt}%
-  \noindent\makebox[\textwidth]{%
-    \includegraphics[height=\paperheight]{slide-smtinterpol.pdf}}
-\end{frame}
-}
-
-{
-\begin{frame}
-  \vspace*{-1pt}%
-  \noindent\makebox[\textwidth]{%
-    \includegraphics[height=\paperheight]{slide-smtrat.pdf}}
-\end{frame}
-}
-
-{
-\begin{frame}
-  \vspace*{-1pt}%
-  \noindent\makebox[\textwidth]{%
-    \includegraphics[height=\paperheight]{slide-solsmt.pdf}}
-\end{frame}
-}
-
-{
-\begin{frame}
-  \vspace*{-1pt}%
-  \noindent\makebox[\textwidth]{%
-    \includegraphics[height=\paperheight]{slide-stp.pdf}}
-\end{frame}
-}
-
-{
-\begin{frame}
-  \vspace*{-1pt}%
-  \noindent\makebox[\textwidth]{%
-    \includegraphics[height=\paperheight]{slide-verit.pdf}}
-\end{frame}
-}
-
-{
-\begin{frame}
-  \vspace*{-1pt}%
-  \noindent\makebox[\textwidth]{%
-    \includegraphics[height=\paperheight]{slide-yices.pdf}}
-\end{frame}
-}
-
-{
-\begin{frame}
-  \vspace*{-1pt}%
-  \noindent\makebox[\textwidth]{%
-    \includegraphics[height=\paperheight]{slide-yices-ismt.pdf}}
-\end{frame}
-}
-
-{
-\begin{frame}
-  \vspace*{-1pt}%
-  \noindent\makebox[\textwidth]{%
-    \includegraphics[height=\paperheight]{slide-yices-qs.pdf}}
-\end{frame}
-}
-
-{
-\begin{frame}
-  \vspace*{-1pt}%
-  \noindent\makebox[\textwidth]{%
-    \includegraphics[height=\paperheight]{slide-z3pp.pdf}}
-\end{frame}
-}
-
-{
   \begin{frame}
@@
   \end{frame}
-}
 
@@
 
-\begin{frame}{Division Winners}
-  \pause
-  \emph{Single Query, sequential score}
-  \begin{itemize}
-  \item \emph{Bitwuzla}: {\small FPArith, QF\_Bitvec, QF\_Equality+Bitvec, QF\_FPArith}
+{
+  \newcommand{\seq}{\texttt{;}}
+  \newcommand{\paral}{\textbardbl}
+  \newcommand{\sat}{$\top$}
+  \newcommand{\unsat}{$\bot$}
+  \newcommand{\fast}{\texttt{24}}
+  \newcommand{\inc}{inc}
+  \newcommand{\uc}{uc}
+  \newcommand{\mv}{mv}
+  \newcommand{\cloud}{cloud}
+  \newcommand{\paralTrack}{parallel}
+  %\newcommand{\all}{{\footnotesize (\seq,\paral,\sat,\unsat,\fast,\inc,\uc\seq,\uc\paral,\mv)}}
+  \newcommand{\withtrack}[2]{\textsc{#1}{{\footnotesize (#2)}}}
 
-  \item \emph{cvc5}: \begin{minipage}{.8\textwidth}\raggedright \tiny Arith,
-    Bitvec, Equality, Equality+LinearArith, Equality+MachineArith,
-    Equality+NonLinearArith, QF\_Datatypes, QF\_Equality+NonLinearArith, QF\_NonLinearIntArith, QF\_NonLinearRealArith, QF\_Strings\end{minipage}
+\def\newpage{}
 
-  \item \emph{OpenSMT}: {\small QF\_LinearIntArith}
-
-  \item \emph{SMTInterpol}: {\small QF\_Equality+LinearArith}
-
-  \item \emph{Yices2}: {\small QF\_Equality, QF\_LinearRealArith}
-  \end{itemize}
+\newcommand{\MakeOnePage}[6]{
+    \begin{frame}
+    \frametitle{#1}
 
     \medskip
+    \ifstrempty{#2}{}{
+    \textcolor{red!30!black!90}
+    {\textit{Overall Winner}}
 
-  \pause
-  \emph{Unsat Core}
-  \begin{itemize}
-\item \emph{cvc5}: Arith, Bitvec, Equality+LinearArith, Equality+MachineArith,Equality+NonLinearArith,Equality(Seq), QF\_Datatypes
-\item \emph{Vampire}: Equality(Par)
-\item \emph{Bitwuzla}: QF\_EqualityBitvec, QF\_FPArith
-\item \emph{Yices2}: QF\_Bitvec, QF\_Equality+LinearArith, QF\_Equality, QF\_LinearIntArith, QF\_LinearRealArith
-\item \emph{SMTInterpol}: QF\_Equality+NonLinearArith
-\item \emph{UltimateEliminator+MathSAT}: FPArith
+    \textcolor{black}{\large #2}
 
-  \end{itemize}
+     \medskip
+    }
 
+    \ifstrempty{#3}{}{
+    \textcolor{red!30!black!90} {\textit{Winner of the Division#5}}
+
+     \textcolor{black}{\large#3}
+
+     \medskip
+    }
+
+    \ifstrempty{#4}{}{
+     \textcolor{red!30!black!90}  {\textit{Winner of the Logic#6
+      \ifstrempty{#3}{}{(where it did not win the corresponding division)}}}
+
+     \textcolor{black}{\large #4}
+    }
+    \vspace{2mm}
     \end{frame}
+}
 
-\begin{frame}{Division Winners}
-  \emph{Incremental}
-  \begin{itemize}
-\item \emph{cvc5}: Arith, Bitvec, Equality+LinearArith,EqualityNonLinearArith,Equality
-\item \emph{UltimateEliminator+MathSAT}: Equality+MachineArith
-\item \emph{Bitwuzla}: FPArith, QF\_FPArith
-\item \emph{Yices2}: QF\_Bitvec, QF\_Equality+Bitvec, QF\_Equality, QF\_LinearIntArith
-\item \emph{SMTInterpol}: QF\_Equality+LinearArith, QF\_Equality+NonLinearArith, QF\_NonLinearIntArith
-\item \emph{OpenSMT}: QF\_LinearRealArith
-  \end{itemize}
-  \medskip
+\input{input_for_certificates.tex}
 
-  \pause
-  \emph{Model Validation (competitive only)}
-  \begin{itemize}
-\item \emph{Bitwuzla}: QF\_Bitvec, QF\_Equality+Bitvec,
-\item \emph{smtinterpol}: QF\_Equality+LinearArith
-\item \emph{Yices2}: QF\_Equality
-\item \emph{Z3++}: QF\_LinearIntArith
-\item \emph{OpenSMT}: QF\_LinearRealArith
+}
 
-\item experimental: QF\_FPArith : Bitwuzla, cvc5
+% \begin{frame}{Division Winners}
+%   \pause
+%   \emph{Single Query, sequential score}
+%   \begin{itemize}
+%   \item \emph{Bitwuzla}: {\small FPArith, QF\_Bitvec, QF\_Equality+Bitvec, QF\_FPArith}
 
-  \end{itemize}
-\end{frame}
+%   \item \emph{cvc5}: \begin{minipage}{.8\textwidth}\raggedright \tiny Arith,
+%     Bitvec, Equality, Equality+LinearArith, Equality+MachineArith,
+%     Equality+NonLinearArith, QF\_Datatypes, QF\_Equality+NonLinearArith, QF\_NonLinearIntArith, QF\_NonLinearRealArith, QF\_Strings\end{minipage}
 
-\begin{frame}{Largest contribution}
-  \begin{tabular}{r|c@{}lc@{}lc@{}l}
-    &\textcolor{gold}{\textbf{1st Place}} &&
-    \textcolor{silver}{\textbf{2nd Place}} &&
-    \textcolor{bronze}{\textbf{3rd Place}}\\
-    \hline
-    \emph{Single Query}\\
-    seq & cvc5&{\tiny(Eq+MA)} & YicesQS&{\tiny(Arith)} & Bitwuzla&{\tiny(FPArith)} \\
-    par & cvc5&{\tiny(Eq+MA)} & YicesQS&{\tiny(Arith)} & Bitwuzla&{\tiny(FPArith)} \\
-    sat & cvc5&{\tiny(Eq+LA)} & YicesQS&{\tiny(Arith)} & Bitwuzla&{\tiny(FPArith)} \\
-    unsat & cvc5&{\tiny(Eq+MA)} & Z3++&{\tiny(QF\_NonLIA)} & OSTRICH&{\tiny(QF\_Strings)}\\
-    24 &  Vampire&{\tiny(Eq+NA)} & Vampire&{\tiny(Equality)} & Yices2&{\tiny(QF\_LinIA)}\\[3pt]
-    \pause
-    \emph{Incremental}\\
-    par & cvc5&{\tiny(Eq+NA)} &Yices2&{\tiny(QF\_Eq+LA)}
-    &SMTInterpol&{\tiny(QF\_Eq+NA)}\\[3pt]
-    \pause
+%   \item \emph{OpenSMT}: {\small QF\_LinearIntArith}
 
-    \emph{Unsat Core}\\
-    seq & cvc5&{\tiny(Eq+LA)} &
-    Bitwuzla&{\tiny(QF\_Eq+Bitvec)}\\
+%   \item \emph{SMTInterpol}: {\small QF\_Equality+LinearArith}
 
-    par &  cvc5&{\tiny(Eq+NA)}&
-    Bitwuzla&{\tiny(QF\_Eq+Bitvec)}\\
-\\[3pt]
-    \pause
-    \emph{Model Validation}\\
-    seq &  Z3++&{\tiny(QF\_LinIA)} & Bitwuzla&{\tiny(QF\_Bitvec)}
-        & smtinterpol&{\tiny(QF\_Eq+LIA)}\\
-    par &  Z3++&{\tiny(QF\_LinIA)} & Bitwuzla&{\tiny(QF\_Bitvec)}
-        & smtinterpol&{\tiny(QF\_Eq+LIA)}\\
-  \end{tabular}
-\end{frame}
+%   \item \emph{Yices2}: {\small QF\_Equality, QF\_LinearRealArith}
+%   \end{itemize}
 
-\begin{frame}{Biggest Lead}
-  \begin{tabular}{r|c@{}lc@{}lc@{}l}
-    &\textcolor{gold}{\textbf{1st Place}} &&
-    \textcolor{silver}{\textbf{2nd Place}} &&
-    \textcolor{bronze}{\textbf{3rd Place}}\\
-    \hline
-    \emph{Single Query}\\
-    seq & cvc5&{\tiny(QF\_DT)} & Bitwuzla&{\tiny(FPArith)} & Yices2&{\tiny(QF\_LinRA)} \\
-    par & cvc5&{\tiny(QF\_DT)} & Bitwuzla&{\tiny(FPArith)} & Yices2&{\tiny(QF\_LinRA)} \\
-    sat & cvc5&{\tiny(QF\_DT)} & Bitwuzla&{\tiny(FPArith)} & Z3++&{\tiny(QF\_NonRA)} \\
-    unsat & cvc5&{\tiny(QF\_DT)} & Z3++&{\tiny(QF\_NonIA)} & Bitwuzla&{\tiny(FPArith)} \\
-    24 &  cvc5&{\tiny(Eq+MA)} & smtinterpol&{\tiny(QF\_DT)} & Vampire&{\tiny(Equality)}\\[3pt]
-    \pause
-    \emph{Incremental}\\
-    par & SMTInterpol&{\tiny(QF\_NIA)}
-    &Yices2&{\tiny(QF\_LinIA)} & cvc5&{\tiny(Eq+NonLA)} \\[3pt]
-    \pause
-    \emph{Unsat Core}\\
-    seq & cvc5&{\tiny(Eq+MA)} &    Yices2&{\tiny(QF\_Eq+LA)} &    smtinterpol&{\tiny(QF\_Eq+NA)} \\
-    par & cvc5&{\tiny(Eq+MA)} &    Yices2&{\tiny(QF\_Eq+LA)} &    smtinterpol&{\tiny(QF\_Eq+NA)} \\
-    \pause
-    \emph{Model Validation}\\
-    seq &  Z3++&{\tiny(QF\_LinIA)} & smtinterpol&{\tiny(QF\_LinA)}        & OpenSMT&{\tiny(QF\_LinRA)} \\
-    par &  Z3++&{\tiny(QF\_LinIA)} & smtinterpol&{\tiny(QF\_LinA)}        & OpenSMT&{\tiny(QF\_LinRA)} \\
-  \end{tabular}
-\end{frame}
+%   \medskip
+
+%   \pause
+%   \emph{Unsat Core}
+%   \begin{itemize}
+% \item \emph{cvc5}: Arith, Bitvec, Equality+LinearArith, Equality+MachineArith,Equality+NonLinearArith,Equality(Seq), QF\_Datatypes
+% \item \emph{Vampire}: Equality(Par)
+% \item \emph{Bitwuzla}: QF\_EqualityBitvec, QF\_FPArith
+% \item \emph{Yices2}: QF\_Bitvec, QF\_Equality+LinearArith, QF\_Equality, QF\_LinearIntArith, QF\_LinearRealArith
+% \item \emph{SMTInterpol}: QF\_Equality+NonLinearArith
+% \item \emph{UltimateEliminator+MathSAT}: FPArith
+
+%   \end{itemize}
+
+% \end{frame}
+
+% \begin{frame}{Division Winners}
+%   \emph{Incremental}
+%   \begin{itemize}
+% \item \emph{cvc5}: Arith, Bitvec, Equality+LinearArith,EqualityNonLinearArith,Equality
+% \item \emph{UltimateEliminator+MathSAT}: Equality+MachineArith
+% \item \emph{Bitwuzla}: FPArith, QF\_FPArith
+% \item \emph{Yices2}: QF\_Bitvec, QF\_Equality+Bitvec, QF\_Equality, QF\_LinearIntArith
+% \item \emph{SMTInterpol}: QF\_Equality+LinearArith, QF\_Equality+NonLinearArith, QF\_NonLinearIntArith
+% \item \emph{OpenSMT}: QF\_LinearRealArith
+%   \end{itemize}
+%   \medskip
+
+%   \pause
+%   \emph{Model Validation (competitive only)}
+%   \begin{itemize}
+% \item \emph{Bitwuzla}: QF\_Bitvec, QF\_Equality+Bitvec,
+% \item \emph{smtinterpol}: QF\_Equality+LinearArith
+% \item \emph{Yices2}: QF\_Equality
+% \item \emph{Z3++}: QF\_LinearIntArith
+% \item \emph{OpenSMT}: QF\_LinearRealArith
+
+% \item experimental: QF\_FPArith : Bitwuzla, cvc5
+
+%   \end{itemize}
+% \end{frame}
+
+% \begin{frame}{Largest contribution}
+%   \begin{tabular}{r|c@{}lc@{}lc@{}l}
+%     &\textcolor{gold}{\textbf{1st Place}} &&
+%     \textcolor{silver}{\textbf{2nd Place}} &&
+%     \textcolor{bronze}{\textbf{3rd Place}}\\
+%     \hline
+%     \emph{Single Query}\\
+%     seq & cvc5&{\tiny(Eq+MA)} & YicesQS&{\tiny(Arith)} & Bitwuzla&{\tiny(FPArith)} \\
+%     par & cvc5&{\tiny(Eq+MA)} & YicesQS&{\tiny(Arith)} & Bitwuzla&{\tiny(FPArith)} \\
+%     sat & cvc5&{\tiny(Eq+LA)} & YicesQS&{\tiny(Arith)} & Bitwuzla&{\tiny(FPArith)} \\
+%     unsat & cvc5&{\tiny(Eq+MA)} & Z3++&{\tiny(QF\_NonLIA)} & OSTRICH&{\tiny(QF\_Strings)}\\
+%     24 &  Vampire&{\tiny(Eq+NA)} & Vampire&{\tiny(Equality)} & Yices2&{\tiny(QF\_LinIA)}\\[3pt]
+%     \pause
+%     \emph{Incremental}\\
+%     par & cvc5&{\tiny(Eq+NA)} &Yices2&{\tiny(QF\_Eq+LA)}
+%     &SMTInterpol&{\tiny(QF\_Eq+NA)}\\[3pt]
+%     \pause
+
+%     \emph{Unsat Core}\\
+%     seq & cvc5&{\tiny(Eq+LA)} &
+%     Bitwuzla&{\tiny(QF\_Eq+Bitvec)}\\
+
+%     par &  cvc5&{\tiny(Eq+NA)}&
+%     Bitwuzla&{\tiny(QF\_Eq+Bitvec)}\\
+% \\[3pt]
+%     \pause
+%     \emph{Model Validation}\\
+%     seq &  Z3++&{\tiny(QF\_LinIA)} & Bitwuzla&{\tiny(QF\_Bitvec)}
+%         & smtinterpol&{\tiny(QF\_Eq+LIA)}\\
+%     par &  Z3++&{\tiny(QF\_LinIA)} & Bitwuzla&{\tiny(QF\_Bitvec)}
+%         & smtinterpol&{\tiny(QF\_Eq+LIA)}\\
+%   \end{tabular}
+% \end{frame}
+
+% \begin{frame}{Biggest Lead}
+%   \begin{tabular}{r|c@{}lc@{}lc@{}l}
+%     &\textcolor{gold}{\textbf{1st Place}} &&
+%     \textcolor{silver}{\textbf{2nd Place}} &&
+%     \textcolor{bronze}{\textbf{3rd Place}}\\
+%     \hline
+%     \emph{Single Query}\\
+%     seq & cvc5&{\tiny(QF\_DT)} & Bitwuzla&{\tiny(FPArith)} & Yices2&{\tiny(QF\_LinRA)} \\
+%     par & cvc5&{\tiny(QF\_DT)} & Bitwuzla&{\tiny(FPArith)} & Yices2&{\tiny(QF\_LinRA)} \\
+%     sat & cvc5&{\tiny(QF\_DT)} & Bitwuzla&{\tiny(FPArith)} & Z3++&{\tiny(QF\_NonRA)} \\
+%     unsat & cvc5&{\tiny(QF\_DT)} & Z3++&{\tiny(QF\_NonIA)} & Bitwuzla&{\tiny(FPArith)} \\
+%     24 &  cvc5&{\tiny(Eq+MA)} & smtinterpol&{\tiny(QF\_DT)} & Vampire&{\tiny(Equality)}\\[3pt]
+%     \pause
+%     \emph{Incremental}\\
+%     par & SMTInterpol&{\tiny(QF\_NIA)}
+%     &Yices2&{\tiny(QF\_LinIA)} & cvc5&{\tiny(Eq+NonLA)} \\[3pt]
+%     \pause
+%     \emph{Unsat Core}\\
+%     seq & cvc5&{\tiny(Eq+MA)} &    Yices2&{\tiny(QF\_Eq+LA)} &    smtinterpol&{\tiny(QF\_Eq+NA)} \\
+%     par & cvc5&{\tiny(Eq+MA)} &    Yices2&{\tiny(QF\_Eq+LA)} &    smtinterpol&{\tiny(QF\_Eq+NA)} \\
+%     \pause
+%     \emph{Model Validation}\\
+%     seq &  Z3++&{\tiny(QF\_LinIA)} & smtinterpol&{\tiny(QF\_LinA)}        & OpenSMT&{\tiny(QF\_LinRA)} \\
+%     par &  Z3++&{\tiny(QF\_LinIA)} & smtinterpol&{\tiny(QF\_LinA)}        & OpenSMT&{\tiny(QF\_LinRA)} \\
+%   \end{tabular}
+% \end{frame}
 
@@
 
-  \vitem Only 18 benchmarks with disagreements (AUFDTLIA, QF\_NIA)
+  \vitem 300 benchmarks with disagreements (ABV,
+  BV,
+  LIA,
+  NIA,
+  QF\_ABV,
+  QF\_AUFBV,
+  QF\_BVFP,
+  QF\_FP,
+  QF\_NRA,
+  QF\_SLIA,
+  UF,
+  UFDT,
+  UFDTLIRA)
 
@@
 
-  \vitem We had only three solvers with soundness issues: SMTIinterpol, Z3++,
-  yices-ismt
-  \begin{itemize}
-    \item Down from 10 last year
-    \pause
-    {\tiny (but note that this may be because of our issue with ignoring most of the
-    new benchmarks in the selection)}
-
-  \end{itemize}
+  \vitem We had only ??? solvers with soundness issues: 
   \end{itemize}

### 2023-07-06 2023/slides/presresults/input_for_certificates.tex
SMTCOMP presentation

@@
+\MakeOnePage{Bitwuzla}{\withtrack{Biggest Lead}{\inc}}{\withtrack{Bitvec}{\sat,\fast}, \withtrack{Equality+MachineArith}{\inc}, \withtrack{FPArith}{\seq,\paral,\sat,\unsat,\fast,\inc,\uc}, \withtrack{QF\_ADT+BitVec}{\mv}, \withtrack{QF\_Bitvec}{\inc}, \withtrack{QF\_Equality+Bitvec}{\seq,\paral,\sat,\unsat,\fast,\inc,\mv}, \withtrack{QF\_FPArith}{\seq,\paral,\sat,\unsat,\fast,\inc,\mv}}{\withtrack{ABVFP}{\sat,\fast}, \withtrack{ABVFPLRA}{\fast}, \withtrack{AUFBV}{\seq,\paral,\sat,\unsat,\fast}, \withtrack{AUFBVFP}{\seq,\paral,\sat,\unsat,\fast}, \withtrack{QF\_ABVFP}{\uc}, \withtrack{QF\_ABVFPLRA}{\uc}, \withtrack{QF\_BVFP}{\uc}, \withtrack{QF\_BVFPLRA}{\uc}, \withtrack{UFBV}{\seq,\paral,\sat,\unsat,\fast}, \withtrack{UFBVFP}{\seq,\paral,\unsat}}{s}{s}
+\newpage
 \MakeOnePage{COLIBRI}{}{}{\withtrack{QF\_ABVFPLRA}{\seq,\paral,\unsat,\fast}, \withtrack{QF\_FP}{\unsat,\fast}, \withtrack{QF\_FPLRA}{\unsat,\fast}}{}{s}
 \newpage
-\MakeOnePage{Z3++}{\withtrack{Biggest Lead}{\mv}, \withtrack{Largest Contribution}{\mv}}{\withtrack{QF\_LinearIntArith}{\seq,\paral,\sat,\mv}, \withtrack{QF\_NonLinearIntArith}{\seq,\paral,\sat,\unsat,\fast}, \withtrack{QF\_NonLinearRealArith}{\seq,\paral,\sat}}{\withtrack{QF\_IDL}{\unsat}}{s}{}
+\MakeOnePage{cvc5}{\withtrack{Biggest Lead}{\seq,\paral,\sat,\unsat,\uc}, \withtrack{Largest Contribution}{\seq,\paral,\sat,\unsat,\fast,\inc,\uc}}{\withtrack{Arith}{\seq,\paral,\unsat,\inc,\uc}, \withtrack{Bitvec}{\seq,\paral,\unsat,\inc,\uc}, \withtrack{Equality}{\seq,\paral,\sat,\unsat,\inc,\uc}, \withtrack{Equality+LinearArith}{\seq,\paral,\sat,\unsat,\fast,\inc,\uc}, \withtrack{Equality+MachineArith}{\seq,\paral,\sat,\unsat,\fast,\uc}, \withtrack{Equality+NonLinearArith}{\seq,\paral,\sat,\unsat,\fast,\inc,\uc}, \withtrack{QF\_Datatypes}{\seq,\paral,\sat,\unsat,\uc\textsuperscript\seq}, \withtrack{QF\_Equality}{\inc}, \withtrack{QF\_Equality+Bitvec+Arith}{\inc}, \withtrack{QF\_Equality+NonLinearArith}{\seq,\paral,\unsat,\fast,\inc,\uc,\mv}, \withtrack{QF\_FPArith}{\uc}, \withtrack{QF\_LinearIntArith}{\unsat}, \withtrack{QF\_LinearRealArith}{\unsat}, \withtrack{QF\_NonLinearRealArith}{\unsat,\fast}, \withtrack{QF\_Strings}{\seq,\paral,\sat,\unsat}}{\withtrack{LIA}{\sat,\fast}, \withtrack{NIA}{\sat,\fast}, \withtrack{QF\_ALIA}{\inc}, \withtrack{QF\_AUFLIA}{\uc,\mv}, \withtrack{QF\_AX}{\mv}, \withtrack{QF\_BVFPLRA}{\inc}, \withtrack{QF\_FP}{\sat,\mv}, \withtrack{QF\_IDL}{\uc}, \withtrack{QF\_NIRA}{\seq,\paral,\unsat}, \withtrack{QF\_UFBVDT}{\seq,\paral,\sat,\unsat,\fast}, \withtrack{QF\_UFDTLIRA}{\seq,\paral,\sat,\unsat,\fast,\uc}, \withtrack{QF\_UFLRA}{\uc}, \withtrack{QF\_UFNIA}{\sat}, \withtrack{UFDT}{\fast}, \withtrack{UFDTLIA}{\cloud}, \withtrack{UFNIA}{\cloud}}{s}{s}
+\newpage
+\MakeOnePage{iProver}{}{}{\withtrack{ANIA}{\unsat}}{}{}
+\newpage
+\MakeOnePage{OpenSMT}{}{\withtrack{QF\_Equality+LinearArith}{\unsat}, \withtrack{QF\_LinearRealArith}{\sat,\inc,\mv}}{\withtrack{QF\_LIA}{\seq,\paral}, \withtrack{QF\_LRA}{\seq,\paral,\unsat,\fast}, \withtrack{QF\_UFIDL}{\seq,\paral,\sat,\mv}}{s}{s}
 \newpage
@@
 \newpage
-\MakeOnePage{SMTInterpol}{\withtrack{Biggest Lead}{\fast}}{\withtrack{QF\_Datatypes}{\fast,\uc\textsuperscript\paral}, \withtrack{QF\_Equality+LinearArith}{\seq,\paral,\sat,\inc,\mv}, \withtrack{QF\_NonLinearIntArith}{\inc}}{\withtrack{ALIA}{\sat,\uc}, \withtrack{AUFDTLIA}{\uc}, \withtrack{QF\_ALIA}{\uc}, \withtrack{QF\_ANIA}{\seq,\paral,\sat,\unsat,\fast,\inc,\uc}, \withtrack{QF\_AUFNIA}{\seq,\paral,\sat,\unsat,\fast,\uc}, \withtrack{QF\_LIA}{\unsat}, \withtrack{QF\_UF}{\uc\textsuperscript\paral}, \withtrack{QF\_UFDT}{\uc\textsuperscript\seq}, \withtrack{QF\_UFDTLIA}{\unsat,\fast,\uc}, \withtrack{UFIDL}{\sat}, \withtrack{UFLIA}{\sat}}{s}{s}
+\MakeOnePage{SMTInterpol}{\withtrack{Biggest Lead}{\fast}}{\withtrack{QF\_ADT+LinArith}{\mv}, \withtrack{QF\_Datatypes}{\fast,\uc\textsuperscript\paral,\mv}, \withtrack{QF\_Equality+LinearArith}{\seq,\paral,\sat,\inc,\mv}, \withtrack{QF\_NonLinearIntArith}{\inc}}{\withtrack{ALIA}{\sat,\uc}, \withtrack{AUFDTLIA}{\uc}, \withtrack{QF\_ALIA}{\uc}, \withtrack{QF\_ANIA}{\seq,\paral,\sat,\unsat,\fast,\inc,\uc}, \withtrack{QF\_AUFNIA}{\seq,\paral,\sat,\unsat,\fast,\uc}, \withtrack{QF\_LIA}{\unsat}, \withtrack{QF\_UF}{\uc\textsuperscript\paral}, \withtrack{QF\_UFDT}{\uc\textsuperscript\seq}, \withtrack{QF\_UFDTLIA}{\unsat,\fast,\uc}, \withtrack{UFIDL}{\sat}, \withtrack{UFLIA}{\sat}}{s}{s}
 \newpage
-\MakeOnePage{Bitwuzla}{\withtrack{Biggest Lead}{\inc}}{\withtrack{Bitvec}{\sat,\fast}, \withtrack{Equality+MachineArith}{\inc}, \withtrack{FPArith}{\seq,\paral,\sat,\unsat,\fast,\inc,\uc}, \withtrack{QF\_Bitvec}{\inc}, \withtrack{QF\_Equality+Bitvec}{\seq,\paral,\sat,\unsat,\fast,\inc,\mv}, \withtrack{QF\_FPArith}{\seq,\paral,\sat,\unsat,\fast,\inc}}{\withtrack{ABVFP}{\sat,\fast}, \withtrack{ABVFPLRA}{\fast}, \withtrack{AUFBV}{\seq,\paral,\sat,\unsat,\fast}, \withtrack{AUFBVFP}{\seq,\paral,\sat,\unsat,\fast}, \withtrack{QF\_ABVFP}{\uc}, \withtrack{QF\_ABVFPLRA}{\uc}, \withtrack{QF\_BVFP}{\uc}, \withtrack{QF\_BVFPLRA}{\uc}, \withtrack{UFBV}{\seq,\paral,\sat,\unsat,\fast}, \withtrack{UFBVFP}{\seq,\paral,\unsat}}{s}{s}
+\MakeOnePage{STP}{}{\withtrack{QF\_Bitvec}{\seq,\paral,\sat,\unsat,\fast,\mv}}{}{}{}
 \newpage
-\MakeOnePage{Vampire}{}{\withtrack{Equality}{\fast}}{\withtrack{ALIA}{\seq,\paral,\unsat,\fast}, \withtrack{AUFLIA}{\unsat,\fast}, \withtrack{AUFLIRA}{\fast}, \withtrack{AUFNIRA}{\paral,\unsat,\fast}, \withtrack{UF}{\seq,\paral,\sat}, \withtrack{UFDTLIA}{\fast,\uc}, \withtrack{UFDTNIA}{\seq,\paral,\unsat,\fast,\uc}}{}{s}
+\MakeOnePage{Vampire}{\withtrack{Biggest Lead}{\cloud,\paralTrack}}{\withtrack{Arith}{\cloud,\paralTrack}, \withtrack{Equality}{\fast,\cloud,\paralTrack}, \withtrack{Equality+LinearArith}{\cloud,\paralTrack}, \withtrack{Equality+NonLinearArith}{\cloud,\paralTrack}}{\withtrack{ALIA}{\seq,\paral,\unsat,\fast}, \withtrack{AUFLIA}{\unsat,\fast}, \withtrack{AUFLIRA}{\fast}, \withtrack{AUFNIRA}{\paral,\unsat,\fast}, \withtrack{UF}{\seq,\paral,\sat}, \withtrack{UFDTLIA}{\fast,\uc}, \withtrack{UFDTNIA}{\seq,\paral,\unsat,\fast,\uc}}{s}{s}
 \newpage
-\MakeOnePage{Yices2}{}{\withtrack{QF\_Bitvec}{\uc}, \withtrack{QF\_Equality}{\seq,\paral,\sat,\unsat,\fast,\uc,\mv}, \withtrack{QF\_Equality+Bitvec}{\uc}, \withtrack{QF\_Equality+LinearArith}{\fast,\uc}, \withtrack{QF\_Equality+NonLinearArith}{\sat}, \withtrack{QF\_LinearIntArith}{\fast,\inc,\uc}, \withtrack{QF\_LinearRealArith}{\seq,\paral,\fast,\uc}}{\withtrack{QF\_ALIA}{\unsat}, \withtrack{QF\_AUFBV}{\fast}, \withtrack{QF\_AUFBVLIA}{\inc}, \withtrack{QF\_AUFLIA}{\seq,\paral,\sat,\unsat}, \withtrack{QF\_LIRA}{\seq,\paral,\sat,\unsat,\mv}, \withtrack{QF\_RDL}{\sat,\unsat,\mv}, \withtrack{QF\_UFBVLIA}{\inc}, \withtrack{QF\_UFLIA}{\unsat,\inc}, \withtrack{QF\_UFLRA}{\seq,\paral,\sat,\unsat,\inc,\mv}, \withtrack{QF\_UFNRA}{\seq,\paral,\unsat,\fast,\inc}}{s}{s}
+\MakeOnePage{Yices2}{}{\withtrack{QF\_Bitvec}{\uc}, \withtrack{QF\_Equality}{\seq,\paral,\sat,\unsat,\fast,\uc,\mv}, \withtrack{QF\_Equality+Bitvec}{\uc}, \withtrack{QF\_Equality+LinearArith}{\fast,\uc}, \withtrack{QF\_Equality+NonLinearArith}{\sat}, \withtrack{QF\_LinearIntArith}{\fast,\inc,\uc}, \withtrack{QF\_LinearRealArith}{\seq,\paral,\fast,\uc}}{\withtrack{QF\_ALIA}{\unsat}, \withtrack{QF\_AUFBV}{\fast}, \withtrack{QF\_AUFBVLIA}{\inc}, \withtrack{QF\_AUFLIA}{\seq,\paral,\sat,\unsat}, \withtrack{QF\_LIRA}{\seq,\paral,\sat,\unsat,\mv}, \withtrack{QF\_RDL}{\sat,\unsat,\mv}, \withtrack{QF\_UFBVLIA}{\inc}, \withtrack{QF\_UFLIA}{\unsat,\inc}, \withtrack{QF\_UFLRA}{\seq,\paral,\sat,\unsat,\inc,\mv}, \withtrack{QF\_UFNRA}{\seq,\paral,\unsat,\fast,\inc,\mv}}{s}{s}
 \newpage
@@
 \newpage
-\MakeOnePage{STP}{}{\withtrack{QF\_Bitvec}{\seq,\paral,\sat,\unsat,\fast,\mv}}{}{}{}
-\newpage
-\MakeOnePage{cvc5}{\withtrack{Biggest Lead}{\seq,\paral,\sat,\unsat,\uc}, \withtrack{Largest Contribution}{\seq,\paral,\sat,\unsat,\fast,\inc,\uc}}{\withtrack{Arith}{\seq,\paral,\unsat,\inc,\uc}, \withtrack{Bitvec}{\seq,\paral,\unsat,\inc,\uc}, \withtrack{Equality}{\seq,\paral,\sat,\unsat,\inc,\uc}, \withtrack{Equality+LinearArith}{\seq,\paral,\sat,\unsat,\fast,\inc,\uc}, \withtrack{Equality+MachineArith}{\seq,\paral,\sat,\unsat,\fast,\uc}, \withtrack{Equality+NonLinearArith}{\seq,\paral,\sat,\unsat,\fast,\inc,\uc}, \withtrack{QF\_Datatypes}{\seq,\paral,\sat,\unsat,\uc\textsuperscript\seq}, \withtrack{QF\_Equality}{\inc}, \withtrack{QF\_Equality+Bitvec+Arith}{\inc}, \withtrack{QF\_Equality+NonLinearArith}{\seq,\paral,\unsat,\fast,\inc,\uc}, \withtrack{QF\_FPArith}{\uc}, \withtrack{QF\_LinearIntArith}{\unsat}, \withtrack{QF\_LinearRealArith}{\unsat}, \withtrack{QF\_NonLinearRealArith}{\unsat,\fast}, \withtrack{QF\_Strings}{\seq,\paral,\sat,\unsat}}{\withtrack{LIA}{\sat,\fast}, \withtrack{NIA}{\sat,\fast}, \withtrack{QF\_ALIA}{\inc}, \withtrack{QF\_AUFLIA}{\uc}, \withtrack{QF\_BVFPLRA}{\inc}, \withtrack{QF\_FP}{\sat}, \withtrack{QF\_IDL}{\uc}, \withtrack{QF\_NIRA}{\seq,\paral,\unsat}, \withtrack{QF\_UFBVDT}{\seq,\paral,\sat,\unsat,\fast}, \withtrack{QF\_UFDTLIRA}{\seq,\paral,\sat,\unsat,\fast,\uc}, \withtrack{QF\_UFLRA}{\uc}, \withtrack{QF\_UFNIA}{\sat}, \withtrack{UFDT}{\fast}}{s}{s}
-\newpage
-\MakeOnePage{OpenSMT}{}{\withtrack{QF\_Equality+LinearArith}{\unsat}, \withtrack{QF\_LinearRealArith}{\sat,\inc,\mv}}{\withtrack{QF\_LIA}{\seq,\paral}, \withtrack{QF\_LRA}{\seq,\paral,\unsat,\fast}, \withtrack{QF\_UFIDL}{\seq,\paral,\sat,\mv}}{s}{s}
+\MakeOnePage{Z3-Z3++}{\withtrack{Biggest Lead}{\mv}, \withtrack{Largest Contribution}{\mv}}{\withtrack{QF\_LinearIntArith}{\seq,\paral,\sat,\mv}, \withtrack{QF\_NonLinearIntArith}{\seq,\paral,\sat,\unsat,\fast,\mv}, \withtrack{QF\_NonLinearRealArith}{\seq,\paral,\sat,\mv}}{\withtrack{QF\_IDL}{\unsat}}{s}{}
 \newpage
@@
 \newpage
-\MakeOnePage{iProver}{}{}{\withtrack{ANIA}{\unsat}}{}{}
-\newpage

### 2023-07-06 2023/slides/presresults/slides.tex
SMTCOMP presentation

@@
 %\tikzexternalize
+\usepackage{multicol}
 
@@
 
+\newcommand{\myvideopdf}[2]{
+\begin{frame}
+  \frametitle{#1}
+  \begin{center}
+    video: \texttt{#2}    
+  \end{center}
+\end{frame}
+}
+
+\myincludepdf{slides-bitwuzla.pdf}
+
+\myincludepdf{slides-colibri.pdf}
+
+\myvideopdf{cvc5-NRA-LS}{slides-cvc5-nra-ls.mp4}
+
+\myvideopdf{iProver}{slides-iProver.mp4}
+
+\myvideopdf{ismt, Yices-ismt}{slides-ismt.mp4}
+
+\myincludepdf{slides-ismt-ppt.pdf}
+
+\myincludepdf{slides-opensmt.pdf}
+
+\myvideopdf{Ostrich}{slides-Ostrich.mkv}
+
+\myincludepdf{slides-smtinterpol.pdf}
+
+\myincludepdf{slides-smtrat.pdf}
+
+\myvideopdf{UltimateEliminator+MathSAT}{slides-UltimateEliminator.mkv}
+
+\myincludepdf{slides-vampire.pdf}
+
+\myincludepdf{slides-yaga.pdf}
+
+\myincludepdf{slides-Yices-2023.pdf}
+
+\myincludepdf{slides-YicesQS-2023.pdf}
+
+%\myvideopdf{Z3-Z3++}{slides-z3-z3++.mp4}
+\begin{frame}
+  \frametitle{Z3-Z3++}
+
+  \begin{center}
+    \url{https://youtu.be/fBB0Wxxf9vA}
+  \end{center}
+\end{frame}
+
   \begin{frame}
@@
     \begin{itemize}
-      \item Q3B
-      \vitem SMT-RAT
-      \vitem SMTS
-      \vitem UltimateEliminatior+MathSAT
-      \vitem Vampire
-      \vitem Z3str4
+\item cvc5
+\vitem Q3B
+\vitem Q3B-pBDD
+\vitem STP
+\vitem UltimateIntBlastingWrapper+SMTInterpol
+\vitem z3-alpha
+\vitem Z3-Noodler
+\vitem Z3-Owl
     \end{itemize}
@@
   \begin{itemize}
-  \item z3-4.8.17
-  \item MathSAT 5.6.8
-  \item Best solvers, per division, from previous years (23 Solvers)
+  \item Best solvers, per division, from previous years (27 Solvers)
   \end{itemize}
@@
   \begin{itemize}
-  \item Fixed solvers (OpenSMT, STP, Yices-ismt, Z3++,smtinterpol)
+  \item Fixed solvers (OSTRICH, Z3-Owl, Bitwuzla, Yices2, Z3-Noodler, iProver)  
   \end{itemize}
@@
   \end{itemize}
-  Error scores are draconian.
+  Error scores are \textbf{draconian}.
 \end{frame}
@@
 
-{
 \newcommand{\seq}{\texttt{;}}
@@
 \newcommand{\paralTrack}{parallel}
+
+\begin{frame}
+  \frametitle{Results}
+  \begin{center}
+    \begin{tabular}{|cl|cl|}
+  \hline
+  \sat & satisfiable & \unsat & unsatisfiable \\
+  \seq & sequential & \paral & parallel \\
+  \fast & less than 24s & \inc & incremental \\
+  \uc & unsat core & \mv & model validation \\
+  \hline
+\end{tabular}
+\end{center}
+\vfill
+Experimental track are added in the slides but are not present
+in the certificates
+\end{frame}
+
+{
   %\newcommand{\all}{{\footnotesize (\seq,\paral,\sat,\unsat,\fast,\inc,\uc\seq,\uc\paral,\mv)}}
@@
   \begin{itemize}
-  \item  111\,451 instances of 391\,363 have no status
+  \item  50411 benchmarks of 227\,938 have no status
 
@@
 
-  \vitem We manually resolved the disagreements
+  \vitem We manually resolved the disagreements: authors confirmed solver
+  unsoundness
+  \vitem We had 10 solvers with soundness issues:
+  \begin{columns}
+    \column{0.45\textwidth}
     \begin{itemize}
-    \item Authors confirmed solver unsoundness
-    \item Sound solvers agreed on result
+      \item Bitwuzla (uc printing error)
+      \item iProver (\& Fixed)
+      \item OSTRICH
+      \item Q3B
+      \item UltimateEliminator+MathSAT
     \end{itemize} 
+    \column{0.55\textwidth}
+    \begin{itemize}
+      \item UltimateIntBlastingWrapper+SMTInterpol
+      \item Vampire
+      \item Yices2 (\& Fixed)
+      \item Z3-Noodler (\& Fixed)
+      \item Z3-Owl (\& Fixed)
+    \end{itemize} 
+\end{columns}
 
-  \vitem We had only ??? solvers with soundness issues: 
   \end{itemize}
@@
 
-\begin{frame}{Plans for SMT-COMP 2022}
+\begin{frame}{Plans for SMT-COMP 2023}
   \begin{itemize}
-    \item Move to Dolmen as single model validator
-
-      \vitem Dolmen worked well in QF\_FP (minor issue with empty output, simple
-      to fix)
-      \vitem pysmt timed out in two cases (locally with more time one of them
-      succeeded)
-      \vitem pysmt could not understand the model in 9 cases
-      \vitem Dolmen is easy to extend to new theories
-      \vitem Easy to integrate with correct-by-construction code extracted from
-      Coq
-      \vitem Should be more efficient for handling function call
-
+    \item "Revelations are found in clouds” --- Serge King
+    \item MV: Algebraic number non experimental
+    \item MV: partial function more discussion needed
+    \item MV: array theory more discussion needed
   \end{itemize}
-
 \end{frame}
 
-\begin{frame}{Plans for SMT-COMP 2022}
+\begin{frame}{Plans for SMT-COMP 2023?}
   \begin{itemize}
@@
 \begin{frame}{SMT-COMP organizing committee}
-  Three people organize the SMT-COMP.  In 2022:
+  Three people organize the SMT-COMP.  In 2023:
   \begin{itemize}
-  \item Haniel Barbosa
+  \item Martin Bromberger
   \item Jochen Hoenicke
@@
 
-  Both Haniel and Jochen have been organizers for three-years. One of them
-  should be replaced.
+  Jochen have been organizer for four-years! He can rest happy.
   \bigskip
@@
     \item \emph{Andrea Micheli}: pysmt
-    \item \emph{Guillaume Bury}: Model Validator
+    \item \emph{Guillaume Bury, FB.}: Model Validator
     \item \emph{Clark Barrett, Pascal Fontaine, Aina Niemetz, Mathias Preiner, Hans-Jörg Schurr}: SMT-LIB benchmarks
@@
 \begin{frame}[shrink=0.95]{Benchmark contributors}
-  In 2022 \emph{new benchmarks} were contributed by:
+  In 2023 \emph{new benchmarks} were contributed by:
 

### 2023-07-06 2023/certificates/compute_from_yaml.py

@@ -123,11 +123,11 @@ def update(solvers,select,yaml):
         select(solvers[yaml["winner_par"]],"mv_par")
         select(solvers[yaml["winner_seq"]],"mv_seq")
     
-    # if yaml["track"] == "track_cloud":
-    #     select(solvers[yaml["winner_par"]],"cloud")
+    if yaml["track"] == "track_cloud":
+         select(solvers[yaml["winner_par"]],"cloud")
         
-    # if yaml["track"] == "track_parallel":
-    #     select(solvers[yaml["winner_par"]],"parallel")
+    if yaml["track"] == "track_parallel":
+         select(solvers[yaml["winner_par"]],"parallel")
 
 
 def select_division(division,logics):
@@ -165,7 +165,8 @@ def main(website_results,input_for_certificates,pretty_names,experimental_divisi
     solvers["-"].members = 0
     
     # Remove experimental division
-    experimental_divisions=parse_experimental_division(solvers,experimental_division)
+    #experimental_divisions=parse_experimental_division(solvers,experimental_division)
+    experimental_divisions={}
 
     existing_logics={}
     delayed_logic=[] #we wait to know which logic are competitive
@@ -209,7 +210,7 @@ def main(website_results,input_for_certificates,pretty_names,experimental_divisi
     
     #print the result
     with open(input_for_certificates, 'w', newline='') as output:
-        for (key,value) in solvers.items():
+        for (key,value) in sorted(solvers.items(),key=lambda x: x[0].lower()):
             if value.isNotEmpty() and value.members != 0:
                 print("solver: ",key,"(",value.members,")")
                 if True:

### 2023-07-06 2023/results/find-disagreements.sh

@@ -2,7 +2,9 @@
 
 #benchmark,solver,configuration,status,cpu time,wallclock time,memory usage,result,expected
 
-cat raw-results-sq.csv | csvcut -c benchmark,result | grep -v -e starexec-unknown -e '--' | sort |uniq | cut -d, -f1 |uniq -c |grep -v ' 1 '  | cut -c 9- > disagreeing-sq.txt
+INPUT=${1:-raw-results-sq.csv}
+
+cat $INPUT | csvcut -c benchmark,result | grep -v -e starexec-unknown -e '--' | sort |uniq | cut -d, -f1 |uniq -c |grep -v ' 1 '  | cut -c 9- > disagreeing-sq.txt
 
 COMMA=""
 PATTERN=""
@@ -11,7 +13,7 @@ while read bench; do
     COMMA="|"
 done < disagreeing-sq.txt
 # remove the non informative result and select the problematic files
-cat raw-results-sq.csv | grep -v -e ",starexec-unknown," | grep -E ",($PATTERN)," | LANG=C sort -t, -k 1 | cut -d, -f2,4,12,13
+cat $INPUT | grep -v -e ",starexec-unknown," | grep -E ",($PATTERN)," | LANG=C sort -t, -k 1 | cut -d, -f2,4,12,13
 
 
 # Solver with answers different from the others

### 2023-07-06 2023/certificates/compute_from_yaml.py
revert compute_from_yaml

@@ -165,8 +165,8 @@ def main(website_results,input_for_certificates,pretty_names,experimental_divisi
     solvers["-"].members = 0
     
     # Remove experimental division
-    #experimental_divisions=parse_experimental_division(solvers,experimental_division)
-    experimental_divisions={}
+    experimental_divisions=parse_experimental_division(solvers,experimental_division)
+    #experimental_divisions={}
 
     existing_logics={}
     delayed_logic=[] #we wait to know which logic are competitive

### 2023-07-06 2023/slides/presresults/slides.tex
revert compute_from_yaml
Last addition in slides

@@
 \pause
-  \emph{This year} the sat/unsat results from sound solvers in SQ were used to
+  \emph{As last year} the sat/unsat results from sound solvers in SQ were used to
   include benchmarks on the MV, UC and PE tracks.
@@
 
+\myincludepdf{slides-cvc5.pdf}
+
 \myvideopdf{cvc5-NRA-LS}{slides-cvc5-nra-ls.mp4}
@@
     \begin{itemize}
-\item cvc5
-\vitem Q3B
+\item Q3B
 \vitem Q3B-pBDD
@@
 
-\begin{frame}{Plans for SMT-COMP 2023}
+\begin{frame}[fragile]
+  \frametitle{Plans for SMT-COMP 2023}
   \begin{itemize}
     \item "Revelations are found in clouds” --- Serge King
-    \item MV: Algebraic number non experimental
+    \item MV: Algebraic number $\implies$ non experimental
+\begin{verbatim}
+(root-of-with-ordering (coeffs p_0 p_1 ... p_n) i)
+
+(root-of-with-interval  (coeffs p_0 p_1 ... p_n) min max)
+(root-of-with-enclosure (coeffs p_0 p_1 ... p_n) min max)
+\end{verbatim}
+    Thanks for the solvers that implemented one of them!
     \item MV: partial function more discussion needed

### 2023-07-06 2023/certificates/compute_from_yaml.py

@@ -6,12 +6,8 @@ from typing import Any
 import frontmatter
 import os
 from collections import defaultdict
- 
 
-    
-track= {
-    "track_incremental": "\\inc",   
-}
+show_experimental=False
 
 class category(dict):
     def latex(self):
@@ -123,10 +119,10 @@ def update(solvers,select,yaml):
         select(solvers[yaml["winner_par"]],"mv_par")
         select(solvers[yaml["winner_seq"]],"mv_seq")
     
-    if yaml["track"] == "track_cloud":
+    if show_experimental and yaml["track"] == "track_cloud":
          select(solvers[yaml["winner_par"]],"cloud")
         
-    if yaml["track"] == "track_parallel":
+    if show_experimental and yaml["track"] == "track_parallel":
          select(solvers[yaml["winner_par"]],"parallel")
 
 
@@ -165,8 +161,10 @@ def main(website_results,input_for_certificates,pretty_names,experimental_divisi
     solvers["-"].members = 0
     
     # Remove experimental division
-    experimental_divisions=parse_experimental_division(solvers,experimental_division)
-    #experimental_divisions={}
+    if show_experimental:
+        experimental_divisions={}
+    else:
+        experimental_divisions=parse_experimental_division(solvers,experimental_division)
 
     existing_logics={}
     delayed_logic=[] #we wait to know which logic are competitive

### 2023-07-06 2023/slides/presresults/input_for_certificates.tex
decide on favor of cvc5 for parallel disagreement

@@
 \newpage
-\MakeOnePage{cvc5}{\withtrack{Biggest Lead}{\seq,\paral,\sat,\unsat,\uc}, \withtrack{Largest Contribution}{\seq,\paral,\sat,\unsat,\fast,\inc,\uc}}{\withtrack{Arith}{\seq,\paral,\unsat,\inc,\uc}, \withtrack{Bitvec}{\seq,\paral,\unsat,\inc,\uc}, \withtrack{Equality}{\seq,\paral,\sat,\unsat,\inc,\uc}, \withtrack{Equality+LinearArith}{\seq,\paral,\sat,\unsat,\fast,\inc,\uc}, \withtrack{Equality+MachineArith}{\seq,\paral,\sat,\unsat,\fast,\uc}, \withtrack{Equality+NonLinearArith}{\seq,\paral,\sat,\unsat,\fast,\inc,\uc}, \withtrack{QF\_Datatypes}{\seq,\paral,\sat,\unsat,\uc\textsuperscript\seq}, \withtrack{QF\_Equality}{\inc}, \withtrack{QF\_Equality+Bitvec+Arith}{\inc}, \withtrack{QF\_Equality+NonLinearArith}{\seq,\paral,\unsat,\fast,\inc,\uc,\mv}, \withtrack{QF\_FPArith}{\uc}, \withtrack{QF\_LinearIntArith}{\unsat}, \withtrack{QF\_LinearRealArith}{\unsat}, \withtrack{QF\_NonLinearRealArith}{\unsat,\fast}, \withtrack{QF\_Strings}{\seq,\paral,\sat,\unsat}}{\withtrack{LIA}{\sat,\fast}, \withtrack{NIA}{\sat,\fast}, \withtrack{QF\_ALIA}{\inc}, \withtrack{QF\_AUFLIA}{\uc,\mv}, \withtrack{QF\_AX}{\mv}, \withtrack{QF\_BVFPLRA}{\inc}, \withtrack{QF\_FP}{\sat,\mv}, \withtrack{QF\_IDL}{\uc}, \withtrack{QF\_NIRA}{\seq,\paral,\unsat}, \withtrack{QF\_UFBVDT}{\seq,\paral,\sat,\unsat,\fast}, \withtrack{QF\_UFDTLIRA}{\seq,\paral,\sat,\unsat,\fast,\uc}, \withtrack{QF\_UFLRA}{\uc}, \withtrack{QF\_UFNIA}{\sat}, \withtrack{UFDT}{\fast}, \withtrack{UFDTLIA}{\cloud}, \withtrack{UFNIA}{\cloud}}{s}{s}
+\MakeOnePage{cvc5}{\withtrack{Biggest Lead}{\seq,\paral,\sat,\unsat,\uc}, \withtrack{Largest Contribution}{\seq,\paral,\sat,\unsat,\fast,\inc,\uc}}{\withtrack{Arith}{\seq,\paral,\unsat,\inc,\uc}, \withtrack{Bitvec}{\seq,\paral,\unsat,\inc,\uc}, \withtrack{Equality}{\seq,\paral,\sat,\unsat,\inc,\uc,\cloud}, \withtrack{Equality+LinearArith}{\seq,\paral,\sat,\unsat,\fast,\inc,\uc,\cloud}, \withtrack{Equality+MachineArith}{\seq,\paral,\sat,\unsat,\fast,\uc}, \withtrack{Equality+NonLinearArith}{\seq,\paral,\sat,\unsat,\fast,\inc,\uc}, \withtrack{QF\_Datatypes}{\seq,\paral,\sat,\unsat,\uc\textsuperscript\seq}, \withtrack{QF\_Equality}{\inc}, \withtrack{QF\_Equality+Bitvec+Arith}{\inc}, \withtrack{QF\_Equality+NonLinearArith}{\seq,\paral,\unsat,\fast,\inc,\uc,\mv}, \withtrack{QF\_FPArith}{\uc}, \withtrack{QF\_LinearIntArith}{\unsat}, \withtrack{QF\_LinearRealArith}{\unsat}, \withtrack{QF\_NonLinearRealArith}{\unsat,\fast}, \withtrack{QF\_Strings}{\seq,\paral,\sat,\unsat}}{\withtrack{LIA}{\sat,\fast}, \withtrack{NIA}{\sat,\fast}, \withtrack{QF\_ALIA}{\inc}, \withtrack{QF\_AUFLIA}{\uc,\mv}, \withtrack{QF\_AX}{\mv}, \withtrack{QF\_BVFPLRA}{\inc}, \withtrack{QF\_FP}{\sat,\mv}, \withtrack{QF\_IDL}{\uc}, \withtrack{QF\_NIRA}{\seq,\paral,\unsat}, \withtrack{QF\_UFBVDT}{\seq,\paral,\sat,\unsat,\fast}, \withtrack{QF\_UFDTLIRA}{\seq,\paral,\sat,\unsat,\fast,\uc}, \withtrack{QF\_UFLRA}{\uc}, \withtrack{QF\_UFNIA}{\sat}, \withtrack{UFDT}{\fast}, \withtrack{UFNIA}{\cloud}}{s}{s}
 \newpage
-\MakeOnePage{iProver}{}{}{\withtrack{ANIA}{\unsat}}{}{}
+\MakeOnePage{iProver}{}{\withtrack{Equality}{\paralTrack}, \withtrack{Equality+LinearArith}{\paralTrack}}{\withtrack{ANIA}{\unsat}}{s}{}
 \newpage
@@
 \newpage
-\MakeOnePage{Vampire}{\withtrack{Biggest Lead}{\cloud,\paralTrack}}{\withtrack{Arith}{\cloud,\paralTrack}, \withtrack{Equality}{\fast,\cloud,\paralTrack}, \withtrack{Equality+LinearArith}{\cloud,\paralTrack}, \withtrack{Equality+NonLinearArith}{\cloud,\paralTrack}}{\withtrack{ALIA}{\seq,\paral,\unsat,\fast}, \withtrack{AUFLIA}{\unsat,\fast}, \withtrack{AUFLIRA}{\fast}, \withtrack{AUFNIRA}{\paral,\unsat,\fast}, \withtrack{UF}{\seq,\paral,\sat}, \withtrack{UFDTLIA}{\fast,\uc}, \withtrack{UFDTNIA}{\seq,\paral,\unsat,\fast,\uc}}{s}{s}
+\MakeOnePage{Vampire}{\withtrack{Biggest Lead}{\cloud,\paralTrack}}{\withtrack{Arith}{\cloud,\paralTrack}, \withtrack{Equality}{\fast}, \withtrack{Equality+NonLinearArith}{\cloud,\paralTrack}}{\withtrack{ALIA}{\seq,\paral,\unsat,\fast}, \withtrack{AUFLIA}{\unsat,\fast,\cloud,\paralTrack}, \withtrack{AUFLIRA}{\fast}, \withtrack{AUFNIRA}{\paral,\unsat,\fast}, \withtrack{UF}{\seq,\paral,\sat}, \withtrack{UFDTLIA}{\fast,\uc}, \withtrack{UFDTNIA}{\seq,\paral,\unsat,\fast,\uc}, \withtrack{UFLIA}{\cloud,\paralTrack}}{s}{s}
 \newpage

### 2023-10-06 2023/certificates/input_for_certificates.tex
update aggregation

--- 2023-06-29 2023/certificates/input_for_certificates.tex
@@
 \newpage
-\MakeOnePage{Z3++}{\withtrack{Biggest Lead}{\mv}, \withtrack{Largest Contribution}{\mv}}{\withtrack{QF\_LinearIntArith}{\seq,\paral,\sat,\mv}, \withtrack{QF\_NonLinearIntArith}{\seq,\paral,\sat,\unsat,\fast}, \withtrack{QF\_NonLinearRealArith}{\seq,\paral,\sat}}{\withtrack{QF\_IDL}{\unsat}}{s}{}
+\MakeOnePage{Z3-Z3++}{\withtrack{Biggest Lead}{\mv}, \withtrack{Largest Contribution}{\mv}}{\withtrack{QF\_LinearIntArith}{\seq,\paral,\sat,\mv}, \withtrack{QF\_NonLinearIntArith}{\seq,\paral,\sat,\unsat,\fast}, \withtrack{QF\_NonLinearRealArith}{\seq,\paral,\sat}}{\withtrack{QF\_IDL}{\unsat}}{s}{}
 \newpage
@@
 \newpage
-\MakeOnePage{Bitwuzla}{\withtrack{Biggest Lead}{\inc}}{\withtrack{Bitvec}{\sat}, \withtrack{Equality+MachineArith}{\inc}, \withtrack{FPArith}{\seq,\paral,\sat,\unsat,\fast,\inc,\uc}, \withtrack{QF\_Bitvec}{\inc}, \withtrack{QF\_Equality+Bitvec}{\seq,\paral,\sat,\unsat,\fast,\inc,\mv}, \withtrack{QF\_FPArith}{\seq,\paral,\sat,\unsat,\fast,\inc}}{\withtrack{ABVFP}{\sat,\fast}, \withtrack{ABVFPLRA}{\fast}, \withtrack{AUFBV}{\seq,\paral,\sat,\unsat,\fast}, \withtrack{AUFBVFP}{\seq,\paral,\sat,\unsat,\fast}, \withtrack{QF\_ABVFP}{\uc}, \withtrack{QF\_ABVFPLRA}{\uc}, \withtrack{QF\_BVFP}{\uc}, \withtrack{QF\_BVFPLRA}{\uc}, \withtrack{UFBV}{\seq,\paral,\sat,\unsat,\fast}, \withtrack{UFBVFP}{\seq,\paral,\unsat}}{s}{s}
+\MakeOnePage{Bitwuzla}{\withtrack{Biggest Lead}{\inc}}{\withtrack{Bitvec}{\sat,\fast}, \withtrack{Equality+MachineArith}{\inc}, \withtrack{FPArith}{\seq,\paral,\sat,\unsat,\fast,\inc,\uc}, \withtrack{QF\_Bitvec}{\inc}, \withtrack{QF\_Equality+Bitvec}{\seq,\paral,\sat,\unsat,\fast,\inc,\mv}, \withtrack{QF\_FPArith}{\seq,\paral,\sat,\unsat,\fast,\inc}}{\withtrack{ABVFP}{\sat,\fast}, \withtrack{ABVFPLRA}{\fast}, \withtrack{AUFBV}{\seq,\paral,\sat,\unsat,\fast}, \withtrack{AUFBVFP}{\seq,\paral,\sat,\unsat,\fast}, \withtrack{QF\_ABVFP}{\uc}, \withtrack{QF\_ABVFPLRA}{\uc}, \withtrack{QF\_BVFP}{\uc}, \withtrack{QF\_BVFPLRA}{\uc}, \withtrack{UFBV}{\seq,\paral,\sat,\unsat,\fast}, \withtrack{UFBVFP}{\seq,\paral,\unsat}}{s}{s}
 \newpage
@@
 \newpage
-\MakeOnePage{Q3B}{}{\withtrack{Bitvec}{\fast}}{}{}{}
-\newpage
 \MakeOnePage{cvc5}{\withtrack{Biggest Lead}{\seq,\paral,\sat,\unsat,\uc}, \withtrack{Largest Contribution}{\seq,\paral,\sat,\unsat,\fast,\inc,\uc}}{\withtrack{Arith}{\seq,\paral,\unsat,\inc,\uc}, \withtrack{Bitvec}{\seq,\paral,\unsat,\inc,\uc}, \withtrack{Equality}{\seq,\paral,\sat,\unsat,\inc,\uc}, \withtrack{Equality+LinearArith}{\seq,\paral,\sat,\unsat,\fast,\inc,\uc}, \withtrack{Equality+MachineArith}{\seq,\paral,\sat,\unsat,\fast,\uc}, \withtrack{Equality+NonLinearArith}{\seq,\paral,\sat,\unsat,\fast,\inc,\uc}, \withtrack{QF\_Datatypes}{\seq,\paral,\sat,\unsat,\uc\textsuperscript\seq}, \withtrack{QF\_Equality}{\inc}, \withtrack{QF\_Equality+Bitvec+Arith}{\inc}, \withtrack{QF\_Equality+NonLinearArith}{\seq,\paral,\unsat,\fast,\inc,\uc}, \withtrack{QF\_FPArith}{\uc}, \withtrack{QF\_LinearIntArith}{\unsat}, \withtrack{QF\_LinearRealArith}{\unsat}, \withtrack{QF\_NonLinearRealArith}{\unsat,\fast}, \withtrack{QF\_Strings}{\seq,\paral,\sat,\unsat}}{\withtrack{LIA}{\sat,\fast}, \withtrack{NIA}{\sat,\fast}, \withtrack{QF\_ALIA}{\inc}, \withtrack{QF\_AUFLIA}{\uc}, \withtrack{QF\_BVFPLRA}{\inc}, \withtrack{QF\_FP}{\sat}, \withtrack{QF\_IDL}{\uc}, \withtrack{QF\_NIRA}{\seq,\paral,\unsat}, \withtrack{QF\_UFBVDT}{\seq,\paral,\sat,\unsat,\fast}, \withtrack{QF\_UFDTLIRA}{\seq,\paral,\sat,\unsat,\fast,\uc}, \withtrack{QF\_UFLRA}{\uc}, \withtrack{QF\_UFNIA}{\sat}, \withtrack{UFDT}{\fast}}{s}{s}

### 2023-10-06 2023/results/find-disagreements.sh

@@ -3,6 +3,7 @@
 #benchmark,solver,configuration,status,cpu time,wallclock time,memory usage,result,expected
 
 INPUT=${1:-raw-results-sq.csv}
+CUTWHAT=${2:-2,4,12,13}
 
 cat $INPUT | csvcut -c benchmark,result | grep -v -e starexec-unknown -e '--' | sort |uniq | cut -d, -f1 |uniq -c |grep -v ' 1 '  | cut -c 9- > disagreeing-sq.txt
 
@@ -13,7 +14,7 @@ while read bench; do
     COMMA="|"
 done < disagreeing-sq.txt
 # remove the non informative result and select the problematic files
-cat $INPUT | grep -v -e ",starexec-unknown," | grep -E ",($PATTERN)," | LANG=C sort -t, -k 1 | cut -d, -f2,4,12,13
+cat $INPUT | grep -v -e ",starexec-unknown," | grep -E ",($PATTERN)," | LANG=C sort -t, -k 1 | csvcut -c$CUTWHAT
 
 
 # Solver with answers different from the others

### 2023-10-06 2023/scoring/make_pivot_table_csv.sh

@@ -1,3 +1,3 @@
 #/bin/sh -eu
 
-python3 ../../tools/results_visualization/aggregations.py --csv results-sq.csv --solvers ../registration/solvers_divisions_all.csv --out ../../../smt-comp.github.io/2022/sq.csv --divisions-map ../new-divisions.json --time 1200
+python3 ../../tools/results_visualization/aggregations.py --csv results-sq.csv --solvers ../registration/solvers_divisions_all.csv --out ../../../smt-comp.github.io/2023/sq.csv --divisions-map ../new-divisions.json --time 1200

### 2024-04-02 rules/rules24.tex
First draft of the rules for 2024.

--- 2023-05-21 rules/rules23.tex
@@
 \newcommand{\prooftrack}{Proof Exhibition Track\xspace}
+
+\newcommand{\executionservice}{execution service\xspace}
 
@@
 \and
-Jochen Hoenicke\\
-Certora\\
-Germany\\
-{\small\href{mailto:jochen@certora.com}{\texttt{jochen@certora.com}}}
+Martin Jon\'{a}\v{s}\\
+Masaryk University\\
+Czechia\\
+{\small\href{mailto:martin.jonas@mail.muni.cz}{\texttt{martin.jonas@mail.muni.cz}}}
 }
@@
 \begin{itemize}
-  \item {\bf System descriptions.}  \emergencystretch.5cm The system description 
-  for a participating solver must be submitted by the deadline for the preliminary 
-  solver versions. In the case a system description contains not all necessary information,
-  participants will be asked to submit an updated version of their 
-  system description as part of the submission of the final version of their solver.
-%
-  \rationale{We need this time to check whether the system descriptions contain all
-  necessary information and to give participants the chance to fix their system 
-  descriptions if necessary.}
-
-  \item {\bf System descriptions.}  \emergencystretch.5cm Some formulations 
-  in the requirements for the system descriptions have been updated from 
-  \emph{should} to \textbf{must} to make it clearer that these requirements 
-  are mandatory and not just recommended/optional.
-%
-  \rationale{We did this to ensure that derived tools are more easily recognizable and 
-  that it is always clear in which way wrapper tools and derived tools improve 
-  on the original solvers. 
-  Our changes follow the key words for use in RFCs to indicate requirement levels 
-  as proposed by \url{https://www.ietf.org/rfc/rfc2119.txt}.}
-
-  \item {\bf \mvaltrack.}  \emergencystretch.5cm Last year's
-    competition introduced the experimental divisions QF\_FPArith
-    (excluding the logics QF\_ABVFP, QF\_AUFBVFP, and QF\_ABVFPLRA).
-  %
-  This year these divisions will be officially counted and no longer be experimental.
-  %
-  In addition, we add this year new experimental divisions for
-  arrays, non-linear arithmetic and for datatypes.  These include the divisions
-  QF\_NonLinearIntArith, QF\_NonLinearRealArith,
-  QF\_Equality+NonLinearArithm,
-  and QF\_Datatypes.
-%
-  \rationale{Last year's divisions ran successfully, so there
-    is no reason to keep them experimental.
-    %
-    For the new divisions, as before, given the inconsistencies across different
-    model producing solvers, we proceed in an experimental fashion to push for
-    model standardization.}
-
-\item {\bf \prooftrack.}
-  Last year we added this as experimental track. We will continue with
-  this track in more or less the same format.  We will reduce the
-  number of benchmarks, though.
-%  
-  \rationale{We received several submissions that showed that there is
-    interest in a proof track.
-
-    We are still far away from a common proof format, so changing the
-    track to a competition track or making it non-experimental is not
-    feasible at this time.
-
-    The number of benchmarks and the size of the produced proofs
-    turned out to be a major stress to the StarExec infrastructure,
-    while not giving only little insight.  Therefore, we will reduce
-    the number of benchmarks in this track.
-  }
-
-\item {\bf Wrapper Script for \prooftrack.}
-   The wrapper script is changed to remove very large proofs and
-   to cut very large error/debug output.
-%
-   \rationale{Last Year, the \prooftrack produced 800~GB of output, most
-   of that stemming from a few benchmark/solver pairs. These cannot be
-   removed without losing the whole proof track job.   It also makes
-   downloading and sharing the result much harder.}
-
-\item {\bf Scoring.}  \emergencystretch.5cm We adjusted the wall-clock and 
-CPU time scores so only the benchmarks that are correctly solved within the 
-time limit $T$ are counted.
-%
-  \rationale{We noticed that in the previous scoring unintended results 
-  did occur because timeouts were scored worse than aborts and could 
-  overshadow the times of correctly solved problems. For instance, 
-  solver A that never aborts could lose to solver B that frequently aborts 
-  although A solved exactly the same problems B could solve and A was always 
-  faster on the solved problems than B.}
+  \item {\bf Submission process.}  \emergencystretch.5cm \todo{Details}.
+%
+  \rationale{\todo{Details}}
+
+  \item {\bf Move from StarExec to BenchExec.}  \emergencystretch.5cm \todo{Details}
+%
+  \rationale{\todo{Details}}
 \end{itemize}
@@
 %
-An entrant to SMT-COMP is a solver submitted by its authors using
-the StarExec (\url{http://www.starexec.org}) service, or, for
+An entrant to SMT-COMP is a solver submitted by its authors via
+a push request to the SMT-COMP GitHub repository (\url{https://github.com/SMT-COMP/smt-comp.github.io/tree/master/submissions}), or, for
 \paralleltrack{} and \cloudtrack{}, otherwise communicated to the
-organisers.
+organisers. The final solver version needs to be uploaded as a Zenodo (https://zenodo.org/ <https://zenodo.org/>) submission 
+that must contain a docker file that compiles the solver.
 
@@
 %
-The StarExec execution
-service enables members of the SMT research community to run solvers
-on jobs consisting of benchmarks from the SMT-LIB benchmark library.
-Jobs are run on a shared computer cluster.  The execution service is
-provided free of charge, but requires registration to create a
-login account.  Registered users may then upload solvers to
-run, or may run public solvers already uploaded to the service.
-Information about how to configure and upload a solver is contained in
-the StarExec user guide,
-\url{https://wiki.uiowa.edu/display/stardev/User+Guide}.
+BenchExec (\url{https://github.com/sosy-lab/benchexec}) is a framework for reliable benchmarking and resource 
+measurement developed by LMU's Software and Computational Systems Lab (SoSy-Lab \url{https://www.sosy-lab.org/}).
+The framework itself can be downloaded and used locally by anyone. 
+The competition itself will be executed on a BenchExec cluster owned by SoSy-Lab, 
+who are kind enough to support our competition with their computing power. 
+\todo{Is there a way for the users to run tests directly on the SoSy-Lab BenchExec cluster?}
+%
+%
+%service enables members of the SMT research community to run solvers
+%on jobs consisting of benchmarks from the SMT-LIB benchmark library.
+%Jobs are run on a shared computer cluster.  The execution service is
+%provided free of charge, but requires registration to create a
+%login account.  Registered users may then upload solvers to
+%run, or may run public solvers already uploaded to the service.
+%Information about how to configure and upload a solver is contained in
+%the StarExec user guide,
+%\url{https://wiki.uiowa.edu/display/stardev/User+Guide}.
 
@@
 %
-For participation in SMT-COMP, a solver must be uploaded to StarExec
-and made publicly available, or communicated separately to the
-organisers for the \cloudtrack{} and \paralleltrack{}.  StarExec
-supports solver configurations.  You can have at most one configuration
-for each track (named after the track) and a default configuration used
-for tracks without a track-specific configuration.
-Moreover, the organizers must be informed of the solver's presence
-\emph{and the tracks and divisions which it enters} via the web form
-at
+For participation in SMT-COMP, the organizers must be informed of the solver's presence
+\emph{and the tracks and divisions which it enters} via a push request 
+to the SMT-COMP GitHub repository
 \begin{center}
-  \url{https://forms.gle/xhUDQaTynbS3mccE7}
+  \url{https://github.com/SMT-COMP/smt-comp.github.io/tree/master/submissions}
 \end{center}
-For each track the submission must specify the logics which are
+The easiest way to create this push request is via the web-interface available under 
+the above URL. The actual solver must be submitted via a link to a publicly available 
+docker file that compiles the solver. For the \cloudtrack{} and \paralleltrack{},
+it must be communicated separately to the organisers by email to 
+\href{mailto:aws-smtcomp-2024@googlegroups.com}{aws-smtcomp-2024@googlegroups.com}. 
+Note that independent of the tracks, the final solver version must be uploaded as a Zenodo 
+(https://zenodo.org/ <https://zenodo.org/>) submission.
+Moreover, for each track, the submission must specify the logics which are
 supported by the solver. The solver will enter all divisions where it
-supports at least one logic.  A submission \textbf{must} also include a
-link to the \emph{system description} (see below) and a \emph{32-bit
-  unsigned integer}.  These integer numbers, collected from all
+supports at least one logic. It is possible to submit specific configurations 
+of command line  options per track/logic/division as well as a default configuration 
+of command line options for all tracks/logics/divisions without their own configuration.
+A submission \textbf{must} also include a link to the \emph{system description} (see below) 
+and a \emph{32-bit unsigned integer}. These integer numbers, collected from all
 submissions, are used to seed competition tools.
@@
 
-SMT-COMP entrants must be submitted via StarExec (solvers), or
-communicated separately to the organisers for the \paralleltrack{} and
-\cloudtrack{}, \emph{and}
-the above web form (accompanying information) until the end of
-{\bf May~13, 2023} anywhere on earth.
+SMT-COMP entrants must be submitted via a push request as explained above and,
+in the case of the \paralleltrack{} and \cloudtrack{}, 
+communicated separately to the organisers via email until the end of
+{\bf May~27, 2024} anywhere on earth.
 After this date \emph{no new entrants} will be accepted.
-However, updates to existing entrants on StarExec or \paralleltrack{}
-and \cloudtrack{}
-will be accepted until the end of {\bf May~27, 2023} anywhere on earth.
+However, updates to existing entrants via push requests or,
+in the case of the \paralleltrack{} and \cloudtrack{}, via email,
+will be accepted until the end of {\bf June~8, 2024} anywhere on earth.
 
@@
 and not for adding new features, as there may be no opportunity to do
-extensive testing using StarExec or other means after the initial deadline.
-
-The solver versions that are present on StarExec or communicated
-otherwise to the organisers for \paralleltrack{} and \cloudtrack{} at the conclusion of
+extensive testing using the \executionservice or other means after the initial deadline.
+
+The last solver links pushed to the repository or communicated
+via email to the organisers for \paralleltrack{} and \cloudtrack{} at the conclusion of
 the grace period will be the ones used for the competition.  Versions
@@
     is available at \url{https://github.com/SMT-COMP/trace-executor}
-  \item \textbf{Post-Processors.} These are used by StarExec to translate the
+  \item \textbf{Post-Processors.} These are used by the \executionservice to translate the
     output of tools to the format required for scoring. All post-processors (per
@@
 variables.  See the StarExec user guide for more information.
+\todo{What are the limits for BenchExec? Do we set limits ourselves?}
 
@@
 machines, e.g., over the network.
+\todo{What are the limits for BenchExec? Do we set limits ourselves?}
 
@@
 to validate and accumulate the results.
+\todo{We need a new link for the corresponding benchexec script.}
 
@@
 time (summed over all individual commands) taken by the solver to
-respond to commands.\footnote{Times measured by StarExec may include
+respond to commands.\footnote{Times measured by the \executionservice may include
   time spent in the trace executor.  We expect that this time will
@@
 benchmark library.
-The competition uses the
-\href{https://www.starexec.org/}{StarExec} service, which is hosted at
-the \href{http://www.cs.uiowa.edu/}{University of Iowa}.  Aaron Stump
-is providing essential StarExec support.
+The competition uses a \href{https://github.com/sosy-lab/benchexec}{BenchExec} cluster 
+owned by LMU's Software and Computational Systems Lab (SoSy-Lab https://www.sosy-lab.org/ <https://www.sosy-lab.org/>), 
+who are kind enough to support our competition with their computing power. Dirk Beyer 
+is providing essential BenchExec support.
 
 \header{Disclosure.}
-Fran\c{c}ois is part of the developing team of the SMT solver COLIBRI~\cite{colibri}.
-%
-Martin is part of the developing team of the SMT solver
+Fran\c{c}ois Bobot is part of the developing team of the SMT solver COLIBRI~\cite{colibri}.
+%
+Martin Bromberger is part of the developing team of the SMT solver
 SPASS-SATT~\cite{spass-satt}.
 %
-Jochen is part of the developing team of the SMT solver
-SMTInterpol~\cite{smtinterpol}.
+Martin Jon\'{a}\v{s} is part of the developing team of \todo{Martin J. please fill this out}.
 

### 2024-04-22 rules/rules24.tex
Adjusted dates in the SMT-COMP rules and worked on the ToDos that came from changing the execution service.

@@
 
-\title{18th International Satisfiability Modulo Theories Competition
-  (SMT-COMP 2023): Rules and Procedures}
+\title{19th International Satisfiability Modulo Theories Competition
+  (SMT-COMP 2024): Rules and Procedures}
 
@@
 \begin{description}
-\item[Mar~31] Deadline for new benchmark contributions.
-\item[April~29] Final versions of competition tools (e.g., benchmark
+\item[April~13] Deadline for new benchmark contributions.
+\item[May~11] Final versions of competition tools (e.g., benchmark
   scrambler) are made available.  Benchmark libraries are frozen.
-\item[May~13] Deadline for first versions of solvers (for all tracks),
+\item[May~27] Deadline for first versions of solvers (for all tracks),
   including information about which tracks and divisions are being
   entered, and magic numbers for benchmark scrambling.
-\item[May~27] Deadline for final versions of solvers, including
+\item[June~8] Deadline for final versions of solvers, including
   system descriptions.
-\item[May~30] Opening value of NYSE Composite Index used to compute
+\item[June~11] Opening value of NYSE Composite Index used to compute
   random seed for competition tools.
-\item[July~5-6] SMT Workshop; end of competition, presentation of
+\item[July~22-23] SMT Workshop; end of competition, presentation of
   results.
@@
 
-SMT-COMP~2023 is part of the SMT Workshop~2023
-(\url{http://smt-workshop.cs.uiowa.edu/2023/}),
-which is affiliated with CADE~29 (\url{https://easyconferences.eu/cade2023/}).
+SMT-COMP~2024 is part of the SMT Workshop~2024
+(\url{http://smt-workshop.cs.uiowa.edu/2024/}),
+which is affiliated with CAV~2024 (\url{https://i-cav.org/2024/}).
 The SMT Workshop will include a block of time to present the results of the
@@
 
-SMT-COMP 2023 will have seven tracks: the \maintrack (before 2019: Main Track),
+SMT-COMP 2024 will have seven tracks: the \maintrack (before 2019: Main Track),
 the \inctrack (before 2019: Application Track), the \ucoretrack, the \mvaltrack,
@@
   Liana Hadarean,
-  Matthias Heizmann, Antti Hyvarinen, Aina Niemetz, Albert Oliveras, Giles Reger, Aaron Stump,
+  Matthias Heizmann, Antti Hyvarinen, Jochen Hoenicke, Aina Niemetz, Albert Oliveras, Giles Reger, Aaron Stump,
   and Tjark Weber.}  describes the rules and competition procedures for
-SMT-COMP~2023.
-%
-
-As in previous years, we have revised the rules slightly.  Some rule
-changes in 2023 are designed to improve how logics are organized into
-divisions. We have also added more divisions to the \mvaltrack and have defined a
-new \prooftrack.
+SMT-COMP~2024.
+%
+
+As in previous years, we have revised the rules slightly. Most changes are due to our move from StarExec to BenchExec.
 %
@@
 \begin{itemize}
-  \item {\bf Submission process.}  \emergencystretch.5cm \todo{Details}.
-%
-  \rationale{\todo{Details}}
-
-  \item {\bf Move from StarExec to BenchExec.}  \emergencystretch.5cm \todo{Details}
-%
-  \rationale{\todo{Details}}
+
+  \item {\bf Move from StarExec to BenchExec.}  \emergencystretch.5cm
+  The single query, incremental, unsat-core, model-validation and proof exhibition tracks 
+  will no longer run on the StarExec platform hosted by the University of Iowa.
+  Starting this year, we will run these tracks on the BenchExec cluster 
+  (\url{https://github.com/sosy-lab/benchexec}) owned by LMU's Software 
+  and Computational Systems Lab (SoSy-Lab \url{https://www.sosy-lab.org/}).
+%
+  \rationale{The StarExec cluster is in the process of being decommissioned. We picked 
+             BenchExec as the new platform because it is host to similar competitions 
+             and the experience collected there is a big help in our migration process.
+             Moreover, it is in academic hands, so less likely to change conditions on
+             short notice.}
+
+  \item {\bf Submission process.}  \emergencystretch.5cm
+  We changed the submission process from a Google form to a push request to the 
+  SMT-COMP GitHub repository (\url{https://github.com/SMT-COMP/smt-comp.github.io/tree/master/submissions}). 
+  Detailed instructions can be found in the README file there.
+  Moreover, participants are now required to upload their final solver versions as a Zenodo 
+  (\url{https://zenodo.org/}) submission that must contain a docker file that compiles the solver.
+%
+  \rationale{The change from Google form to GitHub push request makes it easier for us to 
+             automatically create scripts for BenchExec. The submission of the final solver 
+             versions to Zenodo makes it more likely that the competition results stay replicable.}
+
+  \item {\bf Time limits.}  \emergencystretch.5cm
+  The time limits for the cloud and parallel tracks are reduced to 2 minutes per problem.
+%
+  \rationale{The analysis of last years results showed that most problems in these tracks are solved quickly or not at all.}
+
+  \item {\bf Memory limits.}  \emergencystretch.5cm
+  The memory limits for the single query, incremental, unsat-core, model-validation and proof exhibition tracks are reduced to 30\,GB.
+%
+  \rationale{The reason are hardware limits of the new execution platform.}
 \end{itemize}
@@
 who are kind enough to support our competition with their computing power. 
-\todo{Is there a way for the users to run tests directly on the SoSy-Lab BenchExec cluster?}
-%
-%
-%service enables members of the SMT research community to run solvers
-%on jobs consisting of benchmarks from the SMT-LIB benchmark library.
-%Jobs are run on a shared computer cluster.  The execution service is
-%provided free of charge, but requires registration to create a
-%login account.  Registered users may then upload solvers to
-%run, or may run public solvers already uploaded to the service.
-%Information about how to configure and upload a solver is contained in
-%the StarExec user guide,
-%\url{https://wiki.uiowa.edu/display/stardev/User+Guide}.
+To be more precise, the competition will be run on the 168 apollon nodes of the 
+SoSy-Lab BenchExec cluster (for more details see \url{https://vcloud.sosy-lab.org/cpachecker/webclient/master/info}). 
+It is also possible to locally emulate and test the computing environment on 
+the competition machines using the following instructions: 
+\url{https://gitlab.com/sosy-lab/benchmarking/competition-scripts/#computing-environment-on-competition-machines}.
 
@@
 The bulk of the computation will take place during the weeks leading
-up to SMT 2023.  Intermediate results will be regularly posted to the
+up to SMT 2024.  Intermediate results will be regularly posted to the
 SMT-COMP website as the competition runs.
@@
 
-The StarExec service also limits the memory consumption of the solver
+The \executionservice also limits the memory consumption of the solver
 processes.  We expect the memory limit per solver/benchmark pair to be
-on the order of 60\,GB.  The values of both the time limit and the
+on the order of 30\,GB.  The values of both the time limit and the
 memory limit are available to a solver process through environment
-variables.  See the StarExec user guide for more information.
-\todo{What are the limits for BenchExec? Do we set limits ourselves?}
+variables.  See the user guide for the \executionservice for more information.
 
 The limits for \paralleltrack{} and \cloudtrack{} are available at
-\url{https://smt-comp.github.io/2023/parallel-and-cloud-tracks.html}.
+\url{https://smt-comp.github.io/2024/parallel-and-cloud-tracks.html}.
 
@@
 produced there (and not, say, in the system's \texttt{/tmp}
-directory).  The StarExec system sets a limit on the amount of disk
-storage permitted---typically 20\,GB.  See the StarExec user guide for
-more information.  The temporary directory is deleted after the job is
-complete.  Solvers must not attempt to communicate with other
-machines, e.g., over the network.
+directory).  The \executionservice sets a limit on the amount of disk
+storage permitted---typically 20\,GB.  See the user guide for the 
+\executionservice for more information.  The temporary directory is 
+deleted after the job is complete.  Solvers must not attempt to 
+communicate with other machines, e.g., over the network.
 \todo{What are the limits for BenchExec? Do we set limits ourselves?}
@@
 \header{Time Limit.}
-This track will use a wall-clock time limit of 20 minutes per
+This track will use a wall-clock time limit of 2 minutes per
 solver/benchmark pair.
@@
 \header{New benchmarks.}
-The deadline for submission of new benchmarks was {\bf March~31, 2023}.
+The deadline for submission of new benchmarks was {\bf April~13, 2024}.
 %
 The organizers, in collaboration with the SMT-LIB maintainers, will be
-checking and curating these until {\bf May~13, 2023}.
+checking and curating these until {\bf May~11, 2024}.
 
@@
       solvers (including non-competitive solvers) in less than one second in
-          the corresponding track in 2018--2022.
+          the corresponding track in 2018--2023.
     \item \emph{\ucoretrack.} All benchmarks with only a single assertion.
@@
 
-SMT-COMP 2023 is organized under the direction of the SMT Steering
+SMT-COMP 2024 is organized under the direction of the SMT Steering
 Committee. The organizing team is

### 2024-05-07 rules/rules24.tex
Changed date in the rules for taking the opening value of the NYSE Composite Index.
Update Disclosure for M. Jonáš.

@@
   system descriptions.
-\item[June~11] Opening value of NYSE Composite Index used to compute
+\item[June~10] Opening value of NYSE Composite Index used to compute
   random seed for competition tools.
@@
 %
-Martin Jon\'{a}\v{s} is part of the developing team of \todo{Martin J. please fill this out}.
+Martin Jon\'{a}\v{s} is part of the developing team of the SMT solver Q3B~\cite{Q3B} and was a member of the developing team of the SMT solver MathSAT5~\cite{MathSAT5}.
 

### 2024-05-07 rules/rules24.tex
The rules for 2024 mention now that the proof track has been discontinued.

--- 2024-04-22 rules/rules24.tex
@@
 \newcommand{\cloudtrack}{Cloud Track\xspace}
-\newcommand{\prooftrack}{Proof Exhibition Track\xspace}
 
@@
 the \inctrack (before 2019: Application Track), the \ucoretrack, the \mvaltrack,
-the \paralleltrack{} and the \cloudtrack{} (both sponsered by Amazon Web
-Services), and an experimental \prooftrack{} focused on a qualitative evaluation
-of different proof formats, proof checkers and proof-producing solvers.
+and the \paralleltrack{} and the \cloudtrack{} (both sponsered by Amazon Web
+Services).
 %
@@
 %
-We will recognize winners in all tracks but the \prooftrack{}.
+We will recognize winners in all tracks.
 %
@@
   \item {\bf Move from StarExec to BenchExec.}  \emergencystretch.5cm
-  The single query, incremental, unsat-core, model-validation and proof exhibition tracks 
-  will no longer run on the StarExec platform hosted by the University of Iowa.
+  The single query, incremental, unsat-core, and model-validation will no longer 
+  run on the StarExec platform hosted by the University of Iowa.
   Starting this year, we will run these tracks on the BenchExec cluster 
@@
   \item {\bf Memory limits.}  \emergencystretch.5cm
-  The memory limits for the single query, incremental, unsat-core, model-validation and proof exhibition tracks are reduced to 30\,GB.
+  The memory limits for the single query, incremental, unsat-core, and model-validation tracks are reduced to 30\,GB.
 %
   \rationale{The reason are hardware limits of the new execution platform.}
+
+  \item {\bf Proof track.}  \emergencystretch.5cm
+  The previously experimental evaluation proof track will be discontinued.
+%
+  \rationale{There are three reasons that led to this decision. 
+             First, we were unable to find a way of turning the proof track into a competition that would not lead to 
+             an unmanageable amount of overhead on the competition organizers or the participants.
+             Second, we have collected vast amounts of data in the last two years and thoroughly evaluating it takes time.
+             Third, this year we would need to restrict the allowed proof size due to hardware limits of the new execution platform.}
 \end{itemize}
@@
 As part of the submission, SMT-COMP entrants are \textbf{required} to provide a
-short (1-2 pages, excluding references; plus 2 pages for proof format and proof
-checker if the entrant is for the proof exhibition track) description of the system, which \textbf{must} explicitly
+short (1-2 pages, excluding references) description of the system, which \textbf{must} explicitly
 acknowledge any solver it wraps or is based on in case of a \emph{wrapper} or
@@
     submitted solver, and
-  \item for participants of the \prooftrack{} a short description
-    of their proof format of up to two extra pages.
 \end{itemize}
@@
       single \akey{(set-option :produce-unsat-cores true)} command as
-      the second command.
-    \item In the \emph{\prooftrack}, a benchmark file contains a
-      single \akey{(set-option :produce-proofs true)} command as
       the second command.
@@
     \akey{get-model} command.
-  \item \bkey{(get-proof)}\\
-    In the \emph{\prooftrack}, the \akey{check-sat} command (which is
-    always issued in an unsatisfiable context) is followed by a single
-    \akey{get-proof} command.
   \item \bkey{(exit)}\\
@@
 their models.  We propose the new syntax on the SMT-COMP website
-{\url{https://smt-comp.github.io/2023/model.html}}.
+{\url{https://smt-comp.github.io/2024/model.html}}.
 
@@
 solver/benchmark pair.
-
-\subsection{\prooftrack}
-\label{sec:exec:proof}
-
-In the \prooftrack, teams can submit a proof-producing solver together with a
-proof checker for its proof format.  We will compile and present the results, as
-well as assemble a panel of experts (not necessarily organizers) to do a
-qualitative assessment for each proof-producing solver, proof format, and proof
-checker.
-
-\header{Benchmark Selection.}
-This track will run on a selection of non-incremental \emph{unsat} benchmarks
-(as described on page~\pageref{benchmark-selection}).
-
-\header{Input/Output Solver.}
-For the \prooftrack, solver authors should provide two scripts
-with their solver.  The first script,
-\texttt{smtcomp\_solver}, should take the name of the benchmark file as
-a single argument and run the solver on the benchmark.
-%
-As described in Section~\ref{sec:logistics}, the benchmark
-will contain the commands \akey{(check-sat)} and \akey{(get-proof)}.
-%
-The solver must output the answers to both of these commands to stdout.
-Output to stderr is ignored by the toolchain.
-
-Solvers must respond to each command in the benchmark script with the
-answers defined in the SMT-LIB format specification.  If the solver
-outputs a proof, this proof must be an s-expression according to the
-SMT-LIB standard, but otherwise the format is not specified.
-%
-Solvers that respond \texttt{unknown} to the \akey{check-sat} command should
-respond with an error to the following \akey{get-proof} command.  Note that the
-SMT-LIB conformant error result should be output to stdout.
-
-\header{Input/Output Checker.}
-The second script, \texttt{smtcomp\_checker}, should take
-the benchmark file name as first argument and the stdout output of the
-solver script as second argument.  Note that this output will
-usually start with the \texttt{unsat} result of the \akey{(check-sat)}
-command, which the checker must either parse or skip.
-
-The checker should check the proof within the output and provide the result to
-stdout.
-%
-Output printed to stderr is ignored.
-%
-The first line of the proof checker result should be either \texttt{valid},
-\texttt{invalid}, \texttt{holey}, \texttt{sat}, or \texttt{unknown}.
-%
-The answer \texttt{valid} must only be given when the checker certifies that the
-given proof justifies the unsatisfiability of the given benchmark.
-%
-A checker that returns \texttt{valid} to a satisfiable benchmark is deemed to be
-unsound.
-%
-The answer \texttt{invalid} should be returned if the proof is erroneous or
-otherwise malformed.
-%
-If the proof checker determines that the proof is valid but it contains holes,
-i.e., steps that are not checked for correctness, the answer should be
-\texttt{holey}.
-%
-The answer \texttt{sat} should be given if the solver claimed that the benchmark
-is satisfiable, and \texttt{unknown} should be given if (1) the solver answered
-\texttt{unknown}, (2) it answered \texttt{unsat} but did not give a proof, or
-(3) if the solver gave an error result.
-
-After the first line, the proof checker can provide arbitrary
-\texttt{key=value} pairs.
-%
-These will be collected in the final result table and can include for example
-information about the number of proof steps, the number of nodes in the proof,
-the number of holes, the number of different proof rules, etc.
-Each proof checker can define its own key/value pairs, but we suggest
-to implement the following:
-\begin{itemize}
-\item \texttt{holes} -- number of unchecked axioms or rewrite rules (that
-  can introduce unsoundness),
-\item \texttt{axioms} -- number of checked axioms or rewrite rules,
-\item \texttt{steps} -- number of proof steps (in some proof-specific
-  granularity),
-\item \texttt{assertions} -- number of asserted formulas used in the proof.
-\end{itemize}
-
-\header{Result.}
-%
-The result of a solver is considered \emph{erroneous} if (i) the
-proof checker returns \texttt{sat} (as the
-benchmark is necessarily unsatisfiable), or
-%
-(ii) the proof checker returns \texttt{invalid} to
-the given proof.
-%
-Since the \prooftrack is non-competitive and we are not fixing a definition of a
-valid proof, there will be no score computed for this track.
-
-A proof checker is unsound if it returns \texttt{valid} for an (invalid) proof
-of a satisfiable benchmark.
-%
-Thus, a proof checker must also check that the formula that was proved
-corresponds to the benchmark given.  Soundness of the proof checker is a central
-criterion by which the participants will be judged.
-
-\header{Evaluation Criteria.}
-%
-Since different proof formats are not easily comparable we will not do
-any scoring by counting solved benchmarks.  Instead we will evaluate
-both solvers and proof checkers using different criteria:
-\begin{itemize}
-\item \emph{soundness}: does the proof checker only accept correct
-  proofs?  In particular, does it check that the proof proves the formula
-  in the benchmark, and does it warn about unchecked rewrite rules?
-\item \emph{trust-base}: how big is the trusted code and how much is
-  shared between proof checker and solver?
-\item \emph{proof overhead}: what is the performance of the solver and
-  the proof checker compared to running the solver without proof
-  production?
-\item \emph{granularity}: what is the granularity of the proof?
-\item \emph{readability}: is the proof easy to digest for a human?
-\item \emph{extractability}: is the proof suitable for automatic
-  processing?  Are there some implicit rewrites that one has to be
-  aware of?
-\item \emph{stability}: Is the proof checker specific to the current
-  version of the solver and needs to be updated with each solver
-  release, or is the proof checker fixed (except when adding new
-  theories)?
-\end{itemize}
-
-\header{Time Limit.}
-This track will use a wall-clock time limit of 20 minutes per solver/benchmark
-pair. This time limit includes the time for proof checking.
-
-\header{Wrapper and Post-Processor.}
-Solvers in this track will be wrapped in the competition to include the script
-{\url{https://github.com/SMT-COMP/postprocessors/tree/master/proof-track/starexec_run_proof}},
-which calls the solver and checker script.
-Participants are encouraged to wrap their solvers themselves to test
-their submission.
-The track will use
-{\url{https://github.com/SMT-COMP/postprocessors/tree/master/proof-track/process}}
-as a post-processor
-to validate and accumulate the results.
-\todo{We need a new link for the corresponding benchexec script.}
 
@@
 QF\_LIA, QF\_LRA, QF\_LIRA, QF\_UF, QF\_UFBV, QF\_UFIDL, QF\_UFLIA, QF\_UFLRA.
-The \prooftrack will use a selection of non-incremental
-\emph{unsat} benchmarks.
 To determine whether a benchmark is sat or unsat, a combination of
@@
 \item
-  For the \prooftrack and \ucoretrack, all benchmarks with status
+  For the \ucoretrack, all benchmarks with status
   \texttt{sat} are removed.  We further remove benchmarks with status
@@
     \end{enumerate}
-    For the \prooftrack, we will only run $min(n, max(150,
-    25n/100)))$ benchmarks.
 \end{enumerate}

### 2024-05-07 rules/rules24.tex
Added the new smtcomp tool to the rules document.

@@
 %
-  \rationale{The reason are hardware limits of the new execution platform.}
+  \rationale{The reasons are hardware limits of the new execution platform.}
 
@@
              Third, this year we would need to restrict the allowed proof size due to hardware limits of the new execution platform.}
+
+  \item {\bf Tools.}  \emergencystretch.5cm
+    All the relevant scripts in \url{https://github.com/SMT-COMP/smt-comp} have been combined into one tool called \textbf{smtcomp}
+    that is available at 
+    \url{https://github.com/SMT-COMP/smt-comp.github.io}.
+%
+  \rationale{The reason for this new tool is that the sheer number of old scripts and their various locations 
+             caused a lot of confusion to many new and several longtime participants.
+             The tool also has better run time compared to some of the old scripts because it uses parallelization where possible.
+             Moreover, it provides a nicer UI compared to the old scripts.}
 \end{itemize}
@@
 The competition uses a number of tools/scripts to run the competition. In the
-following, we briefly describe these tools. Unless stated otherwise, these
-tools are found at \url{https://github.com/SMT-COMP/smt-comp/tree/master/tools}.
+following, we briefly describe these tools.
 \begin{itemize}
-  \item \textbf{Benchmark Selection.} We use a script to implement the
+  \item \textbf{smtcomp.} This tool combines the functionality of most of the 
+    scripts used in previous years and more. It is available at 
+    \url{https://github.com/SMT-COMP/smt-comp.github.io}. Some of its functionalities include:
+    \begin{itemize}
+      \item \textbf{Benchmark Selection.} The tool has a command that executes the
         benchmark selection policy described on page~\pageref{benchmark-selection}.
@@
         for all tools requiring randomisation.
+      \item \textbf{Scoring.} The tool has a command that executes the scoring computation
+        described on in Section~\ref{sec:scoring}. It also includes the scoring
+        computations used in previous competitions (since 2015).
+    \end{itemize}
+    For a full list of the capabilities of the smtcomp tool and an explanation of all important commands
+    see \url{https://github.com/SMT-COMP/smt-comp.github.io/blob/master/README.md}
   \item \textbf{Scrambler.} This tool is used to scramble benchmarks during the
@@
     track) are available at \url{https://github.com/SMT-COMP/postprocessors}.
-  \item \textbf{Scoring.} We use a script to implement the scoring computation
-    described on in Section~\ref{sec:scoring}. It also includes the scoring
-    computations used in previous competitions (since 2015).
 \end{itemize}

### 2024-05-09 rules/rules24.tex
Clarify persistent storage.

@@
 course of an execution, but they must not read such files back during
-later executions.  Each solver is executed with a temporary directory
-as its current working directory.  Any generated files should be
-produced there (and not, say, in the system's \texttt{/tmp}
-directory).  The \executionservice sets a limit on the amount of disk
-storage permitted---typically 20\,GB.  See the user guide for the
-\executionservice for more information.  The temporary directory is
-deleted after the job is complete.  Solvers must not attempt to
-communicate with other machines, e.g., over the network.
-\todo{What are the limits for BenchExec? Do we set limits ourselves?}
+later executions. This is ensured by BenchExec by executing each solver
+with the whole filesystem mounted as read-only with an overlay writeable
+layer that is mounted as a RAM disk. Any generated files will be therefore
+written to the RAM disk. The used storage is counted into the
+memory limit. The temporary overlay layer is deleted after the job is complete.
+Solvers must not attempt to communicate with other machines, e.g., over the network.
 

### 2024-05-24 rules/rules24.tex
Remove mention of the dockerfile

@@
   Moreover, participants are now required to upload their final solver versions as a Zenodo
-  (\url{https://zenodo.org/}) submission that must contain a docker file that compiles the solver.
+  (\url{https://zenodo.org/}) submission.
 %
@@
 \paralleltrack{} and \cloudtrack{}, otherwise communicated to the
-organisers. The final solver version needs to be uploaded as a Zenodo (https://zenodo.org/ <https://zenodo.org/>) submission
-that must contain a docker file that compiles the solver.
+organisers.
+The final solver version needs to be uploaded as a Zenodo (https://zenodo.org/ <https://zenodo.org/>) submission.
+The solver is an archive that contains the executable precompiled (statically linked is preferable).
+It will be executed on a computer that have the same installation than the docker image \texttt{docker image name}.
 
@@
 The easiest way to create this push request is via the web-interface available under
-the above URL. The actual solver must be submitted via a link to a publicly available
-docker file that compiles the solver. For the \cloudtrack{} and \paralleltrack{},
+the above URL. For the \cloudtrack{} and \paralleltrack{},
 it must be communicated separately to the organisers by email to

### 2024-07-18 2024/slides/presresults/input_for_certificates.tex
SMT Workshop 2024 slides draft.

\MakeOnePage{Algaroba}{}{\withtrack{QF\_Datatypes}{\seq,\paral,\fast}}{}{}{}
\newpage
\MakeOnePage{Amaya}{}{}{\withtrack{NIA}{\fast}}{}{}
\newpage
\MakeOnePage{Bitwuzla}{}{\withtrack{Bitvec}{\sat}, \withtrack{FPArith}{\seq,\paral,\sat,\unsat,\fast}, \withtrack{QF\_Bitvec}{\seq,\paral,\unsat,\fast}, \withtrack{QF\_Equality\_Bitvec}{\seq,\paral,\sat,\unsat}, \withtrack{QF\_FPArith}{\seq,\paral,\sat,\unsat,\fast}}{\withtrack{ABVFP}{\sat}, \withtrack{ABVFPLRA}{\sat}, \withtrack{AUFBV}{\seq,\paral,\sat,\unsat,\fast}, \withtrack{AUFBVFP}{\seq,\paral,\sat,\unsat,\fast}, \withtrack{QF\_UFBV}{\fast}, \withtrack{UFBV}{\fast}, \withtrack{UFBVFP}{\seq,\paral,\unsat,\fast}}{s}{s}
\newpage
\MakeOnePage{COLIBRI}{}{}{\withtrack{QF\_FP}{\fast}, \withtrack{QF\_FPLRA}{\fast}}{}{s}
\newpage
\MakeOnePage{cvc5}{\withtrack{Biggest Lead}{\seq,\paral,\sat,\unsat,\fast}, \withtrack{Largest Contribution}{\seq,\paral,\sat,\unsat,\fast}}{\withtrack{Arith}{\seq,\paral,\unsat}, \withtrack{Bitvec}{\seq,\paral,\unsat}, \withtrack{Equality}{\seq,\paral,\sat,\unsat,\fast}, \withtrack{Equality\_LinearArith}{\seq,\paral,\sat,\unsat,\fast}, \withtrack{Equality\_MachineArith}{\seq,\paral,\sat,\unsat,\fast}, \withtrack{Equality\_NonLinearArith}{\seq,\paral,\sat,\unsat,\fast}, \withtrack{QF\_Datatypes}{\sat}, \withtrack{QF\_Equality}{\sat}, \withtrack{QF\_Equality\_NonLinearArith}{\unsat}, \withtrack{QF\_LinearIntArith}{\unsat}, \withtrack{QF\_LinearRealArith}{\unsat}, \withtrack{QF\_NonLinearRealArith}{\unsat}}{\withtrack{FP}{\fast}, \withtrack{LIA}{\sat,\fast}, \withtrack{NIA}{\sat}, \withtrack{NRA}{\sat}, \withtrack{QF\_ABVFPLRA}{\seq,\paral,\sat,\unsat}, \withtrack{QF\_AUFNIA}{\seq,\paral,\fast}, \withtrack{QF\_AX}{\fast}, \withtrack{QF\_FP}{\sat}, \withtrack{QF\_LIRA}{\fast}, \withtrack{QF\_UFBVDT}{\seq,\paral,\fast}, \withtrack{QF\_UFDT}{\seq,\paral}, \withtrack{QF\_UFDTNIA}{\seq,\paral,\sat,\fast}, \withtrack{QF\_UFFPDTNIRA}{\seq,\paral,\sat,\unsat,\fast}, \withtrack{QF\_UFLRA}{\unsat}}{s}{s}
\newpage
\MakeOnePage{iProver v3.9}{}{}{\withtrack{ALIA}{\paral,\unsat}, \withtrack{UF}{\fast}, \withtrack{UFDTNIA}{\paral,\unsat}, \withtrack{UFLRA}{\seq,\paral,\unsat,\fast}, \withtrack{UFNIRA}{\seq,\unsat}}{}{s}
\newpage
\MakeOnePage{OpenSMT}{}{\withtrack{QF\_Equality\_LinearArith}{\unsat}, \withtrack{QF\_LinearIntArith}{\seq,\paral}, \withtrack{QF\_LinearRealArith}{\seq,\paral,\sat}}{\withtrack{QF\_AX}{\seq,\paral,\sat}, \withtrack{QF\_LIA}{\sat}, \withtrack{QF\_LRA}{\unsat,\fast}, \withtrack{QF\_UFIDL}{\seq,\paral,\sat}}{s}{s}
\newpage
\MakeOnePage{OSTRICH}{}{}{\withtrack{QF\_SNIA}{\seq,\paral,\sat,\fast}}{}{}
\newpage
\MakeOnePage{SMT-RAT}{}{}{\withtrack{NRA}{\unsat,\fast}}{}{}
\newpage
\MakeOnePage{SMTInterpol}{}{\withtrack{QF\_Equality\_LinearArith}{\seq,\paral,\sat}}{\withtrack{ALIA}{\sat}, \withtrack{ANIA}{\seq,\paral,\sat,\unsat,\fast}, \withtrack{QF\_ANIA}{\unsat,\fast}, \withtrack{QF\_AUFLIA}{\fast}, \withtrack{QF\_AX}{\unsat}, \withtrack{QF\_LIA}{\unsat}, \withtrack{QF\_LIRA}{\sat}, \withtrack{QF\_NIRA}{\seq,\paral,\unsat}, \withtrack{QF\_UF}{\sat}, \withtrack{QF\_UFBVDT}{\sat,\unsat}, \withtrack{QF\_UFDTLIA}{\unsat,\fast}, \withtrack{QF\_UFDTLIRA}{\unsat,\fast}, \withtrack{QF\_UFLIA}{\unsat}, \withtrack{UFLIA}{\sat}}{}{s}
\newpage
\MakeOnePage{STP}{}{\withtrack{QF\_Bitvec}{\sat}}{}{}{}
\newpage
\MakeOnePage{Yices2}{}{\withtrack{QF\_Equality}{\fast}, \withtrack{QF\_Equality\_Bitvec}{\fast}, \withtrack{QF\_Equality\_LinearArith}{\fast}, \withtrack{QF\_Equality\_NonLinearArith}{\seq,\paral,\sat,\fast}, \withtrack{QF\_LinearIntArith}{\fast}, \withtrack{QF\_LinearRealArith}{\fast}, \withtrack{QF\_NonLinearIntArith}{\fast}, \withtrack{QF\_NonLinearRealArith}{\fast}}{\withtrack{QF\_LIRA}{\seq,\paral,\unsat}, \withtrack{QF\_RDL}{\seq,\paral,\sat}, \withtrack{QF\_UFLRA}{\seq,\paral}, \withtrack{QF\_UFNRA}{\unsat}}{s}{s}
\newpage
\MakeOnePage{YicesQS}{}{\withtrack{Arith}{\sat,\fast}, \withtrack{Bitvec}{\fast}}{\withtrack{LRA}{\seq,\paral,\unsat}, \withtrack{NRA}{\seq,\paral}}{s}{s}
\newpage
\MakeOnePage{Z3-alpha}{}{\withtrack{QF\_Datatypes}{\unsat}, \withtrack{QF\_Equality}{\seq,\paral,\unsat}, \withtrack{QF\_LinearIntArith}{\sat}, \withtrack{QF\_NonLinearIntArith}{\seq,\paral,\sat,\unsat}, \withtrack{QF\_NonLinearRealArith}{\seq,\paral,\sat}}{\withtrack{QF\_AUFBV}{\unsat}, \withtrack{QF\_IDL}{\seq,\paral,\unsat}, \withtrack{QF\_NIRA}{\fast}, \withtrack{QF\_RDL}{\unsat}}{s}{s}
\newpage
\MakeOnePage{Z3-Noodler}{}{\withtrack{QF\_Strings}{\seq,\paral,\sat,\unsat,\fast}}{}{}{}
\newpage

### 2024-07-18 2024/slides/presresults/slides.tex
SMT Workshop 2024 slides draft.

--- 2023-07-06 2023/slides/presresults/slides.tex
@@
 %
-%   SMT-COMP 2023 - 
+%   SMT-COMP 2024 - 
 %
@@
 %%% Titel, Autor und Datum des Vortrags:
-\title{SMT-COMP 2023\\
-18th International Satisfiability Modulo Theory Competition}
-\author{Martin Bromberger \and Jochen Hoenicke \and \emph{Fran\c{c}ois Bobot}}
-\date{July 5, 2023}
+\title{SMT-COMP 20243\\
+19th International Satisfiability Modulo Theory Competition}
+\author{Fran\c{c}ois Bobot \and \emph{Martin Bromberger} \and Martin Jon\'{a}\v{s} }
+\date{July 22, 2024}
 
@@
 MPI für Informatik, Germany \and
-Certora, Israel
+Masaryk University, Czechia
 }
@@
 
-  \begin{minipage}[b]{.6\textwidth}
+  \begin{columns}
+    \begin{column}{0.6\textwidth}
     Annual competition for \emph{SMT solvers}\\
     on (a selection of) benchmarks from \emph{SMT-LIB}
-  \end{minipage}%
-  \begin{minipage}{.4\textwidth}
-    \begin{block}{History}
-      \begin{tabular}{rp{3cm}}
-        \textbf{2005} & first competition \\
-        \textbf{2013} & evaluation instead \\
-        & of competition\\
-        \textbf{2014} & since then hosted\\
-        & by \emph{StarExec}
-      \end{tabular}
-    \end{block}
-  \end{minipage}
+
+    \bigskip
+    \bigskip
 
@@
     \end{itemize}
+    \end{column}
+    \begin{column}{0.4\textwidth}
+    \begin{block}{History}
+      \begin{tabular}{rp{3cm}}
+        \textbf{2005} & first competition \\
+        \textbf{2013} & evaluation instead \\
+        & of competition\\
+        \textbf{2014} & since then hosted\\
+        & by \emph{StarExec}\\
+        \textbf{2024} & since then hosted\\
+        & by \emph{BenchExec} and the \emph{SoSy-Lab} 
+      \end{tabular}
+    \end{block}
+    \end{column}
+  \end{columns}
 
@@
       \begin{block}{Non-incremental}
-        434\,212 instances {\small (+42849)}\\ % 434212-391363=42849
+        438\,631 instances {\small (+4\,419)}\\ % 438631-434212=4419
         with 1 query each \\
-        in 83 logics {\small (+2)}.
+        in 84 logics {\small (+1)}.
       \end{block}
@@
       \begin{block}{Incremental}
-        43\,287 instances {\small (+2)}\\
-        with 34\,036\,491 queries {\small (+37\,556)} \\ %34036491-33998935=37556
-        in 38 logics. % -1 ???
+        44\,333 instances {\small (+1\,046)}\\ % 44333-43287=1046
+        with 34\,069\,145 queries {\small (+32\,654)} \\ %34036491-33998935=37556
+        in 39 logics. % -1 ???
       \end{block}
@@
       \begin{block}{Selected Non-incremental}
-        227\,940 instances
+        249\,301 instances % old 227\,940???
       \end{block}
@@
       \begin{block}{Selected Incremental}
-        22\,302 instances
+        22\,826 instances % old 22\,302
       \end{block}
@@
 
-  \emph{Cloud and Parallel Track} (sponsored by AWS, led by Mike Whalen)
+  \emph{Cloud and Parallel Track} (sponsored by AWS, led by Robert Jones and Benjamin F Jones)
   \begin{itemize}
@@
   \item Solver answers sat/unsat/unknown
-  \end{itemize}
-
-  \pause\bigskip
-
-  \emph{Proof Exhibition Track}
-  \begin{itemize}
-  \item Solver submitted together with a checker for unsatisfiability proofs
-  \item No predefined format or checker
-  \item No ranking
-  \item Qualitative assessment
+  \item Thanks to Mike Whalen for managing these tracks the last two years and 
+        thanks to Robert Jones and Benjamin F Jones for taking over
   \end{itemize}
@@
 
+\begin{frame}[fragile]{SMT-COMP Tracks (discontinued)}
+
+  \emph{Proof Exhibition Track}
+  \begin{itemize}
+  \item Solver submitted together with a checker for unsatisfiability proofs
+  \item No predefined format or checker
+  \item No ranking
+  \item Qualitative assessment
+  \item Discontinued because:
+    \begin{itemize}
+    \item unable to turn this into competition
+    \item still processing the data of the last two years
+    \item restrictions of the BenchExec cluster (no disk space to store proofs)
+    \end{itemize}
+  \end{itemize}
+
+\end{frame}
+
 \begin{frame}{Tracks, Solvers, Divisions, and Benchmarks}
-  Teams: 25 (+4) %2022 21
+  Teams: 20 (-5) %2023 25
   \bigskip
@@
     \hline
-    Single Query  &  22&(=)  & 19&(=)  & 113\,139 \\
-    Incremental &  7&(-1)   & 17&(=)  & 22\,301   \\
-    Unsat Core  &  6&(=)   & 16&(-1)  & 72\,958  \\
-    Model Validation  &  11&(+3)    &  13& (+ 6 exp.)  & 61\,083  \\
-    Proof Exhibition  &  4&(=)    &  & 19 exp.  & 59\,114  \\
+    Single Query  &  16&(-6)  & 19&(=)  & 123\,486 \\ %&(+10\,347)
+    Incremental &  7&(=)   & 18&(+1)  & 22\,826   \\ %&(+525) Bitvec+Arith
+    Unsat Core  &  6&(=)   & 19&(=)  & 66\,190  \\ %&(-6\,768)72\,958
+    Model Validation  &  8&(-3)    &  7& (+ 8 exp.)  & 59\,625  \\ %-61\,083
+%    Proof Exhibition  &  4&(=)    &  & 19 exp.  & 59\,114  \\
     \hline
-    Parallel &   3&(-1)      &   &4 exp.  & 400 \\
-    Cloud & 2&(-2)      &  &4 exp.  & 400 \\
+    Parallel &   2&(-1)      &   &2 exp.  & 400 \\
+    Cloud & 3&(+1)      &  &5 exp.  & 400 \\
 
@@
 
-  Number in parenthesis shows changes from 2022
+  Number in parenthesis shows changes from 2023
 \end{frame}
@@
 
-  SMT-COMP 2022 participants rely on multiple reasoning frameworks:
+  SMT-COMP 2024 participants rely on multiple reasoning frameworks:
   \begin{itemize}
@@
   \bigskip
-  Seven new solvers participated:
+  Six new solvers participated:
   \begin{itemize}
-\item iProver {\footnotesize (Korovin et al.)}
-\item SMT-RAT-MCSAT {\footnotesize (Jasper Nalbach et al.)}
-\item UltimateIntBlastingWrapper+SMTInterpol {\footnotesize (Max Barth et al.)}
-\item Yaga {\footnotesize (Hanák et al.)}
-\item Z3-alpha {\footnotesize (Lu et al.)}
-\item Z3-Noodler {\footnotesize (Havlena et al.)}
-\item Z3-Owl {\footnotesize (Ma et al.)}
+\item Algaroba {\footnotesize (Shah et al.)}
+\item Amaya {\footnotesize (Havlena et al.)}
+\item plat-smt {\footnotesize (Ewert)}
+\item SMTS {\footnotesize (Kol\'{a}rik et al.)}
+\item (STP-Parti-Bitwuzla {\footnotesize (Zhao et al.)})
+\item Z3-Parti-Z3++ {\footnotesize (Zhao et al.)}
 \end{itemize}
@@
 
-\myincludepdf{slides-bitwuzla.pdf}
+\myincludepdf{amaya.pdf}
 
-\myincludepdf{slides-colibri.pdf}
+\myincludepdf{Bitwuzla.pdf}
 
-\myincludepdf{slides-cvc5.pdf}
+\myincludepdf{cvc5.pdf}
 
-\myvideopdf{cvc5-NRA-LS}{slides-cvc5-nra-ls.mp4}
+\myvideopdf{OSTRICH}{Ostrich.mkv}
 
-\myvideopdf{iProver}{slides-iProver.mp4}
+\myincludepdf{smtinterpol.pdf}
 
-\myvideopdf{ismt, Yices-ismt}{slides-ismt.mp4}
+\myvideopdf{SMT-RAT}{SMT-RAT.mkv}
 
-\myincludepdf{slides-ismt-ppt.pdf}
+\myincludepdf{Yices2.pdf}
 
-\myincludepdf{slides-opensmt.pdf}
+\myincludepdf{YicesQS.pdf}
 
-\myvideopdf{Ostrich}{slides-Ostrich.mkv}
+\myincludepdf{z3-alpha.pdf}
 
-\myincludepdf{slides-smtinterpol.pdf}
-
-\myincludepdf{slides-smtrat.pdf}
-
-\myvideopdf{UltimateEliminator+MathSAT}{slides-UltimateEliminator.mkv}
-
-\myincludepdf{slides-vampire.pdf}
-
-\myincludepdf{slides-yaga.pdf}
-
-\myincludepdf{slides-Yices-2023.pdf}
-
-\myincludepdf{slides-YicesQS-2023.pdf}
-
-%\myvideopdf{Z3-Z3++}{slides-z3-z3++.mp4}
-\begin{frame}
-  \frametitle{Z3-Z3++}
-
-  \begin{center}
-    \url{https://youtu.be/fBB0Wxxf9vA}
-  \end{center}
-\end{frame}
+\myincludepdf{Z3-Parti-Z3++.pdf}
 
@@
     \begin{itemize}
-\item Q3B
-\vitem Q3B-pBDD
+\item Algaroba
+\vitem COLIBRI
+\vitem iProver
+\vitem OpenSMT
+\vitem plat-smt
+\vitem SMTS
 \vitem STP
-\vitem UltimateIntBlastingWrapper+SMTInterpol
-\vitem z3-alpha
+\vitem (STP-Parti-Bitwuzla)
 \vitem Z3-Noodler
-\vitem Z3-Owl
     \end{itemize}
@@
   \begin{itemize}
-  \item Best solvers, per division, from previous years (27 Solvers)
+  \item Best solvers, per division, from previous years
   \end{itemize}
@@
   \begin{itemize}
-  \item Fixed solvers (OSTRICH, Z3-Owl, Bitwuzla, Yices2, Z3-Noodler, iProver)  
+  \item Fixed solvers (Amaya, cvc5, OSTRICH, iProver)  
   \end{itemize}
+  \bigskip
+  \bigskip
+  (All still in the process of running)
 \end{frame}
@@
   \begin{itemize}
-  \item  50411 benchmarks of 227\,938 have no status
+  \item  50411 benchmarks of 249\,301 have no status
 
-  \vitem 300 benchmarks with disagreements (ABV,
-  BV,
-  LIA,
-  NIA,
-  QF\_ABV,
-  QF\_AUFBV,
-  QF\_BVFP,
-  QF\_FP,
-  QF\_NRA,
-  QF\_SLIA,
-  UF,
-  UFDT,
-  UFDTLIRA)
+  \vitem 2 benchmarks with disagreements (QF\_SLIA)
 
@@
   unsoundness
-  \vitem We had 10 solvers with soundness issues:
-  \begin{columns}
-    \column{0.45\textwidth}
+  \vitem We had 4 solvers with soundness issues:
     \begin{itemize}
-      \item Bitwuzla (uc printing error)
+      \item Amaya (\& Fixed)
+      \item cvc5 (\& Fixed)
       \item iProver (\& Fixed)
-      \item OSTRICH
-      \item Q3B
-      \item UltimateEliminator+MathSAT
+      \item OSTRICH (\& Fixed)
     \end{itemize}
-    \column{0.55\textwidth}
-    \begin{itemize}
-      \item UltimateIntBlastingWrapper+SMTInterpol
-      \item Vampire
-      \item Yices2 (\& Fixed)
-      \item Z3-Noodler (\& Fixed)
-      \item Z3-Owl (\& Fixed)
-    \end{itemize} 
-\end{columns}
-
   \end{itemize}
@@
 \begin{frame}[fragile]
-  \frametitle{Plans for SMT-COMP 2023}
+  \frametitle{Plans for SMT-COMP 2025?}
   \begin{itemize}
-    \item "Revelations are found in clouds” --- Serge King
+    \item General: Documentation and streamlining
+    \item General: More CI support for submissions
+    \item Cloud/Parallel: Integrate them into the normal process
     \item MV: Algebraic number $\implies$ non experimental
@@
 
-\begin{frame}{Plans for SMT-COMP 2023?}
+\begin{frame}{Plans for SMT-COMP 2025?}
   \begin{itemize}
     \item Proof \textit{validation} track
-
-      \vitem Hopefully proof exhibition this year will help
-
-      \vitem We have to analyze the data still
       \begin{itemize}
-        \item Job only finished last week (took 18 days to run)
-        \item 830gb
+        \item We have to analyze the data still (830gb)
+        \item Ideas to turn this into a competition are welcome
       \end{itemize}
@@
 \begin{frame}{SMT-COMP organizing committee}
-  Three people organize the SMT-COMP.  In 2023:
+  Three people organize the SMT-COMP.  In 2024:
   \begin{itemize}
+  \item Fran\c{c}ois Bobot
   \item Martin Bromberger
-  \item Jochen Hoenicke
-  \item Fran\c{c}ois Bobot
+  \item Martin Jon\'{a}\v{s}
   \end{itemize}
 
-  Jochen have been organizer for four-years! He can rest happy.
+  Martin B. has to leave early due to conflicts with his new job.\newline\newline
+  Fran\c{c}ois will stay but only in an advisory role.
   \bigskip
 
-  We need a successor for next year's competition.
+  We need two successors for next year's competition.
   Contact us if you would like to volunteer!
@@
     \item \emph{Clark Barrett, Pascal Fontaine, Aina Niemetz, Mathias Preiner, Hans-Jörg Schurr}: SMT-LIB benchmarks
+    \item \emph{Robert Jones, Benjamin F Jones, and team}: Cloud/Parallel Track
+    \item \emph{Dirk Beyer and Philipp}: BenchExec and VerifierCloud support   
     \item \emph{Aaron Stump}: StarExec support
-    \item \emph{Mike Whalen and team}: Cloud/Parallel Track
   \end{itemize}
@@
 \begin{frame}[shrink=0.95]{Benchmark contributors}
-  In 2023 \emph{new benchmarks} were contributed by:
+  In 2024 \emph{new benchmarks} were contributed by:
 
@@
   \begin{itemize}
-    \item  Alex Coffin
-    \item  Alex Ozdemir
-    \item  Ali Uncu, James Davenport and Matthew England
-    \item  Bohan Li
-    \item  Elizabeth Polgreen
-    \item  Fuqi Jia
-    \item  Johann-Tobias Aaron and Raphael Schäg
-    \item  Matthew England and Miguel Del Rio Almajano
-    \item  Nicolas Amat
-    \item  Yannick Moy
-    \item  Yoni Zohar
+    \item TODO
   \end{itemize}

### 2024-07-19 2024/slides/presresults/input_for_certificates.tex
Updated slides with QF_BVFP incr. results.

@@
-\MakeOnePage{Algaroba}{}{\withtrack{QF\_Datatypes}{\seq,\paral,\fast}}{}{}{}
+\MakeOnePage{Algaroba}{}{\withtrack{QF\_Datatypes}{\seq,\paral,\fast}}{\withtrack{QF\_DT}{\sat}}{}{}
 \newpage
@@
 \newpage
-\MakeOnePage{Bitwuzla}{}{\withtrack{Bitvec}{\sat}, \withtrack{FPArith}{\seq,\paral,\sat,\unsat,\fast}, \withtrack{QF\_Bitvec}{\seq,\paral,\unsat,\fast}, \withtrack{QF\_Equality\_Bitvec}{\seq,\paral,\sat,\unsat}, \withtrack{QF\_FPArith}{\seq,\paral,\sat,\unsat,\fast}}{\withtrack{ABVFP}{\sat}, \withtrack{ABVFPLRA}{\sat}, \withtrack{AUFBV}{\seq,\paral,\sat,\unsat,\fast}, \withtrack{AUFBVFP}{\seq,\paral,\sat,\unsat,\fast}, \withtrack{QF\_UFBV}{\fast}, \withtrack{UFBV}{\fast}, \withtrack{UFBVFP}{\seq,\paral,\unsat,\fast}}{s}{s}
+\MakeOnePage{Bitwuzla}{\withtrack{Biggest Lead}{\inc}}{\withtrack{Bitvec}{\sat}, \withtrack{Equality\_MachineArith}{\inc,\uc}, \withtrack{FPArith}{\seq,\paral,\sat,\unsat,\fast,\inc}, \withtrack{QF\_ADT\_BitVec}{\mv}, \withtrack{QF\_Bitvec}{\seq,\paral,\unsat,\fast,\inc}, \withtrack{QF\_Equality\_Bitvec}{\seq,\paral,\sat,\unsat,\inc}, \withtrack{QF\_FPArith}{\seq,\paral,\sat,\unsat,\fast,\inc,\uc}}{\withtrack{ABVFP}{\sat}, \withtrack{AUFBV}{\seq,\paral,\sat,\unsat,\fast}, \withtrack{AUFBVFP}{\seq,\paral,\sat,\unsat,\fast}, \withtrack{BVFPLRA}{\uc}, \withtrack{QF\_ABV}{\uc\textsuperscript\seq}, \withtrack{QF\_ABVFP}{\mv}, \withtrack{QF\_BVFPLRA}{\mv}, \withtrack{QF\_FPLRA}{\mv}, \withtrack{QF\_UFBV}{\fast}, \withtrack{UFBV}{\fast}}{s}{s}
 \newpage
-\MakeOnePage{COLIBRI}{}{}{\withtrack{QF\_FP}{\fast}, \withtrack{QF\_FPLRA}{\fast}}{}{s}
+\MakeOnePage{COLIBRI}{}{}{\withtrack{QF\_ABVFPLRA}{\unsat}, \withtrack{QF\_FP}{\fast}, \withtrack{QF\_FPLRA}{\unsat,\fast}}{}{s}
 \newpage
-\MakeOnePage{cvc5}{\withtrack{Biggest Lead}{\seq,\paral,\sat,\unsat,\fast}, \withtrack{Largest Contribution}{\seq,\paral,\sat,\unsat,\fast}}{\withtrack{Arith}{\seq,\paral,\unsat}, \withtrack{Bitvec}{\seq,\paral,\unsat}, \withtrack{Equality}{\seq,\paral,\sat,\unsat,\fast}, \withtrack{Equality\_LinearArith}{\seq,\paral,\sat,\unsat,\fast}, \withtrack{Equality\_MachineArith}{\seq,\paral,\sat,\unsat,\fast}, \withtrack{Equality\_NonLinearArith}{\seq,\paral,\sat,\unsat,\fast}, \withtrack{QF\_Datatypes}{\sat}, \withtrack{QF\_Equality}{\sat}, \withtrack{QF\_Equality\_NonLinearArith}{\unsat}, \withtrack{QF\_LinearIntArith}{\unsat}, \withtrack{QF\_LinearRealArith}{\unsat}, \withtrack{QF\_NonLinearRealArith}{\unsat}}{\withtrack{FP}{\fast}, \withtrack{LIA}{\sat,\fast}, \withtrack{NIA}{\sat}, \withtrack{NRA}{\sat}, \withtrack{QF\_ABVFPLRA}{\seq,\paral,\sat,\unsat}, \withtrack{QF\_AUFNIA}{\seq,\paral,\fast}, \withtrack{QF\_AX}{\fast}, \withtrack{QF\_FP}{\sat}, \withtrack{QF\_LIRA}{\fast}, \withtrack{QF\_UFBVDT}{\seq,\paral,\fast}, \withtrack{QF\_UFDT}{\seq,\paral}, \withtrack{QF\_UFDTNIA}{\seq,\paral,\sat,\fast}, \withtrack{QF\_UFFPDTNIRA}{\seq,\paral,\sat,\unsat,\fast}, \withtrack{QF\_UFLRA}{\unsat}}{s}{s}
+\MakeOnePage{cvc5}{\withtrack{Biggest Lead}{\seq,\paral,\sat,\unsat,\fast}, \withtrack{Largest Contribution}{\seq,\paral,\sat,\unsat,\fast}}{\withtrack{Arith}{\seq,\paral,\unsat,\inc}, \withtrack{Bitvec}{\seq,\paral,\unsat,\inc,\uc}, \withtrack{Equality}{\seq,\paral,\sat,\unsat,\fast,\inc}, \withtrack{Equality\_LinearArith}{\seq,\paral,\sat,\unsat,\fast,\inc}, \withtrack{Equality\_MachineArith}{\seq,\paral,\sat,\unsat,\fast}, \withtrack{Equality\_NonLinearArith}{\seq,\paral,\sat,\unsat,\fast,\inc}, \withtrack{FPArith}{\uc}, \withtrack{QF\_Datatypes}{\sat,\uc}, \withtrack{QF\_Equality\_LinearArith}{\uc\textsuperscript\paral}, \withtrack{QF\_Equality\_NonLinearArith}{\unsat,\inc,\uc\textsuperscript\seq,\mv}, \withtrack{QF\_FPArith}{\mv}, \withtrack{QF\_LinearIntArith}{\unsat}, \withtrack{QF\_LinearRealArith}{\unsat}, \withtrack{QF\_NonLinearRealArith}{\unsat}, \withtrack{QF\_Strings}{\uc}}{\withtrack{ANIA}{\uc}, \withtrack{AUFBV}{\uc\textsuperscript\paral}, \withtrack{AUFBVDTLIA}{\uc}, \withtrack{AUFBVDTNIRA}{\uc}, \withtrack{AUFDTLIRA}{\uc\textsuperscript\seq}, \withtrack{AUFFPDTNIRA}{\uc}, \withtrack{AUFLIRA}{\uc\textsuperscript\seq}, \withtrack{AUFNIA}{\uc\textsuperscript\paral}, \withtrack{BVFPLRA}{\unsat}, \withtrack{FP}{\fast}, \withtrack{LIA}{\sat,\fast}, \withtrack{NIA}{\sat}, \withtrack{QF\_AUFLIA}{\inc,\uc\textsuperscript\seq}, \withtrack{QF\_AX}{\mv}, \withtrack{QF\_BVFP}{\inc}, \withtrack{QF\_FP}{\sat,\uc}, \withtrack{QF\_IDL}{\uc}, \withtrack{QF\_LIA}{\mv}, \withtrack{QF\_SNIA}{\seq,\paral,\sat,\fast}, \withtrack{QF\_UFBVDT}{\seq,\paral,\unsat,\fast,\uc,\mv}, \withtrack{QF\_UFDT}{\seq,\paral,\mv}, \withtrack{QF\_UFDTLIRA}{\seq,\paral,\sat,\unsat,\fast,\uc\textsuperscript\seq,\mv}, \withtrack{QF\_UFDTNIA}{\seq,\paral,\sat,\fast}, \withtrack{QF\_UFFPDTNIRA}{\seq,\paral,\sat,\unsat,\fast}, \withtrack{QF\_UFLRA}{\inc,\uc\textsuperscript\seq}, \withtrack{UFDT}{\uc\textsuperscript\seq}, \withtrack{UFDTLIA}{\uc\textsuperscript\seq}, \withtrack{UFDTNIA}{\uc\textsuperscript\seq}, \withtrack{UFFPDTNIRA}{\uc}, \withtrack{UFIDL}{\uc\textsuperscript\seq}, \withtrack{UFLRA}{\uc}, \withtrack{UFNIRA}{\uc\textsuperscript\seq}}{s}{s}
 \newpage
-\MakeOnePage{iProver v3.9}{}{}{\withtrack{ALIA}{\paral,\unsat}, \withtrack{UF}{\fast}, \withtrack{UFDTNIA}{\paral,\unsat}, \withtrack{UFLRA}{\seq,\paral,\unsat,\fast}, \withtrack{UFNIRA}{\seq,\unsat}}{}{s}
+\MakeOnePage{iProver v3.9}{}{}{\withtrack{ALIA}{\paral,\unsat}, \withtrack{UF}{\fast}, \withtrack{UFNIRA}{\seq,\unsat}}{}{s}
 \newpage
-\MakeOnePage{OpenSMT}{}{\withtrack{QF\_Equality\_LinearArith}{\unsat}, \withtrack{QF\_LinearIntArith}{\seq,\paral}, \withtrack{QF\_LinearRealArith}{\seq,\paral,\sat}}{\withtrack{QF\_AX}{\seq,\paral,\sat}, \withtrack{QF\_LIA}{\sat}, \withtrack{QF\_LRA}{\unsat,\fast}, \withtrack{QF\_UFIDL}{\seq,\paral,\sat}}{s}{s}
+\MakeOnePage{OpenSMT}{}{\withtrack{QF\_Equality}{\mv}, \withtrack{QF\_Equality\_LinearArith}{\unsat,\mv}, \withtrack{QF\_LinearIntArith}{\seq,\paral,\mv}, \withtrack{QF\_LinearRealArith}{\seq,\paral,\sat,\inc,\mv}}{\withtrack{QF\_LIA}{\sat}, \withtrack{QF\_LRA}{\unsat,\fast}, \withtrack{QF\_UFIDL}{\seq,\paral,\sat}}{s}{s}
 \newpage
-\MakeOnePage{OSTRICH}{}{}{\withtrack{QF\_SNIA}{\seq,\paral,\sat,\fast}}{}{}
+\MakeOnePage{SMT-RAT}{}{\withtrack{QF\_NonLinearRealArith}{\mv}}{\withtrack{NRA}{\seq,\paral,\unsat,\fast}}{}{}
 \newpage
-\MakeOnePage{SMT-RAT}{}{}{\withtrack{NRA}{\unsat,\fast}}{}{}
+\MakeOnePage{SMTInterpol}{\withtrack{Biggest Lead}{\uc,\mv}}{\withtrack{Arith}{\uc}, \withtrack{Equality}{\uc\textsuperscript\paral}, \withtrack{Equality\_LinearArith}{\uc}, \withtrack{Equality\_NonLinearArith}{\uc}, \withtrack{QF\_ADT\_LinArith}{\mv}, \withtrack{QF\_Datatypes}{\mv}, \withtrack{QF\_Equality\_LinearArith}{\seq,\paral,\sat,\inc,\uc\textsuperscript\seq}, \withtrack{QF\_Equality\_NonLinearArith}{\uc\textsuperscript\paral}, \withtrack{QF\_NonLinearIntArith}{\inc,\uc}, \withtrack{QF\_NonLinearRealArith}{\uc}}{\withtrack{ALIA}{\sat}, \withtrack{ANIA}{\seq,\paral,\sat,\unsat,\fast}, \withtrack{QF\_ALIA}{\uc\textsuperscript\paral}, \withtrack{QF\_ANIA}{\unsat,\fast,\inc,\uc\textsuperscript\seq,\mv}, \withtrack{QF\_AUFNIA}{\sat,\uc\textsuperscript\seq,\mv}, \withtrack{QF\_LIA}{\unsat}, \withtrack{QF\_LIRA}{\uc\textsuperscript\paral}, \withtrack{QF\_UF}{\uc\textsuperscript\paral}, \withtrack{QF\_UFBVDT}{\sat}, \withtrack{QF\_UFDTLIA}{\unsat,\fast,\uc\textsuperscript\paral}, \withtrack{QF\_UFDTNIA}{\uc\textsuperscript\seq,\mv}, \withtrack{QF\_UFLIA}{\unsat,\mv}, \withtrack{QF\_UFNRA}{\uc\textsuperscript\seq}, \withtrack{UFIDL}{\sat}, \withtrack{UFLIA}{\sat}}{s}{s}
 \newpage
-\MakeOnePage{SMTInterpol}{}{\withtrack{QF\_Equality\_LinearArith}{\seq,\paral,\sat}}{\withtrack{ALIA}{\sat}, \withtrack{ANIA}{\seq,\paral,\sat,\unsat,\fast}, \withtrack{QF\_ANIA}{\unsat,\fast}, \withtrack{QF\_AUFLIA}{\fast}, \withtrack{QF\_AX}{\unsat}, \withtrack{QF\_LIA}{\unsat}, \withtrack{QF\_LIRA}{\sat}, \withtrack{QF\_NIRA}{\seq,\paral,\unsat}, \withtrack{QF\_UF}{\sat}, \withtrack{QF\_UFBVDT}{\sat,\unsat}, \withtrack{QF\_UFDTLIA}{\unsat,\fast}, \withtrack{QF\_UFDTLIRA}{\unsat,\fast}, \withtrack{QF\_UFLIA}{\unsat}, \withtrack{UFLIA}{\sat}}{}{s}
+\MakeOnePage{STP}{}{\withtrack{QF\_Bitvec}{\sat,\mv}}{}{}{}
 \newpage
-\MakeOnePage{STP}{}{\withtrack{QF\_Bitvec}{\sat}}{}{}{}
+\MakeOnePage{Yices2}{\withtrack{Largest Contribution}{\uc,\mv}}{\withtrack{Equality}{\uc\textsuperscript\seq}, \withtrack{QF\_Bitvec}{\uc}, \withtrack{QF\_Equality}{\seq,\paral,\sat,\unsat,\fast,\inc,\uc}, \withtrack{QF\_Equality\_Bitvec}{\fast,\uc,\mv}, \withtrack{QF\_Equality\_Bitvec\_Arith}{\inc}, \withtrack{QF\_Equality\_LinearArith}{\fast}, \withtrack{QF\_Equality\_NonLinearArith}{\seq,\paral,\sat,\fast}, \withtrack{QF\_LinearIntArith}{\fast,\inc,\uc}, \withtrack{QF\_LinearRealArith}{\fast,\uc}, \withtrack{QF\_NonLinearIntArith}{\fast,\mv}, \withtrack{QF\_NonLinearRealArith}{\fast}}{\withtrack{QF\_ALIA}{\unsat}, \withtrack{QF\_AUFLIA}{\seq,\paral,\sat,\unsat}, \withtrack{QF\_AUFNIA}{\unsat}, \withtrack{QF\_IDL}{\mv}, \withtrack{QF\_LIRA}{\sat,\mv}, \withtrack{QF\_RDL}{\seq,\paral,\sat,\unsat,\mv}, \withtrack{QF\_UFLIA}{\inc,\uc\textsuperscript\seq}, \withtrack{QF\_UFLRA}{\seq,\paral,\sat,\unsat,\mv}, \withtrack{QF\_UFNRA}{\unsat,\mv}, \withtrack{UF}{\uc\textsuperscript\paral}}{s}{s}
 \newpage
-\MakeOnePage{Yices2}{}{\withtrack{QF\_Equality}{\fast}, \withtrack{QF\_Equality\_Bitvec}{\fast}, \withtrack{QF\_Equality\_LinearArith}{\fast}, \withtrack{QF\_Equality\_NonLinearArith}{\seq,\paral,\sat,\fast}, \withtrack{QF\_LinearIntArith}{\fast}, \withtrack{QF\_LinearRealArith}{\fast}, \withtrack{QF\_NonLinearIntArith}{\fast}, \withtrack{QF\_NonLinearRealArith}{\fast}}{\withtrack{QF\_LIRA}{\seq,\paral,\unsat}, \withtrack{QF\_RDL}{\seq,\paral,\sat}, \withtrack{QF\_UFLRA}{\seq,\paral}, \withtrack{QF\_UFNRA}{\unsat}}{s}{s}
+\MakeOnePage{YicesQS}{}{\withtrack{Arith}{\sat,\fast}, \withtrack{Bitvec}{\fast}}{\withtrack{LRA}{\seq,\paral,\unsat}}{s}{}
 \newpage
-\MakeOnePage{YicesQS}{}{\withtrack{Arith}{\sat,\fast}, \withtrack{Bitvec}{\fast}}{\withtrack{LRA}{\seq,\paral,\unsat}, \withtrack{NRA}{\seq,\paral}}{s}{s}
-\newpage
-\MakeOnePage{Z3-alpha}{}{\withtrack{QF\_Datatypes}{\unsat}, \withtrack{QF\_Equality}{\seq,\paral,\unsat}, \withtrack{QF\_LinearIntArith}{\sat}, \withtrack{QF\_NonLinearIntArith}{\seq,\paral,\sat,\unsat}, \withtrack{QF\_NonLinearRealArith}{\seq,\paral,\sat}}{\withtrack{QF\_AUFBV}{\unsat}, \withtrack{QF\_IDL}{\seq,\paral,\unsat}, \withtrack{QF\_NIRA}{\fast}, \withtrack{QF\_RDL}{\unsat}}{s}{s}
+\MakeOnePage{Z3-alpha}{}{\withtrack{QF\_Datatypes}{\unsat}, \withtrack{QF\_LinearIntArith}{\sat}, \withtrack{QF\_NonLinearIntArith}{\seq,\paral,\sat,\unsat}, \withtrack{QF\_NonLinearRealArith}{\seq,\paral,\sat}}{\withtrack{QF\_AUFBV}{\unsat}, \withtrack{QF\_IDL}{\seq,\paral,\unsat}, \withtrack{QF\_LIRA}{\seq,\paral,\unsat}, \withtrack{QF\_NIRA}{\fast}}{s}{s}
 \newpage

### 2024-07-19 2024/slides/presresults/slides.tex
Updated slides with QF_BVFP incr. results.

@@
 
+\myvideopdf{Algaroba}{Algaroba.mp4}
+
 \myincludepdf{amaya.pdf}
@@
     \begin{itemize}
-\item Algaroba
-\vitem COLIBRI
-\vitem iProver
-\vitem OpenSMT
-\vitem plat-smt
-\vitem SMTS
-\vitem STP
-\vitem (STP-Parti-Bitwuzla)
-\vitem Z3-Noodler
+\item COLIBRI
+\item iProver
+\item OpenSMT
+\item plat-smt
+\item SMTS
+\item STP
+\item (STP-Parti-Bitwuzla)
+\item Z3-Noodler
     \end{itemize}
@@
     \begin{itemize}
-      \item Amaya (\& Fixed)
-      \item cvc5 (\& Fixed)
-      \item iProver (\& Fixed)
-      \item OSTRICH (\& Fixed)
+      \item Amaya (fixed version available)
+      \item cvc5 (fixed version available)
+      \item iProver (fixed version available)
+      \item OSTRICH (fixed version available)
     \end{itemize}
@@
   \end{itemize}
+  \bigskip
 
@@
     \item \emph{Robert Jones, Benjamin F Jones, and team}: Cloud/Parallel Track
-    \item \emph{Dirk Beyer and Philipp}: BenchExec and VerifierCloud support   
+    \item \emph{Dirk Beyer and Philipp Wendler}: BenchExec and VerifierCloud support   
     \item \emph{Aaron Stump}: StarExec support
@@
   \begin{itemize}
-    \item TODO
+    \item Matthias Heizmann (30)
+    \item Mirek Olšák, Mikoláš Janota, Chad E. Brown (266)
+    \item Tomas Kolarik (1046)
+    \item Martin von Berg, Arthur Sanin, Aron Spang, Christoph Beierle (80)
+    \item Michele Chiari, Francesco Pontiggia (14)
+    \item Tobias Winkler (6)
+    \item Certora (submitted by Antti Hyvärinen) (210)
+    \item Denghang Hu, Rongcheng Li, Zhilin Wu, Philipp Rummer, Oliver Markgraf (3287)
+    \item Federico Mora (500)
+    \item Oliver Markgraf (17)
+    \item Shilpi Goel, Nathan Wetzler, Yan Peng, Jim Grundy (Courtesy of AWS) (9)
   \end{itemize}

### 2024-07-20 2024/slides/presresults/slides.tex
Updated slides for 2024.

@@
         & of competition\\
-        \textbf{2014} & since then hosted\\
-        & by \emph{StarExec}\\
+        \textbf{2014} & since then until 2024\\
+        & hosted by \emph{StarExec}\\
         \textbf{2024} & since then hosted\\
@@
   \begin{itemize}
-    \item General: Documentation and streamlining
-    \item General: More CI support for submissions
-    \item Cloud/Parallel: Integrate them into the normal process
-    \item MV: Algebraic number $\implies$ non experimental
-\begin{verbatim}
-(root-of-with-ordering (coeffs p_0 p_1 ... p_n) i)
-
-(root-of-with-interval  (coeffs p_0 p_1 ... p_n) min max)
-(root-of-with-enclosure (coeffs p_0 p_1 ... p_n) min max)
-\end{verbatim}
-    Thanks for the solvers that implemented one of them!
-    \item MV: partial function more discussion needed
-    \item MV: array theory more discussion needed
+    \item<1-> General: documentation and streamlining
+    \item<2-> General: more CI support for submissions
+    \item<3-> Cloud/Parallel: (re)gain more control
+      \begin{itemize}
+        \item<4-> long term guarantee that the tracks will be held
+        \item<5-> more transparency
+        \item<6-> better communication
+      \end{itemize}
+    \item<7-> Proof \textit{validation} track:
+      \begin{itemize}
+        \item<8-> we still have to analyze the data (830gb)
+        \item<9-> ideas to turn this into a competition are welcome
+      \end{itemize}
+    \item<10-> Derived tools: how to determine their contribution compared to the tools they are derived from
+      \begin{itemize}
+        \item<11-> esp. competition wide scoring, e.g., biggest contribution
+        \item<12-> potential solution: run the tools they are derived from non-competitively and disqualify from logics if there is not a sufficient amount of improvement
+      \end{itemize}
   \end{itemize}
@@
 
-\begin{frame}{Plans for SMT-COMP 2025?}
-  \begin{itemize}
-    \item Proof \textit{validation} track
-      \begin{itemize}
-        \item We have to analyze the data still (830gb)
-        \item Ideas to turn this into a competition are welcome
-      \end{itemize}
-
-  \end{itemize}
-
-\end{frame}
+%\begin{frame}{Plans for SMT-COMP 2025?}
+%  \begin{itemize}
+%    
+%
+%  \end{itemize}
+%
+%
+%\end{frame}
 

### 2024-07-20 2024/slides/presresults/slides.tex
Updated slides for 2024

@@
 \begin{frame}[fragile]
-  \frametitle{Plans for SMT-COMP 2025?}
+  \frametitle{SMT-COMP 2024: a year of changes}
+  \begin{itemize}
+    \item Switch from StarExec to BenchExec
+    \begin{itemize}
+	    \item A big thanks to Dirk Beyer and Philipp Wendler for offering us to use the VerifierCloud and their support   
+        \item A big thanks to Aaron Stump for his StarExec support over the years
+    \end{itemize}
+    \item New submission process (pull requests)
+    \item CI support for submissions
+    \item Merge of all competition scripts into one tool
+    \begin{itemize}
+        \item enhancing their speed by orders of magnitude
+    \end{itemize}
+    \item New AWS team taking care of the cloud and parallel tracks
+    \item Proof track discontinued (for now)
+  \end{itemize}
+\end{frame}
+
+\begin{frame}[fragile]
+  \frametitle{Plans for SMT-COMP 2025}
   \begin{itemize}
@@
       \end{itemize}
-    \item<7-> Proof \textit{validation} track:
+    \item<7-> Proof track:
       \begin{itemize}
